### 2023-12-04 Code/MultiDataImportPico.Rmd
MultiDataPico moved in

---
title: "MultiDataImportTemplate"
author:
- Laurel Genge
- Carlie Barnhill
- Max Berthold
- Mireille Savoie
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Options

## Set figure caption font size

```{css, echo=FALSE}
p.caption {
  font-size: 18px;
}
```

## Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# To Do

-move filter for negative OD to point of log curve fitting Filtering
negative points needed for current noise filtering, so placed just
before noise filtering; with more sophisticated noise filtering -add
dynamic extraction of StartTime from first row of AbsTime Done

# Introduction

The PSI Multicultivator is used to grow 8 x 80 ml of phytoplankton
culture under a common temperature regime, with individual control of
bubbling, light level, light spectral quality and photoperiod for each
of the 8 culture tubes.

This .Rmd Rworkbook imports data in simple .csv long form exported from
PSI Multicultivators based upon project specific values for variables
set by the user.

It tidies and organizes the data. It uses a pivot_wider and
interpolation approach to get the Actinic_par and OD values in line
rowwise. This requires careful 'arrange' of the rows. It imports a
metadata Catalog and merges the metadata with the imported data based
upon shared values for the variables 'MC', 'Tube', and 'Filename' which
should unambiguously identify a given growth trajectory measured at
OD680 or OD720.

It generates preliminary data plots. It filters the data for outliers by
screening out values distant from the moving average of a window in the
stream; this requires careful 'arrange' of the rows so sequential rows
represent sequential time steps.

This works because the OD680 & OD720 data are only episodically, but
widely, aberrant when a bubble interrupts the measurement, and if the
MultiCultivator is running properly these bubble aberration events are
rare.

# Load Libraries and set Project Variables

```{r load libraries}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
library(knitr)
library(zoo)
library(data.table)
library(googledrive)
library(googlesheets4)

```

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..","MultiCultiData")
PlotsPath <- file.path("..","Plots")
DataOut <- file.path("..","ImportedData")
#MetaCatalog <- file.path("..","PicoCatalog.csv")

Sensor <- "od-680"

#interactively set the hour of day at which photoperiod starts for later generation of ToD Time of Day
#replaced by dynamic extraction from the first row of the AbsTime column in the datafile
#StartHour <- 7

```

```{r set colours}
MyWavelengths = c(405, 450, 475, 530, 615, 660, 730, "WW")
MCMIXColours = c("violet", "darkblue", "dodgerblue", "green","orange","red","purple", "black")

names(MCMIXColours) <- MyWavelengths
MCMIXColours

# SensorWavebands = c(680, 720)
# SensorColours = c("red", "black")
# names(SensorColours) <- SensorWavebands
# 
# SensorColours
```

# Import MetaData 
```{r load Catalog direct from googlesheet, results = "hide"}
# #implement read with googlesheet name instead of full url

gs4_deauth()

# imagine this is the URL or ID of a Sheet readable by anyone (with a link)

Catalog <- read_sheet("https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0") %>%

  # read_sheet has an annoying "feature" to set the type of columns it can't parse to a list.
  # ggplot/dplyr doesn't like working with a dataframe of lists.
  # In this case WL is set to a list since some values are numbers, some are strings, some are blank.
  # To fix this, first drop all rows missing WL, then unlist.
  # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.
  drop_na(WL) %>%
  mutate(WL = unlist(WL))

as.data.frame(Catalog)

Catalog <- Catalog %>%
   mutate(ExpDate = ymd(ExpDate),
          ExpEndDate = ymd_hms(`ExpEndDate`))

```

# List previously imported files

```{r previously imported files}
list.files(path = DataOut, pattern = Project, full.names = TRUE)
```

# List MultiCulti files

for Project that are saved in DataIn and Previously Processed Files

```{r MultiCulti files}
MultiFiles <- list.files(path = DataIn, pattern = Project, full.names = TRUE)

#check file names
MultiFiles

```

# Set Target File

Could implement function to list difference between
unique(GrowthSummaryAppend\$Filename) and MultiFiles if needed later;
scan visually to set TargetFile for now.

```{r set TargetFile}
TargetFile <- "../MultiCultiData/20230413_PICO_MCMIX004_RUN113.csv"

TargetFileName <- str_split(string = TargetFile, "/")[[1]][3] %>%
  str_remove(pattern = ".csv")

TargetFileName
```

## Create function using data.table::fread to skip the beginning comments and starts reading file after key word Skip

```{r fread_plus}
fread_plus <- function(Flnm, Skip){data.table::fread(file = Flnm, skip = Skip) %>%
    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(Flnm)$ctime))
}
```

# Read in TargetFile

select(-c(V5)) only needed for some files.

```{r Read TargetFile}
#abs-time is failing because it contains ',' in the variable values; file is actually a .tsv, not a .csv
#abs-time not currently used?
# TargetData <- fread_plus(Flnm = TargetFile, Skip = "key") %>%
# select(-c(V5))

#run this if V5 is the 'value' column
TargetData <- fread_plus(Flnm = TargetFile, Skip = "key")  %>%
   select(-c(V5))

# %>%
#  select(-c(value)) %>%
#   rename(value = V5)

TargetData[1:10,]

#check whether all necessary values for 'key' are present; people forget to 'export all' values from PSI
unique(TargetData$key)
```

```{r read in all MultiData}
# MultiData <- MultiFiles %>%
#   map_df(~fread_plus(Flnm = ., Skip = "key")) %>%
#   select(-c(V5))
# 
# MultiData[1:10,]

# MultiDataTarget <- MultiData %>%
   #filter(Filename == TargetFile)
```

```{r TargetFile actinic light NA to 0}
# TargetData <- TargetData %>%
#   mutate(value = if_else(grepl("actinic-lights", key), if_else(is.na(value), 0, value), value))

```

# Filter superfluous rows, Add ToD column, extract ExpDate, extract MC,

```{r tidy MultiDataTarget}
#filter superfluous rows to simplify later pivot
TargetData <- TargetData %>%
  # filter(key != "thermo.temperature",
  #        key !="thermo.thermo-reg",
  #        key != "mc-airpump.airpump") %>%
  filter(str_detect(key, "od-720|od-680|actinic-lights.light"))

TargetData <- TargetData %>%
  select(key, time, `abs-time`, value, Filename, CDateTime) %>%
  mutate(Tube = str_extract(key, "-[:digit:]"),
         Tube = as.numeric(str_extract(Tube, "[:digit:]")),
         abs_time = dmy_hms(`abs-time`)) %>%
  select(-`abs-time`)

#extract StartHour dynamically from first row of abs_time and display for cross check
StartHour <- as.numeric(format(TargetData$abs_time[1], format = "%H"))
StartHour

StartDate <- TargetData$abs_time[1]
StartDate

#Generate ToD as mod 24 of time + StartHour
TargetData <- TargetData %>%
  mutate(ToD = (time + StartHour) %% 24,
         Day = round((time/24), digits = 0))
#had trouble extracting 'Day' from abs_time, only got 3 unique values

#extract ExpDate for matching with Catalog
TargetData <- TargetData %>% 
    mutate(ExpDate = str_extract(Filename, "/202[:digit:][:digit:][:digit:][:digit:][:digit:]_"),
           ExpDate = ymd(str_extract(ExpDate, "202[:digit:][:digit:][:digit:][:digit:][:digit:]")))

#extract MC for matching with Catalog
#fixed to run with MC or MCMIX.
#fixed to work for RUN #'s > 100. MC extracted from filename when Runs >99 returns the MC name and RUN #, this removes '_RUN#'
TargetData <- TargetData %>% 
    mutate(MC = str_extract(Filename, "MC.*[:digit:][:digit:][:digit:]"),
           MC = str_remove(MC, pattern = "\\_.*"))

#Run this if Run number exceeds 99.  MC extracted from filename when Runs >99 returns the MC name and RUN #, this removes '_RUN#'

#add ln(value) later

```

## Create preliminary plot for TargetData

```{r prelim plot}
#Run <- c("MultiCulti/20200124_PICO_MCMIX004_RUN1.csv", "MultiCulti/20200124_PICO_MCMIX006_RUN2.csv")

# TargetDataPlotPrelim <- 
  TargetData %>%
  filter(grepl("od-", key)) %>%
  #filter(grepl("od-sensors-", key)) %>%
  ggplot(data = .) +
  geom_point(aes(x = time, y = value, colour = as.factor(str_detect(key, "680"))), size = 0.5) +
  #scale_x_continuous(breaks=seq(0, 800, by = 125)) + 
  #coord_cartesian(xlim = c(-5, 800)) +
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  scale_colour_manual(values = c("black", "red")) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", title = "Tubes") +
  facet_grid(cols = vars(as.factor(Tube))) +
  theme_bw()

# + 
#     theme(legend.position="none")

# TargetDataPlotPrelim

#cols = vars(Filename),

#, fill = if_else(str_detect(key, "680"), "red", "black")

#
```

## Save Preliminary Plot to PlotsPath folder if desired

Generates .png for later presentation if needed.

```{r save preliminary plot as .png to folder}

 # ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataPlotPrelim",".png",sep = "")), plot = TargetDataPlotPrelim, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
```

# Generate par_ue column with rows aligned with OD measures

Pivot_wider to get actinic-lights data aligned with relevant sensor
data. Why are there NULL values in the OD sensor columns? Should always
have a value? Import issue? Misalignment b/t light and OD? Need to
include arrange(Filename, time, Tube) to keep things aligned! Need to
group_by and/or reorder rows appropirately; Be Careful

```{r pivot_wider}
#possible issue with data structure; there are multiple values for some of the rows of actinic light columns, so the column becomes a list.
#Can add  values_fn = 
#to arbitrarily take the max or min etc. element of the list; but there might be a wider problem here when importing multiple files

TargetDataWide <- TargetData %>%
  pivot_wider(names_from = key, values_from = value, values_fn = list(value = max)) %>%
  arrange(Filename, MC, Tube, time)

TargetDataWide[1:10,]

rm(TargetData)
```

Actinic light values do not align time wise with OD measures.
Interpolate NA in actinic light columns from last observation, arrange
by MC & Tube Then generate Actinic_par summary column If multiple lights
are activated this chunk will give the summed par of all different
colours for the tube. If a single actinic light is activated per tube,
this gives the par for that tube. Filter rows where !is.na(Actinic_par)
to check for incorrect row sums.

Interpolation for Sine is not necessarily appropriate interpolation for
Square photoregime; issues with propagating last Actinic_par of
afternoon through evening, or back-casting first Actinic_par of morning.

Small glitching adding actinic_light values for tubes where
actinic_light column should be 0; issue with interpolation we think.

```{r interpolate and summarize actinic_par by tube}
#http://publish.illinois.edu/spencer-guerrero/2014/12/11/2-dealing-with-missing-data-in-r-omit-approx-or-spline-part-1/

#https://dplyr.tidyverse.org/dev/articles/colwise.html

#Interpolation causes problems with final rows that repeat last value.

interpolate <- function(x){zoo::na.locf(x, na.rm = FALSE, fromLast = FALSE, type = "l", maxgap = Inf)}

#possible problem with actinic_par for MC data b/c actinic-lights.light1 = NA generates actinic_par of 0 b/c in rowSums na.rm = TRUE, which treats NA as 0.
#possibly not a big problem but watch for bugs
#na.rm = FALSE fails to run
TargetDataWide <- TargetDataWide %>%
  group_by(Tube) %>%
  arrange(Filename, MC, Tube, time) %>%
  mutate(across(.cols = starts_with("actinic-lights.light"), .fns = interpolate)) %>%
  ungroup() %>%
  mutate(Actinic_par = rowSums(.[grep("actinic-lights.light", names(.))], na.rm = TRUE)) %>%
  filter(!is.na(Actinic_par)) %>%
   select(!contains("actinic-lights.light"))

#drop original actinic light columns?
# select(!contains("actinic-lights.light"))

TargetDataWide[1:10,]
```

Now that Actinic_par is aligned with each row, coalesce
od-sensors-X.od-720 and od-sensors-X.od-680 into 2 columns, b/c 'Tube'
is already a column, so no need to identify tube X in
od-sensors-X.od-680 columns. This might cause problems later matching OD
measures to actinic light colours. Filter out rows where OD \<= 0

```{r consolidate OD}
TargetDataWide <- TargetDataWide  %>%
   mutate(OD680 = rowSums(.[grep("od-680", names(.))], na.rm = TRUE),
          OD720 = rowSums(.[grep("od-720", names(.))], na.rm = TRUE)) %>%
   select(!contains("od-sensors"))
  # filter(OD680 > 0,
  #        OD720 > 0

#move filtering for OD680 >0 until just before curve fitting to avoid data structure problems
TargetDataWide[1:10,]

```

# Merge Data with meta data

```{r metadata merge}
#This generates 'NA' values for ~1,000,000 rows of 'O2'; possibly the temperature rows?
TargetDataMeta <- left_join(x = TargetDataWide, y= Catalog, by = c("ExpDate", "MC", "Tube"), suffix  = c("_multi", "_cat"))

TargetDataMeta

rm(TargetDataWide)
```

```{r second prelim plot}
#TargetDataPlotFacet <- 
  TargetDataMeta %>% ggplot() +
  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.15) +
  geom_point(aes(x = time, y = OD720), size = 0.15, colour = "orange") +
  #geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  #scale_x_continuous(breaks=seq(0, 800, by = 125)) +
  #coord_cartesian(xlim = c(-10, 800)) +
  scale_colour_manual(values = MCMIXColours) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
  facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, ID)) +
  theme_bw() +  
  labs(colour = "Actinic PAR (nm)")

#TargetDataPlotFacet

```

Run this chunk only for tubes with OD680 and/or OD720 < 0
This will keep record of tubes even if they did not grow or had negative growth. These tubes get filtered out later if you do not run this chunk
Remember to comment out after use 
```{r, Add dummy points if a tube has OD values less than zero}

# TargetDataMeta <- TargetDataMeta %>%
# mutate(OD680 = if_else(Tube == 1, 0.005, OD680),
#        OD720 = if_else(Tube == 1, 0.003, OD720))

```

Run this chunk if some tubes have poor data
This is bad practice;
Only use if light recordings were actually wrong
Consider a rule-based filtering to eliminate points after curve reaches peak
```{r filter aberrant tube(s)}
# TargetDataMeta <- TargetDataMeta %>%
#   filter(Tube != 1) %>%
#   filter(Tube != 8)
# 
# TargetDataMeta5 <- TargetDataMeta %>%
#   filter(Tube == 5,
#          time <= 300)
# 
# TargetDataMeta <- TargetDataMeta %>%
#   filter(Tube != 5) %>%
#   rbind(., TargetDataMeta5)
# 
# TargetDataMeta %>% ggplot() +
#   geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
#   geom_point(aes(x = time, y = OD720), size = 0.01, alpha = 0.1, colour = "black") +
#   geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
#   geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
#   geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
#   #scale_x_continuous(breaks=seq(0, 800, by = 125)) +
#   #coord_cartesian(xlim = c(-10, 800)) +
#   #scale_colour_manual(values = MCMIXColours) +
#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
#   facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, ID)) +
#   theme_bw() +  
#   labs(colour = "Actinic PAR (nm)")

```

## Save second preliminary plot if desired

```{r save second preliminary plot as .png to folder}

 # ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataPlotFacet",".png",sep = "")), plot = TargetDataPlotFacet, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
```

# Filter OD outliers

Rewrite with Time Series tools?? Filtering messes up unless - values
removed b/c of divisions

Experiment end times are tube specific taken from metacatalog
StartDate taken from first abs_time point from MC software

MAD is median absolute deviation Used median as opposed to mean to filter anomalous OD values due to affects of bubbling interference because determining outliers from the mean in a given window with many outliers were not detected since deviations from the mean were low. 
```{r filter bad OD and data points after experiment end time }

#moving average screen
MovAvgScreen <- 6
MovAvgWindow <- 20

TargetDataMetaFilter <- TargetDataMeta %>%
  filter(OD680 > 0) %>% # consider this rule for OD720 as well
  group_by(ID) %>%
  arrange(Filename, MC, Tube, time) %>%
  mutate(ExpEndHour = (difftime(ExpEndDate, StartDate, units = "hours"))) %>%
   mutate(TimeFlag = case_when(time >= ExpEndHour  ~ 1, 
                              time < ExpEndHour ~ 0)) %>%
  mutate(MovMedian680 = rollapply(OD680, MovAvgWindow, median, fill = "extend",  align = "left"),
         MovMedian720 = rollapply(OD720, MovAvgWindow, median, fill = "extend",  align = "left"),
         MovMAD680 = rollapply(OD680, MovAvgWindow, mad, fill = "extend",  align = "left"), 
         MovMAD720 = rollapply(OD720, MovAvgWindow, mad, fill = "extend",  align = "left"), 
         IsMovMAD680Outlier = if_else(OD680 > MovMedian680 + (MovMAD680 * MovAvgScreen) | OD680 < MovMedian680 - (MovMAD680 * MovAvgScreen), 1,0),
         IsMovMAD720Outlier = if_else(OD720 > MovMedian720 + (MovMAD720 * MovAvgScreen) | OD720 < MovMedian720 - (MovMAD720 * MovAvgScreen), 1,0))

         # OD680 = if_else(OD680 > MovMedian680 + (MovMAD680 * MovAvgScreen) | OD680 < MovMedian680 - (MovMAD680 * MovAvgScreen), MovMedian680, OD680), #consider replacing OD680 and OD720 rather than filter
         # OD720 = if_else(OD720 > MovMedian720 + (MovMAD720 * MovAvgScreen) | OD720 < MovMedian720 - (MovMAD720 * MovAvgScreen), MovMedian720, OD720)

print(paste("Outliers caught by IsMovMAD680Outlier filter:",
            sum(TargetDataMetaFilter$IsMovMAD680Outlier, na.rm = TRUE)))
print(paste("Outliers caught by IsMovMAD720Outlier filter:",
            sum(TargetDataMetaFilter$IsMovMAD720Outlier, na.rm = TRUE)))

TargetDataMetaFilter <- TargetDataMetaFilter %>%
  filter(
    !is.na(IsMovMAD680Outlier),
    !is.na(IsMovMAD720Outlier),
    IsMovMAD680Outlier == 0,
    IsMovMAD720Outlier == 0
         )%>%
    filter(TimeFlag == 0)

# "actinic-lights.light"

#rm(TargetDataMeta)
```

```{r filterdataplot}

TargetDataMetaFilterPlot <- TargetDataMetaFilter %>% 
  ggplot() +
  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.15) +
  geom_point(aes(x = time, y = OD720), size = 0.15, colour = "orange") +
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  #geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
 # geom_point(aes(x = time, y = IsMovAvgOutlier680)) +
#scale_x_continuous(limits = c(0,100))+
  #scale_x_continuous(breaks=seq(0, 800, by = 125)) +
  #coord_cartesian(xlim = c(-10, 800)) +
  scale_colour_manual(values = MCMIXColours) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
 facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, ID)) +
  theme_bw() +  
  labs(colour = "Actinic PAR (nm)")

TargetDataMetaFilterPlot
```

Supplementary Growth Plot
```{r, fig.height = 6, fig.width = 4}

# ExpandTube = 1
# OD680_x = median(TargetDataMetaFilter$time)
# OD720_x = median(TargetDataMetaFilter$time)
# OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 0.2
# OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD720))
# TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>%
#   filter(Tube == ExpandTube) %>%
#   ggplot() +
#   geom_point(aes(x = time, y = OD680), colour = "darkgreen", size = 0.1) +
#   geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
#   scale_y_continuous(breaks=seq(0, 1.0, by = 0.2)) +
#   coord_cartesian(ylim = c(0, 1.0)) +
#   scale_colour_manual(values = MCMIXColours) +
#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)") +
#   ggh4x::facet_nested(rows = vars(WL), cols = vars(Strain, Par_ue), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_both)) +
#   theme_bw()
# TargetDataMetaFilterExpandPlot
# 
# 
# 
# Par_ue.labs <- c("Growth Light Intensity: 60 µE")
# names(Par_ue.labs) <- c("60")
# WL.labs <- c("Growth Color Light: 660 nm")
# names(WL.labs) <- c("660")
# ExpandTube = 1
# OD680_x = median(TargetDataMetaFilter$time)
# OD720_x = median(TargetDataMetaFilter$time)
# OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 0.2
# OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD720))
# TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>%
#   filter(Tube == ExpandTube) %>%
#   ggplot() +
#   geom_point(aes(x = time, y = OD680), colour = "darkgreen", size = 0.1) +
#   geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
#   scale_y_continuous(breaks=seq(0, 1.0, by = 0.2)) +
#   coord_cartesian(ylim = c(0, 1.0)) +
#   scale_colour_manual(values = MCMIXColours) +
#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)") +
#   ggh4x::facet_nested(cols = vars(Strain, WL, Par_ue), labeller = labeller(strain = label_value, Photoperiod = label_both, Par_ue = Par_ue.labs, WL = WL.labs)) +
#   # annotate(geom = "text", x = OD680_x, y = OD680_y, label = ""~OD[680]~"", size = 4.5, colour = "darkgreen", vjust = -14.5, hjust = 2.5) +
#   # annotate(geom = "text", x = OD720_x, y = OD720_y, label = ""~OD[720]~"", size = 4.5, colour = "blue", vjust = -20, hjust = 2.5) +
# theme_bw() +
# theme(strip.text.x = element_text(size = 12),
#       strip.text.y = element_text(size = 12),
#       #strip.background = element_rect(color="black", size=0.5, linetype="solid"),
#       axis.text = element_text(size = 12),
#       axis.title = element_text(size = 12))
# 
# # theme(strip.background = element_rect(color="black", size=1.5, linetype="solid"))
# 
# TargetDataMetaFilterExpandPlot
# # grob <- grobTree(textGrob("Scatter plot", x=0.1,  y=0.95, hjust=0,
# #   gp=gpar(col="red", fontsize=13, fontface="italic")))
# #annotation_custom(grob)+facet_wrap(~cyl, scales="free")
# 
# 
# 
# #labelling dynamically offset from data traces.
# #use 'median' for 'x' and OD680 + offset for 'y'
# ExpandTube = 1
# OD680_x = median(TargetDataMetaFilter$time)
# OD720_x = median(TargetDataMetaFilter$time) 
# Light_x = max(TargetDataMetaFilter$time) - 200
# 
# OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 0.2
# 
# OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD720))
# 
# Light_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select( Actinic_par))/1000 + 0.1
# 
# TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>% 
#   filter(Tube == ExpandTube) %>%
#   ggplot() +
#   geom_point(aes(x = time, y = OD680), size = 0.1, colour = "darkgreen") +
#   geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
#   scale_y_continuous(breaks=seq(0, 1.0, by = 0.2)) +
#   coord_cartesian(ylim = c(0, 1.0)) +
#   
#   # scale_x_continuous(breaks=seq(0, 250, by = 50)) +
#   # coord_cartesian(xlim = c(0, 250)) +
#   
#   scale_colour_manual(values = MCMIXColours) +
#   geom_point(aes(x = time, y = Actinic_par/1000), colour = "orange",  size = 0.0001) +
#   #geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
#   #geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
#   # scale_x_continuous(breaks=seq(0, 800, by = 125)) +
#   # coord_cartesian(xlim = c(0, 800)) +
#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)") +
#   #facet_grid(rows = vars(O2), cols = vars(Tube, Par_ue, Strain, ID)) +
#   ggh4x::facet_nested(cols = vars(Strain, WL, Par_ue), labeller = labeller(strain = label_value, Photoperiod = label_both, Par_ue = Par_ue.labs, WL = WL.labs)) +
#   #annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkgreen") +
#   #annotate(geom = "text", x = OD720_x, y = OD720_y, label = "OD720", size = 5, colour = "blue") +
#   #annotate(geom = "text", x = Light_x, y = Light_y, label = "Light level", size = 5, colour = "orange") +
#   theme_bw() +
#   theme(strip.text.x = element_text(size = 12),
#       strip.text.y = element_text(size = 12),
#       axis.text = element_text(size = 12),
#       axis.title = element_text(size = 12))
#   labs(colour = "Actinic PAR (nm)")
# 
# TargetDataMetaFilterExpandPlot

```

```{r filterdataplotexpand}
#labelling dynamically offset from data traces.
#use 'median' for 'x' and OD680 + offset for 'y'
ExpandTube = 1
OD680_x = median(TargetDataMetaFilter$time)
OD720_x = median(TargetDataMetaFilter$time) 
Light_x = max(TargetDataMetaFilter$time) + 100

OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 0.2

OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD720))

Light_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select( Actinic_par))/1000 + 0.1

TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>% 
  filter(Tube == ExpandTube) %>%
  ggplot() +
  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
  geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = time, y = Actinic_par/1000), colour = "orange",  size = 0.0001) +
   geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  # scale_x_continuous(breaks=seq(0, 800, by = 125)) +
  # coord_cartesian(xlim = c(0, 800)) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; ID; Tube") +
  facet_grid(rows = vars(O2), cols = vars(Tube, Par_ue, Strain, ID)) +
  annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkblue") +
  annotate(geom = "text", x = OD720_x, y = OD720_y, label = "OD720", size = 5, colour = "black") +
  annotate(geom = "text", x = Light_x, y = Light_y, label = "Light level", size = 5, colour = "orange") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

TargetDataMetaFilterExpandPlot

# TargetDataPlotFacet <- TargetDataMeta %>% ggplot() +
#   geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
#   geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
#   scale_x_continuous(breaks=seq(0, 800, by = 125)) +
#   scale_colour_manual(values = MCMIXColours) +
#   labs(y = "Optical Density 680nm (OD680)", x = "Elapsed Time (h)") +
#   facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Par_ue),Strain, as.factor(Tube))) +
#   theme_bw() +  
#   labs(colour = "Actinic PAR (nm)")

```

## Save filtered preliminary plot if desired

```{r save filtered preliminary plot as .png to folder}
# 
#  ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataMetaFilterPlot",".png",sep = "")), plot = TargetDataMetaFilterPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
# # 
#  ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataMetaFilterExpandPlot",".png",sep = "")), plot = TargetDataMetaFilterExpandPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
```

```{r DailyPAR}
TargetDataMetaFilter <- TargetDataMetaFilter %>%
  mutate(SetActinic_day = case_when(LightShape == 'Sine' ~ Par_ue/2 * 3600 * Photoperiod,
                                  LightShape == 'Square' ~ Par_ue * 3600 * Photoperiod))

```

Implement Daily Cumulative PAR for Corrected Actinic by numeric integration

```{r Actinic_parOD}
#generate corrected values of Actinic_par accounting for OD
#correction assumes true 100% transmission through Tube + Media + Waterbath;  we could account for the 'background' OD as well if needed
#correction assumes that OD is attributable solely to change in culture suspension
#correction does not account for different absorbance of different incident light coloures
TargetDataMetaFilter <- TargetDataMetaFilter %>%
  mutate(ActinicMin_parOD680 = Actinic_par * (10^-OD680),
         ActinicMid_parOD680 = Actinic_par * (10^-(OD680*0.5)),
         ActinicMin_parOD720 = Actinic_par * (10^-OD720),
         ActinicMid_parOD720 = Actinic_par * (10^-(OD720*0.5)))

#generate daily photon dose umol photon m-2 d-1 after accounting for attenuation
TargetDataMetaFilter <- TargetDataMetaFilter %>%
  group_by(MC, Tube, Day) %>%
  mutate(ActinicMid_intervalOD720 = ActinicMid_parOD720 * ((time - dplyr::lag(time)) * 3600),
         ActinicMid_dayOD720 = sum(ActinicMid_intervalOD720, na.rm = TRUE))

```

```{r filterdataplotexpandActinicMid_parOD720}
#labelling dynamically offset from data traces.
#use 'median' for 'x' and OD680 + offset for 'y'
ExpandTube = 5
OD680_x = median(TargetDataMetaFilter$time)
OD720_x = median(TargetDataMetaFilter$time) + 100
Light_x = max(TargetDataMetaFilter$time) + 72

OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 2.2

OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD720_x) %>% select(OD720)) + 1.1

Light_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select( Actinic_par))/1000 + 0.15

TargetDataMetaFilter %>% 
  filter(Tube == ExpandTube) %>%
  ggplot() +
  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
  geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "black") +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = time, y = ActinicMid_parOD720/100), colour = "orange",  size = 0.0001) +
  geom_point(aes(x = time, y = ActinicMid_dayOD720/100000), colour = "red",  size = 0.0001) +
  scale_x_continuous(breaks=seq(0, 400, by = 125)) +
  coord_cartesian(xlim = c(0, 400)) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; ID; Tube") +
  facet_grid(rows = vars(O2), cols = vars(Par_ue, Strain, ID, Tube)) +
  annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkblue") +
  annotate(geom = "text", x = OD720_x, y = OD720_y, label = "OD720", size = 5, colour = "black") +
  annotate(geom = "text", x = Light_x, y = Light_y, label = "Light level", size = 5, colour = "orange") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+ 
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

```

# Save .Rds of Imported Data from TargetFile

```{r save Rds of imported data}
saveRDS(object = TargetDataMetaFilter, file = file.path(DataOut, paste(TargetFileName, "TargetDataMetaFilter.Rds",  sep = "_")), ascii = FALSE, version = NULL,
        compress = TRUE, refhook = NULL)
```

### 2023-12-04 Code/MetaDataImport.Rmd
created rmd to read and filter culture catalog and save as .Rds

--- 2023-12-04 Code/MultiDataImportPico.Rmd
@@
 ---
-title: "MultiDataImportTemplate"
+title: "MetaDataImport"
 author:
-- Laurel Genge
-- Carlie Barnhill
-- Max Berthold
 - Mireille Savoie
@@
 
-# To Do
-
--move filter for negative OD to point of log curve fitting Filtering
-negative points needed for current noise filtering, so placed just
-before noise filtering; with more sophisticated noise filtering -add
-dynamic extraction of StartTime from first row of AbsTime Done
-
 # Introduction
 
-The PSI Multicultivator is used to grow 8 x 80 ml of phytoplankton
-culture under a common temperature regime, with individual control of
-bubbling, light level, light spectral quality and photoperiod for each
-of the 8 culture tubes.
-
-This .Rmd Rworkbook imports data in simple .csv long form exported from
-PSI Multicultivators based upon project specific values for variables
-set by the user.
-
-It tidies and organizes the data. It uses a pivot_wider and
-interpolation approach to get the Actinic_par and OD values in line
-rowwise. This requires careful 'arrange' of the rows. It imports a
-metadata Catalog and merges the metadata with the imported data based
-upon shared values for the variables 'MC', 'Tube', and 'Filename' which
-should unambiguously identify a given growth trajectory measured at
-OD680 or OD720.
-
-It generates preliminary data plots. It filters the data for outliers by
-screening out values distant from the moving average of a window in the
-stream; this requires careful 'arrange' of the rows so sequential rows
-represent sequential time steps.
-
-This works because the OD680 & OD720 data are only episodically, but
-widely, aberrant when a bubble interrupts the measurement, and if the
-MultiCultivator is running properly these bubble aberration events are
-rare.
+This RMD imports culture meta data from a google sheet.
 
@@
 library(lubridate)
-library(broom)
 library(knitr)
-library(zoo)
 library(data.table)
@@
 Project <- "PICO"
-DataIn <- file.path("..","MultiCultiData")
-PlotsPath <- file.path("..","Plots")
-DataOut <- file.path("..","ImportedData")
-#MetaCatalog <- file.path("..","PicoCatalog.csv")
+DataOut <- file.path("..","Data")
 
-Sensor <- "od-680"
-
-#interactively set the hour of day at which photoperiod starts for later generation of ToD Time of Day
-#replaced by dynamic extraction from the first row of the AbsTime column in the datafile
-#StartHour <- 7
-
-```
-
-```{r set colours}
-MyWavelengths = c(405, 450, 475, 530, 615, 660, 730, "WW")
-MCMIXColours = c("violet", "darkblue", "dodgerblue", "green","orange","red","purple", "black")
-
-names(MCMIXColours) <- MyWavelengths
-MCMIXColours
-
-# SensorWavebands = c(680, 720)
-# SensorColours = c("red", "black")
-# names(SensorColours) <- SensorWavebands
-# 
-# SensorColours
 ```
@@
 
-# imagine this is the URL or ID of a Sheet readable by anyone (with a link)
+# this is the URL or ID of a Sheet readable by anyone (with a link)
 
-Catalog <- read_sheet("https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0") %>%
+CultureCatalog <- read_sheet("https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0") %>%
 
@@
   drop_na(WL) %>%
-  mutate(WL = unlist(WL))
+  mutate(WL = unlist(WL)) %>%
+   mutate(ExpDate = ymd(ExpDate),
+          ExpEndDate = ymd_hms(`ExpEndDate`)) %>% 
+  filter(str_detect(ID,  "MiSa|JuNa|SaAr")) %>% 
+  select(c("PrimaryOperator", "SampleID", "ID", "Strain", "ExpCul", "ExpDate", "ExpStartTime", "Par_ue", "Photoperiod", "Temp_c", "MC", "Tube", "EndDate","O2", "O2_Category", "WL","LightShape", "Optode","OptodeCh","OptodeMeasure", "ExpEndDate"))
 
-as.data.frame(Catalog)
-
-Catalog <- Catalog %>%
-   mutate(ExpDate = ymd(ExpDate),
-          ExpEndDate = ymd_hms(`ExpEndDate`))
+saveRDS(object = CultureCatalog, file = file.path("..", "Data", "CultureCatalog.Rds"))
 
 ```
-
-# List previously imported files
-
-```{r previously imported files}
-list.files(path = DataOut, pattern = Project, full.names = TRUE)
-```
-
-# List MultiCulti files
-
-for Project that are saved in DataIn and Previously Processed Files
-
-```{r MultiCulti files}
-MultiFiles <- list.files(path = DataIn, pattern = Project, full.names = TRUE)
-
-#check file names
-MultiFiles
-
-```
-
-# Set Target File
-
-Could implement function to list difference between
-unique(GrowthSummaryAppend\$Filename) and MultiFiles if needed later;
-scan visually to set TargetFile for now.
-
-```{r set TargetFile}
-TargetFile <- "../MultiCultiData/20230413_PICO_MCMIX004_RUN113.csv"
-
-TargetFileName <- str_split(string = TargetFile, "/")[[1]][3] %>%
-  str_remove(pattern = ".csv")
-
-TargetFileName
-```
-
-## Create function using data.table::fread to skip the beginning comments and starts reading file after key word Skip
-
-```{r fread_plus}
-fread_plus <- function(Flnm, Skip){data.table::fread(file = Flnm, skip = Skip) %>%
-    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(Flnm)$ctime))
-}
-```
-
-# Read in TargetFile
-
-select(-c(V5)) only needed for some files.
-
-```{r Read TargetFile}
-#abs-time is failing because it contains ',' in the variable values; file is actually a .tsv, not a .csv
-#abs-time not currently used?
-# TargetData <- fread_plus(Flnm = TargetFile, Skip = "key") %>%
-# select(-c(V5))
-
-#run this if V5 is the 'value' column
-TargetData <- fread_plus(Flnm = TargetFile, Skip = "key")  %>%
-   select(-c(V5))
-
-# %>%
-#  select(-c(value)) %>%
-#   rename(value = V5)
-
-TargetData[1:10,]
-
-#check whether all necessary values for 'key' are present; people forget to 'export all' values from PSI
-unique(TargetData$key)
-```
-
-```{r read in all MultiData}
-# MultiData <- MultiFiles %>%
-#   map_df(~fread_plus(Flnm = ., Skip = "key")) %>%
-#   select(-c(V5))
-# 
-# MultiData[1:10,]
-
-# MultiDataTarget <- MultiData %>%
-   #filter(Filename == TargetFile)
-```
-
-```{r TargetFile actinic light NA to 0}
-# TargetData <- TargetData %>%
-#   mutate(value = if_else(grepl("actinic-lights", key), if_else(is.na(value), 0, value), value))
-
-```
-
-# Filter superfluous rows, Add ToD column, extract ExpDate, extract MC,
-
-```{r tidy MultiDataTarget}
-#filter superfluous rows to simplify later pivot
-TargetData <- TargetData %>%
-  # filter(key != "thermo.temperature",
-  #        key !="thermo.thermo-reg",
-  #        key != "mc-airpump.airpump") %>%
-  filter(str_detect(key, "od-720|od-680|actinic-lights.light"))
-
-TargetData <- TargetData %>%
-  select(key, time, `abs-time`, value, Filename, CDateTime) %>%
-  mutate(Tube = str_extract(key, "-[:digit:]"),
-         Tube = as.numeric(str_extract(Tube, "[:digit:]")),
-         abs_time = dmy_hms(`abs-time`)) %>%
-  select(-`abs-time`)
-
-#extract StartHour dynamically from first row of abs_time and display for cross check
-StartHour <- as.numeric(format(TargetData$abs_time[1], format = "%H"))
-StartHour
-
-StartDate <- TargetData$abs_time[1]
-StartDate
-
-#Generate ToD as mod 24 of time + StartHour
-TargetData <- TargetData %>%
-  mutate(ToD = (time + StartHour) %% 24,
-         Day = round((time/24), digits = 0))
-#had trouble extracting 'Day' from abs_time, only got 3 unique values
-
-#extract ExpDate for matching with Catalog
-TargetData <- TargetData %>% 
-    mutate(ExpDate = str_extract(Filename, "/202[:digit:][:digit:][:digit:][:digit:][:digit:]_"),
-           ExpDate = ymd(str_extract(ExpDate, "202[:digit:][:digit:][:digit:][:digit:][:digit:]")))
-
-#extract MC for matching with Catalog
-#fixed to run with MC or MCMIX.
-#fixed to work for RUN #'s > 100. MC extracted from filename when Runs >99 returns the MC name and RUN #, this removes '_RUN#'
-TargetData <- TargetData %>% 
-    mutate(MC = str_extract(Filename, "MC.*[:digit:][:digit:][:digit:]"),
-           MC = str_remove(MC, pattern = "\\_.*"))
-
-#Run this if Run number exceeds 99.  MC extracted from filename when Runs >99 returns the MC name and RUN #, this removes '_RUN#'
-
-#add ln(value) later
-
-```
-
-## Create preliminary plot for TargetData
-
-```{r prelim plot}
-#Run <- c("MultiCulti/20200124_PICO_MCMIX004_RUN1.csv", "MultiCulti/20200124_PICO_MCMIX006_RUN2.csv")
-
-# TargetDataPlotPrelim <- 
-  TargetData %>%
-  filter(grepl("od-", key)) %>%
-  #filter(grepl("od-sensors-", key)) %>%
-  ggplot(data = .) +
-  geom_point(aes(x = time, y = value, colour = as.factor(str_detect(key, "680"))), size = 0.5) +
-  #scale_x_continuous(breaks=seq(0, 800, by = 125)) + 
-  #coord_cartesian(xlim = c(-5, 800)) +
-  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
-  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
-  scale_colour_manual(values = c("black", "red")) +
-  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", title = "Tubes") +
-  facet_grid(cols = vars(as.factor(Tube))) +
-  theme_bw()
-
-# + 
-#     theme(legend.position="none")
-
-# TargetDataPlotPrelim
-
-#cols = vars(Filename),
-
-#, fill = if_else(str_detect(key, "680"), "red", "black")
-
-#
-```
-
-## Save Preliminary Plot to PlotsPath folder if desired
-
-Generates .png for later presentation if needed.
-
-```{r save preliminary plot as .png to folder}
-
- # ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataPlotPrelim",".png",sep = "")), plot = TargetDataPlotPrelim, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
-```
-
-# Generate par_ue column with rows aligned with OD measures
-
-Pivot_wider to get actinic-lights data aligned with relevant sensor
-data. Why are there NULL values in the OD sensor columns? Should always
-have a value? Import issue? Misalignment b/t light and OD? Need to
-include arrange(Filename, time, Tube) to keep things aligned! Need to
-group_by and/or reorder rows appropirately; Be Careful
-
-```{r pivot_wider}
-#possible issue with data structure; there are multiple values for some of the rows of actinic light columns, so the column becomes a list.
-#Can add  values_fn = 
-#to arbitrarily take the max or min etc. element of the list; but there might be a wider problem here when importing multiple files
-
-TargetDataWide <- TargetData %>%
-  pivot_wider(names_from = key, values_from = value, values_fn = list(value = max)) %>%
-  arrange(Filename, MC, Tube, time)
-
-TargetDataWide[1:10,]
-
-rm(TargetData)
-```
-
-Actinic light values do not align time wise with OD measures.
-Interpolate NA in actinic light columns from last observation, arrange
-by MC & Tube Then generate Actinic_par summary column If multiple lights
-are activated this chunk will give the summed par of all different
-colours for the tube. If a single actinic light is activated per tube,
-this gives the par for that tube. Filter rows where !is.na(Actinic_par)
-to check for incorrect row sums.
-
-Interpolation for Sine is not necessarily appropriate interpolation for
-Square photoregime; issues with propagating last Actinic_par of
-afternoon through evening, or back-casting first Actinic_par of morning.
-
-Small glitching adding actinic_light values for tubes where
-actinic_light column should be 0; issue with interpolation we think.
-
-```{r interpolate and summarize actinic_par by tube}
-#http://publish.illinois.edu/spencer-guerrero/2014/12/11/2-dealing-with-missing-data-in-r-omit-approx-or-spline-part-1/
-
-#https://dplyr.tidyverse.org/dev/articles/colwise.html
-
-#Interpolation causes problems with final rows that repeat last value.
-
-interpolate <- function(x){zoo::na.locf(x, na.rm = FALSE, fromLast = FALSE, type = "l", maxgap = Inf)}
-
-#possible problem with actinic_par for MC data b/c actinic-lights.light1 = NA generates actinic_par of 0 b/c in rowSums na.rm = TRUE, which treats NA as 0.
-#possibly not a big problem but watch for bugs
-#na.rm = FALSE fails to run
-TargetDataWide <- TargetDataWide %>%
-  group_by(Tube) %>%
-  arrange(Filename, MC, Tube, time) %>%
-  mutate(across(.cols = starts_with("actinic-lights.light"), .fns = interpolate)) %>%
-  ungroup() %>%
-  mutate(Actinic_par = rowSums(.[grep("actinic-lights.light", names(.))], na.rm = TRUE)) %>%
-  filter(!is.na(Actinic_par)) %>%
-   select(!contains("actinic-lights.light"))
-
-#drop original actinic light columns?
-# select(!contains("actinic-lights.light"))
-
-TargetDataWide[1:10,]
-```
-
-Now that Actinic_par is aligned with each row, coalesce
-od-sensors-X.od-720 and od-sensors-X.od-680 into 2 columns, b/c 'Tube'
-is already a column, so no need to identify tube X in
-od-sensors-X.od-680 columns. This might cause problems later matching OD
-measures to actinic light colours. Filter out rows where OD \<= 0
-
-```{r consolidate OD}
-TargetDataWide <- TargetDataWide  %>%
-   mutate(OD680 = rowSums(.[grep("od-680", names(.))], na.rm = TRUE),
-          OD720 = rowSums(.[grep("od-720", names(.))], na.rm = TRUE)) %>%
-   select(!contains("od-sensors"))
-  # filter(OD680 > 0,
-  #        OD720 > 0
-
-#move filtering for OD680 >0 until just before curve fitting to avoid data structure problems
-TargetDataWide[1:10,]
-
-```
-
-# Merge Data with meta data
-
-```{r metadata merge}
-#This generates 'NA' values for ~1,000,000 rows of 'O2'; possibly the temperature rows?
-TargetDataMeta <- left_join(x = TargetDataWide, y= Catalog, by = c("ExpDate", "MC", "Tube"), suffix  = c("_multi", "_cat"))
-
-TargetDataMeta
-
-rm(TargetDataWide)
-```
-
-```{r second prelim plot}
-#TargetDataPlotFacet <- 
-  TargetDataMeta %>% ggplot() +
-  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.15) +
-  geom_point(aes(x = time, y = OD720), size = 0.15, colour = "orange") +
-  #geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
-  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
-  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
-  #scale_x_continuous(breaks=seq(0, 800, by = 125)) +
-  #coord_cartesian(xlim = c(-10, 800)) +
-  scale_colour_manual(values = MCMIXColours) +
-  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
-  facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, ID)) +
-  theme_bw() +  
-  labs(colour = "Actinic PAR (nm)")
-
-#TargetDataPlotFacet
-
-```
-
-Run this chunk only for tubes with OD680 and/or OD720 < 0
-This will keep record of tubes even if they did not grow or had negative growth. These tubes get filtered out later if you do not run this chunk
-Remember to comment out after use 
-```{r, Add dummy points if a tube has OD values less than zero}
-
-# TargetDataMeta <- TargetDataMeta %>%
-# mutate(OD680 = if_else(Tube == 1, 0.005, OD680),
-#        OD720 = if_else(Tube == 1, 0.003, OD720))
-
-```
-
-Run this chunk if some tubes have poor data
-This is bad practice;
-Only use if light recordings were actually wrong
-Consider a rule-based filtering to eliminate points after curve reaches peak
-```{r filter aberrant tube(s)}
-# TargetDataMeta <- TargetDataMeta %>%
-#   filter(Tube != 1) %>%
-#   filter(Tube != 8)
-# 
-# TargetDataMeta5 <- TargetDataMeta %>%
-#   filter(Tube == 5,
-#          time <= 300)
-# 
-# TargetDataMeta <- TargetDataMeta %>%
-#   filter(Tube != 5) %>%
-#   rbind(., TargetDataMeta5)
-# 
-# TargetDataMeta %>% ggplot() +
-#   geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
-#   geom_point(aes(x = time, y = OD720), size = 0.01, alpha = 0.1, colour = "black") +
-#   geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
-#   geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
-#   geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
-#   #scale_x_continuous(breaks=seq(0, 800, by = 125)) +
-#   #coord_cartesian(xlim = c(-10, 800)) +
-#   #scale_colour_manual(values = MCMIXColours) +
-#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
-#   facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, ID)) +
-#   theme_bw() +  
-#   labs(colour = "Actinic PAR (nm)")
-
-```
-
-## Save second preliminary plot if desired
-
-```{r save second preliminary plot as .png to folder}
-
- # ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataPlotFacet",".png",sep = "")), plot = TargetDataPlotFacet, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
-```
-
-# Filter OD outliers
-
-Rewrite with Time Series tools?? Filtering messes up unless - values
-removed b/c of divisions
-
-Experiment end times are tube specific taken from metacatalog
-StartDate taken from first abs_time point from MC software
-
-MAD is median absolute deviation Used median as opposed to mean to filter anomalous OD values due to affects of bubbling interference because determining outliers from the mean in a given window with many outliers were not detected since deviations from the mean were low.
-```{r filter bad OD and data points after experiment end time }
-
-#moving average screen
-MovAvgScreen <- 6
-MovAvgWindow <- 20
-
-TargetDataMetaFilter <- TargetDataMeta %>%
-  filter(OD680 > 0) %>% # consider this rule for OD720 as well
-  group_by(ID) %>%
-  arrange(Filename, MC, Tube, time) %>%
-  mutate(ExpEndHour = (difftime(ExpEndDate, StartDate, units = "hours"))) %>%
-   mutate(TimeFlag = case_when(time >= ExpEndHour  ~ 1, 
-                              time < ExpEndHour ~ 0)) %>%
-  mutate(MovMedian680 = rollapply(OD680, MovAvgWindow, median, fill = "extend",  align = "left"),
-         MovMedian720 = rollapply(OD720, MovAvgWindow, median, fill = "extend",  align = "left"),
-         MovMAD680 = rollapply(OD680, MovAvgWindow, mad, fill = "extend",  align = "left"), 
-         MovMAD720 = rollapply(OD720, MovAvgWindow, mad, fill = "extend",  align = "left"), 
-         IsMovMAD680Outlier = if_else(OD680 > MovMedian680 + (MovMAD680 * MovAvgScreen) | OD680 < MovMedian680 - (MovMAD680 * MovAvgScreen), 1,0),
-         IsMovMAD720Outlier = if_else(OD720 > MovMedian720 + (MovMAD720 * MovAvgScreen) | OD720 < MovMedian720 - (MovMAD720 * MovAvgScreen), 1,0))
-
-         # OD680 = if_else(OD680 > MovMedian680 + (MovMAD680 * MovAvgScreen) | OD680 < MovMedian680 - (MovMAD680 * MovAvgScreen), MovMedian680, OD680), #consider replacing OD680 and OD720 rather than filter
-         # OD720 = if_else(OD720 > MovMedian720 + (MovMAD720 * MovAvgScreen) | OD720 < MovMedian720 - (MovMAD720 * MovAvgScreen), MovMedian720, OD720)
-
-print(paste("Outliers caught by IsMovMAD680Outlier filter:",
-            sum(TargetDataMetaFilter$IsMovMAD680Outlier, na.rm = TRUE)))
-print(paste("Outliers caught by IsMovMAD720Outlier filter:",
-            sum(TargetDataMetaFilter$IsMovMAD720Outlier, na.rm = TRUE)))
-
-TargetDataMetaFilter <- TargetDataMetaFilter %>%
-  filter(
-    !is.na(IsMovMAD680Outlier),
-    !is.na(IsMovMAD720Outlier),
-    IsMovMAD680Outlier == 0,
-    IsMovMAD720Outlier == 0
-         )%>%
-    filter(TimeFlag == 0)
-
-# "actinic-lights.light"
-
-#rm(TargetDataMeta)
-```
-
-```{r filterdataplot}
-
-TargetDataMetaFilterPlot <- TargetDataMetaFilter %>% 
-  ggplot() +
-  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.15) +
-  geom_point(aes(x = time, y = OD720), size = 0.15, colour = "orange") +
-  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
-  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
-  #geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
- # geom_point(aes(x = time, y = IsMovAvgOutlier680)) +
-#scale_x_continuous(limits = c(0,100))+
-  #scale_x_continuous(breaks=seq(0, 800, by = 125)) +
-  #coord_cartesian(xlim = c(-10, 800)) +
-  scale_colour_manual(values = MCMIXColours) +
-  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
- facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, ID)) +
-  theme_bw() +  
-  labs(colour = "Actinic PAR (nm)")
-
-TargetDataMetaFilterPlot
-```
-
-Supplementary Growth Plot
-```{r, fig.height = 6, fig.width = 4}
-
-# ExpandTube = 1
-# OD680_x = median(TargetDataMetaFilter$time)
-# OD720_x = median(TargetDataMetaFilter$time)
-# OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 0.2
-# OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD720))
-# TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>%
-#   filter(Tube == ExpandTube) %>%
-#   ggplot() +
-#   geom_point(aes(x = time, y = OD680), colour = "darkgreen", size = 0.1) +
-#   geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
-#   scale_y_continuous(breaks=seq(0, 1.0, by = 0.2)) +
-#   coord_cartesian(ylim = c(0, 1.0)) +
-#   scale_colour_manual(values = MCMIXColours) +
-#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)") +
-#   ggh4x::facet_nested(rows = vars(WL), cols = vars(Strain, Par_ue), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_both)) +
-#   theme_bw()
-# TargetDataMetaFilterExpandPlot
-# 
-# 
-# 
-# Par_ue.labs <- c("Growth Light Intensity: 60 µE")
-# names(Par_ue.labs) <- c("60")
-# WL.labs <- c("Growth Color Light: 660 nm")
-# names(WL.labs) <- c("660")
-# ExpandTube = 1
-# OD680_x = median(TargetDataMetaFilter$time)
-# OD720_x = median(TargetDataMetaFilter$time)
-# OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 0.2
-# OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD720))
-# TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>%
-#   filter(Tube == ExpandTube) %>%
-#   ggplot() +
-#   geom_point(aes(x = time, y = OD680), colour = "darkgreen", size = 0.1) +
-#   geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
-#   scale_y_continuous(breaks=seq(0, 1.0, by = 0.2)) +
-#   coord_cartesian(ylim = c(0, 1.0)) +
-#   scale_colour_manual(values = MCMIXColours) +
-#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)") +
-#   ggh4x::facet_nested(cols = vars(Strain, WL, Par_ue), labeller = labeller(strain = label_value, Photoperiod = label_both, Par_ue = Par_ue.labs, WL = WL.labs)) +
-#   # annotate(geom = "text", x = OD680_x, y = OD680_y, label = ""~OD[680]~"", size = 4.5, colour = "darkgreen", vjust = -14.5, hjust = 2.5) +
-#   # annotate(geom = "text", x = OD720_x, y = OD720_y, label = ""~OD[720]~"", size = 4.5, colour = "blue", vjust = -20, hjust = 2.5) +
-# theme_bw() +
-# theme(strip.text.x = element_text(size = 12),
-#       strip.text.y = element_text(size = 12),
-#       #strip.background = element_rect(color="black", size=0.5, linetype="solid"),
-#       axis.text = element_text(size = 12),
-#       axis.title = element_text(size = 12))
-# 
-# # theme(strip.background = element_rect(color="black", size=1.5, linetype="solid"))
-# 
-# TargetDataMetaFilterExpandPlot
-# # grob <- grobTree(textGrob("Scatter plot", x=0.1,  y=0.95, hjust=0,
-# #   gp=gpar(col="red", fontsize=13, fontface="italic")))
-# #annotation_custom(grob)+facet_wrap(~cyl, scales="free")
-# 
-# 
-# 
-# #labelling dynamically offset from data traces.
-# #use 'median' for 'x' and OD680 + offset for 'y'
-# ExpandTube = 1
-# OD680_x = median(TargetDataMetaFilter$time)
-# OD720_x = median(TargetDataMetaFilter$time) 
-# Light_x = max(TargetDataMetaFilter$time) - 200
-# 
-# OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 0.2
-# 
-# OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD720))
-# 
-# Light_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select( Actinic_par))/1000 + 0.1
-# 
-# TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>% 
-#   filter(Tube == ExpandTube) %>%
-#   ggplot() +
-#   geom_point(aes(x = time, y = OD680), size = 0.1, colour = "darkgreen") +
-#   geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
-#   scale_y_continuous(breaks=seq(0, 1.0, by = 0.2)) +
-#   coord_cartesian(ylim = c(0, 1.0)) +
-#   
-#   # scale_x_continuous(breaks=seq(0, 250, by = 50)) +
-#   # coord_cartesian(xlim = c(0, 250)) +
-#   
-#   scale_colour_manual(values = MCMIXColours) +
-#   geom_point(aes(x = time, y = Actinic_par/1000), colour = "orange",  size = 0.0001) +
-#   #geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
-#   #geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
-#   # scale_x_continuous(breaks=seq(0, 800, by = 125)) +
-#   # coord_cartesian(xlim = c(0, 800)) +
-#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)") +
-#   #facet_grid(rows = vars(O2), cols = vars(Tube, Par_ue, Strain, ID)) +
-#   ggh4x::facet_nested(cols = vars(Strain, WL, Par_ue), labeller = labeller(strain = label_value, Photoperiod = label_both, Par_ue = Par_ue.labs, WL = WL.labs)) +
-#   #annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkgreen") +
-#   #annotate(geom = "text", x = OD720_x, y = OD720_y, label = "OD720", size = 5, colour = "blue") +
-#   #annotate(geom = "text", x = Light_x, y = Light_y, label = "Light level", size = 5, colour = "orange") +
-#   theme_bw() +
-#   theme(strip.text.x = element_text(size = 12),
-#       strip.text.y = element_text(size = 12),
-#       axis.text = element_text(size = 12),
-#       axis.title = element_text(size = 12))
-#   labs(colour = "Actinic PAR (nm)")
-# 
-# TargetDataMetaFilterExpandPlot
-
-```
-
-```{r filterdataplotexpand}
-#labelling dynamically offset from data traces.
-#use 'median' for 'x' and OD680 + offset for 'y'
-ExpandTube = 1
-OD680_x = median(TargetDataMetaFilter$time)
-OD720_x = median(TargetDataMetaFilter$time) 
-Light_x = max(TargetDataMetaFilter$time) + 100
-
-OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 0.2
-
-OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD720))
-
-Light_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select( Actinic_par))/1000 + 0.1
-
-TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>% 
-  filter(Tube == ExpandTube) %>%
-  ggplot() +
-  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
-  geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_point(aes(x = time, y = Actinic_par/1000), colour = "orange",  size = 0.0001) +
-   geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
-  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
-  # scale_x_continuous(breaks=seq(0, 800, by = 125)) +
-  # coord_cartesian(xlim = c(0, 800)) +
-  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; ID; Tube") +
-  facet_grid(rows = vars(O2), cols = vars(Tube, Par_ue, Strain, ID)) +
-  annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkblue") +
-  annotate(geom = "text", x = OD720_x, y = OD720_y, label = "OD720", size = 5, colour = "black") +
-  annotate(geom = "text", x = Light_x, y = Light_y, label = "Light level", size = 5, colour = "orange") +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")
-
-TargetDataMetaFilterExpandPlot
-
-# TargetDataPlotFacet <- TargetDataMeta %>% ggplot() +
-#   geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
-#   geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
-#   scale_x_continuous(breaks=seq(0, 800, by = 125)) +
-#   scale_colour_manual(values = MCMIXColours) +
-#   labs(y = "Optical Density 680nm (OD680)", x = "Elapsed Time (h)") +
-#   facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Par_ue),Strain, as.factor(Tube))) +
-#   theme_bw() +  
-#   labs(colour = "Actinic PAR (nm)")
-
-```
-
-## Save filtered preliminary plot if desired
-
-```{r save filtered preliminary plot as .png to folder}
-# 
-#  ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataMetaFilterPlot",".png",sep = "")), plot = TargetDataMetaFilterPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
-# # 
-#  ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataMetaFilterExpandPlot",".png",sep = "")), plot = TargetDataMetaFilterExpandPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
-```
-
-```{r DailyPAR}
-TargetDataMetaFilter <- TargetDataMetaFilter %>%
-  mutate(SetActinic_day = case_when(LightShape == 'Sine' ~ Par_ue/2 * 3600 * Photoperiod,
-                                  LightShape == 'Square' ~ Par_ue * 3600 * Photoperiod))
-
-```
-
-Implement Daily Cumulative PAR for Corrected Actinic by numeric integration
-
-```{r Actinic_parOD}
-#generate corrected values of Actinic_par accounting for OD
-#correction assumes true 100% transmission through Tube + Media + Waterbath;  we could account for the 'background' OD as well if needed
-#correction assumes that OD is attributable solely to change in culture suspension
-#correction does not account for different absorbance of different incident light coloures
-TargetDataMetaFilter <- TargetDataMetaFilter %>%
-  mutate(ActinicMin_parOD680 = Actinic_par * (10^-OD680),
-         ActinicMid_parOD680 = Actinic_par * (10^-(OD680*0.5)),
-         ActinicMin_parOD720 = Actinic_par * (10^-OD720),
-         ActinicMid_parOD720 = Actinic_par * (10^-(OD720*0.5)))
-
-#generate daily photon dose umol photon m-2 d-1 after accounting for attenuation
-TargetDataMetaFilter <- TargetDataMetaFilter %>%
-  group_by(MC, Tube, Day) %>%
-  mutate(ActinicMid_intervalOD720 = ActinicMid_parOD720 * ((time - dplyr::lag(time)) * 3600),
-         ActinicMid_dayOD720 = sum(ActinicMid_intervalOD720, na.rm = TRUE))
-
-```
-
-```{r filterdataplotexpandActinicMid_parOD720}
-#labelling dynamically offset from data traces.
-#use 'median' for 'x' and OD680 + offset for 'y'
-ExpandTube = 5
-OD680_x = median(TargetDataMetaFilter$time)
-OD720_x = median(TargetDataMetaFilter$time) + 100
-Light_x = max(TargetDataMetaFilter$time) + 72
-
-OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 2.2
-
-OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD720_x) %>% select(OD720)) + 1.1
-
-Light_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select( Actinic_par))/1000 + 0.15
-
-TargetDataMetaFilter %>% 
-  filter(Tube == ExpandTube) %>%
-  ggplot() +
-  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
-  geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "black") +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_point(aes(x = time, y = ActinicMid_parOD720/100), colour = "orange",  size = 0.0001) +
-  geom_point(aes(x = time, y = ActinicMid_dayOD720/100000), colour = "red",  size = 0.0001) +
-  scale_x_continuous(breaks=seq(0, 400, by = 125)) +
-  coord_cartesian(xlim = c(0, 400)) +
-  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; ID; Tube") +
-  facet_grid(rows = vars(O2), cols = vars(Par_ue, Strain, ID, Tube)) +
-  annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkblue") +
-  annotate(geom = "text", x = OD720_x, y = OD720_y, label = "OD720", size = 5, colour = "black") +
-  annotate(geom = "text", x = Light_x, y = Light_y, label = "Light level", size = 5, colour = "orange") +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")+ 
-  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))
-
-```
-
-# Save .Rds of Imported Data from TargetFile
-
-```{r save Rds of imported data}
-saveRDS(object = TargetDataMetaFilter, file = file.path(DataOut, paste(TargetFileName, "TargetDataMetaFilter.Rds",  sep = "_")), ascii = FALSE, version = NULL,
-        compress = TRUE, refhook = NULL)
-```

### 2023-12-04 Code/OlisImportPurCalc.Rmd
Move in Olis Import Rmd

---
title: "Import OLIS spectral data"
author: "Douglas A. Campbell, Sylwia Sliwinska-Wilczewska, Sarah Gore, Adrian Kryk, Mireille Savoie"
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
    code_folding: show
---

# Import spectral files generated by OLIS spectrophotometer
# Import emission files generated by Jaz spectrophotometer
# Calculate PUR of each Strain at each spectral color and PAR

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r set project variables, include = FALSE}
Project <- "PICO"
DataOut <- file.path("..", "GrowthAssessData")

#Sylwia's file path
#DataIn <- file.path("..", "OLISSpectraCorr", "SySlCCASingleTest", fsep = .Platform$file.sep)

#Mireille's file path
DataIn <- file.path("..", "OLISSpectraCorr", "MiSa", fsep = .Platform$file.sep)

DataInSpectra <- file.path("..", "ImportedData", "Jaz", fsep = .Platform$file.sep)

DataInPAR <- file.path("..", "MultiCultiSpectra", fsep = .Platform$file.sep)

PlotsPath <- file.path("..", "MireilleSavoieMSc", "Figures")

FileID <- "Smooth"

#MDPicoGoogle <- "https://docs.google.com/spreadsheets/d/1Lerp5u25kzBtaBbnOYElYqUP59cn68gJpxxayhnGdkw/edit#gid=0"

FileEncode <- "UTF-8" 
Delimiter <- ""

HeaderRows <- 0
RollWindow <- 10

```

```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(plotly)
library(dplyr)
library(magrittr)
library(googledrive)
library(googlesheets4)
library(readxl)

library(ggspectra)
library(ggpubr)
library(caret)
```

```{r set colours}
Wavelengths_nm = c(405, 450, 475, 530, 615, 660, 730, "WW")
Colours_nm = c("violet", "darkblue", "dodgerblue", "darkgreen","orange","red","purple", "black")

names(Colours_nm) <- Wavelengths_nm
Colours_nm

# StrainNames = c("MIT9313" , "SS120", "MED4")
# ColoursStrain <- c("#E69F00","#F0E442","#CC79A7")

ColoursStrain = c(MIT9313 = "#E69F00", SS120 = "#F0E442", MED4 = "#CC79A7" )
# names(ColoursStrain) <- StrainNames
# ColoursStrain

```

For SySl files 'baseline' in filename means baseline spectra already subtracted within OLIS software.
This was not universallly true across all projects; be careful.
For SySl files 'raw' means spectra of undiluted culture; other spectra are 1 or 4 ml culture + 8 or 4 ml media.

Ideally: we want to read and tidy some user-selected set of files taken from multiple dates

```{r list available OLIS ascii Files}
OlisAsciiFiles <- list.files(path = DataIn, pattern = ".asc", full.names = TRUE)
OlisAsciiFiles

#test for duplicate file names
unique(duplicated(OlisAsciiFiles))
```

# set up read_delim_plus
```{r}
# #make this more robust to variable file formats
#FileEncode <- "UTF-8"
#Delimiter <- ""
# #.asc files from export from OLIS seem to use spaces as delimiter
# 
#HeaderRows <- 0

read.delim_plus <- function(flnm, filencode, delimiter, headerrows){read.delim(flnm, fileEncoding = filencode, sep = delimiter,  skip = headerrows, header = FALSE, row.names = NULL) %>%
     mutate(Filename = flnm, Cdatetime = ymd_hms(file.info(flnm)$ctime))
}

#read.delim_long meant for map over a vector of filepaths to read, convert to long format and tidy the imported data
read.delim_long <- function(flnm, filencode, delimiter, headerrows){read.delim(flnm, fileEncoding = filencode, sep = delimiter,  skip = headerrows, header = TRUE, row.names = NULL) %>%
    mutate(Filename = flnm, Cdatetime = ymd_hms(file.info(flnm)$ctime)) %>%
 rename(nm = X350) %>%
  mutate(FirstLastSpec = str_extract(Filename, "_[A-Z][a-z][A-Z][a-z][:digit:][:digit:][:digit:][:digit:]_[A-Z][a-z][A-Z][a-z][:digit:][:digit:][:digit:][:digit:]_")) %>%
  mutate(SampleNumbers = str_extract_all(FirstLastSpec, "[:digit:][:digit:][:digit:][:digit:]")) %>%
  mutate(FirstSampleNumber = as.numeric(map(SampleNumbers, ~.[[1]]))) %>%
  mutate(LastSampleNumber = as.numeric(map(SampleNumbers, ~.[[2]]))) %>%
  mutate(OperatorID = str_extract(Filename,"[A-Z][a-z][A-Z][a-z]")) %>%
  pivot_longer(cols = starts_with("X"), names_to = "SpectraID", values_to = "Abs") %>%
  mutate(SampleCode = as.numeric(str_remove(SpectraID, "X"))) %>%
  mutate(SampleNumber = SampleCode - min(SampleCode, na.rm = TRUE) + FirstSampleNumber) %>%
  relocate(OperatorID, SampleNumber) %>%
  unite(col = SampleID, OperatorID:SampleNumber, sep = "", remove = FALSE) %>%
  arrange(SampleID, nm) %>%
  relocate(SampleID, nm, Abs) %>%
  mutate(SpectraDate = str_extract(Filename, "/[:digit:][:digit:][:digit:][:digit:][:digit:][:digit:][:digit:][:digit:]_"),
         SpectraDate = str_remove_all(SpectraDate, "_"),
         SpectraDate = str_remove_all(SpectraDate, "/"),
         SpectraDate = ymd(SpectraDate)
  )
}
```

# Import OLISSpectra files
```{r import OLIS jav corr file}

TargetFile <-  OlisAsciiFiles

TargetSpectra <- TargetFile %>% map_df(~read.delim_plus(flnm = ., filencode = FileEncode, delimiter = Delimiter, headerrows = FALSE)) %>% 
  #pivot_longer(., -c(`X375`, Filename, Cdatetime), values_to = "Absorbance", names_to = "SampleID") %>%
   rename(nm = `V1`,
          Absorbance = `V2`) %>% 
  filter(!is.na(Absorbance))

  #separate(col = SampleID, into = c("SampleID", "Replicate"), sep = "_")

TargetSpectraLong <- TargetSpectra %>%
  # rename(nm = OLIS.3D.ASCII) %>%
  separate(col = Filename, into = c("fp1", "fp2", "fp3", "SpectraDate", "Project", "Source", "Range", "Type", "Correction", "Smooth"), sep = "([\\/\\_\\:])", remove = FALSE)

TargetSpectraLong2 <- TargetSpectraLong %>%
  select(-c(fp1, fp2, fp3, Type, Correction, Smooth)) %>% 
  rename(CultureID = Source) %>% 
  mutate(SpectraDate = str_extract(Filename, "/202[:digit:][:digit:][:digit:][:digit:][:digit:]"),
           SpectraDate = ymd(str_extract(SpectraDate, "202[:digit:][:digit:][:digit:][:digit:][:digit:]")))

glimpse(TargetSpectraLong2)
```

Load Multiculti catalog
```{r load local multiculticatalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()

# imagine this is the URL or ID of a Sheet readable by anyone (with a link)
# MultiCulti metadata
MetaData <- read_sheet("https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0") %>%
  # read_sheet has an annoying "feature" to set the type of columns it can't parse to a list.
  # ggplot/dplyr doesn't like working with a dataframe of lists.
  # In this case WL is set to a list since some values are numbers, some are strings, some are blank.
  # To fix this, first drop all rows missing WL, then unlist.
  # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.
  drop_na(WL) %>%
  mutate(WL = unlist(WL))

as.data.frame(MetaData)

MetaData <- MetaData %>%
   mutate(ExpDate = ymd(ExpDate),
          ExpEndDate = ymd_hms(`ExpEndDate`)) %>% 
  select(-c(...46,...47))

```

# Merge OLISSpectra with MetaData
```{r OLISDateSpectra with MetaData}

OLISSpectraMeta <- MetaData %>%
  right_join(., TargetSpectraLong2, by = c("ID" = "CultureID"))

OLISSpectraMeta <- OLISSpectraMeta %>%
group_by(ID) %>%
  arrange(SpectraDate) %>%
  mutate(E_days = as.numeric((SpectraDate - ExpDate[1]))) %>%
ungroup()

remove(TargetSpectra)
remove(TargetSpectraLong)
remove(TargetSpectraLong2)
rm(MetaData)

glimpse(OLISSpectraMeta)
```
# remove extra columns from metacatelog
```{r remove columns}
 OLISSpectraMeta <- OLISSpectraMeta %>% 
  select(-c(OptodeMeasure,SampleID))

```

List the rds of spectras that were combined in 1 ascii file but separated in 'OlisImportCombined_MS.Rmd'
```{r read list available OLIS rds Files}
OlisRdsFiles <- list.files(path = DataIn, pattern = ".Rds", full.names = TRUE)
OlisRdsFiles

#test for duplicate file names
unique(duplicated(OlisRdsFiles))
```
# Read .Rds, Summarize, Combine to single data frame

## Create function using to read in .Rds, adding source filename as a column

```{r readRDS_plus}
readRDS_plus <- function(Flnm){readRDS(file = Flnm) 
  #%>%
    #mutate(Filename = Flnm)
}
```

## Read in ProcessedFiles .Rds
```{r read selected ProcessedData}

RdsData <-  OlisRdsFiles %>%
    map_df(~readRDS_plus(Flnm = .)) %>% 
  select(-c(...44,...45))

glimpse(RdsData)

```

merge all Olis spectra data from single ascii imported files and spectras from combined ascii files tidied in .rds files.
```{r}

OlisSpectraMetaCombined <- rbind(OLISSpectraMeta, RdsData)

glimpse(OlisSpectraMetaCombined)

remove(OLISSpectraMeta)
remove(RdsData)
```

read emission spectras from MultiCultis for PUR determinations
```{r}

MC_Spectra <- readRDS(file = file.path(DataInSpectra, "PICO_MultiCultiSpectra.Rds"))

```

read measured PAR from Mulitcultis for PUR determinations
```{r}
MC_PAR <- read_csv(file = file.path(DataInPAR, "MultiCulti_PAR.csv"))

```

Unnest MC spectra and join MC measured PAR
```{r join MC emission and PAR data}

 MC_Spectra <- MC_Spectra %>%
  unnest(Spectra) %>%
  group_by(MultiCulti, Par, WL, Wavelength) %>%
  mutate(nm = round(Wavelength)) %>%
  ungroup() %>%
  group_by(Filename, MultiCulti, Par, WL, nm, is_nm) %>%
  summarise(MeanEmission = mean(Counts)) %>%
  ungroup() %>%
  mutate(Emission = round(MeanEmission, digits = 1),
         MC = MultiCulti,
         SetPar_uE = Par,
         ID = paste(MC,WL, sep = "_"))

MC_SpectraPAR <- left_join(MC_Spectra, MC_PAR, by = c("WL" = "Actinic_nm", "SetPar_uE", "MC" = "Multiculti")) %>%
  rename(EMSetPar_uE = 'SetPar_uE',
         EMMeasuredPar_uE = 'MeasuredPar_uE') %>% 
  select(-c(Par, MultiCulti))

MC_SpectraPAR <- MC_SpectraPAR %>% 
  filter(ID != "MCMIX004_WW",
         EMSetPar_uE == 30 ) %>% 
  rename(MC_SpectralID = 'ID') %>% 
  select(-c( Filename, MC)) %>% 
  group_by(WL) %>% 
  mutate(MC_NormEm = round(Emission / Emission[which.max(Emission)], digits = 4),
         MC_Max_nm = round(nm[which.max(Emission)])) %>% 
  select(-c(is_nm, MeanEmission, Date)) %>% 
ungroup()

OlisSpectraMetaData <- left_join(OlisSpectraMetaCombined , MC_SpectraPAR, by = c("WL", "nm"))

#   
#   pivot_wider(names_from = c("MultiCulti","WL"), values_from = "Counts") %>%
#   pivot_longer(c("MC257_WW", "MCMIX004_470", "MCMIX004_660", "MCMIX004_405","MCMIX004_450", "MCMIX004_530", "MCMIX004_620", "MCMIX004_730", "MCMIX004_WW"), names_to = "ID", values_to = "Emission" ) %>% 
#   group_by(ID) %>%
#   mutate(nm = round(Wavelength)) %>% 
#   ungroup()
# 
# MC_Spectra_test2 <- MC_Spectra_test %>% 
#   group_by(ID, nm)  %>% 
#   summarise(MeanAbs = (Emission)) %>% 
#   ungroup()

#OlisSpectraMetaData <- bind_rows(OlisSpectraMetaCombined, MC_Spectra)

remove(MC_PAR)
remove(MC_Spectra)
remove(MC_SpectraPAR)

```

Normalization
https://www.digitalocean.com/community/tutorials/normalize-data-in-r
```{r}
# OLISSpectraMetaNorm <- OlisSpectraMetaData %>%
# summary(Absorbance) 
# process <- preProcess(as.data.frame(Absorbance), method=c("range")) %>% 
# norm_scale <- predict(process, as.data.frame(Absorbance))

```

Find nm at red and blue max Chla peak then extract absorbance. Use this absorbance to normalize later on
```{r}
OlisSpectraMetaData_red <- OlisSpectraMetaData %>% 
  filter(Run != 35) %>% 
  group_by(ID, E_days) %>%
  filter(nm >= 575 & nm <= 750) %>% 
   mutate(Red_nm = round(nm[which.max(Absorbance)]),
          MaxAbs_Red_nm = Absorbance[which.max(Absorbance)]) %>% 
  ungroup() %>% 
  filter(nm == 675) %>% 
  select(ID, Strain, Red_nm, MaxAbs_Red_nm, Par_ue, E_days)

 OlisSpectraMetaData <- left_join(OlisSpectraMetaData, OlisSpectraMetaData_red)

 OlisSpectraMetaData_blue <- OlisSpectraMetaData %>% 
  group_by(ID, E_days) %>%
  filter(nm >= 400 & nm <= 460) %>% 
   mutate(Blue_nm = round(nm[which.max(Absorbance)]),
          MaxAbs_Blue_nm = Absorbance[which.max(Absorbance)]) %>% 
  ungroup() %>% 
  filter(nm == 440) %>% 
  select(ID, Strain, Blue_nm,MaxAbs_Blue_nm,  Par_ue, E_days)

 OlisSpectraMetaData <- left_join(OlisSpectraMetaData, OlisSpectraMetaData_blue)

 remove(OlisSpectraMetaData_red)
 remove(OlisSpectraMetaData_blue)
 remove(OlisSpectraMetaCombined)

 glimpse(OlisSpectraMetaData)
```

Normalization
Used max peak of each spectra to normalize peaks to red Chla region (750 < nm > 575) and blue Chla region (460 < nm > 400 )
```{r}

OlisSpectraMetaData <- OlisSpectraMetaData %>% 
  group_by(ID, E_days) %>%
 mutate(NormAbs_Blue_nm = Absorbance / MaxAbs_Blue_nm,
        NormAbs_Red_nm = Absorbance / MaxAbs_Red_nm) %>% 
  ungroup()

glimpse(OlisSpectraMetaData)
```

PUR Calculations

```{r PUR}
OlisSpectraMetaData <- OlisSpectraMetaData %>%
    filter(nm >= 400 &
           nm <= 700) %>%
  mutate(PURAbsWholeCell_Norm = MC_NormEm * NormAbs_Blue_nm) %>% 
  group_by(ID, E_days) %>% 
  mutate(SumPURAbsWholeCell_Norm = sum(MC_NormEm * NormAbs_Blue_nm),
         CalcPur_ue = round(Par_ue * (SumPURAbsWholeCell_Norm / sum(MC_NormEm))),
         ParPurRatio = sum(MC_NormEm) / SumPURAbsWholeCell_Norm,
         PurParRatio =  SumPURAbsWholeCell_Norm / sum(MC_NormEm)) %>% 
ungroup() %>% 
  select(-SumPURAbsWholeCell_Norm)

glimpse(OlisSpectraMetaData)

```

Find Strain specific average PUR for each spectral color and each growth PAR 
```{r}

OlisSpectraMetaData <- OlisSpectraMetaData %>%
  group_by(Strain, WL) %>% 
  mutate(meanParPurRatio = (mean(ParPurRatio)),
         meanPurParRatio = (mean(PurParRatio)))%>% 
ungroup()

OlisSpectraMetaData <- OlisSpectraMetaData %>%
  group_by(Strain, WL, Par_ue) %>% 
  mutate(Pur_ue = round(mean(CalcPur_ue)))%>% 
ungroup()

```

Nest 
```{r Nest}

PicoNestedPurOlisData <- OlisSpectraMetaData %>% 
  group_by(ID, E_days) %>% 
  nest(PurData = c(nm, Absorbance, Emission, MC_NormEm, PURAbsWholeCell_Norm, NormAbs_Red_nm, NormAbs_Blue_nm,  EMMeasuredPar_uE, EMSetPar_uE, MC_SpectralID, SpectraDate, Range, Cdatetime))

```

 save nested 
```{r Save rds and csv}

saveRDS(object = PicoNestedPurOlisData, file = file.path(DataOut, "PicoNestedPurOlisData.Rds"))

write_csv(PicoNestedPurOlisData, file = file.path(DataOut, paste(Project, "NestedPurOlisData",".csv",sep = ""),fsep = .Platform$file.sep))

```

```{r, Initial Plots}
OlisSpectraMetaData %>%
  ggplot() +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = Colours_nm) +
 # guides(colour = FALSE) +
  labs(y = "Absorbance", x = "Wavelength (nm)") +
  scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
  coord_cartesian(ylim = c (0, 0.2)) +
  ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

OlisSpectraMetaData %>%
   filter(Strain == "MED4",
          ID != "MiSa1289",
          ID != "MiSa1294") %>% 
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Blue_nm, colour = "violet", label = ID)) +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = Colours_nm) +
 # guides(colour = FALSE) +
  labs(subtitle = "Normalized to Max Abs in blue range (400 to 460 nm)", y = "Normalized Absorbance", x = "Wavelength (nm)") +
  #scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
  ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

OlisSpectraMetaData %>%
   filter(Strain == "MED4",
          ID != "MiSa1289",
          ID != "MiSa1294") %>% 
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Red_nm, colour = "violet", label = ID)) +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = Colours_nm) +
  #guides(colour = FALSE) +
 labs(subtitle = "Normalized to Max Abs in red range (575 to 750 nm)", y = "Normalized Absorbance", x = "Wavelength (nm)") +
  # scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
  # coord_cartesian(ylim = c (0, 0.2)) +
 ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

OlisSpectraMetaData %>%
   filter(Strain == "SS120",
          ID != "MiSa1289",
          ID != "MiSa1315") %>% 
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Blue_nm, colour = "violet", label = ID)) +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = Colours_nm) +
 # guides(colour = FALSE) +
  labs(subtitle = "Normalized to Max Abs in blue range (400 to 460 nm)", y = "Normalized Absorbance", x = "Wavelength (nm)") +
  #scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
  ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

OlisSpectraMetaData %>%
   filter(Strain == "SS120",
          ID != "MiSa1289",
          ID != "MiSa1315") %>% 
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Red_nm, colour = "violet", label = ID)) +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = Colours_nm) +
  #guides(colour = FALSE) +
 labs(subtitle = "Normalized to Max Abs in red range (575 to 750 nm)", y = "Normalized Absorbance", x = "Wavelength (nm)") +
  # scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
  # coord_cartesian(ylim = c (0, 0.2)) +
 ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

OlisSpectraMetaData %>%
   filter(Strain == "MIT9313",
          ID != "MiSa1294",
          ID != "MiSa1315") %>% 
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Blue_nm, colour = "violet", label = ID)) +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = Colours_nm) +
 # guides(colour = FALSE) +
  labs(subtitle = "Normalized to Max Abs in blue range (400 to 460 nm)", y = "Normalized Absorbance", x = "Wavelength (nm)") +
  #scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
  ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

OlisSpectraMetaData %>%
   filter(Strain == "MIT9313",
          ID != "MiSa1315",
          ID != "MiSa1294") %>% 
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Red_nm, colour = "violet", label = ID)) +
  geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
  scale_color_manual(values = Colours_nm) +
  #guides(colour = FALSE) +
 labs(subtitle = "Normalized to Max Abs in red range (575 to 750 nm)", y = "Normalized Absorbance", x = "Wavelength (nm)") +
  # scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
  # coord_cartesian(ylim = c (0, 0.2)) +
 ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+
  labs(colour = "Actinic PAR (nm)")

```

# Stock cultures grown in incubators 
```{r stock cultures}

# Stock_ID = c("MiSa1289", "MiSa1294", "MiSa1315")
# Culture_ID = c("MIT9313", "SS120", "MED4")
# 
# names(ColoursMiSaID) <- Stock_ID

Stock_ID = c(MiSa1289 = "#E69F00", MiSa1294 = "#F0E442", MiSa1315 = "#CC79A7")
Stock_Label = c(MiSa1289 = "MIT9313",  MiSa1294 = "SS120", MiSa1315 = "MED4")

OlisSpectraMetaData %>%
   filter(ID == "MiSa1289" |
          ID == "MiSa1315" |
          ID == "MiSa1294" |
          ID == "MiSa1722" |
          ID == "MiSa1723") %>%
  ggplot() +
  geom_point(aes(x = nm, y = NormAbs_Blue_nm, colour = (ID))) +
 # geom_point(aes(x = nm, y = Absorbance, colour = ID)) +
 #scale_color_manual(values = Colours_nm) +
  #guides(colour = FALSE) +
 labs(y = "Normalized Absorbance", x = "Wavelength (nm)", size = 20, color = "black" ) +
    scale_y_continuous(breaks = c(0,0.2, 0.4,0.6, 0.8, 1.0, 1.2), limits = c (0, 1.2)) +
   # scale_y_continuous(breaks=seq(0, 0.2, by = 0.05)) +
 scale_color_manual(values = Stock_ID, label = Stock_Label) +
  # coord_cartesian(ylim = c (0, 0.2)) +
 #ggh4x::facet_nested(rows = vars(Par_ue),cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()+ 
 theme(
        axis.title = element_text(size = 20, color = "black"),
        axis.text = element_text(size = 15, color = "black"),
        # strip.background=element_rect(color="grey", fill = "grey"),
        # strip.background=element_rect(fill = "grey"),
        # legend.key.size = unit(1, 'cm'), #change legend key size
        # legend.key.height = unit(1, 'cm'), #change legend key height
        # legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title = element_text(size = 15),  #change legend title font size
   legend.text = element_text(size = 15)) + #change legend text font size
  labs(colour = "Strain")

AbsAllStrains
```

```{r remove unnecessary DF}
remove(OlisSpectraMetaData)
```

### 2023-12-04 Code/JazDataImport.Rmd
Copied Multi Culti emission spectra data from the Jaz instrument into RawData and copied the Jaz Import RMD.

---
title: "Import Jaz data"
output: html_notebook
---

```{r libraries}
#library(dplyr) 
library(tidyverse)
library(lubridate)
library(googledrive)
library(googlesheets4)

library(gghighlight)
library(ggrepel)

#library(ggplot2)
library(scales)
library(photobiology)
library(photobiologyWavebands)
library(ggspectra)
library(ggrepel)
```

```{r import the data}
Project <- "PICO"

#DataIn <- file.path("..", "Jaz", fsep = .Platform$file.sep)
DataIn <- file.path("..", "MultiCultiSpectra", fsep = .Platform$file.sep)

#ExpDate <- "20220520"
DataOut<- file.path("..", "ImportedData", "Jaz", fsep = .Platform$file.sep)
#CatalogGoogle <- "https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0"

#set variables for file import & processing of fluorescence files Jaz
#DataPathCS <- file.path("..", "Jaz", fsep = .Platform$file.sep)
#FileIDSingle <- "202205201054_PICO_SySl1246_445_LL_Subt6_10-59-24-712"

Jazfile <- list.files(path = DataIn, pattern = ".txt", full.names = TRUE)

Jazfile[1:10]

unique(duplicated(Jazfile))
SkipCS <- 14
FileEncodeCS <- "UTF-8"
DelimCS <- "\t"
RollWindow <- 10

```

```{r set colours}
Wavelengths_nm = c(405, 450, 470, 530, 620, 660, 720, "WW")
Colours_nm = c("yellow", "dodgerblue", "darkblue", "yellowgreen", "darkgreen", "Red",  "darkorange", "black")

names(Colours_nm) <- Wavelengths_nm
Colours_nm
```

```{r read multiculti PAR data}

MultiCultiPAR <- read.csv(file.path(DataIn, "MultiCulti_PAR.csv"))

```

```{r read Jaz data using map_df}
fread_plus <- function(Flnm, Skip, FileEncode, Delim){data.table::fread(file = Flnm, skip = Skip, encoding = FileEncode, sep = Delim, header = FALSE) %>%
    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(Flnm)$ctime))
}

JazSpec <- Jazfile %>%
  map_df(~fread_plus(Flnm = ., Skip = SkipCS, FileEncode = FileEncodeCS, Delim = DelimCS))

# JazSpec <- JazSpec %>%
#   filter(!str_detect(V2, pattern = "Content"))

colnames(JazSpec)[1] <- "Wavelength"
colnames(JazSpec)[2] <- "Counts"

JazSpec[1:10]

# JazSpec |>
#   ggplot() +
#   geom_point(aes(x = Wavelength, y = Counts)) +
#   theme_bw()
```

```{r filename separation}

JazSpec <- JazSpec %>% 
  mutate(Filename = str_remove(Filename, pattern = "../")) |>
  separate(col = Filename, into = c("Instrument","Date", "MultiCulti", "Par", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE)

# JazSpecTrim <- JazSpecTrim %>% 
# select(-fp1, -fp2, -fp3, -txt, -date_experiment, -device2, -Project, -CDateTime, -Subt, -subseconde)

JazSpec <- JazSpec %>% 
mutate(Date = ymd(Date),
       Par = as.numeric(Par),
       WL = as.factor(WL))

JazSpec[1:10]

```

```{r remove the wl < 350 and > 750}

JazSpecTrim <- JazSpec %>% 
  subset(JazSpec$Wavelength >= 350 & JazSpec$Wavelength <= 750)

```

Remove all NA columns & empty rows, fix column types
```{r remove missing columns}

#https://community.rstudio.com/t/drop-all-na-columns-from-a-dataframe/5844/2
not_all_na <- function(x) {!all(is.na(x))}

JazSpecTrim <- JazSpecTrim %>%
  select_if(not_all_na)

# JazSpecTrim <- JazSpecTrim %>%
#   mutate(JazTimeHMS = lubridate::hms(stringr::str_sub(CDateTime, start = 1L, end = 8L)), .after = CDateTime)

# JazData2 <- JazData %>%
#   filter(!is.na(Wavelength))
# 
# JazSpecTrim <- JazSpecTrim %>%
#   mutate(Duration_s = as.numeric(Duration_s)) %>% 
#   mutate(AquisitionTime_ms = as.numeric(AquisitionTime_ms))

```

Find nm at max count and compare with rolling mean of counts
```{r, fig.height = 6, fig.width = 8}

JazSpecTrim <- JazSpecTrim %>% 
  group_by(WL, MultiCulti) %>%
   mutate(rollmeanCounts = zoo::rollmean(Counts, k = RollWindow, align = "left", fill = NA),
          is_nm = round(Wavelength[which.max(Counts)]),
          is_nm_rollmean= round(Wavelength[which.max(rollmeanCounts)])) %>% 
  ungroup()

```

```{r nest the spectral data}

JazSpecNest <- JazSpecTrim %>%
  nest(Spectra = c(Wavelength, Counts, rollmeanCounts))

```

```{r annotate measured nm, fig.height = 6, fig.width = 8}

JazSpecNest %>%
  unnest(Spectra) %>%
    ggplot() +
  geom_point(aes(x = Wavelength, y = Counts, colour = as.factor(WL))) +
  # geom_point(aes(x = Wavelength, y = is_nm, colour = as.factor(WL))) +
  geom_text(aes(x = is_nm, y= max(Counts), label= is_nm), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
  scale_color_manual(values = Colours_nm) +
  guides(colour = "none") +
  geom_vline(aes(xintercept = is_nm), linetype = "dashed") +
  scale_y_continuous(limits = c(0,100000)) +
  ggh4x::facet_nested(rows = vars(MultiCulti, WL), labeller = labeller(WL = label_both, Par = label_both, MultiCulti = label_both)) +
  theme_bw()

```

```{r estimate peak ratios}
# JazSpecWideNest <- JazSpecWide %>%
#   nest(Spectra = c(One_Wavelength, One_Counts, Two_Counts, Three_Counts, Four_Counts, CountsAv, CountsMax, CountsMin)) %>%
#   mutate(CountsBack = map_dbl(.x = Spectra, ~mean(.$CountsAv[.$One_Wavelength > 740])),
#     Counts680690 = map_dbl(.x = Spectra, ~mean(.$CountsAv[.$One_Wavelength > 680 & .$One_Wavelength < 690])),
#          Counts715725 = map_dbl(.x = Spectra, ~mean(.$CountsAv[.$One_Wavelength > 715 & .$One_Wavelength < 725])),
#          Counts685_720 = Counts680690/Counts715725,
#     Counts685_720back = (Counts680690 - CountsBack)/(Counts715725 - CountsBack)
#     )
# 
# JazSpecWideNest %>%
#   filter(Par_ue == 60) %>%
#   #filter(Ex_WL != 445) %>%
#   ggplot() +
#   geom_point(aes(x = Ex_WL, y = Counts685_720)) +
#   geom_point(aes(x = Ex_WL, y = Counts685_720back), colour = "red") +
#   scale_color_manual(values = Colours_nm) +
#   guides(colour = "none") +
#   #coord_cartesian(xlim = c(660, 750), ylim =  c(0,5000)) +
#   ggh4x::facet_nested(cols = vars(Strain, Par_ue, WL), labeller = labeller(strain = label_value, Par_ue = label_both, WL = label_both))  +
#   theme_bw()
```

XXXX6 June 2022XXX

Adding the maximum (peak) value in ggplot for geom_smoth
https://stackoverflow.com/questions/71162252/adding-the-maximum-peak-value-in-ggplot-for-geom-smoth
```{r}

# sm_max <- JazSpecTrim %>% 
#   group_by(WL) %>%
#   mutate(smooth =predict(loess(Counts~as.numeric(Wavelength), span=.05))) %>%
#   slice_max(order_by = smooth)
# 
# JazSpecTrim |>
#   group_by(WL) %>%
#   mutate(is_nm = Wavelength[which.max(Counts)]) %>%
#   ggplot(df, mapping = aes(Wavelength, Counts, color = MultiCulti)) +
#   geom_point(aes(x = Wavelength, y = Counts, colour = as.factor(MultiCulti))) +
#   scale_color_manual(values = Colours_nm) +
#   guides(colour = FALSE) +
#   scale_y_continuous(limits = c(0,60000)) +
#   ggh4x::facet_nested(rows = vars(WL), labeller = labeller(WL = label_both, strain = label_value, Par = label_both, WL = label_both))  +
#   geom_smooth(span=.05, se=F) +
#   geom_point(size = 3) +
#   gghighlight(is_max,
#               n = 1,
#               unhighlighted_params = list(alpha = 0),
#               label_key = Counts)

```
ggspectra:
https://cran.r-project.org/web/packages/ggspectra/vignettes/userguide1-grammar.html
https://cran.r-project.org/web/packages/ggspectra/vignettes/userguide2-autoplot-methods.html
```{r}

# JazSpecTrim |> 
#   # group_by(Filename) %>%
#     filter(
#          Ex_WL != "470",
#          Ex_WL != "505") %>%
#   #mutate(is_max = Counts == max(Counts)) %>%
#   ggplot(df, mapping = aes(Wavelength, Counts, color = Filename)) +
# 
#   geom_point(aes(x = Wavelength, y = Counts, colour = as.factor(Ex_WL))) +
#   scale_color_manual(values = Colours_nm) +
#   guides(colour = FALSE) +
# 
#   scale_y_continuous(limits = c(0,60000)) +
#   ggh4x::facet_nested(rows = vars(Ex_WL), cols = vars(Strain, Par_ue, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both))  +
#   #geom_point(size = 3) +
#   geom_line() +
#   stat_peaks(geom = "point",
#              span = 51,
#              color = "red",
#              vjust = "bottom",
#              position = position_nudge(y = 0.01)) +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 45))
# # 
# 
# 
# #Showed y-value on spectra
# ggplot(sun.spct) + geom_line() + 
#   stat_peaks(shape = 21, span = 35, size = 2) + 
#   stat_label_peaks(aes(label = stat(y.label)),
#                    span = 35, geom = "label", size = 3,
#                    position = position_nudge(y = 0.04),
#                    label.fmt = "%1.2f") +
#   expand_limits(y = 1) +
#   scale_fill_identity() + scale_color_identity()

```

```{r save rds}
 saveRDS(JazSpecNest, file.path(DataOut, paste(Project, "MultiCultiSpectra.Rds", sep = "_"), fsep = .Platform$file.sep))
```

### 2023-12-04 Code/JazDataImport.Rmd
Fixed file path assignments.

@@
 
-#DataIn <- file.path("..", "Jaz", fsep = .Platform$file.sep)
-DataIn <- file.path("..", "MultiCultiSpectra", fsep = .Platform$file.sep)
+DataIn <- file.path("..", "Data","RawData", "MCEmissionSpectra", fsep = .Platform$file.sep)
 
-#ExpDate <- "20220520"
-DataOut<- file.path("..", "ImportedData", "Jaz", fsep = .Platform$file.sep)
-#CatalogGoogle <- "https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0"
+DataOut<- file.path("..", "Data", "ProcessedData", fsep = .Platform$file.sep)
 
@@
 ```{r read Jaz data using map_df}
+
 fread_plus <- function(Flnm, Skip, FileEncode, Delim){data.table::fread(file = Flnm, skip = Skip, encoding = FileEncode, sep = Delim, header = FALSE) %>%
@@
 #   theme_bw()
+
 ```
@@
 
-```{r remove the wl < 350 and > 750}
+```{r remove wl < 350 and > 750}
 
@@
 ```
+
 ggspectra:
@@
 ```{r save rds}
+
  saveRDS(JazSpecNest, file.path(DataOut, paste(Project, "MultiCultiSpectra.Rds", sep = "_"), fsep = .Platform$file.sep))
+
 ```

### 2023-12-04 Code/JazDataImport.Rmd
Fixed information extracted from filename column due to new data file path. Generated Emission spectra .Rds

@@
 JazSpec <- JazSpec %>% 
-  mutate(Filename = str_remove(Filename, pattern = "../")) |>
-  separate(col = Filename, into = c("Instrument","Date", "MultiCulti", "Par", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE)
+  mutate(Filename = str_remove(Filename, pattern = "../Data/RawData/MCEmissionSpectra/")) |>
+  separate(col = Filename, into = c("Date", "MultiCulti", "Par", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE)
 
@@
        WL = as.factor(WL))
-
-JazSpec[1:10]
 
@@
   nest(Spectra = c(Wavelength, Counts, rollmeanCounts))
+
+```
+
+```{r remove redundant DF}
+
+remove(JazSpecTrim)
+remove(JazSpec)
 

### 2023-12-04 Code/OlisImportPurCalc.Rmd
Tidied script. Removed redundant lines.
Fixed extraction of information from Filename column due to new data file path.

@@
 ```{r set project variables, include = FALSE}
+
 Project <- "PICO"
-DataOut <- file.path("..", "GrowthAssessData")
 
-#Sylwia's file path
-#DataIn <- file.path("..", "OLISSpectraCorr", "SySlCCASingleTest", fsep = .Platform$file.sep)
+DataIn <- file.path("..", "Data","RawData", "OLISSpectraCorr", fsep = .Platform$file.sep)
 
-#Mireille's file path
-DataIn <- file.path("..", "OLISSpectraCorr", "MiSa", fsep = .Platform$file.sep)
+DataInCatalog <- file.path("..", "Data", fsep = .Platform$file.sep)
 
-DataInSpectra <- file.path("..", "ImportedData", "Jaz", fsep = .Platform$file.sep)
+DataInSpectra <- file.path("..", "Data", "ProcessedData",  fsep = .Platform$file.sep)
 
-DataInPAR <- file.path("..", "MultiCultiSpectra", fsep = .Platform$file.sep)
+DataInPAR <- file.path("..", "Data","RawData","MCEmissionSpectra", fsep = .Platform$file.sep)
 
-PlotsPath <- file.path("..", "MireilleSavoieMSc", "Figures")
+DataOut <- file.path("..", "ProcessedData")
 
@@
 library(broom)
-library(knitr)
-library(OneR)
+# library(knitr)
+# library(OneR)
 library(zoo)
-library(strucchange)
-library(plotly)
-library(dplyr)
-library(magrittr)
-library(googledrive)
-library(googlesheets4)
+# library(strucchange)
+# library(plotly)
+# library(dplyr)
+# library(magrittr)
+# library(googledrive)
+# library(googlesheets4)
 library(readxl)
@@
 
-TargetSpectraLong <- TargetSpectra %>%
+TargetSpectra <- TargetSpectra %>%
   # rename(nm = OLIS.3D.ASCII) %>%
-  separate(col = Filename, into = c("fp1", "fp2", "fp3", "SpectraDate", "Project", "Source", "Range", "Type", "Correction", "Smooth"), sep = "([\\/\\_\\:])", remove = FALSE)
+  separate(col = Filename, into = c("fp1", "fp2", "fp3", "fp4","SpectraDate", "Project", "CultureID", "Range", "Type", "Correction", "Smooth"), sep = "([\\/\\_\\:])", remove = FALSE)
 
-TargetSpectraLong2 <- TargetSpectraLong %>%
-  select(-c(fp1, fp2, fp3, Type, Correction, Smooth)) %>% 
-  rename(CultureID = Source) %>% 
+TargetSpectra <- TargetSpectra %>%
+  select(-c(fp1, fp2, fp3, fp4, Type, Correction, Smooth)) %>% 
   mutate(SpectraDate = str_extract(Filename, "/202[:digit:][:digit:][:digit:][:digit:][:digit:]"),
@@
 
-glimpse(TargetSpectraLong2)
+glimpse(TargetSpectra)
 ```
@@
 ```{r load local multiculticatalog, message = FALSE, warning = FALSE, echo=FALSE}
-gs4_deauth()
 
-# imagine this is the URL or ID of a Sheet readable by anyone (with a link)
-# MultiCulti metadata
-MetaData <- read_sheet("https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0") %>%
-  # read_sheet has an annoying "feature" to set the type of columns it can't parse to a list.
+# MultiCulti metadata filtered to include only runs for Prochlorococcus O2 Project
+CultureCatalog <- readRDS(file = file.path(DataInCatalog, "CultureCatalog.Rds")) %>%
+
   # ggplot/dplyr doesn't like working with a dataframe of lists.
@@
 
-as.data.frame(MetaData)
-
-MetaData <- MetaData %>%
+CultureCatalog <- CultureCatalog %>%
    mutate(ExpDate = ymd(ExpDate),
-          ExpEndDate = ymd_hms(`ExpEndDate`)) %>% 
-  select(-c(...46,...47))
+          ExpEndDate = ymd_hms(`ExpEndDate`))
 
@@
 
-OLISSpectraMeta <- MetaData %>%
-  right_join(., TargetSpectraLong2, by = c("ID" = "CultureID"))
+OLISSpectraMeta <- CultureCatalog %>%
+  right_join(., TargetSpectra, by = c("ID" = "CultureID"))
 
@@
 remove(TargetSpectra)
-remove(TargetSpectraLong)
-remove(TargetSpectraLong2)
-rm(MetaData)
+remove(CultureCatalog)
 
 glimpse(OLISSpectraMeta)
-```
-# remove extra columns from metacatelog
-```{r remove columns}
- OLISSpectraMeta <- OLISSpectraMeta %>% 
-  select(-c(OptodeMeasure,SampleID))
 
@@
 ```
+
 # Read .Rds, Summarize, Combine to single data frame

### 2023-12-04 Code/MetaDataImport.Rmd
Added "Run" column to the CultureCatalog as it is needed subsequent scripts. Saved a new CultureCatalog.Rds

@@
   filter(str_detect(ID,  "MiSa|JuNa|SaAr")) %>% 
-  select(c("PrimaryOperator", "SampleID", "ID", "Strain", "ExpCul", "ExpDate", "ExpStartTime", "Par_ue", "Photoperiod", "Temp_c", "MC", "Tube", "EndDate","O2", "O2_Category", "WL","LightShape", "Optode","OptodeCh","OptodeMeasure", "ExpEndDate"))
+  select(c("PrimaryOperator", "SampleID", "Run", "ID", "Strain", "ExpCul", "ExpDate", "ExpStartTime", "Par_ue", "Photoperiod", "Temp_c", "MC", "Tube", "EndDate","O2", "O2_Category", "WL","LightShape", "Optode","OptodeCh","OptodeMeasure", "ExpEndDate"))
 

### 2023-12-04 Code/OlisImportPurCalc.Rmd
Copied OlisImportCombinedFiles.Rmd This rmd assigns CultureID to columns of Olis .asc files that were combinedinto 1 file. This file does not have a header.
Added chunk names

@@
 RdsData <-  OlisRdsFiles %>%
-    map_df(~readRDS_plus(Flnm = .)) %>% 
-  select(-c(...44,...45))
+    map_df(~readRDS_plus(Flnm = .))
 
@@
  glimpse(OlisSpectraMetaData)
+
 ```
@@
 Find Strain specific average PUR for each spectral color and each growth PAR 
-```{r}
+```{r Calc mean PUR}
 
@@
 
-write_csv(PicoNestedPurOlisData, file = file.path(DataOut, paste(Project, "NestedPurOlisData",".csv",sep = ""),fsep = .Platform$file.sep))
+# write_csv(PicoNestedPurOlisData, file = file.path(DataOut, paste(Project, "NestedPurOlisData",".csv",sep = ""),fsep = .Platform$file.sep))
 
@@
 
-AbsAllStrains
 ```

### 2023-12-06 Code/MetaDataImport.Rmd
Set project variables for Metadata import

--- 2023-12-04 Code/MetaDataImport.Rmd
@@
 DataOut <- file.path("..","Data")
+ProjectRows <- c("MiSa|JuNa|SaAr")
+ProjectCols <- c("PrimaryOperator", "SampleID", "Run", "ID", "Strain", "ExpCul", "ExpDate", "ExpStartTime", "Par_ue", "Photoperiod", "Temp_c", "MC", "Tube", "EndDate","O2", "O2_Category", "WL","LightShape", "Optode","OptodeCh","OptodeMeasure", "ExpEndDate")
 
@@
           ExpEndDate = ymd_hms(`ExpEndDate`)) %>% 
-  filter(str_detect(ID,  "MiSa|JuNa|SaAr")) %>% 
-  select(c("PrimaryOperator", "SampleID", "ID", "Strain", "ExpCul", "ExpDate", "ExpStartTime", "Par_ue", "Photoperiod", "Temp_c", "MC", "Tube", "EndDate","O2", "O2_Category", "WL","LightShape", "Optode","OptodeCh","OptodeMeasure", "ExpEndDate"))
+  filter(str_detect(ID,  ProjectRows)) %>% 
+  select(ProjectCols)
 
-saveRDS(object = CultureCatalog, file = file.path("..", "Data", "CultureCatalog.Rds"))
+saveRDS(object = CultureCatalog, file = file.path("..", "Data", "CultureCatalog.Rds"), compress = "xz")
 

### 2023-12-06 Code/MultiDataImportPico.Rmd
Fixed file path and save compressed .rds

@@
 ---
-title: "MultiDataImportTemplate"
+title: "MultiDataImportPico"
 author:
@@
 library(broom)
-library(knitr)
 library(zoo)
@@
 Project <- "PICO"
-DataIn <- file.path("..","MultiCultiData")
-PlotsPath <- file.path("..","Plots")
-DataOut <- file.path("..","ImportedData")
-#MetaCatalog <- file.path("..","PicoCatalog.csv")
-
-Sensor <- "od-680"
-
-#interactively set the hour of day at which photoperiod starts for later generation of ToD Time of Day
-#replaced by dynamic extraction from the first row of the AbsTime column in the datafile
-#StartHour <- 7
+DataIn <- file.path("..", "Data", "RawData", "MultiCulti")
+DataOut <- file.path("..","Data", "ImportedData", "MultiCultiData")
 
@@
 
+#set Photobiology colors
 ```{r set colours}
@@
 
-# SensorWavebands = c(680, 720)
-# SensorColours = c("red", "black")
-# names(SensorColours) <- SensorWavebands
-# 
-# SensorColours
 ```
@@
 
-gs4_deauth()
+# gs4_deauth()
 
@@
 
-Catalog <- read_sheet("https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0") %>%
+# Catalog <- read_sheet("https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0") %>%
 
@@
   # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.
-  drop_na(WL) %>%
-  mutate(WL = unlist(WL))
-
-as.data.frame(Catalog)
-
-Catalog <- Catalog %>%
-   mutate(ExpDate = ymd(ExpDate),
-          ExpEndDate = ymd_hms(`ExpEndDate`))
+#   drop_na(WL) %>%
+#   mutate(WL = unlist(WL))
+# 
+# as.data.frame(Catalog)
+# 
+# Catalog <- Catalog %>%
+#    mutate(ExpDate = ymd(ExpDate),
+#           ExpEndDate = ymd_hms(`ExpEndDate`))
 
@@
 
-# List previously imported files
+```{r read locally stored metadata from rds}
+
+CultureCatalog <- readRDS(file = file.path("..", "Data","CultureCatalog.Rds"))
+
+```
+
+# List previously imported MultiCulti files
 
@@
 
-for Project that are saved in DataIn and Previously Processed Files
+for Project that are saved in DataIn
 
 ```{r MultiCulti files}
+
 MultiFiles <- list.files(path = DataIn, pattern = Project, full.names = TRUE)
@@
 
-#Run this if Run number exceeds 99.  MC extracted from filename when Runs >99 returns the MC name and RUN #, this removes '_RUN#'
-
 #add ln(value) later
@@
 
-# TargetDataPlotPrelim <- 
   TargetData %>%
@@
 
-# + 
-#     theme(legend.position="none")
-
-# TargetDataPlotPrelim
-
-#cols = vars(Filename),
-
-#, fill = if_else(str_detect(key, "680"), "red", "black")
-
-#
-```
-
-## Save Preliminary Plot to PlotsPath folder if desired
-
-Generates .png for later presentation if needed.
-
-```{r save preliminary plot as .png to folder}
-
- # ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataPlotPrelim",".png",sep = "")), plot = TargetDataPlotPrelim, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
 ```
@@
 ```{r second prelim plot}
-#TargetDataPlotFacet <- 
+
   TargetDataMeta %>% ggplot() +
@@
   labs(colour = "Actinic PAR (nm)")
-
-#TargetDataPlotFacet
 
@@
 
-```
-
-## Save second preliminary plot if desired
-
-```{r save second preliminary plot as .png to folder}
-
- # ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataPlotFacet",".png",sep = "")), plot = TargetDataPlotFacet, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
 ```
@@
 
-TargetDataMetaFilterPlot <- TargetDataMetaFilter %>% 
+TargetDataMetaFilter %>% 
   ggplot() +
@@
   labs(colour = "Actinic PAR (nm)")
-
-TargetDataMetaFilterPlot
-```
-
-Supplementary Growth Plot
-```{r, fig.height = 6, fig.width = 4}
-
-# ExpandTube = 1
-# OD680_x = median(TargetDataMetaFilter$time)
-# OD720_x = median(TargetDataMetaFilter$time)
-# OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 0.2
-# OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD720))
-# TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>%
-#   filter(Tube == ExpandTube) %>%
-#   ggplot() +
-#   geom_point(aes(x = time, y = OD680), colour = "darkgreen", size = 0.1) +
-#   geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
-#   scale_y_continuous(breaks=seq(0, 1.0, by = 0.2)) +
-#   coord_cartesian(ylim = c(0, 1.0)) +
-#   scale_colour_manual(values = MCMIXColours) +
-#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)") +
-#   ggh4x::facet_nested(rows = vars(WL), cols = vars(Strain, Par_ue), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_both)) +
-#   theme_bw()
-# TargetDataMetaFilterExpandPlot
-# 
-# 
-# 
-# Par_ue.labs <- c("Growth Light Intensity: 60 µE")
-# names(Par_ue.labs) <- c("60")
-# WL.labs <- c("Growth Color Light: 660 nm")
-# names(WL.labs) <- c("660")
-# ExpandTube = 1
-# OD680_x = median(TargetDataMetaFilter$time)
-# OD720_x = median(TargetDataMetaFilter$time)
-# OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 0.2
-# OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD720))
-# TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>%
-#   filter(Tube == ExpandTube) %>%
-#   ggplot() +
-#   geom_point(aes(x = time, y = OD680), colour = "darkgreen", size = 0.1) +
-#   geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
-#   scale_y_continuous(breaks=seq(0, 1.0, by = 0.2)) +
-#   coord_cartesian(ylim = c(0, 1.0)) +
-#   scale_colour_manual(values = MCMIXColours) +
-#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)") +
-#   ggh4x::facet_nested(cols = vars(Strain, WL, Par_ue), labeller = labeller(strain = label_value, Photoperiod = label_both, Par_ue = Par_ue.labs, WL = WL.labs)) +
-#   # annotate(geom = "text", x = OD680_x, y = OD680_y, label = ""~OD[680]~"", size = 4.5, colour = "darkgreen", vjust = -14.5, hjust = 2.5) +
-#   # annotate(geom = "text", x = OD720_x, y = OD720_y, label = ""~OD[720]~"", size = 4.5, colour = "blue", vjust = -20, hjust = 2.5) +
-# theme_bw() +
-# theme(strip.text.x = element_text(size = 12),
-#       strip.text.y = element_text(size = 12),
-#       #strip.background = element_rect(color="black", size=0.5, linetype="solid"),
-#       axis.text = element_text(size = 12),
-#       axis.title = element_text(size = 12))
-# 
-# # theme(strip.background = element_rect(color="black", size=1.5, linetype="solid"))
-# 
-# TargetDataMetaFilterExpandPlot
-# # grob <- grobTree(textGrob("Scatter plot", x=0.1,  y=0.95, hjust=0,
-# #   gp=gpar(col="red", fontsize=13, fontface="italic")))
-# #annotation_custom(grob)+facet_wrap(~cyl, scales="free")
-# 
-# 
-# 
-# #labelling dynamically offset from data traces.
-# #use 'median' for 'x' and OD680 + offset for 'y'
-# ExpandTube = 1
-# OD680_x = median(TargetDataMetaFilter$time)
-# OD720_x = median(TargetDataMetaFilter$time) 
-# Light_x = max(TargetDataMetaFilter$time) - 200
-# 
-# OD680_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD680)) + 0.2
-# 
-# OD720_y =  as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select(OD720))
-# 
-# Light_y = as.numeric(TargetDataMetaFilter %>% ungroup() %>% filter(Tube == ExpandTube, time == OD680_x) %>% select( Actinic_par))/1000 + 0.1
-# 
-# TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>% 
-#   filter(Tube == ExpandTube) %>%
-#   ggplot() +
-#   geom_point(aes(x = time, y = OD680), size = 0.1, colour = "darkgreen") +
-#   geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
-#   scale_y_continuous(breaks=seq(0, 1.0, by = 0.2)) +
-#   coord_cartesian(ylim = c(0, 1.0)) +
-#   
-#   # scale_x_continuous(breaks=seq(0, 250, by = 50)) +
-#   # coord_cartesian(xlim = c(0, 250)) +
-#   
-#   scale_colour_manual(values = MCMIXColours) +
-#   geom_point(aes(x = time, y = Actinic_par/1000), colour = "orange",  size = 0.0001) +
-#   #geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
-#   #geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
-#   # scale_x_continuous(breaks=seq(0, 800, by = 125)) +
-#   # coord_cartesian(xlim = c(0, 800)) +
-#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)") +
-#   #facet_grid(rows = vars(O2), cols = vars(Tube, Par_ue, Strain, ID)) +
-#   ggh4x::facet_nested(cols = vars(Strain, WL, Par_ue), labeller = labeller(strain = label_value, Photoperiod = label_both, Par_ue = Par_ue.labs, WL = WL.labs)) +
-#   #annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkgreen") +
-#   #annotate(geom = "text", x = OD720_x, y = OD720_y, label = "OD720", size = 5, colour = "blue") +
-#   #annotate(geom = "text", x = Light_x, y = Light_y, label = "Light level", size = 5, colour = "orange") +
-#   theme_bw() +
-#   theme(strip.text.x = element_text(size = 12),
-#       strip.text.y = element_text(size = 12),
-#       axis.text = element_text(size = 12),
-#       axis.title = element_text(size = 12))
-#   labs(colour = "Actinic PAR (nm)")
-# 
-# TargetDataMetaFilterExpandPlot
 
@@
 
-TargetDataMetaFilterExpandPlot <- TargetDataMetaFilter %>% 
+TargetDataMetaFilter %>% 
   filter(Tube == ExpandTube) %>%
@@
 
-TargetDataMetaFilterExpandPlot
-
-# TargetDataPlotFacet <- TargetDataMeta %>% ggplot() +
-#   geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
-#   geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
-#   scale_x_continuous(breaks=seq(0, 800, by = 125)) +
-#   scale_colour_manual(values = MCMIXColours) +
-#   labs(y = "Optical Density 680nm (OD680)", x = "Elapsed Time (h)") +
-#   facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Par_ue),Strain, as.factor(Tube))) +
-#   theme_bw() +  
-#   labs(colour = "Actinic PAR (nm)")
-
-```
-
-## Save filtered preliminary plot if desired
-
-```{r save filtered preliminary plot as .png to folder}
-# 
-#  ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataMetaFilterPlot",".png",sep = "")), plot = TargetDataMetaFilterPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
-# # 
-#  ggsave(file = file.path(PlotsPath, paste(TargetFileName, "TargetDataMetaFilterExpandPlot",".png",sep = "")), plot = TargetDataMetaFilterExpandPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
 ```
@@
 saveRDS(object = TargetDataMetaFilter, file = file.path(DataOut, paste(TargetFileName, "TargetDataMetaFilter.Rds",  sep = "_")), ascii = FALSE, version = NULL,
-        compress = TRUE, refhook = NULL)
+        compress = "xz", refhook = NULL)
 ```

### 2023-12-06 Code/MultiDataImportPico.Rmd
Fixed import to read unzipped file.

@@
 Project <- "PICO"
-DataIn <- file.path("..", "Data", "RawData", "MultiCulti")
+DataIn <- file.path("..", "Data", "RawData", "MultiCultiData.zip")
 DataOut <- file.path("..","Data", "ImportedData", "MultiCultiData")
@@
 
-MultiFiles <- list.files(path = DataIn, pattern = Project, full.names = TRUE)
+unzip(DataIn, list = TRUE)
 
 #check file names
-MultiFiles
 
@@
 ```{r set TargetFile}
-TargetFile <- "../MultiCultiData/20230413_PICO_MCMIX004_RUN113.csv"
 
-TargetFileName <- str_split(string = TargetFile, "/")[[1]][3] %>%
-  str_remove(pattern = ".csv")
+TargetFile <- unzip(DataIn, "20211223_PICO_MCMIX006_RUN42.csv")
+
+TargetFileName <- str_remove(string = TargetFile, pattern = ".csv")
 
 TargetFileName
+
 ```
@@
 #This generates 'NA' values for ~1,000,000 rows of 'O2'; possibly the temperature rows?
-TargetDataMeta <- left_join(x = TargetDataWide, y= Catalog, by = c("ExpDate", "MC", "Tube"), suffix  = c("_multi", "_cat"))
+TargetDataMeta <- left_join(x = TargetDataWide, y= CultureCatalog, by = c("ExpDate", "MC", "Tube"))
 
@@
 TargetDataMetaFilter <- TargetDataMeta %>%
-  filter(OD680 > 0) %>% # consider this rule for OD720 as well
+  # filter(OD680 > 0) %>% # consider this rule for OD720 as well
   group_by(ID) %>%
@@
 ```{r filterdataplotexpand}
+
 #labelling dynamically offset from data traces.
@@
   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; ID; Tube") +
-  facet_grid(rows = vars(O2), cols = vars(Tube, Par_ue, Strain, ID)) +
+  # facet_grid(rows = vars(O2), cols = vars(Tube, Par_ue, Strain, ID)) +
   annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkblue") +

### 2023-12-06 Code/MultiDataImportPico.Rmd
Changes to read_csv

@@
 
+Skip <- 19
+
 ```
@@
 
-unzip(DataIn, list = TRUE)
-
-#check file names
+#List files in the extracted folder with a ".asc" extension
+# MCFiles <- unzip(DataIn, list = TRUE)
+# MCFiles <- MCFiles[grepl(".csv$", MCFiles$Name), "Name"]
+# print(MCFiles)
 
@@
 
-TargetFile <- unzip(DataIn, "20211223_PICO_MCMIX006_RUN42.csv")
+TargetFile <- "20211223_PICO_MCMIX006_RUN42.csv"
 
-TargetFileName <- str_remove(string = TargetFile, pattern = ".csv")
+# This opens a compressed file without decompressing.
+TargetData <- read_csv(unz(DataIn, TargetFile),  skip = 20, id = "path", col_names = c("key", "time", "abs-time", "value")) %>% 
+  separate(col = path, into = c("path", "Filename"), sep = ":")
 
-TargetFileName
+# TargetFileName <- str_remove(string = TargetFile, pattern = ".csv")
+# 
+# TargetFileName
 
@@
 ```{r fread_plus}
-fread_plus <- function(Flnm, Skip){data.table::fread(file = Flnm, skip = Skip) %>%
-    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(Flnm)$ctime))
-}
+# fread_plus <- function(Flnm, Skip){data.table::fread(file = Flnm, skip = Skip) %>%
+#     mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(Flnm)$ctime))
+# }
 ```
@@
 ```{r Read TargetFile}
-#abs-time is failing because it contains ',' in the variable values; file is actually a .tsv, not a .csv
-#abs-time not currently used?
+# #abs-time is failing because it contains ',' in the variable values; file is actually a .tsv, not a .csv
+# #abs-time not currently used?
+# # TargetData <- fread_plus(Flnm = TargetFile, Skip = "key") %>%
+# # select(-c(V5))
+# 
+# #run this if V5 is the 'value' column
 # TargetData <- fread_plus(Flnm = TargetFile, Skip = "key")  %>%
 #    select(-c(V5))
-
-#run this if V5 is the 'value' column
-TargetData <- fread_plus(Flnm = TargetFile, Skip = "key")  %>%
-   select(-c(V5))
-
-# %>%
-#  select(-c(value)) %>%
-#   rename(value = V5)
-
-TargetData[1:10,]
-
-#check whether all necessary values for 'key' are present; people forget to 'export all' values from PSI
-unique(TargetData$key)
+# TargetData <- fread_plus(Flnm = paste(DataIn, "20211223_PICO_MCMIX006_RUN42.csv", sep = ":"), Skip = "key")  %>%
+#    select(-c(V5))
+# # %>%
+# #  select(-c(value)) %>%
+# #   rename(value = V5)
+# 
+# 
+# TargetData[1:10,]
+# 
+# #check whether all necessary values for 'key' are present; people forget to 'export all' values from PSI
+# unique(TargetData$key)
 ```
@@
 TargetData <- TargetData %>%
-  select(key, time, `abs-time`, value, Filename, CDateTime) %>%
+  select(key, time, `abs-time`, value, Filename) %>% #, CDateTime
   mutate(Tube = str_extract(key, "-[:digit:]"),

### 2023-12-06 Code/MultiDataImportPico.Rmd
read_csv files

@@
 
-Skip <- 19
+Skip <- 20
 
@@
 # This opens a compressed file without decompressing.
-TargetData <- read_csv(unz(DataIn, TargetFile),  skip = 20, id = "path", col_names = c("key", "time", "abs-time", "value")) %>% 
+TargetData <- read_csv(unz(DataIn, TargetFile),  skip = Skip, id = "path", col_names = c("key", "time", "abs-time", "value")) %>% 
   separate(col = path, into = c("path", "Filename"), sep = ":")

### 2023-12-06 Code/MultiDataImportPico.Rmd
Added library(photobiologyWavebands) for WL colors

@@
 negative points needed for current noise filtering, so placed just
-before noise filtering; with more sophisticated noise filtering -add
-dynamic extraction of StartTime from first row of AbsTime Done
+before noise filtering; with more sophisticated noise filtering
 
@@
 library(googlesheets4)
+library(photobiologyWavebands)
 
@@
 ```{r set colours}
-MyWavelengths = c(405, 450, 475, 530, 615, 660, 730, "WW")
-MCMIXColours = c("violet", "darkblue", "dodgerblue", "green","orange","red","purple", "black")
+MyWavelengths = c(405, 445, 470, 530, 620, 660, 730, "WW")
+MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(445), w_length2rgb(470), w_length2rgb(530),            w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black"))
+
+# MyWavelengths = c(450, 530, 660, "WW")
+# MCMIXColours = c(w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "black")
 
@@
 
-# List MultiCulti files
-
-for Project that are saved in DataIn
+# List MultiCulti files for Project that are saved in DataIn
 
@@
 #List files in the extracted folder with a ".asc" extension
-# MCFiles <- unzip(DataIn, list = TRUE)
-# MCFiles <- MCFiles[grepl(".csv$", MCFiles$Name), "Name"]
-# print(MCFiles)
+MCFiles <- unzip(DataIn, list = TRUE)
+MCFiles <- MCFiles[grepl(".csv$", MCFiles$Name), "Name"]
+print(MCFiles)
 
@@
 # Set Target File
+```{r set TargetFile and read csv}
 
-Could implement function to list difference between
-unique(GrowthSummaryAppend\$Filename) and MultiFiles if needed later;
-scan visually to set TargetFile for now.
-
-```{r set TargetFile}
-
-TargetFile <- "20211223_PICO_MCMIX006_RUN42.csv"
+TargetFile <- "20221021_PICO_MCMIX006_RUN96.csv"
 
 # This opens a compressed file without decompressing.
-TargetData <- read_csv(unz(DataIn, TargetFile),  skip = Skip, id = "path", col_names = c("key", "time", "abs-time", "value")) %>% 
-  separate(col = path, into = c("path", "Filename"), sep = ":")
+TargetData <- read_csv(unz(DataIn, TargetFile),  skip = Skip, id = "Path", col_names = c("key", "time", "abs-time", "value")) %>% 
+  separate(col =Path, into = c("Path", "Filename"), sep = ":")
 
-# TargetFileName <- str_remove(string = TargetFile, pattern = ".csv")
-# 
-# TargetFileName
+TargetFileName <- str_remove(string = TargetFile, pattern = ".csv")
+
+TargetFileName
 
@@
 TargetData <- TargetData %>% 
-    mutate(ExpDate = str_extract(Filename, "/202[:digit:][:digit:][:digit:][:digit:][:digit:]_"),
+    mutate(ExpDate = str_extract(Filename, "202[:digit:][:digit:][:digit:][:digit:][:digit:]_"),
            ExpDate = ymd(str_extract(ExpDate, "202[:digit:][:digit:][:digit:][:digit:][:digit:]")))
@@
 
-Run this chunk only for tubes with OD680 and/or OD720 < 0
-This will keep record of tubes even if they did not grow or had negative growth. These tubes get filtered out later if you do not run this chunk
-Remember to comment out after use 
-```{r, Add dummy points if a tube has OD values less than zero}
-
-# TargetDataMeta <- TargetDataMeta %>%
-# mutate(OD680 = if_else(Tube == 1, 0.005, OD680),
-#        OD720 = if_else(Tube == 1, 0.003, OD720))
-
-```
-
-Run this chunk if some tubes have poor data
-This is bad practice;
-Only use if light recordings were actually wrong
-Consider a rule-based filtering to eliminate points after curve reaches peak
-```{r filter aberrant tube(s)}
-# TargetDataMeta <- TargetDataMeta %>%
-#   filter(Tube != 1) %>%
-#   filter(Tube != 8)
-# 
-# TargetDataMeta5 <- TargetDataMeta %>%
-#   filter(Tube == 5,
-#          time <= 300)
-# 
-# TargetDataMeta <- TargetDataMeta %>%
-#   filter(Tube != 5) %>%
-#   rbind(., TargetDataMeta5)
-# 
-# TargetDataMeta %>% ggplot() +
-#   geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
-#   geom_point(aes(x = time, y = OD720), size = 0.01, alpha = 0.1, colour = "black") +
-#   geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
-#   geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
-#   geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
-#   #scale_x_continuous(breaks=seq(0, 800, by = 125)) +
-#   #coord_cartesian(xlim = c(-10, 800)) +
-#   #scale_colour_manual(values = MCMIXColours) +
-#   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
-#   facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, ID)) +
-#   theme_bw() +  
-#   labs(colour = "Actinic PAR (nm)")
-
-```
-
 # Filter OD outliers
@@
 #moving average screen
-MovAvgScreen <- 6
-MovAvgWindow <- 20
+MovAvgScreen <- 6 # 6
+MovAvgWindow <- 20 # 20
 
@@
 #use 'median' for 'x' and OD680 + offset for 'y'
-ExpandTube = 1
+ExpandTube = 2
+
 OD680_x = median(TargetDataMetaFilter$time)

### 2023-12-06 Code/MultiDataImportPico.Rmd
Removed redundant columns from DF before saveRDS

@@
 
-```{r read in all MultiData}
-# MultiData <- MultiFiles %>%
-#   map_df(~fread_plus(Flnm = ., Skip = "key")) %>%
-#   select(-c(V5))
-# 
-# MultiData[1:10,]
-
-# MultiDataTarget <- MultiData %>%
-   #filter(Filename == TargetFile)
-```
-
-```{r TargetFile actinic light NA to 0}
-# TargetData <- TargetData %>%
-#   mutate(value = if_else(grepl("actinic-lights", key), if_else(is.na(value), 0, value), value))
-
-```
-
 # Filter superfluous rows, Add ToD column, extract ExpDate, extract MC,
@@
 
+# some files have "V5"  instead of "value" column
 TargetData <- TargetData %>%
@@
 
+Run this chunk only for tubes with OD680 and/or OD720 < 0
+This will keep record of tubes even if they did not grow or had negative growth. These tubes get filtered out later if you do not run this chunk
+Remember to comment out after use 
+```{r, Add dummy points if a tube has OD values less than zero}
+
+# TargetDataMeta <- TargetDataMeta %>%
+# mutate(OD680 = if_else(Tube == 1, 0.005, OD680),
+#        OD720 = if_else(Tube == 1, 0.003, OD720))
+
+```
+
 # Filter OD outliers
@@
 #moving average screen
-MovAvgScreen <- 6 # 6
-MovAvgWindow <- 20 # 20
+MovAvgScreen <- 2 # 6
+MovAvgWindow <- 2 # 20
 
 TargetDataMetaFilter <- TargetDataMeta %>%
-  # filter(OD680 > 0) %>% # consider this rule for OD720 as well
+ filter(OD680 > 0) %>% # consider this rule for OD720 as well
   group_by(ID) %>%
@@
 ```
-
+# check to confirm filter and ensure there are data points for all 8 tubes.
+If there is a missing tube, confirm that data was filtered out because OD680 and/or OD720 <0.
+If this is the case run the chunk "Add dummy points if a tube has OD values less than zero" above and rerun subsequent chunks.
 ```{r filterdataplot}
@@
 
+```{r remove redundant columns}
+
+TargetDataMetaFilter <- TargetDataMetaFilter %>% 
+select(-c("MovMAD680", "MovMAD720",  "MovMedian680", "MovMedian720", "IsMovMAD680Outlier", "IsMovMAD720Outlier","ActinicMin_parOD680", "ActinicMid_parOD680", "ActinicMin_parOD720", "ActinicMid_intervalOD720", "abs_time" , "TimeFlag"))
+
+```
+
 # Save .Rds of Imported Data from TargetFile

### 2023-12-07 Code/MultiDataProcessPico.Rmd
Added MultiCulti Process rmd to Git

---
title: "MultiDataProcessPico"
author:
- Laurel Genge
- Carlie Barnhill
- Max Berthold
- Douglas A. Campbell
- Mireille Savoie
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

## Set figure caption font size
```{css, echo=FALSE}
p.caption {
  font-size: 18px;
}
```

## Set Chunk Options
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Implement logistic and other growth curve fits to MultiCulti growth trajectories.

# Load Libraries and set project variables
Run only first time in session

```{r load libraries}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(zoo)
#library(tidyquant)
#library(data.table)
#library(googledrive)
#library(googlesheets4)
library(minpack.lm)
#library(dplyr)

#attach psych for harmonic.mean() for averaging rates
#library(psych)
#library(RcppRoll) #replaced by zoo::rollmean for rolling mean consistent with MultiDataImportPico.Rmd usage

```

Run only first time in session

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("ImportedData")
PlotsPath <- file.path("..","Plots")
DataOut <- file.path("ProcessedData", "MultiCultiData")

InitialTime <- 24 #hours to filter off start of data set to eliminate initial fluctuations common in SS120

ReplaceOD <- 0.0001 #replace OD720 and/or deltaOD when log of original OD results in NAN or infinite #

TruncFactor = 0.5 # fraction of max OD for truncating full growth trajectory to compare mu.

GrowthFlagError <- 0.20 # percentage of growth parameter is flagged as growth when std error is less than xx of mu .

Sensor <- "od-680"

RollWindow = 20 #measurements every 5 min; 20 points is 1 h to generate rolling averages

OD720GrowthFlagValue = 0.010 # OD720 absolute change for setting GrowthFlag = 1 and DeclineFlag = 1; did culture show  growth;

deltaODGrowthFlagValue = 0.007 #deltaOD absolute change for setting GrowthFlag = 1 and DeclineFlag = 1; did culture show  growth;

GrowthAmpWindow = 14 * 24 # maximum hours to determine if cultures doubled.

MaxAmpHour <- 48  # used to determine if max OD was achieved within xx hours which then is used to calculate growthAmp on decline growth.

DeclineWindow <- 12 #duration in hours overwhich we test for decline from max by amplitude GrowthFlagValue in OD720 or deltaOD

#set the hour of day at which photoperiod starts for later generation of ToD Time of Day
#replaced by extraction of StartHour from first row of data file in MultiDataImport.Rmd
#StartHour <- 6
#EndHour <- 18

```

Run only first time in session

```{r set colours}
MyWavelengths = c(405, 450, 470, 530, 620, 660, 730, "WW")
MCMIXColours = c("violet", "darkblue", "dodgerblue", "green","orange","red","purple", "black")

names(MCMIXColours) <- MyWavelengths
MCMIXColours
```

# List previously processed files

Run only first time in session

```{r previously processed files}
list.files(path = DataOut, pattern = Project, full.names = TRUE)

```

# List available tidied, organized .Rds files of MultiCulti data.

Exported from runs of MultiDataImport.Rmd Run only first time in session

```{r list tidied data files}
list.files(path = DataIn, pattern = Project, full.names = TRUE)

```

# Select and Read ProcessFile

Run for each file in a session; all chunks below run for each file.

Moving this template to a working project folder will need editing of this file path to a relative path within the project folder.
```{r read ProcessFile}
ProcessFile <- "ImportedData/20220929_PICO_MCMIX006_RUN92_TargetDataMetaFilter.Rds"

ProcessFileName <- str_split(string = ProcessFile, "/")[[1]][2] %>%
  str_remove(pattern = ".Rds") %>%
  str_remove(pattern = "_TargetDataMetaFilter")
ProcessFileName

ProcessData <- readRDS(ProcessFile)  %>%
  ungroup()

colnames(ProcessData)
```

Remove extraneous columns from ProcessData; could have been done at end of MultiDataImport.Rmd

SS120 show anomalous jump in OD720 within first 24 h after inoculation.
Therefore we add a filter to remove the first InitialTime  from all SS120 runs.
```{r filter initial data  ProcessData}

ProcessData <- ProcessData %>%
  filter(Strain == "SS120" & time >= InitialTime |
         Strain == "MIT9313" |
         Strain =="MED4"  )

```

```{r remove problem tube}

# ProcessData <- ProcessData %>%
#   filter(Tube !=4)

```

```{r filter time tube specific}

# ProcessData <- ProcessData %>%
#   filter(Tube == 1 |
#          Tube == 2 |
#          Tube == 3 & time >= 24 & time <= 125  |
#          Tube == 4 |
#          Tube == 5 |
#          Tube == 6 |
#          Tube == 7 |
#          Tube == 8 )

```

Add deltaOD columns; filter for failed ln; add lognorm columns; add lagseed for each tube
```{r add columns for fitting}

ProcessData <- ProcessData %>%
  mutate(deltaOD = OD680 - OD720) %>%
  filter(!is.infinite(log(OD720))) %>%
  filter(!is.infinite(log(OD680))) %>%
  filter(!is.nan(log(OD720))) %>%
  filter(!is.nan(log(OD680))) %>%
  mutate(#log of zero results in -infinite #'s. Replace with 0.0001. Replacing with 0 creates very low (10e-20) rollmeans which results in very high log normalized values further on in this chunk.
       deltaOD = if_else(!is.infinite(log(deltaOD)), deltaOD, ReplaceOD),
       deltaOD = if_else(!is.nan(log(deltaOD)), deltaOD, ReplaceOD)
        )

#lognormOD720 and deltaOD for Gompertz
#using RcppRoll functions to find the minimum of a k point window to lower noise in normalizations

ProcessData <- ProcessData %>%
  group_by(Tube) %>%
  mutate(rollmeanOD720 = zoo::rollmean(OD720, k = RollWindow, align = "left", fill = NA),
         rollmeandeltaOD = zoo::rollmean(deltaOD, k = RollWindow, align = "left", fill = NA),
         lognormOD720 = if_else(OD720 == (min(rollmeanOD720, na.rm = TRUE)), ReplaceOD, log(OD720/min(rollmeanOD720, na.rm = TRUE))),
         lognormdeltaOD = if_else(deltaOD == (min(rollmeandeltaOD, na.rm = TRUE)), ReplaceOD, log(deltaOD/min(rollmeandeltaOD, na.rm = TRUE)))) %>%
  mutate(LagSeedOD720 = time[which.min(rollmeanOD720)],
         LagSeeddeltaOD = time[which.min(rollmeandeltaOD)]
         ) %>%
  ungroup()

```

# Generate a plot of the data in the selected tidied MultiCulti file.
# Remember data has been filtered to remove first InitialTime h after start of Multiculti program, which is actually InitialTime + ~18 h after inoculation.

```{r prelim ProcessPlot}
#Run <- c("MultiCulti/20200124_PICO_MCMIX004_RUN1.csv", "MultiCulti/20200124_PICO_MCMIX006_RUN2.csv")

ProcessData %>%
  ggplot() +
  geom_point(aes(x = time, y = OD720), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/1000, colour = as.factor(WL)), size = 0.05) +
   geom_vline(aes(xintercept = 1 * 24), linetype = "dashed") + 
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
  #filter(Tube == 5) %>%
  ggplot() +
  geom_point(aes(x = time, y = log(OD720)), size = 0.1) +
  geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
 # filter(Tube == 1) %>%
  ggplot() +
  geom_point(aes(x = time, y = deltaOD), size = 0.1) +
   geom_vline(aes(xintercept = 1 * 24), linetype = "dashed") + 
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
 # filter(Tube == 1) %>%
  ggplot() +
  geom_point(aes(x = time, y = lognormOD720), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
 # filter(Tube == 1) %>%
  ggplot() +
  geom_point(aes(x = time, y = lognormdeltaOD), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
 filter(Tube == 5) %>%
  ggplot() +
  geom_point(aes(x = time, y = deltaOD), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()
```

# For split files only; select the interval that covers before the change in actinic light
```{r Interval Data for split files}
#even multiples of 24 + StartHour to start at photoperiod
# LowerTime <- 24 * 0
# UpperTime <- 24 * 17
# #
# ProcessData <- ProcessData %>%
#   filter(time <= UpperTime)
```

```{r,  remove  decline growth data. Filter x hr after max OD720 and deltaOD }

# ProcessData <- ProcessData %>%
#   group_by(Tube) %>%
#    mutate(TrimRollMeanOD720 = zoo::rollmean(OD720, k = RollWindow, align = "right", fill = NA),
#           TrimRollMeandeltaOD = zoo::rollmean(deltaOD, k = RollWindow, align = "right", fill = NA)
#           ) %>%
#   mutate(DeclineFlagdeltaOD = if_else(time > (time[which.max(TrimRollMeandeltaOD)] + DeclineWindow) & (max(TrimRollMeandeltaOD, na.rm = TRUE) - min(TrimRollMeandeltaOD, na.rm = TRUE)) > deltaODGrowthFlagValue, 1, 0),
#          DeclineFlagOD720 = if_else(time > (time[which.max(TrimRollMeanOD720)] + DeclineWindow) & (max(TrimRollMeanOD720, na.rm = TRUE) - min(TrimRollMeanOD720, na.rm = TRUE)) > OD720GrowthFlagValue, 1, 0)) %>%
#     filter(DeclineFlagdeltaOD == 0,
#            DeclineFlagOD720 == 0) %>%
#   select(-c("TrimRollMeanOD720", "TrimRollMeandeltaOD")) %>%
#   ungroup()
# 
# glimpse(ProcessData)

```

```{r add min meanOD}

ProcessData <- ProcessData %>%
  group_by(Tube) %>%
   mutate(minRollMeanOD720 = min(rollmeanOD720, na.rm = TRUE),
          minRollMeandeltaOD = min(rollmeandeltaOD, na.rm = TRUE)) %>% 
  ungroup()

glimpse(ProcessData)

```

```{r plot filtered data}

ProcessData %>%
  ggplot() +
  geom_point(aes(x = time, y = OD720), size = 0.1) +
 # geom_point(aes(x = time, y = Actinic_par/1000, colour = as.factor(WL)), size = 0.05) +
   geom_vline(aes(xintercept = 1 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
  #filter(Tube == 5) %>%
  ggplot() +
  geom_point(aes(x = time, y = log(OD720)), size = 0.1) +
  geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
   geom_vline(aes(xintercept = 1 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
 # filter(Tube == 1) %>%
  ggplot() +
  geom_point(aes(x = time, y = deltaOD), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
   geom_vline(aes(xintercept = 1 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
 # filter(Tube == 1) %>%
  ggplot() +
  geom_point(aes(x = time, y = lognormOD720), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
 # filter(Tube == 6) %>%
  ggplot() +
  geom_point(aes(x = time, y = lognormdeltaOD), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
 filter(Tube == 6) %>%
  ggplot() +
  geom_point(aes(x = time, y = lognormdeltaOD), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

ProcessData %>%
 filter(Tube == 6) %>%
  ggplot() +
  geom_point(aes(x = time, y = deltaOD), size = 0.1) +
  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
  theme_bw()

```

# Attempt  Fits of Data
Create R function for logistic equation.
Check with Max for alternate formulations that include lag?
Consider which parameter(s) to report for comparison(s) of strain responses to growth conditions
  -mu
  -Pmax
  -other...
```{r fitting functions, message = FALSE}
#define a logistic equation as a function.
#x will be taken from 'time' when we run the fit.
logistic_eqn <- function(x, Lmax, Lmu, Lintercept){(Lmax*Lintercept*exp(Lmu*x))/(Lmax + (Lintercept*(exp(Lmu*x)-1)))}

#Modified Gompertz equation
ModGompertzEqn <- function(x,GLag,Gmax,Gmu){(Gmax*(exp(-exp((Gmu*exp(1))/Gmax*(GLag-x)+1))))}

# Exponential equation 
exp_eqn <- function(x, Emu, Eintercept){(Eintercept*exp(x*Emu))}

#Estimate absolute amplitude of growth
growth_amp <- function(y){(max(as.numeric(y), na.rm = TRUE) - min(as.numeric(y), na.rm = TRUE))}

#returns a negative absolute amplitude of growth if OD decline
growth_amp_decline <- function(y){(min(as.numeric(y), na.rm = TRUE)) - max(as.numeric(y), na.rm = TRUE)}

# bob <- c(1,2,4,5,6,7)
# 
# growth_amp(y = bob)

```

# As of Dec 2023 all the na_if code are not working so are commented out
```{r nested regressions }

#nest must include all variables that have more than one value for a given tube nest.
#filtering to remove negative lognorm data only upon transition to ProcessDataNestGrowth and fitting; could do earlier?
ProcessDataNestGrowth  <- ProcessData %>%
  filter(lognormdeltaOD >= 0) %>%
  filter(lognormOD720 >= 0) %>%
nest(tubedata = c(time, ToD, Day, Actinic_par, OD680, OD720, deltaOD, ActinicMid_parOD720, ActinicMid_dayOD720,rollmeanOD720,rollmeandeltaOD,lognormOD720, lognormdeltaOD, LagSeedOD720, LagSeeddeltaOD))

#test of nesting
nrow(ProcessDataNestGrowth)

ProcessDataNestGrowth <- ProcessDataNestGrowth %>%
  mutate(OD720_logistic = map(tubedata, possibly(~nlsLM(OD720 ~ logistic_eqn(x = time, Lmax, Lmu, Lintercept),
                            data = .x,
                            start = list(Lmax = max(.$rollmeanOD720, na.rm = TRUE),  Lmu = (log(max(.$rollmeanOD720, na.rm = TRUE)) - log(min(.$rollmeanOD720, na.rm = TRUE)))/max(.$time), Lintercept = min(.$rollmeanOD720, na.rm = TRUE)),
                            control = list(maxiter = 500)), otherwise = NULL)),
         OD720_logistic_tidied =  map(OD720_logistic, possibly(tidy, otherwise = NULL)),
         OD720_logistic_param = map(OD720_logistic,possibly(glance, otherwise = NULL)),
         OD720_logistic_predict = map(OD720_logistic, possibly(augment, otherwise = NULL))
         ) %>%
  mutate(OD720_TimetoMax = map(.x = OD720_logistic_predict, possibly(~.$time[which.max(.$`.fitted`)], otherwise = NULL))  
         ) %>% 
  mutate(OD720_TimetoMax = as.numeric(ifelse(OD720_TimetoMax == "NULL" , NA, OD720_TimetoMax))
         ) %>%
  mutate(OD720trunc_logistic = map(tubedata, possibly(~nlsLM(OD720 ~ logistic_eqn(x = time, Lmax, Lmu, Lintercept),
                            data = .x %>%
                            filter(OD720 <= (max(OD720) * TruncFactor)),
                            start = list(Lmax = max(.$rollmeanOD720, na.rm = TRUE),  Lmu = (log(max(.$rollmeanOD720, na.rm = TRUE)) - log(min(.$rollmeanOD720, na.rm = TRUE)))/max(.$time), Lintercept = min(.$rollmeanOD720, na.rm = TRUE)),
                            control = list(maxiter = 500)), otherwise = NULL)),
         OD720trunc_logistic_tidied =  map(OD720trunc_logistic, possibly(tidy, otherwise = NULL)),
         OD720trunc_logistic_param = map(OD720trunc_logistic,possibly(glance, otherwise = NULL)),
         OD720trunc_logistic_predict = map(OD720trunc_logistic, possibly(augment, otherwise = NULL))
         ) %>%
  mutate(OD720trunc_TimetoMax = map(.x = OD720trunc_logistic_predict, possibly(~.$time[which.max(.$`.fitted`)], otherwise = NULL))  
         ) %>%  
  mutate(OD720trunc_TimetoMax = as.numeric(ifelse(OD720trunc_TimetoMax == "NULL" , NA, OD720trunc_TimetoMax))
         ) %>%
   mutate(deltaOD_logistic = map(tubedata, possibly(~nlsLM(deltaOD ~ logistic_eqn(x = time, Lmax, Lmu, Lintercept),
                            data = .x,
                            start = list(Lmax = max(.$rollmeandeltaOD, na.rm = TRUE),  Lmu = (log(max(.$rollmeandeltaOD, na.rm = TRUE)) - log(min(.$rollmeandeltaOD, na.rm =  TRUE)))/max(.$time), Lintercept = min(.$rollmeandeltaOD, na.rm = TRUE)),
                            control = list(maxiter = 500)), otherwise = NULL)),
         deltaOD_logistic_tidied =  map(deltaOD_logistic, possibly(tidy, otherwise = NULL)),
         deltaOD_logistic_param = map(deltaOD_logistic,possibly(glance, otherwise = NULL)),
         deltaOD_logistic_predict = map(deltaOD_logistic, possibly(augment, otherwise = NULL))
         ) %>%
  mutate(deltaOD_TimetoMax = map(.x = deltaOD_logistic_predict, possibly(~.$time[which.max(.$`.fitted`)], otherwise = NA))  
         ) %>% 
  mutate(deltaOD_TimetoMax = as.numeric(ifelse(deltaOD_TimetoMax == "NULL" , NA, deltaOD_TimetoMax))
         ) %>%
   mutate(deltaODtrunc_logistic = map(tubedata, possibly(~nlsLM(deltaOD ~ logistic_eqn(x = time, Lmax, Lmu, Lintercept),
                            data = .x %>%
                            filter(deltaOD <= (max(deltaOD) * TruncFactor)),
                            start = list(Lmax = max(.$rollmeandeltaOD, na.rm = TRUE),  Lmu = (log(max(.$rollmeandeltaOD, na.rm = TRUE)) - log(min(.$rollmeandeltaOD, na.rm = TRUE)))/max(.$time), Lintercept = min(.$rollmeandeltaOD, na.rm = TRUE)),
                            control = list(maxiter = 500)), otherwise = NULL)),
         deltaODtrunc_logistic_tidied =  map(deltaODtrunc_logistic, possibly(tidy, otherwise = NULL)),
         deltaODtrunc_logistic_param = map(deltaODtrunc_logistic, possibly(glance, otherwise = NULL)),
         deltaODtrunc_logistic_predict = map(deltaODtrunc_logistic, possibly(augment, otherwise = NULL))
         ) %>%
   mutate(deltaODtrunc_TimetoMax = map(.x = deltaODtrunc_logistic_predict, possibly(~.$time[which.max(.$`.fitted`)], otherwise = NULL))  
         ) %>%  
  mutate(deltaODtrunc_TimetoMax = as.numeric(ifelse(deltaODtrunc_TimetoMax == "NULL" , NA, deltaOD_TimetoMax))
         ) %>%
   mutate(GrowthAmpdeltaOD = if_else(deltaOD_TimetoMax <= MaxAmpHour | is.na(deltaOD_TimetoMax), map(tubedata, ~growth_amp_decline(y = .$rollmeandeltaOD)), map(tubedata, ~growth_amp(y = .$rollmeandeltaOD))),
          GrowthAmpOD720 = if_else(OD720_TimetoMax <= MaxAmpHour | is.na(OD720_TimetoMax), map(tubedata, ~growth_amp_decline(y = .$rollmeanOD720)), map(tubedata, ~growth_amp(y = .$rollmeanOD720)))
         ) %>%
   mutate(GrowthAmpdeltaODFlag = if_else(GrowthAmpdeltaOD >= deltaODGrowthFlagValue , 1, 0),
           GrowthAmpOD720Flag = if_else(GrowthAmpOD720 >= OD720GrowthFlagValue, 1, 0)
           )

#XXXDoug 16 May 2022XXX
# %>%
#    mutate(IsOD720_GLagNeg = if_else(lognormOD720_GompLag <= 0, 1, 0), # fails here because of Nulls generated line 437
#           IsdeltaOD_GLagNeg = if_else(lognormdeltaOD_GompLag <= 0, 1, 0))
#

#Growthamp flags for growth up to 14 days 
ProcessDataNestGrowth2 <- ProcessDataNestGrowth %>%
  unnest(c(tubedata)) %>%
   filter(time <= GrowthAmpWindow) %>%
  nest(tubedata = c(time, ToD, Day, Actinic_par, OD680, OD720, deltaOD, ActinicMid_parOD720,
                  ActinicMid_dayOD720,rollmeanOD720,rollmeandeltaOD,lognormOD720, lognormdeltaOD, LagSeedOD720, LagSeeddeltaOD)) %>%
   mutate(GrowthAmpdeltaOD_14days = if_else(deltaOD_TimetoMax <= MaxAmpHour | is.na(deltaOD_TimetoMax), map(tubedata, ~growth_amp_decline(y = .$rollmeandeltaOD)), map(tubedata, ~growth_amp(y = .$rollmeandeltaOD))),
          GrowthAmpOD720_14days = if_else(OD720_TimetoMax <= MaxAmpHour| is.na(OD720_TimetoMax) , map(tubedata, ~growth_amp_decline(y = .$rollmeanOD720)), map(tubedata, ~growth_amp(y = .$rollmeanOD720))),
          minRollMeanOD720_14days = map(tubedata, ~min(.$rollmeanOD720, na.rm = TRUE)),
          maxRollMeanOD720_14days = map(tubedata, ~max(.$rollmeanOD720, na.rm = TRUE)),
          minRollMeandeltaOD_14days = map(tubedata, ~min(.$rollmeandeltaOD, na.rm = TRUE)),
          maxRollMeandeltaOD_14days = map(tubedata, ~max(.$rollmeandeltaOD, na.rm = TRUE)),
          minRollMeanOD720_14days = as.numeric(minRollMeanOD720_14days),
          maxRollMeanOD720_14days = as.numeric(maxRollMeanOD720_14days),
          minRollMeandeltaOD_14days = as.numeric(minRollMeandeltaOD_14days),
          maxRollMeandeltaOD_14days = as.numeric(maxRollMeandeltaOD_14days)
           ) %>%
      mutate(GrowthAmpdeltaODFlag_14days = if_else(GrowthAmpdeltaOD_14days >= deltaODGrowthFlagValue, 1, 0),
             GrowthAmpOD720Flag_14days = if_else(GrowthAmpOD720_14days >= OD720GrowthFlagValue, 1, 0)
      ) %>% 
       mutate(DoubleOD720Flag_14days = if_else(maxRollMeanOD720_14days >= minRollMeanOD720_14days * 2 & !is.na(OD720_TimetoMax) >= MaxAmpHour & !is.na(OD720_TimetoMax) & GrowthAmpOD720_14days >= 0, 1, 0),
             DoubledeltaODFlag_14days = if_else(maxRollMeandeltaOD_14days >= minRollMeandeltaOD_14days * 2 & !is.na(deltaOD_TimetoMax) >= MaxAmpHour & !is.na(deltaOD_TimetoMax) & GrowthAmpdeltaOD_14days >= 0, 1, 0)
           )

ProcessDataNestGrowth <- ProcessDataNestGrowth %>%
  left_join(., ProcessDataNestGrowth2 %>% select(Tube, GrowthAmpdeltaOD_14days, GrowthAmpOD720_14days,  minRollMeanOD720_14days, maxRollMeanOD720_14days, minRollMeandeltaOD_14days, maxRollMeandeltaOD_14days, GrowthAmpdeltaODFlag_14days, GrowthAmpOD720Flag_14days, DoubledeltaODFlag_14days, DoubleOD720Flag_14days), by = "Tube")

remove(ProcessDataNestGrowth2)

#failed attempt with map2
# test = map2(.x = lognormOD720_Gompertz_tidied, .y = lognormOD720_Gompertz_predict, ~if_else(as.numeric(~pluck(.x, 2, 1)) <= as.numeric(~.y$time[which.max(.$`.fitted`)]), 1, 0))
```
```{r}
glimpse(ProcessDataNestGrowth)
```

```{r filter }
ProcessDataNestGrowth <- ProcessDataNestGrowth %>% 
  select(-contains(c("trunc", "Gompertz", "Gomp", "OD720_G", "deltaOD_G")))
```

# Save .Rds of ProcessDataNestGrowth containing logistic and gompertz fits of growth data from time resolved and whole interval fits.
This .Rds is the substrate for the 'MultiCultiCompare.Rmd to compare information across multiple runs.
```{r save rds}

 saveRDS(object = ProcessDataNestGrowth, file = file.path(DataOut, paste(ProcessFileName,  "ProcessDataNestGrowth.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

```

```{r test fits}
#Chunk to work out additions of new fit models

# testamp <- ProcessData %>%
#   filter(lognormdeltaOD > 0) %>%
#   filter(lognormOD720 > 0) %>%
# nest(tubedata = c(time,  ToD, Day, Actinic_par, OD680, OD720, deltaOD, ActinicMid_parOD720, ActinicMid_dayOD720,rollmeanOD720,rollmeandeltaOD,lognormOD720, lognormdeltaOD, LagSeedOD720, LagSeeddeltaOD)) %>%
#   mutate(GrowthAmpdeltaOD = map(tubedata, ~growth_amp(y = .$rollmeandeltaOD)))
#

```

```{r plot logistics predictions}
#improve with automated annotate placement based upon data traces; difficulty is that data is nested until expansion for ggplot b/c we need to conserve memory so data traces are not easily accessible
# segmentYstart <- as.numeric(IntervalDataTube1[IntervalDataTube1$time == 52, "lnOD680"])
# segmentYend <- as.numeric(IntervalDataTube1[IntervalDataTube1$time == 54, "lnOD680"])

OD_x = 7
OD_y = 0.15

Par_x = 15
Par_y = 0.04

Resid_x = 3
Resid_y = -0.03

Predict_x = 4
Predict_y = 0.06

# #predictions of condition specific fits
OD720LogGrowthPlot <-ProcessDataNestGrowth %>%
#drop_na(OD720_logistic) %>%
  mutate(OD720_logistic_predict = map(OD720_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, OD720_logistic_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_OD720), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.resid), colour = "gold", size = 0.05) +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
#scale_x_continuous(breaks=seq(0, 25, by = 5)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "OD720 Logistic:  Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "Optical Density (OD720)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

OD720LogGrowthPlot

deltaODLogGrowthPlot <- ProcessDataNestGrowth %>%
  mutate(deltaOD_logistic_predict = map(deltaOD_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_deltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.resid), colour = "gold", size = 0.05) +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "DeltaOD Logistic:   Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "Delta Optical Density (deltaOD)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

deltaODLogGrowthPlot

ProcessDataNestGrowth %>%
  filter(Tube == 5) %>%
  mutate(OD720_logistic_predict = map(OD720_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, OD720_logistic_predict),names_sep = "_") %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_OD720), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.resid), colour = "gold", size = 0.05, alpha = 0.5) +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.01, alpha = 0.1) +
  #coord_cartesian(xlim = c(0, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  annotate(geom = "text", x = OD_x, y = OD_y, label = "OD720", size = 5, colour = "darkgreen") +
  annotate(geom = "text", x = Par_x, y = Par_y, label = "Light level", size = 5, colour = "darkblue") +
  annotate(geom = "text", x = Resid_x, y = Resid_y, label = "Model residuals", size = 5, colour = "red") +
  annotate(geom = "text", x = Predict_x, y = Predict_y, label = "Logistic Regression", size = 5, colour = "black") +
  labs(subtitle = "Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName , y = "Optical Density (OD720)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)") +
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

ProcessDataNestGrowth %>%
  #drop_na(deltaOD_logistic) %>%
  filter(Tube == 6) %>%
  mutate(deltaOD_logistic_predict = map(deltaOD_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_") %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_deltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.resid), colour = "gold", size = 0.05, alpha = 0.5) +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.01, alpha = 0.1) +
  #coord_cartesian(xlim = c(0, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  annotate(geom = "text", x = OD_x, y = OD_y, label = "deltaOD", size = 5, colour = "darkgreen") +
  annotate(geom = "text", x = Par_x, y = Par_y, label = "Light level", size = 5, colour = "darkblue") +
  annotate(geom = "text", x = Resid_x, y = Resid_y, label = "Model residuals", size = 5, colour = "red") +
  annotate(geom = "text", x = Predict_x, y = Predict_y, label = "Logistic Regression", size = 5, colour = "black") +
  labs(subtitle = "Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName , y = "Delta Optical Density (deltaOD)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)") +
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

ProcessDataNestGrowth %>%
 mutate(OD720trunc_logistic_predict = map(OD720trunc_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(OD720trunc_logistic_predict), names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_OD720), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
 # geom_text(data = . %>% filter(GrowthFlag_OD720 == 0), aes(x = 200, y = 0.2, label = "*"), size = 5) +
  geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_.resid), colour = "gold", size = 0.05) + 
  #geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "Dynamically Truncated Logistic Growth Curve (50% of max OD720):  Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "Optical Density (OD720)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

ProcessDataNestGrowth %>%
  mutate(deltaODtrunc_logistic_predict = map(deltaODtrunc_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(deltaODtrunc_logistic_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = deltaODtrunc_logistic_predict_deltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = deltaODtrunc_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = deltaODtrunc_logistic_predict_.resid), colour = "gold", size = 0.05) +
  #geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "Dynamically Truncated Logistic Growth Curve (50% of max deltaOD):   Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "Delta Optical Density (deltaOD)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

ProcessDataNestGrowth %>%
  filter(Tube == 5) %>%
  mutate(OD720trunc_logistic_predict = map(OD720trunc_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(OD720trunc_logistic_predict),names_sep = "_") %>%
  ggplot() +
  geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_OD720), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_.resid), colour = "gold", size = 0.05, alpha = 0.5) +
 # geom_point(aes(x = OD720trunc_logistic_predict_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.01, alpha = 0.1) +
  #coord_cartesian(xlim = c(0, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  annotate(geom = "text", x = OD_x, y = OD_y, label = "OD720", size = 5, colour = "darkgreen") +
  annotate(geom = "text", x = Par_x, y = Par_y, label = "Light level", size = 5, colour = "darkblue") +
  annotate(geom = "text", x = Resid_x, y = Resid_y, label = "Model residuals", size = 5, colour = "red") +
  annotate(geom = "text", x = Predict_x, y = Predict_y, label = "Logistic Regression", size = 5, colour = "black") +
  labs(subtitle = "Dynamically Truncated Logistic Growth Curve:  Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName , y = "Optical Density (OD720)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)") +
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

ProcessDataNestGrowth %>%
  filter(Tube == 5) %>%
  mutate(deltaODtrunc_logistic_predict = map(deltaODtrunc_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(deltaODtrunc_logistic_predict),names_sep = "_") %>%
  ggplot() +
  geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = deltaODtrunc_logistic_predict_deltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = deltaODtrunc_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = deltaODtrunc_logistic_predict_.resid), colour = "gold", size = 0.05, alpha = 0.5) +
 # geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.01, alpha = 0.1) +
  #coord_cartesian(xlim = c(0, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  annotate(geom = "text", x = OD_x, y = OD_y, label = "deltaOD", size = 5, colour = "darkgreen") +
  annotate(geom = "text", x = Par_x, y = Par_y, label = "Light level", size = 5, colour = "darkblue") +
  annotate(geom = "text", x = Resid_x, y = Resid_y, label = "Model residuals", size = 5, colour = "red") +
  annotate(geom = "text", x = Predict_x, y = Predict_y, label = "Logistic Regression", size = 5, colour = "black") +
  labs(subtitle = "Dynamically Truncated Logistic Growth Curve:  Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName , y = "Delta Optical Density (deltaOD)", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)") +
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

lognormOD720GompertzGrowthPlot <- ProcessDataNestGrowth %>%
  mutate(lognormOD720_Gompertz_predict = map(lognormOD720_Gompertz, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, lognormOD720_Gompertz_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_lognormOD720), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = lognormOD720_Gompertz_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = lognormOD720_Gompertz_predict_.resid), colour = "gold", size = 0.05) +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "lognormOD720_Gompertz; Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "lognormOD720", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+ 
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

lognormOD720GompertzGrowthPlot

ProcessDataNestGrowth %>%
  filter(Tube == 5) %>%
  mutate(lognormOD720_Gompertz_predict = map(lognormOD720_Gompertz, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, lognormOD720_Gompertz_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_lognormOD720), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = lognormOD720_Gompertz_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = lognormOD720_Gompertz_predict_.resid), colour = "gold", size = 0.05) +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "lognormOD720_Gompertz; Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "lognormOD720", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+ 
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

lognormdeltaODGompertzGrowthPlot <- ProcessDataNestGrowth %>%
  mutate(lognormdeltaOD_Gompertz_predict = map(lognormdeltaOD_Gompertz, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, lognormdeltaOD_Gompertz_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_lognormdeltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.resid), colour = "gold", size = 0.05) +geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "lognormdeltaOD_Gompertz; Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "lognormdeltaOD", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+ 
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

lognormdeltaODGompertzGrowthPlot

ProcessDataNestGrowth %>%
  filter(Tube == 2) %>%
  mutate(lognormdeltaOD_Gompertz_predict = map(lognormdeltaOD_Gompertz, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, lognormdeltaOD_Gompertz_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_lognormdeltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.resid), colour = "gold", size = 0.05) +geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
  labs(subtitle = "lognormdeltaOD_Gompertz; Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "lognormdeltaOD", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+ 
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

ProcessDataNestGrowth %>%
  filter(Tube == 5) %>%
  mutate(PhotoperiodLabel = "Photoperiod",
         OxygenLabel = "Oxygen level") %>% 
  mutate(lognormdeltaOD_Gompertz_predict = map(lognormdeltaOD_Gompertz, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, lognormdeltaOD_Gompertz_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_lognormdeltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.resid), colour = "gold", size = 0.05) +geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
   facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
 # guides(fill = "none") +
  labs(subtitle = "lognormdeltaOD_Gompertz; Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "lognormdeltaOD", x = "Elapsed Time (h)") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")+ 
  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))

```

```{r save logistic model plots}
# ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "OD720LogGrowthPlot",".png",sep = "")), plot = OD720LogGrowthPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "deltaODLogGrowthPlot",".png",sep = "")), plot = deltaODLogGrowthPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)

 # ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "OD720LogGrowthPlotExpand",".png",sep = "")), plot = OD720LogGrowthPlotExpand, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
#

 # ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "DeltaODLogGrowthPlotExpand",".png",sep = "")), plot = DeltaODLogGrowthPlotExpand, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)

 # ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "lognormOD720GompertzGrowthPlot",".png",sep = "")), plot = lognormOD720GompertzGrowthPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
 # 
 #  ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "lognormdeltaODGompertzGrowthPlot",".png",sep = "")), plot = lognormdeltaODGompertzGrowthPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)

```

```{r exclude poor fits}
# TestProcessDataNestGrowth %>%
#   filter(Tube != 4)
```

```{r logistic vs gompertz fit plots}

ProcessDataNestGrowth %>%
unnest(cols = c(OD720_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error, OD720_logistic_tidied_statistic, OD720_logistic_tidied_p.value), names_sep = "_")  %>%
  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
         OD720_Lmu = OD720_logistic_tidied_estimate_Lmu,
         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,
         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept)  %>%
  unnest(cols = c(lognormOD720_Gompertz_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  lognormOD720_Gompertz_tidied_term, values_from = c(lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error, lognormOD720_Gompertz_tidied_statistic, lognormOD720_Gompertz_tidied_p.value), names_sep = "_") %>%
  rename(OD720_Gmax = lognormOD720_Gompertz_tidied_estimate_Gmax,
         OD720_Gmax_se = lognormOD720_Gompertz_tidied_std.error_Gmax,
         OD720_Gmu = lognormOD720_Gompertz_tidied_estimate_Gmu,
         OD720_Gmu_se = lognormOD720_Gompertz_tidied_std.error_Gmu,
         OD720_GLag = lognormOD720_Gompertz_tidied_estimate_GLag,             
         OD720_GLag_se = lognormOD720_Gompertz_tidied_std.error_GLag)  %>%
   ggplot() +
  geom_point(aes(x = OD720_Lmu, y = OD720_Gmu, colour = as.factor(WL),  shape = as.factor(IsOD720_GLagNeg)), size = 4)  +
  ggrepel::geom_text_repel(aes(x = OD720_Lmu, y = OD720_Gmu, label= Tube),hjust=0, vjust=0) +
scale_colour_manual(values = MCMIXColours) +
  scale_shape_manual(values = c(13, 16)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  coord_fixed(ratio = 1) +
  coord_cartesian(xlim = c (0, 0.06), ylim = c(0, 0.06)) +
  scale_x_continuous(breaks=seq(0, 0.06, by = 0.02)) +
  labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Gompertz Growth Rate (OD720_Gmu)", x = "Logistic Growth Rate (OD720_Lmu)") +
  facet_grid(rows = vars(Strain), cols = vars(O2, WL)) + 
  theme_bw() + 
  labs(title = "Logistic vs. Gompertz Cell Specific Growth Rates (µ" ~ h^-1~")- All Growth",
       colour = "Actinic PAR (nm)")

ProcessDataNestGrowth %>%
unnest(cols = c(deltaOD_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error, deltaOD_logistic_tidied_statistic, deltaOD_logistic_tidied_p.value), names_sep = "_")  %>%
  rename(deltaOD_Lmax = deltaOD_logistic_tidied_estimate_Lmax,
         deltaOD_Lmax_se = deltaOD_logistic_tidied_std.error_Lmax,
         deltaOD_Lmu = deltaOD_logistic_tidied_estimate_Lmu,
         deltaOD_Lmu_se = deltaOD_logistic_tidied_std.error_Lmu,
         deltaOD_Lintercept = deltaOD_logistic_tidied_estimate_Lintercept,
         deltaOD_Lintercept_se = deltaOD_logistic_tidied_std.error_Lintercept)  %>%
  unnest(cols = c(lognormdeltaOD_Gompertz_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  lognormdeltaOD_Gompertz_tidied_term, values_from = c(lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error, lognormdeltaOD_Gompertz_tidied_statistic, lognormdeltaOD_Gompertz_tidied_p.value), names_sep = "_") %>%
  rename(deltaOD_Gmax = lognormdeltaOD_Gompertz_tidied_estimate_Gmax,
         deltaOD_Gmax_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmax,
         deltaOD_Gmu = lognormdeltaOD_Gompertz_tidied_estimate_Gmu,
         deltaOD_Gmu_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmu,
         deltaOD_GLag = lognormdeltaOD_Gompertz_tidied_estimate_GLag,             
         deltaOD_GLag_se = lognormdeltaOD_Gompertz_tidied_std.error_GLag)  %>%
   ggplot() +
  geom_point(aes(x = deltaOD_Lmu, y = deltaOD_Gmu, colour = as.factor(WL),  shape = as.factor(IsdeltaOD_GLagNeg)), size = 4) +
  ggrepel::geom_text_repel(aes(x = deltaOD_Lmu, y = deltaOD_Gmu, label= Tube),hjust=0, vjust=0) +
scale_colour_manual(values = MCMIXColours) +
  scale_shape_manual(values = c(13, 16)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  coord_fixed(ratio = 1) +
  coord_cartesian(xlim = c (0, 0.06), ylim = c(0, 0.06)) +
  scale_x_continuous(breaks=seq(0, 0.06, by = 0.02)) +
  labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Gompertz Growth Rate (deltaOD_Gmu)", x = "Logistic Growth Rate (deltaOD_Lmu)") +
  facet_grid(rows = vars(Strain), cols = vars(O2, WL)) + 
  theme_bw() + 
  labs(title = "Logistic vs. Gompertz Chlorophyll Specific Growth Rates (µ" ~ h^-1~")- All Growth",
       colour = "Actinic PAR (nm)")

```

Truncated Logistic fits vs. Logistic fits
```{r compare trunc to full plots}

ProcessDataNestGrowth %>%
unnest(cols = c(OD720_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error, OD720_logistic_tidied_statistic, OD720_logistic_tidied_p.value), names_sep = "_")  %>%
  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
         OD720_Lmu = OD720_logistic_tidied_estimate_Lmu,
         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,
         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept)  %>%
  unnest(cols = c(OD720trunc_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  OD720trunc_logistic_tidied_term, values_from = c(OD720trunc_logistic_tidied_estimate, OD720trunc_logistic_tidied_std.error, OD720trunc_logistic_tidied_statistic, OD720trunc_logistic_tidied_p.value), names_sep = "_") %>%
  rename(OD720_Trunc_Lmax = OD720trunc_logistic_tidied_estimate_Lmax,
         OD720_Trunc_Lmax_se = OD720trunc_logistic_tidied_std.error_Lmax,
         OD720_Trunc_Lmu = OD720trunc_logistic_tidied_estimate_Lmu,
         OD720_Trunc_Lmu_se = OD720trunc_logistic_tidied_std.error_Lmu)  %>%
   ggplot() +
  geom_point(aes(x = OD720_Lmu, y = OD720_Trunc_Lmu, colour = as.factor(WL)), size = 4)  +
  ggrepel::geom_text_repel(aes(x = OD720_Lmu, y = OD720_Trunc_Lmu, label= Tube),hjust=0, vjust=0) +
scale_colour_manual(values = MCMIXColours) +
  scale_shape_manual(values = c(13, 16)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  coord_fixed(ratio = 1) +
  coord_cartesian(xlim = c (0, 0.3), ylim = c(0, 0.3)) +
  scale_x_continuous(breaks=seq(0, 0.3, by = 0.1)) +
  labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Truncated Logistic Growth Rate (OD720_Lmu)", x = "Logistic Growth Rate (OD720_Lmu)") +
  facet_grid(rows = vars(Strain), cols = vars(O2, WL)) + 
  theme_bw() + 
  labs(title = "Logistic vs. Truncated Logistic Cell Specific Growth Rates (µ" ~ h^-1~")- All Growth",
       colour = "Actinic PAR (nm)")

ProcessDataNestGrowth %>%
unnest(cols = c(deltaOD_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error, deltaOD_logistic_tidied_statistic, deltaOD_logistic_tidied_p.value), names_sep = "_")  %>%
  rename(deltaOD_Lmax = deltaOD_logistic_tidied_estimate_Lmax,
         deltaOD_Lmax_se = deltaOD_logistic_tidied_std.error_Lmax,
         deltaOD_Lmu = deltaOD_logistic_tidied_estimate_Lmu,
         deltaOD_Lmu_se = deltaOD_logistic_tidied_std.error_Lmu,
         deltaOD_Lintercept = deltaOD_logistic_tidied_estimate_Lintercept,
         deltaOD_Lintercept_se = deltaOD_logistic_tidied_std.error_Lintercept)  %>%
  unnest(cols = c(deltaODtrunc_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  deltaODtrunc_logistic_tidied_term, values_from = c(deltaODtrunc_logistic_tidied_estimate, deltaODtrunc_logistic_tidied_std.error, deltaODtrunc_logistic_tidied_statistic, deltaODtrunc_logistic_tidied_p.value), names_sep = "_") %>%
  rename(deltaOD_Trunc_Lmax = deltaODtrunc_logistic_tidied_estimate_Lmax,
         deltaOD_Trunc_Lmax_se = deltaODtrunc_logistic_tidied_std.error_Lmax,
         deltaOD_Trunc_Lmu = deltaODtrunc_logistic_tidied_estimate_Lmu,
         deltaOD_Trunc_Lmu_se = deltaODtrunc_logistic_tidied_std.error_Lmu)  %>%
   ggplot() +
  geom_point(aes(x = deltaOD_Lmu, y = deltaOD_Trunc_Lmu, colour = as.factor(WL)), size = 4)  +
  ggrepel::geom_text_repel(aes(x = deltaOD_Lmu, y = deltaOD_Trunc_Lmu, label= Tube), hjust=0, vjust=0) +
scale_colour_manual(values = MCMIXColours) +
  scale_shape_manual(values = c(13, 16)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  coord_fixed(ratio = 1) +
  coord_cartesian(xlim = c (0, 0.1), ylim = c(0, 0.1)) +
  scale_x_continuous(breaks=seq(0, 0.1, by = 0.02)) +
  labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Truncated Logistic Growth Rate (deltaOD_Lmu)", x = "Logistic Growth Rate (deltaOD_Lmu)") +
  facet_grid(rows = vars(Strain), cols = vars(O2, WL)) + 
  theme_bw() + 
  labs(title = "Logistic vs. Truncated Logistic Chlorophyll Specific Growth Rates (µ" ~ h^-1~")- All Growth",
       colour = "Actinic PAR (nm)")

```

Plot Fit Terms vs. conditions - High Std error filtered out by flag argument
```{r logistic fit terms plot}
ProcessDataNestGrowth %>%
 unnest(cols = c(OD720_logistic_tidied),names_sep = "_") %>%
  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, OD720_logistic_tidied_term, OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error)) %>%
  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error), names_sep = "_") %>%
  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
         OD720_Lmu = OD720_logistic_tidied_estimate_Lmu,
         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,
         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept) %>%
  mutate(LmuOD720Flag = if_else(OD720_Lmu_se < OD720_Lmu * GrowthFlagError, 1, 0)) %>%
# mutate(GrowthFlag = if_else((OD720_Lintercept + OD720_Lintercept_se) < ((OD720_Lmax - OD720_Lmax_se) & (OD720_Lmu_se < OD720_Lmu * GrowthFlagError) & (OD720_Lmax_se < OD720_Lmax * GrowthFlagError) ), 1, 0)) %>%
  filter(LmuOD720Flag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = OD720_Lmu, colour = as.factor(WL))) +
  geom_errorbar(aes(x = Par_ue, ymin = OD720_Lmu - OD720_Lmu_se, ymax = OD720_Lmu + OD720_Lmu_se, colour = as.factor(WL))) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(Strain), rows = vars(O2)) +
  theme_bw() +
  labs(title = "Logistic cell Specific Growth rates - Flagged High Std error Omitted")

ProcessDataNestGrowth %>%
 unnest(cols = c(deltaOD_logistic_tidied),names_sep = "_") %>%
  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, deltaOD_logistic_tidied_term, deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error)) %>%
  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error), names_sep = "_") %>%
  rename(deltaOD_Lmax = deltaOD_logistic_tidied_estimate_Lmax,
         deltaOD_Lmax_se = deltaOD_logistic_tidied_std.error_Lmax,
         deltaOD_Lmu = deltaOD_logistic_tidied_estimate_Lmu,
         deltaOD_Lmu_se = deltaOD_logistic_tidied_std.error_Lmu,
         deltaOD_Lintercept = deltaOD_logistic_tidied_estimate_Lintercept,
         deltaOD_Lintercept_se = deltaOD_logistic_tidied_std.error_Lintercept) %>%
  mutate(LmudeltaODFlag = if_else(deltaOD_Lmu_se < deltaOD_Lmu * GrowthFlagError, 1, 0)) %>%
 # mutate(GrowthFlag = if_else((deltaOD_Lintercept + deltaOD_Lintercept_se) < ((deltaOD_Lmax - deltaOD_Lmax_se) & (deltaOD_Lmu_se < deltaOD_Lmu * GrowthFlagError) & (deltaOD_Lmax_se < deltaOD_Lmax * GrowthFlagError) ), 1, 0)) %>%
  filter(LmudeltaODFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu, colour = as.factor(WL))) +
  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu - deltaOD_Lmu_se, ymax = deltaOD_Lmu + deltaOD_Lmu_se, colour = as.factor(WL))) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(Strain), rows = vars(O2)) +
  theme_bw() +
  labs(title = "Logistic chlorophyll specific - Flagged High Std error Omitted")

ProcessDataNestGrowth %>%
 unnest(cols = c(lognormOD720_Gompertz_tidied),names_sep = "_") %>%
  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, lognormOD720_Gompertz_tidied_term, lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error)) %>%
  pivot_wider(names_from =  lognormOD720_Gompertz_tidied_term, values_from = c(lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error), names_sep = "_") %>%
  rename(OD720_Gmax = lognormOD720_Gompertz_tidied_estimate_Gmax,
         OD720_Gmax_se = lognormOD720_Gompertz_tidied_std.error_Gmax,
         OD720_Gmu = lognormOD720_Gompertz_tidied_estimate_Gmu,
         OD720_Gmu_se = lognormOD720_Gompertz_tidied_std.error_Gmu,
         OD720_GLag = lognormOD720_Gompertz_tidied_estimate_GLag,
         OD720_GLag_se = lognormOD720_Gompertz_tidied_std.error_GLag) %>%
  mutate(GmuOD720Flag = if_else(OD720_Gmu_se < OD720_Gmu * GrowthFlagError, 1, 0)) %>%
 # mutate(GrowthFlag = if_else((OD720_GLag + OD720_GLag_se) < ((OD720_Gmax - OD720_Gmax_se) & (OD720_Gmu_se < OD720_Gmu * GrowthFlagError) & (OD720_Gmax_se < OD720_Gmax * GrowthFlagError) ), 1, 0)) %>%
  filter(GmuOD720Flag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = OD720_Gmu, colour = as.factor(WL))) +
  geom_errorbar(aes(x = Par_ue, ymin = OD720_Gmu - OD720_Gmu_se, ymax = OD720_Gmu + OD720_Gmu_se, colour = as.factor(WL))) + 
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(Strain), rows = vars(O2)) +
  theme_bw() +
  labs(title = "Gompertz Cell Specific Growth rates - Flagged High Std error Omitted")

ProcessDataNestGrowth %>%
 unnest(cols = c(lognormdeltaOD_Gompertz_tidied),names_sep = "_") %>%
  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, lognormdeltaOD_Gompertz_tidied_term, lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error)) %>%
  pivot_wider(names_from =  lognormdeltaOD_Gompertz_tidied_term, values_from = c(lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error), names_sep = "_") %>%
  rename(deltaOD_Gmax = lognormdeltaOD_Gompertz_tidied_estimate_Gmax,
         deltaOD_Gmax_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmax,
         deltaOD_Gmu = lognormdeltaOD_Gompertz_tidied_estimate_Gmu,
         deltaOD_Gmu_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmu,
         deltaOD_GLag = lognormdeltaOD_Gompertz_tidied_estimate_GLag,
         deltaOD_GLag_se = lognormdeltaOD_Gompertz_tidied_std.error_GLag) %>%
  mutate(GmudeltaODFlag = if_else(deltaOD_Gmu_se < deltaOD_Gmu * GrowthFlagError, 1, 0)) %>%
 # mutate(GrowthFlag = if_else((deltaOD_GLag + deltaOD_GLag_se) < ((deltaOD_Gmax - deltaOD_Gmax_se) & (deltaOD_Gmu_se < deltaOD_Gmu * GrowthFlagError) & (deltaOD_Gmax_se < deltaOD_Gmax * GrowthFlagError) ), 1, 0)) %>%
  filter(GmudeltaODFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Gmu, colour = as.factor(WL))) +
  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Gmu - deltaOD_Gmu_se, ymax = deltaOD_Gmu + deltaOD_Gmu_se, colour = as.factor(WL))) + 
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(Strain), rows = vars(O2)) +
  theme_bw() +
  labs(title = "Gompertz Chlorophyll Specific Growth rates - Flagged High Std error Omitted")

ProcessDataNestGrowth %>%
 unnest(cols = c(lognormOD720_Gompertz_tidied),names_sep = "_") %>%
  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, lognormOD720_Gompertz_tidied_term, lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error)) %>%
  pivot_wider(names_from =  lognormOD720_Gompertz_tidied_term, values_from = c(lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error), names_sep = "_") %>%
  rename(OD720_Gmax = lognormOD720_Gompertz_tidied_estimate_Gmax,
         OD720_Gmax_se = lognormOD720_Gompertz_tidied_std.error_Gmax,
         OD720_Gmu = lognormOD720_Gompertz_tidied_estimate_Gmu,
         OD720_Gmu_se = lognormOD720_Gompertz_tidied_std.error_Gmu,
         OD720_GLag = lognormOD720_Gompertz_tidied_estimate_GLag,
         OD720_GLag_se = lognormOD720_Gompertz_tidied_std.error_GLag) %>%
   mutate(GmuOD720Flag = if_else(OD720_Gmu_se < OD720_Gmu * GrowthFlagError, 1, 0)) %>%
  # mutate(GrowthFlag = if_else((OD720_GLag + OD720_GLag_se) < ((OD720_Gmax - OD720_Gmax_se) & (OD720_Gmu_se < OD720_Gmu * GrowthFlagError) & (OD720_Gmax_se < OD720_Gmax * GrowthFlagError) ), 1, 0)) %>%
   filter(GmuOD720Flag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = OD720_Gmax)) +
  geom_errorbar(aes(x = Par_ue, ymin = OD720_Gmax - OD720_Gmax_se, ymax = OD720_Gmax + OD720_Gmax_se, colour = as.factor(WL))) + 
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(Strain), rows = vars(O2)) +
  theme_bw() +
  labs(title = "Gompertz Cell Specific gmax - Flagged High Std error Omitted")

ProcessDataNestGrowth %>%
 unnest(cols = c(lognormdeltaOD_Gompertz_tidied),names_sep = "_") %>%
  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, lognormdeltaOD_Gompertz_tidied_term, lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error)) %>%
  pivot_wider(names_from =  lognormdeltaOD_Gompertz_tidied_term, values_from = c(lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error), names_sep = "_") %>%
  rename(deltaOD_Gmax = lognormdeltaOD_Gompertz_tidied_estimate_Gmax,
         deltaOD_Gmax_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmax,
         deltaOD_Gmu = lognormdeltaOD_Gompertz_tidied_estimate_Gmu,
         deltaOD_Gmu_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmu,
         deltaOD_GLag = lognormdeltaOD_Gompertz_tidied_estimate_GLag,
         deltaOD_GLag_se = lognormdeltaOD_Gompertz_tidied_std.error_GLag) %>%
   mutate(GmudeltaODFlag = if_else(deltaOD_Gmu_se < deltaOD_Gmu * GrowthFlagError, 1, 0)) %>%
  # mutate(GrowthFlag = if_else((deltaOD_GLag + deltaOD_GLag_se) < ((deltaOD_Gmax - deltaOD_Gmax_se) & (deltaOD_Gmu_se < deltaOD_Gmu * GrowthFlagError) & (deltaOD_Gmax_se < deltaOD_Gmax * GrowthFlagError) ), 1, 0)) %>%
   filter(GmudeltaODFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Gmax)) +
  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Gmax - deltaOD_Gmax_se, ymax = deltaOD_Gmax + deltaOD_Gmax_se, colour = as.factor(WL))) + 
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(Strain), rows = vars(O2)) +
  theme_bw() +
  labs(title = "Gompertz Chlorophyll Specific gmax - Flagged High Std error Omitted")

```

Plot all Fit Terms vs. conditions- no filters
```{r plot all}
ProcessDataNestGrowth %>%
 unnest(cols = c(OD720_logistic_tidied),names_sep = "_") %>%
  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, OD720_logistic_tidied_term, OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error)) %>%
  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error), names_sep = "_") %>%
  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
         OD720_Lmu = OD720_logistic_tidied_estimate_Lmu,
         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,
         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = OD720_Lmu, colour = as.factor(WL))) +
  geom_errorbar(aes(x = Par_ue, ymin = OD720_Lmu - OD720_Lmu_se, ymax = OD720_Lmu + OD720_Lmu_se, colour = as.factor(WL))) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(Strain), rows = vars(O2)) +
  theme_bw() +
  labs(title = "Logistic cell Specific Growth Rate - All Growth")

ProcessDataNestGrowth %>%
 unnest(cols = c(deltaOD_logistic_tidied),names_sep = "_") %>%
  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, deltaOD_logistic_tidied_term, deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error)) %>%
  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error), names_sep = "_") %>%
  rename(deltaOD_Lmax = deltaOD_logistic_tidied_estimate_Lmax,
         deltaOD_Lmax_se = deltaOD_logistic_tidied_std.error_Lmax,
         deltaOD_Lmu = deltaOD_logistic_tidied_estimate_Lmu,
         deltaOD_Lmu_se = deltaOD_logistic_tidied_std.error_Lmu,
         deltaOD_Lintercept = deltaOD_logistic_tidied_estimate_Lintercept,
         deltaOD_Lintercept_se = deltaOD_logistic_tidied_std.error_Lintercept) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu, colour = as.factor(WL))) +
  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu - deltaOD_Lmu_se, ymax = deltaOD_Lmu + deltaOD_Lmu_se, colour = as.factor(WL))) +
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(Strain), rows = vars(O2)) +
  theme_bw() +
  labs(title = "Logistic chlorophyll specific - All Growth")

ProcessDataNestGrowth %>%
 unnest(cols = c(lognormOD720_Gompertz_tidied),names_sep = "_") %>%
  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, lognormOD720_Gompertz_tidied_term, lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error)) %>%
  pivot_wider(names_from =  lognormOD720_Gompertz_tidied_term, values_from = c(lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error), names_sep = "_") %>%
  rename(OD720_Gmax = lognormOD720_Gompertz_tidied_estimate_Gmax,
         OD720_Gmax_se = lognormOD720_Gompertz_tidied_std.error_Gmax,
         OD720_Gmu = lognormOD720_Gompertz_tidied_estimate_Gmu,
         OD720_Gmu_se = lognormOD720_Gompertz_tidied_std.error_Gmu,
         OD720_GLag = lognormOD720_Gompertz_tidied_estimate_GLag,
         OD720_GLag_se = lognormOD720_Gompertz_tidied_std.error_GLag) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = OD720_Gmu, colour = as.factor(WL))) +
  geom_errorbar(aes(x = Par_ue, ymin = OD720_Gmu - OD720_Gmu_se, ymax = OD720_Gmu + OD720_Gmu_se, colour = as.factor(WL))) + 
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(Strain), rows = vars(O2)) +
  theme_bw()+
  labs(title = "Gompertz Cell Specific Growth Rates- All Growth")

ProcessDataNestGrowth %>%
 unnest(cols = c(lognormdeltaOD_Gompertz_tidied),names_sep = "_") %>%
  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, lognormdeltaOD_Gompertz_tidied_term, lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error)) %>%
  pivot_wider(names_from =  lognormdeltaOD_Gompertz_tidied_term, values_from = c(lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error), names_sep = "_") %>%
  rename(deltaOD_Gmax = lognormdeltaOD_Gompertz_tidied_estimate_Gmax,
         deltaOD_Gmax_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmax,
         deltaOD_Gmu = lognormdeltaOD_Gompertz_tidied_estimate_Gmu,
         deltaOD_Gmu_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmu,
         deltaOD_GLag = lognormdeltaOD_Gompertz_tidied_estimate_GLag,
         deltaOD_GLag_se = lognormdeltaOD_Gompertz_tidied_std.error_GLag) %>%
  mutate(GmudeltaODFlag = if_else(deltaOD_Gmu_se < deltaOD_Gmu * GrowthFlagError, 1, 0)) %>%
 # mutate(GrowthFlag = if_else((deltaOD_GLag + deltaOD_GLag_se) < ((deltaOD_Gmax - deltaOD_Gmax_se) & (deltaOD_Gmu_se < deltaOD_Gmu * GrowthFlagError) & (deltaOD_Gmax_se < deltaOD_Gmax * GrowthFlagError) ), 1, 0)) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Gmu, colour = as.factor(WL))) +
  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Gmu - deltaOD_Gmu_se, ymax = deltaOD_Gmu + deltaOD_Gmu_se, colour = as.factor(WL))) + 
  scale_colour_manual(values = MCMIXColours) +
  facet_grid (cols = vars(Strain), rows = vars(O2)) +
  theme_bw() +
  labs(title = "Gompertz Chlorophyll Specific Growth rates - All Growth")

# ProcessDataNestGrowth %>%
#  unnest(cols = c(lognormOD720_Gompertz_tidied),names_sep = "_") %>%
#   select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, lognormOD720_Gompertz_tidied_term, lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error)) %>%
#   pivot_wider(names_from =  lognormOD720_Gompertz_tidied_term, values_from = c(lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error), names_sep = "_") %>%
#   rename(OD720_Gmax = lognormOD720_Gompertz_tidied_estimate_Gmax,
#          OD720_Gmax_se = lognormOD720_Gompertz_tidied_std.error_Gmax,
#          OD720_Gmu = lognormOD720_Gompertz_tidied_estimate_Gmu,
#          OD720_Gmu_se = lognormOD720_Gompertz_tidied_std.error_Gmu,
#          OD720_GLag = lognormOD720_Gompertz_tidied_estimate_GLag,
#          OD720_GLag_se = lognormOD720_Gompertz_tidied_std.error_GLag) %>%
#   ggplot() +
#   geom_point(aes(x = Par_ue, y = OD720_Gmax)) +
#   geom_errorbar(aes(x = Par_ue, ymin = OD720_Gmax - OD720_Gmax_se, ymax = OD720_Gmax + OD720_Gmax_se, colour = as.factor(WL))) + 
#   scale_colour_manual(values = MCMIXColours) +
#   facet_grid (cols = vars(Strain), rows = vars(O2)) +
#   theme_bw()+
#   labs(title = "Gompertz Cell Specific gmax - All Growth")

# 
# ProcessDataNestGrowth %>%
#  unnest(cols = c(lognormdeltaOD_Gompertz_tidied),names_sep = "_") %>%
#   select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, lognormdeltaOD_Gompertz_tidied_term, lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error)) %>%
#   pivot_wider(names_from =  lognormdeltaOD_Gompertz_tidied_term, values_from = c(lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error), names_sep = "_") %>%
#   rename(deltaOD_Gmax = lognormdeltaOD_Gompertz_tidied_estimate_Gmax,
#          deltaOD_Gmax_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmax,
#          deltaOD_Gmu = lognormdeltaOD_Gompertz_tidied_estimate_Gmu,
#          deltaOD_Gmu_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmu,
#          deltaOD_GLag = lognormdeltaOD_Gompertz_tidied_estimate_GLag,
#          deltaOD_GLag_se = lognormdeltaOD_Gompertz_tidied_std.error_GLag) %>%
#    mutate(GmudeltaODFlag = if_else(deltaOD_Gmu_se < deltaOD_Gmu * GrowthFlagError, 1, 0)) %>%
#   # mutate(GrowthFlag = if_else((deltaOD_GLag + deltaOD_GLag_se) < ((deltaOD_Gmax - deltaOD_Gmax_se) & (deltaOD_Gmu_se < deltaOD_Gmu * GrowthFlagError) & (deltaOD_Gmax_se < deltaOD_Gmax * GrowthFlagError) ), 1, 0)) %>%
#   ggplot() +
#   geom_point(aes(x = Par_ue, y = deltaOD_Gmax)) +
#   geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Gmax - deltaOD_Gmax_se, ymax = deltaOD_Gmax + deltaOD_Gmax_se, colour = as.factor(WL))) + 
#   scale_colour_manual(values = MCMIXColours) +
#   facet_grid (cols = vars(Strain), rows = vars(O2)) +
#   theme_bw() +
#   labs(title = "Gompertz Chlorophyll Specific gmax - All Growth")

```

Compare truncated vs full run 
```{r compare}

ProcessDataNestGrowth %>%
unnest(cols = c(OD720_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error, OD720_logistic_tidied_statistic, OD720_logistic_tidied_p.value), names_sep = "_")  %>%
  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
         OD720_Lmu = OD720_logistic_tidied_estimate_Lmu,
         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,
         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept)  %>%
 unnest(cols = c(OD720trunc_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  OD720trunc_logistic_tidied_term, values_from = c(OD720trunc_logistic_tidied_estimate, OD720trunc_logistic_tidied_std.error, OD720trunc_logistic_tidied_statistic, OD720trunc_logistic_tidied_p.value), names_sep = "_") %>%
  rename(OD720_Trunc_Lmax = OD720trunc_logistic_tidied_estimate_Lmax,
         OD720_Trunc_Lmax_se = OD720trunc_logistic_tidied_std.error_Lmax,
         OD720_Trunc_Lmu = OD720trunc_logistic_tidied_estimate_Lmu,
         OD720_Trunc_Lmu_se = OD720trunc_logistic_tidied_std.error_Lmu)  %>%
  ggplot() +
  geom_point(aes(x = OD720_TimetoMax, y = OD720_Lmu), colour = "Darkgreen", size = 4) +
  #scale_colour_manual(values = MCMIXColours) +
 geom_point(aes(x = OD720trunc_TimetoMax, y = OD720_Trunc_Lmu), colour = "Red", size = 4) +
ggrepel::geom_text_repel(aes(x = OD720trunc_TimetoMax, y = OD720_Trunc_Lmu, label= "Truncated"),hjust=0.5, vjust=1) +
# scale_colour_manual(values = MCMIXColours) +
#   scale_shape_manual(values = c(13, 16)) +
#   geom_hline(yintercept = 0, linetype = "dashed") +
#   geom_vline(xintercept = 0, linetype = "dashed") +
#   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
#   coord_fixed(ratio = 1) +
#   coord_cartesian(xlim = c (0, 0.05), ylim = c(0, 0.05)) +
#   scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
  # labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Gompertz Growth Rate (OD720_Gmu)", x = "Logistic Growth Rate (OD720_Lmu)") +
  facet_grid(cols = vars(Tube, WL, Strain)) +
  theme_bw() +
  labs(title = "Full and Truncated Logistic Cell Specific Growth Rates (µ" ~ h^-1~")- All Growth",
       x = "Time (h)")

ProcessDataNestGrowth %>%
unnest(cols = c(deltaOD_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error, deltaOD_logistic_tidied_statistic, deltaOD_logistic_tidied_p.value), names_sep = "_")  %>%
  rename(deltaOD_Lmax = deltaOD_logistic_tidied_estimate_Lmax,
         deltaOD_Lmax_se = deltaOD_logistic_tidied_std.error_Lmax,
         deltaOD_Lmu = deltaOD_logistic_tidied_estimate_Lmu,
         deltaOD_Lmu_se = deltaOD_logistic_tidied_std.error_Lmu,
         deltaOD_Lintercept = deltaOD_logistic_tidied_estimate_Lintercept,
         deltaOD_Lintercept_se = deltaOD_logistic_tidied_std.error_Lintercept)  %>%
 unnest(cols = c(deltaODtrunc_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  deltaODtrunc_logistic_tidied_term, values_from = c(deltaODtrunc_logistic_tidied_estimate, deltaODtrunc_logistic_tidied_std.error, deltaODtrunc_logistic_tidied_statistic, deltaODtrunc_logistic_tidied_p.value), names_sep = "_") %>%
  rename(deltaOD_Trunc_Lmax = deltaODtrunc_logistic_tidied_estimate_Lmax,
         deltaOD_Trunc_Lmax_se = deltaODtrunc_logistic_tidied_std.error_Lmax,
         deltaOD_Trunc_Lmu = deltaODtrunc_logistic_tidied_estimate_Lmu,
         deltaOD_Trunc_Lmu_se = deltaODtrunc_logistic_tidied_std.error_Lmu)  %>%
  ggplot() +
  geom_point(aes(x = deltaOD_TimetoMax, y = deltaOD_Lmu), colour = "Darkgreen", size = 4) +
  #scale_colour_manual(values = MCMIXColours) +
 geom_point(aes(x = deltaODtrunc_TimetoMax, y = deltaOD_Trunc_Lmu), colour = "Red", size = 4) +
ggrepel::geom_text_repel(aes(x = deltaODtrunc_TimetoMax, y = deltaOD_Trunc_Lmu, label= "Truncated"),hjust=0.5, vjust=1) +
# scale_colour_manual(values = MCMIXColours) +
#   scale_shape_manual(values = c(13, 16)) +
#   geom_hline(yintercept = 0, linetype = "dashed") +
#   geom_vline(xintercept = 0, linetype = "dashed") +
#   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
#   coord_fixed(ratio = 1) +
#   coord_cartesian(xlim = c (0, 0.05), ylim = c(0, 0.05)) +
#   scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
  # labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Gompertz Growth Rate (deltaOD_Gmu)", x = "Logistic Growth Rate (deltaOD_Lmu)") +
  facet_grid(cols = vars(Tube, WL, Strain)) +
  theme_bw() +
  labs(title = "Full and Truncated Logistic Chlorophyll Specific Growth Rates (µ" ~ h^-1~")- All Growth",
       x = "Time (h)")

```

### 2023-12-07 Code/MultiDataProcessPico.Rmd
Fixed file path in ProcessPico rmd

@@
 
-## Set figure caption font size
-```{css, echo=FALSE}
-p.caption {
-  font-size: 18px;
-}
-```
-
 ## Set Chunk Options
@@
 library(zoo)
-#library(tidyquant)
-#library(data.table)
-#library(googledrive)
-#library(googlesheets4)
 library(minpack.lm)
-#library(dplyr)
-
-#attach psych for harmonic.mean() for averaging rates
-#library(psych)
-#library(RcppRoll) #replaced by zoo::rollmean for rolling mean consistent with MultiDataImportPico.Rmd usage
+library(photobiologyWavebands)
 
@@
 Project <- "PICO"
-DataIn <- file.path("ImportedData")
-PlotsPath <- file.path("..","Plots")
-DataOut <- file.path("ProcessedData", "MultiCultiData")
+DataIn <- file.path("..", "Data", "ImportedData", "MultiCultiData")
+DataOut <- file.path("..", "Data","ProcessedData", "MultiCultiData")
 
@@
 
-GrowthFlagError <- 0.20 # percentage of growth parameter is flagged as growth when std error is less than xx of mu .
-
-Sensor <- "od-680"
+GrowthFlagError <- 0.20 # percentage of growth parameter is flagged as growth when std error is less than xx of mu.
 
@@
 
-#set the hour of day at which photoperiod starts for later generation of ToD Time of Day
-#replaced by extraction of StartHour from first row of data file in MultiDataImport.Rmd
-#StartHour <- 6
-#EndHour <- 18
-
-```
-
-Run only first time in session
+```
 
 ```{r set colours}
-MyWavelengths = c(405, 450, 470, 530, 620, 660, 730, "WW")
-MCMIXColours = c("violet", "darkblue", "dodgerblue", "green","orange","red","purple", "black")
+MyWavelengths = c(405, 445, 470, 530, 620, 660, 730, "WW")
+MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(445), w_length2rgb(470), w_length2rgb(530),            w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black"))
 
@@
 ```{r read ProcessFile}
-ProcessFile <- "ImportedData/20220929_PICO_MCMIX006_RUN92_TargetDataMetaFilter.Rds"
-
-ProcessFileName <- str_split(string = ProcessFile, "/")[[1]][2] %>%
+ProcessFile <- "../Data/ImportedData/MultiCultiData/20211223_PICO_MCMIX006_RUN42_TargetDataMetaFilter.Rds"
+
+ProcessFileName <- str_split(string = ProcessFile, "/")[[1]][5] %>%
   str_remove(pattern = ".Rds") %>%
   str_remove(pattern = "_TargetDataMetaFilter")
+
 ProcessFileName
@@
 
-```{r filter }
-ProcessDataNestGrowth <- ProcessDataNestGrowth %>% 
-  select(-contains(c("trunc", "Gompertz", "Gomp", "OD720_G", "deltaOD_G")))
-```
-
 # Save .Rds of ProcessDataNestGrowth containing logistic and gompertz fits of growth data from time resolved and whole interval fits.
@@
 # #predictions of condition specific fits
-OD720LogGrowthPlot <-ProcessDataNestGrowth %>%
+ProcessDataNestGrowth %>%
 #drop_na(OD720_logistic) %>%
@@
 
-OD720LogGrowthPlot
-
-deltaODLogGrowthPlot <- ProcessDataNestGrowth %>%
+ProcessDataNestGrowth %>%
   mutate(deltaOD_logistic_predict = map(deltaOD_logistic, possibly(augment, otherwise = NULL))) %>%
@@
   guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))
-
-deltaODLogGrowthPlot
 
@@
 
-lognormOD720GompertzGrowthPlot <- ProcessDataNestGrowth %>%
-  mutate(lognormOD720_Gompertz_predict = map(lognormOD720_Gompertz, possibly(augment, otherwise = NULL))) %>%
-  unnest(cols = c(tubedata, lognormOD720_Gompertz_predict),names_sep = "_", keep_empty = TRUE) %>%
-  ggplot() +
-  geom_point(aes(x = tubedata_time, y = tubedata_lognormOD720), colour = "darkgreen", size = 0.1) +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_point(aes(x = tubedata_time, y = lognormOD720_Gompertz_predict_.fitted), colour = "black", size = 0.1) +
-  geom_point(aes(x = tubedata_time, y = lognormOD720_Gompertz_predict_.resid), colour = "gold", size = 0.05) +
-  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
-  #coord_cartesian(xlim = c(-5, 675)) +
-  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
-  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
-  labs(subtitle = "lognormOD720_Gompertz; Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "lognormOD720", x = "Elapsed Time (h)") +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")+ 
-  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))
-
-lognormOD720GompertzGrowthPlot
-
-ProcessDataNestGrowth %>%
-  filter(Tube == 5) %>%
-  mutate(lognormOD720_Gompertz_predict = map(lognormOD720_Gompertz, possibly(augment, otherwise = NULL))) %>%
-  unnest(cols = c(tubedata, lognormOD720_Gompertz_predict),names_sep = "_", keep_empty = TRUE) %>%
-  ggplot() +
-  geom_point(aes(x = tubedata_time, y = tubedata_lognormOD720), colour = "darkgreen", size = 0.1) +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_point(aes(x = tubedata_time, y = lognormOD720_Gompertz_predict_.fitted), colour = "black", size = 0.1) +
-  geom_point(aes(x = tubedata_time, y = lognormOD720_Gompertz_predict_.resid), colour = "gold", size = 0.05) +
-  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
-  #coord_cartesian(xlim = c(-5, 675)) +
-  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
-  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
-  labs(subtitle = "lognormOD720_Gompertz; Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "lognormOD720", x = "Elapsed Time (h)") +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")+ 
-  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))
-
-lognormdeltaODGompertzGrowthPlot <- ProcessDataNestGrowth %>%
-  mutate(lognormdeltaOD_Gompertz_predict = map(lognormdeltaOD_Gompertz, possibly(augment, otherwise = NULL))) %>%
-  unnest(cols = c(tubedata, lognormdeltaOD_Gompertz_predict),names_sep = "_", keep_empty = TRUE) %>%
-  ggplot() +
-  geom_point(aes(x = tubedata_time, y = tubedata_lognormdeltaOD), colour = "darkgreen", size = 0.1) +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.fitted), colour = "black", size = 0.1) +
-  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.resid), colour = "gold", size = 0.05) +geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
-  #coord_cartesian(xlim = c(-5, 675)) +
-  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
-  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
-  labs(subtitle = "lognormdeltaOD_Gompertz; Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "lognormdeltaOD", x = "Elapsed Time (h)") +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")+ 
-  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))
-
-lognormdeltaODGompertzGrowthPlot
-
-ProcessDataNestGrowth %>%
-  filter(Tube == 2) %>%
-  mutate(lognormdeltaOD_Gompertz_predict = map(lognormdeltaOD_Gompertz, possibly(augment, otherwise = NULL))) %>%
-  unnest(cols = c(tubedata, lognormdeltaOD_Gompertz_predict),names_sep = "_", keep_empty = TRUE) %>%
-  ggplot() +
-  geom_point(aes(x = tubedata_time, y = tubedata_lognormdeltaOD), colour = "darkgreen", size = 0.1) +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.fitted), colour = "black", size = 0.1) +
-  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.resid), colour = "gold", size = 0.05) +geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
-  #coord_cartesian(xlim = c(-5, 675)) +
-  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
-  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
-  labs(subtitle = "lognormdeltaOD_Gompertz; Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "lognormdeltaOD", x = "Elapsed Time (h)") +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")+ 
-  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))
-
-ProcessDataNestGrowth %>%
-  filter(Tube == 5) %>%
-  mutate(PhotoperiodLabel = "Photoperiod",
-         OxygenLabel = "Oxygen level") %>% 
-  mutate(lognormdeltaOD_Gompertz_predict = map(lognormdeltaOD_Gompertz, possibly(augment, otherwise = NULL))) %>%
-  unnest(cols = c(tubedata, lognormdeltaOD_Gompertz_predict),names_sep = "_", keep_empty = TRUE) %>%
-  ggplot() +
-  geom_point(aes(x = tubedata_time, y = tubedata_lognormdeltaOD), colour = "darkgreen", size = 0.1) +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.fitted), colour = "black", size = 0.1) +
-  geom_point(aes(x = tubedata_time, y = lognormdeltaOD_Gompertz_predict_.resid), colour = "gold", size = 0.05) +geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
-  #coord_cartesian(xlim = c(-5, 675)) +
-  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
-   facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
- # guides(fill = "none") +
-  labs(subtitle = "lognormdeltaOD_Gompertz; Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "lognormdeltaOD", x = "Elapsed Time (h)") +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")+ 
-  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))
-
-```
-
-```{r save logistic model plots}
-# ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "OD720LogGrowthPlot",".png",sep = "")), plot = OD720LogGrowthPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
-# 
-# ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "deltaODLogGrowthPlot",".png",sep = "")), plot = deltaODLogGrowthPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
-
- # ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "OD720LogGrowthPlotExpand",".png",sep = "")), plot = OD720LogGrowthPlotExpand, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
-#
-
- # ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "DeltaODLogGrowthPlotExpand",".png",sep = "")), plot = DeltaODLogGrowthPlotExpand, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
-
- # ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "lognormOD720GompertzGrowthPlot",".png",sep = "")), plot = lognormOD720GompertzGrowthPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
- # 
- #  ggsave(file = file.path(PlotsPath, paste(ProcessFileName, "lognormdeltaODGompertzGrowthPlot",".png",sep = "")), plot = lognormdeltaODGompertzGrowthPlot, device = NULL, scale = 1, height=10, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
-
 ```
@@
 #   filter(Tube != 4)
-```
-
-```{r logistic vs gompertz fit plots}
-
-ProcessDataNestGrowth %>%
-unnest(cols = c(OD720_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error, OD720_logistic_tidied_statistic, OD720_logistic_tidied_p.value), names_sep = "_")  %>%
-  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
-         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
-         OD720_Lmu = OD720_logistic_tidied_estimate_Lmu,
-         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
-         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,
-         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept)  %>%
-  unnest(cols = c(lognormOD720_Gompertz_tidied), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_wider(names_from =  lognormOD720_Gompertz_tidied_term, values_from = c(lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error, lognormOD720_Gompertz_tidied_statistic, lognormOD720_Gompertz_tidied_p.value), names_sep = "_") %>%
-  rename(OD720_Gmax = lognormOD720_Gompertz_tidied_estimate_Gmax,
-         OD720_Gmax_se = lognormOD720_Gompertz_tidied_std.error_Gmax,
-         OD720_Gmu = lognormOD720_Gompertz_tidied_estimate_Gmu,
-         OD720_Gmu_se = lognormOD720_Gompertz_tidied_std.error_Gmu,
-         OD720_GLag = lognormOD720_Gompertz_tidied_estimate_GLag,             
-         OD720_GLag_se = lognormOD720_Gompertz_tidied_std.error_GLag)  %>%
-   ggplot() +
-  geom_point(aes(x = OD720_Lmu, y = OD720_Gmu, colour = as.factor(WL),  shape = as.factor(IsOD720_GLagNeg)), size = 4)  +
-  ggrepel::geom_text_repel(aes(x = OD720_Lmu, y = OD720_Gmu, label= Tube),hjust=0, vjust=0) +
-scale_colour_manual(values = MCMIXColours) +
-  scale_shape_manual(values = c(13, 16)) +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  coord_fixed(ratio = 1) +
-  coord_cartesian(xlim = c (0, 0.06), ylim = c(0, 0.06)) +
-  scale_x_continuous(breaks=seq(0, 0.06, by = 0.02)) +
-  labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Gompertz Growth Rate (OD720_Gmu)", x = "Logistic Growth Rate (OD720_Lmu)") +
-  facet_grid(rows = vars(Strain), cols = vars(O2, WL)) + 
-  theme_bw() + 
-  labs(title = "Logistic vs. Gompertz Cell Specific Growth Rates (µ" ~ h^-1~")- All Growth",
-       colour = "Actinic PAR (nm)")
-
-ProcessDataNestGrowth %>%
-unnest(cols = c(deltaOD_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error, deltaOD_logistic_tidied_statistic, deltaOD_logistic_tidied_p.value), names_sep = "_")  %>%
-  rename(deltaOD_Lmax = deltaOD_logistic_tidied_estimate_Lmax,
-         deltaOD_Lmax_se = deltaOD_logistic_tidied_std.error_Lmax,
-         deltaOD_Lmu = deltaOD_logistic_tidied_estimate_Lmu,
-         deltaOD_Lmu_se = deltaOD_logistic_tidied_std.error_Lmu,
-         deltaOD_Lintercept = deltaOD_logistic_tidied_estimate_Lintercept,
-         deltaOD_Lintercept_se = deltaOD_logistic_tidied_std.error_Lintercept)  %>%
-  unnest(cols = c(lognormdeltaOD_Gompertz_tidied), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_wider(names_from =  lognormdeltaOD_Gompertz_tidied_term, values_from = c(lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error, lognormdeltaOD_Gompertz_tidied_statistic, lognormdeltaOD_Gompertz_tidied_p.value), names_sep = "_") %>%
-  rename(deltaOD_Gmax = lognormdeltaOD_Gompertz_tidied_estimate_Gmax,
-         deltaOD_Gmax_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmax,
-         deltaOD_Gmu = lognormdeltaOD_Gompertz_tidied_estimate_Gmu,
-         deltaOD_Gmu_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmu,
-         deltaOD_GLag = lognormdeltaOD_Gompertz_tidied_estimate_GLag,             
-         deltaOD_GLag_se = lognormdeltaOD_Gompertz_tidied_std.error_GLag)  %>%
-   ggplot() +
-  geom_point(aes(x = deltaOD_Lmu, y = deltaOD_Gmu, colour = as.factor(WL),  shape = as.factor(IsdeltaOD_GLagNeg)), size = 4) +
-  ggrepel::geom_text_repel(aes(x = deltaOD_Lmu, y = deltaOD_Gmu, label= Tube),hjust=0, vjust=0) +
-scale_colour_manual(values = MCMIXColours) +
-  scale_shape_manual(values = c(13, 16)) +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  coord_fixed(ratio = 1) +
-  coord_cartesian(xlim = c (0, 0.06), ylim = c(0, 0.06)) +
-  scale_x_continuous(breaks=seq(0, 0.06, by = 0.02)) +
-  labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Gompertz Growth Rate (deltaOD_Gmu)", x = "Logistic Growth Rate (deltaOD_Lmu)") +
-  facet_grid(rows = vars(Strain), cols = vars(O2, WL)) + 
-  theme_bw() + 
-  labs(title = "Logistic vs. Gompertz Chlorophyll Specific Growth Rates (µ" ~ h^-1~")- All Growth",
-       colour = "Actinic PAR (nm)")
-
 ```
@@
   theme_bw() +
-  labs(title = "Logistic cell Specific Growth rates - Flagged High Std error Omitted")
+  labs(title = "Logistic cell scatter growth rates - High std error fits omitted")
 
@@
   theme_bw() +
-  labs(title = "Logistic chlorophyll specific - Flagged High Std error Omitted")
-
-ProcessDataNestGrowth %>%
- unnest(cols = c(lognormOD720_Gompertz_tidied),names_sep = "_") %>%
-  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, lognormOD720_Gompertz_tidied_term, lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error)) %>%
-  pivot_wider(names_from =  lognormOD720_Gompertz_tidied_term, values_from = c(lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error), names_sep = "_") %>%
-  rename(OD720_Gmax = lognormOD720_Gompertz_tidied_estimate_Gmax,
-         OD720_Gmax_se = lognormOD720_Gompertz_tidied_std.error_Gmax,
-         OD720_Gmu = lognormOD720_Gompertz_tidied_estimate_Gmu,
-         OD720_Gmu_se = lognormOD720_Gompertz_tidied_std.error_Gmu,
-         OD720_GLag = lognormOD720_Gompertz_tidied_estimate_GLag,
-         OD720_GLag_se = lognormOD720_Gompertz_tidied_std.error_GLag) %>%
-  mutate(GmuOD720Flag = if_else(OD720_Gmu_se < OD720_Gmu * GrowthFlagError, 1, 0)) %>%
- # mutate(GrowthFlag = if_else((OD720_GLag + OD720_GLag_se) < ((OD720_Gmax - OD720_Gmax_se) & (OD720_Gmu_se < OD720_Gmu * GrowthFlagError) & (OD720_Gmax_se < OD720_Gmax * GrowthFlagError) ), 1, 0)) %>%
-  filter(GmuOD720Flag == 1) %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = OD720_Gmu, colour = as.factor(WL))) +
-  geom_errorbar(aes(x = Par_ue, ymin = OD720_Gmu - OD720_Gmu_se, ymax = OD720_Gmu + OD720_Gmu_se, colour = as.factor(WL))) + 
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid (cols = vars(Strain), rows = vars(O2)) +
-  theme_bw() +
-  labs(title = "Gompertz Cell Specific Growth rates - Flagged High Std error Omitted")
-
-ProcessDataNestGrowth %>%
- unnest(cols = c(lognormdeltaOD_Gompertz_tidied),names_sep = "_") %>%
-  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, lognormdeltaOD_Gompertz_tidied_term, lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error)) %>%
-  pivot_wider(names_from =  lognormdeltaOD_Gompertz_tidied_term, values_from = c(lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error), names_sep = "_") %>%
-  rename(deltaOD_Gmax = lognormdeltaOD_Gompertz_tidied_estimate_Gmax,
-         deltaOD_Gmax_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmax,
-         deltaOD_Gmu = lognormdeltaOD_Gompertz_tidied_estimate_Gmu,
-         deltaOD_Gmu_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmu,
-         deltaOD_GLag = lognormdeltaOD_Gompertz_tidied_estimate_GLag,
-         deltaOD_GLag_se = lognormdeltaOD_Gompertz_tidied_std.error_GLag) %>%
-  mutate(GmudeltaODFlag = if_else(deltaOD_Gmu_se < deltaOD_Gmu * GrowthFlagError, 1, 0)) %>%
- # mutate(GrowthFlag = if_else((deltaOD_GLag + deltaOD_GLag_se) < ((deltaOD_Gmax - deltaOD_Gmax_se) & (deltaOD_Gmu_se < deltaOD_Gmu * GrowthFlagError) & (deltaOD_Gmax_se < deltaOD_Gmax * GrowthFlagError) ), 1, 0)) %>%
-  filter(GmudeltaODFlag == 1) %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = deltaOD_Gmu, colour = as.factor(WL))) +
-  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Gmu - deltaOD_Gmu_se, ymax = deltaOD_Gmu + deltaOD_Gmu_se, colour = as.factor(WL))) + 
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid (cols = vars(Strain), rows = vars(O2)) +
-  theme_bw() +
-  labs(title = "Gompertz Chlorophyll Specific Growth rates - Flagged High Std error Omitted")
-
-ProcessDataNestGrowth %>%
- unnest(cols = c(lognormOD720_Gompertz_tidied),names_sep = "_") %>%
-  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, lognormOD720_Gompertz_tidied_term, lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error)) %>%
-  pivot_wider(names_from =  lognormOD720_Gompertz_tidied_term, values_from = c(lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error), names_sep = "_") %>%
-  rename(OD720_Gmax = lognormOD720_Gompertz_tidied_estimate_Gmax,
-         OD720_Gmax_se = lognormOD720_Gompertz_tidied_std.error_Gmax,
-         OD720_Gmu = lognormOD720_Gompertz_tidied_estimate_Gmu,
-         OD720_Gmu_se = lognormOD720_Gompertz_tidied_std.error_Gmu,
-         OD720_GLag = lognormOD720_Gompertz_tidied_estimate_GLag,
-         OD720_GLag_se = lognormOD720_Gompertz_tidied_std.error_GLag) %>%
-   mutate(GmuOD720Flag = if_else(OD720_Gmu_se < OD720_Gmu * GrowthFlagError, 1, 0)) %>%
-  # mutate(GrowthFlag = if_else((OD720_GLag + OD720_GLag_se) < ((OD720_Gmax - OD720_Gmax_se) & (OD720_Gmu_se < OD720_Gmu * GrowthFlagError) & (OD720_Gmax_se < OD720_Gmax * GrowthFlagError) ), 1, 0)) %>%
-   filter(GmuOD720Flag == 1) %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = OD720_Gmax)) +
-  geom_errorbar(aes(x = Par_ue, ymin = OD720_Gmax - OD720_Gmax_se, ymax = OD720_Gmax + OD720_Gmax_se, colour = as.factor(WL))) + 
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid (cols = vars(Strain), rows = vars(O2)) +
-  theme_bw() +
-  labs(title = "Gompertz Cell Specific gmax - Flagged High Std error Omitted")
-
-ProcessDataNestGrowth %>%
- unnest(cols = c(lognormdeltaOD_Gompertz_tidied),names_sep = "_") %>%
-  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, lognormdeltaOD_Gompertz_tidied_term, lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error)) %>%
-  pivot_wider(names_from =  lognormdeltaOD_Gompertz_tidied_term, values_from = c(lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error), names_sep = "_") %>%
-  rename(deltaOD_Gmax = lognormdeltaOD_Gompertz_tidied_estimate_Gmax,
-         deltaOD_Gmax_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmax,
-         deltaOD_Gmu = lognormdeltaOD_Gompertz_tidied_estimate_Gmu,
-         deltaOD_Gmu_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmu,
-         deltaOD_GLag = lognormdeltaOD_Gompertz_tidied_estimate_GLag,
-         deltaOD_GLag_se = lognormdeltaOD_Gompertz_tidied_std.error_GLag) %>%
-   mutate(GmudeltaODFlag = if_else(deltaOD_Gmu_se < deltaOD_Gmu * GrowthFlagError, 1, 0)) %>%
-  # mutate(GrowthFlag = if_else((deltaOD_GLag + deltaOD_GLag_se) < ((deltaOD_Gmax - deltaOD_Gmax_se) & (deltaOD_Gmu_se < deltaOD_Gmu * GrowthFlagError) & (deltaOD_Gmax_se < deltaOD_Gmax * GrowthFlagError) ), 1, 0)) %>%
-   filter(GmudeltaODFlag == 1) %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = deltaOD_Gmax)) +
-  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Gmax - deltaOD_Gmax_se, ymax = deltaOD_Gmax + deltaOD_Gmax_se, colour = as.factor(WL))) + 
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid (cols = vars(Strain), rows = vars(O2)) +
-  theme_bw() +
-  labs(title = "Gompertz Chlorophyll Specific gmax - Flagged High Std error Omitted")
+  labs(title = "Logistic chlorophyll specific growth rates - High Std error fits omitted")
 
@@
   labs(title = "Logistic chlorophyll specific - All Growth")
-
-ProcessDataNestGrowth %>%
- unnest(cols = c(lognormOD720_Gompertz_tidied),names_sep = "_") %>%
-  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, lognormOD720_Gompertz_tidied_term, lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error)) %>%
-  pivot_wider(names_from =  lognormOD720_Gompertz_tidied_term, values_from = c(lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error), names_sep = "_") %>%
-  rename(OD720_Gmax = lognormOD720_Gompertz_tidied_estimate_Gmax,
-         OD720_Gmax_se = lognormOD720_Gompertz_tidied_std.error_Gmax,
-         OD720_Gmu = lognormOD720_Gompertz_tidied_estimate_Gmu,
-         OD720_Gmu_se = lognormOD720_Gompertz_tidied_std.error_Gmu,
-         OD720_GLag = lognormOD720_Gompertz_tidied_estimate_GLag,
-         OD720_GLag_se = lognormOD720_Gompertz_tidied_std.error_GLag) %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = OD720_Gmu, colour = as.factor(WL))) +
-  geom_errorbar(aes(x = Par_ue, ymin = OD720_Gmu - OD720_Gmu_se, ymax = OD720_Gmu + OD720_Gmu_se, colour = as.factor(WL))) + 
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid (cols = vars(Strain), rows = vars(O2)) +
-  theme_bw()+
-  labs(title = "Gompertz Cell Specific Growth Rates- All Growth")
-
-ProcessDataNestGrowth %>%
- unnest(cols = c(lognormdeltaOD_Gompertz_tidied),names_sep = "_") %>%
-  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, lognormdeltaOD_Gompertz_tidied_term, lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error)) %>%
-  pivot_wider(names_from =  lognormdeltaOD_Gompertz_tidied_term, values_from = c(lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error), names_sep = "_") %>%
-  rename(deltaOD_Gmax = lognormdeltaOD_Gompertz_tidied_estimate_Gmax,
-         deltaOD_Gmax_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmax,
-         deltaOD_Gmu = lognormdeltaOD_Gompertz_tidied_estimate_Gmu,
-         deltaOD_Gmu_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmu,
-         deltaOD_GLag = lognormdeltaOD_Gompertz_tidied_estimate_GLag,
-         deltaOD_GLag_se = lognormdeltaOD_Gompertz_tidied_std.error_GLag) %>%
-  mutate(GmudeltaODFlag = if_else(deltaOD_Gmu_se < deltaOD_Gmu * GrowthFlagError, 1, 0)) %>%
- # mutate(GrowthFlag = if_else((deltaOD_GLag + deltaOD_GLag_se) < ((deltaOD_Gmax - deltaOD_Gmax_se) & (deltaOD_Gmu_se < deltaOD_Gmu * GrowthFlagError) & (deltaOD_Gmax_se < deltaOD_Gmax * GrowthFlagError) ), 1, 0)) %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = deltaOD_Gmu, colour = as.factor(WL))) +
-  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Gmu - deltaOD_Gmu_se, ymax = deltaOD_Gmu + deltaOD_Gmu_se, colour = as.factor(WL))) + 
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid (cols = vars(Strain), rows = vars(O2)) +
-  theme_bw() +
-  labs(title = "Gompertz Chlorophyll Specific Growth rates - All Growth")
-
-# ProcessDataNestGrowth %>%
-#  unnest(cols = c(lognormOD720_Gompertz_tidied),names_sep = "_") %>%
-#   select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, lognormOD720_Gompertz_tidied_term, lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error)) %>%
-#   pivot_wider(names_from =  lognormOD720_Gompertz_tidied_term, values_from = c(lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error), names_sep = "_") %>%
-#   rename(OD720_Gmax = lognormOD720_Gompertz_tidied_estimate_Gmax,
-#          OD720_Gmax_se = lognormOD720_Gompertz_tidied_std.error_Gmax,
-#          OD720_Gmu = lognormOD720_Gompertz_tidied_estimate_Gmu,
-#          OD720_Gmu_se = lognormOD720_Gompertz_tidied_std.error_Gmu,
-#          OD720_GLag = lognormOD720_Gompertz_tidied_estimate_GLag,
-#          OD720_GLag_se = lognormOD720_Gompertz_tidied_std.error_GLag) %>%
-#   ggplot() +
-#   geom_point(aes(x = Par_ue, y = OD720_Gmax)) +
-#   geom_errorbar(aes(x = Par_ue, ymin = OD720_Gmax - OD720_Gmax_se, ymax = OD720_Gmax + OD720_Gmax_se, colour = as.factor(WL))) + 
-#   scale_colour_manual(values = MCMIXColours) +
-#   facet_grid (cols = vars(Strain), rows = vars(O2)) +
-#   theme_bw()+
-#   labs(title = "Gompertz Cell Specific gmax - All Growth")
-
-# 
-# ProcessDataNestGrowth %>%
-#  unnest(cols = c(lognormdeltaOD_Gompertz_tidied),names_sep = "_") %>%
-#   select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, lognormdeltaOD_Gompertz_tidied_term, lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error)) %>%
-#   pivot_wider(names_from =  lognormdeltaOD_Gompertz_tidied_term, values_from = c(lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error), names_sep = "_") %>%
-#   rename(deltaOD_Gmax = lognormdeltaOD_Gompertz_tidied_estimate_Gmax,
-#          deltaOD_Gmax_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmax,
-#          deltaOD_Gmu = lognormdeltaOD_Gompertz_tidied_estimate_Gmu,
-#          deltaOD_Gmu_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmu,
-#          deltaOD_GLag = lognormdeltaOD_Gompertz_tidied_estimate_GLag,
-#          deltaOD_GLag_se = lognormdeltaOD_Gompertz_tidied_std.error_GLag) %>%
-#    mutate(GmudeltaODFlag = if_else(deltaOD_Gmu_se < deltaOD_Gmu * GrowthFlagError, 1, 0)) %>%
-#   # mutate(GrowthFlag = if_else((deltaOD_GLag + deltaOD_GLag_se) < ((deltaOD_Gmax - deltaOD_Gmax_se) & (deltaOD_Gmu_se < deltaOD_Gmu * GrowthFlagError) & (deltaOD_Gmax_se < deltaOD_Gmax * GrowthFlagError) ), 1, 0)) %>%
-#   ggplot() +
-#   geom_point(aes(x = Par_ue, y = deltaOD_Gmax)) +
-#   geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Gmax - deltaOD_Gmax_se, ymax = deltaOD_Gmax + deltaOD_Gmax_se, colour = as.factor(WL))) + 
-#   scale_colour_manual(values = MCMIXColours) +
-#   facet_grid (cols = vars(Strain), rows = vars(O2)) +
-#   theme_bw() +
-#   labs(title = "Gompertz Chlorophyll Specific gmax - All Growth")
 

### 2023-12-07 Code/MultiDataProcessPico.Rmd
Added attonation to chunks

@@
 
-# Save .Rds of ProcessDataNestGrowth containing logistic and gompertz fits of growth data from time resolved and whole interval fits.
-This .Rds is the substrate for the 'MultiCultiCompare.Rmd to compare information across multiple runs.
+# Save .Rds of ProcessDataNestGrowth containing logistic fits of growth data from time resolved and whole interval fits.
+This .Rds is the substrate for the 'MultiDataGrowthAssessPico.Rmd to compare information across multiple runs.
 ```{r save rds}
@@
 
+Plot all Fit Terms vs. conditions- no filters
+```{r plot all}
+ProcessDataNestGrowth %>%
+ unnest(cols = c(OD720_logistic_tidied),names_sep = "_") %>%
+  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, OD720_logistic_tidied_term, OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error)) %>%
+  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error), names_sep = "_") %>%
+  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
+         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
+         OD720_Lmu = OD720_logistic_tidied_estimate_Lmu,
+         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
+         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,
+         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept) %>%
+  ggplot() +
+  geom_point(aes(x = Par_ue, y = OD720_Lmu, colour = as.factor(WL))) +
+  geom_errorbar(aes(x = Par_ue, ymin = OD720_Lmu - OD720_Lmu_se, ymax = OD720_Lmu + OD720_Lmu_se, colour = as.factor(WL))) +
+  scale_colour_manual(values = MCMIXColours) +
+  facet_grid (cols = vars(Strain), rows = vars(O2)) +
+  theme_bw() +
+  labs(title = "Logistic cell Specific Growth Rate - All data")
+
+ProcessDataNestGrowth %>%
+ unnest(cols = c(deltaOD_logistic_tidied),names_sep = "_") %>%
+  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, deltaOD_logistic_tidied_term, deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error)) %>%
+  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error), names_sep = "_") %>%
+  rename(deltaOD_Lmax = deltaOD_logistic_tidied_estimate_Lmax,
+         deltaOD_Lmax_se = deltaOD_logistic_tidied_std.error_Lmax,
+         deltaOD_Lmu = deltaOD_logistic_tidied_estimate_Lmu,
+         deltaOD_Lmu_se = deltaOD_logistic_tidied_std.error_Lmu,
+         deltaOD_Lintercept = deltaOD_logistic_tidied_estimate_Lintercept,
+         deltaOD_Lintercept_se = deltaOD_logistic_tidied_std.error_Lintercept) %>%
+  ggplot() +
+  geom_point(aes(x = Par_ue, y = deltaOD_Lmu, colour = as.factor(WL))) +
+  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu - deltaOD_Lmu_se, ymax = deltaOD_Lmu + deltaOD_Lmu_se, colour = as.factor(WL))) +
+  scale_colour_manual(values = MCMIXColours) +
+  facet_grid (cols = vars(Strain), rows = vars(O2)) +
+  theme_bw() +
+  labs(title = "Logistic chlorophyll specific - All data")
+
+```
+
 Plot Fit Terms vs. conditions - High Std error filtered out by flag argument
@@
   labs(title = "Logistic chlorophyll specific growth rates - High Std error fits omitted")
-
-```
-
-Plot all Fit Terms vs. conditions- no filters
-```{r plot all}
-ProcessDataNestGrowth %>%
- unnest(cols = c(OD720_logistic_tidied),names_sep = "_") %>%
-  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, OD720_logistic_tidied_term, OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error)) %>%
-  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error), names_sep = "_") %>%
-  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
-         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
-         OD720_Lmu = OD720_logistic_tidied_estimate_Lmu,
-         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
-         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,
-         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept) %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = OD720_Lmu, colour = as.factor(WL))) +
-  geom_errorbar(aes(x = Par_ue, ymin = OD720_Lmu - OD720_Lmu_se, ymax = OD720_Lmu + OD720_Lmu_se, colour = as.factor(WL))) +
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid (cols = vars(Strain), rows = vars(O2)) +
-  theme_bw() +
-  labs(title = "Logistic cell Specific Growth Rate - All Growth")
-
-ProcessDataNestGrowth %>%
- unnest(cols = c(deltaOD_logistic_tidied),names_sep = "_") %>%
-  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, deltaOD_logistic_tidied_term, deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error)) %>%
-  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error), names_sep = "_") %>%
-  rename(deltaOD_Lmax = deltaOD_logistic_tidied_estimate_Lmax,
-         deltaOD_Lmax_se = deltaOD_logistic_tidied_std.error_Lmax,
-         deltaOD_Lmu = deltaOD_logistic_tidied_estimate_Lmu,
-         deltaOD_Lmu_se = deltaOD_logistic_tidied_std.error_Lmu,
-         deltaOD_Lintercept = deltaOD_logistic_tidied_estimate_Lintercept,
-         deltaOD_Lintercept_se = deltaOD_logistic_tidied_std.error_Lintercept) %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = deltaOD_Lmu, colour = as.factor(WL))) +
-  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu - deltaOD_Lmu_se, ymax = deltaOD_Lmu + deltaOD_Lmu_se, colour = as.factor(WL))) +
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid (cols = vars(Strain), rows = vars(O2)) +
-  theme_bw() +
-  labs(title = "Logistic chlorophyll specific - All Growth")
 

### 2023-12-07 Code/MultiDataImportPico.Rmd
Fixed file path in ProcessPico rmd
Removed redundant chunks. Added more annotations.

@@
 
-# Load Libraries and set Project Variables
-
+# Load Libraries
 ```{r load libraries}
@@
 
+# Set Project Variables
 ```{r set project variables}
@@
 
+# number of rows to skip upon read csv
 Skip <- 20
@@
 # List previously imported MultiCulti files
-
 ```{r previously imported files}
@@
 # List MultiCulti files for Project that are saved in DataIn
-
 ```{r MultiCulti files}
@@
 
-# Set Target File
+# Set Target File and read in csv
 ```{r set TargetFile and read csv}
 
-TargetFile <- "20221021_PICO_MCMIX006_RUN96.csv"
+TargetFile <- "20211223_PICO_MCMIX006_RUN42.csv"
 
@@
 
-```
-
-## Create function using data.table::fread to skip the beginning comments and starts reading file after key word Skip
-
-```{r fread_plus}
-# fread_plus <- function(Flnm, Skip){data.table::fread(file = Flnm, skip = Skip) %>%
-#     mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(Flnm)$ctime))
-# }
-```
-
-# Read in TargetFile
-
-select(-c(V5)) only needed for some files.
-
-```{r Read TargetFile}
-# #abs-time is failing because it contains ',' in the variable values; file is actually a .tsv, not a .csv
-# #abs-time not currently used?
-# # TargetData <- fread_plus(Flnm = TargetFile, Skip = "key") %>%
-# # select(-c(V5))
-# 
-# #run this if V5 is the 'value' column
-# TargetData <- fread_plus(Flnm = TargetFile, Skip = "key")  %>%
-#    select(-c(V5))
-# TargetData <- fread_plus(Flnm = paste(DataIn, "20211223_PICO_MCMIX006_RUN42.csv", sep = ":"), Skip = "key")  %>%
-#    select(-c(V5))
-# # %>%
-# #  select(-c(value)) %>%
-# #   rename(value = V5)
-# 
-# 
-# TargetData[1:10,]
-# 
-# #check whether all necessary values for 'key' are present; people forget to 'export all' values from PSI
-# unique(TargetData$key)
 ```
@@
 
-Run this chunk only for tubes with OD680 and/or OD720 < 0
-This will keep record of tubes even if they did not grow or had negative growth. These tubes get filtered out later if you do not run this chunk
-Remember to comment out after use 
-```{r, Add dummy points if a tube has OD values less than zero}
+ Run this chunk only for tubes with OD680 and/or OD720 < 0 --> -->
+This will keep record of tubes even if they did not grow or had negative growth. These tubes get filtered out later if you do not run this chunk.
+Remember to comment out after use.
+```{r, Add positive OD dummy points}
 
@@
 
-MAD is median absolute deviation Used median as opposed to mean to filter anomalous OD values due to affects of bubbling interference because determining outliers from the mean in a given window with many outliers were not detected since deviations from the mean were low.
+MAD is median absolute deviation.
+Used median as opposed to mean to filter anomalous OD values due to affects of bubbling interference because determining outliers from the mean in a given window with many outliers were not detected since deviations from the mean were low.
 ```{r filter bad OD and data points after experiment end time }
@@
 #moving average screen
-MovAvgScreen <- 2 # 6
-MovAvgWindow <- 2 # 20
+MovAvgScreen <- 6 # 6
+MovAvgWindow <- 20 # 20
 
@@
 ```
+
 # check to confirm filter and ensure there are data points for all 8 tubes.
 If there is a missing tube, confirm that data was filtered out because OD680 and/or OD720 <0.
-If this is the case run the chunk "Add dummy points if a tube has OD values less than zero" above and rerun subsequent chunks.
+If this is the case run the chunk "Add positive OD dummy points" above and rerun subsequent chunks.
 ```{r filterdataplot}

### 2023-12-07 Code/MultiDataImportPico.Rmd
Added more chunk annotations

@@
 
-TargetFile <- "20211223_PICO_MCMIX006_RUN42.csv"
+TargetFile <- "20230210_PICO_MCMIX006_RUN108.csv"
 
@@
 
-#add ln(value) later
-
 ```
@@
 ## Create preliminary plot for TargetData
-
+# Plots all OD values. True detection is OD680 and false detection is OD720.
 ```{r prelim plot}
-#Run <- c("MultiCulti/20200124_PICO_MCMIX004_RUN1.csv", "MultiCulti/20200124_PICO_MCMIX006_RUN2.csv")
 
@@
 Pivot_wider to get actinic-lights data aligned with relevant sensor
-data. Why are there NULL values in the OD sensor columns? Should always
-have a value? Import issue? Misalignment b/t light and OD? Need to
-include arrange(Filename, time, Tube) to keep things aligned! Need to
-group_by and/or reorder rows appropirately; Be Careful
+data. Need to include arrange(Filename, time, Tube) to keep things aligned! Need to
+group_by and/or reorder rows appropriately; Be Careful
 
@@
 Interpolate NA in actinic light columns from last observation, arrange
-by MC & Tube Then generate Actinic_par summary column If multiple lights
-are activated this chunk will give the summed par of all different
+by MC & Tube Then generate Actinic_par summary column. If multiple lights
+are activated, this chunk will give the summed par of all different
 colours for the tube. If a single actinic light is activated per tube,
@@
 
-#drop original actinic light columns?
-# select(!contains("actinic-lights.light"))
-
 TargetDataWide[1:10,]
@@
 od-sensors-X.od-680 columns. This might cause problems later matching OD
-measures to actinic light colours. Filter out rows where OD \<= 0
+measures to actinic light colours.
 
@@
    select(!contains("od-sensors"))
-  # filter(OD680 > 0,
-  #        OD720 > 0
 
-#move filtering for OD680 >0 until just before curve fitting to avoid data structure problems
 TargetDataWide[1:10,]
@@
 ```
-
+# Prelim plot with culture meta data
 ```{r second prelim plot}
@@
          IsMovMAD720Outlier = if_else(OD720 > MovMedian720 + (MovMAD720 * MovAvgScreen) | OD720 < MovMedian720 - (MovMAD720 * MovAvgScreen), 1,0))
-
-         # OD680 = if_else(OD680 > MovMedian680 + (MovMAD680 * MovAvgScreen) | OD680 < MovMedian680 - (MovMAD680 * MovAvgScreen), MovMedian680, OD680), #consider replacing OD680 and OD720 rather than filter
-         # OD720 = if_else(OD720 > MovMedian720 + (MovMAD720 * MovAvgScreen) | OD720 < MovMedian720 - (MovMAD720 * MovAvgScreen), MovMedian720, OD720)
 
@@
 
-Implement Daily Cumulative PAR for Corrected Actinic by numeric integration
+# Implement Daily Cumulative PAR for Corrected Actinic by numeric integration
 
@@
 
-# Save .Rds of Imported Data from TargetFile
-
+# Save compressed .Rds of Imported Data from TargetFile
 ```{r save Rds of imported data}

### 2023-12-07 Code/OlisImportPurCalc.Rmd
Fixed saveRDS filepath so that PUR generated data is saved.
Changed path to DataOut

@@
 
-DataOut <- file.path("..", "ProcessedData")
+DataOut <- file.path("..", "Data", "ProcessedData","MultiCultiEmissionData")
 
@@
 
- save nested 
-```{r Save rds and csv}
+# save nested 
+```{r Save rds}
 
-saveRDS(object = PicoNestedPurOlisData, file = file.path(DataOut, "PicoNestedPurOlisData.Rds"))
+# saveRDS(object = PicoNestedPurOlisData, file = file.path(DataOut, "PicoNestedPurOlisData.Rds"))
 
-# write_csv(PicoNestedPurOlisData, file = file.path(DataOut, paste(Project, "NestedPurOlisData",".csv",sep = ""),fsep = .Platform$file.sep))
+saveRDS(PicoNestedPurOlisData, file.path(DataOut, paste(Project, "PicoNestedPurOlisData.Rds", sep = "_"), fsep = .Platform$file.sep))
 

### 2023-12-07 Code/JazDataImport.Rmd
Changed folder names and paths to align with Sylwia

@@
 
-DataIn <- file.path("..", "Data","RawData", "MCEmissionSpectra", fsep = .Platform$file.sep)
+DataIn <- file.path("..", "Data","RawData", "JazEm", fsep = .Platform$file.sep)
 
-DataOut<- file.path("..", "Data", "ProcessedData", fsep = .Platform$file.sep)
+DataOut<- file.path("..", "Data", "ImportedData", "ImportedJazEmData", fsep = .Platform$file.sep)
 

### 2023-12-07 Code/MultiDataImportPico.Rmd
Changed folder names and paths to align with Sylwia

@@
 DataIn <- file.path("..", "Data", "RawData", "MultiCultiData.zip")
-DataOut <- file.path("..","Data", "ImportedData", "MultiCultiData")
+DataOut <- file.path("..","Data", "ImportedData", "ImportedMCData")
 

### 2023-12-07 Code/MultiDataProcessPico.Rmd
Changed folder names and paths to align with Sylwia

@@
 Project <- "PICO"
-DataIn <- file.path("..", "Data", "ImportedData", "MultiCultiData")
-DataOut <- file.path("..", "Data","ProcessedData", "MultiCultiData")
+DataIn <- file.path("..", "Data", "ImportedData", "ImportedMCData")
+DataOut <- file.path("..", "Data","ProcessedData", "ProcessedMCData")
 

### 2023-12-07 Code/OlisImportPurCalc.Rmd
Changed DataOut path
Changed folder names and paths to align with Sylwia

@@
 
-DataInSpectra <- file.path("..", "Data", "ProcessedData",  fsep = .Platform$file.sep)
+DataInSpectra <- file.path("..", "Data", "ImportedData","ImportedJazEmData",  fsep = .Platform$file.sep)
 
-DataInPAR <- file.path("..", "Data","RawData","MCEmissionSpectra", fsep = .Platform$file.sep)
+DataInPAR <- file.path("..", "Data","RawData","JazEm", fsep = .Platform$file.sep)
 
-DataOut <- file.path("..", "Data", "ProcessedData","MultiCultiEmissionData")
+DataOut <- file.path("..", "Data", "ImportedData","ImportedOlisData")
 

### 2023-12-07 Code/JazDataImport.Rmd
Change file path

@@
 JazSpec <- JazSpec %>% 
-  mutate(Filename = str_remove(Filename, pattern = "../Data/RawData/MCEmissionSpectra/")) |>
-  separate(col = Filename, into = c("Date", "MultiCulti", "Par", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE)
+  mutate(Filename = str_remove(Filename, pattern = DataIn)) |>
+  separate(col = Filename, into = c("FP0","Date", "MultiCulti", "Par", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE) %>% 
+  select(-FP0)
 
@@
 
- saveRDS(JazSpecNest, file.path(DataOut, paste(Project, "MultiCultiSpectra.Rds", sep = "_"), fsep = .Platform$file.sep))
+ saveRDS(JazSpecNest, file.path(DataOut, paste(Project, "JazEmSpectra.Rds", sep = "_"), fsep = .Platform$file.sep))
 

### 2023-12-07 Code/OlisImportPurCalc.Rmd
Change file path

@@
 library(readxl)
-
+library(photobiologyWavebands)
 library(ggspectra)
@@
 ```{r set colours}
-Wavelengths_nm = c(405, 450, 475, 530, 615, 660, 730, "WW")
-Colours_nm = c("violet", "darkblue", "dodgerblue", "darkgreen","orange","red","purple", "black")
+MyWavelengths = c(405, 445, 470, 530, 620, 660, 730, "WW")
+MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(445), w_length2rgb(470), w_length2rgb(530), 
+                   w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black"))
 
-names(Colours_nm) <- Wavelengths_nm
-Colours_nm
+names(MCMIXColours) <- MyWavelengths
+MCMIXColours
 
@@
 
-MC_Spectra <- readRDS(file = file.path(DataInSpectra, "PICO_MultiCultiSpectra.Rds"))
+MC_Spectra <- readRDS(file = file.path(DataInSpectra, "PICO_JazEmSpectra.Rds"))
 
@@
   geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
-  scale_color_manual(values = Colours_nm) +
+  scale_color_manual(values = MCMIXColours) +
  # guides(colour = FALSE) +
@@
   geom_point(aes(x = nm, y = Absorbance, colour = as.factor(WL), label = ID)) +
-  scale_color_manual(values = Colours_nm) +
+  scale_color_manual(values = MCMIXColours) +
   #guides(colour = FALSE) +
@@
  # geom_point(aes(x = nm, y = Absorbance, colour = ID)) +
- #scale_color_manual(values = Colours_nm) +
+ #scale_color_manual(values = MCMIXColours) +
   #guides(colour = FALSE) +

### 2023-12-07 Code/MetaDataImport.Rmd
Removed EndDate from CultureCatalog.

@@
 ProjectRows <- c("MiSa|JuNa|SaAr")
-ProjectCols <- c("PrimaryOperator", "SampleID", "Run", "ID", "Strain", "ExpCul", "ExpDate", "ExpStartTime", "Par_ue", "Photoperiod", "Temp_c", "MC", "Tube", "EndDate","O2", "O2_Category", "WL","LightShape", "Optode","OptodeCh","OptodeMeasure", "ExpEndDate")
+ProjectCols <- c("PrimaryOperator", "SampleID", "Run", "ID", "Strain", "ExpCul", "ExpDate", "ExpStartTime", "Par_ue", "Photoperiod", "Temp_c", "MC", "Tube","O2", "O2_Category", "WL","LightShape", "Optode","OptodeCh","OptodeMeasure", "ExpEndDate")
 
@@
   filter(str_detect(ID,  ProjectRows)) %>% 
-  select(ProjectCols)
+  select(ProjectCols) %>% 
+  rename(CultureID = ID)
 

### 2023-12-07 Code/MultiDataImportPico.Rmd
Changed file name to process

@@
 
-# Import MetaData 
-```{r load Catalog direct from googlesheet, results = "hide"}
-# #implement read with googlesheet name instead of full url
-
-# gs4_deauth()
-
-# imagine this is the URL or ID of a Sheet readable by anyone (with a link)
-
-# Catalog <- read_sheet("https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0") %>%
-
-  # read_sheet has an annoying "feature" to set the type of columns it can't parse to a list.
-  # ggplot/dplyr doesn't like working with a dataframe of lists.
-  # In this case WL is set to a list since some values are numbers, some are strings, some are blank.
-  # To fix this, first drop all rows missing WL, then unlist.
-  # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.
-#   drop_na(WL) %>%
-#   mutate(WL = unlist(WL))
-# 
-# as.data.frame(Catalog)
-# 
-# Catalog <- Catalog %>%
-#    mutate(ExpDate = ymd(ExpDate),
-#           ExpEndDate = ymd_hms(`ExpEndDate`))
-
-```
-
 ```{r read locally stored metadata from rds}
@@
 
-TargetFile <- "20230210_PICO_MCMIX006_RUN108.csv"
+TargetFile <- "20221021_PICO_MCMIX006_RUN96.csv"
 
@@
   scale_colour_manual(values = MCMIXColours) +
-  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
-  facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, ID)) +
+  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; CultureID; Tube") +
+  facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, CultureID)) +
   theme_bw() +  
@@
  filter(OD680 > 0) %>% # consider this rule for OD720 as well
-  group_by(ID) %>%
+  group_by(CultureID) %>%
   arrange(Filename, MC, Tube, time) %>%
@@
   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
- facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, ID)) +
+ facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, CultureID)) +
   theme_bw() +  
@@
   # coord_cartesian(xlim = c(0, 800)) +
-  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; ID; Tube") +
-  # facet_grid(rows = vars(O2), cols = vars(Tube, Par_ue, Strain, ID)) +
+  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; CultureID; Tube") +
+  # facet_grid(rows = vars(O2), cols = vars(Tube, Par_ue, Strain, CultureID)) +
   annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkblue") +
@@
   coord_cartesian(xlim = c(0, 400)) +
-  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; ID; Tube") +
-  facet_grid(rows = vars(O2), cols = vars(Par_ue, Strain, ID, Tube)) +
+  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; CultureID; Tube") +
+  facet_grid(rows = vars(O2), cols = vars(Par_ue, Strain, CultureID, Tube)) +
   annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkblue") +

### 2023-12-07 Code/MultiDataProcessPico.Rmd
Removed some extra plots

@@
 ```{r read ProcessFile}
-ProcessFile <- "../Data/ImportedData/MultiCultiData/20211223_PICO_MCMIX006_RUN42_TargetDataMetaFilter.Rds"
+ProcessFile <- "../Data/ImportedData/ImportedMCData/20230210_PICO_MCMIX006_RUN108_TargetDataMetaFilter.Rds"
 
@@
 
-ProcessData <- ProcessData %>%
-  filter(Strain == "SS120" & time >= InitialTime |
-         Strain == "MIT9313" |
-         Strain =="MED4"  )
+# ProcessData <- ProcessData %>%
+#   filter(Strain == "SS120" & time >= InitialTime |
+#          Strain == "MIT9313" |
+#          Strain =="MED4"  )
 
@@
 ```{r prelim ProcessPlot}
-#Run <- c("MultiCulti/20200124_PICO_MCMIX004_RUN1.csv", "MultiCulti/20200124_PICO_MCMIX006_RUN2.csv")
 
@@
    geom_vline(aes(xintercept = 1 * 24), linetype = "dashed") + 
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
-  theme_bw()
-
-ProcessData %>%
-  #filter(Tube == 5) %>%
-  ggplot() +
-  geom_point(aes(x = time, y = log(OD720)), size = 0.1) +
-  geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
-  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
-  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
   scale_colour_manual(values = MCMIXColours) +
@@
 
-ProcessData %>%
- # filter(Tube == 1) %>%
-  ggplot() +
-  geom_point(aes(x = time, y = lognormOD720), size = 0.1) +
-  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
-  theme_bw()
-
-ProcessData %>%
- # filter(Tube == 1) %>%
-  ggplot() +
-  geom_point(aes(x = time, y = lognormdeltaOD), size = 0.1) +
-  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
-  theme_bw()
-
-ProcessData %>%
- filter(Tube == 5) %>%
-  ggplot() +
-  geom_point(aes(x = time, y = deltaOD), size = 0.1) +
-  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
-  theme_bw()
 ```
@@
 
-# ProcessData <- ProcessData %>%
-#   group_by(Tube) %>%
-#    mutate(TrimRollMeanOD720 = zoo::rollmean(OD720, k = RollWindow, align = "right", fill = NA),
-#           TrimRollMeandeltaOD = zoo::rollmean(deltaOD, k = RollWindow, align = "right", fill = NA)
-#           ) %>%
-#   mutate(DeclineFlagdeltaOD = if_else(time > (time[which.max(TrimRollMeandeltaOD)] + DeclineWindow) & (max(TrimRollMeandeltaOD, na.rm = TRUE) - min(TrimRollMeandeltaOD, na.rm = TRUE)) > deltaODGrowthFlagValue, 1, 0),
-#          DeclineFlagOD720 = if_else(time > (time[which.max(TrimRollMeanOD720)] + DeclineWindow) & (max(TrimRollMeanOD720, na.rm = TRUE) - min(TrimRollMeanOD720, na.rm = TRUE)) > OD720GrowthFlagValue, 1, 0)) %>%
-#     filter(DeclineFlagdeltaOD == 0,
-#            DeclineFlagOD720 == 0) %>%
-#   select(-c("TrimRollMeanOD720", "TrimRollMeandeltaOD")) %>%
-#   ungroup()
-# 
-# glimpse(ProcessData)
+ProcessData <- ProcessData %>%
+  group_by(Tube) %>%
+   mutate(TrimRollMeanOD720 = zoo::rollmean(OD720, k = RollWindow, align = "right", fill = NA),
+          TrimRollMeandeltaOD = zoo::rollmean(deltaOD, k = RollWindow, align = "right", fill = NA)
+          ) %>%
+  mutate(DeclineFlagdeltaOD = if_else(time > (time[which.max(TrimRollMeandeltaOD)] + DeclineWindow) & (max(TrimRollMeandeltaOD, na.rm = TRUE) - min(TrimRollMeandeltaOD, na.rm = TRUE)) > deltaODGrowthFlagValue, 1, 0),
+         DeclineFlagOD720 = if_else(time > (time[which.max(TrimRollMeanOD720)] + DeclineWindow) & (max(TrimRollMeanOD720, na.rm = TRUE) - min(TrimRollMeanOD720, na.rm = TRUE)) > OD720GrowthFlagValue, 1, 0)) %>%
+    filter(DeclineFlagdeltaOD == 0,
+           DeclineFlagOD720 == 0) %>%
+  select(-c("TrimRollMeanOD720", "TrimRollMeandeltaOD")) %>%
+  ungroup()
+
+glimpse(ProcessData)
 
@@
 ProcessData %>%
-  #filter(Tube == 5) %>%
-  ggplot() +
-  geom_point(aes(x = time, y = log(OD720)), size = 0.1) +
-  geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
-   geom_vline(aes(xintercept = 1 * 24), linetype = "dashed") + 
-  geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
-  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
-  theme_bw()
-
-ProcessData %>%
  # filter(Tube == 1) %>%
@@
 
-ProcessData %>%
- # filter(Tube == 1) %>%
-  ggplot() +
-  geom_point(aes(x = time, y = lognormOD720), size = 0.1) +
-  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
-  theme_bw()
-
-ProcessData %>%
- # filter(Tube == 6) %>%
-  ggplot() +
-  geom_point(aes(x = time, y = lognormdeltaOD), size = 0.1) +
-  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
-  theme_bw()
-
-ProcessData %>%
- filter(Tube == 6) %>%
-  ggplot() +
-  geom_point(aes(x = time, y = lognormdeltaOD), size = 0.1) +
-  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
-  theme_bw()
-
-ProcessData %>%
- filter(Tube == 6) %>%
-  ggplot() +
-  geom_point(aes(x = time, y = deltaOD), size = 0.1) +
-  #geom_point(aes(x = time, y = Actinic_par/100, colour = as.factor(WL)), size = 0.05) +
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid(rows = vars(O2), cols = vars(as.factor(Tube), Strain, Par_ue)) +
-  theme_bw()
-
 ```
 
-# Attempt  Fits of Data
+# Fits of Data
 Create R function for logistic equation.
-Check with Max for alternate formulations that include lag?
-Consider which parameter(s) to report for comparison(s) of strain responses to growth conditions
-  -mu
-  -Pmax
-  -other...
 ```{r fitting functions, message = FALSE}
@@
 
-# bob <- c(1,2,4,5,6,7)
-# 
-# growth_amp(y = bob)
-
 ```
 
-# As of Dec 2023 all the na_if code are not working so are commented out
 ```{r nested regressions }
@@
 
-#XXXDoug 16 May 2022XXX
-# %>%
-#    mutate(IsOD720_GLagNeg = if_else(lognormOD720_GompLag <= 0, 1, 0), # fails here because of Nulls generated line 437
-#           IsdeltaOD_GLagNeg = if_else(lognormdeltaOD_GompLag <= 0, 1, 0))
-#
-
 #Growthamp flags for growth up to 14 days 
@@
  saveRDS(object = ProcessDataNestGrowth, file = file.path(DataOut, paste(ProcessFileName,  "ProcessDataNestGrowth.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
-
-```
-
-```{r test fits}
-#Chunk to work out additions of new fit models
-
-# testamp <- ProcessData %>%
-#   filter(lognormdeltaOD > 0) %>%
-#   filter(lognormOD720 > 0) %>%
-# nest(tubedata = c(time,  ToD, Day, Actinic_par, OD680, OD720, deltaOD, ActinicMid_parOD720, ActinicMid_dayOD720,rollmeanOD720,rollmeandeltaOD,lognormOD720, lognormdeltaOD, LagSeedOD720, LagSeeddeltaOD)) %>%
-#   mutate(GrowthAmpdeltaOD = map(tubedata, ~growth_amp(y = .$rollmeandeltaOD)))
-#
 
@@
 
-ProcessDataNestGrowth %>%
-  filter(Tube == 5) %>%
-  mutate(OD720_logistic_predict = map(OD720_logistic, possibly(augment, otherwise = NULL))) %>%
-  unnest(cols = c(tubedata, OD720_logistic_predict),names_sep = "_") %>%
-  ggplot() +
-  geom_point(aes(x = tubedata_time, y = tubedata_OD720), colour = "darkgreen", size = 0.1) +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.fitted), colour = "black", size = 0.1) +
-  geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.resid), colour = "gold", size = 0.05, alpha = 0.5) +
-  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.01, alpha = 0.1) +
-  #coord_cartesian(xlim = c(0, 675)) +
-  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
-  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
-  annotate(geom = "text", x = OD_x, y = OD_y, label = "OD720", size = 5, colour = "darkgreen") +
-  annotate(geom = "text", x = Par_x, y = Par_y, label = "Light level", size = 5, colour = "darkblue") +
-  annotate(geom = "text", x = Resid_x, y = Resid_y, label = "Model residuals", size = 5, colour = "red") +
-  annotate(geom = "text", x = Predict_x, y = Predict_y, label = "Logistic Regression", size = 5, colour = "black") +
-  labs(subtitle = "Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName , y = "Optical Density (OD720)", x = "Elapsed Time (h)") +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)") +
-  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))
-
-ProcessDataNestGrowth %>%
-  #drop_na(deltaOD_logistic) %>%
-  filter(Tube == 6) %>%
-  mutate(deltaOD_logistic_predict = map(deltaOD_logistic, possibly(augment, otherwise = NULL))) %>%
-  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_") %>%
-  ggplot() +
-  geom_point(aes(x = tubedata_time, y = tubedata_deltaOD), colour = "darkgreen", size = 0.1) +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.fitted), colour = "black", size = 0.1) +
-  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.resid), colour = "gold", size = 0.05, alpha = 0.5) +
-  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.01, alpha = 0.1) +
-  #coord_cartesian(xlim = c(0, 675)) +
-  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
-  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
-  annotate(geom = "text", x = OD_x, y = OD_y, label = "deltaOD", size = 5, colour = "darkgreen") +
-  annotate(geom = "text", x = Par_x, y = Par_y, label = "Light level", size = 5, colour = "darkblue") +
-  annotate(geom = "text", x = Resid_x, y = Resid_y, label = "Model residuals", size = 5, colour = "red") +
-  annotate(geom = "text", x = Predict_x, y = Predict_y, label = "Logistic Regression", size = 5, colour = "black") +
-  labs(subtitle = "Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName , y = "Delta Optical Density (deltaOD)", x = "Elapsed Time (h)") +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)") +
-  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))
-
-ProcessDataNestGrowth %>%
- mutate(OD720trunc_logistic_predict = map(OD720trunc_logistic, possibly(augment, otherwise = NULL))) %>%
-  unnest(cols = c(OD720trunc_logistic_predict), names_sep = "_", keep_empty = TRUE) %>%
-  ggplot() +
-  geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_OD720), colour = "darkgreen", size = 0.1) +
-  scale_colour_manual(values = MCMIXColours) +
- # geom_text(data = . %>% filter(GrowthFlag_OD720 == 0), aes(x = 200, y = 0.2, label = "*"), size = 5) +
-  geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_.fitted), colour = "black", size = 0.1) +
-  geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_.resid), colour = "gold", size = 0.05) + 
-  #geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
-  #coord_cartesian(xlim = c(-5, 675)) +
-  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
-  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
-  labs(subtitle = "Dynamically Truncated Logistic Growth Curve (50% of max OD720):  Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "Optical Density (OD720)", x = "Elapsed Time (h)") +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")
-
-ProcessDataNestGrowth %>%
-  mutate(deltaODtrunc_logistic_predict = map(deltaODtrunc_logistic, possibly(augment, otherwise = NULL))) %>%
-  unnest(cols = c(deltaODtrunc_logistic_predict),names_sep = "_", keep_empty = TRUE) %>%
-  ggplot() +
-  geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = deltaODtrunc_logistic_predict_deltaOD), colour = "darkgreen", size = 0.1) +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = deltaODtrunc_logistic_predict_.fitted), colour = "black", size = 0.1) +
-  geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = deltaODtrunc_logistic_predict_.resid), colour = "gold", size = 0.05) +
-  #geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.05, alpha = 0.1) +
-  #coord_cartesian(xlim = c(-5, 675)) +
-  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
-  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
-  labs(subtitle = "Dynamically Truncated Logistic Growth Curve (50% of max deltaOD):   Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName, y = "Delta Optical Density (deltaOD)", x = "Elapsed Time (h)") +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")+
-  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))
-
-ProcessDataNestGrowth %>%
-  filter(Tube == 5) %>%
-  mutate(OD720trunc_logistic_predict = map(OD720trunc_logistic, possibly(augment, otherwise = NULL))) %>%
-  unnest(cols = c(OD720trunc_logistic_predict),names_sep = "_") %>%
-  ggplot() +
-  geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_OD720), colour = "darkgreen", size = 0.1) +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_.fitted), colour = "black", size = 0.1) +
-  geom_point(aes(x = OD720trunc_logistic_predict_time, y = OD720trunc_logistic_predict_.resid), colour = "gold", size = 0.05, alpha = 0.5) +
- # geom_point(aes(x = OD720trunc_logistic_predict_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.01, alpha = 0.1) +
-  #coord_cartesian(xlim = c(0, 675)) +
-  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
-  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
-  annotate(geom = "text", x = OD_x, y = OD_y, label = "OD720", size = 5, colour = "darkgreen") +
-  annotate(geom = "text", x = Par_x, y = Par_y, label = "Light level", size = 5, colour = "darkblue") +
-  annotate(geom = "text", x = Resid_x, y = Resid_y, label = "Model residuals", size = 5, colour = "red") +
-  annotate(geom = "text", x = Predict_x, y = Predict_y, label = "Logistic Regression", size = 5, colour = "black") +
-  labs(subtitle = "Dynamically Truncated Logistic Growth Curve:  Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName , y = "Optical Density (OD720)", x = "Elapsed Time (h)") +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)") +
-  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))
-
-ProcessDataNestGrowth %>%
-  filter(Tube == 5) %>%
-  mutate(deltaODtrunc_logistic_predict = map(deltaODtrunc_logistic, possibly(augment, otherwise = NULL))) %>%
-  unnest(cols = c(deltaODtrunc_logistic_predict),names_sep = "_") %>%
-  ggplot() +
-  geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = deltaODtrunc_logistic_predict_deltaOD), colour = "darkgreen", size = 0.1) +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = deltaODtrunc_logistic_predict_.fitted), colour = "black", size = 0.1) +
-  geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = deltaODtrunc_logistic_predict_.resid), colour = "gold", size = 0.05, alpha = 0.5) +
- # geom_point(aes(x = deltaODtrunc_logistic_predict_time, y = tubedata_Actinic_par/1000, colour = as.factor(WL)), size = 0.01, alpha = 0.1) +
-  #coord_cartesian(xlim = c(0, 675)) +
-  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
-  facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
-  annotate(geom = "text", x = OD_x, y = OD_y, label = "deltaOD", size = 5, colour = "darkgreen") +
-  annotate(geom = "text", x = Par_x, y = Par_y, label = "Light level", size = 5, colour = "darkblue") +
-  annotate(geom = "text", x = Resid_x, y = Resid_y, label = "Model residuals", size = 5, colour = "red") +
-  annotate(geom = "text", x = Predict_x, y = Predict_y, label = "Logistic Regression", size = 5, colour = "black") +
-  labs(subtitle = "Dynamically Truncated Logistic Growth Curve:  Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName , y = "Delta Optical Density (deltaOD)", x = "Elapsed Time (h)") +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)") +
-  guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))
+# ProcessDataNestGrowth %>%
+#   filter(Tube == 5) %>%
+#   mutate(OD720_logistic_predict = map(OD720_logistic, possibly(augment, otherwise = NULL))) %>%
+#   unnest(cols = c(tubedata, OD720_logistic_predict),names_sep = "_") %>%
+#   ggplot() +
+#   geom_point(aes(x = tubedata_time, y = tubedata_OD720), colour = "darkgreen", size = 0.1) +
+#   scale_colour_manual(values = MCMIXColours) +
+#   geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.fitted), colour = "black", size = 0.1) +
+#   geom_point(aes(x = tubedata_time, y = OD720_logistic_predict_.resid), colour = "gold", size = 0.05, alpha = 0.5) +
+#   geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/10000, colour = as.factor(WL)), size = 0.01, alpha = 0.1) +
+#   #coord_cartesian(xlim = c(0, 675)) +
+#   #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
+#   facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
+#   annotate(geom = "text", x = OD_x, y = OD_y, label = "OD720", size = 5, colour = "darkgreen") +
+#   annotate(geom = "text", x = Par_x, y = Par_y, label = "Light level", size = 5, colour = "darkblue") +
+#   annotate(geom = "text", x = Resid_x, y = Resid_y, label = "Model residuals", size = 5, colour = "red") +
+#   annotate(geom = "text", x = Predict_x, y = Predict_y, label = "Logistic Regression", size = 5, colour = "black") +
+#   labs(subtitle = "Tube; Growth Light (nm; µE); Strain; Photoperiod", caption = ProcessFileName , y = "Optical Density (OD720)", x = "Elapsed Time (h)") +
+#   theme_bw() +
+#   labs(colour = "Actinic PAR (nm)") +
+#   guides(colour = guide_legend(override.aes = list(size = 3,  alpha = 1)))
 
@@
 ```
-
-Compare truncated vs full run 
-```{r compare}
-
-ProcessDataNestGrowth %>%
-unnest(cols = c(OD720_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error, OD720_logistic_tidied_statistic, OD720_logistic_tidied_p.value), names_sep = "_")  %>%
-  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
-         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
-         OD720_Lmu = OD720_logistic_tidied_estimate_Lmu,
-         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
-         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,
-         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept)  %>%
- unnest(cols = c(OD720trunc_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_wider(names_from =  OD720trunc_logistic_tidied_term, values_from = c(OD720trunc_logistic_tidied_estimate, OD720trunc_logistic_tidied_std.error, OD720trunc_logistic_tidied_statistic, OD720trunc_logistic_tidied_p.value), names_sep = "_") %>%
-  rename(OD720_Trunc_Lmax = OD720trunc_logistic_tidied_estimate_Lmax,
-         OD720_Trunc_Lmax_se = OD720trunc_logistic_tidied_std.error_Lmax,
-         OD720_Trunc_Lmu = OD720trunc_logistic_tidied_estimate_Lmu,
-         OD720_Trunc_Lmu_se = OD720trunc_logistic_tidied_std.error_Lmu)  %>%
-  ggplot() +
-  geom_point(aes(x = OD720_TimetoMax, y = OD720_Lmu), colour = "Darkgreen", size = 4) +
-  #scale_colour_manual(values = MCMIXColours) +
- geom_point(aes(x = OD720trunc_TimetoMax, y = OD720_Trunc_Lmu), colour = "Red", size = 4) +
-ggrepel::geom_text_repel(aes(x = OD720trunc_TimetoMax, y = OD720_Trunc_Lmu, label= "Truncated"),hjust=0.5, vjust=1) +
-# scale_colour_manual(values = MCMIXColours) +
-#   scale_shape_manual(values = c(13, 16)) +
-#   geom_hline(yintercept = 0, linetype = "dashed") +
-#   geom_vline(xintercept = 0, linetype = "dashed") +
-#   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-#   coord_fixed(ratio = 1) +
-#   coord_cartesian(xlim = c (0, 0.05), ylim = c(0, 0.05)) +
-#   scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
-  # labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Gompertz Growth Rate (OD720_Gmu)", x = "Logistic Growth Rate (OD720_Lmu)") +
-  facet_grid(cols = vars(Tube, WL, Strain)) +
-  theme_bw() +
-  labs(title = "Full and Truncated Logistic Cell Specific Growth Rates (µ" ~ h^-1~")- All Growth",
-       x = "Time (h)")
-
-ProcessDataNestGrowth %>%
-unnest(cols = c(deltaOD_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error, deltaOD_logistic_tidied_statistic, deltaOD_logistic_tidied_p.value), names_sep = "_")  %>%
-  rename(deltaOD_Lmax = deltaOD_logistic_tidied_estimate_Lmax,
-         deltaOD_Lmax_se = deltaOD_logistic_tidied_std.error_Lmax,
-         deltaOD_Lmu = deltaOD_logistic_tidied_estimate_Lmu,
-         deltaOD_Lmu_se = deltaOD_logistic_tidied_std.error_Lmu,
-         deltaOD_Lintercept = deltaOD_logistic_tidied_estimate_Lintercept,
-         deltaOD_Lintercept_se = deltaOD_logistic_tidied_std.error_Lintercept)  %>%
- unnest(cols = c(deltaODtrunc_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_wider(names_from =  deltaODtrunc_logistic_tidied_term, values_from = c(deltaODtrunc_logistic_tidied_estimate, deltaODtrunc_logistic_tidied_std.error, deltaODtrunc_logistic_tidied_statistic, deltaODtrunc_logistic_tidied_p.value), names_sep = "_") %>%
-  rename(deltaOD_Trunc_Lmax = deltaODtrunc_logistic_tidied_estimate_Lmax,
-         deltaOD_Trunc_Lmax_se = deltaODtrunc_logistic_tidied_std.error_Lmax,
-         deltaOD_Trunc_Lmu = deltaODtrunc_logistic_tidied_estimate_Lmu,
-         deltaOD_Trunc_Lmu_se = deltaODtrunc_logistic_tidied_std.error_Lmu)  %>%
-  ggplot() +
-  geom_point(aes(x = deltaOD_TimetoMax, y = deltaOD_Lmu), colour = "Darkgreen", size = 4) +
-  #scale_colour_manual(values = MCMIXColours) +
- geom_point(aes(x = deltaODtrunc_TimetoMax, y = deltaOD_Trunc_Lmu), colour = "Red", size = 4) +
-ggrepel::geom_text_repel(aes(x = deltaODtrunc_TimetoMax, y = deltaOD_Trunc_Lmu, label= "Truncated"),hjust=0.5, vjust=1) +
-# scale_colour_manual(values = MCMIXColours) +
-#   scale_shape_manual(values = c(13, 16)) +
-#   geom_hline(yintercept = 0, linetype = "dashed") +
-#   geom_vline(xintercept = 0, linetype = "dashed") +
-#   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-#   coord_fixed(ratio = 1) +
-#   coord_cartesian(xlim = c (0, 0.05), ylim = c(0, 0.05)) +
-#   scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
-  # labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Gompertz Growth Rate (deltaOD_Gmu)", x = "Logistic Growth Rate (deltaOD_Lmu)") +
-  facet_grid(cols = vars(Tube, WL, Strain)) +
-  theme_bw() +
-  labs(title = "Full and Truncated Logistic Chlorophyll Specific Growth Rates (µ" ~ h^-1~")- All Growth",
-       x = "Time (h)")
-
-```

### 2023-12-07 Code/MultiDataGrowthAssessPico.Rmd
Added MultiCultiGrowthAssessPico to Github

---
title: "MultiDataGrowthAssess"
author:
- Laurel Genge
- Carlie Barnhill
- Max Berthold
- Douglas A. Campbell
- Mireille Savoie
date: "`r format(Sys.Date())`"
output:
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

## Set figure caption font size
```{css, echo=FALSE}
p.caption {
  font-size: 25px;
}
```

## Set Chunk Options
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

# Materials and Methods

## Load Libraries and set project variables

```{r load libraries, message= TRUE}
# libraries; Note check actual dependencies

library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(zoo)
library(RColorBrewer)
library(grid)
library(tidyverse)
#library(tidyquant)
#library(data.table)
#library(googledrive)
#library(googlesheets4)
#library(dplyr)
```

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn1 <- file.path("..","ProcessedData", "LogGrowthFits1")
DataIn2 <- file.path("..","ProcessedData", "LogGrowthFits2")
PlotsPath <- file.path("..","Plots")
ShinyPath <- file.path("..", "ShinyPico", "data")
DataOut <- file.path("..","GrowthAssessData")
MetaCatalog <- file.path("..","PicoCatalog.csv")

GrowthFlagError <- 0.2       # percentage of mu that std error must be less than

OD720GrowthAmpFlagValue = 0.010 # OD720 absolute change for setting GrowthFlag = 1 and DeclineFlag = 1; did culture show  growth;

deltaODGrowthAmpFlagValue = 0.007 # deltaOD absolute change for setting GrowthFlag = 1 and DeclineFlag = 1; did culture show  growth;

GrowthTerm <- "Gompertz Growth Rate"

```

```{r set colours}
MyWavelengths = c(405, 450, 475, 530, 615, 660, 730, "WW")
MCMIXColours = c("violet", "darkblue", "dodgerblue", "darkgreen","orange","red","purple", "black")

names(MCMIXColours) <- MyWavelengths
MCMIXColours

```

## List previously processed data

Note: Split files will not be correct for Par_ue, but Actinic_par should be OK Fix: replace MetaData Par_ue with max(Actinic_par) for each file or split file

```{r previous ProcessedData}
ProcessedFiles1 <- list.files(path = DataIn1, pattern = Project, full.names = TRUE)

ProcessedFiles1

ProcessedFiles2 <- list.files(path = DataIn2, pattern = Project, full.names = TRUE)

ProcessedFiles2
```

# Read .Rds, Summarize, Combine to single data frame

## Create function using to read in .Rds, adding source filename as a column

```{r readRDS_plus}
readRDS_plus <- function(Flnm){readRDS(file = Flnm) %>%
    mutate(Filename = Flnm)
}
```

## Read in ProcessedFiles .Rds 
## April 2023, Had to split the read in into 2 as there was not enough memory to read all files at once.

```{r read selected ProcessedData}

# TestData <- readRDS_plus(Flnm = file.path("../ProcessedData/LogGrowthFits/20200731_PICO_MCMIX004_RUN17_ProcessDataNestGrowth.Rds"))

LogFitsData1 <-  ProcessedFiles1 %>%
    map_df(~readRDS_plus(Flnm = .)) %>%
    select(-c("Motivation", "doi", "SourceSalinity", "EndDate", "Salinity",  "InocpH","lognormdeltaOD_Gompertz", "lognormOD720_Gompertz", "OD720_logistic", "deltaOD_logistic","OD720trunc_logistic", "deltaODtrunc_logistic", "OD720trunc_exp", "deltaODtrunc_exp",
              "lognormOD720_Gompertz_param",
              "lognormdeltaOD_Gompertz_param",
              "OD720_logistic_param",
              "OD720trunc_exp_param",
              "deltaODtrunc_logistic_param",
              "OD720trunc_logistic_param",
              "deltaOD_logistic_param",
              "deltaODtrunc_exp_param"
              ))

LogFitsData2 <-  ProcessedFiles2 %>%
    map_df(~readRDS_plus(Flnm = .)) %>%
    select(-c("Motivation", "doi", "SourceSalinity", "EndDate", "Salinity",  "InocpH","lognormdeltaOD_Gompertz", "lognormOD720_Gompertz", "OD720_logistic", "deltaOD_logistic","OD720trunc_logistic", "deltaODtrunc_logistic", "OD720trunc_exp", "deltaODtrunc_exp",
              "lognormOD720_Gompertz_param",
              "lognormdeltaOD_Gompertz_param",
              "OD720_logistic_param",
              "OD720trunc_exp_param",
              "deltaODtrunc_logistic_param",
              "OD720trunc_logistic_param",
              "deltaOD_logistic_param",
              "deltaODtrunc_exp_param"
              ))

glimpse(LogFitsData1)
glimpse(LogFitsData2)

LogFitsData <- rbind(LogFitsData1, LogFitsData2)

remove(LogFitsData1)
remove(LogFitsData2)

```

#Unnest data
# assign growth rate to zero if model returns mu < 0 or if growth amplitude flag = 0

```{r unnest fits}

# OD720 gompertz fits
# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007.Defined at line 75 
lognormOD720_unnest <- LogFitsData %>%
   select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720, GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, lognormOD720_Gompertz_tidied, lognormOD720_Gompertz_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
          ) %>%
  unnest(cols = c(lognormOD720_Gompertz_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  lognormOD720_Gompertz_tidied_term, values_from = c(lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error, lognormOD720_Gompertz_tidied_statistic, lognormOD720_Gompertz_tidied_p.value), names_sep = "_") %>%
  rename(OD720_Gmax = lognormOD720_Gompertz_tidied_estimate_Gmax,
         OD720_Gmax_se = lognormOD720_Gompertz_tidied_std.error_Gmax,
         OD720_Gmu_raw = lognormOD720_Gompertz_tidied_estimate_Gmu,
         OD720_Gmu_se = lognormOD720_Gompertz_tidied_std.error_Gmu,
         OD720_GLag = lognormOD720_Gompertz_tidied_estimate_GLag,             
         OD720_GLag_se = lognormOD720_Gompertz_tidied_std.error_GLag)  %>%
   mutate(OD720_Gmu_corr = if_else(!is.na(OD720_Gmu_raw), OD720_Gmu_raw, 0),
          OD720_Gmu_se = if_else(!is.na(OD720_Gmu_se), OD720_Gmu_se, 0),
          OD720_GLag = if_else(!is.na(OD720_GLag), OD720_GLag, 0),
          OD720_GLag_se = if_else(!is.na(OD720_GLag_se), OD720_GLag_se, 0),
          OD720_Gmax = if_else(!is.na(OD720_Gmax), OD720_Gmax, 0),
          OD720_Gmax_se = if_else(!is.na(OD720_Gmax_se), OD720_Gmax_se, 0),
          GrowthAmpOD720Flag = if_else(GrowthAmpOD720 >= OD720GrowthAmpFlagValue, 1, 0),
          GrowthAmpOD720Flag_14days = if_else(GrowthAmpOD720_14days >= OD720GrowthAmpFlagValue, 1, 0),
          OD720_Gmu_corr = if_else(GrowthAmpOD720Flag_14days == 1 & OD720_Gmu_corr >= 0, OD720_Gmu_corr, 0),
          # OD720_GseGrowthFlag = case_when(OD720_Gmu_corr > 0 & OD720_Gmu_corr * GrowthFlagError > OD720_Gmu_se ~ 1,
          #                                   OD720_Gmu_corr > 0 & OD720_Gmu_corr * GrowthFlagError < OD720_Gmu_se ~ 0,
          #                                   OD720_Gmu_corr == 0 ~ 1),

           OD720_GseGrowthFlag = if_else(OD720_Gmu_se < OD720_Gmu_corr * GrowthFlagError, 1, 0),
   )

# deltaOD gompertz fits
# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007.Defined at line 75 
lognormdeltaOD_unnest <- LogFitsData %>% 
select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720, GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, lognormdeltaOD_Gompertz_tidied, lognormdeltaOD_Gompertz_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
       ) %>%
unnest(cols = c(lognormdeltaOD_Gompertz_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  lognormdeltaOD_Gompertz_tidied_term, values_from = c(lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error, lognormdeltaOD_Gompertz_tidied_statistic, lognormdeltaOD_Gompertz_tidied_p.value), names_sep = "_")  %>%
  rename(deltaOD_Gmax = lognormdeltaOD_Gompertz_tidied_estimate_Gmax,
         deltaOD_Gmax_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmax,
         deltaOD_Gmu_raw = lognormdeltaOD_Gompertz_tidied_estimate_Gmu,
         deltaOD_Gmu_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmu,
         deltaOD_GLag = lognormdeltaOD_Gompertz_tidied_estimate_GLag,
         deltaOD_GLag_se = lognormdeltaOD_Gompertz_tidied_std.error_GLag) %>%
   mutate(deltaOD_Gmu_corr = if_else(!is.na(deltaOD_Gmu_raw), deltaOD_Gmu_raw, 0),
          deltaOD_Gmu_se = if_else(!is.na(deltaOD_Gmu_se), deltaOD_Gmu_se, 0),
          deltaOD_GLag = if_else(!is.na(deltaOD_GLag), deltaOD_GLag, 0),
          deltaOD_GLag_se = if_else(!is.na(deltaOD_GLag_se), deltaOD_GLag_se, 0),
          deltaOD_Gmax = if_else(!is.na(deltaOD_Gmax), deltaOD_Gmax, 0),
          deltaOD_Gmax_se = if_else(!is.na(deltaOD_Gmax_se), deltaOD_Gmax_se, 0),
          GrowthAmpdeltaODFlag = if_else(GrowthAmpdeltaOD >= deltaODGrowthAmpFlagValue , 1, 0),
          GrowthAmpdeltaODFlag_14days = if_else(GrowthAmpdeltaOD_14days >= deltaODGrowthAmpFlagValue, 1, 0),
          deltaOD_Gmu_corr = if_else(GrowthAmpdeltaODFlag_14days == 1 & deltaOD_Gmu_corr >= 0, deltaOD_Gmu_corr, 0),
          # deltaOD_GseGrowthFlag = case_when(deltaOD_Gmu_corr > 0 & deltaOD_Gmu_corr * GrowthFlagError > deltaOD_Gmu_se ~ 1,
          #                                   deltaOD_Gmu_corr > 0 & deltaOD_Gmu_corr * GrowthFlagError < deltaOD_Gmu_se ~ 0,
          #                                   deltaOD_Gmu_corr == 0 ~ 1),

         deltaOD_GseGrowthFlag = if_else(deltaOD_Gmu_se < deltaOD_Gmu_corr * GrowthFlagError, 1, 0),
          )

# OD720 logistic fits
# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007.Defined at line 75 
OD720_unnest <- LogFitsData %>%
  select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720, GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, OD720_logistic_tidied, OD720_logistic_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
         ) %>%
  unnest(cols = c(OD720_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error, OD720_logistic_tidied_statistic, OD720_logistic_tidied_p.value), names_sep = "_") %>%
  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
         OD720_Lmu_raw = OD720_logistic_tidied_estimate_Lmu,
         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,             
         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept)  %>%
   mutate(OD720_Lmu_corr = if_else(!is.na(OD720_Lmu_raw), OD720_Lmu_raw, 0),
          OD720_Lmu_se = if_else(!is.na(OD720_Lmu_se), OD720_Lmu_se, 0),
          OD720_Lintercept = if_else(!is.na(OD720_Lintercept), OD720_Lintercept, 0),
          OD720_Lintercept_se = if_else(!is.na(OD720_Lintercept_se), OD720_Lintercept_se, 0),
          OD720_Lmax = if_else(!is.na(OD720_Lmax), OD720_Lmax, 0),
          OD720_Lmax_se = if_else(!is.na(OD720_Lmax_se), OD720_Lmax_se, 0),
          GrowthAmpOD720Flag = if_else(GrowthAmpOD720 >= OD720GrowthAmpFlagValue, 1, 0),
          GrowthAmpOD720Flag_14days = if_else(GrowthAmpOD720_14days >= OD720GrowthAmpFlagValue, 1, 0),
          OD720_Lmu_corr = if_else(GrowthAmpOD720Flag_14days == 1 & OD720_Lmu_corr >= 0 , OD720_Lmu_corr, 0),
          # OD720_LseGrowthFlag = case_when(OD720_Lmu_corr > 0 & OD720_Lmu_corr * GrowthFlagError > OD720_Lmu_se ~ 1,
          #                                   OD720_Lmu_corr > 0 & OD720_Lmu_corr * GrowthFlagError < OD720_Lmu_se ~ 0,
          #                                   OD720_Lmu_corr == 0 ~ 1),
          OD720_LseGrowthFlag = if_else(OD720_Lmu_se < OD720_Lmu_corr * GrowthFlagError, 1, 0),
          OD720_TimeHalfPmax_h = (log(2-(OD720_Lintercept/(OD720_Lmax - OD720_Lintercept))))/OD720_Lmu_corr,
          OD720_TimeHalfPmax_h = if_else(!is.infinite(OD720_TimeHalfPmax_h), OD720_TimeHalfPmax_h, 0),
          OD720_TimeHalfPmax_h = if_else(!is.nan(OD720_TimeHalfPmax_h), OD720_TimeHalfPmax_h, 0)
          )

# deltaOD logistic fits
# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007 and less than 14 days.Defined at line 75 
deltaOD_unnest <- LogFitsData %>%
   select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720,  GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, deltaOD_logistic_tidied, deltaOD_logistic_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
          ) %>%
unnest(cols = c(deltaOD_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error, deltaOD_logistic_tidied_statistic, deltaOD_logistic_tidied_p.value), names_sep = "_")  %>%
  rename(deltaOD_Lmax = deltaOD_logistic_tidied_estimate_Lmax,
         deltaOD_Lmax_se = deltaOD_logistic_tidied_std.error_Lmax,
         deltaOD_Lmu_raw = deltaOD_logistic_tidied_estimate_Lmu,
         deltaOD_Lmu_se = deltaOD_logistic_tidied_std.error_Lmu,
         deltaOD_Lintercept = deltaOD_logistic_tidied_estimate_Lintercept,
         deltaOD_Lintercept_se = deltaOD_logistic_tidied_std.error_Lintercept) %>%
   mutate(deltaOD_Lmu_corr = if_else(!is.na(deltaOD_Lmu_raw), deltaOD_Lmu_raw, 0),
          deltaOD_Lmu_se = if_else(!is.na(deltaOD_Lmu_se), deltaOD_Lmu_se, 0),
          deltaOD_Lintercept = if_else(!is.na(deltaOD_Lintercept), deltaOD_Lintercept, 0),
          deltaOD_Lintercept_se = if_else(!is.na(deltaOD_Lintercept_se), deltaOD_Lintercept_se, 0),
          deltaOD_Lmax = if_else(!is.na(deltaOD_Lmax), deltaOD_Lmax, 0),
          deltaOD_Lmax_se = if_else(!is.na(deltaOD_Lmax_se), deltaOD_Lmax_se, 0),
          GrowthAmpdeltaODFlag = if_else(GrowthAmpdeltaOD >= deltaODGrowthAmpFlagValue , 1, 0),
          GrowthAmpdeltaODFlag_14days = if_else(GrowthAmpdeltaOD_14days >= deltaODGrowthAmpFlagValue, 1, 0),
          deltaOD_Lmu_corr = if_else(GrowthAmpdeltaODFlag_14days == 1 & deltaOD_Lmu_corr >= 0, deltaOD_Lmu_corr, 0),
          # deltaOD_LseGrowthFlag = case_when(deltaOD_Lmu_corr > 0 & deltaOD_Lmu_corr * GrowthFlagError > deltaOD_Lmu_se ~ 1,
                                            # deltaOD_Lmu_corr > 0 & deltaOD_Lmu_corr * GrowthFlagError < deltaOD_Lmu_se ~ 0,
                                            # deltaOD_Lmu_corr == 0 ~ 1),
         deltaOD_LseGrowthFlag = if_else(deltaOD_Lmu_se < deltaOD_Lmu_corr * GrowthFlagError, 1, 0),
          deltaOD_TimeHalfPmax_h = (log(2-(deltaOD_Lintercept/(deltaOD_Lmax - deltaOD_Lintercept))))/deltaOD_Lmu_corr,
          deltaOD_TimeHalfPmax_h = if_else(!is.infinite(deltaOD_TimeHalfPmax_h), deltaOD_TimeHalfPmax_h, 0),
          deltaOD_TimeHalfPmax_h = if_else(!is.nan(deltaOD_TimeHalfPmax_h), deltaOD_TimeHalfPmax_h, 0)
          )

# OD720 truncated logistic fits
# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007.Defined at line 75 
OD720truncLog_unnest <- LogFitsData %>%
   select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720, GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, OD720trunc_logistic_tidied, OD720trunc_logistic_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
          ) %>%
  unnest(cols = c(OD720trunc_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  OD720trunc_logistic_tidied_term, values_from = c(OD720trunc_logistic_tidied_estimate, OD720trunc_logistic_tidied_std.error, OD720trunc_logistic_tidied_statistic, OD720trunc_logistic_tidied_p.value), names_sep = "_") %>%
  rename(OD720trunc_Lmax = OD720trunc_logistic_tidied_estimate_Lmax,
         OD720trunc_Lmax_se = OD720trunc_logistic_tidied_std.error_Lmax,
         OD720trunc_Lmu_raw = OD720trunc_logistic_tidied_estimate_Lmu,
         OD720trunc_Lmu_se = OD720trunc_logistic_tidied_std.error_Lmu,
         OD720trunc_Lintercept = OD720trunc_logistic_tidied_estimate_Lintercept,             
         OD720trunc_Lintercept_se = OD720trunc_logistic_tidied_std.error_Lintercept)  %>%
   mutate(OD720trunc_Lmu_corr = if_else(!is.na(OD720trunc_Lmu_raw), OD720trunc_Lmu_raw, 0),
          OD720trunc_Lmu_se = if_else(!is.na(OD720trunc_Lmu_se), OD720trunc_Lmu_se, 0),
          OD720trunc_Lintercept = if_else(!is.na(OD720trunc_Lintercept), OD720trunc_Lintercept, 0),
          OD720trunc_Lintercept_se = if_else(!is.na(OD720trunc_Lintercept_se), OD720trunc_Lintercept_se, 0),
          OD720trunc_Lmax = if_else(!is.na(OD720trunc_Lmax), OD720trunc_Lmax, 0),
          OD720trunc_Lmax_se = if_else(!is.na(OD720trunc_Lmax_se), OD720trunc_Lmax_se, 0),
          GrowthAmpOD720Flag = if_else(GrowthAmpOD720 >= OD720GrowthAmpFlagValue, 1, 0),
          GrowthAmpOD720Flag_14days = if_else(GrowthAmpOD720_14days >= OD720GrowthAmpFlagValue, 1, 0),
          OD720trunc_Lmu_corr = if_else(GrowthAmpOD720Flag_14days == 1 & OD720trunc_Lmu_corr >= 0 , OD720trunc_Lmu_corr, 0),
          # OD720trunc_LseGrowthFlag = case_when(OD720trunc_Lmu_corr > 0 & OD720trunc_Lmu_corr * GrowthFlagError > OD720trunc_Lmu_se ~ 1,
          #                                   OD720trunc_Lmu_corr > 0 & OD720trunc_Lmu_corr * GrowthFlagError < OD720trunc_Lmu_se ~ 0,
          #                                   OD720trunc_Lmu_corr == 0 ~ 1),

           OD720trunc_LseGrowthFlag = if_else(OD720trunc_Lmu_se < OD720trunc_Lmu_corr * GrowthFlagError, 1, 0),
          OD720trunc_TimeHalfPmax_h = (log(2-(OD720trunc_Lintercept/(OD720trunc_Lmax - OD720trunc_Lintercept))))/OD720trunc_Lmu_corr,
          OD720trunc_TimeHalfPmax_h = if_else(!is.infinite(OD720trunc_TimeHalfPmax_h), OD720trunc_TimeHalfPmax_h, 0),
          OD720trunc_TimeHalfPmax_h = if_else(!is.nan(OD720trunc_TimeHalfPmax_h), OD720trunc_TimeHalfPmax_h, 0)
          )

# deltaOD truncated logistic fits
# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007.Defined at line 75 
deltaODtruncLog_unnest <- LogFitsData %>%
   select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720, GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, deltaODtrunc_logistic_tidied, deltaODtrunc_logistic_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
          ) %>%
unnest(cols = c(deltaODtrunc_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  deltaODtrunc_logistic_tidied_term, values_from = c(deltaODtrunc_logistic_tidied_estimate, deltaODtrunc_logistic_tidied_std.error, deltaODtrunc_logistic_tidied_statistic, deltaODtrunc_logistic_tidied_p.value), names_sep = "_")  %>%
  rename(deltaODtrunc_Lmax = deltaODtrunc_logistic_tidied_estimate_Lmax,
         deltaODtrunc_Lmax_se = deltaODtrunc_logistic_tidied_std.error_Lmax,
         deltaODtrunc_Lmu_raw = deltaODtrunc_logistic_tidied_estimate_Lmu,
         deltaODtrunc_Lmu_se = deltaODtrunc_logistic_tidied_std.error_Lmu,
         deltaODtrunc_Lintercept = deltaODtrunc_logistic_tidied_estimate_Lintercept,
         deltaODtrunc_Lintercept_se = deltaODtrunc_logistic_tidied_std.error_Lintercept) %>%
   mutate(deltaODtrunc_Lmu_corr = if_else(!is.na(deltaODtrunc_Lmu_raw), deltaODtrunc_Lmu_raw, 0),
          deltaODtrunc_Lmu_se = if_else(!is.na(deltaODtrunc_Lmu_se), deltaODtrunc_Lmu_se, 0),
          deltaODtrunc_Lintercept = if_else(!is.na(deltaODtrunc_Lintercept), deltaODtrunc_Lintercept, 0),
          deltaODtrunc_Lintercept_se = if_else(!is.na(deltaODtrunc_Lintercept_se), deltaODtrunc_Lintercept_se, 0),
          deltaODtrunc_Lmax = if_else(!is.na(deltaODtrunc_Lmax), deltaODtrunc_Lmax, 0),
          deltaODtrunc_Lmax_se = if_else(!is.na(deltaODtrunc_Lmax_se), deltaODtrunc_Lmax_se, 0),
          GrowthAmpdeltaODFlag = if_else(GrowthAmpdeltaOD >= deltaODGrowthAmpFlagValue , 1, 0),
          GrowthAmpdeltaODFlag_14days = if_else(GrowthAmpdeltaOD_14days >= deltaODGrowthAmpFlagValue, 1, 0),
          deltaODtrunc_Lmu_corr = if_else(GrowthAmpdeltaODFlag_14days == 1 & deltaODtrunc_Lmu_corr >= 0, deltaODtrunc_Lmu_corr, 0),
          # deltaODtrunc_LseGrowthFlag = case_when(deltaODtrunc_Lmu_corr > 0 & deltaODtrunc_Lmu_corr * GrowthFlagError > deltaODtrunc_Lmu_se ~ 1,
          #                                   deltaODtrunc_Lmu_corr > 0 & deltaODtrunc_Lmu_corr * GrowthFlagError < deltaODtrunc_Lmu_se ~ 0,
          #                                   deltaODtrunc_Lmu_corr == 0 ~ 1),

          deltaODtrunc_LseGrowthFlag = if_else(deltaODtrunc_Lmu_se < deltaODtrunc_Lmu_corr * GrowthFlagError, 1, 0),
          deltaODtrunc_TimeHalfPmax_h = (log(2-(deltaODtrunc_Lintercept/(deltaODtrunc_Lmax - deltaODtrunc_Lintercept))))/deltaODtrunc_Lmu_corr,
          deltaODtrunc_TimeHalfPmax_h = if_else(!is.infinite(deltaODtrunc_TimeHalfPmax_h), deltaODtrunc_TimeHalfPmax_h, 0),
          deltaODtrunc_TimeHalfPmax_h = if_else(!is.nan(deltaODtrunc_TimeHalfPmax_h), deltaODtrunc_TimeHalfPmax_h, 0)
          )

# OD720 truncated exponential fits
# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007.Defined at line 75 
OD720truncExp_unnest <- LogFitsData %>%
   select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720, GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, OD720trunc_exp_tidied, OD720trunc_exp_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
          ) %>%
  unnest(cols = c(OD720trunc_exp_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  OD720trunc_exp_tidied_term, values_from = c(OD720trunc_exp_tidied_estimate, OD720trunc_exp_tidied_std.error, OD720trunc_exp_tidied_statistic, OD720trunc_exp_tidied_p.value), names_sep = "_") %>%
  rename(OD720trunc_Emu_raw = OD720trunc_exp_tidied_estimate_Emu,
         OD720trunc_Emu_se = OD720trunc_exp_tidied_std.error_Emu,
         OD720trunc_Eintercept = OD720trunc_exp_tidied_estimate_Eintercept,             
         OD720trunc_Eintercept_se = OD720trunc_exp_tidied_std.error_Eintercept)  %>%
   mutate(OD720trunc_Emu_corr = if_else(!is.na(OD720trunc_Emu_raw), OD720trunc_Emu_raw, 0),
          OD720trunc_Emu_se = if_else(!is.na(OD720trunc_Emu_se), OD720trunc_Emu_se, 0),
          OD720trunc_Eintercept = if_else(!is.na(OD720trunc_Eintercept), OD720trunc_Eintercept, 0),
          OD720trunc_Eintercept_se = if_else(!is.na(OD720trunc_Eintercept_se), OD720trunc_Eintercept_se, 0),
          GrowthAmpOD720Flag = if_else(GrowthAmpOD720 >= OD720GrowthAmpFlagValue, 1, 0),
          GrowthAmpOD720Flag_14days = if_else(GrowthAmpOD720_14days >= OD720GrowthAmpFlagValue, 1, 0),
          OD720trunc_Emu_corr = if_else(GrowthAmpOD720Flag_14days == 1 & OD720trunc_Emu_corr >= 0 , OD720trunc_Emu_corr, 0),
          # OD720trunc_EseGrowthFlag = case_when(OD720trunc_Emu_corr > 0 & OD720trunc_Emu_corr * GrowthFlagError > OD720trunc_Emu_se ~ 1,
          #                                   OD720trunc_Emu_corr > 0 & OD720trunc_Emu_corr * GrowthFlagError < OD720trunc_Emu_se ~ 0,
          #                                   OD720trunc_Emu_corr == 0 ~ 1)
         OD720trunc_EseGrowthFlag = if_else(OD720trunc_Emu_se < OD720trunc_Emu_corr * GrowthFlagError, 1, 0),
          )

# deltaOD truncated exponential fits
# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007.Defined at line 75 
deltaODtruncExp_unnest <- LogFitsData %>%
   select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720, GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, deltaODtrunc_exp_tidied, deltaODtrunc_exp_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
          ) %>%
unnest(cols = c(deltaODtrunc_exp_tidied), names_sep = "_", keep_empty = TRUE) %>%
  pivot_wider(names_from =  deltaODtrunc_exp_tidied_term, values_from = c(deltaODtrunc_exp_tidied_estimate, deltaODtrunc_exp_tidied_std.error, deltaODtrunc_exp_tidied_statistic, deltaODtrunc_exp_tidied_p.value), names_sep = "_")  %>%
  rename(deltaODtrunc_Emu_raw = deltaODtrunc_exp_tidied_estimate_Emu,
         deltaODtrunc_Emu_se = deltaODtrunc_exp_tidied_std.error_Emu,
         deltaODtrunc_Eintercept = deltaODtrunc_exp_tidied_estimate_Eintercept,
         deltaODtrunc_Eintercept_se = deltaODtrunc_exp_tidied_std.error_Eintercept) %>%
   mutate(deltaODtrunc_Emu_corr = if_else(!is.na(deltaODtrunc_Emu_raw), deltaODtrunc_Emu_raw, 0),
          deltaODtrunc_Emu_se = if_else(!is.na(deltaODtrunc_Emu_se), deltaODtrunc_Emu_se, 0),
          deltaODtrunc_Eintercept = if_else(!is.na(deltaODtrunc_Eintercept), deltaODtrunc_Eintercept, 0),
          deltaODtrunc_Eintercept_se = if_else(!is.na(deltaODtrunc_Eintercept_se), deltaODtrunc_Eintercept_se, 0),
          GrowthAmpdeltaODFlag = if_else(GrowthAmpdeltaOD >= deltaODGrowthAmpFlagValue , 1, 0),
          GrowthAmpdeltaODFlag_14days = if_else(GrowthAmpdeltaOD_14days >= deltaODGrowthAmpFlagValue, 1, 0),
          deltaODtrunc_Emu_corr = if_else(GrowthAmpdeltaODFlag_14days == 1 & deltaODtrunc_Emu_corr >= 0, deltaODtrunc_Emu_corr, 0),
          # deltaODtrunc_EseGrowthFlag = case_when(deltaODtrunc_Emu_corr > 0 & deltaODtrunc_Emu_corr * GrowthFlagError > deltaODtrunc_Emu_se ~ 1,
          #                                   deltaODtrunc_Emu_corr > 0 & deltaODtrunc_Emu_corr * GrowthFlagError < deltaODtrunc_Emu_se ~ 0,
          #                                   deltaODtrunc_Emu_corr == 0 ~ 1),
           deltaODtrunc_EseGrowthFlag = if_else(deltaODtrunc_Emu_se < deltaODtrunc_Emu_corr * GrowthFlagError, 1, 0),
          )

glimpse(lognormdeltaOD_unnest)

```

```{r combine unnested fits for PICO Shiny App}

# OD720 gompertz fits
lognormOD720_unnest <- lognormOD720_unnest %>%
select(-c(lognormOD720_Gompertz_tidied_estimate_NA,
            lognormOD720_Gompertz_tidied_p.value_NA,
            lognormOD720_Gompertz_tidied_statistic_NA,
            lognormOD720_Gompertz_tidied_std.error_NA,
            lognormOD720_Gompertz_tidied_statistic_GLag,
            lognormOD720_Gompertz_tidied_statistic_Gmax,
            lognormOD720_Gompertz_tidied_statistic_Gmu,
            lognormOD720_Gompertz_tidied_p.value_GLag,
            lognormOD720_Gompertz_tidied_p.value_Gmax,
            lognormOD720_Gompertz_tidied_p.value_Gmu)
       )

# deltaOD gompertz fits
lognormdeltaOD_unnest <- lognormdeltaOD_unnest %>%
  select(-c(lognormdeltaOD_Gompertz_tidied_estimate_NA,
            lognormdeltaOD_Gompertz_tidied_p.value_NA,
            lognormdeltaOD_Gompertz_tidied_statistic_NA,
            lognormdeltaOD_Gompertz_tidied_std.error_NA,
            lognormdeltaOD_Gompertz_tidied_statistic_GLag,
            lognormdeltaOD_Gompertz_tidied_statistic_Gmax,
            lognormdeltaOD_Gompertz_tidied_statistic_Gmu,
            lognormdeltaOD_Gompertz_tidied_p.value_GLag,
            lognormdeltaOD_Gompertz_tidied_p.value_Gmax,
            lognormdeltaOD_Gompertz_tidied_p.value_Gmu)
         )

# OD720 logistic fits
OD720_unnest <- OD720_unnest %>%
select(-c(OD720_logistic_tidied_estimate_NA,
          OD720_logistic_tidied_p.value_NA,
          OD720_logistic_tidied_statistic_NA,
          OD720_logistic_tidied_std.error_NA,
          OD720_logistic_tidied_statistic_Lintercept,
          OD720_logistic_tidied_statistic_Lmax,
          OD720_logistic_tidied_statistic_Lmu,
          OD720_logistic_tidied_p.value_Lintercept,
          OD720_logistic_tidied_p.value_Lmax,
          OD720_logistic_tidied_p.value_Lmu)
       )

# deltaOD logistic fits
deltaOD_unnest <- deltaOD_unnest %>%
  select(-c(deltaOD_logistic_tidied_estimate_NA,
            deltaOD_logistic_tidied_p.value_NA,
            deltaOD_logistic_tidied_statistic_NA,
            deltaOD_logistic_tidied_std.error_NA,
            deltaOD_logistic_tidied_statistic_Lintercept,
            deltaOD_logistic_tidied_statistic_Lmax,
            deltaOD_logistic_tidied_statistic_Lmu,
            deltaOD_logistic_tidied_p.value_Lintercept,
            deltaOD_logistic_tidied_p.value_Lmax,
            deltaOD_logistic_tidied_p.value_Lmu)
         )

# OD720 truncated logistic fits
OD720truncLog_unnest <- OD720truncLog_unnest %>%
select(-c(OD720trunc_logistic_tidied_estimate_NA,
           OD720trunc_logistic_tidied_p.value_NA,
           OD720trunc_logistic_tidied_statistic_NA,
           OD720trunc_logistic_tidied_std.error_NA,
            OD720trunc_logistic_tidied_statistic_Lintercept,
            OD720trunc_logistic_tidied_statistic_Lmax,
            OD720trunc_logistic_tidied_statistic_Lmu,
            OD720trunc_logistic_tidied_p.value_Lintercept,
            OD720trunc_logistic_tidied_p.value_Lmax,
            OD720trunc_logistic_tidied_p.value_Lmu)
       )

# deltaOD truncated logistic fits
deltaODtruncLog_unnest <- deltaODtruncLog_unnest %>%
  select(-c(deltaODtrunc_logistic_tidied_estimate_NA,
            deltaODtrunc_logistic_tidied_p.value_NA,
            deltaODtrunc_logistic_tidied_statistic_NA,
            deltaODtrunc_logistic_tidied_std.error_NA,
            deltaODtrunc_logistic_tidied_statistic_Lintercept,
            deltaODtrunc_logistic_tidied_statistic_Lmax,
            deltaODtrunc_logistic_tidied_statistic_Lmu,
            deltaODtrunc_logistic_tidied_p.value_Lintercept,
            deltaODtrunc_logistic_tidied_p.value_Lmax,
            deltaODtrunc_logistic_tidied_p.value_Lmu)
         )

# OD720 truncated exponential fits
OD720truncExp_unnest <- OD720truncExp_unnest %>%
select(-c(OD720trunc_exp_tidied_estimate_NA,
           OD720trunc_exp_tidied_p.value_NA,
           OD720trunc_exp_tidied_statistic_NA,
           OD720trunc_exp_tidied_std.error_NA,
            OD720trunc_exp_tidied_statistic_Eintercept,
            OD720trunc_exp_tidied_statistic_Emu,
            OD720trunc_exp_tidied_p.value_Eintercept,
            OD720trunc_exp_tidied_p.value_Emu)
       )

# deltaOD truncated exponential fits
deltaODtruncExp_unnest <- deltaODtruncExp_unnest %>%
  select(-c(deltaODtrunc_exp_tidied_estimate_NA,
            deltaODtrunc_exp_tidied_p.value_NA,
            deltaODtrunc_exp_tidied_statistic_NA,
            deltaODtrunc_exp_tidied_std.error_NA,
            deltaODtrunc_exp_tidied_statistic_Eintercept,
            deltaODtrunc_exp_tidied_statistic_Emu,
            deltaODtrunc_exp_tidied_p.value_Eintercept,
            deltaODtrunc_exp_tidied_p.value_Emu)
         )

glimpse(deltaOD_unnest)

# Join Full Growth Rate Data
UnnestedGompertzData <- left_join(x = lognormOD720_unnest, y = lognormdeltaOD_unnest)

UnnestedLogData <- left_join(x = OD720_unnest, y = deltaOD_unnest)

UnnestedFullData <- left_join(x = UnnestedLogData, y = UnnestedGompertzData)

glimpse(UnnestedFullData)

# Join Truncated Growth Rate Data
UnnestedTruncLogData <- left_join(x = OD720truncLog_unnest, y =  deltaODtruncLog_unnest)

UnnestedTruncExpData <- left_join(x = OD720truncExp_unnest, y =  deltaODtruncExp_unnest)

UnnestedTruncData <- left_join(x = UnnestedTruncLogData, y = UnnestedTruncExpData)

#combine Full and Truncated unnested data
NestedFitsData <- left_join(x = UnnestedFullData, y = UnnestedTruncData)

glimpse(NestedFitsData)

#remove redundant objects
remove(lognormOD720_unnest,
       lognormdeltaOD_unnest,
       OD720_unnest,
       deltaOD_unnest,
       UnnestedGompertzData,
       UnnestedLogData,
       OD720truncLog_unnest,
       deltaODtruncLog_unnest,
       OD720truncExp_unnest,
       deltaODtruncExp_unnest,
       UnnestedTruncLogData,
       UnnestedTruncExpData,
       UnnestedTruncData,
       UnnestedFullData
       )

```

<!-- Chunk to convert categorize oxygen levels based on input in metacatalog.  Have to do this here as this column was added after many runs were already processed and the merge with metacatalog already occured.  Run numbers >= 36 and <= 91 and 0% oxygen are labelled 'Low', runs <= 35  and 0% oxygen are labelled 'Intermediate'.  All runs >= 92 are from the metacatelog. All runs with 21% oxygen are labelled 'High'.  Assign [O2] to O2_uM based on category -->

```{r}
NestedFitsData <- NestedFitsData %>% 
  mutate(O2_Category = case_when(Run <= 35 & O2 == 0 ~ "Intermediate",
                                 Run >= 36 & Run <= 91 & O2 == 0 ~ "Low",
                                 O2 == 21 ~ "High",
                                 Run >= 92 ~ O2_Category),
         O2_uM = case_when(O2_Category == "Low" ~ 2.5,
                            O2_Category == "Intermediate" ~ 25,
                            O2_Category == "High" ~ 250))

```

<!-- Chunk to calculate the rate per hour of actinic light rise to peak. -->
```{r}
AllNestedFitsData <- NestedFitsData %>% 
  mutate(RateActinic_h = case_when(LightShape == "Sine"  ~ Par_ue/(Photoperiod/2)))

glimpse(AllNestedFitsData)

```

```{r remove trunc and gompertz from nested DF}

# remove gompertz and truncated growth data
NestedFitsData <- NestedFitsData %>% 
  select(-contains(c("trunc", "Gompertz", "Gomp", "OD720_G", "deltaOD_G")))

# need the deltaOD trunc growth rate for future comparisons
onlydeltaODtrunc<- AllNestedFitsData %>% 
  select((c("ID", "deltaODtrunc_Lmu_corr")))

# add deltaOD truncated growth rates to DF
NestedFitsData <- full_join(NestedFitsData, onlydeltaODtrunc)

glimpse(NestedFitsData)

remove(onlydeltaODtrunc)

```

```{r, pivot Nested data longer for GAM}

# OD720 pivot longer Gmax, Gmu, Glag, Lmu, Lmax and Lintercept estimates
Pivot_Longer_OD720_est <- AllNestedFitsData %>%
  select(c(Filename, Tube, ID, Run, PrimaryOperator, Strain, Par_ue,RateActinic_h, Photoperiod, SetActinic_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormOD720_GompLag ,GrowthAmpOD720, GrowthAmpOD720Flag, GrowthAmpOD720_14days, GrowthAmpOD720Flag_14days, DoubleOD720Flag_14days, OD720_GseGrowthFlag, OD720_LseGrowthFlag, OD720trunc_LseGrowthFlag, OD720_Gmu_corr, OD720_Gmax, OD720_GLag, OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720trunc_Lmu_corr, OD720trunc_Lmax, OD720trunc_Lintercept
            )) %>%
   pivot_longer(c(OD720_Gmu_corr, OD720_Gmax, OD720_GLag, OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720trunc_Lmu_corr, OD720trunc_Lmax, OD720trunc_Lintercept), names_to = c("Wavelength", "term"), values_to = c("estimate"), names_sep = '\\_')

# OD720 pivot longer Gmax, Gmu, Glag , Lmu, Lmax and Lintercept standard error
Pivot_Longer_OD720_se <- AllNestedFitsData %>%
  select(c(Filename, Tube, ID, Run, PrimaryOperator, Strain, Par_ue, RateActinic_h, Photoperiod, SetActinic_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormOD720_GompLag ,GrowthAmpOD720, GrowthAmpOD720Flag, GrowthAmpOD720_14days, GrowthAmpOD720Flag_14days, DoubleOD720Flag_14days, OD720_GseGrowthFlag, OD720_LseGrowthFlag, OD720trunc_LseGrowthFlag,  OD720_Gmu_se, OD720_Gmax_se, OD720_GLag_se, OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se,OD720trunc_Lmu_se, OD720trunc_Lmax_se, OD720trunc_Lintercept_se
            )) %>%
   pivot_longer(c(OD720_Gmu_se, OD720_Gmax_se, OD720_GLag_se, OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se, OD720trunc_Lmu_se, OD720trunc_Lmax_se, OD720trunc_Lintercept_se), names_to = c("Wavelength", "term"), values_to = c("se"), names_sep = '\\_')

# Join OD720 estimate and se DF 
Longer_OD720_Joined <- full_join(Pivot_Longer_OD720_est, Pivot_Longer_OD720_se)

remove(Pivot_Longer_OD720_est, Pivot_Longer_OD720_se)

# rename common columns for full join
Longer_OD720_Joined <- Longer_OD720_Joined %>%
  rename(Is_GLagNeg = 'IsOD720_GLagNeg',
         lognorm_TimetoMax = 'lognormOD720_TimetoMax',
         lognorm_GompLag = 'lognormOD720_GompLag',
         GrowthAmp = 'GrowthAmpOD720',
         GrowthAmpFlag = 'GrowthAmpOD720Flag',
         GrowthAmp_14days = 'GrowthAmpOD720_14days',
         GrowthAmp_14daysFlag = 'GrowthAmpOD720Flag_14days',
         Doubled_14daysFlag = 'DoubleOD720Flag_14days',
         Gmu_seFlag = 'OD720_GseGrowthFlag',
         Lmu_seFlag = 'OD720_LseGrowthFlag',
         Lmutrunc_seFlag = 'OD720trunc_LseGrowthFlag'
         )

# deltaOD pivot longer Gmax, Gmu, Glag, Lmu, Lmax and Lintercept estimates
Pivot_Longer_deltaOD_est <- AllNestedFitsData %>%
  select(c(Filename, Tube, ID, Run, PrimaryOperator, Strain, Par_ue, RateActinic_h, Photoperiod, SetActinic_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape, IsdeltaOD_GLagNeg, lognormdeltaOD_TimetoMax, lognormdeltaOD_GompLag ,GrowthAmpdeltaOD, GrowthAmpdeltaODFlag, GrowthAmpdeltaOD_14days, GrowthAmpdeltaODFlag_14days, DoubledeltaODFlag_14days, deltaOD_GseGrowthFlag, deltaOD_LseGrowthFlag, deltaODtrunc_LseGrowthFlag,  deltaOD_Gmu_corr, deltaOD_Gmax, deltaOD_GLag, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept, deltaODtrunc_Lmu_corr, deltaODtrunc_Lmax, deltaODtrunc_Lintercept
            )) %>%
   pivot_longer(c(deltaOD_Gmu_corr, deltaOD_Gmax, deltaOD_GLag, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept, deltaODtrunc_Lmu_corr, deltaODtrunc_Lmax, deltaODtrunc_Lintercept), names_to = c("Wavelength", "term"), values_to = c("estimate"), names_sep = '\\_')

# deltaOD pivot longer Gmax, Gmu, Glag , Lmu, Lmax and Lintercept standard error
Pivot_Longer_deltaOD_se <- AllNestedFitsData %>%
  select(c(Filename, Tube, ID, Run, PrimaryOperator, Strain, Par_ue, RateActinic_h, Photoperiod, SetActinic_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape, IsdeltaOD_GLagNeg, lognormdeltaOD_TimetoMax, lognormdeltaOD_GompLag ,GrowthAmpdeltaOD, GrowthAmpdeltaODFlag, GrowthAmpdeltaOD_14days, GrowthAmpdeltaODFlag_14days, DoubledeltaODFlag_14days, deltaOD_GseGrowthFlag, deltaOD_LseGrowthFlag, deltaODtrunc_LseGrowthFlag, deltaOD_Gmu_se, deltaOD_Gmax_se, deltaOD_GLag_se, deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se, deltaODtrunc_Lmu_se, deltaODtrunc_Lmax_se, deltaODtrunc_Lintercept_se
            )) %>%
   pivot_longer(c(deltaOD_Gmu_se, deltaOD_Gmax_se, deltaOD_GLag_se, deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se, deltaODtrunc_Lmu_se, deltaODtrunc_Lmax_se, deltaODtrunc_Lintercept_se), names_to = c("Wavelength", "term"), values_to = c("se"), names_sep = '\\_')

# Join deltaOD estimate and se DF 
Longer_deltaOD_Joined <- full_join(Pivot_Longer_deltaOD_est, Pivot_Longer_deltaOD_se)

remove(Pivot_Longer_deltaOD_est, Pivot_Longer_deltaOD_se)

# rename common columns for full join
Longer_deltaOD_Joined <- Longer_deltaOD_Joined %>%
  rename(Is_GLagNeg = 'IsdeltaOD_GLagNeg',
         lognorm_TimetoMax = 'lognormdeltaOD_TimetoMax',
         lognorm_GompLag = 'lognormdeltaOD_GompLag',
         GrowthAmp = 'GrowthAmpdeltaOD',
         GrowthAmpFlag = 'GrowthAmpdeltaODFlag',
         GrowthAmp_14days = 'GrowthAmpdeltaOD_14days',
         GrowthAmp_14daysFlag = 'GrowthAmpdeltaODFlag_14days',
         Doubled_14daysFlag = 'DoubledeltaODFlag_14days',
         Gmu_seFlag = 'deltaOD_GseGrowthFlag',
         Lmu_seFlag = 'deltaOD_LseGrowthFlag',
         Lmutrunc_seFlag = 'deltaODtrunc_LseGrowthFlag'
         )

#Join OD720 and deltaOD fits data
LongerFitsData <- rbind(Longer_OD720_Joined, Longer_deltaOD_Joined) %>%
  mutate_if(is.numeric, round, digits = 3)

remove(Longer_OD720_Joined, Longer_deltaOD_Joined)

glimpse(LongerFitsData)

```

Save Long DF for GAM and Nested for further analysis 
```{r save files for GAM and Shiny App}

saveRDS(object = LongerFitsData, file = file.path(DataOut, paste(Project, "MiSa_LongerFitsData.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = TRUE, refhook = NULL)

# write_csv(LongerFitsData, file = file.path(DataOut, paste(Project, "MiSa_LongerFitsData",".csv",sep = "_"),fsep = .Platform$file.sep))

saveRDS(object = NestedFitsData, file = file.path(DataOut, paste(Project, "MiSa_NestedFitsData.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = TRUE, refhook = NULL)

saveRDS(NestedFitsData, file = file.path(ShinyPath, paste(Project, "MiSa_GrowthLogs", ".Rds",sep = "_"),fsep = .Platform$file.sep))

```

```{r LogisticdeltaODPlots, fig.height= 10, fig.width= 10}

SS120deltaODLmuMatrixPlot <- NestedFitsData %>%
   filter(Strain == "SS120") %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.5) +
 geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
   labs(subtitle = "Strain, [Oxygen], Photoperiod, Actinic PAR (nm)", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
 geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
  geom_errorbar(aes(x = Par_ue, ymin = (deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
  #   scale_y_continuous(breaks=seq(-0.03, 0.07, by = 0.01)) +
  # coord_cartesian(ylim = c (-0.03, 0.07)) +
  scale_colour_manual(values = MCMIXColours) +
  ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

SS120deltaODLmuMatrixPlot

 NestedFitsData %>%
   filter(Strain == "SS120",
          deltaOD_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.5) +
 geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
   labs(subtitle = "Strain, [Oxygen],Photoperiod, Actinic PAR (nm) - Outliers filtered by standard error > 20% of growth rate", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
 geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
  geom_errorbar(aes(x = Par_ue, ymin = (deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
  #   scale_y_continuous(breaks=seq(-0.03, 0.07, by = 0.01)) +
  # coord_cartesian(ylim = c (-0.03, 0.07)) +
  scale_colour_manual(values = MCMIXColours) +
  ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

 NestedFitsData %>%
   filter(Strain == "SS120",
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.5) +
 geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
   labs(subtitle = "Strain, [Oxygen],Photoperiod, Actinic PAR (nm) - Of cultures that grew, outliers filtered by standard error > 20% of growth rate.", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
 geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
  geom_errorbar(aes(x = Par_ue, ymin = (deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
  #   scale_y_continuous(breaks=seq(-0.03, 0.07, by = 0.01)) +
  # coord_cartesian(ylim = c (-0.03, 0.07)) +
  scale_colour_manual(values = MCMIXColours) +
  ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

MIT9313deltaODLmuMatrixPlot <- NestedFitsData %>%
   filter(Strain == "MIT9313",
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.4) +
 geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
 labs(subtitle = "Strain, [Oxygen],Photoperiod, Actinic PAR (nm) - Of cultures that grew, outliers filtered by standard error > 20% of growth rate.", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
   geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5,hjust = 0.5, vjust=-0.5) +
  # geom_jitter(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 6) +
  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
  #   scale_y_continuous(breaks=seq(0, 0.07, by = 0.01)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours) +
  ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

MIT9313deltaODLmuMatrixPlot

NestedFitsData %>%
   filter(Strain == "MIT9313",
          deltaOD_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.4) +
 geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
 labs(subtitle = "Strain, [Oxygen], Photoperiod, Actinic PAR (nm) - Outliers filtered by standard error > 20% of growth rate", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
 geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5,hjust = 0.5, vjust=-0.5) +
  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
  #   scale_y_continuous(breaks=seq(0, 0.07, by = 0.01)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours) +
  ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

 MED4deltaODLmuMatrixPlot <- NestedFitsData %>%
   filter(Strain == "MED4",
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.4) +
 geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
   labs(subtitle = "Strain, [Oxygen],Photoperiod, Actinic PAR (nm) - Of cultures that grew, outliers filtered by standard error > 20% of growth rate.", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
 geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5,hjust = 0.5, vjust=-0.5) +
  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
  #   scale_y_continuous(breaks=seq(0, 0.115, by = 0.01)) +
  # coord_cartesian(ylim = c (0, 0.115)) +
  scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

MED4deltaODLmuMatrixPlot

 NestedFitsData %>%
   filter(Strain == "MED4",
          deltaOD_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.4) +
 geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
   labs(subtitle = "Strain, [Oxygen], Photoperiod, Actinic PAR (nm) - Outliers filtered by standard error > 20% of growth rate", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
 geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5,hjust = 0.5, vjust=-0.5) +
  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
  #   scale_y_continuous(breaks=seq(0, 0.115, by = 0.01)) +
  # coord_cartesian(ylim = c (0, 0.115)) +
  scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

deltaOD_LmuSummaryGrowthPlot <- NestedFitsData %>%
   filter(Strain == "MIT9313" |
         Strain == "SS120" |
         Strain == "MED4",
         deltaOD_LseGrowthFlag == 1) %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.5) +
  geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
labs(subtitle = "Strain, [Oxygen], Photoperiod, Actinic PAR (nm)", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
 geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run),alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
 #   scale_y_continuous(breaks=seq(-0.03, 0.07, by = 0.01)) +
  # coord_cartesian(ylim = c (-0.03, 0.07)) +
  scale_colour_manual(values = MCMIXColours) +
  ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

deltaOD_LmuSummaryGrowthPlot

#plotly::ggplotly(deltaOD_LmuSummaryGrowthPlot)

 NestedFitsData %>%
   filter(WL == "WW") %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(O2_uM)), size = 4, alpha = 0.5) +
 geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(O2_uM)), linewidth = 0.1, alpha = 0.4) +
   labs(subtitle = "Actinic PAR (nm), Strain, Photoperiod", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
 geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
  geom_errorbar(aes(x = Par_ue, ymin = (deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
  #   scale_y_continuous(breaks=seq(-0.03, 0.07, by = 0.01)) +
  # coord_cartesian(ylim = c (-0.03, 0.07)) +
  #scale_colour_manual(values = MCMIXColours) +
  ggh4x::facet_nested(cols = vars(WL, Strain), rows = vars(Photoperiod), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Oxygen Concentration")

NestedFitsData %>%
   filter(WL == "450") %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(O2_uM)), size = 4, alpha = 0.5) +
 geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(O2_uM)), linewidth = 0.1, alpha = 0.4) +
   labs(subtitle = "Actinic PAR (nm), Strain, Photoperiod", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
 geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
  geom_errorbar(aes(x = Par_ue, ymin = (deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
  #   scale_y_continuous(breaks=seq(-0.03, 0.07, by = 0.01)) +
  # coord_cartesian(ylim = c (-0.03, 0.07)) +
  #scale_colour_manual(values = MCMIXColours) +
  ggh4x::facet_nested(cols = vars(WL, Strain), rows = vars(Photoperiod), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Oxygen Concentration")

NestedFitsData %>%
   filter(WL == "660") %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(O2_uM)), size = 4, alpha = 0.5) +
 geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(O2_uM)), linewidth = 0.1, alpha = 0.4) +
   labs(subtitle = "Actinic PAR (nm), Strain, Photoperiod", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
 geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
  geom_errorbar(aes(x = Par_ue, ymin = (deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
  coord_cartesian(xlim = c (0, 200)) +
  #   scale_y_continuous(breaks=seq(-0.03, 0.07, by = 0.01)) +
  # coord_cartesian(ylim = c (-0.03, 0.07)) +
  #scale_colour_manual(values = MCMIXColours) +
  ggh4x::facet_nested(cols = vars(WL, Strain), rows = vars(Photoperiod), 
                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
  theme_bw() +
  labs(colour = "Oxygen Concentration")

```

```{r save summary growth plots}

# ggsave(file = file.path(PlotsPath, paste("MIT9313deltaODLmuMatrixPlot",".png",sep = "")), plot = MIT9313deltaODLmuMatrixPlot, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsPath, paste("SS120deltaODLmuMatrixPlot",".png",sep = "")), plot = SS120deltaODLmuMatrixPlot, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsPath, paste("MED4deltaODLmuMatrixPlot",".png",sep = "")), plot = MED4deltaODLmuMatrixPlot, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)

```

Compare truncated runs
```{r CompareTruncated, fig.height= 15, fig.width= 15}

 NestedFitsData %>%
  filter(Strain == "MIT9313" |
         Strain == "SS120" |
         Strain == "MED4",
           WL == 450 |
           WL == 530 |
           WL == 660 |
           WL == "WW",
          Run >= 25 & 
           Run < 80, ) %>%
  ggplot(aes(x = OD720_Lmu_corr, y = OD720trunc_Lmu_corr, colour = WL)) +
  theme(panel.spacing.x = unit(10, "cm"), panel.spacing.y = unit(2, "cm")) +
  geom_point(aes(labels = c(Run))) +
  geom_errorbar(aes(xmin = OD720_Lmu_corr - OD720_Lmu_se, xmax = OD720_Lmu_corr + OD720_Lmu_se, ymin = OD720trunc_Lmu_corr - OD720trunc_Lmu_se, ymax = OD720trunc_Lmu_corr + OD720trunc_Lmu_se), size = 0.05, color = 'black', data = . %>% filter(GrowthAmpOD720Flag_14days == 1)) +
  scale_colour_manual(values = MCMIXColours) +
  geom_text(aes(x = OD720_Lmu_corr, y = OD720trunc_Lmu_corr, label= Run),hjust=0, vjust=0) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  coord_fixed(ratio = 1, xlim = c (0, 0.05), ylim = c(0, 0.05) ) +
 # coord_cartesian() +
  scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
  labs(subtitle = "Strain, O2, Actinic PAR (nm)  All Growth Data From Runs >= #25", y = "Corrected Truncated Logistic Growth Rate (OD720trunc_Lmu)", x = "Corrected Logistic Growth Rate (OD720_Lmu)") +
   ggh4x::facet_nested(cols = vars(O2, WL), rows = vars(Strain), 
                    labeller = labeller(WL = label_both, Strain = label_value, O2 = label_both)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

NestedFitsData %>%
  filter(Strain == "MIT9313" |
         Strain == "SS120" |
         Strain == "MED4",
           WL == 450 |
           WL == 530 |
           WL == 660 |
           WL == "WW",
          Run >= 25 & 
           Run < 80, ) %>%
  ggplot(aes(x = deltaOD_Lmu_corr, y = deltaODtrunc_Lmu_corr, colour = WL)) +
  theme(panel.spacing.x = unit(10, "cm"), panel.spacing.y = unit(2, "cm")) +
  geom_point(aes(labels = c(Run))) +
   geom_errorbar(aes(xmin = deltaOD_Lmu_corr - deltaOD_Lmu_se, xmax = deltaOD_Lmu_corr + deltaOD_Lmu_se, ymin = deltaODtrunc_Lmu_corr - deltaODtrunc_Lmu_se, ymax = deltaODtrunc_Lmu_corr + deltaODtrunc_Lmu_se), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days == 1)) +
  scale_colour_manual(values = MCMIXColours) +
  geom_text(aes(x = deltaOD_Lmu_corr, y = deltaODtrunc_Lmu_corr, label= Run),hjust=0, vjust=0) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  coord_fixed(ratio = 1, xlim = c (0, 0.05), ylim = c(0, 0.05) ) +
 # coord_cartesian() +
  scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
  labs(subtitle = "Strain, O2, Actinic PAR (nm) All Growth Data From Runs >= #25", y = "Corrected Truncated Logistic Growth Rate (deltaODtrunc_Lmu)", x = "Corrected Logistic Growth Rate (deltaOD_Lmu)") +
   ggh4x::facet_nested(cols = vars(O2, WL), rows = vars(Strain), 
                    labeller = labeller(WL = label_both, Strain = label_value, O2 = label_both)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

NestedFitsData %>%
  filter(Strain == "MIT9313" |
         Strain == "SS120" |
         Strain == "MED4",
           WL == 450 |
           WL == 530 |
           WL == 660 |
           WL == "WW",
          Run >= 25 & 
           Run < 80, 
          OD720trunc_Lmu_corr == 0 |
          OD720trunc_Lmu_corr != 0 & OD720trunc_LseGrowthFlag == 1,
          OD720_Lmu_corr == 0 |
          OD720_Lmu_corr != 0 & OD720_LseGrowthFlag == 1 ) %>%
  ggplot(aes(x = OD720_Lmu_corr, y = OD720trunc_Lmu_corr, colour = WL)) +
  theme(panel.spacing.x = unit(10, "cm"), panel.spacing.y = unit(2, "cm")) +
  geom_point(aes(labels = c(Run))) +
  geom_errorbar(aes(xmin = OD720_Lmu_corr - OD720_Lmu_se, xmax = OD720_Lmu_corr + OD720_Lmu_se, ymin = OD720trunc_Lmu_corr - OD720trunc_Lmu_se, ymax = OD720trunc_Lmu_corr + OD720trunc_Lmu_se), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpOD720Flag_14days == 1)) +
  scale_colour_manual(values = MCMIXColours) +
  geom_text(aes(x = OD720_Lmu_corr, y = OD720trunc_Lmu_corr, label= Run),hjust=0, vjust=0) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  coord_fixed(ratio = 1, xlim = c (0, 0.05), ylim = c(0, 0.05) ) +
 # coord_cartesian() +
  scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
  labs(subtitle = "Strain, O2, Actinic PAR (nm) Standard Error Filtered Showing Runs >= #25", y = "Corrected Truncated Logistic Growth Rate  (OD720trunc_Lmu)", x = "Corrected Logistic Growth Rate (OD720_Lmu)") +
   ggh4x::facet_nested(cols = vars(O2, WL), rows = vars(Strain), 
                    labeller = labeller(WL = label_both, Strain = label_value, O2 = label_both)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

NestedFitsData %>%
  filter(Strain == "MIT9313" |
         Strain == "SS120" |
         Strain == "MED4",
           WL == 450 |
           WL == 530 |
           WL == 660 |
           WL == "WW",
          Run >= 25 & 
           Run < 80, 
          deltaODtrunc_Lmu_corr == 0 |
          deltaODtrunc_Lmu_corr != 0 & deltaODtrunc_LseGrowthFlag == 1,
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1 ) %>%
  ggplot(aes(x = deltaOD_Lmu_corr, y = deltaODtrunc_Lmu_corr, colour = WL)) +
  theme(panel.spacing.x = unit(10, "cm"), panel.spacing.y = unit(2, "cm")) +
  geom_point(aes(labels = c(Run))) +
  geom_errorbar(aes(xmin = deltaOD_Lmu_corr - deltaOD_Lmu_se, xmax = deltaOD_Lmu_corr + deltaOD_Lmu_se, ymin = deltaODtrunc_Lmu_corr - deltaODtrunc_Lmu_se, ymax = deltaODtrunc_Lmu_corr + deltaODtrunc_Lmu_se), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days == 1)) +
  scale_colour_manual(values = MCMIXColours) +
  geom_text(aes(x = deltaOD_Lmu_corr, y = deltaODtrunc_Lmu_corr, label= Run),hjust=0, vjust=0) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  coord_fixed(ratio = 1, xlim = c (0, 0.05), ylim = c(0, 0.05) ) +
 # coord_cartesian() +
  scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
  labs(subtitle = "Strain, O2, Actinic PAR (nm) Standard Error Filtered Showing Runs >= #25", y = "Corrected Truncated Logistic Growth Rate  (deltaODtrunc_Lmu)", x = "Corrected Logistic Growth Rate (deltaOD_Lmu)") +
   ggh4x::facet_nested(cols = vars(O2, WL), rows = vars(Strain), 
                    labeller = labeller(WL = label_both, Strain = label_value, O2 = label_both)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

NestedFitsData %>%
  filter(Strain == "MIT9313" |
         Strain == "SS120" |
         Strain == "MED4",
           WL == 450 |
           WL == 530 |
           WL == 660 |
           WL == "WW",
          Run >= 25 & 
           Run < 80, ) %>%
  ggplot(aes(x = deltaOD_Lmu_corr, y = deltaODtrunc_Lmu_corr, colour = WL)) +
  theme(panel.spacing.x = unit(10, "cm"), panel.spacing.y = unit(2, "cm")) +
  geom_point(aes(labels = c(Run))) +
  geom_errorbar(aes(xmin = deltaOD_Lmu_corr - deltaOD_Lmu_se, xmax = deltaOD_Lmu_corr + deltaOD_Lmu_se, ymin = deltaODtrunc_Lmu_corr - deltaODtrunc_Lmu_se, ymax = deltaODtrunc_Lmu_corr + deltaODtrunc_Lmu_se), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days == 1)) +
  scale_colour_manual(values = MCMIXColours) +
  geom_text(aes(x = deltaOD_Lmu_corr, y = deltaODtrunc_Lmu_corr, label= Run),hjust=0, vjust=0) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  coord_fixed(ratio = 1, xlim = c (0, 0.05), ylim = c(0, 0.05) ) +
 # coord_cartesian() +
  scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
  labs(subtitle = "Strain, O2, Actinic PAR (nm)  All Growth Data From Runs >= #25", y = "Corrected Truncated Logistic Growth Rate  (deltaODtrunc_Lmu)", x = "Corrected Logistic Growth Rate (deltaOD_Lmu)") +
  #facet_grid(rows = vars(Strain), cols = vars(O2, WL)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

NestedFitsData %>%
  filter(Strain == "MIT9313" |
         Strain == "SS120" |
         Strain == "MED4",
           WL == 450 |
           WL == 530 |
           WL == 660 |
           WL == "WW",
          Run >= 25 & 
           Run < 80, 
          deltaODtrunc_Lmu_corr == 0 |
          deltaODtrunc_Lmu_corr != 0 & deltaODtrunc_LseGrowthFlag == 1,
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  ggplot(aes(x = deltaOD_Lmu_corr, y = deltaODtrunc_Lmu_corr, colour = WL)) +
  theme(panel.spacing.x = unit(10, "cm"), panel.spacing.y = unit(2, "cm")) +
  geom_point(aes(labels = c(Run))) +
  geom_errorbar(aes(xmin = deltaOD_Lmu_corr - deltaOD_Lmu_se, xmax = deltaOD_Lmu_corr + deltaOD_Lmu_se, ymin = deltaODtrunc_Lmu_corr - deltaODtrunc_Lmu_se, ymax = deltaODtrunc_Lmu_corr + deltaODtrunc_Lmu_se), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days == 1)) +
  scale_colour_manual(values = MCMIXColours) +
  geom_text(aes(x = deltaOD_Lmu_corr, y = deltaODtrunc_Lmu_corr, label= Run),hjust=0, vjust=0) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  coord_fixed(ratio = 1, xlim = c (0, 0.05), ylim = c(0, 0.05) ) +
 # coord_cartesian() +
  scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
  labs(subtitle = "Strain, O2, Actinic PAR (nm) Standard Error Filtered From Runs >= #25 ", y = "Corrected Truncated Logistic Growth Rate  (deltaODtrunc_Lmu)", x = "Corrected Logistic Growth Rate (deltaOD_Lmu)") +
  #facet_grid(rows = vars(Strain), cols = vars(O2, WL)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

NestedFitsData %>%
  filter(Strain == "MIT9313" |
         Strain == "SS120" |
         Strain == "MED4",
           WL == 450 |
           WL == 530 |
           WL == 660 |
           WL == "WW",
          Run >= 25 & 
           Run < 80, 
          deltaODtrunc_Lmu_corr == 0 |
          deltaODtrunc_Lmu_corr != 0 & deltaODtrunc_LseGrowthFlag == 1,
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  ggplot() +
  theme(panel.spacing.x = unit(10, "cm"), panel.spacing.y = unit(2, "cm")) +
  geom_point(aes(x = deltaOD_TimeHalfPmax_h, y = deltaODtrunc_TimetoMax, colour = WL), size = 3) +
  # geom_errorbar(aes(xmin = deltaOD_Lmu_corr - deltaOD_Lmu_se, xmax = deltaOD_Lmu_corr + deltaOD_Lmu_se, ymin = deltaODtrunc_Lmu_corr - deltaODtrunc_Lmu_se, ymax = deltaODtrunc_Lmu_corr + deltaODtrunc_Lmu_se), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days == 1)) +
  scale_colour_manual(values = MCMIXColours) +
  # geom_text(aes(x = deltaOD_Lmu_corr, y = deltaODtrunc_Lmu_corr, label= Run),hjust=0, vjust=0) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
 coord_fixed(ratio = 1, xlim = c (0, 600), ylim = c(0, 600) ) +
 # coord_cartesian() +
  # scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
  # labs(subtitle = "Strain, O2, Actinic PAR (nm) Standard Error Filtered From Runs >= #25 ", y = "deltaOD time to half pmax (Calculate from full growth trajectory)", x = "deltaOD truncated time to pmax") +
  #facet_grid(rows = vars(Strain), cols = vars(O2, WL)) +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

```

### 2023-12-07 Code/MultiDataProcessPico.Rmd
Removed annotation that does not apply

@@
 ```{r read ProcessFile}
-ProcessFile <- "../Data/ImportedData/ImportedMCData/20230210_PICO_MCMIX006_RUN108_TargetDataMetaFilter.Rds"
+ProcessFile <- "../Data/ImportedData/ImportedMCData/20211223_PICO_MCMIX006_RUN42_TargetDataMetaFilter.Rds"
 
@@
 ```
-
-Remove extraneous columns from ProcessData; could have been done at end of MultiDataImport.Rmd
 

### 2023-12-07 Code/MultiDataGrowthAssessPico.Rmd
Editing MultiCultiGrowthAccessPico

@@
 ---
-title: "MultiDataGrowthAssess"
+title: "MultiDataGrowthAssessPico"
 author:
@@
 
+library(tidyverse)
 library(lubridate)
@@
 library(grid)
-library(tidyverse)
+library(photobiologyWavebands)
 #library(tidyquant)
@@
 #"..", takes up a level in the directory path
+
 Project <- "PICO"
-DataIn1 <- file.path("..","ProcessedData", "LogGrowthFits1")
-DataIn2 <- file.path("..","ProcessedData", "LogGrowthFits2")
-PlotsPath <- file.path("..","Plots")
-ShinyPath <- file.path("..", "ShinyPico", "data")
-DataOut <- file.path("..","GrowthAssessData")
-MetaCatalog <- file.path("..","PicoCatalog.csv")
+
+DataOut <- file.path("..", "Data", "CleanData", "CleanedMCData")
+DataIn <- file.path("..", "Data","ProcessedData", "ProcessedMCData")
 
@@
 
-GrowthTerm <- "Gompertz Growth Rate"
-
 ```
@@
 ```{r set colours}
-MyWavelengths = c(405, 450, 475, 530, 615, 660, 730, "WW")
-MCMIXColours = c("violet", "darkblue", "dodgerblue", "darkgreen","orange","red","purple", "black")
+
+MyWavelengths = c(405, 445, 470, 530, 620, 660, 730, "WW")
+MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(445), w_length2rgb(470), w_length2rgb(530),
+                   w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black"))
 
@@
 ```{r previous ProcessedData}
-ProcessedFiles1 <- list.files(path = DataIn1, pattern = Project, full.names = TRUE)
-
-ProcessedFiles1
-
-ProcessedFiles2 <- list.files(path = DataIn2, pattern = Project, full.names = TRUE)
-
-ProcessedFiles2
+
+ProcessedFiles <- list.files(path = DataIn, pattern = Project, full.names = TRUE)
+
+ProcessedFiles
+
 ```
@@
 ## Read in ProcessedFiles .Rds
-## April 2023, Had to split the read in into 2 as there was not enough memory to read all files at once.
 
@@
 
-LogFitsData1 <-  ProcessedFiles1 %>%
-    map_df(~readRDS_plus(Flnm = .)) %>%
-    select(-c("Motivation", "doi", "SourceSalinity", "EndDate", "Salinity",  "InocpH","lognormdeltaOD_Gompertz", "lognormOD720_Gompertz", "OD720_logistic", "deltaOD_logistic","OD720trunc_logistic", "deltaODtrunc_logistic", "OD720trunc_exp", "deltaODtrunc_exp",
-              "lognormOD720_Gompertz_param",
-              "lognormdeltaOD_Gompertz_param",
-              "OD720_logistic_param",
-              "OD720trunc_exp_param",
-              "deltaODtrunc_logistic_param",
-              "OD720trunc_logistic_param",
-              "deltaOD_logistic_param",
-              "deltaODtrunc_exp_param"
-              ))
-
-LogFitsData2 <-  ProcessedFiles2 %>%
-    map_df(~readRDS_plus(Flnm = .)) %>%
-    select(-c("Motivation", "doi", "SourceSalinity", "EndDate", "Salinity",  "InocpH","lognormdeltaOD_Gompertz", "lognormOD720_Gompertz", "OD720_logistic", "deltaOD_logistic","OD720trunc_logistic", "deltaODtrunc_logistic", "OD720trunc_exp", "deltaODtrunc_exp",
-              "lognormOD720_Gompertz_param",
-              "lognormdeltaOD_Gompertz_param",
-              "OD720_logistic_param",
-              "OD720trunc_exp_param",
-              "deltaODtrunc_logistic_param",
-              "OD720trunc_logistic_param",
-              "deltaOD_logistic_param",
-              "deltaODtrunc_exp_param"
-              ))
-
-glimpse(LogFitsData1)
-glimpse(LogFitsData2)
-
-LogFitsData <- rbind(LogFitsData1, LogFitsData2)
-
-remove(LogFitsData1)
-remove(LogFitsData2)
+LogFitsData <-  ProcessedFiles %>%
+    map_df(~readRDS_plus(Flnm = .))
+
+%>%
+    # select(-c("Motivation", "doi", "SourceSalinity", "EndDate", "Salinity",  "InocpH","lognormdeltaOD_Gompertz", "lognormOD720_Gompertz", "OD720_logistic", "deltaOD_logistic","OD720trunc_logistic", "deltaODtrunc_logistic", "OD720trunc_exp", "deltaODtrunc_exp",
+              # "lognormOD720_Gompertz_param",
+              # "lognormdeltaOD_Gompertz_param",
+              # "OD720_logistic_param",
+              # "OD720trunc_exp_param",
+              # "deltaODtrunc_logistic_param",
+              # "OD720trunc_logistic_param",
+              # "deltaOD_logistic_param",
+              # "deltaODtrunc_exp_param"
+              # ))
 

### 2023-12-07 Code/MultiDataProcessPico.Rmd
Moved to load tidyverse after all other packages to avoid discrepencies.

@@
 # libraries; Note check actual dependencies
-library(tidyverse)
+
 library(lubridate)
@@
 library(photobiologyWavebands)
+library(tidyverse)
 
@@
 ```{r read ProcessFile}
-ProcessFile <- "../Data/ImportedData/ImportedMCData/20211223_PICO_MCMIX006_RUN42_TargetDataMetaFilter.Rds"
+ProcessFile <- "../Data/ImportedData/ImportedMCData/20221021_PICO_MCMIX006_RUN96_TargetDataMetaFilter.Rds"
 

### 2023-12-07 Code/MultiDataGrowthAssessPico.Rmd
Fixed filepath

@@
 
-library(tidyverse)
 library(lubridate)
@@
 library(photobiologyWavebands)
-#library(tidyquant)
-#library(data.table)
-#library(googledrive)
-#library(googlesheets4)
-#library(dplyr)
+library(tidyverse)
+
 ```
@@
     map_df(~readRDS_plus(Flnm = .))
-
-%>%
-    # select(-c("Motivation", "doi", "SourceSalinity", "EndDate", "Salinity",  "InocpH","lognormdeltaOD_Gompertz", "lognormOD720_Gompertz", "OD720_logistic", "deltaOD_logistic","OD720trunc_logistic", "deltaODtrunc_logistic", "OD720trunc_exp", "deltaODtrunc_exp",
-              # "lognormOD720_Gompertz_param",
-              # "lognormdeltaOD_Gompertz_param",
-              # "OD720_logistic_param",
-              # "OD720trunc_exp_param",
-              # "deltaODtrunc_logistic_param",
-              # "OD720trunc_logistic_param",
-              # "deltaOD_logistic_param",
-              # "deltaODtrunc_exp_param"
-              # ))
 

### 2023-12-08 Code/MetaDataImport.Rmd
Used SampleID instead of ID column

--- 2023-12-06 Code/MetaDataImport.Rmd
@@
 ProjectRows <- c("MiSa|JuNa|SaAr")
-ProjectCols <- c("PrimaryOperator", "SampleID", "Run", "ID", "Strain", "ExpCul", "ExpDate", "ExpStartTime", "Par_ue", "Photoperiod", "Temp_c", "MC", "Tube", "EndDate","O2", "O2_Category", "WL","LightShape", "Optode","OptodeCh","OptodeMeasure", "ExpEndDate")
+ProjectCols <- c("PrimaryOperator", "SampleID", "Run", "Strain", "ExpCul", "ExpDate", "ExpStartTime", "Par_ue", "Photoperiod", "Temp_c", "MC", "Tube","O2", "O2_Category", "WL","LightShape", "Optode","OptodeCh","OptodeMeasure", "ExpEndDate")
 
@@
           ExpEndDate = ymd_hms(`ExpEndDate`)) %>% 
-  filter(str_detect(ID,  ProjectRows)) %>% 
-  select(ProjectCols)
+  filter(str_detect(SampleID,  ProjectRows)) %>% 
+  select(ProjectCols) %>% 
+  rename(CultureID = SampleID)
 

### 2023-12-08 Code/MetaDataImport.Rmd
Edit

@@
   filter(str_detect(SampleID,  ProjectRows)) %>% 
-  select(ProjectCols) %>% 
-  rename(CultureID = SampleID)
+  select(ProjectCols)
 

### 2023-12-08 Code/MultiDataImportPico.Rmd
Edit Changed CultureID to SampleID

@@
 
-TargetFile <- "20221021_PICO_MCMIX006_RUN96.csv"
+TargetFile <- "20230210_PICO_MCMIX006_RUN108.csv"
 
@@
   scale_colour_manual(values = MCMIXColours) +
-  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; CultureID; Tube") +
-  facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, CultureID)) +
+  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; SampleID; Tube") +
+  facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, SampleID)) +
   theme_bw() +  
@@
  filter(OD680 > 0) %>% # consider this rule for OD720 as well
-  group_by(CultureID) %>%
+  group_by(SampleID) %>%
   arrange(Filename, MC, Tube, time) %>%
@@
   labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
- facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, CultureID)) +
+ facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, SampleID)) +
   theme_bw() +  
@@
   # coord_cartesian(xlim = c(0, 800)) +
-  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; CultureID; Tube") +
-  # facet_grid(rows = vars(O2), cols = vars(Tube, Par_ue, Strain, CultureID)) +
+  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; SampleID; Tube") +
+  # facet_grid(rows = vars(O2), cols = vars(Tube, Par_ue, Strain, SampleID)) +
   annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkblue") +
@@
   coord_cartesian(xlim = c(0, 400)) +
-  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; CultureID; Tube") +
-  facet_grid(rows = vars(O2), cols = vars(Par_ue, Strain, CultureID, Tube)) +
+  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; SampleID; Tube") +
+  facet_grid(rows = vars(O2), cols = vars(Par_ue, Strain, SampleID, Tube)) +
   annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkblue") +

### 2023-12-08 Code/MultiDataImportPico.Rmd
Edit annotations
Removed Googlesheet and GoogleDrive libraries

@@
 
-# To Do
-
--move filter for negative OD to point of log curve fitting Filtering
-negative points needed for current noise filtering, so placed just
-before noise filtering; with more sophisticated noise filtering
-
 # Introduction
@@
 library(data.table)
-library(googledrive)
-library(googlesheets4)
 library(photobiologyWavebands)
@@
 ```{r set colours}
-MyWavelengths = c(405, 445, 470, 530, 620, 660, 730, "WW")
-MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(445), w_length2rgb(470), w_length2rgb(530),            w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black"))
+MyWavelengths = c(405, 450, 470, 530, 620, 660, 730, "WW")
+MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(450), w_length2rgb(470), w_length2rgb(530),            w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black"))
 
@@
 
-TargetFile <- "20230210_PICO_MCMIX006_RUN108.csv"
+TargetFile <- "20211223_PICO_MCMIX006_RUN42.csv"
 

### 2023-12-08 Code/MultiDataProcessPico.Rmd
Removed knit output to Html. Will never knit this rmd. Removed stringr library

--- 2023-12-07 Code/MultiDataProcessPico.Rmd
@@
 date: "`r format(Sys.Date())`"
-output:
-bookdown::html_document2:
-    code_folding: show
-    keep_md: yes
-    toc: TRUE
-    toc_float: TRUE
-    toc_depth: 6
-    fig_caption: yes
 bibliography: Prochlorococcus_O2_NPQ.bib
@@
 # libraries; Note check actual dependencies
-library(tidyverse)
+
 library(lubridate)
-library(stringr)
 library(broom)
@@
 
-DeclineWindow <- 12 #duration in hours overwhich we test for decline from max by amplitude GrowthFlagValue in OD720 or deltaOD
+DeclineWindow <- 12 #duration in hours overwhich we test for decline from max in OD720 or deltaOD
 
@@
 
+```{r add min and max meanOD}
+
+ProcessData <- ProcessData %>%
+  group_by(Tube) %>%
+   mutate(minRollMeanOD720 = min(rollmeanOD720, na.rm = TRUE),
+          minRollMeandeltaOD = min(rollmeandeltaOD, na.rm = TRUE),
+          maxRollMeanOD720 = max(rollmeanOD720, na.rm = TRUE),
+          maxRollMeandeltaOD = max(rollmeandeltaOD, na.rm = TRUE)) %>% 
+  ungroup()
+
+glimpse(ProcessData)
+
+```
+
 # Generate a plot of the data in the selected tidied MultiCulti file.
@@
            DeclineFlagOD720 == 0) %>%
-  select(-c("TrimRollMeanOD720", "TrimRollMeandeltaOD")) %>%
-  ungroup()
-
-glimpse(ProcessData)
-
-```
-
-```{r add min meanOD}
-
-ProcessData <- ProcessData %>%
-  group_by(Tube) %>%
-   mutate(minRollMeanOD720 = min(rollmeanOD720, na.rm = TRUE),
-          minRollMeandeltaOD = min(rollmeandeltaOD, na.rm = TRUE)) %>% 
+  select(-c("TrimRollMeanOD720", "TrimRollMeandeltaOD", "DeclineFlagdeltaOD", 
+            "DeclineFlagOD720")) %>%
   ungroup()
@@
   filter(lognormOD720 >= 0) %>%
-nest(tubedata = c(time, ToD, Day, Actinic_par, OD680, OD720, deltaOD, ActinicMid_parOD720, ActinicMid_dayOD720,rollmeanOD720,rollmeandeltaOD,lognormOD720, lognormdeltaOD, LagSeedOD720, LagSeeddeltaOD))
+nest(tubedata = c(time, ToD, Day, Actinic_par, OD680, OD720, deltaOD, ActinicMid_parOD720, ActinicMid_dayOD720, rollmeanOD720, rollmeandeltaOD, lognormOD720, lognormdeltaOD, LagSeedOD720, LagSeeddeltaOD))
 
@@
           GrowthAmpOD720 = if_else(OD720_TimetoMax <= MaxAmpHour | is.na(OD720_TimetoMax), map(tubedata, ~growth_amp_decline(y = .$rollmeanOD720)), map(tubedata, ~growth_amp(y = .$rollmeanOD720)))
-         ) %>%
-   mutate(GrowthAmpdeltaODFlag = if_else(GrowthAmpdeltaOD >= deltaODGrowthFlagValue , 1, 0),
-           GrowthAmpOD720Flag = if_else(GrowthAmpOD720 >= OD720GrowthFlagValue, 1, 0)
          )
 
-#Growthamp flags for growth up to 14 days 
+#Growthamp flags to determine if growth occurred before 14 days 
 ProcessDataNestGrowth2 <- ProcessDataNestGrowth %>%
@@
            ) %>%
-      mutate(GrowthAmpdeltaODFlag_14days = if_else(GrowthAmpdeltaOD_14days >= deltaODGrowthFlagValue, 1, 0),
-             GrowthAmpOD720Flag_14days = if_else(GrowthAmpOD720_14days >= OD720GrowthFlagValue, 1, 0)
-      ) %>% 
        mutate(DoubleOD720Flag_14days = if_else(maxRollMeanOD720_14days >= minRollMeanOD720_14days * 2 & !is.na(OD720_TimetoMax) >= MaxAmpHour & !is.na(OD720_TimetoMax) & GrowthAmpOD720_14days >= 0, 1, 0),
@@
 ProcessDataNestGrowth <- ProcessDataNestGrowth %>%
-  left_join(., ProcessDataNestGrowth2 %>% select(Tube, GrowthAmpdeltaOD_14days, GrowthAmpOD720_14days,  minRollMeanOD720_14days, maxRollMeanOD720_14days, minRollMeandeltaOD_14days, maxRollMeandeltaOD_14days, GrowthAmpdeltaODFlag_14days, GrowthAmpOD720Flag_14days, DoubledeltaODFlag_14days, DoubleOD720Flag_14days), by = "Tube")
+  left_join(., ProcessDataNestGrowth2 %>% select(Tube, GrowthAmpdeltaOD_14days, GrowthAmpOD720_14days,  minRollMeanOD720_14days, maxRollMeanOD720_14days, minRollMeandeltaOD_14days, maxRollMeandeltaOD_14days,  DoubledeltaODFlag_14days, DoubleOD720Flag_14days), by = "Tube")
 

### 2023-12-08 Code/JazDataImport.Rmd
Removed lubridate removed knit output

@@
 title: "Import Jaz data"
-output: html_notebook
 ---
@@
 library(tidyverse)
-library(lubridate)
 library(googledrive)
@@
 
-MultiCultiPAR <- read.csv(file.path(DataIn, "MultiCulti_PAR.csv"))
+MultiCultiPAR <- read_csv(file.path(DataIn, "MultiCulti_PAR.csv"))
 

### 2023-12-08 Code/MultiDataProcessPico.Rmd
removed knit html output
Removed redundant variables

@@
 ```{r read ProcessFile}
-ProcessFile <- "../Data/ImportedData/ImportedMCData/20211223_PICO_MCMIX006_RUN42_TargetDataMetaFilter.Rds"
+ProcessFile <- "../Data/ImportedData/ImportedMCData/20230210_PICO_MCMIX006_RUN108_TargetDataMetaFilter.Rds"
 
@@
           maxRollMeandeltaOD_14days = as.numeric(maxRollMeandeltaOD_14days)
-           ) %>%
-       mutate(DoubleOD720Flag_14days = if_else(maxRollMeanOD720_14days >= minRollMeanOD720_14days * 2 & !is.na(OD720_TimetoMax) >= MaxAmpHour & !is.na(OD720_TimetoMax) & GrowthAmpOD720_14days >= 0, 1, 0),
-             DoubledeltaODFlag_14days = if_else(maxRollMeandeltaOD_14days >= minRollMeandeltaOD_14days * 2 & !is.na(deltaOD_TimetoMax) >= MaxAmpHour & !is.na(deltaOD_TimetoMax) & GrowthAmpdeltaOD_14days >= 0, 1, 0)
            )
@@
 ProcessDataNestGrowth <- ProcessDataNestGrowth %>%
-  left_join(., ProcessDataNestGrowth2 %>% select(Tube, GrowthAmpdeltaOD_14days, GrowthAmpOD720_14days,  minRollMeanOD720_14days, maxRollMeanOD720_14days, minRollMeandeltaOD_14days, maxRollMeandeltaOD_14days,  DoubledeltaODFlag_14days, DoubleOD720Flag_14days), by = "Tube")
+  left_join(., ProcessDataNestGrowth2 %>% select(Tube, GrowthAmpdeltaOD_14days, GrowthAmpOD720_14days,  minRollMeanOD720_14days, maxRollMeanOD720_14days, minRollMeandeltaOD_14days, maxRollMeandeltaOD_14days), by = "Tube")
 
@@
 ```
-
-Plot Fit Terms vs. conditions - High Std error filtered out by flag argument
-```{r logistic fit terms plot}
-ProcessDataNestGrowth %>%
- unnest(cols = c(OD720_logistic_tidied),names_sep = "_") %>%
-  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, OD720_logistic_tidied_term, OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error)) %>%
-  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error), names_sep = "_") %>%
-  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
-         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
-         OD720_Lmu = OD720_logistic_tidied_estimate_Lmu,
-         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
-         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,
-         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept) %>%
-  mutate(LmuOD720Flag = if_else(OD720_Lmu_se < OD720_Lmu * GrowthFlagError, 1, 0)) %>%
-# mutate(GrowthFlag = if_else((OD720_Lintercept + OD720_Lintercept_se) < ((OD720_Lmax - OD720_Lmax_se) & (OD720_Lmu_se < OD720_Lmu * GrowthFlagError) & (OD720_Lmax_se < OD720_Lmax * GrowthFlagError) ), 1, 0)) %>%
-  filter(LmuOD720Flag == 1) %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = OD720_Lmu, colour = as.factor(WL))) +
-  geom_errorbar(aes(x = Par_ue, ymin = OD720_Lmu - OD720_Lmu_se, ymax = OD720_Lmu + OD720_Lmu_se, colour = as.factor(WL))) +
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid (cols = vars(Strain), rows = vars(O2)) +
-  theme_bw() +
-  labs(title = "Logistic cell scatter growth rates - High std error fits omitted")
-
-ProcessDataNestGrowth %>%
- unnest(cols = c(deltaOD_logistic_tidied),names_sep = "_") %>%
-  select(c(Filename, Tube, Strain, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, deltaOD_logistic_tidied_term, deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error)) %>%
-  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error), names_sep = "_") %>%
-  rename(deltaOD_Lmax = deltaOD_logistic_tidied_estimate_Lmax,
-         deltaOD_Lmax_se = deltaOD_logistic_tidied_std.error_Lmax,
-         deltaOD_Lmu = deltaOD_logistic_tidied_estimate_Lmu,
-         deltaOD_Lmu_se = deltaOD_logistic_tidied_std.error_Lmu,
-         deltaOD_Lintercept = deltaOD_logistic_tidied_estimate_Lintercept,
-         deltaOD_Lintercept_se = deltaOD_logistic_tidied_std.error_Lintercept) %>%
-  mutate(LmudeltaODFlag = if_else(deltaOD_Lmu_se < deltaOD_Lmu * GrowthFlagError, 1, 0)) %>%
- # mutate(GrowthFlag = if_else((deltaOD_Lintercept + deltaOD_Lintercept_se) < ((deltaOD_Lmax - deltaOD_Lmax_se) & (deltaOD_Lmu_se < deltaOD_Lmu * GrowthFlagError) & (deltaOD_Lmax_se < deltaOD_Lmax * GrowthFlagError) ), 1, 0)) %>%
-  filter(LmudeltaODFlag == 1) %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = deltaOD_Lmu, colour = as.factor(WL))) +
-  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu - deltaOD_Lmu_se, ymax = deltaOD_Lmu + deltaOD_Lmu_se, colour = as.factor(WL))) +
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid (cols = vars(Strain), rows = vars(O2)) +
-  theme_bw() +
-  labs(title = "Logistic chlorophyll specific growth rates - High Std error fits omitted")
-
-```

### 2023-12-08 Code/MultiDataImportPico.Rmd
Removed knit to html output

@@
 # libraries; Note check actual dependencies
+
 library(tidyverse)

### 2023-12-08 Code/MultiDataGrowthAssessPico.Rmd
Removed all redundant varibles

@@
 library(lubridate)
-library(stringr)
 library(broom)
@@
 
-MyWavelengths = c(405, 445, 470, 530, 620, 660, 730, "WW")
-MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(445), w_length2rgb(470), w_length2rgb(530),
+MyWavelengths = c(405, 450, 470, 530, 620, 660, 730, "WW")
+MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(450), w_length2rgb(470), w_length2rgb(530),
                    w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black"))
@@
 
-## List previously processed data
-
-Note: Split files will not be correct for Par_ue, but Actinic_par should be OK Fix: replace MetaData Par_ue with max(Actinic_par) for each file or split file
+## List processed data
 
@@
 
-# TestData <- readRDS_plus(Flnm = file.path("../ProcessedData/LogGrowthFits/20200731_PICO_MCMIX004_RUN17_ProcessDataNestGrowth.Rds"))
-
 LogFitsData <-  ProcessedFiles %>%
     map_df(~readRDS_plus(Flnm = .))
+
+glimpse(LogFitsData)
 
@@
 
-# OD720 gompertz fits
-# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007.Defined at line 75 
-lognormOD720_unnest <- LogFitsData %>%
-   select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720, GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, lognormOD720_Gompertz_tidied, lognormOD720_Gompertz_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
-          ) %>%
-  unnest(cols = c(lognormOD720_Gompertz_tidied), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_wider(names_from =  lognormOD720_Gompertz_tidied_term, values_from = c(lognormOD720_Gompertz_tidied_estimate, lognormOD720_Gompertz_tidied_std.error, lognormOD720_Gompertz_tidied_statistic, lognormOD720_Gompertz_tidied_p.value), names_sep = "_") %>%
-  rename(OD720_Gmax = lognormOD720_Gompertz_tidied_estimate_Gmax,
-         OD720_Gmax_se = lognormOD720_Gompertz_tidied_std.error_Gmax,
-         OD720_Gmu_raw = lognormOD720_Gompertz_tidied_estimate_Gmu,
-         OD720_Gmu_se = lognormOD720_Gompertz_tidied_std.error_Gmu,
-         OD720_GLag = lognormOD720_Gompertz_tidied_estimate_GLag,             
-         OD720_GLag_se = lognormOD720_Gompertz_tidied_std.error_GLag)  %>%
-   mutate(OD720_Gmu_corr = if_else(!is.na(OD720_Gmu_raw), OD720_Gmu_raw, 0),
-          OD720_Gmu_se = if_else(!is.na(OD720_Gmu_se), OD720_Gmu_se, 0),
-          OD720_GLag = if_else(!is.na(OD720_GLag), OD720_GLag, 0),
-          OD720_GLag_se = if_else(!is.na(OD720_GLag_se), OD720_GLag_se, 0),
-          OD720_Gmax = if_else(!is.na(OD720_Gmax), OD720_Gmax, 0),
-          OD720_Gmax_se = if_else(!is.na(OD720_Gmax_se), OD720_Gmax_se, 0),
-          GrowthAmpOD720Flag = if_else(GrowthAmpOD720 >= OD720GrowthAmpFlagValue, 1, 0),
-          GrowthAmpOD720Flag_14days = if_else(GrowthAmpOD720_14days >= OD720GrowthAmpFlagValue, 1, 0),
-          OD720_Gmu_corr = if_else(GrowthAmpOD720Flag_14days == 1 & OD720_Gmu_corr >= 0, OD720_Gmu_corr, 0),
-          # OD720_GseGrowthFlag = case_when(OD720_Gmu_corr > 0 & OD720_Gmu_corr * GrowthFlagError > OD720_Gmu_se ~ 1,
-          #                                   OD720_Gmu_corr > 0 & OD720_Gmu_corr * GrowthFlagError < OD720_Gmu_se ~ 0,
-          #                                   OD720_Gmu_corr == 0 ~ 1),
+# OD720 logistic fits
+# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change defined in project variables chunk.
 
-           OD720_GseGrowthFlag = if_else(OD720_Gmu_se < OD720_Gmu_corr * GrowthFlagError, 1, 0),
-   )
-
-# deltaOD gompertz fits
-# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007.Defined at line 75 
-lognormdeltaOD_unnest <- LogFitsData %>% 
-select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720, GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, lognormdeltaOD_Gompertz_tidied, lognormdeltaOD_Gompertz_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
-       ) %>%
-unnest(cols = c(lognormdeltaOD_Gompertz_tidied), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_wider(names_from =  lognormdeltaOD_Gompertz_tidied_term, values_from = c(lognormdeltaOD_Gompertz_tidied_estimate, lognormdeltaOD_Gompertz_tidied_std.error, lognormdeltaOD_Gompertz_tidied_statistic, lognormdeltaOD_Gompertz_tidied_p.value), names_sep = "_")  %>%
-  rename(deltaOD_Gmax = lognormdeltaOD_Gompertz_tidied_estimate_Gmax,
-         deltaOD_Gmax_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmax,
-         deltaOD_Gmu_raw = lognormdeltaOD_Gompertz_tidied_estimate_Gmu,
-         deltaOD_Gmu_se = lognormdeltaOD_Gompertz_tidied_std.error_Gmu,
-         deltaOD_GLag = lognormdeltaOD_Gompertz_tidied_estimate_GLag,
-         deltaOD_GLag_se = lognormdeltaOD_Gompertz_tidied_std.error_GLag) %>%
-   mutate(deltaOD_Gmu_corr = if_else(!is.na(deltaOD_Gmu_raw), deltaOD_Gmu_raw, 0),
-          deltaOD_Gmu_se = if_else(!is.na(deltaOD_Gmu_se), deltaOD_Gmu_se, 0),
-          deltaOD_GLag = if_else(!is.na(deltaOD_GLag), deltaOD_GLag, 0),
-          deltaOD_GLag_se = if_else(!is.na(deltaOD_GLag_se), deltaOD_GLag_se, 0),
-          deltaOD_Gmax = if_else(!is.na(deltaOD_Gmax), deltaOD_Gmax, 0),
-          deltaOD_Gmax_se = if_else(!is.na(deltaOD_Gmax_se), deltaOD_Gmax_se, 0),
-          GrowthAmpdeltaODFlag = if_else(GrowthAmpdeltaOD >= deltaODGrowthAmpFlagValue , 1, 0),
-          GrowthAmpdeltaODFlag_14days = if_else(GrowthAmpdeltaOD_14days >= deltaODGrowthAmpFlagValue, 1, 0),
-          deltaOD_Gmu_corr = if_else(GrowthAmpdeltaODFlag_14days == 1 & deltaOD_Gmu_corr >= 0, deltaOD_Gmu_corr, 0),
-          # deltaOD_GseGrowthFlag = case_when(deltaOD_Gmu_corr > 0 & deltaOD_Gmu_corr * GrowthFlagError > deltaOD_Gmu_se ~ 1,
-          #                                   deltaOD_Gmu_corr > 0 & deltaOD_Gmu_corr * GrowthFlagError < deltaOD_Gmu_se ~ 0,
-          #                                   deltaOD_Gmu_corr == 0 ~ 1),
-
-         deltaOD_GseGrowthFlag = if_else(deltaOD_Gmu_se < deltaOD_Gmu_corr * GrowthFlagError, 1, 0),
-          )
-
-# OD720 logistic fits
-# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007.Defined at line 75 
 OD720_unnest <- LogFitsData %>%
-  select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720, GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, OD720_logistic_tidied, OD720_logistic_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
+  select(c(Filename, Tube, ExpDate, MC, PrimaryOperator, Run,  SampleID, Strain, ExpCul, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Optode, OptodeCh, OptodeMeasure, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, minRollMeanOD720, maxRollMeanOD720, minRollMeandeltaOD, maxRollMeandeltaOD,  GrowthAmpOD720_14days,  GrowthAmpdeltaOD_14days, OD720_logistic_tidied, OD720_logistic_predict, O2_Category)
          ) %>%
@@
           OD720_Lmax_se = if_else(!is.na(OD720_Lmax_se), OD720_Lmax_se, 0),
-          GrowthAmpOD720Flag = if_else(GrowthAmpOD720 >= OD720GrowthAmpFlagValue, 1, 0),
           GrowthAmpOD720Flag_14days = if_else(GrowthAmpOD720_14days >= OD720GrowthAmpFlagValue, 1, 0),
           OD720_Lmu_corr = if_else(GrowthAmpOD720Flag_14days == 1 & OD720_Lmu_corr >= 0 , OD720_Lmu_corr, 0),
-          # OD720_LseGrowthFlag = case_when(OD720_Lmu_corr > 0 & OD720_Lmu_corr * GrowthFlagError > OD720_Lmu_se ~ 1,
-          #                                   OD720_Lmu_corr > 0 & OD720_Lmu_corr * GrowthFlagError < OD720_Lmu_se ~ 0,
-          #                                   OD720_Lmu_corr == 0 ~ 1),
-          OD720_LseGrowthFlag = if_else(OD720_Lmu_se < OD720_Lmu_corr * GrowthFlagError, 1, 0),
-          OD720_TimeHalfPmax_h = (log(2-(OD720_Lintercept/(OD720_Lmax - OD720_Lintercept))))/OD720_Lmu_corr,
-          OD720_TimeHalfPmax_h = if_else(!is.infinite(OD720_TimeHalfPmax_h), OD720_TimeHalfPmax_h, 0),
-          OD720_TimeHalfPmax_h = if_else(!is.nan(OD720_TimeHalfPmax_h), OD720_TimeHalfPmax_h, 0)
+          OD720_LseGrowthFlag = if_else(OD720_Lmu_se < OD720_Lmu_corr * GrowthFlagError, 1, 0)
           )
@@
 # deltaOD logistic fits
-# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007 and less than 14 days.Defined at line 75 
+# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change defined in project variables chunk.
+
 deltaOD_unnest <- LogFitsData %>%
-   select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720,  GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, deltaOD_logistic_tidied, deltaOD_logistic_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
+   select(c(Filename,  Tube, ExpDate, MC, PrimaryOperator, Run,  SampleID, Strain, ExpCul, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape,  Optode, OptodeCh, OptodeMeasure,  ExpEndDate, ExpEndHour, SetActinic_day, tubedata, minRollMeanOD720, maxRollMeanOD720, minRollMeandeltaOD, maxRollMeandeltaOD, GrowthAmpOD720_14days,  GrowthAmpdeltaOD_14days, deltaOD_logistic_tidied, deltaOD_logistic_predict, O2_Category)
           ) %>%
@@
           deltaOD_Lmax_se = if_else(!is.na(deltaOD_Lmax_se), deltaOD_Lmax_se, 0),
-          GrowthAmpdeltaODFlag = if_else(GrowthAmpdeltaOD >= deltaODGrowthAmpFlagValue , 1, 0),
           GrowthAmpdeltaODFlag_14days = if_else(GrowthAmpdeltaOD_14days >= deltaODGrowthAmpFlagValue, 1, 0),
           deltaOD_Lmu_corr = if_else(GrowthAmpdeltaODFlag_14days == 1 & deltaOD_Lmu_corr >= 0, deltaOD_Lmu_corr, 0),
-          # deltaOD_LseGrowthFlag = case_when(deltaOD_Lmu_corr > 0 & deltaOD_Lmu_corr * GrowthFlagError > deltaOD_Lmu_se ~ 1,
-                                            # deltaOD_Lmu_corr > 0 & deltaOD_Lmu_corr * GrowthFlagError < deltaOD_Lmu_se ~ 0,
-                                            # deltaOD_Lmu_corr == 0 ~ 1),
-         deltaOD_LseGrowthFlag = if_else(deltaOD_Lmu_se < deltaOD_Lmu_corr * GrowthFlagError, 1, 0),
-          deltaOD_TimeHalfPmax_h = (log(2-(deltaOD_Lintercept/(deltaOD_Lmax - deltaOD_Lintercept))))/deltaOD_Lmu_corr,
-          deltaOD_TimeHalfPmax_h = if_else(!is.infinite(deltaOD_TimeHalfPmax_h), deltaOD_TimeHalfPmax_h, 0),
-          deltaOD_TimeHalfPmax_h = if_else(!is.nan(deltaOD_TimeHalfPmax_h), deltaOD_TimeHalfPmax_h, 0)
+         deltaOD_LseGrowthFlag = if_else(deltaOD_Lmu_se < deltaOD_Lmu_corr * GrowthFlagError, 1, 0)
           )
@@
 # OD720 truncated logistic fits
-# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007.Defined at line 75 
+# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change defined in project variables chunk.
+
 OD720truncLog_unnest <- LogFitsData %>%
-   select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720, GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, OD720trunc_logistic_tidied, OD720trunc_logistic_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
+   select(c(Filename, Tube, ExpDate, MC, PrimaryOperator, Run,  SampleID, Strain, ExpCul, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape,  Optode, OptodeCh, OptodeMeasure,  ExpEndDate, ExpEndHour, SetActinic_day, tubedata, minRollMeanOD720, maxRollMeanOD720, minRollMeandeltaOD, maxRollMeandeltaOD, GrowthAmpOD720_14days,  GrowthAmpdeltaOD_14days,OD720trunc_logistic_tidied, OD720trunc_logistic_predict, O2_Category)
           ) %>%
@@
           OD720trunc_Lmax_se = if_else(!is.na(OD720trunc_Lmax_se), OD720trunc_Lmax_se, 0),
-          GrowthAmpOD720Flag = if_else(GrowthAmpOD720 >= OD720GrowthAmpFlagValue, 1, 0),
           GrowthAmpOD720Flag_14days = if_else(GrowthAmpOD720_14days >= OD720GrowthAmpFlagValue, 1, 0),
           OD720trunc_Lmu_corr = if_else(GrowthAmpOD720Flag_14days == 1 & OD720trunc_Lmu_corr >= 0 , OD720trunc_Lmu_corr, 0),
-          # OD720trunc_LseGrowthFlag = case_when(OD720trunc_Lmu_corr > 0 & OD720trunc_Lmu_corr * GrowthFlagError > OD720trunc_Lmu_se ~ 1,
-          #                                   OD720trunc_Lmu_corr > 0 & OD720trunc_Lmu_corr * GrowthFlagError < OD720trunc_Lmu_se ~ 0,
-          #                                   OD720trunc_Lmu_corr == 0 ~ 1),
-
-           OD720trunc_LseGrowthFlag = if_else(OD720trunc_Lmu_se < OD720trunc_Lmu_corr * GrowthFlagError, 1, 0),
-          OD720trunc_TimeHalfPmax_h = (log(2-(OD720trunc_Lintercept/(OD720trunc_Lmax - OD720trunc_Lintercept))))/OD720trunc_Lmu_corr,
-          OD720trunc_TimeHalfPmax_h = if_else(!is.infinite(OD720trunc_TimeHalfPmax_h), OD720trunc_TimeHalfPmax_h, 0),
-          OD720trunc_TimeHalfPmax_h = if_else(!is.nan(OD720trunc_TimeHalfPmax_h), OD720trunc_TimeHalfPmax_h, 0)
+          OD720trunc_LseGrowthFlag = if_else(OD720trunc_Lmu_se < OD720trunc_Lmu_corr * GrowthFlagError, 1, 0)
           )
@@
 # deltaOD truncated logistic fits
-# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007.Defined at line 75 
+# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change defined in project variables chunk.
+
 deltaODtruncLog_unnest <- LogFitsData %>%
-   select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720, GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, deltaODtrunc_logistic_tidied, deltaODtrunc_logistic_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
+   select(c(Filename, Tube, ExpDate, MC, PrimaryOperator, Run,  SampleID, Strain, ExpCul, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape,  Optode, OptodeCh, OptodeMeasure,  ExpEndDate, ExpEndHour, SetActinic_day, tubedata, minRollMeanOD720, maxRollMeanOD720, minRollMeandeltaOD, maxRollMeandeltaOD, GrowthAmpOD720_14days,  GrowthAmpdeltaOD_14days, deltaODtrunc_logistic_tidied, deltaODtrunc_logistic_predict, O2_Category)
           ) %>%
@@
           deltaODtrunc_Lmax_se = if_else(!is.na(deltaODtrunc_Lmax_se), deltaODtrunc_Lmax_se, 0),
-          GrowthAmpdeltaODFlag = if_else(GrowthAmpdeltaOD >= deltaODGrowthAmpFlagValue , 1, 0),
           GrowthAmpdeltaODFlag_14days = if_else(GrowthAmpdeltaOD_14days >= deltaODGrowthAmpFlagValue, 1, 0),
           deltaODtrunc_Lmu_corr = if_else(GrowthAmpdeltaODFlag_14days == 1 & deltaODtrunc_Lmu_corr >= 0, deltaODtrunc_Lmu_corr, 0),
-          # deltaODtrunc_LseGrowthFlag = case_when(deltaODtrunc_Lmu_corr > 0 & deltaODtrunc_Lmu_corr * GrowthFlagError > deltaODtrunc_Lmu_se ~ 1,
-          #                                   deltaODtrunc_Lmu_corr > 0 & deltaODtrunc_Lmu_corr * GrowthFlagError < deltaODtrunc_Lmu_se ~ 0,
-          #                                   deltaODtrunc_Lmu_corr == 0 ~ 1),
-
-          deltaODtrunc_LseGrowthFlag = if_else(deltaODtrunc_Lmu_se < deltaODtrunc_Lmu_corr * GrowthFlagError, 1, 0),
-          deltaODtrunc_TimeHalfPmax_h = (log(2-(deltaODtrunc_Lintercept/(deltaODtrunc_Lmax - deltaODtrunc_Lintercept))))/deltaODtrunc_Lmu_corr,
-          deltaODtrunc_TimeHalfPmax_h = if_else(!is.infinite(deltaODtrunc_TimeHalfPmax_h), deltaODtrunc_TimeHalfPmax_h, 0),
-          deltaODtrunc_TimeHalfPmax_h = if_else(!is.nan(deltaODtrunc_TimeHalfPmax_h), deltaODtrunc_TimeHalfPmax_h, 0)
+          deltaODtrunc_LseGrowthFlag = if_else(deltaODtrunc_Lmu_se < deltaODtrunc_Lmu_corr * GrowthFlagError, 1, 0)
           )
-
-# OD720 truncated exponential fits
-# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007.Defined at line 75 
-OD720truncExp_unnest <- LogFitsData %>%
-   select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720, GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, OD720trunc_exp_tidied, OD720trunc_exp_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
-          ) %>%
-  unnest(cols = c(OD720trunc_exp_tidied), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_wider(names_from =  OD720trunc_exp_tidied_term, values_from = c(OD720trunc_exp_tidied_estimate, OD720trunc_exp_tidied_std.error, OD720trunc_exp_tidied_statistic, OD720trunc_exp_tidied_p.value), names_sep = "_") %>%
-  rename(OD720trunc_Emu_raw = OD720trunc_exp_tidied_estimate_Emu,
-         OD720trunc_Emu_se = OD720trunc_exp_tidied_std.error_Emu,
-         OD720trunc_Eintercept = OD720trunc_exp_tidied_estimate_Eintercept,             
-         OD720trunc_Eintercept_se = OD720trunc_exp_tidied_std.error_Eintercept)  %>%
-   mutate(OD720trunc_Emu_corr = if_else(!is.na(OD720trunc_Emu_raw), OD720trunc_Emu_raw, 0),
-          OD720trunc_Emu_se = if_else(!is.na(OD720trunc_Emu_se), OD720trunc_Emu_se, 0),
-          OD720trunc_Eintercept = if_else(!is.na(OD720trunc_Eintercept), OD720trunc_Eintercept, 0),
-          OD720trunc_Eintercept_se = if_else(!is.na(OD720trunc_Eintercept_se), OD720trunc_Eintercept_se, 0),
-          GrowthAmpOD720Flag = if_else(GrowthAmpOD720 >= OD720GrowthAmpFlagValue, 1, 0),
-          GrowthAmpOD720Flag_14days = if_else(GrowthAmpOD720_14days >= OD720GrowthAmpFlagValue, 1, 0),
-          OD720trunc_Emu_corr = if_else(GrowthAmpOD720Flag_14days == 1 & OD720trunc_Emu_corr >= 0 , OD720trunc_Emu_corr, 0),
-          # OD720trunc_EseGrowthFlag = case_when(OD720trunc_Emu_corr > 0 & OD720trunc_Emu_corr * GrowthFlagError > OD720trunc_Emu_se ~ 1,
-          #                                   OD720trunc_Emu_corr > 0 & OD720trunc_Emu_corr * GrowthFlagError < OD720trunc_Emu_se ~ 0,
-          #                                   OD720trunc_Emu_corr == 0 ~ 1)
-         OD720trunc_EseGrowthFlag = if_else(OD720trunc_Emu_se < OD720trunc_Emu_corr * GrowthFlagError, 1, 0),
-          )
-
-# deltaOD truncated exponential fits
-# assign 0 to growth fits that are NA's and for tubes with absolute amplitude change of less than 0.007.Defined at line 75 
-deltaODtruncExp_unnest <- LogFitsData %>%
-   select(c(Filename, CDateTime, Tube, ExpDate, MC, PrimaryOperator, Run, Description, ProjectID, ID, Strain, Inoc_mL, Media_mL, ExpCul, InnocDate, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Media, Source, Optode, OptodeCh, FinalpH, Par_ueAdjusted, DateOfAdjustment, ElaspedHoursAtAdjustment, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormdeltaOD_TimetoMax, OD720trunc_TimetoMax, deltaODtrunc_TimetoMax, IsdeltaOD_GLagNeg, lognormOD720_GompLag, lognormdeltaOD_GompLag, GrowthAmpOD720, GrowthAmpOD720_14days, GrowthAmpdeltaOD, GrowthAmpdeltaOD_14days, deltaODtrunc_exp_tidied, deltaODtrunc_exp_predict, DoubledeltaODFlag_14days, DoubleOD720Flag_14days, O2_Category)
-          ) %>%
-unnest(cols = c(deltaODtrunc_exp_tidied), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_wider(names_from =  deltaODtrunc_exp_tidied_term, values_from = c(deltaODtrunc_exp_tidied_estimate, deltaODtrunc_exp_tidied_std.error, deltaODtrunc_exp_tidied_statistic, deltaODtrunc_exp_tidied_p.value), names_sep = "_")  %>%
-  rename(deltaODtrunc_Emu_raw = deltaODtrunc_exp_tidied_estimate_Emu,
-         deltaODtrunc_Emu_se = deltaODtrunc_exp_tidied_std.error_Emu,
-         deltaODtrunc_Eintercept = deltaODtrunc_exp_tidied_estimate_Eintercept,
-         deltaODtrunc_Eintercept_se = deltaODtrunc_exp_tidied_std.error_Eintercept) %>%
-   mutate(deltaODtrunc_Emu_corr = if_else(!is.na(deltaODtrunc_Emu_raw), deltaODtrunc_Emu_raw, 0),
-          deltaODtrunc_Emu_se = if_else(!is.na(deltaODtrunc_Emu_se), deltaODtrunc_Emu_se, 0),
-          deltaODtrunc_Eintercept = if_else(!is.na(deltaODtrunc_Eintercept), deltaODtrunc_Eintercept, 0),
-          deltaODtrunc_Eintercept_se = if_else(!is.na(deltaODtrunc_Eintercept_se), deltaODtrunc_Eintercept_se, 0),
-          GrowthAmpdeltaODFlag = if_else(GrowthAmpdeltaOD >= deltaODGrowthAmpFlagValue , 1, 0),
-          GrowthAmpdeltaODFlag_14days = if_else(GrowthAmpdeltaOD_14days >= deltaODGrowthAmpFlagValue, 1, 0),
-          deltaODtrunc_Emu_corr = if_else(GrowthAmpdeltaODFlag_14days == 1 & deltaODtrunc_Emu_corr >= 0, deltaODtrunc_Emu_corr, 0),
-          # deltaODtrunc_EseGrowthFlag = case_when(deltaODtrunc_Emu_corr > 0 & deltaODtrunc_Emu_corr * GrowthFlagError > deltaODtrunc_Emu_se ~ 1,
-          #                                   deltaODtrunc_Emu_corr > 0 & deltaODtrunc_Emu_corr * GrowthFlagError < deltaODtrunc_Emu_se ~ 0,
-          #                                   deltaODtrunc_Emu_corr == 0 ~ 1),
-           deltaODtrunc_EseGrowthFlag = if_else(deltaODtrunc_Emu_se < deltaODtrunc_Emu_corr * GrowthFlagError, 1, 0),
-          )
-
-glimpse(lognormdeltaOD_unnest)
 
@@
 ```{r combine unnested fits for PICO Shiny App}
-
-# OD720 gompertz fits
-lognormOD720_unnest <- lognormOD720_unnest %>%
-select(-c(lognormOD720_Gompertz_tidied_estimate_NA,
-            lognormOD720_Gompertz_tidied_p.value_NA,
-            lognormOD720_Gompertz_tidied_statistic_NA,
-            lognormOD720_Gompertz_tidied_std.error_NA,
-            lognormOD720_Gompertz_tidied_statistic_GLag,
-            lognormOD720_Gompertz_tidied_statistic_Gmax,
-            lognormOD720_Gompertz_tidied_statistic_Gmu,
-            lognormOD720_Gompertz_tidied_p.value_GLag,
-            lognormOD720_Gompertz_tidied_p.value_Gmax,
-            lognormOD720_Gompertz_tidied_p.value_Gmu)
-       )
-
-# deltaOD gompertz fits
-lognormdeltaOD_unnest <- lognormdeltaOD_unnest %>%
-  select(-c(lognormdeltaOD_Gompertz_tidied_estimate_NA,
-            lognormdeltaOD_Gompertz_tidied_p.value_NA,
-            lognormdeltaOD_Gompertz_tidied_statistic_NA,
-            lognormdeltaOD_Gompertz_tidied_std.error_NA,
-            lognormdeltaOD_Gompertz_tidied_statistic_GLag,
-            lognormdeltaOD_Gompertz_tidied_statistic_Gmax,
-            lognormdeltaOD_Gompertz_tidied_statistic_Gmu,
-            lognormdeltaOD_Gompertz_tidied_p.value_GLag,
-            lognormdeltaOD_Gompertz_tidied_p.value_Gmax,
-            lognormdeltaOD_Gompertz_tidied_p.value_Gmu)
-         )
 
@@
 
-# OD720 truncated exponential fits
-OD720truncExp_unnest <- OD720truncExp_unnest %>%
-select(-c(OD720trunc_exp_tidied_estimate_NA,
-           OD720trunc_exp_tidied_p.value_NA,
-           OD720trunc_exp_tidied_statistic_NA,
-           OD720trunc_exp_tidied_std.error_NA,
-            OD720trunc_exp_tidied_statistic_Eintercept,
-            OD720trunc_exp_tidied_statistic_Emu,
-            OD720trunc_exp_tidied_p.value_Eintercept,
-            OD720trunc_exp_tidied_p.value_Emu)
-       )
-
-# deltaOD truncated exponential fits
-deltaODtruncExp_unnest <- deltaODtruncExp_unnest %>%
-  select(-c(deltaODtrunc_exp_tidied_estimate_NA,
-            deltaODtrunc_exp_tidied_p.value_NA,
-            deltaODtrunc_exp_tidied_statistic_NA,
-            deltaODtrunc_exp_tidied_std.error_NA,
-            deltaODtrunc_exp_tidied_statistic_Eintercept,
-            deltaODtrunc_exp_tidied_statistic_Emu,
-            deltaODtrunc_exp_tidied_p.value_Eintercept,
-            deltaODtrunc_exp_tidied_p.value_Emu)
-         )
-
-glimpse(deltaOD_unnest)
-
 # Join Full Growth Rate Data
-UnnestedGompertzData <- left_join(x = lognormOD720_unnest, y = lognormdeltaOD_unnest)
 
 UnnestedLogData <- left_join(x = OD720_unnest, y = deltaOD_unnest)
-
-UnnestedFullData <- left_join(x = UnnestedLogData, y = UnnestedGompertzData)
-
-glimpse(UnnestedFullData)
 
@@
 
-UnnestedTruncExpData <- left_join(x = OD720truncExp_unnest, y =  deltaODtruncExp_unnest)
-
-UnnestedTruncData <- left_join(x = UnnestedTruncLogData, y = UnnestedTruncExpData)
-
 #combine Full and Truncated unnested data
-NestedFitsData <- left_join(x = UnnestedFullData, y = UnnestedTruncData)
-
-glimpse(NestedFitsData)
+NestedFitsData <- left_join(x = UnnestedLogData, y = UnnestedTruncLogData)
 
 #remove redundant objects
-remove(lognormOD720_unnest,
-       lognormdeltaOD_unnest,
-       OD720_unnest,
+remove(OD720_unnest,
        deltaOD_unnest,
-       UnnestedGompertzData,
        UnnestedLogData,
@@
        deltaODtruncLog_unnest,
-       OD720truncExp_unnest,
-       deltaODtruncExp_unnest,
        UnnestedTruncLogData,
-       UnnestedTruncExpData,
-       UnnestedTruncData,
        UnnestedFullData
@@
 ```{r}
+
 NestedFitsData <- NestedFitsData %>% 
-  mutate(O2_Category = case_when(Run <= 35 & O2 == 0 ~ "Intermediate",
-                                 Run >= 36 & Run <= 91 & O2 == 0 ~ "Low",
-                                 O2 == 21 ~ "High",
-                                 Run >= 92 ~ O2_Category),
-         O2_uM = case_when(O2_Category == "Low" ~ 2.5,
+  mutate(O2_uM = case_when(O2_Category == "Low" ~ 2.5,
                             O2_Category == "Intermediate" ~ 25,
@@
 ```{r}
-AllNestedFitsData <- NestedFitsData %>% 
+NestedFitsData <- NestedFitsData %>% 
   mutate(RateActinic_h = case_when(LightShape == "Sine"  ~ Par_ue/(Photoperiod/2)))
 
-glimpse(AllNestedFitsData)
-
-```
-
-```{r remove trunc and gompertz from nested DF}
-
-# remove gompertz and truncated growth data
-NestedFitsData <- NestedFitsData %>% 
-  select(-contains(c("trunc", "Gompertz", "Gomp", "OD720_G", "deltaOD_G")))
-
-# need the deltaOD trunc growth rate for future comparisons
-onlydeltaODtrunc<- AllNestedFitsData %>% 
-  select((c("ID", "deltaODtrunc_Lmu_corr")))
-
-# add deltaOD truncated growth rates to DF
-NestedFitsData <- full_join(NestedFitsData, onlydeltaODtrunc)
-
 glimpse(NestedFitsData)
-
-remove(onlydeltaODtrunc)
 
@@
 # OD720 pivot longer Gmax, Gmu, Glag, Lmu, Lmax and Lintercept estimates
-Pivot_Longer_OD720_est <- AllNestedFitsData %>%
-  select(c(Filename, Tube, ID, Run, PrimaryOperator, Strain, Par_ue,RateActinic_h, Photoperiod, SetActinic_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormOD720_GompLag ,GrowthAmpOD720, GrowthAmpOD720Flag, GrowthAmpOD720_14days, GrowthAmpOD720Flag_14days, DoubleOD720Flag_14days, OD720_GseGrowthFlag, OD720_LseGrowthFlag, OD720trunc_LseGrowthFlag, OD720_Gmu_corr, OD720_Gmax, OD720_GLag, OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720trunc_Lmu_corr, OD720trunc_Lmax, OD720trunc_Lintercept
+Pivot_Longer_OD720_est <- NestedFitsData %>%
+  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue,RateActinic_h, Photoperiod, SetActinic_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape,  GrowthAmpOD720_14days, GrowthAmpOD720Flag_14days,  OD720_LseGrowthFlag, OD720trunc_LseGrowthFlag,  OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720trunc_Lmu_corr, OD720trunc_Lmax, OD720trunc_Lintercept
             )) %>%
-   pivot_longer(c(OD720_Gmu_corr, OD720_Gmax, OD720_GLag, OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720trunc_Lmu_corr, OD720trunc_Lmax, OD720trunc_Lintercept), names_to = c("Wavelength", "term"), values_to = c("estimate"), names_sep = '\\_')
+   pivot_longer(c(OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720trunc_Lmu_corr, OD720trunc_Lmax, OD720trunc_Lintercept), names_to = c("Wavelength", "term"), values_to = c("estimate"), names_sep = '\\_')
 
 # OD720 pivot longer Gmax, Gmu, Glag , Lmu, Lmax and Lintercept standard error
-Pivot_Longer_OD720_se <- AllNestedFitsData %>%
-  select(c(Filename, Tube, ID, Run, PrimaryOperator, Strain, Par_ue, RateActinic_h, Photoperiod, SetActinic_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape, IsOD720_GLagNeg, lognormOD720_TimetoMax, lognormOD720_GompLag ,GrowthAmpOD720, GrowthAmpOD720Flag, GrowthAmpOD720_14days, GrowthAmpOD720Flag_14days, DoubleOD720Flag_14days, OD720_GseGrowthFlag, OD720_LseGrowthFlag, OD720trunc_LseGrowthFlag,  OD720_Gmu_se, OD720_Gmax_se, OD720_GLag_se, OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se,OD720trunc_Lmu_se, OD720trunc_Lmax_se, OD720trunc_Lintercept_se
+Pivot_Longer_OD720_se <- NestedFitsData %>%
+  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue, RateActinic_h, Photoperiod, SetActinic_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape, GrowthAmpOD720_14days, GrowthAmpOD720Flag_14days,  OD720_LseGrowthFlag, OD720trunc_LseGrowthFlag,   OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se,OD720trunc_Lmu_se, OD720trunc_Lmax_se, OD720trunc_Lintercept_se
             )) %>%
-   pivot_longer(c(OD720_Gmu_se, OD720_Gmax_se, OD720_GLag_se, OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se, OD720trunc_Lmu_se, OD720trunc_Lmax_se, OD720trunc_Lintercept_se), names_to = c("Wavelength", "term"), values_to = c("se"), names_sep = '\\_')
+   pivot_longer(c(OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se, OD720trunc_Lmu_se, OD720trunc_Lmax_se, OD720trunc_Lintercept_se), names_to = c("Wavelength", "term"), values_to = c("se"), names_sep = '\\_')
 
@@
 Longer_OD720_Joined <- Longer_OD720_Joined %>%
-  rename(Is_GLagNeg = 'IsOD720_GLagNeg',
-         lognorm_TimetoMax = 'lognormOD720_TimetoMax',
-         lognorm_GompLag = 'lognormOD720_GompLag',
-         GrowthAmp = 'GrowthAmpOD720',
-         GrowthAmpFlag = 'GrowthAmpOD720Flag',
-         GrowthAmp_14days = 'GrowthAmpOD720_14days',
+  rename(GrowthAmp_14days = 'GrowthAmpOD720_14days',
          GrowthAmp_14daysFlag = 'GrowthAmpOD720Flag_14days',
-         Doubled_14daysFlag = 'DoubleOD720Flag_14days',
-         Gmu_seFlag = 'OD720_GseGrowthFlag',
          Lmu_seFlag = 'OD720_LseGrowthFlag',
@@
 # deltaOD pivot longer Gmax, Gmu, Glag, Lmu, Lmax and Lintercept estimates
-Pivot_Longer_deltaOD_est <- AllNestedFitsData %>%
-  select(c(Filename, Tube, ID, Run, PrimaryOperator, Strain, Par_ue, RateActinic_h, Photoperiod, SetActinic_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape, IsdeltaOD_GLagNeg, lognormdeltaOD_TimetoMax, lognormdeltaOD_GompLag ,GrowthAmpdeltaOD, GrowthAmpdeltaODFlag, GrowthAmpdeltaOD_14days, GrowthAmpdeltaODFlag_14days, DoubledeltaODFlag_14days, deltaOD_GseGrowthFlag, deltaOD_LseGrowthFlag, deltaODtrunc_LseGrowthFlag,  deltaOD_Gmu_corr, deltaOD_Gmax, deltaOD_GLag, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept, deltaODtrunc_Lmu_corr, deltaODtrunc_Lmax, deltaODtrunc_Lintercept
+Pivot_Longer_deltaOD_est <- NestedFitsData %>%
+  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue, RateActinic_h, Photoperiod, SetActinic_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape,  GrowthAmpdeltaOD_14days, GrowthAmpdeltaODFlag_14days,  deltaOD_LseGrowthFlag, deltaODtrunc_LseGrowthFlag,  deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept, deltaODtrunc_Lmu_corr, deltaODtrunc_Lmax, deltaODtrunc_Lintercept
             )) %>%
-   pivot_longer(c(deltaOD_Gmu_corr, deltaOD_Gmax, deltaOD_GLag, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept, deltaODtrunc_Lmu_corr, deltaODtrunc_Lmax, deltaODtrunc_Lintercept), names_to = c("Wavelength", "term"), values_to = c("estimate"), names_sep = '\\_')
+   pivot_longer(c( deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept, deltaODtrunc_Lmu_corr, deltaODtrunc_Lmax, deltaODtrunc_Lintercept), names_to = c("Wavelength", "term"), values_to = c("estimate"), names_sep = '\\_')
 
 # deltaOD pivot longer Gmax, Gmu, Glag , Lmu, Lmax and Lintercept standard error
-Pivot_Longer_deltaOD_se <- AllNestedFitsData %>%
-  select(c(Filename, Tube, ID, Run, PrimaryOperator, Strain, Par_ue, RateActinic_h, Photoperiod, SetActinic_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape, IsdeltaOD_GLagNeg, lognormdeltaOD_TimetoMax, lognormdeltaOD_GompLag ,GrowthAmpdeltaOD, GrowthAmpdeltaODFlag, GrowthAmpdeltaOD_14days, GrowthAmpdeltaODFlag_14days, DoubledeltaODFlag_14days, deltaOD_GseGrowthFlag, deltaOD_LseGrowthFlag, deltaODtrunc_LseGrowthFlag, deltaOD_Gmu_se, deltaOD_Gmax_se, deltaOD_GLag_se, deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se, deltaODtrunc_Lmu_se, deltaODtrunc_Lmax_se, deltaODtrunc_Lintercept_se
+Pivot_Longer_deltaOD_se <- NestedFitsData %>%
+  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue, RateActinic_h, Photoperiod, SetActinic_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape,  GrowthAmpdeltaOD_14days, GrowthAmpdeltaODFlag_14days,  deltaOD_LseGrowthFlag, deltaODtrunc_LseGrowthFlag,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se, deltaODtrunc_Lmu_se, deltaODtrunc_Lmax_se, deltaODtrunc_Lintercept_se
             )) %>%
-   pivot_longer(c(deltaOD_Gmu_se, deltaOD_Gmax_se, deltaOD_GLag_se, deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se, deltaODtrunc_Lmu_se, deltaODtrunc_Lmax_se, deltaODtrunc_Lintercept_se), names_to = c("Wavelength", "term"), values_to = c("se"), names_sep = '\\_')
+   pivot_longer(c(deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se, deltaODtrunc_Lmu_se, deltaODtrunc_Lmax_se, deltaODtrunc_Lintercept_se), names_to = c("Wavelength", "term"), values_to = c("se"), names_sep = '\\_')
 
@@
 Longer_deltaOD_Joined <- Longer_deltaOD_Joined %>%
-  rename(Is_GLagNeg = 'IsdeltaOD_GLagNeg',
-         lognorm_TimetoMax = 'lognormdeltaOD_TimetoMax',
-         lognorm_GompLag = 'lognormdeltaOD_GompLag',
-         GrowthAmp = 'GrowthAmpdeltaOD',
-         GrowthAmpFlag = 'GrowthAmpdeltaODFlag',
-         GrowthAmp_14days = 'GrowthAmpdeltaOD_14days',
+  rename(GrowthAmp_14days = 'GrowthAmpdeltaOD_14days',
          GrowthAmp_14daysFlag = 'GrowthAmpdeltaODFlag_14days',
-         Doubled_14daysFlag = 'DoubledeltaODFlag_14days',
-         Gmu_seFlag = 'deltaOD_GseGrowthFlag',
          Lmu_seFlag = 'deltaOD_LseGrowthFlag',
@@
 Save Long DF for GAM and Nested for further analysis 
-```{r save files for GAM and Shiny App}
+```{r save files}
 
-saveRDS(object = LongerFitsData, file = file.path(DataOut, paste(Project, "MiSa_LongerFitsData.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = TRUE, refhook = NULL)
+saveRDS(object = LongerFitsData, file = file.path(DataOut, paste(Project, "LongerFitsData.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
 
-# write_csv(LongerFitsData, file = file.path(DataOut, paste(Project, "MiSa_LongerFitsData",".csv",sep = "_"),fsep = .Platform$file.sep))
-
-saveRDS(object = NestedFitsData, file = file.path(DataOut, paste(Project, "MiSa_NestedFitsData.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = TRUE, refhook = NULL)
-
-saveRDS(NestedFitsData, file = file.path(ShinyPath, paste(Project, "MiSa_GrowthLogs", ".Rds",sep = "_"),fsep = .Platform$file.sep))
+saveRDS(object = NestedFitsData, file = file.path(DataOut, paste(Project, "NestedFitsData.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = TRUE, refhook = NULL)
 
@@
 
+Plot All
 ```{r LogisticdeltaODPlots, fig.height= 10, fig.width= 10}
 
-SS120deltaODLmuMatrixPlot <- NestedFitsData %>%
+NestedFitsData %>%
    filter(Strain == "SS120") %>%
@@
 
-SS120deltaODLmuMatrixPlot
-
 NestedFitsData %>%
-   filter(Strain == "SS120",
-          deltaOD_LseGrowthFlag == 1) %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.5) +
- geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
-   labs(subtitle = "Strain, [Oxygen],Photoperiod, Actinic PAR (nm) - Outliers filtered by standard error > 20% of growth rate", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
- geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
-  geom_errorbar(aes(x = Par_ue, ymin = (deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
-  coord_cartesian(xlim = c (0, 200)) +
-  #   scale_y_continuous(breaks=seq(-0.03, 0.07, by = 0.01)) +
-  # coord_cartesian(ylim = c (-0.03, 0.07)) +
-  scale_colour_manual(values = MCMIXColours) +
-  ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
-                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")
-
- NestedFitsData %>%
-   filter(Strain == "SS120",
-          deltaOD_Lmu_corr == 0 |
-          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.5) +
- geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
-   labs(subtitle = "Strain, [Oxygen],Photoperiod, Actinic PAR (nm) - Of cultures that grew, outliers filtered by standard error > 20% of growth rate.", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
- geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
-  geom_errorbar(aes(x = Par_ue, ymin = (deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
-  coord_cartesian(xlim = c (0, 200)) +
-  #   scale_y_continuous(breaks=seq(-0.03, 0.07, by = 0.01)) +
-  # coord_cartesian(ylim = c (-0.03, 0.07)) +
-  scale_colour_manual(values = MCMIXColours) +
-  ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
-                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")
-
-MIT9313deltaODLmuMatrixPlot <- NestedFitsData %>%
    filter(Strain == "MIT9313",
@@
 
-MIT9313deltaODLmuMatrixPlot
-
  NestedFitsData %>%
-   filter(Strain == "MIT9313",
-          deltaOD_LseGrowthFlag == 1) %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.4) +
- geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
- labs(subtitle = "Strain, [Oxygen], Photoperiod, Actinic PAR (nm) - Outliers filtered by standard error > 20% of growth rate", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
- geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5,hjust = 0.5, vjust=-0.5) +
-  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
-  coord_cartesian(xlim = c (0, 200)) +
-  #   scale_y_continuous(breaks=seq(0, 0.07, by = 0.01)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours) +
-  ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
-                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")
-
- MED4deltaODLmuMatrixPlot <- NestedFitsData %>%
    filter(Strain == "MED4",
@@
 
-MED4deltaODLmuMatrixPlot
-
  NestedFitsData %>%
-   filter(Strain == "MED4",
-          deltaOD_LseGrowthFlag == 1) %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.4) +
- geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
-   labs(subtitle = "Strain, [Oxygen], Photoperiod, Actinic PAR (nm) - Outliers filtered by standard error > 20% of growth rate", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
- geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5,hjust = 0.5, vjust=-0.5) +
-  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
-  coord_cartesian(xlim = c (0, 200)) +
-  #   scale_y_continuous(breaks=seq(0, 0.115, by = 0.01)) +
-  # coord_cartesian(ylim = c (0, 0.115)) +
-  scale_colour_manual(values = MCMIXColours) +
- ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
-                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")
-
-deltaOD_LmuSummaryGrowthPlot <- NestedFitsData %>%
    filter(Strain == "MIT9313" |
@@
          Strain == "MED4",
-         deltaOD_LseGrowthFlag == 1) %>%
+          deltaOD_Lmu_corr == 0 |
+          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
   ggplot() +
@@
 
-deltaOD_LmuSummaryGrowthPlot
-
-#plotly::ggplotly(deltaOD_LmuSummaryGrowthPlot)
-
- NestedFitsData %>%
-   filter(WL == "WW") %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(O2_uM)), size = 4, alpha = 0.5) +
- geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(O2_uM)), linewidth = 0.1, alpha = 0.4) +
-   labs(subtitle = "Actinic PAR (nm), Strain, Photoperiod", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
- geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
-  geom_errorbar(aes(x = Par_ue, ymin = (deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
-  coord_cartesian(xlim = c (0, 200)) +
-  #   scale_y_continuous(breaks=seq(-0.03, 0.07, by = 0.01)) +
-  # coord_cartesian(ylim = c (-0.03, 0.07)) +
-  #scale_colour_manual(values = MCMIXColours) +
-  ggh4x::facet_nested(cols = vars(WL, Strain), rows = vars(Photoperiod), 
-                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
-  theme_bw() +
-  labs(colour = "Oxygen Concentration")
-
-NestedFitsData %>%
-   filter(WL == "450") %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(O2_uM)), size = 4, alpha = 0.5) +
- geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(O2_uM)), linewidth = 0.1, alpha = 0.4) +
-   labs(subtitle = "Actinic PAR (nm), Strain, Photoperiod", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
- geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
-  geom_errorbar(aes(x = Par_ue, ymin = (deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
-  coord_cartesian(xlim = c (0, 200)) +
-  #   scale_y_continuous(breaks=seq(-0.03, 0.07, by = 0.01)) +
-  # coord_cartesian(ylim = c (-0.03, 0.07)) +
-  #scale_colour_manual(values = MCMIXColours) +
-  ggh4x::facet_nested(cols = vars(WL, Strain), rows = vars(Photoperiod), 
-                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
-  theme_bw() +
-  labs(colour = "Oxygen Concentration")
-
-NestedFitsData %>%
-   filter(WL == "660") %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(O2_uM)), size = 4, alpha = 0.5) +
- geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(O2_uM)), linewidth = 0.1, alpha = 0.4) +
-   labs(subtitle = "Actinic PAR (nm), Strain, Photoperiod", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
- geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
-  geom_errorbar(aes(x = Par_ue, ymin = (deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
-  coord_cartesian(xlim = c (0, 200)) +
-  #   scale_y_continuous(breaks=seq(-0.03, 0.07, by = 0.01)) +
-  # coord_cartesian(ylim = c (-0.03, 0.07)) +
-  #scale_colour_manual(values = MCMIXColours) +
-  ggh4x::facet_nested(cols = vars(WL, Strain), rows = vars(Photoperiod), 
-                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
-  theme_bw() +
-  labs(colour = "Oxygen Concentration")
-
 ```
-
-```{r save summary growth plots}
-
-# ggsave(file = file.path(PlotsPath, paste("MIT9313deltaODLmuMatrixPlot",".png",sep = "")), plot = MIT9313deltaODLmuMatrixPlot, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)
-# 
-# ggsave(file = file.path(PlotsPath, paste("SS120deltaODLmuMatrixPlot",".png",sep = "")), plot = SS120deltaODLmuMatrixPlot, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)
-# 
-# ggsave(file = file.path(PlotsPath, paste("MED4deltaODLmuMatrixPlot",".png",sep = "")), plot = MED4deltaODLmuMatrixPlot, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-```
-
-Compare truncated runs
-```{r CompareTruncated, fig.height= 15, fig.width= 15}
-
- NestedFitsData %>%
-  filter(Strain == "MIT9313" |
-         Strain == "SS120" |
-         Strain == "MED4",
-           WL == 450 |
-           WL == 530 |
-           WL == 660 |
-           WL == "WW",
-          Run >= 25 & 
-           Run < 80, ) %>%
-  ggplot(aes(x = OD720_Lmu_corr, y = OD720trunc_Lmu_corr, colour = WL)) +
-  theme(panel.spacing.x = unit(10, "cm"), panel.spacing.y = unit(2, "cm")) +
-  geom_point(aes(labels = c(Run))) +
-  geom_errorbar(aes(xmin = OD720_Lmu_corr - OD720_Lmu_se, xmax = OD720_Lmu_corr + OD720_Lmu_se, ymin = OD720trunc_Lmu_corr - OD720trunc_Lmu_se, ymax = OD720trunc_Lmu_corr + OD720trunc_Lmu_se), size = 0.05, color = 'black', data = .
-%>% filter(GrowthAmpOD720Flag_14days == 1)) +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_text(aes(x = OD720_Lmu_corr, y = OD720trunc_Lmu_corr, label= Run),hjust=0, vjust=0) +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  coord_fixed(ratio = 1, xlim = c (0, 0.05), ylim = c(0, 0.05) ) +
- # coord_cartesian() +
-  scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
-  labs(subtitle = "Strain, O2, Actinic PAR (nm)  All Growth Data From Runs >= #25", y = "Corrected Truncated Logistic Growth Rate (OD720trunc_Lmu)", x = "Corrected Logistic Growth Rate (OD720_Lmu)") +
-   ggh4x::facet_nested(cols = vars(O2, WL), rows = vars(Strain), 
-                    labeller = labeller(WL = label_both, Strain = label_value, O2 = label_both)) +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")
-
-NestedFitsData %>%
-  filter(Strain == "MIT9313" |
-         Strain == "SS120" |
-         Strain == "MED4",
-           WL == 450 |
-           WL == 530 |
-           WL == 660 |
-           WL == "WW",
-          Run >= 25 & 
-           Run < 80, ) %>%
-  ggplot(aes(x = deltaOD_Lmu_corr, y = deltaODtrunc_Lmu_corr, colour = WL)) +
-  theme(panel.spacing.x = unit(10, "cm"), panel.spacing.y = unit(2, "cm")) +
-  geom_point(aes(labels = c(Run))) +
-   geom_errorbar(aes(xmin = deltaOD_Lmu_corr - deltaOD_Lmu_se, xmax = deltaOD_Lmu_corr + deltaOD_Lmu_se, ymin = deltaODtrunc_Lmu_corr - deltaODtrunc_Lmu_se, ymax = deltaODtrunc_Lmu_corr + deltaODtrunc_Lmu_se), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days == 1)) +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_text(aes(x = deltaOD_Lmu_corr, y = deltaODtrunc_Lmu_corr, label= Run),hjust=0, vjust=0) +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  coord_fixed(ratio = 1, xlim = c (0, 0.05), ylim = c(0, 0.05) ) +
- # coord_cartesian() +
-  scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
-  labs(subtitle = "Strain, O2, Actinic PAR (nm) All Growth Data From Runs >= #25", y = "Corrected Truncated Logistic Growth Rate (deltaODtrunc_Lmu)", x = "Corrected Logistic Growth Rate (deltaOD_Lmu)") +
-   ggh4x::facet_nested(cols = vars(O2, WL), rows = vars(Strain), 
-                    labeller = labeller(WL = label_both, Strain = label_value, O2 = label_both)) +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")
-
-NestedFitsData %>%
-  filter(Strain == "MIT9313" |
-         Strain == "SS120" |
-         Strain == "MED4",
-           WL == 450 |
-           WL == 530 |
-           WL == 660 |
-           WL == "WW",
-          Run >= 25 & 
-           Run < 80, 
-          OD720trunc_Lmu_corr == 0 |
-          OD720trunc_Lmu_corr != 0 & OD720trunc_LseGrowthFlag == 1,
-          OD720_Lmu_corr == 0 |
-          OD720_Lmu_corr != 0 & OD720_LseGrowthFlag == 1 ) %>%
-  ggplot(aes(x = OD720_Lmu_corr, y = OD720trunc_Lmu_corr, colour = WL)) +
-  theme(panel.spacing.x = unit(10, "cm"), panel.spacing.y = unit(2, "cm")) +
-  geom_point(aes(labels = c(Run))) +
-  geom_errorbar(aes(xmin = OD720_Lmu_corr - OD720_Lmu_se, xmax = OD720_Lmu_corr + OD720_Lmu_se, ymin = OD720trunc_Lmu_corr - OD720trunc_Lmu_se, ymax = OD720trunc_Lmu_corr + OD720trunc_Lmu_se), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpOD720Flag_14days == 1)) +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_text(aes(x = OD720_Lmu_corr, y = OD720trunc_Lmu_corr, label= Run),hjust=0, vjust=0) +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  coord_fixed(ratio = 1, xlim = c (0, 0.05), ylim = c(0, 0.05) ) +
- # coord_cartesian() +
-  scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
-  labs(subtitle = "Strain, O2, Actinic PAR (nm) Standard Error Filtered Showing Runs >= #25", y = "Corrected Truncated Logistic Growth Rate  (OD720trunc_Lmu)", x = "Corrected Logistic Growth Rate (OD720_Lmu)") +
-   ggh4x::facet_nested(cols = vars(O2, WL), rows = vars(Strain), 
-                    labeller = labeller(WL = label_both, Strain = label_value, O2 = label_both)) +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")
-
-NestedFitsData %>%
-  filter(Strain == "MIT9313" |
-         Strain == "SS120" |
-         Strain == "MED4",
-           WL == 450 |
-           WL == 530 |
-           WL == 660 |
-           WL == "WW",
-          Run >= 25 & 
-           Run < 80, 
-          deltaODtrunc_Lmu_corr == 0 |
-          deltaODtrunc_Lmu_corr != 0 & deltaODtrunc_LseGrowthFlag == 1,
-          deltaOD_Lmu_corr == 0 |
-          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1 ) %>%
-  ggplot(aes(x = deltaOD_Lmu_corr, y = deltaODtrunc_Lmu_corr, colour = WL)) +
-  theme(panel.spacing.x = unit(10, "cm"), panel.spacing.y = unit(2, "cm")) +
-  geom_point(aes(labels = c(Run))) +
-  geom_errorbar(aes(xmin = deltaOD_Lmu_corr - deltaOD_Lmu_se, xmax = deltaOD_Lmu_corr + deltaOD_Lmu_se, ymin = deltaODtrunc_Lmu_corr - deltaODtrunc_Lmu_se, ymax = deltaODtrunc_Lmu_corr + deltaODtrunc_Lmu_se), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days == 1)) +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_text(aes(x = deltaOD_Lmu_corr, y = deltaODtrunc_Lmu_corr, label= Run),hjust=0, vjust=0) +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  coord_fixed(ratio = 1, xlim = c (0, 0.05), ylim = c(0, 0.05) ) +
- # coord_cartesian() +
-  scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
-  labs(subtitle = "Strain, O2, Actinic PAR (nm) Standard Error Filtered Showing Runs >= #25", y = "Corrected Truncated Logistic Growth Rate  (deltaODtrunc_Lmu)", x = "Corrected Logistic Growth Rate (deltaOD_Lmu)") +
-   ggh4x::facet_nested(cols = vars(O2, WL), rows = vars(Strain), 
-                    labeller = labeller(WL = label_both, Strain = label_value, O2 = label_both)) +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")
-
-NestedFitsData %>%
-  filter(Strain == "MIT9313" |
-         Strain == "SS120" |
-         Strain == "MED4",
-           WL == 450 |
-           WL == 530 |
-           WL == 660 |
-           WL == "WW",
-          Run >= 25 & 
-           Run < 80, ) %>%
-  ggplot(aes(x = deltaOD_Lmu_corr, y = deltaODtrunc_Lmu_corr, colour = WL)) +
-  theme(panel.spacing.x = unit(10, "cm"), panel.spacing.y = unit(2, "cm")) +
-  geom_point(aes(labels = c(Run))) +
-  geom_errorbar(aes(xmin = deltaOD_Lmu_corr - deltaOD_Lmu_se, xmax = deltaOD_Lmu_corr + deltaOD_Lmu_se, ymin = deltaODtrunc_Lmu_corr - deltaODtrunc_Lmu_se, ymax = deltaODtrunc_Lmu_corr + deltaODtrunc_Lmu_se), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days == 1)) +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_text(aes(x = deltaOD_Lmu_corr, y = deltaODtrunc_Lmu_corr, label= Run),hjust=0, vjust=0) +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  coord_fixed(ratio = 1, xlim = c (0, 0.05), ylim = c(0, 0.05) ) +
- # coord_cartesian() +
-  scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
-  labs(subtitle = "Strain, O2, Actinic PAR (nm)  All Growth Data From Runs >= #25", y = "Corrected Truncated Logistic Growth Rate  (deltaODtrunc_Lmu)", x = "Corrected Logistic Growth Rate (deltaOD_Lmu)") +
-  #facet_grid(rows = vars(Strain), cols = vars(O2, WL)) +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")
-
-NestedFitsData %>%
-  filter(Strain == "MIT9313" |
-         Strain == "SS120" |
-         Strain == "MED4",
-           WL == 450 |
-           WL == 530 |
-           WL == 660 |
-           WL == "WW",
-          Run >= 25 & 
-           Run < 80, 
-          deltaODtrunc_Lmu_corr == 0 |
-          deltaODtrunc_Lmu_corr != 0 & deltaODtrunc_LseGrowthFlag == 1,
-          deltaOD_Lmu_corr == 0 |
-          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
-  ggplot(aes(x = deltaOD_Lmu_corr, y = deltaODtrunc_Lmu_corr, colour = WL)) +
-  theme(panel.spacing.x = unit(10, "cm"), panel.spacing.y = unit(2, "cm")) +
-  geom_point(aes(labels = c(Run))) +
-  geom_errorbar(aes(xmin = deltaOD_Lmu_corr - deltaOD_Lmu_se, xmax = deltaOD_Lmu_corr + deltaOD_Lmu_se, ymin = deltaODtrunc_Lmu_corr - deltaODtrunc_Lmu_se, ymax = deltaODtrunc_Lmu_corr + deltaODtrunc_Lmu_se), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days == 1)) +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_text(aes(x = deltaOD_Lmu_corr, y = deltaODtrunc_Lmu_corr, label= Run),hjust=0, vjust=0) +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  coord_fixed(ratio = 1, xlim = c (0, 0.05), ylim = c(0, 0.05) ) +
- # coord_cartesian() +
-  scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
-  labs(subtitle = "Strain, O2, Actinic PAR (nm) Standard Error Filtered From Runs >= #25 ", y = "Corrected Truncated Logistic Growth Rate  (deltaODtrunc_Lmu)", x = "Corrected Logistic Growth Rate (deltaOD_Lmu)") +
-  #facet_grid(rows = vars(Strain), cols = vars(O2, WL)) +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")
-
-NestedFitsData %>%
-  filter(Strain == "MIT9313" |
-         Strain == "SS120" |
-         Strain == "MED4",
-           WL == 450 |
-           WL == 530 |
-           WL == 660 |
-           WL == "WW",
-          Run >= 25 & 
-           Run < 80, 
-          deltaODtrunc_Lmu_corr == 0 |
-          deltaODtrunc_Lmu_corr != 0 & deltaODtrunc_LseGrowthFlag == 1,
-          deltaOD_Lmu_corr == 0 |
-          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
-  ggplot() +
-  theme(panel.spacing.x = unit(10, "cm"), panel.spacing.y = unit(2, "cm")) +
-  geom_point(aes(x = deltaOD_TimeHalfPmax_h, y = deltaODtrunc_TimetoMax, colour = WL), size = 3) +
-  # geom_errorbar(aes(xmin = deltaOD_Lmu_corr - deltaOD_Lmu_se, xmax = deltaOD_Lmu_corr + deltaOD_Lmu_se, ymin = deltaODtrunc_Lmu_corr - deltaODtrunc_Lmu_se, ymax = deltaODtrunc_Lmu_corr + deltaODtrunc_Lmu_se), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days == 1)) +
-  scale_colour_manual(values = MCMIXColours) +
-  # geom_text(aes(x = deltaOD_Lmu_corr, y = deltaODtrunc_Lmu_corr, label= Run),hjust=0, vjust=0) +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
- coord_fixed(ratio = 1, xlim = c (0, 600), ylim = c(0, 600) ) +
- # coord_cartesian() +
-  # scale_x_continuous(breaks=seq(0, 0.05, by = 0.01)) +
-  # labs(subtitle = "Strain, O2, Actinic PAR (nm) Standard Error Filtered From Runs >= #25 ", y = "deltaOD time to half pmax (Calculate from full growth trajectory)", x = "deltaOD truncated time to pmax") +
-  #facet_grid(rows = vars(Strain), cols = vars(O2, WL)) +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")
-
-```

### 2023-12-08 Code/MultiDataGrowthAssessPico.Rmd
Removed redundant lines

@@
        deltaODtruncLog_unnest,
-       UnnestedTruncLogData,
-       UnnestedFullData
+       UnnestedTruncLogData
        )

### 2023-12-08 Code/MultiDataProcessPico.Rmd
Removed plots

@@
 Run for each file in a session; all chunks below run for each file.
-
-Moving this template to a working project folder will need editing of this file path to a relative path within the project folder.
 ```{r read ProcessFile}
-ProcessFile <- "../Data/ImportedData/ImportedMCData/20230210_PICO_MCMIX006_RUN108_TargetDataMetaFilter.Rds"
+ProcessFile <- "../Data/ImportedData/ImportedMCData/20221021_PICO_MCMIX006_RUN96_TargetDataMetaFilter.Rds"
 
@@
 
-Truncated Logistic fits vs. Logistic fits
-```{r compare trunc to full plots}
-
-ProcessDataNestGrowth %>%
-unnest(cols = c(OD720_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_wider(names_from =  OD720_logistic_tidied_term, values_from = c(OD720_logistic_tidied_estimate, OD720_logistic_tidied_std.error, OD720_logistic_tidied_statistic, OD720_logistic_tidied_p.value), names_sep = "_")  %>%
-  rename(OD720_Lmax = OD720_logistic_tidied_estimate_Lmax,
-         OD720_Lmax_se = OD720_logistic_tidied_std.error_Lmax,
-         OD720_Lmu = OD720_logistic_tidied_estimate_Lmu,
-         OD720_Lmu_se = OD720_logistic_tidied_std.error_Lmu,
-         OD720_Lintercept = OD720_logistic_tidied_estimate_Lintercept,
-         OD720_Lintercept_se = OD720_logistic_tidied_std.error_Lintercept)  %>%
-  unnest(cols = c(OD720trunc_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_wider(names_from =  OD720trunc_logistic_tidied_term, values_from = c(OD720trunc_logistic_tidied_estimate, OD720trunc_logistic_tidied_std.error, OD720trunc_logistic_tidied_statistic, OD720trunc_logistic_tidied_p.value), names_sep = "_") %>%
-  rename(OD720_Trunc_Lmax = OD720trunc_logistic_tidied_estimate_Lmax,
-         OD720_Trunc_Lmax_se = OD720trunc_logistic_tidied_std.error_Lmax,
-         OD720_Trunc_Lmu = OD720trunc_logistic_tidied_estimate_Lmu,
-         OD720_Trunc_Lmu_se = OD720trunc_logistic_tidied_std.error_Lmu)  %>%
-   ggplot() +
-  geom_point(aes(x = OD720_Lmu, y = OD720_Trunc_Lmu, colour = as.factor(WL)), size = 4)  +
-  ggrepel::geom_text_repel(aes(x = OD720_Lmu, y = OD720_Trunc_Lmu, label= Tube),hjust=0, vjust=0) +
-scale_colour_manual(values = MCMIXColours) +
-  scale_shape_manual(values = c(13, 16)) +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  coord_fixed(ratio = 1) +
-  coord_cartesian(xlim = c (0, 0.3), ylim = c(0, 0.3)) +
-  scale_x_continuous(breaks=seq(0, 0.3, by = 0.1)) +
-  labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Truncated Logistic Growth Rate (OD720_Lmu)", x = "Logistic Growth Rate (OD720_Lmu)") +
-  facet_grid(rows = vars(Strain), cols = vars(O2, WL)) + 
-  theme_bw() + 
-  labs(title = "Logistic vs. Truncated Logistic Cell Specific Growth Rates (µ" ~ h^-1~")- All Growth",
-       colour = "Actinic PAR (nm)")
-
-ProcessDataNestGrowth %>%
-unnest(cols = c(deltaOD_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_wider(names_from =  deltaOD_logistic_tidied_term, values_from = c(deltaOD_logistic_tidied_estimate, deltaOD_logistic_tidied_std.error, deltaOD_logistic_tidied_statistic, deltaOD_logistic_tidied_p.value), names_sep = "_")  %>%
-  rename(deltaOD_Lmax = deltaOD_logistic_tidied_estimate_Lmax,
-         deltaOD_Lmax_se = deltaOD_logistic_tidied_std.error_Lmax,
-         deltaOD_Lmu = deltaOD_logistic_tidied_estimate_Lmu,
-         deltaOD_Lmu_se = deltaOD_logistic_tidied_std.error_Lmu,
-         deltaOD_Lintercept = deltaOD_logistic_tidied_estimate_Lintercept,
-         deltaOD_Lintercept_se = deltaOD_logistic_tidied_std.error_Lintercept)  %>%
-  unnest(cols = c(deltaODtrunc_logistic_tidied), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_wider(names_from =  deltaODtrunc_logistic_tidied_term, values_from = c(deltaODtrunc_logistic_tidied_estimate, deltaODtrunc_logistic_tidied_std.error, deltaODtrunc_logistic_tidied_statistic, deltaODtrunc_logistic_tidied_p.value), names_sep = "_") %>%
-  rename(deltaOD_Trunc_Lmax = deltaODtrunc_logistic_tidied_estimate_Lmax,
-         deltaOD_Trunc_Lmax_se = deltaODtrunc_logistic_tidied_std.error_Lmax,
-         deltaOD_Trunc_Lmu = deltaODtrunc_logistic_tidied_estimate_Lmu,
-         deltaOD_Trunc_Lmu_se = deltaODtrunc_logistic_tidied_std.error_Lmu)  %>%
-   ggplot() +
-  geom_point(aes(x = deltaOD_Lmu, y = deltaOD_Trunc_Lmu, colour = as.factor(WL)), size = 4)  +
-  ggrepel::geom_text_repel(aes(x = deltaOD_Lmu, y = deltaOD_Trunc_Lmu, label= Tube), hjust=0, vjust=0) +
-scale_colour_manual(values = MCMIXColours) +
-  scale_shape_manual(values = c(13, 16)) +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  coord_fixed(ratio = 1) +
-  coord_cartesian(xlim = c (0, 0.1), ylim = c(0, 0.1)) +
-  scale_x_continuous(breaks=seq(0, 0.1, by = 0.02)) +
-  labs(subtitle = "Strain, O2, Actinic PAR (nm)", y = "Truncated Logistic Growth Rate (deltaOD_Lmu)", x = "Logistic Growth Rate (deltaOD_Lmu)") +
-  facet_grid(rows = vars(Strain), cols = vars(O2, WL)) + 
-  theme_bw() + 
-  labs(title = "Logistic vs. Truncated Logistic Chlorophyll Specific Growth Rates (µ" ~ h^-1~")- All Growth",
-       colour = "Actinic PAR (nm)")
-
-```
-
 Plot all Fit Terms vs. conditions- no filters

### 2023-12-08 Code/MultiDataGrowthAssessPico.Rmd
Consolidated variable names to align with PICO Baltic

@@
 OD720_unnest <- LogFitsData %>%
-  select(c(Filename, Tube, ExpDate, MC, PrimaryOperator, Run,  SampleID, Strain, ExpCul, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Optode, OptodeCh, OptodeMeasure, ExpEndDate, ExpEndHour, SetActinic_day, tubedata, minRollMeanOD720, maxRollMeanOD720, minRollMeandeltaOD, maxRollMeandeltaOD,  GrowthAmpOD720_14days,  GrowthAmpdeltaOD_14days, OD720_logistic_tidied, OD720_logistic_predict, O2_Category)
+  select(c(Filename, Tube, ExpDate, MC, PrimaryOperator, Run,  SampleID, Strain, ExpCul, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape, Optode, OptodeCh, OptodeMeasure, ExpEndDate, ExpEndHour, PARPhotonDose_day, tubedata, minRollMeanOD720, maxRollMeanOD720, minRollMeandeltaOD, maxRollMeandeltaOD,  GrowthAmpOD720_14days,  GrowthAmpdeltaOD_14days, OD720_logistic_tidied, OD720_logistic_predict, O2_Category)
          ) %>%
@@
 deltaOD_unnest <- LogFitsData %>%
-   select(c(Filename,  Tube, ExpDate, MC, PrimaryOperator, Run,  SampleID, Strain, ExpCul, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape,  Optode, OptodeCh, OptodeMeasure,  ExpEndDate, ExpEndHour, SetActinic_day, tubedata, minRollMeanOD720, maxRollMeanOD720, minRollMeandeltaOD, maxRollMeandeltaOD, GrowthAmpOD720_14days,  GrowthAmpdeltaOD_14days, deltaOD_logistic_tidied, deltaOD_logistic_predict, O2_Category)
+   select(c(Filename,  Tube, ExpDate, MC, PrimaryOperator, Run,  SampleID, Strain, ExpCul, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape,  Optode, OptodeCh, OptodeMeasure,  ExpEndDate, ExpEndHour, PARPhotonDose_day, tubedata, minRollMeanOD720, maxRollMeanOD720, minRollMeandeltaOD, maxRollMeandeltaOD, GrowthAmpOD720_14days,  GrowthAmpdeltaOD_14days, deltaOD_logistic_tidied, deltaOD_logistic_predict, O2_Category)
           ) %>%
@@
 OD720truncLog_unnest <- LogFitsData %>%
-   select(c(Filename, Tube, ExpDate, MC, PrimaryOperator, Run,  SampleID, Strain, ExpCul, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape,  Optode, OptodeCh, OptodeMeasure,  ExpEndDate, ExpEndHour, SetActinic_day, tubedata, minRollMeanOD720, maxRollMeanOD720, minRollMeandeltaOD, maxRollMeandeltaOD, GrowthAmpOD720_14days,  GrowthAmpdeltaOD_14days,OD720trunc_logistic_tidied, OD720trunc_logistic_predict, O2_Category)
+   select(c(Filename, Tube, ExpDate, MC, PrimaryOperator, Run,  SampleID, Strain, ExpCul, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape,  Optode, OptodeCh, OptodeMeasure,  ExpEndDate, ExpEndHour, PARPhotonDose_day, tubedata, minRollMeanOD720, maxRollMeanOD720, minRollMeandeltaOD, maxRollMeandeltaOD, GrowthAmpOD720_14days,  GrowthAmpdeltaOD_14days,OD720trunc_logistic_tidied, OD720trunc_logistic_predict, O2_Category)
           ) %>%
@@
 deltaODtruncLog_unnest <- LogFitsData %>%
-   select(c(Filename, Tube, ExpDate, MC, PrimaryOperator, Run,  SampleID, Strain, ExpCul, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape,  Optode, OptodeCh, OptodeMeasure,  ExpEndDate, ExpEndHour, SetActinic_day, tubedata, minRollMeanOD720, maxRollMeanOD720, minRollMeandeltaOD, maxRollMeandeltaOD, GrowthAmpOD720_14days,  GrowthAmpdeltaOD_14days, deltaODtrunc_logistic_tidied, deltaODtrunc_logistic_predict, O2_Category)
+   select(c(Filename, Tube, ExpDate, MC, PrimaryOperator, Run,  SampleID, Strain, ExpCul, ExpStartTime, Par_ue, Photoperiod, Temp_c, O2, WL, LightShape,  Optode, OptodeCh, OptodeMeasure,  ExpEndDate, ExpEndHour, PARPhotonDose_day, tubedata, minRollMeanOD720, maxRollMeanOD720, minRollMeandeltaOD, maxRollMeandeltaOD, GrowthAmpOD720_14days,  GrowthAmpdeltaOD_14days, deltaODtrunc_logistic_tidied, deltaODtrunc_logistic_predict, O2_Category)
           ) %>%
@@
 
-<!-- Chunk to calculate the rate per hour of actinic light rise to peak. -->
-```{r}
-NestedFitsData <- NestedFitsData %>% 
-  mutate(RateActinic_h = case_when(LightShape == "Sine"  ~ Par_ue/(Photoperiod/2)))
-
-glimpse(NestedFitsData)
-
-```
-
 ```{r, pivot Nested data longer for GAM}
@@
 Pivot_Longer_OD720_est <- NestedFitsData %>%
-  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue,RateActinic_h, Photoperiod, SetActinic_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape,  GrowthAmpOD720_14days, GrowthAmpOD720Flag_14days,  OD720_LseGrowthFlag, OD720trunc_LseGrowthFlag,  OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720trunc_Lmu_corr, OD720trunc_Lmax, OD720trunc_Lintercept
+  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue, Photoperiod, PARPhotonDose_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape,  GrowthAmpOD720_14days, GrowthAmpOD720Flag_14days,  OD720_LseGrowthFlag, OD720trunc_LseGrowthFlag,  OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720trunc_Lmu_corr, OD720trunc_Lmax, OD720trunc_Lintercept
             )) %>%
@@
 Pivot_Longer_OD720_se <- NestedFitsData %>%
-  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue, RateActinic_h, Photoperiod, SetActinic_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape, GrowthAmpOD720_14days, GrowthAmpOD720Flag_14days,  OD720_LseGrowthFlag, OD720trunc_LseGrowthFlag,   OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se,OD720trunc_Lmu_se, OD720trunc_Lmax_se, OD720trunc_Lintercept_se
+  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue,  Photoperiod, PARPhotonDose_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape, GrowthAmpOD720_14days, GrowthAmpOD720Flag_14days,  OD720_LseGrowthFlag, OD720trunc_LseGrowthFlag,   OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se,OD720trunc_Lmu_se, OD720trunc_Lmax_se, OD720trunc_Lintercept_se
             )) %>%
@@
 Pivot_Longer_deltaOD_est <- NestedFitsData %>%
-  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue, RateActinic_h, Photoperiod, SetActinic_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape,  GrowthAmpdeltaOD_14days, GrowthAmpdeltaODFlag_14days,  deltaOD_LseGrowthFlag, deltaODtrunc_LseGrowthFlag,  deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept, deltaODtrunc_Lmu_corr, deltaODtrunc_Lmax, deltaODtrunc_Lintercept
+  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue,  Photoperiod, PARPhotonDose_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape,  GrowthAmpdeltaOD_14days, GrowthAmpdeltaODFlag_14days,  deltaOD_LseGrowthFlag, deltaODtrunc_LseGrowthFlag,  deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept, deltaODtrunc_Lmu_corr, deltaODtrunc_Lmax, deltaODtrunc_Lintercept
             )) %>%
@@
 Pivot_Longer_deltaOD_se <- NestedFitsData %>%
-  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue, RateActinic_h, Photoperiod, SetActinic_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape,  GrowthAmpdeltaOD_14days, GrowthAmpdeltaODFlag_14days,  deltaOD_LseGrowthFlag, deltaODtrunc_LseGrowthFlag,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se, deltaODtrunc_Lmu_se, deltaODtrunc_Lmax_se, deltaODtrunc_Lintercept_se
+  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue,  Photoperiod, PARPhotonDose_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape,  GrowthAmpdeltaOD_14days, GrowthAmpdeltaODFlag_14days,  deltaOD_LseGrowthFlag, deltaODtrunc_LseGrowthFlag,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se, deltaODtrunc_Lmu_se, deltaODtrunc_Lmax_se, deltaODtrunc_Lintercept_se
             )) %>%

### 2023-12-08 Code/MultiDataImportPico.Rmd
Consolidated variable names to align with PICO Baltic

@@
 TargetDataMetaFilter <- TargetDataMetaFilter %>%
-  mutate(SetActinic_day = case_when(LightShape == 'Sine' ~ Par_ue/2 * 3600 * Photoperiod,
+  mutate(PARPhotonDose_day = case_when(LightShape == 'Sine' ~ Par_ue/2 * 3600 * Photoperiod,
                                   LightShape == 'Square' ~ Par_ue * 3600 * Photoperiod))

### 2023-12-14 Code/MultiDataImportPico.Rmd
test
test commit

@@
 Project <- "PICO"
-DataIn <- file.path("..", "Data", "RawData", "MultiCultiData.zip")
+ # DataIn <- file.path("..", "Data", "RawData", "MultiCultiData1.zip")
+DataIn <- file.path("..", "Data", "RawData", "MultiCultiData2.zip")
+
 DataOut <- file.path("..","Data", "ImportedData", "ImportedMCData")
@@
 Skip <- 20
-
 ```
@@
 
-TargetFile <- "20211223_PICO_MCMIX006_RUN42.csv"
+TargetFile <- "20231207_PICO_MCMIX004_RUN131.csv"
 

### 2023-12-14 Code/MultiDataImportPico.Rmd
Added DataIn for the 3rd folder

@@
 DataIn <- file.path("..", "Data", "RawData", "MultiCultiData2.zip")
+# DataIn <- file.path("..", "Data", "RawData", "MultiCultiData3.zip")
 
@@
 
-TargetFile <- "20231207_PICO_MCMIX004_RUN131.csv"
+TargetFile <- "20220910_PICO_MCMIX004_RUN88.csv"
 
@@
 ```{r, Add positive OD dummy points}
-
+# 
 # TargetDataMeta <- TargetDataMeta %>%
-# mutate(OD680 = if_else(Tube == 1, 0.005, OD680),
-#        OD720 = if_else(Tube == 1, 0.003, OD720))
+# mutate(OD680 = if_else(Tube == 7, 0.005, OD680),
+#        OD720 = if_else(Tube == 7, 0.003, OD720))
 
@@
 #use 'median' for 'x' and OD680 + offset for 'y'
-ExpandTube = 5
+ExpandTube = 3
 OD680_x = median(TargetDataMetaFilter$time)

### 2023-12-15 Code/MultiDataProcessPico.Rmd
Fixed annotations re:  SS120

@@
 ```{r read ProcessFile}
-ProcessFile <- "../Data/ImportedData/ImportedMCData/20221021_PICO_MCMIX006_RUN96_TargetDataMetaFilter.Rds"
+ProcessFile <- "../Data/ImportedData/ImportedMCData/20231026_PICO_MCMIX006_RUN126_TargetDataMetaFilter.Rds"
 
@@
 SS120 show anomalous jump in OD720 within first 24 h after inoculation.
-Therefore we add a filter to remove the first InitialTime  from all SS120 runs.
+Therefore we add a filter to remove the first InitialTime  from anomalous SS120 runs.
 ```{r filter initial data  ProcessData}
@@
 #          Tube == 2 |
-#          Tube == 3 & time >= 24 & time <= 125  |
+#          Tube == 3  |
 #          Tube == 4 |
@@
 #          Tube == 7 |
-#          Tube == 8 )
+#          Tube == 8 & time >= 48 & time <= 250)
 

### 2023-12-15 Code/MultiDataGrowthAssessPico.Rmd
Changed save rds. to compressed "xz" to compress

@@
 
-saveRDS(object = NestedFitsData, file = file.path(DataOut, paste(Project, "NestedFitsData.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = TRUE, refhook = NULL)
+saveRDS(object = NestedFitsData, file = file.path(DataOut, paste(Project, "NestedFitsData.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
 

### 2023-12-21 Code/Import_JazEmData.Rmd
Renamed RMDs to match Baltic_Photoperiod Git

---
title: "Import_JazEmData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Import_JazEmData.Rmd imports Jaz radiospectrometer files from Data/RawData/JazEmData.zip folder and stored in Data/ImportedData/ImportedJazEmData folder as: 
Baltic_Photoperiod_Imported_JazEmData.Rds

# Load Libraries and set Project Variables

```{r load libraries, warning = FALSE, echo=FALSE}
library(tidyverse)
library(lubridate)
library(googledrive)
```

```{r set project variables, read zipped files, list available files, warning = FALSE, echo=FALSE}
Project <- "Baltic_Photoperiod"
DataOut <- file.path("..", "Data", "ImportedData", "ImportedJazEmData")

# Set the path to the zip folder and the destination folder
zip_file <- file.path("..", "Data", "RawData", "JazEmData.zip")

# List files in the extracted folder with a ".txt" extension
Jazfile <- unzip(zip_file, list = TRUE)
Jazfile <- Jazfile[grepl(".txt$", Jazfile$Name), "Name"]
print(Jazfile)
```

# Set up fread_plus function

```{r set up fread_plus, warning = FALSE, echo=FALSE}
SkipCS <- 14
FileEncodeCS <- "UTF-8"
DelimCS <- "\t"
RollWindow <- 10

# Define function to read and process each file
fread_plus <- function(Flnm, Skip, FileEncode, Delim) {
  con <- unz(zip_file, Flnm)  # Corrected the file path within the zip archive
  data <- read.table(con, skip = Skip, encoding = FileEncode, sep = Delim, header = FALSE)

# Use tryCatch to handle errors during the closing of the connection
  tryCatch(
    close(con),
    error = function(e) {
      warning("Error closing connection: ", e$message)
    })

  data <- data %>%
    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(zip_file)$ctime)) 
  return(data)
}

# Use map_df to read and process all files in Jazfile
JazSpec <- Jazfile %>%
  map_df(~fread_plus(Flnm = ., Skip = SkipCS, FileEncode = FileEncodeCS, Delim = DelimCS))

# Rename columns
colnames(JazSpec)[1] <- "Wavelength"
colnames(JazSpec)[2] <- "Counts"
```

# Import and prepare files

```{r filename separation, warning = FALSE, echo=FALSE}
JazSpec <- JazSpec %>% 
  mutate(Filename = str_remove(Filename, pattern = " "))  %>% 
  separate(col = Filename, into = c("ObsDate", "Strain", "Par_ue", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE) %>% 
  mutate(FilenameJaz=Filename) %>% 
  select(-c("Filename"))

JazSpec <- JazSpec %>% 
mutate(ObsDate = ymd(ObsDate),
       Par_ue = as.numeric(Par_ue),
       WL = as.factor(WL))
```

# Select wavelength range from 400 to 700 nm

```{r select range of nm}
JazSpecTrim <- JazSpec %>% 
  subset(JazSpec$Wavelength >= 400 & JazSpec$Wavelength <= 701)
```

# Remove all NA columns & empty rows, fix column types

```{r remove empty rows and fix column types}
not_all_na <- function(x) {!all(is.na(x))}

JazSpecTrim <- JazSpecTrim %>%
  select_if(not_all_na)
```

# Find nm at max count and compare with rolling mean of counts

```{r find nm at max count}
JazSpecTrim <- JazSpecTrim %>% 
  group_by(WL, Strain) %>%
   mutate(rollmeanCounts = zoo::rollmean(Counts, k = RollWindow, align = "left", fill = NA),
          is_nm = round(Wavelength[which.max(Counts)]),
          is_nm_rollmean= round(Wavelength[which.max(rollmeanCounts)])) %>% 
  ungroup()
```

# Cleaning df before saving as rds and removed unnecessary files from the environment

```{r cleaning JazSpecTrim for final rds}
JazSpecTrim<-JazSpecTrim %>% 
  select(-c(CDateTime))

colnames(JazSpecTrim)
```

```{r removed unnecessary files from environment}
rm(JazSpec)
```

# Save rds for further analysis

```{r save rds}
saveRDS(JazSpecTrim, file.path(DataOut, paste(Project, "Imported_JazEmData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
colnames(JazSpecTrim)
```

### 2023-12-21 Code/Import_MetaData.Rmd
Renamed RMDs to match Baltic_Photoperiod Git

--- 2023-12-08 Code/MetaDataImport.Rmd
@@
   filter(str_detect(SampleID,  ProjectRows)) %>% 
-  select(ProjectCols)
+  select(all_of(ProjectCols))
 

### 2023-12-21 Code/Import_OlisData.Rmd
Renamed RMDs to match Baltic_Photoperiod Git

---
title: "Import_OlisData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Import_OlisData.Rmd imports OLIS CLARiTY spectrophotometer files from Data/RawData/OlisData.zip folder and stored in Data/ImportedData/ImportedOlisData folder as: 
Baltic_Photoperiod_Imported_OlisData.Rds

# Load Libraries and set Project Variables

```{r load libraries, warning = FALSE, echo=FALSE} 
library(tidyverse)
library(lubridate)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(googledrive)
library(googlesheets4)
library(readxl)
```

```{r set project variables, read zipped files, list available files, warning = FALSE, echo=FALSE}
Project <- "Baltic_Photoperiod"
DataOut <- file.path("..", "Data", "ImportedData", "ImportedOlisData")

# Set the path to the zip folder and the destination folder
zip_file <- file.path("..", "Data", "RawData", "OlisData.zip")

#List files in the extracted folder with a ".asc" extension
OlisFiles <- unzip(zip_file, list = TRUE)
OlisFiles <- OlisFiles[grepl(".asc$", OlisFiles$Name), "Name"]
print(OlisFiles)

FileID <- "Smooth"
FileEncode <- "UTF-8" 
Delimiter <- ""
headerrows <- 0
```

# Set up fread_plus and read.delim_long function

```{r set up fread_plus and read.delim_long, warning = FALSE, echo=FALSE}
# Define function to read and process each file
fread_plus <- function(Flnm, Skip, FileEncode, Delim) {
  con <- unz(zip_file, Flnm)  # Corrected the file path within the zip archive
  data <- read.table(con, skip = Skip, encoding = FileEncode, sep = Delim, header = TRUE, row.names = NULL)

# Use tryCatch to handle errors during the closing of the connection
  tryCatch(
    close(con),
    error = function(e) {
      warning("Error closing connection: ", e$message)
    })

  data <- data %>%
    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(zip_file)$ctime)) 
  return(data)
}

#read.delim_long meant for map over a vector of filepaths to read, convert to long format and tidy the imported data
read.delim_long <- function(Flnm, FileEncode, Delimiter, headerrows){
  read.delim(Flnm, encoding = FileEncode, sep = Delimiter, skip = headerrows, header = TRUE, row.names = NULL) %>%
  mutate(Filename = flnm, CDateTime = ymd_hms(file.info(flnm)$ctime)) %>%
  rename(nm = OLIS.3D.ASCII) %>%
  mutate(FirstLastSpec = str_extract(Filename, "_[A-Z][a-z][A-Z][a-z][:digit:][:digit:][:digit:][:digit:]_[A-Z][a-z][A-Z][a-z][:digit:][:digit:][:digit:][:digit:]_")) %>%
  mutate(SampleNumbers = str_extract_all(FirstLastSpec, "[:digit:][:digit:][:digit:][:digit:]")) %>%
  mutate(FirstSampleNumber = as.numeric(map(SampleNumbers, ~.[[1]]))) %>%
  mutate(LastSampleNumber = as.numeric(map(SampleNumbers, ~.[[2]]))) %>%
  mutate(OperatorID = str_extract(Filename,"[A-Z][a-z][A-Z][a-z]")) %>%
  pivot_longer(cols = starts_with("X"), names_to = "SpectraID", values_to = "Abs") %>%
  mutate(SampleCode = as.numeric(str_remove(SpectraID, "X"))) %>%
  mutate(SampleNumber = SampleCode - min(SampleCode, na.rm = TRUE) + FirstSampleNumber) %>%
  relocate(OperatorID, SampleNumber) %>%
  unite(col = SampleID, OperatorID:SampleNumber, sep = "", remove = FALSE) %>%
  arrange(SampleID, nm) %>%
  relocate(SampleID, nm, Abs) %>%
  mutate(SpectraDate = str_extract(Filename, "/[:digit:][:digit:][:digit:][:digit:][:digit:][:digit:][:digit:][:digit:]_"),
         SpectraDate = str_remove_all(SpectraDate, "_"),
         SpectraDate = str_remove_all(SpectraDate, "/"),
         SpectraDate = ymd(SpectraDate)
  )
}
```

# Import and prepare files

```{r import OLIS Spectra corrected files, warning = FALSE, echo=FALSE}
TargetFile <-  OlisFiles
TargetSpectra <- TargetFile %>% 
  map_df(~fread_plus(Flnm = ., FileEncode = FileEncode, Delim = Delimiter, Skip = headerrows)) %>% 
  pivot_longer(., -c(`OLIS.3D.ASCII`, Filename, CDateTime), values_to = "Absorbance", names_to = "SampleID") %>%
  filter(!is.na(Absorbance)) %>%
  mutate(nm = `OLIS.3D.ASCII`) %>% 
  select(-c(`OLIS.3D.ASCII`))

TargetSpectraLong <- TargetSpectra %>%
  separate(col = Filename, into = c("ObsDate", "Project", "SampleID", "Range", "Type", "Correction", "Smooth"), sep = "([\\/\\_\\:])", remove = FALSE)

TargetSpectraLong <- TargetSpectraLong %>%
  mutate(FilenameOlis=Filename) %>% 
  mutate(ObsDate = ymd(`ObsDate`)) %>% 
  select(-c(Type, Correction, Smooth, Project, Filename)) 
```

# Read MetaData

```{r read locally stored metadata from rds}
CultureCatalog <- readRDS(file = file.path("..", "Data","CultureCatalog.Rds"))

CultureCatalog<-CultureCatalog %>% 
  select(-c(PrimaryOperator, Temp_c, ExpCul, ExpStartTime, O2_Category, Optode, OptodeCh, OptodeMeasure))
```

# Merge OlisSpectra with MetaData

```{r merge OlisSpectra with MetaData, warning = FALSE, echo=FALSE}
OLISSpectraMeta <- CultureCatalog %>%
  left_join(., TargetSpectraLong, by = c("SampleID" = "SampleID"))

OLISSpectraMeta <- OLISSpectraMeta %>%
group_by(SampleID) %>%
  arrange(ObsDate) %>%
  mutate(E_days = as.numeric((ObsDate - ExpDate[1]))) %>%
  mutate(SumAb = sum(Absorbance)) %>% 
ungroup()

OLISSpectraMeta <- OLISSpectraMeta %>%
  filter(nm >= 400 & nm <= 700)
```

# Normalize spectra to 440 nm

```{r normalization at 440, warning = FALSE, echo=FALSE}
Absorbance440 <- OLISSpectraMeta %>% 
  filter(nm == 440) %>%
  mutate(Abs440 = Absorbance) %>%
  select(SampleID, Strain, Abs440, Par_ue, Photoperiod, E_days)

OLISSpectraMeta440 <- OLISSpectraMeta %>%
  left_join(., Absorbance440) %>%
  mutate(AbsNorm440 = Absorbance / Abs440)

OLISSpectraMeta440 <- OLISSpectraMeta440 %>%
group_by(SampleID, E_days, Par_ue, Photoperiod) %>%
  mutate(SumAbNorm = sum(AbsNorm440)) %>% 
ungroup()
```
# Cleaning df before saving as rds and removed unnecessary files from the environment

```{r cleaning and ordering OLISSpectraMeta440 before creating rds}
OLISSpectraMeta440<-OLISSpectraMeta440 %>% 
  select(-c(CDateTime, Range)) 
```

```{r removed unnecessary df from the environment}
rm(Absorbance440, CultureCatalog, TargetSpectra, OLISSpectraMeta, TargetSpectraLong)
```

# Save rds for further analysis

```{r save rds}
saveRDS(OLISSpectraMeta440, file.path(DataOut, paste(Project, "Imported_OlisData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
colnames(OLISSpectraMeta440)
```

### 2023-12-21 Code/Process_OlisJazEmData.Rmd
Renamed RMDs to match Baltic_Photoperiod Git

---
title: "Process_OlisSpectraJazEmData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Process_OlisSpectraJazEmData.Rmd processes and combines Baltic_Photoperiod_Imported_JazEmData.Rds from Data/ImportedData/ImportedJazEmData folder and Baltic_Photoperiod_Imported_OlisData.Rds from Data/ImportedData/ImportedOlisData folder. This .Rmd generates Baltic_Photoperiod_Processed_OlisSpectraAll.Rds and Baltic_Photoperiod_Processed_OlisSpectraTidy.Rds (both stored in Data/ProcessedData/ProcessedOlisJazData folder) and OlisSpectra_Plot.png (stored in Output/Plots folder).

# Load Libraries and set Project Variables

```{r load libraries, warning = FALSE, echo=FALSE} 
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(ggspectra)
library(ggpubr)
library(caret)
library(photobiologyWavebands)
library(reshape2)
library(photobiology)
library(gcookbook)
```

```{r set project variables}
Project <- "Baltic_Photoperiod"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedOlisJazData")
DataInOlis <- file.path("..", "Data", "ImportedData", "ImportedOlisData", fsep = .Platform$file.sep)
DataInJaz <- file.path("..", "Data", "ImportedData", "ImportedJazEmData", fsep = .Platform$file.sep)

PlotsPath <- file.path("..", "Output", "Plots")
RDSPlotPath <- file.path("..", "Output", "PlotsRDS")

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# List and read imported Olis and Jaz files

```{r exported Rmd only first time in session}
list.files(path = DataInOlis, pattern = Project, full.names = TRUE)
list.files(path = DataInJaz, pattern = Project, full.names = TRUE)
```

```{r read imported Olis file}
OLISSpectraFile <- "../Data/ImportedData/ImportedOlisData/Baltic_Photoperiod_Imported_OlisData.Rds"
OLISSpectraFileName <- str_split(string = OLISSpectraFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
OLISSpectra <- readRDS(OLISSpectraFile)  %>%
  ungroup()

JazFile <- "../Data/ImportedData/ImportedJazEmData/Baltic_Photoperiod_Imported_JazEmData.Rds"
JazFileName <- str_split(string = JazFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
JazData <- readRDS(JazFile)  %>%
  ungroup()
```

# Preparing df for further analysis

```{r round nm}
JazData <- JazData %>%
   mutate(WavelengthRound = round(Wavelength))
colnames(JazData)

JazDataRound <- JazData %>%
group_by(FilenameJaz, WavelengthRound) %>%
  summarize(Counts, FilenameJaz, ObsDate, Strain, Par_ue, WL, WavelengthRound, CountsMean = mean(Counts)) %>%
ungroup()

JazDataRound <- JazDataRound %>%
  summarize(FilenameJaz, Strain, Par_ue, WL, WavelengthRound, CountsMean) %>%
  unique()

JazDataRound <- JazDataRound %>%
  filter(WavelengthRound >= 400 & WavelengthRound <= 700)
```

# Normalize Jaz emission to 439 nm

```{r Normalization Jaz emission at 439}
EmissionJazWW <- JazDataRound %>%
  group_by(WL, Strain, Par_ue) %>%
  filter(WavelengthRound == 439) %>%
  mutate(EmJaz439 = CountsMean) %>%
  select(Strain, EmJaz439, Par_ue) %>%
  ungroup()

JazDataRoundMeta <- JazDataRound %>%
  left_join(., EmissionJazWW) %>%
  mutate(EmNormJaz439 = CountsMean / EmJaz439)
```

# Merge Olis and Jaz data

```{r combine Olis spectra and Jaz data}
OLISSpectraMeta <- OLISSpectra %>%
  left_join(., JazDataRoundMeta, by = c("Par_ue" = "Par_ue", "nm" = "WavelengthRound", "Strain" = "Strain", "WL" = "WL")) %>%
  unique()
```

# Estimate PUR

```{r estimate PUR}
OLISSpectraMetaPUR <- OLISSpectraMeta %>%
  mutate(PURNorm = (AbsNorm440*EmNormJaz439)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz439 = sum(EmNormJaz439)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz439)) %>% 
  ungroup() 
```

# Calculate daily PUR photon dose

```{r calculate PUR Photon dose}
OLISSpectraMetaPUR1 <- OLISSpectraMetaPUR %>%
  filter(Photoperiod != "24") %>% 
  mutate(PURPhotonDose_day =(PUR/2)*Photoperiod*3600)

OLISSpectraMetaPUR2 <- OLISSpectraMetaPUR %>%
  filter(Photoperiod == "24") %>% 
  mutate(PURPhotonDose_day = PUR*Photoperiod*3600)

  OLISSpectraMetaPUR <-rbind(OLISSpectraMetaPUR1, OLISSpectraMetaPUR2)
  rm(OLISSpectraMetaPUR1,OLISSpectraMetaPUR2)
```

# Filter unrevelant data

```{r filter unrevelant data}
OLISSpectraMetaPUR<-OLISSpectraMetaPUR %>% 
  filter(PUR>=0) %>% 
  filter(PUR<=900)
```

# Preparing df for creating representative plot

```{r preparing selected data for creating representative plot}
OLISSpectraMetaPURShortBA127R<- OLISSpectraMetaPUR %>%
  filter(Photoperiod == "12") %>% 
  filter(Strain == "BA127R") %>% 
  filter(Par_ue == 300) %>% 
  filter(E_days == "4" | E_days == "8") %>% 
  mutate(E_days=case_when(E_days==4~3,
         E_days==8~7)) %>% 
  mutate(PURNormBA127R = PURNorm) %>% 
  select(-c(PURNorm, FilenameJaz, FilenameOlis))

OLISSpectraMetaPURShortBA77G<- OLISSpectraMetaPUR %>%
  filter(Photoperiod == "12") %>% 
  filter(Strain == "BA77G") %>% 
  filter(Par_ue == 300) %>% 
  filter(E_days == "3" | E_days == "7") %>% 
  mutate(PURNormBA77G = PURNorm) %>% 
  select(-c(PURNorm, FilenameJaz, FilenameOlis))

OLISSpectraMetaPURShort <- OLISSpectraMetaPURShortBA127R %>%
  full_join(., OLISSpectraMetaPURShortBA77G, by = c("SampleID" = "SampleID", "Run" = "Run", "Strain" = "Strain", "ExpDate" = "ExpDate", "Par_ue" = "Par_ue", "Photoperiod" = "Photoperiod", "MC"="MC", "Tube" = "Tube", "O2" = "O2", "WL" = "WL", "LightShape" = "LightShape", "ExpEndDate"="ExpEndDate", "nm" = "nm", "ObsDate" = "ObsDate", "Absorbance" = "Absorbance", "SumAb" = "SumAb", "Abs440" = "Abs440", "AbsNorm440" = "AbsNorm440", "SumAbNorm" = "SumAbNorm", "E_days" = "E_days", "CountsMean" = "CountsMean", "EmJaz439" = "EmJaz439", "EmNormJaz439" = "EmNormJaz439", "PURNormSum" = "PURNormSum", "SumEmNormJaz439" = "SumEmNormJaz439", "PUR" = "PUR", "PURPhotonDose_day" = "PURPhotonDose_day", "PARPhotonDose_day" = "PARPhotonDose_day")) 
```

```{r Changes strain names}
OLISSpectraMetaPURShort <- OLISSpectraMetaPURShort %>%
      mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077"))
```

# Create plot

```{r Create plot, fig.height = 10, fig.width = 8}
Par_ue.labs <- c("30 µE", "90 µE", "180 µE", "Phase of growth", "900 µE")
names(Par_ue.labs) <- c("30", "90", "180", "300", "900")

Photoperiod.labs <- c("8 h", "Photoperiod: 12 h", "16 h", "24 h")
names(Photoperiod.labs) <- c("8", "12", "16", "24")

E_days.labs <- c("Exponential", "Pre-stationary")
names(E_days.labs) <- c("3", "7")

Strain.labs <- c("PC-rich", "PE-rich")
names(Strain.labs) <- c("PC-rich_077", "PE-rich_127")

O2.labs <- c("Strain")
names(O2.labs) <- c(21)

data_textPUR0 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PAR = 300 µE', 'PAR = 300 µE'))

data_textPUR00 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PC-rich_077", "PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PAR = 300 µE', 'PAR = 300 µE'))

data_textPUR1 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PUR = 176 µE', 'PUR = 129 µE'))

data_textPUR2 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PC-rich_077", "PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PUR = 139 µE', 'PUR = 128 µE'))

data_textpigment1 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 440 nm'))
data_textpigment3 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 680 nm'))
data_textpigment4 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PC 620 nm'))
data_textpigment5 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('Car 480 nm'))
data_textpigment6 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PUB 500 nm'))

arrowdf1 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf3 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf4 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf5 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf6 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))

data_textpigment7 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 440 nm'))
data_textpigment8 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('Car 480 nm'))
data_textpigment9 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PE 570 nm'))
data_textpigment10 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 680 nm'))
data_textpigment11 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PC 620 nm'))
data_textpigment12 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PUB 500 nm'))

arrowdf7 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf8 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf9 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf10 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf11 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
arrowdf12 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))

OLISSpectraMetaPURShort %>%
  filter(Photoperiod == "12") %>%
  filter(Strain == "PC-rich_077" | Strain == "PE-rich_127") %>%
  filter(Par_ue == 300) %>%
  filter(E_days == "3" | E_days == "7") %>%
  ggplot() +

  geom_area(aes(x = nm, y = EmNormJaz439, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = PURNormBA127R, fill = "brown4"), alpha = 0.5, show.legend = F) +
  geom_area(aes(x = nm, y = PURNormBA77G, fill = "palegreen3"), alpha = 0.5, show.legend = F) +
  geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F, size = 0.4) +

  geom_text(data=data_textPUR0, aes(x=446, y=1.26, label=label), size=3.7) +
  geom_text(data=data_textPUR00, aes(x=446, y=1.26, label=label), size=3.7) +
  geom_text(data=data_textPUR1, aes(x=446, y=1.21, label=label), size=3.7) +
  geom_text(data=data_textPUR2, aes(x=446, y=1.21, label=label), size=3.7) +

  geom_text(data=data_textpigment1, aes(x=500, y=1.1, label=label), size=4, colour = "darkgreen") + #chla440
  geom_text(data=data_textpigment5, aes(x=500, y=0.8, label=label), size=4, colour = "orange") + #Car
  geom_text(data=data_textpigment3, aes(x=650, y=1.2, label=label), size=4, colour = "darkgreen") +#chla680
  geom_text(data=data_textpigment4, aes(x=590, y=0.95, label=label), size=4, colour = "deepskyblue4") + #PC
  geom_text(data=data_textpigment6, aes(x=485, y=0.25, label=label), size=4, colour = "sienna4") + #PUB
  geom_segment(data = arrowdf1,
               aes(x = 480, xend = 445, y = 1.05, yend = 1),
               colour = "darkgreen", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla440
  geom_segment(data = arrowdf5,
               aes(x = 480, xend = 475, y = 0.75, yend = 0.54),
               colour = "orange", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #Car
  geom_segment(data = arrowdf3,
               aes(x = 660, xend = 680, y = 1.14, yend = 0.95),
               colour = "darkgreen", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla680
  geom_segment(data = arrowdf4,
               aes(x = 610, xend = 630, y = 0.90, yend = 0.82),
               colour = "deepskyblue4", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PC
  geom_segment(data = arrowdf4,
               aes(x = 480, xend = 494, y = 0.30, yend = 0.41),
               colour = "sienna4", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PUB
  geom_text(data=data_textpigment7, aes(x=500, y=1.1, label=label), size=4, colour = "darkgreen") + #chla440
  geom_text(data=data_textpigment8, aes(x=500, y=0.8, label=label), size=4, colour = "orange") + #Car
  geom_text(data=data_textpigment9, aes(x=580, y=1.0, label=label), size=4, colour = "darkmagenta") + #PE
  geom_text(data=data_textpigment10, aes(x=650, y=1.2, label=label), size=4, colour = "darkgreen") +#chla680
  geom_text(data=data_textpigment11, aes(x=600, y=0.17, label=label), size=4, colour = "deepskyblue4") + #PC
  geom_text(data=data_textpigment12, aes(x=495, y=0.30, label=label), size=4, colour = "sienna4") + #PUB
  geom_segment(data = arrowdf7,
               aes(x = 480, xend = 445, y = 1.05, yend = 1),
               colour = "darkgreen", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla440
  geom_segment(data = arrowdf8,
               aes(x = 480, xend = 475, y = 0.75, yend = 0.55),
               colour = "orange", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #Car
  geom_segment(data = arrowdf9,
               aes(x = 590, xend = 575, y = 0.95, yend = 0.85),
               colour = "darkmagenta", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PE
  geom_segment(data = arrowdf10,
               aes(x = 660, xend = 680, y = 1.14, yend = 0.85),
               colour = "darkgreen", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla680
  geom_segment(data = arrowdf11,
               aes(x = 610, xend = 630, y = 0.2, yend = 0.3),
               colour = "deepskyblue4", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PC
  geom_segment(data = arrowdf12,
               aes(x = 490, xend = 500, y = 0.35, yend = 0.52),
               colour = "sienna4", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PUB
  scale_color_manual(values = c("PC-rich_077" ="palegreen3", "PE-rich_127" ="brown4")) +
  scale_linetype_manual(values = c("PC-rich_077" ="solid", "PE-rich_127" ="longdash")) +
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  labs(y = "Normalized absorbance", x = "Wavelength (nm)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c (-0.01, 1.25)) +
  ggh4x::facet_nested(cols = vars(Par_ue, E_days), rows = vars(O2, Strain),labeller = labeller(Ex_WL = label_both, WL = label_both, E_days = E_days.labs, Photoperiod = Photoperiod.labs, Par_ue = Par_ue.labs, Strain = Strain.labs, O2 = O2.labs, )) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.title = element_blank(),
        legend.direction="horizontal",
        legend.position = c(0.08,0.97),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text.align = 0,
        legend.key.width= unit(0.3, 'cm'),
        legend.text = element_text(size=10))
```

# Save plot

```{r save plot}
ggsave(file = file.path(PlotsPath, paste("OlisSpectra_Plot",".png",sep = "")), height=10, width= 8,  dpi = 300, limitsize = TRUE)
```

```{r Create plot, fig.height = 6, fig.width = 8}

Par_ue.labs <- c("30 µE", "90 µE", "180 µE", "Phase of growth", "900 µE")
names(Par_ue.labs) <- c("30", "90", "180", "300", "900")

Photoperiod.labs <- c("8 h", "Photoperiod: 12 h", "16 h", "24 h")
names(Photoperiod.labs) <- c("8", "12", "16", "24")

E_days.labs <- c("Exponential", "Pre-stationary")
names(E_days.labs) <- c("3", "7")

Strain.labs <- c("PE-rich_127", "PC-rich_077")
names(Strain.labs) <- c("PE-rich_127", "PC-rich_077")

data_textPUR0 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), label = c('PAR = 300 µE', 'PAR = 300 µE'))

data_textPUR1 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), label = c('PUR (PE-rich) = 176 µE', 'PUR (PE-rich) = 129 µE'))

data_textPUR2 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), label = c('PUR (PC-rich) = 139 µE', 'PUR (PC-rich) = 128 µE'))

data_textpigment1 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('Chl a 440 nm'))
data_textpigment2 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('PE 570 nm'))
data_textpigment3 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('Chl a 680 nm'))
data_textpigment4 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('PC 620 nm'))
data_textpigment5 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('Car 480 nm'))
data_textpigment6 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('PUB 500 nm'))

arrowdf1 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
arrowdf2 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
arrowdf3 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
arrowdf4 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
arrowdf5 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
arrowdf6 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)

OLISSpectraMetaPURShort %>%
  filter(Photoperiod == "12") %>%
  filter(Strain == "PE-rich_127" | Strain == "PC-rich_077") %>%
  filter(Par_ue == 300) %>%
  filter(E_days == "3" | E_days == "7") %>%
  ggplot() +
  geom_area(aes(x = nm, y = EmNormJaz439, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_area(aes(x = nm, y = PURNormBA127R, fill = "brown4"), alpha = 0.5, show.legend = F) +
  geom_area(aes(x = nm, y = PURNormBA77G, fill = "palegreen3"), alpha = 0.5, show.legend = F) +
  geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F, size = 0.7) +

  geom_text(data=data_textPUR0, aes(x=435, y=1.26, label=label), size=3.5) +
  geom_text(data=data_textPUR1, aes(x=462, y=1.21, label=label), size=3.5) +
  geom_text(data=data_textPUR2, aes(x=462, y=1.16, label=label), size=3.5) +

  geom_text(data=data_textpigment1, aes(x=450, y=1.07, label=label), size=4, colour = "darkgreen") + #chla440
  geom_text(data=data_textpigment5, aes(x=430, y=0.36, label=label), size=4, colour = "coral3") + #Car
  geom_text(data=data_textpigment2, aes(x=520, y=0.92, label=label), size=4, colour = "darkmagenta") + #PE
  geom_text(data=data_textpigment3, aes(x=660, y=1.08, label=label), size=4, colour = "darkgreen") +#chla680
  geom_text(data=data_textpigment4, aes(x=605, y=1.0, label=label), size=4, colour = "deepskyblue4") + #PC
  geom_text(data=data_textpigment6, aes(x=485, y=0.08, label=label), size=4, colour = "sienna4") + #PUB

  geom_segment(data = arrowdf1,
               aes(x = 470, xend = 440, y = 1.04, yend = 1.02),
               colour = "darkgreen", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla440
  geom_segment(data = arrowdf5,
               aes(x = 450, xend = 470, y = 0.4, yend = 0.48),
               colour = "coral3", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #Car
  geom_segment(data = arrowdf2,
               aes(x = 538, xend = 568, y = 0.88, yend = 0.86),
               colour = "darkmagenta", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PE
  geom_segment(data = arrowdf3,
               aes(x = 697, xend = 680, y = 1.05, yend = 0.92),
               colour = "darkgreen", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla680
  geom_segment(data = arrowdf4,
               aes(x = 632, xend = 630, y = 0.95, yend = 0.82),
               colour = "deepskyblue4", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PC
  geom_segment(data = arrowdf4,
               aes(x = 465, xend = 500, y = 0.12, yend = 0.52),
               colour = "sienna4", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PUB
  scale_color_manual(values = c("PE-rich_127" ="brown4", "PC-rich_077" ="palegreen3")) +
  scale_linetype_manual(values = c("PE-rich_127" ="longdash", "PC-rich_077" ="solid")) +
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) + 
  scale_fill_identity() +
  labs(y = "Normalized absorbance", x = "Wavelength (nm)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c (-0.01, 1.25)) +
  ggh4x::facet_nested(cols = vars(Par_ue, E_days), labeller = labeller(Ex_WL = label_both, WL = label_both, E_days = E_days.labs, Photoperiod = Photoperiod.labs, Par_ue = Par_ue.labs, Strain = Strain.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.title = element_blank(),
        legend.direction="horizontal",
        legend.position = c(0.08,0.97),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text.align = 0,
        legend.key.width= unit(0.3, 'cm'),
        legend.text = element_text(size=10))
```

# Cleaning df before saving as rds and removed unnecessary files from the environment

```{r delete unused df from the environment}
rm(data_textpigment1,data_textpigment2,data_textpigment3,data_textpigment4,data_textpigment5,data_textpigment6, data_textpigment7, data_textpigment8, data_textpigment9, data_textpigment10, data_textpigment11, data_textpigment12, arrowdf1,arrowdf2,arrowdf3,arrowdf4,arrowdf5,arrowdf6, arrowdf7, arrowdf8, arrowdf9, arrowdf10, arrowdf11, arrowdf12, data_textPUR0, data_textPUR00, data_textPUR1,data_textPUR2, EmissionJazWW, JazData, JazDataRound, JazDataRoundMeta, OLISSpectraMetaPURShortBA127R, OLISSpectraMetaPURShortBA77G, OLISSpectraMeta, OLISSpectra)
```

# Create tidy df without all nm

```{r clean df, create smaller df - without absorbance and all nm}
OLISAllPURTidy<-OLISSpectraMetaPUR %>% 
  select(-c(Absorbance, nm, Abs440, AbsNorm440, EmJaz439, EmNormJaz439, PURNorm, CountsMean, SumAbNorm, PURNormSum, SumEmNormJaz439)) %>% 
  unique()

OLISAllPURTidy<-OLISAllPURTidy %>% 
  group_by(Strain, Par_ue, Photoperiod, E_days, MC, Run) %>%
  mutate(PURPARRatio = PUR/Par_ue) %>% 
ungroup()

OLISAllPURTidy <- OLISAllPURTidy %>% 
  mutate(E_hours = E_days*24) %>% 
  filter(PURPARRatio<=1) %>% 
  filter(PURPARRatio>0)
```

# Preparing df for creating plot

```{r create tidy PAR photon dose and facets for plot}
OLISAllPURTidy <- OLISAllPURTidy %>%
    mutate(PARPhotonDoseTidy=PARPhotonDose_day/100000) %>% 
    mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077"))

OLISAllPURTidy$facetsPar_ue = factor(OLISAllPURTidy$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
OLISAllPURTidy$facetsPhotoperiod = factor(OLISAllPURTidy$WL, labels = c("Photoperiod~(h)"))
OLISAllPURTidy$facetsStrain = factor(OLISAllPURTidy$WL, labels = c("Strain"))
OLISAllPURTidy$facetsPhase = factor(OLISAllPURTidy$WL, labels = c("Phase~of~growth"))
OLISAllPURTidy$facetsPARPhotonDose_day = factor(OLISAllPURTidy$WL, labels = c("PAR~photon~dose~(10^{5}~µmol~photons~m^{-2}~d^{-1})"))
```

# Create preliminary PUR/PAR ratio plot

```{r preliminary plot}
# lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
# lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
# lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
# 
# OLISAllPURTidy %>%
#   ggplot() +
#   geom_point(aes(x = E_hours, y = PURPARRatio, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = T) +
#   scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
#   scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
#   coord_cartesian(ylim = c(0, 1.7)) +
#   ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
#   theme_bw()
```

# Load tmaxAG catalog

```{r}
gs4_deauth()
tmaxAG<- read_sheet("https://docs.google.com/spreadsheets/d/1ksY7xlg9wOsICOBRmZkHPKdd9KOislNwPDzyuJ3UIUI/edit#gid=0")
as.data.frame(tmaxAG)
tmaxAG <- tmaxAG

tmaxAG<-tmaxAG %>% 
  mutate(Par_ue = as.numeric(Par_ue)) %>%
  mutate(Photoperiod = as.numeric(Photoperiod)) %>%
  mutate(tMaxAG = as.numeric(tMaxAG)) %>%
  mutate(dayRound_tmaxAG=tMaxAG/24) %>% 
  mutate(dayRound_tmaxAG = round(dayRound_tmaxAG, digits = 0)) %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077"))

tmaxAG$facetsPar_ue = factor(tmaxAG$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
tmaxAG$facetsPhotoperiod = factor(tmaxAG$WL, labels = c("Photoperiod~(h)"))
tmaxAG$facetsStrain = factor(tmaxAG$O2, labels = c("Strain"))
tmaxAG$facetsPARPhotonDose_day = factor(tmaxAG$WL, labels = c("PAR~photon~dose~(10^{5}~µmol~photons~m^{-2}~d^{-1})"))

tmaxAGno24<-tmaxAG %>% 
  filter(Photoperiod != "24") %>% 
  mutate(PARPhotonDose_day =(Par_ue/2)*Photoperiod*3600)
tmaxAG24<-tmaxAG %>% 
  filter(Photoperiod == "24") %>% 
  mutate(PARPhotonDose_day = Par_ue*Photoperiod*3600) 
tmaxAG <-rbind(tmaxAGno24, tmaxAG24)
  rm(tmaxAGno24, tmaxAG24)
```

# Select variable for choosen PARPhotonDose to create a plot

```{r select variable for choosen PARPhotonDose to create a plot}
tmaxAGSelect<-tmaxAG %>% 
  mutate(PARPhotonDoseTidy=PARPhotonDose_day/100000) %>% 
  filter(PARPhotonDoseTidy == 4.32000|
  PARPhotonDoseTidy == 6.48000|
  PARPhotonDoseTidy == 8.64000|
  PARPhotonDoseTidy == 43.20000|
  PARPhotonDoseTidy == 64.80000|
  PARPhotonDoseTidy == 86.40000) 
```

# Create 4 df for vertical lines (coloured as Strain) contained tMaxAG value

```{r select revelant columns}
tMaxAGLines_056Select<-tmaxAGSelect %>% 
  filter(Strain == "PC-rich_056") %>% 
  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PARPhotonDoseTidy, tMaxAG)) %>% 
  unique()
tMaxAGLines_077Select<-tmaxAGSelect %>% 
  filter(Strain == "PC-rich_077") %>% 
  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PARPhotonDoseTidy, tMaxAG)) %>% 
  unique()
tMaxAGLines_048Select<-tmaxAGSelect %>% 
  filter(Strain == "PE-rich_048") %>% 
  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PARPhotonDoseTidy, tMaxAG)) %>% 
  unique()
tMaxAGLines_127Select<-tmaxAGSelect %>% 
  filter(Strain == "PE-rich_127") %>% 
  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PARPhotonDoseTidy, tMaxAG)) %>% 
  unique()
```

# Create plot

```{r Create final PUR/PAR ratio plot, fig.height = 5, fig.width = 8}
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

OLISAllPURTidy %>%
  filter(PARPhotonDoseTidy == 4.32000|
  PARPhotonDoseTidy == 6.48000|
  PARPhotonDoseTidy == 8.64000|
  PARPhotonDoseTidy == 43.20000|
  PARPhotonDoseTidy == 64.80000|
  PARPhotonDoseTidy == 86.40000) %>%
  ggplot() +
  geom_point(aes(x = E_hours, y = PURPARRatio, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = T) +
  geom_vline(data = tMaxAGLines_056Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "seagreen4", size=0.4) +
  geom_vline(data = tMaxAGLines_077Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "palegreen3", size=0.4) +
  geom_vline(data = tMaxAGLines_048Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown4", size=0.4) +
  geom_vline(data = tMaxAGLines_127Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown1", size=0.4) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
  labs(y = "PUR/PAR ratio", x = "Elapsed time (h)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.5)) +
  ggh4x::facet_nested(cols = vars(facetsPARPhotonDose_day, PARPhotonDoseTidy), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="white"),
        legend.position = c(0.08,0.87),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.y = unit(-0.005, "cm"),
        legend.spacing.x = unit(-0.005, "cm"),
        legend.title = element_blank(),
        legend.text = element_text(size=10))
```

# Cleaning df before saving as rds and removed unnecessary files from the environment

```{r}
rm(tMaxAGLines_056Select, tMaxAGLines_077Select, tMaxAGLines_048Select, tMaxAGLines_127Select, tmaxAG, tmaxAGSelect)
```

# Save rds for further analysis

```{r save rds}
saveRDS(OLISSpectraMetaPUR, file.path(DataOut, paste(Project, "Processed_OlisSpectraAll.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(OLISAllPURTidy, file.path(DataOut, paste(Project, "Processed_OlisSpectraTidy.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(OLISSpectraMetaPURShort, file.path(RDSPlotPath, paste(Project, "Plot_OlisSpectra.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
colnames(OLISSpectraMetaPUR)
```

# Variable names used in Data Dictionary

```{r}
colnames(OLISAllPURTidy)
```

### 2023-12-21 Code/Unused/OlisImportCombinedFiles.Rmd
Renamed RMDs to match Baltic_Photoperiod Git

---
title: "Import OLIS spectral data import"
author: "Douglas A. Campbell, Sylwia Sliwinska-Wilczewska, Sarah Gore, Adrian Kryk, Mireille Savoie"
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
---

# Import spectral files generated by OLIS spectrophotometer
# Specifically ascii files generated with more than 1 sample in a tab seperated format
# User input is needed to rename columns with the appropriate sample name according to users notes.
# Automation of renaming is not possible given that sometimes there were gaps in the sample id codes or codes were not sequential.
# Imported and renamed spectras are merged with meta catalog.
# output .RDS sent to folder that imports ascii files containing single spectras.
# Next .rmd to run is 'OlisImportCorrPICO_MS.rmd' which imports single spectras from .asc files, merge with meta catelog and will merge the already imported spectras generated from this .rmd.

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r set project variables}
Project <- "PICO"
DataOut <- file.path("..", "OLISSpectraCorr", "MiSa")

#Sylwia's file path
#DataIn <- file.path("..", "OLISSpectraCorr", "SySlCCASingleTest", fsep = .Platform$file.sep)

#Mireille's file path
DataIn <- file.path("..", "OLISSpectraCorr", "OtherCombinedData_375710", fsep = .Platform$file.sep)

FileID <- "Smooth"

#MDPicoGoogle <- "https://docs.google.com/spreadsheets/d/1Lerp5u25kzBtaBbnOYElYqUP59cn68gJpxxayhnGdkw/edit#gid=0"

FileEncode <- "UTF-8"

HeaderRows <- 1
RollWindow <- 10

FileEncode <- "UTF-8" 
Delimiter <- "\t"

Skip <- 0  
Comment <- "#"

```

```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)

library(broom)
library(knitr)
library(OneR)

library(magrittr)
library(googledrive)
library(googlesheets4)
library(readxl)

library(ggspectra)
library(ggpubr)
library(caret)
```

```{r set colours}
Wavelengths_nm = c(405, 450, 475, 530, 615, 660, 730, "WW")
Colours_nm = c("violet", "darkblue", "dodgerblue", "darkgreen","orange","red","purple", "black")

names(Colours_nm) <- Wavelengths_nm
Colours_nm

```

For SySl files 'baseline' in filename means baseline spectra already subtracted within OLIS software.
This was not universallly true across all projects; be careful.
For SySl files 'raw' means spectra of undiluted culture; other spectra are 1 or 4 ml culture + 8 or 4 ml media.

Ideally: we want to read and tidy some user-selected set of files taken from multiple dates

```{r list available OLIS Files}
OlisFiles <- list.files(path = DataIn, pattern = ".asc", full.names = TRUE)
OlisFiles

#test for duplicate file names
unique(duplicated(OlisFiles))
```

Must import 1 file at time in order to assign proper culture id codes to the corresponding column.  Automation is not possible because each ascii file was generated with different column header names.
```{r set TargetFile}

TargetFile <- file.path(DataIn, "20220203_PICO_MiSa1081_MiSa1088_375710_baseline_JavCorr_Smooth.asc")

TargetFileName <- str_split(string = TargetFile, "/")[[1]][4] %>%
  str_remove(pattern = ".asc")

TargetFileName

```

# set up read_tsv_plus
```{r}
#make this more robust to variable file formats
#FileEncode <- "UTF-8"
#Delimiter <- ""
#.asc files from export from OLIS seem to use spaces as delimiter
# 
#HeaderRows <- 0

# read.delim_plus <- function(flnm, filencode, delimiter, headerrows){read.delim(flnm, fileEncoding = filencode, sep = delimiter,  skip = headerrows, header = TRUE, row.names = NULL) %>%
#      mutate(Filename = flnm, Cdatetime = ymd_hms(file.info(flnm)$ctime))
# }

#reads in tab as delimiter for multi columns of data of the combined ascii file
read_tsv_plus <- function(Flnm = TargetFile, HeaderRows){read_tsv(Flnm,  col_names = TRUE,  comment = Comment, locale=locale(encoding="latin1"), skip = HeaderRows) %>%
    #mutate(Filename = TargetFileName)}
     mutate(Filename = Flnm, Cdatetime = ymd_hms(file.info(Flnm)$ctime))}

```

# Import OLISSpectra corrected files
```{r import from specific OLIS corrected file containing multiple spectra}

OLIS_Data <- read_tsv_plus(Flnm = TargetFile, HeaderRows = Skip)

glimpse(OLIS_Data)

```

Rename columns with proper SampleID
```{r}
OLIS_Data <- OLIS_Data %>%
  rename(nm = `OLIS-3D-ASCII`,
         MiSa1081 = `3`,  
         MiSa1082 = `4`,
         MiSa1083 = `5`,
         MiSa1084 = `6`,
         MiSa1085 = `7`,
         MiSa1086 = `8`,
         MiSa1087 = `9`,
         MiSa1088 = `10`)

glimpse(OLIS_Data)

```

#Pivot Longer to get in same format as single sample saved ascii files.
```{r set up DF}
OLIS_Data <- OLIS_Data %>%
pivot_longer(., -c(`nm`, Filename, Cdatetime), values_to = "Absorbance", names_to = c("SampleID"))

glimpse(OLIS_Data)

OLIS_Data <- OLIS_Data %>%
  separate(col = Filename, into = c("Directory","Folder", "SubFolder", "Subsubfolder",  "Date", "Project", "FirstID", "LastID", "Range", "Source", "Correction", "Type"), sep = "([\\/\\_\\:])", remove = FALSE) %>% 
  arrange(SampleID, nm) %>%
  select(-c(Type, Correction, Source, Folder, Directory, SubFolder, Subsubfolder, Date,  FirstID, LastID)) %>% 
  rename(CultureID = SampleID) %>% 
 mutate(SpectraDate = str_extract(Filename, "[:digit:][:digit:][:digit:][:digit:][:digit:][:digit:][:digit:][:digit:]_"),
         SpectraDate = str_remove_all(SpectraDate, "_"),
         SpectraDate = str_remove_all(SpectraDate, "/"),
         SpectraDate = ymd(SpectraDate))

glimpse(OLIS_Data)
```

#Load Multiculti catalog
```{r load local multiculticatalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()

# imagine this is the URL or ID of a Sheet readable by anyone (with a link)
# MultiCulti metadata
MetaData <- read_sheet("https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0") %>%
  # read_sheet has an annoying "feature" to set the type of columns it can't parse to a list.
  # ggplot/dplyr doesn't like working with a dataframe of lists.
  # In this case WL is set to a list since some values are numbers, some are strings, some are blank.
  # To fix this, first drop all rows missing WL, then unlist.
  # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.
  drop_na(WL) %>%
  mutate(WL = unlist(WL))

as.data.frame(MetaData)

MetaData <- MetaData %>%
   mutate(ExpDate = ymd(ExpDate),
          ExpEndDate = ymd_hms(`ExpEndDate`))
```

# Merge OLISSpectra with MetaData
```{r OLISDateSpectra with MetaData}

#OLISSpectraMeta <- left_join(x = TargetSpectraLong2, y = MetaData, by = c("CultureID" = "ID"))

#OLISSpectraDirtyMeta <- left_join(x = OLISSpectraDirty, y = MetaData,  by = c("SampleID" = "ID"))

# rm(MetaData)
# rm(OLISSpectra)
#remove large MetaData dataframe to lower memory overhead

OLISSpectraMeta <- MetaData %>%
  right_join(., OLIS_Data, by = c("ID" = "CultureID"))

OLISSpectraMeta <- OLISSpectraMeta %>%
group_by(ID) %>%
  arrange(SpectraDate) %>%
  mutate(E_days = as.numeric((SpectraDate - ExpDate[1]))) %>%
ungroup()

```

# Save assembled spectra data set
```{r save Olis}

saveRDS(object = OLISSpectraMeta, file = file.path(DataOut, paste(TargetFileName, "CombinedLabeled.Rds",  sep = "_")), ascii = FALSE, version = NULL,
        compress = TRUE, refhook = NULL)

```

### 2024-01-03 Code/Import_JazEmData.Rmd
Fix code

@@
 author:
+- Mireille Savoie
 - Sylwia Sliwinska-Wilczewska
@@
     fig_caption: yes
-bibliography: BalticPhotoperiod.bib
+bibliography: [Prochlorococcus_O2_NPQ.bib, RPackages.bib]
 csl: plos-one.csl
@@
 
-Import_JazEmData.Rmd imports Jaz radiospectrometer files from Data/RawData/JazEmData.zip folder and stored in Data/ImportedData/ImportedJazEmData folder as: 
-Baltic_Photoperiod_Imported_JazEmData.Rds
+Import_JazEmData.Rmd imports and tidies Jaz radiospectrometer files from Data/RawData/JazEmData.zip The tidied data is saved as a .Rds in Data/ImportedData/ImportedJazEmData folder as: 
+PICO_Imported_JazEmData.Rds
 
-# Load Libraries and set Project Variables
-
+# Load Libraries 
 ```{r load libraries, warning = FALSE, echo=FALSE}
 library(tidyverse)
-library(lubridate)
-library(googledrive)
+library(photobiologyWavebands)
 ```
 
+#set Photobiology colors
+```{r set colours}
+Wavelengths_nm = c(405, 445, 470, 530, 620, 660, 730, "WW")
+MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(445), w_length2rgb(470), w_length2rgb(530), 
+                   w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black"))
+
+names(MCMIXColours) <- Wavelengths_nm
+MCMIXColours
+```
+
+# Set Project Variables
 ```{r set project variables, read zipped files, list available files, warning = FALSE, echo=FALSE}
-Project <- "Baltic_Photoperiod"
-DataOut <- file.path("..", "Data", "ImportedData", "ImportedJazEmData")
+Project <- "PICO"
+DataOut <- file.path("..", "Data", "ImportedData", "ImportedJazEmData", fsep = .Platform$file.sep)
 
-# Set the path to the zip folder and the destination folder
+# Set the path to the zip folder
 zip_file <- file.path("..", "Data", "RawData", "JazEmData.zip")
@@
 # Set up fread_plus function
-
 ```{r set up fread_plus, warning = FALSE, echo=FALSE}
@@
 fread_plus <- function(Flnm, Skip, FileEncode, Delim) {
-  con <- unz(zip_file, Flnm)  # Corrected the file path within the zip archive
+  con <- unz(zip_file, Flnm)  # Connect to the file path within the zip archive
   data <- read.table(con, skip = Skip, encoding = FileEncode, sep = Delim, header = FALSE)
@@
 
-# Import and prepare files
-
+# Import and tidy columns
 ```{r filename separation, warning = FALSE, echo=FALSE}
@@
   mutate(Filename = str_remove(Filename, pattern = " "))  %>% 
-  separate(col = Filename, into = c("ObsDate", "Strain", "Par_ue", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE) %>% 
+  separate(col = Filename, into = c("ObsDate", "MultiCulti", "Par_ue", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE) %>% 
   mutate(FilenameJaz=Filename) %>% 
@@
 
-# Select wavelength range from 400 to 700 nm
-
+# Select wavelength range from 350 to 750 nm
 ```{r select range of nm}
 JazSpecTrim <- JazSpec %>% 
-  subset(JazSpec$Wavelength >= 400 & JazSpec$Wavelength <= 701)
+  subset(JazSpec$Wavelength >= 350 & JazSpec$Wavelength <= 750)
 ```
@@
 # Remove all NA columns & empty rows, fix column types
-
 ```{r remove empty rows and fix column types}
@@
 # Find nm at max count and compare with rolling mean of counts
-
 ```{r find nm at max count}
 JazSpecTrim <- JazSpecTrim %>% 
-  group_by(WL, Strain) %>%
+  group_by(WL, MultiCulti) %>%
    mutate(rollmeanCounts = zoo::rollmean(Counts, k = RollWindow, align = "left", fill = NA),
-          is_nm = round(Wavelength[which.max(Counts)]),
-          is_nm_rollmean= round(Wavelength[which.max(rollmeanCounts)])) %>% 
+          EmMax_nm = round(Wavelength[which.max(Counts)]),
+          EmMax_nm_rollmean= round(Wavelength[which.max(rollmeanCounts)])) %>% 
   ungroup()
@@
 
+# Nest data for each MC emission wavelenth
+```{r nest the spectral data}
+
+JazSpecNest <- JazSpecTrim %>%
+  nest(Spectra = c(Wavelength, Counts, rollmeanCounts))
+
+```
+
+```{r remove redundant DF}
+remove(JazSpecTrim)
+remove(JazSpec)
+```
+
+# Plot to confirm data tidy
+```{r Prelim plot}
+
+# Adding the maximum (peak) value in ggplot for geom_smoth
+# https://stackoverflow.com/questions/71162252/adding-the-maximum-peak-value-in-ggplot-for-geom-smooth
+
+JazSpecNest %>%
+  unnest(Spectra) %>%
+    ggplot() +
+  geom_point(aes(x = Wavelength, y = Counts, colour = as.factor(WL))) +
+  geom_text(aes(x = EmMax_nm, y= max(Counts), label= EmMax_nm), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
+  scale_color_manual(values = MCMIXColours) +
+  guides(colour = "none") +
+  geom_vline(aes(xintercept = EmMax_nm), linetype = "dashed") +
+  scale_y_continuous(limits = c(0,100000)) +
+  ggh4x::facet_nested(rows = vars(MultiCulti, WL), labeller = labeller(WL = label_both, Par = label_both, MultiCulti = label_both)) +
+  theme_bw() 
+```
+
 # Cleaning df before saving as rds and removed unnecessary files from the environment
-
 ```{r cleaning JazSpecTrim for final rds}
-JazSpecTrim<-JazSpecTrim %>% 
+JazSpecNest <- JazSpecNest %>% 
   select(-c(CDateTime))
 
-colnames(JazSpecTrim)
+colnames(JazSpecNest)
 ```

### 2024-01-03 Code/Import_JazEmData.Rmd
Fixed code and nested df before saving .rds

@@
 # Set the path to the zip folder
-zip_file <- file.path("..", "Data", "RawData", "JazEmData.zip")
+DataIn <- file.path("..", "Data", "RawData", "JazEmData.zip")
+
+RollWindow <- 10
 
 # List files in the extracted folder with a ".txt" extension
-Jazfile <- unzip(zip_file, list = TRUE)
+Jazfile <- unzip(DataIn, list = TRUE)
 Jazfile <- Jazfile[grepl(".txt$", Jazfile$Name), "Name"]
 print(Jazfile)
+```
+# Import MultiCulti actinic par data
+```{r read multiculti PAR data}
+
+TargetFile <- "MultiCulti_PAR.csv"
+
+MultiCultiPAR <- read_csv(unz(DataIn, TargetFile)) %>% 
+  rename(MultiCulti = "Multiculti")
 ```
@@
 DelimCS <- "\t"
-RollWindow <- 10
 
@@
 fread_plus <- function(Flnm, Skip, FileEncode, Delim) {
-  con <- unz(zip_file, Flnm)  # Connect to the file path within the zip archive
+  con <- unz(DataIn, Flnm)  # Connect to the file path within the zip archive
   data <- read.table(con, skip = Skip, encoding = FileEncode, sep = Delim, header = FALSE)
@@
   data <- data %>%
-    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(zip_file)$ctime)) 
+    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(DataIn)$ctime)) 
   return(data)
@@
 
-# Import and tidy columns
+# Import and tidy emission data columns
 ```{r filename separation, warning = FALSE, echo=FALSE}
@@
 
-# Find nm at max count and compare with rolling mean of counts
+# Find nm at max count
 ```{r find nm at max count}
@@
   group_by(WL, MultiCulti) %>%
-   mutate(rollmeanCounts = zoo::rollmean(Counts, k = RollWindow, align = "left", fill = NA),
-          EmMax_nm = round(Wavelength[which.max(Counts)]),
-          EmMax_nm_rollmean= round(Wavelength[which.max(rollmeanCounts)])) %>% 
+   mutate(EmMax_nm = round(Wavelength[which.max(Counts)])) %>% 
   ungroup()
+```
+
+# Get 1 mean emission count for each wavelength after rounding for a resolution of 1 nm   
+```{r tidy to get one count for each wavelength}
+JazSpecTrim <- JazSpecTrim %>% 
+   group_by(MultiCulti, Par_ue, WL, Wavelength) %>%
+  mutate(MCEm_nm = round(Wavelength)) %>%
+  ungroup() %>%
+  group_by(FilenameJaz, MultiCulti, Par_ue, WL, MCEm_nm, EmMax_nm, ObsDate) %>%
+  summarise(MeanEmission = mean(Counts)) %>%
+  ungroup() %>%
+  mutate(Emission = round(MeanEmission, digits = 1),
+         MC = MultiCulti,
+         SetPar_uE = Par_ue,
+         MC_SpectralID = paste(MC,WL, sep = "_")) %>% 
+  select(-c(MeanEmission))
+
+```
+
+# Join MulitiCulti par data with emission data
+```{r join par with spectral data}
+MC_SpectraPAR <- left_join(JazSpecTrim, MultiCultiPAR, by = c("WL" = "Actinic_nm", "SetPar_uE", "MC" = "MultiCulti")) %>%
+  rename(MCSetPar_uE = 'SetPar_uE',
+         MCMeasuredPar_uE = 'MeasuredPar_uE') %>% 
+  select(-c(Par_ue, MultiCulti, Date))
+
 ```
@@
 
-JazSpecNest <- JazSpecTrim %>%
-  nest(Spectra = c(Wavelength, Counts, rollmeanCounts))
+JazSpecNest <- MC_SpectraPAR %>%
+  nest(Spectra = c(MCEm_nm, Emission))
 
+colnames(JazSpecNest)
 ```
@@
 remove(JazSpec)
+remove(MC_SpectraPAR)
+remove(MultiCultiPAR)
 ```
@@
     ggplot() +
-  geom_point(aes(x = Wavelength, y = Counts, colour = as.factor(WL))) +
-  geom_text(aes(x = EmMax_nm, y= max(Counts), label= EmMax_nm), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
+  geom_point(aes(x = MCEm_nm, y = Emission, colour = as.factor(WL))) +
+  geom_text(aes(x = EmMax_nm, y= max(Emission), label= EmMax_nm), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
   scale_color_manual(values = MCMIXColours) +
@@
   scale_y_continuous(limits = c(0,100000)) +
-  ggh4x::facet_nested(rows = vars(MultiCulti, WL), labeller = labeller(WL = label_both, Par = label_both, MultiCulti = label_both)) +
+  ggh4x::facet_nested(rows = vars(MC, WL), labeller = labeller(WL = label_both, Par = label_both, MultiCulti = label_both)) +
   theme_bw()
-```
 
-# Cleaning df before saving as rds and removed unnecessary files from the environment
-```{r cleaning JazSpecTrim for final rds}
-JazSpecNest <- JazSpecNest %>% 
-  select(-c(CDateTime))
-
-colnames(JazSpecNest)
-```
-
-```{r removed unnecessary files from environment}
-rm(JazSpec)
 ```
@@
 ```{r save rds}
-saveRDS(JazSpecTrim, file.path(DataOut, paste(Project, "Imported_JazEmData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
+saveRDS(JazSpecNest, file.path(DataOut, paste(Project, "Imported_JazEmData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
 ```
@@
 ```{r}
-colnames(JazSpecTrim)
+colnames(JazSpecNest)
 ```

### 2024-01-04 Code/Import_OlisData.Rmd
Tidied scripts

@@
 author:
+- Douglas A. Campbell
+- Sarah Gore
+- Adrian Kryk
 - Sylwia Sliwinska-Wilczewska
-- Douglas A. Campbell
+- Mireille Savoie
 date: "`r format(Sys.Date())`"
@@
 library(zoo)
-library(googledrive)
-library(googlesheets4)
 library(readxl)
@@
 ```{r set project variables, read zipped files, list available files, warning = FALSE, echo=FALSE}
-Project <- "Baltic_Photoperiod"
+Project <- "PICO"
 DataOut <- file.path("..", "Data", "ImportedData", "ImportedOlisData")
@@
 # Set the path to the zip folder and the destination folder
-zip_file <- file.path("..", "Data", "RawData", "OlisData.zip")
+DataIn <- file.path("..", "Data", "RawData", "OlisData.zip")
 
 #List files in the extracted folder with a ".asc" extension
-OlisFiles <- unzip(zip_file, list = TRUE)
+OlisFiles <- unzip(DataIn, list = TRUE)
 OlisFiles <- OlisFiles[grepl(".asc$", OlisFiles$Name), "Name"]
@@
 Delimiter <- ""
-headerrows <- 0
+HeaderRows <- 0
 ```
@@
 # Set up fread_plus and read.delim_long function
-
 ```{r set up fread_plus and read.delim_long, warning = FALSE, echo=FALSE}
@@
 fread_plus <- function(Flnm, Skip, FileEncode, Delim) {
-  con <- unz(zip_file, Flnm)  # Corrected the file path within the zip archive
-  data <- read.table(con, skip = Skip, encoding = FileEncode, sep = Delim, header = TRUE, row.names = NULL)
+  con <- unz(DataIn, Flnm)  # Corrected the file path within the zip archive
+  data <- read.table(con, skip = Skip, encoding = FileEncode, sep = Delim, header = FALSE, row.names = NULL)
 
@@
 #read.delim_long meant for map over a vector of filepaths to read, convert to long format and tidy the imported data
-read.delim_long <- function(Flnm, FileEncode, Delimiter, headerrows){
-  read.delim(Flnm, encoding = FileEncode, sep = Delimiter, skip = headerrows, header = TRUE, row.names = NULL) %>%
+read.delim_long <- function(Flnm, FileEncode, Delimiter, HeaderRows){
+  read.delim(Flnm, encoding = FileEncode, sep = Delimiter, skip = HeaderRows, header = FALSE, row.names = NULL) %>%
   mutate(Filename = flnm, CDateTime = ymd_hms(file.info(flnm)$ctime)) %>%
-  rename(nm = OLIS.3D.ASCII) %>%
   mutate(FirstLastSpec = str_extract(Filename, "_[A-Z][a-z][A-Z][a-z][:digit:][:digit:][:digit:][:digit:]_[A-Z][a-z][A-Z][a-z][:digit:][:digit:][:digit:][:digit:]_")) %>%
@@
 # Import and prepare files
-
 ```{r import OLIS Spectra corrected files, warning = FALSE, echo=FALSE}
 TargetFile <-  OlisFiles
+
 TargetSpectra <- TargetFile %>% 
-  map_df(~fread_plus(Flnm = ., FileEncode = FileEncode, Delim = Delimiter, Skip = headerrows)) %>% 
-  pivot_longer(., -c(`OLIS.3D.ASCII`, Filename, CDateTime), values_to = "Absorbance", names_to = "SampleID") %>%
-  filter(!is.na(Absorbance)) %>%
-  mutate(nm = `OLIS.3D.ASCII`) %>% 
-  select(-c(`OLIS.3D.ASCII`))
+  map_df(~fread_plus(Flnm = ., FileEncode = FileEncode, Delim = Delimiter, Skip = HeaderRows)) %>% 
+  rename(OlisAbs_nm = `V1`,
+          Absorbance = `V2`) %>% 
+  filter(!is.na(Absorbance))
 
@@
 TargetSpectraLong <- TargetSpectraLong %>%
-  mutate(FilenameOlis=Filename) %>% 
-  mutate(ObsDate = ymd(`ObsDate`)) %>% 
-  select(-c(Type, Correction, Smooth, Project, Filename)) 
+  mutate(FilenameOlis = Filename) %>% 
+  mutate(ObsDate = ymd(str_extract(ObsDate, "202[:digit:][:digit:][:digit:][:digit:][:digit:]"))) %>% 
+  select(-c(Type, Correction, Smooth, Project, Filename, Range)) 
 ```
@@
 # Read MetaData
-
 ```{r read locally stored metadata from rds}
@@
 
-CultureCatalog<-CultureCatalog %>% 
-  select(-c(PrimaryOperator, Temp_c, ExpCul, ExpStartTime, O2_Category, Optode, OptodeCh, OptodeMeasure))
+CultureCatalog <- CultureCatalog %>% 
+  select(-c(PrimaryOperator, Temp_c, ExpCul, ExpStartTime, Optode, OptodeCh, OptodeMeasure))
 ```
@@
 # Merge OlisSpectra with MetaData
-
 ```{r merge OlisSpectra with MetaData, warning = FALSE, echo=FALSE}
 OLISSpectraMeta <- CultureCatalog %>%
-  left_join(., TargetSpectraLong, by = c("SampleID" = "SampleID"))
+  right_join(., TargetSpectraLong, by = c("SampleID" = "SampleID"))
 
@@
   mutate(E_days = as.numeric((ObsDate - ExpDate[1]))) %>%
-  mutate(SumAb = sum(Absorbance)) %>% 
+  filter(!is.na(MC)) %>%
+   select(-c(CDateTime)) %>% 
 ungroup()
 
-OLISSpectraMeta <- OLISSpectraMeta %>%
-  filter(nm >= 400 & nm <= 700)
 ```
 
-# Normalize spectra to 440 nm
-
-```{r normalization at 440, warning = FALSE, echo=FALSE}
-Absorbance440 <- OLISSpectraMeta %>% 
-  filter(nm == 440) %>%
-  mutate(Abs440 = Absorbance) %>%
-  select(SampleID, Strain, Abs440, Par_ue, Photoperiod, E_days)
-
-OLISSpectraMeta440 <- OLISSpectraMeta %>%
-  left_join(., Absorbance440) %>%
-  mutate(AbsNorm440 = Absorbance / Abs440)
-
-OLISSpectraMeta440 <- OLISSpectraMeta440 %>%
-group_by(SampleID, E_days, Par_ue, Photoperiod) %>%
-  mutate(SumAbNorm = sum(AbsNorm440)) %>% 
-ungroup()
-```
 # Cleaning df before saving as rds and removed unnecessary files from the environment
-
-```{r cleaning and ordering OLISSpectraMeta440 before creating rds}
-OLISSpectraMeta440<-OLISSpectraMeta440 %>% 
-  select(-c(CDateTime, Range)) 
+```{r nest absorbance spectra}
+OLISSpectraMeta <- OLISSpectraMeta %>% 
+  nest(AbsSpectra = c(OlisAbs_nm, Absorbance)) 
 ```
 
-```{r removed unnecessary df from the environment}
-rm(Absorbance440, CultureCatalog, TargetSpectra, OLISSpectraMeta, TargetSpectraLong)
+```{r removed redundant df }
+rm(CultureCatalog, TargetSpectra, TargetSpectraLong)
 ```
@@
 # Save rds for further analysis
-
 ```{r save rds}
-saveRDS(OLISSpectraMeta440, file.path(DataOut, paste(Project, "Imported_OlisData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
+saveRDS(OLISSpectraMeta, file.path(DataOut, paste(Project, "Imported_OlisData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
 ```
@@
 # Variable names used in Data Dictionary
-
 ```{r}
-colnames(OLISSpectraMeta440)
+colnames(OLISSpectraMeta)
 ```

### 2024-01-04 Code/Process_OlisJazEmData.Rmd
Fixing code to make this a script to merge and process Olis absorbance and MC emission data.

@@
 library(photobiologyWavebands)
-library(reshape2)
+# library(reshape2)
 library(photobiology)
-library(gcookbook)
+# library(gcookbook)
 ```
@@
 
-FileEncode <- "UTF-8" 
-Delimiter <- ""
-HeaderRows <- 0
 ```
 
-# List and read imported Olis and Jaz files
+# List imported Olis and Jaz files
+```{r exported Rmd only first time in session}
+list.files(path = DataInOlis, pattern = ".Rds", full.names = TRUE)
+list.files(path = DataInJaz, pattern = ".Rds", full.names = TRUE)
+```
+# Read Olis whole cell absorbance and MultiCulti Jaz emission files
+```{r read imported Olis and Jaz file}
+OLISSpectraFile <- readRDS(file = file.path(DataInOlis,"PICO_Imported_OlisData.Rds"))
 
-```{r exported Rmd only first time in session}
-list.files(path = DataInOlis, pattern = Project, full.names = TRUE)
-list.files(path = DataInJaz, pattern = Project, full.names = TRUE)
+JazEmFile <- readRDS(file = file.path(DataInJaz,"PICO_Imported_JazEmData.Rds"))
 ```
 
-```{r read imported Olis file}
-OLISSpectraFile <- "../Data/ImportedData/ImportedOlisData/Baltic_Photoperiod_Imported_OlisData.Rds"
-OLISSpectraFileName <- str_split(string = OLISSpectraFile, "/")[[1]][3] %>%
-  str_remove(pattern = ".Rds")
-OLISSpectra <- readRDS(OLISSpectraFile)  %>%
-  ungroup()
-
-JazFile <- "../Data/ImportedData/ImportedJazEmData/Baltic_Photoperiod_Imported_JazEmData.Rds"
-JazFileName <- str_split(string = JazFile, "/")[[1]][3] %>%
-  str_remove(pattern = ".Rds")
-JazData <- readRDS(JazFile)  %>%
+#Left off here
+```{r}
+JazEmFile <- JazEmFile %>% 
+  filter(MC_SpectralID != "MCMIX004_WW",
+         MCSetPar_uE == 30 ) %>% 
+  select(-c( FilenameJaz, MC)) %>% 
+  unnest(Spectra) %>%  
+  group_by(WL) %>% 
+  mutate(MC_NormEm = round(Emission / Emission[which.max(Emission)], digits = 4)) %>% 
 ungroup()
@@
 # Preparing df for further analysis
-
 ```{r round nm}

### 2024-01-04 Code/Process_OlisJazEmData.Rmd
Fixing more code to include all WL normalization.

@@
 
-#Left off here
-```{r}
+# Filter out the white light emission data for mixed light color MC since not used. Calculate MC normalized emission to the emission maxima for each wavelength.
+```{r calculate normalized emission for each WL}
 JazEmFile <- JazEmFile %>% 
   filter(MC_SpectralID != "MCMIX004_WW",
-         MCSetPar_uE == 30 ) %>% 
+         MCSetPar_uE == 30 |
+         MCSetPar_uE == 15) %>% 
   select(-c( FilenameJaz, MC)) %>% 
@@
   mutate(MC_NormEm = round(Emission / Emission[which.max(Emission)], digits = 4)) %>% 
+  select(-c(ObsDate)) %>% 
 ungroup()
+```
+
+# Unnest the Olis whole cell absorbance data and calculate absorbance maxima for 675 nm (red) and 450 (blue) and extract nm (wavelength) at maxima 
+```{r}
+OLISSpectraUnnest <- OLISSpectraFile %>% 
+  unnest(AbsSpectra)
+
+OlisSpectra_red <- OLISSpectraUnnest %>% 
+  group_by(SampleID, E_days) %>%
+  filter(OlisAbs_nm >= 575 & OlisAbs_nm <= 750) %>% 
+   mutate(Red_nm = round(OlisAbs_nm[which.max(Absorbance)]),
+          MaxAbs_Red = Absorbance[which.max(Absorbance)]) %>% 
+  filter(OlisAbs_nm == 675) %>% 
+  select(SampleID, Run, Strain, Red_nm, MaxAbs_Red, Par_ue, E_days) %>% 
+     ungroup()
+
+OlisSpectra_blue <- OLISSpectraUnnest %>% 
+  group_by(SampleID, E_days) %>%
+  filter(OlisAbs_nm >= 400 & OlisAbs_nm <= 460) %>% 
+   mutate(Blue_nm = round(OlisAbs_nm[which.max(Absorbance)]),
+          MaxAbs_Blue = Absorbance[which.max(Absorbance)])  %>% 
+  filter(OlisAbs_nm == 440) %>% 
+  select(SampleID, Run, Strain, Blue_nm, MaxAbs_Blue,  Par_ue, E_days) %>% 
+  ungroup()
+
+OLISSpectraFile <- OLISSpectraFile %>%
+  group_by(SampleID, E_days) %>%
+  nest(AbsSpectra = c(OlisAbs_nm, Absorbance))
+
+ OlisSpectraMeta_red <- left_join(OLISSpectraFile, OlisSpectra_red)
+
+```
+
+# Left join Olis whole cell absorbance data with Jaz MC emission data. Emission measurements were performed on the mixed color MCMIX004 and the white light MC257
+```{r join whole cell absorbance with MC emission data}
+
+OlisJazMetaData <- left_join(OLISSpectraFile , JazEmFile, by = c("WL", "OlisAbs_nm" = "MCEm_nm")) %>% 
+  mutate(MCEm_nm = OlisAbs_nm)
 ```

### 2024-01-05 Code/Process_OlisJazEmData.Rmd
Fixing variable names so that Baltic and PICO projects are same

--- 2024-01-04 Code/Process_OlisJazEmData.Rmd
@@
   mutate(MC_NormEm = round(Emission / Emission[which.max(Emission)], digits = 4)) %>% 
+  select(-c(ObsDate)) %>% 
 ungroup()
 ```
+
+# Unnest the Olis whole cell absorbance data and extract absorbance maxima for 675 nm (red) and 450 (blue) regions and extract nm (wavelength) at that absorbance maxima 
+```{r}
+OLISSpectraUnnest <- OLISSpectraFile %>% 
+  unnest(AbsSpectra)
+
+OlisSpectra_red <- OLISSpectraUnnest %>% 
+  group_by(SampleID, E_days) %>%
+  filter(OlisAbs_nm >= 625 & OlisAbs_nm <= 750) %>% 
+   mutate(RedMaxima_nm = round(OlisAbs_nm[which.max(Absorbance)]),
+          MaxAbs_Red = Absorbance[which.max(Absorbance)]) %>% 
+  filter(OlisAbs_nm == 675) %>% # filter only 675 nm to get df that matches the nested df to join
+  select(SampleID, Run, Strain, RedMaxima_nm, MaxAbs_Red, Par_ue, E_days) %>% 
+     ungroup()
+
+OlisSpectra_blue <- OLISSpectraUnnest %>% 
+  group_by(SampleID, E_days) %>%
+  filter(OlisAbs_nm >= 400 & OlisAbs_nm <= 460) %>% 
+   mutate(BlueMaxima_nm = round(OlisAbs_nm[which.max(Absorbance)]),
+          MaxAbs_Blue = Absorbance[which.max(Absorbance)])  %>% 
+  filter(OlisAbs_nm == 440) %>% # filter only 440 nm to get df that matches the nested df to join
+  select(SampleID, Run, Strain, BlueMaxima_nm, MaxAbs_Blue,  Par_ue, E_days) %>% 
+  ungroup()
+
+ OlisSpectraMeta <- left_join(OLISSpectraFile, OlisSpectra_red)
+ OlisSpectraMeta <- left_join(OlisSpectraMeta, OlisSpectra_blue)
+
+remove(OlisSpectra_red)
+remove(OlisSpectra_blue)
+remove(OLISSpectraUnnest)
+
+```
+
+# Left join Olis whole cell absorbance data with Jaz MC emission data. Emission measurements were performed on the mixed color MCMIX004 and the white light MC257
+```{r join whole cell absorbance with MC emission data}
+
+OlisSpectraMeta <- OlisSpectraMeta %>% 
+  unnest(AbsSpectra)
+
+OlisJazMetaData <- left_join(OlisSpectraMeta, JazEmFile, by = c("WL", "OlisAbs_nm" = "MCEm_nm")) %>% 
+  mutate(MCEm_nm = OlisAbs_nm)
+
+remove(OlisSpectraMeta)
+remove(JazEmFile)
+remove(OLISSpectraFile)
+```
+
+# Normalization. Used max peak of each spectra to normalize peaks to red Chla region (625 to 750 nm) and blue Chla region (400 to 460 nm).
+```{r normalization }
+
+OlisJazMetaData <- OlisJazMetaData %>% 
+  group_by(SampleID, E_days) %>%
+ mutate(AbsNorm440 = Absorbance / MaxAbs_Blue,
+        AbsNorm675 = Absorbance / MaxAbs_Red) %>% 
+  ungroup()
+
+glimpse(OlisJazMetaData)
+```
+
+# Calculate Photosynthetic Usable Radiation (PUR) from MC normalized emission and normalized Olis whole cell absorbance spectrums.  
+```{r PUR}
+OlisJazMetaData <- OlisJazMetaData %>%
+    filter(OlisAbs_nm >= 400 &
+           OlisAbs_nm <= 700) %>%
+  mutate(PURAbsWholeCell_Norm = MC_NormEm * AbsNorm440) %>% 
+  group_by(ID, E_days) %>% 
+  mutate(SumPURAbsWholeCell_Norm = sum(MC_NormEm * AbsNorm440),
+         Pur_ue = round(Par_ue * (SumPURAbsWholeCell_Norm / sum(MC_NormEm))),
+         ParPurRatio = sum(MC_NormEm) / SumPURAbsWholeCell_Norm,
+         PurParRatio =  SumPURAbsWholeCell_Norm / sum(MC_NormEm)) %>% 
+ungroup() %>% 
+  select(-SumPURAbsWholeCell_Norm)
+
+glimpse(OlisJazMetaData)
+
+```
+
+# Calculate daily PUR photon dose
 

### 2024-01-08 Code/Process_OlisJazEmData.Rmd
Finalized rmd such that it can be used by any project.

@@
 ---
-title: "Process_OlisSpectraJazEmData"
+title: "Process_OlisJazEmData"
 author:
+- Mireille Savoie
 - Sylwia Sliwinska-Wilczewska
@@
 library(lubridate)
-library(stringr)
+# library(stringr)
 library(broom)
 library(knitr)
-library(OneR)
+# library(OneR)
 library(zoo)
-library(strucchange)
-library(ggspectra)
-library(ggpubr)
-library(caret)
+# library(strucchange)
+# library(ggspectra)
+# library(ggpubr)
+# library(caret)
 library(photobiologyWavebands)
 # library(reshape2)
-library(photobiology)
+# library(photobiology)
 # library(gcookbook)
@@
 ```{r set project variables}
-Project <- "Baltic_Photoperiod"
+
+Project <- "PICO"
 DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedOlisJazData")
@@
 PlotsPath <- file.path("..", "Output", "Plots")
-RDSPlotPath <- file.path("..", "Output", "PlotsRDS")
+
+SectoHour <- 3600 #convert seconds to hours for PUR photon dose per day
 
@@
   mutate(MC_NormEm = round(Emission / Emission[which.max(Emission)], digits = 4)) %>% 
-  select(-c(ObsDate)) %>% 
+  select(-c(ObsDate, MCSetPar_uE, MC_SpectralID, MCMeasuredPar_uE)) %>% 
 ungroup()
@@
 ```{r PUR}
-OlisJazMetaData <- OlisJazMetaData %>%
+OlisJazMetaPUR <- OlisJazMetaData %>%
     filter(OlisAbs_nm >= 400 &
            OlisAbs_nm <= 700) %>%
-  mutate(PURAbsWholeCell_Norm = MC_NormEm * AbsNorm440) %>% 
-  group_by(ID, E_days) %>% 
-  mutate(SumPURAbsWholeCell_Norm = sum(MC_NormEm * AbsNorm440),
-         Pur_ue = round(Par_ue * (SumPURAbsWholeCell_Norm / sum(MC_NormEm))),
-         ParPurRatio = sum(MC_NormEm) / SumPURAbsWholeCell_Norm,
-         PurParRatio =  SumPURAbsWholeCell_Norm / sum(MC_NormEm)) %>% 
+  mutate(PURAbsWholeCell_Norm440 = MC_NormEm * AbsNorm440) %>% 
+  group_by(SampleID, E_days) %>% 
+  mutate(SumPURAbsWholeCell_Norm440 = sum(MC_NormEm * AbsNorm440),
+         CalcPur_ue = round(Par_ue * (SumPURAbsWholeCell_Norm440 / sum(MC_NormEm))),
+         CalcPurParRatio = round(CalcPur_ue / Par_ue, 3)) %>% 
 ungroup() %>% 
-  select(-SumPURAbsWholeCell_Norm)
+  select(-SumPURAbsWholeCell_Norm440)
 
-glimpse(OlisJazMetaData)
+remove(OlisJazMetaData)
+glimpse(OlisJazMetaPUR)
 
@@
 
-# Calculate daily PUR photon dose
+# Find Strain specific average PUR for each spectral color and each growth PAR
+```{r Calc mean PUR}
 
-# Preparing df for further analysis
-```{r round nm}
-JazData <- JazData %>%
-   mutate(WavelengthRound = round(Wavelength))
-colnames(JazData)
-
-JazDataRound <- JazData %>%
-group_by(FilenameJaz, WavelengthRound) %>%
-  summarize(Counts, FilenameJaz, ObsDate, Strain, Par_ue, WL, WavelengthRound, CountsMean = mean(Counts)) %>%
+OlisJazMetaPUR <- OlisJazMetaPUR %>%
+  group_by(Strain, WL) %>% 
+  mutate(PurParRatio = (mean(CalcPurParRatio)))%>% 
 ungroup()
 
-JazDataRound <- JazDataRound %>%
-  summarize(FilenameJaz, Strain, Par_ue, WL, WavelengthRound, CountsMean) %>%
-  unique()
+OlisJazMetaPUR <- OlisJazMetaPUR %>%
+  group_by(Strain, WL, Par_ue) %>% 
+  mutate(Pur_ue = round(mean(CalcPur_ue)))%>% 
+ungroup()  %>% 
+  select(-c(CalcPurParRatio, CalcPur_ue))
 
-JazDataRound <- JazDataRound %>%
-  filter(WavelengthRound >= 400 & WavelengthRound <= 700)
-```
-
-# Normalize Jaz emission to 439 nm
-
-```{r Normalization Jaz emission at 439}
-EmissionJazWW <- JazDataRound %>%
-  group_by(WL, Strain, Par_ue) %>%
-  filter(WavelengthRound == 439) %>%
-  mutate(EmJaz439 = CountsMean) %>%
-  select(Strain, EmJaz439, Par_ue) %>%
-  ungroup()
-
-JazDataRoundMeta <- JazDataRound %>%
-  left_join(., EmissionJazWW) %>%
-  mutate(EmNormJaz439 = CountsMean / EmJaz439)
-```
-
-# Merge Olis and Jaz data
-
-```{r combine Olis spectra and Jaz data}
-OLISSpectraMeta <- OLISSpectra %>%
-  left_join(., JazDataRoundMeta, by = c("Par_ue" = "Par_ue", "nm" = "WavelengthRound", "Strain" = "Strain", "WL" = "WL")) %>%
-  unique()
-```
-
-# Estimate PUR
-
-```{r estimate PUR}
-OLISSpectraMetaPUR <- OLISSpectraMeta %>%
-  mutate(PURNorm = (AbsNorm440*EmNormJaz439)) %>% 
-  group_by(WL, Strain, Par_ue, Photoperiod, E_days) %>%
-  mutate(PURNormSum = sum(PURNorm)) %>% 
-  mutate(SumEmNormJaz439 = sum(EmNormJaz439)) %>% 
-  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz439)) %>% 
-  ungroup() 
+glimpse(OlisJazMetaPUR)
 ```
@@
 # Calculate daily PUR photon dose
+```{r calculate PUR Photon dose}
 
-```{r calculate PUR Photon dose}
-OLISSpectraMetaPUR1 <- OLISSpectraMetaPUR %>%
-  filter(Photoperiod != "24") %>% 
-  mutate(PURPhotonDose_day =(PUR/2)*Photoperiod*3600)
+OlisJazMetaPUR <- OlisJazMetaPUR %>%
+ mutate(PURPhotonDose_day = case_when(LightShape == 'Sine' ~ Pur_ue/2 * SectoHour * Photoperiod,
+                                  LightShape == 'Square' ~ Pur_ue * SectoHour * Photoperiod))
 
-OLISSpectraMetaPUR2 <- OLISSpectraMetaPUR %>%
-  filter(Photoperiod == "24") %>% 
-  mutate(PURPhotonDose_day = PUR*Photoperiod*3600)
-
-  OLISSpectraMetaPUR <-rbind(OLISSpectraMetaPUR1, OLISSpectraMetaPUR2)
-  rm(OLISSpectraMetaPUR1,OLISSpectraMetaPUR2)
+glimpse(OlisJazMetaPUR)
 ```
 
-# Filter unrevelant data
+# Nest whole cell absorbance and emission data
+```{r Nest spectra data}
 
-```{r filter unrevelant data}
-OLISSpectraMetaPUR<-OLISSpectraMetaPUR %>% 
-  filter(PUR>=0) %>% 
-  filter(PUR<=900)
+OlisJazMetaPUR <- OlisJazMetaPUR %>% 
+  group_by(SampleID, E_days) %>% 
+  nest(PurData = c(OlisAbs_nm, Absorbance, AbsNorm440, AbsNorm675, PURAbsWholeCell_Norm440, BlueMaxima_nm, MaxAbs_Blue, RedMaxima_nm, MaxAbs_Red, MCEm_nm, Emission, MC_NormEm, EmMax_nm))
+
+glimpse(OlisJazMetaPUR)
 ```
 
-# Preparing df for creating representative plot
+# Save nested rds for further analysis
+```{r save rds}
+saveRDS(OlisJazMetaPUR, file.path(DataOut, paste(Project, "Processed_OlisJazMetaPUR.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
 
-```{r preparing selected data for creating representative plot}
-OLISSpectraMetaPURShortBA127R<- OLISSpectraMetaPUR %>%
-  filter(Photoperiod == "12") %>% 
-  filter(Strain == "BA127R") %>% 
-  filter(Par_ue == 300) %>% 
-  filter(E_days == "4" | E_days == "8") %>% 
-  mutate(E_days=case_when(E_days==4~3,
-         E_days==8~7)) %>% 
-  mutate(PURNormBA127R = PURNorm) %>% 
-  select(-c(PURNorm, FilenameJaz, FilenameOlis))
-
-OLISSpectraMetaPURShortBA77G<- OLISSpectraMetaPUR %>%
-  filter(Photoperiod == "12") %>% 
-  filter(Strain == "BA77G") %>% 
-  filter(Par_ue == 300) %>% 
-  filter(E_days == "3" | E_days == "7") %>% 
-  mutate(PURNormBA77G = PURNorm) %>% 
-  select(-c(PURNorm, FilenameJaz, FilenameOlis))
-
-OLISSpectraMetaPURShort <- OLISSpectraMetaPURShortBA127R %>%
-  full_join(., OLISSpectraMetaPURShortBA77G, by = c("SampleID" = "SampleID", "Run" = "Run", "Strain" = "Strain", "ExpDate" = "ExpDate", "Par_ue" = "Par_ue", "Photoperiod" = "Photoperiod", "MC"="MC", "Tube" = "Tube", "O2" = "O2", "WL" = "WL", "LightShape" = "LightShape", "ExpEndDate"="ExpEndDate", "nm" = "nm", "ObsDate" = "ObsDate", "Absorbance" = "Absorbance", "SumAb" = "SumAb", "Abs440" = "Abs440", "AbsNorm440" = "AbsNorm440", "SumAbNorm" = "SumAbNorm", "E_days" = "E_days", "CountsMean" = "CountsMean", "EmJaz439" = "EmJaz439", "EmNormJaz439" = "EmNormJaz439", "PURNormSum" = "PURNormSum", "SumEmNormJaz439" = "SumEmNormJaz439", "PUR" = "PUR", "PURPhotonDose_day" = "PURPhotonDose_day", "PARPhotonDose_day" = "PARPhotonDose_day"))
 ```
-
-```{r Changes strain names}
-OLISSpectraMetaPURShort <- OLISSpectraMetaPURShort %>%
-      mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
-         Strain=="BA48R"~"PE-rich_048",
-        Strain=="BA56G"~"PC-rich_056",
-         Strain=="BA77G"~"PC-rich_077"))
-```
-
-# Create plot
-
-```{r Create plot, fig.height = 10, fig.width = 8}
-Par_ue.labs <- c("30 µE", "90 µE", "180 µE", "Phase of growth", "900 µE")
-names(Par_ue.labs) <- c("30", "90", "180", "300", "900")
-
-Photoperiod.labs <- c("8 h", "Photoperiod: 12 h", "16 h", "24 h")
-names(Photoperiod.labs) <- c("8", "12", "16", "24")
-
-E_days.labs <- c("Exponential", "Pre-stationary")
-names(E_days.labs) <- c("3", "7")
-
-Strain.labs <- c("PC-rich", "PE-rich")
-names(Strain.labs) <- c("PC-rich_077", "PE-rich_127")
-
-O2.labs <- c("Strain")
-names(O2.labs) <- c(21)
-
-data_textPUR0 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PAR = 300 µE', 'PAR = 300 µE'))
-
-data_textPUR00 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PC-rich_077", "PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PAR = 300 µE', 'PAR = 300 µE'))
-
-data_textPUR1 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PUR = 176 µE', 'PUR = 129 µE'))
-
-data_textPUR2 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PC-rich_077", "PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PUR = 139 µE', 'PUR = 128 µE'))
-
-data_textpigment1 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 440 nm'))
-data_textpigment3 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 680 nm'))
-data_textpigment4 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PC 620 nm'))
-data_textpigment5 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('Car 480 nm'))
-data_textpigment6 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PC-rich_077"), Photoperiod = c(12), O2 = c(21), label = c('PUB 500 nm'))
-
-arrowdf1 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
-arrowdf3 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
-arrowdf4 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
-arrowdf5 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
-arrowdf6 <- tibble(Strain = "PC-rich_077", E_days = 3, Par_ue = 300, O2 = c(21))
-
-data_textpigment7 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 440 nm'))
-data_textpigment8 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('Car 480 nm'))
-data_textpigment9 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PE 570 nm'))
-data_textpigment10 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('Chl a 680 nm'))
-data_textpigment11 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PC 620 nm'))
-data_textpigment12 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), O2 = c(21), label = c('PUB 500 nm'))
-
-arrowdf7 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
-arrowdf8 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
-arrowdf9 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
-arrowdf10 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
-arrowdf11 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
-arrowdf12 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300, O2 = c(21))
-
-OLISSpectraMetaPURShort %>%
-  filter(Photoperiod == "12") %>%
-  filter(Strain == "PC-rich_077" | Strain == "PE-rich_127") %>%
-  filter(Par_ue == 300) %>%
-  filter(E_days == "3" | E_days == "7") %>%
-  ggplot() +
-
-  geom_area(aes(x = nm, y = EmNormJaz439, fill = "gray84"), alpha = 0.6, show.legend = F) +
-  geom_area(aes(x = nm, y = PURNormBA127R, fill = "brown4"), alpha = 0.5, show.legend = F) +
-  geom_area(aes(x = nm, y = PURNormBA77G, fill = "palegreen3"), alpha = 0.5, show.legend = F) +
-  geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F, size = 0.4) +
-
-  geom_text(data=data_textPUR0, aes(x=446, y=1.26, label=label), size=3.7) +
-  geom_text(data=data_textPUR00, aes(x=446, y=1.26, label=label), size=3.7) +
-  geom_text(data=data_textPUR1, aes(x=446, y=1.21, label=label), size=3.7) +
-  geom_text(data=data_textPUR2, aes(x=446, y=1.21, label=label), size=3.7) +
-
-  geom_text(data=data_textpigment1, aes(x=500, y=1.1, label=label), size=4, colour = "darkgreen") + #chla440
-  geom_text(data=data_textpigment5, aes(x=500, y=0.8, label=label), size=4, colour = "orange") + #Car
-  geom_text(data=data_textpigment3, aes(x=650, y=1.2, label=label), size=4, colour = "darkgreen") +#chla680
-  geom_text(data=data_textpigment4, aes(x=590, y=0.95, label=label), size=4, colour = "deepskyblue4") + #PC
-  geom_text(data=data_textpigment6, aes(x=485, y=0.25, label=label), size=4, colour = "sienna4") + #PUB
-  geom_segment(data = arrowdf1,
-               aes(x = 480, xend = 445, y = 1.05, yend = 1),
-               colour = "darkgreen", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla440
-  geom_segment(data = arrowdf5,
-               aes(x = 480, xend = 475, y = 0.75, yend = 0.54),
-               colour = "orange", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #Car
-  geom_segment(data = arrowdf3,
-               aes(x = 660, xend = 680, y = 1.14, yend = 0.95),
-               colour = "darkgreen", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla680
-  geom_segment(data = arrowdf4,
-               aes(x = 610, xend = 630, y = 0.90, yend = 0.82),
-               colour = "deepskyblue4", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PC
-  geom_segment(data = arrowdf4,
-               aes(x = 480, xend = 494, y = 0.30, yend = 0.41),
-               colour = "sienna4", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PUB
-  geom_text(data=data_textpigment7, aes(x=500, y=1.1, label=label), size=4, colour = "darkgreen") + #chla440
-  geom_text(data=data_textpigment8, aes(x=500, y=0.8, label=label), size=4, colour = "orange") + #Car
-  geom_text(data=data_textpigment9, aes(x=580, y=1.0, label=label), size=4, colour = "darkmagenta") + #PE
-  geom_text(data=data_textpigment10, aes(x=650, y=1.2, label=label), size=4, colour = "darkgreen") +#chla680
-  geom_text(data=data_textpigment11, aes(x=600, y=0.17, label=label), size=4, colour = "deepskyblue4") + #PC
-  geom_text(data=data_textpigment12, aes(x=495, y=0.30, label=label), size=4, colour = "sienna4") + #PUB
-  geom_segment(data = arrowdf7,
-               aes(x = 480, xend = 445, y = 1.05, yend = 1),
-               colour = "darkgreen", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla440
-  geom_segment(data = arrowdf8,
-               aes(x = 480, xend = 475, y = 0.75, yend = 0.55),
-               colour = "orange", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #Car
-  geom_segment(data = arrowdf9,
-               aes(x = 590, xend = 575, y = 0.95, yend = 0.85),
-               colour = "darkmagenta", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PE
-  geom_segment(data = arrowdf10,
-               aes(x = 660, xend = 680, y = 1.14, yend = 0.85),
-               colour = "darkgreen", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla680
-  geom_segment(data = arrowdf11,
-               aes(x = 610, xend = 630, y = 0.2, yend = 0.3),
-               colour = "deepskyblue4", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PC
-  geom_segment(data = arrowdf12,
-               aes(x = 490, xend = 500, y = 0.35, yend = 0.52),
-               colour = "sienna4", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PUB
-  scale_color_manual(values = c("PC-rich_077" ="palegreen3", "PE-rich_127" ="brown4")) +
-  scale_linetype_manual(values = c("PC-rich_077" ="solid", "PE-rich_127" ="longdash")) +
-  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
-  scale_fill_identity() +
-  labs(y = "Normalized absorbance", x = "Wavelength (nm)") +
-  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
-  coord_cartesian(ylim = c (-0.01, 1.25)) +
-  ggh4x::facet_nested(cols = vars(Par_ue, E_days), rows = vars(O2, Strain),labeller = labeller(Ex_WL = label_both, WL = label_both, E_days = E_days.labs, Photoperiod = Photoperiod.labs, Par_ue = Par_ue.labs, Strain = Strain.labs, O2 = O2.labs, )) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        panel.spacing.x = unit(0.4, 'cm'),
-        axis.text = element_text(size=12),
-        axis.text.x = element_text(size=12),
-        axis.title = element_text(size=16),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=12),
-        axis.title.y = element_text(margin=margin(r=10)),
-        axis.title.x = element_text(margin=margin(t=10)),
-        legend.background = element_rect(fill="transparent"),
-        legend.title = element_blank(),
-        legend.direction="horizontal",
-        legend.position = c(0.08,0.97),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text.align = 0,
-        legend.key.width= unit(0.3, 'cm'),
-        legend.text = element_text(size=10))
-```
-
-# Save plot
-
-```{r save plot}
-ggsave(file = file.path(PlotsPath, paste("OlisSpectra_Plot",".png",sep = "")), height=10, width= 8,  dpi = 300, limitsize = TRUE)
-```
-
-```{r Create plot, fig.height = 6, fig.width = 8}
-
-Par_ue.labs <- c("30 µE", "90 µE", "180 µE", "Phase of growth", "900 µE")
-names(Par_ue.labs) <- c("30", "90", "180", "300", "900")
-
-Photoperiod.labs <- c("8 h", "Photoperiod: 12 h", "16 h", "24 h")
-names(Photoperiod.labs) <- c("8", "12", "16", "24")
-
-E_days.labs <- c("Exponential", "Pre-stationary")
-names(E_days.labs) <- c("3", "7")
-
-Strain.labs <- c("PE-rich_127", "PC-rich_077")
-names(Strain.labs) <- c("PE-rich_127", "PC-rich_077")
-
-data_textPUR0 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), label = c('PAR = 300 µE', 'PAR = 300 µE'))
-
-data_textPUR1 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), label = c('PUR (PE-rich) = 176 µE', 'PUR (PE-rich) = 129 µE'))
-
-data_textPUR2 <- data.frame(Par_ue = c(300, 300), E_days = c(3, 7), Strain  = c("PE-rich_127", "PE-rich_127"), Photoperiod = c(12), label = c('PUR (PC-rich) = 139 µE', 'PUR (PC-rich) = 128 µE'))
-
-data_textpigment1 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('Chl a 440 nm'))
-data_textpigment2 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('PE 570 nm'))
-data_textpigment3 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('Chl a 680 nm'))
-data_textpigment4 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('PC 620 nm'))
-data_textpigment5 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('Car 480 nm'))
-data_textpigment6 <- data.frame(Par_ue = c(300), E_days = c(3), Strain  = c("PE-rich_127"), Photoperiod = c(12), label = c('PUB 500 nm'))
-
-arrowdf1 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
-arrowdf2 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
-arrowdf3 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
-arrowdf4 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
-arrowdf5 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
-arrowdf6 <- tibble(Strain = "PE-rich_127", E_days = 3, Par_ue = 300)
-
-OLISSpectraMetaPURShort %>%
-  filter(Photoperiod == "12") %>%
-  filter(Strain == "PE-rich_127" | Strain == "PC-rich_077") %>%
-  filter(Par_ue == 300) %>%
-  filter(E_days == "3" | E_days == "7") %>%
-  ggplot() +
-  geom_area(aes(x = nm, y = EmNormJaz439, fill = "gray84"), alpha = 0.6, show.legend = F) +
-  geom_area(aes(x = nm, y = PURNormBA127R, fill = "brown4"), alpha = 0.5, show.legend = F) +
-  geom_area(aes(x = nm, y = PURNormBA77G, fill = "palegreen3"), alpha = 0.5, show.legend = F) +
-  geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F, size = 0.7) +
-
-  geom_text(data=data_textPUR0, aes(x=435, y=1.26, label=label), size=3.5) +
-  geom_text(data=data_textPUR1, aes(x=462, y=1.21, label=label), size=3.5) +
-  geom_text(data=data_textPUR2, aes(x=462, y=1.16, label=label), size=3.5) +
-
-  geom_text(data=data_textpigment1, aes(x=450, y=1.07, label=label), size=4, colour = "darkgreen") + #chla440
-  geom_text(data=data_textpigment5, aes(x=430, y=0.36, label=label), size=4, colour = "coral3") + #Car
-  geom_text(data=data_textpigment2, aes(x=520, y=0.92, label=label), size=4, colour = "darkmagenta") + #PE
-  geom_text(data=data_textpigment3, aes(x=660, y=1.08, label=label), size=4, colour = "darkgreen") +#chla680
-  geom_text(data=data_textpigment4, aes(x=605, y=1.0, label=label), size=4, colour = "deepskyblue4") + #PC
-  geom_text(data=data_textpigment6, aes(x=485, y=0.08, label=label), size=4, colour = "sienna4") + #PUB
-
-  geom_segment(data = arrowdf1,
-               aes(x = 470, xend = 440, y = 1.04, yend = 1.02),
-               colour = "darkgreen", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla440
-  geom_segment(data = arrowdf5,
-               aes(x = 450, xend = 470, y = 0.4, yend = 0.48),
-               colour = "coral3", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #Car
-  geom_segment(data = arrowdf2,
-               aes(x = 538, xend = 568, y = 0.88, yend = 0.86),
-               colour = "darkmagenta", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PE
-  geom_segment(data = arrowdf3,
-               aes(x = 697, xend = 680, y = 1.05, yend = 0.92),
-               colour = "darkgreen", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #chla680
-  geom_segment(data = arrowdf4,
-               aes(x = 632, xend = 630, y = 0.95, yend = 0.82),
-               colour = "deepskyblue4", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PC
-  geom_segment(data = arrowdf4,
-               aes(x = 465, xend = 500, y = 0.12, yend = 0.52),
-               colour = "sienna4", size = 1, alpha=0.9, arrow = arrow(length=unit(0.2, 'cm'))) + #PUB
-  scale_color_manual(values = c("PE-rich_127" ="brown4", "PC-rich_077" ="palegreen3")) +
-  scale_linetype_manual(values = c("PE-rich_127" ="longdash", "PC-rich_077" ="solid")) +
-  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) + 
-  scale_fill_identity() +
-  labs(y = "Normalized absorbance", x = "Wavelength (nm)") +
-  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
-  coord_cartesian(ylim = c (-0.01, 1.25)) +
-  ggh4x::facet_nested(cols = vars(Par_ue, E_days), labeller = labeller(Ex_WL = label_both, WL = label_both, E_days = E_days.labs, Photoperiod = Photoperiod.labs, Par_ue = Par_ue.labs, Strain = Strain.labs)) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        panel.spacing.x = unit(0.4, 'cm'),
-        axis.text = element_text(size=12),
-        axis.text.x = element_text(size=12),
-        axis.title = element_text(size=16),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=12),
-        axis.title.y = element_text(margin=margin(r=10)),
-        axis.title.x = element_text(margin=margin(t=10)),
-        legend.background = element_rect(fill="transparent"),
-        legend.title = element_blank(),
-        legend.direction="horizontal",
-        legend.position = c(0.08,0.97),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text.align = 0,
-        legend.key.width= unit(0.3, 'cm'),
-        legend.text = element_text(size=10))
-```
-
-# Cleaning df before saving as rds and removed unnecessary files from the environment
-
-```{r delete unused df from the environment}
-rm(data_textpigment1,data_textpigment2,data_textpigment3,data_textpigment4,data_textpigment5,data_textpigment6, data_textpigment7, data_textpigment8, data_textpigment9, data_textpigment10, data_textpigment11, data_textpigment12, arrowdf1,arrowdf2,arrowdf3,arrowdf4,arrowdf5,arrowdf6, arrowdf7, arrowdf8, arrowdf9, arrowdf10, arrowdf11, arrowdf12, data_textPUR0, data_textPUR00, data_textPUR1,data_textPUR2, EmissionJazWW, JazData, JazDataRound, JazDataRoundMeta, OLISSpectraMetaPURShortBA127R, OLISSpectraMetaPURShortBA77G, OLISSpectraMeta, OLISSpectra)
-```
-
-# Create tidy df without all nm
-
-```{r clean df, create smaller df - without absorbance and all nm}
-OLISAllPURTidy<-OLISSpectraMetaPUR %>% 
-  select(-c(Absorbance, nm, Abs440, AbsNorm440, EmJaz439, EmNormJaz439, PURNorm, CountsMean, SumAbNorm, PURNormSum, SumEmNormJaz439)) %>% 
-  unique()
-
-OLISAllPURTidy<-OLISAllPURTidy %>% 
-  group_by(Strain, Par_ue, Photoperiod, E_days, MC, Run) %>%
-  mutate(PURPARRatio = PUR/Par_ue) %>% 
-ungroup()
-
-OLISAllPURTidy <- OLISAllPURTidy %>% 
-  mutate(E_hours = E_days*24) %>% 
-  filter(PURPARRatio<=1) %>% 
-  filter(PURPARRatio>0)
-```
-
-# Preparing df for creating plot
-
-```{r create tidy PAR photon dose and facets for plot}
-OLISAllPURTidy <- OLISAllPURTidy %>%
-    mutate(PARPhotonDoseTidy=PARPhotonDose_day/100000) %>% 
-    mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
-         Strain=="BA48R"~"PE-rich_048",
-        Strain=="BA56G"~"PC-rich_056",
-         Strain=="BA77G"~"PC-rich_077"))
-
-OLISAllPURTidy$facetsPar_ue = factor(OLISAllPURTidy$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
-OLISAllPURTidy$facetsPhotoperiod = factor(OLISAllPURTidy$WL, labels = c("Photoperiod~(h)"))
-OLISAllPURTidy$facetsStrain = factor(OLISAllPURTidy$WL, labels = c("Strain"))
-OLISAllPURTidy$facetsPhase = factor(OLISAllPURTidy$WL, labels = c("Phase~of~growth"))
-OLISAllPURTidy$facetsPARPhotonDose_day = factor(OLISAllPURTidy$WL, labels = c("PAR~photon~dose~(10^{5}~µmol~photons~m^{-2}~d^{-1})"))
-```
-
-# Create preliminary PUR/PAR ratio plot
-
-```{r preliminary plot}
-# lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
-# lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
-# lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
-# 
-# OLISAllPURTidy %>%
-#   ggplot() +
-#   geom_point(aes(x = E_hours, y = PURPARRatio, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = T) +
-#   scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
-#   scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
-#   coord_cartesian(ylim = c(0, 1.7)) +
-#   ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
-#   theme_bw()
-```
-
-# Load tmaxAG catalog
-
-```{r}
-gs4_deauth()
-tmaxAG<- read_sheet("https://docs.google.com/spreadsheets/d/1ksY7xlg9wOsICOBRmZkHPKdd9KOislNwPDzyuJ3UIUI/edit#gid=0")
-as.data.frame(tmaxAG)
-tmaxAG <- tmaxAG
-
-tmaxAG<-tmaxAG %>% 
-  mutate(Par_ue = as.numeric(Par_ue)) %>%
-  mutate(Photoperiod = as.numeric(Photoperiod)) %>%
-  mutate(tMaxAG = as.numeric(tMaxAG)) %>%
-  mutate(dayRound_tmaxAG=tMaxAG/24) %>% 
-  mutate(dayRound_tmaxAG = round(dayRound_tmaxAG, digits = 0)) %>% 
-  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
-         Strain=="BA48R"~"PE-rich_048",
-        Strain=="BA56G"~"PC-rich_056",
-         Strain=="BA77G"~"PC-rich_077"))
-
-tmaxAG$facetsPar_ue = factor(tmaxAG$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
-tmaxAG$facetsPhotoperiod = factor(tmaxAG$WL, labels = c("Photoperiod~(h)"))
-tmaxAG$facetsStrain = factor(tmaxAG$O2, labels = c("Strain"))
-tmaxAG$facetsPARPhotonDose_day = factor(tmaxAG$WL, labels = c("PAR~photon~dose~(10^{5}~µmol~photons~m^{-2}~d^{-1})"))
-
-tmaxAGno24<-tmaxAG %>% 
-  filter(Photoperiod != "24") %>% 
-  mutate(PARPhotonDose_day =(Par_ue/2)*Photoperiod*3600)
-tmaxAG24<-tmaxAG %>% 
-  filter(Photoperiod == "24") %>% 
-  mutate(PARPhotonDose_day = Par_ue*Photoperiod*3600) 
-tmaxAG <-rbind(tmaxAGno24, tmaxAG24)
-  rm(tmaxAGno24, tmaxAG24)
-```
-
-# Select variable for choosen PARPhotonDose to create a plot
-
-```{r select variable for choosen PARPhotonDose to create a plot}
-tmaxAGSelect<-tmaxAG %>% 
-  mutate(PARPhotonDoseTidy=PARPhotonDose_day/100000) %>% 
-  filter(PARPhotonDoseTidy == 4.32000|
-  PARPhotonDoseTidy == 6.48000|
-  PARPhotonDoseTidy == 8.64000|
-  PARPhotonDoseTidy == 43.20000|
-  PARPhotonDoseTidy == 64.80000|
-  PARPhotonDoseTidy == 86.40000) 
-```
-
-# Create 4 df for vertical lines (coloured as Strain) contained tMaxAG value
-
-```{r select revelant columns}
-tMaxAGLines_056Select<-tmaxAGSelect %>% 
-  filter(Strain == "PC-rich_056") %>% 
-  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PARPhotonDoseTidy, tMaxAG)) %>% 
-  unique()
-tMaxAGLines_077Select<-tmaxAGSelect %>% 
-  filter(Strain == "PC-rich_077") %>% 
-  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PARPhotonDoseTidy, tMaxAG)) %>% 
-  unique()
-tMaxAGLines_048Select<-tmaxAGSelect %>% 
-  filter(Strain == "PE-rich_048") %>% 
-  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PARPhotonDoseTidy, tMaxAG)) %>% 
-  unique()
-tMaxAGLines_127Select<-tmaxAGSelect %>% 
-  filter(Strain == "PE-rich_127") %>% 
-  select(c(Par_ue, Photoperiod, facetsPARPhotonDose_day, PARPhotonDoseTidy, tMaxAG)) %>% 
-  unique()
-```
-
-# Create plot
-
-```{r Create final PUR/PAR ratio plot, fig.height = 5, fig.width = 8}
-lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
-lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
-lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))
-
-OLISAllPURTidy %>%
-  filter(PARPhotonDoseTidy == 4.32000|
-  PARPhotonDoseTidy == 6.48000|
-  PARPhotonDoseTidy == 8.64000|
-  PARPhotonDoseTidy == 43.20000|
-  PARPhotonDoseTidy == 64.80000|
-  PARPhotonDoseTidy == 86.40000) %>%
-  ggplot() +
-  geom_point(aes(x = E_hours, y = PURPARRatio, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = T) +
-  geom_vline(data = tMaxAGLines_056Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "seagreen4", size=0.4) +
-  geom_vline(data = tMaxAGLines_077Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "palegreen3", size=0.4) +
-  geom_vline(data = tMaxAGLines_048Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown4", size=0.4) +
-  geom_vline(data = tMaxAGLines_127Select, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown1", size=0.4) +
-  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4")) +
-  labs(y = "PUR/PAR ratio", x = "Elapsed time (h)") +
-  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
-  coord_cartesian(ylim = c(0, 1.5)) +
-  ggh4x::facet_nested(cols = vars(facetsPARPhotonDose_day, PARPhotonDoseTidy), labeller = label_parsed) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_text(size=12),
-        axis.title = element_text(size=16),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=12),
-        axis.title.y = element_text(margin=margin(r=10)),
-        axis.title.x = element_text(margin=margin(t=10)),
-        legend.background = element_rect(fill="white"),
-        legend.position = c(0.08,0.87),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.y = unit(-0.005, "cm"),
-        legend.spacing.x = unit(-0.005, "cm"),
-        legend.title = element_blank(),
-        legend.text = element_text(size=10))
-```
-
-# Cleaning df before saving as rds and removed unnecessary files from the environment
-
-```{r}
-rm(tMaxAGLines_056Select, tMaxAGLines_077Select, tMaxAGLines_048Select, tMaxAGLines_127Select, tmaxAG, tmaxAGSelect)
-```
-
-# Save rds for further analysis
-
-```{r save rds}
-saveRDS(OLISSpectraMetaPUR, file.path(DataOut, paste(Project, "Processed_OlisSpectraAll.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
-
-saveRDS(OLISAllPURTidy, file.path(DataOut, paste(Project, "Processed_OlisSpectraTidy.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
-
-saveRDS(OLISSpectraMetaPURShort, file.path(RDSPlotPath, paste(Project, "Plot_OlisSpectra.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
-```
-
-# Variable names used in Data Dictionary
-
-```{r}
-colnames(OLISSpectraMetaPUR)
-```
-
-# Variable names used in Data Dictionary
-
-```{r}
-colnames(OLISAllPURTidy)
-```

### 2024-01-08 Code/Process_OlisJazEmData.Rmd
removed redundant libraries

@@
 ```{r load libraries, warning = FALSE, echo=FALSE}
+
 library(tidyverse)
 library(lubridate)
-# library(stringr)
 library(broom)
 library(knitr)
-# library(OneR)
 library(zoo)
-# library(strucchange)
-# library(ggspectra)
-# library(ggpubr)
-# library(caret)
 library(photobiologyWavebands)
-# library(reshape2)
-# library(photobiology)
-# library(gcookbook)
+
 ```

### 2024-01-08 Code/Merge_MCGrowthData.Rmd
Changed the name of the saved .rds to a more explicit description

--- 2023-12-15 Code/MultiDataGrowthAssessPico.Rmd
@@
 library(zoo)
-library(RColorBrewer)
+# library(RColorBrewer)
 library(grid)
-library(photobiologyWavebands)
+# library(photobiologyWavebands)
 library(tidyverse)
@@
 ## List processed data
-
 ```{r previous ProcessedData}
@@
 
-# Read .Rds, Summarize, Combine to single data frame
-
-## Create function using to read in .Rds, adding source filename as a column
-
+# Read .Rds, Summarize, Combine to single data frame. Create function using to read in .Rds, adding source filename as a column
 ```{r readRDS_plus}
@@
 
-## Read in ProcessedFiles .Rds
-
+# Read in ProcessedFiles .Rds 
 ```{r read selected ProcessedData}
@@
 
-#Unnest data
+# Unnest data
 # assign growth rate to zero if model returns mu < 0 or if growth amplitude flag = 0 
-
 ```{r unnest fits}
@@
 # Join Full Growth Rate Data
-
 UnnestedLogData <- left_join(x = OD720_unnest, y = deltaOD_unnest)
@@
 
-#combine Full and Truncated unnested data
-NestedFitsData <- left_join(x = UnnestedLogData, y = UnnestedTruncLogData)
+#combine Full and Truncated fits data
+MCGrowthFits <- left_join(x = UnnestedLogData, y = UnnestedTruncLogData)
 
@@
 
+glimpse(MCGrowthFits)
+
 ```
 
-<!-- Chunk to convert categorize oxygen levels based on input in metacatalog.
+# Chunk to convert categorize oxygen levels based on input in metacatalog.
 Have to do this here as this column was added after many runs were already processed and the merge with metacatalog already occured.
@@
 All runs with 21% oxygen are labelled 'High'.
-Assign [O2] to O2_uM based on category -->
+Assign [O2] to O2_uM based on category
+```{r O2 levels}
 
-```{r}
-
-NestedFitsData <- NestedFitsData %>% 
+MCGrowthFits <- MCGrowthFits %>% 
   mutate(O2_uM = case_when(O2_Category == "Low" ~ 2.5,
@@
 # OD720 pivot longer Gmax, Gmu, Glag, Lmu, Lmax and Lintercept estimates
-Pivot_Longer_OD720_est <- NestedFitsData %>%
+Pivot_Longer_OD720_est <- MCGrowthFits %>%
   select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue, Photoperiod, PARPhotonDose_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape,  GrowthAmpOD720_14days, GrowthAmpOD720Flag_14days,  OD720_LseGrowthFlag, OD720trunc_LseGrowthFlag,  OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720trunc_Lmu_corr, OD720trunc_Lmax, OD720trunc_Lintercept
@@
 # OD720 pivot longer Gmax, Gmu, Glag , Lmu, Lmax and Lintercept standard error
-Pivot_Longer_OD720_se <- NestedFitsData %>%
+Pivot_Longer_OD720_se <- MCGrowthFits %>%
   select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue,  Photoperiod, PARPhotonDose_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape, GrowthAmpOD720_14days, GrowthAmpOD720Flag_14days,  OD720_LseGrowthFlag, OD720trunc_LseGrowthFlag,   OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se,OD720trunc_Lmu_se, OD720trunc_Lmax_se, OD720trunc_Lintercept_se
@@
 # deltaOD pivot longer Gmax, Gmu, Glag, Lmu, Lmax and Lintercept estimates
-Pivot_Longer_deltaOD_est <- NestedFitsData %>%
+Pivot_Longer_deltaOD_est <- MCGrowthFits %>%
   select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue,  Photoperiod, PARPhotonDose_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape,  GrowthAmpdeltaOD_14days, GrowthAmpdeltaODFlag_14days,  deltaOD_LseGrowthFlag, deltaODtrunc_LseGrowthFlag,  deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept, deltaODtrunc_Lmu_corr, deltaODtrunc_Lmax, deltaODtrunc_Lintercept
@@
 # deltaOD pivot longer Gmax, Gmu, Glag , Lmu, Lmax and Lintercept standard error
-Pivot_Longer_deltaOD_se <- NestedFitsData %>%
+Pivot_Longer_deltaOD_se <- MCGrowthFits %>%
   select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue,  Photoperiod, PARPhotonDose_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape,  GrowthAmpdeltaOD_14days, GrowthAmpdeltaODFlag_14days,  deltaOD_LseGrowthFlag, deltaODtrunc_LseGrowthFlag,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se, deltaODtrunc_Lmu_se, deltaODtrunc_Lmax_se, deltaODtrunc_Lintercept_se
@@
 
-saveRDS(object = NestedFitsData, file = file.path(DataOut, paste(Project, "NestedFitsData.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
+saveRDS(object = MCGrowthFits, file = file.path(DataOut, paste(Project, "Processed_MCGrowthFits.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
 
@@
 
-NestedFitsData %>%
+MCGrowthFits %>%
    filter(Strain == "SS120") %>%
@@
 
-NestedFitsData %>%
+MCGrowthFits %>%
    filter(Strain == "MIT9313",
@@
 
- NestedFitsData %>%
+ MCGrowthFits %>%
    filter(Strain == "MED4",
@@
 
- NestedFitsData %>%
+ MCGrowthFits %>%
    filter(Strain == "MIT9313" |

### 2024-01-08 Code/Process_OlisJazEmData.Rmd
removed extra lines

@@
 
-# Load Libraries and set Project Variables
-
+# Load Libraries
 ```{r load libraries, warning = FALSE, echo=FALSE}
@@
 Project <- "PICO"
-DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedOlisJazData")
+
 DataInOlis <- file.path("..", "Data", "ImportedData", "ImportedOlisData", fsep = .Platform$file.sep)
 DataInJaz <- file.path("..", "Data", "ImportedData", "ImportedJazEmData", fsep = .Platform$file.sep)
-
+DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedOlisJazData")
 PlotsPath <- file.path("..", "Output", "Plots")

### 2024-01-09 Code/Merge_GrowthPURData.Rmd
Created rmd to merge PUR with growth data

---
title: "Merge_PICO_Growth_PUR"
author: 
- Mireille Savoie
date: "`r format(Sys.Date())`"
output:
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  bookdown::word_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
bibliography: [Prochlorococcus_O2_NPQ.bib, RPackages.bib]
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

## Set figure caption font size
```{css, echo=FALSE}
p.caption {
  font-size: 25px;
}
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = F)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r load libraries, include=FALSE}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
library(knitr)
library(zoo)
library(RColorBrewer)
library(grid)
library(bookdown)
library(glue)
library(egg)
library(ggspectra)
library(minpack.lm)

knitr::write_bib(c("tidyverse", "lubridate","knitr", "broom", "zoo", "RColorBrewer", "grid", "glue", "bookdown"), 'RPackages.bib')

```

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"

DataInPUR <- file.path("..", "Data", "ProcessedData", "ProcessedOlisJazData", fsep = .Platform$file.sep)
DataInGrowth <- file.path("..", "Data", "CleanData", "CleanedMCData", fsep = .Platform$file.sep)
DataOut <- file.path("..", "Data", "CleanData")
PlotsPath <- file.path("..", "Output", "Plots")

SectoHour <- 3600 #seconds to hour
```

# Read in MC growth fits and PUR .Rds
```{r read ProcessFile}

NestedFitsData <- readRDS(file = file.path(DataInGrowth, "PICO_Processed_MCGrowthFits.Rds"))
NestedPURData <- readRDS(file = file.path(DataInPUR, "PICO_Processed_OlisJazMetaPUR.Rds"))

glimpse(NestedPURData)
```

# Join PUR data to wide dataframe containing growth estimates and PAR. Note: PUR data were calculated using whole cell spectras of cultures grown in high [O2] only. Assumed PUR results were same for all [O2], thus the calculated PUR results were joined to the appropriate matching PAR and WL for each strain.  
```{r Join PUR with PAR and growth fits data}
#add Purdata, e-days and parpurratios to PurParFits
PurData <- NestedPURData %>% 
  select(c("Strain", "SampleID", "WL", "Run",  "Par_ue",  "PurData", "E_days", "PurParRatio", "PURPhotonDose_day")) %>% 
 group_by(Strain, WL, SampleID, Run, Par_ue) %>% 
  summarise(E_days, PurData, PurParRatio, PURPhotonDose_day) %>% 
ungroup

glimpse(PurData)

PURPARFits <- right_join(PurData, NestedFitsData,  by = c("Strain", "SampleID", "WL", "Run",  "Par_ue"), keep = NULL)

glimpse(PURPARFits)

PurDataSum <- NestedPURData %>% 
  select(c("Strain", "WL", "Par_ue", "Pur_ue")) %>% 
 group_by(Strain, WL, Par_ue, Pur_ue) %>% 
  summarise() %>% 
ungroup

glimpse(PurDataSum)

PURPARFits <- left_join(PURPARFits, PurDataSum, by = c("Strain", "WL", "Par_ue"))

glimpse(PURPARFits)

remove(PurDataSum)
remove(PurData)
```
# mutate PurParRatio to get ratios for all growth estimates as well as PURPhotonDose_day
```{r purparratio}
PURPARFits <- PURPARFits %>% 
  mutate(PurParRatio = Pur_ue / Par_ue,
         PURPhotonDose_day = case_when(LightShape == 'Sine' ~ Pur_ue/2 * SectoHour * Photoperiod,
                                  LightShape == 'Square' ~ Pur_ue * SectoHour * Photoperiod))

glimpse (PURPARFits)
```

```{r save Growth estimates with PUR and PAR combined }
saveRDS(object = PURPARFits, file = file.path(DataOut, paste(Project, "Merged_GrowthFitsPURPAR.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

### 2024-01-09 Code/Merge_MCGrowthData.Rmd
Added replicate mean growth estimates and converted growth estimates from per hour to per day

@@
 
-```{r combine unnested fits for PICO Shiny App}
+```{r combine unnested fits}
 
@@
 
+# Add mean growth estimates for conditions that were replicated. 
+```{r add mean growth estimates}
+MCGrowthFits <- MCGrowthFits %>% 
+   group_by(Strain, WL,  Par_ue, Photoperiod, O2_uM) %>% 
+  mutate(ReplicateMean_deltaOD_Lmu_corr = mean(deltaOD_Lmu_corr),
+         ReplicateSD_deltaOD_Lmu_corr = case_when(ReplicateMean_deltaOD_Lmu_corr > 0 ~ sd(deltaOD_Lmu_corr),
+                                                  ReplicateMean_deltaOD_Lmu_corr <= 0 ~ 0), 
+         ReplicateSE_deltaOD_Lmu_corr = ReplicateSD_deltaOD_Lmu_corr/n()^(1/2),
+         ReplicateMean_deltaOD_Lmu_corr_day = ReplicateMean_deltaOD_Lmu_corr * 24,
+         ReplicateSE_deltaOD_Lmu_corr_day = ReplicateSE_deltaOD_Lmu_corr *24) %>% 
+  ungroup() %>% 
+  glimpse()
+
+```
+
 ```{r, pivot Nested data longer for GAM}
@@
 
-saveRDS(object = LongerFitsData, file = file.path(DataOut, paste(Project, "LongerFitsData.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
+saveRDS(object = LongerFitsData, file = file.path(DataOut, paste(Project, "LongerGrowthFitsData.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
 
@@
   ggplot() +
-  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.5) +
- geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
+  geom_point(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.5) +
+ geom_line(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
    labs(subtitle = "Strain, [Oxygen], Photoperiod, Actinic PAR (nm)", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
- geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
-  geom_errorbar(aes(x = Par_ue, ymin = (deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
+ geom_text(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, label= Run), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
+  geom_errorbar(aes(x = Par_ue, ymin = (ReplicateMean_deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
 %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
@@
    filter(Strain == "MIT9313",
-          deltaOD_Lmu_corr == 0 |
-          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
+          ReplicateMean_deltaOD_Lmu_corr == 0 |
+          ReplicateMean_deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
   ggplot() +
-  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.4) +
- geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
+  geom_point(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.4) +
+ geom_line(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
  labs(subtitle = "Strain, [Oxygen],Photoperiod, Actinic PAR (nm) - Of cultures that grew, outliers filtered by standard error > 20% of growth rate.", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
-   geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5,hjust = 0.5, vjust=-0.5) +
-  # geom_jitter(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 6) +
-  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = .
+   geom_text(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, label= Run), alpha = 0.5,hjust = 0.5, vjust=-0.5) +
+  # geom_jitter(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), size = 6) +
+  geom_errorbar(aes(x = Par_ue, ymin = ReplicateMean_deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = ReplicateMean_deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = .
 %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
@@
    filter(Strain == "MED4",
-          deltaOD_Lmu_corr == 0 |
-          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
+          ReplicateMean_deltaOD_Lmu_corr == 0 |
+          ReplicateMean_deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
   ggplot() +
-  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.4) +
- geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
+  geom_point(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.4) +
+ geom_line(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
    labs(subtitle = "Strain, [Oxygen],Photoperiod, Actinic PAR (nm) - Of cultures that grew, outliers filtered by standard error > 20% of growth rate.", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
- geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run), alpha = 0.5,hjust = 0.5, vjust=-0.5) +
-  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = .
+ geom_text(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, label= Run), alpha = 0.5,hjust = 0.5, vjust=-0.5) +
+  geom_errorbar(aes(x = Par_ue, ymin = ReplicateMean_deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = ReplicateMean_deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = .
 %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
@@
          Strain == "MED4",
-          deltaOD_Lmu_corr == 0 |
-          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
+          ReplicateMean_deltaOD_Lmu_corr == 0 |
+          ReplicateMean_deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
   ggplot() +
-  geom_point(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.5) +
-  geom_line(aes(x = Par_ue, y = deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
+  geom_point(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.5) +
+  geom_line(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
 labs(subtitle = "Strain, [Oxygen], Photoperiod, Actinic PAR (nm)", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
- geom_text(aes(x = Par_ue, y = deltaOD_Lmu_corr, label= Run),alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
-  geom_errorbar(aes(x = Par_ue, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = .
+ geom_text(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, label= Run),alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
+  geom_errorbar(aes(x = Par_ue, ymin = ReplicateMean_deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = ReplicateMean_deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = .
 %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +

### 2024-01-09 Code/Process_OlisJazEmData.Rmd
Removed PurParRatio from this rmd and added to the merge rmd

@@
   mutate(SumPURAbsWholeCell_Norm440 = sum(MC_NormEm * AbsNorm440),
-         CalcPur_ue = round(Par_ue * (SumPURAbsWholeCell_Norm440 / sum(MC_NormEm))),
-         CalcPurParRatio = round(CalcPur_ue / Par_ue, 3)) %>% 
+         CalcPur_ue = round(Par_ue * (SumPURAbsWholeCell_Norm440 / sum(MC_NormEm)))) %>% 
 ungroup() %>% 
@@
 OlisJazMetaPUR <- OlisJazMetaPUR %>%
-  group_by(Strain, WL) %>% 
-  mutate(PurParRatio = (mean(CalcPurParRatio)))%>% 
-ungroup()
-
-OlisJazMetaPUR <- OlisJazMetaPUR %>%
   group_by(Strain, WL, Par_ue) %>% 
-  mutate(Pur_ue = round(mean(CalcPur_ue)))%>% 
+  mutate(Pur_ue = round(mean(CalcPur_ue)),
+         PurParRatio = (Pur_ue / Par_ue))%>% 
 ungroup()  %>% 
-  select(-c(CalcPurParRatio, CalcPur_ue))
+  select(-c(CalcPur_ue))
 

### 2024-01-10 Code/Merge_GrowthPURData.Rmd
Removed redundant libraries and added ObsDate to merged DF

@@
 library(knitr)
-library(zoo)
-library(RColorBrewer)
-library(grid)
-library(bookdown)
-library(glue)
-library(egg)
-library(ggspectra)
-library(minpack.lm)
 
@@
 PurData <- NestedPURData %>% 
-  select(c("Strain", "SampleID", "WL", "Run",  "Par_ue",  "PurData", "E_days", "PurParRatio", "PURPhotonDose_day")) %>% 
+  select(c("Strain", "SampleID", "WL", "Run",  "Par_ue",  "PurData", "ObsDate", "E_days", "PurParRatio", "PURPhotonDose_day")) %>% 
  group_by(Strain, WL, SampleID, Run, Par_ue) %>% 
-  summarise(E_days, PurData, PurParRatio, PURPhotonDose_day) %>% 
+  summarise(ObsDate, E_days, PurData, PurParRatio, PURPhotonDose_day) %>% 
 ungroup

### 2024-01-10 Code/ManuscriptFigures.Rmd
Added rmd for generating figures for manuscript

---
title: "PICO_Growth_Manuscript_Plots"
author: 
- Mireille Savoie
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
  bookdown::word_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
bibliography: [Prochlorococcus_O2_NPQ.bib, RPackages.bib]
csl: frontiers.csl
editor_options: 
  markdown: 
    wrap: 72
---

## Set figure caption font size
```{css, echo=FALSE}
p.caption {
  font-size: 25px;
}
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = F)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r load libraries, include=FALSE}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
# library(stringr)
library(broom)
library(knitr)
# library(zoo)
library(RColorBrewer)
library(grid)
library(bookdown)
library(glue)
library(egg)
library(ggspectra)
library(photobiologyWavebands)
library(photobiology)
library(ggpubr)
library(ggh4x)
library(cowplot)
library(jmv)
# library(pgirmess) # for the post hoc kruskalalmc test
library(rcompanion) # for Scheirer-Ray-Hare non-parametric 2 way test, derived from Kruskal-Wallis
# library(FSA) # for Dunn test
library(dunn.test)
# library(rstatix)
library(minpack.lm)
#library(tidyquant)
#library(data.table)
# library(googledrive)
# library(googlesheets4)
library(dplyr)
library(tidyverse)

knitr::write_bib(c("tidyverse", "lubridate","knitr", "stringr", "broom", "zoo", "RColorBrewer", "grid", "glue", "bookdown"), 'RPackages.bib')

```

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..","Data", "CleanData")
PlotsPath <- file.path("..","Output", "Figures")
# DataOut <- file.path("..","GrowthAssessData")

```

Read .Rds
```{r read ProcessFile}

PURPARFits <- readRDS(file = file.path(DataIn,"PICO_Merged_GrowthFitsPURPAR.Rds"))

glimpse(PURPARFits)

```

Make O2_uM, PAR and WL as factor levels from highest to lowest
```{r O2 levels}

PURPARFits <- PURPARFits %>% 
  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         WL= factor(WL, levels = c("WW", 660, 530, 450)),
         deltaOD_Lmu_corr_day = deltaOD_Lmu_corr *24)
#  Par_ue = factor(Par_ue, levels =  c(180, 120, 100,90,60, 30, 15))
```

```{r set colours}

# MyWavelengths = c(450, 530, 660, "WW")
# MCMIXColours = c(w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "black")

MyWavelengths = c("WW", 660, 530, 450)
MCMIXColours = c("black", w_length2rgb(660), w_length2rgb(530),  w_length2rgb(450))

names(MCMIXColours) <- MyWavelengths
MCMIXColours

ColoursStrain = c(MIT9313 = "#E69F00", SS120 = "#F0E442", MED4 = "#CC79A7" )

MyOxygen = c(2.5, 25, 250 )
# O2Colours = c("#99CCFF", "dodgerblue", "blue1")
O2Colours = c("#FFCC00", "#FF9900", "#663300")
names(O2Colours) <- MyOxygen
O2Colours

MyOxygen = c(2.5, 25, 250 )
O2LineType = c("dotted", "longdash", "solid")
names(O2LineType) <- MyOxygen
O2LineType

MyPhotoperiods = as.factor(c(4, 8, 12, 16))
ColoursPhotoperiod = c("gray88", "lightcyan3", "gray47", "gray8")
names(ColoursPhotoperiod) <- MyPhotoperiods
ColoursPhotoperiod

```

```{r set shapes}

MyPhotoperiods = as.factor(c(4, 8, 12, 16))
PhotoperiodShapes = c(6, 18, 16, 17)

names(PhotoperiodShapes) <- MyPhotoperiods
PhotoperiodShapes

O2Shapes <- c(13, 1, 19)

```

Set Strip colors for WL x_strip is for WL faceted by columns and y_strip is for WL faceted by rows
```{r}
x_strip <- strip_themed(background_x = elem_list_rect(fill = MCMIXColours, alpha = 0.8),
                      background_y = elem_list_rect(fill = "grey27"))

x_stripWW <- strip_themed(background_x = elem_list_rect(fill = "black"),
                      background_y = elem_list_rect(fill = "#grey27"))

x_strip660 <- strip_themed(background_x = elem_list_rect(fill = "#730000"),
                      background_y = elem_list_rect(fill = "#grey27"))

x_strip530 <- strip_themed(background_x = elem_list_rect(fill = "#00FF00"),
                      background_y = elem_list_rect(fill = "#grey27"))

x_strip450 <- strip_themed(background_x = elem_list_rect(fill = "#0600FF"),
                      background_y = elem_list_rect(fill = "#grey27"))

y_strip <- strip_themed(background_y = elem_list_rect(fill = MCMIXColours),
                      background_x = elem_list_rect(fill = "#grey27"))

y_stripWW <- strip_themed(background_y = elem_list_rect(fill = "black"),
                      background_x = elem_list_rect(fill = "#grey27"))

y_strip660 <- strip_themed(background_y = elem_list_rect(fill = "#730000"),
                      background_x = elem_list_rect(fill = "#grey27"))

y_strip530 <- strip_themed(background_y = elem_list_rect(fill = "#00FF00"),
                      background_x = elem_list_rect(fill = "#grey27"))

y_strip450 <- strip_themed(background_y = elem_list_rect(fill = "#0600FF"),
                      background_x = elem_list_rect(fill = "#grey27"))

```

# Remove redundant columns 
```{r}
PURPARFits <- PURPARFits %>% 
  select(!contains(c("trunc", "OD720", "OptodeMeasure"))) %>% 
  filter(Strain %in% c("MED4", "MIT9313", "SS120"))

glimpse(PURPARFits)
```

```{r LogisticFitPlot, fig.height= 10, fig.width= 10 }
maxOD_x = 500
maxOD_y = 0.165

minOD_x =500
minOD_y = 0.005

time_x = 300
time_y = -0.005

Predict_x = 4
Predict_y = 0.06

deltaODLogGrowthPlot <- PURPARFits %>%
  filter(Run == 114) %>% 
  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel_title = "Oxygen Concentration",
         Oxygen_label = case_when(O2_uM %in% c(2.5, 25, 250) ~ paste("[Oxygen]", O2_uM, "µM", sep = " ")),
         WL_label_title = "Growth Wavelength",
         WL_label = case_when(WL %in% c(450, 530, 660) ~ paste(WL, "nm", sep = " "),
                              WL %in% c("WW") ~ paste("White LED", sep = " ")),
         Par_label = case_when(Par_ue %in% c(30, 90, 180) ~ paste(Par_ue, "µE", sep = " ")),
         PhotoLabel = case_when(Photoperiod == 16 ~ "16 h Photoperiod", 
                                 Photoperiod == 12 ~ "12 h Photoperiod",
                                 Photoperiod == 8 ~ "8 h Photoperiod",
                                 Photoperiod == 4 ~ "4 h Photoperiod")) %>%
  # mutate(deltaOD_logistic_predict = map(deltaOD_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_deltaOD), colour = "darkgreen", size = 0.1) +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.fitted), colour = "black", size = 0.1) +
  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.resid), colour = "gold", size = 0.05) +
  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/5000, colour = as.factor(WL)), size = 0.25, alpha = 1.0) +
   scale_y_continuous(name="Chlorophyll proxy (ΔOD)", sec.axis=sec_axis(~.*5000, name = Actinic ~PAR~(µmol~photons~m^{-2}~s^{-1}))) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  # facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
   # ggh4x::facet_nested(cols = vars(Tube, Strain,Photoperiod, Oxygen_label, WL_label, Par_label), 
   #                  labeller = labeller(Tube = label_both, WL_label = label_value, WL = label_value, Strain = label_value, OxygenLabel_title = label_value,Oxygen_label = label_value, OxygenLabel = label_value, Photoperiod = label_both, Par_label = label_value))+
   ggh4x::facet_nested(cols = vars(PhotoLabel, Oxygen_label, Tube, SampleID,  Strain, WL_label, Par_label), 
                    labeller = labeller(Tube = label_both, WL_label = label_value, WL = label_value, Strain = label_value, OxygenLabel_title = label_value,Oxygen_label = label_value, OxygenLabel = label_value, Photoperiod = label_both, Par_label = label_value, SampleID = label_both))+
  labs(y = "Chlorophyll proxy (ΔOD)" , x = "Elapsed Time (h)") +
   guides(colour = "none") +
  theme_bw() +
  theme( strip.text = element_text(size = 11),
        axis.title = element_text(size = 20, color = "black"),
        axis.text.x = element_text(size = 15, color = "black", angle = 60, hjust = 1.0),
        axis.text.y = element_text(size = 15, color = "black", angle = 0, hjust = 1.0),
        # strip.background=element_rect(color="grey", fill = "grey"),
        strip.background=element_rect(fill = "grey"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title = element_text(size = 20),  #change legend title font size
        legend.text = element_text(size = 20),   #change legend text font size
        legend.position = "top")

deltaODLogGrowthPlot

deltaODLogGrowthPlotExpand <- PURPARFits %>%
  filter(Run == 28,
         Tube == 6) %>% 
  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel_title = "Oxygen Concentration",
         Oxygen_label = case_when(O2_uM %in% c(2.5, 25, 250) ~ paste("[Oxygen]", O2_uM, "µM", sep = " ")),
         WL_label_title = "Growth Wavelength",
         WL_label = case_when(WL %in% c(450, 530, 660) ~ paste(WL, "nm", sep = " "),
                              WL %in% c("WW") ~ paste("White LED", sep = " ")),
         Par_label = case_when(Par_ue %in% c(30, 90, 180) ~ paste(Par_ue, "µE", sep = " ")),
         PhotoLabel = case_when(Photoperiod == 16 ~ "16 h Photoperiod", 
                                 Photoperiod == 12 ~ "12 h Photoperiod",
                                 Photoperiod == 8 ~ "8 h Photoperiod",
                                 Photoperiod == 4 ~ "4 h Photoperiod")) %>%
  # mutate(deltaOD_logistic_predict = map(deltaOD_logistic, possibly(augment, otherwise = NULL))) %>%
  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = tubedata_time, y = tubedata_deltaOD), colour = "darkgreen", size = 0.1) +
  geom_line(aes(x = tubedata_time, y = min(tubedata_deltaOD)), linetype = "dashed", size = 2) + 
   geom_line(aes(x = tubedata_time, y = max(tubedata_deltaOD)), linetype = "dashed", size =2) + 
    geom_vline(xintercept = 610, linetype = "dashed", size =2) +
 scale_colour_manual(values = MCMIXColours) +
  # geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.fitted), colour = "black", size = 0.1) +
  # geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.resid), colour = "gold", size = 0.05) +
  # geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/5000, colour = as.factor(WL)), size = 0.25, alpha = 1.0) +
   # scale_y_continuous(name="Optical Density (ΔOD)", sec.axis=sec_axis(~.*5000, name = "Actinic PAR (µE)")) +
  #coord_cartesian(xlim = c(-5, 675)) +
  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
  # facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
   # ggh4x::facet_nested(cols = vars(Tube, Strain,Photoperiod, Oxygen_label, WL_label, Par_label), 
   #                  labeller = labeller(Tube = label_both, WL_label = label_value, WL = label_value, Strain = label_value, OxygenLabel_title = label_value,Oxygen_label = label_value, OxygenLabel = label_value, Photoperiod = label_both, Par_label = label_value))+
  annotate(geom = "text", x = maxOD_x, y = maxOD_y, label = "Maximum ΔOD", size = 7, colour = "darkgreen") +
  annotate(geom = "text", x = minOD_x, y = minOD_y, label = "Minimum ΔOD", size = 7, colour = "darkgreen") +
  annotate(geom = "text", x = time_x, y = time_y, label = "Time", size = 7, colour = "red") +
  # annotate(geom = "text", x = Predict_x, y = Predict_y, label = "Logistic Regression", size = 5, colour = "black") +
   # ggh4x::facet_nested(cols = vars(PhotoLabel, Oxygen_label, Tube, SampleID,  Strain, WL_label, Par_label), 
                    # labeller = labeller(Tube = label_both, WL_label = label_value, WL = label_value, Strain = label_value, OxygenLabel_title = label_value,Oxygen_label = label_value, OxygenLabel = label_value, Photoperiod = label_both, Par_label = label_value, SampleID = label_both))+
  labs(y = "Chlorophyll proxy (ΔOD)", x = "Elapsed Time (h)") +
   guides(colour = "none") +
  theme_bw() +
  theme( strip.text = element_text(size = 11),
        axis.title = element_text(size = 20, color = "black"),
        axis.text.x = element_text(size = 15, color = "black", angle = 00, hjust = 1.0),
        axis.text.y = element_text(size = 15, color = "black", angle = 0, hjust = 1.0),
        # strip.background=element_rect(color="grey", fill = "grey"),
        strip.background=element_rect(fill = "grey"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title = element_text(size = 20),  #change legend title font size
        legend.text = element_text(size = 20),   #change legend text font size
        legend.position = "top")

deltaODLogGrowthPlotExpand

deltaODGrowthRatesPlot <- PURPARFits %>%
  filter(Run == 114,
         Par_ue %in% c(30,90,180)) %>% 
  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel_title = "Oxygen Concentration",
         Oxygen_label = case_when(O2_uM %in% c(2.5, 25, 250) ~ paste("[Oxygen]", O2_uM, "µM", sep = " ")),
         WL_label_title = "Growth Wavelength",
         WL_label = case_when(WL %in% c(450, 530, 660) ~ paste(WL, "nm", sep = " "),
                              WL %in% c("WW") ~ paste("White LED", sep = " ")),
         Par_label = case_when(Par_ue %in% c(30, 90, 180) ~ paste(Par_ue, "µE", sep = " ")),
         PhotoLabel = case_when(Photoperiod == 16 ~ "16 h Photoperiod", 
                                 Photoperiod == 12 ~ "12 h Photoperiod",
                                 Photoperiod == 8 ~ "8 h Photoperiod",
                                 Photoperiod == 4 ~ "4 h Photoperiod"),
         deltaOD_Lmu_se_day = deltaOD_Lmu_se * 24) %>%
  # mutate(deltaOD_logistic_predict = map(deltaOD_logistic, possibly(augment, otherwise = NULL))) %>%
  # unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) %>%
  ggplot() +
  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5.0) +
   # geom_errorbar(aes(x = Photoperiod, ymin = deltaOD_Lmu_corr_day - deltaOD_Lmu_se_day, ymax = deltaOD_Lmu_corr_day + deltaOD_Lmu_se_day), width = 0.2 , size = 0.3, color = 'black', alpha = 0.3, data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
  scale_colour_manual(values = MCMIXColours) +
  # geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.fitted), colour = "black", size = 0.1) +
  # geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.resid), colour = "gold", size = 0.05) +
  # geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/5000, colour = as.factor(WL)), size = 0.25, alpha = 1.0) +
  #coord_cartesian(xlim = c(-5, 675)) +
  scale_x_continuous(breaks=seq(0, 16, by = 4)) +
  # facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
   # ggh4x::facet_nested(cols = vars(Tube, Strain,Photoperiod, Oxygen_label, WL_label, Par_label), 
   #                  labeller = labeller(Tube = label_both, WL_label = label_value, WL = label_value, Strain = label_value, OxygenLabel_title = label_value,Oxygen_label = label_value, OxygenLabel = label_value, Photoperiod = label_both, Par_label = label_value))+
   ggh4x::facet_nested(cols = vars(PhotoLabel, Oxygen_label, Tube, SampleID,  Strain, WL_label, Par_label), 
                    labeller = labeller(Tube = label_both, WL_label = label_value, WL = label_value, Strain = label_value, OxygenLabel_title = label_value,Oxygen_label = label_value, OxygenLabel = label_value, Photoperiod = label_both, Par_label = label_value, SampleID = label_both))+
  labs(y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   guides(colour = "none") +
  theme_bw() +
  theme( strip.text = element_text(size = 11),
        axis.title = element_text(size = 20, color = "black"),
        axis.text.x = element_text(size = 15, color = "black", angle = 0, hjust = 1.0),
        axis.text.y = element_text(size = 15, color = "black", angle = 0, hjust = 1.0),
        # strip.background=element_rect(color="grey", fill = "grey"),
        strip.background=element_rect(fill = "grey"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title = element_text(size = 20),  #change legend title font size
        legend.text = element_text(size = 20),   #change legend text font size
        legend.position = "top")

deltaODGrowthRatesPlot

```

```{r PURPARRatioPlots, fig.height= 10, fig.width= 10}

PurParPlot <- PURPARFits %>%
  filter(Par_ue %in% c(30, 90, 180)) %>%
  mutate(Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>% 
  ggplot() +
  geom_point(aes(x = Par_ue, y = Pur_ue, colour = as.factor(WL)), size = 3, alpha = 0.5) +
 geom_line(aes(x = Par_ue, y = Pur_ue,colour = as.factor(WL)), linewidth = 0.7) +
    geom_abline(slope = 1, intercept = 0, colour = "grey39", linetype = "dashed", linewidth = 1.2) +
  #geom_jitter(aes(x = Pur_ue, y = Par_ue, colour = as.factor(Strain)), size = 3, alpha = 0.5) +
  labs(y = "PUR (µE)" , x = "PAR (µE)") +
 #geom_text(aes(x = Pur_ue, y = deltaOD_Lmu_corr, label= WL), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
 # geom_errorbar(aes(x = Pur_ue, ymin = (deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +\
   # scale_linetype_manual(values = c("MED4" = "solid", "MIT9313" = "longdash",  "SS120" = "dotted")) +
   scale_x_continuous(breaks=seq(0, 180, by = 30)) +
  # coord_cartesian(xlim = c (0, 180)) +
    scale_y_continuous(breaks=seq(0, 180, by = 30)) +
  coord_fixed(ylim = c (0, 180), xlim = c (0, 180), ratio = 1) +
   scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660","530", "450" )) +
 # ggh4x::facet_nested(rows = vars(Strain), 
 #                     labeller = labeller(WL = label_both, Strain = label_both)) + 
   geom_text(aes(x = 60, y = 180, label = paste(Strain), show.legend = FALSE, ),    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 8.0
  )  +
  facet_wrap(~Strain, ncol = 2) +
  theme_bw() +
  labs(colour = "Growth Waveband (nm)") +
  theme(strip.text = element_blank(),
        legend.text = element_text(size = 20),
        legend.title = element_text(size = 25),
        legend.position = c(0.80, 0.25),
        axis.title = element_text(hjust= 0.60, vjust = -0.2, size = 20),
        strip.text.x = element_blank(),
        axis.text = element_text(size = 15, color = "black"),)

PurParPlot <- tag_facet(PurParPlot, open = "", close = "", tag_pool = LETTERS, size = 8)

PurParPlot

```

```{r save ParPurPlots}

ggsave(file = file.path(PlotsPath, paste("PurParPlot",".png",sep = "")), plot = PurParPlot, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

```

```{r MED4 PURPAR, fig.height= 10, fig.width= 10}

MED4PurParPlot <- PURPARFits %>%
  filter(Par_ue %in% c(30, 90, 180)) %>%
  mutate(Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
  filter(Strain == "MED4") %>% 
  ggplot() +
  geom_point(aes(x = Par_ue, y = Pur_ue, colour = as.factor(WL)), size = 3, alpha = 0.5) +
 geom_line(aes(x = Par_ue, y = Pur_ue,colour = as.factor(WL)), linewidth = 0.7) +
    geom_abline(slope = 1, intercept = 0, colour = "grey39", linetype = "dashed", linewidth = 1.2) +
  #geom_jitter(aes(x = Pur_ue, y = Par_ue, colour = as.factor(Strain)), size = 3, alpha = 0.5) +
  labs(y = "PUR (µE)" , x = "PAR (µE)") +
 #geom_text(aes(x = Pur_ue, y = deltaOD_Lmu_corr, label= WL), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
 # geom_errorbar(aes(x = Pur_ue, ymin = (deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +\
   # scale_linetype_manual(values = c("MED4" = "solid", "MIT9313" = "longdash",  "SS120" = "dotted")) +
   scale_x_continuous(breaks=seq(0, 180, by = 30)) +
  # coord_cartesian(xlim = c (0, 180)) +
    scale_y_continuous(breaks=seq(0, 180, by = 30)) +
  coord_fixed(ylim = c (0, 180), xlim = c (0, 180), ratio = 1) +
   scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660","530", "450" )) +
 # ggh4x::facet_nested(rows = vars(Strain), 
 #                     labeller = labeller(WL = label_both, Strain = label_both)) + 
   geom_text(aes(x = 60, y = 180, label = paste(Strain), show.legend = FALSE, ),    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 8.0
  )  +
  facet_wrap(~Strain, ncol = 2) +
  theme_bw() +
  labs(colour = "Growth Waveband (nm)") +
  theme(strip.text = element_blank(),
        legend.text = element_text(size = 20),
        legend.title = element_text(size = 25),
        # legend.position = c(0.30, 0.7),
        legend.position = "none",
        axis.title = element_text(hjust= 0.60, vjust = -0.2, size = 20),
        strip.text.x = element_blank(),
        axis.text = element_text(size = 15, color = "black"))
MED4PurParPlot

```

```{r save individual ParPurPlots}

ggsave(file = file.path(PlotsPath, paste("MED4PurParPlot",".png",sep = "")), plot = MED4PurParPlot, device = NULL, scale = 1, height=10, width= 10, units = c("cm"),dpi = 300, limitsize = TRUE)

```

```{r PUR per day, fig.height= 10, fig.width= 10 }

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }

MED4NoPhotoPUR <- PURPARFits %>%
   filter(Strain == "MED4", 
         Par_ue %in% c(30,90,180)) %>%
   mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel = "Oxygen Concentration (µM)",
         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.5, alpha = 0.8) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
scale_x_continuous(label=scientific_10) +
   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660","530", "450" )) +
   scale_shape_manual(values = PhotoperiodShapes)  +
  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
 guides(linetype = "none",
        fill = "none",
        colour = guide_legend(ncol = 4)) +
 guides(shape = guide_legend(nrow = 1)) +
  theme_bw() +
   theme( strip.text = element_text(size = 30),
        axis.title = element_text(size = 30, color = "black"),
        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
        strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title =  element_text(size = 20),  #change legend title font size
        legend.text = element_text(size = 20),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Waveband (nm)",
       shape = "Photoperiod (h)")

MED4NoPhotoPUR

SS120NoPhotoPUR <- PURPARFits %>%
   filter(Strain == "SS120", 
           Par_ue %in% c(30,90,180)) %>%
   mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel = "Oxygen Concentration (µM)",
         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.5, alpha = 0.8) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
scale_x_continuous(label=scientific_10) +
   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660","530", "450" )) +
   scale_shape_manual(values = PhotoperiodShapes)  +
  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
 guides(linetype = "none",
        fill = "none",
        colour = guide_legend(ncol = 4)) +
 guides(shape = guide_legend(nrow = 1)) +
  theme_bw() +
   theme( strip.text = element_text(size = 30),
        axis.title = element_text(size = 30, color = "black"),
        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
        strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title =  element_text(size = 20),  #change legend title font size
        legend.text = element_text(size = 20),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Waveband (nm)",
       shape = "Photoperiod (h)")

SS120NoPhotoPUR

MIT9313NoPhotoPUR <- PURPARFits %>%
   filter(Strain == "MIT9313", 
          Par_ue %in% c(30,90,180)) %>%
  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel = "Oxygen Concentration (µM)",
         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.5, alpha = 0.8) +
 # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
scale_x_continuous(label=scientific_10) +
   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660","530", "450" )) +
   scale_shape_manual(values = PhotoperiodShapes)  +
  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
 guides(linetype = "none",
        fill = "none",
        colour = guide_legend(ncol = 4)) +
 guides(shape = guide_legend(nrow = 1)) +
  theme_bw() +
   theme( strip.text = element_text(size = 30),
        axis.title = element_text(size = 30, color = "black"),
        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
        strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title =  element_text(size = 20),  #change legend title font size
        legend.text = element_text(size = 20),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Waveband (nm)",
       shape = "Photoperiod (h)")

MIT9313NoPhotoPUR

```

```{r, save O2ColorPURPlots}
# ggsave(file = file.path(PlotsPath, paste("MED4PhotobyO2PUR",".png",sep = "")), plot = MED4PhotobyO2PUR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsPath, paste("MIT9313PhotobyO2PUR",".png",sep = "")), plot = MIT9313PhotobyO2PUR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsPath, paste("SS120PhotobyO2PUR",".png",sep = "")), plot = SS120PhotobyO2PUR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsPath, paste("MED4NoPhotoPUR",".png",sep = "")), plot = MED4NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsPath, paste("MIT9313NoPhotoPUR",".png",sep = "")), plot = MIT9313NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsPath, paste("SS120NoPhotoPUR",".png",sep = "")), plot = SS120NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

```

Ecological plots
```{r ParPlots, fig.height= 10, fig.width= 10}

MED4PAR <- PURPARFits %>%
   filter(Strain == "MED4",
           Par_ue %in% c(30,90,180),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  mutate(PhotoperiodLabel_title = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~Concentration~(µM)",
         WL_label_title = "Growth~Wavelength",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         Par_ue = factor(Par_ue, levels = c(180, 90, 30))) %>%
  ggplot() +
  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 0.5) +
 geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5) +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.5) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3) +
  scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm","530 nm", "450 nm" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, Par_ue), rows = vars(OxygenLabel, O2_uM), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( strip.text = element_text(size = 20),
       axis.title.x.bottom = element_text(size = 30, color = "black", vjust = 1.0),
      axis.title.y = element_text(size = 30, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
        # strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 25),  #change legend title font size
        legend.text = element_text(size = 25),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Wavelength",
       fill = "Growth Wavelength")
MED4PAR

SS120PAR <- PURPARFits %>%
   filter(Strain == "SS120",
          Par_ue %in% c(30,90,180),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  mutate(PhotoperiodLabel_title = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~Concentration~(µM)",
         WL_label_title = "Growth~Wavelength",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         Par_ue = factor(Par_ue, levels = c(180, 90, 30))) %>%
  ggplot() +
  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 0.5) +
 geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5) +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.5) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3) +
  scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm","530 nm", "450 nm" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, Par_ue), rows = vars(OxygenLabel, O2_uM), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( strip.text = element_text(size = 20),
       axis.title.x.bottom = element_text(size = 30, color = "black", vjust = 1.0),
      axis.title.y = element_text(size = 30, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
        # strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 25),  #change legend title font size
        legend.text = element_text(size = 25),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Wavelength",
       fill = "Growth Wavelength")

SS120PAR

MIT9313PAR <- PURPARFits %>%
   filter(Strain == "MIT9313",
            Par_ue %in% c(30,90,180),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
   mutate(PhotoperiodLabel_title = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~Concentration~(µM)",
         WL_label_title = "Growth~Wavelength",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         Par_ue = factor(Par_ue, levels = c(180, 90, 30))) %>%
  ggplot() +
  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 0.5) +
 geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5) +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.5) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3) +
  scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm","530 nm", "450 nm" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, Par_ue), rows = vars(OxygenLabel, O2_uM), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( strip.text = element_text(size = 20),
       axis.title.x.bottom = element_text(size = 30, color = "black", vjust = 1.0),
      axis.title.y = element_text(size = 30, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
        # strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 25),  #change legend title font size
        legend.text = element_text(size = 25),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Wavelength",
       fill = "Growth Wavelength")

MIT9313PAR
```

```{r, save PARPlots}

ggsave(file = file.path(PlotsPath, paste("MED4PAR",".png",sep = "")), plot = MED4PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsPath, paste("SS120PAR",".png",sep = "")), plot = SS120PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsPath, paste("MIT9313PAR",".png",sep = "")), plot = MIT9313PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

```

Overlay
```{r MED4 All Spectral Emission,  fig.height = 10, fig.width = 10}

MyWavelengths = c("WW", 660, 530, 450)
OverlayColours = c("black", w_length2rgb(660), w_length2rgb(530),  w_length2rgb(450))

names(OverlayColours) <- MyWavelengths
OverlayColours

MED4OverlayPlots <- PURPARFits %>%
  filter(Strain == "MED4",
          Par_ue == 90,
          O2_Category == "High" & WL == 450 & Photoperiod == 12 |
          O2_Category == "High" & WL == 530 & Photoperiod == 16 |
          O2_Category == "Intermediate" & WL == "WW" & Photoperiod == 16 |
          O2_Category == "Intermediate" & WL == 660 & Photoperiod == 12) %>%
  mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste("Growth", "waveband", "=", WL, "nm", sep = " "),
        WL %in% c("WW") ~ paste("Growth", "waveband", "=", "White LED", sep = " "))) %>% 
   unnest(cols = c(PurData), names_sep = "_", keep_empty = TRUE) %>%
  pivot_longer(cols = c(PurData_PURAbsWholeCell_Norm440, PurData_AbsNorm440,  PurData_MC_NormEm), values_to = "Abs_Em_Value", names_to = "Abs_Em_Names") %>%
ggplot()+
  geom_area(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, fill = as.factor(WL)), color = "black", 
            size = 0.5, alpha = 0.7, show.legend = FALSE, 
            data = . %>% filter(Abs_Em_Names == "PurData_PURAbsWholeCell_Norm440")) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = Abs_Em_Names,  linetype = Abs_Em_Names), size = 0.85) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = as.factor(WL),  linetype = Abs_Em_Names), size = 1.0, data = . %>% filter(Abs_Em_Names == "PurData_MC_NormEm")) +
  scale_color_manual(values = c(MCMIXColours, "PurData_PURAbsWholeCell_Norm440" = "black", "PurData_AbsNorm440" = "darkorchid3", "PurData_MC_NormEm" = "white")) +
  scale_linetype_manual(values = c("PurData_PURAbsWholeCell_Norm440" = "solid", "PurData_AbsNorm440" = "twodash",  "PurData_MC_NormEm" = "dotted"),
                        labels = c("LED emission", "Whole cell abs.", "PUR")) +
  scale_fill_manual(values = MCMIXColours) +
 # guides(colour = FALSE) +
  labs(y = "Normalized Absorbance and Emission", x = "Wavelength (nm)") +
  labs(linetype = "Spectra Type")+
  scale_y_continuous(breaks=seq(0, 1.5, by = 0.25)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
   facet_wrap(vars(WL),
              labeller = labeller(strain = label_value, WL = label_value, Photoperiod = label_both, Par_ue = label_both, O2_Category = label_both, Pur_ue = label_both)) +
  geom_text(aes(x = 430, y = 1.1, label = WL_label, color = as.factor(WL)), show.legend = FALSE,
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
   geom_text(aes(x = 560, y = 0.95, label = paste("PAR", "=", Par_ue, sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
  geom_text(aes(x = 560, y = 0.85, label = paste("PUR", "=", Pur_ue,sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text = element_blank(),
       legend.background = element_rect(color = "transparent", fill = "transparent"),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 20),
        # legend.position = c(0.94,0.96),
        legend.position = "top",
        axis.title = element_text(vjust = 1.0, size = 20),
        # strip.text.x = element_text(size = 20),
        axis.text = element_text(size = 15, color = "black"))

MED4OverlayPlots <- tag_facet(MED4OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)

MED4OverlayPlots

MED4WWOverlayPlots <- PURPARFits %>%
  filter(Strain == "MED4",
          Par_ue == 90,
          O2_Category == "Intermediate" & WL == "WW" & Photoperiod == 16) %>%
  mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste("Growth", "waveband", "=", WL, "nm", sep = " "),
        WL %in% c("WW") ~ paste("Growth", "waveband", "=", "White LED", sep = " "))) %>% 
   unnest(cols = c(PurData), names_sep = "_", keep_empty = TRUE) %>%
  pivot_longer(cols = c(PurData_PURAbsWholeCell_Norm440, PurData_AbsNorm440,  PurData_MC_NormEm), values_to = "Abs_Em_Value", names_to = "Abs_Em_Names") %>%
ggplot()+
  geom_area(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, fill = as.factor(WL)), color = "black", 
            size = 0.5, alpha = 0.7, show.legend = FALSE, 
            data = . %>% filter(Abs_Em_Names == "PurData_PURAbsWholeCell_Norm440")) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = Abs_Em_Names,  linetype = Abs_Em_Names), size = 2) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = as.factor(WL),  linetype = Abs_Em_Names), size = 2.0, data = . %>% filter(Abs_Em_Names == "PurData_MC_NormEm")) +
  scale_color_manual(values = c(MCMIXColours, "PurData_PURAbsWholeCell_Norm440" = "black", "PurData_AbsNorm440" = "aquamarine4", "PurData_MC_NormEm" = "white")) +
  scale_linetype_manual(values = c("PurData_PURAbsWholeCell_Norm440" = "solid", "PurData_AbsNorm440" = "solid",  "PurData_MC_NormEm" = "dotted"),
                        labels = c("LED emission", "Whole cell abs.", "PUR")) +
  scale_fill_manual(values = MCMIXColours) +
 # guides(colour = FALSE) +
  labs(y = "Normalized Absorbance and Emission", x = "Wavelength (nm)") +
  labs(linetype = "Spectra Type")+
  scale_y_continuous(breaks=seq(0, 1.5, by = 0.25)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
   facet_wrap(vars(WL),
              labeller = labeller(strain = label_value, WL = label_value, Photoperiod = label_both, Par_ue = label_both, O2_Category = label_both, Pur_ue = label_both)) +
  geom_text(aes(x = 430, y = 1.1, label = WL_label, color = as.factor(WL)), show.legend = FALSE,
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 7.0
  )  +
   geom_text(aes(x = 560, y = 0.95, label = paste("PAR", "=", Par_ue, "uE", sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 6.0
  )  +
  geom_text(aes(x = 560, y = 0.85, label = paste("PUR", "=", Pur_ue, "uE",sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 6.0
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text = element_blank(),
       legend.background = element_rect(color = "transparent", fill = "transparent"),
        legend.text = element_text(size = 25),
        legend.title = element_text(size = 25),
        # legend.position = c(0.94,0.96),
        legend.position = "top",
        axis.title = element_text(vjust = 1.0, size = 30),
        # strip.text.x = element_text(size = 20),
        axis.text = element_text(size = 25, color = "black"))

MED4WWOverlayPlots

```

```{r save MED4 PUR overlay plots}

ggsave(file = file.path(PlotsPath, paste("MED4OverlayPlots",".png",sep = "")), plot = MED4OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsPath, paste("MED4WWOverlayPlots",".png",sep = "")), plot = MED4WWOverlayPlots, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

```

```{r MIT9313 All Spectral Emission,  fig.height = 10, fig.width = 10}

MIT9313OverlayPlots <- PURPARFits %>%
   filter(Strain == "MIT9313",
          O2_Category == "High",
          Par_ue == 30,
          Photoperiod == 12 & WL == 450 |
          Photoperiod == 12 & WL == 530 |
          Photoperiod == 12 & WL == 660 |
          Photoperiod == 16 & WL == "WW") %>% 
  mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste("Growth", "wavelength", "=", WL, "nm", sep = " "),
        WL %in% c("WW") ~ paste("Growth", "wavelength", "=", "White LED", sep = " "))) %>% 
   unnest(cols = c(PurData), names_sep = "_", keep_empty = TRUE) %>%
  pivot_longer(cols = c(PurData_PURAbsWholeCell_Norm440, PurData_AbsNorm440,  PurData_MC_NormEm), values_to = "Abs_Em_Value", names_to = "Abs_Em_Names") %>%
ggplot()+
  geom_area(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, fill = as.factor(WL)), color = "black", 
            size = 0.5, alpha = 0.7, show.legend = FALSE, 
            data = . %>% filter(Abs_Em_Names == "PurData_PURAbsWholeCell_Norm440")) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = Abs_Em_Names,  linetype = Abs_Em_Names), size = 0.85) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = as.factor(WL),  linetype = Abs_Em_Names), size = 1.0, data = . %>% filter(Abs_Em_Names == "PurData_MC_NormEm")) +
  scale_color_manual(values = c(MCMIXColours, "PurData_PURAbsWholeCell_Norm440" = "black", "PurData_AbsNorm440" = "darkorchid3", "PurData_MC_NormEm" = "white")) +
  scale_linetype_manual(values = c("PurData_PURAbsWholeCell_Norm440" = "solid", "PurData_AbsNorm440" = "twodash",  "PurData_MC_NormEm" = "dotted"),
                        labels = c("LED emission", "Whole cell abs.", "PUR")) +
  scale_fill_manual(values = MCMIXColours) +
 # guides(colour = FALSE) +
  labs(y = "Normalized Absorbance and Emission", x = "Wavelength (nm)") +
  labs(linetype = "Spectra Type")+
  scale_y_continuous(breaks=seq(0, 1.5, by = 0.25)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
   facet_wrap(vars(WL),
              labeller = labeller(strain = label_value, WL = label_value, Photoperiod = label_both, Par_ue = label_both, O2_Category = label_both, Pur_ue = label_both)) +
  geom_text(aes(x = 430, y = 1.1, label = WL_label, color = as.factor(WL)), show.legend = FALSE,
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
   geom_text(aes(x = 560, y = 0.95, label = paste("PAR", "=", Par_ue, sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
  geom_text(aes(x = 560, y = 0.85, label = paste("PUR", "=", Pur_ue,sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text = element_blank(),
       legend.background = element_rect(color = "transparent", fill = "transparent"),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 20),
        # legend.position = c(0.94,0.96),
        legend.position = "top",
        axis.title = element_text(vjust = 1.0, size = 20),
        # strip.text.x = element_text(size = 20),
        axis.text = element_text(size = 15, color = "black"))

 MIT9313OverlayPlots <- tag_facet(MIT9313OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)

 MIT9313OverlayPlots
```

```{r save MIT9313 PUR overlay plots}

ggsave(file = file.path(PlotsPath, paste("MIT9313OverlayPlots",".png",sep = "")), plot = MIT9313OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

```

```{r SS120 PUR overlay with legend,  fig.height = 10, fig.width = 10}
SS120OverlayPlots <- PURPARFits %>%
   filter(Strain == "SS120",
          O2_Category == "High",
          Par_ue == 30,
          Photoperiod == 8 |
          Photoperiod == 12 & WL == 530,
          Run != 113 & Run != 112) %>%
  mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste("Growth", "wavelength", "=", WL, "nm", sep = " "),
        WL %in% c("WW") ~ paste("Growth", "wavelength", "=", "White LED", sep = " "))) %>% 
   unnest(cols = c(PurData), names_sep = "_", keep_empty = TRUE) %>%
  pivot_longer(cols = c(PurData_PURAbsWholeCell_Norm440, PurData_AbsNorm440,  PurData_MC_NormEm), values_to = "Abs_Em_Value", names_to = "Abs_Em_Names") %>%
ggplot()+
  geom_area(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, fill = as.factor(WL)), color = "black", 
            size = 0.5, alpha = 0.7, show.legend = FALSE, 
            data = . %>% filter(Abs_Em_Names == "PurData_PURAbsWholeCell_Norm440")) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = Abs_Em_Names,  linetype = Abs_Em_Names), size = 0.85) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = as.factor(WL),  linetype = Abs_Em_Names), size = 1.0, data = . %>% filter(Abs_Em_Names == "PurData_MC_NormEm")) +
  scale_color_manual(values = c(MCMIXColours, "PurData_PURAbsWholeCell_Norm440" = "black", "PurData_AbsNorm440" = "darkorchid3", "PurData_MC_NormEm" = "white")) +
  scale_linetype_manual(values = c("PurData_PURAbsWholeCell_Norm440" = "solid", "PurData_AbsNorm440" = "twodash",  "PurData_MC_NormEm" = "dotted"),
                        labels = c("LED emission", "Whole cell abs.", "PUR")) +
  scale_fill_manual(values = MCMIXColours) +
 # guides(colour = FALSE) +
  labs(y = "Normalized Absorbance and Emission", x = "Wavelength (nm)") +
  labs(linetype = "Spectra Type")+
  scale_y_continuous(breaks=seq(0, 1.5, by = 0.25)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
   facet_wrap(vars(WL),
              labeller = labeller(strain = label_value, WL = label_value, Photoperiod = label_both, Par_ue = label_both, O2_Category = label_both, Pur_ue = label_both))+
  geom_text(aes(x = 430, y = 1.1, label = WL_label, color = as.factor(WL)), show.legend = FALSE,
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
   geom_text(aes(x = 560, y = 0.95, label = paste("PAR", "=", Par_ue, sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
  geom_text(aes(x = 560, y = 0.85, label = paste("PUR", "=", Pur_ue,sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text = element_blank(),
       legend.background = element_rect(color = "transparent", fill = "transparent"),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 20),
        # legend.position = c(0.94,0.96),
        legend.position = "top",
        axis.title = element_text(vjust = 1.0, size = 20),
        # strip.text.x = element_text(size = 20),
        axis.text = element_text(size = 15, color = "black"))

 SS120OverlayPlots <- tag_facet(SS120OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)

 SS120OverlayPlots

```

```{r save SS120 PUR overlay plots}

ggsave(file = file.path(PlotsPath, paste("SS120OverlayPlots",".png",sep = "")), plot = SS120OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

```

### 2024-01-11 Code/ManuscriptFigures.Rmd
edit .rmd for manuscript

@@
 ---
-title: "PICO_Growth_Manuscript_Plots"
+title: "ManuscriptFigures"
 author: 
@@
 bibliography: [Prochlorococcus_O2_NPQ.bib, RPackages.bib]
-csl: frontiers.csl
+csl: plos-one.csl
 editor_options: 
@@
 ```
-
+# Global chunk settings 
 ```{r setup, include = FALSE}
@@
 ```{r load libraries, include=FALSE}
-# libraries; Note check actual dependencies
-library(tidyverse)
+
 library(lubridate)
@@
 library(glue)
-library(egg)
-library(ggspectra)
+library(egg) # Adds Letters to grid plots
+# library(ggspectra)
 library(photobiologyWavebands)
-library(photobiology)
-library(ggpubr)
+# library(photobiology)
+# library(ggpubr)
 library(ggh4x)
 library(cowplot)
-library(jmv)
-# library(pgirmess) # for the post hoc kruskalalmc test
-library(rcompanion) # for Scheirer-Ray-Hare non-parametric 2 way test, derived from Kruskal-Wallis
-# library(FSA) # for Dunn test
-library(dunn.test)
-# library(rstatix)
-library(minpack.lm)
-#library(tidyquant)
-#library(data.table)
-# library(googledrive)
-# library(googlesheets4)
-library(dplyr)
 library(tidyverse)
 
-knitr::write_bib(c("tidyverse", "lubridate","knitr", "stringr", "broom", "zoo", "RColorBrewer", "grid", "glue", "bookdown"), 'RPackages.bib')
+knitr::write_bib(c("tidyverse", "lubridate","knitr", "stringr", "broom", "zoo", "RColorBrewer", "grid", "glue", "bookdown","egg"), 'RPackages.bib')
 
@@
 
-Read .Rds
+# Read data
 ```{r read ProcessFile}
@@
 
-Make O2_uM, PAR and WL as factor levels from highest to lowest
+# Make O2_uM and WL as factor levels from highest to lowest
 ```{r O2 levels}
@@
 
-# MyWavelengths = c(450, 530, 660, "WW")
-# MCMIXColours = c(w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "black")
+MyWavelengths = c("WW", 660, 530, 450)
 
-MyWavelengths = c("WW", 660, 530, 450)
 MCMIXColours = c("black", w_length2rgb(660), w_length2rgb(530),  w_length2rgb(450))
@@
 
-Set Strip colors for WL x_strip is for WL faceted by columns and y_strip is for WL faceted by rows
+# Set Strip colors for WL x_strip is for WL faceted by columns and y_strip is for WL faceted by rows
 ```{r}
-x_strip <- strip_themed(background_x = elem_list_rect(fill = MCMIXColours, alpha = 0.8),
-                      background_y = elem_list_rect(fill = "grey27"))
-
-x_stripWW <- strip_themed(background_x = elem_list_rect(fill = "black"),
-                      background_y = elem_list_rect(fill = "#grey27"))
-
-x_strip660 <- strip_themed(background_x = elem_list_rect(fill = "#730000"),
-                      background_y = elem_list_rect(fill = "#grey27"))
-
-x_strip530 <- strip_themed(background_x = elem_list_rect(fill = "#00FF00"),
-                      background_y = elem_list_rect(fill = "#grey27"))
-
-x_strip450 <- strip_themed(background_x = elem_list_rect(fill = "#0600FF"),
-                      background_y = elem_list_rect(fill = "#grey27"))
-
-y_strip <- strip_themed(background_y = elem_list_rect(fill = MCMIXColours),
-                      background_x = elem_list_rect(fill = "#grey27"))
-
-y_stripWW <- strip_themed(background_y = elem_list_rect(fill = "black"),
-                      background_x = elem_list_rect(fill = "#grey27"))
-
-y_strip660 <- strip_themed(background_y = elem_list_rect(fill = "#730000"),
-                      background_x = elem_list_rect(fill = "#grey27"))
-
-y_strip530 <- strip_themed(background_y = elem_list_rect(fill = "#00FF00"),
-                      background_x = elem_list_rect(fill = "#grey27"))
-
-y_strip450 <- strip_themed(background_y = elem_list_rect(fill = "#0600FF"),
-                      background_x = elem_list_rect(fill = "#grey27"))
+# x_strip <- strip_themed(background_x = elem_list_rect(fill = MCMIXColours, alpha = 0.8),
+#                       background_y = elem_list_rect(fill = "grey27")) 
+# 
+# x_stripWW <- strip_themed(background_x = elem_list_rect(fill = "black"),
+#                       background_y = elem_list_rect(fill = "#grey27"))
+# 
+# x_strip660 <- strip_themed(background_x = elem_list_rect(fill = "#730000"),
+#                       background_y = elem_list_rect(fill = "#grey27"))
+# 
+# x_strip530 <- strip_themed(background_x = elem_list_rect(fill = "#00FF00"),
+#                       background_y = elem_list_rect(fill = "#grey27"))
+# 
+# x_strip450 <- strip_themed(background_x = elem_list_rect(fill = "#0600FF"),
+#                       background_y = elem_list_rect(fill = "#grey27"))
+# 
+# y_strip <- strip_themed(background_y = elem_list_rect(fill = MCMIXColours),
+#                       background_x = elem_list_rect(fill = "#grey27")) 
+# 
+# y_stripWW <- strip_themed(background_y = elem_list_rect(fill = "black"),
+#                       background_x = elem_list_rect(fill = "#grey27"))
+# 
+# y_strip660 <- strip_themed(background_y = elem_list_rect(fill = "#730000"),
+#                       background_x = elem_list_rect(fill = "#grey27"))
+# 
+# y_strip530 <- strip_themed(background_y = elem_list_rect(fill = "#00FF00"),
+#                       background_x = elem_list_rect(fill = "#grey27"))
+# 
+# y_strip450 <- strip_themed(background_y = elem_list_rect(fill = "#0600FF"),
+#                       background_x = elem_list_rect(fill = "#grey27"))
 
@@
 
-```{r LogisticFitPlot, fig.height= 10, fig.width= 10 }
-maxOD_x = 500
-maxOD_y = 0.165
-
-minOD_x =500
-minOD_y = 0.005
-
-time_x = 300
-time_y = -0.005
-
-Predict_x = 4
-Predict_y = 0.06
-
-deltaODLogGrowthPlot <- PURPARFits %>%
-  filter(Run == 114) %>% 
-  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
-         OxygenLabel_title = "Oxygen Concentration",
-         Oxygen_label = case_when(O2_uM %in% c(2.5, 25, 250) ~ paste("[Oxygen]", O2_uM, "µM", sep = " ")),
-         WL_label_title = "Growth Wavelength",
-         WL_label = case_when(WL %in% c(450, 530, 660) ~ paste(WL, "nm", sep = " "),
-                              WL %in% c("WW") ~ paste("White LED", sep = " ")),
-         Par_label = case_when(Par_ue %in% c(30, 90, 180) ~ paste(Par_ue, "µE", sep = " ")),
-         PhotoLabel = case_when(Photoperiod == 16 ~ "16 h Photoperiod", 
-                                 Photoperiod == 12 ~ "12 h Photoperiod",
-                                 Photoperiod == 8 ~ "8 h Photoperiod",
-                                 Photoperiod == 4 ~ "4 h Photoperiod")) %>%
-  # mutate(deltaOD_logistic_predict = map(deltaOD_logistic, possibly(augment, otherwise = NULL))) %>%
-  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) %>%
-  ggplot() +
-  geom_point(aes(x = tubedata_time, y = tubedata_deltaOD), colour = "darkgreen", size = 0.1) +
-  scale_colour_manual(values = MCMIXColours) +
-  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.fitted), colour = "black", size = 0.1) +
-  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.resid), colour = "gold", size = 0.05) +
-  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/5000, colour = as.factor(WL)), size = 0.25, alpha = 1.0) +
-   scale_y_continuous(name="Chlorophyll proxy (ΔOD)", sec.axis=sec_axis(~.*5000, name = Actinic ~PAR~(µmol~photons~m^{-2}~s^{-1}))) +
-  #coord_cartesian(xlim = c(-5, 675)) +
-  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
-  # facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
-   # ggh4x::facet_nested(cols = vars(Tube, Strain,Photoperiod, Oxygen_label, WL_label, Par_label), 
-   #                  labeller = labeller(Tube = label_both, WL_label = label_value, WL = label_value, Strain = label_value, OxygenLabel_title = label_value,Oxygen_label = label_value, OxygenLabel = label_value, Photoperiod = label_both, Par_label = label_value))+
-   ggh4x::facet_nested(cols = vars(PhotoLabel, Oxygen_label, Tube, SampleID,  Strain, WL_label, Par_label), 
-                    labeller = labeller(Tube = label_both, WL_label = label_value, WL = label_value, Strain = label_value, OxygenLabel_title = label_value,Oxygen_label = label_value, OxygenLabel = label_value, Photoperiod = label_both, Par_label = label_value, SampleID = label_both))+
-  labs(y = "Chlorophyll proxy (ΔOD)" , x = "Elapsed Time (h)") +
-   guides(colour = "none") +
-  theme_bw() +
-  theme( strip.text = element_text(size = 11),
-        axis.title = element_text(size = 20, color = "black"),
-        axis.text.x = element_text(size = 15, color = "black", angle = 60, hjust = 1.0),
-        axis.text.y = element_text(size = 15, color = "black", angle = 0, hjust = 1.0),
-        # strip.background=element_rect(color="grey", fill = "grey"),
-        strip.background=element_rect(fill = "grey"),
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title = element_text(size = 20),  #change legend title font size
-        legend.text = element_text(size = 20),   #change legend text font size
-        legend.position = "top")
-
-deltaODLogGrowthPlot
-
-deltaODLogGrowthPlotExpand <- PURPARFits %>%
-  filter(Run == 28,
-         Tube == 6) %>% 
-  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
-         OxygenLabel_title = "Oxygen Concentration",
-         Oxygen_label = case_when(O2_uM %in% c(2.5, 25, 250) ~ paste("[Oxygen]", O2_uM, "µM", sep = " ")),
-         WL_label_title = "Growth Wavelength",
-         WL_label = case_when(WL %in% c(450, 530, 660) ~ paste(WL, "nm", sep = " "),
-                              WL %in% c("WW") ~ paste("White LED", sep = " ")),
-         Par_label = case_when(Par_ue %in% c(30, 90, 180) ~ paste(Par_ue, "µE", sep = " ")),
-         PhotoLabel = case_when(Photoperiod == 16 ~ "16 h Photoperiod", 
-                                 Photoperiod == 12 ~ "12 h Photoperiod",
-                                 Photoperiod == 8 ~ "8 h Photoperiod",
-                                 Photoperiod == 4 ~ "4 h Photoperiod")) %>%
-  # mutate(deltaOD_logistic_predict = map(deltaOD_logistic, possibly(augment, otherwise = NULL))) %>%
-  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) %>%
-  ggplot() +
-  geom_point(aes(x = tubedata_time, y = tubedata_deltaOD), colour = "darkgreen", size = 0.1) +
-  geom_line(aes(x = tubedata_time, y = min(tubedata_deltaOD)), linetype = "dashed", size = 2) + 
-   geom_line(aes(x = tubedata_time, y = max(tubedata_deltaOD)), linetype = "dashed", size =2) + 
-    geom_vline(xintercept = 610, linetype = "dashed", size =2) +
- scale_colour_manual(values = MCMIXColours) +
-  # geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.fitted), colour = "black", size = 0.1) +
-  # geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.resid), colour = "gold", size = 0.05) +
-  # geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/5000, colour = as.factor(WL)), size = 0.25, alpha = 1.0) +
-   # scale_y_continuous(name="Optical Density (ΔOD)", sec.axis=sec_axis(~.*5000, name = "Actinic PAR (µE)")) +
-  #coord_cartesian(xlim = c(-5, 675)) +
-  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
-  # facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
-   # ggh4x::facet_nested(cols = vars(Tube, Strain,Photoperiod, Oxygen_label, WL_label, Par_label), 
-   #                  labeller = labeller(Tube = label_both, WL_label = label_value, WL = label_value, Strain = label_value, OxygenLabel_title = label_value,Oxygen_label = label_value, OxygenLabel = label_value, Photoperiod = label_both, Par_label = label_value))+
-  annotate(geom = "text", x = maxOD_x, y = maxOD_y, label = "Maximum ΔOD", size = 7, colour = "darkgreen") +
-  annotate(geom = "text", x = minOD_x, y = minOD_y, label = "Minimum ΔOD", size = 7, colour = "darkgreen") +
-  annotate(geom = "text", x = time_x, y = time_y, label = "Time", size = 7, colour = "red") +
-  # annotate(geom = "text", x = Predict_x, y = Predict_y, label = "Logistic Regression", size = 5, colour = "black") +
-   # ggh4x::facet_nested(cols = vars(PhotoLabel, Oxygen_label, Tube, SampleID,  Strain, WL_label, Par_label), 
-                    # labeller = labeller(Tube = label_both, WL_label = label_value, WL = label_value, Strain = label_value, OxygenLabel_title = label_value,Oxygen_label = label_value, OxygenLabel = label_value, Photoperiod = label_both, Par_label = label_value, SampleID = label_both))+
-  labs(y = "Chlorophyll proxy (ΔOD)", x = "Elapsed Time (h)") +
-   guides(colour = "none") +
-  theme_bw() +
-  theme( strip.text = element_text(size = 11),
-        axis.title = element_text(size = 20, color = "black"),
-        axis.text.x = element_text(size = 15, color = "black", angle = 00, hjust = 1.0),
-        axis.text.y = element_text(size = 15, color = "black", angle = 0, hjust = 1.0),
-        # strip.background=element_rect(color="grey", fill = "grey"),
-        strip.background=element_rect(fill = "grey"),
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title = element_text(size = 20),  #change legend title font size
-        legend.text = element_text(size = 20),   #change legend text font size
-        legend.position = "top")
-
-deltaODLogGrowthPlotExpand
-
-deltaODGrowthRatesPlot <- PURPARFits %>%
-  filter(Run == 114,
-         Par_ue %in% c(30,90,180)) %>% 
-  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
-         OxygenLabel_title = "Oxygen Concentration",
-         Oxygen_label = case_when(O2_uM %in% c(2.5, 25, 250) ~ paste("[Oxygen]", O2_uM, "µM", sep = " ")),
-         WL_label_title = "Growth Wavelength",
-         WL_label = case_when(WL %in% c(450, 530, 660) ~ paste(WL, "nm", sep = " "),
-                              WL %in% c("WW") ~ paste("White LED", sep = " ")),
-         Par_label = case_when(Par_ue %in% c(30, 90, 180) ~ paste(Par_ue, "µE", sep = " ")),
-         PhotoLabel = case_when(Photoperiod == 16 ~ "16 h Photoperiod", 
-                                 Photoperiod == 12 ~ "12 h Photoperiod",
-                                 Photoperiod == 8 ~ "8 h Photoperiod",
-                                 Photoperiod == 4 ~ "4 h Photoperiod"),
-         deltaOD_Lmu_se_day = deltaOD_Lmu_se * 24) %>%
-  # mutate(deltaOD_logistic_predict = map(deltaOD_logistic, possibly(augment, otherwise = NULL))) %>%
-  # unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) %>%
-  ggplot() +
-  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5.0) +
-   # geom_errorbar(aes(x = Photoperiod, ymin = deltaOD_Lmu_corr_day - deltaOD_Lmu_se_day, ymax = deltaOD_Lmu_corr_day + deltaOD_Lmu_se_day), width = 0.2 , size = 0.3, color = 'black', alpha = 0.3, data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-  scale_colour_manual(values = MCMIXColours) +
-  # geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.fitted), colour = "black", size = 0.1) +
-  # geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.resid), colour = "gold", size = 0.05) +
-  # geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/5000, colour = as.factor(WL)), size = 0.25, alpha = 1.0) +
-  #coord_cartesian(xlim = c(-5, 675)) +
-  scale_x_continuous(breaks=seq(0, 16, by = 4)) +
-  # facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
-   # ggh4x::facet_nested(cols = vars(Tube, Strain,Photoperiod, Oxygen_label, WL_label, Par_label), 
-   #                  labeller = labeller(Tube = label_both, WL_label = label_value, WL = label_value, Strain = label_value, OxygenLabel_title = label_value,Oxygen_label = label_value, OxygenLabel = label_value, Photoperiod = label_both, Par_label = label_value))+
-   ggh4x::facet_nested(cols = vars(PhotoLabel, Oxygen_label, Tube, SampleID,  Strain, WL_label, Par_label), 
-                    labeller = labeller(Tube = label_both, WL_label = label_value, WL = label_value, Strain = label_value, OxygenLabel_title = label_value,Oxygen_label = label_value, OxygenLabel = label_value, Photoperiod = label_both, Par_label = label_value, SampleID = label_both))+
-  labs(y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
-   guides(colour = "none") +
-  theme_bw() +
-  theme( strip.text = element_text(size = 11),
-        axis.title = element_text(size = 20, color = "black"),
-        axis.text.x = element_text(size = 15, color = "black", angle = 0, hjust = 1.0),
-        axis.text.y = element_text(size = 15, color = "black", angle = 0, hjust = 1.0),
-        # strip.background=element_rect(color="grey", fill = "grey"),
-        strip.background=element_rect(fill = "grey"),
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title = element_text(size = 20),  #change legend title font size
-        legend.text = element_text(size = 20),   #change legend text font size
-        legend.position = "top")
-
-deltaODGrowthRatesPlot
-
-```
-
 ```{r PURPARRatioPlots, fig.height= 10, fig.width= 10}
@@
     geom_abline(slope = 1, intercept = 0, colour = "grey39", linetype = "dashed", linewidth = 1.2) +
-  #geom_jitter(aes(x = Pur_ue, y = Par_ue, colour = as.factor(Strain)), size = 3, alpha = 0.5) +
   labs(y = "PUR (µE)" , x = "PAR (µE)") +
- #geom_text(aes(x = Pur_ue, y = deltaOD_Lmu_corr, label= WL), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
- # geom_errorbar(aes(x = Pur_ue, ymin = (deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +\
-   # scale_linetype_manual(values = c("MED4" = "solid", "MIT9313" = "longdash",  "SS120" = "dotted")) +
    scale_x_continuous(breaks=seq(0, 180, by = 30)) +
@@
    scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660","530", "450" )) +
- # ggh4x::facet_nested(rows = vars(Strain), 
- #                     labeller = labeller(WL = label_both, Strain = label_both)) + 
    geom_text(aes(x = 60, y = 180, label = paste(Strain), show.legend = FALSE, ),    # parse = TRUE,
@@
 ggsave(file = file.path(PlotsPath, paste("PurParPlot",".png",sep = "")), plot = PurParPlot, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-```
-
-```{r MED4 PURPAR, fig.height= 10, fig.width= 10}
-
-MED4PurParPlot <- PURPARFits %>%
-  filter(Par_ue %in% c(30, 90, 180)) %>%
-  mutate(Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
-  filter(Strain == "MED4") %>% 
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = Pur_ue, colour = as.factor(WL)), size = 3, alpha = 0.5) +
- geom_line(aes(x = Par_ue, y = Pur_ue,colour = as.factor(WL)), linewidth = 0.7) +
-    geom_abline(slope = 1, intercept = 0, colour = "grey39", linetype = "dashed", linewidth = 1.2) +
-  #geom_jitter(aes(x = Pur_ue, y = Par_ue, colour = as.factor(Strain)), size = 3, alpha = 0.5) +
-  labs(y = "PUR (µE)" , x = "PAR (µE)") +
- #geom_text(aes(x = Pur_ue, y = deltaOD_Lmu_corr, label= WL), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
- # geom_errorbar(aes(x = Pur_ue, ymin = (deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +\
-   # scale_linetype_manual(values = c("MED4" = "solid", "MIT9313" = "longdash",  "SS120" = "dotted")) +
-   scale_x_continuous(breaks=seq(0, 180, by = 30)) +
-  # coord_cartesian(xlim = c (0, 180)) +
-    scale_y_continuous(breaks=seq(0, 180, by = 30)) +
-  coord_fixed(ylim = c (0, 180), xlim = c (0, 180), ratio = 1) +
-   scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660","530", "450" )) +
- # ggh4x::facet_nested(rows = vars(Strain), 
- #                     labeller = labeller(WL = label_both, Strain = label_both)) + 
-   geom_text(aes(x = 60, y = 180, label = paste(Strain), show.legend = FALSE, ),    # parse = TRUE,
-    hjust = 0,
-    vjust = 1,
-    size = 8.0
-  )  +
-  facet_wrap(~Strain, ncol = 2) +
-  theme_bw() +
-  labs(colour = "Growth Waveband (nm)") +
-  theme(strip.text = element_blank(),
-        legend.text = element_text(size = 20),
-        legend.title = element_text(size = 25),
-        # legend.position = c(0.30, 0.7),
-        legend.position = "none",
-        axis.title = element_text(hjust= 0.60, vjust = -0.2, size = 20),
-        strip.text.x = element_blank(),
-        axis.text = element_text(size = 15, color = "black"))
-MED4PurParPlot
-
-```
-
-```{r save individual ParPurPlots}
-
-ggsave(file = file.path(PlotsPath, paste("MED4PurParPlot",".png",sep = "")), plot = MED4PurParPlot, device = NULL, scale = 1, height=10, width= 10, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
 ```{r, save O2ColorPURPlots}
-# ggsave(file = file.path(PlotsPath, paste("MED4PhotobyO2PUR",".png",sep = "")), plot = MED4PhotobyO2PUR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+# ggsave(file = file.path(PlotsPath, paste("MED4NoPhotoPUR",".png",sep = "")), plot = MED4NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
 # 
-# ggsave(file = file.path(PlotsPath, paste("MIT9313PhotobyO2PUR",".png",sep = "")), plot = MIT9313PhotobyO2PUR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsPath, paste("MIT9313NoPhotoPUR",".png",sep = "")), plot = MIT9313NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
 # 
-# ggsave(file = file.path(PlotsPath, paste("SS120PhotobyO2PUR",".png",sep = "")), plot = SS120PhotobyO2PUR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-ggsave(file = file.path(PlotsPath, paste("MED4NoPhotoPUR",".png",sep = "")), plot = MED4NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-ggsave(file = file.path(PlotsPath, paste("MIT9313NoPhotoPUR",".png",sep = "")), plot = MIT9313NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-ggsave(file = file.path(PlotsPath, paste("SS120NoPhotoPUR",".png",sep = "")), plot = SS120NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsPath, paste("SS120NoPhotoPUR",".png",sep = "")), plot = SS120NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
 
-Ecological plots
+# PAR plots
 ```{r ParPlots, fig.height= 10, fig.width= 10}
@@
 
-Overlay
+# Overlay whole cell absorbance with emission spectra
 ```{r MED4 All Spectral Emission,  fig.height = 10, fig.width = 10}
@@
 
-MED4WWOverlayPlots <- PURPARFits %>%
-  filter(Strain == "MED4",
-          Par_ue == 90,
-          O2_Category == "Intermediate" & WL == "WW" & Photoperiod == 16) %>%
-  mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste("Growth", "waveband", "=", WL, "nm", sep = " "),
-        WL %in% c("WW") ~ paste("Growth", "waveband", "=", "White LED", sep = " "))) %>% 
-   unnest(cols = c(PurData), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_longer(cols = c(PurData_PURAbsWholeCell_Norm440, PurData_AbsNorm440,  PurData_MC_NormEm), values_to = "Abs_Em_Value", names_to = "Abs_Em_Names") %>%
-ggplot()+
-  geom_area(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, fill = as.factor(WL)), color = "black", 
-            size = 0.5, alpha = 0.7, show.legend = FALSE, 
-            data = . %>% filter(Abs_Em_Names == "PurData_PURAbsWholeCell_Norm440")) +
-  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = Abs_Em_Names,  linetype = Abs_Em_Names), size = 2) +
-  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = as.factor(WL),  linetype = Abs_Em_Names), size = 2.0, data = . %>% filter(Abs_Em_Names == "PurData_MC_NormEm")) +
-  scale_color_manual(values = c(MCMIXColours, "PurData_PURAbsWholeCell_Norm440" = "black", "PurData_AbsNorm440" = "aquamarine4", "PurData_MC_NormEm" = "white")) +
-  scale_linetype_manual(values = c("PurData_PURAbsWholeCell_Norm440" = "solid", "PurData_AbsNorm440" = "solid",  "PurData_MC_NormEm" = "dotted"),
-                        labels = c("LED emission", "Whole cell abs.", "PUR")) +
-  scale_fill_manual(values = MCMIXColours) +
- # guides(colour = FALSE) +
-  labs(y = "Normalized Absorbance and Emission", x = "Wavelength (nm)") +
-  labs(linetype = "Spectra Type")+
-  scale_y_continuous(breaks=seq(0, 1.5, by = 0.25)) +
- # coord_cartesian(ylim = c (0, 0.2)) +
-   facet_wrap(vars(WL),
-              labeller = labeller(strain = label_value, WL = label_value, Photoperiod = label_both, Par_ue = label_both, O2_Category = label_both, Pur_ue = label_both)) +
-  geom_text(aes(x = 430, y = 1.1, label = WL_label, color = as.factor(WL)), show.legend = FALSE,
-    # parse = TRUE,
-    hjust = 0,
-    vjust = 1,
-    size = 7.0
-  )  +
-   geom_text(aes(x = 560, y = 0.95, label = paste("PAR", "=", Par_ue, "uE", sep = " "), show.legend = FALSE, ),
-    # parse = TRUE,
-    hjust = 0,
-    vjust = 1,
-    size = 6.0
-  )  +
-  geom_text(aes(x = 560, y = 0.85, label = paste("PUR", "=", Pur_ue, "uE",sep = " "), show.legend = FALSE, ),
-    # parse = TRUE,
-    hjust = 0,
-    vjust = 1,
-    size = 6.0
-  )  +
-  guides(color = "none") +
-  theme_bw() +
- theme(strip.text = element_blank(),
-       legend.background = element_rect(color = "transparent", fill = "transparent"),
-        legend.text = element_text(size = 25),
-        legend.title = element_text(size = 25),
-        # legend.position = c(0.94,0.96),
-        legend.position = "top",
-        axis.title = element_text(vjust = 1.0, size = 30),
-        # strip.text.x = element_text(size = 20),
-        axis.text = element_text(size = 25, color = "black"))
-
-MED4WWOverlayPlots
-
 ```
@@
 
-ggsave(file = file.path(PlotsPath, paste("MED4OverlayPlots",".png",sep = "")), plot = MED4OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-ggsave(file = file.path(PlotsPath, paste("MED4WWOverlayPlots",".png",sep = "")), plot = MED4WWOverlayPlots, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsPath, paste("MED4OverlayPlots",".png",sep = "")), plot = MED4OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+# 
+# ggsave(file = file.path(PlotsPath, paste("MED4WWOverlayPlots",".png",sep = "")), plot = MED4WWOverlayPlots, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
 
-ggsave(file = file.path(PlotsPath, paste("MIT9313OverlayPlots",".png",sep = "")), plot = MIT9313OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsPath, paste("MIT9313OverlayPlots",".png",sep = "")), plot = MIT9313OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
 
-ggsave(file = file.path(PlotsPath, paste("SS120OverlayPlots",".png",sep = "")), plot = SS120OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsPath, paste("SS120OverlayPlots",".png",sep = "")), plot = SS120OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 

### 2024-01-15 Code/Import_JazEmData.Rmd
Tidied scripts
Corrected incorrect variable name for unnest column

@@
 JazSpecNest <- MC_SpectraPAR %>%
-  nest(Spectra = c(MCEm_nm, Emission))
+  nest(EmSpectra = c(MCEm_nm, Emission))
 
@@
 JazSpecNest %>%
-  unnest(Spectra) %>%
+  unnest(EmSpectra) %>%
     ggplot() +

### 2024-01-15 Code/Merge_GrowthPURData.Rmd
Changed folder name to Figures in PlotsPath

@@
 DataOut <- file.path("..", "Data", "CleanData")
-PlotsPath <- file.path("..", "Output", "Plots")
+PlotsPath <- file.path("..", "Output", "Figures")
 

### 2024-01-15 Code/Merge_MCGrowthData.Rmd
Fixed ExpStartTime to extract time

@@
 library(grid)
-# library(photobiologyWavebands)
+library(photobiologyWavebands)
 library(tidyverse)
@@
 
+```
+
+#Fix ExpStartTime such that only time is extracted
+```{r fix start time column}
+LogFitsData <- LogFitsData %>%
+   mutate(ExpStartTime = hms::as_hms(ymd_hms(ExpStartTime)))
+
+glimpse(LogFitsData)
 ```
@@
 
-# Chunk to convert categorize oxygen levels based on input in metacatalog.
-Have to do this here as this column was added after many runs were already processed and the merge with metacatalog already occured.
-Run numbers >= 36 and <= 91 and 0% oxygen are labelled 'Low', runs <= 35  and 0% oxygen are labelled 'Intermediate'.
-All runs >= 92 are from the metacatelog.
-All runs with 21% oxygen are labelled 'High'.
-Assign [O2] to O2_uM based on category
+# Chunk to convert categorize oxygen levels based on input in metacatalog into O2 concentration (uM).
+Runs <= 36 and 0% oxygen are labelled 'Intermediate' because the purity of the nitrogen tank used for those experiments were lower and contained O2.
 ```{r O2 levels}
@@
 ```
+# Remove redundant df
+```{r remove}
+remove(LogFitsData)
+```
 
-Save Long DF for GAM and Nested for further analysis 
+# Save Long DF for GAM and Nested for further analysis 
 ```{r save files}
@@
 ```
-
-Plot All
-```{r LogisticdeltaODPlots, fig.height= 10, fig.width= 10}
-
-MCGrowthFits %>%
-   filter(Strain == "SS120") %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.5) +
- geom_line(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
-   labs(subtitle = "Strain, [Oxygen], Photoperiod, Actinic PAR (nm)", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
- geom_text(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, label= Run), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
-  geom_errorbar(aes(x = Par_ue, ymin = (ReplicateMean_deltaOD_Lmu_corr - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
-  coord_cartesian(xlim = c (0, 200)) +
-  #   scale_y_continuous(breaks=seq(-0.03, 0.07, by = 0.01)) +
-  # coord_cartesian(ylim = c (-0.03, 0.07)) +
-  scale_colour_manual(values = MCMIXColours) +
-  ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
-                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")
-
-MCGrowthFits %>%
-   filter(Strain == "MIT9313",
-          ReplicateMean_deltaOD_Lmu_corr == 0 |
-          ReplicateMean_deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.4) +
- geom_line(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
- labs(subtitle = "Strain, [Oxygen],Photoperiod, Actinic PAR (nm) - Of cultures that grew, outliers filtered by standard error > 20% of growth rate.", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
-   geom_text(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, label= Run), alpha = 0.5,hjust = 0.5, vjust=-0.5) +
-  # geom_jitter(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), size = 6) +
-  geom_errorbar(aes(x = Par_ue, ymin = ReplicateMean_deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = ReplicateMean_deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
-  coord_cartesian(xlim = c (0, 200)) +
-  #   scale_y_continuous(breaks=seq(0, 0.07, by = 0.01)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours) +
-  ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
-                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")
-
- MCGrowthFits %>%
-   filter(Strain == "MED4",
-          ReplicateMean_deltaOD_Lmu_corr == 0 |
-          ReplicateMean_deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.4) +
- geom_line(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
-   labs(subtitle = "Strain, [Oxygen],Photoperiod, Actinic PAR (nm) - Of cultures that grew, outliers filtered by standard error > 20% of growth rate.", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
- geom_text(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, label= Run), alpha = 0.5,hjust = 0.5, vjust=-0.5) +
-  geom_errorbar(aes(x = Par_ue, ymin = ReplicateMean_deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = ReplicateMean_deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
-  coord_cartesian(xlim = c (0, 200)) +
-  #   scale_y_continuous(breaks=seq(0, 0.115, by = 0.01)) +
-  # coord_cartesian(ylim = c (0, 0.115)) +
-  scale_colour_manual(values = MCMIXColours) +
- ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
-                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")
-
- MCGrowthFits %>%
-   filter(Strain == "MIT9313" |
-         Strain == "SS120" |
-         Strain == "MED4",
-          ReplicateMean_deltaOD_Lmu_corr == 0 |
-          ReplicateMean_deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
-  ggplot() +
-  geom_point(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), size = 3, alpha = 0.5) +
-  geom_line(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, colour = as.factor(WL)), linewidth = 0.1, alpha = 0.4) +
-labs(subtitle = "Strain, [Oxygen], Photoperiod, Actinic PAR (nm)", y = "deltaOD [~Chl] " ~ "Logistic Growth Rate" ~ "("~h^-1~")" , x = "Growth Light (µmol photons" ~m^-2 ~s^-1~")") +
- geom_text(aes(x = Par_ue, y = ReplicateMean_deltaOD_Lmu_corr, label= Run),alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
-  geom_errorbar(aes(x = Par_ue, ymin = ReplicateMean_deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = ReplicateMean_deltaOD_Lmu_corr + deltaOD_Lmu_se), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-  scale_x_continuous(breaks=seq(0, 200, by = 50)) +
-  coord_cartesian(xlim = c (0, 200)) +
- #   scale_y_continuous(breaks=seq(-0.03, 0.07, by = 0.01)) +
-  # coord_cartesian(ylim = c (-0.03, 0.07)) +
-  scale_colour_manual(values = MCMIXColours) +
-  ggh4x::facet_nested(cols = vars(Strain, O2_uM, Photoperiod), rows = vars(WL), 
-                    labeller = labeller(WL = label_both, O2_uM = label_both, Strain = label_both, Photoperiod = label_value)) +
-  theme_bw() +
-  labs(colour = "Actinic PAR (nm)")
-
-```

### 2024-01-17 Code/Merge_MCGrowthData.Rmd
Added an intro and removed the pivot longer for GAM data frame. Structured the data frame in the PICOgam.Rmd.

@@
 ---
-title: "MultiDataGrowthAssessPico"
+title: "Merge_MCGrowthData"
 author:
@@
 # Introduction
+This Rmd, "Merge_MCGrowthData", reads in all individually processed MultiCulti runs from the "\Data\ProcessedData\ProcessedMCData" folder and merges the data into 1 data frame.
+Growth estimate flags are defined based on absolute amplitude change.
+Growth estimates are set to 0 for models that returned a negative growth estimate and if the absolute amplitude change threshold was not met.
+For conditions that were replicated, a mean growth estimate was calculated.
+This single data frame is saved as a .Rds for further analysis called "PICO_Processed_MCGrowthFits.Rds" in the "\Data\CleanData\CleanedMCData" folder.
 
-# Materials and Methods
-
-## Load Libraries and set project variables
-
+# Load Libraries and set project variables
 ```{r load libraries, message= TRUE}
@@
 
-# Read .Rds, Summarize, Combine to single data frame. Create function using to read in .Rds, adding source filename as a column
+# Create function using to read in .Rds, adding source filename as a column. Read .Rds, summarize, combine to single data frame. 
 ```{r readRDS_plus}
@@
 
-#Fix ExpStartTime such that only time is extracted
+#Fix ExpStartTime to extract only time 
 ```{r fix start time column}
@@
 
+# Merge OD720 with deltaOD fits
 ```{r combine unnested fits}
@@
 
-```{r, pivot Nested data longer for GAM}
-
-# OD720 pivot longer Gmax, Gmu, Glag, Lmu, Lmax and Lintercept estimates
-Pivot_Longer_OD720_est <- MCGrowthFits %>%
-  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue, Photoperiod, PARPhotonDose_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape,  GrowthAmpOD720_14days, GrowthAmpOD720Flag_14days,  OD720_LseGrowthFlag, OD720trunc_LseGrowthFlag,  OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720trunc_Lmu_corr, OD720trunc_Lmax, OD720trunc_Lintercept
-            )) %>%
-   pivot_longer(c(OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720trunc_Lmu_corr, OD720trunc_Lmax, OD720trunc_Lintercept), names_to = c("Wavelength", "term"), values_to = c("estimate"), names_sep = '\\_')
-
-# OD720 pivot longer Gmax, Gmu, Glag , Lmu, Lmax and Lintercept standard error
-Pivot_Longer_OD720_se <- MCGrowthFits %>%
-  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue,  Photoperiod, PARPhotonDose_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape, GrowthAmpOD720_14days, GrowthAmpOD720Flag_14days,  OD720_LseGrowthFlag, OD720trunc_LseGrowthFlag,   OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se,OD720trunc_Lmu_se, OD720trunc_Lmax_se, OD720trunc_Lintercept_se
-            )) %>%
-   pivot_longer(c(OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se, OD720trunc_Lmu_se, OD720trunc_Lmax_se, OD720trunc_Lintercept_se), names_to = c("Wavelength", "term"), values_to = c("se"), names_sep = '\\_')
-
-# Join OD720 estimate and se DF 
-Longer_OD720_Joined <- full_join(Pivot_Longer_OD720_est, Pivot_Longer_OD720_se)
-
-remove(Pivot_Longer_OD720_est, Pivot_Longer_OD720_se)
-
-# rename common columns for full join
-Longer_OD720_Joined <- Longer_OD720_Joined %>%
-  rename(GrowthAmp_14days = 'GrowthAmpOD720_14days',
-         GrowthAmp_14daysFlag = 'GrowthAmpOD720Flag_14days',
-         Lmu_seFlag = 'OD720_LseGrowthFlag',
-         Lmutrunc_seFlag = 'OD720trunc_LseGrowthFlag'
-         )
-
-# deltaOD pivot longer Gmax, Gmu, Glag, Lmu, Lmax and Lintercept estimates
-Pivot_Longer_deltaOD_est <- MCGrowthFits %>%
-  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue,  Photoperiod, PARPhotonDose_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape,  GrowthAmpdeltaOD_14days, GrowthAmpdeltaODFlag_14days,  deltaOD_LseGrowthFlag, deltaODtrunc_LseGrowthFlag,  deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept, deltaODtrunc_Lmu_corr, deltaODtrunc_Lmax, deltaODtrunc_Lintercept
-            )) %>%
-   pivot_longer(c( deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept, deltaODtrunc_Lmu_corr, deltaODtrunc_Lmax, deltaODtrunc_Lintercept), names_to = c("Wavelength", "term"), values_to = c("estimate"), names_sep = '\\_')
-
-# deltaOD pivot longer Gmax, Gmu, Glag , Lmu, Lmax and Lintercept standard error
-Pivot_Longer_deltaOD_se <- MCGrowthFits %>%
-  select(c(Filename, Tube, SampleID, Run, PrimaryOperator, Strain, Par_ue,  Photoperiod, PARPhotonDose_day, Temp_c, O2, O2_Category,O2_uM, WL, LightShape,  GrowthAmpdeltaOD_14days, GrowthAmpdeltaODFlag_14days,  deltaOD_LseGrowthFlag, deltaODtrunc_LseGrowthFlag,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se, deltaODtrunc_Lmu_se, deltaODtrunc_Lmax_se, deltaODtrunc_Lintercept_se
-            )) %>%
-   pivot_longer(c(deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se, deltaODtrunc_Lmu_se, deltaODtrunc_Lmax_se, deltaODtrunc_Lintercept_se), names_to = c("Wavelength", "term"), values_to = c("se"), names_sep = '\\_')
-
-# Join deltaOD estimate and se DF 
-Longer_deltaOD_Joined <- full_join(Pivot_Longer_deltaOD_est, Pivot_Longer_deltaOD_se)
-
-remove(Pivot_Longer_deltaOD_est, Pivot_Longer_deltaOD_se)
-
-# rename common columns for full join
-Longer_deltaOD_Joined <- Longer_deltaOD_Joined %>%
-  rename(GrowthAmp_14days = 'GrowthAmpdeltaOD_14days',
-         GrowthAmp_14daysFlag = 'GrowthAmpdeltaODFlag_14days',
-         Lmu_seFlag = 'deltaOD_LseGrowthFlag',
-         Lmutrunc_seFlag = 'deltaODtrunc_LseGrowthFlag'
-         )
-
-#Join OD720 and deltaOD fits data
-LongerFitsData <- rbind(Longer_OD720_Joined, Longer_deltaOD_Joined) %>%
-  mutate_if(is.numeric, round, digits = 3)
-
-remove(Longer_OD720_Joined, Longer_deltaOD_Joined)
-
-glimpse(LongerFitsData)
-
-```
 # Remove redundant df
@@
 
-saveRDS(object = LongerFitsData, file = file.path(DataOut, paste(Project, "LongerGrowthFitsData.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
-
 saveRDS(object = MCGrowthFits, file = file.path(DataOut, paste(Project, "Processed_MCGrowthFits.Rds",  sep = "_")), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

### 2024-01-17 Code/ManuscriptFigures.Rmd
Fixed order of PAR to increase from 30, 90, 180 uE when faceted by row

@@
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         WL= factor(WL, levels = c("WW", 660, 530, 450)),
-         deltaOD_Lmu_corr_day = deltaOD_Lmu_corr *24)
+         WL = factor(WL, levels = c("WW", 660, 530, 450)),
+         deltaOD_Lmu_corr_day = deltaOD_Lmu_corr * 24,
+         deltaOD_Lmu_se_day = deltaOD_Lmu_se * 24)
 #  Par_ue = factor(Par_ue, levels =  c(180, 120, 100,90,60, 30, 15))
@@
   select(!contains(c("trunc", "OD720", "OptodeMeasure"))) %>% 
-  filter(Strain %in% c("MED4", "MIT9313", "SS120"))
+  filter(Strain %in% c("MED4", "MIT9313", "SS120"),
+         WL %in% c("WW", 450, 660))
 
@@
 
-MED4NoPhotoPUR <- PURPARFits %>%
+# MED4NoPhotoPUR <- PURPARFits %>%
+PURPARFits %>%
    filter(Strain == "MED4", 
@@
 
-MED4NoPhotoPUR
+# MED4NoPhotoPUR
 
-SS120NoPhotoPUR <- PURPARFits %>%
+# SS120NoPhotoPUR <- PURPARFits %>%
+PURPARFits %>%
    filter(Strain == "SS120", 
@@
 
-SS120NoPhotoPUR
+# SS120NoPhotoPUR
 
-MIT9313NoPhotoPUR <- PURPARFits %>%
+# MIT9313NoPhotoPUR <- PURPARFits %>%
+   PURPARFits %>%
      filter(Strain == "MIT9313", 
@@
 
-MIT9313NoPhotoPUR
+# MIT9313NoPhotoPUR
 
@@
          ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
-         Par_ue = factor(Par_ue, levels = c(180, 90, 30))) %>%
+         Par_ue = factor(Par_ue, levels = c(30, 90, 180))) %>%
   ggplot() +
@@
 
-MIT9313OverlayPlots <- PURPARFits %>%
+# MIT9313OverlayPlots <- PURPARFits %>%
+PURPARFits %>%
    filter(Strain == "MIT9313",
@@
 
- MIT9313OverlayPlots <- tag_facet(MIT9313OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
-
- MIT9313OverlayPlots
+ # MIT9313OverlayPlots <- tag_facet(MIT9313OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
+ # 
+ # MIT9313OverlayPlots
 ```
@@
 ```{r SS120 PUR overlay with legend,  fig.height = 10, fig.width = 10}
-SS120OverlayPlots <- PURPARFits %>%
+# SS120OverlayPlots <- PURPARFits %>%
+PURPARFits %>%
    filter(Strain == "SS120",
@@
 
- SS120OverlayPlots <- tag_facet(SS120OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
-
- SS120OverlayPlots
+ # SS120OverlayPlots <- tag_facet(SS120OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
+ # 
+ # SS120OverlayPlots
 

### 2024-01-18 Code/Merge_GrowthPURData.Rmd
Removed unneccesary libraries

@@
 library(knitr)
-
-knitr::write_bib(c("tidyverse", "lubridate","knitr", "broom", "zoo", "RColorBrewer", "grid", "glue", "bookdown"), 'RPackages.bib')
+library(tidyverse)
 

### 2024-01-18 Code/ManuscriptFigures.Rmd
removed the RPackages.bib in this RMD and placed it in the manuscript RMD
Changed PlotsPath to PlotsOut for clarity

@@
 
-knitr::write_bib(c("tidyverse", "lubridate","knitr", "stringr", "broom", "zoo", "RColorBrewer", "grid", "glue", "bookdown","egg"), 'RPackages.bib')
-
 ```
@@
 DataIn <- file.path("..","Data", "CleanData")
-PlotsPath <- file.path("..","Output", "Figures")
+PlotsOut <- file.path("..","Output", "Figures")
 # DataOut <- file.path("..","GrowthAssessData")

### 2024-01-18 Code/Manuscript_O2.Rmd
Added necessary files and edited Manuscript_O2.Rmd so that knit to HTML works

---
title: "Functional Analyses of Distinct Oxygen Concentrations and Light Niches of *Prochlorococcus marinus*"
author:
  - name: '**Mireille Savoie**'
    affil: 1
    main: true
    email: msavoie@mta.ca
  - name: Julie Nadeau
    affil: 1
  - name: Laurel Genge
    affil: 1
  - name: Sylwia Śliwińska-Wilczewska
    affil: 1,2
  - name: Maximilian Berthold
    affil: 1
  - name: Naaman Omar
    affil: 1
  - name: Douglas A. Campbell
    affil: 1
    main: false
    orcid: ''
    email: 'dcampbel@mta.ca'
affiliation:
  - num: 1
    address: Department of Biology, Mount Allison University
institute:
  - mta: 'Department of Biology, Mount Allison University, 53 York St., Sackville NB, Canada, E4L 1C9.'
date: "`r format(Sys.Date())`"
output:
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  bookdown::word_document2:
    code_folding: show
    reference_docx: KnitTemplate.docx
    keep_md: yes
    toc: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
always_allow_html: true
bibliography: [Prochlorococcus_O2_NPQ.bib, RPackages.bib]
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

```{css, echo=FALSE}
p.caption {
  font-size: 12px;
}
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r load libraries, include = FALSE}
# libraries; Note check actual dependencies

library(lubridate)
library(broom)
library(knitr)
library(grid)
library(bookdown)
library(glue)
library(cowplot)
library(ggpubr)
# library(RColorBrewer)
library(tidyverse)

knitr::write_bib(c("tidyverse", "lubridate","knitr",  "broom", "zoo", "photobiologyWavebands", "RColorBrewer", "data.table","googlesheets4",  "grid", "glue", "bookdown", "photobiology", "mgcv", "minpack.lm", "ggh4x", "cowplot", "egg"), 'RPackages.bib')

```

```{r set project variables, include = FALSE}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "CleanData")
FiguresIn <- file.path("..","Output", "Figures")
FiguresInOceanPro <- file.path( "..", "..", "OceanProteinProchlor", "Output")
FigureInO2Analy <- file.path(  "..", "..", "O2Analyses", "Output")

```

```{r read ProcessFile, include = FALSE}

# PURPARFits <- readRDS(file.path(DataIn, "PICO_Merged_GrowthFitsPURPAR.Rds"))

```

```{r, echo=FALSE, results='asis'}
citations <- list()
knitr::knit_hooks$set(knitcitations = function(before, options, envir) {
  if (before) {
    citations$reflist <- options$reflist
    citations$section <- options$section
  }
})
```

# Abstract {.unnumbered}

\newpage

# Introduction {.unnumbered}

\newpage

# Materials and methods {.unnumbered}

## Culturing {.unnumbered}

%%%%%% Taken from my thesis word for word, need to reword and shorten %%%%

Three xenic *P. marinus* cultures, obtained from Bigelow Labs, NCMA
Maine, US: MED4 (CCMP1986) from a High Light-adapted (HLI) clade, SS120
(CCMP1375) from a Low Light-adapted (LLIII) clade and MIT9313 (CCMP2773)
also from a Low Light-adapted (LLIV) clade. These cultures were then
maintained in two separate incubators. The temperature for both
incubators was set to 22°C and a light/dark cycle of 12 h. The PAR level
of the incubator was chosen to reflect the light level of the natural
niche of the ecotype during culturation. The PAR level of the incubator
containing the HLI clade, MED4, was set at 160 µmol photons m^-2^ s^-1^,
whereas the incubator containing the LLIII and LLIV clades, SS120 and
MIT9313 respectively, was set at 30 µmol photons m^-2^ s^-1^. To ensure
cultures remained in exponential growth phase, all strains were
transferred weekly in Pro99 media prepared according to
[@mooreCulturingMarineCyanobacterium2007] in autoclaved artificial
seawater. Artificial seawater was prepared according to the National
Center for Marine Algae and Microbiota (NCMA) protocol by combining salt
solution I and salt solution II using the enriched artificial seawater
(ESAW) recipe.

## Experimental design {.unnumbered}

%%%%%% Taken from my thesis word for word, need to reword and shorten %%%%

For each of three ecotypes, we imposed [O~2~] (three levels: 2.5 µM,
25µM, 250 µM), photoperiod (four levels: 4 h, 8 h, 12 h, 16 h), spectral
waveband (four bands: full spectrum white LED, 660 nm, 530 nm, 450 nm),
and light level (three levels: 30, 90, 180 µmol photons m^-2^ s^-1^)
treatments in a factorial design. Each factor is explained below. The
full crossing of all factors would yield 3 x 4 x 4 x 3 = 144 treatments
per ecotype (432 total), but due to time constraints and total absence
of growth of some ecotypes under some conditions, not all treatments
were carried out. In total, we completed 291 treatments.

All growth experiments were conducted at 22°C.

## Experimental light conditions {.unnumbered}

%%%%%% Taken from my thesis word for word, need to reword and shorten %%%%

Three growth Photosynthetically Active Radiation (PAR) levels (180, 90,
and 30 µmol photons m^-2^ s^-1^) and four spectral wavebands (white LED
full spectrum, 660 nm, 530 nm, and 450 nm) were chosen to simulate light
levels and spectral color spanning the vertical ocean water column, from
near-surface to the lower euphotic zone depths (Figure
\@ref(fig:SunDepth)). For simplicity, actinic light used for growth
under specific wavebands will be referred by the respective spectral
color; white LED for LED full spectrum, red for 660 nm, green for 530 nm
and blue for 450 nm. Four different photoperiods were chosen to simulate
various diel cycles characteristic of current and hypothetical future
niches of *P. marinus*. A photoperiod of 16 h was chosen to represent
temperate (45°N) summer at the ocean surface, 12 h for equatorial (0°N)
ocean surface or temperate (45°N) spring and fall ocean surface or
temperate (45°N) summer at deep ocean depths, 8 h for temperate (45°N)
winter at the surface or at temperate (45°N) spring and fall at depth
and equatorial (0°N) deep ocean depths and 4 h for temperate (45°N)
winter or deep ocean depths during temperate (45°N) spring and fall.

## Experimental oxygen conditions {.unnumbered}

%%%%%% Taken from my thesis word for word, need to reword and shorten %%%%

Three target dissolved oxygen concentrations [O~2~] were delivered to
tubes of the Multicultivator by mixing varying ratios of air and
Nitrogen (N~2~) gases while delivering 0.05% of Carbon Dioxide (CO~2~)
gas through a 0.2 μm sterile microfilter via a G400 gas mixing system.
To confirm and monitor the [O~2~], 4 FireSting optodes (PyroScience,
Germany) were inserted into select tubes of each modified [O~2~] run for
real-time measurements. A compensation temperature probe was placed in
the aquarium of the bioreactor to correct [O~2~] for temperature
fluctuations. In addition, the software corrected [O~2~] based on the
salinity of the media (32 ppt). For the low O~2~ environment
experiments, 0.5 to 1.0 µM of O~2~ was delivered to each Multicultivator
tube by sparging with a gas mixture containing 99.95% N~2~ and 0.05%
CO~2~ to purge dissolved O~2~ out of the culture. The intermediate O~2~
environment experiments were sparged to deliver 10 to 25 µM of O~2~
using a gas mixture containing 98.95% N~2~, 0.05% CO~2~ and 1% O~2~. The
high O~2~ environment experiments were sparged with lab air (78% N~2~,
21% O~2~, 1% Ar and 0.05% CO~2~) to deliver 230 µM of O~2~. While the
flow rate of the gas mixture was controlled, variations in bubbling
speed affected the [O~2~] delivered to each tube; therefore, a range of
[O~2~] was defined for each experimental O~2~ level; 0.5 µM - 5 µM for
low, 5 µM - 50 µM for intermediate and 200 µM - 280 µM for high O~2~
experiments. To simplify the representation of experimental [O~2~]
conditions in graphs and discussions, the approximate median [O~2~] of
each experimental range: 2.5 µM, 25 µM, and 250 µM, will be used for
low, intermediate, and high conditions, respectively. Figure
\@ref(fig:O2DataCapture) shows the data capture software of the
FireSting Oxygen Logger. Dissolved [O~2~] were measured every 5 minutes
over the duration of the Multicultivator run and recorded in a text file
for later processing in R-Studio (Figure \@ref(fig:O2Plot)).

\newpage

## Bioreactors {.unnumbered}

%%%%%% Taken from my thesis word for word, need to reword and shorten %%%%

Growth experiments under different spectral wavebands were performed
using a PSI MCMIX-OD Multicultivator (Figure \@ref(fig:MCpicture)) or a
PSI MC1000-OD Multicultivator for white LED experiments. Each
Multicultivator has the capacity to individually control 8 tubes with
specific PAR levels and photoperiods and the MCMIX-OD has options for
individually controlled spectral wavebands. 10 mL of exponential growth
culture was added to 70 mL of Pro99 media and all 8 tubes were situated
in a common temperature-controlled water bath to ensure the temperature
remained constant at 22°C over the duration of the experiment. Real time
absorbance measurements of Optical Density (OD) 680 nm (a proxy for cell
suspension density, cell scatter and cell chlorophyll content) and OD
720 nm (a proxy for cell suspension density and cell scatter) were
recorded every 5 minutes for at least 8 to 14 days depending on the
duration of the lag phase, if any. Figure \@ref(fig:MCDataCapture) is a
typical readout from the MCMIX-OD Multicultivator software. Real time OD
measurements eliminate intrusive subsampling of sterile cultures and
provide high resolution chlorophyll and cell scatter proxies over the
duration of the experiment. All data from the Multicultivator were saved
as a comma separated values file and processed in R-Studio for
calculations of growth rate estimates and graphical plotting.

\newpage

```{r MCpicture, fig.cap = MCpicture_cap , fig.height = 8, fig.width = 6, echo = FALSE}

MCpicture_cap <- glue("**PSI MCMIX-OD Multicultivator.**",
                      "The image illustrates the capability to set different spectral wavebands and light levels for individual culture tubes.",
                      "Tubes 4 and 7 have oxygen optodes inserted for real-time dissolved oxygen concentration measurements.",
                      "Real time Optical Density (OD) measurements eliminate intrusive subsampling of sterile cultures.",

                       .sep = " ")

knitr::include_graphics(file.path(FiguresIn, "MCMIX004_Picture.jpg"))
```

\newpage

## Data management and analysis {.unnumbered}

%%%%%% Taken from my thesis word for word, need to reword and shorten %%%%

Data from the Multicultivators were imported into R-Studio for data
management, growth rate calculations, statistics, and generation of
figures with the `ggplot2` package [@R-tidyverse]. The chlorophyll proxy
optical density (OD680 - OD720) or ΔOD was used to determine the growth
rate for each condition. We used a rolling mean from the RStudio `zoo`
package [@R-zoo] to calculate the average ΔOD data over a 1-hour window.
This was done to prevent extraneous data points from affecting the
growth rate estimates. A Levenberg-Marquardt algorithm
[@bellaviaLevenbergMarquardtMethod2018] modification of the non-linear
least squares fit equation using the R package `minpack.lm`
[@R-minpack.lm] was used to calculate growth rate (µ) using the logistic
equation \@ref(eq:GrowthRate):

```{=tex}
\begin{equation}
  µ = \frac{ΔOD_{max} × ΔOD_{min} × exp^{(µ × t)}}{ΔOD_{max} + (ΔOD_{min} × exp^{((µ × t) - 1)})}
  (\#eq:GrowthRate)
\end{equation}
```
where ΔOD~max~ is maximum ΔOD, ΔOD~min~ is minimum ΔOD, t is time
duration over the growth trajectory. Figure
\@ref(fig:deltaODLogGrowthPlot) is an example of a chlorophyll proxy
growth estimates fitted from the high resolution ΔOD measurements for
each tube in a Multicultivator. The residuals of the logistic growth
curve fit are shown and the growth spectral waveband is plotted and
illustrates the imposed PAR (µmol photons m^-2^ s^-1^) and photoperiod
(h). Although the chlorophyll proxy (ΔOD) growth rate was used in this
study, we also determined the cell scatter proxy (OD720) growth rate.
The correlation between the chlorophyll proxy growth rate and the cell
scatter proxy growth rate of *P. marinus* under all conditions examined
in this study was shown in Figure \@ref(fig:AllBalanceGrowthPlot) and
generally showed balance growth. The high cell scatter growth rate of
cultures that exhibited no chlorophyll proxy growth may be the logistic
model over-estimating the fits as the amplitude of the OD720 signal
maybe very small.

## Generalized additive model {.unnumbered}

%%%%%% Taken from my thesis word for word, need to reword and shorten %%%%

A Generalized Additive Model (GAM) was applied to examine the
relationship between the chlorophyll proxy (ΔOD) growth rate across the
blue spectral waveband, photoperiod and PAR levels for each *P.marinus*
ecotype in this study. The gam function from the R package `mgcv`
[@R-mgcv] was used to model the growth rate with smoothing terms to
indicate the 90, 50 and 10% quantiles. Only data below a standard error
tolerance of 30% of the fit was used in the model. Because of time
limitations, we were unable to conduct sufficient growth response
experiments for all the other spectral wavebands, except for the blue,
to fulfill the input requirements for the GAM. Therefore, our priority
was on studying the effect of blue light on growth trends, considering
that blue light is the most ecologically relevant spectral waveband for
deep ocean niches.

\newpage

# Results {.unnumbered}

\newpage

# Supplemental {.unnumbered}

```{r MED4PAR, fig.cap = MED4PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MED4PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade) vs. photoperiod (h).  **",

                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
                    "Colors represent the actinic spectral waveband (nm).",
                    "Large circles show mean or single determinations of growth rate from logistic curve fits (ex. Figure \\@ref(fig:deltaODLogGrowthPlot)); small circles show values for replicate determinations, if any: replicates often fall with larger circles",

                       .sep = " ")

knitr::include_graphics(file.path(FiguresIn, "MED4PAR.png"))
```

\newpage

```{r SS120PAR, fig.cap = SS120PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}

SS120PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low Light (LLIII) deep ocean clade) vs. photoperiod (h). **",

                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
                    "Colors represent the actinic spectral waveband (nm).",
                    "Large circles show mean or single determinations of growth rate from logistic curve fits (ex. Figure \\@ref(fig:deltaODLogGrowthPlot)); small circles show values for replicate determinations, if any: replicates often fall with larger circles",

                       .sep = " ")

knitr::include_graphics(file.path(FiguresIn, "SS120PAR.png"))

```

\newpage

```{r MIT9313PAR, fig.cap = MIT9313PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}

MIT9313PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade) vs. photoperiod (h). **",

                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
                    "Colors represent the actinic spectral waveband (nm).",
                    "Large circles show mean or single determinations of growth rate from logistic curve fits (ex. Figure \\@ref(fig:deltaODLogGrowthPlot)); small circles show values for replicate determinations, if any: replicates often fall with larger circles",

                       .sep = " ")

knitr::include_graphics(file.path(FiguresIn, "MIT9313PAR.png"))

```

\newpage

# References {.unnumbered}

### 2024-01-18 Code/ManuscriptGAM.Rmd
Renamed PICOgam to ManuscriptGAM. Any RMD that generates figures or stats for the manuscript will be named Manuscript*.Rmd

---
title: "PICOgam"
author:
- Max Berthold
- Mireille Savoie
output: html_notebook
---

# Introduction
This .Rmd produces a Generalized Additive Model (GAM) to examine the relationship between the chlorophyll proxy (ΔOD) growth rate across the blue and red spectral wavebands, photoperiod and PAR levels for each P.marinus ecotype in this study. The gam function from the R package mgcv (Wood, 2022) was used to model the growth rate with smoothing terms to indicate the 90, 50 and 10% quantiles. "PICO_Merged_GrowthFitsPURPAR.Rds" is called in from \Data\CleanData\CleanedMCData folder and generated GAM plots are saved in \Output\Figures folder as .png.

# Set variables for project
```{r project data}
FP1 <- ".."
Project <- "PICO"
FileID <- "GAM"
Expert <- "MiSa" #MiSa SySl
GamFit <- "PICO_Merged_GrowthFitsPURPAR.Rds"

#"..", takes up a level in the directory path
DataIn <- file.path("..","Data", "CleanData")
DataOut <- file.path("..","Data", "CleanData")
PlotsPath <- file.path("..","Output", "Figures")

is_all_numeric <- function(x) { 
  !any(is.na(suppressWarnings(as.numeric(na.omit(x))))) & is.character(x) 
}
#https://stackoverflow.com/questions/22772279/converting-multiple-columns-from-character-to-numeric-format-in-r

GamPara <- "Lmu" # Stabds for growth estimates determined by logistic model

```

```{r load libraries, message=FALSE}
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(minpack.lm)
library(nlstools)
library(nlsMicrobio)
library(plotly)
library(mgcv)
library(tidymv)
library(CCA)
library(vegan)
library(cowplot)
library(glue)
library(gtable)
library(car)
library(MASS)
library(faraway)
library(gridExtra)
library(ggh4x)
library(ggspectra) 
library(photobiologyWavebands) 
library(photobiology)
library(metR)
library(Rcpp)

```

# Read data nad select relevant columns
```{r read data and select relevant columns}

GrowthFits <- readRDS(file = file.path(DataIn, GamFit))

GrowthFits <- GrowthFits %>% 
 dplyr::select(c(Filename, PrimaryOperator, Tube, SampleID, Run, Photoperiod, Strain, WL, O2_Category, O2_uM, LightShape, Pur_ue, Par_ue, PURPhotonDose_day, PARPhotonDose_day, OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se))

ReplNo <- GrowthFits %>%
  distinct(Photoperiod, Strain, O2_uM, WL, Par_ue)

```

# make df longer for GAM
```{r set up df for GAM}
 Pivot_Longer_OD720_est <- GrowthFits %>% 
  dplyr::select(-c(OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se)) %>%
   pivot_longer(c(OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept), names_to = c("Wavelength", "term"), values_to = c("estimate"), names_sep = '\\_')

# OD720 pivot longer Gmax, Gmu, Glag , Lmu, Lmax and Lintercept standard error
Pivot_Longer_OD720_se <- GrowthFits %>%
  dplyr::select(-c(OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se)) %>%
   pivot_longer(c(OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se), names_to = c("Wavelength", "term"), values_to = c("se"), names_sep = '\\_')

# Join OD720 estimate and se DF 
Longer_OD720_Joined <- full_join(Pivot_Longer_OD720_est, Pivot_Longer_OD720_se)

remove(Pivot_Longer_OD720_est, Pivot_Longer_OD720_se)

# deltaOD pivot longer Gmax, Gmu, Glag, Lmu, Lmax and Lintercept estimates
Pivot_Longer_deltaOD_est <- GrowthFits %>%
  dplyr::select(-c(OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se)) %>%
   pivot_longer(c(deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept), names_to = c("Wavelength", "term"), values_to = c("estimate"), names_sep = '\\_')

# deltaOD pivot longer Gmax, Gmu, Glag , Lmu, Lmax and Lintercept standard error
Pivot_Longer_deltaOD_se <- GrowthFits %>%
  dplyr::select(-c(OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept)) %>%
   pivot_longer(c(deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se), names_to = c("Wavelength", "term"), values_to = c("se"), names_sep = '\\_')

# Join deltaOD estimate and se DF 
Longer_deltaOD_Joined <- full_join(Pivot_Longer_deltaOD_est, Pivot_Longer_deltaOD_se)

remove(Pivot_Longer_deltaOD_est, Pivot_Longer_deltaOD_se)

#Join OD720 and deltaOD fits data
ComGrowthFits <- rbind(Longer_OD720_Joined, Longer_deltaOD_Joined) %>%
  mutate_if(is.numeric, round, digits = 3) %>% 
  filter(Strain %in% c("MED4", "SS120", "MIT9313"),
         WL %in% c(450, 660, "WW"))

remove(Longer_OD720_Joined, Longer_deltaOD_Joined)

glimpse(ComGrowthFits)

```

```{r DF preparation Prochloroccus}
GamWL = "deltaOD"
GamVar = "450"

#DummyDF for MED4; MED4 is a high light strain, based on literature it can grow up to 800 uE; we never exposed it to such high light levels and will not impose an upper end, but only a lower, i.e. Par_ue = 0, Lmu = 0, there are no reliable points for low O2 in shorter photoperiods
Strain <- c("MED4")
Photoperiod <- c(4, 8, 12, 16)
Par_ue<- c(0)
O2_uM <- c(2.5, 25.0, 250.0)
WL <- c(450, 530, 660, "WW")
estimate <- c(0)
term <- GamPara
Wavelength <- c("deltaOD", "OD720")
Tube <- c(9)

DummyDF_MED4 <- expand_grid(
  Strain, Photoperiod, Par_ue, O2_uM, WL, estimate, Wavelength, term, Tube
  ) %>%
  mutate(Lmu_seFlag = 1) 
DummyDF_Expand_MED4 <- rbind(DummyDF_MED4, DummyDF_MED4, DummyDF_MED4)

#DummyDF for MIT9313; MIT9313 is a low light strain, based on literature it can only grow up to 300 uE WW; MIT9313 consistently died at various light colors and oxygen levels latest at ~PAR 400; it can safely be assumed it dies at par_ue = 0
Strain <- c("MIT9313")
Photoperiod <- c(4, 8, 12, 16)
Par_ue<- c(0)
O2_uM <- c(2.5, 25.0, 250.0)
WL <- c(450, 530, 660, "WW")
estimate <- c(0)
term <- GamPara
Wavelength <- c("deltaOD", "OD720")
Tube <- c(9)

DummyDF_MIT9313 <- expand_grid(
  Strain, Photoperiod, Par_ue, O2_uM, WL, estimate, Wavelength, term, Tube
  ) %>%
  mutate(Lmu_seFlag = 1) 
DummyDF_Expand_MIT9313 <- rbind(DummyDF_MIT9313, DummyDF_MIT9313, DummyDF_MIT9313)

#DummyDF for SS120; SS120 is a low light strain, based on literature it can only grow up to 300 uE WW; SS120 consistently died at various light colors and oxygen levels latest at ~PAR 400; it can safely be assumed it dies at par_ue = 0
Strain <- c("SS120")
Photoperiod <- c(4, 8, 12, 16)
Par_ue<- c(0, 400)
O2_uM <- c(2.5, 25.0, 250.0)
WL <- c(450, 530, 660, "WW")
estimate <- c(0)
term <- GamPara
Wavelength <- c("deltaOD", "OD720")
Tube <- c(9)

DummyDF_SS120 <- expand_grid(
  Strain, Photoperiod, Par_ue, O2_uM, WL, estimate, Wavelength, term, Tube
  ) %>%
  mutate(Lmu_seFlag = 1) 
DummyDF_Expand_SS120 <- rbind(DummyDF_SS120, DummyDF_SS120, DummyDF_SS120)

DummyDF_Expand <- rbind(DummyDF_Expand_SS120, DummyDF_Expand_MIT9313, DummyDF_Expand_MED4)

PicoGrowthFits <-    ComGrowthFits # full_join(ComGrowthFits, DummyDF_Expand)

PicoLmuAb <- PicoGrowthFits %>%
  filter(term %in% GamPara) %>%
  filter(Wavelength %in% GamWL) %>%
  filter(WL %in% GamVar) %>%
  mutate(Strain = as.factor(Strain))

PicoLogGamAb <-  gam(estimate ~ s(Par_ue,  by = Strain, k = 3) + s(Photoperiod,  by = Strain, k = 3) + ti(Photoperiod, Par_ue, by = Strain, k = 3), data = PicoLmuAb, method = "REML")
summary(PicoLogGamAb)

PicoLogPar <- gam(estimate ~ s(Par_ue,  by = Strain, k = 3), data = PicoLmuAb, method = "REML")

PicoLogPhotPer <- gam(estimate ~ s(Photoperiod,  by = Strain, k = 3), data = PicoLmuAb, method = "REML")

AIC(PicoLogPar, PicoLogPhotPer, PicoLogGamAb)

ModelResid <- resid(PicoLogGamAb)
gam.check(PicoLogGamAb)
concurvity(PicoLogGamAb)
plot(PicoLogGamAb, residuals = TRUE, pch = 1, all.terms = TRUE)

#AIC of Gompertz-fitted model comparably low as to only-par and only-light model. 
#Next step, fitting Strain-specific models. 
#MED4 model to Par_ue-response falsy fits, due to badly fitted µ-rates -> cultures died, but model tried to fit anywy. Maybe filter everything below a certain R^2 in the fit?

```

```{r GAM separate niches hypervolume}
GamWL = c("deltaOD", "OD720") #deltaOD OD720
Proxy= "[~Chl]" #~Chl ~Cells 
GamParaMod = "Lmu"
GamVar = c("450")# 450 660 WW
ErrorTolGrowth = 30 # defined for the growth estimates
ErrorTol = 30 # defined for the GAM fit
# OxyLev = 25

#https://stackoverflow.com/questions/49570452/is-it-possible-to-specify-lower-bound-in-response-variable-during-smooth-with-ga 
possibGAM = possibly(.f = mgcv::gam, otherwise = NULL)
possibPRED = possibly(.f = mgcv::predict.gam, otherwise = NULL)

PAR_Photoperiod_Model_predi <- expand_grid(
  Par_ue = seq(from=min(10), 
              to=max(200), 
              length.out = 100),
  Photoperiod = seq(from=min(2), 
              to=max(18), 
              length.out = 100)
)

PicoGAM <- PicoGrowthFits %>%
  ungroup() %>%
  dplyr::mutate(Lmu_seFlag = case_when(se/estimate*100 < ErrorTolGrowth ~ 1, #filters faulty data where Standarderror larger +/- Errortolerance
                         FALSE ~ 0)) %>%
  dplyr::filter(
                estimate == 0 |
                estimate != 0 & Lmu_seFlag == 1,
                term %in% GamParaMod, 
                Wavelength %in% GamWL
                ) %>%
  mutate(estimate = estimate*24, #to convert growth from per hour to per day
         se = se*24) %>%
  group_by(Strain, Wavelength, WL, O2_uM) %>%
  nest() %>%
  dplyr::arrange(Strain, Wavelength, WL, O2_uM) %>%
  mutate(GamModel = map(data, ~possibGAM(estimate ~ s(Par_ue, k = 3) + s(Photoperiod, k = 3) + ti(Photoperiod, Par_ue, k = 3),  data = .x,
                                    family = "gaussian"(link = "log"), 
                                    method = "REML")),
         predicted = map(GamModel, ~possibPRED(.x, newdata = PAR_Photoperiod_Model_predi, type = 'response', se.fit=TRUE)),
         augmented = map(GamModel, ~augment(.x))
         )

PicoGAM_Pred <- PicoGAM %>%
  dplyr::select(Strain, Wavelength, WL, O2_uM, predicted) %>%
  dplyr::filter(predicted != "NULL") %>%
  rowwise() %>%
  mutate(db = list(cbind(predicted, PAR_Photoperiod_Model_predi))) %>%
  dplyr::select(-predicted) %>%
  unnest(col = db) %>%
  group_by(Strain, Wavelength, WL, O2_uM) %>%
  dplyr::filter(fit < 1.2) %>% #with two exceptions, growth rates were never higher than 1.2; GAM model creates some unrealistic high growth rates due to low data availability
  mutate(
    IsFitGood = case_when(se.fit/fit*100 < ErrorTol ~ 1, #flags faulty data where Standarderror larger +/- Errortolerance
                         se.fit/fit*100 > ErrorTol ~ 0
                    )
    #se_erro_per = se.fit/fit*100
  # ,fit = case_when(fit >= quantile(fit, 0.75, na.rm = TRUE) ~ fit*1, #leaves only top-10%, that means fastest growth rates in the dataframe
  #                 FALSE ~ fit)
  ) %>% 
  dplyr::filter(IsFitGood == 1)

```

# Plot red light GAM
``` {r GAM Plot Red WL}
GamStrain = "MIT9313" # MIT9313 MED4 SS120
GamColor = "Red" 
WL_nm = 660 
PlotWL <- "deltaOD"

maxMu <- PicoGAM_Pred %>%
  ungroup() %>%
  filter(Wavelength %in% PlotWL) %>%
  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
maxMu <- maxMu$fit

minMu <- PicoGAM_Pred %>%
  ungroup() %>%
  filter(Wavelength %in% PlotWL) %>%
  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
  #        fit == min(fit, na.rm = TRUE)) %>%
  # distinct(fit)
minMu <- minMu$fit

PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
  filter(Wavelength %in% PlotWL,
         Strain %in% GamStrain,
         WL %in% WL_nm) %>%
  mutate(
         # PhotoperiodLabel = "Photoperiod",

         OxygenLabel = "Oxygen Concentration (uM)",
         O2_level = case_when(O2_uM == 2.5 ~ "low",
                              O2_uM == 25 ~ "intermediate",
                              O2_uM == 250 ~ "high"),
         Color_name = case_when(WL == "450" ~ 'Blue',
                                WL == "530" ~ 'Green',
                                WL == "660" ~ 'Red',
                                WL == "WW" ~ 'White')) %>%
  unite(WL_O2, Color_name, O2_level, sep = "_", remove = FALSE)

WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")

ColourDF <- data.frame(
  ColorName = c('Blue', 'Green', 'Red', 'White'),
  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
) %>%
  filter(ColorName %in% GamColor) %>%
  dplyr::select(WL_O2_Colors)

ContourBreaks <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         Wavelength %in% PlotWL
  ) %>%
  group_by(O2_uM) %>%
  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
         median50 = quantile(fit, 0.5, na.rm = TRUE),
         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
  ungroup() %>%
  dplyr::select(O2_uM, upper10, median50, lower10) %>%
  distinct() %>%
  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
  mutate(quantileValue = round(quantileValue, digits = 2))

##############
###plot
#https://stackoverflow.com/questions/28775036/ggplot-line-graph-with-na-values
#https://stackoverflow.com/questions/6906661/ggplot2-make-missing-value-in-geom-tile-not-blank
#https://stackoverflow.com/questions/24822621/multiple-legends-in-a-plot-with-geom-tile
#https://stackoverflow.com/questions/43395219/plotting-multiple-layers-with-geom-raster-or-geom-tile-or-geom-rect
#https://stackoverflow.com/questions/59949635/ggplot-align-grid-lines-with-end-of-geom-tile
#https://stackoverflow.com/questions/22945651/remove-space-between-plotted-data-and-the-axes
#https://stackoverflow.com/questions/5293715/how-to-use-greek-symbols-in-ggplot2

HyperChlPlotLow <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         #DM == "Chl",
         Wavelength %in% PlotWL,
         O2_uM == "2.5"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "2.5") 
ContourLines <- ContourLines$quantileValue

(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "C", size = 5) +
    xlab(NULL)+
      # xlab("Photoperiod (h)") +
    # ylab("                                  ") +
      ylab(NULL)+
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    labs(title = bquote("  C.   " ~ .(GamStrain) ~ '    2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
    theme_classic() +
    theme(axis.text=element_text(size=20),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))# change to 25 and 30 for thesis
          # axis.title.y = element_blank()))

HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         #DM == "Chl",
         Wavelength %in% PlotWL,
         O2_uM == "25"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "25") 
ContourLines <- ContourLines$quantileValue

(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "B", size = 5) +
    xlab(NULL)+
     # xlab("Photoperiod (h)") +
      ylab(NULL)+
    # ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")") +
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    labs(title = bquote("  B.   " ~ .(GamStrain) ~ '    25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
   theme_classic() +
  theme(axis.text=element_text(size=20),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=23)))# change to 25 and 30 for thesis
          # axis.title.y = element_blank()))

HyperChlPlotHigh <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         #DM == "Chl",
         Wavelength %in% PlotWL,
         O2_uM == "250"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "250") 
ContourLines <- ContourLines$quantileValue

(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "A", size = 5) +
    xlab(NULL)+
     # xlab("Photoperiod (h)") +
    # ylab("                                  ") +
      ylab(NULL)+
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    labs(title = bquote("  A.   " ~ .(GamStrain) ~ '    250 µM' ~ "[" ~ O[2]~ "]")) +  #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
    theme_classic() +
   theme(axis.text=element_text(size=20),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))# change to 25 and 30 for thesis
          # axis.title.y = element_blank()))

g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  legend
}

(g_dummy1 <- ggplot(subset(HyperChlPlotLow, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
 limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
legend1 <- g_legend(g_dummy1)
(g_dummy2 <- ggplot(subset(HyperChlPlotInt, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
legend2 <- g_legend(g_dummy2)
(g_dummy3 <- ggplot(subset(HyperChlPlotHigh, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
legend3 <- g_legend(g_dummy3)

LayoutNiche <- rbind(
                     c(3, 3, 3, 3, 6),
                     c(3, 3, 3, 3, 6),
                     c(2, 2, 2, 2, 5),
                     c(2, 2, 2, 2, 5),
                     c(1, 1, 1, 1, 4), 
                     c(1, 1, 1, 1, 4)
                     )

#LayoutNiche <- rbind(c(1, 1, 1, 2, 2, 2, 3, 3, 3, 4))

p3 <- grid.arrange(ContourLowO2 + theme(legend.position = 'none'), ContourIntO2 + theme(legend.position = 'none'), ContourHighO2 + theme(legend.position = 'none'), legend1, legend2, legend3, layout_matrix = LayoutNiche)

                   # ,  left = textGrob("PAR (µmol photons"~ m^-2~ ~s^-1~ ")", rot = 90, vjust = 0.5, hjust = 0.45, gp=gpar(fontsize=30)), bottom = textGrob("Photoperiod (h)", gp=gpar(fontsize=20), vjust = 0.2, hjust = 0.6))

#  for thesis
  # ggsave(file = file.path(paste(FP1, "Plots", sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3,  height = 10, width = 6)

# for presentation
  ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3,  height = 7.6, width = 6)

```

# Plot blue light GAM
``` {r GAM Plot Blue WL}
GamStrain = "MIT9313" # MIT9313 MED4 SS120
GamColor = "Blue"
WL_nm = 450 
PlotWL <- "deltaOD"

maxMu <- PicoGAM_Pred %>%
  ungroup() %>%
  filter(Wavelength %in% PlotWL) %>%
  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
maxMu <- maxMu$fit

minMu <- PicoGAM_Pred %>%
  ungroup() %>%
  filter(Wavelength %in% PlotWL) %>%
  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
  #        fit == min(fit, na.rm = TRUE)) %>%
  # distinct(fit)
minMu <- minMu$fit

PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
  filter(Wavelength %in% PlotWL,
         Strain %in% GamStrain,
         WL %in% WL_nm) %>%
  mutate(

         # PhotoperiodLabel = "Photoperiod",

         OxygenLabel = "Oxygen Concentration (uM)",
         O2_level = case_when(O2_uM == 2.5 ~ "low",
                              O2_uM == 25 ~ "intermediate",
                              O2_uM == 250 ~ "high"),
         Color_name = case_when(WL == "450" ~ 'Blue',
                                WL == "530" ~ 'Green',
                                WL == "660" ~ 'Red',
                                WL == "WW" ~ 'White')) %>%
  unite(WL_O2, Color_name, O2_level, sep = "_", remove = FALSE)

WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")

ColourDF <- data.frame(
  ColorName = c('Blue', 'Green', 'Red', 'White'),
  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
) %>%
  filter(ColorName %in% GamColor) %>%
  dplyr::select(WL_O2_Colors)

ContourBreaks <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         Wavelength %in% PlotWL
  ) %>%
  group_by(O2_uM) %>%
  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
         median50 = quantile(fit, 0.5, na.rm = TRUE),
         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
  ungroup() %>%
  dplyr::select(O2_uM, upper10, median50, lower10) %>%
  distinct() %>%
  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
  mutate(quantileValue = round(quantileValue, digits = 2))

##############
###plot
#https://stackoverflow.com/questions/28775036/ggplot-line-graph-with-na-values
#https://stackoverflow.com/questions/6906661/ggplot2-make-missing-value-in-geom-tile-not-blank
#https://stackoverflow.com/questions/24822621/multiple-legends-in-a-plot-with-geom-tile
#https://stackoverflow.com/questions/43395219/plotting-multiple-layers-with-geom-raster-or-geom-tile-or-geom-rect
#https://stackoverflow.com/questions/59949635/ggplot-align-grid-lines-with-end-of-geom-tile
#https://stackoverflow.com/questions/22945651/remove-space-between-plotted-data-and-the-axes
#https://stackoverflow.com/questions/5293715/how-to-use-greek-symbols-in-ggplot2

HyperChlPlotLow <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         #DM == "Chl",
         Wavelength %in% PlotWL,
         O2_uM == "2.5"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "2.5") 
ContourLines <- ContourLines$quantileValue

(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "C", size = 5) +
    xlab(NULL)+
      # xlab("Photoperiod (h)") +
    # ylab("                                  ") +
      ylab(NULL)+
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    labs(title = bquote("  C.   " ~ .(GamStrain) ~ '    2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
    theme_classic() +
    theme(axis.text=element_text(size=20),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))# change to 25 and 30 for thesis
          # axis.title.y = element_blank()))

HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         #DM == "Chl",
         Wavelength %in% PlotWL,
         O2_uM == "25"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "25") 
ContourLines <- ContourLines$quantileValue

(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "B", size = 5) +
    xlab(NULL)+
     # xlab("Photoperiod (h)") +
      ylab(NULL)+
    # ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")") +
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    labs(title = bquote("  B.   " ~ .(GamStrain) ~ '    25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
   theme_classic() +
  theme(axis.text=element_text(size=20),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=23)))# change to 25 and 30 for thesis
          # axis.title.y = element_blank()))

HyperChlPlotHigh <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         #DM == "Chl",
         Wavelength %in% PlotWL,
         O2_uM == "250"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "250") 
ContourLines <- ContourLines$quantileValue

(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "A", size = 5) +
    xlab(NULL)+
     # xlab("Photoperiod (h)") +
    # ylab("                                  ") +
      ylab(NULL)+
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    labs(title = bquote("  A.   " ~ .(GamStrain) ~ '    250 µM' ~ "[" ~ O[2]~ "]")) +  #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
    theme_classic() +
   theme(axis.text=element_text(size=20),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))# change to 25 and 30 for thesis
          # axis.title.y = element_blank()))

g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  legend
}

# remove Photoperiod from aes when plotting 450 (Blue light)
(g_dummy1 <- ggplot(subset(HyperChlPlotLow, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
 + scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"),
 limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
legend1 <- g_legend(g_dummy1)
(g_dummy2 <- ggplot(subset(HyperChlPlotInt, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
 + scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"),
  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
legend2 <- g_legend(g_dummy2)
(g_dummy3 <- ggplot(subset(HyperChlPlotHigh, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"),
  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
legend3 <- g_legend(g_dummy3)

LayoutNiche <- rbind(
                     c(3, 3, 3, 3, 6),
                     c(3, 3, 3, 3, 6),
                     c(2, 2, 2, 2, 5),
                     c(2, 2, 2, 2, 5),
                     c(1, 1, 1, 1, 4), 
                     c(1, 1, 1, 1, 4)
                     )

#LayoutNiche <- rbind(c(1, 1, 1, 2, 2, 2, 3, 3, 3, 4))

p3 <- grid.arrange(ContourLowO2 + theme(legend.position = 'none'), ContourIntO2 + theme(legend.position = 'none'), ContourHighO2 + theme(legend.position = 'none'), legend1, legend2, legend3, layout_matrix = LayoutNiche)

# , left = textGrob("PAR (µmol photons"~ m^-2~ ~s^-1~ ")", rot = 90, vjust = 0.5, hjust = 0.45, gp=gpar(fontsize=30)), bottom = textGrob("Photoperiod (h)", gp=gpar(fontsize=20), vjust = 0.2, hjust = 0.6))

#  for thesis
  # ggsave(file = file.path(paste(FP1, "Plots", sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3,  height = 10, width = 6)

# for presentation
  ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3,  height = 7.6, width = 6)

```

``` {r GAM PUR comparison}

GamWL = c("deltaOD") #deltaOD OD720
Proxy= "[~Chl]" #~Chl ~Cells 
GamParaMod = "Lmu"
#GamVar = c("450")# 450 660 WW
GamStrain = "MED4" # MIT9313 MED4 SS120
# ErrorTol = 20
OxyLev = 250

################ check smooth terms #https://fromthebottomoftheheap.net/2017/12/14/difference-splines-ii/
#https://stackoverflow.com/questions/70922283/gam-smooths-interaction-differences-calculate-p-value-using-mgcv-and-gratia-0
PurGAM <- ComGrowthFits %>%
  mutate(ordPP = ordered(Photoperiod, levels = c('4', '8', '12', '16')),
         Lmu_seFlag = case_when(se/estimate*100 < ErrorTolGrowth ~ 1, #filters faulty data where Standarderror larger +/- Errortolerance
                         FALSE ~ 0)) %>%
  ungroup() %>%
  dplyr::filter(
                Photoperiod != 4, 
                Lmu_seFlag == 1,
                term %in% GamParaMod,
                Wavelength %in% GamWL,
                Strain %in% GamStrain,
                O2_uM %in% OxyLev) %>%
  mutate(estimate = estimate*24,
         se = se*24)

m_PUR_gam <- gamm(estimate ~ s(PURPhotonDose_day, k = -1) + s(PURPhotonDose_day, by = ordPP), random=list(WL=~1), data = PurGAM, method = "REML")
m_PUR_gam <- m_PUR_gam$gam

plot(m_PUR_gam, shade = TRUE, pages = 1, scale = 0, seWithMean = TRUE)
summary(m_PUR_gam)

# zoom_Chl_TreatCheck <- zoom_log %>%
#   filter(Group != "ES") %>%
#   mutate(ordGroup = ordered(Group, levels = c('ES', 'Fish', 'noFish')))
# 
# m_Chl_Treatgam <- gamm(Chla_ugL ~ Group +  s(DayFrFrst) +s(DayFrFrst, by = ordGroup), random=list(SampleYear=~1), data = zoom_Chl_TreatCheck, method = "REML")
# m_Chl_Treatgam <- m_Chl_Treatgam$gam
# 
# plot(m_Chl_Treatgam, shade = TRUE, pages = 1, scale = 0, seWithMean = TRUE)
# summary(m_Chl_Treatgam)

# PurGAM <- ComGrowthFits %>% 
#   ungroup() %>%
#   dplyr::filter(Lmu_seFlag == 1, 
#                 term %in% GamParaMod, 
#                 Wavelength %in% GamWL,
#                 strain %in% GamStrain) %>%
#   mutate(estimate = estimate*24,
#          se = se*24) %>%
#   group_by(Strain, Wavelength, O2_uM, Photoperiod) %>%
#   nest() %>%
#   dplyr::arrange(Strain, Wavelength, O2_uM) %>%
#   mutate(GamModel = map(data, ~possibGAM(estimate ~ s(PUR_day, k = 3) + s(Photoperiod, k = 3) + ti(Photoperiod, Par_ue, k = 3),  data = .x,
#                                     family = "gaussian"(link = "log"), 
#                                     method = "REML")),
#          predicted = map(GamModel, ~possibPRED(.x, newdata = PAR_Photoperiod_Model_predi, type = 'response', se.fit=TRUE)),
#          augmented = map(GamModel, ~augment(.x))
#          )
# 
# PicoGAM_Pred <- PicoGAM %>%
#   dplyr::select(Strain, Wavelength, WL, O2_uM, predicted) %>%
#   dplyr::filter(predicted != "NULL") %>%
#   rowwise() %>%
#   mutate(db = list(cbind(predicted, PAR_Photoperiod_Model_predi))) %>%
#   dplyr::select(-predicted) %>%
#   unnest(col = db) %>%
#   group_by(Strain, Wavelength, WL, O2_uM) %>%
#   dplyr::filter(fit < 1) %>% #with two expections, growth rates were never higher than 0.06; GAM model creates some unrealistic high growth rates due to low data availability
#   mutate(
#     fit = case_when(se.fit/fit*100 < ErrorTol ~ fit*1, #filters faulty data where Standarderror larger +/- Errortolerance
#                          FALSE ~ fit)
#   # ,fit = case_when(fit >= quantile(fit, 0.75, na.rm = TRUE) ~ fit*1, #leaves only top-10%, that means fastest growth rates in the dataframe
#   #                 FALSE ~ fit)
#   )

```

### 2024-01-18 Code/Import_JazEmData.Rmd
Replaced .bib with newly created Manuscript_O2.bib

@@
     fig_caption: yes
-bibliography: [Prochlorococcus_O2_NPQ.bib, RPackages.bib]
+bibliography: [Manuscript_O2.bib, RPackages.bib]
 csl: plos-one.csl

### 2024-01-18 Code/Import_MCData.Rmd
Replaced .bib with newly created Manuscript_O2.bib

--- 2023-12-14 Code/MultiDataImportPico.Rmd
@@
 ---
-title: "MultiDataImportPico"
+title: "Import_MCData"
 author:
@@
 date: "`r format(Sys.Date())`"
-bibliography: Prochlorococcus_O2_NPQ.bib
+bibliography: Manuscript_O2.bib
 csl: plos-one.csl

### 2024-01-18 Code/Import_MetaData.Rmd
Removed unnecessary libraries
Replaced .bib with newly created Manuscript_O2.bib

@@
 ---
-title: "MetaDataImport"
+title: "Import_MetaData"
 author:
@@
     fig_caption: yes
-bibliography: Prochlorococcus_O2_NPQ.bib
+bibliography: Manuscript_O2.bib
 csl: plos-one.csl
@@
 ```{r load libraries}
-# libraries; Note check actual dependencies
+
 library(tidyverse)
@@
 library(data.table)
-library(googledrive)
 library(googlesheets4)

### 2024-01-18 Code/Import_OlisData.Rmd
Removed unneccesary libraries
Replaced .bib with newly created Manuscript_O2.bib

@@
     fig_caption: yes
-bibliography: [Prochlorococcus_O2_NPQ.bib, RPackages.bib]
+bibliography: [Manuscript_O2, RPackages.bib]
 csl: plos-one.csl
@@
 ```{r load libraries, warning = FALSE, echo=FALSE}
-library(tidyverse)
+
 library(lubridate)
@@
 library(knitr)
-library(OneR)
-library(zoo)
-library(readxl)
+library(tidyverse)
+
 ```

### 2024-01-18 Code/ManuscriptFigures.Rmd
Replaced .bib with newly created Manuscript_O2.bib

@@
       - '--lua-filter=author-info-blocks.lua'
-bibliography: [Prochlorococcus_O2_NPQ.bib, RPackages.bib]
+bibliography: [Manuscript_O2.bib, RPackages.bib]
 csl: plos-one.csl

### 2024-01-18 Code/ManuscriptGAM.Rmd
Replaced .bib with newly created Manuscript_O2.bib

@@
 ---
-title: "PICOgam"
+title: "ManuscriptGAM"
 author:
@@
 - Mireille Savoie
-output: html_notebook
+output:
+bookdown::html_document2:
+    code_folding: show
+    keep_md: yes
+    toc: TRUE
+    toc_float: TRUE
+    toc_depth: 6
+    fig_caption: yes
+bibliography: [Manuscript_O2, RPackages.bib]
+csl: plos-one.csl
+editor_options: 
+  markdown: 
+    wrap: 72
 ---

### 2024-01-18 Code/Merge_GrowthPURData.Rmd
Replaced .bib with newly created Manuscript_O2.bib

@@
 ---
-title: "Merge_PICO_Growth_PUR"
+title: "Merge_GrowthPURData"
 author: 

### 2024-01-18 Code/Process_MCData.Rmd
Replaced .bib with newly created Manuscript_O2.bib

--- 2023-12-15 Code/MultiDataProcessPico.Rmd
@@
 ---
-title: "MultiDataProcessPico"
+title: "Process_MCData"
 author:

### 2024-01-18 Code/Process_OlisJazEmData.Rmd
Replaced .bib with newly created Manuscript_O2.bib

@@
     fig_caption: yes
-bibliography: BalticPhotoperiod.bib
+bibliography: Manuscript_O2.bib
 csl: plos-one.csl

### 2024-01-18 Code/Import_MetaData.Rmd
Added MaBe to extract Max's runs from MC catalog

@@
 DataOut <- file.path("..","Data")
-ProjectRows <- c("MiSa|JuNa|SaAr")
+ProjectRows <- c("MiSa|JuNa|SaAr|MaBe")
 ProjectCols <- c("PrimaryOperator", "SampleID", "Run", "Strain", "ExpCul", "ExpDate", "ExpStartTime", "Par_ue", "Photoperiod", "Temp_c", "MC", "Tube","O2", "O2_Category", "WL","LightShape", "Optode","OptodeCh","OptodeMeasure", "ExpEndDate")

### 2024-01-18 Code/ManuscriptPURFits.Rmd
Edit to run in Github

---
title: "ManuscriptPURFits"
author: 
- Mireille Savoie
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  bookdown::word_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
bibliography: [Manuscript_O2.bib, RPackages.bib]
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

To Do

## Set figure caption font size
```{css, echo=FALSE}
p.caption {
  font-size: 25px;
}
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = F)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r load libraries, include=FALSE}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
#library(stringr)
library(broom)
library(knitr)
library(zoo)
#library(AICcmodavg)
# library(RColorBrewer)
# library(grid)
# library(bookdown)
# library(glue)
# library(egg)
# library(ggspectra)
# library(photobiologyWavebands)
# library(photobiology)
#library(ggpubr)
#library(ggh4x)
#library(cowplot)
#library(jmv)
# library(pgirmess) # for the post hoc kruskalalmc test
#library(rcompanion) # for Scheirer-Ray-Hare non-parametric 2 way test, derived from Kruskal-Wallis
# library(FSA) # for Dunn test
#library(dunn.test)
# library(rstatix)
library(minpack.lm)

```

```{r set project variables}

#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..","Data", "CleanData")
PlotsOut <- file.path("..","Output", "Figures")

```

Read .Rds
Multiple 'list' columns removed; this can sometimes happen if early steps generate 2 values for a single data frame column element; this converts the column to 'list' format to accomodate more than one value in a single data from column/row position.

```{r read ProcessFile}

PURPARFits <- readRDS(file = file.path(DataIn,"PICO_Merged_GrowthFitsPURPAR.Rds"))

glimpse(PURPARFits)

PURPARFits <- PURPARFits|>
  select(-c("tubedata")) |>
  select(-contains("OD720")) |>
  select(-c("ExpCul", "Optode", "OptodeCh", "ExpEndDate", "ExpEndHour")) |>
  select(-contains("trunc_")) |>
  select(-contains("predict")) |>
  select(-c("deltaOD_Lmax", "deltaOD_Lmu_raw", "deltaOD_Lintercept",  "deltaOD_Lmax_se",  "deltaOD_Lintercept_se")) |>
  select(-c("GrowthAmpdeltaOD_14days", "PurData")) |>
  select(-c("ReplicateMean_deltaOD_Lmu_corr", "ReplicateSD_deltaOD_Lmu_corr", "ReplicateSE_deltaOD_Lmu_corr" )) |>
 filter(Par_ue %in% c(30,90,180)) |>
  filter(!is.na(PURPhotonDose_day)) # PURPhotonDose_day NA mess up fits Strain = MED4 x 250 =  O2_uM

 # y = ReplicateMean_deltaOD_Lmu_corr_day

PURPARFits <- PURPARFits |>
  mutate(deltaOD_Lmu_corr_day = deltaOD_Lmu_corr * 24)

glimpse(PURPARFits)

```

Make O2_uM and WL as factor levels from highest to lowest
```{r O2 levels}

PURPARFits <- PURPARFits %>%
  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         WL= factor(WL, levels = c("WW", 660, 530, 450)),
        Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" )))

 # Par_ue = factor(Par_ue, levels =  c(180, 120, 100,90,60, 30, 15))
```

```{r set colours and shapes}

# MyWavelengths = c(450, 530, 660, "WW")
# MCMIXColours = c(w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "black")
library(photobiology)

MyWavelengths = c("WW", 660, 530, 450)
# MCMIXColours = c("black", w_length2rgb(660), w_length2rgb(530),  w_length2rgb(450))
MCMIXColours = c("black", "orange", w_length2rgb(530),  w_length2rgb(450))

names(MCMIXColours) <- MyWavelengths
MCMIXColours

MyPhotoperiods = as.factor(c(4, 8, 12, 16))
PhotoperiodShapes = c(6, 18, 16, 17)

names(PhotoperiodShapes) <- MyPhotoperiods
PhotoperiodShapes

```

```{r create dummy no growths for dark conditions}

#DummyDF for SS120; SS120 is a low light strain, based on literature it can only grow up to 300 uE WW; SS120 consistently died at various light colors and oxygen levels latest at ~PUR 400; it can safely be assumed it dies at par_ue = 0
Dummy_Strain <- c("SS120")
Dummy_Photoperiod <- c(4, 8, 12, 16)
Dummy_Par_ue<- c(0)
Dummy_O2_uM <- c(2.5, 25.0, 250.0)
Dummy_WL <- c(450, 530, 660, "WW")
Dummy_deltaOD_Lmu_corr <- c(0)
Dummy_Pur_ue<- c(0)
Dummy_deltaOD_Lmu_corr_day <- c(0)
Dummy_PUR_day <- c(0)

DummyDF_SS120 <- expand_grid(
  Dummy_Strain, Dummy_Photoperiod, Dummy_Par_ue, Dummy_O2_uM, Dummy_WL, Dummy_deltaOD_Lmu_corr, Dummy_Pur_ue, Dummy_deltaOD_Lmu_corr_day,Dummy_PUR_day
  ) %>%
  mutate(ID = "DummySS120")

DummyDF_Expand_SS120 <- rbind(DummyDF_SS120, DummyDF_SS120, DummyDF_SS120) %>% 
        rename(Strain = "Dummy_Strain",
        Photoperiod = "Dummy_Photoperiod",
        Par_ue = "Dummy_Par_ue",
        O2_uM = "Dummy_O2_uM", 
        WL = "Dummy_WL", 
        deltaOD_Lmu_corr = "Dummy_deltaOD_Lmu_corr",
        Pur_ue = "Dummy_Pur_ue",
        deltaOD_Lmu_corr_day = "Dummy_deltaOD_Lmu_corr_day",
        PURPhotonDose_day = "Dummy_PUR_day")

Dummy_Strain <- c("MIT9313")

DummyDF_MIT9313 <- expand_grid(
  Dummy_Strain, Dummy_Photoperiod, Dummy_Par_ue, Dummy_O2_uM, Dummy_WL, Dummy_deltaOD_Lmu_corr, Dummy_Pur_ue, Dummy_deltaOD_Lmu_corr_day,Dummy_PUR_day
  ) %>%
  mutate(ID = "DummyMIT9313")

DummyDF_Expand_MIT9313 <- rbind(DummyDF_MIT9313, DummyDF_MIT9313, DummyDF_MIT9313) %>% 
  rename(Strain = "Dummy_Strain",
        Photoperiod = "Dummy_Photoperiod",
        Par_ue = "Dummy_Par_ue",
        O2_uM = "Dummy_O2_uM", 
        WL = "Dummy_WL", 
        deltaOD_Lmu_corr = "Dummy_deltaOD_Lmu_corr",
        Pur_ue = "Dummy_Pur_ue",
        deltaOD_Lmu_corr_day = "Dummy_deltaOD_Lmu_corr_day",
        PURPhotonDose_day = "Dummy_PUR_day")

Dummy_Strain <- c("MED4")

DummyDF_MED4 <- expand_grid(
  Dummy_Strain, Dummy_Photoperiod, Dummy_Par_ue, Dummy_O2_uM, Dummy_WL, Dummy_deltaOD_Lmu_corr, Dummy_Pur_ue, Dummy_deltaOD_Lmu_corr_day,Dummy_PUR_day
  ) %>%
  mutate(ID = "DummyMED4")

DummyDF_Expand_MED4 <- rbind(DummyDF_MED4, DummyDF_MED4, DummyDF_MED4) %>% 
  rename(Strain = "Dummy_Strain",
        Photoperiod = "Dummy_Photoperiod",
        Par_ue = "Dummy_Par_ue",
        O2_uM = "Dummy_O2_uM", 
        WL = "Dummy_WL", 
        deltaOD_Lmu_corr = "Dummy_deltaOD_Lmu_corr",
        Pur_ue = "Dummy_Pur_ue",
        deltaOD_Lmu_corr_day = "Dummy_deltaOD_Lmu_corr_day",
        PURPhotonDose_day = "Dummy_PUR_day")

DummyDF_Expand <- rbind(DummyDF_Expand_SS120, DummyDF_Expand_MIT9313, DummyDF_Expand_MED4)

remove(DummyDF_MED4)
remove(DummyDF_MIT9313)
remove(DummyDF_SS120)
remove(DummyDF_Expand_MED4)
remove(DummyDF_Expand_MIT9313)
remove(DummyDF_Expand_SS120)

```

```{r add dummy dark growth to DF}

library(plyr)
PURPARFits_dummy<- rbind.fill(PURPARFits, DummyDF_Expand) # Apply the rbind.fill plyr function

detach("package:plyr")

# PURPARFits_dummy <- PURPARFits_dummy %>% 
#   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
#          WL= factor(WL, levels = c("WW", 660, 530, 450)),
#         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" )))

```

```{r testplot}
 PURPARFits %>% 
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
    scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660","530", "450" )) +
  facet_grid(rows = vars(Par_ue), cols = vars(Strain)) +
  theme_bw()
```

```{r test MED4 issues}
# PURPARFits |>
#   filter(Strain == "MED4",
#          O2_uM == 250) |>
#   select(c(ReplicateMean_deltaOD_Lmu_corr_day,  OrgPur_day))
```

```{r set colours}

# MyWavelengths = c(450, 530, 660, "WW")
# MCMIXColours = c(w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "black")
# 
# MyWavelengths = c("WW", 660, 530, 450)
# MCMIXColours = c("black", w_length2rgb(660), w_length2rgb(530),  w_length2rgb(450))
# 
# names(MCMIXColours) <- MyWavelengths
# MCMIXColours
# 
# 
# 
# 
# ColoursStrain = c(MIT9313 = "#E69F00", SS120 = "#F0E442", MED4 = "#CC79A7" )
# 
# MyOxygen = c(2.5, 25, 250 )
# # ColourOxygen = c("#99CCFF", "dodgerblue", "blue1")
# ColourOxygen = c("#FFCC00", "#FF9900", "#663300")
# names(ColourOxygen) <- MyOxygen
# ColourOxygen
# 
# MyOxygen = c(2.5, 25, 250 )
# LineTypeOxygen = c("dotted", "longdash", "solid")
# names(LineTypeOxygen) <- MyOxygen
# LineTypeOxygen
# 
# MyPhotoperiods = as.factor(c(4, 8, 12, 16))
# ColoursPhotoperiod = c("gray88", "lightcyan3", "gray47", "gray8")
# names(ColoursPhotoperiod) <- MyPhotoperiods
# ColoursPhotoperiod

```

```{r set shapes}

# MyPhotoperiods = as.factor(c(4, 8, 12, 16))
# PhotoperiodShapes = c(6, 18, 1, 17)
# 
# 
# names(PhotoperiodShapes) <- MyPhotoperiods
# PhotoperiodShapes
# 
# O2Shapes <- c(13, 1, 19)

```

Set Strip colors for WL x_strip is for WL facetted by columns and y_strip is for WL faceted by rows
```{r}
# x_strip <- strip_themed(background_x = elem_list_rect(fill = MCMIXColours, alpha = 0.8),
#                       background_y = elem_list_rect(fill = "grey27")) 
# 
# x_stripWW <- strip_themed(background_x = elem_list_rect(fill = "black"),
#                       background_y = elem_list_rect(fill = "#grey27"))
# 
# x_strip660 <- strip_themed(background_x = elem_list_rect(fill = "#730000"),
#                       background_y = elem_list_rect(fill = "#grey27"))
# 
# x_strip530 <- strip_themed(background_x = elem_list_rect(fill = "#00FF00"),
#                       background_y = elem_list_rect(fill = "#grey27"))
# 
# x_strip450 <- strip_themed(background_x = elem_list_rect(fill = "#0600FF"),
#                       background_y = elem_list_rect(fill = "#grey27"))
# 
# y_strip <- strip_themed(background_y = elem_list_rect(fill = MCMIXColours),
#                       background_x = elem_list_rect(fill = "#grey27")) 
# 
# y_stripWW <- strip_themed(background_y = elem_list_rect(fill = "black"),
#                       background_x = elem_list_rect(fill = "#grey27"))
# 
# y_strip660 <- strip_themed(background_y = elem_list_rect(fill = "#730000"),
#                       background_x = elem_list_rect(fill = "#grey27"))
# 
# y_strip530 <- strip_themed(background_y = elem_list_rect(fill = "#00FF00"),
#                       background_x = elem_list_rect(fill = "#grey27"))
# 
# y_strip450 <- strip_themed(background_y = elem_list_rect(fill = "#0600FF"),
#                       background_x = elem_list_rect(fill = "#grey27"))

```

Citations: Ma X, Liu Q, Zhang Z, Zhang Z, Zhou Z, Jiang Y, et al. (2021) Effects of photosynthetic models on the calculation results of photosynthetic response parameters in young Larix principis- rupprechtii Mayr. plantation. PLoS ONE 16(12): e0261683. https://doi.org/10.1371/journal.pone.0261683

https://www.frontiersin.org/articles/10.3389/fpls.2020.581851/full

I: incident light, umol photons m-2 s-1
a: alpha, initial slope of light response curve under limiting light; the 'affinity' of the culture for light.
Pmax: maximum rate of photosynthesis; umol O2 chl-1 s-1; the 'capacity' of the culture for photosynthesis.

R: dark respiration, umol O2 chl-1 s-1

b: beta 'photoinhibition' term for decline in oxygen evolution under increasing incident light.  This decrease can result from multiple mechanisms.

g: gamma fitting term related to curvature of response.

d: change in respiration under illumination.
```{r grc models}
# simple saturating function; rectangular hyperbola
grc <- function(I, a, Pmax){((a * I * Pmax)/((a*I) + Pmax))
}
  #(equivalent to mm <- function(I, KM, Pmax){(Pmax* I)/(KM + I)})

TestI = c(0:14)

plot(x = TestI, y = grc(I = TestI, a = 0.1, Pmax = 1))

# # function with beta photoinhibition;
#https://www.frontiersin.org/articles/10.3389/fpls.2020.581851/full
 grcbeta <- function(I, a, b, g){(a * ((1 - (b*I))/(1 + (g*I)))*I)
 }
# 
 plot(x = TestI, y = grcbeta(I = TestI, a = 0.1, b = 0.1, g = 0.01))

#Platt et al., 1980
#Harrison & Platt, 1986
grcplatt <- function(I, a, b, Pmax){Pmax * (1-exp(-a*I/Pmax)) * exp(-b*I/Pmax)}

plot(x = TestI, y = grcplatt(I = TestI, a = 0.1, b = 0.1, Pmax = 1))

# mm <- function(I, KM, Pmax){(Pmax* I)/(KM + I)}
# 
# plot(x = TestI, y = mm(I = TestI, KM = 10, Pmax = 1))

# mmsubi <- function(I, KM, Pmax, Ki){(Pmax* I)/(KM + (I * (1 + I/Ki)))}
# 
# plot(x = TestI, y = mmsubi(I = TestI, KM = 10, Pmax = 1, Ki = 1))

# linear equation to deal with photoperiods and exclusively no growth
LinEqn <- function(x, M, Intercept){((x*M)+ Intercept)}

LinEqnStart <- list(M = 0, Intercept = 0)

```

Issue with MED4 data at 250 uM; lhs of model 42, right hand 40; for some reason lhs prediction missing for two of the rhs diel PUR values

Causes 'augment' to fail.
Get around other ways if needed.

Issue: OrgPur_day is 'NA' for 3 rows of MED4 x O2_um = 250
Substitute in PURPhotonDose_day which includes extrapolated estimates of PUR for strain x growth light that lack OLIS spectra

```{r growthPURfits}

#constrain with lower 0 and upper 1 limits to avoid excessive Pmax and negative b

# PURPARStrainO2Nest <- PURPARFits |>
#   nest(data = -c("Strain","O2_uM")) |>
#   mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PUR_day, a, Pmax),
#                               data = .x,
#                               start = list(a = 1e-6,
#                                            Pmax = 1),
#                               lower = c(0, 0),
#                               upper = c(1,100)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRC_Param = map(GRC_Model, tidy),
#          GRC_Predict = map(GRC_Model, possibly(augment), NULL),
#          GRC_Glance = map(GRC_Model, possibly(glance))) |>
#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
#                               data = .x,
#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
#                               lower = c(0, 0, 0),
#                               upper = c(1,1,100)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
#          )

# model with dummy dark, 0 PAR,  growth rates. Also removed data if no growth occurred under an O2 and photoperiod condition so that the model would not be skewed towards zero. As per Amanda and Doug's advice, filtered out PUR d-1 above 1.5e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
PURPARStrainO2NestDummy_filtered <- PURPARFits_dummy |>
  mutate(remove = case_when(Strain == "MED4" & Photoperiod == 4 ~ 1,
                            Strain == "MED4" & O2_uM == 25 & Photoperiod == 8 & WL == "WW" ~ 1,
                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 16 ~ 1,
                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 12 & WL == "WW" ~ 1,
                            Strain == "SS120"  & O2_uM == 2.5 & Photoperiod %in% c(16,8,4) ~ 1,
                            Strain == "SS120"  & O2_uM == 25 & Photoperiod %in% c(16) & WL == 450 ~ 1,
                            Strain == "SS120"  & O2_uM == 250 & Photoperiod %in% c(4) & WL == 450 ~ 1,
                            TRUE ~ 0)) |>
   filter(remove == 0,
          PURPhotonDose_day <= 1.5e+06) |>
  nest(data = -c("Strain","O2_uM")) |>
  # mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
  #                             data = .x,
  #                             start = list(a = 1e-6,
  #                                          Pmax = 1),
  #                             lower = c(0, 0),
  #                             upper = c(1,100)
  #                        ), NULL)
  #                        )
  #        ) |>
  # mutate(GRC_Param = map(GRC_Model, tidy),
  #        GRC_Predict = map(GRC_Model, possibly(augment), NULL),
  #        GRC_Glance = map(GRC_Model, possibly(glance))) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
                              lower = c(0, 0, 0),
                              upper = c(1,1,100)
                         ), 0)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

PURPARStrainO2NestDummy <- PURPARFits_dummy |>
  nest(data = -c("Strain","O2_uM")) |>
  # mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
  #                             data = .x,
  #                             start = list(a = 1e-6,
  #                                          Pmax = 1),
  #                             lower = c(0, 0),
  #                             upper = c(1,100)
  #                        ), NULL)
  #                        )
  #        ) |>
  # mutate(GRC_Param = map(GRC_Model, tidy),
  #        GRC_Predict = map(GRC_Model, possibly(augment), NULL),
  #        GRC_Glance = map(GRC_Model, possibly(glance))) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
                              lower = c(0, 0, 0),
                              upper = c(1,1,100)
                         ), 0)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

# PURPARStrainO2NestDummy_TEST <- PURPARFits_dummy |>
#   nest(data = -c("Strain","O2_uM")) |>
# mutate(GRC_Model_Photoperiod = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day * Photoperiod ~ grc(I = PURPhotonDose_day, a, Pmax),
#                             data = .x,
#                             start = list(a = 1e-6,
#                                          Pmax = 1),
#                             lower = c(0, 0),
#                             upper = c(1,100)
#                        ), NULL)
#                        )
#        ) |>
# mutate(GRC_Param_Photoperiod = map(GRC_Model_Photoperiod, tidy),
#        GRC_Predict_Photoperiod = map(GRC_Model_Photoperiod, possibly(augment), NULL),
#        GRC_Glance_Photoperiod = map(GRC_Model_Photoperiod, possibly(glance))) |>
#   mutate(GRCplatt_Model_Photoperiod = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day * Photoperiod ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
#                               data = .x,
#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1),
#                               lower = c(0, 0, 0),
#                               upper = c(1,1,100)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRCplatt_Param_Photoperiod = map(GRCplatt_Model_Photoperiod, tidy),
#          GRCplatt_Predict_Photoperiod = map(GRCplatt_Model_Photoperiod, possibly(augment)),
#          GRCplatt_Glance_Photoperiod = map(GRCplatt_Model_Photoperiod, possibly(glance))
#          ) %>%
#     mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
#                               data = .x,
#                               start = list(a = 1e-6,
#                                            Pmax = 1),
#                               lower = c(0, 0),
#                               upper = c(1,100)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRC_Param = map(GRC_Model, tidy),
#          GRC_Predict = map(GRC_Model, possibly(augment), NULL),
#          GRC_Glance = map(GRC_Model, possibly(glance))) |>
#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
#                               data = .x,
#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1),
#                               lower = c(0, 0, 0),
#                               upper = c(1,1,100)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
#          )
# 
# PURPARStrainO2NestDummy_TEST

# PURPARStrainO2PhotoperiodNest <- PURPARFits |>
#   nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
#   mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
#                               data = .x,
#                               start = list(a = 1e-6,
#                                            Pmax = 1),
#                               lower = c(0, 0),
#                               upper = c(1,100)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRC_Param = map(GRC_Model, possibly(tidy)),
#          GRC_Predict = map(GRC_Model, possibly(augment), NULL),
#          GRC_Glance = map(GRC_Model, possibly(glance))) |>
#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
#                               data = .x,
#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1),
#                               lower = c(0, 0, 0),
#                               upper = c(1,1,100)
#                          ), NULL)
#                          )
#          ) |>
#   mutate(GRCplatt_Param = map(GRCplatt_Model, possibly(tidy)),
#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
#          )

# model with dummy dark, 0 PAR, 0 growth rates
#Note: fit fails for SS120, 12h photoperiod and O2 = 25uM. Works if I remove outlier(WL = 660 and PAR = 30 or MiSa1456) 
PURPARStrainO2PhotoperiodNestDummy <- PURPARFits_dummy |>
   filter(ID != "MiSa1456") %>% 
   # filter(ID != "JuNa1068") %>% 
 nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
  # mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
  #                             data = .x,
  #                             start = list(a = 1e-6,
  #                                          Pmax = 1),
  #                             lower = c(0, 0),
  #                             upper = c(1,100)
  #                        ), NULL)
  #                        )
  #        ) |>
  # mutate(GRC_Param = map(GRC_Model, tidy),
  #        GRC_Predict = map(GRC_Model, possibly(augment), NULL),
  #        GRC_Glance = map(GRC_Model, possibly(glance))) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-8, b = 1e-9, Pmax = 1),
                              lower = c(-0, 0, 0),
                              upper = c(1,1,100)
                         ), NULL)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         ) |>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

# model with dummy dark, 0 PAR,  growth rates
PURPARStrainO2WLNestDummy <- PURPARFits_dummy |>
  nest(data = -c("Strain","O2_uM", "WL")) |>
  # mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
  #                             data = .x,
  #                             start = list(a = 1e-6,
  #                                          Pmax = 1),
  #                             lower = c(0, 0),
  #                             upper = c(1,100)
  #                        ), 0)
  #                        )
  #        ) |>
  # mutate(GRC_Param = map(GRC_Model, tidy),
  #        GRC_Predict = map(GRC_Model, possibly(augment), NULL),
  #        GRC_Glance = map(GRC_Model, possibly(glance))) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1),
                              lower = c(0, 0, 0),
                              upper = c(1,1,100)
                         ), 0)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )|>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

# model with dummy dark, 0 PAR,  growth rates
PURPARStrainO2PeriodWLNestDummy <- PURPARFits_dummy |>
  nest(data = -c("Strain","O2_uM", "Photoperiod", "WL")) |>
  # mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
  #                             data = .x,
  #                             start = list(a = 1e-6,
  #                                          Pmax = 1),
  #                             lower = c(0, 0),
  #                             upper = c(1,100)
  #                        ), 0)
  #                        )
  #        ) |>
  # mutate(GRC_Param = map(GRC_Model, tidy),
  #        GRC_Predict = map(GRC_Model, possibly(augment), NULL),
  #        GRC_Glance = map(GRC_Model, possibly(glance), )) |>
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
                              data = .x,
                              start = list(a = 1e-7, b = 1e-8, Pmax = 1),
                              lower = c(0, 0, 0),
                              upper = c(1,1,100)
                         ), 0)
                         )
         ) |>
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
         )|>
  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
                              data = .x,
                              start = LinEqnStart
                         ), NULL)
                         )
         ) |>
  mutate(GRClm_Param = map(GRClm_Model, tidy),
         GRClm_Predict = map(GRClm_Model, possibly(augment)),
         GRClm_Glance = map(GRClm_Model, possibly(glance))
         )

```

```{r growthPURplots, fig.height= 10, fig.width= 10}
#ReplicateMean_

# PURPARStrainWLNest |>
#   #filter(!is.null(GRC_Model)) |>
#   filter(!map_lgl(GRC_Model, is.null)) |>  
#   unnest(GRC_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
#   facet_grid(rows = vars(WL), cols = vars(Strain)) + 
#   theme_bw()

# PURPARStrainO2Nest |>
#   filter(!map_lgl(GRC_Model, is.null)) |> #https://stackoverflow.com/questions/57336319/how-to-filter-out-null-elements-of-tibbles-list-column 
#   unnest(GRC_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
#     labs(title = "PURPARStrainO2Nest GRC") +
#   theme_bw()

# PURPARStrainO2NestDummy |>
#   filter(!map_lgl(GRC_Model, is.null)) |> #https://stackoverflow.com/questions/57336319/how-to-filter-out-null-elements-of-tibbles-list-column 
#   unnest(GRC_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
#     labs(title = "PURPARStrainO2NestDummy GRC") +
#   theme_bw()

# PURPARStrainO2Nest |>
#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
#   unnest(GRCplatt_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
#     labs(title = "PURPARStrainO2Nest Platt") +
#   theme_bw()
#

PURPARStrainO2NestDummy |>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
  labs(title = "PURPARStrainO2NestDummy Platt") +
  theme_bw()

PURPARStrainO2NestDummy_filtered|>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
  labs(title = "PURPARStrainO2NestDummy_filtered Platt") +
  theme_bw()

# PURPARStrainO2PhotoperiodNest |>
#   filter(!map_lgl(GRC_Model, is.null)) |>
#   unnest(GRC_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
#     labs(title = "PURPARStrainO2PhotoperiodNest GRC") +
#   theme_bw()

# PURPARStrainO2PhotoperiodNestDummy |>
#    filter(!map_lgl(GRC_Model, is.null)) |>
#   unnest(GRC_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
#     labs(title = "PURPARStrainO2PhotoperiodNestDummy GRC") +
#   theme_bw()

# PURPARStrainO2PhotoperiodNest |>
#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
#   unnest(GRCplatt_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
#     labs(title = "PURPARStrainO2PhotoperiodNest Platt") +
#   theme_bw()

PURPARStrainO2PhotoperiodNestDummy |>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +   
  scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
    labs(title = "PURPARStrainO2PhotoperiodNestDummy Platt") +
  theme_bw()

PURPARStrainO2PhotoperiodNestDummy |>
  filter(!map_lgl(GRClm_Model, is.null)) |>
  unnest(GRClm_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
   scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
    labs(title = "PURPARStrainO2PhotoperiodNestDummy Linear Model") +
  theme_bw()

PURPARStrainO2PhotoperiodNestDummy |>
  unnest(data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  # geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
     scale_colour_manual(values = MCMIXColours) +
    facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
    labs(title = "PURPARStrainO2PhotoperiodNestDummy all data no fits") +
  theme_bw()

PURPARStrainO2WLNestDummy |>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
  facet_grid(rows = vars(O2_uM, WL), cols = vars(Strain)) +
    labs(title = "PURPARStrainO2WLNestDummy Platt") +
  theme_bw()

# PURPARStrainO2PeriodWLNestDummy |>
#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
#   unnest(GRCplatt_Predict, data) |>
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
#   facet_grid(rows = vars(O2_uM, Photoperiod, WL), cols = vars(Strain)) +
#     labs(title = "PURPARStrainO2PeriodWLNestDummy Platt") +
#   theme_bw()

```

nlsLM generates AIC accessed with broom::glance
Choose best model between platt and lm based on lowest GIC 
```{r aic comparisons}
#https://www.scribbr.com/statistics/akaike-information-criterion/

#need to remove 'null' models to facilitate conversion of AIC from 'list' derived from 'Glance' column, to dbl
# PURPARStrainO2BestModels <- PURPARStrainO2Nest|>
#   select(-c(data)) |>
#   pivot_longer(cols = -c(Strain, O2_uM)) |>
#   drop_na(value) |>
#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
#   pivot_wider(names_from = Output, values_from = value) |>
#   filter(!map_lgl(Model, is.null)) |>
#   filter(!map_lgl(Glance, is.null)) |>
#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
#   group_by(Strain, O2_uM) |>
#   filter(AIC == min(AIC)) |>
#   ungroup() |>
#   select(-c(Model, Glance)) |>
#   unnest(Param) |>
#   select(-c(statistic)) |>
#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
#  
# PURPARStrainO2BestModels

PURPARStrainO2BestModelsDummy <- PURPARStrainO2NestDummy|>
  # select(-c(data)) |>
  pivot_longer(cols = -c(Strain, O2_uM, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
   # filter(!map_lgl(Model, is.null)) |>
  filter(!map_lgl(Glance, is.null)) |>
  mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
  group_by(Strain, O2_uM) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
  select(-c(Model, Glance)) |>
  unnest(Param) |>
  select(-c(statistic)) |>
  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))

PURPARStrainO2BestModelsDummy

PURPARStrainO2BestModelsDummy_filtered <- PURPARStrainO2NestDummy_filtered|>
  # select(-c(data)) |>
  pivot_longer(cols = -c(Strain, O2_uM, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
   # filter(!map_lgl(Model, is.null)) |>
  filter(!map_lgl(Glance, is.null)) |>
  mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
  group_by(Strain, O2_uM) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
  select(-c(Model, Glance)) |>
  unnest(Param) |>
  select(-c(statistic)) |>
  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))

PURPARStrainO2BestModelsDummy_filtered

PURPARStrainO2PhotoperiodBestModelsDummy <- PURPARStrainO2PhotoperiodNestDummy|>
  # select(-c(data)) |>
  pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
  filter(!map_lgl(Model, is.null)) |>
  filter(!map_lgl(Glance, is.null)) |>
  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
  group_by(Strain, O2_uM, Photoperiod) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
  select(-c(Model, Glance)) |>
  unnest(Param) |>
  select(-c(statistic)) |>
  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))

PURPARStrainO2PhotoperiodBestModelsDummy

PURPARStrainO2WLBestModelsDummy <- PURPARStrainO2WLNestDummy|>
  # select(-c(data)) |>
  pivot_longer(cols = -c(Strain, O2_uM, WL, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
 filter(!map_lgl(Model, is.null)) |>
  filter(!map_lgl(Glance, is.null)) |>
  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
  group_by(Strain, O2_uM, WL) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
  select(-c(Model, Glance)) |>
  unnest(Param) |>
  select(-c(statistic)) |>
  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))

PURPARStrainO2WLBestModelsDummy

# PURPARStrainO2PhotoperiodWLBestModels <- PURPARStrainO2PhotoperiodNest|>
#   select(-c(data)) |>
#   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, WL)) |>
#   drop_na(value) |>
#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
#   pivot_wider(names_from = Output, values_from = value) |>
#   filter(!map_lgl(Model, is.null)) |>
#   filter(!map_lgl(Param, is.null)) |>
#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
#   group_by(Strain, O2_uM, Photoperiod) |>
#   filter(AIC == min(AIC)) |>
#   ungroup() |>
#   select(-c(Model, Glance)) |>
#   unnest(Param) |>
#   select(-c(statistic)) |>
#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
#  
# PURPARStrainO2PhotoperiodWLBestModels

# mutate(Pmax_Ye = if_else(ModelType == "GRCbeta", estimate_a * ((sqrt(estimate_b + estimate_g) - sqrt(estimate_b))/estimate_g)^2, NA))

```

Want platt model for all fits that did not fail and lm for platt models that returned a NULL
```{r}

#filter to keep platt models
KeepPlattModel <- PURPARStrainO2PhotoperiodNestDummy|>
  select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
   filter(!map_lgl(GRCplatt_Model, is.null))

#filter to keep only the models that failed to fit a platt model, fits by lm remains. 
KeepLmModel <- PURPARStrainO2PhotoperiodNestDummy|>
  filter(map_lgl(GRCplatt_Model, is.null)) |>
 select(-c(GRCplatt_Glance, GRCplatt_Model, GRCplatt_Param, GRCplatt_Predict))

# Join  
StrainO2Photoperiod_AllModels <- full_join(KeepPlattModel, KeepLmModel)

 remove(KeepPlattModel)
 remove(KeepLmModel)

 StrainO2Photoperiod_PlattLmParam <- StrainO2Photoperiod_AllModels |>
   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
filter(!map_lgl(Model, is.null)) |>
  filter(!map_lgl(Glance, is.null)) |>
  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
  group_by(Strain, O2_uM, Photoperiod) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
  select(-c(Model, Glance)) |>
  unnest(Param) |>
  select(-c(statistic)) |>
  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))

 StrainO2filtered_PlattLmModel <- PURPARStrainO2NestDummy_filtered|>
  # select(-c(data)) |>
  pivot_longer(cols = -c(Strain, O2_uM, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
   # filter(!map_lgl(Model, is.null)) |>
  filter(!map_lgl(Glance, is.null)) |>
  mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
  group_by(Strain, O2_uM) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
  select(-c(Glance))

```

The linear models do not have alpha, beta and pmax so inf and NA are generated. Change them to 0.
```{r lm platt parameters set to zero}

PURPARStrainO2BestModelsDummy <- PURPARStrainO2BestModelsDummy|>
  mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
         estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
         estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
         AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC))

PURPARStrainO2BestModelsDummy

PURPARStrainO2WLBestModelsDummy <- PURPARStrainO2WLBestModelsDummy|>
  mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
         estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
         estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
         AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC))

PURPARStrainO2WLBestModelsDummy

StrainO2Photoperiod_PlattLmParam <- StrainO2Photoperiod_PlattLmParam|>
  mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
         estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
         estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
         AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC))

StrainO2Photoperiod_PlattLmParam

```

```{r plot models}

PURPARStrainO2PhotoperiodNestDummy |>
  # select(-c(data)) |>
  pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")| str_detect(name, pattern = "Predict")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
  filter(!map_lgl(Model, is.null)) |>
  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
  group_by(Strain, O2_uM, Photoperiod) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
   # filter(!map_lgl(GRClm_Model, is.null)) |>
  unnest(Predict, data) |>

  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
   geom_text(aes(x = 3500000, y = 0.25, label = paste(ModelType), show.legend = FALSE, ),    # parse = TRUE,
    # hjust = 0,
    # vjust = 1,
    # size = 8.0
  ) +
     scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
    labs(title = "PURPARStrainO2PhotoperiodNestDummy Best Model") +
  theme_bw()

 StrainO2Photoperiod_AllModels |>
  # select(-c(data)) |>
  pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")| str_detect(name, pattern = "Predict")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
  filter(!map_lgl(Model, is.null)) |>
  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
  group_by(Strain, O2_uM, Photoperiod) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
   # filter(!map_lgl(GRClm_Model, is.null)) |>
  unnest(Predict, data) |>
  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
   geom_text(aes(x = 3500000, y = 0.25, label = paste(ModelType), show.legend = FALSE, ),    # parse = TRUE,
    # hjust = 0,
    # vjust = 1,
    # size = 8.0
  ) +
      scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
    labs(title = "Linear models replace null platt models.") +
  theme_bw()

PURPARStrainO2PhotoperiodNestDummy |>
  # filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(data) |>
    # filter(WL %in% 450) %>% )),
  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
  # geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
     scale_colour_manual(values = MCMIXColours) +
  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
    labs(title = "PURPARStrainO2PhotoperiodNestDummy all data no fits") +
  theme_bw()

```

```{r compare 1 fit of all photoperiod to each photoperiods using platt or lm}

#extract fit parameters from each photoperiod.
StrainO2Photoperiod_PlattLmModel <- StrainO2Photoperiod_AllModels |>
   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  filter(Output == "Model") |>
  rename(Model = "value")

# make wider to join with DF that contains the 1 fit through all photoperiods
Wider_Photoperiods <- StrainO2Photoperiod_PlattLmModel %>% 
  select(Strain, Photoperiod, O2_uM, Model) %>% 
  pivot_wider(names_from = Photoperiod, values_from = Model)

# this contains 1 fit through all photoperiods, the photoperiods with no growth were filtered out.
AllPhotoperiods <- StrainO2filtered_PlattLmModel %>% 
  select(Strain, O2_uM, Model) %>% 
 rename(All = 'Model')

CombinePhotoperiods <- left_join(Wider_Photoperiods, AllPhotoperiods)

ANOVA_AllPhotoperiods <- CombinePhotoperiods %>% 
  mutate(twelve = `12`,
         four = `4`,
         eight = `8`,
         sixteen = `16`) %>%
  mutate(fourvsAll = map(map2(four, All, possibly(anova, otherwise = NULL)), tidy),
         eightvsAll = map(map2(eight, All, possibly(anova, otherwise = NULL)), tidy),
         twelvevsAll = map(map2(twelve, All, possibly(anova, otherwise = NULL)), tidy),
         sixteenvsAll = map(map2(sixteen, All, possibly(anova, otherwise = NULL)), tidy)) %>% 
  select(Strain, O2_uM, fourvsAll, eightvsAll, twelvevsAll, sixteenvsAll) %>% 
  pivot_longer(cols = c(fourvsAll, eightvsAll, twelvevsAll, sixteenvsAll)) %>% 
  unnest(value, keep_empty = TRUE) %>% 
  filter(is.na(term) & is.na(p.value) |
           !is.na(term) & !is.na(p.value)) %>%
  select(Strain, O2_uM, name, p.value) %>% 
  separate(name, into = c("Photoperiod1", "AllPhotoperiod"), sep = "vs")

# %>% 
#   mutate(p.value = case_when(is.na(p.value) ~ 0,
#                              TRUE ~ p.value)) # Changed all failed fits to p.value = 0
  # mutate(pval = pluck(value, "p.value", 2))

ANOVA_AllPhotoperiods %>% 
  mutate(Photoperiod1 = as.numeric(case_when(Photoperiod1 == 'four' ~ 4,
                                  Photoperiod1 == 'eight' ~ 8,
                                  Photoperiod1 == 'twelve' ~ 12,
                                  Photoperiod1 == 'sixteen' ~ 16)),
         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
    # mutate(Photoperiod1 = factor(Photoperiod1, levels = c('four','eight', 'twelve', 'sixteen'))) %>% 
  ggplot() +
  geom_point(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(`p.value` < 0.05)) +
  geom_text(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(`p.value` > 0.05), label = "ns") +
  geom_text(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(is.na(`p.value`)), label = "NA") +
  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
  labs(title = "ANOVA compare all models",
       caption = "NA = atleast one model did not fit; 
       ns = not significantly different from all photoperiod model (same); 
       dot = significantly different from all photoperiod model")

```
# Remove the photoperiods from the model that are significantly different from the ANOVA run on the fit including all photoperiods against each individual photoperiod.   
```{r}

```

# Doug said not to do this
```{r ANOVA between photoperiods platt model}

# ANOVA_Photoperiods <- PURPARStrainO2PhotoperiodNestDummy %>% 
#   select(Strain, Photoperiod, O2_uM, GRCplatt_Model) %>% 
#   pivot_wider(names_from = Photoperiod, values_from = GRCplatt_Model) %>% 
#   mutate(twelve = `12`,
#          four = `4`,
#          eight = `8`,
#          sixteen = `16`) %>% 
#   # select(-c(eight, four)) %>% 
#   # filter(!map_lgl(twelve, is.null),
#   #        !map_lgl(sixteen, is.null)) %>% 
#   mutate(fourvseight = map(map2(four, eight, possibly(anova, otherwise = NULL)), tidy),
#          fourvstwelve = map(map2(four, twelve, possibly(anova, otherwise = NULL)), tidy),
#          fourvssixteen = map(map2(four, sixteen, possibly(anova, otherwise = NULL)), tidy),
#          eightvstwelve = map(map2(eight, twelve, possibly(anova, otherwise = NULL)), tidy),
#          eightvssixteen = map(map2(eight, sixteen, possibly(anova, otherwise = NULL)), tidy),
#          twelvevssixteen =map(map2(twelve, sixteen, possibly(anova, otherwise = NULL)), tidy)) %>% 
#   select(Strain, O2_uM, fourvseight, fourvstwelve, fourvssixteen, eightvstwelve, eightvssixteen, twelvevssixteen) %>% 
#   pivot_longer(cols = c(fourvseight, fourvstwelve, fourvssixteen, eightvstwelve, eightvssixteen, twelvevssixteen)) %>% 
#   unnest(value, keep_empty = TRUE) %>% 
#   filter(is.na(term) & is.na(p.value) |
#            !is.na(term) & !is.na(p.value)) %>%
#   select(Strain, O2_uM, name, p.value) %>% 
#   separate(name, into = c("Photoperiod1", "Photoperiod2"), sep = "vs") 
# 
# # %>% 
# #   mutate(p.value = case_when(is.na(p.value) ~ 0,
# #                              TRUE ~ p.value)) # Changed all failed fits to p.value = 0
#   # mutate(pval = pluck(value, "p.value", 2))
#   
# # ANOVA_Photoperiods %>% 
# #     mutate(Photoperiod1 = factor(Photoperiod1, levels = c("four", "eight", "twelve", "sixteen")),
# #            Photoperiod2 = factor(Photoperiod2, levels = c( "four","eight", "twelve", "sixteen"))) %>% 
# #   ggplot() +
# #   geom_point(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(`p.value` < 0.05)) +
# #   geom_text(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(`p.value` > 0.05), label = "ns") +
# #   geom_text(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(is.na(`p.value`)), label = "NA") +
# #   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
# #   labs(caption = "NA = atleast one model did not fit; 
# #        ns = not significantly different from each other (same); 
# #        dot = significantly different from each other")
# 
# 
# 
# ANOVA_Photoperiods %>% 
#   mutate(Photoperiod1 = as.numeric(case_when(Photoperiod1 == 'four' ~ 4,
#                                             Photoperiod1 == 'eight' ~ 8,
#                                             Photoperiod1 == 'twelve' ~ 12,
#                                             Photoperiod1 == 'sixteen' ~ 16))) %>% 
#   mutate(Photoperiod2 = as.numeric(case_when(Photoperiod2 == 'four' ~ 4,
#                                             Photoperiod2 == 'eight' ~ 8,
#                                             Photoperiod2 == 'twelve' ~ 12,
#                                             Photoperiod2 == 'sixteen' ~ 16)),
#          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
#          Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>% 
#     # mutate(Photoperiod2 = factor(Photoperiod2, levels = c("four", "eight", "twelve", "sixteen")),
#     #        Photoperiod1 = factor(Photoperiod1, levels = c( "four","eight", "twelve", "sixteen"))) %>% 
#   ggplot() +
#   geom_point(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(`p.value` < 0.05)) +
#   geom_text(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(`p.value` > 0.05), label = "ns") +
#   geom_text(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(is.na(`p.value`)), label = "NA") +
#   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
#   scale_y_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
#   labs(title = "ANOVA compare GRCplatt_Model",
#        caption = "NA = atleast one model did not fit; 
#        ns = not significantly different from each other (same); 
#        dot = significantly different from each other")
# 
#

```
4 h photoperiod is almost always different from others. 
8 h photoperiod is different for MED4 at 25 uM; MIT9313, 8 and 12 are different at 2.5. all others are not significantly different from one another

#now do ANOVA on fits that include lm for conditions where no growth occured across photoperiod
# Doug said this is not what I should do, only ANOVA of 1 fit through all photoperiod against each photoperiod as done chunk above.
```{r ANOVA using best model platt or lm}

# # PURPARStrainO2PhotoperiodBestModels <- PURPARStrainO2PhotoperiodNestDummy |>
# #   select(-c(data)) |>
# #   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod)) |>
# #   drop_na(value) |>
# #   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
# #   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
# #   pivot_wider(names_from = Output, values_from = value) |>
# #   filter(!map_lgl(Model, is.null)) |>
# #   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
# #   group_by(Strain, O2_uM, Photoperiod) |>
# #   filter(AIC == min(AIC)) |>
# #   ungroup()
# 
# ANOVA_BestModel <- StrainO2Photoperiod_PlattLmModel %>% 
#   select(Strain, Photoperiod, O2_uM, Model) %>% 
#   pivot_wider(names_from = Photoperiod, values_from = Model) %>% 
#   mutate(twelve = `12`,
#          four = `4`,
#          eight = `8`,
#          sixteen = `16`) %>% 
#   # select(-c(eight, four)) %>% 
#   # filter(!map_lgl(twelve, is.null),
#   #        !map_lgl(sixteen, is.null)) %>% 
#   mutate(fourvseight = map(map2(four, eight, possibly(anova, otherwise = 0)), tidy),
#          fourvstwelve = map(map2(four, twelve, possibly(anova, otherwise = 0)), tidy),
#          fourvssixteen = map(map2(four, sixteen, possibly(anova, otherwise = 0)), tidy),
#          eightvstwelve = map(map2(eight, twelve, possibly(anova, otherwise = 0)), tidy),
#          eightvssixteen = map(map2(eight, sixteen, possibly(anova, otherwise = 0)), tidy),
#          twelvevssixteen =map(map2(twelve, sixteen, possibly(anova, otherwise = 0)), tidy)) %>% 
#   select(Strain, O2_uM, fourvseight, fourvstwelve, fourvssixteen, eightvstwelve, eightvssixteen, twelvevssixteen) %>% 
#   pivot_longer(cols = c(fourvseight, fourvstwelve, fourvssixteen, eightvstwelve, eightvssixteen, twelvevssixteen)) %>% 
#   unnest(value, keep_empty = TRUE) %>% 
#   filter(is.na(term) & is.na(p.value) |
#            !is.na(term) & !is.na(p.value)) %>%
#   select(Strain, O2_uM, name, p.value) %>% 
#   separate(name, into = c("Photoperiod1", "Photoperiod2"), sep = "vs") 
# 
# # %>% 
# #   mutate(p.value = case_when(is.na(p.value) ~ 0,
# #                              TRUE ~ p.value)) # Changed all failed fits to p.value = 0
#   # mutate(pval = pluck(value, "p.value", 2))
#   
# # ANOVA_Photoperiods %>% 
# #     mutate(Photoperiod1 = factor(Photoperiod1, levels = c("four", "eight", "twelve", "sixteen")),
# #            Photoperiod2 = factor(Photoperiod2, levels = c( "four","eight", "twelve", "sixteen"))) %>% 
# #   ggplot() +
# #   geom_point(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(`p.value` < 0.05)) +
# #   geom_text(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(`p.value` > 0.05), label = "ns") +
# #   geom_text(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(is.na(`p.value`)), label = "NA") +
# #   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
# #   labs(caption = "NA = atleast one model did not fit; 
# #        ns = not significantly different from each other (same); 
# #        dot = significantly different from each other")
# 
# 
# 
# ANOVA_BestModel %>% 
#   mutate(Photoperiod1 = as.numeric(case_when(Photoperiod1 == 'four' ~ 4,
#                                             Photoperiod1 == 'eight' ~ 8,
#                                             Photoperiod1 == 'twelve' ~ 12,
#                                             Photoperiod1 == 'sixteen' ~ 16))) %>% 
#   mutate(Photoperiod2 = as.numeric(case_when(Photoperiod2 == 'four' ~ 4,
#                                             Photoperiod2 == 'eight' ~ 8,
#                                             Photoperiod2 == 'twelve' ~ 12,
#                                             Photoperiod2 == 'sixteen' ~ 16)),
#          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
#          Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
#     # mutate(Photoperiod2 = factor(Photoperiod2, levels = c("four", "eight", "twelve", "sixteen")),
#     #        Photoperiod1 = factor(Photoperiod1, levels = c( "four","eight", "twelve", "sixteen"))) %>% 
#   ggplot() +
#   geom_point(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(`p.value` < 0.05)) +
#   geom_text(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(`p.value` > 0.05), label = "ns") +
#   geom_text(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(is.na(`p.value`)), label = "NA") +
#     geom_text(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(is.nan(`p.value`)), label = "Not a number") + #tried this did not work
#   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
#   scale_y_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
#   labs(title = "ANOVA compare Best Model",
#        caption = "NA = atleast one model did not fit; 
#        ns = not significantly different from each other (same); 
#        dot = significantly different from each other")
#

```
The no growths, linear fit return NaN in ANOVA

```{r PUR per day, fig.height= 20, fig.width= 20 }

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }

PURPARStrainO2PhotoperiodNestDummy |>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, data) |>
   filter(Strain == "MED4") %>%
  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel = "Oxygen Concentration (µM)",
         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1, alpha = 0.8) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`, line = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), size = 1) + 
 # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
 labs(title = "MED4", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
 #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
    #                    # limits = c(10^4, 10^7),
    #                    breaks = c(10^4, 10^5, 10^6)) +
  scale_x_continuous(label=scientific_10) +
      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
  # coord_cartesian(xlim = c (0, 16)) +
   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours) +
   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
  # scale_y_continuous(limits = c(-0.05,0.050)) +
  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
   scale_shape_manual(values = PhotoperiodShapes)  +
  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
 guides(linetype = guide_legend(nrow = 4),
        fill = "none",
        colour = guide_legend(nrow = 4)) +
 guides(shape = guide_legend(nrow = 4)) +
  theme_bw() +
   theme( strip.text = element_text(size = 30),
        axis.title = element_text(size = 30, color = "black"),
        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
        strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title =  element_text(size = 30),  #change legend title font size
        legend.text = element_text(size = 30),   #change legend text font size
        legend.position = "top") +
  labs( shape = "Photoperiod (h)",
        color = "Growth Waveband (nm)",
       linetype = "Photoperiod (h) "
      )

PURPARStrainO2PhotoperiodNestDummy |>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, data) |>
   filter(Strain == "SS120") %>%
  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel = "Oxygen Concentration (µM)",
         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
  ggplot() +

  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1, alpha = 0.8) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`, line = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), size = 1) + 
 # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
 labs(title = "SS120", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
 #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
    #                    # limits = c(10^4, 10^7),
    #                    breaks = c(10^4, 10^5, 10^6)) +
  scale_x_continuous(label=scientific_10) +
      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
  # coord_cartesian(xlim = c (0, 16)) +
   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours) +
   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
  # scale_y_continuous(limits = c(-0.05,0.050)) +
  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
   scale_shape_manual(values = PhotoperiodShapes)  +
  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
 guides(linetype = guide_legend(nrow = 4),
        fill = "none",
        colour = guide_legend(nrow = 4)) +
 guides(shape = guide_legend(nrow = 4)) +
  theme_bw() +
   theme( strip.text = element_text(size = 30),
        axis.title = element_text(size = 30, color = "black"),
        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
        strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title =  element_text(size = 30),  #change legend title font size
        legend.text = element_text(size = 30),   #change legend text font size
        legend.position = "top") +
  labs( shape = "Photoperiod (h)",
        color = "Growth Waveband (nm)",
       linetype = "Photoperiod (h) "
      )

PURPARStrainO2PhotoperiodNestDummy |>
  filter(!map_lgl(GRCplatt_Model, is.null)) |>
  unnest(GRCplatt_Predict, data) |>
   filter(Strain == "MIT9313") %>%
  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel = "Oxygen Concentration (µM)",
         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
  ggplot() +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1, alpha = 0.8) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`, line = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), size = 1) + 
 # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
 labs(title = "MIT9313", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
 #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
    #                    # limits = c(10^4, 10^7),
    #                    breaks = c(10^4, 10^5, 10^6)) +
  scale_x_continuous(label=scientific_10) +
      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
  # coord_cartesian(xlim = c (0, 16)) +
   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours) +
   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
  # scale_y_continuous(limits = c(-0.05,0.050)) +
  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
   scale_shape_manual(values = PhotoperiodShapes)  +
  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
 guides(linetype = guide_legend(nrow = 4),
        fill = "none",
        colour = guide_legend(nrow = 4)) +
 guides(shape = guide_legend(nrow = 4)) +
  theme_bw() +
   theme( strip.text = element_text(size = 30),
        axis.title = element_text(size = 30, color = "black"),
        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
        strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title =  element_text(size = 30),  #change legend title font size
        legend.text = element_text(size = 30),   #change legend text font size
        legend.position = "top") +
  labs( shape = "Photoperiod (h)",
        color = "Growth Waveband (nm)",
       linetype = "Photoperiod (h) "
      )

```

Would like to add Compact Letter Displays (cld) but do not know how. Some examples:
https://stackoverflow.com/questions/70854552/any-other-options-besides-the-traditional-cld-bar-graph/70863531#70863531
https://stackoverflow.com/questions/72756490/loop-tukey-post-hoc-letters-extraction/73274274#73274274

Need test, other than nesting, to determine if Photoperiod has a significant influence (and interaction) on growth rate?

GrowthRate function of PUR, 
  separate models for Strain & O2_uM,

GrowthRate function of PUR in interaction term with Photoperiod and/or light colour
  separate models for Strain & O2_uM,

```{r PUR per day best, fig.height= 20, fig.width= 20 }

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }

MED4PURFITPlot <- PURPARStrainO2PhotoperiodNestDummy |>
  # select(-c(data)) |>
  pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) |>  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")| str_detect(name, pattern = "Predict")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
  filter(!map_lgl(Model, is.null)) |>
  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
  group_by(Strain, O2_uM, Photoperiod) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
   # filter(!map_lgl(GRClm_Model, is.null)) |>
  unnest(Predict, data) |>
   filter(Strain == "MED4") %>%
  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel = "Oxygen Concentration (µM)",
         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
  ggplot() +
   geom_point(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0, data = . %>% filter(PURPhotonDose_day  != 0)) +
   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8, data = . %>% filter(PURPhotonDose_day  != 0)) +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 0.03, data = . %>% filter(PURPhotonDose_day  == 0)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`, line = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), size = 1.0) + 
 # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
 labs(y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
 #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
    #                    # limits = c(10^4, 10^7),
    #                    breaks = c(10^4, 10^5, 10^6)) +
  scale_x_continuous(label=scientific_10) +
      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
  # coord_cartesian(xlim = c (0, 16)) +
   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
   scale_colour_manual(values = MCMIXColours) +
   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
  # scale_y_continuous(limits = c(-0.05,0.050)) +
  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
   scale_shape_manual(values = PhotoperiodShapes)  +
  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
 # guides(linetype = guide_legend(nrow = 4),
 #        fill = "none",
 #        colour = guide_legend(nrow = 4)) +
 # guides(shape = guide_legend(nrow = 4)) +
   guides(linetype = "none",
        fill = "none",
        colour = guide_legend(ncol = 4)) +
 guides(shape = guide_legend(nrow = 1)) +
 theme_bw() +
   theme( strip.text = element_text(size = 30),
        axis.title = element_text(size = 30, color = "black"),
        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
        strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title =  element_text(size = 20),  #change legend title font size
        legend.text = element_text(size = 20),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Waveband (nm)",
       shape = "Photoperiod (h)")

MED4PURFITPlot

SS120PURFITPlot <- PURPARStrainO2PhotoperiodNestDummy |>
  # select(-c(data)) |>
  pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) |>  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")| str_detect(name, pattern = "Predict")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
  filter(!map_lgl(Model, is.null)) |>
  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
  group_by(Strain, O2_uM, Photoperiod) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
   # filter(!map_lgl(GRClm_Model, is.null)) |>
  unnest(Predict, data) |>
   filter(Strain == "SS120") %>%
  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel = "Oxygen Concentration (µM)",
         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
   ggplot() +
   geom_point(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0, data = . %>% filter(PURPhotonDose_day  != 0)) +
   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8, data = . %>% filter(PURPhotonDose_day  != 0)) +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 0.03, data = . %>% filter(PURPhotonDose_day  == 0)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`, line = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), size = 1.0) + 
 # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
 #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
    #                    # limits = c(10^4, 10^7),
    #                    breaks = c(10^4, 10^5, 10^6)) +
  scale_x_continuous(label=scientific_10) +
      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
  # coord_cartesian(xlim = c (0, 16)) +
   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
   scale_colour_manual(values = MCMIXColours) +
   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
  # scale_y_continuous(limits = c(-0.05,0.050)) +
 scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
   scale_shape_manual(values = PhotoperiodShapes)  +
  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
 # guides(linetype = guide_legend(nrow = 4),
 #        fill = "none",
 #        colour = guide_legend(nrow = 4)) +
 # guides(shape = guide_legend(nrow = 4)) +
   guides(linetype = "none",
        fill = "none",
        colour = guide_legend(ncol = 4)) +
 guides(shape = guide_legend(nrow = 1)) +
 theme_bw() +
   theme( strip.text = element_text(size = 30),
        axis.title = element_text(size = 30, color = "black"),
        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
        strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title =  element_text(size = 20),  #change legend title font size
        legend.text = element_text(size = 20),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Waveband (nm)",
       shape = "Photoperiod (h)")

SS120PURFITPlot

MIT9313PURFITPlot <- PURPARStrainO2PhotoperiodNestDummy |>
  # select(-c(data)) |>
  pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) |>  drop_na(value) |>
  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")| str_detect(name, pattern = "Predict")) |>
  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
  pivot_wider(names_from = Output, values_from = value) |>
  filter(!map_lgl(Model, is.null)) |>
  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
  group_by(Strain, O2_uM, Photoperiod) |>
  filter(AIC == min(AIC)) |>
  ungroup() |>
   # filter(!map_lgl(GRClm_Model, is.null)) |>
  unnest(Predict, data) |>
   filter(Strain == "MIT9313") %>%
  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel = "Oxygen Concentration (µM)",
         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
  ggplot() +
   geom_point(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0, data = . %>% filter(PURPhotonDose_day  != 0)) +
   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8, data = . %>% filter(PURPhotonDose_day  != 0)) +
  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 0.03, data = . %>% filter(PURPhotonDose_day  == 0)) +
  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`, line = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), size = 1.0) + 
 # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
 labs(y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
 #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
    #                    # limits = c(10^4, 10^7),
    #                    breaks = c(10^4, 10^5, 10^6)) +
  scale_x_continuous(label=scientific_10) +
      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
  # coord_cartesian(xlim = c (0, 16)) +
   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
    scale_colour_manual(values = MCMIXColours) +
   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
  # scale_y_continuous(limits = c(-0.05,0.050)) +
  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
   scale_shape_manual(values = PhotoperiodShapes)  +
  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
 # guides(linetype = guide_legend(nrow = 4),
 #        fill = "none",
 #        colour = guide_legend(nrow = 4)) +
 # guides(shape = guide_legend(nrow = 4)) +
   guides(linetype = "none",
        fill = "none",
        colour = guide_legend(ncol = 4)) +
 guides(shape = guide_legend(nrow = 1)) +
 theme_bw() +
   theme( strip.text = element_text(size = 30),
        axis.title = element_text(size = 30, color = "black"),
        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
        strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title =  element_text(size = 20),  #change legend title font size
        legend.text = element_text(size = 20),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Waveband (nm)",
       shape = "Photoperiod (h)")

MIT9313PURFITPlot

```

```{r, save PURFitPlots}

ggsave(file = file.path(PlotsPath, paste("MED4PURFITPlot",".png",sep = "")), plot = MED4PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsPath, paste("SS120PURFITPlot",".png",sep = "")), plot = SS120PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsPath, paste("MIT9313PURFITPlot",".png",sep = "")), plot = MIT9313PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

```

``` {r}
# PURPARStrainO2PeriodWLNestDummy |>
#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
#   unnest(GRCplatt_Predict, data) |>
#    filter(Strain == "MIT9313") %>%
#   mutate(PhotoperiodLabel_title = "Photoperiod (h)",
#          OxygenLabel = "Oxygen Concentration (µM)",
#          Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
#   ggplot() +
#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
#     geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1, alpha = 0.8) +
#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`, line = as.factor(WL), color = as.factor(WL))) + 
#  # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
#  labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
#  #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
#   # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
#   # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = . %>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
#     # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
#     #                    # limits = c(10^4, 10^7),
#     #                    breaks = c(10^4, 10^5, 10^6)) +
# 
#       # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
#     # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
#   # coord_cartesian(xlim = c (0, 16)) +
#    scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
#   # coord_cartesian(ylim = c (0, 0.07)) +
#   scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660","530", "450" )) +
#    # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
#    # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
#   # scale_y_continuous(limits = c(-0.05,0.050)) +
#    scale_shape_manual(values = PhotoperiodShapes)  +
#   ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM, Photoperiod), 
#                     labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
#  guides(linetype = "none",
#         fill = "none",
#         colour = guide_legend(ncol = 4)) +
#  guides(shape = guide_legend(nrow = 1)) +
#   theme_bw() +
#    theme( strip.text = element_text(size = 30),
#         axis.title = element_text(size = 30, color = "black"),
#         axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
#         axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
#         strip.background=element_rect(color="grey87", fill = "grey82"),
#         # strip.background=element_rect(fill = "white"),
#         legend.key.size = unit(1, 'cm'), #change legend key size
#         legend.key.height = unit(1, 'cm'), #change legend key height
#         legend.key.width = unit(0.5, 'cm'), #change legend key width
#         legend.title =  element_text(size = 20),  #change legend title font size
#         legend.text = element_text(size = 20),   #change legend text font size
#         legend.position = "top") +
#   labs(color = "Growth Waveband (nm)",
#        shape = "Photoperiod (h)")

```

### 2024-01-18 Code/ManuscriptTargetProtein.Rmd
Edit to run in Github

---
title: "ManuscriptTargetProtein"
author: "Mireille Savoie"
date: "`r format(Sys.Date())`"
output:
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  bookdown::word_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
bibliography: [Manuscript_O2.bib, RPackages.bib]
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Introduction

*Some of the code used to create this R Notebook was refurbished from "PlateAbImport.Rmd" written by Maximilian Berthold, Douglas A. Campbell, Melissa L. Rioux, Sarah J Gore, and Alyson MacCormack.*

Importing and tidying data from a .csv containing already processed target proteins

```{r set project variables}

Project <- "PICO"
DataIn <- file.path("..","Data", "ProcessedData")
DataOut <- file.path("..", "Data", "CleanData")
PlotsOut <- file.path("..","Output", "Figures")

FileEncode <- "UTF-8" 
Delimiter <- ","

HeaderRows <- 0
#AbsWL = c(680, 720, 750) #select OD's of interest from plategrowth.Rds
```

```{r}
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
# library(OneR)
# library(zoo)
# library(strucchange)

library(dplyr)
# library(magrittr)
library(googledrive)
library(googlesheets4)
library(readxl)
```

```{r read locally stored metadata from rds}

CultureCatalog <- readRDS(file = file.path("..", "Data","CultureCatalog.Rds"))

```

```{r read ProcessFile}

TargetProtein <- read.csv(file = file.path(DataIn,"2020_PICO_Multi_TargetProteins.csv"))

glimpse(TargetProtein)

TargetProtein <- TargetProtein %>%
  rename(SampleID = "ï..Sample")

glimpse(TargetProtein)

```

```{r set colours}
MyWavelengths = c(405, 450, 475, 530, 615, 660, 730, "WW")
MCMIXColours = c("violet", "darkblue", "dodgerblue", "darkgreen","orange","red","purple", "black")

names(MCMIXColours) <- MyWavelengths
MCMIXColours
```

```{r join deltaOD with chl DF}

TargetProtein  <- TargetProtein %>% 
 left_join(., CultureCatalog, by = c("SampleID" = "SampleID"))

glimpse(TargetProtein)

```

```{r explore plots}
TargetProtein %>%
   filter(Strain == "MIT9313") %>%
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
  geom_col() +
  # ggplot() +
  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
  # scale_fill_viridis_d(fill = "f68060") %>% 
  # scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
                    labeller = labeller(WL = label_both, O2 = label_both, Strain = label_both)) +
  theme_bw()

TargetProtein %>%
   filter(Strain == "MED4") %>%
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
  geom_col() +
  # ggplot() +
  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
  # scale_fill_viridis_d(fill = "f68060") %>% 
  # scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
                    labeller = labeller(WL = label_both, O2 = label_both, Strain = label_both)) +
  theme_bw()

TargetProtein %>%
   filter(Strain == "MIT9313",
          O2 == 21) %>%
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
  geom_col() +
  # ggplot() +
  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
  # scale_fill_viridis_d(fill = "f68060") %>% 
  # scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
                    labeller = labeller(WL = label_both, O2 = label_both, Strain = label_both)) +
  theme_bw()

TargetProtein %>%
   filter(Strain == "MED4",
          O2 == 21) %>%
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
  geom_col() +
  # ggplot() +
  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
  # scale_fill_viridis_d(fill = "f68060") %>% 
  # scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
                    labeller = labeller(WL = label_both, O2 = label_both, Strain = label_both)) +
  theme_bw()

TargetProtein %>%
   filter(Strain == "MIT9313",
          O2 == 0) %>%
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
  geom_col() +
  # ggplot() +
  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
  # scale_fill_viridis_d(fill = "f68060") %>% 
  # scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
                    labeller = labeller(WL = label_both, O2 = label_both, Strain = label_both)) +
  theme_bw()

TargetProtein %>%
   filter(Strain == "MED4",
          O2 == 0) %>%
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
  geom_col() +
  # ggplot() +
  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
  # scale_fill_viridis_d(fill = "f68060") %>% 
  # scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
                    labeller = labeller(WL = label_both, O2 = label_both, Strain = label_both)) +
  theme_bw()

MIT9313ProteinAttonated <- TargetProtein %>%
  filter( Strain == "MIT9313") %>% 
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
  geom_col() +
   geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.6, position = "stack", check_overlap = T), color = "Black") +
  # ggplot() +
  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
  # scale_fill_viridis_d(fill = "f68060") %>% 
  # scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
                    labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_both)) +
  theme_bw()

MIT9313ProteinAttonated

MED4ProteinAttonated <- TargetProtein %>%
  filter( Strain == "MED4") %>% 
  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
  geom_col() +
   geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black") +
  # ggplot() +
  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
  # scale_fill_viridis_d(fill = "f68060") %>% 
  # scale_colour_manual(values = MCMIXColours) +
 ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
                    labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_both)) +
  theme_bw()

MED4ProteinAttonated
```

```{r }

 ggsave(file = file.path(PlotsOut, paste("MED4ProteinAttonated",".png",sep = "")), plot = MED4ProteinAttonated, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsOut, paste("MIT9313ProteinAttonated",".png",sep = "")), plot = MIT9313ProteinAttonated, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)

```

```{r, save rds}

saveRDS(TargetProtein, file.path(DataOut, paste(Project, "TargetProtein.Rds", sep = "_"), fsep = .Platform$file.sep))

# saveRDS(ChlTurnerCytometerAll, file.path(DataOut, paste(Project, "ChlTurnerMiSa.Rds", sep = "_"), fsep = .Platform$file.sep))
```

### 2024-01-18 Code/Manuscript_O2.Rmd
Generated new plots

@@
 always_allow_html: true
-bibliography: [Prochlorococcus_O2_NPQ.bib, RPackages.bib]
+bibliography: [Manuscript_O2.bib, RPackages.bib]
 csl: plos-one.csl
@@
 
+```{r MED4ProteinAttonated, fig.cap = MED4ProteinAttonated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+
+MED4ProteinAttonated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade).  **",
+
+                    "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",
+                    "Numbers over each bar are fmole/ug",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "MED4ProteinAttonated.png"))
+```
+
+\newpage
+
+```{r MIT9313ProteinAttonated, fig.cap = MIT9313ProteinAttonated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+
+MIT9313ProteinAttonated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade).  **",
+
+                    "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",
+                    "Numbers over each bar are fmole/ug",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "MIT9313ProteinAttonated.png"))
+```
+
 \newpage

### 2024-01-23 Code/Import_MCData.Rmd
Changed 'ID' to 'SampleID' in plot title

@@
 
-TargetFile <- "20220910_PICO_MCMIX004_RUN88.csv"
+TargetFile <- "20220824_PICO_MC257_RUN86.csv"
 
@@
 ```{r, Add positive OD dummy points}
-# 
-# TargetDataMeta <- TargetDataMeta %>%
-# mutate(OD680 = if_else(Tube == 7, 0.005, OD680),
-#        OD720 = if_else(Tube == 7, 0.003, OD720))
+
+TargetDataMeta <- TargetDataMeta %>%
+mutate(OD680 = if_else(Tube == 5, 0.005, OD680),
+       OD720 = if_else(Tube == 5, 0.003, OD720))
 
@@
   scale_colour_manual(values = MCMIXColours) +
-  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; ID; Tube") +
+  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)", subtitle = "Growth Light (µE); Strain; SampleID; Tube") +
  facet_grid(rows = vars(as.factor(O2)), cols = vars(as.factor(Tube), as.factor(Par_ue),Strain, SampleID)) +

### 2024-01-23 Code/Process_MCData.Rmd
Uncommented chunk

@@
 ```{r read ProcessFile}
-ProcessFile <- "../Data/ImportedData/ImportedMCData/20231026_PICO_MCMIX006_RUN126_TargetDataMetaFilter.Rds"
+ProcessFile <- "../Data/ImportedData/ImportedMCData/20220824_PICO_MC257_RUN86_TargetDataMetaFilter.Rds"
 
@@
 
-# ProcessData <- ProcessData %>%
-#   filter(Strain == "SS120" & time >= InitialTime |
-#          Strain == "MIT9313" |
-#          Strain =="MED4"  )
+ProcessData <- ProcessData %>%
+  filter(Strain == "SS120" & time >= InitialTime |
+         Strain == "MIT9313" |
+         Strain =="MED4"  )
 

### 2024-01-23 Code/ManuscriptPURFits.Rmd
Fixed .Rmd to run - needs more edits

@@
 
-# MyWavelengths = c(450, 530, 660, "WW")
-# MCMIXColours = c(w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "black")
 library(photobiology)
@@
 MyWavelengths = c("WW", 660, 530, 450)
-# MCMIXColours = c("black", w_length2rgb(660), w_length2rgb(530),  w_length2rgb(450))
-MCMIXColours = c("black", "orange", w_length2rgb(530),  w_length2rgb(450))
+MCMIXColours = c("black", w_length2rgb(660), w_length2rgb(530),  w_length2rgb(450))
 
@@
   ) %>%
-  mutate(ID = "DummySS120")
+  mutate(SampleID = "DummySS120")
 
@@
   ) %>%
-  mutate(ID = "DummyMIT9313")
+  mutate(SampleID = "DummyMIT9313")
 
@@
   ) %>%
-  mutate(ID = "DummyMED4")
+  mutate(SampleID = "DummyMED4")
 
@@
 
+# Join dummy df to growth df
 ```{r add dummy dark growth to DF}
@@
 
-```{r test MED4 issues}
-# PURPARFits |>
-#   filter(Strain == "MED4",
-#          O2_uM == 250) |>
-#   select(c(ReplicateMean_deltaOD_Lmu_corr_day,  OrgPur_day))
-```
-
-```{r set colours}
-
-# MyWavelengths = c(450, 530, 660, "WW")
-# MCMIXColours = c(w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "black")
-# 
-# MyWavelengths = c("WW", 660, 530, 450)
-# MCMIXColours = c("black", w_length2rgb(660), w_length2rgb(530),  w_length2rgb(450))
-# 
-# names(MCMIXColours) <- MyWavelengths
-# MCMIXColours
-# 
-# 
-# 
-# 
-# ColoursStrain = c(MIT9313 = "#E69F00", SS120 = "#F0E442", MED4 = "#CC79A7" )
-# 
-# MyOxygen = c(2.5, 25, 250 )
-# # ColourOxygen = c("#99CCFF", "dodgerblue", "blue1")
-# ColourOxygen = c("#FFCC00", "#FF9900", "#663300")
-# names(ColourOxygen) <- MyOxygen
-# ColourOxygen
-# 
-# MyOxygen = c(2.5, 25, 250 )
-# LineTypeOxygen = c("dotted", "longdash", "solid")
-# names(LineTypeOxygen) <- MyOxygen
-# LineTypeOxygen
-# 
-# MyPhotoperiods = as.factor(c(4, 8, 12, 16))
-# ColoursPhotoperiod = c("gray88", "lightcyan3", "gray47", "gray8")
-# names(ColoursPhotoperiod) <- MyPhotoperiods
-# ColoursPhotoperiod
-
-```
-
-```{r set shapes}
-
-# MyPhotoperiods = as.factor(c(4, 8, 12, 16))
-# PhotoperiodShapes = c(6, 18, 1, 17)
-# 
-# 
-# names(PhotoperiodShapes) <- MyPhotoperiods
-# PhotoperiodShapes
-# 
-# O2Shapes <- c(13, 1, 19)
-
-```
-
-Set Strip colors for WL x_strip is for WL facetted by columns and y_strip is for WL faceted by rows
-```{r}
-# x_strip <- strip_themed(background_x = elem_list_rect(fill = MCMIXColours, alpha = 0.8),
-#                       background_y = elem_list_rect(fill = "grey27")) 
-# 
-# x_stripWW <- strip_themed(background_x = elem_list_rect(fill = "black"),
-#                       background_y = elem_list_rect(fill = "#grey27"))
-# 
-# x_strip660 <- strip_themed(background_x = elem_list_rect(fill = "#730000"),
-#                       background_y = elem_list_rect(fill = "#grey27"))
-# 
-# x_strip530 <- strip_themed(background_x = elem_list_rect(fill = "#00FF00"),
-#                       background_y = elem_list_rect(fill = "#grey27"))
-# 
-# x_strip450 <- strip_themed(background_x = elem_list_rect(fill = "#0600FF"),
-#                       background_y = elem_list_rect(fill = "#grey27"))
-# 
-# y_strip <- strip_themed(background_y = elem_list_rect(fill = MCMIXColours),
-#                       background_x = elem_list_rect(fill = "#grey27")) 
-# 
-# y_stripWW <- strip_themed(background_y = elem_list_rect(fill = "black"),
-#                       background_x = elem_list_rect(fill = "#grey27"))
-# 
-# y_strip660 <- strip_themed(background_y = elem_list_rect(fill = "#730000"),
-#                       background_x = elem_list_rect(fill = "#grey27"))
-# 
-# y_strip530 <- strip_themed(background_y = elem_list_rect(fill = "#00FF00"),
-#                       background_x = elem_list_rect(fill = "#grey27"))
-# 
-# y_strip450 <- strip_themed(background_y = elem_list_rect(fill = "#0600FF"),
-#                       background_x = elem_list_rect(fill = "#grey27"))
-
-```
-
 Citations: Ma X, Liu Q, Zhang Z, Zhang Z, Zhou Z, Jiang Y, et al.
@@
 plot(x = TestI, y = grcplatt(I = TestI, a = 0.1, b = 0.1, Pmax = 1))
-
-# mm <- function(I, KM, Pmax){(Pmax* I)/(KM + I)}
-# 
-# plot(x = TestI, y = mm(I = TestI, KM = 10, Pmax = 1))
-
-# mmsubi <- function(I, KM, Pmax, Ki){(Pmax* I)/(KM + (I * (1 + I/Ki)))}
-# 
-# plot(x = TestI, y = mmsubi(I = TestI, KM = 10, Pmax = 1, Ki = 1))
 
@@
 # model with dummy dark, 0 PAR,  growth rates.
-Also removed data if no growth occurred under an O2 and photoperiod condition so that the model would not be skewed towards zero.
+Also removed data if no growth occurred for an O2 and photoperiod combination so that the model including all photoperiods would not be skewed towards zero.
 As per Amanda and Doug's advice, filtered out PUR d-1 above 1.5e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
@@
   nest(data = -c("Strain","O2_uM")) |>
-  # mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
-  #                             data = .x,
-  #                             start = list(a = 1e-6,
-  #                                          Pmax = 1),
-  #                             lower = c(0, 0),
-  #                             upper = c(1,100)
-  #                        ), NULL)
-  #                        )
-  #        ) |>
-  # mutate(GRC_Param = map(GRC_Model, tidy),
-  #        GRC_Predict = map(GRC_Model, possibly(augment), NULL),
-  #        GRC_Glance = map(GRC_Model, possibly(glance))) |>
   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
@@
                               lower = c(0, 0, 0),
-                              upper = c(1,1,100)
-                         ), 0)
+                              upper = c(1,1,100),
+                              control = list(maxiter = 500)
+                         ), NULL)
                          )
@@
 
-# PURPARStrainO2NestDummy_TEST <- PURPARFits_dummy |>
-#   nest(data = -c("Strain","O2_uM")) |>
-# mutate(GRC_Model_Photoperiod = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day * Photoperiod ~ grc(I = PURPhotonDose_day, a, Pmax),
-#                             data = .x,
-#                             start = list(a = 1e-6,
-#                                          Pmax = 1),
-#                             lower = c(0, 0),
-#                             upper = c(1,100)
-#                        ), NULL)
-#                        )
-#        ) |>
-# mutate(GRC_Param_Photoperiod = map(GRC_Model_Photoperiod, tidy),
-#        GRC_Predict_Photoperiod = map(GRC_Model_Photoperiod, possibly(augment), NULL),
-#        GRC_Glance_Photoperiod = map(GRC_Model_Photoperiod, possibly(glance))) |>
-#   mutate(GRCplatt_Model_Photoperiod = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day * Photoperiod ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
-#                               data = .x,
-#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1),
-#                               lower = c(0, 0, 0),
-#                               upper = c(1,1,100)
-#                          ), NULL)
-#                          )
-#          ) |>
-#   mutate(GRCplatt_Param_Photoperiod = map(GRCplatt_Model_Photoperiod, tidy),
-#          GRCplatt_Predict_Photoperiod = map(GRCplatt_Model_Photoperiod, possibly(augment)),
-#          GRCplatt_Glance_Photoperiod = map(GRCplatt_Model_Photoperiod, possibly(glance))
-#          ) %>%
-#     mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
-#                               data = .x,
-#                               start = list(a = 1e-6,
-#                                            Pmax = 1),
-#                               lower = c(0, 0),
-#                               upper = c(1,100)
-#                          ), NULL)
-#                          )
-#          ) |>
-#   mutate(GRC_Param = map(GRC_Model, tidy),
-#          GRC_Predict = map(GRC_Model, possibly(augment), NULL),
-#          GRC_Glance = map(GRC_Model, possibly(glance))) |>
-#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
-#                               data = .x,
-#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1),
-#                               lower = c(0, 0, 0),
-#                               upper = c(1,1,100)
-#                          ), NULL)
-#                          )
-#          ) |>
-#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
-#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
-#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
-#          )
-# 
-# PURPARStrainO2NestDummy_TEST
-
-# PURPARStrainO2PhotoperiodNest <- PURPARFits |>
-#   nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
-#   mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
-#                               data = .x,
-#                               start = list(a = 1e-6,
-#                                            Pmax = 1),
-#                               lower = c(0, 0),
-#                               upper = c(1,100)
-#                          ), NULL)
-#                          )
-#          ) |>
-#   mutate(GRC_Param = map(GRC_Model, possibly(tidy)),
-#          GRC_Predict = map(GRC_Model, possibly(augment), NULL),
-#          GRC_Glance = map(GRC_Model, possibly(glance))) |>
-#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
-#                               data = .x,
-#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1),
-#                               lower = c(0, 0, 0),
-#                               upper = c(1,1,100)
-#                          ), NULL)
-#                          )
-#          ) |>
-#   mutate(GRCplatt_Param = map(GRCplatt_Model, possibly(tidy)),
-#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
-#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
-#          )
-
 # model with dummy dark, 0 PAR, 0 growth rates
@@
 PURPARStrainO2PhotoperiodNestDummy <- PURPARFits_dummy |>
-   filter(ID != "MiSa1456") %>% 
-   # filter(ID != "JuNa1068") %>% 
+   filter(SampleID != "MiSa1456") %>% 
+   # filter(SampleID != "JuNa1068") %>% 
  nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
-  # mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
-  #                             data = .x,
-  #                             start = list(a = 1e-6,
-  #                                          Pmax = 1),
-  #                             lower = c(0, 0),
-  #                             upper = c(1,100)
-  #                        ), NULL)
-  #                        )
-  #        ) |>
-  # mutate(GRC_Param = map(GRC_Model, tidy),
-  #        GRC_Predict = map(GRC_Model, possibly(augment), NULL),
-  #        GRC_Glance = map(GRC_Model, possibly(glance))) |>
   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
@@
                               lower = c(-0, 0, 0),
-                              upper = c(1,1,100)
+                              upper = c(1,1,100),
+                              control = list(maxiter = 500)
                          ), NULL)
@@
   nest(data = -c("Strain","O2_uM", "WL")) |>
-  # mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
-  #                             data = .x,
-  #                             start = list(a = 1e-6,
-  #                                          Pmax = 1),
-  #                             lower = c(0, 0),
-  #                             upper = c(1,100)
-  #                        ), 0)
-  #                        )
-  #        ) |>
-  # mutate(GRC_Param = map(GRC_Model, tidy),
-  #        GRC_Predict = map(GRC_Model, possibly(augment), NULL),
-  #        GRC_Glance = map(GRC_Model, possibly(glance))) |>
   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
@@
   nest(data = -c("Strain","O2_uM", "Photoperiod", "WL")) |>
-  # mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PURPhotonDose_day, a, Pmax),
-  #                             data = .x,
-  #                             start = list(a = 1e-6,
-  #                                          Pmax = 1),
-  #                             lower = c(0, 0),
-  #                             upper = c(1,100)
-  #                        ), 0)
-  #                        )
-  #        ) |>
-  # mutate(GRC_Param = map(GRC_Model, tidy),
-  #        GRC_Predict = map(GRC_Model, possibly(augment), NULL),
-  #        GRC_Glance = map(GRC_Model, possibly(glance), )) |>
   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
@@
   pivot_wider(names_from = Output, values_from = value) |>
-   # filter(!map_lgl(Model, is.null)) |>
+  filter(!map_lgl(Model, is.null)) |>
   filter(!map_lgl(Glance, is.null)) |>
@@
   pivot_wider(names_from = Output, values_from = value) |>
-   # filter(!map_lgl(Model, is.null)) |>
+    filter(!map_lgl(Model, is.null)) |>
   filter(!map_lgl(Glance, is.null)) |>

### 2024-01-29 Code/ManuscriptPURFits.Rmd
Simplify code , removed redundant variables

@@
 
-Make O2_uM and WL as factor levels from highest to lowest
+Make O2_uM and WL as factor levels from highest to lowest and remove all green light (WL= 530) growth data
 ```{r O2 levels}
@@
 PURPARFits <- PURPARFits %>%
+  filter(WL %in% c("WW", 660, 450)) %>% 
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         WL= factor(WL, levels = c("WW", 660, 530, 450)),
+         WL= factor(WL, levels = c("WW", 660, 450)),
         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" )))
@@
 Dummy_O2_uM <- c(2.5, 25.0, 250.0)
-Dummy_WL <- c(450, 530, 660, "WW")
+Dummy_WL <- c(450, 660, "WW")
 Dummy_deltaOD_Lmu_corr <- c(0)
@@
 
-# PURPARFits_dummy <- PURPARFits_dummy %>% 
-#   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-#          WL= factor(WL, levels = c("WW", 660, 530, 450)),
-#         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" )))
+remove(DummyDF_Expand)
 
@@
   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
-    scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660","530", "450" )) +
+    scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
   facet_grid(rows = vars(Par_ue), cols = vars(Strain)) +
@@
 As per Amanda and Doug's advice, filtered out PUR d-1 above 1.5e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
-PURPARStrainO2NestDummy_filtered <- PURPARFits_dummy |>
+PURPARStrainO2NestModels_filtered <- PURPARFits_dummy |>
   mutate(remove = case_when(Strain == "MED4" & Photoperiod == 4 ~ 1,
@@
 
-PURPARStrainO2NestDummy <- PURPARFits_dummy |>
+# PURPARStrainO2NestModels <- PURPARFits_dummy |>
+#   nest(data = -c("Strain","O2_uM")) |>
+#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
+#                               data = .x,
+#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
+#                               lower = c(0, 0, 0),
+#                               upper = c(1,1,100),
+#                               control = list(maxiter = 500)
+#                          ), NULL)
+#                          )
+#          ) |>
+#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
+#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
+#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
+#          ) |>
+#   mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
+#                               data = .x,
+#                               start = LinEqnStart
+#                          ), NULL)
+#                          )
+#          ) |>
+#   mutate(GRClm_Param = map(GRClm_Model, tidy),
+#          GRClm_Predict = map(GRClm_Model, possibly(augment)),
+#          GRClm_Glance = map(GRClm_Model, possibly(glance))
+#          )
+
+# # model with dummy dark, 0 PAR, 0 growth rates
+# PURPARStrainO2PhotoNestModels <- PURPARFits_dummy  |>
+#  nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
+#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
+#                               data = .x,
+#                               start = list(a = 1e-8, b = 1e-9, Pmax = 1),
+#                               lower = c(-0, 0, 0),
+#                               upper = c(1,1,100),
+#                               control = list(maxiter = 500)
+#                          ), NULL)
+#                          )
+#          ) |>
+#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
+#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
+#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
+#          ) |>
+#   mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
+#                               data = .x,
+#                               start = LinEqnStart
+#                          ), NULL)
+#                          )
+#          ) |>
+#   mutate(GRClm_Param = map(GRClm_Model, tidy),
+#          GRClm_Predict = map(GRClm_Model, possibly(augment)),
+#          GRClm_Glance = map(GRClm_Model, possibly(glance))
+#          )
+
+PURPARStrainO2PhotoNestModels_filtered <- PURPARFits_dummy |>
+   filter(PURPhotonDose_day <= 1.5e+06) |>
+ nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
+  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
+                              data = .x,
+                              start = list(a = 1e-8, b = 1e-9, Pmax = 1),
+                              lower = c(-0, 0, 0),
+                              upper = c(1,1,100),
+                              control = list(maxiter = 500)
+                         ), NULL)
+                         )
+         ) |>
+  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
+         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
+         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
+         ) |>
+  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
+                              data = .x,
+                              start = LinEqnStart
+                         ), NULL)
+                         )
+         ) |>
+  mutate(GRClm_Param = map(GRClm_Model, tidy),
+         GRClm_Predict = map(GRClm_Model, possibly(augment)),
+         GRClm_Glance = map(GRClm_Model, possibly(glance))
+         )
+
+# # model with dummy dark, 0 PAR,  growth rates 
+# PURPARStrainO2WLNestModels <- PURPARFits_dummy |>
+#   nest(data = -c("Strain","O2_uM", "WL")) |>
+#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
+#                               data = .x,
+#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1),
+#                               lower = c(0, 0, 0),
+#                               upper = c(1,1,100),
+#                               control = list(maxiter = 500)
+#                          ), NULL)
+#                          )
+#          ) |>
+#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
+#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
+#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
+#          )|>
+#   mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
+#                               data = .x,
+#                               start = LinEqnStart
+#                          ), NULL)
+#                          )
+#          ) |>
+#   mutate(GRClm_Param = map(GRClm_Model, tidy),
+#          GRClm_Predict = map(GRClm_Model, possibly(augment)),
+#          GRClm_Glance = map(GRClm_Model, possibly(glance))
+#          )
+# 
+# 
+# # model with dummy dark, 0 PAR,  growth rates
+# PURPARStrainO2PeriodWLNest <- PURPARFits_dummy |>
+#   nest(data = -c("Strain","O2_uM", "Photoperiod", "WL")) |>
+#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
+#                               data = .x,
+#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1),
+#                               lower = c(0, 0, 0),
+#                               upper = c(1,1,100),
+#                               control = list(maxiter = 500)
+#                          ), NULL)
+#                          )
+#          ) |>
+#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
+#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
+#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
+#          )|>
+#   mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
+#                               data = .x,
+#                               start = LinEqnStart
+#                          ), NULL)
+#                          )
+#          ) |>
+#   mutate(GRClm_Param = map(GRClm_Model, tidy),
+#          GRClm_Predict = map(GRClm_Model, possibly(augment)),
+#          GRClm_Glance = map(GRClm_Model, possibly(glance))
+#          )
+
+```
+
+# Plot fits
+```{r growthPURplots, fig.height= 10, fig.width= 10}
+#ReplicateMean_
+
+# PURPARStrainWLNest |>
+#   #filter(!is.null(GRC_Model)) |>
+#   filter(!map_lgl(GRC_Model, is.null)) |>  
+#   unnest(GRC_Predict, data) |>
+#   ggplot() +
+#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
+#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
+#   facet_grid(rows = vars(WL), cols = vars(Strain)) + 
+#   theme_bw()
+
+# PURPARStrainO2Nest |>
+#   filter(!map_lgl(GRC_Model, is.null)) |> #https://stackoverflow.com/questions/57336319/how-to-filter-out-null-elements-of-tibbles-list-column 
+#   unnest(GRC_Predict, data) |>
+#   ggplot() +
+#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
+#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
+#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
+#     labs(title = "PURPARStrainO2Nest GRC") +
+#   theme_bw()
+
+# PURPARStrainO2NestModels |>
+#   filter(!map_lgl(GRC_Model, is.null)) |> #https://stackoverflow.com/questions/57336319/how-to-filter-out-null-elements-of-tibbles-list-column 
+#   unnest(GRC_Predict, data) |>
+#   ggplot() +
+#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
+#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
+#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
+#     labs(title = "PURPARStrainO2NestModels GRC") +
+#   theme_bw()
+
+# PURPARStrainO2Nest |>
+#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
+#   unnest(GRCplatt_Predict, data) |>
+#   ggplot() +
+#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
+#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
+#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
+#     labs(title = "PURPARStrainO2Nest Platt") +
+#   theme_bw()
+#
+
+# PURPARStrainO2NestModels |>
+#   filter(!map_lgl(GRCplatt_Model, is.null)) |> # only include fits that did not fail
+#   unnest(GRCplatt_Predict, data) |>
+#    mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+#          Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
+#          Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
+#   ggplot() +
+#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
+#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
+#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
+#   labs(title = "PURPARStrainO2NestModels Platt") +
+#   theme_bw()
+
+PURPARStrainO2NestModels_filtered|>
+  filter(!map_lgl(GRCplatt_Model, is.null)) |>
+  unnest(GRCplatt_Predict, data) |>
+   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
+         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
+  ggplot() +
+  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
+  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
+  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
+  labs(title = "PURPARStrainO2NestModels_filtered Platt") +
+  theme_bw()
+
+# PURPARStrainO2PhotoNestModels |>
+#   filter(!map_lgl(GRC_Model, is.null)) |>
+#   unnest(GRC_Predict, data) |>
+#   ggplot() +
+#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
+#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
+#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
+#     labs(title = "PURPARStrainO2PhotoNestModels GRC") +
+#   theme_bw()
+
+# PURPARStrainO2PhotoNestModels |>
+#    filter(!map_lgl(GRC_Model, is.null)) |>
+#   unnest(GRC_Predict, data) |>
+#   ggplot() +
+#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
+#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
+#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
+#     labs(title = "PURPARStrainO2PhotoNestModels GRC") +
+#   theme_bw()
+
+# PURPARStrainO2PhotoNestModels |>
+#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
+#   unnest(GRCplatt_Predict, data) |>
+#   ggplot() +
+#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
+#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
+#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
+#     labs(title = "PURPARStrainO2PhotoNestModels Platt") +
+#   theme_bw()
+
+PURPARStrainO2PhotoNestModels_filtered |>
+  filter(!map_lgl(GRCplatt_Model, is.null)) |>
+  unnest(GRCplatt_Predict, data) |>
+   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
+         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
+  ggplot() +
+  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
+  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +   
+  scale_colour_manual(values = MCMIXColours) +
+  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
+    labs(title = "PURPARStrainO2PhotoNestModels_filtered Platt") +
+  theme_bw()
+
+PURPARStrainO2PhotoNestModels_filtered |>
+  filter(!map_lgl(GRClm_Model, is.null)) |>
+  unnest(GRClm_Predict, data) |>
+   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
+         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
+  ggplot() +
+  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
+  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
+   scale_colour_manual(values = MCMIXColours) +
+  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
+    labs(title = "PURPARStrainO2PhotoNestModels_filtered Linear Model") +
+  theme_bw()
+
+PURPARFits_dummy |>
+  # unnest(data) |>
+   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
+         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
+  ggplot() +
+  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
+  # geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
+     scale_colour_manual(values = MCMIXColours) +
+    facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
+    labs(title = "PURPARStrainO2PhotoNestModels all data no filter") +
+  theme_bw()
+
+# PURPARStrainO2WLNestModels |>
+#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
+#   unnest(GRCplatt_Predict, data) |>
+#    mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+#          Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
+#          Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
+#   ggplot() +
+#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) +
+#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
+#   facet_grid(rows = vars(O2_uM, WL), cols = vars(Strain)) +
+#     labs(title = "PURPARStrainO2WLNestModels Platt") +
+#   theme_bw()
+
+# PURPARStrainO2PeriodWLNest |>
+#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
+#   unnest(GRCplatt_Predict, data) |>
+#   ggplot() +
+#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
+#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
+#   facet_grid(rows = vars(O2_uM, Photoperiod, WL), cols = vars(Strain)) +
+#     labs(title = "PURPARStrainO2PeriodWLNest Platt") +
+#   theme_bw()
+
+```
+
+nlsLM generates AIC accessed with broom::glance
+Choose best model between platt and lm based on lowest GIC 
+```{r aic comparisons}
+#https://www.scribbr.com/statistics/akaike-information-criterion/
+
+#need to remove 'null' models to facilitate conversion of AIC from 'list' derived from 'Glance' column, to dbl
+# PURPARStrainO2BestModels <- PURPARStrainO2Nest|>
+#   select(-c(data)) |>
+#   pivot_longer(cols = -c(Strain, O2_uM)) |>
+#   drop_na(value) |>
+#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
+#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
+#   pivot_wider(names_from = Output, values_from = value) |>
+#   filter(!map_lgl(Model, is.null)) |>
+#   filter(!map_lgl(Glance, is.null)) |>
+#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
+#   group_by(Strain, O2_uM) |>
+#   filter(AIC == min(AIC)) |>
+#   ungroup() |>
+#   select(-c(Model, Glance)) |>
+#   unnest(Param) |>
+#   select(-c(statistic)) |>
+#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
+#  
+# PURPARStrainO2BestModels
+
+# PURPARStrainO2BestModels <- PURPARStrainO2NestModels|>
+#   # select(-c(data)) |>
+#   pivot_longer(cols = -c(Strain, O2_uM, data)) |>
+#   drop_na(value) |>
+#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
+#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
+#   pivot_wider(names_from = Output, values_from = value) |>
+#   filter(!map_lgl(Model, is.null)) |>
+#   filter(!map_lgl(Glance, is.null)) |>
+#   mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
+#   group_by(Strain, O2_uM) |>
+#   filter(AIC == min(AIC)) |>
+#   ungroup() |>
+#   select(-c(Model, Glance)) |>
+#   unnest(Param) |>
+#   select(-c(statistic)) |>
+#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
+#  
+# PURPARStrainO2BestModels
+
+# PURPARStrainO2BestModels_filtered <- PURPARStrainO2NestModels_filtered|>
+#   # select(-c(data)) |>
+#   pivot_longer(cols = -c(Strain, O2_uM, data)) |>
+#   drop_na(value) |>
+#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
+#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
+#   pivot_wider(names_from = Output, values_from = value) |>
+#     filter(!map_lgl(Model, is.null)) |>
+#   filter(!map_lgl(Glance, is.null)) |>
+#   mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
+#   group_by(Strain, O2_uM) |>
+#   filter(AIC == min(AIC)) |>
+#   ungroup() |>
+#   select(-c(Model, Glance)) |>
+#   unnest(Param) |>
+#   select(-c(statistic)) |>
+#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
+#  
+# PURPARStrainO2BestModels_filtered
+# 
+# PURPARStrainO2PhotoBestModels_filtered <- PURPARStrainO2PhotoNestModels_filtered|>
+#   # select(-c(data)) |>
+#   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
+#   drop_na(value) |>
+#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
+#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
+#   pivot_wider(names_from = Output, values_from = value) |>
+#   filter(!map_lgl(Model, is.null)) |>
+#   filter(!map_lgl(Glance, is.null)) |>
+#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
+#   group_by(Strain, O2_uM, Photoperiod) |>
+#   filter(AIC == min(AIC)) |>
+#   ungroup() |>
+#   select(-c(Model, Glance)) |>
+#   unnest(Param) |>
+#   select(-c(statistic)) |>
+#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
+# 
+# PURPARStrainO2PhotoBestModels_filtered
+
+# PURPARStrainO2PhotoBestModels <- PURPARStrainO2PhotoNestModels|>
+#   # select(-c(data)) |>
+#   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
+#   drop_na(value) |>
+#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
+#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
+#   pivot_wider(names_from = Output, values_from = value) |>
+#   filter(!map_lgl(Model, is.null)) |>
+#   filter(!map_lgl(Glance, is.null)) |>
+#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
+#   group_by(Strain, O2_uM, Photoperiod) |>
+#   filter(AIC == min(AIC)) |>
+#   ungroup() |>
+#   select(-c(Model, Glance)) |>
+#   unnest(Param) |>
+#   select(-c(statistic)) |>
+#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
+#  
+# PURPARStrainO2PhotoBestModels
+
+# PURPARStrainO2WLBestModels <- PURPARStrainO2WLNestModels|>
+#   # select(-c(data)) |>
+#   pivot_longer(cols = -c(Strain, O2_uM, WL, data)) |>
+#   drop_na(value) |>
+#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
+#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
+#   pivot_wider(names_from = Output, values_from = value) |>
+#  filter(!map_lgl(Model, is.null)) |>
+#   filter(!map_lgl(Glance, is.null)) |>
+#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
+#   group_by(Strain, O2_uM, WL) |>
+#   filter(AIC == min(AIC)) |>
+#   ungroup() |>
+#   select(-c(Model, Glance)) |>
+#   unnest(Param) |>
+#   select(-c(statistic)) |>
+#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
+#  
+# PURPARStrainO2WLBestModels
+
+# PURPARStrainO2PhotoWLBestModels <- PURPARStrainO2PhotoNestModels|>
+#   select(-c(data)) |>
+#   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, WL)) |>
+#   drop_na(value) |>
+#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
+#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
+#   pivot_wider(names_from = Output, values_from = value) |>
+#   filter(!map_lgl(Model, is.null)) |>
+#   filter(!map_lgl(Param, is.null)) |>
+#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
+#   group_by(Strain, O2_uM, Photoperiod) |>
+#   filter(AIC == min(AIC)) |>
+#   ungroup() |>
+#   select(-c(Model, Glance)) |>
+#   unnest(Param) |>
+#   select(-c(statistic)) |>
+#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
+#  
+# PURPARStrainO2PhotoWLBestModels
+
+# mutate(Pmax_Ye = if_else(ModelType == "GRCbeta", estimate_a * ((sqrt(estimate_b + estimate_g) - sqrt(estimate_b))/estimate_g)^2, NA))
+
+```
+
+Want platt model for all fits that did not fail and lm for platt models that returned a NULL
+```{r}
+
+#filter to keep platt models
+KeepPlattModel <- PURPARStrainO2PhotoNestModels_filtered|>
+  select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
+   filter(!map_lgl(GRCplatt_Model, is.null))
+
+#filter to keep only the models that failed to fit a platt model, fits by lm remains. 
+KeepLmModel <- PURPARStrainO2PhotoNestModels_filtered|>
+  filter(map_lgl(GRCplatt_Model, is.null)) |>
+ select(-c(GRCplatt_Glance, GRCplatt_Model, GRCplatt_Param, GRCplatt_Predict))
+
+# Join  
+StrainO2Photoperiod_AllModels <- full_join(KeepPlattModel, KeepLmModel)
+
+ remove(KeepPlattModel)
+ remove(KeepLmModel)
+
+ StrainO2Photofiltered_PlattLmModel <- StrainO2Photoperiod_AllModels |>
+   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
+  drop_na(value) |>
+  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param") | str_detect(name, pattern = "Predict")) |>
+  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
+  pivot_wider(names_from = Output, values_from = value) |>
+filter(!map_lgl(Model, is.null)) |>
+  filter(!map_lgl(Glance, is.null)) |>
+  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
+  group_by(Strain, O2_uM, Photoperiod) |>
+  filter(AIC == min(AIC)) |>
+  ungroup() |>
+  select(-c(Glance)) |>
+  unnest(Param) |>
+  select(-c(statistic)) |>
+  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
+
+ #filter to keep platt models
+KeepPlattModel <- PURPARStrainO2NestModels_filtered|>
+  select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
+   filter(!map_lgl(GRCplatt_Model, is.null))
+
+#filter to keep only the models that failed to fit a platt model, fits by lm remains. 
+KeepLmModel <- PURPARStrainO2NestModels_filtered|>
+  filter(map_lgl(GRCplatt_Model, is.null)) |>
+ select(-c(GRCplatt_Glance, GRCplatt_Model, GRCplatt_Param, GRCplatt_Predict))
+
+# Join  
+StrainO2_AllModels <- full_join(KeepPlattModel, KeepLmModel)
+
+ StrainO2filtered_PlattLmModel <- StrainO2_AllModels|>
+  # select(-c(data)) |>
+  pivot_longer(cols = -c(Strain, O2_uM, data)) |>
+  drop_na(value) |>
+  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param") | str_detect(name, pattern = "Predict")) |>
+  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
+  pivot_wider(names_from = Output, values_from = value) |>
+  filter(!map_lgl(Model, is.null)) |>
+  filter(!map_lgl(Glance, is.null)) |>
+  mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
+  group_by(Strain, O2_uM) |>
+  filter(AIC == min(AIC)) |>
+  ungroup() |>
+  select(-c(Glance))|>
+  unnest(Param) |>
+  select(-c(statistic)) |>
+  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
+
+ remove(KeepPlattModel)
+ remove(KeepLmModel)
+ # remove(PURPARStrainO2NestModels_filtered)
+ # remove(PURPARStrainO2PhotoNestModels_filtered)
+
+```
+
+Linear models do not have alpha, beta and pmax so inf and NA are generated. Change them to 0.
+```{r lm platt parameters set to zero}
+
+StrainO2filtered_PlattLmModel <- StrainO2filtered_PlattLmModel|>
+  mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
+         estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
+         estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
+         AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC))
+
+StrainO2filtered_PlattLmModel
+
+# PURPARStrainO2WLBestModels <- PURPARStrainO2WLBestModels|>
+#   mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
+#          estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
+#          estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
+#          AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC)) 
+#  
+# PURPARStrainO2WLBestModels
+
+StrainO2Photofiltered_PlattLmModel <- StrainO2Photofiltered_PlattLmModel|>
+  mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
+         estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
+         estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
+         AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC))
+
+StrainO2Photofiltered_PlattLmModel
+
+```
+
+```{r plot models}
+
+StrainO2filtered_PlattLmModel |>
+  unnest(Predict, data) |>
+  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         WL= factor(WL, levels = c("WW", 660, 450)),
+         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
+         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4"))) |>
+  ggplot() +
+  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL))) +
+  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
+   geom_text(aes(x = 500000, y = 0.75, label = paste(ModelType), show.legend = FALSE)
+  ) +
+     scale_colour_manual(values = MCMIXColours) +
+   scale_shape_manual(values = PhotoperiodShapes)  +
+  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
+    labs(title = "Single fit for each [O2]- all photoperiods included that had growth") +
+  theme_bw()
+
+StrainO2Photofiltered_PlattLmModel |>
+  unnest(Predict, data) |>
+
+  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
+         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
+  ggplot() +
+  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
+  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
+   geom_text(aes(x = 500000, y = 0.75, label = paste(ModelType), show.legend = FALSE)
+  ) +
+     scale_colour_manual(values = MCMIXColours) +
+  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
+    labs(title = "Fits to be used for ANOVA comparison to single fit in each [O2]") +
+  theme_bw()
+
+```
+
+```{r compare 1 fit of all photoperiod to each photoperiods using platt or lm}
+
+# make wider to join with DF that contains the 1 fit through all photoperiods
+Wider_Photoperiods <- StrainO2Photofiltered_PlattLmModel %>% 
+  select(Strain, Photoperiod, O2_uM, Model) %>% 
+  pivot_wider(names_from = Photoperiod, values_from = Model)
+
+# this contains 1 fit through all photoperiods, the photoperiods with no growth were filtered out.
+AllPhotoperiods <- StrainO2filtered_PlattLmModel %>% 
+  select(Strain, O2_uM, Model) %>% 
+ rename(All = 'Model')
+
+CombinePhotoperiods <- left_join(Wider_Photoperiods, AllPhotoperiods)
+
+ANOVA_AllPhotoperiods <- CombinePhotoperiods %>% 
+  mutate(twelve = `12`,
+         four = `4`,
+         eight = `8`,
+         sixteen = `16`) %>%
+  mutate(fourvsAll = map(map2(four, All, possibly(anova, otherwise = NULL)), tidy),
+         eightvsAll = map(map2(eight, All, possibly(anova, otherwise = NULL)), tidy),
+         twelvevsAll = map(map2(twelve, All, possibly(anova, otherwise = NULL)), tidy),
+         sixteenvsAll = map(map2(sixteen, All, possibly(anova, otherwise = NULL)), tidy)) %>% 
+  select(Strain, O2_uM, fourvsAll, eightvsAll, twelvevsAll, sixteenvsAll) %>% 
+  pivot_longer(cols = c(fourvsAll, eightvsAll, twelvevsAll, sixteenvsAll)) %>% 
+  unnest(value, keep_empty = TRUE) %>% 
+  filter(is.na(term) & is.na(p.value) |
+           !is.na(term) & !is.na(p.value)) %>%
+  select(Strain, O2_uM, name, p.value) %>% 
+  separate(name, into = c("Photoperiod1", "AllPhotoperiod"), sep = "vs")
+
+# %>% 
+#   mutate(p.value = case_when(is.na(p.value) ~ 0,
+#                              TRUE ~ p.value)) # Changed all failed fits to p.value = 0
+  # mutate(pval = pluck(value, "p.value", 2))
+
+ANOVA_AllPhotoperiods %>% 
+  mutate(Photoperiod1 = as.numeric(case_when(Photoperiod1 == 'four' ~ 4,
+                                  Photoperiod1 == 'eight' ~ 8,
+                                  Photoperiod1 == 'twelve' ~ 12,
+                                  Photoperiod1 == 'sixteen' ~ 16)),
+         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
+    # mutate(Photoperiod1 = factor(Photoperiod1, levels = c('four','eight', 'twelve', 'sixteen'))) %>% 
+  ggplot() +
+  geom_point(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(`p.value` < 0.05)) +
+  geom_text(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(`p.value` > 0.05), label = "ns") +
+  geom_text(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(is.na(`p.value`)), label = "NA") +
+  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
+  labs(title = "ANOVA compare all models",
+       caption = "NA = atleast one model did not fit due to lack of data points; 
+       ns = not significantly different from all photoperiod model (same); 
+       dot = significantly different from all photoperiod model")
+
+```
+# Remove the photoperiods from the model that are significantly different from the ANOVA run on the single fit against each individual photoperiod.   
+```{r}
+# model with dummy dark, 0 PAR,  growth rates.
+Also removed data if no growth occurred for an O2 and photoperiod combination so that the model including all photoperiods would not be skewed towards zero.
+As per Amanda and Doug's advice, filtered out PUR d-1 above 1.5e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
+PURPARStrainO2NestModels_filteredPhotoperiods <- PURPARFits_dummy |>
+  mutate(remove = case_when(Strain == "MED4" & Photoperiod == 4 ~ 1,
+                            Strain == "MED4" & O2_uM == 25 & Photoperiod == 8 & WL == "WW" ~ 1,
+                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 16 ~ 1,
+                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 12 & WL == "WW" ~ 1,
+                            Strain == "SS120"  & O2_uM == 2.5 & Photoperiod %in% c(16,8,4) ~ 1,
+                            Strain == "SS120"  & O2_uM == 25 & Photoperiod %in% c(16) & WL == 450 ~ 1,
+                            Strain == "SS120"  & O2_uM == 250 & Photoperiod %in% c(4) & WL == 450 ~ 1,
+                            TRUE ~ 0)) |>
+   filter(remove == 0,
+          PURPhotonDose_day <= 1.5e+06) |>
+  mutate(removephotoperiod =  case_when(Strain == "MED4" & Photoperiod == 4 ~ 1,
+                                        Strain == "MED4" & O2_uM == 250 & Photoperiod == 8 ~ 1,
+                                        Strain == "MED4" & O2_uM == 25 & Photoperiod == 16 ~ 1,
+                                        Strain == "MIT9313" & Photoperiod == 4 ~ 1,
+                                        Strain == "MIT9313" & O2_uM == 25 & Photoperiod %in% c(8,12) ~ 1,
+                                        Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod %in% c(12,16) ~ 1,
+                                        Strain == "SS120" & Photoperiod == 4 ~ 1,
+                                        Strain == "SS120"  & O2_uM == 250 & Photoperiod %in% c(8,12) ~ 1,
+                                        Strain == "SS120"  & O2_uM == 25 & Photoperiod %in% c(8) ~ 1,
+                                        Strain == "SS120"  & O2_uM == 2.5 & Photoperiod %in% c(8) ~ 1,
+                                        TRUE ~ 0))  |>
   nest(data = -c("Strain","O2_uM")) |>
@@
 
-# model with dummy dark, 0 PAR, 0 growth rates
-#Note: fit fails for SS120, 12h photoperiod and O2 = 25uM. Works if I remove outlier(WL = 660 and PAR = 30 or MiSa1456) 
-PURPARStrainO2PhotoperiodNestDummy <- PURPARFits_dummy |>
-   filter(SampleID != "MiSa1456") %>% 
-   # filter(SampleID != "JuNa1068") %>% 
- nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
-  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
-                              data = .x,
-                              start = list(a = 1e-8, b = 1e-9, Pmax = 1),
-                              lower = c(-0, 0, 0),
-                              upper = c(1,1,100),
-                              control = list(maxiter = 500)
-                         ), NULL)
-                         )
-         ) |>
-  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
-         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
-         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
-         ) |>
-  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
-                              data = .x,
-                              start = LinEqnStart
-                         ), NULL)
-                         )
-         ) |>
-  mutate(GRClm_Param = map(GRClm_Model, tidy),
-         GRClm_Predict = map(GRClm_Model, possibly(augment)),
-         GRClm_Glance = map(GRClm_Model, possibly(glance))
-         )
-
-# model with dummy dark, 0 PAR,  growth rates
-PURPARStrainO2WLNestDummy <- PURPARFits_dummy |>
-  nest(data = -c("Strain","O2_uM", "WL")) |>
-  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
-                              data = .x,
-                              start = list(a = 1e-7, b = 1e-8, Pmax = 1),
-                              lower = c(0, 0, 0),
-                              upper = c(1,1,100),
-                              control = list(maxiter = 500)
-                         ), NULL)
-                         )
-         ) |>
-  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
-         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
-         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
-         )|>
-  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
-                              data = .x,
-                              start = LinEqnStart
-                         ), NULL)
-                         )
-         ) |>
-  mutate(GRClm_Param = map(GRClm_Model, tidy),
-         GRClm_Predict = map(GRClm_Model, possibly(augment)),
-         GRClm_Glance = map(GRClm_Model, possibly(glance))
-         )
-
-# model with dummy dark, 0 PAR,  growth rates
-PURPARStrainO2PeriodWLNestDummy <- PURPARFits_dummy |>
-  nest(data = -c("Strain","O2_uM", "Photoperiod", "WL")) |>
-  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
-                              data = .x,
-                              start = list(a = 1e-7, b = 1e-8, Pmax = 1),
-                              lower = c(0, 0, 0),
-                              upper = c(1,1,100),
-                              control = list(maxiter = 500)
-                         ), NULL)
-                         )
-         ) |>
-  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
-         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
-         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
-         )|>
-  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
-                              data = .x,
-                              start = LinEqnStart
-                         ), NULL)
-                         )
-         ) |>
-  mutate(GRClm_Param = map(GRClm_Model, tidy),
-         GRClm_Predict = map(GRClm_Model, possibly(augment)),
-         GRClm_Glance = map(GRClm_Model, possibly(glance))
-         )
-
-```
-
-```{r growthPURplots, fig.height= 10, fig.width= 10}
-#ReplicateMean_
-
-# PURPARStrainWLNest |>
-#   #filter(!is.null(GRC_Model)) |>
-#   filter(!map_lgl(GRC_Model, is.null)) |>  
-#   unnest(GRC_Predict, data) |>
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
-#   facet_grid(rows = vars(WL), cols = vars(Strain)) + 
-#   theme_bw()
-
-# PURPARStrainO2Nest |>
-#   filter(!map_lgl(GRC_Model, is.null)) |> #https://stackoverflow.com/questions/57336319/how-to-filter-out-null-elements-of-tibbles-list-column 
-#   unnest(GRC_Predict, data) |>
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
-#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
-#     labs(title = "PURPARStrainO2Nest GRC") +
-#   theme_bw()
-
-# PURPARStrainO2NestDummy |>
-#   filter(!map_lgl(GRC_Model, is.null)) |> #https://stackoverflow.com/questions/57336319/how-to-filter-out-null-elements-of-tibbles-list-column 
-#   unnest(GRC_Predict, data) |>
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
-#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
-#     labs(title = "PURPARStrainO2NestDummy GRC") +
-#   theme_bw()
-
-# PURPARStrainO2Nest |>
-#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
-#   unnest(GRCplatt_Predict, data) |>
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
-#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
-#     labs(title = "PURPARStrainO2Nest Platt") +
-#   theme_bw()
-#
-
-PURPARStrainO2NestDummy |>
-  filter(!map_lgl(GRCplatt_Model, is.null)) |>
-  unnest(GRCplatt_Predict, data) |>
-   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
-         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
-  ggplot() +
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
-  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
-  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
-  labs(title = "PURPARStrainO2NestDummy Platt") +
-  theme_bw()
-
-PURPARStrainO2NestDummy_filtered|>
-  filter(!map_lgl(GRCplatt_Model, is.null)) |>
-  unnest(GRCplatt_Predict, data) |>
-   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
-         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
-  ggplot() +
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
-  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
-  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
-  labs(title = "PURPARStrainO2NestDummy_filtered Platt") +
-  theme_bw()
-
-# PURPARStrainO2PhotoperiodNest |>
-#   filter(!map_lgl(GRC_Model, is.null)) |>
-#   unnest(GRC_Predict, data) |>
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
-#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-#     labs(title = "PURPARStrainO2PhotoperiodNest GRC") +
-#   theme_bw()
-
-# PURPARStrainO2PhotoperiodNestDummy |>
-#    filter(!map_lgl(GRC_Model, is.null)) |>
-#   unnest(GRC_Predict, data) |>
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
-#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-#     labs(title = "PURPARStrainO2PhotoperiodNestDummy GRC") +
-#   theme_bw()
-
-# PURPARStrainO2PhotoperiodNest |>
-#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
-#   unnest(GRCplatt_Predict, data) |>
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
-#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-#     labs(title = "PURPARStrainO2PhotoperiodNest Platt") +
-#   theme_bw()
-
-PURPARStrainO2PhotoperiodNestDummy |>
-  filter(!map_lgl(GRCplatt_Model, is.null)) |>
-  unnest(GRCplatt_Predict, data) |>
-   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
-         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
-  ggplot() +
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
-  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +   
-  scale_colour_manual(values = MCMIXColours) +
-  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-    labs(title = "PURPARStrainO2PhotoperiodNestDummy Platt") +
-  theme_bw()
-
-PURPARStrainO2PhotoperiodNestDummy |>
-  filter(!map_lgl(GRClm_Model, is.null)) |>
-  unnest(GRClm_Predict, data) |>
-   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
-         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
-  ggplot() +
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
-  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
-   scale_colour_manual(values = MCMIXColours) +
-  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-    labs(title = "PURPARStrainO2PhotoperiodNestDummy Linear Model") +
-  theme_bw()
-
-PURPARStrainO2PhotoperiodNestDummy |>
-  unnest(data) |>
-   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
-         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
-  ggplot() +
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
-  # geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
-     scale_colour_manual(values = MCMIXColours) +
-    facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-    labs(title = "PURPARStrainO2PhotoperiodNestDummy all data no fits") +
-  theme_bw()
-
-PURPARStrainO2WLNestDummy |>
-  filter(!map_lgl(GRCplatt_Model, is.null)) |>
-  unnest(GRCplatt_Predict, data) |>
-   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
-         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
-  ggplot() +
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) +
-  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
-  facet_grid(rows = vars(O2_uM, WL), cols = vars(Strain)) +
-    labs(title = "PURPARStrainO2WLNestDummy Platt") +
-  theme_bw()
-
-# PURPARStrainO2PeriodWLNestDummy |>
-#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
-#   unnest(GRCplatt_Predict, data) |>
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
-#   facet_grid(rows = vars(O2_uM, Photoperiod, WL), cols = vars(Strain)) +
-#     labs(title = "PURPARStrainO2PeriodWLNestDummy Platt") +
-#   theme_bw()
-
-```
-
-nlsLM generates AIC accessed with broom::glance
-Choose best model between platt and lm based on lowest GIC 
-```{r aic comparisons}
-#https://www.scribbr.com/statistics/akaike-information-criterion/
-
-#need to remove 'null' models to facilitate conversion of AIC from 'list' derived from 'Glance' column, to dbl
-# PURPARStrainO2BestModels <- PURPARStrainO2Nest|>
-#   select(-c(data)) |>
-#   pivot_longer(cols = -c(Strain, O2_uM)) |>
-#   drop_na(value) |>
-#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
-#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-#   pivot_wider(names_from = Output, values_from = value) |>
-#   filter(!map_lgl(Model, is.null)) |>
-#   filter(!map_lgl(Glance, is.null)) |>
-#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
-#   group_by(Strain, O2_uM) |>
-#   filter(AIC == min(AIC)) |>
-#   ungroup() |>
-#   select(-c(Model, Glance)) |>
-#   unnest(Param) |>
-#   select(-c(statistic)) |>
-#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
-#  
-# PURPARStrainO2BestModels
-
-PURPARStrainO2BestModelsDummy <- PURPARStrainO2NestDummy|>
+```
+
+Want platt model for all fits that did not fail and lm for platt models that returned a NULL
+```{r}
+
+ #filter to keep platt models
+KeepPlattModel <- PURPARStrainO2NestModels_filteredPhotoperiods|>
+  select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
+   filter(!map_lgl(GRCplatt_Model, is.null))
+
+#filter to keep only the models that failed to fit a platt model, fits by lm remains. 
+KeepLmModel <- PURPARStrainO2NestModels_filteredPhotoperiods|>
+  filter(map_lgl(GRCplatt_Model, is.null)) |>
+ select(-c(GRCplatt_Glance, GRCplatt_Model, GRCplatt_Param, GRCplatt_Predict))
+
+# Join  
+StrainO2_AllModels <- full_join(KeepPlattModel, KeepLmModel)
+
+ StrainO2filteredPhotoperiod_PlattLmModel <- StrainO2_AllModels|>
   # select(-c(data)) |>
@@
   drop_na(value) |>
-  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
+  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param") | str_detect(name, pattern = "Predict")) |>
   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
@@
   ungroup() |>
-  select(-c(Model, Glance)) |>
+  select(-c(Glance))|>
   unnest(Param) |>
@@
 
-PURPARStrainO2BestModelsDummy
-
-PURPARStrainO2BestModelsDummy_filtered <- PURPARStrainO2NestDummy_filtered|>
-  # select(-c(data)) |>
-  pivot_longer(cols = -c(Strain, O2_uM, data)) |>
-  drop_na(value) |>
-  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
-  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-  pivot_wider(names_from = Output, values_from = value) |>
-    filter(!map_lgl(Model, is.null)) |>
-  filter(!map_lgl(Glance, is.null)) |>
-  mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
-  group_by(Strain, O2_uM) |>
-  filter(AIC == min(AIC)) |>
-  ungroup() |>
-  select(-c(Model, Glance)) |>
-  unnest(Param) |>
-  select(-c(statistic)) |>
-  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
-
-PURPARStrainO2BestModelsDummy_filtered
-
-PURPARStrainO2PhotoperiodBestModelsDummy <- PURPARStrainO2PhotoperiodNestDummy|>
-  # select(-c(data)) |>
-  pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
-  drop_na(value) |>
-  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
-  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-  pivot_wider(names_from = Output, values_from = value) |>
-  filter(!map_lgl(Model, is.null)) |>
-  filter(!map_lgl(Glance, is.null)) |>
-  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
-  group_by(Strain, O2_uM, Photoperiod) |>
-  filter(AIC == min(AIC)) |>
-  ungroup() |>
-  select(-c(Model, Glance)) |>
-  unnest(Param) |>
-  select(-c(statistic)) |>
-  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
-
-PURPARStrainO2PhotoperiodBestModelsDummy
-
-PURPARStrainO2WLBestModelsDummy <- PURPARStrainO2WLNestDummy|>
-  # select(-c(data)) |>
-  pivot_longer(cols = -c(Strain, O2_uM, WL, data)) |>
-  drop_na(value) |>
-  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
-  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-  pivot_wider(names_from = Output, values_from = value) |>
- filter(!map_lgl(Model, is.null)) |>
-  filter(!map_lgl(Glance, is.null)) |>
-  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
-  group_by(Strain, O2_uM, WL) |>
-  filter(AIC == min(AIC)) |>
-  ungroup() |>
-  select(-c(Model, Glance)) |>
-  unnest(Param) |>
-  select(-c(statistic)) |>
-  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
-
-PURPARStrainO2WLBestModelsDummy
-
-# PURPARStrainO2PhotoperiodWLBestModels <- PURPARStrainO2PhotoperiodNest|>
-#   select(-c(data)) |>
-#   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, WL)) |>
-#   drop_na(value) |>
-#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
-#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-#   pivot_wider(names_from = Output, values_from = value) |>
-#   filter(!map_lgl(Model, is.null)) |>
-#   filter(!map_lgl(Param, is.null)) |>
-#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
-#   group_by(Strain, O2_uM, Photoperiod) |>
-#   filter(AIC == min(AIC)) |>
-#   ungroup() |>
-#   select(-c(Model, Glance)) |>
-#   unnest(Param) |>
-#   select(-c(statistic)) |>
-#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
-#  
-# PURPARStrainO2PhotoperiodWLBestModels
-
-# mutate(Pmax_Ye = if_else(ModelType == "GRCbeta", estimate_a * ((sqrt(estimate_b + estimate_g) - sqrt(estimate_b))/estimate_g)^2, NA))
-
-```
-
-Want platt model for all fits that did not fail and lm for platt models that returned a NULL
-```{r}
-
-#filter to keep platt models
-KeepPlattModel <- PURPARStrainO2PhotoperiodNestDummy|>
-  select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
-   filter(!map_lgl(GRCplatt_Model, is.null))
-
-#filter to keep only the models that failed to fit a platt model, fits by lm remains. 
-KeepLmModel <- PURPARStrainO2PhotoperiodNestDummy|>
-  filter(map_lgl(GRCplatt_Model, is.null)) |>
- select(-c(GRCplatt_Glance, GRCplatt_Model, GRCplatt_Param, GRCplatt_Predict))
-
-# Join  
-StrainO2Photoperiod_AllModels <- full_join(KeepPlattModel, KeepLmModel)
-
  remove(KeepPlattModel)
  remove(KeepLmModel)
-
- StrainO2Photoperiod_PlattLmParam <- StrainO2Photoperiod_AllModels |>
-   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
-  drop_na(value) |>
-  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
-  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-  pivot_wider(names_from = Output, values_from = value) |>
-filter(!map_lgl(Model, is.null)) |>
-  filter(!map_lgl(Glance, is.null)) |>
-  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
-  group_by(Strain, O2_uM, Photoperiod) |>
-  filter(AIC == min(AIC)) |>
-  ungroup() |>
-  select(-c(Model, Glance)) |>
-  unnest(Param) |>
-  select(-c(statistic)) |>
-  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
-
- StrainO2filtered_PlattLmModel <- PURPARStrainO2NestDummy_filtered|>
-  # select(-c(data)) |>
-  pivot_longer(cols = -c(Strain, O2_uM, data)) |>
-  drop_na(value) |>
-  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
-  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-  pivot_wider(names_from = Output, values_from = value) |>
-  filter(!map_lgl(Model, is.null)) |>
-  filter(!map_lgl(Glance, is.null)) |>
-  mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
-  group_by(Strain, O2_uM) |>
-  filter(AIC == min(AIC)) |>
-  ungroup() |>
-  select(-c(Glance))
-
-```
-
-The linear models do not have alpha, beta and pmax so inf and NA are generated. Change them to 0.
-```{r lm platt parameters set to zero}
-
-PURPARStrainO2BestModelsDummy <- PURPARStrainO2BestModelsDummy|>
-  mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
-         estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
-         estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
-         AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC))
-
-PURPARStrainO2BestModelsDummy
-
-PURPARStrainO2WLBestModelsDummy <- PURPARStrainO2WLBestModelsDummy|>
-  mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
-         estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
-         estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
-         AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC))
-
-PURPARStrainO2WLBestModelsDummy
-
-StrainO2Photoperiod_PlattLmParam <- StrainO2Photoperiod_PlattLmParam|>
-  mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
-         estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
-         estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
-         AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC))
-
-StrainO2Photoperiod_PlattLmParam
-
-```
-
-```{r plot models}
-
-PURPARStrainO2PhotoperiodNestDummy |>
-  # select(-c(data)) |>
-  pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
-  drop_na(value) |>
-  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")| str_detect(name, pattern = "Predict")) |>
-  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-  pivot_wider(names_from = Output, values_from = value) |>
-  filter(!map_lgl(Model, is.null)) |>
-  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
-  group_by(Strain, O2_uM, Photoperiod) |>
-  filter(AIC == min(AIC)) |>
-  ungroup() |>
-   # filter(!map_lgl(GRClm_Model, is.null)) |>
+ # remove(PURPARStrainO2NestModels_filtered)
+ # remove(PURPARStrainO2PhotoNestModels_filtered)
+
+```
+
+```{r plot new models}
+
+StrainO2filteredPhotoperiod_PlattLmModel |>
+  unnest(Predict, data) |>
+  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         WL= factor(WL, levels = c("WW", 660, 450)),
+         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
+         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4"))) |>
+  ggplot() +
+  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL))) +
+  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
+   geom_text(aes(x = 500000, y = 0.75, label = paste(ModelType), show.legend = FALSE)
+  ) +
+     scale_colour_manual(values = MCMIXColours) +
+   scale_shape_manual(values = PhotoperiodShapes)  +
+  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
+    labs(title = "New single fit for each [O2]- photoperiods that were significantly different were removed from single fit") +
+  theme_bw()
+
+StrainO2Photofiltered_PlattLmModel |>
   unnest(Predict, data) |>
@@
   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
-   geom_text(aes(x = 3500000, y = 0.25, label = paste(ModelType), show.legend = FALSE, ),    # parse = TRUE,
-    # hjust = 0,
-    # vjust = 1,
-    # size = 8.0
+   geom_text(aes(x = 500000, y = 0.75, label = paste(ModelType), show.legend = FALSE)
   ) +
@@
   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-    labs(title = "PURPARStrainO2PhotoperiodNestDummy Best Model") +
+    labs(title = "Fits to be used for ANOVA comparison to single fit in each [O2]") +
   theme_bw()
 
- StrainO2Photoperiod_AllModels |>
-  # select(-c(data)) |>
-  pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
-  drop_na(value) |>
-  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")| str_detect(name, pattern = "Predict")) |>
-  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-  pivot_wider(names_from = Output, values_from = value) |>
-  filter(!map_lgl(Model, is.null)) |>
-  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
-  group_by(Strain, O2_uM, Photoperiod) |>
-  filter(AIC == min(AIC)) |>
-  ungroup() |>
-   # filter(!map_lgl(GRClm_Model, is.null)) |>
-  unnest(Predict, data) |>
-  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
-         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
-  ggplot() +
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
-  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
-   geom_text(aes(x = 3500000, y = 0.25, label = paste(ModelType), show.legend = FALSE, ),    # parse = TRUE,
-    # hjust = 0,
-    # vjust = 1,
-    # size = 8.0
-  ) +
-      scale_colour_manual(values = MCMIXColours) +
-  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-    labs(title = "Linear models replace null platt models.") +
-  theme_bw()
-
-PURPARStrainO2PhotoperiodNestDummy |>
-  # filter(!map_lgl(GRCplatt_Model, is.null)) |>
-  unnest(data) |>
-    # filter(WL %in% 450) %>% )),
-  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
-         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
-  ggplot() +
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
-  # geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
-     scale_colour_manual(values = MCMIXColours) +
-  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-    labs(title = "PURPARStrainO2PhotoperiodNestDummy all data no fits") +
-  theme_bw()
-
-```
-
+```
+# ANOVA on new model with signifiacntly different fits removed from the single fit.
 ```{r compare 1 fit of all photoperiod to each photoperiods using platt or lm}
 
-#extract fit parameters from each photoperiod.
-StrainO2Photoperiod_PlattLmModel <- StrainO2Photoperiod_AllModels |>
-   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
-  drop_na(value) |>
-  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
-  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-  filter(Output == "Model") |>
-  rename(Model = "value")
-
 # make wider to join with DF that contains the 1 fit through all photoperiods
-Wider_Photoperiods <- StrainO2Photoperiod_PlattLmModel %>% 
+Wider_Photoperiods <- StrainO2Photofiltered_PlattLmModel %>% 
   select(Strain, Photoperiod, O2_uM, Model) %>% 
@@
 # this contains 1 fit through all photoperiods, the photoperiods with no growth were filtered out.
-AllPhotoperiods <- StrainO2filtered_PlattLmModel %>% 
+AllPhotoperiods <- StrainO2filteredPhotoperiod_PlattLmModel %>% 
   select(Strain, O2_uM, Model) %>% 
@@
   labs(title = "ANOVA compare all models",
-       caption = "NA = atleast one model did not fit; 
+       caption = "NA = atleast one model did not fit due to lack of data points; 
        ns = not significantly different from all photoperiod model (same); 
@@
 ```
-# Remove the photoperiods from the model that are significantly different from the ANOVA run on the fit including all photoperiods against each individual photoperiod.   
+
+#Plot fits on same graph
 ```{r}
@@
 
-# ANOVA_Photoperiods <- PURPARStrainO2PhotoperiodNestDummy %>% 
+# ANOVA_Photoperiods <- PURPARStrainO2PhotoNestModels %>% 
 #   select(Strain, Photoperiod, O2_uM, GRCplatt_Model) %>% 
@@
 
-# # PURPARStrainO2PhotoperiodBestModels <- PURPARStrainO2PhotoperiodNestDummy |>
+# # PURPARStrainO2PhotoperiodBestModels <- PURPARStrainO2PhotoNestModels |>
 # #   select(-c(data)) |>
@@
 
-PURPARStrainO2PhotoperiodNestDummy |>
+PURPARStrainO2PhotoNestModels |>
   filter(!map_lgl(GRCplatt_Model, is.null)) |>
@@
 
-MED4PURFITPlot <- PURPARStrainO2PhotoperiodNestDummy |>
+MED4PURFITPlot <- PURPARStrainO2PhotoNestModels |>
   # select(-c(data)) |>
@@
 
-SS120PURFITPlot <- PURPARStrainO2PhotoperiodNestDummy |>
+SS120PURFITPlot <- PURPARStrainO2PhotoNestModels |>
   # select(-c(data)) |>
@@
 
-MIT9313PURFITPlot <- PURPARStrainO2PhotoperiodNestDummy |>
+MIT9313PURFITPlot <- PURPARStrainO2PhotoNestModels |>
   # select(-c(data)) |>
@@
 ``` {r}
-# PURPARStrainO2PeriodWLNestDummy |>
+# PURPARStrainO2PeriodWLNest |>
 #   filter(!map_lgl(GRCplatt_Model, is.null)) |>

### 2024-01-30 Code/ManuscriptFigures.Rmd
Fixed wrong color assignment in figures. Added fig caption

@@
 
-MyWavelengths = c("WW", 660, 530, 450)
+MyWavelengths = c("WW", 660, 450)
 
-MCMIXColours = c("black", w_length2rgb(660), w_length2rgb(530),  w_length2rgb(450))
+MCMIXColours = c("black", w_length2rgb(660), w_length2rgb(450))
 
@@
 
-```{r PURPARRatioPlots, fig.height= 10, fig.width= 10}
+```{r PURPARRatioPlots, fig.height= 10, fig.width= 15}
 
@@
   coord_fixed(ylim = c (0, 180), xlim = c (0, 180), ratio = 1) +
-   scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660","530", "450" )) +
-   geom_text(aes(x = 60, y = 180, label = paste(Strain), show.legend = FALSE, ),    # parse = TRUE,
+   scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450")) +
+   geom_text(aes(x = 60, y = 181, label = paste(Strain), show.legend = FALSE, ),    # parse = TRUE,
     hjust = 0,
@@
   )  +
-  facet_wrap(~Strain, ncol = 2) +
+  facet_wrap(~Strain, ncol = 3) +
   theme_bw() +
@@
   theme(strip.text = element_blank(),
-        legend.text = element_text(size = 20),
-        legend.title = element_text(size = 25),
-        legend.position = c(0.80, 0.25),
-        axis.title = element_text(hjust= 0.60, vjust = -0.2, size = 20),
+        legend.text = element_text(size = 35),
+        legend.title = element_text(size = 35),
+        # legend.position = c(0.80, 0.25),
+         legend.position = "top",
+        axis.title = element_text(hjust= 0.5, vjust = -0.2, size = 20),
         strip.text.x = element_blank(),
@@
 
-ggsave(file = file.path(PlotsPath, paste("PurParPlot",".png",sep = "")), plot = PurParPlot, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("PurParPlot",".png",sep = "")), plot = PurParPlot, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
 
-# ggsave(file = file.path(PlotsPath, paste("MED4NoPhotoPUR",".png",sep = "")), plot = MED4NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsOut, paste("MED4NoPhotoPUR",".png",sep = "")), plot = MED4NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
 # 
-# ggsave(file = file.path(PlotsPath, paste("MIT9313NoPhotoPUR",".png",sep = "")), plot = MIT9313NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsOut, paste("MIT9313NoPhotoPUR",".png",sep = "")), plot = MIT9313NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
 # 
-# ggsave(file = file.path(PlotsPath, paste("SS120NoPhotoPUR",".png",sep = "")), plot = SS120NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsOut, paste("SS120NoPhotoPUR",".png",sep = "")), plot = SS120NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
   # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm","530 nm", "450 nm" )) +
+  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm", "450 nm" )) +
    scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
@@
 
-ggsave(file = file.path(PlotsPath, paste("MED4PAR",".png",sep = "")), plot = MED4PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("MED4PAR",".png",sep = "")), plot = MED4PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 
-ggsave(file = file.path(PlotsPath, paste("SS120PAR",".png",sep = "")), plot = SS120PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("SS120PAR",".png",sep = "")), plot = SS120PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 
-ggsave(file = file.path(PlotsPath, paste("MIT9313PAR",".png",sep = "")), plot = MIT9313PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("MIT9313PAR",".png",sep = "")), plot = MIT9313PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
 
-MyWavelengths = c("WW", 660, 530, 450)
-OverlayColours = c("black", w_length2rgb(660), w_length2rgb(530),  w_length2rgb(450))
+MyWavelengths = c("WW", 660, 450)
+OverlayColours = c("black", w_length2rgb(660),  w_length2rgb(450))
 
@@
   scale_linetype_manual(values = c("PurData_PURAbsWholeCell_Norm440" = "solid", "PurData_AbsNorm440" = "twodash",  "PurData_MC_NormEm" = "dotted"),
-                        labels = c("LED emission", "Whole cell abs.", "PUR")) +
+                        labels = c("Whole cell abs.",  "LED emission", "PUR")) +
   scale_fill_manual(values = MCMIXColours) +
@@
 
-# ggsave(file = file.path(PlotsPath, paste("MED4OverlayPlots",".png",sep = "")), plot = MED4OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsOut, paste("MED4OverlayPlots",".png",sep = "")), plot = MED4OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 # 
-# ggsave(file = file.path(PlotsPath, paste("MED4WWOverlayPlots",".png",sep = "")), plot = MED4WWOverlayPlots, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsOut, paste("MED4WWOverlayPlots",".png",sep = "")), plot = MED4WWOverlayPlots, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
 
-# ggsave(file = file.path(PlotsPath, paste("MIT9313OverlayPlots",".png",sep = "")), plot = MIT9313OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsOut, paste("MIT9313OverlayPlots",".png",sep = "")), plot = MIT9313OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
  scale_linetype_manual(values = c("PurData_PURAbsWholeCell_Norm440" = "solid", "PurData_AbsNorm440" = "twodash",  "PurData_MC_NormEm" = "dotted"),
-                        labels = c("LED emission", "Whole cell abs.", "PUR")) +
+                        labels = c("Whole cell abs.",  "LED emission", "PUR")) +
   scale_fill_manual(values = MCMIXColours) +
@@
 
-# ggsave(file = file.path(PlotsPath, paste("SS120OverlayPlots",".png",sep = "")), plot = SS120OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsOut, paste("SS120OverlayPlots",".png",sep = "")), plot = SS120OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 

### 2024-01-30 Code/Manuscript_O2.Rmd
Fixed wrong color assignment in figures. Added fig caption

@@
 output:
+  bookdown::word_document2:
+    code_folding: show
+    reference_docx: KnitTemplate.docx
+    keep_md: yes
+    toc: TRUE
+    toc_depth: 6
+    fig_caption: yes
+    pandoc_args: 
+      - '--lua-filter=scholarly-metadata.lua'
+      - '--lua-filter=author-info-blocks.lua'
   bookdown::html_document2:
@@
     toc_float: TRUE
-    toc_depth: 6
-    fig_caption: yes
-    pandoc_args: 
-      - '--lua-filter=scholarly-metadata.lua'
-      - '--lua-filter=author-info-blocks.lua'
-  bookdown::word_document2:
-    code_folding: show
-    reference_docx: KnitTemplate.docx
-    keep_md: yes
-    toc: TRUE
     toc_depth: 6
@@
 levels and spectral color spanning the vertical ocean water column, from
-near-surface to the lower euphotic zone depths (Figure
-\@ref(fig:SunDepth)). For simplicity, actinic light used for growth
+near-surface to the lower euphotic zone depths. For simplicity, actinic light used for growth
 under specific wavebands will be referred by the respective spectral
@@
 each experimental range: 2.5 µM, 25 µM, and 250 µM, will be used for
-low, intermediate, and high conditions, respectively. Figure
-\@ref(fig:O2DataCapture) shows the data capture software of the
-FireSting Oxygen Logger. Dissolved [O~2~] were measured every 5 minutes
-over the duration of the Multicultivator run and recorded in a text file
-for later processing in R-Studio (Figure \@ref(fig:O2Plot)).
+low, intermediate, and high conditions, respectively.
 
@@
 Growth experiments under different spectral wavebands were performed
-using a PSI MCMIX-OD Multicultivator (Figure \@ref(fig:MCpicture)) or a
+using a PSI MCMIX-OD Multicultivator (Figure \@ref(fig:LabeledMC)) or a
 PSI MC1000-OD Multicultivator for white LED experiments. Each
@@
 recorded every 5 minutes for at least 8 to 14 days depending on the
-duration of the lag phase, if any. Figure \@ref(fig:MCDataCapture) is a
-typical readout from the MCMIX-OD Multicultivator software. Real time OD
+duration of the lag phase, if any. Real time OD
 measurements eliminate intrusive subsampling of sterile cultures and
@@
 
-```{r MCpicture, fig.cap = MCpicture_cap , fig.height = 8, fig.width = 6, echo = FALSE}
+```{r LabeledMC, fig.cap = LabeledMC_cap , fig.height = 8, fig.width = 6, echo = FALSE}
 
-MCpicture_cap <- glue("**PSI MCMIX-OD Multicultivator.**",
-                      "The image illustrates the capability to set different spectral wavebands and light levels for individual culture tubes.",
-                      "Tubes 4 and 7 have oxygen optodes inserted for real-time dissolved oxygen concentration measurements.",
+LabeledMC_cap <- glue("**PSI MCMIX-OD Multicultivator.**",
+                      "Spectral wavebands and light levels are individually controlled for each culture tube.",
                       "Real time Optical Density (OD) measurements eliminate intrusive subsampling of sterile cultures.",
+                      "The temperature of culture tubes are controlled via heating or cooling of the aquarium water.",
+                      "Gas with specific oxygen concentrations are bubbled through a humidifier and passed through a 0.2 um filter.",
 
@@
 
-knitr::include_graphics(file.path(FiguresIn, "MCMIX004_Picture.jpg"))
+knitr::include_graphics(file.path(FiguresIn, "LabeledMC.png"))
+```
+
+\newpage
+
+```{r PurParPlot, fig.cap = PurParPlot_cap , fig.height = 20, fig.width = 10, echo = FALSE}
+
+PurParPlot_cap <- glue("**The absorbed Photosynthetically Usable Radiation (PUR) (µmol photons m^-2^ s^-1^) vs. the Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^).**",
+                       "The correlation between PAR, plotted on the x-axis and absorbed PUR, plotted on the y-axis, are colored for each spectral waveband; blue for 450 nm, red for 660 nm and black for white LED full spectrum light.",
+                       "The grey dashed line represents a hypothetical one to one correlation.",
+                       "**A.** is *Prochlorococcus marinus*  MED4.",
+                       "**B.** is *Prochlorococcus marinus*  SS120.",
+                       "**C.** is *Prochlorococcus marinus*  MIT9313.",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "PurParPlot.png"))
 ```
@@
 where ΔOD~max~ is maximum ΔOD, ΔOD~min~ is minimum ΔOD, t is time
-duration over the growth trajectory. Figure
-\@ref(fig:deltaODLogGrowthPlot) is an example of a chlorophyll proxy
-growth estimates fitted from the high resolution ΔOD measurements for
-each tube in a Multicultivator. The residuals of the logistic growth
-curve fit are shown and the growth spectral waveband is plotted and
-illustrates the imposed PAR (µmol photons m^-2^ s^-1^) and photoperiod
-(h). Although the chlorophyll proxy (ΔOD) growth rate was used in this
-study, we also determined the cell scatter proxy (OD720) growth rate.
-The correlation between the chlorophyll proxy growth rate and the cell
-scatter proxy growth rate of *P. marinus* under all conditions examined
-in this study was shown in Figure \@ref(fig:AllBalanceGrowthPlot) and
-generally showed balance growth. The high cell scatter growth rate of
-cultures that exhibited no chlorophyll proxy growth may be the logistic
-model over-estimating the fits as the amplitude of the OD720 signal
-maybe very small.
+duration over the growth trajectory.
 
@@
 # Results {.unnumbered}
+
+%%%% Insert OceanDepthO2ProteinPhotosynth figure from OceanPortal repository  %%%
+
+%%%% Insert GAM figures  %%%
+
+%%%% Insert PURFits figures  %%%
+
+\newpage
+
+%%% TO DO Fits and ANOVA %%
+```{r MED4PAR, fig.cap = MED4PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+
+MED4PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade) vs. photoperiod (h).  **",
+
+                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
+                    "Colors represent the actinic spectral waveband (nm).",
+                    "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "MED4PAR.png"))
+```
+
+\newpage
+
+%%% TO DO Fits and ANOVA %%
+```{r SS120PAR, fig.cap = SS120PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+
+SS120PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low Light (LLIII) deep ocean clade) vs. photoperiod (h). **",
+
+                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
+                    "Colors represent the actinic spectral waveband (nm).",
+                    "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "SS120PAR.png"))
+
+```
+
+\newpage
+
+%%% TO DO Fits and ANOVA %%
+```{r MIT9313PAR, fig.cap = MIT9313PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+
+MIT9313PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
+
+                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
+                    "Colors represent the actinic spectral waveband (nm).",
+                    "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "MIT9313PAR.png"))
+
+```
+
+\newpage
+
+%%%% Insert OceanFtsHRibosomeProteins figure from OceanPortal repository  %%%
 
@@
 
-```{r MED4PAR, fig.cap = MED4PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}
-
-MED4PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade) vs. photoperiod (h).  **",
-
-                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
-                    "Colors represent the actinic spectral waveband (nm).",
-                    "Large circles show mean or single determinations of growth rate from logistic curve fits (ex.
-Figure \\@ref(fig:deltaODLogGrowthPlot)); small circles show values for replicate determinations, if any: replicates often fall with larger circles",
-
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "MED4PAR.png"))
-```
-
-\newpage
-
-```{r SS120PAR, fig.cap = SS120PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}
-
-SS120PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low Light (LLIII) deep ocean clade) vs. photoperiod (h). **",
-
-                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
-                    "Colors represent the actinic spectral waveband (nm).",
-                    "Large circles show mean or single determinations of growth rate from logistic curve fits (ex.
-Figure \\@ref(fig:deltaODLogGrowthPlot)); small circles show values for replicate determinations, if any: replicates often fall with larger circles",
-
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "SS120PAR.png"))
-
-```
-
-\newpage
-
-```{r MIT9313PAR, fig.cap = MIT9313PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}
-
-MIT9313PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
-
-                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
-                    "Colors represent the actinic spectral waveband (nm).",
-                    "Large circles show mean or single determinations of growth rate from logistic curve fits (ex.
-Figure \\@ref(fig:deltaODLogGrowthPlot)); small circles show values for replicate determinations, if any: replicates often fall with larger circles",
-
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "MIT9313PAR.png"))
-
-```
-
-\newpage
-
 # References {.unnumbered}

### 2024-02-02 Code/Manuscript_O2.Rmd
Added figures from the OceanProteinProchloro repository.

@@
 output:
+  bookdown::html_document2:
+    code_folding: show
+    keep_md: yes
+    toc: TRUE
+    toc_float: TRUE
+    toc_depth: 6
+    fig_caption: yes
+    pandoc_args: 
+      - '--lua-filter=scholarly-metadata.lua'
+      - '--lua-filter=author-info-blocks.lua'
   bookdown::word_document2:
@@
     toc: TRUE
-    toc_depth: 6
-    fig_caption: yes
-    pandoc_args: 
-      - '--lua-filter=scholarly-metadata.lua'
-      - '--lua-filter=author-info-blocks.lua'
-  bookdown::html_document2:
-    code_folding: show
-    keep_md: yes
-    toc: TRUE
-    toc_float: TRUE
     toc_depth: 6
@@
 FiguresIn <- file.path("..","Output", "Figures")
-FiguresInOceanPro <- file.path( "..", "..", "OceanProteinProchlor", "Output")
+FiguresInOceanPro <- file.path( "..", "..", "OceanProteinProchloro", "Output")
 FigureInO2Analy <- file.path(  "..", "..", "O2Analyses", "Output")
@@
 
+```{r ProchloroElectronTrans, fig.cap = ProchloroElectronTrans_cap , fig.height = 20, fig.width = 10, echo = FALSE}
+
+ProchloroElectronTrans_cap <- glue("**Occurance of electron transport complexes data from the Ocean Protein Portal.
+X-axis indicates the depth (m) of occurance and the y-axis is the oxygen concentration (µM) **",
+                       "Rows are...",
+                       "Columns are...",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresInOceanPro, "ProchloroElectronTrans.png"))
+```
+
 %%%% Insert GAM figures  %%%
@@
 
+```{r ProchloroMetabDepthO2, fig.cap = ProchloroMetabDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
+
+ProchloroMetabDepthO2_cap <- glue("**Protein turnover complexes data from the Ocean Protein Portal. X-axis indicates the depth (m) of occurance and the y-axis is the oxygen concentration (µM) **",
+                       "Rows are...",
+                       "Columns are...",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresInOceanPro, "ProchloroMetabDepthO2.png"))
+```
+
 ```{r MED4ProteinAttonated, fig.cap = MED4ProteinAttonated_cap, fig.height = 6, fig.width = 8, echo = FALSE}

### 2024-02-05 Code/ManuscriptGAM.Rmd
Set up RMD to generate GAMs then plot red then blue light rather than using 1 chunk to generate each color.

@@
 library(car)
-library(MASS)
-library(faraway)
+library(MASS) # estimating linear models through generalized least squares (GLS), fitting negative binomial linear models, the robust fitting of linear models, and Kruskal's non-metric multidimensional scaling.
+library(faraway) # LM package
 library(gridExtra)
@@
 library(photobiologyWavebands) 
-library(photobiology)
+# library(photobiology)
 library(metR)
-library(Rcpp)
+library(Rcpp) #'Rcpp' package provides R functions as well as C++ classes which offer a seamless integration of R and C++.
 
@@
 #Next step, fitting Strain-specific models. 
-#MED4 model to Par_ue-response falsy fits, due to badly fitted µ-rates -> cultures died, but model tried to fit anywy. Maybe filter everything below a certain R^2 in the fit?
+#MED4 model to Par_ue-response falsely fits, due to badly fitted µ-rates -> cultures died, but model tried to fit anyway. Maybe filter everything below a certain R^2 in the fit?
 
@@
 
-```{r GAM separate niches hypervolume}
+# Generate GAM for red light conditions for all strains using chlorophyll proxy logistic growth rate. 
+```{r GAM separate niches hypervolume for red light}
 GamWL = c("deltaOD", "OD720") #deltaOD OD720
@@
 GamParaMod = "Lmu"
-GamVar = c("450")# 450 660 WW
+GamVar = c("660")
 ErrorTolGrowth = 30 # defined for the growth estimates
@@
 
-# Plot red light GAM
+# Plot red light GAM, must change GAMStrain and rerun chunk to generate plot of each strain
 ``` {r GAM Plot Red WL}
@@
 # for presentation
-  ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3,  height = 7.6, width = 6)
+  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3,  height = 7.6, width = 6)
 
@@
 
-# Plot blue light GAM
+# Generate GAM for blue light conditions for all strains using chlorophyll proxy logistic growth rate. 
+```{r GAM separate niches hypervolume for blue light}
+GamWL = c("deltaOD", "OD720") #deltaOD OD720
+Proxy= "[~Chl]" #~Chl ~Cells 
+GamParaMod = "Lmu"
+GamVar = c("450")
+ErrorTolGrowth = 30 # defined for the growth estimates
+ErrorTol = 30 # defined for the GAM fit
+# OxyLev = 25
+
+#https://stackoverflow.com/questions/49570452/is-it-possible-to-specify-lower-bound-in-response-variable-during-smooth-with-ga 
+possibGAM = possibly(.f = mgcv::gam, otherwise = NULL)
+possibPRED = possibly(.f = mgcv::predict.gam, otherwise = NULL)
+
+PAR_Photoperiod_Model_predi <- expand_grid(
+  Par_ue = seq(from=min(10), 
+              to=max(200), 
+              length.out = 100),
+  Photoperiod = seq(from=min(2), 
+              to=max(18), 
+              length.out = 100)
+)
+
+PicoGAM <- PicoGrowthFits %>%
+  ungroup() %>%
+  dplyr::mutate(Lmu_seFlag = case_when(se/estimate*100 < ErrorTolGrowth ~ 1, #filters faulty data where Standarderror larger +/- Errortolerance
+                         FALSE ~ 0)) %>%
+  dplyr::filter(
+                estimate == 0 |
+                estimate != 0 & Lmu_seFlag == 1,
+                term %in% GamParaMod, 
+                Wavelength %in% GamWL
+                ) %>%
+  mutate(estimate = estimate*24, #to convert growth from per hour to per day
+         se = se*24) %>%
+  group_by(Strain, Wavelength, WL, O2_uM) %>%
+  nest() %>%
+  dplyr::arrange(Strain, Wavelength, WL, O2_uM) %>%
+  mutate(GamModel = map(data, ~possibGAM(estimate ~ s(Par_ue, k = 3) + s(Photoperiod, k = 3) + ti(Photoperiod, Par_ue, k = 3),  data = .x,
+                                    family = "gaussian"(link = "log"), 
+                                    method = "REML")),
+         predicted = map(GamModel, ~possibPRED(.x, newdata = PAR_Photoperiod_Model_predi, type = 'response', se.fit=TRUE)),
+         augmented = map(GamModel, ~augment(.x))
+         )
+
+PicoGAM_Pred <- PicoGAM %>%
+  dplyr::select(Strain, Wavelength, WL, O2_uM, predicted) %>%
+  dplyr::filter(predicted != "NULL") %>%
+  rowwise() %>%
+  mutate(db = list(cbind(predicted, PAR_Photoperiod_Model_predi))) %>%
+  dplyr::select(-predicted) %>%
+  unnest(col = db) %>%
+  group_by(Strain, Wavelength, WL, O2_uM) %>%
+  dplyr::filter(fit < 1.2) %>% #with two exceptions, growth rates were never higher than 1.2; GAM model creates some unrealistic high growth rates due to low data availability
+  mutate(
+    IsFitGood = case_when(se.fit/fit*100 < ErrorTol ~ 1, #flags faulty data where Standarderror larger +/- Errortolerance
+                         se.fit/fit*100 > ErrorTol ~ 0
+                    )
+    #se_erro_per = se.fit/fit*100
+  # ,fit = case_when(fit >= quantile(fit, 0.75, na.rm = TRUE) ~ fit*1, #leaves only top-10%, that means fastest growth rates in the dataframe
+  #                 FALSE ~ fit)
+  ) %>% 
+  dplyr::filter(IsFitGood == 1)
+
+```
+
+# Plot blue light GAM, must change GAMStrain and rerun chunk to generate plot of each strain
 ``` {r GAM Plot Blue WL}

### 2024-02-06 Code/Manuscript_O2.Rmd
Generated combined blue and red GAMs

@@
 library(tidyverse)
+library(png)
+library(cowplot)
 
@@
 
-# Results {.unnumbered}
+# Results and Discussion {.unnumbered}
 
-%%%% Insert OceanDepthO2ProteinPhotosynth figure from OceanPortal repository  %%%
+%%%% OceanProteinPortal data show complexes in environment  %%%
 
@@
 %%%% Insert GAM figures  %%%
+
+```{r MED4GAM,  fig.cap = MED4GAM_cap, fig.height = 10, fig.width = 10, echo = FALSE}
+
+MED4GAM_cap <- glue("** The Generalized Additive Models (GAM) for red light at 660 nm and blue light at 450 nm.
+The x-axis is photoperiod (h) and the y-axis is the Photosynethetic Active Radiation (PAR) (µmole photons m-2 s-1) **",
+                       "Rows are...",
+                       "Columns are...",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "PICO_Hypervolume_GAM_MED4_Oxy_.png"))
+
+```
 

### 2024-02-06 Code/Manuscript_O2.Rmd
Added more GAM figs

@@
 PurParPlot_cap <- glue("**The absorbed Photosynthetically Usable Radiation (PUR) (µmol photons m^-2^ s^-1^) vs. the Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^).**",
-                       "The correlation between PAR, plotted on the x-axis and absorbed PUR, plotted on the y-axis, are colored for each spectral waveband; blue for 450 nm, red for 660 nm and black for white LED full spectrum light.",
+                       "The correlation between PAR, plotted on the x-axis and absorbed PUR, plotted on the y-axis, are colored for each growth spectral waveband; blue for 450 nm, red for 660 nm and black for white LED full spectrum light.",
                        "The grey dashed line represents a hypothetical one to one correlation.",
@@
 ProchloroElectronTrans_cap <- glue("**Occurance of electron transport complexes data from the Ocean Protein Portal.
-X-axis indicates the depth (m) of occurance and the y-axis is the oxygen concentration (µM) **",
+X-axis is the oxygen concentration (µM) and the y-axis indicates the depth (m) of occurance**",
                        "Rows are...",
@@
 
-%%%% Insert GAM figures  %%%
+\newpage
+
+%%%% Insert GAM figures to show lab results confirming Ocean Protein Portal environment results %%%
 
@@
 MED4GAM_cap <- glue("** The Generalized Additive Models (GAM) for red light at 660 nm and blue light at 450 nm.
-The x-axis is photoperiod (h) and the y-axis is the Photosynethetic Active Radiation (PAR) (µmole photons m-2 s-1) **",
+The x-axis is photoperiod (h) and the y-axis is the Photosynethetic Active Radiation (PAR) (µmol photons m^-2^ s^-1^) **",
                        "Rows are...",
@@
 ```
+
+\newpage
+
+```{r SS120GAM,  fig.cap = SS120GAM_cap, fig.height = 10, fig.width = 10, echo = FALSE}
+
+SS120GAM_cap <- glue("** The Generalized Additive Models (GAM) for red light at 660 nm and blue light at 450 nm.
+The x-axis is photoperiod (h) and the y-axis is the Photosynethetic Active Radiation (PAR) (µmol photons m^-2^ s^-1^) **",
+                       "Rows are...",
+                       "Columns are...",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "PICO_Hypervolume_GAM_SS120_Oxy_.png"))
+
+```
+
+\newpage
+
+```{r MIT9313GAM,  fig.cap = MIT9313GAM_cap, fig.height = 10, fig.width = 10, echo = FALSE}
+
+MIT9313GAM_cap <- glue("** The Generalized Additive Models (GAM) for red light at 660 nm and blue light at 450 nm.
+The x-axis is photoperiod (h) and the y-axis is the Photosynethetic Active Radiation (PAR) (µmol photons m^-2^ s^-1^) **",
+                       "Rows are...",
+                       "Columns are...",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "PICO_Hypervolume_GAM_MIT9313_Oxy_.png"))
+
+```
+
+\newpage
 
@@
 
-%%%% Insert OceanFtsHRibosomeProteins figure from OceanPortal repository  %%%
+%%%% OceanFtsHRibosomeProteins figure from OceanPortal repository  %%%
 
@@
 
-ProchloroMetabDepthO2_cap <- glue("**Protein turnover complexes data from the Ocean Protein Portal. X-axis indicates the depth (m) of occurance and the y-axis is the oxygen concentration (µM) **",
+ProchloroMetabDepthO2_cap <- glue("**Protein turnover complexes data from the Ocean Protein Portal. The x-axis is the oxygen concentration (µM) and the y-axis indicates the depth (m) of occurance**",
                        "Rows are...",

### 2024-02-07 Code/ManuscriptPURFits.Rmd
Edit code

@@
 remove(DummyDF_Expand)
+remove(PURPARFits)
 
@@
 ```{r testplot}
- PURPARFits %>% 
+ PURPARFits_dummy %>% 
   ggplot() +
@@
 ```{r growthPURfits}
-
-#constrain with lower 0 and upper 1 limits to avoid excessive Pmax and negative b
-
-# PURPARStrainO2Nest <- PURPARFits |>
-#   nest(data = -c("Strain","O2_uM")) |>
-#   mutate(GRC_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grc(I = PUR_day, a, Pmax),
-#                               data = .x,
-#                               start = list(a = 1e-6,
-#                                            Pmax = 1),
-#                               lower = c(0, 0),
-#                               upper = c(1,100)
-#                          ), NULL)
-#                          )
-#          ) |>
-#   mutate(GRC_Param = map(GRC_Model, tidy),
-#          GRC_Predict = map(GRC_Model, possibly(augment), NULL),
-#          GRC_Glance = map(GRC_Model, possibly(glance))) |>
-#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
-#                               data = .x,
-#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
-#                               lower = c(0, 0, 0),
-#                               upper = c(1,1,100)
-#                          ), NULL)
-#                          )
-#          ) |>
-#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
-#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
-#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
-#          )
 
@@
 
-PURPARStrainO2PhotoNestModels_filtered <- PURPARFits_dummy |>
+PURPARStrainO2PhotoNestModels <- PURPARFits_dummy |>
    filter(PURPhotonDose_day <= 1.5e+06) |>
@@
 ```{r growthPURplots, fig.height= 10, fig.width= 10}
-#ReplicateMean_
-
-# PURPARStrainWLNest |>
-#   #filter(!is.null(GRC_Model)) |>
-#   filter(!map_lgl(GRC_Model, is.null)) |>  
-#   unnest(GRC_Predict, data) |>
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
-#   facet_grid(rows = vars(WL), cols = vars(Strain)) + 
-#   theme_bw()
-
-# PURPARStrainO2Nest |>
-#   filter(!map_lgl(GRC_Model, is.null)) |> #https://stackoverflow.com/questions/57336319/how-to-filter-out-null-elements-of-tibbles-list-column 
-#   unnest(GRC_Predict, data) |>
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
-#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
-#     labs(title = "PURPARStrainO2Nest GRC") +
-#   theme_bw()
 
@@
 #   filter(!map_lgl(GRC_Model, is.null)) |> #https://stackoverflow.com/questions/57336319/how-to-filter-out-null-elements-of-tibbles-list-column 
-#   unnest(GRC_Predict, data) |>
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
-#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
-#     labs(title = "PURPARStrainO2NestModels GRC") +
-#   theme_bw()
-
-# PURPARStrainO2Nest |>
-#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
-#   unnest(GRCplatt_Predict, data) |>
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
-#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
-#     labs(title = "PURPARStrainO2Nest Platt") +
-#   theme_bw()
-#
-
-# PURPARStrainO2NestModels |>
-#   filter(!map_lgl(GRCplatt_Model, is.null)) |> # only include fits that did not fail
-#   unnest(GRCplatt_Predict, data) |>
-#    mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-#          Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
-#          Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) + 
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
-#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
-#   labs(title = "PURPARStrainO2NestModels Platt") +
-#   theme_bw()
-
 PURPARStrainO2NestModels_filtered|>
@@
 
-# PURPARStrainO2PhotoNestModels |>
-#   filter(!map_lgl(GRC_Model, is.null)) |>
-#   unnest(GRC_Predict, data) |>
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
-#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-#     labs(title = "PURPARStrainO2PhotoNestModels GRC") +
-#   theme_bw()
-
-# PURPARStrainO2PhotoNestModels |>
-#    filter(!map_lgl(GRC_Model, is.null)) |>
-#   unnest(GRC_Predict, data) |>
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
-#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-#     labs(title = "PURPARStrainO2PhotoNestModels GRC") +
-#   theme_bw()
-
-# PURPARStrainO2PhotoNestModels |>
-#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
-#   unnest(GRCplatt_Predict, data) |>
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
-#   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-#     labs(title = "PURPARStrainO2PhotoNestModels Platt") +
-#   theme_bw()
-
-PURPARStrainO2PhotoNestModels_filtered |>
+PURPARStrainO2PhotoNestModels |>
   filter(!map_lgl(GRCplatt_Model, is.null)) |>
@@
   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-    labs(title = "PURPARStrainO2PhotoNestModels_filtered Platt") +
+    labs(title = "PURPARStrainO2PhotoNestModels Platt") +
   theme_bw()
 
-PURPARStrainO2PhotoNestModels_filtered |>
+PURPARStrainO2PhotoNestModels |>
   filter(!map_lgl(GRClm_Model, is.null)) |>
@@
   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-    labs(title = "PURPARStrainO2PhotoNestModels_filtered Linear Model") +
+    labs(title = "PURPARStrainO2PhotoNestModels Linear Model") +
   theme_bw()
@@
 
-# PURPARStrainO2WLNestModels |>
-#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
-#   unnest(GRCplatt_Predict, data) |>
-#    mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-#          Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
-#          Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = Photoperiod)) +
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
-#   facet_grid(rows = vars(O2_uM, WL), cols = vars(Strain)) +
-#     labs(title = "PURPARStrainO2WLNestModels Platt") +
-#   theme_bw()
-
-# PURPARStrainO2PeriodWLNest |>
-#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
-#   unnest(GRCplatt_Predict, data) |>
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
-#   facet_grid(rows = vars(O2_uM, Photoperiod, WL), cols = vars(Strain)) +
-#     labs(title = "PURPARStrainO2PeriodWLNest Platt") +
-#   theme_bw()
-
-```
-
-nlsLM generates AIC accessed with broom::glance
-Choose best model between platt and lm based on lowest GIC 
-```{r aic comparisons}
-#https://www.scribbr.com/statistics/akaike-information-criterion/
-
-#need to remove 'null' models to facilitate conversion of AIC from 'list' derived from 'Glance' column, to dbl
-# PURPARStrainO2BestModels <- PURPARStrainO2Nest|>
-#   select(-c(data)) |>
-#   pivot_longer(cols = -c(Strain, O2_uM)) |>
-#   drop_na(value) |>
-#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
-#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-#   pivot_wider(names_from = Output, values_from = value) |>
-#   filter(!map_lgl(Model, is.null)) |>
-#   filter(!map_lgl(Glance, is.null)) |>
-#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
-#   group_by(Strain, O2_uM) |>
-#   filter(AIC == min(AIC)) |>
-#   ungroup() |>
-#   select(-c(Model, Glance)) |>
-#   unnest(Param) |>
-#   select(-c(statistic)) |>
-#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
-#  
-# PURPARStrainO2BestModels
-
-# PURPARStrainO2BestModels <- PURPARStrainO2NestModels|>
-#   # select(-c(data)) |>
-#   pivot_longer(cols = -c(Strain, O2_uM, data)) |>
-#   drop_na(value) |>
-#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
-#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-#   pivot_wider(names_from = Output, values_from = value) |>
-#   filter(!map_lgl(Model, is.null)) |>
-#   filter(!map_lgl(Glance, is.null)) |>
-#   mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
-#   group_by(Strain, O2_uM) |>
-#   filter(AIC == min(AIC)) |>
-#   ungroup() |>
-#   select(-c(Model, Glance)) |>
-#   unnest(Param) |>
-#   select(-c(statistic)) |>
-#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
-#  
-# PURPARStrainO2BestModels
-
-# PURPARStrainO2BestModels_filtered <- PURPARStrainO2NestModels_filtered|>
-#   # select(-c(data)) |>
-#   pivot_longer(cols = -c(Strain, O2_uM, data)) |>
-#   drop_na(value) |>
-#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
-#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-#   pivot_wider(names_from = Output, values_from = value) |>
-#     filter(!map_lgl(Model, is.null)) |>
-#   filter(!map_lgl(Glance, is.null)) |>
-#   mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
-#   group_by(Strain, O2_uM) |>
-#   filter(AIC == min(AIC)) |>
-#   ungroup() |>
-#   select(-c(Model, Glance)) |>
-#   unnest(Param) |>
-#   select(-c(statistic)) |>
-#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
-#  
-# PURPARStrainO2BestModels_filtered
-# 
-# PURPARStrainO2PhotoBestModels_filtered <- PURPARStrainO2PhotoNestModels_filtered|>
-#   # select(-c(data)) |>
-#   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
-#   drop_na(value) |>
-#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
-#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-#   pivot_wider(names_from = Output, values_from = value) |>
-#   filter(!map_lgl(Model, is.null)) |>
-#   filter(!map_lgl(Glance, is.null)) |>
-#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
-#   group_by(Strain, O2_uM, Photoperiod) |>
-#   filter(AIC == min(AIC)) |>
-#   ungroup() |>
-#   select(-c(Model, Glance)) |>
-#   unnest(Param) |>
-#   select(-c(statistic)) |>
-#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
-# 
-# PURPARStrainO2PhotoBestModels_filtered
-
-# PURPARStrainO2PhotoBestModels <- PURPARStrainO2PhotoNestModels|>
-#   # select(-c(data)) |>
-#   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
-#   drop_na(value) |>
-#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
-#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-#   pivot_wider(names_from = Output, values_from = value) |>
-#   filter(!map_lgl(Model, is.null)) |>
-#   filter(!map_lgl(Glance, is.null)) |>
-#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
-#   group_by(Strain, O2_uM, Photoperiod) |>
-#   filter(AIC == min(AIC)) |>
-#   ungroup() |>
-#   select(-c(Model, Glance)) |>
-#   unnest(Param) |>
-#   select(-c(statistic)) |>
-#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
-#  
-# PURPARStrainO2PhotoBestModels
-
-# PURPARStrainO2WLBestModels <- PURPARStrainO2WLNestModels|>
-#   # select(-c(data)) |>
-#   pivot_longer(cols = -c(Strain, O2_uM, WL, data)) |>
-#   drop_na(value) |>
-#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
-#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-#   pivot_wider(names_from = Output, values_from = value) |>
-#  filter(!map_lgl(Model, is.null)) |>
-#   filter(!map_lgl(Glance, is.null)) |>
-#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
-#   group_by(Strain, O2_uM, WL) |>
-#   filter(AIC == min(AIC)) |>
-#   ungroup() |>
-#   select(-c(Model, Glance)) |>
-#   unnest(Param) |>
-#   select(-c(statistic)) |>
-#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
-#  
-# PURPARStrainO2WLBestModels
-
-# PURPARStrainO2PhotoWLBestModels <- PURPARStrainO2PhotoNestModels|>
-#   select(-c(data)) |>
-#   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, WL)) |>
-#   drop_na(value) |>
-#   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
-#   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-#   pivot_wider(names_from = Output, values_from = value) |>
-#   filter(!map_lgl(Model, is.null)) |>
-#   filter(!map_lgl(Param, is.null)) |>
-#   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
-#   group_by(Strain, O2_uM, Photoperiod) |>
-#   filter(AIC == min(AIC)) |>
-#   ungroup() |>
-#   select(-c(Model, Glance)) |>
-#   unnest(Param) |>
-#   select(-c(statistic)) |>
-#   pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
-#  
-# PURPARStrainO2PhotoWLBestModels
-
-# mutate(Pmax_Ye = if_else(ModelType == "GRCbeta", estimate_a * ((sqrt(estimate_b + estimate_g) - sqrt(estimate_b))/estimate_g)^2, NA))
-
-```
-
-Want platt model for all fits that did not fail and lm for platt models that returned a NULL
+```
+
+# Want platt model for all fits that did not fail and lm for platt models that returned a NULL
 ```{r}
-
+# O2 and Photoperiod nested data frame containing the fits for each photoperiod for each strain
 #filter to keep platt models
-KeepPlattModel <- PURPARStrainO2PhotoNestModels_filtered|>
+KeepPlattModel <- PURPARStrainO2PhotoNestModels|>
   select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
@@
 #filter to keep only the models that failed to fit a platt model, fits by lm remains. 
-KeepLmModel <- PURPARStrainO2PhotoNestModels_filtered|>
+KeepLmModel <- PURPARStrainO2PhotoNestModels|>
   filter(map_lgl(GRCplatt_Model, is.null)) |>
@@
 
- StrainO2Photofiltered_PlattLmModel <- StrainO2Photoperiod_AllModels |>
+# O2 and Photoperiod nested data frame containing the fits for each photoperiod for each strain
+ StrainO2Photoperiod_PlattLmModel <- StrainO2Photoperiod_AllModels |>
    pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
@@
 
+# O2 nested data frame containing the single fit of pooled photoperiods 
  #filter to keep platt models
@@
 
+# O2 nested data frame containing the single fit of pooled photoperiods 
  StrainO2filtered_PlattLmModel <- StrainO2_AllModels|>
@@
  remove(KeepLmModel)
- # remove(PURPARStrainO2NestModels_filtered)
- # remove(PURPARStrainO2PhotoNestModels_filtered)
+ remove(StrainO2Photoperiod_AllModels)
+ remove(StrainO2_AllModels)
 
@@
 
+# O2 nested data frame containing the single fit of pooled photoperiods for each strain 
 StrainO2filtered_PlattLmModel <- StrainO2filtered_PlattLmModel|>
@@
 
-# PURPARStrainO2WLBestModels <- PURPARStrainO2WLBestModels|>
-#   mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
-#          estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
-#          estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
-#          AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC)) 
-#  
-# PURPARStrainO2WLBestModels
-
-StrainO2Photofiltered_PlattLmModel <- StrainO2Photofiltered_PlattLmModel|>
+# O2 and Photoperiod nested data frame containing the fits for each photoperiod for each strain
+StrainO2Photoperiod_PlattLmModel <- StrainO2Photoperiod_PlattLmModel|>
   mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
@@
 
-StrainO2Photofiltered_PlattLmModel
+StrainO2Photoperiod_PlattLmModel
 
@@
 
+# O2 nested data frame containing the single fit of pooled photoperiods for each strain
 StrainO2filtered_PlattLmModel |>
@@
 
-StrainO2Photofiltered_PlattLmModel |>
+# O2 nested data frame containing the single fit of pooled photoperiods for each strain 
+StrainO2Photoperiod_PlattLmModel |>
   unnest(Predict, data) |>
-
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
@@
   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-    labs(title = "Fits to be used for ANOVA comparison to single fit in each [O2]") +
+    labs(title = "Fits to be used for ANOVA comparison to single fit across each strain and [O2]") +
   theme_bw()
@@
 
+# ANOVA comparison of single fit through pooled photoperiods for each strain and [O2] to the fit of each photoperiod in that pool. 
 ```{r compare 1 fit of all photoperiod to each photoperiods using platt or lm}
@@
 # make wider to join with DF that contains the 1 fit through all photoperiods
-Wider_Photoperiods <- StrainO2Photofiltered_PlattLmModel %>% 
-  select(Strain, Photoperiod, O2_uM, Model) %>% 
-  pivot_wider(names_from = Photoperiod, values_from = Model)
+Wider_Photoperiods <- StrainO2Photoperiod_PlattLmModel %>% 
+  select(Strain, Photoperiod, O2_uM, Model, Predict) %>% 
+  pivot_wider(names_from = Photoperiod, values_from = c(Model, Predict))
 
@@
 AllPhotoperiods <- StrainO2filtered_PlattLmModel %>% 
-  select(Strain, O2_uM, Model) %>% 
- rename(All = 'Model')
-
-CombinePhotoperiods <- left_join(Wider_Photoperiods, AllPhotoperiods)
-
-ANOVA_AllPhotoperiods <- CombinePhotoperiods %>% 
-  mutate(twelve = `12`,
-         four = `4`,
-         eight = `8`,
-         sixteen = `16`) %>%
+  select(Strain, O2_uM, Model, Predict, data) %>% 
+ rename(All = 'Model',
+        Predict_all = 'Predict',
+        Data_all = 'data')
+
+AllFitsCombined <- left_join(Wider_Photoperiods, AllPhotoperiods)
+
+ANOVA_AllPhotoperiods <- AllFitsCombined %>% 
+  mutate(twelve = `Model_12`,
+         four = `Model_4`,
+         eight = `Model_8`,
+         sixteen = `Model_16`) %>%
   mutate(fourvsAll = map(map2(four, All, possibly(anova, otherwise = NULL)), tidy),
@@
   select(Strain, O2_uM, name, p.value) %>% 
-  separate(name, into = c("Photoperiod1", "AllPhotoperiod"), sep = "vs")
+  separate(name, into = c("Photoperiod1", "AllPhotoperiod"), sep = "vs") %>% 
+  mutate(pvalue = as.numeric(`p.value`))
 
@@
        caption = "NA = atleast one model did not fit due to lack of data points; 
-       ns = not significantly different from all photoperiod model (same); 
-       dot = significantly different from all photoperiod model")
-
-```
+       ns = not significantly different from all photoperiod model (p value > 0.05); 
+       dot = significantly different from all photoperiod model (p value < 0.05)")
+
+remove(Wider_Photoperiods)
+remove(AllPhotoperiods)
+```
+#Mirelle left off here,
+# Need to use the DF with all data (all the photoperiods that showed complete no growth )
+#next add fits that were sig different, do this dynamically
+```{r Plot fits, fig.height= 20, fig.width= 20 }
+
+scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
+
+AllFitsCombined |>
+   filter(Strain == "MED4") |>
+  unnest(cols = c(Data_all, Predict_all), names_sep = "_", keep_empty = TRUE) |>
+  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
+         OxygenLabel = "Oxygen Concentration (µM)",
+         Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4" )),
+         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) %>%
+  ggplot() +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 6, alpha = 1.0) +
+    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 1, alpha = 0.8) +
+  geom_line(aes(x = Predict_all_PURPhotonDose_day, y = Predict_all_.fitted), size = 1) + 
+ # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
+ labs(title = "MED4", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
+ #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
+  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
+  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
+%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
+    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
+    #                    # limits = c(10^4, 10^7),
+    #                    breaks = c(10^4, 10^5, 10^6)) +
+  scale_x_continuous(label=scientific_10) +
+      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
+    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
+  # coord_cartesian(xlim = c (0, 16)) +
+   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
+  # coord_cartesian(ylim = c (0, 0.07)) +
+  scale_colour_manual(values = MCMIXColours) +
+   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
+   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
+  # scale_y_continuous(limits = c(-0.05,0.050)) +
+  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
+   scale_shape_manual(values = PhotoperiodShapes)  +
+  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
+                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
+ guides(linetype = guide_legend(nrow = 4),
+        fill = "none",
+        colour = guide_legend(nrow = 4)) +
+ guides(shape = guide_legend(nrow = 4)) +
+  theme_bw() +
+   theme( strip.text = element_text(size = 30),
+        axis.title = element_text(size = 30, color = "black"),
+        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
+        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
+        strip.background=element_rect(color="grey87", fill = "grey82"),
+        # strip.background=element_rect(fill = "white"),
+        legend.key.size = unit(1, 'cm'), #change legend key size
+        legend.key.height = unit(1, 'cm'), #change legend key height
+        legend.key.width = unit(0.5, 'cm'), #change legend key width
+        legend.title =  element_text(size = 30),  #change legend title font size
+        legend.text = element_text(size = 30),   #change legend text font size
+        legend.position = "top") +
+  labs( shape = "Photoperiod (h)",
+        color = "Growth Waveband (nm)",
+       linetype = "Photoperiod (h) "
+      )
+
+AllFitsCombined |>
+   filter(Strain == "SS120") |>
+  unnest(cols = c(Data_all, Predict_all), names_sep = "_", keep_empty = TRUE) |>
+  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
+         OxygenLabel = "Oxygen Concentration (µM)",
+         Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4" )),
+         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) %>%
+  ggplot() +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 6, alpha = 1.0) +
+    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 1, alpha = 0.8) +
+  geom_line(aes(x = Predict_all_PURPhotonDose_day, y = Predict_all_.fitted), size = 1) + 
+ # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
+ labs(title = "SS120", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
+ #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
+  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
+  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
+%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
+    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
+    #                    # limits = c(10^4, 10^7),
+    #                    breaks = c(10^4, 10^5, 10^6)) +
+  scale_x_continuous(label=scientific_10) +
+      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
+    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
+  # coord_cartesian(xlim = c (0, 16)) +
+   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
+  # coord_cartesian(ylim = c (0, 0.07)) +
+  scale_colour_manual(values = MCMIXColours) +
+   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
+   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
+  # scale_y_continuous(limits = c(-0.05,0.050)) +
+  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
+   scale_shape_manual(values = PhotoperiodShapes)  +
+  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
+                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
+ guides(linetype = guide_legend(nrow = 4),
+        fill = "none",
+        colour = guide_legend(nrow = 4)) +
+ guides(shape = guide_legend(nrow = 4)) +
+  theme_bw() +
+   theme( strip.text = element_text(size = 30),
+        axis.title = element_text(size = 30, color = "black"),
+        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
+        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
+        strip.background=element_rect(color="grey87", fill = "grey82"),
+        # strip.background=element_rect(fill = "white"),
+        legend.key.size = unit(1, 'cm'), #change legend key size
+        legend.key.height = unit(1, 'cm'), #change legend key height
+        legend.key.width = unit(0.5, 'cm'), #change legend key width
+        legend.title =  element_text(size = 30),  #change legend title font size
+        legend.text = element_text(size = 30),   #change legend text font size
+        legend.position = "top") +
+  labs( shape = "Photoperiod (h)",
+        color = "Growth Waveband (nm)",
+       linetype = "Photoperiod (h) "
+      )
+
+AllFitsCombined |>
+   filter(Strain == "MIT9313") |>
+  unnest(cols = c(Data_all, Predict_all), names_sep = "_", keep_empty = TRUE) |>
+  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
+         OxygenLabel = "Oxygen Concentration (µM)",
+         Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4" )),
+         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) %>%
+  ggplot() +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 6, alpha = 1.0) +
+    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 1, alpha = 0.8) +
+  geom_line(aes(x = Predict_all_PURPhotonDose_day, y = Predict_all_.fitted), size = 1) + 
+ # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
+ labs(title = "MIT9313", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
+ #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
+  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
+  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
+%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
+    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
+    #                    # limits = c(10^4, 10^7),
+    #                    breaks = c(10^4, 10^5, 10^6)) +
+  scale_x_continuous(label=scientific_10) +
+      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
+    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
+  # coord_cartesian(xlim = c (0, 16)) +
+   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
+  # coord_cartesian(ylim = c (0, 0.07)) +
+  scale_colour_manual(values = MCMIXColours) +
+   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
+   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
+  # scale_y_continuous(limits = c(-0.05,0.050)) +
+  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
+   scale_shape_manual(values = PhotoperiodShapes)  +
+  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
+                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
+ guides(linetype = guide_legend(nrow = 4),
+        fill = "none",
+        colour = guide_legend(nrow = 4)) +
+ guides(shape = guide_legend(nrow = 4)) +
+  theme_bw() +
+   theme( strip.text = element_text(size = 30),
+        axis.title = element_text(size = 30, color = "black"),
+        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
+        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
+        strip.background=element_rect(color="grey87", fill = "grey82"),
+        # strip.background=element_rect(fill = "white"),
+        legend.key.size = unit(1, 'cm'), #change legend key size
+        legend.key.height = unit(1, 'cm'), #change legend key height
+        legend.key.width = unit(0.5, 'cm'), #change legend key width
+        legend.title =  element_text(size = 30),  #change legend title font size
+        legend.text = element_text(size = 30),   #change legend text font size
+        legend.position = "top") +
+  labs( shape = "Photoperiod (h)",
+        color = "Growth Waveband (nm)",
+       linetype = "Photoperiod (h) "
+      )
+
+```
+
 # Remove the photoperiods from the model that are significantly different from the ANOVA run on the single fit against each individual photoperiod.   
@@
                                         TRUE ~ 0))  |>
+  filter(removephotoperiod == 0,
+          PURPhotonDose_day <= 1.5e+06) |>
   nest(data = -c("Strain","O2_uM")) |>
@@
  # remove(PURPARStrainO2NestModels_filtered)
- # remove(PURPARStrainO2PhotoNestModels_filtered)
+ # remove(PURPARStrainO2PhotoNestModels)
 
@@
 
-StrainO2Photofiltered_PlattLmModel |>
+StrainO2filteredPhotoperiod_PlattLmModel |>
   unnest(Predict, data) |>
@@
   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-    labs(title = "Fits to be used for ANOVA comparison to single fit in each [O2]") +
+    labs(title = "Photoperiods included in the single fit for each [O2]") +
   theme_bw()
@@
 ```
-# ANOVA on new model with signifiacntly different fits removed from the single fit.
+
+# ANOVA on new model with significantly different fits removed from the single fit.
 ```{r compare 1 fit of all photoperiod to each photoperiods using platt or lm}
@@
 AllPhotoperiods <- StrainO2filteredPhotoperiod_PlattLmModel %>% 
-  select(Strain, O2_uM, Model) %>% 
- rename(All = 'Model')
-
-CombinePhotoperiods <- left_join(Wider_Photoperiods, AllPhotoperiods)
-
-ANOVA_AllPhotoperiods <- CombinePhotoperiods %>% 
+  select(Strain, O2_uM, Model, Predict) %>% 
+ rename(All = 'Model',
+        Predict_all = 'Predict')
+
+AllFitsCombined_filtered <- left_join(Wider_Photoperiods, AllPhotoperiods)
+
+ANOVA_AllPhotoperiods <- AllFitsCombined_filtered %>% 
   mutate(twelve = `12`,
@@
 ```
-
-# Doug said not to do this
-```{r ANOVA between photoperiods platt model}
-
-# ANOVA_Photoperiods <- PURPARStrainO2PhotoNestModels %>% 
-#   select(Strain, Photoperiod, O2_uM, GRCplatt_Model) %>% 
-#   pivot_wider(names_from = Photoperiod, values_from = GRCplatt_Model) %>% 
-#   mutate(twelve = `12`,
-#          four = `4`,
-#          eight = `8`,
-#          sixteen = `16`) %>% 
-#   # select(-c(eight, four)) %>% 
-#   # filter(!map_lgl(twelve, is.null),
-#   #        !map_lgl(sixteen, is.null)) %>% 
-#   mutate(fourvseight = map(map2(four, eight, possibly(anova, otherwise = NULL)), tidy),
-#          fourvstwelve = map(map2(four, twelve, possibly(anova, otherwise = NULL)), tidy),
-#          fourvssixteen = map(map2(four, sixteen, possibly(anova, otherwise = NULL)), tidy),
-#          eightvstwelve = map(map2(eight, twelve, possibly(anova, otherwise = NULL)), tidy),
-#          eightvssixteen = map(map2(eight, sixteen, possibly(anova, otherwise = NULL)), tidy),
-#          twelvevssixteen =map(map2(twelve, sixteen, possibly(anova, otherwise = NULL)), tidy)) %>% 
-#   select(Strain, O2_uM, fourvseight, fourvstwelve, fourvssixteen, eightvstwelve, eightvssixteen, twelvevssixteen) %>% 
-#   pivot_longer(cols = c(fourvseight, fourvstwelve, fourvssixteen, eightvstwelve, eightvssixteen, twelvevssixteen)) %>% 
-#   unnest(value, keep_empty = TRUE) %>% 
-#   filter(is.na(term) & is.na(p.value) |
-#            !is.na(term) & !is.na(p.value)) %>%
-#   select(Strain, O2_uM, name, p.value) %>% 
-#   separate(name, into = c("Photoperiod1", "Photoperiod2"), sep = "vs") 
-# 
-# # %>% 
-# #   mutate(p.value = case_when(is.na(p.value) ~ 0,
-# #                              TRUE ~ p.value)) # Changed all failed fits to p.value = 0
-#   # mutate(pval = pluck(value, "p.value", 2))
-#   
-# # ANOVA_Photoperiods %>% 
-# #     mutate(Photoperiod1 = factor(Photoperiod1, levels = c("four", "eight", "twelve", "sixteen")),
-# #            Photoperiod2 = factor(Photoperiod2, levels = c( "four","eight", "twelve", "sixteen"))) %>% 
-# #   ggplot() +
-# #   geom_point(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(`p.value` < 0.05)) +
-# #   geom_text(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(`p.value` > 0.05), label = "ns") +
-# #   geom_text(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(is.na(`p.value`)), label = "NA") +
-# #   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
-# #   labs(caption = "NA = atleast one model did not fit; 
-# #        ns = not significantly different from each other (same); 
-# #        dot = significantly different from each other")
-# 
-# 
-# 
-# ANOVA_Photoperiods %>% 
-#   mutate(Photoperiod1 = as.numeric(case_when(Photoperiod1 == 'four' ~ 4,
-#                                             Photoperiod1 == 'eight' ~ 8,
-#                                             Photoperiod1 == 'twelve' ~ 12,
-#                                             Photoperiod1 == 'sixteen' ~ 16))) %>% 
-#   mutate(Photoperiod2 = as.numeric(case_when(Photoperiod2 == 'four' ~ 4,
-#                                             Photoperiod2 == 'eight' ~ 8,
-#                                             Photoperiod2 == 'twelve' ~ 12,
-#                                             Photoperiod2 == 'sixteen' ~ 16)),
-#          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-#          Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>% 
-#     # mutate(Photoperiod2 = factor(Photoperiod2, levels = c("four", "eight", "twelve", "sixteen")),
-#     #        Photoperiod1 = factor(Photoperiod1, levels = c( "four","eight", "twelve", "sixteen"))) %>% 
-#   ggplot() +
-#   geom_point(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(`p.value` < 0.05)) +
-#   geom_text(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(`p.value` > 0.05), label = "ns") +
-#   geom_text(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(is.na(`p.value`)), label = "NA") +
-#   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
-#   scale_y_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
-#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
-#   labs(title = "ANOVA compare GRCplatt_Model",
-#        caption = "NA = atleast one model did not fit; 
-#        ns = not significantly different from each other (same); 
-#        dot = significantly different from each other")
-# 
-#
-
-```
-4 h photoperiod is almost always different from others. 
-8 h photoperiod is different for MED4 at 25 uM; MIT9313, 8 and 12 are different at 2.5. all others are not significantly different from one another
-
-#now do ANOVA on fits that include lm for conditions where no growth occured across photoperiod
-# Doug said this is not what I should do, only ANOVA of 1 fit through all photoperiod against each photoperiod as done chunk above.
-```{r ANOVA using best model platt or lm}
-
-# # PURPARStrainO2PhotoperiodBestModels <- PURPARStrainO2PhotoNestModels |>
-# #   select(-c(data)) |>
-# #   pivot_longer(cols = -c(Strain, O2_uM, Photoperiod)) |>
-# #   drop_na(value) |>
-# #   filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")) |>
-# #   separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-# #   pivot_wider(names_from = Output, values_from = value) |>
-# #   filter(!map_lgl(Model, is.null)) |>
-# #   mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
-# #   group_by(Strain, O2_uM, Photoperiod) |>
-# #   filter(AIC == min(AIC)) |>
-# #   ungroup()
-# 
-# ANOVA_BestModel <- StrainO2Photoperiod_PlattLmModel %>% 
-#   select(Strain, Photoperiod, O2_uM, Model) %>% 
-#   pivot_wider(names_from = Photoperiod, values_from = Model) %>% 
-#   mutate(twelve = `12`,
-#          four = `4`,
-#          eight = `8`,
-#          sixteen = `16`) %>% 
-#   # select(-c(eight, four)) %>% 
-#   # filter(!map_lgl(twelve, is.null),
-#   #        !map_lgl(sixteen, is.null)) %>% 
-#   mutate(fourvseight = map(map2(four, eight, possibly(anova, otherwise = 0)), tidy),
-#          fourvstwelve = map(map2(four, twelve, possibly(anova, otherwise = 0)), tidy),
-#          fourvssixteen = map(map2(four, sixteen, possibly(anova, otherwise = 0)), tidy),
-#          eightvstwelve = map(map2(eight, twelve, possibly(anova, otherwise = 0)), tidy),
-#          eightvssixteen = map(map2(eight, sixteen, possibly(anova, otherwise = 0)), tidy),
-#          twelvevssixteen =map(map2(twelve, sixteen, possibly(anova, otherwise = 0)), tidy)) %>% 
-#   select(Strain, O2_uM, fourvseight, fourvstwelve, fourvssixteen, eightvstwelve, eightvssixteen, twelvevssixteen) %>% 
-#   pivot_longer(cols = c(fourvseight, fourvstwelve, fourvssixteen, eightvstwelve, eightvssixteen, twelvevssixteen)) %>% 
-#   unnest(value, keep_empty = TRUE) %>% 
-#   filter(is.na(term) & is.na(p.value) |
-#            !is.na(term) & !is.na(p.value)) %>%
-#   select(Strain, O2_uM, name, p.value) %>% 
-#   separate(name, into = c("Photoperiod1", "Photoperiod2"), sep = "vs") 
-# 
-# # %>% 
-# #   mutate(p.value = case_when(is.na(p.value) ~ 0,
-# #                              TRUE ~ p.value)) # Changed all failed fits to p.value = 0
-#   # mutate(pval = pluck(value, "p.value", 2))
-#   
-# # ANOVA_Photoperiods %>% 
-# #     mutate(Photoperiod1 = factor(Photoperiod1, levels = c("four", "eight", "twelve", "sixteen")),
-# #            Photoperiod2 = factor(Photoperiod2, levels = c( "four","eight", "twelve", "sixteen"))) %>% 
-# #   ggplot() +
-# #   geom_point(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(`p.value` < 0.05)) +
-# #   geom_text(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(`p.value` > 0.05), label = "ns") +
-# #   geom_text(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(is.na(`p.value`)), label = "NA") +
-# #   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
-# #   labs(caption = "NA = atleast one model did not fit; 
-# #        ns = not significantly different from each other (same); 
-# #        dot = significantly different from each other")
-# 
-# 
-# 
-# ANOVA_BestModel %>% 
-#   mutate(Photoperiod1 = as.numeric(case_when(Photoperiod1 == 'four' ~ 4,
-#                                             Photoperiod1 == 'eight' ~ 8,
-#                                             Photoperiod1 == 'twelve' ~ 12,
-#                                             Photoperiod1 == 'sixteen' ~ 16))) %>% 
-#   mutate(Photoperiod2 = as.numeric(case_when(Photoperiod2 == 'four' ~ 4,
-#                                             Photoperiod2 == 'eight' ~ 8,
-#                                             Photoperiod2 == 'twelve' ~ 12,
-#                                             Photoperiod2 == 'sixteen' ~ 16)),
-#          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-#          Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
-#     # mutate(Photoperiod2 = factor(Photoperiod2, levels = c("four", "eight", "twelve", "sixteen")),
-#     #        Photoperiod1 = factor(Photoperiod1, levels = c( "four","eight", "twelve", "sixteen"))) %>% 
-#   ggplot() +
-#   geom_point(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(`p.value` < 0.05)) +
-#   geom_text(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(`p.value` > 0.05), label = "ns") +
-#   geom_text(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(is.na(`p.value`)), label = "NA") +
-#     geom_text(aes(x = Photoperiod1, y = Photoperiod2), data = . %>% filter(is.nan(`p.value`)), label = "Not a number") + #tried this did not work
-#   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
-#   scale_y_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
-#   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
-#   labs(title = "ANOVA compare Best Model",
-#        caption = "NA = atleast one model did not fit; 
-#        ns = not significantly different from each other (same); 
-#        dot = significantly different from each other")
-#
-
-```
-The no growths, linear fit return NaN in ANOVA
 

### 2024-02-07 Code/Manuscript_O2.Rmd
fixed fig caps

@@
 
-MED4GAM_cap <- glue("** The Generalized Additive Models (GAM) for red light at 660 nm and blue light at 450 nm.
-The x-axis is photoperiod (h) and the y-axis is the Photosynethetic Active Radiation (PAR) (µmol photons m^-2^ s^-1^) **",
-                       "Rows are...",
-                       "Columns are...",
+MED4GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MED4 grown under 660 nm (red) and 450 nm (blue) light.**",
+                    "The x-axis is photoperiod (h).",
+                    "The y-axis is actinic Photosynethetic Active Radiation (PAR) level (µmol photons m^-2^ s^-1^).",
+                    "**A.** represents the model under 250 µM of O~2~ and red light.",
+                    "**B.** represents the model under 25 µM of O~2~ and red light.",
+                    "**C.** represents the model under 250 µM of O~2~ and blue light.",
+                    "**D.** represents the model under 25 µM of O~2~ and blue light.",
+                    "The legend represents a colour gradient of growth rate from no growth (white) to 1 d^-1^ (dark blue).",
+                    "The labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",
 
@@
 
-SS120GAM_cap <- glue("** The Generalized Additive Models (GAM) for red light at 660 nm and blue light at 450 nm.
-The x-axis is photoperiod (h) and the y-axis is the Photosynethetic Active Radiation (PAR) (µmol photons m^-2^ s^-1^) **",
-                       "Rows are...",
-                       "Columns are...",
+SS120GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* SS120 grown under 660 nm (red) and 450 nm (blue) light.**",
+                    "The x-axis is photoperiod (h).",
+                    "The y-axis is actinic Photosynethetic Active Radiation (PAR) level (µmol photons m^-2^ s^-1^).",
+                    "**A.** represents the model under 250 µM of O~2~ and red light.",
+                    "**B.** represents the model under 25 µM of O~2~ and red light.",
+                    "**C.** represents the model under 250 µM of O~2~ and blue light.",
+                    "**D.** represents the model under 25 µM of O~2~ and blue light.",
+                    "The legend represents a colour gradient of growth rate from no growth (white) to 1 d^-1^ (dark blue).",
+                    "The labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",
 
@@
 
-MIT9313GAM_cap <- glue("** The Generalized Additive Models (GAM) for red light at 660 nm and blue light at 450 nm.
-The x-axis is photoperiod (h) and the y-axis is the Photosynethetic Active Radiation (PAR) (µmol photons m^-2^ s^-1^) **",
-                       "Rows are...",
-                       "Columns are...",
+MIT9313GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 grown under 660 nm (red) and 450 nm (blue) light.**",
+                    "The x-axis is photoperiod (h).",
+                    "The y-axis is actinic Photosynethetic Active Radiation (PAR) level (µmol photons m^-2^ s^-1^).",
+                    "**A.** represents the model under 250 µM of O~2~ and red light.",
+                    "**B.** represents the model under 25 µM of O~2~ and red light.",
+                    "**C.** represents the model under 2.5 µM of O~2~ and red light.",
+                    "**D.** represents the model under 250 µM of O~2~ and blue light.",
+                    "**E.** represents the model under 25 µM of O~2~ and blue light.",
+                    "**F.** represents the model under 2.5 µM of O~2~ and blue light.",
+                    "The legend represents a colour gradient of growth rate from no growth (white) to 1 d^-1^ (dark blue).",
+                    "The labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",
 
@@
                     "Colors represent the actinic spectral waveband (nm).",
-                    "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles",
+                    "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
 

### 2024-02-12 Code/ManuscriptPURFits.Rmd
added fits to plots

@@
 Also removed data if no growth occurred for an O2 and photoperiod combination so that the model including all photoperiods would not be skewed towards zero.
-As per Amanda and Doug's advice, filtered out PUR d-1 above 1.5e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
+As per Amanda and Doug's advice, filtered out PUR d-1 above 2.0e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
 PURPARStrainO2NestModels_filtered <- PURPARFits_dummy |>
@@
    filter(remove == 0,
-          PURPhotonDose_day <= 1.5e+06) |>
+          PURPhotonDose_day <= 2.0e+06) |>
   nest(data = -c("Strain","O2_uM")) |>
@@
          )
+
+# Nest all data before photoperiods with no growths were filtered out
+NoFilter <- PURPARFits_dummy |>
+   filter(PURPhotonDose_day <= 2.0e+06) |>
+  mutate(Photoperiod_all = Photoperiod) %>% 
+  nest(Data_all = -c("Strain","O2_uM"))
+
+ # Join nested df with all data to df containing filtered data 
+  PURPARStrainO2NestModels_filtered <- full_join(PURPARStrainO2NestModels_filtered, NoFilter) %>% 
+    rename(Data_filtered = 'data')
 
@@
 PURPARStrainO2PhotoNestModels <- PURPARFits_dummy |>
-   filter(PURPhotonDose_day <= 1.5e+06) |>
+   filter(PURPhotonDose_day <= 2.0e+06) |>
  nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
@@
 
+UnnestTest <- PURPARStrainO2NestModels_filtered %>% 
+  # unnest(Data_all, names_sep = "_", keep_empty = TRUE) %>% 
+  unnest(GRCplatt_Predict, keep_empty = TRUE)
+
 ```
@@
 #   filter(!map_lgl(GRC_Model, is.null)) |> #https://stackoverflow.com/questions/57336319/how-to-filter-out-null-elements-of-tibbles-list-column
+
 PURPARStrainO2NestModels_filtered|>
   filter(!map_lgl(GRCplatt_Model, is.null)) |>
-  unnest(GRCplatt_Predict, data) |>
+  unnest(GRCplatt_Predict, Data_filtered) |>
    mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
@@
   # select(-c(data)) |>
-  pivot_longer(cols = -c(Strain, O2_uM, data)) |>
+  pivot_longer(cols = -c(Strain, O2_uM, Data_filtered, Data_all)) |>
   drop_na(value) |>
@@
  remove(KeepLmModel)
- remove(StrainO2Photoperiod_AllModels)
- remove(StrainO2_AllModels)
+ # remove(StrainO2Photoperiod_AllModels)
+ # remove(StrainO2_AllModels)
 
@@
 StrainO2filtered_PlattLmModel |>
-  unnest(Predict, data) |>
+  unnest(Predict, Data_filtered) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
@@
   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
-    labs(title = "Single fit for each [O2]- all photoperiods included that had growth") +
+    labs(title = "Single fit for each strain in each [O2]- all photoperiods included that had growth") +
   theme_bw()
 
-# O2 nested data frame containing the single fit of pooled photoperiods for each strain 
+# O2 and Photoperiod nested data frame containing the fits for each photoperiod for each strain
 StrainO2Photoperiod_PlattLmModel |>
@@
 Wider_Photoperiods <- StrainO2Photoperiod_PlattLmModel %>% 
-  select(Strain, Photoperiod, O2_uM, Model, Predict) %>% 
-  pivot_wider(names_from = Photoperiod, values_from = c(Model, Predict))
+  select(Strain, Photoperiod, O2_uM, Model, Predict, data) %>% 
+  pivot_wider(names_from = Photoperiod, values_from = c(Model, Predict, data))
+
+# Wider_Photoperiods <- StrainO2Photoperiod_PlattLmModel %>% 
+#   mutate(PhotoperiodLabel = Photoperiod) %>% 
+#   select(Strain, Photoperiod, O2_uM, Model, Predict, data, PhotoperiodLabel) %>% 
+#   pivot_wider(names_from = PhotoperiodLabel, values_from = c(Model, Predict)) %>% 
+#     unnest(data) %>% 
+#   group_by(Strain, O2_uM) %>% 
+#     nest(Data_Photoperiod = -c(Strain, O2_uM, Model_16,Model_12, Model_8, Model_4, Predict_16, Predict_12, Predict_8, Predict_4)) %>% 
+#   filter(!is.null(Model_16) & !is.null(Predict_16) |
+#            !is.null(Model_12) & !is.null(Predict_12)|
+#            !is.null(Model_8) & !is.null(Predict_8) |
+#            !is.null(Model_4) & !is.null(Predict_4))
+
+# Wider_Photoperiods <- StrainO2Photoperiod_PlattLmModel %>% 
+#   select(Strain, Photoperiod, O2_uM, Model, Predict) %>% 
+#   pivot_wider(names_from = Photoperiod, values_from = c(Model, Predict)) %>% 
+#   unnest(Predict_16, keep_empty = TRUE) %>% 
+#     mutate(Photoperiod = 16)%>% 
+#     nest(Predict_16 = -c(Strain, O2_uM, Model_16, Model_12, Model_8, Model_4, Predict_12, Predict_8, Predict_4)) %>% 
+#   unnest(Predict_12, keep_empty = TRUE) %>% 
+#     mutate(Photoperiod = 12)%>% 
+#     nest(Predict_12 = -c(Strain, O2_uM, Model_16, Model_12, Model_8, Model_4, Predict_16, Predict_8, Predict_4))%>% 
+#   unnest(Predict_8, keep_empty = TRUE) %>% 
+#     mutate(Photoperiod = 8)%>% 
+#     nest(Predict_8 = -c(Strain, O2_uM, Model_16, Model_12, Model_8, Model_4, Predict_16, Predict_12, Predict_4))%>% 
+#   unnest(Predict_4, keep_empty = TRUE) %>% 
+#     mutate(Photoperiod = 4)%>% 
+#     nest(Predict_4 = -c(Strain, O2_uM, Model_16, Model_12, Model_8, Model_4, Predict_16, Predict_12, Predict_8))
 
@@
 AllPhotoperiods <- StrainO2filtered_PlattLmModel %>% 
-  select(Strain, O2_uM, Model, Predict, data) %>% 
+  select(Strain, O2_uM, Model, Predict, Data_filtered, Data_all) %>% 
  rename(All = 'Model',
-        Predict_all = 'Predict',
-        Data_all = 'data')
+        Predict_all = 'Predict')
 
@@
   separate(name, into = c("Photoperiod1", "AllPhotoperiod"), sep = "vs") %>% 
-  mutate(pvalue = as.numeric(`p.value`))
+  mutate(pvalue = signif(`p.value`, digits = 2))
 
@@
   ggplot() +
-  geom_point(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(`p.value` < 0.05)) +
-  geom_text(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(`p.value` > 0.05), label = "ns") +
-  geom_text(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(is.na(`p.value`)), label = "NA") +
+  geom_text(aes(x = Photoperiod1, y = AllPhotoperiod, label = pvalue), data = . %>% filter(pvalue < 0.05), size = 2.5) +
+  geom_text(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(pvalue > 0.05), label = "ns") +
+  geom_text(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(is.na(pvalue)), label = "NA") +
   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
@@
        ns = not significantly different from all photoperiod model (p value > 0.05); 
-       dot = significantly different from all photoperiod model (p value < 0.05)")
+       numbers = significantly different pvalues from all photoperiod model (p value < 0.05)")
 
@@
 ```
+
+# Unnest predict df for each photoperiod in order to plot fitted 
+```{r}
+Unnest_16 <- AllFitsCombined %>% 
+  select(c(Strain, O2_uM, Predict_16)) %>%  
+  unnest(Predict_16, keep_empty = TRUE) %>% 
+  mutate(FitCategory = "Photoperiod16")
+
+Unnest_12 <- AllFitsCombined %>% 
+  select(c(Strain, O2_uM, Predict_12)) %>%  
+  unnest(Predict_12, keep_empty = TRUE) %>% 
+  mutate(FitCategory = "Photoperiod12")
+
+Unnest_8 <- AllFitsCombined %>% 
+  select(c(Strain, O2_uM, Predict_8)) %>%  
+  unnest(Predict_8, keep_empty = TRUE) %>% 
+  mutate(FitCategory = "Photoperiod8")
+
+Unnest_4 <- AllFitsCombined %>% 
+  select(c(Strain, O2_uM, Predict_4)) %>%  
+  unnest(Predict_4, keep_empty = TRUE) %>% 
+  mutate(FitCategory = "Photoperiod4")
+
+Unnest_all <- AllFitsCombined %>% 
+  select(c(Strain, O2_uM, Predict_all, Data_all)) %>% 
+  # unnest(Data_all, keep_empty = TRUE) %>% 
+  unnest(Predict_all, keep_empty = TRUE) %>% 
+  mutate(FitCategory = "Pooled")
+
+ForFitPlots <- bind_rows(Unnest_all, Unnest_16, Unnest_12, Unnest_8, Unnest_4)
+
+remove(Unnest_16, Unnest_12, Unnest_8, Unnest_4, Unnest_all)
+
+```
+
 #Mirelle left off here,
@@
 
-AllFitsCombined |>
+ForFitPlots |>
     filter(Strain == "MED4") |>
-  unnest(cols = c(Data_all, Predict_all), names_sep = "_", keep_empty = TRUE) |>
+    unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
+  # unnest(Predict_4, names_sep = "_", keep_empty = TRUE) |>
+  # unnest(Predict_8, names_sep = "_", keep_empty = TRUE) |>
+  # unnest(Predict_12, names_sep = "_", keep_empty = TRUE) |>
+  # unnest(Predict_16, names_sep = "_", keep_empty = TRUE) |>
   mutate(PhotoperiodLabel_title = "Photoperiod (h)",
          OxygenLabel = "Oxygen Concentration (µM)",
-         Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4" )),
+         Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4")),
          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) %>%
   ggplot()  +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 6, alpha = 1.0) +
-    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 1, alpha = 0.8) +
-  geom_line(aes(x = Predict_all_PURPhotonDose_day, y = Predict_all_.fitted), size = 1) + 
- # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
+   geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 6, alpha = 0.8) +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 2, alpha = 1.0) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), data = . %>% filter(FitCategory == "Pooled"), size = 1) + 
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, linetype = "twodash"), data = . %>% filter(FitCategory == "Photoperiod16" & O2_uM == 25), size = 0.5) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, linetype = "dotdash"), data = . %>% filter(FitCategory == "Photoperiod8"), size = 0.5) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted,  linetype = "aa"), data = . %>% filter(FitCategory == "Photoperiod4"), size = 0.5) +
+  # geom_line(aes(x = PURPhotonDose_day, y = .fitted, shape = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), data = . %>% filter(FitCategory == "Photoperiod4"), size = 0.5) +
  labs(title = "MED4", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
@@
   # scale_y_continuous(limits = c(-0.05,0.050)) +
-  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
+   scale_linetype_manual(values = c("solid", "twodash", "dotted","dotdash", "aa"),labels = c("Pooled", "16 hr", "12 hr", "8 hr", "4 hr")) +
    scale_shape_manual(values = PhotoperiodShapes)  +
@@
                     labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
- guides(linetype = guide_legend(nrow = 4),
+ guides(linetype = guide_legend(nrow = 5),
         fill = "none",
@@
         legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title =  element_text(size = 30),  #change legend title font size
-        legend.text = element_text(size = 30),   #change legend text font size
+        legend.title =  element_text(size = 25),  #change legend title font size
+        legend.text = element_text(size = 25),   #change legend text font size
         legend.position = "top") +
@@
   ggplot()  +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 6, alpha = 1.0) +
-    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 1, alpha = 0.8) +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 6, alpha = 1.0) +
+    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 2, alpha = 0.8) +
   geom_line(aes(x = Predict_all_PURPhotonDose_day, y = Predict_all_.fitted), size = 1) + 
@@
   ggplot() +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 6, alpha = 1.0) +
-    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 1, alpha = 0.8) +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 6, alpha = 1.0) +
+    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 2, alpha = 0.8) +
   geom_line(aes(x = Predict_all_PURPhotonDose_day, y = Predict_all_.fitted), size = 1) + 
@@
 Also removed data if no growth occurred for an O2 and photoperiod combination so that the model including all photoperiods would not be skewed towards zero.
-As per Amanda and Doug's advice, filtered out PUR d-1 above 1.5e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
+As per Amanda and Doug's advice, filtered out PUR d-1 above 2.0e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
 PURPARStrainO2NestModels_filteredPhotoperiods <- PURPARFits_dummy |>
@@
    filter(remove == 0,
-          PURPhotonDose_day <= 1.5e+06) |>
+          PURPhotonDose_day <= 2.0e+06) |>
   mutate(removephotoperiod =  case_when(Strain == "MED4" & Photoperiod == 4 ~ 1,
@@
   filter(removephotoperiod == 0,
-          PURPhotonDose_day <= 1.5e+06) |>
+          PURPhotonDose_day <= 2.0e+06) |>
   nest(data = -c("Strain","O2_uM")) |>

### 2024-02-12 Code/ManuscriptPURFits.Rmd
Testing adding fits to 1 plot

@@
 As per Amanda and Doug's advice, filtered out PUR d-1 above 2.0e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
-PURPARStrainO2NestModels_filtered <- PURPARFits_dummy |>
+PURPARStrainO2NestModels <- PURPARFits_dummy |>
   mutate(remove = case_when(Strain == "MED4" & Photoperiod == 4 ~ 1,
@@
                             TRUE ~ 0)) |>
-   filter(remove == 0,
-          PURPhotonDose_day <= 2.0e+06) |>
+   filter(remove == 0) |>
+          # PURPhotonDose_day <= 2.0e+06) |>
   nest(data = -c("Strain","O2_uM")) |>
@@
 NoFilter <- PURPARFits_dummy |>
-   filter(PURPhotonDose_day <= 2.0e+06) |>
+   # filter(PURPhotonDose_day <= 2.0e+06) |>
   mutate(Photoperiod_all = Photoperiod) %>% 
@@
  # Join nested df with all data to df containing filtered data 
-  PURPARStrainO2NestModels_filtered <- full_join(PURPARStrainO2NestModels_filtered, NoFilter) %>% 
+  PURPARStrainO2NestModels <- full_join(PURPARStrainO2NestModels, NoFilter) %>% 
     rename(Data_filtered = 'data')
+
+remove(NoFilter)
 
@@
 PURPARStrainO2PhotoNestModels <- PURPARFits_dummy |>
-   filter(PURPhotonDose_day <= 2.0e+06) |>
+   # filter(PURPhotonDose_day <= 2.0e+06) |>
  nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
@@
 
-UnnestTest <- PURPARStrainO2NestModels_filtered %>% 
-  # unnest(Data_all, names_sep = "_", keep_empty = TRUE) %>% 
-  unnest(GRCplatt_Predict, keep_empty = TRUE)
-
 ```
@@
 
-PURPARStrainO2NestModels_filtered|>
+PURPARStrainO2NestModels|>
   filter(!map_lgl(GRCplatt_Model, is.null)) |>
@@
   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) + 
-  labs(title = "PURPARStrainO2NestModels_filtered Platt") +
+  labs(title = "PURPARStrainO2NestModels Platt") +
   theme_bw()
@@
  #filter to keep platt models
-KeepPlattModel <- PURPARStrainO2NestModels_filtered|>
+KeepPlattModel <- PURPARStrainO2NestModels|>
   select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
@@
 #filter to keep only the models that failed to fit a platt model, fits by lm remains. 
-KeepLmModel <- PURPARStrainO2NestModels_filtered|>
+KeepLmModel <- PURPARStrainO2NestModels|>
   filter(map_lgl(GRCplatt_Model, is.null)) |>
@@
  remove(KeepLmModel)
- # remove(StrainO2Photoperiod_AllModels)
- # remove(StrainO2_AllModels)
+  remove(StrainO2Photoperiod_AllModels)
+  remove(StrainO2_AllModels)
 
@@
 
-# Unnest predict df for each photoperiod in order to plot fitted 
+# Unnest predict df for each photoperiod and join with pooled fit in order to plot fitted 
 ```{r}
+
 Unnest_16 <- AllFitsCombined %>% 
@@
   unnest(Predict_16, keep_empty = TRUE) %>% 
-  mutate(FitCategory = "Photoperiod16")
+  mutate(FitCategory = "sixteen",
+         Photoperiod = 16)
 
@@
   unnest(Predict_12, keep_empty = TRUE) %>% 
-  mutate(FitCategory = "Photoperiod12")
+  mutate(FitCategory = "twelve",
+         Photoperiod = 12)
 
@@
   unnest(Predict_8, keep_empty = TRUE) %>% 
-  mutate(FitCategory = "Photoperiod8")
+  mutate(FitCategory = "eight",
+         Photoperiod = 8)
 
@@
   unnest(Predict_4, keep_empty = TRUE) %>% 
-  mutate(FitCategory = "Photoperiod4")
-
-Unnest_all <- AllFitsCombined %>% 
+  mutate(FitCategory = "four",
+         Photoperiod = 4)
+
+Unnest_pooled <- AllFitsCombined %>% 
   select(c(Strain, O2_uM, Predict_all, Data_all)) %>% 
@@
 
-ForFitPlots <- bind_rows(Unnest_all, Unnest_16, Unnest_12, Unnest_8, Unnest_4)
-
-remove(Unnest_16, Unnest_12, Unnest_8, Unnest_4, Unnest_all)
+ForFitPlots <- bind_rows(Unnest_pooled, Unnest_16, Unnest_12, Unnest_8, Unnest_4)
+
+remove(Unnest_16, Unnest_12, Unnest_8, Unnest_4, Unnest_pooled)
+
+ForFitPlots <- left_join(ForFitPlots, ANOVA_AllPhotoperiods %>% select(Strain, O2_uM, Photoperiod1, pvalue), by = c("Strain", "O2_uM", "FitCategory" = "Photoperiod1"))
 
@@
   geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 2, alpha = 1.0) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), data = . %>% filter(FitCategory == "Pooled"), size = 1) + 
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted, linetype = "twodash"), data = . %>% filter(FitCategory == "Photoperiod16" & O2_uM == 25), size = 0.5) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted, linetype = "dotdash"), data = . %>% filter(FitCategory == "Photoperiod8"), size = 0.5) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted,  linetype = "aa"), data = . %>% filter(FitCategory == "Photoperiod4"), size = 0.5) +
-  # geom_line(aes(x = PURPhotonDose_day, y = .fitted, shape = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), data = . %>% filter(FitCategory == "Photoperiod4"), size = 0.5) +
- labs(title = "MED4", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), data = . %>% filter(FitCategory == "Pooled"), size = 2, color = "Blue") + 
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, linetype = "twodash"), data = . %>% filter(FitCategory == "sixteen" & O2_uM == 25), size = 0.5) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, linetype = "dotdash"), data = . %>% filter(FitCategory == "eight"), size = 0.5) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted,  linetype = "aa"), data = . %>% filter(FitCategory == "four"), size = 0.5) +
+  # geom_line(aes(x = PURPhotonDose_day, y = .fitted, shape = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), data = . %>% filter(FitCategory == "four"), size = 0.5) +
+ # labs(title = "MED4", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
  #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
@@
   # scale_y_continuous(limits = c(-0.05,0.050)) +
-   scale_linetype_manual(values = c("solid", "twodash", "dotted","dotdash", "aa"),labels = c("Pooled", "16 hr", "12 hr", "8 hr", "4 hr")) +
+   scale_linetype_manual(values = c("twodash", "dotdash", "aa"),labels = c("16 hr", "8 hr", "4 hr")) +
    scale_shape_manual(values = PhotoperiodShapes)  +
@@
 
-# Remove the photoperiods from the model that are significantly different from the ANOVA run on the single fit against each individual photoperiod.   
-```{r}
-# model with dummy dark, 0 PAR,  growth rates.
-Also removed data if no growth occurred for an O2 and photoperiod combination so that the model including all photoperiods would not be skewed towards zero.
-As per Amanda and Doug's advice, filtered out PUR d-1 above 2.0e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
-PURPARStrainO2NestModels_filteredPhotoperiods <- PURPARFits_dummy |>
-  mutate(remove = case_when(Strain == "MED4" & Photoperiod == 4 ~ 1,
-                            Strain == "MED4" & O2_uM == 25 & Photoperiod == 8 & WL == "WW" ~ 1,
-                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 16 ~ 1,
-                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 12 & WL == "WW" ~ 1,
-                            Strain == "SS120"  & O2_uM == 2.5 & Photoperiod %in% c(16,8,4) ~ 1,
-                            Strain == "SS120"  & O2_uM == 25 & Photoperiod %in% c(16) & WL == 450 ~ 1,
-                            Strain == "SS120"  & O2_uM == 250 & Photoperiod %in% c(4) & WL == 450 ~ 1,
-                            TRUE ~ 0)) |>
-   filter(remove == 0,
-          PURPhotonDose_day <= 2.0e+06) |>
-  mutate(removephotoperiod =  case_when(Strain == "MED4" & Photoperiod == 4 ~ 1,
-                                        Strain == "MED4" & O2_uM == 250 & Photoperiod == 8 ~ 1,
-                                        Strain == "MED4" & O2_uM == 25 & Photoperiod == 16 ~ 1,
-                                        Strain == "MIT9313" & Photoperiod == 4 ~ 1,
-                                        Strain == "MIT9313" & O2_uM == 25 & Photoperiod %in% c(8,12) ~ 1,
-                                        Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod %in% c(12,16) ~ 1,
-                                        Strain == "SS120" & Photoperiod == 4 ~ 1,
-                                        Strain == "SS120"  & O2_uM == 250 & Photoperiod %in% c(8,12) ~ 1,
-                                        Strain == "SS120"  & O2_uM == 25 & Photoperiod %in% c(8) ~ 1,
-                                        Strain == "SS120"  & O2_uM == 2.5 & Photoperiod %in% c(8) ~ 1,
-                                        TRUE ~ 0))  |>
-  filter(removephotoperiod == 0,
-          PURPhotonDose_day <= 2.0e+06) |>
-  nest(data = -c("Strain","O2_uM")) |>
-  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
-                              data = .x,
-                              start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
-                              lower = c(0, 0, 0),
-                              upper = c(1,1,100),
-                              control = list(maxiter = 500)
-                         ), NULL)
-                         )
-         ) |>
-  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
-         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
-         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
-         ) |>
-  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
-                              data = .x,
-                              start = LinEqnStart
-                         ), NULL)
-                         )
-         ) |>
-  mutate(GRClm_Param = map(GRClm_Model, tidy),
-         GRClm_Predict = map(GRClm_Model, possibly(augment)),
-         GRClm_Glance = map(GRClm_Model, possibly(glance))
-         )
-
-```
-
-Want platt model for all fits that did not fail and lm for platt models that returned a NULL
-```{r}
-
- #filter to keep platt models
-KeepPlattModel <- PURPARStrainO2NestModels_filteredPhotoperiods|>
-  select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
-   filter(!map_lgl(GRCplatt_Model, is.null))
-
-#filter to keep only the models that failed to fit a platt model, fits by lm remains. 
-KeepLmModel <- PURPARStrainO2NestModels_filteredPhotoperiods|>
-  filter(map_lgl(GRCplatt_Model, is.null)) |>
- select(-c(GRCplatt_Glance, GRCplatt_Model, GRCplatt_Param, GRCplatt_Predict))
-
-# Join  
-StrainO2_AllModels <- full_join(KeepPlattModel, KeepLmModel)
-
- StrainO2filteredPhotoperiod_PlattLmModel <- StrainO2_AllModels|>
-  # select(-c(data)) |>
-  pivot_longer(cols = -c(Strain, O2_uM, data)) |>
-  drop_na(value) |>
-  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param") | str_detect(name, pattern = "Predict")) |>
-  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-  pivot_wider(names_from = Output, values_from = value) |>
-  filter(!map_lgl(Model, is.null)) |>
-  filter(!map_lgl(Glance, is.null)) |>
-  mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
-  group_by(Strain, O2_uM) |>
-  filter(AIC == min(AIC)) |>
-  ungroup() |>
-  select(-c(Glance))|>
-  unnest(Param) |>
-  select(-c(statistic)) |>
-  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
-
- remove(KeepPlattModel)
- remove(KeepLmModel)
- # remove(PURPARStrainO2NestModels_filtered)
- # remove(PURPARStrainO2PhotoNestModels)
-
-```
-
-```{r plot new models}
-
-StrainO2filteredPhotoperiod_PlattLmModel |>
-  unnest(Predict, data) |>
-  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         WL= factor(WL, levels = c("WW", 660, 450)),
-         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
-         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4"))) |>
-  ggplot() +
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL))) +
-  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
-   geom_text(aes(x = 500000, y = 0.75, label = paste(ModelType), show.legend = FALSE)
-  ) +
-     scale_colour_manual(values = MCMIXColours) +
-   scale_shape_manual(values = PhotoperiodShapes)  +
-  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
-    labs(title = "New single fit for each [O2]- photoperiods that were significantly different were removed from single fit") +
-  theme_bw()
-
-StrainO2filteredPhotoperiod_PlattLmModel |>
-  unnest(Predict, data) |>
-
-  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
-         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
-  ggplot() +
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
-  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
-   geom_text(aes(x = 500000, y = 0.75, label = paste(ModelType), show.legend = FALSE)
-  ) +
-     scale_colour_manual(values = MCMIXColours) +
-  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-    labs(title = "Photoperiods included in the single fit for each [O2]") +
-  theme_bw()
-
-```
-
-# ANOVA on new model with significantly different fits removed from the single fit.
-```{r compare 1 fit of all photoperiod to each photoperiods using platt or lm}
-
-# make wider to join with DF that contains the 1 fit through all photoperiods
-Wider_Photoperiods <- StrainO2Photoperiod_PlattLmModel %>% 
-  select(Strain, Photoperiod, O2_uM, Model, Predict) %>% 
-  pivot_wider(names_from = Photoperiod, values_from = c(Model, Predict))
-
-# this contains 1 fit through all photoperiods, the photoperiods with no growth were filtered out.
-AllPhotoperiods <- StrainO2filteredPhotoperiod_PlattLmModel %>% 
-  select(Strain, O2_uM, Model, Predict) %>% 
- rename(All = 'Model',
-        Predict_all = 'Predict')
-
-AllFitsCombined_filtered <- left_join(Wider_Photoperiods, AllPhotoperiods)
-
-ANOVA_AllPhotoperiods <- AllFitsCombined_filtered %>% 
-  mutate(twelve = `12`,
-         four = `4`,
-         eight = `8`,
-         sixteen = `16`) %>%
-  mutate(fourvsAll = map(map2(four, All, possibly(anova, otherwise = NULL)), tidy),
-         eightvsAll = map(map2(eight, All, possibly(anova, otherwise = NULL)), tidy),
-         twelvevsAll = map(map2(twelve, All, possibly(anova, otherwise = NULL)), tidy),
-         sixteenvsAll = map(map2(sixteen, All, possibly(anova, otherwise = NULL)), tidy)) %>% 
-  select(Strain, O2_uM, fourvsAll, eightvsAll, twelvevsAll, sixteenvsAll) %>% 
-  pivot_longer(cols = c(fourvsAll, eightvsAll, twelvevsAll, sixteenvsAll)) %>% 
-  unnest(value, keep_empty = TRUE) %>% 
-  filter(is.na(term) & is.na(p.value) |
-           !is.na(term) & !is.na(p.value)) %>%
-  select(Strain, O2_uM, name, p.value) %>% 
-  separate(name, into = c("Photoperiod1", "AllPhotoperiod"), sep = "vs")
-
-# %>% 
-#   mutate(p.value = case_when(is.na(p.value) ~ 0,
-#                              TRUE ~ p.value)) # Changed all failed fits to p.value = 0
-  # mutate(pval = pluck(value, "p.value", 2))
-
-ANOVA_AllPhotoperiods %>% 
-  mutate(Photoperiod1 = as.numeric(case_when(Photoperiod1 == 'four' ~ 4,
-                                  Photoperiod1 == 'eight' ~ 8,
-                                  Photoperiod1 == 'twelve' ~ 12,
-                                  Photoperiod1 == 'sixteen' ~ 16)),
-         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
-    # mutate(Photoperiod1 = factor(Photoperiod1, levels = c('four','eight', 'twelve', 'sixteen'))) %>% 
-  ggplot() +
-  geom_point(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(`p.value` < 0.05)) +
-  geom_text(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(`p.value` > 0.05), label = "ns") +
-  geom_text(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(is.na(`p.value`)), label = "NA") +
-  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
-  labs(title = "ANOVA compare all models",
-       caption = "NA = atleast one model did not fit due to lack of data points; 
-       ns = not significantly different from all photoperiod model (same); 
-       dot = significantly different from all photoperiod model")
-
-```
-
 #Plot fits on same graph
@@
 
+# TESTing additions to GGplot objects
+
 ```{r PUR per day, fig.height= 20, fig.width= 20 }
@@
 scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
+
+TestAddition <- StrainO2filtered_PlattLmModel |>
+  unnest(Predict, Data_filtered) |>
+   filter(Strain == "MED4") %>%
+  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
+         OxygenLabel = "Oxygen Concentration (µM)",
+         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" )),
+         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) %>%
+  ggplot() +
+  geom_point(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
+    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
+  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`, linetype = "solid"), size = 2, color ="blue") + 
+ # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
+ labs(title = "MED4", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
+ #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
+  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
+  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
+%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
+    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
+    #                    # limits = c(10^4, 10^7),
+    #                    breaks = c(10^4, 10^5, 10^6)) +
+  scale_x_continuous(label=scientific_10) +
+      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
+    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
+  # coord_cartesian(xlim = c (0, 16)) +
+   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
+  # coord_cartesian(ylim = c (0, 0.07)) +
+  scale_colour_manual(values = MCMIXColours) +
+   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
+   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
+  # scale_y_continuous(limits = c(-0.05,0.050)) +
+  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
+   scale_shape_manual(values = PhotoperiodShapes)  +
+  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
+                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
+ guides(linetype = guide_legend(nrow = 4),
+        fill = "none",
+        colour = guide_legend(nrow = 4)) +
+ guides(shape = guide_legend(nrow = 4)) +
+  theme_bw() +
+   theme( strip.text = element_text(size = 30),
+        axis.title = element_text(size = 30, color = "black"),
+        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
+        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
+        strip.background=element_rect(color="grey87", fill = "grey82"),
+        # strip.background=element_rect(fill = "white"),
+        legend.key.size = unit(1, 'cm'), #change legend key size
+        legend.key.height = unit(1, 'cm'), #change legend key height
+        legend.key.width = unit(0.5, 'cm'), #change legend key width
+        legend.title =  element_text(size = 30),  #change legend title font size
+        legend.text = element_text(size = 30),   #change legend text font size
+        legend.position = "top") +
+  labs( shape = "Photoperiod (h)",
+        color = "Growth Waveband (nm)",
+       linetype = "Photoperiod (h) "
+      )
+
+TestAddition
+
+AddPhotoperiod <- TestAddition %>%
 
@@
   ggplot() +
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
-    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1, alpha = 0.8) +
+  geom_point(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
+    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`, line = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), size = 1) + 
@@
          Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
-  ggplot() +
-
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
-    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1, alpha = 0.8) +
+  ggplot()+
+  geom_point(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
+    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`, line = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), size = 1) + 

### 2024-02-13 Code/ManuscriptTargetProtein.Rmd
Fixed x-axis order of Target proteins to represent biological process
Edits to ManuscriptTargetProtein.Rmd and Manuscript_O2.Rmd figure names and captions

@@
 
-```{r join deltaOD with chl DF}
+```{r join protein data with culture meta data}
 
@@
  left_join(., CultureCatalog, by = c("SampleID" = "SampleID"))
+
+glimpse(TargetProtein)
+
+```
+
+```{r order protein by biological process}
+
+TargetProtein  <- TargetProtein %>% 
+ mutate(Target = factor(Target, levels = c("FtsH", "PsbA", "PetC", "PsaC", "RbcL")))
 
@@
 
-MIT9313ProteinAttonated <- TargetProtein %>%
+MIT9313ProteinAnotated <- TargetProtein %>%
   filter( Strain == "MIT9313") %>% 
@@
 
-MIT9313ProteinAttonated
+MIT9313ProteinAnotated
 
-MED4ProteinAttonated <- TargetProtein %>%
+MED4ProteinAnotated <- TargetProtein %>%
   filter( Strain == "MED4") %>% 
@@
 
-MED4ProteinAttonated
+MED4ProteinAnotated
 ```
@@
 
- ggsave(file = file.path(PlotsOut, paste("MED4ProteinAttonated",".png",sep = "")), plot = MED4ProteinAttonated, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)
+ ggsave(file = file.path(PlotsOut, paste("MED4ProteinAnotated",".png",sep = "")), plot = MED4ProteinAttonated, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)
 
-ggsave(file = file.path(PlotsOut, paste("MIT9313ProteinAttonated",".png",sep = "")), plot = MIT9313ProteinAttonated, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("MIT9313ProteinAnotated",".png",sep = "")), plot = MIT9313ProteinAttonated, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)
 

### 2024-02-13 Code/Manuscript_O2.Rmd
Edits to ManuscriptTargetProtein.Rmd and Manuscript_O2.Rmd figure names and captions

@@
 
-```{r ProchloroElectronTrans, fig.cap = ProchloroElectronTrans_cap , fig.height = 20, fig.width = 10, echo = FALSE}
+```{r ProchloroPhotosynthDepthO2, fig.cap = ProchloroPhotosynthDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
 
-ProchloroElectronTrans_cap <- glue("**Occurance of electron transport complexes data from the Ocean Protein Portal.
-X-axis is the oxygen concentration (µM) and the y-axis indicates the depth (m) of occurance**",
-                       "Rows are...",
-                       "Columns are...",
-
+ProchloroPhotosynthDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* photosynthesis complexes.**", 
+                       "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
+                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4, SS120 and MIT9313.",
+                       "Columns show detections of proteins annotated as from Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
+                       "Horizontal lines indicate depths equivalent to the Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) used for later culture growth.",
+                       "Vertical lines indicate O~2~ (µM) used for  later culture growth.",
+                       "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",
  .sep = " ")
 
-knitr::include_graphics(file.path(FiguresInOceanPro, "ProchloroElectronTrans.png"))
+knitr::include_graphics(file.path(FiguresInOceanPro, "ProchloroPhotosynthDepthO2.png"))
 ```
@@
                     "The x-axis is photoperiod (h).",
-                    "The y-axis is actinic Photosynethetic Active Radiation (PAR) level (µmol photons m^-2^ s^-1^).",
+                    "The y-axis is actinic Photosynthetically Active Radiation (PAR) level (µmol photons m^-2^ s^-1^).",
                     "**A.** represents the model under 250 µM of O~2~ and red light.",
@@
 
-```{r ProchloroMetabDepthO2, fig.cap = ProchloroMetabDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
+```{r ProchloroProteinMetabDepthO2, fig.cap = ProchloroProteinMetabDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
 
-ProchloroMetabDepthO2_cap <- glue("**Protein turnover complexes data from the Ocean Protein Portal. The x-axis is the oxygen concentration (µM) and the y-axis indicates the depth (m) of occurance**",
+ProchloroProteinMetabDepthO2_cap <- glue("**Protein turnover complexes data from the Ocean Protein Portal.
+The x-axis is the oxygen concentration (µM) and the y-axis indicates the depth (m) of occurance**",
                        "Rows are...",
@@
 
+ProchloroElectronTrans_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein turnover complexes.**", 
+                       "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
+                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4, SS120 and MIT9313.",
+                       "Columns show detections of proteins annotated as from FtsH1, FtsH2, FtsH3 or Ribosome).",
+                       "Horizontal lines indicate depths equivalent to the Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) used for later culture growth.",
+                       "Vertical lines indicate O~2~ (µM) used for  later culture growth.",
+                       "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",
+ .sep = " ")
+
 knitr::include_graphics(file.path(FiguresInOceanPro, "ProchloroMetabDepthO2.png"))
@@
 
-```{r MED4ProteinAttonated, fig.cap = MED4ProteinAttonated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+```{r MED4ProteinAnotated, fig.cap = MED4ProteinAnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
 
-MED4ProteinAttonated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade).  **",
+MED4ProteinAnotated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade).  **",
 
@@
 
-knitr::include_graphics(file.path(FiguresIn, "MED4ProteinAttonated.png"))
+knitr::include_graphics(file.path(FiguresIn, "MED4ProteinAnotated.png"))
 ```
@@
 
-```{r MIT9313ProteinAttonated, fig.cap = MIT9313ProteinAttonated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+```{r MIT9313ProteinAnotated, fig.cap = MIT9313ProteinAnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
 
-MIT9313ProteinAttonated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade).  **",
+MIT9313ProteinAnotated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade).  **",
 
@@
 
-knitr::include_graphics(file.path(FiguresIn, "MIT9313ProteinAttonated.png"))
+knitr::include_graphics(file.path(FiguresIn, "MIT9313ProteinAnotated.png"))
 ```

### 2024-02-13 Code/ManuscriptPURFits.Rmd

--- 2024-02-12 Code/ManuscriptPURFits.Rmd
@@
 
-# Nest all data before photoperiods with no growths were filtered out
-NoFilter <- PURPARFits_dummy |>
+# nest unfiltered data and join with filtered data to have all data to plot later 
+AllData <- PURPARFits_dummy |>
    filter(PURPhotonDose_day <= 2.0e+06) |>
-  mutate(Photoperiod_all = Photoperiod) %>% 
     nest(Data_all = -c("Strain","O2_uM"))
 
- # Join nested df with all data to df containing filtered data 
-  PURPARStrainO2NestModels_filtered <- full_join(PURPARStrainO2NestModels_filtered, NoFilter) %>% 
-    rename(Data_filtered = 'data')
+PURPARStrainO2NestModels_filtered <- full_join(PURPARStrainO2NestModels_filtered, AllData)
 
@@
 #          )
-
-UnnestTest <- PURPARStrainO2NestModels_filtered %>% 
-  # unnest(Data_all, names_sep = "_", keep_empty = TRUE) %>% 
-  unnest(GRCplatt_Predict, keep_empty = TRUE)
+remove(AllData)
 
@@
 #   filter(!map_lgl(GRC_Model, is.null)) |> #https://stackoverflow.com/questions/57336319/how-to-filter-out-null-elements-of-tibbles-list-column 
-
 PURPARStrainO2NestModels_filtered|>
   filter(!map_lgl(GRCplatt_Model, is.null)) |>
-  unnest(GRCplatt_Predict, Data_filtered) |>
+  unnest(GRCplatt_Predict, data) |>
    mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
@@
   # select(-c(data)) |>
-  pivot_longer(cols = -c(Strain, O2_uM, Data_filtered, Data_all)) |>
+  pivot_longer(cols = -c(Strain, O2_uM, data, Data_all)) |>
   drop_na(value) |>
@@
 StrainO2filtered_PlattLmModel |>
-  unnest(Predict, Data_filtered) |>
+  unnest(Predict, data) |>
   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
@@
 Wider_Photoperiods <- StrainO2Photoperiod_PlattLmModel %>% 
-  select(Strain, Photoperiod, O2_uM, Model, Predict, data) %>% 
-  pivot_wider(names_from = Photoperiod, values_from = c(Model, Predict, data))
+  select(Strain, Photoperiod, O2_uM, Model, Predict) %>% 
+  pivot_wider(names_from = Photoperiod, values_from = c(Model, Predict))
 
@@
 AllPhotoperiods <- StrainO2filtered_PlattLmModel %>% 
-  select(Strain, O2_uM, Model, Predict, Data_filtered, Data_all) %>% 
+  select(Strain, O2_uM, Model, Predict, Data_all, data) %>% 
  rename(All = 'Model',
-        Predict_all = 'Predict')
+        Predict_pooled = 'Predict',
+        Data_filtered = 'data')
 
@@
 remove(AllPhotoperiods)
-```
-
-# Unnest predict df for each photoperiod in order to plot fitted 
-```{r}
-Unnest_16 <- AllFitsCombined %>% 
-  select(c(Strain, O2_uM, Predict_16)) %>%  
-  unnest(Predict_16, keep_empty = TRUE) %>% 
-  mutate(FitCategory = "Photoperiod16")
-
-Unnest_12 <- AllFitsCombined %>% 
-  select(c(Strain, O2_uM, Predict_12)) %>%  
-  unnest(Predict_12, keep_empty = TRUE) %>% 
-  mutate(FitCategory = "Photoperiod12")
-
-Unnest_8 <- AllFitsCombined %>% 
-  select(c(Strain, O2_uM, Predict_8)) %>%  
-  unnest(Predict_8, keep_empty = TRUE) %>% 
-  mutate(FitCategory = "Photoperiod8")
-
-Unnest_4 <- AllFitsCombined %>% 
-  select(c(Strain, O2_uM, Predict_4)) %>%  
-  unnest(Predict_4, keep_empty = TRUE) %>% 
-  mutate(FitCategory = "Photoperiod4")
-
-Unnest_all <- AllFitsCombined %>% 
-  select(c(Strain, O2_uM, Predict_all, Data_all)) %>% 
-  # unnest(Data_all, keep_empty = TRUE) %>% 
-  unnest(Predict_all, keep_empty = TRUE) %>% 
-  mutate(FitCategory = "Pooled")
-
-ForFitPlots <- bind_rows(Unnest_all, Unnest_16, Unnest_12, Unnest_8, Unnest_4)
-
-remove(Unnest_16, Unnest_12, Unnest_8, Unnest_4, Unnest_all)
-
-```
-
+
+AllFitsTest <- AllFitsCombined %>%
+  # unnest(Data_all) %>% 
+  tidyr::unnest(Predict_4, names_sep = "_", keep_empty = TRUE) %>% 
+  tidyr::unnest(Predict_8, names_sep = "_", keep_empty = TRUE) %>%
+  tidyr::unnest(Predict_12, names_sep = "_", keep_empty = TRUE) %>%
+  tidyr::unnest(Predict_16, names_sep = "_", keep_empty = TRUE) %>%
+
+  rename(Four_PURPhotonDose_day = PURPhotonDose_day,
+         Four_deltaOD_Lmu_corr_day = deltaOD_Lmu_corr_day,
+         Four_Fitted = .fitted) %>% 
+  select(-c(.resid)) %>%
+  unnest(Predict_8) %>% 
+  rename(Eight_PURPhotonDose_day = PURPhotonDose_day,
+         Eight_deltaOD_Lmu_corr_day = deltaOD_Lmu_corr_day,
+         Eight_Fitted = .fitted) %>% 
+  select(-c(.resid))
+
+```
 #Mirelle left off here,
@@
 
-ForFitPlots |>
+AllFitsCombined |>
    filter(Strain == "MED4") |>
-    unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
-  # unnest(Predict_4, names_sep = "_", keep_empty = TRUE) |>
-  # unnest(Predict_8, names_sep = "_", keep_empty = TRUE) |>
-  # unnest(Predict_12, names_sep = "_", keep_empty = TRUE) |>
-  # unnest(Predict_16, names_sep = "_", keep_empty = TRUE) |>
+  unnest(cols = c(Data_all, Predict_pooled), names_sep = "_", keep_empty = TRUE) |>
+  unnest(Predict_4, names_sep = "_", keep_empty = TRUE) |>
+  unnest(Predict_8, names_sep = "_", keep_empty = TRUE) |>
+  unnest(Predict_12, names_sep = "_", keep_empty = TRUE) |>
+  unnest(Predict_16, names_sep = "_", keep_empty = TRUE) |>
   mutate(PhotoperiodLabel_title = "Photoperiod (h)",
          OxygenLabel = "Oxygen Concentration (µM)",
-         Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4")),
+         Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4" )),
          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) %>%
   ggplot()  +
-   geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 6, alpha = 0.8) +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 2, alpha = 1.0) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), data = . %>% filter(FitCategory == "Pooled"), size = 1) + 
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted, linetype = "twodash"), data = . %>% filter(FitCategory == "Photoperiod16" & O2_uM == 25), size = 0.5) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted, linetype = "dotdash"), data = . %>% filter(FitCategory == "Photoperiod8"), size = 0.5) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted,  linetype = "aa"), data = . %>% filter(FitCategory == "Photoperiod4"), size = 0.5) +
-  # geom_line(aes(x = PURPhotonDose_day, y = .fitted, shape = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), data = . %>% filter(FitCategory == "Photoperiod4"), size = 0.5) +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 6, alpha = 1.0) +
+    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 2, alpha = 0.8) +
+  geom_line(aes(x = Predict_pooled_PURPhotonDose_day, y = Predict_pooled_.fitted), size = 1) + 
+  geom_line(aes(x = Predict_4_PURPhotonDose_day, y = Predict_4_.fitted, shape = as.factor(Predict_4_Photoperiod), linetype = as.factor(Predict_4_Photoperiod)), size = 0.5) +
+  geom_line(aes(x = Predict_8_PURPhotonDose_day, y = Predict_8_.fitted, shape = as.factor(Predict_8_Photoperiod), linetype = as.factor(Predict_8_Photoperiod)), size = 0.5) +
+  geom_line(aes(x = Predict_12_PURPhotonDose_day, y = Predict_12_.fitted, shape = as.factor(Predict_12_Photoperiod), linetype = as.factor(Predict_12_Photoperiod)), size = 0.5) +
+  geom_line(aes(x = Predict_16_PURPhotonDose_day, y = Predict_16_.fitted, shape = as.factor(Predict_16_Photoperiod), linetype = as.factor(Predict_16_Photoperiod)), size = 0.5) +
  labs(title = "MED4", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
@@
   # scale_y_continuous(limits = c(-0.05,0.050)) +
-   scale_linetype_manual(values = c("solid", "twodash", "dotted","dotdash", "aa"),labels = c("Pooled", "16 hr", "12 hr", "8 hr", "4 hr")) +
+  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
    scale_shape_manual(values = PhotoperiodShapes)  +
@@
                     labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
- guides(linetype = guide_legend(nrow = 5),
+ guides(linetype = guide_legend(nrow = 4),
         fill = "none",
@@
         legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title =  element_text(size = 25),  #change legend title font size
-        legend.text = element_text(size = 25),   #change legend text font size
+        legend.title =  element_text(size = 30),  #change legend title font size
+        legend.text = element_text(size = 30),   #change legend text font size
         legend.position = "top") +
@@
    filter(Strain == "SS120") |>
-  unnest(cols = c(Data_all, Predict_all), names_sep = "_", keep_empty = TRUE) |>
+  unnest(cols = c(Data_all, Predict_pooled), names_sep = "_", keep_empty = TRUE) |>
   mutate(PhotoperiodLabel_title = "Photoperiod (h)",
@@
     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 2, alpha = 0.8) +
-  geom_line(aes(x = Predict_all_PURPhotonDose_day, y = Predict_all_.fitted), size = 1) + 
+  geom_line(aes(x = Predict_pooled_PURPhotonDose_day, y = Predict_pooled_.fitted), size = 1) + 
  # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
@@
    filter(Strain == "MIT9313") |>
-  unnest(cols = c(Data_all, Predict_all), names_sep = "_", keep_empty = TRUE) |>
+  unnest(cols = c(Data_all, Predict_pooled), names_sep = "_", keep_empty = TRUE) |>
   mutate(PhotoperiodLabel_title = "Photoperiod (h)",
@@
  rename(All = 'Model',
-        Predict_all = 'Predict')
+        Predict_pooled = 'Predict')
 

### 2024-02-13 Code/Manuscript_O2.Rmd
edit ocean protein captions

@@
                        "Columns show detections of proteins annotated as from Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
-                       "Horizontal lines indicate depths equivalent to the Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) used for later culture growth.",
-                       "Vertical lines indicate O~2~ (µM) used for  later culture growth.",
+                       "Horizontal grey lines indicate depths equivalent to the Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) used for later culture growth.",
+                       "Vertical grey lines indicate O~2~ (µM) used for  later culture growth.",
                        "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",
@@
                        "Columns show detections of proteins annotated as from FtsH1, FtsH2, FtsH3 or Ribosome).",
-                       "Horizontal lines indicate depths equivalent to the Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) used for later culture growth.",
-                       "Vertical lines indicate O~2~ (µM) used for  later culture growth.",
+                       "Horizontal grey lines indicate depths equivalent to the Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) used for later culture growth.",
+                       "Vertical grey lines indicate O~2~ (µM) used for  later culture growth.",
                        "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",

### 2024-02-14 Code/Manuscript_O2.Rmd
Edits to OceanProtein fig caps

--- 2024-02-13 Code/Manuscript_O2.Rmd
@@
                        "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4, SS120 and MIT9313.",
-                       "Columns show detections of proteins annotated as from Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
-                       "Horizontal lines indicate depths equivalent to the Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) used for later culture growth.",
-                       "Vertical lines indicate O~2~ (µM) used for  later culture growth.",
+                       "Columns show detections of proteins annotated as  Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
+                       "Culture growth experimental conditions indicated by horizontal grey lines for depths approximating Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) and vertical grey lines for O~2~ (µM).",
                        "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",
@@
 
-ProchloroProteinMetabDepthO2_cap <- glue("**Protein turnover complexes data from the Ocean Protein Portal.
-The x-axis is the oxygen concentration (µM) and the y-axis indicates the depth (m) of occurance**",
-                       "Rows are...",
-                       "Columns are...",
-
-                       .sep = " ")
-
-ProchloroElectronTrans_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein turnover complexes.**", 
+ProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein turnover complexes.**", 
                        "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
                        "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4, SS120 and MIT9313.",
-                       "Columns show detections of proteins annotated as from FtsH1, FtsH2, FtsH3 or Ribosome).",
-                       "Horizontal lines indicate depths equivalent to the Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) used for later culture growth.",
-                       "Vertical lines indicate O~2~ (µM) used for  later culture growth.",
+                       "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome).",
+                       "Culture growth experimental conditions indicated by horizontal grey lines for depths approximating Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) and vertical grey lines for O~2~ (µM).",
                        "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",

### 2024-02-14 Code/Manuscript_O2.Rmd
Edits to Materials & Methods

@@
 
-## Culturing {.unnumbered}
+## Ocean Protein Portal analyses {.unnumbered}
 
-%%%%%% Taken from my thesis word for word, need to reword and shorten %%%%
+## *Prochlorococcus* culturing {.unnumbered}
 
-Three xenic *P. marinus* cultures, obtained from Bigelow Labs, NCMA
-Maine, US: MED4 (CCMP1986) from a High Light-adapted (HLI) clade, SS120
-(CCMP1375) from a Low Light-adapted (LLIII) clade and MIT9313 (CCMP2773)
-also from a Low Light-adapted (LLIV) clade. These cultures were then
-maintained in two separate incubators. The temperature for both
-incubators was set to 22°C and a light/dark cycle of 12 h. The PAR level
-of the incubator was chosen to reflect the light level of the natural
-niche of the ecotype during culturation. The PAR level of the incubator
-containing the HLI clade, MED4, was set at 160 µmol photons m^-2^ s^-1^,
-whereas the incubator containing the LLIII and LLIV clades, SS120 and
-MIT9313 respectively, was set at 30 µmol photons m^-2^ s^-1^. To ensure
-cultures remained in exponential growth phase, all strains were
-transferred weekly in Pro99 media prepared according to
-[@mooreCulturingMarineCyanobacterium2007] in autoclaved artificial
-seawater. Artificial seawater was prepared according to the National
+Three xenic cultures of *P. marinus* were obtained from Bigelow Labs, NCMA
+Maine, US (REFERENCE). MED4 (CCMP1986) is from High Light-adapted (HLI) clade; SS120
+(CCMP1375) is from Low Light-adapted (LLIII) clade; and MIT9313 (CCMP2773)
+is from Low Light-adapted (LLIV) clade. Cultures were
+maintained in incubators set to 22°C with a light/dark cycle of 12 h, with illumination from XXXXX.
+The PAR level for maintenance cultures reflected  Photosynthetically Active Radiation (PAR) in the source
+niche of the ecotype; MED4, of 160 µmol photons m^-2^ s^-1^; SS120 and
+MIT9313 at 30 µmol photons m^-2^ s^-1^. To maintain active growth all strains were
+transferred weekly with XX to YY dilution with Pro99 media
+[@mooreCulturingMarineCyanobacterium2007] prepared with autoclaved artificial
+seawater (National
 Center for Marine Algae and Microbiota (NCMA) protocol by combining salt
 solution I and salt solution II using the enriched artificial seawater
-(ESAW) recipe.
+(ESAW) recipe.  REPLACe with CITATION OF NCMA protocol)XXXX
 
-## Experimental design {.unnumbered}
+## Experimental design using bioreactor control of light and [O~2~] {.unnumbered}
 
-%%%%%% Taken from my thesis word for word, need to reword and shorten %%%%
+Controlled growth experiments were performed using PSI Multicultivators (Figure \@ref(fig:LabeledMC); MCMIX-OD orMC1000-OD, Brno, Czech Republic ).
+Each multicultivator individually controls 8 tubes at a common temperature of 22°C.
+Each tube containing 70 mL of Pro99 media was inoculated with 10 mL of growing maintenance culture.
+In a factorial matrix design, each tube was then subject to an individual combination of sinusoidal photoperiod (4, 8, 12, 16  h);  reaching a peak PAR (30, 90, 180 µmol photons m^-2^ s^-1^), with defined spectral bandwidth (AA, BB, CC, DD nm).
+[O~2~] levels (2.5 µM, 25 µM, 250 µM) were imposed by bubbling tubes with varying ratios of air and
+Nitrogen (N~2~), with consistent 0.05% of Carbon Dioxide (CO~2~)
+gas, delivered through a 0.2 μm sterile microfilter via a G400 gas mixing system XXXXGIVE SOURCEXXXX. [O~2~] in situ was verified using oxygen optodes (PyroScience,
+Germany) inserted into tubes for
+real-time measurements, with a temperature probe in
+the aquarium of the bioreactor to correct [O~2~] measures for temperature
+fluctuations. In addition, the Pyroscience software corrected [O~2~] based on the
+salinity of the media (32 ppt).
+The flow rate of the gas mixture was controlled, but variations in bubbling speed, PAR and culture density affected the [O~2~] achieved in each tube.
+A low [O~2~] of 0.5 µM - 5 µM (reported as 2.5 µM hereafter),  was achieved by sparging with a gas mixture containing 99.95% N~2~ and 0.05%
+CO~2~.
+An intermediate [O~2~] of 10 - 25 µM (reported hereafter as 25 µM) was achieved by sparging with a gas mixture containing 98.95% N~2~, 0.05% CO~2~ and 1% O~2~.
+A high O~2~ of 200 µM - 280 µM (reported hereafter as 250 µM) was achieved by sparging with lab air (78% N~2~, 21% O~2~, 1% Ar and 0.05% CO~2~).
 
-For each of three ecotypes, we imposed [O~2~] (three levels: 2.5 µM,
-25µM, 250 µM), photoperiod (four levels: 4 h, 8 h, 12 h, 16 h), spectral
-waveband (four bands: full spectrum white LED, 660 nm, 530 nm, 450 nm),
-and light level (three levels: 30, 90, 180 µmol photons m^-2^ s^-1^)
-treatments in a factorial design. Each factor is explained below. The
-full crossing of all factors would yield 3 x 4 x 4 x 3 = 144 treatments
-per ecotype (432 total), but due to time constraints and total absence
-of growth of some ecotypes under some conditions, not all treatments
-were carried out. In total, we completed 291 treatments.
+The full crossing of all factor levels would yield 4 x 3 x 4 x 3 = 144 treatments, x 3 strains for 432 possible combinations.
+Consistent absence of growth of some strains under some levels of photoperiod, PAR, or [O~2~] meant we completed 291 growth factor treatment combinations.
 
-All growth experiments were conducted at 22°C.
+In situ XXXXItalicsXXX measurements of Optical Density (OD) 680 nm, a proxy for cell suspension density, cell size dependent scatter and cell chlorophyll content;  and OD 720 nm, a proxy for cell suspension density and cell size dependent scatter, were recorded every 5 minutes over least 8 to 14 days,  depending on the
+duration of the lag phase, if any. All data from the Multicultivator were saved
+as comma separated values file  (CITATION of FILES LOCATION).
 
-## Experimental light conditions {.unnumbered}
-
-%%%%%% Taken from my thesis word for word, need to reword and shorten %%%%
-
-Three growth Photosynthetically Active Radiation (PAR) levels (180, 90,
-and 30 µmol photons m^-2^ s^-1^) and four spectral wavebands (white LED
-full spectrum, 660 nm, 530 nm, and 450 nm) were chosen to simulate light
-levels and spectral color spanning the vertical ocean water column, from
-near-surface to the lower euphotic zone depths. For simplicity, actinic light used for growth
-under specific wavebands will be referred by the respective spectral
-color; white LED for LED full spectrum, red for 660 nm, green for 530 nm
-and blue for 450 nm. Four different photoperiods were chosen to simulate
-various diel cycles characteristic of current and hypothetical future
-niches of *P. marinus*. A photoperiod of 16 h was chosen to represent
-temperate (45°N) summer at the ocean surface, 12 h for equatorial (0°N)
+PAR of 180, 90 or 30 µmol photons m^-2^ s^-1^, and spectral wavebands (white LED
+full spectrum, 660 nm, 530 nm, and 450 nm) were chosen to approximate light
+levels and spectral colors spanning the vertical ocean water column, from
+near-surface to the lower euphotic zone depths. Photoperiods were chosen to approximate diel cycles characteristic of current and hypothetical future
+niches of *P. marinus*; 16 h represents
+temperate (45°N) summer at the ocean surface; 12 h for equatorial (0°N)
 ocean surface or temperate (45°N) spring and fall ocean surface or
-temperate (45°N) summer at deep ocean depths, 8 h for temperate (45°N)
+temperate (45°N) summer at deeper ocean depths; 8 h for temperate (45°N)
 winter at the surface or at temperate (45°N) spring and fall at depth
-and equatorial (0°N) deep ocean depths and 4 h for temperate (45°N)
+and equatorial (0°N) deep ocean depths; and 4 h for temperate (45°N)
 winter or deep ocean depths during temperate (45°N) spring and fall.
-
-## Experimental oxygen conditions {.unnumbered}
-
-%%%%%% Taken from my thesis word for word, need to reword and shorten %%%%
-
-Three target dissolved oxygen concentrations [O~2~] were delivered to
-tubes of the Multicultivator by mixing varying ratios of air and
-Nitrogen (N~2~) gases while delivering 0.05% of Carbon Dioxide (CO~2~)
-gas through a 0.2 μm sterile microfilter via a G400 gas mixing system.
-To confirm and monitor the [O~2~], 4 FireSting optodes (PyroScience,
-Germany) were inserted into select tubes of each modified [O~2~] run for
-real-time measurements. A compensation temperature probe was placed in
-the aquarium of the bioreactor to correct [O~2~] for temperature
-fluctuations. In addition, the software corrected [O~2~] based on the
-salinity of the media (32 ppt). For the low O~2~ environment
-experiments, 0.5 to 1.0 µM of O~2~ was delivered to each Multicultivator
-tube by sparging with a gas mixture containing 99.95% N~2~ and 0.05%
-CO~2~ to purge dissolved O~2~ out of the culture. The intermediate O~2~
-environment experiments were sparged to deliver 10 to 25 µM of O~2~
-using a gas mixture containing 98.95% N~2~, 0.05% CO~2~ and 1% O~2~. The
-high O~2~ environment experiments were sparged with lab air (78% N~2~,
-21% O~2~, 1% Ar and 0.05% CO~2~) to deliver 230 µM of O~2~. While the
-flow rate of the gas mixture was controlled, variations in bubbling
-speed affected the [O~2~] delivered to each tube; therefore, a range of
-[O~2~] was defined for each experimental O~2~ level; 0.5 µM - 5 µM for
-low, 5 µM - 50 µM for intermediate and 200 µM - 280 µM for high O~2~
-experiments. To simplify the representation of experimental [O~2~]
-conditions in graphs and discussions, the approximate median [O~2~] of
-each experimental range: 2.5 µM, 25 µM, and 250 µM, will be used for
-low, intermediate, and high conditions, respectively.
-
-\newpage
-
-## Bioreactors {.unnumbered}
-
-%%%%%% Taken from my thesis word for word, need to reword and shorten %%%%
-
-Growth experiments under different spectral wavebands were performed
-using a PSI MCMIX-OD Multicultivator (Figure \@ref(fig:LabeledMC)) or a
-PSI MC1000-OD Multicultivator for white LED experiments. Each
-Multicultivator has the capacity to individually control 8 tubes with
-specific PAR levels and photoperiods and the MCMIX-OD has options for
-individually controlled spectral wavebands. 10 mL of exponential growth
-culture was added to 70 mL of Pro99 media and all 8 tubes were situated
-in a common temperature-controlled water bath to ensure the temperature
-remained constant at 22°C over the duration of the experiment. Real time
-absorbance measurements of Optical Density (OD) 680 nm (a proxy for cell
-suspension density, cell scatter and cell chlorophyll content) and OD
-720 nm (a proxy for cell suspension density and cell scatter) were
-recorded every 5 minutes for at least 8 to 14 days depending on the
-duration of the lag phase, if any. Real time OD
-measurements eliminate intrusive subsampling of sterile cultures and
-provide high resolution chlorophyll and cell scatter proxies over the
-duration of the experiment. All data from the Multicultivator were saved
-as a comma separated values file and processed in R-Studio for
-calculations of growth rate estimates and graphical plotting.
-
-\newpage
 

### 2024-02-14 Code/Manuscript_O2.Rmd
more mat met edits

@@
 
+## Data management and analysis {.unnumbered}
+
+### Chlorophyll specific exponential growth rates
+Data files saved form from the Multicultivator software were imported into R-Studio (CITATION) for data management [@R-tidyverse], growth rate calculations CITATION, comparisons of model fits CITATION, and generation of
+figures`ggplot2` CITATION. The chlorophyll proxy
+optical density (OD680 - OD720;  ΔOD) was used to determine the chlorophyll-specific exponential growth
+rate (µ, h^-1^) for each treatment combination.
+We first we used a rolling mean from the RStudio `zoo` package [@R-zoo] to calculate the average ΔOD data over a 1-hour window, to lower influence of outlier points XXXXother trimmingXXXXX using a Levenberg-Marquardt algorithm
+[@bellaviaLevenbergMarquardtMethod2018] modification of the non-linear
+least squares,  using the R package `minpack.lm`
+[@R-minpack.lm], to fit a logistic
+equation \@ref(eq:GrowthRate) where ΔOD~max~ is maximum ΔOD, ΔOD~min~ is minimum ΔOD, t is time
+duration over the growth trajectory. 
+OTHER MOREXXXXXX
+
+```{=tex}
+\begin{equation}
+  µ = \frac{ΔOD_{max} × ΔOD_{min} × exp^{(µ × t)}}{ΔOD_{max} + (ΔOD_{min} × exp^{((µ × t) - 1)})}
+  (\#eq:GrowthRate)
+\end{equation}
+```
+
+CITAtIONS of github locations of code etc. XXXXX
+
+### Generalized additive model of growth responses {.unnumbered}
+
+%%%%%% Taken from my thesis word for word, need to reword and shorten %%%%
+
+A Generalized Additive Model (GAM) was applied to examine the
+relationship between chlorophyll-specific µ, h^-1^, for each [O~2~] level, across the blue and red spectral wavebands, photoperiods and PAR levels for each *P.marinus* strain in this study.
+The gam function from the R package `mgcv`
+[@R-mgcv] was used to model the growth rate with smoothing terms to
+indicate the 90, 50 and 10% quantiles for growth rate across the levels of factors.
+Only data  XXXXXWHAT DATAXXXX BE SPECIFICXXXX below a standard error tolerance of 30% of the fit was used in the model.
+Our priority
+was studying the effect of blue light on growth trends, since blue light is the most ecologically relevant spectral waveband for
+deep ocean niches.  We included analyses of responses of red light, which is not ecophysiologically relevant but might prove mechanistically informative (CITE MURPHY ETC)
+
+### Estimation of Photosynthetically Usable Radiation
+
+XXXXTEXT NEEDEDXXXX
 ```{r PurParPlot, fig.cap = PurParPlot_cap , fig.height = 20, fig.width = 10, echo = FALSE}
@@
 ```
-
-\newpage
-
-## Data management and analysis {.unnumbered}
-
-%%%%%% Taken from my thesis word for word, need to reword and shorten %%%%
-
-Data from the Multicultivators were imported into R-Studio for data
-management, growth rate calculations, statistics, and generation of
-figures with the `ggplot2` package [@R-tidyverse]. The chlorophyll proxy
-optical density (OD680 - OD720) or ΔOD was used to determine the growth
-rate for each condition. We used a rolling mean from the RStudio `zoo`
-package [@R-zoo] to calculate the average ΔOD data over a 1-hour window.
-This was done to prevent extraneous data points from affecting the
-growth rate estimates. A Levenberg-Marquardt algorithm
-[@bellaviaLevenbergMarquardtMethod2018] modification of the non-linear
-least squares fit equation using the R package `minpack.lm`
-[@R-minpack.lm] was used to calculate growth rate (µ) using the logistic
-equation \@ref(eq:GrowthRate):
-
-```{=tex}
-\begin{equation}
-  µ = \frac{ΔOD_{max} × ΔOD_{min} × exp^{(µ × t)}}{ΔOD_{max} + (ΔOD_{min} × exp^{((µ × t) - 1)})}
-  (\#eq:GrowthRate)
-\end{equation}
-```
-where ΔOD~max~ is maximum ΔOD, ΔOD~min~ is minimum ΔOD, t is time
-duration over the growth trajectory.
-
-## Generalized additive model {.unnumbered}
-
-%%%%%% Taken from my thesis word for word, need to reword and shorten %%%%
-
-A Generalized Additive Model (GAM) was applied to examine the
-relationship between the chlorophyll proxy (ΔOD) growth rate across the
-blue spectral waveband, photoperiod and PAR levels for each *P.marinus*
-ecotype in this study. The gam function from the R package `mgcv`
-[@R-mgcv] was used to model the growth rate with smoothing terms to
-indicate the 90, 50 and 10% quantiles. Only data below a standard error
-tolerance of 30% of the fit was used in the model. Because of time
-limitations, we were unable to conduct sufficient growth response
-experiments for all the other spectral wavebands, except for the blue,
-to fulfill the input requirements for the GAM. Therefore, our priority
-was on studying the effect of blue light on growth trends, considering
-that blue light is the most ecologically relevant spectral waveband for
-deep ocean niches.
 

### 2024-02-14 Code/Manuscript_O2.Rmd
metaproteomics mat met

@@
 
-## Ocean Protein Portal analyses {.unnumbered}
+## MetaProteomic data {.unnumbered}
+
+The OceansMap Protein Portal (OPP; https://proteinportal.whoi.edu/) is an open access online data repository  (Woods Hole Oceanographic Institute, WHOI) for mass spectroscopy data on marine microbial peptides, found at various depths and locations worldwide.
+We screened the OPP for proteins annotated as from *Prochlorococcus* strains, to identify differential strategies employed by strains living at varying depths and oxygen levels within the marine water column.
+We focussed particularly on the proteins from photosynthetic electron transport and photosystem repair proteins – Pcbs, PSI and II, Cytochrome b6f, NDH, PTOX, Rubsico, ATP Synthase and the FtsH proteases.
+the analyzed metaproteomic data was collected from 12 locations in the tropical North Pacific ocean along 150 W from 18 N of the equator between October 1, 2011 and October 25, 2011 during the voyage of the R/V Kilo Moana MetZyme cruise KM1128 (https://www.rvdata.us/search/cruise/KM1128; original datasets in the Biological and Chemical Oceanography Data Management Office repository; https://www.bco-dmo.org/project/2236).
+
+### Sample Treatment and Peptide Identification
+Collection and treatment of protein samples were performed following  Saito et al., (2014, 2015) XXXXADD to ZoteroXXXX .
+Briefly, samples of seawater from depths of 20, 40, 50, 60, 70, 80, 90, 120, 150, 200, 250, 300, 380, 400, 500, 550, 600, and 800 m below the ocean surface were pumped through a 0.2 µm filter, preserved in RNAlater and frozen at -80°C until extraction.
+Proteins were extracted from the filter in an SDS-based detergent, embedded in tube gel, alkylated and reduced prior to in-gel trypsin digestion.
+Peptide spectra were generated using a Q-Exactive Orbitrap Mass Spectrometer, searched in the SEQUEST CITATIONXXXX and labelled with the most likely protein and species annotation from Uniprot.
+Oxygen levels at the location of sampling were recorded.
 
@@
 ## Data management and analysis {.unnumbered}
+
+### Data Processing and Bioinformatic Analyses
+
+	Datasets were obtained from the KM1128 entry in the BCO-DMO database (https://www.bco-dmo.org/deployment/59053) accessed via the OPP in June 2019.
+Datasets contained: i) peptide sequences and sample identification (ID) number; ii) sample ID number, station, depth in meters below the surface the sample was collected at, best-hit BLASTP protein and species annotation and the corresponding Uniprot Entry number for the identified proteins and iii) depth, station and oxygen levels.
+Environmental conditions (depth and oxygen concentration) were joined to peptide sequence and BLASTP annotations by ID number, depth and station using the functions in the Tidyverse package (https://www.tidyverse.org/) in RStudio v1.2.5019 (https://rstudio.com/).
+The resulting merged dataset was filtered for Prochlorococcus peptides detected from 0 to 300 m below the surface that were annotated as a subunit of PSI, PSII, Pcbs, Cyt b6f, Rubisco, NDH, plastocyanin, ferredoxin, ATP Synthase or FtsH proteases.
+Peptides were re-annotated for consistency and labelled according to strain, clade, subunit and protein complex (if possible).
+Data for each strain was plotted against exact depth and O2 values.
+All protein sequences were obtained from UniProt (https://www.uniprot.org/) and analyzed in Molecular Evolution and Genetic Analyses X (MEGAX) software  (https://www.megasoftware.net/).
+Sequences for each protein and/or subunits for each of the thirteen Prochlorococcus strains identified in the dataset were aligned with MUSCLE using UPGMA cluster method and a lambda of 24 with a -2.9 gap open penalty and 1.20 hydrophobicity multiplier.
+Overall mean pairwise distance between protein sequences was determined using bootstrap variance estimation methods.
+Maximum likelihood phylogenetic trees were assembled using 1000 bootstrap replications with a 95% site coverage cut off.
+Prochlorococcus FtsH isoform identities were specified by phylogenetic comparison to the FtsH proteases of Synechocystis sp.
+PCC6803.
+
+#### Data interpretation, assumptions and limitations
+	Graphs depict the presence of mass-spectrally detected peptides at varying depths and O2 levels in the water column for each Prochlorococcus strain identified in the dataset.
+When analyzing the presence of a particular protein complex, all peptides belonging to all subunits were included to give the greatest number of data points.
+Where a particular metabolic pathway or reaction was examined, the activity of the pathway was interpreted by analysis of the rate-limiting enzyme or unique enzyme in the pathway (i.e.
+Rubisco was used as proxy for the activity of the Calvin Cycle).
+	Although not a direct measurement, it is assumed that light intensity is inversely correlated with depth.
+The terms “light” and “depth” therefore denote the same parameter the present paper.
+It is also assumed that the presence of a protein indicates that it is active under the given environmental parameters.
+	As this data was acquired on a discovery mission rather than through targeted peptide approaches, it is difficult to discern how accurate strain annotation of a particular peptide is, particularly as the proteins of interest in this study are highly conserved in sequence.
+We are confident in clade and ecotypic classification for each protein examined and although exact strain annotation may be ambiguous for the purposes of this research, we assume strain identification is accurate.
+Another caveat to interpretation of this data is the “peptide detection bias” inherent to mass spectrometry: certain peptides are more easily detected and thus dominate the spectra over less easily detected peptides.
+The data is also limited by the number and nature of protein spectra in the SEQUEST database: a peptide sequence cannot be determined unless there is already a known spectrum for that peptide in the SEQUEST database, hence some peptides of interest may not be identifiable.
+Therefore, the absence of a particular does not necessarily rule out its presence overall.
+This bias, however, does not render the laws of probability moot: there is still likely to be a correlation between peptide abundance and detection.
+Furthermore, a peptide must be detected above a certain threshold abundance in order to be considered an accurate ‘hit’.
+Therefore, the ‘absence’ of a particular protein structure is here interpreted as low in quantity, while its presence is interpreted as high in quantity, and this is reflected in the results and discussion of the present data.
+Finally, we have not assessed the ativity of these peptides, only their presence or absence from a particular environment.
+Therefore, we cannot accurately gauge total activity of Prochlorococcus proteins.
 

### 2024-02-14 Code/Manuscript_O2.Rmd
Aurora metaproteomics matmet added

--- 2024-02-14 Code/Manuscript_O2.Rmd
@@
 
-## Ocean Protein Portal analyses {.unnumbered}
+## MetaProteomics {.unnumbered}
 
-## *Prochlorococcus* culturing {.unnumbered}
+The OceansMap Protein Portal (OPP; https://proteinportal.whoi.edu/) is an open access online data repository (Woods Hole Oceanographic Institute, WHOI) of mass spectroscopy data on marine microbial peptides, sampled from various depths and locations worldwide.
+We screened a subset of the OPP for proteins annotated as from *Prochlorococcus* strains, to identify differential strategies employed by strains living at varying depths and oxygen levels within the marine water column.
+We focussed on proteins mediating photosynthesis and protein metabolism.
+The samples for metaproteomic analyses were collected from 12 locations in the tropical North Pacific ocean along 150 W from 18 N of the equator between October 1, 2011 and October 25, 2011 during the voyage of the R/V Kilo Moana MetZyme cruise KM1128 (https://www.rvdata.us/search/cruise/KM1128; original datasets in the Biological and Chemical Oceanography Data Management Office repository; https://www.bco-dmo.org/project/2236).
+
+Collection and treatment of protein samples were performed following Saito et al., (2014, 2015) XXXXADD to ZoteroXXXX .
+Briefly, samples of seawater from depths of 20, 40, 50, 60, 70, 80, 90, 120, 150, 200, 250, 300, 380, 400, 500, 550, 600, and 800 m below the ocean surface were pumped through a 0.2 µm filter, preserved in RNAlater and frozen at -80°C until extraction.
+Proteins were extracted from the filter in an SDS-based detergent, embedded in tube gel, alkylated and reduced prior to in-gel trypsin digestion.
+Peptide spectra were generated using a Q-Exactive Orbitrap Mass Spectrometer, searched in the SEQUEST CITATIONXXXX and labelled with the most likely protein and species annotation from Uniprot.
+Oxygen levels at the location of sampling were recorded.
+
+## *Prochlorococcus* culturing and experimental design {.unnumbered}
 
@@
 (ESAW) recipe.  REPLACe with CITATION OF NCMA protocol)XXXX
-
-## Experimental design using bioreactor control of light and [O~2~] {.unnumbered}
 
@@
 
-## Data management and analysis {.unnumbered}
+## MetaProteomics bioinformatic analyses and limitations  {.unnumbered}
 
-### Chlorophyll specific exponential growth rates
+	Metaproteomic datasets were obtained from the KM1128 entry in the BCO-DMO database (https://www.bco-dmo.org/deployment/59053) accessed via the OPP in June 2019. Datasets contained:
+	i) Peptide sequences and sample identification (ID) number;
+	ii) Sample ID number, station, depth in meters below the surface the sample was collected at, best-hit BLASTP protein and species annotation and the corresponding Uniprot Entry number for the identified proteins;
+	iii) Sample station depth and [O~2].  
+	The depth and [O~2] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using the functions in the Tidyverse package (https://www.tidyverse.org/) in RStudio v1.2.5019 (https://rstudio.com/)  (LOCATION OF CODE ON GITHUBO.
+The resulting merged dataset was filtered for *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b6f (Cytb6f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Terminal Oxidase (PTOX); plastocyanin (PC); ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  ATP Synthase;  FtsH proteases (FtsH) or ribosomes.
+	Detected peptides were re-annotated for consistency and labelled according to strain, clade, subunit and protein complex (where possible).
+Full protein sequences corresponding to detected proteins were obtained from UniProt (https://www.uniprot.org/) and analyzed in Molecular Evolution and Genetic Analyses X (MEGAX) software  (https://www.megasoftware.net/).
+Sequences for each protein and/or subunits for each of the thirteen Prochlorococcus strains identified in the dataset were aligned with MUSCLE using UPGMA cluster method and a lambda of 24 with a -2.9 gap open penalty and 1.20 hydrophobicity multiplier.
+Overall mean pairwise distance between protein sequences was determined using bootstrap variance estimation methods.
+Maximum likelihood phylogenetic trees were assembled using 1000 bootstrap replications with a 95% site coverage cut off.
+*Prochlorococcus* FtsH isoform identities were specified by phylogenetic comparison to the characterized FtsH proteases of Synechocystis sp.
+PCC6803 (CITATONS).
+Data for each strain was plotted against depth and  [O~2] and sampling station.
+
+	Graphs depict the detection of mass-spectrally detected peptides at varying depths and [O~2] in the water column for  *Prochlorococcus* strains and clades identified in the dataset.
+When assessing the presence of a particular protein complex, all peptides belonging to all subunits of the complex were included to give the greatest number of data points.
+	Although not a direct measurement, it is assumed that light intensity is inversely correlated with depth. 
+	As this data was acquired on a discovery mission rather than through targeted peptide approaches, it is difficult to discern accuracies of strain annotations, particularly as the proteins of interest in this study are highly conserved in sequence across strain.
+We are confident in clade and ecotypic classification for each protein examined, although exact strain annotation may be ambiguous.
+Another caveat to interpretation of this data is the “peptide detection bias” inherent to mass spectrometry: certain peptides are more easily detected and thus dominate the spectra over less easily detected peptides.
+The data is also limited by the number and nature of protein spectra in the SEQUEST database: a peptide sequence cannot be determined unless there is already a known spectrum for that peptide in the SEQUEST database, hence some peptides of interest may not be identifiable.
+Therefore, the absence of a particular does not necessarily rule out its presence overall.
+Furthermore, a peptide must be detected above a certain threshold abundance in order to be considered an accurate ‘hit’.
+Therefore, the ‘absence’ of a particular protein structure is here interpreted as low in quantity, while its presence is interpreted as higher in quantity.
+
+## Growth data management and analysis {.unnumbered}
 Data files saved form from the Multicultivator software were imported into R-Studio (CITATION) for data management [@R-tidyverse], growth rate calculations CITATION, comparisons of model fits CITATION, and generation of

### 2024-02-14 Code/ManuscriptPURFits.Rmd
Added fits to plots

@@
 Also removed data if no growth occurred for an O2 and photoperiod combination so that the model including all photoperiods would not be skewed towards zero.
-As per Amanda and Doug's advice, filtered out PUR d-1 above 2.0e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
 PURPARStrainO2NestModels_filtered <- PURPARFits_dummy |>
@@
                             TRUE ~ 0)) |>
-   filter(remove == 0,
-          PURPhotonDose_day <= 2.0e+06) |>
+   filter(remove == 0) |>
   nest(data = -c("Strain","O2_uM")) |>
@@
 AllData <- PURPARFits_dummy |>
-   filter(PURPhotonDose_day <= 2.0e+06) |>
     nest(Data_all = -c("Strain","O2_uM"))
@@
 PURPARStrainO2PhotoNestModels <- PURPARFits_dummy |>
-   filter(PURPhotonDose_day <= 2.0e+06) |>
  nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
@@
 
-AllFitsTest <- AllFitsCombined %>%
-  # unnest(Data_all) %>% 
-  tidyr::unnest(Predict_4, names_sep = "_", keep_empty = TRUE) %>% 
-  tidyr::unnest(Predict_8, names_sep = "_", keep_empty = TRUE) %>%
-  tidyr::unnest(Predict_12, names_sep = "_", keep_empty = TRUE) %>%
-  tidyr::unnest(Predict_16, names_sep = "_", keep_empty = TRUE) %>%
-
-  rename(Four_PURPhotonDose_day = PURPhotonDose_day,
-         Four_deltaOD_Lmu_corr_day = deltaOD_Lmu_corr_day,
-         Four_Fitted = .fitted) %>% 
-  select(-c(.resid)) %>%
-  unnest(Predict_8) %>% 
-  rename(Eight_PURPhotonDose_day = PURPhotonDose_day,
-         Eight_deltaOD_Lmu_corr_day = deltaOD_Lmu_corr_day,
-         Eight_Fitted = .fitted) %>% 
-  select(-c(.resid))
-
-```
-#Mirelle left off here,
-# Need to use the DF with all data (all the photoperiods that showed complete no growth )
-#next add fits that were sig different, do this dynamically
+```
+
+# Fits are added that are not sig different individually,  next add fits that were sig different dynamically
 ```{r Plot fits, fig.height= 20, fig.width= 20 }
@@
 
-AllFitsCombined |>
+MED4PURFITPlot <- AllFitsCombined |>
     filter(Strain == "MED4") |>
-  unnest(cols = c(Data_all, Predict_pooled), names_sep = "_", keep_empty = TRUE) |>
-  unnest(Predict_4, names_sep = "_", keep_empty = TRUE) |>
-  unnest(Predict_8, names_sep = "_", keep_empty = TRUE) |>
-  unnest(Predict_12, names_sep = "_", keep_empty = TRUE) |>
-  unnest(Predict_16, names_sep = "_", keep_empty = TRUE) |>
+  unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
   mutate(PhotoperiodLabel_title = "Photoperiod (h)",
@@
          Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4" )),
-         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) %>%
-  ggplot()  +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 6, alpha = 1.0) +
-    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 2, alpha = 0.8) +
-  geom_line(aes(x = Predict_pooled_PURPhotonDose_day, y = Predict_pooled_.fitted), size = 1) + 
-  geom_line(aes(x = Predict_4_PURPhotonDose_day, y = Predict_4_.fitted, shape = as.factor(Predict_4_Photoperiod), linetype = as.factor(Predict_4_Photoperiod)), size = 0.5) +
-  geom_line(aes(x = Predict_8_PURPhotonDose_day, y = Predict_8_.fitted, shape = as.factor(Predict_8_Photoperiod), linetype = as.factor(Predict_8_Photoperiod)), size = 0.5) +
-  geom_line(aes(x = Predict_12_PURPhotonDose_day, y = Predict_12_.fitted, shape = as.factor(Predict_12_Photoperiod), linetype = as.factor(Predict_12_Photoperiod)), size = 0.5) +
-  geom_line(aes(x = Predict_16_PURPhotonDose_day, y = Predict_16_.fitted, shape = as.factor(Predict_16_Photoperiod), linetype = as.factor(Predict_16_Photoperiod)), size = 0.5) +
+         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
+  ggplot() +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
+    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 2, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
   labs(title = "MED4", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
- #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
-  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
-  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
-    #                    # limits = c(10^4, 10^7),
-    #                    breaks = c(10^4, 10^5, 10^6)) +
   scale_x_continuous(label=scientific_10) +
-      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
-    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
-  # coord_cartesian(xlim = c (0, 16)) +
    scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours) +
-   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
-   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
-  # scale_y_continuous(limits = c(-0.05,0.050)) +
-  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
+  scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
+  scale_linetype_manual(values = c("twodash","dashed", "dotted", "aa"), labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
    scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
+  ggh4x::facet_nested(rows = vars(O2_uM), 
                     labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
@@
       )
-
-AllFitsCombined |>
+MED4PURFITPlot
+
+SS120PURFITPlot <- AllFitsCombined |>
     filter(Strain == "SS120") |>
-  unnest(cols = c(Data_all, Predict_pooled), names_sep = "_", keep_empty = TRUE) |>
+  unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
   mutate(PhotoperiodLabel_title = "Photoperiod (h)",
@@
          Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4" )),
-         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) %>%
-  ggplot()  +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 6, alpha = 1.0) +
-    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 2, alpha = 0.8) +
-  geom_line(aes(x = Predict_pooled_PURPhotonDose_day, y = Predict_pooled_.fitted), size = 1) + 
- # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
+         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
+  ggplot() +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
+    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 2, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) + 
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
      labs(title = "SS120", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
- #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
-  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
-  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
-    #                    # limits = c(10^4, 10^7),
-    #                    breaks = c(10^4, 10^5, 10^6)) +
   scale_x_continuous(label=scientific_10) +
-      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
-    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
-  # coord_cartesian(xlim = c (0, 16)) +
    scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
   # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours) +
-   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
-   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
-  # scale_y_continuous(limits = c(-0.05,0.050)) +
-  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
+  scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
+  scale_linetype_manual(values = c("twodash","dashed", "dotted", "aa"), labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
    scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
+  ggh4x::facet_nested(rows = vars(O2_uM), 
                     labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
@@
       )
-
-AllFitsCombined |>
+   SS120PURFITPlot
+
+MIT9313PURFITPlot <- AllFitsCombined |>
    filter(Strain == "MIT9313") |>
-  unnest(cols = c(Data_all, Predict_pooled), names_sep = "_", keep_empty = TRUE) |>
+  unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
   mutate(PhotoperiodLabel_title = "Photoperiod (h)",
@@
          Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4" )),
-         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) %>%
-  ggplot() +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 6, alpha = 1.0) +
-    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Data_all_Photoperiod), color = as.factor(Data_all_WL), fill = as.factor(Data_all_WL)), size = 2, alpha = 0.8) +
-  geom_line(aes(x = Predict_pooled_PURPhotonDose_day, y = Predict_pooled_.fitted), size = 1) + 
- # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
+         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
+  ggplot() +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
+    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 2, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) + 
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "twodash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM == 25, Strain == "MIT9313")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +
   labs(title = "MIT9313", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
- #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
-  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
-  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
-    #                    # limits = c(10^4, 10^7),
-    #                    breaks = c(10^4, 10^5, 10^6)) +
   scale_x_continuous(label=scientific_10) +
-      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
-    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
-  # coord_cartesian(xlim = c (0, 16)) +
    scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours) +
-   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
-   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
-  # scale_y_continuous(limits = c(-0.05,0.050)) +
-  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
+  scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
+  scale_linetype_manual(values = c("solid","twodash","dashed", "dotted", "aa"), labels = c("Pooled","16 hr", "12 hr", "8 hr", "4 hr")) +
    scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
+  ggh4x::facet_nested(rows = vars(O2_uM), 
                     labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
@@
       )
-
-```
-
-# Remove the photoperiods from the model that are significantly different from the ANOVA run on the single fit against each individual photoperiod.   
-```{r}
-# model with dummy dark, 0 PAR,  growth rates.
-Also removed data if no growth occurred for an O2 and photoperiod combination so that the model including all photoperiods would not be skewed towards zero.
-As per Amanda and Doug's advice, filtered out PUR d-1 above 2.0e+06 because only photoperiods greater than 4 hrs have PUR d-1 above.
-PURPARStrainO2NestModels_filteredPhotoperiods <- PURPARFits_dummy |>
-  mutate(remove = case_when(Strain == "MED4" & Photoperiod == 4 ~ 1,
-                            Strain == "MED4" & O2_uM == 25 & Photoperiod == 8 & WL == "WW" ~ 1,
-                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 16 ~ 1,
-                            Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod == 12 & WL == "WW" ~ 1,
-                            Strain == "SS120"  & O2_uM == 2.5 & Photoperiod %in% c(16,8,4) ~ 1,
-                            Strain == "SS120"  & O2_uM == 25 & Photoperiod %in% c(16) & WL == 450 ~ 1,
-                            Strain == "SS120"  & O2_uM == 250 & Photoperiod %in% c(4) & WL == 450 ~ 1,
-                            TRUE ~ 0)) |>
-   filter(remove == 0,
-          PURPhotonDose_day <= 2.0e+06) |>
-  mutate(removephotoperiod =  case_when(Strain == "MED4" & Photoperiod == 4 ~ 1,
-                                        Strain == "MED4" & O2_uM == 250 & Photoperiod == 8 ~ 1,
-                                        Strain == "MED4" & O2_uM == 25 & Photoperiod == 16 ~ 1,
-                                        Strain == "MIT9313" & Photoperiod == 4 ~ 1,
-                                        Strain == "MIT9313" & O2_uM == 25 & Photoperiod %in% c(8,12) ~ 1,
-                                        Strain == "MIT9313" & O2_uM == 2.5 & Photoperiod %in% c(12,16) ~ 1,
-                                        Strain == "SS120" & Photoperiod == 4 ~ 1,
-                                        Strain == "SS120"  & O2_uM == 250 & Photoperiod %in% c(8,12) ~ 1,
-                                        Strain == "SS120"  & O2_uM == 25 & Photoperiod %in% c(8) ~ 1,
-                                        Strain == "SS120"  & O2_uM == 2.5 & Photoperiod %in% c(8) ~ 1,
-                                        TRUE ~ 0))  |>
-  filter(removephotoperiod == 0,
-          PURPhotonDose_day <= 2.0e+06) |>
-  nest(data = -c("Strain","O2_uM")) |>
-  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
-                              data = .x,
-                              start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
-                              lower = c(0, 0, 0),
-                              upper = c(1,1,100),
-                              control = list(maxiter = 500)
-                         ), NULL)
-                         )
-         ) |>
-  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
-         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
-         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
-         ) |>
-  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
-                              data = .x,
-                              start = LinEqnStart
-                         ), NULL)
-                         )
-         ) |>
-  mutate(GRClm_Param = map(GRClm_Model, tidy),
-         GRClm_Predict = map(GRClm_Model, possibly(augment)),
-         GRClm_Glance = map(GRClm_Model, possibly(glance))
-         )
-
-```
-
-Want platt model for all fits that did not fail and lm for platt models that returned a NULL
-```{r}
-
- #filter to keep platt models
-KeepPlattModel <- PURPARStrainO2NestModels_filteredPhotoperiods|>
-  select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
-   filter(!map_lgl(GRCplatt_Model, is.null))
-
-#filter to keep only the models that failed to fit a platt model, fits by lm remains. 
-KeepLmModel <- PURPARStrainO2NestModels_filteredPhotoperiods|>
-  filter(map_lgl(GRCplatt_Model, is.null)) |>
- select(-c(GRCplatt_Glance, GRCplatt_Model, GRCplatt_Param, GRCplatt_Predict))
-
-# Join  
-StrainO2_AllModels <- full_join(KeepPlattModel, KeepLmModel)
-
- StrainO2filteredPhotoperiod_PlattLmModel <- StrainO2_AllModels|>
-  # select(-c(data)) |>
-  pivot_longer(cols = -c(Strain, O2_uM, data)) |>
-  drop_na(value) |>
-  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param") | str_detect(name, pattern = "Predict")) |>
-  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-  pivot_wider(names_from = Output, values_from = value) |>
-  filter(!map_lgl(Model, is.null)) |>
-  filter(!map_lgl(Glance, is.null)) |>
-  mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
-  group_by(Strain, O2_uM) |>
-  filter(AIC == min(AIC)) |>
-  ungroup() |>
-  select(-c(Glance))|>
-  unnest(Param) |>
-  select(-c(statistic)) |>
-  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
-
- remove(KeepPlattModel)
- remove(KeepLmModel)
- # remove(PURPARStrainO2NestModels_filtered)
- # remove(PURPARStrainO2PhotoNestModels)
-
-```
-
-```{r plot new models}
-
-StrainO2filteredPhotoperiod_PlattLmModel |>
-  unnest(Predict, data) |>
-  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         WL= factor(WL, levels = c("WW", 660, 450)),
-         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
-         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4"))) |>
-  ggplot() +
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL))) +
-  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
-   geom_text(aes(x = 500000, y = 0.75, label = paste(ModelType), show.legend = FALSE)
-  ) +
-     scale_colour_manual(values = MCMIXColours) +
-   scale_shape_manual(values = PhotoperiodShapes)  +
-  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
-    labs(title = "New single fit for each [O2]- photoperiods that were significantly different were removed from single fit") +
-  theme_bw()
-
-StrainO2filteredPhotoperiod_PlattLmModel |>
-  unnest(Predict, data) |>
-
-  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
-         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
-  ggplot() +
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
-  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
-   geom_text(aes(x = 500000, y = 0.75, label = paste(ModelType), show.legend = FALSE)
-  ) +
-     scale_colour_manual(values = MCMIXColours) +
-  facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-    labs(title = "Photoperiods included in the single fit for each [O2]") +
-  theme_bw()
-
-```
-
-# ANOVA on new model with significantly different fits removed from the single fit.
-```{r compare 1 fit of all photoperiod to each photoperiods using platt or lm}
-
-# make wider to join with DF that contains the 1 fit through all photoperiods
-Wider_Photoperiods <- StrainO2Photoperiod_PlattLmModel %>% 
-  select(Strain, Photoperiod, O2_uM, Model, Predict) %>% 
-  pivot_wider(names_from = Photoperiod, values_from = c(Model, Predict))
-
-# this contains 1 fit through all photoperiods, the photoperiods with no growth were filtered out.
-AllPhotoperiods <- StrainO2filteredPhotoperiod_PlattLmModel %>% 
-  select(Strain, O2_uM, Model, Predict) %>% 
- rename(All = 'Model',
-        Predict_pooled = 'Predict')
-
-AllFitsCombined_filtered <- left_join(Wider_Photoperiods, AllPhotoperiods)
-
-ANOVA_AllPhotoperiods <- AllFitsCombined_filtered %>% 
-  mutate(twelve = `12`,
-         four = `4`,
-         eight = `8`,
-         sixteen = `16`) %>%
-  mutate(fourvsAll = map(map2(four, All, possibly(anova, otherwise = NULL)), tidy),
-         eightvsAll = map(map2(eight, All, possibly(anova, otherwise = NULL)), tidy),
-         twelvevsAll = map(map2(twelve, All, possibly(anova, otherwise = NULL)), tidy),
-         sixteenvsAll = map(map2(sixteen, All, possibly(anova, otherwise = NULL)), tidy)) %>% 
-  select(Strain, O2_uM, fourvsAll, eightvsAll, twelvevsAll, sixteenvsAll) %>% 
-  pivot_longer(cols = c(fourvsAll, eightvsAll, twelvevsAll, sixteenvsAll)) %>% 
-  unnest(value, keep_empty = TRUE) %>% 
-  filter(is.na(term) & is.na(p.value) |
-           !is.na(term) & !is.na(p.value)) %>%
-  select(Strain, O2_uM, name, p.value) %>% 
-  separate(name, into = c("Photoperiod1", "AllPhotoperiod"), sep = "vs")
-
-# %>% 
-#   mutate(p.value = case_when(is.na(p.value) ~ 0,
-#                              TRUE ~ p.value)) # Changed all failed fits to p.value = 0
-  # mutate(pval = pluck(value, "p.value", 2))
-
-ANOVA_AllPhotoperiods %>% 
-  mutate(Photoperiod1 = as.numeric(case_when(Photoperiod1 == 'four' ~ 4,
-                                  Photoperiod1 == 'eight' ~ 8,
-                                  Photoperiod1 == 'twelve' ~ 12,
-                                  Photoperiod1 == 'sixteen' ~ 16)),
-         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
-    # mutate(Photoperiod1 = factor(Photoperiod1, levels = c('four','eight', 'twelve', 'sixteen'))) %>% 
-  ggplot() +
-  geom_point(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(`p.value` < 0.05)) +
-  geom_text(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(`p.value` > 0.05), label = "ns") +
-  geom_text(aes(x = Photoperiod1, y = AllPhotoperiod), data = . %>% filter(is.na(`p.value`)), label = "NA") +
-  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
-  labs(title = "ANOVA compare all models",
-       caption = "NA = atleast one model did not fit due to lack of data points; 
-       ns = not significantly different from all photoperiod model (same); 
-       dot = significantly different from all photoperiod model")
-
-```
-
-#Plot fits on same graph
-```{r}
-
-```
-
-```{r PUR per day, fig.height= 20, fig.width= 20 }
-
-scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
-
-PURPARStrainO2PhotoNestModels |>
-  filter(!map_lgl(GRCplatt_Model, is.null)) |>
-  unnest(GRCplatt_Predict, data) |>
-   filter(Strain == "MED4") %>%
-  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
-         OxygenLabel = "Oxygen Concentration (µM)",
-         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
-  ggplot() +
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
-    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1, alpha = 0.8) +
-  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`, line = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), size = 1) + 
- # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
- labs(title = "MED4", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
- #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
-  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
-  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
-    #                    # limits = c(10^4, 10^7),
-    #                    breaks = c(10^4, 10^5, 10^6)) +
-  scale_x_continuous(label=scientific_10) +
-      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
-    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
-  # coord_cartesian(xlim = c (0, 16)) +
-   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours) +
-   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
-   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
-  # scale_y_continuous(limits = c(-0.05,0.050)) +
-  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
-   scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
-                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
- guides(linetype = guide_legend(nrow = 4),
-        fill = "none",
-        colour = guide_legend(nrow = 4)) +
- guides(shape = guide_legend(nrow = 4)) +
-  theme_bw() +
-   theme( strip.text = element_text(size = 30),
-        axis.title = element_text(size = 30, color = "black"),
-        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
-        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
-        strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"),
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title =  element_text(size = 30),  #change legend title font size
-        legend.text = element_text(size = 30),   #change legend text font size
-        legend.position = "top") +
-  labs( shape = "Photoperiod (h)",
-        color = "Growth Waveband (nm)",
-       linetype = "Photoperiod (h) "
-      )
-
-PURPARStrainO2PhotoNestModels |>
-  filter(!map_lgl(GRCplatt_Model, is.null)) |>
-  unnest(GRCplatt_Predict, data) |>
-   filter(Strain == "SS120") %>%
-  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
-         OxygenLabel = "Oxygen Concentration (µM)",
-         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
-  ggplot() +
-
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
-    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1, alpha = 0.8) +
-  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`, line = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), size = 1) + 
- # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
- labs(title = "SS120", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
- #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
-  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
-  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
-    #                    # limits = c(10^4, 10^7),
-    #                    breaks = c(10^4, 10^5, 10^6)) +
-  scale_x_continuous(label=scientific_10) +
-      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
-    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
-  # coord_cartesian(xlim = c (0, 16)) +
-   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours) +
-   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
-   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
-  # scale_y_continuous(limits = c(-0.05,0.050)) +
-  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
-   scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
-                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
- guides(linetype = guide_legend(nrow = 4),
-        fill = "none",
-        colour = guide_legend(nrow = 4)) +
- guides(shape = guide_legend(nrow = 4)) +
-  theme_bw() +
-   theme( strip.text = element_text(size = 30),
-        axis.title = element_text(size = 30, color = "black"),
-        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
-        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
-        strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"),
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title =  element_text(size = 30),  #change legend title font size
-        legend.text = element_text(size = 30),   #change legend text font size
-        legend.position = "top") +
-  labs( shape = "Photoperiod (h)",
-        color = "Growth Waveband (nm)",
-       linetype = "Photoperiod (h) "
-      )
-
-PURPARStrainO2PhotoNestModels |>
-  filter(!map_lgl(GRCplatt_Model, is.null)) |>
-  unnest(GRCplatt_Predict, data) |>
-   filter(Strain == "MIT9313") %>%
-  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
-         OxygenLabel = "Oxygen Concentration (µM)",
-         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
-  ggplot() +
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
-    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1, alpha = 0.8) +
-  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`, line = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), size = 1) + 
- # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
- labs(title = "MIT9313", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
- #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
-  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
-  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
-    #                    # limits = c(10^4, 10^7),
-    #                    breaks = c(10^4, 10^5, 10^6)) +
-  scale_x_continuous(label=scientific_10) +
-      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
-    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
-  # coord_cartesian(xlim = c (0, 16)) +
-   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours) +
-   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
-   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
-  # scale_y_continuous(limits = c(-0.05,0.050)) +
-  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
-   scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
-                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
- guides(linetype = guide_legend(nrow = 4),
-        fill = "none",
-        colour = guide_legend(nrow = 4)) +
- guides(shape = guide_legend(nrow = 4)) +
-  theme_bw() +
-   theme( strip.text = element_text(size = 30),
-        axis.title = element_text(size = 30, color = "black"),
-        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
-        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
-        strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"),
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title =  element_text(size = 30),  #change legend title font size
-        legend.text = element_text(size = 30),   #change legend text font size
-        legend.position = "top") +
-  labs( shape = "Photoperiod (h)",
-        color = "Growth Waveband (nm)",
-       linetype = "Photoperiod (h) "
-      )
+MIT9313PURFITPlot
 
@@
 
-```{r PUR per day best, fig.height= 20, fig.width= 20 }
-
-scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
-
-MED4PURFITPlot <- PURPARStrainO2PhotoNestModels |>
-  # select(-c(data)) |>
-  pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) |>  drop_na(value) |>
-  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")| str_detect(name, pattern = "Predict")) |>
-  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-  pivot_wider(names_from = Output, values_from = value) |>
-  filter(!map_lgl(Model, is.null)) |>
-  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
-  group_by(Strain, O2_uM, Photoperiod) |>
-  filter(AIC == min(AIC)) |>
-  ungroup() |>
-   # filter(!map_lgl(GRClm_Model, is.null)) |>
-  unnest(Predict, data) |>
-   filter(Strain == "MED4") %>%
-  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
-         OxygenLabel = "Oxygen Concentration (µM)",
-         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
-  ggplot() +
-   geom_point(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0, data = .
-%>% filter(PURPhotonDose_day  != 0)) +
-   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8, data = .
-%>% filter(PURPhotonDose_day  != 0)) +
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 0.03, data = .
-%>% filter(PURPhotonDose_day  == 0)) +
-  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`, line = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), size = 1.0) + 
- # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
- labs(y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
- #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
-  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
-  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
-    #                    # limits = c(10^4, 10^7),
-    #                    breaks = c(10^4, 10^5, 10^6)) +
-  scale_x_continuous(label=scientific_10) +
-      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
-    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
-  # coord_cartesian(xlim = c (0, 16)) +
-   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
-   scale_colour_manual(values = MCMIXColours) +
-   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
-   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
-  # scale_y_continuous(limits = c(-0.05,0.050)) +
-  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
-   scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
-                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
- # guides(linetype = guide_legend(nrow = 4),
- #        fill = "none",
- #        colour = guide_legend(nrow = 4)) +
- # guides(shape = guide_legend(nrow = 4)) +
-   guides(linetype = "none",
-        fill = "none",
-        colour = guide_legend(ncol = 4)) +
- guides(shape = guide_legend(nrow = 1)) +
- theme_bw() +
-   theme( strip.text = element_text(size = 30),
-        axis.title = element_text(size = 30, color = "black"),
-        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
-        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
-        strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"),
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title =  element_text(size = 20),  #change legend title font size
-        legend.text = element_text(size = 20),   #change legend text font size
-        legend.position = "top") +
-  labs(color = "Growth Waveband (nm)",
-       shape = "Photoperiod (h)")
-
-MED4PURFITPlot
-
-SS120PURFITPlot <- PURPARStrainO2PhotoNestModels |>
-  # select(-c(data)) |>
-  pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) |>  drop_na(value) |>
-  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")| str_detect(name, pattern = "Predict")) |>
-  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-  pivot_wider(names_from = Output, values_from = value) |>
-  filter(!map_lgl(Model, is.null)) |>
-  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
-  group_by(Strain, O2_uM, Photoperiod) |>
-  filter(AIC == min(AIC)) |>
-  ungroup() |>
-   # filter(!map_lgl(GRClm_Model, is.null)) |>
-  unnest(Predict, data) |>
-   filter(Strain == "SS120") %>%
-  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
-         OxygenLabel = "Oxygen Concentration (µM)",
-         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
-   ggplot() +
-   geom_point(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0, data = .
-%>% filter(PURPhotonDose_day  != 0)) +
-   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8, data = .
-%>% filter(PURPhotonDose_day  != 0)) +
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 0.03, data = .
-%>% filter(PURPhotonDose_day  == 0)) +
-  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`, line = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), size = 1.0) + 
- # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
- labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
- #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
-  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
-  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
-    #                    # limits = c(10^4, 10^7),
-    #                    breaks = c(10^4, 10^5, 10^6)) +
-  scale_x_continuous(label=scientific_10) +
-      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
-    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
-  # coord_cartesian(xlim = c (0, 16)) +
-   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
-   scale_colour_manual(values = MCMIXColours) +
-   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
-   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
-  # scale_y_continuous(limits = c(-0.05,0.050)) +
- scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
-   scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
-                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
- # guides(linetype = guide_legend(nrow = 4),
- #        fill = "none",
- #        colour = guide_legend(nrow = 4)) +
- # guides(shape = guide_legend(nrow = 4)) +
-   guides(linetype = "none",
-        fill = "none",
-        colour = guide_legend(ncol = 4)) +
- guides(shape = guide_legend(nrow = 1)) +
- theme_bw() +
-   theme( strip.text = element_text(size = 30),
-        axis.title = element_text(size = 30, color = "black"),
-        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
-        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
-        strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"),
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title =  element_text(size = 20),  #change legend title font size
-        legend.text = element_text(size = 20),   #change legend text font size
-        legend.position = "top") +
-  labs(color = "Growth Waveband (nm)",
-       shape = "Photoperiod (h)")
-
-SS120PURFITPlot
-
-MIT9313PURFITPlot <- PURPARStrainO2PhotoNestModels |>
-  # select(-c(data)) |>
-  pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
-  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) |>  drop_na(value) |>
-  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param")| str_detect(name, pattern = "Predict")) |>
-  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
-  pivot_wider(names_from = Output, values_from = value) |>
-  filter(!map_lgl(Model, is.null)) |>
-  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
-  group_by(Strain, O2_uM, Photoperiod) |>
-  filter(AIC == min(AIC)) |>
-  ungroup() |>
-   # filter(!map_lgl(GRClm_Model, is.null)) |>
-  unnest(Predict, data) |>
-   filter(Strain == "MIT9313") %>%
-  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
-         OxygenLabel = "Oxygen Concentration (µM)",
-         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
-  ggplot() +
-   geom_point(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0, data = .
-%>% filter(PURPhotonDose_day  != 0)) +
-   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8, data = .
-%>% filter(PURPhotonDose_day  != 0)) +
-  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 0.03, data = .
-%>% filter(PURPhotonDose_day  == 0)) +
-  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`, line = as.factor(Photoperiod), linetype = as.factor(Photoperiod)), size = 1.0) + 
- # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
- labs(y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
- #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
-  # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
-  # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-    # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
-    #                    # limits = c(10^4, 10^7),
-    #                    breaks = c(10^4, 10^5, 10^6)) +
-  scale_x_continuous(label=scientific_10) +
-      # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
-    # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
-  # coord_cartesian(xlim = c (0, 16)) +
-   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
-    scale_colour_manual(values = MCMIXColours) +
-   # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
-   # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
-  # scale_y_continuous(limits = c(-0.05,0.050)) +
-  scale_linetype_manual(values = c("solid", "twodash", "dotted", "aa")) +
-   scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
-                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
- # guides(linetype = guide_legend(nrow = 4),
- #        fill = "none",
- #        colour = guide_legend(nrow = 4)) +
- # guides(shape = guide_legend(nrow = 4)) +
-   guides(linetype = "none",
-        fill = "none",
-        colour = guide_legend(ncol = 4)) +
- guides(shape = guide_legend(nrow = 1)) +
- theme_bw() +
-   theme( strip.text = element_text(size = 30),
-        axis.title = element_text(size = 30, color = "black"),
-        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
-        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
-        strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"),
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title =  element_text(size = 20),  #change legend title font size
-        legend.text = element_text(size = 20),   #change legend text font size
-        legend.position = "top") +
-  labs(color = "Growth Waveband (nm)",
-       shape = "Photoperiod (h)")
-
-MIT9313PURFITPlot
-
-```
-
 ```{r, save PURFitPlots}
 
-ggsave(file = file.path(PlotsPath, paste("MED4PURFITPlot",".png",sep = "")), plot = MED4PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-ggsave(file = file.path(PlotsPath, paste("SS120PURFITPlot",".png",sep = "")), plot = SS120PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-ggsave(file = file.path(PlotsPath, paste("MIT9313PURFITPlot",".png",sep = "")), plot = MIT9313PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-```
-
-``` {r}
-# PURPARStrainO2PeriodWLNest |>
-#   filter(!map_lgl(GRCplatt_Model, is.null)) |>
-#   unnest(GRCplatt_Predict, data) |>
-#    filter(Strain == "MIT9313") %>%
-#   mutate(PhotoperiodLabel_title = "Photoperiod (h)",
-#          OxygenLabel = "Oxygen Concentration (µM)",
-#          Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
-#   ggplot() +
-#   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
-#     geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1, alpha = 0.8) +
-#   geom_line(aes(x = PURPhotonDose_day, y = `.fitted`, line = as.factor(WL), color = as.factor(WL))) + 
-#  # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
-#  labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
-#  #geom_text(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr, label= Run),hjust=0.3, vjust=0) +
-#   # geom_ribbon(aes(x = PURPhotonDose_day, ymin = ReplicateMean_deltaOD_Lmu_corr_day - ReplicateSE_deltaOD_Lmu_corr_day, ymax = ReplicateMean_deltaOD_Lmu_corr_day + ReplicateSE_deltaOD_Lmu_corr_day, fill = as.factor(WL)), alpha = 0.2, color = NA) +
-#   # geom_errorbar(aes(x = PURPhotonDose_day, ymin = (ReplicateMean_deltaOD_Lmu_corr_day - deltaOD_Lmu_se), ymax = (ReplicateMean_deltaOD_Lmu_corr_day + deltaOD_Lmu_se)), size = 0.3, color = 'black', data = .
-%>% filter(GrowthAmpdeltaODFlag_14days  == 1)) +
-#     # scale_x_continuous(labels=scales::trans_format('log10', scales::math_format(10^.x)),
-#     #                    # limits = c(10^4, 10^7),
-#     #                    breaks = c(10^4, 10^5, 10^6)) +
-# 
-#       # scale_x_continuous(breaks = c(10^5, 10^6.0, 10^7), limits = c(10^5, 10^7)) +
-#     # scale_x_continuous(breaks = c(10^4.2, 10^6, 10^6.7), limits = c(10^4.2, 10^6.7)) +
-#   # coord_cartesian(xlim = c (0, 16)) +
-#    scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
-#   # coord_cartesian(ylim = c (0, 0.07)) +
-#   scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660","530", "450" )) +
-#    # scale_x_continuous(values = c(min(PURPARFits$PURPhotonDose_day), max(PURPARFits$PURPhotonDose_day)), breaks = seq) +
-#    # scale_x_log10(labels=scales::trans_format('log10',scales::math_format(10^.x)), breaks = c(10^4, 10^5, 10^6, 10^7), limits = c(10^4, 10^7)) +
-#   # scale_y_continuous(limits = c(-0.05,0.050)) +
-#    scale_shape_manual(values = PhotoperiodShapes)  +
-#   ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM, Photoperiod), 
-#                     labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
-#  guides(linetype = "none",
-#         fill = "none",
-#         colour = guide_legend(ncol = 4)) +
-#  guides(shape = guide_legend(nrow = 1)) +
-#   theme_bw() +
-#    theme( strip.text = element_text(size = 30),
-#         axis.title = element_text(size = 30, color = "black"),
-#         axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
-#         axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
-#         strip.background=element_rect(color="grey87", fill = "grey82"),
-#         # strip.background=element_rect(fill = "white"),
-#         legend.key.size = unit(1, 'cm'), #change legend key size
-#         legend.key.height = unit(1, 'cm'), #change legend key height
-#         legend.key.width = unit(0.5, 'cm'), #change legend key width
-#         legend.title =  element_text(size = 20),  #change legend title font size
-#         legend.text = element_text(size = 20),   #change legend text font size
-#         legend.position = "top") +
-#   labs(color = "Growth Waveband (nm)",
-#        shape = "Photoperiod (h)")
-
-```
+ggsave(file = file.path(PlotsOut, paste("MED4PURFITPlot",".png",sep = "")), plot = MED4PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+ggsave(file = file.path(PlotsOut, paste("SS120PURFITPlot",".png",sep = "")), plot = SS120PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+ggsave(file = file.path(PlotsOut, paste("MIT9313PURFITPlot",".png",sep = "")), plot = MIT9313PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+ggsave(file = file.path(PlotsOut, paste("MED4PURFITPlot",".tiff",sep = "")), plot = MED4PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+ggsave(file = file.path(PlotsOut, paste("SS120PURFITPlot",".tiff",sep = "")), plot = SS120PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+ggsave(file = file.path(PlotsOut, paste("MIT9313PURFITPlot",".tiff",sep = "")), plot = MIT9313PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+```

### 2024-02-15 Code/Manuscript_O2.Rmd
working on introduction

@@
 ---
-title: "Functional Analyses of Distinct Oxygen Concentrations and Light Niches of *Prochlorococcus marinus*"
+title: "*Prochlorococcus marinus* responses to light and oxygen" 
 author:
@@
     email: msavoie@mta.ca
+  - name: Aurora Mattison
+    affil: 1,2
   - name: Julie Nadeau
@@
   - name: Sylwia Śliwińska-Wilczewska
-    affil: 1,2
+    affil: 1
   - name: Maximilian Berthold
-    affil: 1
+    affil: 1,3
   - name: Naaman Omar
     affil: 1
+- name: Ondřej Prášil
+    affil: 1,4
+    main: false
+  - name: Amanda M. Cockshutt
+    affil: 1,5
+    main: false
   - name: Douglas A. Campbell
@@
     main: false
-    orcid: ''
+    orcid: '0000-0001-8996-5463'
     email: 'dcampbel@mta.ca'
@@
   - mta: 'Department of Biology, Mount Allison University, 53 York St., Sackville NB, Canada, E4L 1C9.'
+  - num: 2
+institute:
+  - ubc: 'Department of Biology, University of British Columbia'
+  - num: 4
+institute:
+  - alga: 'MAX INSTITUTE'
+  - num: 4
+institute:
+  - alga: 'Algatech, Czech Academy of Science'
+  - num: 5
+institute:
+  - sfx: 'Department of Chemistry, St. Frances Xavier University'
 date: "`r format(Sys.Date())`"
@@
 # Introduction {.unnumbered}
+
+## Aurora
+*Prochlorococcus marinus*, a species of picocyanobacteria, are tiny, photosynthetic, marine prokaryotes.
+At nder 1 µm in diameter, they are the smallest photosynthetic organisms on the planet, but at 10^4^-10^5^ cells per millilitre of seawater  (ampbell and Vaulot, 1993), they heavily influence global biogeochemical cycles (Partensky et al., 1999) (Flombaum et al., 2013).
+*Prochlorococcus* are currently restricted to between 40°N and 40°S, from surface to 300 m  depth, spanning 3 orders of magnitudes of light (Partensky et al., 1999) (Chisholm et al., 1992).
+Some *Prochlorococcus* extend into Oxygen Minimum Zones (OMZ), at less than  20 µM O2 (Johnson et al., 1999).
+*Prochlorococcus* is divided into numerous strains, categorized into high-light clades HLI, HLII, HLIII or low-light clades LLI, LLII, LLIII, LLIV, LLV & LLVI, based on their 16S-23S intergenic transcribed ribosomal sequence signatures (Rocap et al., 2003).
+The LLIV clade, including strain MIT9313, falls near the base of the *Prochlorococcus* radiation.
+First isolated in 1993 from 135 m into the north Atlantic, Clade LLIV are characterized by preference for low light,  and are most populous between 120 m and 200 m depths (Partensky et al., 1999).
+LLIV members are also the only strains found in OMZ that have been, to date, cultured, although two as yet uncultured clades, LLV and LLVI, have been detected in the OMZ of the eastern Tropical Pacific Ocean (Lavin et al., 2010) ADDITIONAL REFS XXXX.
+LLII and LLIII clades are often grouped together as the second oldest phylogenetic clades and share an affinity for low light conditions; LLIII strain SS120, the first *Prochlorococcus* strain to be characterized in 1988, was isolated 135 m into the Sargasso Sea.
+The LLI clade includes NATL1A and NATL2A, which prefer moderate irradiances found between 30 and 100 m.
+HL clades are the most recently evolved and despite reduced genome size in comparison to LL ecotypes, have adapted to life at higher irradiances.
+HLII is the most abundant group in the North Atlantic and North Pacific Oceans, often constituting over 90% of the total population (Partensky et al., 1999),  and are most numerous around 50 m depth (Partensky et al., 1999).
+The HLI clade, including MED4, was found at the very surface of the Mediterranean Sea, just 5 m below the surface (Partensky et al., 1999).
+
+*Prochlorococcus* are difficult to culture, as their reduced genome – the smallest of any known oxyphototroph – render them partially dependent upon mutualistic heterotrophic bacteria to  detoxify reactive oxygen species (Moore et al., 2007; Morris et al., 2008).
+MED4, SS120 and MIT9313 have been successfully cultured in laboratories, and used to show that ecotypic classifications correspond to biochemical differences among strains.
+CITATONS OUR LAB and OTHERS
+
+The main target of photoinhibition is PSII, in particular its PsbA protein, which along with its homolog PsbD forms a heterodimer binding all redox active components at the photosystem’s reaction center core and is therefore the most vulnerable to redox damage (Barber, 2012).
+Under light-induced damage, PsbA transcripts accumulate as the organism attempts to replace the damaged protein, however protein levels remain relatively constant, if inoperative.
+The new copy cannot be incorporated until the damaged one is degraded thus, the degradation of PsbA has been considered the rate-limiting step in recovery from photoinhibition (Kanervo et al., 1993).
+The proteins believed to be responsible for this crucial step are the FtsH proteases, which have been found localized to the thylakoid membrane of cyanobacteria and higher plants (Sacharz et al., 2015) as well as co-purified with His-tagged PSII (Zak et al., 2001).
+Furthermore, mutants lacking FtsH have increased sensitivity to photoinactivation (Mann et al., 2000; Adam et al., 2005).
+Originally identified in Escherichia coli, (Tomoyasu et al., 1993) FtsH is a membrane-bound, ATP, zinc metalloprotease that extracts and degrades membrane-bound proteins for degradation (Chiba et al., 2002).
+FtsH are embedded in membranes via two N-terminal transmembrane domains connected by a small hydrophilic loop in the thylakoid lumen (Figure 9A).
+The main hydrophilic portion sits in the bacterial cytoplasm and contains an ATP-ase Associated with various cellular Activities (AAA) domain as well as a zinc-binding active site (Yoshioka-Nishimura and Yamamoto, 2014) (Figure 10a).
+Chloroplast FtsH were first identified when immunoblot analysis with antibodies against E.
+coli FtsH cross reacted with thylakoid membrane proteins in spinach (Lindahl et al., 1996).
+The chloroplast genome of higher plants can encode up to 8 FtsH homologs (Adam et al., 2005).
+Cyanobacterial genomes encode only 4 homologs.
+In the model cyanobacterium Synechocystis sp.
+PCC 6803 (Synechocystis) these are encoded by the slr1390, slr0228, slr1604 and sll1463 genes, which will be used to identify their respective proteins for clarity.
+Slr0228 and sll1463 are found localized to patches in the thylakoid membrane (Sacharz et al., 2015) and it has been shown that sll1463 accumulation is dependent upon slr0228 (Pisareva et al., 2007).
+Furthermore, slr0228 has been shown to be indispensable for PSII repair and PSI biogenesis but intriguingly is not required for cell viability, nor is sll1463 (Mann et al., 2000).
+In contrast, slr1390 and slr1604 are found in both plasma and thylakoid membranes (Pisareva et al., 2007; Sacharz et al., 2015) and are essential for cell viability (Mann et al., 2000).
+FtsH proteases have been shown to associate in homo- and hetero-oligomers (Yu et al., 2004).
+In Synechocystis, slr1390 and slr1604 associate in hetero-oligomers (Sacharz et al., 2015).
+Slr0228 and slr1604 form a hetero-hexameric ring in the thylakoid membrane with a central pore through which proteins are translocated as they are digested and it is this complex that is responsible for PSII repair (Adam et al., 2005; Boehm et al., 2012) (Figure 10b).
+Nixon et al.
+(2010) have proposed a model for the PSII repair process in which destabilization of PsbA, resulting in either unusual exposure or post-translational modification of PsbA’s N-terminus (Komenda et al., 2007), exposes an N-terminal “docking site” for FtsH to initiate  degradation (Figure 11).
+
+Representatives of LL clades of *Prochlorococcus* suffer photoinhibition at irradiance levels preferred by their HL relatives.
+The main target of photoinhibition is PSII, in particular the PsbA protein, which along with its homolog PsbD forms a heterodimer binding all redox active components at the photosystem’s reaction center core and is therefore the most vulnerable to redox damage (Barber, 2012).
+Under light-induced damage, new PsbA cannot be incorporated until the damaged PsbA is removed thus, degradation of PsbA is a rate-limiting step in recovery from photoinhibition (Kanervo et al., 1993).
+PsbA degradation is mediated largely by FtsH proteases (Mann et al., 2000; Adam et al., 2005), localized to the thylakoid membrane (Sacharz et al., 2015) and PSII (Zak et al., 2001).
+FtsH is a membrane-bound, ATP, zinc metalloprotease that extracts and degrades membrane-bound proteins for degradation (Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
+In the model cyanobacterium *Synechocystis* sp.
+PCC 6803 4 isoforms of FtsH proteins are encoded by the slr1390, slr0228, slr1604 and sll1463 genes.
+Slr0228 and sll1463 are found localized to patches in the thylakoid membrane (Sacharz et al., 2015) and it has been shown that sll1463 accumulation is dependent upon slr0228 (Pisareva et al., 2007).
+Furthermore, slr0228 has been shown to be indispensable for PSII repair and PSI biogenesis but intriguingly is not required for cell viability, nor is sll1463 (Mann et al., 2000).
+In contrast, slr1390 and slr1604 are found in both plasma and thylakoid membranes (Pisareva et al., 2007; Sacharz et al., 2015) and are essential for cell viability (Mann et al., 2000).
+FtsH proteases have been shown to associate in homo- and hetero-oligomers (Yu et al., 2004).
+In Synechocystis, slr1390 and slr1604 associate in hetero-oligomers (Sacharz et al., 2015).
+Slr0228 and slr1604 form a hetero-hexameric ring in the thylakoid membrane with a central pore through which proteins are translocated as they are digested and it is this complex that is responsible for PSII repair (Adam et al., 2005; Boehm et al., 2012) (Figure 10b).
+Nixon et al.
+(2010) have proposed a model for the PSII repair process in which destabilization of PsbA, resulting in either unusual exposure or post-translational modification of PsbA’s N-terminus (Komenda et al., 2007), exposes an N-terminal “docking site” for FtsH to initiate  degradation (Figure 11).
+
+*Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4.
+Bonisteel et al.
+(2018) found that these were homologs of *Synechocystis* FtsH (Table 1).
+Upon a shift to higher light MED4 upregulated expression of FtsH1 and FtsH2, homologous to *Synechocystis* slr0228 and slr1604, implicated in PSII repair.
+In contrast representative LL strain MIT9313 shows less expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem,  MIT9313 expressed primarily FtsH3 and expression did not change in response to light stress.
+Bonisteel concluded with the hypothesis that LL Prochlorococcus may be allocating their energy resources to other processes that would advantage life under low light conditions.
+
+Table 1.
+FtsH protease homologs amongst the model cyanobacterium Synechocystis sp.
+PCC6803 and Prochlorococcus marinus.
+Protein homology determined by multiple sequence alignment with MUSCLE followed by construction of maximum likelihood phylogenetic tree using 1000 bootstrap replicates in MEGAX
+
+Organism	Protein Homolog			
+Prochlorococcus marinus	FtsH1	FtsH2	FtsH3	FtsH4
+Synechocystis sp. PCC6803	Slr0228	Slr1604	Sll1463	Slr1390
+k
+Function
+
+This correlates with the above research on photosystem composition in laboratory cultivated HL and LL Prochlorococcus.
+HL strains are found primarily in oligotrophic surface waters where light is abundant, thus allocate more of their energy to maintaining their photosynthetic apparatuses and can obtain energy from the reduction of sugars.
+In contrast, LL strains live under eponymically low irradiances and may depend on environmental nutrients and cyclic electron flow to maintain energy homeostasis.
 
@@
 
-%%%% Insert GAM figures to show lab results confirming Ocean Protein Portal environment results %%%
+\newpage
+
+```{r MED4PAR, fig.cap = MED4PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+
+MED4PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade) vs. photoperiod (h).  **",
+
+                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
+                    "Colors represent the actinic spectral waveband (nm).",
+                    "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "MED4PAR.png"))
+```
+
+\newpage
+
+```{r SS120PAR, fig.cap = SS120PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+
+SS120PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low Light (LLIII) deep ocean clade) vs. photoperiod (h). **",
+
+                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
+                    "Colors represent the actinic spectral waveband (nm).",
+                    "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "SS120PAR.png"))
+
+```
+
+\newpage
+
+```{r MIT9313PAR, fig.cap = MIT9313PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+
+MIT9313PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
+
+                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
+                    "Colors represent the actinic spectral waveband (nm).",
+                    "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "MIT9313PAR.png"))
+
+```
 
@@
 
-%%% TO DO Fits and ANOVA %%
-```{r MED4PAR, fig.cap = MED4PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}
-
-MED4PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade) vs. photoperiod (h).  **",
-
-                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
-                    "Colors represent the actinic spectral waveband (nm).",
-                    "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
-
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "MED4PAR.png"))
-```
-
-\newpage
-
-%%% TO DO Fits and ANOVA %%
-```{r SS120PAR, fig.cap = SS120PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}
-
-SS120PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low Light (LLIII) deep ocean clade) vs. photoperiod (h). **",
-
-                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
-                    "Colors represent the actinic spectral waveband (nm).",
-                    "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
-
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "SS120PAR.png"))
-
-```
-
-\newpage
-
-%%% TO DO Fits and ANOVA %%
-```{r MIT9313PAR, fig.cap = MIT9313PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}
-
-MIT9313PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
-
-                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
-                    "Colors represent the actinic spectral waveband (nm).",
-                    "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
-
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "MIT9313PAR.png"))
-
-```
-
-\newpage
-
 %%%% OceanFtsHRibosomeProteins figure from OceanPortal repository  %%%
@@
 
+# Acknowledgements
+Jonah Sheinin assisted with growth of some cultures for protein analyses.
+
+# Funding
+To Be Entered through PLoSONe system and deleted here
+Czech Academy of Science visiting fellowship (DAC)
+Canada Research Chair in Phytoplankton Ecophysiology (DAC)
+Natural Sciences and Engineering Research Council of Canada, 'Latitude and Light' (DAC)
+Canada Foundation for Innovation (DAC)
+New Brunswick Foundation for Innovation (DAC)
+Rice Graduate Fellowship (MS)
+
 # References {.unnumbered}

### 2024-02-15 Code/ManuscriptPURFits.Rmd
Combined PURfit for each strain into 1 plot

@@
 # library(RColorBrewer)
-# library(grid)
+library(grid)
+library(gridExtra)
 # library(bookdown)
@@
 #library(ggh4x)
-#library(cowplot)
+library(cowplot)
 #library(jmv)
@@
    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
-  labs(title = "MED4", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
+ geom_text(aes(x = 1000, y = 0.9, label= "A"), data = . %>% filter(O2_uM == 250, Strain == "MED4"), size = 20, hjust = 0.3, vjust = 0) +
   scale_x_continuous(label=scientific_10) +
@@
    scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(O2_uM), 
-                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
+  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
+                    labeller = labeller(Strain = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
  guides(linetype = guide_legend(nrow = 4),
@@
    theme( strip.text = element_text(size = 30),
-        axis.title = element_text(size = 30, color = "black"),
-        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
+        axis.title.y = element_blank(),
+        axis.title.x.bottom = element_blank(),
+        axis.text.x = element_blank(),
         axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
@@
    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
-     labs(title = "SS120", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
+ geom_text(aes(x = 1000, y = 0.9, label= "B"), data = . %>% filter(O2_uM == 250, Strain == "SS120"), size = 20, hjust = 0.3, vjust = 0) +
   scale_x_continuous(label=scientific_10) +
@@
    scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(O2_uM), 
-                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
- guides(linetype = guide_legend(nrow = 4),
-        fill = "none",
-        colour = guide_legend(nrow = 4)) +
- guides(shape = guide_legend(nrow = 4)) +
+  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
+                    labeller = labeller(Strain = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
+ # guides(linetype = guide_legend(nrow = 4),
+ #        fill = "none",
+ #        colour = guide_legend(nrow = 4)) +
+ # guides(shape = guide_legend(nrow = 4)) +
   theme_bw() +
    theme( strip.text = element_text(size = 30),
-        axis.title = element_text(size = 30, color = "black"),
-        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
+        axis.title.y = element_blank(),
+        axis.title.x.bottom = element_blank(),
+        axis.text.x = element_blank(),
         axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
@@
         legend.text = element_text(size = 30),   #change legend text font size
-        legend.position = "top") +
+        legend.position = "none") +
   labs( shape = "Photoperiod (h)",
@@
    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +
-  labs(title = "MIT9313", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
+  labs(x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
+ geom_text(aes(x = 1000, y = 0.9, label= "C"), data = . %>% filter(O2_uM == 250, Strain == "MIT9313"), size = 20, hjust = 0.3, vjust = 0) +
   scale_x_continuous(label=scientific_10) +
@@
    scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(O2_uM), 
-                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
+  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
+                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
  guides(linetype = guide_legend(nrow = 4),
@@
    theme( strip.text = element_text(size = 30),
-        axis.title = element_text(size = 30, color = "black"),
+          axis.title.y = element_blank(),
+          axis.title.x = element_text(size = 30, color = "black"),
           axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
@@
 MIT9313PURFITPlot
+
+```
+
+# Combine the 3 strains into 1 plot 
+```{r combine plots}
+
+AllStrainPurFitsPlots <- plot_grid(MED4PURFITPlot, SS120PURFITPlot, MIT9313PURFITPlot, ncol = 1)
+
+#create common x and y labels
+y.grob <- textGrob("Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")",
+                   gp = gpar(col="black", fontsize = 20), rot = 90)
+
+#add to plot
+AllStrainPurFitsPlots <- grid.arrange(arrangeGrob(AllStrainPurFitsPlots, left = y.grob))
 
@@
 
-ggsave(file = file.path(PlotsOut, paste("MED4PURFITPlot",".png",sep = "")), plot = MED4PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("AllStrainPurFitsPlots",".png",sep = "")), plot = AllStrainPurFitsPlots, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
 
-ggsave(file = file.path(PlotsOut, paste("SS120PURFITPlot",".png",sep = "")), plot = SS120PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("AllStrainPurFitsPlots",".tiff",sep = "")), plot = AllStrainPurFitsPlots, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
 
-ggsave(file = file.path(PlotsOut, paste("MIT9313PURFITPlot",".png",sep = "")), plot = MIT9313PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-ggsave(file = file.path(PlotsOut, paste("MED4PURFITPlot",".tiff",sep = "")), plot = MED4PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-ggsave(file = file.path(PlotsOut, paste("SS120PURFITPlot",".tiff",sep = "")), plot = SS120PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-ggsave(file = file.path(PlotsOut, paste("MIT9313PURFITPlot",".tiff",sep = "")), plot = MIT9313PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsOut, paste("MED4PURFITPlot",".png",sep = "")), plot = MED4PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+# 
+# ggsave(file = file.path(PlotsOut, paste("SS120PURFITPlot",".png",sep = "")), plot = SS120PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+# 
+# ggsave(file = file.path(PlotsOut, paste("MIT9313PURFITPlot",".png",sep = "")), plot = MIT9313PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+# 
+# ggsave(file = file.path(PlotsOut, paste("MED4PURFITPlot",".tiff",sep = "")), plot = MED4PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+# 
+# ggsave(file = file.path(PlotsOut, paste("SS120PURFITPlot",".tiff",sep = "")), plot = SS120PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+# 
+# ggsave(file = file.path(PlotsOut, paste("MIT9313PURFITPlot",".tiff",sep = "")), plot = MIT9313PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
 

### 2024-02-15 Code/Manuscript_O2.Rmd

@@
 
-*Prochlorococcus* are difficult to culture, as their reduced genome – the smallest of any known oxyphototroph – render them partially dependent upon mutualistic heterotrophic bacteria to  detoxify reactive oxygen species (Moore et al., 2007; Morris et al., 2008).
+*Prochlorococcus* are difficult to culture, as their reduced genomes – the smallest of any known oxyphototroph – render them partially dependent upon mutualistic heterotrophic bacteria to  detoxify reactive oxygen species (Moore et al., 2007; Morris et al., 2008).
 MED4, SS120 and MIT9313 have been successfully cultured in laboratories, and used to show that ecotypic classifications correspond to biochemical differences among strains.
-CITATONS OUR LAB and OTHERS
+CITATONS OUR LAB and OTHERS.
 
-The main target of photoinhibition is PSII, in particular its PsbA protein, which along with its homolog PsbD forms a heterodimer binding all redox active components at the photosystem’s reaction center core and is therefore the most vulnerable to redox damage (Barber, 2012).
-Under light-induced damage, PsbA transcripts accumulate as the organism attempts to replace the damaged protein, however protein levels remain relatively constant, if inoperative.
-The new copy cannot be incorporated until the damaged one is degraded thus, the degradation of PsbA has been considered the rate-limiting step in recovery from photoinhibition (Kanervo et al., 1993).
-The proteins believed to be responsible for this crucial step are the FtsH proteases, which have been found localized to the thylakoid membrane of cyanobacteria and higher plants (Sacharz et al., 2015) as well as co-purified with His-tagged PSII (Zak et al., 2001).
-Furthermore, mutants lacking FtsH have increased sensitivity to photoinactivation (Mann et al., 2000; Adam et al., 2005).
-Originally identified in Escherichia coli, (Tomoyasu et al., 1993) FtsH is a membrane-bound, ATP, zinc metalloprotease that extracts and degrades membrane-bound proteins for degradation (Chiba et al., 2002).
-FtsH are embedded in membranes via two N-terminal transmembrane domains connected by a small hydrophilic loop in the thylakoid lumen (Figure 9A).
-The main hydrophilic portion sits in the bacterial cytoplasm and contains an ATP-ase Associated with various cellular Activities (AAA) domain as well as a zinc-binding active site (Yoshioka-Nishimura and Yamamoto, 2014) (Figure 10a).
-Chloroplast FtsH were first identified when immunoblot analysis with antibodies against E.
-coli FtsH cross reacted with thylakoid membrane proteins in spinach (Lindahl et al., 1996).
-The chloroplast genome of higher plants can encode up to 8 FtsH homologs (Adam et al., 2005).
-Cyanobacterial genomes encode only 4 homologs.
-In the model cyanobacterium Synechocystis sp.
-PCC 6803 (Synechocystis) these are encoded by the slr1390, slr0228, slr1604 and sll1463 genes, which will be used to identify their respective proteins for clarity.
-Slr0228 and sll1463 are found localized to patches in the thylakoid membrane (Sacharz et al., 2015) and it has been shown that sll1463 accumulation is dependent upon slr0228 (Pisareva et al., 2007).
-Furthermore, slr0228 has been shown to be indispensable for PSII repair and PSI biogenesis but intriguingly is not required for cell viability, nor is sll1463 (Mann et al., 2000).
-In contrast, slr1390 and slr1604 are found in both plasma and thylakoid membranes (Pisareva et al., 2007; Sacharz et al., 2015) and are essential for cell viability (Mann et al., 2000).
-FtsH proteases have been shown to associate in homo- and hetero-oligomers (Yu et al., 2004).
-In Synechocystis, slr1390 and slr1604 associate in hetero-oligomers (Sacharz et al., 2015).
-Slr0228 and slr1604 form a hetero-hexameric ring in the thylakoid membrane with a central pore through which proteins are translocated as they are digested and it is this complex that is responsible for PSII repair (Adam et al., 2005; Boehm et al., 2012) (Figure 10b).
-Nixon et al.
-(2010) have proposed a model for the PSII repair process in which destabilization of PsbA, resulting in either unusual exposure or post-translational modification of PsbA’s N-terminus (Komenda et al., 2007), exposes an N-terminal “docking site” for FtsH to initiate  degradation (Figure 11).
-
-Representatives of LL clades of *Prochlorococcus* suffer photoinhibition at irradiance levels preferred by their HL relatives.
-The main target of photoinhibition is PSII, in particular the PsbA protein, which along with its homolog PsbD forms a heterodimer binding all redox active components at the photosystem’s reaction center core and is therefore the most vulnerable to redox damage (Barber, 2012).
-Under light-induced damage, new PsbA cannot be incorporated until the damaged PsbA is removed thus, degradation of PsbA is a rate-limiting step in recovery from photoinhibition (Kanervo et al., 1993).
-PsbA degradation is mediated largely by FtsH proteases (Mann et al., 2000; Adam et al., 2005), localized to the thylakoid membrane (Sacharz et al., 2015) and PSII (Zak et al., 2001).
-FtsH is a membrane-bound, ATP, zinc metalloprotease that extracts and degrades membrane-bound proteins for degradation (Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
+Under full atmospheric [O~2~], LL clades of *Prochlorococcus* are restricted to growth under low light, in part because they suffer photoinhibition of Photosystem II (PSII) at irradiances preferred by their HL relatives.
+The main target of photoinhibition is the PsbA protein, which along with its homolog PsbD forms a heterodimer binding all redox active components of the PSII reaction center core (Barber, 2012).
+Under light-induced damage, new PsbA cannot be incorporated until the damaged PsbA is removed.
+Thus, degradation of PsbA, mediated largely by FtsH proteases (Mann et al., 2000; Adam et al., 2005), is a rate-limiting step in recovery from photoinhibition (Kanervo et al., 1993).
+FtsH is a membrane-bound (Sacharz et al., 2015)(Zak et al., 2001), ATP, zinc metalloprotease that extracts and degrades membrane-bound proteins for degradation (Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
 In the model cyanobacterium *Synechocystis* sp.
 PCC 6803 4 isoforms of FtsH proteins are encoded by the slr1390, slr0228, slr1604 and sll1463 genes.
-Slr0228 and sll1463 are found localized to patches in the thylakoid membrane (Sacharz et al., 2015) and it has been shown that sll1463 accumulation is dependent upon slr0228 (Pisareva et al., 2007).
-Furthermore, slr0228 has been shown to be indispensable for PSII repair and PSI biogenesis but intriguingly is not required for cell viability, nor is sll1463 (Mann et al., 2000).
-In contrast, slr1390 and slr1604 are found in both plasma and thylakoid membranes (Pisareva et al., 2007; Sacharz et al., 2015) and are essential for cell viability (Mann et al., 2000).
-FtsH proteases have been shown to associate in homo- and hetero-oligomers (Yu et al., 2004).
-In Synechocystis, slr1390 and slr1604 associate in hetero-oligomers (Sacharz et al., 2015).
-Slr0228 and slr1604 form a hetero-hexameric ring in the thylakoid membrane with a central pore through which proteins are translocated as they are digested and it is this complex that is responsible for PSII repair (Adam et al., 2005; Boehm et al., 2012) (Figure 10b).
-Nixon et al.
-(2010) have proposed a model for the PSII repair process in which destabilization of PsbA, resulting in either unusual exposure or post-translational modification of PsbA’s N-terminus (Komenda et al., 2007), exposes an N-terminal “docking site” for FtsH to initiate  degradation (Figure 11).
+In *Synechocystis*, Slr0228 and slr1604 form a hetero-hexameric ring in the thylakoid membrane with a central pore through which proteins are translocated as they are digested, a process key for PSII repair (Adam et al., 2005; Boehm et al., 2012) (Nixon et al.
+(2010)) (Komenda et al., 2007), when photoinactivation exposes an N-terminal “docking site” for FtsH to initiate degradation.
+In contrast, slr1390 and slr1604 are found in both plasma and thylakoid membranes (Pisareva et al., 2007; Sacharz et al., 2015), are essential for cell viability (Mann et al., 2000), and implicated in PSI biogenesis (AMANDA REF from ALGATECH).
 
-*Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4.
-Bonisteel et al.
-(2018) found that these were homologs of *Synechocystis* FtsH (Table 1).
-Upon a shift to higher light MED4 upregulated expression of FtsH1 and FtsH2, homologous to *Synechocystis* slr0228 and slr1604, implicated in PSII repair.
-In contrast representative LL strain MIT9313 shows less expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem,  MIT9313 expressed primarily FtsH3 and expression did not change in response to light stress.
-Bonisteel concluded with the hypothesis that LL Prochlorococcus may be allocating their energy resources to other processes that would advantage life under low light conditions.
+*Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4, homologous to the *Synechocystis* FtsH isofoms, and with presumably parallel functions (Table 1).
+Upon a shift to higher light HLIII MED4 upregulated expression of FtsH1 and FtsH2 (Bonisteel et al.
+(2018)), homologs to *Synechocystis* slr0228 and slr1604, implicated in PSII repair.
+In contrast representative LLIII strain MIT9313 shows less overall expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem.
+Furthermore MIT9313 expressed primarily FtsH3 and expression did not increase in response to light stress.
+Through adaptation to steady low light, LLIII **Prochlorococcus* allocate resources to other processes.
 
@@
 Function
-
-This correlates with the above research on photosystem composition in laboratory cultivated HL and LL Prochlorococcus.
-HL strains are found primarily in oligotrophic surface waters where light is abundant, thus allocate more of their energy to maintaining their photosynthetic apparatuses and can obtain energy from the reduction of sugars.
-In contrast, LL strains live under eponymically low irradiances and may depend on environmental nutrients and cyclic electron flow to maintain energy homeostasis.
 

### 2024-02-15 Code/Manuscript_O2.Rmd
Dumped Intros from Chapter 1,2 and 3 MIreille Thesis. Fixed Max's affiliation from #4 to #3 but that did not fix the problem with the YAML

@@
   - ubc: 'Department of Biology, University of British Columbia'
-  - num: 4
+  - num: 3
 institute:
@@
 # Introduction {.unnumbered}
+
+## Mireille
+### Chapter 1 General Intro
+
+Marine phytoplankton are ubiquitous and serve as an important base of the aquatic food chain.
+They contribute to more than 50% of the net global primary food production [@falkowskiOceanSciencePower2012], while comprising only a small fraction of the global primary producer biomass [@fieldPrimaryProductionBiosphere1998].
+*Prochlorococcus marinus*, a genus of the phylum Cyanobacteria, is the smallest known photosynthetic prokaryote, with cell diameters ranging from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992].
+Despite a small cell size, *P.
+marinus* contribute 13 to 48% of net primary production in oligotrophic oceans, corresponding to about 30% of  global oxygen production [@partenskyProchlorococcusMarinePhotosynthetic1999].
+
+*Prochlorococcus marinus* comprises many strains, organized into clades,
+which in turn are grouped into ecotypes defined largely as High-Light (HL) or Low-Light (LL) adapted,  and aligned phylogenetically [@moorePhysiologyMolecularPhylogeny1998].
+The biomass distribution of *P.
+marinus* is constrained to between latitudes of 40°N to 40°S in open ocean waters [@partenskyProchlorococcusMarinePhotosynthetic1999] with different ecotypes inhabiting distinct ecological niches.
+High-Light ecotypes are typically observed as the dominant picophytoplankton in near-surface oligotrophic waters that are, characterized by low nutrient concentrations, and high light levels.
+The monophyletic high light ecotype is subdivided into clades based on iron adaptation, whereby HLIII/IV are low iron adapted, whereas HLI is a high iron, low temperature adapted clade and HLII is a high iron, high temperature adapted clade [@kentParallelPhylogeographyProchlorococcus2019; @johnsonNichePartitioningProchlorococcus2006; @zinserInfluenceLightTemperature2007].
+Low-Light ecotypes thrive in deeper ocean waters, extending beyond 200 m in depth [@partenskyProchlorococcusMarinePhotosynthetic1999].
+In these deeper regions, only 1% of the surface irradiance penetrates, primarily in the blue (450 nm) to green (520 nm) spectral waveband ranges, due to light and spectral attenuation [@holtropVibrationalModesWater2021].
+Additionally, some *P.
+marinus* strains in clade LLV and LLVI thrive in  Oxygen Minimum Zones (OMZ) of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021].
+Currently there are at least 12 clades but only 5 have been cultivated; HLI, HLII, LLI, LLII/III and LIV [@billerProchlorococcusStructureFunction2015].
+
+Our changing climate, characterized by warming ocean waters, is rapidly altering conditions for these highly specialized strains of marine picophytoplankton.
+Predictions indicate a net global increase of *P.
+marinus* cell abundances of 29% and poleward latitudinal shifts of at least 10° in marine phytoplankton niches by the end of this century [@flombaumPresentFutureGlobal2013] in response to warming waters, with cell abundance increases of approximately 50% in the more poleward regions.
+As the solar incidence angles are lower and photoperiod seasonality is more pronounced at higher latitudes, this shift will carry these phytoplankters into new combinations of photoperiod, seasonal regimes and changing spectral regimes [@bartonAnthropogenicClimateChange2016].
+A 10° poleward shift of *P.
+marinus*, coupled with a dramatic increase in cell abundance between 40°N and 50°N,  could have a large impact on ocean ecosystems and global biogeochemical cycles [@flombaumPresentFutureGlobal2013], and thus will undoubtedly impact the ecosystem balance off our Canadian waters.
+
+Global warming is also rapidly changing the chemistry of our oceans.
+By the end of this century, surface ocean pH is projected to decline by 0.1 to 0.4  due to  projected increases in carbon dioxide concentrations [@garcia-sotoOverviewOceanClimate2021].
+Moreover, substantial changes in the global water cycle, leading to extensive changes in worldwide precipitation patterns, are affecting ocean salinity levels on a global scale, and  ice melts due to rising temperatures are impacting salinity levels in the Arctic and Northwest Atlantic oceans [@leeRecognizingSalinityThreats2022].
+There is evidence that increasing sea temperatures are also causing a decrease in [O~2~] across our global oceans [@matearLongtermChangesDissolved2003], with significant declines observed toward the poles in both hemispheres [@helmObservedDecreasesOxygen2011].
+Warmer ocean waters decrease oxygen solubility at the surface which in turn reduces the amount of oxygen that can be mixed downwards by ocean currents [@garcia-sotoOverviewOceanClimate2021].
+Furthermore, models predict that the OMZ in the Pacific and Indian Oceans are expanding [@garcia-sotoOverviewOceanClimate2021; @buseckeDivergingFatesPacific2022].
+In light of these expanding OMZ, a recent study by @buseckeDivergingFatesPacific2022 highlights an intriguing finding; the core of the OMZ, where the oxygen levels are lowest, is projected to contract.
+Given the predicted decrease in overall oceanic [O~2~],   projected expansion of OMZs, and possibly decline in the OMZ core volumes, we set forth to examine the influence of [O~2~] on *P.
+marinus* growth as this area of research has been relatively understudied.
+
+To determine the viability of *P.
+marinus* strains in changing ecosystems, we analyzed the growth and physiological responses of representative strains from three clades to varying [O~2~], light levels, spectral waveband ranges, and photoperiods,  to simulate a matrix of eco-physiological conditions representative of current and hypothetical future ocean zones.
+The following *P.
+marinus* clades were examined: *P.
+marinus* MED4, classified as a clade HLI (Figure \@ref(fig:PhylogenyTreeYan2018edit)), was isolated near the ocean surface (5m depth) of the Mediterranean Sea where [O~2~] are near saturation, light levels are high and spectral bias from full solar irradiance is minimal.
+*P.
+marinus* SS120, a clade LLIII (Figure \@ref(fig:PhylogenyTreeYan2018edit)), was isolated from the Sargasso Sea at a depth of 120 m, while *P.
+marinus* MIT9313, a clade LLIV (Figure \@ref(fig:PhylogenyTreeYan2018edit)), was isolated from the North Atlantic Gulf Stream at a depth of 135 m.
+At these depths, light attenuation and spectral shifts occur, resulting in low blue and green light levels, while [O~2~] varies from near-surface saturation levels to decreased concentrations, but it does not necessarily decrease with depth [@billheimerOxygenSeasonalityUtilization2021].
+In chapter 2, we define the interactions between oxygen, light level, light colour and photoperiod that help define their complex niches.
+
+In chapter 3, to better decipher the physiological processes driving the observed growth responses to a complex matrix of spectral light regimes and [O~2~], we express growth rates in terms of cumulative diel Photosynthetically Usable Radiation (PUR).
+Photosynthetic organisms rely on absorbing light energy within the visible spectrum, 350 to 700 nm, for photosynthesis.
+This range of light, known as Photosynthetic Active Radiation (PAR) [@morelAvailableUsableStored1978], is essential for the photosynthetic process.
+PUR represents the fraction of PAR that is absorbed by the pigments of photosynthetic organisms [@morelAvailableUsableStored1978], thus we can compare light levels across different spectral wavebands that are absorbed differently by cells.
+Moreover, expressing growth rates in terms of cumulative diel absorbed PUR has the potential to simplify different photoperiods, spectral bands, and PAR levels into a common parameter, making growth response comparisons across different oxygen levels more attainable and may allow us to determine whether growth responses are primarily influenced by cumulative diel absorbed PUR, specific photoperiods or spectral bands.
+
+To the best of our knowledge, no other laboratory study has extensively examined the growth response of *Prochlorococcus* under such a diverse set of conditions.
+This study specifically focuses on evaluating how *Prochlorococcus* responds to varying [O~2~], different spectral wavebands, light levels and photoperiods.
+This comprehensive approach distinguishes this study from previous ones conducted on *Prochlorococcus* growth.
+
+### Chapter 2 PAR Intro
+*Prochlorococcus marinus* ecotypes are characterized by their distinct
+tolerance for High-Light (HL) or Low-Light (LL) levels
+[@moorePhysiologyMolecularPhylogeny1998]. *Prochlorococcus marinus* is
+classified into at least 12 major clades
+[@billerProchlorococcusStructureFunction2015], that respectively inhabit
+a range of ecological niches across vertical ocean water columns
+[@chisholmNovelFreelivingProchlorophyte1988;
+@veldhuisVerticalDistributionPigment1990;
+@partenskyProchlorococcusMarinePhotosynthetic1999].
+
+Previous studies have observed that the diversification of *P. marinus*
+niches extends into regions considered unfavorable for photosynthesis to
+occur. @goerickeNovelNicheProchlorococcus2000 first reported the
+existence of *P. marinus* below the oxyclines of the Oxygen Minimum
+Zones (OMZ) of the Arabian Sea and the Eastern Tropical North Pacific.
+In an OMZ, oxygen concentrations [O~2~] can be less than 20 µM, and in
+some regions [O~2~] is undetectable
+[@garcia-robledoCrypticOxygenCycling2017a]. Subsequent research has
+revealed that *P. marinus* LL ecotypes dominate the OMZ
+[@lavinNovelLineagesProchlorococcus2010;
+@ulloaCyanobacteriumProchlorococcusHas2021] and are believed to
+contribute to approximately 90% of the *P. marinus* diversity in the
+eastern tropical Pacific Ocean OMZ
+[@partenskyProchlorococcusAdvantagesLimits2010].
+
+Although *P. marinus* ecotypes are defined by their ecological niches,
+there is evidence to suggest that ecotypes can exist in environments
+beyond their optimal habitats. HL ecotypes are known to
+inhabit depths where LL ecotypes also inhabit
+[@westNichePartitioningProchlorococcusPopulationsStratified1999;
+@zinserInfluenceLightTemperature2007;
+@delmontLinkingPangenomesMetagenomes2018] but at light levels still
+within the range of confirmed growth irradiance limits
+[@moorePhotophysiologyMarineCyanobacterium1999]. Studies by
+@lavinNovelLineagesProchlorococcus2010 and
+@mattisonPhotosyntheticStrategiesWild2020 show evidence that LL ecotypes
+can occupy regions in the OMZ at depths above 40 m. Since light levels
+were not reported at every depth of these studies, it is presumed that
+at a depth of 40 m, closer to the surface, light levels are higher than
+what LL ecotypes can tolerate. Furthermore,
+@mattisonPhotosyntheticStrategiesWild2020 presented evidence of proteins
+derived from HL ecotypes of *P. marinus* in the OMZ at depths up to 200
+meters with O~2~ of 15 µM. However, the extent to which [O~2~] defines
+the niches occupied by different *P. marinus* ecotypes, as compared to
+potentially covarying environmental variables like photoperiod, light
+spectrum, and light level, is poorly described.
+
+Photosynthetic organisms rely on the absorption of light energy within
+the visible spectral range of 350 to 700 nm to drive the photosynthetic
+process. This spectral range of light, known as Photosynthetic Active
+Radiation (PAR) [@morelAvailableUsableStored1978], is essential for
+photosynthesis. However, as sunlight enters the marine environment, it
+undergoes attenuation, resulting in a decline of specific wavebands of
+light through the water column from the surface. This attenuation
+primarily affects the longer wavelengths in the red region of the
+spectrum (600 to 700 nm), followed by wavelengths in the green region
+(500 to 600 nm) and, finally, wavelengths in the blue region (400 to 500
+nm) [@holtropVibrationalModesWater2021]. Thus, as sunlight penetrates the
+marine environment, the light level diminishes and the residual spectral
+wavebands shift with depth, where only blue spectral wavelengths
+dominate. The region of the water column with enough light to support
+photosynthesis is known as the photic zone, defined as the depth where
+light levels remain above 20 µmol photons m^-2^ s^-1^, 1% of the surface
+solar incident radiation, of 2000 µmol photons m^-2^ s^-1^.
+
+In growth studies of *P. marinus*, it is common to use a broad spectrum
+light source to approximate the solar spectral wavelengths found in the
+uppermost layers of the ocean. The actinic photon flux is adjusted to
+simulate the specific light levels appropriate for the ecotype of
+interest. However, this approach falls short when attempting to
+accurately reproduce the ambient spectral light quality of deep ocean
+habitats, where only blue spectral wavelengths prevail
+[@holtropVibrationalModesWater2021]. *Prochlorococcus marinus* contain a
+unique light-harvesting complex composed primarily of divinyl
+chlorophyll a and b [@chisholmProchlorococcusMarinusNov1992;
+@goerickePigmentsProchlorococcusMarinus1992], the only photosynthetic
+organism to possess these chlorophyll derivatives. The absorption maxima
+of 442 nm for divinyl chlorophyll a and 478 nm for divinyl chlorophyll b
+[@goerickePigmentsProchlorococcusMarinus1992] allow *P. marinus* to
+efficiently harvest the light energy emitted by blue light in the 400 nm
+to 500 nm range [@morelAvailableUsableStored1978].
+
+At most latitudes, the duration of the photoperiod (day length)
+undergoes seasonal variations. However, at the equator, the photoperiod
+remains relatively constant at the ocean surface, approximately 12 hours
+(h) of daylight and 12 h of darkness throughout the entire year. As *P.
+marinus* potentially expands its temperature-permissive niches poleward
+into temperate regions due to climate change
+[@flombaumPresentFutureGlobal2013;
+@bartonAnthropogenicClimateChange2016], it will encounter more
+pronounced seasonal variations in photoperiod regimes. Photoperiods are
+longer at temperate regions during the summer, while in spring, fall and
+winter, photoperiods are shorter. Additionally, when considering the
+influence of light attenuation with depth, temperate regions exhibit
+more combinations of photoperiod compared to equatorial regions. The
+effects of photoperiod on the ecophysiology of phytoplankton is
+underscored by several studies. @liDiatomGrowthResponses2017
+demonstrated complex interactions of photoperiod and growth rate of
+diatoms. Similarly, @prezelinDielPeriodicityPhytoplankton1992 expressed
+the importance of considering photoperiod on *in situ* rates of primary
+production, as the diel light to dark ratio regulates metabolic
+processes throughout the day. Furthermore,
+@vaulotGrowthProchlorococcusPhotosynthetic1995 showed that
+*Prochlorococcus* undergoes DNA replication in the afternoon, while cell
+division occurs at night. Further research is needed to investigate the
+impact of different photoperiods on the growth of *Prochlorococcus*, as
+this aspect remains inadequately studied.
+
+\newpage
+
+(fig:SunDepth) shows light levels and spectral waveband
+attenuation at ocean surface to ocean depths of 1000 m, as well as the
+hours of light above the minimum photic zone of 20 µmol photons m^-2^
+s^-1^, representing the photoperiod. This figure is modeled using the
+solar incident angle at 45°N, a hypothetical future niche, at summer
+solstice and illustrates the light parameters that define the
+photoregimes of the niches of *P. marinus* that we studied. Figure (fig:CardinalSeasons) illustrates light attenuation through ocean waters at 45°N at winter solstice, equinox and summer solstice.
+
+### Chapter 3 Intro (PUR)
+
+*Prochlorococcus marinus* ecotypes are characterized by their distinct
+tolerance for High-Light (HL) or Low-Light (LL) levels.
+The photosynthetic strategies between *Prochlorococcus marinus* ecotypes must differ in order to exploit the very diverse photo regimes in their respective niches and may be explained by their unique cellular compositions.
+*Prochlorococcus marinus* MED4 has the smallest genome size of the 3 ecotypes we studied, only 1.66 Mbp, while *P.
+marinus* MIT9313 has the largest genome size of 2.41 Mbp [@rocapGenomeDivergenceTwo2003].
+*Prochlorococcus marinus* SS120 genome size is 1.75 Mbp [@dufresneGenomeSequenceCyanobacterium2003].
+Due to the small genome size and small cell diameters, ranging from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992], *Prochlorococcus* are the smallest known photosynthetic prokaryote.
+The simplistic cellular structure and small size of *P.
+marinus* minimizes the pigment package effect or intracellular self-shading, due to the high surface area to volume ratio, contributing to very efficient optical absorption capabilities [@morelProchlorococcusSynechococcusComparative1993].
+
+Photosynthetic organisms depend on the absorption of light energy in the visible spectrum, 350 to 700 nm, to carry out photosynthesis.
+This range of light, referred to as Photosynthetic Active Radiation (PAR) [@morelAvailableUsableStored1978], is crucial for the photosynthetic process.
+The Photosynthetic Usable Radiation (PUR) is defined as the fraction of PAR absorbed by the pigments of a given photosynthetic taxon [@morelAvailableUsableStored1978].
+PUR, therefore, takes into account the pigment composition of photosynthetic organisms and the specific spectral wavebands that these pigments absorb.
+*Prochlorococcus marinus* MED4, a clade HLI ecotype, dominate the near ocean surface where spectral attenuation from full solar irradiance is minimal and light levels are high [@partenskyProchlorococcusMarinePhotosynthetic1999].
+*Prochlorococcus marinus* SS120, a clade LLIII ecotype, and *P.
+marinus* MIT9313, a clade LLIV ecotype, dominate the deep ocean [@partenskyProchlorococcusMarinePhotosynthetic1999] where extreme light attenuation and spectral shifts occur, resulting in the availability of very low light levels in the blue (450 nm) to green (520 nm) spectral range [@holtropVibrationalModesWater2021].
+Given the different spectral light regimes of the different ecotype niches, understanding how the quantity of available light levels, PAR, converts to what these ecotypes can use, PUR, can give some insight into how they are able to exploit light energy.
+
+The photosynthesis process can be divided into two distinct reactions: the
+light-dependent and the light-independent reactions. *Prochlorococcus marinus* does not contain
+chloroplasts [@chisholmNovelFreelivingProchlorophyte1988], and the
+light-dependent reactions occur in thylakoid membranes arranged concentrically around the periphery of the cell. Light harvesting complexes spanning a thylakoid membrane capture or 'harvest' light
+energy. The light harvesting complexes in *P. marinus* consist of Prochlorophyte Chlorophyll Binding
+proteins (Pcb) [@larocheIndependentEvolutionProchlorophyte1996]. Once photons are absorbed by light harvesting pigments, the energy is transferred to the reaction center of Photosystem II
+(PSII) where water is split, catalyzed by the manganese cluster of the
+oxygen evolving complex. Here, 2 water molecules are oxidized to produce 1 oxygen
+(O~2~) molecule, releasing 4 protons into the thylakoid lumen, which contribute to the transmembrane proton
+potential,  and 4 electrons. These electrons are passed to Photosystem I
+(PSI) through a series of reduction and oxidation reactions in the
+electron transport chain in the thylakoid membrane, and in the process, deliver more protons to the
+proton pool within the lumen side of the thylakoid membrane. Photosystem I
+(PSI) also harvest light energy but does not split water, rather the
+reaction center uses excitation energy to excite electrons received from PSII
+and transfer them by the reduction and oxidation of iron-sulphur
+clusters to reduce NADP^+^ to NADPH. The Adenosine Triphosphate (ATP) synthase complex produces ATP in the stroma, driven by protons passing from the lumen out to the stroma side of the thylakoid
+membrane. The light-independent reaction involves the RuBisCO enzyme
+which uses the NADPH and ATP generated in the light-dependent reaction
+to convert dissolved carbon dioxide (CO~2~) gas into carbohydrates.
+
+*Prochlorococcus marinus* is differentiated from other cyanobacteria as a distinct lineage, primarily due to the absence of phycobilisomes [@chisholmProchlorococcusMarinusNov1992].
+Instead, *Prochlorococcus*  utilizes intra-membrane Pcb proteins bound to divinylchlorophyll a (Chl a2), and α-carotene, as the major light harvesting complex [@goerickePigmentsProchlorococcusMarinus1992]; [@larocheIndependentEvolutionProchlorophyte1996].
+Not all *Prochlorococcus* encode the same number of Pcb proteins.
+The representative of HLI clade, *P.
+marinus* MED4 has 1 gene encoding pcbA protein [@garczarekMultiplicationAntennaGenes2000] and the LLIV clade, *P.
+marinus* MIT9313, has 2 genes encoding pcbB and pcbG proteins [@rocapGenomeDivergenceTwo2003].
+The LLIII clade, *P.
+marinus* SS120, however, has 7 genes encoding pcbA, pcbB, pcbC, pcbE, pcbF, pcbG and pcbH [@garczarekMultiplicationAntennaGenes2000].
+According to @garczarekMultiplicationAntennaGenes2000, the expression of some of the pcb genes might be specifically induced under low light conditions, after noting the thickening of the antenna band of the thylakoid membrane when SS120 was switched to low light after high light exposure.
+Another difference within the cell structure among *P.
+marinus* ecotypes is the 2 to 4 thylakoids that run parallel to the cell membrane.
+For SS120, the thylakoids are closed around the periphery of the cell; however, in MED4 and MIT9313, there is a gap resulting in a horseshoe shape for the thylakoids [@partenskyProchlorococcusMarinePhotosynthetic1999].
+Despite the deviation in the light harvesting complex from cyanobacteria, the genes encoding the rest of photosynthetic apparatus is highly conserved in *Prochlorococcus* [@kettlerPatternsImplicationsGene2007], though the photosynthetic efficiency may vary between ecotypes [@hessPhotosyntheticApparatusProchlorococcus2001; @moorePhotophysiologyMarineCyanobacterium1999].
+
+The efficient ability of *P.
+marinus* to harvest light energy allows LL ecotypes to thrive and exploit the low, attenuated light levels present in deep ocean waters.
+However, this efficiency also makes them vulnerable to photo damage under high light levels [@aroPhotoinhibitionPhotosystemII1993; @soitamoPhotoinhibitionMarinePicocyanobacteria2017].
+The proteins in the reaction centers of PSII are vulnerable to photo damage, which can result in the disruption of electron transport and irreversible damage to the reaction center subunit D1 protein [@murphyPhotoinactivationPhotosystemII2017].
+Additionally, direct absorption of a photon in the UV or blue range by the Mn~4~Ca cluster within the oxygen-evolving complex of PSII can lead to its inactivation [@hakalaEvidenceRoleOxygenevolving2005].
+Without the proper functioning of the oxygen-evolving complex, the P680^+^ radical, which is formed during the light absorption process, cannot be efficiently reduced.
+This can result in the accumulation of P680^+^ radicals and lead to irreversible oxidative damage to the PsbA protein, within PSII.
+The damaged PsbA protein must then be removed to reactivate the PSII center.
+This process relies on the degradation and removal of damaged PsbA by protease isoforms FtsH 2 and 3 and the production of newly synthesized PsbA [@nixonRecentAdvancesUnderstanding2010].
+Generation of Reactive Oxygen Species (ROS) can also cause photoinhibition if the electron flow is slowed downstream of the P680^+^ radical [@aroPhotoinhibitionPhotosystemII1993], producing  singlet oxygen (^1^O~2~).
+
+There are metabolic processes occurring in both the light-dependent and light-independent reactions of photosynthesis that are greatly influenced by the duration of light exposure [@liDiatomGrowthResponses2017]; [@prezelinDielPeriodicityPhytoplankton1992].
+@vaulotGrowthProchlorococcusPhotosynthetic1995 showed that
+*Prochlorococcus* replication of DNA occurs in the afternoon and cell division occurs at night.
+It is often overlooked that the duration of dark exposure is just as important as light exposure for photosynthetic organisms.
+
+Converting the quantity of ambient light levels, PAR, to absorbed PUR, makes it possible to directly compare light levels across different spectral wavebands that are differentially absorbed by the cells.
+This conversion enables us to assess and compare the amount of light that can be effectively utilized for photosynthesis by specific ecotypes in different spectral regimes.
+Furthermore, expressing cumulative diel absorbed PUR can potentially collapse different photoperiods, spectral bands and PAR levels to a common denominator, allowing us to detect whether growth responses are driven simply by cumulative diel absorbed PUR, or whether specific photoperiods, spectral bands or PAR levels have independent effects on growth.
+We can draw meaningful insights by evaluating the growth responses based on cumulative diel absorbed PUR across different oxygen levels that represent distinct ecological niches.
 
@@
 
+```{r AllStrainPurFitsPlots,  fig.cap = AllStrainPurFitsPlots_cap, fig.height = 10, fig.width = 10, echo = FALSE}
+
+AllStrainPurFitsPlots_cap <- glue("** The chlorophyll proxy growth rate (d^-1^) vs. the Photosynthetic Usable Radiation (PUR) (µmol photons m^-2^ d^-1^).**",
+                    "The x-axis is the Photosynthetic Usable Radiation (PUR) (µmol photons m^-2^ s^-1^) .",
+                    "The y-axis is the chlorophyll specific growth rate (d^-1^).",
+                    "**A.** The High Light I (HLI) ecotype MED4.  under 250 µM of O~2~ and red light.",
+                    "**B.** The Low Light II/II (LLII/III) ecotype SS120. under 25 µM of O~2~ and red light.",
+                    "**C.** The Low Light IV (LLIV) ecotype MIT9313. under 2.5 µM of O~2~ and red light.",
+                     "Shapes show the imposed photoperiod (h); hollow inverted triangle for 4 h, solid diamond for 8 h, solid circle for 12 h, solid upright triangle for 16 h.",
+                      "Symbol colours show the spectral waveband for growth; black for white LED light (full spectrum), red for red light (660 nm), and blue for blue light (450 nm).",
+                      "Large shapes show mean or single determinations of growth rate from logistic curve fits; small shapes show values for replicate determinations, if any.",
+                    "The 3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "AllStrainPurFitsPlots.png"))
+
+```
+
 \newpage

### 2024-02-15 Code/Manuscript_O2.Rmd
initial edits to intro and captions

@@
 institute:
-  - alga: 'MAX INSTITUTE'
+  - umwelt: 'Umweltbundesamtm, Dessau-Roßlau, Germany'
   - num: 4
@@
 
-Marine phytoplankton are ubiquitous and serve as an important base of the aquatic food chain.
-They contribute to more than 50% of the net global primary food production [@falkowskiOceanSciencePower2012], while comprising only a small fraction of the global primary producer biomass [@fieldPrimaryProductionBiosphere1998].
 *Prochlorococcus marinus*, a genus of the phylum Cyanobacteria, is the smallest known photosynthetic prokaryote, with cell diameters ranging from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992].
@@
 
-To the best of our knowledge, no other laboratory study has extensively examined the growth response of *Prochlorococcus* under such a diverse set of conditions.
-This study specifically focuses on evaluating how *Prochlorococcus* responds to varying [O~2~], different spectral wavebands, light levels and photoperiods.
-This comprehensive approach distinguishes this study from previous ones conducted on *Prochlorococcus* growth.
+This study focuses on evaluating how growth of *Prochlorococcus* strains from different clades responds to varying [O~2~], spectral wavebands, light levels and photoperiods.
 
@@
                        "Culture growth experimental conditions indicated by horizontal grey lines for depths approximating Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) and vertical grey lines for O~2~ (µM).",
+                       "Point colours identify *Prochlorococcus* clade assignments",
                        "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",
@@
 
-ProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein turnover complexes.**", 
+ProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein metabolism complexes.**", 
                        "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
@@
 
-```{r MED4ProteinAnotated, fig.cap = MED4ProteinAnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+```{r MED4ProteinAnnotated, fig.cap = MED4ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
 
-MED4ProteinAnotated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade).  **",
+MED4ProteinAnnotated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade).  **",
 
@@
 
-knitr::include_graphics(file.path(FiguresIn, "MED4ProteinAnotated.png"))
+knitr::include_graphics(file.path(FiguresIn, "MED4ProteinAnnotated.png"))
 ```
@@
 
-```{r MIT9313ProteinAnotated, fig.cap = MIT9313ProteinAnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+```{r MIT9313ProteinAnmotated, fig.cap = MIT9313ProteinAnmotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
 
-MIT9313ProteinAnotated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade).  **",
+MIT9313ProteinAmnotated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade).  **",
 
@@
 
-knitr::include_graphics(file.path(FiguresIn, "MIT9313ProteinAnotated.png"))
+knitr::include_graphics(file.path(FiguresIn, "MIT9313ProteinAnnotated.png"))
 ```
@@
 # Acknowledgements
-Jonah Sheinin assisted with growth of some cultures for protein analyses.
+Jonah Sheinin assisted with growth of some cultures for protein analyses, while Carlie Barnhill assisted with code for import of multicultivator growth data files.
 

### 2024-02-15 Code/Manuscript_O2.Rmd
working on captions

@@
                       "Real time Optical Density (OD) measurements eliminate intrusive subsampling of sterile cultures.",
-                      "The temperature of culture tubes are controlled via heating or cooling of the aquarium water.",
-                      "Gas with specific oxygen concentrations are bubbled through a humidifier and passed through a 0.2 um filter.",
+                      "The temperature of culture tubes are collectively controlled via heating or cooling of the aquarium water.",
+                      "Gas with specific oxygen concentrations is bubbled through a humidifier and passed through a 0.2 um filter.",
 

### 2024-02-15 Code/Manuscript_O2.Rmd
Mireille, Aurora, introduction merge

@@
 *Prochlorococcus marinus*, a genus of the phylum Cyanobacteria, is the smallest known photosynthetic prokaryote, with cell diameters ranging from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992].
-Despite a small cell size, *P.
+Despite small cell size, *P.
 marinus* contribute 13 to 48% of net primary production in oligotrophic oceans, corresponding to about 30% of  global oxygen production [@partenskyProchlorococcusMarinePhotosynthetic1999].
+*P.
+marinus* growth is currently constrained to between latitudes of 40°N to 40°S in open ocean waters, from surface to 300 m  depth, thus spanning 3 orders of magnitudes of light (Partensky et al., 1999) (Chisholm et al., 1992)  [@partenskyProchlorococcusMarinePhotosynthetic1999].
 
-*Prochlorococcus marinus* comprises many strains, organized into clades,
-which in turn are grouped into ecotypes defined largely as High-Light (HL) or Low-Light (LL) adapted,  and aligned phylogenetically [@moorePhysiologyMolecularPhylogeny1998].
-The biomass distribution of *P.
-marinus* is constrained to between latitudes of 40°N to 40°S in open ocean waters [@partenskyProchlorococcusMarinePhotosynthetic1999] with different ecotypes inhabiting distinct ecological niches.
-High-Light ecotypes are typically observed as the dominant picophytoplankton in near-surface oligotrophic waters that are, characterized by low nutrient concentrations, and high light levels.
-The monophyletic high light ecotype is subdivided into clades based on iron adaptation, whereby HLIII/IV are low iron adapted, whereas HLI is a high iron, low temperature adapted clade and HLII is a high iron, high temperature adapted clade [@kentParallelPhylogeographyProchlorococcus2019; @johnsonNichePartitioningProchlorococcus2006; @zinserInfluenceLightTemperature2007].
-Low-Light ecotypes thrive in deeper ocean waters, extending beyond 200 m in depth [@partenskyProchlorococcusMarinePhotosynthetic1999].
-In these deeper regions, only 1% of the surface irradiance penetrates, primarily in the blue (450 nm) to green (520 nm) spectral waveband ranges, due to light and spectral attenuation [@holtropVibrationalModesWater2021].
-Additionally, some *P.
-marinus* strains in clade LLV and LLVI thrive in  Oxygen Minimum Zones (OMZ) of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021].
-Currently there are at least 12 clades but only 5 have been cultivated; HLI, HLII, LLI, LLII/III and LIV [@billerProchlorococcusStructureFunction2015].
+*Prochlorococcus marinus* is functionally differentiated from other cyanobacteria primarily by the absence of phycobilisomes [@chisholmProchlorococcusMarinusNov1992].
+Instead, *Prochlorococcus*  utilizes intra-membrane Pcb proteins bound to divinylchlorophyll a (Chl a2), and α-carotene, as the major light harvesting complex [@goerickePigmentsProchlorococcusMarinus1992]; [@larocheIndependentEvolutionProchlorophyte1996], with diversity in the number of genes encoding Pcb, expression of Pcb under changing light [@garczarekMultiplicationAntennaGenes2000]  [@rocapGenomeDivergenceTwo2003] [@garczarekMultiplicationAntennaGenes2000], and in thylakoid organization [@partenskyProchlorococcusMarinePhotosynthetic1999].
+the genes encoding most of the rest of the photosynthetic apparatus is highly conserved in *Prochlorococcus* [@kettlerPatternsImplicationsGene2007], though the photosynthetic efficiency may vary among clades [@hessPhotosyntheticApparatusProchlorococcus2001; @moorePhotophysiologyMarineCyanobacterium1999].
+
+*Prochlorococcus marinus* comprises many strains, organized into clades, defined by 16S-23S intergenic transcribed ribosomal sequence signatures (Rocap et al., 2003).
+The various clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined by Low Light or High Light.
+Of at least 12 known *Prochlorococcus* clades only 5 to date have cultured representatives; HLI, HLII, LLI, LLII/III and LIV [@billerProchlorococcusStructureFunction2015].
+
+XXXXMIREILLE Check strain descriptions for accuracyXXXX
+Low-Light clades thrive in deeper ocean waters, extending beyond 200 m in depth [@partenskyProchlorococcusMarinePhotosynthetic1999], where only ~1% of the surface irradiance penetrates, primarily in the blue (450 nm) to green (520 nm) spectral ranges [@holtropVibrationalModesWater2021].
+Clade LLIV, including cultured strain MIT9313, falls near the base of the *Prochlorococcus* radiation, and is characterized by preference for low light, at depths from 120 m and 200 m (Partensky et al., 1999).
+LLIV members are, as yet, the only cultured strains found in Oxygen Minimum Zones (OMZ).
+Some as yet uncultured *P.
+marinus* strains in clades LLV and LLVI thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021] (Lavin et al., 2010) ADDITIONAL REFS XXXX.
+(Johnson et al., 1999).
+@goerickeNovelNicheProchlorococcus2000
+[@garcia-robledoCrypticOxygenCycling2017a]. *P. marinus* LL ecotypes may indeed dominate the phytoplankton wihthin OMZ
+[@lavinNovelLineagesProchlorococcus2010;
+@ulloaCyanobacteriumProchlorococcusHas2021]
+[@partenskyProchlorococcusAdvantagesLimits2010].
+
+Clades LLII and LLIII are often grouped together as the second oldest phylogenetic lineages in the *Prochlorococcus* radiation, and share an affinity for low light; LLIII cultured strain SS120, was isolated from 135 m depth in the Sargasso Sea.
+
+Clade LLI  includes cultured strains NATL1A and NATL2A, which prefer moderate irradiances found between 30 and 100 m depth.
+
+HL clades are the most recently evolved lineages, with reduced genome sizes in comparison to LL ecotypes.
+High-Light clades are  typically dominant picophytoplankton in near-surface, oligotrophic waters, characterized by high light levels.
+Clade HLI, including cultured strain MED4,is adapted to higher iron, and lower temperatures, and originated from the Mediterranean Sea, just 5 m below the surface (Partensky et al., 1999).
+Clade HLII adapted to higher iron, and higher temperatures, is the most abundant group in the North Atlantic and North Pacific Oceans, often constituting over 90% of the total population (Partensky et al., 1999),  and are most numerous around 50 m depth (Partensky et al., 1999).
+Clade HLIII/IV is adapted to lower iron [@kentParallelPhylogeographyProchlorococcus2019; @johnsonNichePartitioningProchlorococcus2006; @zinserInfluenceLightTemperature2007].
+
+*P. marinus* clades are found  in environments beyond their optimal habitats. HL clades inhabit depths overlapping with LL ecotypes
+[@westNichePartitioningProchlorococcusPopulationsStratified1999;
+@zinserInfluenceLightTemperature2007;
+@delmontLinkingPangenomesMetagenomes2018] 
+[@moorePhotophysiologyMarineCyanobacterium1999]. 
+@lavinNovelLineagesProchlorococcus2010 and
+@mattisonPhotosyntheticStrategiesWild2020 show that LL ecotypes
+can occupy regions in the OMZ at depths above 40 m, reaching ambient light levels above what LL clades were thought to tolerate.
+
+*Prochlorococcus* remain challenging to culture, as their reduced genomes – the smallest of any known oxyphototroph – render them partially dependent upon mutualistic heterotrophic bacteria to  detoxify reactive oxygen species (Moore et al., 2007; Morris et al., 2008).
+MED4, SS120 and MIT9313 have been successfully cultured in laboratories, and used to show that ecotypic classifications correspond to biochemical differences among strains.
+CITATONS OUR LAB and OTHERS.
 
@@
 Predictions indicate a net global increase of *P.
-marinus* cell abundances of 29% and poleward latitudinal shifts of at least 10° in marine phytoplankton niches by the end of this century [@flombaumPresentFutureGlobal2013] in response to warming waters, with cell abundance increases of approximately 50% in the more poleward regions.
+marinus* cell abundances of 29%, along with  poleward latitudinal shifts of at least 10° in marine phytoplankton niches by the end of this century [@flombaumPresentFutureGlobal2013] in response to warming waters, with increases in *Prochlorococcus* of approximately 50% in the more poleward regions.
 As the solar incidence angles are lower and photoperiod seasonality is more pronounced at higher latitudes, this shift will carry these phytoplankters into new combinations of photoperiod, seasonal regimes and changing spectral regimes [@bartonAnthropogenicClimateChange2016].
@@
 Moreover, substantial changes in the global water cycle, leading to extensive changes in worldwide precipitation patterns, are affecting ocean salinity levels on a global scale, and  ice melts due to rising temperatures are impacting salinity levels in the Arctic and Northwest Atlantic oceans [@leeRecognizingSalinityThreats2022].
-There is evidence that increasing sea temperatures are also causing a decrease in [O~2~] across our global oceans [@matearLongtermChangesDissolved2003], with significant declines observed toward the poles in both hemispheres [@helmObservedDecreasesOxygen2011].
-Warmer ocean waters decrease oxygen solubility at the surface which in turn reduces the amount of oxygen that can be mixed downwards by ocean currents [@garcia-sotoOverviewOceanClimate2021].
-Furthermore, models predict that the OMZ in the Pacific and Indian Oceans are expanding [@garcia-sotoOverviewOceanClimate2021; @buseckeDivergingFatesPacific2022].
-In light of these expanding OMZ, a recent study by @buseckeDivergingFatesPacific2022 highlights an intriguing finding; the core of the OMZ, where the oxygen levels are lowest, is projected to contract.
-Given the predicted decrease in overall oceanic [O~2~],   projected expansion of OMZs, and possibly decline in the OMZ core volumes, we set forth to examine the influence of [O~2~] on *P.
-marinus* growth as this area of research has been relatively understudied.
+Increasing sea temperatures are also causing a decrease in [O~2~] across our global oceans [@matearLongtermChangesDissolved2003], with significant declines in [O~2~] observed toward the poles in both hemispheres [@helmObservedDecreasesOxygen2011].
+Warmer ocean waters increase stratification, and decrease oxygen solubility at the surface, which in turn decreases oxygen mixing downwards by ocean currents [@garcia-sotoOverviewOceanClimate2021].
+Models predict that the OMZ in the Pacific and Indian Oceans are expanding [@garcia-sotoOverviewOceanClimate2021; @buseckeDivergingFatesPacific2022].
+In light of these expanding OMZ, a recent study by @buseckeDivergingFatesPacific2022 highlights an intriguing finding; the cores of the OMZ, where the oxygen levels are lowest, is projected to contract.
+Given the predicted decrease in overall oceanic [O~2~],projected expansion of OMZs, and possible decline in the OMZ core volumes, we set forth to examine the influence of [O~2~] on *P.
+marinus* growth, as this area of research has been relatively understudied.
 
-To determine the viability of *P.
-marinus* strains in changing ecosystems, we analyzed the growth and physiological responses of representative strains from three clades to varying [O~2~], light levels, spectral waveband ranges, and photoperiods,  to simulate a matrix of eco-physiological conditions representative of current and hypothetical future ocean zones.
-The following *P.
-marinus* clades were examined: *P.
-marinus* MED4, classified as a clade HLI (Figure \@ref(fig:PhylogenyTreeYan2018edit)), was isolated near the ocean surface (5m depth) of the Mediterranean Sea where [O~2~] are near saturation, light levels are high and spectral bias from full solar irradiance is minimal.
+Near the equator, photoperiod remains relatively constant at the ocean surface, approximately 12 hours (h) of daylight and 12 h of darkness throughout the entire year.
+The effective length of the photoperiod does, however attentuate with depth as dawn and dusk light drops below the level needed for biological processes.
+As *P.
+marinus* potentially expands its temperature-permissive niches poleward into temperate regions
+[@flombaumPresentFutureGlobal2013; @bartonAnthropogenicClimateChange2016], it will encounter more
+pronounced seasonal variations in photoperiod regimes at surface and at depth.
+With the influence of light attenuation with depth, temperate regions exhibit more combinations of photoperiod, compared to equatorial regions, with potentially complex effects upon viable growth niches @liDiatomGrowthResponses2017 @prezelinDielPeriodicityPhytoplankton1992.
+@vaulotGrowthProchlorococcusPhotosynthetic1995 showed that *Prochlorococcus* replication of DNA occurs in the afternoon, while cell division occurs at night.
+
+We therefore analyzed the growth and physiological responses of representative strains from three clades under a matrix of [O~2~], light levels, spectral waveband ranges, and photoperiods,  to approximate eco-physiological conditions representative of current and hypothetical future ocean zones.
+*P.
+marinus* MED4, a clade HLI strain (Figure \@ref(fig:PhylogenyTreeYan2018edit)), was isolated near the ocean surface (5m depth) of the Mediterranean Sea where [O~2~] is near saturation, light levels are high and spectral bias from full solar irradiance is minimal.
 *P.
@@
 marinus* MIT9313, a clade LLIV (Figure \@ref(fig:PhylogenyTreeYan2018edit)), was isolated from the North Atlantic Gulf Stream at a depth of 135 m.
-At these depths, light attenuation and spectral shifts occur, resulting in low blue and green light levels, while [O~2~] varies from near-surface saturation levels to decreased concentrations, but it does not necessarily decrease with depth [@billheimerOxygenSeasonalityUtilization2021].
-In chapter 2, we define the interactions between oxygen, light level, light colour and photoperiod that help define their complex niches.
+At these depths, light attenuation and spectral shifts occur, resulting in low blue and green light levels, while [O~2~] varies from near-surface saturation levels to decreased concentrations, but does not necessarily decrease systematically with depth [@billheimerOxygenSeasonalityUtilization2021].
 
-In chapter 3, to better decipher the physiological processes driving the observed growth responses to a complex matrix of spectral light regimes and [O~2~], we express growth rates in terms of cumulative diel Photosynthetically Usable Radiation (PUR).
-Photosynthetic organisms rely on absorbing light energy within the visible spectrum, 350 to 700 nm, for photosynthesis.
-This range of light, known as Photosynthetic Active Radiation (PAR) [@morelAvailableUsableStored1978], is essential for the photosynthetic process.
-PUR represents the fraction of PAR that is absorbed by the pigments of photosynthetic organisms [@morelAvailableUsableStored1978], thus we can compare light levels across different spectral wavebands that are absorbed differently by cells.
-Moreover, expressing growth rates in terms of cumulative diel absorbed PUR has the potential to simplify different photoperiods, spectral bands, and PAR levels into a common parameter, making growth response comparisons across different oxygen levels more attainable and may allow us to determine whether growth responses are primarily influenced by cumulative diel absorbed PUR, specific photoperiods or spectral bands.
-
-This study focuses on evaluating how growth of *Prochlorococcus* strains from different clades responds to varying [O~2~], spectral wavebands, light levels and photoperiods.
-
-### Chapter 2 PAR Intro
-*Prochlorococcus marinus* ecotypes are characterized by their distinct
-tolerance for High-Light (HL) or Low-Light (LL) levels
-[@moorePhysiologyMolecularPhylogeny1998]. *Prochlorococcus marinus* is
-classified into at least 12 major clades
-[@billerProchlorococcusStructureFunction2015], that respectively inhabit
-a range of ecological niches across vertical ocean water columns
-[@chisholmNovelFreelivingProchlorophyte1988;
-@veldhuisVerticalDistributionPigment1990;
-@partenskyProchlorococcusMarinePhotosynthetic1999].
-
-Previous studies have observed that the diversification of *P. marinus*
-niches extends into regions considered unfavorable for photosynthesis to
-occur. @goerickeNovelNicheProchlorococcus2000 first reported the
-existence of *P. marinus* below the oxyclines of the Oxygen Minimum
-Zones (OMZ) of the Arabian Sea and the Eastern Tropical North Pacific.
-In an OMZ, oxygen concentrations [O~2~] can be less than 20 µM, and in
-some regions [O~2~] is undetectable
-[@garcia-robledoCrypticOxygenCycling2017a]. Subsequent research has
-revealed that *P. marinus* LL ecotypes dominate the OMZ
-[@lavinNovelLineagesProchlorococcus2010;
-@ulloaCyanobacteriumProchlorococcusHas2021] and are believed to
-contribute to approximately 90% of the *P. marinus* diversity in the
-eastern tropical Pacific Ocean OMZ
-[@partenskyProchlorococcusAdvantagesLimits2010].
-
-Although *P. marinus* ecotypes are defined by their ecological niches,
-there is evidence to suggest that ecotypes can exist in environments
-beyond their optimal habitats. HL ecotypes are known to
-inhabit depths where LL ecotypes also inhabit
-[@westNichePartitioningProchlorococcusPopulationsStratified1999;
-@zinserInfluenceLightTemperature2007;
-@delmontLinkingPangenomesMetagenomes2018] but at light levels still
-within the range of confirmed growth irradiance limits
-[@moorePhotophysiologyMarineCyanobacterium1999]. Studies by
-@lavinNovelLineagesProchlorococcus2010 and
-@mattisonPhotosyntheticStrategiesWild2020 show evidence that LL ecotypes
-can occupy regions in the OMZ at depths above 40 m. Since light levels
-were not reported at every depth of these studies, it is presumed that
-at a depth of 40 m, closer to the surface, light levels are higher than
-what LL ecotypes can tolerate. Furthermore,
-@mattisonPhotosyntheticStrategiesWild2020 presented evidence of proteins
-derived from HL ecotypes of *P. marinus* in the OMZ at depths up to 200
-meters with O~2~ of 15 µM. However, the extent to which [O~2~] defines
-the niches occupied by different *P. marinus* ecotypes, as compared to
-potentially covarying environmental variables like photoperiod, light
-spectrum, and light level, is poorly described.
-
-Photosynthetic organisms rely on the absorption of light energy within
-the visible spectral range of 350 to 700 nm to drive the photosynthetic
-process. This spectral range of light, known as Photosynthetic Active
-Radiation (PAR) [@morelAvailableUsableStored1978], is essential for
-photosynthesis. However, as sunlight enters the marine environment, it
-undergoes attenuation, resulting in a decline of specific wavebands of
-light through the water column from the surface. This attenuation
-primarily affects the longer wavelengths in the red region of the
-spectrum (600 to 700 nm), followed by wavelengths in the green region
-(500 to 600 nm) and, finally, wavelengths in the blue region (400 to 500
-nm) [@holtropVibrationalModesWater2021]. Thus, as sunlight penetrates the
-marine environment, the light level diminishes and the residual spectral
-wavebands shift with depth, where only blue spectral wavelengths
-dominate. The region of the water column with enough light to support
-photosynthesis is known as the photic zone, defined as the depth where
-light levels remain above 20 µmol photons m^-2^ s^-1^, 1% of the surface
-solar incident radiation, of 2000 µmol photons m^-2^ s^-1^.
-
-In growth studies of *P. marinus*, it is common to use a broad spectrum
-light source to approximate the solar spectral wavelengths found in the
-uppermost layers of the ocean. The actinic photon flux is adjusted to
-simulate the specific light levels appropriate for the ecotype of
-interest. However, this approach falls short when attempting to
-accurately reproduce the ambient spectral light quality of deep ocean
-habitats, where only blue spectral wavelengths prevail
-[@holtropVibrationalModesWater2021]. *Prochlorococcus marinus* contain a
-unique light-harvesting complex composed primarily of divinyl
-chlorophyll a and b [@chisholmProchlorococcusMarinusNov1992;
-@goerickePigmentsProchlorococcusMarinus1992], the only photosynthetic
-organism to possess these chlorophyll derivatives. The absorption maxima
+We then analyzed growth rates in terms of cumulative diel Photosynthetically Usable Radiation (PUR).
+Photosynthetic organisms rely on absorbing light energy within the PAR range, 350 to 700 nm, for photosynthesis [@morelAvailableUsableStored1978].
+PUR represents the fraction of PAR that is absorbed by the pigments of photosynthetic organisms [@morelAvailableUsableStored1978].
+PUR, therefore, takes into account the pigment composition of photosynthetic organisms and the specific spectral wavebands these pigments absorb.
+*Prochlorococcus marinus* light-harvesting complexes, [@chisholmProchlorococcusMarinusNov1992;
+@goerickePigmentsProchlorococcusMarinus1992], show an absorption maxima
 of 442 nm for divinyl chlorophyll a and 478 nm for divinyl chlorophyll b
-[@goerickePigmentsProchlorococcusMarinus1992] allow *P. marinus* to
-efficiently harvest the light energy emitted by blue light in the 400 nm
-to 500 nm range [@morelAvailableUsableStored1978].
-
-At most latitudes, the duration of the photoperiod (day length)
-undergoes seasonal variations. However, at the equator, the photoperiod
-remains relatively constant at the ocean surface, approximately 12 hours
-(h) of daylight and 12 h of darkness throughout the entire year. As *P.
-marinus* potentially expands its temperature-permissive niches poleward
-into temperate regions due to climate change
-[@flombaumPresentFutureGlobal2013;
-@bartonAnthropogenicClimateChange2016], it will encounter more
-pronounced seasonal variations in photoperiod regimes. Photoperiods are
-longer at temperate regions during the summer, while in spring, fall and
-winter, photoperiods are shorter. Additionally, when considering the
-influence of light attenuation with depth, temperate regions exhibit
-more combinations of photoperiod compared to equatorial regions. The
-effects of photoperiod on the ecophysiology of phytoplankton is
-underscored by several studies. @liDiatomGrowthResponses2017
-demonstrated complex interactions of photoperiod and growth rate of
-diatoms. Similarly, @prezelinDielPeriodicityPhytoplankton1992 expressed
-the importance of considering photoperiod on *in situ* rates of primary
-production, as the diel light to dark ratio regulates metabolic
-processes throughout the day. Furthermore,
-@vaulotGrowthProchlorococcusPhotosynthetic1995 showed that
-*Prochlorococcus* undergoes DNA replication in the afternoon, while cell
-division occurs at night. Further research is needed to investigate the
-impact of different photoperiods on the growth of *Prochlorococcus*, as
-this aspect remains inadequately studied.
+[@goerickePigmentsProchlorococcusMarinus1992] allowing *P. marinus* to
+efficiently harvestblue light in the 400 nm
+to 500 nm range [@morelAvailableUsableStored1978] prevailing in deep ocean
+habitats, where only blue spectral wavelengths prevail [@holtropVibrationalModesWater2021].
+In *Prochlorococcus* small cell diameters, from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992], and simple cell structures, minimize the complication of pigment package effect or intracellular self-shading [@morelProchlorococcusSynechococcusComparative1993].
+Given the different spectral light regimes typical of the niches of different ecotypes,  expressing growth rates in terms of cumulative diel absorbed PUR might simplify different photoperiods, spectral bands, and PAR levels into a common parameter, making growth response comparisons across strains and different oxygen levels more accessible.
+We also aimed to detect whether growth responses are driven simply by cumulative diel absorbed PUR, or whether specific photoperiods, spectral bands or PAR levels have independent, albeit interacting, effects on growth.
 
@@
 
-(fig:SunDepth) shows light levels and spectral waveband
-attenuation at ocean surface to ocean depths of 1000 m, as well as the
-hours of light above the minimum photic zone of 20 µmol photons m^-2^
-s^-1^, representing the photoperiod. This figure is modeled using the
-solar incident angle at 45°N, a hypothetical future niche, at summer
-solstice and illustrates the light parameters that define the
-photoregimes of the niches of *P. marinus* that we studied. Figure (fig:CardinalSeasons) illustrates light attenuation through ocean waters at 45°N at winter solstice, equinox and summer solstice.
+Under full atmospheric [O~2~], LL clades of *Prochlorococcus* are restricted to growth under low light, in part because they suffer photoinhibition of Photosystem II (PSII) through several paths, including direct absorbance of UV or blue light, in parallel with generation of Reactive Oxygen Species (ROS) if the electron flow is slowed, [@aroPhotoinhibitionPhotosystemII1993], producing  damaging singlet oxygen (^1^O~2~).
+[@aroPhotoinhibitionPhotosystemII1993; @soitamoPhotoinhibitionMarinePicocyanobacteria2017] [@murphyPhotoinactivationPhotosystemII2017][@hakalaEvidenceRoleOxygenevolving2005].
+Repair of inhibited PSII process relies on the removal of damaged PsbA (Mann et al., 2000; Adam et al., 2005), followed by reassembly with newly synthesized PsbA [@nixonRecentAdvancesUnderstanding2010].
+Thus, degradation of PsbA is a rate-limiting step in recovery from photoinhibition (Kanervo et al., 1993), mediated largely by a heterohexamer of (FtsH12)3, a membrane-bound (Sacharz et al., 2015)(Zak et al., 2001) metalloprotease  (Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
+(Adam et al., 2005; Boehm et al., 2012) (Nixon et al.
+(2010)) (Komenda et al., 2007).
+(Pisareva et al., 2007; Sacharz et al., 2015),  (Mann et al., 2000), (AMANDA REF from ALGATECH).
 
-### Chapter 3 Intro (PUR)
+*Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4, homologous to the characterized FtsH isoforms of the model cyanobacterium *Synechocystis* FtsH, with presumably parallel functions (Table 1).
+Upon a shift to higher light HLIII MED4 upregulated expression of FtsH1 and FtsH2 (Bonisteel et al.
+(2018)), homologs to the *Synechocystis* slr0228 and slr1604, implicated in PSII repair.
+In contrast representative LLIII strain MIT9313 showed less overall expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem.
+Furthermore MIT9313 expressed primarily FtsH3, homologous to Sll1463 involved in PSI biogenesis, and FtsH expression did not increase in response to light stress.
+Through adaptation to steady low light, LLIII **Prochlorococcus* instead allocates resources processes other than dynamic regulation of PSII repair.
 
-*Prochlorococcus marinus* ecotypes are characterized by their distinct
-tolerance for High-Light (HL) or Low-Light (LL) levels.
-The photosynthetic strategies between *Prochlorococcus marinus* ecotypes must differ in order to exploit the very diverse photo regimes in their respective niches and may be explained by their unique cellular compositions.
-*Prochlorococcus marinus* MED4 has the smallest genome size of the 3 ecotypes we studied, only 1.66 Mbp, while *P.
-marinus* MIT9313 has the largest genome size of 2.41 Mbp [@rocapGenomeDivergenceTwo2003].
-*Prochlorococcus marinus* SS120 genome size is 1.75 Mbp [@dufresneGenomeSequenceCyanobacterium2003].
-Due to the small genome size and small cell diameters, ranging from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992], *Prochlorococcus* are the smallest known photosynthetic prokaryote.
-The simplistic cellular structure and small size of *P.
-marinus* minimizes the pigment package effect or intracellular self-shading, due to the high surface area to volume ratio, contributing to very efficient optical absorption capabilities [@morelProchlorococcusSynechococcusComparative1993].
+```{r FtsHtable, table.cap = FtsHtable_cap, echo = FALSE}
 
-Photosynthetic organisms depend on the absorption of light energy in the visible spectrum, 350 to 700 nm, to carry out photosynthesis.
-This range of light, referred to as Photosynthetic Active Radiation (PAR) [@morelAvailableUsableStored1978], is crucial for the photosynthetic process.
-The Photosynthetic Usable Radiation (PUR) is defined as the fraction of PAR absorbed by the pigments of a given photosynthetic taxon [@morelAvailableUsableStored1978].
-PUR, therefore, takes into account the pigment composition of photosynthetic organisms and the specific spectral wavebands that these pigments absorb.
-*Prochlorococcus marinus* MED4, a clade HLI ecotype, dominate the near ocean surface where spectral attenuation from full solar irradiance is minimal and light levels are high [@partenskyProchlorococcusMarinePhotosynthetic1999].
-*Prochlorococcus marinus* SS120, a clade LLIII ecotype, and *P.
-marinus* MIT9313, a clade LLIV ecotype, dominate the deep ocean [@partenskyProchlorococcusMarinePhotosynthetic1999] where extreme light attenuation and spectral shifts occur, resulting in the availability of very low light levels in the blue (450 nm) to green (520 nm) spectral range [@holtropVibrationalModesWater2021].
-Given the different spectral light regimes of the different ecotype niches, understanding how the quantity of available light levels, PAR, converts to what these ecotypes can use, PUR, can give some insight into how they are able to exploit light energy.
+FtsHtable_cap <- glue("FtsH protease homologs in *Prochlorococcus marinus* and the model cyanobacterium *Synechocystis* sp.
+PCC6803.
+Protein homology determined by multiple sequence alignment with MUSCLE followed by construction of maximum likelihood phylogenetic tree using 1000 bootstrap replicates in MEGAX.",
 
-The photosynthesis process can be divided into two distinct reactions: the
-light-dependent and the light-independent reactions. *Prochlorococcus marinus* does not contain
-chloroplasts [@chisholmNovelFreelivingProchlorophyte1988], and the
-light-dependent reactions occur in thylakoid membranes arranged concentrically around the periphery of the cell. Light harvesting complexes spanning a thylakoid membrane capture or 'harvest' light
-energy. The light harvesting complexes in *P. marinus* consist of Prochlorophyte Chlorophyll Binding
-proteins (Pcb) [@larocheIndependentEvolutionProchlorophyte1996]. Once photons are absorbed by light harvesting pigments, the energy is transferred to the reaction center of Photosystem II
-(PSII) where water is split, catalyzed by the manganese cluster of the
-oxygen evolving complex. Here, 2 water molecules are oxidized to produce 1 oxygen
-(O~2~) molecule, releasing 4 protons into the thylakoid lumen, which contribute to the transmembrane proton
-potential,  and 4 electrons. These electrons are passed to Photosystem I
-(PSI) through a series of reduction and oxidation reactions in the
-electron transport chain in the thylakoid membrane, and in the process, deliver more protons to the
-proton pool within the lumen side of the thylakoid membrane. Photosystem I
-(PSI) also harvest light energy but does not split water, rather the
-reaction center uses excitation energy to excite electrons received from PSII
-and transfer them by the reduction and oxidation of iron-sulphur
-clusters to reduce NADP^+^ to NADPH. The Adenosine Triphosphate (ATP) synthase complex produces ATP in the stroma, driven by protons passing from the lumen out to the stroma side of the thylakoid
-membrane. The light-independent reaction involves the RuBisCO enzyme
-which uses the NADPH and ATP generated in the light-dependent reaction
-to convert dissolved carbon dioxide (CO~2~) gas into carbohydrates.
+                       .sep = " ")
+FtsHTable <- tibble(Organism = c("Prochlorococcus marinus", "Synechocystis sp. PCC6803", "Function"),
+                    FtsH1 = c("FtsH1", "SlrO22", "PSII Repair"),
+                    FtsH2 = c("FtsH2", "Slr1604", "PSII Repair"),
+                    FtsH3 = c("FtsH3", "Slr1463", "PSI biogenesis"),
+                    FtsH4 = c("FtsH4", "Slr1390", "Cell viability")
+                    )
 
-*Prochlorococcus marinus* is differentiated from other cyanobacteria as a distinct lineage, primarily due to the absence of phycobilisomes [@chisholmProchlorococcusMarinusNov1992].
-Instead, *Prochlorococcus*  utilizes intra-membrane Pcb proteins bound to divinylchlorophyll a (Chl a2), and α-carotene, as the major light harvesting complex [@goerickePigmentsProchlorococcusMarinus1992]; [@larocheIndependentEvolutionProchlorophyte1996].
-Not all *Prochlorococcus* encode the same number of Pcb proteins.
-The representative of HLI clade, *P.
-marinus* MED4 has 1 gene encoding pcbA protein [@garczarekMultiplicationAntennaGenes2000] and the LLIV clade, *P.
-marinus* MIT9313, has 2 genes encoding pcbB and pcbG proteins [@rocapGenomeDivergenceTwo2003].
-The LLIII clade, *P.
-marinus* SS120, however, has 7 genes encoding pcbA, pcbB, pcbC, pcbE, pcbF, pcbG and pcbH [@garczarekMultiplicationAntennaGenes2000].
-According to @garczarekMultiplicationAntennaGenes2000, the expression of some of the pcb genes might be specifically induced under low light conditions, after noting the thickening of the antenna band of the thylakoid membrane when SS120 was switched to low light after high light exposure.
-Another difference within the cell structure among *P.
-marinus* ecotypes is the 2 to 4 thylakoids that run parallel to the cell membrane.
-For SS120, the thylakoids are closed around the periphery of the cell; however, in MED4 and MIT9313, there is a gap resulting in a horseshoe shape for the thylakoids [@partenskyProchlorococcusMarinePhotosynthetic1999].
-Despite the deviation in the light harvesting complex from cyanobacteria, the genes encoding the rest of photosynthetic apparatus is highly conserved in *Prochlorococcus* [@kettlerPatternsImplicationsGene2007], though the photosynthetic efficiency may vary between ecotypes [@hessPhotosyntheticApparatusProchlorococcus2001; @moorePhotophysiologyMarineCyanobacterium1999].
-
-The efficient ability of *P.
-marinus* to harvest light energy allows LL ecotypes to thrive and exploit the low, attenuated light levels present in deep ocean waters.
-However, this efficiency also makes them vulnerable to photo damage under high light levels [@aroPhotoinhibitionPhotosystemII1993; @soitamoPhotoinhibitionMarinePicocyanobacteria2017].
-The proteins in the reaction centers of PSII are vulnerable to photo damage, which can result in the disruption of electron transport and irreversible damage to the reaction center subunit D1 protein [@murphyPhotoinactivationPhotosystemII2017].
-Additionally, direct absorption of a photon in the UV or blue range by the Mn~4~Ca cluster within the oxygen-evolving complex of PSII can lead to its inactivation [@hakalaEvidenceRoleOxygenevolving2005].
-Without the proper functioning of the oxygen-evolving complex, the P680^+^ radical, which is formed during the light absorption process, cannot be efficiently reduced.
-This can result in the accumulation of P680^+^ radicals and lead to irreversible oxidative damage to the PsbA protein, within PSII.
-The damaged PsbA protein must then be removed to reactivate the PSII center.
-This process relies on the degradation and removal of damaged PsbA by protease isoforms FtsH 2 and 3 and the production of newly synthesized PsbA [@nixonRecentAdvancesUnderstanding2010].
-Generation of Reactive Oxygen Species (ROS) can also cause photoinhibition if the electron flow is slowed downstream of the P680^+^ radical [@aroPhotoinhibitionPhotosystemII1993], producing  singlet oxygen (^1^O~2~).
-
-There are metabolic processes occurring in both the light-dependent and light-independent reactions of photosynthesis that are greatly influenced by the duration of light exposure [@liDiatomGrowthResponses2017]; [@prezelinDielPeriodicityPhytoplankton1992].
-@vaulotGrowthProchlorococcusPhotosynthetic1995 showed that
-*Prochlorococcus* replication of DNA occurs in the afternoon and cell division occurs at night.
-It is often overlooked that the duration of dark exposure is just as important as light exposure for photosynthetic organisms.
-
-Converting the quantity of ambient light levels, PAR, to absorbed PUR, makes it possible to directly compare light levels across different spectral wavebands that are differentially absorbed by the cells.
-This conversion enables us to assess and compare the amount of light that can be effectively utilized for photosynthesis by specific ecotypes in different spectral regimes.
-Furthermore, expressing cumulative diel absorbed PUR can potentially collapse different photoperiods, spectral bands and PAR levels to a common denominator, allowing us to detect whether growth responses are driven simply by cumulative diel absorbed PUR, or whether specific photoperiods, spectral bands or PAR levels have independent effects on growth.
-We can draw meaningful insights by evaluating the growth responses based on cumulative diel absorbed PUR across different oxygen levels that represent distinct ecological niches.
-
-## Aurora
-*Prochlorococcus marinus*, a species of picocyanobacteria, are tiny, photosynthetic, marine prokaryotes.
-At nder 1 µm in diameter, they are the smallest photosynthetic organisms on the planet, but at 10^4^-10^5^ cells per millilitre of seawater  (ampbell and Vaulot, 1993), they heavily influence global biogeochemical cycles (Partensky et al., 1999) (Flombaum et al., 2013).
-*Prochlorococcus* are currently restricted to between 40°N and 40°S, from surface to 300 m  depth, spanning 3 orders of magnitudes of light (Partensky et al., 1999) (Chisholm et al., 1992).
-Some *Prochlorococcus* extend into Oxygen Minimum Zones (OMZ), at less than  20 µM O2 (Johnson et al., 1999).
-*Prochlorococcus* is divided into numerous strains, categorized into high-light clades HLI, HLII, HLIII or low-light clades LLI, LLII, LLIII, LLIV, LLV & LLVI, based on their 16S-23S intergenic transcribed ribosomal sequence signatures (Rocap et al., 2003).
-The LLIV clade, including strain MIT9313, falls near the base of the *Prochlorococcus* radiation.
-First isolated in 1993 from 135 m into the north Atlantic, Clade LLIV are characterized by preference for low light,  and are most populous between 120 m and 200 m depths (Partensky et al., 1999).
-LLIV members are also the only strains found in OMZ that have been, to date, cultured, although two as yet uncultured clades, LLV and LLVI, have been detected in the OMZ of the eastern Tropical Pacific Ocean (Lavin et al., 2010) ADDITIONAL REFS XXXX.
-LLII and LLIII clades are often grouped together as the second oldest phylogenetic clades and share an affinity for low light conditions; LLIII strain SS120, the first *Prochlorococcus* strain to be characterized in 1988, was isolated 135 m into the Sargasso Sea.
-The LLI clade includes NATL1A and NATL2A, which prefer moderate irradiances found between 30 and 100 m.
-HL clades are the most recently evolved and despite reduced genome size in comparison to LL ecotypes, have adapted to life at higher irradiances.
-HLII is the most abundant group in the North Atlantic and North Pacific Oceans, often constituting over 90% of the total population (Partensky et al., 1999),  and are most numerous around 50 m depth (Partensky et al., 1999).
-The HLI clade, including MED4, was found at the very surface of the Mediterranean Sea, just 5 m below the surface (Partensky et al., 1999).
-
-*Prochlorococcus* are difficult to culture, as their reduced genomes – the smallest of any known oxyphototroph – render them partially dependent upon mutualistic heterotrophic bacteria to  detoxify reactive oxygen species (Moore et al., 2007; Morris et al., 2008).
-MED4, SS120 and MIT9313 have been successfully cultured in laboratories, and used to show that ecotypic classifications correspond to biochemical differences among strains.
-CITATONS OUR LAB and OTHERS.
-
-Under full atmospheric [O~2~], LL clades of *Prochlorococcus* are restricted to growth under low light, in part because they suffer photoinhibition of Photosystem II (PSII) at irradiances preferred by their HL relatives.
-The main target of photoinhibition is the PsbA protein, which along with its homolog PsbD forms a heterodimer binding all redox active components of the PSII reaction center core (Barber, 2012).
-Under light-induced damage, new PsbA cannot be incorporated until the damaged PsbA is removed.
-Thus, degradation of PsbA, mediated largely by FtsH proteases (Mann et al., 2000; Adam et al., 2005), is a rate-limiting step in recovery from photoinhibition (Kanervo et al., 1993).
-FtsH is a membrane-bound (Sacharz et al., 2015)(Zak et al., 2001), ATP, zinc metalloprotease that extracts and degrades membrane-bound proteins for degradation (Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
-In the model cyanobacterium *Synechocystis* sp.
-PCC 6803 4 isoforms of FtsH proteins are encoded by the slr1390, slr0228, slr1604 and sll1463 genes.
-In *Synechocystis*, Slr0228 and slr1604 form a hetero-hexameric ring in the thylakoid membrane with a central pore through which proteins are translocated as they are digested, a process key for PSII repair (Adam et al., 2005; Boehm et al., 2012) (Nixon et al.
-(2010)) (Komenda et al., 2007), when photoinactivation exposes an N-terminal “docking site” for FtsH to initiate degradation.
-In contrast, slr1390 and slr1604 are found in both plasma and thylakoid membranes (Pisareva et al., 2007; Sacharz et al., 2015), are essential for cell viability (Mann et al., 2000), and implicated in PSI biogenesis (AMANDA REF from ALGATECH).
-
-*Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4, homologous to the *Synechocystis* FtsH isofoms, and with presumably parallel functions (Table 1).
-Upon a shift to higher light HLIII MED4 upregulated expression of FtsH1 and FtsH2 (Bonisteel et al.
-(2018)), homologs to *Synechocystis* slr0228 and slr1604, implicated in PSII repair.
-In contrast representative LLIII strain MIT9313 shows less overall expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem.
-Furthermore MIT9313 expressed primarily FtsH3 and expression did not increase in response to light stress.
-Through adaptation to steady low light, LLIII **Prochlorococcus* allocate resources to other processes.
-
-Table 1.
-FtsH protease homologs amongst the model cyanobacterium Synechocystis sp.
-PCC6803 and Prochlorococcus marinus.
-Protein homology determined by multiple sequence alignment with MUSCLE followed by construction of maximum likelihood phylogenetic tree using 1000 bootstrap replicates in MEGAX
-
-Organism	Protein Homolog			
-Prochlorococcus marinus	FtsH1	FtsH2	FtsH3	FtsH4
-Synechocystis sp. PCC6803	Slr0228	Slr1604	Sll1463	Slr1390
-k
-Function
+FtsHTable
+```
 
@@
 
+Furthermore,
+Evidence of proteins
+derived from HL ecotypes of *P. marinus* inOMZ at depths up to 200
+meters,  with O~2~ of 15 µM. The extent to which [O~2~] defines
+the niches occupied by different *P. marinus* ecotypes, as compared to
+potentially covarying environmental variables like photoperiod, light
+spectrum, and light level, is poorly described.
+
 ```{r ProchloroPhotosynthDepthO2, fig.cap = ProchloroPhotosynthDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
@@
 
-knitr::include_graphics(file.path(FiguresInOceanPro, "ProchloroMetabDepthO2.png"))
+knitr::include_graphics(file.path(FiguresInOceanPro, "ProchloroProteinMetabDepthO2.png"))
 ```

### 2024-02-15 Code/Manuscript_O2.Rmd
intro subheadings

@@
 
-## Mireille
-### Chapter 1 General Intro
+## *Prochlorococcus* evolutionary and functional diversity
 
@@
 *Prochlorococcus marinus* comprises many strains, organized into clades, defined by 16S-23S intergenic transcribed ribosomal sequence signatures (Rocap et al., 2003).
-The various clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined by Low Light or High Light.
+The clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined by Low Light or High Light.
 Of at least 12 known *Prochlorococcus* clades only 5 to date have cultured representatives; HLI, HLII, LLI, LLII/III and LIV [@billerProchlorococcusStructureFunction2015].
@@
 
-*Prochlorococcus* remain challenging to culture, as their reduced genomes – the smallest of any known oxyphototroph – render them partially dependent upon mutualistic heterotrophic bacteria to  detoxify reactive oxygen species (Moore et al., 2007; Morris et al., 2008).
-MED4, SS120 and MIT9313 have been successfully cultured in laboratories, and used to show that ecotypic classifications correspond to biochemical differences among strains.
-CITATONS OUR LAB and OTHERS.
+## *Prochlorococcus* responses to changing niches
 
@@
 \newpage
+
+## Photosystem II maintenance as a limitation on *Prochlorococcus* growth
+
+*Prochlorococcus* remain challenging to culture, as their reduced genomes – the smallest of any known oxyphototroph – render them partially dependent upon mutualistic heterotrophic bacteria to  detoxify reactive oxygen species (Moore et al., 2007; Morris et al., 2008).
+MED4, SS120 and MIT9313 have been successfully cultured in laboratories, and used to show that ecotypic classifications correspond to biochemical differences among strains.
+CITATONS OUR LAB and OTHERS.
 

### 2024-02-15 Code/ManuscriptTargetProtein.Rmd
fix target protein file names

@@
 TargetProtein <- TargetProtein %>%
-  rename(SampleID = "ï..Sample")
+  rename(SampleID = "Sample")
 
@@
 
-MIT9313ProteinAnotated <- TargetProtein %>%
+MIT9313ProteinAnnotated <- TargetProtein %>%
   filter( Strain == "MIT9313") %>% 
@@
 
-MIT9313ProteinAnotated
+MIT9313ProteinAnnotated
 
-MED4ProteinAnotated <- TargetProtein %>%
+MED4ProteinAnnotated <- TargetProtein %>%
   filter( Strain == "MED4") %>% 
@@
 
-MED4ProteinAnotated
+MED4ProteinAnnotated
 ```
@@
 
- ggsave(file = file.path(PlotsOut, paste("MED4ProteinAnotated",".png",sep = "")), plot = MED4ProteinAttonated, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)
+ ggsave(file = file.path(PlotsOut, paste("MED4ProteinAnnotated",".png",sep = "")), plot = MED4ProteinAnnotated, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)
 
-ggsave(file = file.path(PlotsOut, paste("MIT9313ProteinAnotated",".png",sep = "")), plot = MIT9313ProteinAttonated, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("MIT9313ProteinAnnotated",".png",sep = "")), plot = MIT9313ProteinAnnotated, device = NULL, scale = 1, height=15, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)
 

### 2024-02-16 Code/Manuscript_O2.Rmd
Fixed some minor edits

@@
   - name: Aurora Mattison
-    affil: 1,2
+    affil: 1, 2
   - name: Julie Nadeau
@@
   - name: Maximilian Berthold
-    affil: 1,3
+    affil: 1, 3
   - name: Naaman Omar
@@
   - name: Ondřej Prášil
-    affil: 1,4
+    affil: 1, 4
     main: false
   - name: Amanda M. Cockshutt
-    affil: 1,5
+    affil: 1, 5
     main: false
@@
   - num: 2
-institute:
   - ubc: 'Department of Biology, University of British Columbia'
   - num: 3
-institute:
   - umwelt: 'Umweltbundesamtm, Dessau-Roßlau, Germany'
   - num: 4
-institute:
   - alga: 'Algatech, Czech Academy of Science'
   - num: 5
-institute:
   - sfx: 'Department of Chemistry, St. Frances Xavier University'
@@
 *Prochlorococcus marinus* is functionally differentiated from other cyanobacteria primarily by the absence of phycobilisomes [@chisholmProchlorococcusMarinusNov1992].
-Instead, *Prochlorococcus*  utilizes intra-membrane Pcb proteins bound to divinylchlorophyll a (Chl a2), and α-carotene, as the major light harvesting complex [@goerickePigmentsProchlorococcusMarinus1992]; [@larocheIndependentEvolutionProchlorophyte1996], with diversity in the number of genes encoding Pcb, expression of Pcb under changing light [@garczarekMultiplicationAntennaGenes2000]  [@rocapGenomeDivergenceTwo2003] [@garczarekMultiplicationAntennaGenes2000], and in thylakoid organization [@partenskyProchlorococcusMarinePhotosynthetic1999].
-the genes encoding most of the rest of the photosynthetic apparatus is highly conserved in *Prochlorococcus* [@kettlerPatternsImplicationsGene2007], though the photosynthetic efficiency may vary among clades [@hessPhotosyntheticApparatusProchlorococcus2001; @moorePhotophysiologyMarineCyanobacterium1999].
+Instead, *Prochlorococcus*  utilizes intra-membrane Prochlorophyte Chlorophyll Binding (Pcb) proteins bound to divinylchlorophyll a (Chl a2), and α-carotene, as the major light harvesting complex [@goerickePigmentsProchlorococcusMarinus1992]; [@larocheIndependentEvolutionProchlorophyte1996], with diversity in the number of genes encoding Pcb, expression of Pcb under changing light [@garczarekMultiplicationAntennaGenes2000]  [@rocapGenomeDivergenceTwo2003] [@garczarekMultiplicationAntennaGenes2000], and in thylakoid organization [@partenskyProchlorococcusMarinePhotosynthetic1999].
+The genes encoding most of the rest of the photosynthetic apparatus is highly conserved in *Prochlorococcus* [@kettlerPatternsImplicationsGene2007], though the photosynthetic efficiency may vary among clades [@hessPhotosyntheticApparatusProchlorococcus2001; @moorePhotophysiologyMarineCyanobacterium1999].
 
 *Prochlorococcus marinus* comprises many strains, organized into clades, defined by 16S-23S intergenic transcribed ribosomal sequence signatures (Rocap et al., 2003).
-The clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined by Low Light or High Light.
+The clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined by Low Light (LL) or High Light (HL).
 Of at least 12 known *Prochlorococcus* clades only 5 to date have cultured representatives; HLI, HLII, LLI, LLII/III and LIV [@billerProchlorococcusStructureFunction2015].
@@
 (2018)), homologs to the *Synechocystis* slr0228 and slr1604, implicated in PSII repair.
-In contrast representative LLIII strain MIT9313 showed less overall expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem.
+In contrast representative LLIV strain MIT9313 showed less overall expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem.
 Furthermore MIT9313 expressed primarily FtsH3, homologous to Sll1463 involved in PSI biogenesis, and FtsH expression did not increase in response to light stress.
-Through adaptation to steady low light, LLIII **Prochlorococcus* instead allocates resources processes other than dynamic regulation of PSII repair.
+Through adaptation to steady low light, LLIV *Prochlorococcus* instead allocates resources processes other than dynamic regulation of PSII repair.
 

### 2024-02-16 Code/ManuscriptPURFits.Rmd
Added Strain name to each grid in plot
Fixed pur fit plot

@@
   ggplot() +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 4, alpha = 1.0) +
     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 2, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
- geom_text(aes(x = 1000, y = 0.9, label= "A"), data = . %>% filter(O2_uM == 250, Strain == "MED4"), size = 20, hjust = 0.3, vjust = 0) +
+ geom_text(aes(x = 1000, y = 0.75, label= "A     MED4 HLI"), data = . %>% filter(O2_uM == 250, Strain == "MED4"), size = 3, hjust = 0, vjust = 0) +
   scale_x_continuous(label=scientific_10) +
-   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
+   scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
   scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
@@
                     labeller = labeller(Strain = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
- guides(linetype = guide_legend(nrow = 4),
+ guides(linetype = guide_legend(nrow = 1),
         fill = "none",
-        colour = guide_legend(nrow = 4)) +
- guides(shape = guide_legend(nrow = 4)) +
+        colour = guide_legend(nrow = 1)) +
+ guides(shape = guide_legend(nrow = 1)) +
   theme_bw() +
-   theme( strip.text = element_text(size = 30),
+   theme( strip.text = element_text(size = 10),
         axis.title.y = element_blank(),
@@
         axis.text.x = element_blank(),
-        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
+        axis.text.y = element_text(size = 7, color = "black", angle = 0, hjust = 1.0),
         strip.background=element_rect(color="grey87", fill = "grey82"),
@@
         legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title =  element_text(size = 30),  #change legend title font size
-        legend.text = element_text(size = 30),   #change legend text font size
+        legend.title =  element_text(size = 15),  #change legend title font size
+        legend.text = element_text(size = 15),   #change legend text font size
         legend.position = "top") +
@@
   ggplot() +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 4, alpha = 1.0) +
     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 2, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) + 
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) + 
    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
@@
    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
- geom_text(aes(x = 1000, y = 0.9, label= "B"), data = . %>% filter(O2_uM == 250, Strain == "SS120"), size = 20, hjust = 0.3, vjust = 0) +
+ geom_text(aes(x = 1000, y = 0.75, label= "B     SS120 LLII/III"), data = . %>% filter(O2_uM == 250, Strain == "SS120"), size = 3, hjust = 0, vjust = 0) +
   scale_x_continuous(label=scientific_10) +
-   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
+   scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
   # coord_cartesian(ylim = c (0, 0.07)) +
@@
   theme_bw() +
-   theme( strip.text = element_text(size = 30),
+   theme( strip.text = element_text(size = 10),
         axis.title.y = element_blank(),
@@
         legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title =  element_text(size = 30),  #change legend title font size
-        legend.text = element_text(size = 30),   #change legend text font size
+        # legend.title =  element_text(size = 20),  #change legend title font size
+        # legend.text = element_text(size = 20),   #change legend text font size
         legend.position = "none") +
@@
   ggplot() +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 4, alpha = 1.0) +
     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 2, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) + 
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) + 
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "twodash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +
@@
   labs(x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
- geom_text(aes(x = 1000, y = 0.9, label= "C"), data = . %>% filter(O2_uM == 250, Strain == "MIT9313"), size = 20, hjust = 0.3, vjust = 0) +
-  scale_x_continuous(label=scientific_10) +
-   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
+ geom_text(aes(x = 1000, y = 0.75, label= "C     MIT9313 LLIV"), data = . %>% filter(O2_uM == 250, Strain == "MIT9313"), size = 3, hjust = 0, vjust = 0) +
+  scale_x_continuous(breaks = c(0, 1000000,2000000, 3000000, 4000000),label=scientific_10, limits = c (-100, 5000000)) +
+   scale_y_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
   scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
@@
   theme_bw() +
-   theme( strip.text = element_text(size = 30),
+   theme( strip.text = element_text(size = 10),
           axis.title.y = element_blank(),
-          axis.title.x = element_text(size = 30, color = "black"),
-          axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
-          axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
+          axis.title.x = element_text(size = 15, color = "black"),
+          axis.text.x = element_text(size = 10, color = "black", angle = 0, hjust = 1.0),
+          axis.text.y = element_text(size = 7, color = "black", angle = 0, hjust = 1.0),
         strip.background=element_rect(color="grey87", fill = "grey82"),
@@
 y.grob <- textGrob("Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")",
-                   gp = gpar(col="black", fontsize = 20), rot = 90)
+                   gp = gpar(col="black", fontsize = 15), rot = 90)
 

### 2024-02-16 Code/Manuscript_O2.Rmd
edits

@@
 
-```{r FtsHtable, table.cap = FtsHtable_cap, echo = FALSE}
+```{r FtsHtable, echo = FALSE}
 
-FtsHtable_cap <- glue("FtsH protease homologs in *Prochlorococcus marinus* and the model cyanobacterium *Synechocystis* sp.
+FtsHtable_cap <- "FtsH protease homologs in *Prochlorococcus marinus* and the model cyanobacterium *Synechocystis* sp.
 PCC6803.
-Protein homology determined by multiple sequence alignment with MUSCLE followed by construction of maximum likelihood phylogenetic tree using 1000 bootstrap replicates in MEGAX.",
+Protein homology determined by multiple sequence alignment with MUSCLE followed by construction of maximum likelihood phylogenetic tree using 1000 bootstrap replicates in MEGAX."
 
-                       .sep = " ")
 FtsHTable <- tibble(Organism = c("Prochlorococcus marinus", "Synechocystis sp. PCC6803", "Function"),

### 2024-02-16 Code/ManuscriptPURFits.Rmd
Fixed letter size in plot, deleted old individual purfit figures

@@
 PhotoperiodShapes
+
+```
+# set linetypes
+```{r linetypes}
+
+MyPhotoperiods = c(16, 12, 8, 4)
+MyLineTypes = c("twodash","dashed", "dotted", "aa")
+
+names(MyLineTypes) <- MyPhotoperiods
+MyLineTypes
 
@@
          OxygenLabel = "Oxygen Concentration (µM)",
-         Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4" )),
+         Photoperiod = factor(Data_all_Photoperiod, levels = c(16, 12, 8, 4)),
          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
@@
    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
- geom_text(aes(x = 1000, y = 0.75, label= "A     MED4 HLI"), data = . %>% filter(O2_uM == 250, Strain == "MED4"), size = 3, hjust = 0, vjust = 0) +
+ geom_text(aes(x = 1000, y = 0.75, label= "A     MED4 HLI"), data = . %>% filter(O2_uM == 250, Strain == "MED4"), size = 4, hjust = 0, vjust = 0) +
   scale_x_continuous(label=scientific_10) +
@@
   scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
-  scale_linetype_manual(values = c("twodash","dashed", "dotted", "aa"), labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
+  scale_linetype_manual(values = MyLineTypes, labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
    scale_shape_manual(values = PhotoperiodShapes)  +
@@
         fill = "none",
-        colour = guide_legend(nrow = 1)) +
+        color = guide_legend(nrow = 1)) +
  guides(shape = guide_legend(nrow = 1)) +
@@
         axis.text.x = element_blank(),
-        axis.text.y = element_text(size = 7, color = "black", angle = 0, hjust = 1.0),
+        axis.text.y = element_text(size = 9, color = "black", angle = 0, hjust = 1.0),
         strip.background=element_rect(color="grey87", fill = "grey82"),
@@
         color = "Growth Waveband (nm)",
-       linetype = "Photoperiod (h) "
+       linetype = "Photoperiod lines"
       )
@@
    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
- geom_text(aes(x = 1000, y = 0.75, label= "B     SS120 LLII/III"), data = . %>% filter(O2_uM == 250, Strain == "SS120"), size = 3, hjust = 0, vjust = 0) +
+ geom_text(aes(x = 1000, y = 0.75, label= "B     SS120 LLII/III"), data = . %>% filter(O2_uM == 250, Strain == "SS120"), size = 4, hjust = 0, vjust = 0) +
   scale_x_continuous(label=scientific_10) +
    scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
   scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
@@
         axis.text.x = element_blank(),
-        axis.text.y = element_text(size = 7, color = "black", angle = 0, hjust = 1.0),
+        axis.text.y = element_text(size = 10, color = "black", angle = 0, hjust = 1.0),
         strip.background=element_rect(color="grey87", fill = "grey82"),
@@
   labs(x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
- geom_text(aes(x = 1000, y = 0.75, label= "C     MIT9313 LLIV"), data = . %>% filter(O2_uM == 250, Strain == "MIT9313"), size = 3, hjust = 0, vjust = 0) +
+ geom_text(aes(x = 1000, y = 0.75, label= "C     MIT9313 LLIV"), data = . %>% filter(O2_uM == 250, Strain == "MIT9313"), size = 4, hjust = 0, vjust = 0) +
   scale_x_continuous(breaks = c(0, 1000000,2000000, 3000000, 4000000),label=scientific_10, limits = c (-100, 5000000)) +
@@
           axis.text.x = element_text(size = 10, color = "black", angle = 0, hjust = 1.0),
-          axis.text.y = element_text(size = 7, color = "black", angle = 0, hjust = 1.0),
+          axis.text.y = element_text(size = 10, color = "black", angle = 0, hjust = 1.0),
         strip.background=element_rect(color="grey87", fill = "grey82"),

### 2024-02-16 Code/OceanProteinPlots.Rmd
OceanProtein edited code moved into main repository. Separate repository still on GitHub for future work.

---
title: "OceanProteinPlots"
---
```{r libraries}
library(readr)
library(tidyverse)
library(ggplot2)
library(grid)
library(gridExtra)
```

Import Aurora .csv large files from DropBox, save as .RDS for future use and smaller files to post to GitHub
```{r files paths}
#/Users/dcampbel/Dropbox/OceanProteinProchloro/KM1128/2020/Filtered Datasets
#poi <- read_csv(file.path("..", "..", "..","..", "Dropbox", "OceanProteinProchloro", "KM1128", "2020", "Filtered_Datasets", "poi.csv"))
#pro_proteins <- read_csv(file.path("..", "..", "..","..", "Dropbox", "OceanProteinProchloro", "KM1128", "2020", "Filtered_Datasets", "pro_proteins.csv"))

#saveRDS(poi, file = file.path("..", "Data", "ProcessedData", "poi.RDS"))
#saveRDS(pro_proteins, file = file.path("..", "Data", "ProcessedData", "pro_proteins.RDS"))

#Read in previously imported and saved data converted from large .csv to smaller .RDS
poi <- readRDS(file.path("..", "Data", "ProcessedData", "ProcessedOceanProtein", "poi.RDS"))
pro_proteins <- readRDS(file.path("..", "Data", "ProcessedData", "ProcessedOceanProtein", "pro_proteins.RDS"))
```

```{r strains}
HL<-c("AS9601", "MIT9312", "MED4", "MIT9515","MIT9215", "MIT9301", "MIT9202")
LL<-c("MIT9313", "MIT9303", "SS120", "MIT9211", "NATL1A", "NATL2A")

strains_list<-c("MED4","MIT9515","AS9601","MIT9202","MIT9215","MIT9301","MIT9312","NATL1A","NATL2A", "MIT9211","SS120","MIT9303","MIT9313")
```

```{r set depth light and O2}
#estimated from LightPhotoperiodColourImaging/WaterAttenuation.Rmd

DepthPAR <- c(130, 70, 40)
PAR <- c(30, 90, 180)
names(DepthPAR) <- PAR

DepthPAR
names(DepthPAR)

O2_uM <- c(2, 25, 250)

```

```{r string function}
#not used
#wrapper <- function(x)
#{paste(strwrap(x), collapse = "\n")}
```

To analyze for presence/absence of additional proteins like AOX need to extract EC numbers from best_hit_annotation; difficult format delimited by ';' with variable numbers of fields.
EC 1.10.3.11, ubiquinol oxidase (non-electrogenic) 	cyanide-resistant bd-type ubiquinol oxidase, cyanide-resistant ubiquinol oxidase, cytochrome bo3 ubiquinol oxidase, ubiquinol oxidase (non-electrogenic)

EC 1.10.3.11 not detected by scan
KEGG EC 1.6.5.9  not detected; issue with search terms?
```{r extract hit info}
# pro_proteins2 <- pro_proteins |>
#   mutate(EC2 = str_extract(string = best_hit_annotation, pattern = "(?<=EC:)[0-9]*"))
# 
# pro_proteins2 <- pro_proteins |>
#   mutate(EC2 = str_extract(string = best_hit_annotation, pattern = "(?<=EC:)(\\d`.`+)"))
# 
# unique(pro_proteins2$EC2)
# 
# pro_proteins2 <- pro_proteins |>
#   separate_wider_delim(cols = best_hit_annotation, delim = ";", names = c("anno1", "anno2", "anno3", "anno4", "anno5", "anno6" ,"anno7", "anno8"), too_few = "align_start", cols_remove = FALSE)
# 
# head(pro_proteins2)
# 
# #detect EC 1.10.3.11
# pro_proteins2 <- pro_proteins |>
#   mutate(AOX = str_detect(string = best_hit_annotation, pattern = "1.10.3.11"))
# 
# head(pro_proteins2)

# #detect KEGG EC 1.6.5.9  
pro_proteins2 <- pro_proteins |>
   mutate(AOX = str_detect(string = best_hit_annotation, pattern = "1.6.5.9"))

 head(pro_proteins2)
 unique(pro_proteins2$AOX)
```

```{r pro_proteins plots}

pro_proteins |>
  ggplot()+
  geom_point(aes(x = O2, y= depth)) +
  scale_x_continuous(limits = c(0, 260)) +
  scale_y_reverse(limits = c(260, 0)) +
  geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.2) +
  geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.2) +
  labs(title = "All detections of Prochlorococcus proteins from OceanProteinPlots.Rmd, from pro_proteins",
       caption = "Horizontals approximate experimental growth light levels; Verticals indicate experimental growth oxygen levels") +
  theme_bw()

#ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "ProchloroAllProteinsDepthO2.png")))

pro_proteins |>
    filter(strain %in% c("MIT9313","MED4", "SS120")) |>
  ggplot()+
  geom_point(aes(x = O2, y= depth)) +
  scale_x_continuous(limits = c(0, 260)) +
  scale_y_reverse(limits = c(260, 0)) +
  geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.2) +
  geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.2) +
  labs(title = "All detections of MIT9313,MED4, SS120 proteins from OceanProteinPlots.Rmd, from pro_proteins",
       caption = "Horizontals approximate experimental growth light levels; Verticals indicate experimental growth oxygen levels") +
  theme_bw()

#ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "MIT9313MED4SS120AllProteinsDepthO2.png")))

#data for all strains/clades is nearly identical;  were all strains/clades truly detected at all sampling points where any Prochlorococcus is present

poi |>
  filter(strain %in% c("MIT9313","MED4", "SS120")) |>
  ggplot()+
  geom_point(aes(x = O2, y= depth)) +
  scale_x_continuous(limits = c(0, 260)) +
  scale_y_reverse(limits = c(260, 0)) +
  geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.2) +
  geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.2) +
  facet_grid(vars(strain)) +
  theme(panel.grid.minor = element_line(size = 0), panel.grid.major = element_line(size = 2)) +
  theme_bw()

```

Add Supercomplex categories desired for plotting to poi; one column with values or separate 0/1 columns for each category?
One column better for facetting; separate 0/1 columns better for filter/grid arrange
Aurora used grid arrange
```{r}
# poi <- poi |>
#   mutate(Supercomplex = 
#            case_when(complex == "ribosome" ~ complex,
#                      complex == "psii" ~ complex,
#                      complex == "psi" ~ complex,
#                      complex == "carb" ~ complex,
#                      subunit %in% unique(grep("pcb.",poi$subunit, value = TRUE, ignore.case=TRUE)) ~ "Pcb",
#                      subunit %in% c("ftsh1", "ftsh2") ~ "FtsH12",
#                      subunit %in% c("ftsh3", "ftsh4") ~ "FtsH34",
#                      )
#          
#          ) 
# 
# 
# unique(poi$Supercomplex)

#          , 
#   subunit %in% atp ~ "atp",
#   subunit %in% psii ~ "psii", 
#   subunit %in% psi ~ "psi",
#   subunit %in% rbc ~ "rubisco",
#   subunit %in% pet ~ "cytb6f",
#   subunit %in% ndh ~ "ndh",
#   subunit %in% clp ~ "clp",
#   subunit %in% cpe ~ "cpe",
#   subunit %in% ycf ~ "ycf",
#   subunit %in% carb ~ "carb",
#   subunit %in% iron ~ "iron stress",
#   subunit=="ftsZ" ~ subunit,
#   subunit=="ftsh1" ~ subunit,
#   subunit=="ftsh2" ~ subunit,
#   subunit=="ftsh3" ~ subunit,
#   subunit=="ftsh4" ~ subunit,
#   subunit=="fdx" ~ subunit,
#   subunit=="pc" ~ subunit,
#   subunit=="psb28" ~ subunit,
#   subunit=="psb27" ~ subunit,
#   subunit %in% pcb ~ subunit,))
#   
#   
# rp<-unique(grep("rpl.",poi$subunit, value = TRUE, ignore.case=TRUE))
# rp<-append(rp, unique(grep("rps.",poi$subunit, value = TRUE, ignore.case=TRUE)))
# rp<-append(rp, unique(grep("rpm.",poi$subunit, value = TRUE, ignore.case=TRUE)))
# 
# atp<-unique(grep("atp.",poi$subunit, value = TRUE, ignore.case=TRUE))
# 
# pcb<-unique(grep("pcb.",poi$subunit, value = TRUE, ignore.case=TRUE))
# 
# psii<-c("psbA", "psbB", "psbC", "psbD", "psbE", "psbF", "psbJ", "psbO", "psbP", "psbV")
# 
# psi<-unique(grep("psa.",poi$subunit, value = TRUE, ignore.case=TRUE))
# 
# rbc<-unique(grep("rbc.",poi$subunit, value = TRUE, ignore.case=TRUE))
# 
# pet<-unique(grep("pet.",poi$subunit, value = TRUE, ignore.case=TRUE))
# 
# ftsh<-unique(grep("ftsh.",poi$subunit, value = TRUE, ignore.case=TRUE))
# 
# clp<-unique(grep("clp.",poi$subunit, value = TRUE, ignore.case=TRUE))
# 
# cpe<-unique(grep("cpe.",poi$subunit, value = TRUE, ignore.case=TRUE))
# 
# ycf<-unique(grep("ycf.",poi$subunit, value = TRUE, ignore.case=TRUE))
# 
# iron<-unique(grep("isi.",poi$subunit, value = TRUE, ignore.case=TRUE))
# 
# carb<-c("pgm", "glk", "pgi", "zwf", "nagB", "gnd", "prk", "rpe", "rpi", "tkt", "tal","tpi", "gapdh", "pgk", "gpmB", "eno", "pykF", "fba", "glpX", "pgi","pdhA", "pdhB", "pdhC", "lpd", "gltA", "acnB", "icd NAD", "icd NADP","ppc", "dld")
# 
# ndh<- unique(grep("ndh.", poi$subunit, ignore.case=T, value=T))
# 
# ccm<-c("csos2","csos3","cpa","cpb")
# 
# poi<-mutate(poi, complex=case_when(
#   subunit %in% rp ~ "ribosome", 
#   subunit %in% atp ~ "atp",
#   subunit %in% psii ~ "psii", 
#   subunit %in% psi ~ "psi",
#   subunit %in% rbc ~ "rubisco",
#   subunit %in% pet ~ "cytb6f",
#   subunit %in% ndh ~ "ndh",
#   subunit %in% clp ~ "clp",
#   subunit %in% cpe ~ "cpe",
#   subunit %in% ycf ~ "ycf",
#   subunit %in% carb ~ "carb",
#   subunit %in% iron ~ "iron stress",
#   subunit=="ftsZ" ~ subunit,
#   subunit=="ftsh1" ~ subunit,
#   subunit=="ftsh2" ~ subunit,
#   subunit=="ftsh3" ~ subunit,
#   subunit=="ftsh4" ~ subunit,
#   subunit=="fdx" ~ subunit,
#   subunit=="pc" ~ subunit,
#   subunit=="psb28" ~ subunit,
#   subunit=="psb27" ~ subunit,
#   subunit %in% pcb ~ subunit,
#   
#   )
# )
# ppp<-c("tkt", "gnd","pgl","tal","zwf","rpe","rpi","glpX","pgm","pgi","deoC","prpp","glk")
# ppp_enz<-filter(poi, subunit %in% ppp)
# ppp_enz<-mutate(ppp_enz, complex="ppp")
# 
# tca<-c("mqo", "mdh","icd NAD","icd NADP","fdx","sdh", "gltA","fum")
# tca_enz<-filter(poi, subunit %in% tca)
# tca_enz<-mutate(tca_enz, complex="tca")
# 
# calvin<-c("tpi", "fba","tktA", "gapdh", "glpX", "tpiA","prk","pgk","rbcL","rbcS","rpe","rpiA")
# calvin_enz<-filter(poi, subunit %in% calvin)
# calvin_enz<-mutate(calvin_enz, complex="calvin")
# 
# poi<-rbind(calvin_enz, poi)
# poi<-rbind(tca_enz, poi)
# poi<-rbind(ppp_enz, poi)
# 
# poi<-filter(poi,!is.na(poi$complex))
# unique(poi$complex)
# unique(poi$subunit)  
```

```{r depth O2 plots}

#consider including ribosomal target for photoinhibition?
#consider assembling 'pcb' supercomplex?
#https://stackoverflow.com/questions/32555531/how-to-italicize-part-one-or-two-words-of-an-axis-title

PhotosynthLabels <- c("PSII", "Cytb6f", "PSI", "ATP Synthase", "RUBISCO")
ProteinMetabLabels <- c("FtsH1", "FtsH2", "FtsH3", "FtsH4", "Ribosome")
StrainLabels <- c("MED4", "SS120", "MIT9313")

ElectronTrans <- c("psii", "cytb6f", "psi", "rubisco", "atp")

ProteinMetab <- c("ftsh1", "ftsh2", "ftsh3", "ftsh4", "ribosome")

poi |>
  filter(complex %in% ElectronTrans) |>
  filter(strain %in% StrainLabels) |>
  ggplot() +
  geom_point(aes(color=clade, x = O2, y= depth)) +
  scale_x_continuous(limits = c(0, 260)) +
  scale_y_reverse(limits = c(260, 0)) +
  geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.1) +
  geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.1) +
  facet_grid(factor(strain, levels = c("MED4", "SS120", "MIT9313")) ~ factor(complex, levels = c("psii", "cytb6f", "psi", "rubisco", "atp"), labels = PhotosynthLabels)) +
  labs(title = expression('Ocean detection of' ~italic(Prochlorococcus)~ 'photosynthesis complexes'),
       y = "Depth (m)",
       x = expression("O"[2] ~ "(µM)")) +
    # ) +
  theme_bw()

 ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "ProchloroPhotosynthDepthO2.png")))
 ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "ProchloroPhotosynthDepthO2.tiff")))

poi |>
  filter(complex %in% ProteinMetab) |>
  filter(strain %in% StrainLabels) |>
  ggplot() +
  geom_point(aes(color=clade, x = O2, y= depth)) +
  scale_x_continuous(limits = c(0, 260)) +
  scale_y_reverse(limits = c(260, 0)) +
  geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.1) +
  geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.1) +
  facet_grid(factor(strain, levels = c("MED4", "SS120", "MIT9313")) ~ factor(complex, levels = c("ftsh1", "ftsh2", "ftsh3", "ftsh4", "ribosome"), labels = ProteinMetabLabels)) +
   labs(y = "Depth (m)",
        x = expression("O"[2] ~ "(µM)"),
        title = expression('Ocean detection of' ~italic(Prochlorococcus)~ 'protein metabolism complexes')) +
  theme_bw()

 ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "ProchloroProteinMetabDepthO2.png")))
 ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "ProchloroProteinMetabDepthO2.tiff")))

```

### 2024-02-16 Code/Manuscript_O2.Rmd
edited file paths for local versions of oceanprotein figures

@@
 FiguresIn <- file.path("..","Output", "Figures")
-FiguresInOceanPro <- file.path( "..", "..", "OceanProteinProchloro", "Output")
 FigureInO2Analy <- file.path(  "..", "..", "O2Analyses", "Output")
@@
 
-knitr::include_graphics(file.path(FiguresInOceanPro, "ProchloroPhotosynthDepthO2.png"))
+knitr::include_graphics(file.path(FiguresIn, "ProchloroPhotosynthDepthO2.png"))
 ```
@@
 
-knitr::include_graphics(file.path(FiguresInOceanPro, "ProchloroProteinMetabDepthO2.png"))
+knitr::include_graphics(file.path(FiguresIn, "ProchloroProteinMetabDepthO2.png"))
 ```

### 2024-02-16 Code/Manuscript_O2.Rmd
Fixed PURfit caption

--- 2024-02-16 Code/Manuscript_O2.Rmd
@@
 
-%%%% Insert PURFits figures  %%%
-
 ```{r AllStrainPurFitsPlots,  fig.cap = AllStrainPurFitsPlots_cap, fig.height = 10, fig.width = 10, echo = FALSE}
 
-AllStrainPurFitsPlots_cap <- glue("** The chlorophyll proxy growth rate (d^-1^) vs. the Photosynthetic Usable Radiation (PUR) (µmol photons m^-2^ d^-1^).**",
-                    "The x-axis is the Photosynthetic Usable Radiation (PUR) (µmol photons m^-2^ s^-1^) .",
-                    "The y-axis is the chlorophyll specific growth rate (d^-1^).",
-                    "**A.** The High Light I (HLI) ecotype MED4.  under 250 µM of O~2~ and red light.",
-                    "**B.** The Low Light II/II (LLII/III) ecotype SS120. under 25 µM of O~2~ and red light.",
-                    "**C.** The Low Light IV (LLIV) ecotype MIT9313. under 2.5 µM of O~2~ and red light.",
-                     "Shapes show the imposed photoperiod (h); hollow inverted triangle for 4 h, solid diamond for 8 h, solid circle for 12 h, solid upright triangle for 16 h.",
-                      "Symbol colours show the spectral waveband for growth; black for white LED light (full spectrum), red for red light (660 nm), and blue for blue light (450 nm).",
-                      "Large shapes show mean or single determinations of growth rate from logistic curve fits; small shapes show values for replicate determinations, if any.",
-                    "The 3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
+AllStrainPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
+                    "**A.** MED4 High Light I ecotype under 250, 25, or 2.5 µM of O~2~.",
+                    "**B.** SS120 Low Light II/III (LLII/III) ecotype under 250, 25, or 2.5 µM of O~2~.",
+                    "**C.** MIT9313 Low Light IV (LLIV) ecotype under 250, 25, or 2.5 µM of O~2~.",
+                    "3 levels of imposed dissolved O~2~ concentrations (µM) are in rows for each strain.",
+                    "Shapes show the imposed photoperiod (h); 4 h (hollow inverted triangle),  8 h (solid diamond), 12 h (solid circle), 16 h (solid upright triangle).",
+                      "Symbol colours show the spectral waveband for growth; white LED (black symbols), 660 nm (red symbols), and 450 nm (blue symbols).",
+                      "Large symbols show mean of growth rate from logistic curve fits; small symbols show values for replicate determinations, if any.",
+                    "Platt (add Platt citation here) 4 parameter model fits to data pooled for each combination of strain and dissolved oxygen shown with solid lines.
+Seperate models fit to photoperiod data and shown if significantly different from the pooled model; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).
+",
                        .sep = " ")
@@
 
-```{r MIT9313ProteinAnmotated, fig.cap = MIT9313ProteinAnmotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+```{r MIT9313ProteinAnnotated, fig.cap = MIT9313ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
 
-MIT9313ProteinAmnotated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade).  **",
+MIT9313ProteinAnnotated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade).  **",
 

### 2024-02-16 Code/OceanProteinPlots.Rmd

@@
 
-Import Aurora .csv large files from DropBox, save as .RDS for future use and smaller files to post to GitHub
+Imported Aurora .csv large files from DropBox, saved as .RDS for future use and smaller files to post to GitHub
 ```{r files paths}
@@
 
-```{r string function}
-#not used
-#wrapper <- function(x)
-#{paste(strwrap(x), collapse = "\n")}
-```
-
 To analyze for presence/absence of additional proteins like AOX need to extract EC numbers from best_hit_annotation; difficult format delimited by ';' with variable numbers of fields.
@@
 ```{r extract hit info}
-# pro_proteins2 <- pro_proteins |>
-#   mutate(EC2 = str_extract(string = best_hit_annotation, pattern = "(?<=EC:)[0-9]*"))
-# 
-# pro_proteins2 <- pro_proteins |>
-#   mutate(EC2 = str_extract(string = best_hit_annotation, pattern = "(?<=EC:)(\\d`.`+)"))
-# 
-# unique(pro_proteins2$EC2)
-# 
-# pro_proteins2 <- pro_proteins |>
-#   separate_wider_delim(cols = best_hit_annotation, delim = ";", names = c("anno1", "anno2", "anno3", "anno4", "anno5", "anno6" ,"anno7", "anno8"), too_few = "align_start", cols_remove = FALSE)
-# 
-# head(pro_proteins2)
-# 
 # #detect EC 1.10.3.11
@@
 # #detect KEGG EC 1.6.5.9  
-pro_proteins2 <- pro_proteins |>
-   mutate(AOX = str_detect(string = best_hit_annotation, pattern = "1.6.5.9"))
-
- head(pro_proteins2)
- unique(pro_proteins2$AOX)
+# pro_proteins2 <- pro_proteins |>
+#    mutate(AOX = str_detect(string = best_hit_annotation, pattern = "1.6.5.9"))
+#  
+#  head(pro_proteins2)
+#  unique(pro_proteins2$AOX)
 ```
@@
 
-#ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "MIT9313MED4SS120AllProteinsDepthO2.png")))
-
-#data for all strains/clades is nearly identical;  were all strains/clades truly detected at all sampling points where any Prochlorococcus is present
-
 poi |>
@@
 
-```
-
-Add Supercomplex categories desired for plotting to poi; one column with values or separate 0/1 columns for each category?
-One column better for facetting; separate 0/1 columns better for filter/grid arrange
-Aurora used grid arrange
-```{r}
-# poi <- poi |>
-#   mutate(Supercomplex = 
-#            case_when(complex == "ribosome" ~ complex,
-#                      complex == "psii" ~ complex,
-#                      complex == "psi" ~ complex,
-#                      complex == "carb" ~ complex,
-#                      subunit %in% unique(grep("pcb.",poi$subunit, value = TRUE, ignore.case=TRUE)) ~ "Pcb",
-#                      subunit %in% c("ftsh1", "ftsh2") ~ "FtsH12",
-#                      subunit %in% c("ftsh3", "ftsh4") ~ "FtsH34",
-#                      )
-#          
-#          ) 
-# 
-# 
-# unique(poi$Supercomplex)
-
-#          , 
-#   subunit %in% atp ~ "atp",
-#   subunit %in% psii ~ "psii", 
-#   subunit %in% psi ~ "psi",
-#   subunit %in% rbc ~ "rubisco",
-#   subunit %in% pet ~ "cytb6f",
-#   subunit %in% ndh ~ "ndh",
-#   subunit %in% clp ~ "clp",
-#   subunit %in% cpe ~ "cpe",
-#   subunit %in% ycf ~ "ycf",
-#   subunit %in% carb ~ "carb",
-#   subunit %in% iron ~ "iron stress",
-#   subunit=="ftsZ" ~ subunit,
-#   subunit=="ftsh1" ~ subunit,
-#   subunit=="ftsh2" ~ subunit,
-#   subunit=="ftsh3" ~ subunit,
-#   subunit=="ftsh4" ~ subunit,
-#   subunit=="fdx" ~ subunit,
-#   subunit=="pc" ~ subunit,
-#   subunit=="psb28" ~ subunit,
-#   subunit=="psb27" ~ subunit,
-#   subunit %in% pcb ~ subunit,))
-#   
-#   
-# rp<-unique(grep("rpl.",poi$subunit, value = TRUE, ignore.case=TRUE))
-# rp<-append(rp, unique(grep("rps.",poi$subunit, value = TRUE, ignore.case=TRUE)))
-# rp<-append(rp, unique(grep("rpm.",poi$subunit, value = TRUE, ignore.case=TRUE)))
-# 
-# atp<-unique(grep("atp.",poi$subunit, value = TRUE, ignore.case=TRUE))
-# 
-# pcb<-unique(grep("pcb.",poi$subunit, value = TRUE, ignore.case=TRUE))
-# 
-# psii<-c("psbA", "psbB", "psbC", "psbD", "psbE", "psbF", "psbJ", "psbO", "psbP", "psbV")
-# 
-# psi<-unique(grep("psa.",poi$subunit, value = TRUE, ignore.case=TRUE))
-# 
-# rbc<-unique(grep("rbc.",poi$subunit, value = TRUE, ignore.case=TRUE))
-# 
-# pet<-unique(grep("pet.",poi$subunit, value = TRUE, ignore.case=TRUE))
-# 
-# ftsh<-unique(grep("ftsh.",poi$subunit, value = TRUE, ignore.case=TRUE))
-# 
-# clp<-unique(grep("clp.",poi$subunit, value = TRUE, ignore.case=TRUE))
-# 
-# cpe<-unique(grep("cpe.",poi$subunit, value = TRUE, ignore.case=TRUE))
-# 
-# ycf<-unique(grep("ycf.",poi$subunit, value = TRUE, ignore.case=TRUE))
-# 
-# iron<-unique(grep("isi.",poi$subunit, value = TRUE, ignore.case=TRUE))
-# 
-# carb<-c("pgm", "glk", "pgi", "zwf", "nagB", "gnd", "prk", "rpe", "rpi", "tkt", "tal","tpi", "gapdh", "pgk", "gpmB", "eno", "pykF", "fba", "glpX", "pgi","pdhA", "pdhB", "pdhC", "lpd", "gltA", "acnB", "icd NAD", "icd NADP","ppc", "dld")
-# 
-# ndh<- unique(grep("ndh.", poi$subunit, ignore.case=T, value=T))
-# 
-# ccm<-c("csos2","csos3","cpa","cpb")
-# 
-# poi<-mutate(poi, complex=case_when(
-#   subunit %in% rp ~ "ribosome", 
-#   subunit %in% atp ~ "atp",
-#   subunit %in% psii ~ "psii", 
-#   subunit %in% psi ~ "psi",
-#   subunit %in% rbc ~ "rubisco",
-#   subunit %in% pet ~ "cytb6f",
-#   subunit %in% ndh ~ "ndh",
-#   subunit %in% clp ~ "clp",
-#   subunit %in% cpe ~ "cpe",
-#   subunit %in% ycf ~ "ycf",
-#   subunit %in% carb ~ "carb",
-#   subunit %in% iron ~ "iron stress",
-#   subunit=="ftsZ" ~ subunit,
-#   subunit=="ftsh1" ~ subunit,
-#   subunit=="ftsh2" ~ subunit,
-#   subunit=="ftsh3" ~ subunit,
-#   subunit=="ftsh4" ~ subunit,
-#   subunit=="fdx" ~ subunit,
-#   subunit=="pc" ~ subunit,
-#   subunit=="psb28" ~ subunit,
-#   subunit=="psb27" ~ subunit,
-#   subunit %in% pcb ~ subunit,
-#   
-#   )
-# )
-# ppp<-c("tkt", "gnd","pgl","tal","zwf","rpe","rpi","glpX","pgm","pgi","deoC","prpp","glk")
-# ppp_enz<-filter(poi, subunit %in% ppp)
-# ppp_enz<-mutate(ppp_enz, complex="ppp")
-# 
-# tca<-c("mqo", "mdh","icd NAD","icd NADP","fdx","sdh", "gltA","fum")
-# tca_enz<-filter(poi, subunit %in% tca)
-# tca_enz<-mutate(tca_enz, complex="tca")
-# 
-# calvin<-c("tpi", "fba","tktA", "gapdh", "glpX", "tpiA","prk","pgk","rbcL","rbcS","rpe","rpiA")
-# calvin_enz<-filter(poi, subunit %in% calvin)
-# calvin_enz<-mutate(calvin_enz, complex="calvin")
-# 
-# poi<-rbind(calvin_enz, poi)
-# poi<-rbind(tca_enz, poi)
-# poi<-rbind(ppp_enz, poi)
-# 
-# poi<-filter(poi,!is.na(poi$complex))
-# unique(poi$complex)
-# unique(poi$subunit)  
 ```

### 2024-02-16 Code/Manuscript_O2.Rmd
Fixed some fig captions Fixed Aurora's text that was boxed in a different text box

@@
 
-MED4PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade) vs. photoperiod (h).  **",
+MED4PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade) vs. photoperiod (h).  **",
 
@@
 
-SS120PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low Light (LLIII) deep ocean clade) vs. photoperiod (h). **",
+SS120PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low Light (LLIII) deep ocean clade) vs. photoperiod (h). **",
 
@@
 
-MIT9313PAR_cap <- glue("**Chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
+MIT9313PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
 
@@
 
-MED4GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MED4 grown under 660 nm (red) and 450 nm (blue) light.**",
-                    "The x-axis is photoperiod (h).",
-                    "The y-axis is actinic Photosynethetic Active Radiation (PAR) level (µmol photons m^-2^ s^-1^).",
+MED4GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 grown under 660 nm (red) and 450 nm (blue) light.**",
+                    "X-axis is photoperiod (h).",
+                    "Y-axis is actinic Photosynethetic Active Radiation (PAR, µmol photons m^-2^ s^-1^).",
                     "**A.** represents the model under 250 µM of O~2~ and red light.",
@@
                     "**D.** represents the model under 25 µM of O~2~ and blue light.",
-                    "The legend represents a colour gradient of growth rate from no growth (white) to 1 d^-1^ (dark blue).",
-                    "The labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",
+                    "Legends represent a colour gradient of growth rate from no growth (white) to 1.00 d^-1^ (dark red or dark blue).",
+                    "Labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",
 
@@
 
-SS120GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* SS120 grown under 660 nm (red) and 450 nm (blue) light.**",
-                    "The x-axis is photoperiod (h).",
-                    "The y-axis is actinic Photosynethetic Active Radiation (PAR) level (µmol photons m^-2^ s^-1^).",
+SS120GAM_cap <- glue("**Contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 grown under 660 nm (red) and 450 nm (blue) light.**",
+                    "X-axis is photoperiod (h).",
+                    "Y-axis is actinic Photosynethetic Active Radiation (PAR, µmol photons m^-2^ s^-1^).",
                     "**A.** represents the model under 250 µM of O~2~ and red light.",
@@
 
-MIT9313GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll proxy growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 grown under 660 nm (red) and 450 nm (blue) light.**",
-                    "The x-axis is photoperiod (h).",
-                    "The y-axis is actinic Photosynthetically Active Radiation (PAR) level (µmol photons m^-2^ s^-1^).",
+MIT9313GAM_cap <- glue("**Contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 grown under 660 nm (red) and 450 nm (blue) light.**",
+                    "X-axis is photoperiod (h).",
+                    "Y-axis is actinic Photosynthetically Active Radiation (PAR, µmol photons m^-2^ s^-1^).",
                     "**A.** represents the model under 250 µM of O~2~ and red light.",
@@
                     "**F.** represents the model under 2.5 µM of O~2~ and blue light.",
-                    "The legend represents a colour gradient of growth rate from no growth (white) to 1 d^-1^ (dark blue).",
-                    "The labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",
+                    "Legends represent a colour gradient of growth rate from no growth (white) to 1.00 d^-1^ (dark red or dark blue).",
+                    "Labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",
 
@@
                       "Large symbols show mean of growth rate from logistic curve fits; small symbols show values for replicate determinations, if any.",
-                    "Platt (add Platt citation here) 4 parameter model fits to data pooled for each combination of strain and dissolved oxygen shown with solid lines.
+                    "Platt (add Platt citation here) 4 parameter model fit to data pooled for each combination of strain and dissolved oxygen shown with solid lines.
 Seperate models fit to photoperiod data and shown if significantly different from the pooled model; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).

### 2024-02-16 Code/Manuscript_O2.Rmd
edits to Acknowledgements & Funding

@@
 To Be Entered through PLoSONe system and deleted here
-Czech Academy of Science visiting fellowship (DAC)
+Czech Academy of Science visiting fellowship supporting DAC work at AlgaTech (OP)
 Canada Research Chair in Phytoplankton Ecophysiology (DAC)

### 2024-02-16 Code/Manuscript_O2.Rmd
Added results and discussion

--- 2024-02-16 Code/Manuscript_O2.Rmd
@@
 
-# PURPARFits <- readRDS(file.path(DataIn, "PICO_Merged_GrowthFitsPURPAR.Rds"))
+ PURPARFits <- readRDS(file.path(DataIn, "PICO_Merged_GrowthFitsPURPAR.Rds"))
 
@@
 
-## *Prochlorococcus* evolutionary and functional diversity
+## *Prochlorococcus* evolutionary and functional diversity {.unnumbered}
 
@@
 
-## *Prochlorococcus* responses to changing niches
+## *Prochlorococcus* responses to changing niches {.unnumbered}
 
@@
 [@goerickePigmentsProchlorococcusMarinus1992] allowing *P. marinus* to
-efficiently harvestblue light in the 400 nm
+efficiently harvest blue light in the 400 nm
 to 500 nm range [@morelAvailableUsableStored1978] prevailing in deep ocean
@@
 
-## Photosystem II maintenance as a limitation on *Prochlorococcus* growth
+## Photosystem II maintenance as a limitation on *Prochlorococcus* growth {.unnumbered}
 
@@
 MIT9313 at 30 µmol photons m^-2^ s^-1^. To maintain active growth all strains were
-transferred weekly with XX to YY dilution with Pro99 media
+transferred weekly with 1 to 5 dilution with Pro99 media
 [@mooreCulturingMarineCyanobacterium2007] prepared with autoclaved artificial
@@
 
-Controlled growth experiments were performed using PSI Multicultivators (Figure \@ref(fig:LabeledMC); MCMIX-OD orMC1000-OD, Brno, Czech Republic ).
+Controlled growth experiments were performed using PSI Multicultivators (Figure \@ref(fig:LabeledMC); MCMIX-OD or MC1000-OD, Brno, Czech Republic ).
 Each multicultivator individually controls 8 tubes at a common temperature of 22°C.
@@
 
-In situ XXXXItalicsXXX measurements of Optical Density (OD) 680 nm, a proxy for cell suspension density, cell size dependent scatter and cell chlorophyll content;  and OD 720 nm, a proxy for cell suspension density and cell size dependent scatter, were recorded every 5 minutes over least 8 to 14 days,  depending on the
+*In situ* measurements of Optical Density (OD) 680 nm, a proxy for cell suspension density, cell size dependent scatter and cell chlorophyll content;  and OD 720 nm, a proxy for cell suspension density and cell size dependent scatter, were recorded every 5 minutes over least 8 to 14 days,  depending on the
 duration of the lag phase, if any. All data from the Multicultivator were saved
@@
 PAR of 180, 90 or 30 µmol photons m^-2^ s^-1^, and spectral wavebands (white LED
-full spectrum, 660 nm, 530 nm, and 450 nm) were chosen to approximate light
+full spectrum, 660 nm, and 450 nm) were chosen to approximate light
 levels and spectral colors spanning the vertical ocean water column, from
@@
 
-### Estimation of Photosynthetically Usable Radiation
-
-XXXXTEXT NEEDEDXXXX
+### Estimation of Photosynthetically Usable Radiation {.unnumbered}
+
+To calculate the Photosynthetic Usable Radiation (PUR), a proxy of photons absorbed, for each ecotype
+of *P. marinus*, the imposed Photosynthetic Active
+Radiation (PAR) was first determined. An emission profile of each colored LED
+light of the MCMIX-OD Multicultivator and the white LED light of the MC1000-OD Multicultivator was obtained using a Jaz spectrometer (Ocean Optics, Inc.,Dunedin FL, USA) equipped with a fiber
+optic cable, HH2 FiberOpticJmp (Part number A901073, Malvern Panalytical
+Ltd, Malvern, UK) and scanned to measure the emission wavelengths from 200 nm to 1000 nm.
+Following the determination of PAR, an *in-vivo* whole cell absorbance spectrum for each *P.
+marinus* was obtained using the Olis 14 UV/VIS Clarity
+Spectrophotometer (Olis Inc, Bogart, Georgia) by scanning across the visible spectral range of λ = 350 nm to 750 nm at 1 nm intervals.
+A whole cell absorbance spectrum was measured for each strain under each imposed spectral waveband.
+The 20 cm path length of the internally reflective cavity of the Olis spectrophotometer was corrected to a 1 cm path length using the Javorfi correction method [@javorfiQuantitativeSpectrophotometryUsing2006] on a PRO 99 media subtracted whole cell absorbance spectra of each strain.
+
+A weighted PUR spectrum was determined by applying an integrated weighted function to the blank subtracted, whole cell absorbance spectrum for each *P.
+marinus* ecotype and the emission spectrum of the imposed LED growth light [@morelAvailableUsableStored1978].
+The whole cell absorbance spectrum was normalized to the absorbance maximum of divinylchlorophyll a (Chl a~2~), determined dynamically between 400 nm and 460 nm, and each LED spectrum was normalized to the emission maximum.
+
+Equation \@ref(eq:WeightedPUR) was used to determine the weighted PUR spectrum P(λ) according to [@morelAvailableUsableStored1978],
+
+\begin{equation}
+  P(λ) = A(λ) × E(λ) 
+  (\#eq:WeightedPUR)
+\end{equation}
+
+where P(λ) is the weighted PUR absorbance spectrum over 400 nm to 700 nm spectral range, A(λ) is the Chl a~2~ normalized whole cell absorbance spectrum over 400 nm to 700 nm and E(λ) is the imposed growth light emission spectrum over 400 nm to 700 nm.
+
+Actinic absorbed PUR levels (µmol photons m^-2^ s^-1^) were calculated from actinic PAR (µmol photons m^-2^ s^-1^) levels using the equation \@ref(eq:PUR) from [@morelAvailableUsableStored1978],
+
+\begin{equation}
+  PUR = \frac{\int_{400}^{700} P(λ)}{\int_{400}^{700} E(λ)} × PAR
+  (\#eq:PUR)
+\end{equation}
+
+where P(λ) is the weighted PUR absorbance spectrum from equation \@ref(eq:WeightedPUR), E(λ) is the imposed growth light emission spectrum from equation \@ref(eq:WeightedPUR) and PAR is the imposed light level (µmol photons m^-2^ s^-1^).
+Figure (\@ref(fig:PurParPlot)) shows the calculated absorbed PUR (µmol photons m^-2^ d^-1^) versus imposed actinic PAR (µmol photons m^-2^ s^-1^) for each strain and each spectral waveband (nm).
+
+The applied photoperiod was administered using a sinusoidal function to simulate light levels equivalent to sun rise and sunset.
+The area under a sine curve is equivalent to a triangle, therefore the equation to determine the cumulative diel absorbed PUR (µmol photons m^-2^ d^-1^) is one half of the base (photoperiod) multiplied by the height (PUR) equation \@ref(eq:SumPURDay).
+
+\begin{equation}
+  Cumulative diel absorbed PUR = \frac{PUR × 3600 × Photoperiod}{2}
+  (\#eq:SumPURDay)
+\end{equation}
+
+where PUR is the actinic absorbed light calculated from equation \@ref(eq:PUR) (µmol photons m^-2^ s^-1^), 3600 is the time conversion from seconds to hour and photoperiod is the imposed photoperiod (h).
+
 ```{r PurParPlot, fig.cap = PurParPlot_cap , fig.height = 20, fig.width = 10, echo = FALSE}
@@
 Evidence of proteins
-derived from HL ecotypes of *P. marinus* inOMZ at depths up to 200
+derived from HL ecotypes of *P. marinus* in OMZ at depths up to 200
 meters,  with O~2~ of 15 µM. The extent to which [O~2~] defines
@@
 
+### MED4 PAR and growth trends {.unnumbered}
+
+#### High oxygen environment {.unnumbered}
+
+The growth rate of MED4, from the high light (HLI) clade of *P.
+marinus*, increased with higher imposed PAR and longer photoperiods
+(Figure \@ref(fig:MED4PAR)), when grown under 250 µM O~2~. No growth was
+observed under any imposed conditions under a 4 h photoperiod. MED4 was
+able to grow under the lowest PAR treatment of 30 µmol photons m^-2^
+s^-1^ but only when the blue light photoperiod was longer than 4 h; the
+white LED light photoperiod was longer than 8 h; or when the red light
+photoperiod was longer than 16 h. Growth rate increased
+with increasing photoperiods for all spectral wavebands when exposed to
+PAR of 90 and 180 µmol photons m^-2^ s^-1^. MED4 grew fastest for each
+spectral waveband under 16 h photoperiods. The maximum growth rate
+(µ~max~) was
+`r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+d^-1^ achieved under 180 uE blue
+light and 16 h photoperiod.
+
+#### Intermediate oxygen environment {.unnumbered}
+
+Similar to the growth trends of the 250 µM O~2~ experiments, MED4
+maintained at 25 µM O~2~, showed the fastest growth rate when the
+photoperiod was 16 h for each spectral waveband, across PAR levels
+(Figure \@ref(fig:MED4PAR)). The 25 µM O~2~ growth experiments showed
+generally similar growth rate as the 250 µM O~2~ growth experiments,
+with the interesting exception that growth rates increased by 40% under
+25 µM O~2~ at PAR of 30 µmol photons m^-2^ s^-1^ and 16 h photoperiod,
+and even showed growth under 12 h red light photoperiod, in contrast to
+the 250 µM O~2~ growth experiments. White LED light treatments grew
+slower, if at all, under 25 µM O~2~, only growing under higher PAR of 90
+and 180 µmol photons m^-2^ s^-1^ and longer photoperiods of 12 and 16 h.
+As under 250 µM O~2~, the fastest growth rate observed for each spectral
+waveband at each imposed PAR were greatest under the 16 h photoperiod.
+The µ~max~ was
+`r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "25", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+d^-1^  achieved under 180 µmol photons
+m^-2^ s^-1^ blue light and 16 h photoperiod. The 4 h photoperiod
+experiments under white LED light were not performed because no growth
+was achieved when grown under an 8 h photoperiod.
+
+#### Low oxygen environment {.unnumbered}
+
+MED4 did not grow under any tested conditions sparged to the lowest O~2~
+of 2.5 µM (Figure \@ref(fig:MED4PAR)). 2.5 µM O~2~ growth experiments
+were not conducted for 4 and 16 h photoperiods, as no growth occurred
+when MED4 was exposed to 8 and 12 h photoperiods.
+
 \newpage
@@
 
+### SS120 PAR and growth trends {.unnumbered}
+
+#### High oxygen environment {.unnumbered}
+
+The growth rate of SS120, from the low light (LLIII) clade of *P.
+marinus*, increased with lower imposed PAR and longer photoperiods, when
+grown under 250 µM O~2~ (Figure \@ref(fig:SS120PAR)). SS120 was able to
+grow under the lowest PAR treatment of 30 µmol photons m^-2^ s^-1^ but
+only when the photoperiod was longer than 4 h under blue, white, and red
+light. SS120 required longer than 8 h photoperiod of imposed green
+light. No growth was observed under any blue light photoperiods when
+exposed to PAR of 90 µmol photons m^-2^ s^-1^. Growth rate increased
+with increasing photoperiods for white, red and green light when exposed
+to PAR of 90 µmol photons m^-2^ s^-1^; however, no growth was observed
+when the red light photoperiod was 16 h. Experiments conducted under PAR
+of 180 µmol photons m^-2^ s^-1^ showed no growth under imposed blue and
+red lights. Growth rate decreased with longer photoperiods and showed
+growth inhibition at 12 and 16 h photoperiods under PAR of 180 µmol
+photons m^-2^ s^-1^ and white LED light. The growth rate generally
+increased with longer photoperiods under green light treatments, however
+no growth was observed under the 8 h photoperiod. The µ~max~ was
+`r PURPARFits %>% filter(Strain == "SS120", WL == "WW", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+d^-1^  achieved under 90 µmol photons
+m^-2^ s^-1^ white LED light and 16 h photoperiod.
+
+#### Intermediate oxygen environment {.unnumbered}
+
+Similar to the growth trends of the 250 µM O~2~ and PAR of 30 µmol
+photons m^-2^ s^-1^ experiments, SS120 maintained at 25 µM O~2~, no
+growth was observed under a 4 h photoperiod for imposed red spectral
+waveband, however under blue light, SS120 was able to grow (Figure
+\@ref(fig:SS120PAR)). In contrast to the growth trends of the 250 µM
+O~2~ and PAR of 90 µmol photons m^-2^ s^-1^ experiments, SS120 grew
+under 4 and 8 h blue light and 16 h red light photoperiods. The growth
+rate decreased with increasing photoperiod under PAR of 90 µmol photons
+m^-2^ s^-1^ white LED light treatments. Blue light treatments under PAR
+of 180 µmol photons m^-2^ s^-1^ showed growth only under an 8 h
+photoperiod. This growth rate decreased by 53% compared to the 8 h blue
+light photoperiod under PAR of 90 µmol photons m^-2^ s^-1^. The µ~max~
+was
+`r PURPARFits %>% filter(Strain == "SS120", WL == "450", O2_uM == "25", Photoperiod == 8) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+d^-1^ (Table. \@ref(tab:MaxGrowthTable)) achieved under 90 µmol photons
+m^-2^ s^-1^ blue light and 8 h photoperiod.
+
+The 25 µM O~2~, less than 16 h photoperiod and 180 µmol photons m^-2^ s^-1^ experiments under white LED
+light were not performed due to time constraints.
+
+#### Low oxygen environment {.unnumbered}
+
+SS120 only grew
+(`r PURPARFits %>% filter(Strain == "SS120", WL == "660", O2_uM == "2.5", Photoperiod == 12) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+d^-1^) under PAR of 30 µmol photons m^-2^ s^-1^ and 12 h red light
+photoperiod when sparged to the lowest O~2~ of 2.5 µM (Figure
+\@ref(fig:SS120PAR)). SS120 did not grow under any other tested
+conditions. 2.5 µM O~2~ growth experiments were not conducted for 4 and
+16 h photoperiods under PAR of 180 µmol photons m^-2^ s^-1^, as no
+growth occurred when SS120 was exposed to 8 and 12 h photoperiods. Red
+light 16 h photoperiod experiments were not performed due to time
+constraints.
+
+\newpage
+
 ```{r SS120PAR, fig.cap = SS120PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}
@@
 \newpage
+### MIT9313 PAR results {.unnumbered}
+
+#### High oxygen environment {.unnumbered}
+
+The growth rate of MIT9313, from the low light (LLIV) clade of *P.
+marinus*, increased with low to moderate imposed PAR and longer
+photoperiods, when grown under 250 µM O~2~ (Figure
+\@ref(fig:MIT9313PAR)). Growth rate increased with increasing
+photoperiods under the lowest PAR treatment of 30 µmol photons m^-2^
+s^-1^ for blue, white LED and red light. The green light treatment
+showed growth only when the photoperiod was longer than 12 h and
+decreased by \~ 50% under a 16 h photoperiod. Under PAR of 90 µmol
+photons m^-2^ s^-1^, growth rate increased with longer photoperiods for
+white LED, red, and green light treatments. Growth rates decreased from
+4 to 8 h blue light photoperiod and exhibited no growth under
+photoperiods of 12 and 16 h. Blue light did not induce growth at 180
+µmol photons m^-2^ s^-1^ under any photoperiod; white LED and red light
+treatments only exhibited growth under the 8 h photoperiod and growth
+rates increased with longer photoperiods under green light. The µ~max~
+was
+`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+d^-1^ achieved under 30 µmol photons
+m^-2^ s^-1^ blue light and 16 h photoperiod.
+
+#### Intermediate oxygen environment {.unnumbered}
+
+Similar to the growth trends of the 250 µM O~2~ and PAR of 30 µmol
+photons m^-2^ s^-1^ experiments, MIT9313 maintained at 25 µM O~2~,
+growth rate increased with increasing photoperiods for all spectral
+wavebands tested (Figure \@ref(fig:MIT9313PAR)). The 25 µM O~2~ growth
+experiments showed generally similar growth rate as the 250 µM O~2~ and
+PAR of 30 µmol photons m^-2^ s^-1^, with the interesting exception that
+the growth rate increased by 50% under 25 µM O~2~ and 16 h blue light
+photoperiod. In contrast to the blue light growth responses under 250 µM
+O~2~ and PAR of 90 µmol photons m^-2^ s^-1^, growth rate increased with
+longer photoperiods and even grew under 12 and 16 h photoperiods. In
+fact, the fastest growth rate of all the O~2~ experiments was
+`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "25", Photoperiod == 16, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+d^-1^ achieved under 16 h blue light
+photoperiod and PAR of 90 µmol photons m^-2^ s^-1^ under 25 µM O~2~.
+Growth rate increased by 50% under the 4 h blue light photoperiod; by
+400% under the 8 h blue light photoperiod; by 40% under the 12 h red
+light photoperiod and by 80% under the 16 h white LED photoperiod,
+compared to the 250 µM O~2~ and PAR of 90 µmol photons m^-2^ s^-1^
+growth experiments. In contrast to the 250 µM O~2~ growth experiments,
+MIT9313 was able to grow when exposed to PAR of 180 µmol photons m^-2^
+s^-1^ and blue light under all photoperiods except 16 h; additionally,
+white LED and red light treatments induced growth across all tested
+photoperiods under 25 µM O~2~.
+
+The 25 µM O~2~, 4 h photoperiod experiments under white LED light and
+all green light were not performed due to time constraints.
+
+#### Low oxygen environment {.unnumbered}
+
+The growth experiments under 2.5 µM O~2~ for MIT9313 showed growth
+responses for all spectral wavebands except white LED light, albeit
+slower than under the 25 µM O~2~ experiments (Figure
+\@ref(fig:MIT9313PAR)). MIT9313 was able to grow under PAR of 30 µmol
+photons m^-2^ s^-1^ but only under an 8 h blue and red light
+photoperiod. Growth rate increased with longer photoperiods under blue
+light treatments and PAR of 90 µmol photons m^-2^ s^-1^ however, growth
+was inhibited under a 16 h blue light photoperiod and only grew under an
+8 h photoperiod under red and green light treatments. The growth rate
+for MIT9313 under PAR of 180 µmol photons m^-2^ s^-1^ and blue light
+treatment decreased with increasing photoperiods with growth inhibition
+under a 16 h photoperiod. The red light treatments under PAR of 180 µmol
+photons m^-2^ s^-1^ showed similar growth rate for 8 and 12 h
+photoperiods and no growth were observed for green light treatments. The
+µ~max~ was
+`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "2.5", Photoperiod == 4, Par_ue == 180) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+d^-1^ achieved under 4 h blue light
+photoperiod and PAR of 180 µmol photons m^-2^ s^-1^.
+
+The 2.5 µM O~2~ white LED treatments under 4, 8 and 16 h photoperiods
+and red light under 4 and 16 h photoperiods were not performed due to
+time constraints.
 
@@
 ```
+
+\newpage
+
+#### Generalized Additive Model (GAM) of MED4 growth {.unnumbered}
+
+XXX Fig letters do not match as now we have red GAMs. Below is results for Blue GAMsXXXX
+
+Due to the complex interactions of light level and photoperiod, a GAM
+was employed (Figure \@ref(fig:MED4GAM)) to model the growth trends
+of MED4 in response to changing blue and red light PAR and photoperiod, across
+the 3 different imposed oxygen concentrations. Under 250 µM O~2~, Figure
+\@ref(fig:MED4GAM)A showed that the fastest growth rates were
+achieved above 90 µmol photons m^-2^ s^-1^ and photoperiods greater than
+12 h, indicated by the contour line labeled 0.62 d^-1^ (representing the
+90^th^ percentile of achieved growth rate). Figure
+\@ref(fig:MED4GAM)A also illustrated that MED4 exploited all light
+levels as long as the photoperiods were longer than 4 h, albeit at
+slower growth rate at lower PAR and shorter photoperiods. Under 25 µM
+O~2~, MED4 grew, but required longer than 4 h photoperiod (Figure
+\@ref(fig:MED4GAM)B). Interestingly, the GAM illustrated no
+difference in growth rate when MED4 was grown under 25 µM or 250 µM O~2~
+with photoperiods greater than 12 h. Figure \@ref(fig:MED4GAM)C
+showed that MED4 did not grow under the tested conditions at 2.5 µM
+O~2~.
+
+\newpage
 
@@
 
+#### Generalized Additive Model (GAM) of SS120 growth {.unnumbered}
+
+XXX Fig letters do not match as now we have red GAMs. Below is results for Blue GAMsXXXX
+
+The GAM model in Figure \@ref(fig:SS120GAM) displays the growth
+trends of SS120 in response to changing blue light PAR and photoperiod,
+across the 3 different imposed oxygen concentrations. Under 250 µM O~2~,
+Figure \@ref(fig:SS120GAM)A illustrated that the fastest growth
+rates were achieved below PAR of 50 µmol photons m^-2^ s^-1^ and
+photoperiods between 8 and 12 h, indicated by the contour line labeled
+0.29 d^-1^ (representing the 90^th^ percentile of achieved growth rate).
+Figure \@ref(fig:SS120GAM)A also showed that SS120 does not grow at
+PAR above 90 µmol photons m^-2^ s^-1^ and the growth rate are slower as
+photoperiods go above 12 or below 8 h. Under 25 µM O~2~, SS120 grew
+under a photoperiod of 8 h and exploited all light levels and grew under
+a 12 h photoperiod but at PAR of 50 µmol photons m^-2^ s^-1^. The
+fastest growth rate achieved was at a higher PAR of \~100 µmol photons
+m^-2^ s^-1^, indicated by the contour line labeled 0.5 d^-1^
+(representing the 90^th^ percentile of achieved growth rate), out pacing
+the 90^th^ percentile fastest growth rates under 250 µM O~2~. Figure
+\@ref(fig:SS120GAM)C showed that SS120 did not grow under the tested
+conditions at 2.5 µM O~2~.
+
+\newpage
+
 ```{r SS120GAM,  fig.cap = SS120GAM_cap, fig.height = 10, fig.width = 10, echo = FALSE}
@@
 ```
+
+\newpage
+
+#### Generalized Additive Model (GAM) of MIT9313 growth {.unnumbered}
+
+XXX Fig letters do not match as now we have red GAMs. Below is results for Blue GAMsXXXX
+
+The GAM model in Figure \@ref(fig:MIT9313GAM) displays the growth
+trends of MIT9313 in response to changing blue light PAR and
+photoperiod, across the 3 different imposed oxygen concentrations. Under
+250 µM O~2~, Figure \@ref(fig:MIT9313GAM)A illustrated that the
+fastest growth rates were achieved between PAR of 30 µmol photons m^-2^
+s^-1^ and 50 µmol photons m^-2^ s^-1^ and photoperiods longer than 8 h,
+indicated by the contour line labeled 0.51 d^-1^ (representing the
+90^th^ percentile of achieved growth rates). Figure
+\@ref(fig:MIT9313GAM)A also illustrated that growth rate increases
+with longer photoperiods, as long as the PAR levels are below 50 µmol
+photons m^-2^ s^-1^ and that MIT9313 does not grow when exposed to PAR
+levels above 90 µmol photons m^-2^ s^-1^. In contrast to the 250 µM O~2~
+growth experiment, MIT9313 was able to exploit all actinic PAR levels
+(Figure \@ref(fig:MIT9313GAM)B). Interestingly, the growth rate was
+similar across all PAR levels between 4 and 12 h photoperiods, indicated
+by the contour line labeled 0.29 d^-1^ (representing the 10^th^
+percentile of achieved growth rate) and 0.44 d^-1^ (representing the
+50^th^ percentile of achieved growth rate) (Figure
+\@ref(fig:MIT9313GAM)B). However, for photoperiods exceeding 12 h,
+the growth rate showed a decline at higher PAR levels but showed the
+overall fastest growth rate achieved was at PAR levels less than 100
+µmol photons m^-2^ s^-1^, indicated by the contour line labeled 0.69
+d^-1^ (representing the 90^th^ percentile of achieved growth rate)
+(Figure \@ref(fig:MIT9313GAM)B). Figure \@ref(fig:MIT9313GAM)C
+showed that MIT9313 is capable of growing under 2.5 µM O~2~ as long as
+the photoperiod is between 4 and 8 h and between 50 to 150 µmol photons
+m^-2^ s^-1^ PAR levels (Figure \@ref(fig:MIT9313GAM)C).
 
@@
 ```
+
+\newpage
+
+## Discussion PAR and growth trends {.unnumbered}
+
+The purpose of this study was to determine the interactive effects of
+photoperiod, PAR level, spectral bandwidth and dissolved [O~2~] regimes
+on the growth of *P. marinus*, under simulated present day and
+hypothetical future ecological niches.
+
+### Photoperiod {.unnumbered}
+
+The representative of HLI clade, *P. marinus* MED4, was completely
+excluded from growth under the 4 h photoperiod, and then showed
+increasing growth rate with increasing photoperiod. Thus, MED4 can
+potentially exploit longer summer photoperiods in temperate zones, but
+will remain excluded from growth in winter through its requirement for
+more than 4 h of light per day.
+
+The LLIII clade, *P. marinus* SS120, grew under photoperiods longer than
+4 h and showed increasing growth rate with increasing photoperiods.
+Therefore, SS120 can potentially exploit the longer summer photoperiods
+in temperate zones but cannot sustain growth in winter through its
+requirement for more than 4 h of light per day.
+
+The LLIV clade, *P. marinus* MIT9313, exploited all tested photoperiods,
+and showed increasing growth rate with increasing photoperiods. Hence,
+MIT9313 can potentially inhabit temperate zones with shorter winter and
+longer summer photoperiods, and exploit habitats at depth subject to
+photoperiod attenuation.
+
+### PAR Levels {.unnumbered}
+
+The representative of HLI clade, *P. marinus* MED4, was able to grow
+under all PAR levels, so long as the photoperiod was longer than 4 h,
+although growth rate were slower under the lowest PAR level of 30 µmol
+photons m^-2^ s^-1^. Considering the range of PAR levels that MED4 can
+utilize, it is reasonable to suggest that MED4 can inhabit not just
+shallow depths, where light levels are high, but also deeper regions
+characterized by lower light levels, subject to the limitation of a
+photoperiod of at least 4 h even after depth attenuation. The photo
+regimes of winter temperate zones, due to shorter photoperiods, exclude
+MED4 from growth at all depths, however temperate photoperiods and light
+levels for the remainder of the year are adequate to support growth.
+
+The LLIII clade, *P. marinus* SS120, grew under a PAR of 30 µmol photons
+m^-2^ s^-1^, and under some conditions at PAR of 90 µmol photons m^-2^
+s^-1^, but growth was generally inhibited under PAR of 180 µmol photons
+m^-2^ s^-1^. These findings align with the results reported by
+@mooreComparativePhysiologySynechococcus1995 and are expected for a low
+light clade. Given that SS120 can tolerate longer photoperiods and low
+PAR levels, the deep ocean temperate zones are a viable habitat but not
+during temperate winter due to shorter photoperiods.
+
+The LLIV clade, *P. marinus* MIT9313, sometimes grew under all PAR
+levels but generally exhibited slower growth rate under PAR of 180 µmol
+photons m^-2^ s^-1^ and then only under some conditions. MIT9313 is well
+suited to inhabit the deep ocean in temperate zones with wide tolerance
+for photoperiod yet can also tolerate depths closer to the surface
+through its partial tolerance of higher PAR levels.
+
+### Spectral Waveband {.unnumbered}
+
+The representative of HLI clade, *P. marinus* MED4, grew under all
+spectral wavebands, but grew slower under green light. Growth rates were
+generally comparable under blue, white LED and red lights when exposed
+to PAR levels greater than 30 µmol photons m^-2^ s^-1^ for each
+photoperiod. At the lower PAR of 30 µmol photons m^-2^ s^-1^, MED4 grew
+better under blue light. All growth rates for each spectral waveband
+increased with increasing photoperiod. The ability to utilize all
+spectral wavebands at high PAR levels and longer photoperiods make the
+near surface temperate zones available niches for MED4. MED4 ability to
+exploit blue light under low PAR levels and variable photoperiods
+greater than 4 h allow MED4 to exploit deeper regions in these temperate
+zones, where blue light prevails.
+
+The LLIII clade, *P. marinus* SS120 and the LLIV clade, *P. marinus*
+MIT9313, exhibited different growth responses to spectral wavebands
+under varying O~2~ conditions, as such, this section will address the
+growth response under 250 µM O~2~ experiments, while the interactions of
+spectral wavebands under all O~2~ treatments will be discussed in the
+next section. SS120, grew under all spectral wavebands at a PAR of 30
+µmol photons m^-2^ s^-1^. Growth was completely inhibited under blue
+light at PAR levels of 90 and 180 µmol photons m^-2^ s^-1^, but growth
+occurred at PAR of 90 µmol photons m^-2^ s^-1^ under all other spectral
+wavebands. Generally, growth was strongly inhibited under PAR of 180
+µmol photons m^-2^ s^-1^ for all spectral wavebands except for green 16
+h photoperiod. The ability of SS120 to grow under low blue light and
+longer photoperiods, makes the deep ocean waters of the temperate zone a
+viable potential habitat. SS120 is constrained to deeper ocean waters
+through its intolerance of higher blue PAR levels.
+
+The LLIV clade, *P. marinus* MIT9313, grew under all spectral wavebands
+when exposed to PAR of 30 µmol photons m^-2^ s^-1^ and 90 µmol photons
+m^-2^ s^-1^ and was even able to grow under PAR of 180 µmol photons
+m^-2^ s^-1^ for all spectral wavebands except blue light. MIT9313 can
+thus exploit blue light in deep waters of temperate zones and can even
+tolerate moderate depths to exploit higher blue light levels, as long as
+the photoperiod is shorter than 12 h.
+
+### Oxygen {.unnumbered}
+
+The representative of HLI clade, *P. marinus* MED4, was able to grow
+under both 250 µM and 25 µM O~2~ treatments but was unable to grow under
+the lowest O~2~ level of 2.5 µM. MED4 generally exhibited similar growth
+response trends and growth rate under blue and red light treatments
+under both 25 µM and 250 µM of O~2~. This demonstrated ability to grow
+under 25 µM O~2~, coupled with its ability to grow under lower PAR
+levels, enables MED4 to potentially inhabit deeper regions where [O~2~]
+may vary and low blue light is present, as long as the photoperiod
+exceeds 4 h. Our findings are supported by the analysis of TARA Oceans
+Project data conducted by @delmontLinkingPangenomesMetagenomes2018 who
+reported the presence of *P. marinus* MED4-like genomes at depths
+ranging from 5 m to 90 m, representing high to low blue light levels, in
+the Pacific South East Ocean. @delmontLinkingPangenomesMetagenomes2018
+did not analyze data from depths beyond the subsurface chlorophyll
+maximum layer, the layer in the water column where the chlorophyll a
+concentration peaks, nor did they report the [O~2~] at those depths but
+we have shown, in this study, that MED4 can potentially grow in these
+regions. Our findings were also consistent with
+@mattisonPhotosyntheticStrategiesWild2020 who analyzed the OceansMap
+Protein Portal (OPP) [@saitoDevelopmentOceanProtein2021] for proteins
+expressed by vertically stratified *P. marinus* strains at varying
+depths and [O~2~], in the ocean minimal zone of the tropical North
+Pacific Ocean, and found PSII proteins annotated as MED4 expressed at
+depths up to 200 meters with O~2~ of 15 µM.
+
+The LLIII clade, *P. marinus* SS120, was able to grow under both 250 µM
+and 25 µM O~2~ treatments but only grew under 2.5 µM O~2~ with a red
+light photoperiod of 12 h. The growth responses under 250 µM and 25 µM
+O~2~ were very different under the higher PAR level treatments. As
+discussed in the spectral waveband section, SS120 did not grow when
+treated with 250 µM O~2~ under PAR of 90 and 180 µmol photons m^-2^
+s^-1^ blue light. However, SS120 did grow under the lower O~2~ of 25 µM,
+photoperiods of 4 and 8 h and PAR of 90 µmol photons m^-2^ s^-1^ blue
+light and photoperiods of 8 h and PAR of 180 µmol photons m^-2^ s^-1^
+blue light. Under 25 µM O~2~, SS120 grew under all tested white LED
+treatments however, did not grow under PAR of 30 µmol photons m^-2^
+s^-1^ and 4 h red light photoperiod nor under photoperiods longer than 8
+h when treated with PAR of 180 µmol photons m^-2^ s^-1^ red light.
+Beyond photoregimes expected of the deep ocean temperate zone waters,
+characterized by low levels of blue light and extended photoperiods,
+SS120 can also exploit regions closer to the surface where blue light
+PAR levels are higher, provided that the [O~2~] are low, as in the OMZ.
+Our laboratory results support field observations reported by
+@lavinNovelLineagesProchlorococcus2010 who found evidence of LLII/III
+and LLIV ecotypes, using terminal restriction fragment length
+polymorphism analyses, at depths above 40 m where light levels are
+higher in the OMZ. @mattisonPhotosyntheticStrategiesWild2020 found PSII
+protein subunits annotated as derived from SS120 at all depths ranging
+from 20 to 200 m and all [O~2~] in the oxygen minimal zone of the
+tropical North Pacific Ocean.
+
+The LLIV clade, *P. marinus* MIT9313, showed enhanced growth responses
+under the 25 µM O~2~ treatments for all tested spectral wavebands and
+even grew under the highest PAR level of 180 µmol photons m^-2^ s^-1^,
+in contrast to growth inhibition under 250 µM O~2~ and 180 µmol photons
+m^-2^ s^-1^. Most impressively, MIT9313 has the capacity to grow just as
+well, and in some conditions, even better, under high PAR levels of 90
+and 180 µmol photons m^-2^ s^-1^, as compared to the lowest PAR of 30
+µmol photons m^-2^ s^-1^, when treated with the lower O~2~ of 25 µM, for
+all spectral wavebands tested. Interestingly, while generally the growth
+rate were slower under the lowest imposed O~2~ of 2.5 µM compared to
+O~2~ of 25 µM, MIT9313 was able to grow under all blue light with
+photoperiods up to 12 h, along with growth under 2.5 µM O~2~ and some
+combinations of red and green light, across photoperiods. Given that
+MIT9313 can grow under all photoperiods at the lowest blue light PAR of
+30 µmol photons m^-2^ s^-1^, all seasons in the temperate zones are
+potentially viable niches. Like SS120, MIT9313 has the capability to
+exploit different ocean water layers through its tolerance of higher
+light levels under lower [O~2~]. MIT9313 has a remarkable ability to
+thrive under very low [O~2~], potentially allowing it to expand into
+broader ecological niches. These results support the findings of
+@mattisonPhotosyntheticStrategiesWild2020 where PSI protein subunits
+annotated as derived from MIT9313 were detected at depths \> 120 m,
+along with PSII subunits at depths from 50 m to 200 m in regions where
+O~2~ was 15 µM.
+
+Under the 250 µM O~2~ growth experiments and under some photoperiods,
+when subjected to the highest PAR of 180 µmol photons m^-2^ s^-1^,
+MIT9313 grew when treated under white LED, red and green light and SS120
+grew under white LED and green light treatments. However, neither of
+these strains exhibited any growth under blue light conditions. Growth
+studies have demonstrated that LL clades experience growth inhibition at
+PAR levels between 150 and 200 µmol photons m^-2^ s^-1^
+[@moorePhotophysiologyMarineCyanobacterium1999]. In the subsequent
+chapter, we explore the physiological factors contributing to these
+divergent growth responses to different spectral wavebands.
+
+Our growth rate maximums under white LED and 250 µM O~2~, for MED4,
+`r PURPARFits %>% filter(Strain == "MED4", WL == "WW", O2_uM == "250") %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+d^-1^ and SS120,
+`r PURPARFits %>% filter(Strain == "SS120", WL == "WW", O2_uM == "250") %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+d^-1^, compare well with @mooreComparativePhysiologySynechococcus1995,
+who found white light saturated growth rate maximums of 0.63 ± 0.06
+d^-1^ and 0.53 ± 0.06 d^-1^ for MED4 and SS120, respectively.
+
+For each strain of *P. marinus*, Table \@ref(tab:NichesTable) provides a
+summary of our findings for potential temperate growth niches, as
+defined by photoperiod, light level and oxygen level, characteristic of
+different seasons, depths, and oxygen zones. The potential for niche
+expansion into temperate regions by *P. marinus* varies depending on the
+season, which influences achieved underwater photoperiods and light
+levels. Temperate summer delivers 11 hours of blue waveband light
+underwater, above the photic threshold of 20 µmol photons m^-2^ s^-1^,
+while temperate spring/fall delivers 8 hours of blue waveband light
+underwater, photoperiod ranges which are permissive for growth of all
+three *P. marinus*. In contrast temperate winter delivers only about 2 h
+of blue waveband light underwater above the photic threshold (Figure \@ref(fig:CardinalSeasons)), which
+precludes growth of MED4 and SS120, even if winter waters reached
+permissive temperatures. MIT9313 and SS120 will be excluded from
+near-surface growth niches by high PAR, unless OMZ zones extend to the
+near surface.
+
+\newpage
+
+### Results PUR and growth trends {.unnumbered}
+
+Cumulative diel absorbed PUR can potentially collapse photoperiod, PAR and spectral wavebands to a common metric of absorbed light.
+We then plot observed growth rate vs.
+cumulative diel absorbed PUR to determine whether growth is a simple response to absorbed light per day across imposed photoperiods and spectral wavebands, or whether photoperiod or spectral wavebands have specific or interactive influences on growth of each ecotype.
+Cumulative daily absorbed PUR dose (µmol photons m^-2^ d^-1^) was calculated from the imposed absorbed PUR (µmol photons m^-2^ s^-1^) and photoperiod (h).
+
+Due to the highly effective absorption of pigments in the blue spectral waveband range for all ecotypes, the maximum imposed cumulative diel absorbed PUR under blue light treatment is almost 3 times that of white LED light and about 6 times the red light treatment, despite being derived from the same imposed photoperiods and PUR regimes.
+As such, only growths rates treated under blue light extend beyond absorbed PUR of ~ 2 x 10^6^ µmol photons m^-2^ d^-1^.
+A full list of cumulative diel absorbed PUR (µmol photons m^-2^ d^-1^) for all imposed spectral wavebands, PAR and photoperiod regimes can be found in Table \@ref(tab:DailyPURTable).
+
+#### MED4 {.unnumbered}
+
+The representative of HLI clade, *P. marinus* MED4, showed no growth under any 4 h photoperiod treatments, even when a 4 h photoperiod delivered cumulative die
+equivalent to other photoperiod treatments.
+In parallel MED4 showed no growth under 2.5 µM O~2~, under the same level of diel cumulative absorbed PUR. 
+In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 showed a simple saturating response of growth to increasing cumulative diel absorbed PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:AllStrainPurFitsPlots)A).
+
+#### SS120 {.unnumbered}
+
+The representative of the LLIII clade, *P.
+marinus* SS120 showed almost no growth under 2.5 µM O~2~ experiments.
+A majority of the 4 h photoperiod treatments did not grow under 250 µM O~2~ experiments despite having the same absorbed PUR dose as other experimental treatments.
+SS120 did not grow when exposed to more than about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of absorbed PUR under any spectral waveband or photoperiod combination under 250 µM O~2~ experiments(Figure \@ref(fig:AllStrainPurFitsPlots)B).
+
+Under both 25 or 250 µM O~2~ experiments, SS120 growth plateaued by about 5.0 x 10^5^ µmol photons m^-2^ d^-1^, with some scatter among photoperiod and spectral waveband regimes.
+The onset of growth inhibition extended to higher cumulative diel absorbed PUR for cultures growing under 25 µM O~2~.
+
+#### MIT9313  {.unnumbered}
+
+The LLIV clade, *P.
+marinus* MIT9313, showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of absorbed PUR, with higher growth rate at over a narrower plateau under 25 and 250 µM O~2~, compared to a wider, flatter response to cumulative diel absorbed PUR under 2.5 µM O~2~.
+Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of absorbed PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands.
+In contrast, under 25 µM O~2~, MIT9313 showed a greatly extended exploitation of higher cumulative diel absorbed PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^.
+Similarly, under 2.5 µM O~2~, MIT9313 grew more slowly, but only showed full growth inhibition above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Figure \@ref(fig:AllStrainPurFitsPlots)C).
+
+## Discussion PUR and growth trends {.unnumbered}
+
+The absorption maxima of Chl a~2~ and Chl b~2~ are 442 nm and 478 nm, respectively [@goerickePigmentsProchlorococcusMarinus1992].
+At these spectral wavelengths, *P.
+marinus* efficiently harvests the light energy present in the blue and green waveband range, 400 nm to 525 nm [@morelAvailableUsableStored1978] that penetrates the deep ocean waters.
+The high Chl a~2~/Chl b~2~ ratio we observed for MED4 is characteristic of the HL clades and the lower Chl a~2~/Chl b~2~ ratios we observed for SS120 and MIT9313 are typical of the LL clades [@moorePhotophysiologyMarineCyanobacterium1999].
+The lower amounts of  absorbed PUR in the white LED and green waveband regions for MED4, in comparison to SS120 and MIT9313, are the result of higher Chl a~2~/Chl b~2~ content.
+Subsequently, calculating absorbed PUR allows direct and meaningful comparison of the energy absorbed by cells on a per photon basis across different wavebands.
+
+In the previous chapter, under 250 µM O~2~ treatments and all PAR of 90 and 180 µmol photons m^-2^ s^-1^ blue light treatments, *P.
+marinus* SS120, exhibited growth inhibition but was able to exploit all other spectral wavebands under some photoperiods at these PAR levels.
+Similarly, *P.
+marinus* MIT9313, showed complete growth inhibition under all PAR 180 µmol photons m^-2^ s^-1^ blue light treatments and only grew under a 90 µmol photons m^-2^ s^-1^, 4 and 8 h blue light photoperiods, yet was able to grow under all other spectral wavebands to varying degrees at these PAR levels.
+This inhibition initially suggested that blue wavebands triggered photoinhibition at significantly lower levels of Photosynthetically Active Radiation (PAR) compared to other spectral wavebands.
+However, considering the equivalent cumulative diel absorbed PUR of the blue waveband, all treatments including blue, white LED, red and green waveband exhibited approximately the same growth saturation.
+
+*Prochlorococcus marinus* MED4 has a physiological requirement for more than 4 h of light per day, and thus this strain will not exploit habitats with short photoperiods.
+MED4 is also excluded from the lowest oxygen habitats, equivalent to our 2.5 µM O~2~ experimental conditions; however, MED4 can inhabit regions with slightly higher O~2~, as was demonstrated by the growth responses observed under our 25 µM O~2~ experiments.
+
+*Prochlorococcus marinus* SS120, categorized as a LLIII clade representative, showed an interactive growth inhibition between oxygen and cumulative diel absorbed PUR, with a higher tolerance for higher cumulative diel absorbed PUR under 25 µM O~2~, compared to 250 µM O~2~.
+Thus, SS120 can exploit habitats with O~2~ levels spanning 25 µM O~2~ to 250 µM O~2~.
+
+*Prochlorococcus marinus* MIT9313 is categorized as a LLIV clade representative, but under 25 or 2.5 µM O~2~, MIT9313 can actually exploit cumulative diel absorbed PUR comparably to *P.
+marinus* HLI clade MED4.
+Therefore, lower oxygen habitats extending to near the surface could potentially be exploited by MIT9313.
+
+*Prochlorococcus* are highly susceptible to hydrogen peroxide (H~2~O~2~) toxicity as they lack genes which scavenge H~2~O~2~ molecules [@morrisFacilitationRobustGrowth2008].
+The small cell size of *Prochlorococcus* allow the reactive oxygen species (ROS), H~2~O~2~, to cross the cell membrane; however, the accumulation of extracellular H~2~O~2~ can also be toxic to *Prochlorococcus* [@morrisFacilitationRobustGrowth2008].
+In the marine environment and in isolated cultures, @morrisDependenceCyanobacteriumProchlorococcus2011 showed that *Prochlorococcus* rely on catalase-positive heterotrophs to scavenge H~2~O~2~.
+Beyond the scope of our study, the three *Prochlorococcus* strains we examined were likely accompanied by different communities of co-occurring heterotrophs which could confer differential protection against reactive oxygen species [@zinserCrossprotectionHydrogenPeroxide2018a; @zinserMicrobialContributionReactive2018].
+
+Furthermore, our data might support suggestive patterns of enhanced growth under conditions of low cumulative diel absorbed PUR and 660 nm (red) spectral bandwidth, as supported by [@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue wavebands.
+
+## Discussion from Mireille' Thesis General Discussion section {.unnumbered}
+
+@flombaumPresentFutureGlobal2013 modeled a 29% increase of net cell abundance of *Prochlorococcus* by the end of this century and predicts that there will be poleward latitudinal shifts of at least 10° in marine phytoplankton habitats.
+Consequently, *P.
+marinus* will encounter new combinations of photoperiod, seasonal patterns, and altered spectral regimes as they move towards the poles, where solar incidence angles are lower and photoperiod seasonality is more pronounced [@bartonAnthropogenicClimateChange2016].
+The predicted poleward shifts of  *P.
+marinus* niches and the estimated increase in their cell abundances was modeled using climate model projections of sea surface temperatures and greenhouse gases equivalent to 650 ppm CO~2~ for the end of this century [@flombaumPresentFutureGlobal2013].
+While these models suggest that *P.
+marinus* could hypothetically expand into poleward regions by the end of this century, it remains uncertain whether *P.
+marinus* can actually tolerate the longer, and shorter, day lengths of temperate region seasons.
+To our knowledge, no other study has as yet addressed *P.
+marinus* growth responses in relation to a wide range of photoperiods.
+
+The lack of photoperiod growth studies is not surprising, given that higher cell abundances of *P.
+marinus* are currently  concentrated between 30°N and 30°S.
+At 30°N, the photoperiod seasonality ranges from 12 to 14 hours at the ocean surface between the winter and summer solstices, while it remains consistently 12 hours throughout the year at the equator.
+Therefore, growth response studies to date have generally been conducted under either a 12 or 14 hour (h) photoperiod.
+However, the photoperiod at the ocean surface is not fully representative of the photoperiod underwater, as solar radiation is reflected off the surface when the solar incident angle is less than 20°.
+This discrepancy between the duration of daylight hours above water and the effective duration of light exposure underwater is often overlooked in the experimental design of *P.
+marinus* growth studies, even when considering photoperiod.
+
+Current niches of *P. marinus* span across vertical ocean water columns
+[@chisholmNovelFreelivingProchlorophyte1988; @veldhuisVerticalDistributionPigment1990; @partenskyProchlorococcusMarinePhotosynthetic1999] and extend into regions with varying dissolved oxygen concentrations
+[@partenskyProchlorococcusAdvantagesLimits2010; @goerickeNovelNicheProchlorococcus2000] and even into anoxic oceans [@lavinNovelLineagesProchlorococcus2010], [@ulloaCyanobacteriumProchlorococcusHas2021; @garcia-robledoCrypticOxygenCycling2017a].
+Climate change is drastically altering the dissolved oxygen concentrations ([O~2~]) of our ocean waters.
+Research indicates that the oxygen minimum zones (OMZs) in the Pacific and Indian Oceans are expanding [@garcia-sotoOverviewOceanClimate2021; @buseckeDivergingFatesPacific2022] and that the levels of dissolved oxygen (O~2~) in our global oceans are generally decreasing [@matearLongtermChangesDissolved2003; @garcia-sotoOverviewOceanClimate2021], with significant decreases observed toward the poles [@helmObservedDecreasesOxygen2011].
+
+In chapter 2, we analyzed  growth rates to determine the viability of *P. marinus* MED4, a clade HLI ecotype found at depths near the ocean surface,
+*P.
+marinus* SS120, a clade LLIII ecotype found deep in the water column, and *P.
+marinus* MIT9313, a clade LLIV ecotype also found in deep oceans, under present day and hypothetical future niche conditions.
+We designed our study to account for light attenuation through ocean waters, recognizing that low light levels of the blue spectral waveband ultimately prevail in deep ocean waters [@morelAvailableUsableStored1978; @holtropVibrationalModesWater2021] and that the solar incidence angle also attenuates the photoperiod or hours of light exposure beneath the ocean surface.
+We also tested the growth response of *P.
+marinus* to varying [O~2~] under the matrix of light parameters to determine if *P.
+marinus* can cope with  diverse  ecosystem scenarios.
+
+We found that *P.
+marinus* MED4, can grow under near surface O~2~ saturation levels of 250 µM and high light levels, conditions representative of its current ecotype classification [@moorePhysiologyMolecularPhylogeny1998].
+MED4 can also grow under O~2~ of 25 µM, and under all tested levels of light in the blue spectral waveband, so long as the photoperiod is longer than 4 h (Figure \@ref(fig:MED4PAR)).
+Consequently, MED4 can potentially inhabit different ecological niches through its ability to  exploit a wide range of light levels, from the surface to the deep ocean, along with varying levels of dissolved oxygen throughout the water column.
+These findings are supported by evidence of HL ecotype presence even in the OMZ [@mattisonPhotosyntheticStrategiesWild2020] and in deeper regions of the ocean [@mattisonPhotosyntheticStrategiesWild2020; @delmontLinkingPangenomesMetagenomes2018].
+With predicted future ocean warming [@wijffelsOceanTemperaturesChronicle2016], MED4 shows potential to harness the photoregimes prevalent in temperate spring, summer, and fall zones when the duration of blue spectral waveband in the water column exceeds 4 hours.
+
+*Prochlorococcus marinus* SS120 prefers the deeper ocean where blue spectral waveband dominates at low levels, through its demonstrated ability to exploit only the lowest blue spectral waveband levels PAR of 30 µmol photons m^-2^ s^-1^ under 250 µM O~2~.
+However, we found *P.
+marinus* SS120 can exploit more diverse ecological niches within the ocean layers, even in regions with high levels of blue spectral waveband,  but only under O~2~ of 25 µM (Figure \@ref(fig:SS120PAR)).
+@mattisonPhotosyntheticStrategiesWild2020 and @lavinNovelLineagesProchlorococcus2010 show evidence of LLIII ecotypes at varying depths from 20 to 200 m and under all [O~2~] in the oxygen minimum zone (OMZ) of the tropical North Pacific Ocean, illustrating its tolerance of high light levels under low O~2~.
+SS120 has the potential to thrive in deep temperate zones, specifically during the spring, summer, and fall seasons when the duration of daylight exceeds 4 h, if O~2~ are near surface saturation of about 250 µM.
+Under lower oxygen levels of 25 µM, SS120 can also exploit a 4 h photoperiod in the blue waveband, and thus has the potential to inhabit a warmed, deep, temperate region during the winter season.
+
+*Prochlorococcus marinus* MIT9313 shows the potential to inhabit future warmed temperate zones year-round, as it exhibits the ability to grow under a 4 h photoperiod.
+MIT9313 demonstrates an unexpected tolerance to higher light levels,  but only under low oxygen conditions of 25 µM and 2.5 µM (Figure \@ref(fig:MIT9313PAR)).
+The ability to utilize higher levels of blue spectral waveband under 25 µM or 2.5 µM O~2~ enables MIT9313 to grow in regions like the OMZ and even at depths closer to the surface.
+
+We found our experimental growth rates agreed with those from @mooreComparativePhysiologySynechococcus1995, grown under white LED and 250 µM O~2~.
+However, growth response studies are scarce for comparison, especially under varying [O~2~] and even under different spectral wavebands and photoperiods.
+As far as we know, our study is the first to analyze the interactive growth responses of *Prochlorococcus*  to varying [O~2~], spectral wavebands and photoperiods.
+
+The potential expansion of  *P.
+marinus*  polewards will contribute to the primary food base of an aquatic ecosystem that has already undergone changes in Canadian waters; commercial fish populations are shifting with new species immigrating  [@zellerCheungZellerPauly2011], endangered whales actively searching for food sources are becoming more prevalent [@meyer-gutbrodMarineSpeciesRange2018] and the white shark seasonal presence is increasing  either due to rising ocean temperatures or following marine prey [@bastienInconspicuousRecoveringNorthward2020].
+While the exact impact of the presence of *P.
+marinus*  on the species distribution of marine wildlife in Atlantic Canadian waters is unknown, there is little doubt that *Prochlorococcus* will play a significant role in shaping this distribution.
+The shifting dynamics of the aquatic ecosystem in the Atlantic Canadian waters may have consequences for our commercial fishing and shipping sectors, as adjustments to shipping routes and regulations are made to safeguard endangered whales.
+
+In chapter 3, we determined the Photosynthetic Usable Radiation (PUR), the portion of light radiation absorbed differentially by the pigments of the photosynthetic organism [@morelAvailableUsableStored1978] and expressed growth response in terms of cumulative diel PUR.
+We found that approximately 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of PUR is the maximum dosage that the representative LL clades, SS120 and MIT9313 can tolerate under 25 µM O~2~, in contrast to the representative HL clade, MED4 which exhibited growth saturation at the same cumulative diel PUR of 1.0 x 10^6^ µmol photons m^-2^ d^-1^.
+Growth under lower O~2~ allowed MIT9313 to substantially increase its exploitation of higher diel PUR.
+
+To gain insights into the variations we observed in growth responses across strains, particularly the responses to different oxygen levels [O~2~], we used a subset of the dataset of annotated phytoplankton genomes from @omarAnnotationGenesEncoding2023.
+This subset contains annotated phytoplankton gene sequences, with a focus on genes encoding enzymes involved in oxygen metabolism (Figure \@ref(fig:ProchlorococcusEnzymeKms)) or DNA repair (Figure \@ref(fig:DNARepairFig)).
+According to figure \@ref(fig:ProchlorococcusEnzymeKms), we see that *P.
+marinus* MED4 has the gene encoding ubiquinol oxidase (non electrogenic) enzyme, whereas SS120 and MIT9313 do not.
+The ubiquinol oxidase (non electrogenic) enzyme is involved in dissipating excess electrons [@InformationEC10] generated under high light exposure, thereby reducing stress on the electron transport system.
+The O~2~ substrate K~m~ value of approximately 25 µM  for ubiquinol oxidase  may explain why *P.
+marinus* MED4 can grow under 25 µM of O~2~ but not under 2.5 µM of O~2~, since growth under 2.5 µM of O~2~ would suppress use of ubiquinol oxidase to balance electron transport.
+The demonstrated ability of *P.
+marinus* MIT9313 to grow when exposed to high blue light under 2.5 µM and 25 µM O~2~ treatments may be explained by the presence of the gene encoding enzyme 2-hydroxy-acid oxidase (Figure \@ref(fig:ProchlorococcusEnzymeKms)).
+The enzyme 2-hydroxy-acid oxidase, with an O~2~ substrate K~m~ value of approximately 250 µM (Figure \@ref(fig:ProchlorococcusEnzymeKms)), catalyzes the reaction of 2-hydroxy acid with O~2~ to produce toxic hydrogen peroxide [@InformationEC15].
+We hypothesize that under our 250 µM O~2~ and high blue light experiments, *P.
+marinus* MIT9313 exhibited photoinhibition, resulting from the inactivation of PSII caused by the production of the reactive oxygen species, hydrogen peroxide.
+This inhibition was further compounded by the limited induced repair mechanism for PSII, due to the absence of FtsH 2 and 3  proteins in *P.
+marinus* MIT9313 [@bonisteelStrainSpecificDifferences2018].
+We hypothesize that under the conditions of our high light and 2.5 µM and 25 µM O~2~ experiments, the activity of the 2-hydroxy-acid oxidase enzyme is suppressed.
+As a result, the catalyzed production of hydrogen peroxide is inhibited, leading to minimal PSII damage, allowing MIT9313 to avoid photohibition and circumvent limitations on PSII repair.
+Figure \@ref(fig:ProchlorococcusEnzymeKms) also shows that *P.
+marinus* SS120 is the only tested ecotype to lack the pyridoxal 5'-phosphate synthase enzyme.
+The pyridoxal 5'-phosphate synthase enzyme is an important cofactor in the biosynthesis of vitamin B~6~ [@sangIdentificationPyridoxinePyridoxamine2007].
+Vitamin B~6~ is a potential antioxidant and can effectively quench singlet oxygen [@bilskiVitaminB6Pyridoxine2000].
+The absence of the pyridoxal 5'-phosphate synthase enzyme may explain why *P.
+marinus* SS120 does not grow as well as *P.
+marinus* MIT9313 when exposed to high light stress under 25 µM O~2~ and not at all under 2.5 µM O~2~.
+
+\newpage
+
+XXX ProchlorococcusEnzymeKms figure goes here XXX
+
+\newpage
+
+Figure \@ref(fig:DNARepairFig) displays the genes encoding DNA repair for the three *P.
+marinus* strains examined in this study.
+As expected,  *P.
+marinus* MED4 possesses the largest and most complete suite of genes encoding DNA repair enzymes, followed by *P.
+marinus* MIT9313.
+Conversely, *P.
+marinus* SS120 demonstrates the smallest genomic capacity for DNA repair.
+*Prochlorococcus marinus* MED4 was the only strain out of the three strains in this study to possess the gene encoding deoxyribodipyrimidine photolyase, which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003].
+*Prochlorococcus marinus* MED4 was also the only strain to possesses the gene encoding DNA ligase, which uses ATP as a cofactor for DNA repair.
+The absence of the genes encoding deoxyribodipyrimidine photolyase and DNA ligase (ATP) in *P.
+marinus* MIT9313 and *P.
+marinus* SS120 explains why these two strains cannot tolerate the high light levels found at the ocean surface where  *P.
+marinus* MED4 inhabits.
+
+\newpage
+
+XXX DNARepairFig goes here XXX
+
+\newpage
+
+@westNichePartitioningProchlorococcusPopulationsStratified1999 and
+@malmstromTemporalDynamicsProchlorococcus2010 found that decreased
+abundances of the LL ecotypes corresponded to increased depth of the
+surface mixed layer, which thus influences the vertical distribution of
+HL and LL ecotypes. @malmstromTemporalDynamicsProchlorococcus2010
+attributes the transport of LL ecotypes to the surface and exposure to
+photoinhibitory high light levels as the reason for low cell abundances.
+@westNichePartitioningProchlorococcusPopulationsStratified1999 found
+the depth of the mixed layer strongly influenced the depth transition
+from HL to LL ecotypes and that additional factors other than light
+levels may influence the variations in the upper and lower depth limits
+of these ecotypes. Based on our findings, we hypothesize that low cell abundances of LL ecotypes in the mixed layer is likely due to increased [O~2~] at
+those depths and it is [O~2~] that determines the prevalence of the LL
+ecotypes to certain depths, not necessarily the light level.
+
+We have demonstrated that *P.
+marinus*  can exploit the photoregimes of the temperate zone, both at the surface and deep in the water column.
+Additionally, we  confirmed that the *P.
+marinus* strains we tested can survive in significantly lower oxygen environments as is represented in the OMZ and that the LL ecotypes we tested can be labeled as HL strains in oxygen environments of 25 µM and as low as 2.5 µM in the case of MIT9313.
+@billerProchlorococcusStructureFunction2015 has described *Prochlorococcus* as a 'federation' of diverse cells through their extensive genomic and phenotypic diversity.
+They underscore the importance of its diverse members and how this diversity contributes to their wide distribution, stability, and abundance in oceans.
+I like to envision a ‘federation’ of  *Prochlorococcus* cells in perfect floating order, like an army of soldiers  diligently engaging in their expertise: photosynthesis.
+
+@flombaumPresentFutureGlobal2013 modeled a 29% increase of net cell abundance of *Prochlorococcus* by the end of this century and predicts that there will be poleward latitudinal shifts of at least 10° in marine phytoplankton habitats.
+Consequently, *P.
+marinus* will encounter new combinations of photoperiod, seasonal patterns, and altered spectral regimes as they move towards the poles, where solar incidence angles are lower and photoperiod seasonality is more pronounced [@bartonAnthropogenicClimateChange2016].
+The predicted poleward shifts of  *P.
+marinus* niches and the estimated increase in their cell abundances was modeled using climate model projections of sea surface temperatures and greenhouse gases equivalent to 650 ppm CO~2~ for the end of this century [@flombaumPresentFutureGlobal2013].
+While these models suggest that *P.
+marinus* could hypothetically expand into poleward regions by the end of this century, it remains uncertain whether *P.
+marinus* can actually tolerate the longer, and shorter, day lengths of temperate region seasons.
+To our knowledge, no other study has as yet addressed *P.
+marinus* growth responses in relation to a wide range of photoperiods.
+
+The lack of photoperiod growth studies is not surprising, given that higher cell abundances of *P.
+marinus* are currently  concentrated between 30°N and 30°S.
+At 30°N, the photoperiod seasonality ranges from 12 to 14 hours at the ocean surface between the winter and summer solstices, while it remains consistently 12 hours throughout the year at the equator.
+Therefore, growth response studies to date have generally been conducted under either a 12 or 14 hour (h) photoperiod.
+However, the photoperiod at the ocean surface is not fully representative of the photoperiod underwater, as solar radiation is reflected off the surface when the solar incident angle is less than 20°.
+This discrepancy between the duration of daylight hours above water and the effective duration of light exposure underwater is often overlooked in the experimental design of *P.
+marinus* growth studies, even when considering photoperiod.
+
+Current niches of *P. marinus* span across vertical ocean water columns
+[@chisholmNovelFreelivingProchlorophyte1988; @veldhuisVerticalDistributionPigment1990; @partenskyProchlorococcusMarinePhotosynthetic1999] and extend into regions with varying dissolved oxygen concentrations
+[@partenskyProchlorococcusAdvantagesLimits2010; @goerickeNovelNicheProchlorococcus2000] and even into anoxic oceans [@lavinNovelLineagesProchlorococcus2010], [@ulloaCyanobacteriumProchlorococcusHas2021; @garcia-robledoCrypticOxygenCycling2017a].
+Climate change is drastically altering the dissolved oxygen concentrations ([O~2~]) of our ocean waters.
+Research indicates that the oxygen minimum zones (OMZs) in the Pacific and Indian Oceans are expanding [@garcia-sotoOverviewOceanClimate2021; @buseckeDivergingFatesPacific2022] and that the levels of dissolved oxygen (O~2~) in our global oceans are generally decreasing [@matearLongtermChangesDissolved2003; @garcia-sotoOverviewOceanClimate2021], with significant decreases observed toward the poles [@helmObservedDecreasesOxygen2011].
+
+In chapter 2, we analyzed  growth rates to determine the viability of *P. marinus* MED4, a clade HLI ecotype found at depths near the ocean surface,
+*P.
+marinus* SS120, a clade LLIII ecotype found deep in the water column, and *P.
+marinus* MIT9313, a clade LLIV ecotype also found in deep oceans, under present day and hypothetical future niche conditions.
+We designed our study to account for light attenuation through ocean waters, recognizing that low light levels of the blue spectral waveband ultimately prevail in deep ocean waters [@morelAvailableUsableStored1978; @holtropVibrationalModesWater2021] and that the solar incidence angle also attenuates the photoperiod or hours of light exposure beneath the ocean surface.
+We also tested the growth response of *P.
+marinus* to varying [O~2~] under the matrix of light parameters to determine if *P.
+marinus* can cope with  diverse  ecosystem scenarios.
+
+We found that *P.
+marinus* MED4, can grow under near surface O~2~ saturation levels of 250 µM and high light levels, conditions representative of its current ecotype classification [@moorePhysiologyMolecularPhylogeny1998].
+MED4 can also grow under O~2~ of 25 µM, and under all tested levels of light in the blue spectral waveband, so long as the photoperiod is longer than 4 h (Figure \@ref(fig:MED4PAR)).
+Consequently, MED4 can potentially inhabit different ecological niches through its ability to  exploit a wide range of light levels, from the surface to the deep ocean, along with varying levels of dissolved oxygen throughout the water column.
+These findings are supported by evidence of HL ecotype presence even in the OMZ [@mattisonPhotosyntheticStrategiesWild2020] and in deeper regions of the ocean [@mattisonPhotosyntheticStrategiesWild2020; @delmontLinkingPangenomesMetagenomes2018].
+With predicted future ocean warming [@wijffelsOceanTemperaturesChronicle2016], MED4 shows potential to harness the photoregimes prevalent in temperate spring, summer, and fall zones when the duration of blue spectral waveband in the water column exceeds 4 hours.
+
+*Prochlorococcus marinus* SS120 prefers the deeper ocean where blue spectral waveband dominates at low levels, through its demonstrated ability to exploit only the lowest blue spectral waveband levels PAR of 30 µmol photons m^-2^ s^-1^ under 250 µM O~2~.
+However, we found *P.
+marinus* SS120 can exploit more diverse ecological niches within the ocean layers, even in regions with high levels of blue spectral waveband,  but only under O~2~ of 25 µM (Figure \@ref(fig:SS120PAR)).
+@mattisonPhotosyntheticStrategiesWild2020 and @lavinNovelLineagesProchlorococcus2010 show evidence of LLIII ecotypes at varying depths from 20 to 200 m and under all [O~2~] in the oxygen minimum zone (OMZ) of the tropical North Pacific Ocean, illustrating its tolerance of high light levels under low O~2~.
+SS120 has the potential to thrive in deep temperate zones, specifically during the spring, summer, and fall seasons when the duration of daylight exceeds 4 h, if O~2~ are near surface saturation of about 250 µM.
+Under lower oxygen levels of 25 µM, SS120 can also exploit a 4 h photoperiod in the blue waveband, and thus has the potential to inhabit a warmed, deep, temperate region during the winter season.
+
+*Prochlorococcus marinus* MIT9313 shows the potential to inhabit future warmed temperate zones year-round, as it exhibits the ability to grow under a 4 h photoperiod.
+MIT9313 demonstrates an unexpected tolerance to higher light levels,  but only under low oxygen conditions of 25 µM and 2.5 µM (Figure \@ref(fig:MIT9313PAR)).
+The ability to utilize higher levels of blue spectral waveband under 25 µM or 2.5 µM O~2~ enables MIT9313 to grow in regions like the OMZ and even at depths closer to the surface.
+
+We found our experimental growth rates agreed with those from @mooreComparativePhysiologySynechococcus1995, grown under white LED and 250 µM O~2~.
+However, growth response studies are scarce for comparison, especially under varying [O~2~] and even under different spectral wavebands and photoperiods.
+As far as we know, our study is the first to analyze the interactive growth responses of *Prochlorococcus*  to varying [O~2~], spectral wavebands and photoperiods.
+
+The potential expansion of  *P.
+marinus*  polewards will contribute to the primary food base of an aquatic ecosystem that has already undergone changes in Canadian waters; commercial fish populations are shifting with new species immigrating  [@zellerCheungZellerPauly2011], endangered whales actively searching for food sources are becoming more prevalent [@meyer-gutbrodMarineSpeciesRange2018] and the white shark seasonal presence is increasing  either due to rising ocean temperatures or following marine prey [@bastienInconspicuousRecoveringNorthward2020].
+While the exact impact of the presence of *P.
+marinus*  on the species distribution of marine wildlife in Atlantic Canadian waters is unknown, there is little doubt that *Prochlorococcus* will play a significant role in shaping this distribution.
+The shifting dynamics of the aquatic ecosystem in the Atlantic Canadian waters may have consequences for our commercial fishing and shipping sectors, as adjustments to shipping routes and regulations are made to safeguard endangered whales.
+
+In chapter 3, we determined the Photosynthetic Usable Radiation (PUR), the portion of light radiation absorbed differentially by the pigments of the photosynthetic organism [@morelAvailableUsableStored1978] and expressed growth response in terms of cumulative diel PUR.
+We found that approximately 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of PUR is the maximum dosage that the representative LL clades, SS120 and MIT9313 can tolerate under 25 µM O~2~, in contrast to the representative HL clade, MED4 which exhibited growth saturation at the same cumulative diel PUR of 1.0 x 10^6^ µmol photons m^-2^ d^-1^.
+Growth under lower O~2~ allowed MIT9313 to substantially increase its exploitation of higher diel PUR.
+
+To gain insights into the variations we observed in growth responses across strains, particularly the responses to different oxygen levels [O~2~], we used a subset of the dataset of annotated phytoplankton genomes from @omarAnnotationGenesEncoding2023.
+This subset contains annotated phytoplankton gene sequences, with a focus on genes encoding enzymes involved in oxygen metabolism (Figure \@ref(fig:ProchlorococcusEnzymeKms)) or DNA repair (Figure \@ref(fig:DNARepairFig)).
+According to figure \@ref(fig:ProchlorococcusEnzymeKms), we see that *P.
+marinus* MED4 has the gene encoding ubiquinol oxidase (non electrogenic) enzyme, whereas SS120 and MIT9313 do not.
+The ubiquinol oxidase (non electrogenic) enzyme is involved in dissipating excess electrons [@InformationEC10] generated under high light exposure, thereby reducing stress on the electron transport system.
+The O~2~ substrate K~m~ value of approximately 25 µM  for ubiquinol oxidase  may explain why *P.
+marinus* MED4 can grow under 25 µM of O~2~ but not under 2.5 µM of O~2~, since growth under 2.5 µM of O~2~ would suppress use of ubiquinol oxidase to balance electron transport.
+The demonstrated ability of *P.
+marinus* MIT9313 to grow when exposed to high blue light under 2.5 µM and 25 µM O~2~ treatments may be explained by the presence of the gene encoding enzyme 2-hydroxy-acid oxidase (Figure \@ref(fig:ProchlorococcusEnzymeKms)).
+The enzyme 2-hydroxy-acid oxidase, with an O~2~ substrate K~m~ value of approximately 250 µM (Figure \@ref(fig:ProchlorococcusEnzymeKms)), catalyzes the reaction of 2-hydroxy acid with O~2~ to produce toxic hydrogen peroxide [@InformationEC15].
+We hypothesize that under our 250 µM O~2~ and high blue light experiments, *P.
+marinus* MIT9313 exhibited photoinhibition, resulting from the inactivation of PSII caused by the production of the reactive oxygen species, hydrogen peroxide.
+This inhibition was further compounded by the limited induced repair mechanism for PSII, due to the absence of FtsH 2 and 3  proteins in *P.
+marinus* MIT9313 [@bonisteelStrainSpecificDifferences2018].
+We hypothesize that under the conditions of our high light and 2.5 µM and 25 µM O~2~ experiments, the activity of the 2-hydroxy-acid oxidase enzyme is suppressed.
+As a result, the catalyzed production of hydrogen peroxide is inhibited, leading to minimal PSII damage, allowing MIT9313 to avoid photohibition and circumvent limitations on PSII repair.
+Figure \@ref(fig:ProchlorococcusEnzymeKms) also shows that *P.
+marinus* SS120 is the only tested ecotype to lack the pyridoxal 5'-phosphate synthase enzyme.
+The pyridoxal 5'-phosphate synthase enzyme is an important cofactor in the biosynthesis of vitamin B~6~ [@sangIdentificationPyridoxinePyridoxamine2007].
+Vitamin B~6~ is a potential antioxidant and can effectively quench singlet oxygen [@bilskiVitaminB6Pyridoxine2000].
+The absence of the pyridoxal 5'-phosphate synthase enzyme may explain why *P.
+marinus* SS120 does not grow as well as *P.
+marinus* MIT9313 when exposed to high light stress under 25 µM O~2~ and not at all under 2.5 µM O~2~.
+
+XXX ProchlorococcusEnzymeKms figure was here XXX
+
+\newpage
+
+Figure \@ref(fig:DNARepairFig) displays the genes encoding DNA repair for the three *P.
+marinus* strains examined in this study.
+As expected,  *P.
+marinus* MED4 possesses the largest and most complete suite of genes encoding DNA repair enzymes, followed by *P.
+marinus* MIT9313.
+Conversely, *P.
+marinus* SS120 demonstrates the smallest genomic capacity for DNA repair.
+*Prochlorococcus marinus* MED4 was the only strain out of the three strains in this study to possess the gene encoding deoxyribodipyrimidine photolyase, which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003].
+*Prochlorococcus marinus* MED4 was also the only strain to possesses the gene encoding DNA ligase, which uses ATP as a cofactor for DNA repair.
+The absence of the genes encoding deoxyribodipyrimidine photolyase and DNA ligase (ATP) in *P.
+marinus* MIT9313 and *P.
+marinus* SS120 explains why these two strains cannot tolerate the high light levels found at the ocean surface where  *P.
+marinus* MED4 inhabits.
+
+XXX DNARepairFig was here XXX
+
+\newpage
+
+@westNichePartitioningProchlorococcusPopulationsStratified1999 and
+@malmstromTemporalDynamicsProchlorococcus2010 found that decreased
+abundances of the LL ecotypes corresponded to increased depth of the
+surface mixed layer, which thus influences the vertical distribution of
+HL and LL ecotypes. @malmstromTemporalDynamicsProchlorococcus2010
+attributes the transport of LL ecotypes to the surface and exposure to
+photoinhibitory high light levels as the reason for low cell abundances.
+@westNichePartitioningProchlorococcusPopulationsStratified1999 found
+the depth of the mixed layer strongly influenced the depth transition
+from HL to LL ecotypes and that additional factors other than light
+levels may influence the variations in the upper and lower depth limits
+of these ecotypes. Based on our findings, we hypothesize that low cell abundances of LL ecotypes in the mixed layer is likely due to increased [O~2~] at
+those depths and it is [O~2~] that determines the prevalence of the LL
+ecotypes to certain depths, not necessarily the light level.
+
+We have demonstrated that *P.
+marinus*  can exploit the photoregimes of the temperate zone, both at the surface and deep in the water column.
+Additionally, we  confirmed that the *P.
+marinus* strains we tested can survive in significantly lower oxygen environments as is represented in the OMZ and that the LL ecotypes we tested can be labeled as HL strains in oxygen environments of 25 µM and as low as 2.5 µM in the case of MIT9313.
+@billerProchlorococcusStructureFunction2015 has described *Prochlorococcus* as a 'federation' of diverse cells through their extensive genomic and phenotypic diversity.
+They underscore the importance of its diverse members and how this diversity contributes to their wide distribution, stability, and abundance in oceans.
+I like to envision a ‘federation’ of  *Prochlorococcus* cells in perfect floating order, like an army of soldiers  diligently engaging in their expertise: photosynthesis.
 
@@
 
+XXXX Mireille to finish Fig. caption  XXX
 ```{r MED4ProteinAnnotated, fig.cap = MED4ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
 
-MED4ProteinAnnotated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade).  **",
+MED4ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade).**",
 
                     "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",
-                    "Numbers over each bar are fmole/ug",
+                    "Numbers over each bar are fmole target protein per ug total protein.",
 
@@
 
+XXXX Mireille to finish Fig. caption  XXX
 ```{r MIT9313ProteinAnnotated, fig.cap = MIT9313ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
 
-MIT9313ProteinAnnotated_cap <- glue("**fmole target protein per ug total protein for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade).  **",
+MIT9313ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade).  **",
 
                     "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",
-                    "Numbers over each bar are fmole/ug",
+                    "Numbers over each bar are fmole target protein per ug total protein.",
 

### 2024-02-20 Code/Manuscript_O2.Rmd
Added to manuscript_O2

@@
 institute:
-  - mta: 'Department of Biology, Mount Allison University, 53 York St., Sackville NB, Canada, E4L 1C9.'
+  - mta: 'Department of Biology, Mount Allison University, 63B York St., Sackville NB, Canada, E4L 1G7.'
   - num: 2
@@
 
-knitr::write_bib(c("tidyverse", "lubridate","knitr",  "broom", "zoo", "photobiologyWavebands", "RColorBrewer", "data.table","googlesheets4",  "grid", "glue", "bookdown", "photobiology", "mgcv", "minpack.lm", "ggh4x", "cowplot", "egg"), 'RPackages.bib')
+knitr::write_bib(c("tidyverse", "ggplot2", "Studio", "lubridate","knitr",  "broom", "zoo", "photobiologyWavebands", "RColorBrewer", "data.table","googlesheets4",  "grid", "glue", "bookdown", "photobiology", "mgcv", "minpack.lm", "ggh4x", "cowplot", "egg"), 'RPackages.bib')
 
@@
 
-```
-
-```{r, echo=FALSE, results='asis'}
-citations <- list()
-knitr::knit_hooks$set(knitcitations = function(before, options, envir) {
-  if (before) {
-    citations$reflist <- options$reflist
-    citations$section <- options$section
-  }
-})
 ```
@@
 
-```{r FtsHtable, echo = FALSE}
-
-FtsHtable_cap <- "FtsH protease homologs in *Prochlorococcus marinus* and the model cyanobacterium *Synechocystis* sp.
-PCC6803.
-Protein homology determined by multiple sequence alignment with MUSCLE followed by construction of maximum likelihood phylogenetic tree using 1000 bootstrap replicates in MEGAX."
-
-FtsHTable <- tibble(Organism = c("Prochlorococcus marinus", "Synechocystis sp. PCC6803", "Function"),
+```{r BuildFtsHtable, echo = FALSE}
+
+FtsHTable <- tibble(Organism = c("*Prochlorococcus marinus*", "*Synechocystis sp. PCC6803*", "Function"),
                     FtsH1 = c("FtsH1", "SlrO22", "PSII Repair"),
@@
 
-FtsHTable
+```
+
+```{r FtsHTable, fig.height = 6, fig.width = 10, include = TRUE, echo = FALSE}
+
+knitr::kable(FtsHTable,
+             caption = "FtsH protease homologs in *Prochlorococcus marinus* and the model cyanobacterium *Synechocystis* sp.
+PCC6803.
+Protein homology determined by multiple sequence alignment with MUSCLE followed by construction of maximum likelihood phylogenetic tree using 1000 bootstrap replicates in MEGAX.",
+              col.names =  c("Organism",
+                          "Homolog 1",
+                          "Homolog 2",
+                          "Homolog 3",
+                          "Homolog 4"),
+               align = "lcccc"
+             )
 ```
@@
 
-Collection and treatment of protein samples were performed following Saito et al., (2014, 2015) XXXXADD to ZoteroXXXX .
+Collection and treatment of protein samples were performed following Saito et al., [@saitoMultipleNutrientStresses2014; @saitoNeedlesBlueSea2015].
 Briefly, samples of seawater from depths of 20, 40, 50, 60, 70, 80, 90, 120, 150, 200, 250, 300, 380, 400, 500, 550, 600, and 800 m below the ocean surface were pumped through a 0.2 µm filter, preserved in RNAlater and frozen at -80°C until extraction.
@@
 is from Low Light-adapted (LLIV) clade. Cultures were
-maintained in incubators set to 22°C with a light/dark cycle of 12 h, with illumination from XXXXX.
-The PAR level for maintenance cultures reflected  Photosynthetically Active Radiation (PAR) in the source
-niche of the ecotype; MED4, of 160 µmol photons m^-2^ s^-1^; SS120 and
-MIT9313 at 30 µmol photons m^-2^ s^-1^. To maintain active growth all strains were
+maintained in incubators set to 22°C with a light/dark cycle of 12 h. The PAR level for maintenance cultures reflected Photosynthetically Active Radiation (PAR) in the source
+niche of the ecotype; MED4, of 160 µmol photons m^-2^ s^-1^ with illumination from STANDARD Products Inc. Cool White F24T5/41K/8/HO/PS/G5/STD, 24 watts, fluorescent bulbs; SS120 and
+MIT9313 at 30 µmol photons m^-2^ s^-1^ with illumination from Philips Cool White F14T5/841 Alto, 14 watts, fluorescent bulbs. To maintain active growth all strains were
 transferred weekly with 1 to 5 dilution with Pro99 media
 [@mooreCulturingMarineCyanobacterium2007] prepared with autoclaved artificial
-seawater (National
-Center for Marine Algae and Microbiota (NCMA) protocol by combining salt
-solution I and salt solution II using the enriched artificial seawater
-(ESAW) recipe.  REPLACe with CITATION OF NCMA protocol)XXXX
-
-Controlled growth experiments were performed using PSI Multicultivators (Figure \@ref(fig:LabeledMC); MCMIX-OD or MC1000-OD, Brno, Czech Republic ).
+seawater [@bergesEvolutionArtificialSeawater2001].
+
+Controlled growth experiments were performed using PSI Multicultivators (Figure \@ref(fig:LabeledMC); MCMIX-OD or MC1000-OD, Brno, Czech Republic).
 Each multicultivator individually controls 8 tubes at a common temperature of 22°C.
 Each tube containing 70 mL of Pro99 media was inoculated with 10 mL of growing maintenance culture.
-In a factorial matrix design, each tube was then subject to an individual combination of sinusoidal photoperiod (4, 8, 12, 16  h);  reaching a peak PAR (30, 90, 180 µmol photons m^-2^ s^-1^), with defined spectral bandwidth (AA, BB, CC, DD nm).
+In a factorial matrix design, each tube was then subject to an individual combination of sinusoidal photoperiod (4, 8, 12, 16  h);  reaching a peak PAR (30, 90, 180 µmol photons m^-2^ s^-1^), with defined spectral bandwidth (White LED, 660 nm, 450 nm).
 [O~2~] levels (2.5 µM, 25 µM, 250 µM) were imposed by bubbling tubes with varying ratios of air and
 Nitrogen (N~2~), with consistent 0.05% of Carbon Dioxide (CO~2~)
-gas, delivered through a 0.2 μm sterile microfilter via a G400 gas mixing system XXXXGIVE SOURCEXXXX. [O~2~] in situ was verified using oxygen optodes (PyroScience,
+gas, delivered through a 0.2 μm sterile microfilter via a G400 gas mixing system (Qubit Systems Inc, Kingston, Ontario, Canada). [O~2~] in situ was verified using oxygen optodes (PyroScience,
 Germany) inserted into tubes for
@@
 
-The full crossing of all factor levels would yield 4 x 3 x 4 x 3 = 144 treatments, x 3 strains for 432 possible combinations.
-Consistent absence of growth of some strains under some levels of photoperiod, PAR, or [O~2~] meant we completed 291 growth factor treatment combinations.
+The full crossing of all factor levels would yield 4 x 3 x 3 x 3 = 108 treatments, x 3 strains for 324 possible combinations.
+Consistent absence of growth of some strains under some levels of photoperiod, PAR, or [O~2~] meant we completed 268 growth factor treatment combinations.
 
@@
 	ii) Sample ID number, station, depth in meters below the surface the sample was collected at, best-hit BLASTP protein and species annotation and the corresponding Uniprot Entry number for the identified proteins;
-	iii) Sample station depth and [O~2].  
-	The depth and [O~2] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using the functions in the Tidyverse package (https://www.tidyverse.org/) in RStudio v1.2.5019 (https://rstudio.com/)  (LOCATION OF CODE ON GITHUBO.
+	iii) Sample station depth and [O~2~].  
+	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using the functions in the Tidyverse package [@R-tidyverse] in RStudio v1.2.5019 (https://rstudio.com/)  (LOCATION OF CODE ON GITHUBO.
 The resulting merged dataset was filtered for *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b6f (Cytb6f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Terminal Oxidase (PTOX); plastocyanin (PC); ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  ATP Synthase;  FtsH proteases (FtsH) or ribosomes.
@@
 PCC6803 (CITATONS).
-Data for each strain was plotted against depth and  [O~2] and sampling station.
-
-Graphs depict the detection of mass-spectrally detected peptides at varying depths and [O~2] in the water column for  *Prochlorococcus* strains and clades identified in the dataset.
+Data for each strain was plotted against depth and  [O~2~] and sampling station.
+
+Graphs depict the detection of mass-spectrally detected peptides at varying depths and [O~2~] in the water column for  *Prochlorococcus* strains and clades identified in the dataset.
 When assessing the presence of a particular protein complex, all peptides belonging to all subunits of the complex were included to give the greatest number of data points.
@@
 ## Growth data management and analysis {.unnumbered}
-Data files saved form from the Multicultivator software were imported into R-Studio (CITATION) for data management [@R-tidyverse], growth rate calculations CITATION, comparisons of model fits CITATION, and generation of
-figures`ggplot2` CITATION. The chlorophyll proxy
+Data files saved from the Multicultivator software were imported into R-Studio [@R-Studio] for data management [@R-tidyverse], growth rate calculations CITATION, comparisons of model fits CITATION, and generation of
+figures using `ggplot2` [@R-ggplot2]. The chlorophyll proxy
 optical density (OD680 - OD720;  ΔOD) was used to determine the chlorophyll-specific exponential growth
-rate (µ, h^-1^) for each treatment combination.
-We first we used a rolling mean from the RStudio `zoo` package [@R-zoo] to calculate the average ΔOD data over a 1-hour window, to lower influence of outlier points XXXXother trimmingXXXXX using a Levenberg-Marquardt algorithm
+rate (µ, d^-1^) for each treatment combination.
+We first we used a rolling mean from the RStudio `zoo` package [@R-zoo] to calculate the average ΔOD data over a 1-hour window, to lower influence of outlier points and remove data points collected during post stationary phase, if applicable.
+We used the Levenberg-Marquardt algorithm
 [@bellaviaLevenbergMarquardtMethod2018] modification of the non-linear
@@
 
-%%%%%% Taken from my thesis word for word, need to reword and shorten %%%%
-
 A Generalized Additive Model (GAM) was applied to examine the
-relationship between chlorophyll-specific µ, h^-1^, for each [O~2~] level, across the blue and red spectral wavebands, photoperiods and PAR levels for each *P.marinus* strain in this study.
+relationship between chlorophyll-specific µ, d^-1^, for each [O~2~] level, across the blue and red spectral wavebands, photoperiods and PAR levels for each *P.marinus* strain in this study.
 The gam function from the R package `mgcv`
 [@R-mgcv] was used to model the growth rate with smoothing terms to
-indicate the 90, 50 and 10% quantiles for growth rate across the levels of factors.
-Only data  XXXXXWHAT DATAXXXX BE SPECIFICXXXX below a standard error tolerance of 30% of the fit was used in the model.
-Our priority
+indicate the 90, 50 and 10% quantiles for growth rate across the levels of factors. Growth rates with a standard error tolerance below 30% of the fitted growth rate was used in the model. Our priority
 was studying the effect of blue light on growth trends, since blue light is the most ecologically relevant spectral waveband for
-deep ocean niches.  We included analyses of responses of red light, which is not ecophysiologically relevant but might prove mechanistically informative (CITE MURPHY ETC)
+deep ocean niches.  We included analyses of responses of red light, which is not ecophysiologically relevant but might prove mechanistically informative [@murphyPhotoinactivationPhotosystemII2017].
 
@@
 Spectrophotometer (Olis Inc, Bogart, Georgia) by scanning across the visible spectral range of λ = 350 nm to 750 nm at 1 nm intervals.
-A whole cell absorbance spectrum was measured for each strain under each imposed spectral waveband.
-The 20 cm path length of the internally reflective cavity of the Olis spectrophotometer was corrected to a 1 cm path length using the Javorfi correction method [@javorfiQuantitativeSpectrophotometryUsing2006] on a PRO 99 media subtracted whole cell absorbance spectra of each strain.
+The 20 cm path length of the internally reflective cavity of the Olis spectrophotometer was corrected to a 1 cm path length using the Javorfi correction method [@javorfiQuantitativeSpectrophotometryUsing2006] on PRO 99 media subtracted whole cell absorbance spectra.
+Whole cell absorbance spectra were measured for each strain under each imposed spectral waveband.
 
@@
 \newpage
+
+### Protein Immunoblot {.unnumbered}
+
+XXX Mireille to confirm and summarise XXX
+Samples were thawed and placed in FastPrep lysing vials with 500 uL of 1X Protein Extraction Buffer (PEB).
+Cells were lysed for 3 cycles of 60 seconds at 6.5m s-1 with 60 second intervals on ice between cycles.
+The lysing vials were centrifuged at 16100g for 5 minutes, the supernatant was transferred to a 600 uL microcentrifuge tube and centrifuged again at 16100g for 3 minutes.
+40uL of the supernatant were subsampled into labeled vials and stored in  -80 oC freezer until analysis.
+The bicinchoninic acid assay (BCA) was used for total protein determination using a calibration curve of bovine gamma globulin (BGG) standard in the 0 to 1.0 mg/mL range.
+
+All samples and appropriate standards were prepared as described in [@brownFluxCapacitiesAcclimation2008] and loaded onto either 15 or 17 well Invitrogen Bolt 4-12% Bis-Tris gels.
+All sample extract loads were calculated based on 2.0 ug of total protein.
+All gels were run for 25 minutes at 200V and transferred for 60 minutes at 20V onto a PVDF membrane.
+Blots were blocked overnight in 2% ECL blocking solution made with 1XTBS-T, the exception being target protein Fcp6 which was not blocked.
+Fcp6 was incubated overnight with 1:5000 dilution of primary antibody (obtained by J.
+Lavaud) in 2% ECL blocking solution directly after transfer.
+The following morning, each blot was incubated in their appropriate antibody and agitated gently on a rotator table for 1 hour at room temperature.
+Dilution of primary antibodies was  PsbA 1:10000 (Agrisera,  AS05 084), and RbcL 1:10000 (Agrisera,  AS03037).
+Each blot was washed with 10mL of 1XTBS-T.
+Two times briefly preceded by 15 minutes on a rotator table, followed by three times for 5 minutes on the rotator table.
+All blots were incubated in a 1:15000 dilution of secondary antibody (anti-rabbit HRP Biorad lot 64230791) and agitated gently on a rotator table for 1 hour at room temperature.
+All blots were washed as per the wash protocol described above.
+Blots were incubated in Amersham ECL Select chemiluminescent substrate and imaged in a Biorad VersaDoc imager.
+
+Target protein standards were loaded at 3 concentrations to establish a calibration curve.
+PsbA standard (Agrisera, AS01 016S) range 12.5 - 100 fmol per lane and RbcL standard (Agrisera, AS01 017S) range 175 - 1400 fmol per lane.
 

### 2024-02-20 Code/Manuscript_O2.Rmd
Added protein quantification to Methods and materials

@@
 
-### Estimation of Photosynthetically Usable Radiation {.unnumbered}
-
-To calculate the Photosynthetic Usable Radiation (PUR), a proxy of photons absorbed, for each ecotype
-of *P. marinus*, the imposed Photosynthetic Active
+### Estimation of photosynthetically usable radiation {.unnumbered}
+
+To calculate the Photosynthetic Usable Radiation (PUR), a proxy of photons absorbed, for each *P. marinus* ecotype, the imposed Photosynthetic Active
 Radiation (PAR) was first determined. An emission profile of each colored LED
-light of the MCMIX-OD Multicultivator and the white LED light of the MC1000-OD Multicultivator was obtained using a Jaz spectrometer (Ocean Optics, Inc.,Dunedin FL, USA) equipped with a fiber
+light of the MCMIX-OD Multicultivator and the white LED light of the MC1000-OD Multicultivator was obtained using a Jaz spectrometer (Ocean Optics, Inc.,Dunedin, FL, USA) equipped with a fiber
 optic cable, HH2 FiberOpticJmp (Part number A901073, Malvern Panalytical
@@
 marinus* was obtained using the Olis 14 UV/VIS Clarity
-Spectrophotometer (Olis Inc, Bogart, Georgia) by scanning across the visible spectral range of λ = 350 nm to 750 nm at 1 nm intervals.
+Spectrophotometer (Olis Inc, Bogart, GA, USA) by scanning across the visible spectral range of λ = 350 nm to 750 nm at 1 nm intervals.
 The 20 cm path length of the internally reflective cavity of the Olis spectrophotometer was corrected to a 1 cm path length using the Javorfi correction method [@javorfiQuantitativeSpectrophotometryUsing2006] on PRO 99 media subtracted whole cell absorbance spectra.
@@
 
-The applied photoperiod was administered using a sinusoidal function to simulate light levels equivalent to sun rise and sunset.
-The area under a sine curve is equivalent to a triangle, therefore the equation to determine the cumulative diel absorbed PUR (µmol photons m^-2^ d^-1^) is one half of the base (photoperiod) multiplied by the height (PUR) equation \@ref(eq:SumPURDay).
+The applied photoperiod was administered using the sine circadian light function of the PSI Multicultivator to simulate light exposure approximating sun rise through to sunset.
+The area under a sine curve is approximately equivalent to the area of a triangle, therefore the equation to determine the cumulative diel absorbed PUR (µmol photons m^-2^ d^-1^) is one half of the base (photoperiod) multiplied by the height (PUR) (equation \@ref(eq:SumPURDay)),
 
@@
 
-### Protein Immunoblot {.unnumbered}
+### Quantitative protein immunoblotting {.unnumbered}
 
 XXX Mireille to confirm and summarise XXX
-Samples were thawed and placed in FastPrep lysing vials with 500 uL of 1X Protein Extraction Buffer (PEB).
+
+Quantitative protein immunoblots were used to determine the concentrations of 5 target proteins; FtsH, PsbA, PetC, PsaC and RbcL in *P.
+marinus* MED4 and MIT9313 cultures grown in the PSI Multicultivator under imposed PAR light levels of 30 and 100 µmol photons m^-2^ s^-1^, spectral wavebands of 660 and 450 nm and [O~2~] of 2.5 and 250 µM.
+40 mL of culture were transferred into a 50 mL falcon tube and 40 µL of 10 % Pluronic F68 acid was added to the cell suspension.
+The cell suspension was centrifuged for 30 minutes at 17664 g using a J-26XP centrifuge (Beckman Coulter, Brea, CA, USA) equipped with a J-10 rotor.
+The supernatant was removed and the resulting pellet was flash frozen in liquid nitrogen and stored at -80 °C for later use.
+
+Protein samples were thawed and placed in 2 mL FastPrep®-24 bead lysing matrix D vials (MP Biomedicals, Irvine, CA, USA; SKU 116913050) with 200 uL of 1X protein extraction buffer (0.0281 mol L^−1 TRIS base buffer, 0.0211 mol L^−1 TRIS HCl buffer, 0.0735 mol L^−1 lithium dodecyl sulfate, 1.08 mol L^−1 glycerol, 0.5 mmol L^−1 ethylenediaminetetraacetic acid, 0.1 mg·mL−1 PefaBloc SC (AEBSF) protease inhibitor) [@brownFluxCapacitiesAcclimation2008]  XXX note we used a low tris PEB recipe not sure where it came from XXX.
 Cells were lysed for 3 cycles of 60 seconds at 6.5m s-1 with 60 second intervals on ice between cycles.
 The lysing vials were centrifuged at 16100g for 5 minutes, the supernatant was transferred to a 600 uL microcentrifuge tube and centrifuged again at 16100g for 3 minutes.
-40uL of the supernatant were subsampled into labeled vials and stored in  -80 oC freezer until analysis.
-The bicinchoninic acid assay (BCA) was used for total protein determination using a calibration curve of bovine gamma globulin (BGG) standard in the 0 to 1.0 mg/mL range.
-
-All samples and appropriate standards were prepared as described in [@brownFluxCapacitiesAcclimation2008] and loaded onto either 15 or 17 well Invitrogen Bolt 4-12% Bis-Tris gels.
-All sample extract loads were calculated based on 2.0 ug of total protein.
-All gels were run for 25 minutes at 200V and transferred for 60 minutes at 20V onto a PVDF membrane.
-Blots were blocked overnight in 2% ECL blocking solution made with 1XTBS-T, the exception being target protein Fcp6 which was not blocked.
-Fcp6 was incubated overnight with 1:5000 dilution of primary antibody (obtained by J.
-Lavaud) in 2% ECL blocking solution directly after transfer.
-The following morning, each blot was incubated in their appropriate antibody and agitated gently on a rotator table for 1 hour at room temperature.
-Dilution of primary antibodies was  PsbA 1:10000 (Agrisera,  AS05 084), and RbcL 1:10000 (Agrisera,  AS03037).
-Each blot was washed with 10mL of 1XTBS-T.
-Two times briefly preceded by 15 minutes on a rotator table, followed by three times for 5 minutes on the rotator table.
-All blots were incubated in a 1:15000 dilution of secondary antibody (anti-rabbit HRP Biorad lot 64230791) and agitated gently on a rotator table for 1 hour at room temperature.
-All blots were washed as per the wash protocol described above.
-Blots were incubated in Amersham ECL Select chemiluminescent substrate and imaged in a Biorad VersaDoc imager.
-
-Target protein standards were loaded at 3 concentrations to establish a calibration curve.
-PsbA standard (Agrisera, AS01 016S) range 12.5 - 100 fmol per lane and RbcL standard (Agrisera, AS01 017S) range 175 - 1400 fmol per lane.
+40 µL of the supernatant were subsampled into labeled vials and stored at -80 °C until analysis.
+The bicinchoninic acid (BCA) assay was used for total protein determination using a calibration curve of bovine gamma globulin (BGG; Bio-Rad, Hercules, CA, USA) standard ranging from 0 to 1.0 mg mL^-1 range.
+
+All samples and appropriate standards were prepared as described in [@brownFluxCapacitiesAcclimation2008].
+Between 0.1 to 4.0 µg of total protein was loaded onto 15 well Invitrogen Bolt 4-12% acrylamide Bis-Tris gels (ThermoFisher Scientific, Waltham, MA, USA).
+All gels were run for 25 minutes at 200V using Invitrogen Bolt Mini Gel tanks and Invitrogen Bolt MES SDS running buffer (ThermoFisher Scientific, Waltham, MA, USA) and transferred for 60 minutes at 20V onto a PVDF membrane (Bio-Rad, Hercules, CA, USA; SKU 1620177).
+Blots were blocked overnight in 2% ECL blocking solution as described by @brownFluxCapacitiesAcclimation2008.
+The following morning, each blot was incubated in their appropriate antibody obtained from Agrisera (Vännäs, Sweden; FtsH  1:5,000 dilution, AS11 1789; PsbA  1:10000 dilution, AS05 084; PetC 1:XXXXX dilution, ASXXXXX; PsaC 1:XXXXXX dilution, ASXXXXXXX ; RbcL 1:10000 dilution, AS03 037) and a 1:15000 dilution of the secondary antibody, goat anti-rabbit HRP conjugated (Bio-Rad, Hercules, CA, USA; SKU 1706515, lot 64230791).
+Blots were incubated in Amersham ECL Select chemiluminescent substrate (Danaher, Washington, DC, USA) and imaged in a Bio-Rad VersaDoc imager (Bio-Rad, Hercules, CA, USA).
+Images were quantitated using the ImageJ2 software (version 1.53c).
 

### 2024-02-21 Code/Manuscript_O2.Rmd
Edit text in Intro

@@
 *Prochlorococcus marinus* comprises many strains, organized into clades, defined by 16S-23S intergenic transcribed ribosomal sequence signatures (Rocap et al., 2003).
-The clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined by Low Light (LL) or High Light (HL).
+The clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined by Low-Light (LL) or High-Light (HL).
 Of at least 12 known *Prochlorococcus* clades only 5 to date have cultured representatives; HLI, HLII, LLI, LLII/III and LIV [@billerProchlorococcusStructureFunction2015].
@@
 A 10° poleward shift of *P.
-marinus*, coupled with a dramatic increase in cell abundance between 40°N and 50°N,  could have a large impact on ocean ecosystems and global biogeochemical cycles [@flombaumPresentFutureGlobal2013], and thus will undoubtedly impact the ecosystem balance off our Canadian waters.
+marinus*, coupled with a dramatic increase in cell abundance between 40°N and 50°N,  could have a large impact on ocean ecosystems and global biogeochemical cycles [@flombaumPresentFutureGlobal2013], and thus will undoubtedly impact the ecosystem balance off Canadian waters.
 
@@
 In light of these expanding OMZ, a recent study by @buseckeDivergingFatesPacific2022 highlights an intriguing finding; the cores of the OMZ, where the oxygen levels are lowest, is projected to contract.
-Given the predicted decrease in overall oceanic [O~2~],projected expansion of OMZs, and possible decline in the OMZ core volumes, we set forth to examine the influence of [O~2~] on *P.
+Given the predicted decrease in overall oceanic [O~2~], projected expansion of OMZs, and possible decline in the OMZ core volumes, we set forth to examine the influence of [O~2~] on *P.
 marinus* growth, as this area of research has been relatively understudied.
@@
 We then analyzed growth rates in terms of cumulative diel Photosynthetically Usable Radiation (PUR).
-Photosynthetic organisms rely on absorbing light energy within the PAR range, 350 to 700 nm, for photosynthesis [@morelAvailableUsableStored1978].
+Photosynthetic organisms rely on absorbing light energy within the Photosynthetically Active Radiation (PAR) range, 350 to 700 nm, for photosynthesis [@morelAvailableUsableStored1978].
 PUR represents the fraction of PAR that is absorbed by the pigments of photosynthetic organisms [@morelAvailableUsableStored1978].
@@
 Three xenic cultures of *P. marinus* were obtained from Bigelow Labs, NCMA
-Maine, US (REFERENCE). MED4 (CCMP1986) is from High Light-adapted (HLI) clade; SS120
-(CCMP1375) is from Low Light-adapted (LLIII) clade; and MIT9313 (CCMP2773)
-is from Low Light-adapted (LLIV) clade. Cultures were
+Maine, US (REFERENCE). MED4 (CCMP1986) is from High-Light adapted (HLI) clade; SS120
+(CCMP1375) is from Low-Light adapted (LLIII) clade; and MIT9313 (CCMP2773)
+is from Low-Light adapted (LLIV) clade. Cultures were
 maintained in incubators set to 22°C with a light/dark cycle of 12 h. The PAR level for maintenance cultures reflected Photosynthetically Active Radiation (PAR) in the source
@@
 
-The growth rate of MED4, from the high light (HLI) clade of *P.
+The growth rate of MED4, from the High-Light (HLI) clade of *P.
 marinus*, increased with higher imposed PAR and longer photoperiods
@@
 
-MED4PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade) vs. photoperiod (h).  **",
+MED4PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade) vs. photoperiod (h).  **",
 
@@
 
-The growth rate of SS120, from the low light (LLIII) clade of *P.
+The growth rate of SS120, from the Low-Light (LLIII) clade of *P.
 marinus*, increased with lower imposed PAR and longer photoperiods, when
@@
 
-SS120PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low Light (LLIII) deep ocean clade) vs. photoperiod (h). **",
+SS120PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low-Light (LLIII) deep ocean clade) vs. photoperiod (h). **",
 
@@
 
-The growth rate of MIT9313, from the low light (LLIV) clade of *P.
+The growth rate of MIT9313, from the Low-Light (LLIV) clade of *P.
 marinus*, increased with low to moderate imposed PAR and longer
@@
 
-MIT9313PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
+MIT9313PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
 
@@
 AllStrainPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
-                    "**A.** MED4 High Light I ecotype under 250, 25, or 2.5 µM of O~2~.",
-                    "**B.** SS120 Low Light II/III (LLII/III) ecotype under 250, 25, or 2.5 µM of O~2~.",
-                    "**C.** MIT9313 Low Light IV (LLIV) ecotype under 250, 25, or 2.5 µM of O~2~.",
+                    "**A.** MED4 High-Light I ecotype under 250, 25, or 2.5 µM of O~2~.",
+                    "**B.** SS120 Low-Light II/III (LLII/III) ecotype under 250, 25, or 2.5 µM of O~2~.",
+                    "**C.** MIT9313 Low-Light IV (LLIV) ecotype under 250, 25, or 2.5 µM of O~2~.",
                     "3 levels of imposed dissolved O~2~ concentrations (µM) are in rows for each strain.",
@@
 
-MED4ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MED4 (High Light (HLI) near surface clade).**",
+MED4ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade).**",
 
@@
 
-MIT9313ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MIT9313 (Low Light (LLIV) deep ocean clade).  **",
+MIT9313ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade).  **",
 

### 2024-02-21 Code/Manuscript_O2.Rmd
mass spec bioinformatics edits

@@
 	iii) Sample station depth and [O~2~].  
-	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using the functions in the Tidyverse package [@R-tidyverse] in RStudio v1.2.5019 (https://rstudio.com/)  (LOCATION OF CODE ON GITHUBO.
-The resulting merged dataset was filtered for *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b6f (Cytb6f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Terminal Oxidase (PTOX); plastocyanin (PC); ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  ATP Synthase;  FtsH proteases (FtsH) or ribosomes.
-	Detected peptides were re-annotated for consistency and labelled according to strain, clade, subunit and protein complex (where possible).
+	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using the Tidyverse package [@R-tidyverse] in RStudio v1.2.5019 (https://rstudio.com/)  (LOCATION OF CODE ON GITHUBO.
+The resulting merged dataset was filtered for those *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b6f (Cytb6f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Terminal Oxidase (PTOX); plastocyanin (PC); ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  ATP Synthase;  FtsH proteases (FtsH) or ribosomes.
+	Detected peptides were re-annotated for consistency and labelled, where feasible, according to strain, clade, subunit and protein complex .
 Full protein sequences corresponding to detected proteins were obtained from UniProt (https://www.uniprot.org/) and analyzed in Molecular Evolution and Genetic Analyses X (MEGAX) software  (https://www.megasoftware.net/).
-Sequences for each protein and/or subunits for each of the thirteen Prochlorococcus strains identified in the dataset were aligned with MUSCLE using UPGMA cluster method and a lambda of 24 with a -2.9 gap open penalty and 1.20 hydrophobicity multiplier.
+Sequences for proteins for each of the thirteen Prochlorococcus strains identified in the dataset were aligned with MUSCLE using UPGMA cluster method and a lambda of 24 with a -2.9 gap open penalty and 1.20 hydrophobicity multiplier.
 Overall mean pairwise distance between protein sequences was determined using bootstrap variance estimation methods.
 Maximum likelihood phylogenetic trees were assembled using 1000 bootstrap replications with a 95% site coverage cut off.
-*Prochlorococcus* FtsH isoform identities were specified by phylogenetic comparison to the characterized FtsH proteases of Synechocystis sp.
+*Prochlorococcus* FtsH isoform identities, and inferred functions, were specified by phylogenetic comparison to the characterized FtsH proteases of Synechocystis sp.
 PCC6803 (CITATONS).
@@
 
-Graphs depict the detection of mass-spectrally detected peptides at varying depths and [O~2~] in the water column for  *Prochlorococcus* strains and clades identified in the dataset.
-When assessing the presence of a particular protein complex, all peptides belonging to all subunits of the complex were included to give the greatest number of data points.
-Although not a direct measurement, it is assumed that light intensity is inversely correlated with depth.
-As this data was acquired on a discovery mission rather than through targeted peptide approaches, it is difficult to discern accuracies of strain annotations, particularly as the proteins of interest in this study are highly conserved in sequence across strain.
-We are confident in clade and ecotypic classification for each protein examined, although exact strain annotation may be ambiguous.
-Another caveat to interpretation of this data is the “peptide detection bias” inherent to mass spectrometry: certain peptides are more easily detected and thus dominate the spectra over less easily detected peptides.
-The data is also limited by the number and nature of protein spectra in the SEQUEST database: a peptide sequence cannot be determined unless there is already a known spectrum for that peptide in the SEQUEST database, hence some peptides of interest may not be identifiable.
-Therefore, the absence of a particular does not necessarily rule out its presence overall.
+When assessing the presence of a particular protein complex at a sampling location, all peptides belonging to all subunits of the complex were included to give the greatest number of data points.
+As this data was acquired on a discovery mission rather than through targeted peptide approaches, it is difficult to discern accuracies of strain assignment annotations, particularly as the proteins of interest in this study are highly conserved across strains.
+We are, however, confident in clade classifications for each protein examined.
+Another caveat to interpretation of this data is the peptide detection bias inherent to mass spectrometry CITATION.
+The data is also limited by the number and nature of protein spectra in the SEQUEST database: a peptide sequence was not determined unless there is already a known spectrum for that peptide in the SEQUEST database, hence some peptides of interest may not be identifiable.
 Furthermore, a peptide must be detected above a certain threshold abundance in order to be considered an accurate ‘hit’.
-Therefore, the ‘absence’ of a particular protein structure is here interpreted as low in quantity, while its presence is interpreted as higher in quantity.
 

### 2024-02-21 Code/Manuscript_O2.Rmd
edits to PUR materials and methods

@@
 ## Growth data management and analysis {.unnumbered}
-Data files saved from the Multicultivator software were imported into R-Studio [@R-Studio] for data management [@R-tidyverse], growth rate calculations CITATION, comparisons of model fits CITATION, and generation of
+Data files (.csv) saved from the Multicultivator software were imported into R-Studio [@R-Studio] for data management [@R-tidyverse], growth rate calculations CITATION, comparisons of model fits CITATION, and generation of
 figures using `ggplot2` [@R-ggplot2]. The chlorophyll proxy
@@
 equation \@ref(eq:GrowthRate) where ΔOD~max~ is maximum ΔOD, ΔOD~min~ is minimum ΔOD, t is time
-duration over the growth trajectory. 
+duration over the growth trajectory.  Annotated code for data import, transformations and analyses is available at XXXXX 
+CITAtIONS of github locations of code etc. XXXXX
+
 OTHER MOREXXXXXX
@@
 
-CITAtIONS of github locations of code etc. XXXXX
-
 ### Generalized additive model of growth responses {.unnumbered}
 
-A Generalized Additive Model (GAM) was applied to examine the
-relationship between chlorophyll-specific µ, d^-1^, for each [O~2~] level, across the blue and red spectral wavebands, photoperiods and PAR levels for each *P.marinus* strain in this study.
+A Generalized Additive Model (GAM) CITATION was applied to the
+relation between chlorophyll-specific µ, d^-1^  to photoperiod and PAR level,  for each growth [O~2~] level, and for the blue and red wavebands for growth, for each *P.marinus* strain in this study.
 The gam function from the R package `mgcv`
-[@R-mgcv] was used to model the growth rate with smoothing terms to
-indicate the 90, 50 and 10% quantiles for growth rate across the levels of factors. Growth rates with a standard error tolerance below 30% of the fitted growth rate was used in the model. Our priority
-was studying the effect of blue light on growth trends, since blue light is the most ecologically relevant spectral waveband for
-deep ocean niches.  We included analyses of responses of red light, which is not ecophysiologically relevant but might prove mechanistically informative [@murphyPhotoinactivationPhotosystemII2017].
+[@R-mgcv] was used to model the growth rate with smoothing terms, to
+indicate the 90, 50 and 10% quantiles for growth rate across the levels of factors.
+Growth rate estimates with a standard error below 30% of the fitted growth rate were included in the gam modelling.
+Our priority
+was the effects of ecologically relevant blue light on growth trends.
+We included analyses of growth responses to red light, which is not ecophysiologically relevant, but which might prove mechanistically informative [@murphyPhotoinactivationPhotosystemII2017].
 
@@
 
-To calculate the Photosynthetic Usable Radiation (PUR), a proxy of photons absorbed, for each *P. marinus* ecotype, the imposed Photosynthetic Active
-Radiation (PAR) was first determined. An emission profile of each colored LED
+To estimate the Photosynthetic Usable Radiation (PUR), a proxy of incident photons absorbed by the cells, for each *P. marinus* ecotype, the imposed Photosynthetic Active
+Radiation (PAR) was first determined using the reported delivery of sinuisoidal diel PAR regimes by the Multicultivators, point validated using an XXXXXcitation of PAR meterXXX.
+An emission profile from 400 nm to 700 nm of each colored LED
 light of the MCMIX-OD Multicultivator and the white LED light of the MC1000-OD Multicultivator was obtained using a Jaz spectrometer (Ocean Optics, Inc.,Dunedin, FL, USA) equipped with a fiber
 optic cable, HH2 FiberOpticJmp (Part number A901073, Malvern Panalytical
-Ltd, Malvern, UK) and scanned to measure the emission wavelengths from 200 nm to 1000 nm.
-Following the determination of PAR, an *in-vivo* whole cell absorbance spectrum for each *P.
-marinus* was obtained using the Olis 14 UV/VIS Clarity
-Spectrophotometer (Olis Inc, Bogart, GA, USA) by scanning across the visible spectral range of λ = 350 nm to 750 nm at 1 nm intervals.
-The 20 cm path length of the internally reflective cavity of the Olis spectrophotometer was corrected to a 1 cm path length using the Javorfi correction method [@javorfiQuantitativeSpectrophotometryUsing2006] on PRO 99 media subtracted whole cell absorbance spectra.
-Whole cell absorbance spectra were measured for each strain under each imposed spectral waveband.
-
-A weighted PUR spectrum was determined by applying an integrated weighted function to the blank subtracted, whole cell absorbance spectrum for each *P.
-marinus* ecotype and the emission spectrum of the imposed LED growth light [@morelAvailableUsableStored1978].
-The whole cell absorbance spectrum was normalized to the absorbance maximum of divinylchlorophyll a (Chl a~2~), determined dynamically between 400 nm and 460 nm, and each LED spectrum was normalized to the emission maximum.
-
-Equation \@ref(eq:WeightedPUR) was used to determine the weighted PUR spectrum P(λ) according to [@morelAvailableUsableStored1978],
+Ltd, Malvern, UK). Each LED spectrum was then normalized to its emission maximum.
+An *in-vivo* whole cell absorbance spectrum for each *P. marinus* strain under each spectral growth condition was obtained using the Olis 14 UV/VIS Clarity
+Spectrophotometer (Olis Inc, Bogart, GA, USA) to scan across range of λ = 350 nm to 750 nm at 1 nm intervals.
+The path length of the internally reflective cavity of the Olis spectrophotometer was corrected to a 1 cm path length using the Javorfi correction method [@javorfiQuantitativeSpectrophotometryUsing2006] on PRO 99 media subtracted whole cell absorbance spectra.
+The blank-corrected whole cell absorbance spectra were normalized to the absorbance maximum of divinylchlorophyll a (Chl a~2~), determined for each spectra, falling between 400 nm and 460 nm.
+
+An integrated weighting Equation \@ref(eq:WeightedPUR) [@morelAvailableUsableStored1978] was used to determine the weighted PUR spectrum P(λ),
 
@@
 
-where P(λ) is the weighted PUR absorbance spectrum over 400 nm to 700 nm spectral range, A(λ) is the Chl a~2~ normalized whole cell absorbance spectrum over 400 nm to 700 nm and E(λ) is the imposed growth light emission spectrum over 400 nm to 700 nm.
+where A(λ) is the blank subtracted, Chl a~2~ peak normalized whole cell absorbance spectrum for each *P.
+marinus* ecotype, over 400 nm to 700 nm, A(λ); and E(λ) is the peak normalized emission spectrum of the imposed LED growth light, over 400 nm to 700 nm.
 
@@
 
-where P(λ) is the weighted PUR absorbance spectrum from equation \@ref(eq:WeightedPUR), E(λ) is the imposed growth light emission spectrum from equation \@ref(eq:WeightedPUR) and PAR is the imposed light level (µmol photons m^-2^ s^-1^).
-Figure (\@ref(fig:PurParPlot)) shows the calculated absorbed PUR (µmol photons m^-2^ d^-1^) versus imposed actinic PAR (µmol photons m^-2^ s^-1^) for each strain and each spectral waveband (nm).
-
-The applied photoperiod was administered using the sine circadian light function of the PSI Multicultivator to simulate light exposure approximating sun rise through to sunset.
-The area under a sine curve is approximately equivalent to the area of a triangle, therefore the equation to determine the cumulative diel absorbed PUR (µmol photons m^-2^ d^-1^) is one half of the base (photoperiod) multiplied by the height (PUR) (equation \@ref(eq:SumPURDay)),
+where P(λ) is the weighted PUR absorbance spectrum from equation \@ref(eq:WeightedPUR), E(λ) is the imposed growth light emission spectrum from equation \@ref(eq:WeightedPUR) and PAR is the imposed peak light level (µmol photons m^-2^ s^-1^).
+Figure (\@ref(fig:PurParPlot)) shows the calculated absorbed peak PUR (µmol photons m^-2^ d^-1^) versus imposed actinic peak PAR (µmol photons m^-2^ s^-1^) for each strain and each spectral waveband (nm).
+
+The applied photoperiods were delivered using the sine circadian light function of the PSI Multicultivator to simulate light exposure approximating sun rise through to sunset.
+The area under the sinusoidal curves is equivalent to the area of a triangular photoregime of equivalent photoperiod (Campbell, unpub), therefore the equation to determine the cumulative diel absorbed PUR (µmol photons m^-2^ d^-1^) is one half of the base (photoperiod) multiplied by the height (PUR) (equation \@ref(eq:SumPURDay)),
 

### 2024-02-21 Code/Manuscript_O2.Rmd
edits to PUR materials & methods
editing growth graph results

@@
 
-PurParPlot_cap <- glue("**The absorbed Photosynthetically Usable Radiation (PUR) (µmol photons m^-2^ s^-1^) vs. the Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^).**",
+PurParPlot_cap <- glue("**Absorbed peak Photosynthetically Usable Radiation (PUR) (µmol photons m^-2^ s^-1^) vs. peak Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^).**",
                        "The correlation between PAR, plotted on the x-axis and absorbed PUR, plotted on the y-axis, are colored for each growth spectral waveband; blue for 450 nm, red for 660 nm and black for white LED full spectrum light.",
@@
 
-%%%% OceanProteinPortal data show complexes in environment  %%%
-
-Furthermore,
-Evidence of proteins
-derived from HL ecotypes of *P. marinus* in OMZ at depths up to 200
-meters,  with O~2~ of 15 µM. The extent to which [O~2~] defines
+## Detection of *Prochlorococcus* proteins across O~2~ and light niches in the ocean
+
+Proteins derived from Clade HLXXX ecotypes of *P. marinus* were detected in OMZ at depths up to 200 meters,  with O~2~ of 15 µM. The extent to which [O~2~] defines
 the niches occupied by different *P. marinus* ecotypes, as compared to
@@
                        "Columns show detections of proteins annotated as  Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
-                       "Culture growth experimental conditions indicated by horizontal grey lines for depths approximating Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) and vertical grey lines for O~2~ (µM).",
+                       "For comparison culture growth experimental conditions are indicated by horizontal grey lines for depths approximating imposed peak Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^); and vertical grey lines for O~2~ (µM).",
                        "Point colours identify *Prochlorococcus* clade assignments",
@@
 
-### MED4 PAR and growth trends {.unnumbered}
+## *Prochlorococcus marinus* growth responses to photoperiod, PAR and O~2~
+
+### MED4 Clade HLI {.unnumbered}
 
@@
 
-The growth rate of MED4, from the High-Light (HLI) clade of *P.
-marinus*, increased with higher imposed PAR and longer photoperiods
+The growth rates of *P. marinus* MED4, Clade HLI, increased with higher imposed PAR and longer photoperiods
 (Figure \@ref(fig:MED4PAR)), when grown under 250 µM O~2~. No growth was
@@
 
-Similar to the growth trends of the 250 µM O~2~ experiments, MED4
-maintained at 25 µM O~2~, showed the fastest growth rate when the
+Similar to the growth trends under 250 µM O~2~, MED4
+maintained at 25 µM O~2~ showed the fastest growth rates when the
 photoperiod was 16 h for each spectral waveband, across PAR levels
 (Figure \@ref(fig:MED4PAR)). The 25 µM O~2~ growth experiments showed
-generally similar growth rate as the 250 µM O~2~ growth experiments,
+generally similar growth rates as the 250 µM O~2~ growth experiments,
 with the interesting exception that growth rates increased by 40% under
@@
 
-MED4 did not grow under any tested conditions sparged to the lowest O~2~
+MED4 did not grow under when sparged to the lowest O~2~
 of 2.5 µM (Figure \@ref(fig:MED4PAR)). 2.5 µM O~2~ growth experiments
-were not conducted for 4 and 16 h photoperiods, as no growth occurred
+were not conducted for 4 and 16 h photoperiods, as no reproducible growth occurred
 when MED4 was exposed to 8 and 12 h photoperiods.
@@
 
-### SS120 PAR and growth trends {.unnumbered}
+### SS120 Clade LLIII {.unnumbered}
 
@@
 
-The growth rate of SS120, from the Low-Light (LLIII) clade of *P.
-marinus*, increased with lower imposed PAR and longer photoperiods, when
+The growth rates of *P. marinus* SS120, Clade LLIII, increased with lower imposed PAR and with longer photoperiods, when
 grown under 250 µM O~2~ (Figure \@ref(fig:SS120PAR)). SS120 was able to
 grow under the lowest PAR treatment of 30 µmol photons m^-2^ s^-1^ but
-only when the photoperiod was longer than 4 h under blue, white, and red
-light. SS120 required longer than 8 h photoperiod of imposed green
+only when the photoperiod was longer than 4 h under white and red
 light. No growth was observed under any blue light photoperiods when
-exposed to PAR of 90 µmol photons m^-2^ s^-1^. Growth rate increased
-with increasing photoperiods for white, red and green light when exposed
+exposed to PAR of 90 µmol photons m^-2^ s^-1^ or greater. Growth rate increased
+with increasing photoperiods for white and red light when exposed
 to PAR of 90 µmol photons m^-2^ s^-1^; however, no growth was observed
 when the red light photoperiod was 16 h. Experiments conducted under PAR
-of 180 µmol photons m^-2^ s^-1^ showed no growth under imposed blue and
+of 180 µmol photons m^-2^ s^-1^ showed no growth under blue nor
 red lights. Growth rate decreased with longer photoperiods and showed
 growth inhibition at 12 and 16 h photoperiods under PAR of 180 µmol
-photons m^-2^ s^-1^ and white LED light. The growth rate generally
-increased with longer photoperiods under green light treatments, however
-no growth was observed under the 8 h photoperiod. The µ~max~ was
+photons m^-2^ s^-1^  white LED light.  The µ~max~ was
 `r PURPARFits %>% filter(Strain == "SS120", WL == "WW", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
@@
 
-Similar to the growth trends of the 250 µM O~2~ and PAR of 30 µmol
-photons m^-2^ s^-1^ experiments, SS120 maintained at 25 µM O~2~, no
-growth was observed under a 4 h photoperiod for imposed red spectral
+Similar to the growth trends under the 250 µM O~2~ and PAR of 30 µmol
+photons m^-2^ s^-1^ experiments, SS120 maintained at 25 µM O~2~ showed no
+growthunder a 4 h photoperiod for imposed red spectral
 waveband, however under blue light, SS120 was able to grow (Figure
@@
 of 180 µmol photons m^-2^ s^-1^ showed growth only under an 8 h
-photoperiod. This growth rate decreased by 53% compared to the 8 h blue
-light photoperiod under PAR of 90 µmol photons m^-2^ s^-1^. The µ~max~
-was
+photoperiod. The µ~max~ was
 `r PURPARFits %>% filter(Strain == "SS120", WL == "450", O2_uM == "25", Photoperiod == 8) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
@@
 
-The 25 µM O~2~, less than 16 h photoperiod and 180 µmol photons m^-2^ s^-1^ experiments under white LED
-light were not performed due to time constraints.
+The 25 µM O~2~, less than 16 h photoperiod and 180 µmol photons m^-2^ s^-1^  under white LED light experiments were not performed due to time constraints.
 
@@
 
-SS120 only grew
-(`r PURPARFits %>% filter(Strain == "SS120", WL == "660", O2_uM == "2.5", Photoperiod == 12) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
-d^-1^) under PAR of 30 µmol photons m^-2^ s^-1^ and 12 h red light
-photoperiod when sparged to the lowest O~2~ of 2.5 µM (Figure
-\@ref(fig:SS120PAR)). SS120 did not grow under any other tested
-conditions. 2.5 µM O~2~ growth experiments were not conducted for 4 and
+SS120 did not reproducibly grow when sparged to the lowest O~2~ of 2.5 µM (Figure
+\@ref(fig:SS120PAR)). 2.5 µM O~2~ growth experiments were not conducted for 4 and
 16 h photoperiods under PAR of 180 µmol photons m^-2^ s^-1^, as no
 growth occurred when SS120 was exposed to 8 and 12 h photoperiods. Red
-light 16 h photoperiod experiments were not performed due to time
-constraints.
+light 16 h photoperiod experiments were not performed due to time constraints.
 
@@
 \newpage
-### MIT9313 PAR results {.unnumbered}
+
+### MIT9313 Clade LLIV {.unnumbered}
 
@@
 
-The growth rate of MIT9313, from the Low-Light (LLIV) clade of *P.
-marinus*, increased with low to moderate imposed PAR and longer
+The growth rates of *P. marinus* MIT9313, Clade LLIV, increased with low to moderate imposed PAR and longer
 photoperiods, when grown under 250 µM O~2~ (Figure

### 2024-02-21 Code/ManuscriptPURFits.Rmd
Changed 16 h linetype to dotdash
Made PURfit plot into 9 panel faceted by Strain in columns.

--- 2024-02-15 Code/ManuscriptPURFits.Rmd
@@
 # library(glue)
-# library(egg)
+library(egg)
 # library(ggspectra)
@@
 PhotoperiodShapes
+
+```
+# set linetypes
+```{r linetypes}
+
+MyPhotoperiods = c(16, 12, 8, 4)
+MyLineTypes = c("dotdash","dashed", "dotted", "aa")
+
+names(MyLineTypes) <- MyPhotoperiods
+MyLineTypes
 
@@
 
-scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
-
-MED4PURFITPlot <- AllFitsCombined |>
-    filter(Strain == "MED4") |>
-  unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
-  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
-         OxygenLabel = "Oxygen Concentration (µM)",
-         Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4" )),
-         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
-  ggplot() +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
-    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 2, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
- geom_text(aes(x = 1000, y = 0.9, label= "A"), data = . %>% filter(O2_uM == 250, Strain == "MED4"), size = 20, hjust = 0.3, vjust = 0) +
-  scale_x_continuous(label=scientific_10) +
-   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
-  scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
-  scale_linetype_manual(values = c("twodash","dashed", "dotted", "aa"), labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
-   scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
-                    labeller = labeller(Strain = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
- guides(linetype = guide_legend(nrow = 4),
-        fill = "none",
-        colour = guide_legend(nrow = 4)) +
- guides(shape = guide_legend(nrow = 4)) +
-  theme_bw() +
-   theme( strip.text = element_text(size = 30),
-        axis.title.y = element_blank(),
-        axis.title.x.bottom = element_blank(),
-        axis.text.x = element_blank(),
-        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
-        strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"),
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title =  element_text(size = 30),  #change legend title font size
-        legend.text = element_text(size = 30),   #change legend text font size
-        legend.position = "top") +
-  labs( shape = "Photoperiod (h)",
-        color = "Growth Waveband (nm)",
-       linetype = "Photoperiod (h) "
-      )
-MED4PURFITPlot
-
-SS120PURFITPlot <- AllFitsCombined |>
-    filter(Strain == "SS120") |>
-  unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
-  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
-         OxygenLabel = "Oxygen Concentration (µM)",
-         Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4" )),
-         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
-  ggplot() +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
-    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 2, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) + 
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
- geom_text(aes(x = 1000, y = 0.9, label= "B"), data = . %>% filter(O2_uM == 250, Strain == "SS120"), size = 20, hjust = 0.3, vjust = 0) +
-  scale_x_continuous(label=scientific_10) +
-   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
-  scale_linetype_manual(values = c("twodash","dashed", "dotted", "aa"), labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
-   scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
-                    labeller = labeller(Strain = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
+# scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
+# 
+# 
+# MED4PURFITPlot <- AllFitsCombined |>
+#     filter(Strain == "MED4") |>
+#   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
+#   mutate(PhotoperiodLabel_title = "Photoperiod (h)",
+#          OxygenLabel = "Oxygen Concentration (µM)",
+#          Photoperiod = factor(Data_all_Photoperiod, levels = c(16, 12, 8, 4)),
+#          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+#          WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
+#   ggplot() +
+#   geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 4, alpha = 1.0) +
+#     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
+#   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
+#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
+#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
+#  geom_text(aes(x = 1000, y = 0.75, label= "A     MED4 HLI"), data = . %>% filter(O2_uM == 250, Strain == "MED4"), size = 4, hjust = 0, vjust = 0) +
+#   scale_x_continuous(label=scientific_10) +
+#    scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
+#   scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
+#   scale_linetype_manual(values = MyLineTypes, labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
+#    scale_shape_manual(values = PhotoperiodShapes)  +
+#   ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
+#                     labeller = labeller(Strain = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
+#  guides(linetype = guide_legend(nrow = 1),
+#         fill = "none",
+#         color = guide_legend(nrow = 1)) +
+#  guides(shape = guide_legend(nrow = 1)) +
+#   theme_bw() +
+#    theme( strip.text = element_text(size = 10),
+#         axis.title.y = element_blank(),
+#         axis.title.x.bottom = element_blank(),
+#         axis.text.x = element_blank(),
+#         axis.text.y = element_text(size = 9, color = "black", angle = 0, hjust = 1.0),
+#         strip.background=element_rect(color="grey87", fill = "grey82"),
+#         # strip.background=element_rect(fill = "white"),
+#         legend.key.size = unit(1, 'cm'), #change legend key size
+#         legend.key.height = unit(1, 'cm'), #change legend key height
+#         legend.key.width = unit(0.5, 'cm'), #change legend key width
+#         legend.title =  element_text(size = 15),  #change legend title font size
+#         legend.text = element_text(size = 15),   #change legend text font size
+#         legend.position = "top") +
+#   labs( shape = "Photoperiod (h)",
+#         color = "Growth Waveband (nm)",
+#        linetype = "Photoperiod lines"
+#       )
+# MED4PURFITPlot
+# 
+# SS120PURFITPlot <- AllFitsCombined |>
+#     filter(Strain == "SS120") |>
+#   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
+#   mutate(PhotoperiodLabel_title = "Photoperiod (h)",
+#          OxygenLabel = "Oxygen Concentration (µM)",
+#          Photoperiod = factor(Data_all_Photoperiod, levels = c(16, 12, 8, 4)),
+#          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+#          WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
+#   ggplot() +
+#   geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 4, alpha = 1.0) +
+#     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
+#   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) + 
+#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
+#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(Strain == "SS120")) +
+#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
+#  geom_text(aes(x = 1000, y = 0.75, label= "B     SS120 LLII/III"), data = . %>% filter(O2_uM == 250, Strain == "SS120"), size = 4, hjust = 0, vjust = 0) +
+#   scale_x_continuous(label=scientific_10) +
+#    scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
+#   scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
+#   scale_linetype_manual(values = c("dotdash","dashed", "dotted", "aa"), labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
+#    scale_shape_manual(values = PhotoperiodShapes)  +
+#   ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
+#                     labeller = labeller(Strain = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
+#  # guides(linetype = guide_legend(nrow = 4),
+#  #        fill = "none",
+#  #        colour = guide_legend(nrow = 4)) +
+#  # guides(shape = guide_legend(nrow = 4)) +
+#   theme_bw() +
+#    theme( strip.text = element_text(size = 10),
+#         axis.title.y = element_blank(),
+#         axis.title.x.bottom = element_blank(),
+#         axis.text.x = element_blank(),
+#         axis.text.y = element_text(size = 10, color = "black", angle = 0, hjust = 1.0),
+#         strip.background=element_rect(color="grey87", fill = "grey82"),
+#         # strip.background=element_rect(fill = "white"),
+#         legend.key.size = unit(1, 'cm'), #change legend key size
+#         legend.key.height = unit(1, 'cm'), #change legend key height
+#         legend.key.width = unit(0.5, 'cm'), #change legend key width
+#         # legend.title =  element_text(size = 20),  #change legend title font size
+#         # legend.text = element_text(size = 20),   #change legend text font size
+#         legend.position = "none") +
+#   labs( shape = "Photoperiod (h)",
+#         color = "Growth Waveband (nm)",
+#        linetype = "Photoperiod (h) "
+#       )
+#    SS120PURFITPlot
+# 
+# MIT9313PURFITPlot <- AllFitsCombined |>
+#    filter(Strain == "MIT9313") |>
+#   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
+#   mutate(PhotoperiodLabel_title = "Photoperiod (h)",
+#          OxygenLabel = "Oxygen Concentration (µM)",
+#          Photoperiod = factor(Data_all_Photoperiod, levels = c(16, 12, 8, 4)),
+#          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+#          WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
+#   ggplot() +
+#   geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 4, alpha = 1.0) +
+#     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
+#   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) + 
+#   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotdash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +
+#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
+#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM == 25, Strain == "MIT9313")) +
+#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +
+#   labs(x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
+#  geom_text(aes(x = 1000, y = 0.75, label= "C     MIT9313 LLIV"), data = . %>% filter(O2_uM == 250, Strain == "MIT9313"), size = 4, hjust = 0, vjust = 0) +
+#   scale_x_continuous(breaks = c(0, 1000000,2000000, 3000000, 4000000),label=scientific_10, limits = c (-100, 5000000)) +
+#    scale_y_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
+#   scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
+#   scale_linetype_manual(values = c("solid","dotdash","dashed", "dotted", "aa"), labels = c("Pooled","16 hr", "12 hr", "8 hr", "4 hr")) +
+#    scale_shape_manual(values = PhotoperiodShapes)  +
+#   ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
+#                     labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
 #  guides(linetype = guide_legend(nrow = 4),
@@
 #  guides(shape = guide_legend(nrow = 4)) +
-  theme_bw() +
-   theme( strip.text = element_text(size = 30),
-        axis.title.y = element_blank(),
-        axis.title.x.bottom = element_blank(),
-        axis.text.x = element_blank(),
-        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
-        strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"),
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title =  element_text(size = 30),  #change legend title font size
-        legend.text = element_text(size = 30),   #change legend text font size
-        legend.position = "none") +
-  labs( shape = "Photoperiod (h)",
-        color = "Growth Waveband (nm)",
-       linetype = "Photoperiod (h) "
-      )
-   SS120PURFITPlot
-
-MIT9313PURFITPlot <- AllFitsCombined |>
-   filter(Strain == "MIT9313") |>
+#   theme_bw() +
+#    theme( strip.text = element_text(size = 10),
+#           axis.title.y = element_blank(),
+#           axis.title.x = element_text(size = 15, color = "black"),
+#           axis.text.x = element_text(size = 10, color = "black", angle = 0, hjust = 1.0),
+#           axis.text.y = element_text(size = 10, color = "black", angle = 0, hjust = 1.0),
+#         strip.background=element_rect(color="grey87", fill = "grey82"),
+#         # strip.background=element_rect(fill = "white"),
+#         legend.key.size = unit(1, 'cm'), #change legend key size
+#         legend.key.height = unit(1, 'cm'), #change legend key height
+#         legend.key.width = unit(0.5, 'cm'), #change legend key width
+#         # legend.title =  element_text(size = 20),  #change legend title font size
+#         # legend.text = element_text(size = 20),   #change legend text font size
+#         legend.position = "none") +
+#   labs( shape = "Photoperiod (h)",
+#         color = "Growth Waveband (nm)",
+#        linetype = "Photoperiod (h) "
+#       )
+# MIT9313PURFITPlot
+
+```
+
+# Combine the 3 strains into 1 plot 
+```{r combine plots}
+
+# AllStrainPurFitsPlots <- plot_grid(MED4PURFITPlot, SS120PURFITPlot, MIT9313PURFITPlot, ncol = 1)
+# 
+# #create common x and y labels
+# y.grob <- textGrob("Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")",
+#                    gp = gpar(col="black", fontsize = 15), rot = 90)
+# 
+# #add to plot
+# AllStrainPurFitsPlots <- grid.arrange(arrangeGrob(AllStrainPurFitsPlots, left = y.grob))
+
+```
+
+```{r Pur plot strain facetted in columns}
+scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
+
+AllPURFITPlot <- AllFitsCombined |>
   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
@@
          OxygenLabel = "Oxygen Concentration (µM)",
-         Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4" )),
+         Photoperiod = factor(Data_all_Photoperiod, levels = c(16, 12, 8, 4)),
          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
+         WL = factor(Data_all_WL, levels = c("WW", 660, 450)),
+         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
   ggplot() +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
-    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 2, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) + 
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "twodash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.5, alpha = 1.0) +
+    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 0.5, alpha = 0.8) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.75, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.75, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) + 
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.75, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) + 
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotdash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +
    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
@@
    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +
-  labs(x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
- geom_text(aes(x = 1000, y = 0.9, label= "C"), data = . %>% filter(O2_uM == 250, Strain == "MIT9313"), size = 20, hjust = 0.3, vjust = 0) +
+ labs(y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
   scale_x_continuous(label=scientific_10) +
-   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
+  scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.00)) +
   scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
-  scale_linetype_manual(values = c("solid","twodash","dashed", "dotted", "aa"), labels = c("Pooled","16 hr", "12 hr", "8 hr", "4 hr")) +
+  scale_linetype_manual(values = MyLineTypes, labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
   scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
-                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
- guides(linetype = guide_legend(nrow = 4),
+  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), cols = vars(Strain), 
+                    labeller = labeller(Strain = label_value, O2_uM = label_value, OxygenLabel = label_value)) +
+ guides(linetype = guide_legend(nrow = 1),
         fill = "none",
-        colour = guide_legend(nrow = 4)) +
- guides(shape = guide_legend(nrow = 4)) +
+        color = guide_legend(nrow = 1)) +
+ guides(shape = guide_legend(nrow = 1)) +
   theme_bw() +
-   theme( strip.text = element_text(size = 30),
-          axis.title.y = element_blank(),
-          axis.title.x = element_text(size = 30, color = "black"),
-          axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
-          axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
+   theme( strip.text = element_text(size = 10),
+        axis.title.y = element_text(color = "black", size = 12,  hjust = 0.40),
+        axis.title.x = element_text(color = "black", size = 12),
+        axis.text.x = element_text(size = 10, color = "black", angle = 45, hjust = 1.0),
+        axis.text.y = element_text(size = 9, color = "black", angle = 0, hjust = 1.0),
         strip.background=element_rect(color="grey87", fill = "grey82"),
         # strip.background=element_rect(fill = "white"), 
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title =  element_text(size = 30),  #change legend title font size
-        legend.text = element_text(size = 30),   #change legend text font size
-        legend.position = "none") +
+        legend.key.size = unit(0.1, 'cm'), #change legend key size
+        legend.key.height = unit(0.1, 'cm'), #change legend key height
+        legend.key.width = unit(0.1, 'cm'), #change legend key width
+        legend.title =  element_text(size = 10),  #change legend title font size
+        legend.text = element_text(size = 10),   #change legend text font size
+        legend.position = "top") +
   labs( shape = "Photoperiod (h)",
         color = "Growth Waveband (nm)",
-       linetype = "Photoperiod (h) "
+       linetype = "Photoperiod lines"
       )
-MIT9313PURFITPlot
-
-```
-
-# Combine the 3 strains into 1 plot 
-```{r combine plots}
-
-AllStrainPurFitsPlots <- plot_grid(MED4PURFITPlot, SS120PURFITPlot, MIT9313PURFITPlot, ncol = 1)
-
-#create common x and y labels
-y.grob <- textGrob("Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")",
-                   gp = gpar(col="black", fontsize = 20), rot = 90)
-
-#add to plot
-AllStrainPurFitsPlots <- grid.arrange(arrangeGrob(AllStrainPurFitsPlots, left = y.grob))
+
+AllPURFITPlot
 
@@
 
-ggsave(file = file.path(PlotsOut, paste("AllStrainPurFitsPlots",".png",sep = "")), plot = AllStrainPurFitsPlots, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-ggsave(file = file.path(PlotsOut, paste("AllStrainPurFitsPlots",".tiff",sep = "")), plot = AllStrainPurFitsPlots, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("AllPURFITPlot",".png",sep = "")), plot = AllPURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+ggsave(file = file.path(PlotsOut, paste("AllPURFITPlot",".tiff",sep = "")), plot = AllPURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
 

### 2024-02-21 Code/Manuscript_O2.Rmd
MIT9313 growth response results.

@@
 The growth rates of *P. marinus* MED4, Clade HLI, increased with higher imposed PAR and longer photoperiods
-(Figure \@ref(fig:MED4PAR)), when grown under 250 µM O~2~. No growth was
+(Figure \@ref(fig:MED4PAR)), under 250 µM O~2~. No growth was
 observed under any imposed conditions under a 4 h photoperiod. MED4 was
@@
 
-The growth rates of *P. marinus* SS120, Clade LLIII, increased with lower imposed PAR and with longer photoperiods, when
-grown under 250 µM O~2~ (Figure \@ref(fig:SS120PAR)). SS120 was able to
-grow under the lowest PAR treatment of 30 µmol photons m^-2^ s^-1^ but
-only when the photoperiod was longer than 4 h under white and red
-light. No growth was observed under any blue light photoperiods when
-exposed to PAR of 90 µmol photons m^-2^ s^-1^ or greater. Growth rate increased
-with increasing photoperiods for white and red light when exposed
-to PAR of 90 µmol photons m^-2^ s^-1^; however, no growth was observed
-when the red light photoperiod was 16 h. Experiments conducted under PAR
+The growth rates of *P.
+marinus* SS120, Clade LLIII, increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^ peak PAR and 250 µM O~2~ (Figure \@ref(fig:SS120PAR)).
+No growth was observed under any blue light photoperiods when
+exposed to peak PAR of 90 µmol photons m^-2^ s^-1^ or greater. Growth rate increased
+with increasing photoperiods for white and red light under peak PAR of 90 µmol photons m^-2^ s^-1^; however, no growth was observed
+when the red light photoperiod was 16 h. Experiments under peak PAR
 of 180 µmol photons m^-2^ s^-1^ showed no growth under blue nor
@@
 
-The growth rates of *P. marinus* MIT9313, Clade LLIV, increased with low to moderate imposed PAR and longer
-photoperiods, when grown under 250 µM O~2~ (Figure
-\@ref(fig:MIT9313PAR)). Growth rate increased with increasing
-photoperiods under the lowest PAR treatment of 30 µmol photons m^-2^
-s^-1^ for blue, white LED and red light. The green light treatment
-showed growth only when the photoperiod was longer than 12 h and
-decreased by \~ 50% under a 16 h photoperiod. Under PAR of 90 µmol
-photons m^-2^ s^-1^, growth rate increased with longer photoperiods for
-white LED, red, and green light treatments. Growth rates decreased from
-4 to 8 h blue light photoperiod and exhibited no growth under
-photoperiods of 12 and 16 h. Blue light did not induce growth at 180
-µmol photons m^-2^ s^-1^ under any photoperiod; white LED and red light
-treatments only exhibited growth under the 8 h photoperiod and growth
-rates increased with longer photoperiods under green light. The µ~max~
+The growth rates of *P. marinus* MIT9313, Clade LLIV increased with longer
+photoperiods under low 30 µmol photons m^-2^ s^-1^ peak PAR, under 250 µM O~2~ (Figure
+\@ref(fig:MIT9313PAR)).
+Under intermediate 90 µmol photons m^-2^ s^-1^ peak PAR growth rates decreased with increasing blue light photoperiod.
+Blue light did not induce growth at 180 µmol photons m^-2^ s^-1^ peak PAR, while cells shows only marginal growth under white LED and red light under the 8 h photoperiod .
+The µ~max~
 was
@@
 
-Similar to the growth trends of the 250 µM O~2~ and PAR of 30 µmol
-photons m^-2^ s^-1^ experiments, MIT9313 maintained at 25 µM O~2~,
-growth rate increased with increasing photoperiods for all spectral
-wavebands tested (Figure \@ref(fig:MIT9313PAR)). The 25 µM O~2~ growth
-experiments showed generally similar growth rate as the 250 µM O~2~ and
-PAR of 30 µmol photons m^-2^ s^-1^, with the interesting exception that
-the growth rate increased by 50% under 25 µM O~2~ and 16 h blue light
-photoperiod. In contrast to the blue light growth responses under 250 µM
-O~2~ and PAR of 90 µmol photons m^-2^ s^-1^, growth rate increased with
-longer photoperiods and even grew under 12 and 16 h photoperiods. In
-fact, the fastest growth rate of all the O~2~ experiments was
-`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "25", Photoperiod == 16, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
-d^-1^ achieved under 16 h blue light
-photoperiod and PAR of 90 µmol photons m^-2^ s^-1^ under 25 µM O~2~.
-Growth rate increased by 50% under the 4 h blue light photoperiod; by
-400% under the 8 h blue light photoperiod; by 40% under the 12 h red
-light photoperiod and by 80% under the 16 h white LED photoperiod,
-compared to the 250 µM O~2~ and PAR of 90 µmol photons m^-2^ s^-1^
-growth experiments. In contrast to the 250 µM O~2~ growth experiments,
-MIT9313 was able to grow when exposed to PAR of 180 µmol photons m^-2^
+For MIT9313 maintained at 25 µM O~2~ growth rate increased with increasing photoperiods for all spectral wavebands tested (Figure \@ref(fig:MIT9313PAR)).
+Under peak PAR of 90 µmol photons m^-2^ s^-1^ growth rate increased with
+longer photoperiods, with the fastest overall growth rate for MIT9313 
+`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "25", Photoperiod == 16, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 16 h blue light
+photoperiod. In contrast to the 250 µM O~2~ growth experiments,
+MIT9313 grew when exposed to peak PAR of 180 µmol photons m^-2^
 s^-1^ and blue light under all photoperiods except 16 h; additionally,
 white LED and red light treatments induced growth across all tested
-photoperiods under 25 µM O~2~.
-
-The 25 µM O~2~, 4 h photoperiod experiments under white LED light and
-all green light were not performed due to time constraints.
+photoperiods under 25 µM O~2~. The 25 µM O~2~, 4 h photoperiod experiments under white LED light and were not performed due to time constraints.
 
@@
 
-The growth experiments under 2.5 µM O~2~ for MIT9313 showed growth
-responses for all spectral wavebands except white LED light, albeit
-slower than under the 25 µM O~2~ experiments (Figure
-\@ref(fig:MIT9313PAR)). MIT9313 was able to grow under PAR of 30 µmol
-photons m^-2^ s^-1^ but only under an 8 h blue and red light
-photoperiod. Growth rate increased with longer photoperiods under blue
-light treatments and PAR of 90 µmol photons m^-2^ s^-1^ however, growth
-was inhibited under a 16 h blue light photoperiod and only grew under an
-8 h photoperiod under red and green light treatments. The growth rate
+Under 2.5 µM O~2~  MIT9313 showed growth, particularly under blue LED light, albeit
+generally slower than under the parallel 25 µM O~2~ experiments (Figure
+\@ref(fig:MIT9313PAR)).
+Growth estimates did, however, show scatter among replicates, suggesting the 2.5 µM O~2~  was near the tolerance limit for growth of  MIT9313.
+Growth rates increased with longer photoperiods under blue
+light treatments under peak PAR of 90 µmol photons m^-2^ s^-1^ . Growth 
 for MIT9313 under PAR of 180 µmol photons m^-2^ s^-1^ and blue light
-treatment decreased with increasing photoperiods with growth inhibition
-under a 16 h photoperiod. The red light treatments under PAR of 180 µmol
-photons m^-2^ s^-1^ showed similar growth rate for 8 and 12 h
-photoperiods and no growth were observed for green light treatments. The
-µ~max~ was
-`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "2.5", Photoperiod == 4, Par_ue == 180) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
-d^-1^ achieved under 4 h blue light
-photoperiod and PAR of 180 µmol photons m^-2^ s^-1^.
+treatment decreased with increasing photoperiods with full growth inhibition
+under a 16 h photoperiod. The red light peak PAR of 180 µmol
+photons m^-2^ s^-1^ showed similar growth rates for 8 and 12 h
+photoperiods. The µ~max~ was
+`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "2.5", Photoperiod == 4, Par_ue == 180) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 4 h blue light
+photoperiod and PAR of 180 µmol photons m^-2^ s^-1^.  XXXXTHIS DOES NOT LOOK correct; 12 h, 90 uE photons blue light looks higher.
 

### 2024-02-21 Code/ManuscriptPURFits.Rmd

@@
 
-AllPURFITPlot <- AllFitsCombined |>
+AllStrainPurFitsPlots <- AllFitsCombined |>
   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
@@
 
-AllPURFITPlot
+AllStrainPurFitsPlots
 
@@
 
-ggsave(file = file.path(PlotsOut, paste("AllPURFITPlot",".png",sep = "")), plot = AllPURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-ggsave(file = file.path(PlotsOut, paste("AllPURFITPlot",".tiff",sep = "")), plot = AllPURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("AllStrainPurFitsPlots",".png",sep = "")), plot = AllStrainPurFitsPlots, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+ggsave(file = file.path(PlotsOut, paste("AllStrainPurFitsPlots",".tiff",sep = "")), plot = AllStrainPurFitsPlots, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
 

### 2024-02-21 Code/ManuscriptPURFits.Rmd
Fixed fig caption for PAR and PUR plots to follow same format as Ocean detection plots (describe rows before columns)

@@
   ggplot() +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.5, alpha = 1.0) +
-    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 0.5, alpha = 0.8) +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 3, alpha = 1.0) +
+    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.0, alpha = 0.8) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.75, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
@@
   scale_x_continuous(label=scientific_10) +
-  scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.00)) +
+  scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
   scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
@@
   theme_bw() +
-   theme( strip.text = element_text(size = 10),
-        axis.title.y = element_text(color = "black", size = 12,  hjust = 0.40),
-        axis.title.x = element_text(color = "black", size = 12),
-        axis.text.x = element_text(size = 10, color = "black", angle = 45, hjust = 1.0),
-        axis.text.y = element_text(size = 9, color = "black", angle = 0, hjust = 1.0),
-        strip.background=element_rect(color="grey87", fill = "grey82"),
+   theme( strip.text = element_text(size = 25),
+        axis.title.y = element_text(color = "black", size = 30,  hjust = 0.40),
+        axis.title.x = element_text(color = "black", size = 30),
+        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
+        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
+        # strip.background=element_rect(color="grey87", fill = "grey82"),
         # strip.background=element_rect(fill = "white"), 
@@
         legend.key.width = unit(0.1, 'cm'), #change legend key width
-        legend.title =  element_text(size = 10),  #change legend title font size
-        legend.text = element_text(size = 10),   #change legend text font size
+        legend.title =  element_text(size = 25),  #change legend title font size
+        legend.text = element_text(size = 25),   #change legend text font size
         legend.position = "top") +
@@
 
+# This labels each pane with a letter but turns of the dacet labels
+# AllStrainPurFitsPlots <- tag_facet(AllStrainPurFitsPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
+
 ```

### 2024-02-21 Code/Manuscript_O2.Rmd
Fixed fig caption for PAR and PUR plots to follow same format as Ocean detection plots (describe rows before columns)

--- 2024-02-21 Code/Manuscript_O2.Rmd
@@
 MED4PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade) vs. photoperiod (h).  **",
-
-                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
+                    "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
+                       "Columns show 3 levels of growth Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^",
                     "Colors represent the actinic spectral waveband (nm).",
@@
 SS120PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low-Light (LLIII) deep ocean clade) vs. photoperiod (h). **",
-
-                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
+                     "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
+                       "Columns show 3 levels of growth Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^",
                     "Colors represent the actinic spectral waveband (nm).",
@@
 MIT9313PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
-
-                    "3 levels of growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) are in columns;  3 levels of imposed growth dissolved O~2~ concentrations (µM) are in rows.",
+                       "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
+                       "Columns show 3 levels of growth Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^",
                     "Colors represent the actinic spectral waveband (nm).",
@@
 AllStrainPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
-                    "**A.** MED4 High-Light I ecotype under 250, 25, or 2.5 µM of O~2~.",
-                    "**B.** SS120 Low-Light II/III (LLII/III) ecotype under 250, 25, or 2.5 µM of O~2~.",
-                    "**C.** MIT9313 Low-Light IV (LLIV) ecotype under 250, 25, or 2.5 µM of O~2~.",
-                    "3 levels of imposed dissolved O~2~ concentrations (µM) are in rows for each strain.",
+                    "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
+                    "Columns are strains; MED4, SS120 and MIT9313.",
                     "Shapes show the imposed photoperiod (h); 4 h (hollow inverted triangle),  8 h (solid diamond), 12 h (solid circle), 16 h (solid upright triangle).",
@@
                     "Platt (add Platt citation here) 4 parameter model fit to data pooled for each combination of strain and dissolved oxygen shown with solid lines.
-Seperate models fit to photoperiod data and shown if significantly different from the pooled model; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).
-",
+Seperate models fit to photoperiod data and shown if significantly different from the pooled model; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).",
                        .sep = " ")

### 2024-02-21 Code/Manuscript_O2.Rmd
GAM results text edits.

--- 2024-02-21 Code/Manuscript_O2.Rmd
@@
 
-## *Prochlorococcus marinus* growth responses to photoperiod, PAR and O~2~
+## *Prochlorococcus marinus* growth responses to photoperiod, PAR, spectral bands,  and O~2~
 
@@
 
-#### Generalized Additive Model (GAM) of MED4 growth {.unnumbered}
+## Generalized Additive Models (GAM) of *Prochlorococcus marinus* growth responses to photoperiod, PAR, spectal bands and O~2~   {.unnumbered}
 
@@
 
-Due to the complex interactions of light level and photoperiod, a GAM
-was employed (Figure \@ref(fig:MED4GAM)) to model the growth trends
-of MED4 in response to changing blue and red light PAR and photoperiod, across
-the 3 different imposed oxygen concentrations. Under 250 µM O~2~, Figure
-\@ref(fig:MED4GAM)A showed that the fastest growth rates were
-achieved above 90 µmol photons m^-2^ s^-1^ and photoperiods greater than
-12 h, indicated by the contour line labeled 0.62 d^-1^ (representing the
-90^th^ percentile of achieved growth rate). Figure
-\@ref(fig:MED4GAM)A also illustrated that MED4 exploited all light
-levels as long as the photoperiods were longer than 4 h, albeit at
-slower growth rate at lower PAR and shorter photoperiods. Under 25 µM
-O~2~, MED4 grew, but required longer than 4 h photoperiod (Figure
-\@ref(fig:MED4GAM)B). Interestingly, the GAM illustrated no
-difference in growth rate when MED4 was grown under 25 µM or 250 µM O~2~
-with photoperiods greater than 12 h. Figure \@ref(fig:MED4GAM)C
-showed that MED4 did not grow under the tested conditions at 2.5 µM
-O~2~.
+We employed GAM to summarize and visualize th complex responses of growth to the interactions of peak PAR, oxygen, photoperiod and blue vs. red spectral bands
+
+### MED4 Clade HLI
+The GAM model in Figure \@ref(fig:MED4GAM) shows MED4 growth in response to red (A) or blue (B) peak PAR and photoperiod across 2 imposed oxygen concentrations.
+Under 250 µM O~2~ MED4 achieved fastest growth rates above peak blue light of ~180 µmol photons m^-2^ s^-1^, and the longest photoperiod of 16, indicated by the 0.69 d^-1^ contour line representing the
+90^th^ percentile of maximum achieved growth rate.
+Growth decreased with decreasing photoperiod and peak PAR.
+Under red light growth was generally slower but the pattern of growth responses to photoperiod and PAR waas similar.
+We again note the exclusion of MED4 from growth under 4 h photoperiod.
+Under 25 µM O~2~ MED4 showed similar growth responses, but was excluded from both 4 and 8 h photoperiods.
 
@@
 
-MED4GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 grown under 660 nm (red) and 450 nm (blue) light.**",
+MED4GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 grown under 660 nm (red) or 450 nm (blue) light.**",
                     "X-axis is photoperiod (h).",
@@
 
-#### Generalized Additive Model (GAM) of SS120 growth {.unnumbered}
+### SS120 Clade Clade LLIII  {.unnumbered}
 
@@
 
-The GAM model in Figure \@ref(fig:SS120GAM) displays the growth
-trends of SS120 in response to changing blue light PAR and photoperiod,
-across the 3 different imposed oxygen concentrations. Under 250 µM O~2~,
-Figure \@ref(fig:SS120GAM)A illustrated that the fastest growth
-rates were achieved below PAR of 50 µmol photons m^-2^ s^-1^ and
+The GAM model in Figure \@ref(fig:SS120GAM) shows growth
+responses of SS120 red (A) or blue (B) peak PAR and photoperiod,
+across the 2 imposed oxygen concentrations. Under 250 µM O~2~,
+Figure \@ref(fig:SS120GAM)A showed highest growth
+rates achieved below PAR of 50 µmol photons m^-2^ s^-1^ and
 photoperiods between 8 and 12 h, indicated by the contour line labeled
 0.29 d^-1^ (representing the 90^th^ percentile of achieved growth rate).
-Figure \@ref(fig:SS120GAM)A also showed that SS120 does not grow at
-PAR above 90 µmol photons m^-2^ s^-1^ and the growth rate are slower as
-photoperiods go above 12 or below 8 h. Under 25 µM O~2~, SS120 grew
-under a photoperiod of 8 h and exploited all light levels and grew under
-a 12 h photoperiod but at PAR of 50 µmol photons m^-2^ s^-1^. The
-fastest growth rate achieved was at a higher PAR of \~100 µmol photons
+Note the disjunct regions of the plots, resulting from variable growth successes of SS120 under 250 µM O~2~.
+Growth rate patterns under red light were similar, although somehwat faster.
+In contrast, under 25 µM O~2~ and a photoperiod of 8 h SS120 exploited all blue peak PAR levels, achieving faster growth ratesat a higher PAR of \~100 µmol photons
 m^-2^ s^-1^, indicated by the contour line labeled 0.5 d^-1^
 (representing the 90^th^ percentile of achieved growth rate), out pacing
-the 90^th^ percentile fastest growth rates under 250 µM O~2~. Figure
-\@ref(fig:SS120GAM)C showed that SS120 did not grow under the tested
-conditions at 2.5 µM O~2~.
+the 90^th^ percentile fastest growth rates under 250 µM O~2~.
+Under red light and 25 µM O~2~ light SS120 grew across most conditions of peak PAR and photoperiod, achieving fastest growhth under long photoperiods and peak PAR below 50 \~100 µmol photons
+m^-2^ s^-1^.  Thus, the designation of SS120 as a LL strain is dependent upon the [O~2]. SS120 did not, however,  grow under tested conditions at 2.5 µM O~2~.
 
@@
 
-SS120GAM_cap <- glue("**Contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 grown under 660 nm (red) and 450 nm (blue) light.**",
+SS120GAM_cap <- glue("**Contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 grown under 660 nm (red) or 450 nm (blue) light.**",
                     "X-axis is photoperiod (h).",
@@
 
-#### Generalized Additive Model (GAM) of MIT9313 growth {.unnumbered}
-
-XXX Fig letters do not match as now we have red GAMs. Below is results for Blue GAMsXXXX
-
-The GAM model in Figure \@ref(fig:MIT9313GAM) displays the growth
-trends of MIT9313 in response to changing blue light PAR and
-photoperiod, across the 3 different imposed oxygen concentrations. Under
-250 µM O~2~, Figure \@ref(fig:MIT9313GAM)A illustrated that the
-fastest growth rates were achieved between PAR of 30 µmol photons m^-2^
+### MIT9313 Clade LLIV {.unnumbered}
+
+The GAM model in Figure \@ref(fig:MIT9313GAM) shows MIT9313 growth responses to red (A) or blue (B) peak PAR and photoperiod. Under 250 µM O~2~,  Figure \@ref(fig:MIT9313GAM)A shows MIT9313 achieves
+fastest growth rates between blue peak PAR of 30 µmol photons m^-2^
 s^-1^ and 50 µmol photons m^-2^ s^-1^ and photoperiods longer than 8 h,
-indicated by the contour line labeled 0.51 d^-1^ (representing the
-90^th^ percentile of achieved growth rates). Figure
-\@ref(fig:MIT9313GAM)A also illustrated that growth rate increases
-with longer photoperiods, as long as the PAR levels are below 50 µmol
-photons m^-2^ s^-1^ and that MIT9313 does not grow when exposed to PAR
-levels above 90 µmol photons m^-2^ s^-1^. In contrast to the 250 µM O~2~
-growth experiment, MIT9313 was able to exploit all actinic PAR levels
-(Figure \@ref(fig:MIT9313GAM)B). Interestingly, the growth rate was
-similar across all PAR levels between 4 and 12 h photoperiods, indicated
-by the contour line labeled 0.29 d^-1^ (representing the 10^th^
-percentile of achieved growth rate) and 0.44 d^-1^ (representing the
-50^th^ percentile of achieved growth rate) (Figure
-\@ref(fig:MIT9313GAM)B). However, for photoperiods exceeding 12 h,
-the growth rate showed a decline at higher PAR levels but showed the
-overall fastest growth rate achieved was at PAR levels less than 100
-µmol photons m^-2^ s^-1^, indicated by the contour line labeled 0.69
-d^-1^ (representing the 90^th^ percentile of achieved growth rate)
+indicated by the contour line labeled 0.51 d^-1^ representing the
+90^th^ percentile of achieved growth rates. Figure
+\@ref(fig:MIT9313GAM)A also shows that growth rate increases
+with longer photoperiods, as long as the blue peak PAR levels remain below 50 µmol
+photons m^-2^ s^-1^.
+In contrast, under red light and 250 µM O~2~ MIT9313 grows faster while exploiting higher peak PAR and longer photoperiods.
+Thus the designation of MIT9313 as a LL clade is dependent upon [O2].
 (Figure \@ref(fig:MIT9313GAM)B).  Figure \@ref(fig:MIT9313GAM)C
-showed that MIT9313 is capable of growing under 2.5 µM O~2~ as long as
-the photoperiod is between 4 and 8 h and between 50 to 150 µmol photons
-m^-2^ s^-1^ PAR levels (Figure \@ref(fig:MIT9313GAM)C).
+shows that MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 4 and 8 h and peak blue PAR between 50 to 10 µmol photons
+m^-2^ s^-1^ PAR (Figure \@ref(fig:MIT9313GAM)C).
 
@@
 
-MIT9313GAM_cap <- glue("**Contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 grown under 660 nm (red) and 450 nm (blue) light.**",
+MIT9313GAM_cap <- glue("**Contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 grown under 660 nm (red) or 450 nm (blue) light.**",
                     "X-axis is photoperiod (h).",

### 2024-02-21 Code/Manuscript_O2.Rmd
Added a bit more to protein materila and methods

--- 2024-02-21 Code/Manuscript_O2.Rmd
@@
 
-Protein samples were thawed and placed in 2 mL FastPrep®-24 bead lysing matrix D vials (MP Biomedicals, Irvine, CA, USA; SKU 116913050) with 200 uL of 1X protein extraction buffer (0.0281 mol L^−1 TRIS base buffer, 0.0211 mol L^−1 TRIS HCl buffer, 0.0735 mol L^−1 lithium dodecyl sulfate, 1.08 mol L^−1 glycerol, 0.5 mmol L^−1 ethylenediaminetetraacetic acid, 0.1 mg·mL−1 PefaBloc SC (AEBSF) protease inhibitor) [@brownFluxCapacitiesAcclimation2008]  XXX note we used a low tris PEB recipe not sure where it came from XXX.
+Protein samples were thawed and placed in 2 mL FastPrep®-24 bead lysing matrix D vials (MP Biomedicals, Irvine, CA, USA; SKU 116913050) with 200 uL of 1X protein extraction buffer (0.0281 mol L^−1^ TRIS base buffer, 0.0211 mol L^−1^ TRIS HCl buffer, 0.0735 mol L^−1^ lithium dodecyl sulfate, 1.08 mol L^−1^ glycerol, 0.5 mmol L^−1^ ethylenediaminetetraacetic acid, 0.1 mg·mL−1 PefaBloc SC (AEBSF) protease inhibitor) [@brownFluxCapacitiesAcclimation2008]  XXX note we used a low tris PEB recipe not sure where it came from (citation??) XXX.
 Cells were lysed for 3 cycles of 60 seconds at 6.5m s-1 with 60 second intervals on ice between cycles.
-The lysing vials were centrifuged at 16100g for 5 minutes, the supernatant was transferred to a 600 uL microcentrifuge tube and centrifuged again at 16100g for 3 minutes.
+The lysing vials were centrifuged at 16100g using XXXXXX centrifuge ( reference here    ) for 5 minutes, the supernatant was transferred to a 600 uL microcentrifuge tube and centrifuged again at 16100g for 3 minutes.
 40 µL of the supernatant were subsampled into labeled vials and stored at -80 °C until analysis.
-The bicinchoninic acid (BCA) assay was used for total protein determination using a calibration curve of bovine gamma globulin (BGG; Bio-Rad, Hercules, CA, USA) standard ranging from 0 to 1.0 mg mL^-1 range.
+The bicinchoninic acid (BCA) assay was used for total protein determination using a calibration curve of bovine gamma globulin (BGG; Bio-Rad, Hercules, CA, USA) standard ranging from 0 to 1.0 mg mL^-1^ range.
 
 All samples and appropriate standards were prepared as described in [@brownFluxCapacitiesAcclimation2008].
+Standards were obtained from Agrisera (Vännäs, Sweden; FtsH AS11 1789S; PsbA AS01 016S; PetC AS08 330S; PsaC AS04 042S; RbcL AS01 017S).
 Between 0.1 to 4.0 µg of total protein was loaded onto 15 well Invitrogen Bolt 4-12% acrylamide Bis-Tris gels (ThermoFisher Scientific, Waltham, MA, USA).
@@
 Blots were blocked overnight in 2% ECL blocking solution as described by @brownFluxCapacitiesAcclimation2008.
-The following morning, each blot was incubated in their appropriate antibody obtained from Agrisera (Vännäs, Sweden; FtsH  1:5,000 dilution, AS11 1789; PsbA  1:10000 dilution, AS05 084; PetC 1:XXXXX dilution, ASXXXXX; PsaC 1:XXXXXX dilution, ASXXXXXXX ; RbcL 1:10000 dilution, AS03 037) and a 1:15000 dilution of the secondary antibody, goat anti-rabbit HRP conjugated (Bio-Rad, Hercules, CA, USA; SKU 1706515, lot 64230791).
+The following morning, each blot was incubated in their appropriate antibody obtained from Agrisera (Vännäs, Sweden; FtsH  1:5,000 dilution, AS11 1789; PsbA  1:10000 dilution, AS05 084; PetC 1:XXXXX dilution, AS08 330; PsaC 1:XXXXXX dilution, AS10 939; RbcL 1:10000 dilution, AS03 037) and a 1:15000 dilution of the secondary antibody, goat anti-rabbit HRP conjugated (Bio-Rad, Hercules, CA, USA; SKU 1706515, lot 64230791).
 Blots were incubated in Amersham ECL Select chemiluminescent substrate (Danaher, Washington, DC, USA) and imaged in a Bio-Rad VersaDoc imager (Bio-Rad, Hercules, CA, USA).
@@
 
-# Results and Discussion {.unnumbered}
+# Results and discussion {.unnumbered}
 
@@
 
-XXXX Mireille to finish Fig. caption  XXX
+XXXX Mireille to finish Fig. caption when figure is complete. Add color ? Remove []? XXX
 ```{r MED4ProteinAnnotated, fig.cap = MED4ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
@@
 
-XXXX Mireille to finish Fig. caption  XXX
+XXXX Mireille to finish Fig. caption when figure is complete. Add color ? Remove []? XXX
 ```{r MIT9313ProteinAnnotated, fig.cap = MIT9313ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
@@
 MIT9313ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade).  **",
-
                                     "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",

### 2024-02-21 Code/Manuscript_O2.Rmd
added {.unnumbered} to all headings

@@
 
-## Detection of *Prochlorococcus* proteins across O~2~ and light niches in the ocean
+## Detection of *Prochlorococcus* proteins across O~2~ and light niches in the ocean  {.unnumbered}
 
@@
 
-## *Prochlorococcus marinus* growth responses to photoperiod, PAR, spectral bands,  and O~2~
+## *Prochlorococcus marinus* growth responses to photoperiod, PAR, spectral bands,  and O~2~  {.unnumbered}
 
@@
 
-### MED4 Clade HLI
+### MED4 Clade HLI  {.unnumbered}
 The GAM model in Figure \@ref(fig:MED4GAM) shows MED4 growth in response to red (A) or blue (B) peak PAR and photoperiod across 2 imposed oxygen concentrations.
@@
 
-# Acknowledgements
+# Acknowledgements  {.unnumbered}
 Jonah Sheinin assisted with growth of some cultures for protein analyses, while Carlie Barnhill assisted with code for import of multicultivator growth data files.
 
-# Funding
+# Funding  {.unnumbered}
 To Be Entered through PLoSONe system and deleted here

### 2024-02-21 Code/Manuscript_O2.Rmd
PUR results edited

--- 2024-02-21 Code/Manuscript_O2.Rmd
@@
 
-Protein samples were thawed and placed in 2 mL FastPrep®-24 bead lysing matrix D vials (MP Biomedicals, Irvine, CA, USA; SKU 116913050) with 200 uL of 1X protein extraction buffer (0.0281 mol L^−1^ TRIS base buffer, 0.0211 mol L^−1^ TRIS HCl buffer, 0.0735 mol L^−1^ lithium dodecyl sulfate, 1.08 mol L^−1^ glycerol, 0.5 mmol L^−1^ ethylenediaminetetraacetic acid, 0.1 mg·mL−1 PefaBloc SC (AEBSF) protease inhibitor) [@brownFluxCapacitiesAcclimation2008]  XXX note we used a low tris PEB recipe not sure where it came from (citation??) XXX.
+Protein samples were thawed and placed in 2 mL FastPrep®-24 bead lysing matrix D vials (MP Biomedicals, Irvine, CA, USA; SKU 116913050) with 200 uL of 1X protein extraction buffer (0.0281 mol L^−1 TRIS base buffer, 0.0211 mol L^−1 TRIS HCl buffer, 0.0735 mol L^−1 lithium dodecyl sulfate, 1.08 mol L^−1 glycerol, 0.5 mmol L^−1 ethylenediaminetetraacetic acid, 0.1 mg·mL−1 PefaBloc SC (AEBSF) protease inhibitor) [@brownFluxCapacitiesAcclimation2008]  XXX note we used a low tris PEB recipe not sure where it came from XXX.
 Cells were lysed for 3 cycles of 60 seconds at 6.5m s-1 with 60 second intervals on ice between cycles.
-The lysing vials were centrifuged at 16100g using XXXXXX centrifuge ( reference here    ) for 5 minutes, the supernatant was transferred to a 600 uL microcentrifuge tube and centrifuged again at 16100g for 3 minutes.
+The lysing vials were centrifuged at 16100g for 5 minutes, the supernatant was transferred to a 600 uL microcentrifuge tube and centrifuged again at 16100g for 3 minutes.
 40 µL of the supernatant were subsampled into labeled vials and stored at -80 °C until analysis.
-The bicinchoninic acid (BCA) assay was used for total protein determination using a calibration curve of bovine gamma globulin (BGG; Bio-Rad, Hercules, CA, USA) standard ranging from 0 to 1.0 mg mL^-1^ range.
+The bicinchoninic acid (BCA) assay was used for total protein determination using a calibration curve of bovine gamma globulin (BGG; Bio-Rad, Hercules, CA, USA) standard ranging from 0 to 1.0 mg mL^-1 range.
 
 All samples and appropriate standards were prepared as described in [@brownFluxCapacitiesAcclimation2008].
-Standards were obtained from Agrisera (Vännäs, Sweden; FtsH AS11 1789S; PsbA AS01 016S; PetC AS08 330S; PsaC AS04 042S; RbcL AS01 017S).
 Between 0.1 to 4.0 µg of total protein was loaded onto 15 well Invitrogen Bolt 4-12% acrylamide Bis-Tris gels (ThermoFisher Scientific, Waltham, MA, USA).
@@
 Blots were blocked overnight in 2% ECL blocking solution as described by @brownFluxCapacitiesAcclimation2008.
-The following morning, each blot was incubated in their appropriate antibody obtained from Agrisera (Vännäs, Sweden; FtsH  1:5,000 dilution, AS11 1789; PsbA  1:10000 dilution, AS05 084; PetC 1:XXXXX dilution, AS08 330; PsaC 1:XXXXXX dilution, AS10 939; RbcL 1:10000 dilution, AS03 037) and a 1:15000 dilution of the secondary antibody, goat anti-rabbit HRP conjugated (Bio-Rad, Hercules, CA, USA; SKU 1706515, lot 64230791).
+The following morning, each blot was incubated in their appropriate antibody obtained from Agrisera (Vännäs, Sweden; FtsH  1:5,000 dilution, AS11 1789; PsbA  1:10000 dilution, AS05 084; PetC 1:XXXXX dilution, ASXXXXX; PsaC 1:XXXXXX dilution, ASXXXXXXX ; RbcL 1:10000 dilution, AS03 037) and a 1:15000 dilution of the secondary antibody, goat anti-rabbit HRP conjugated (Bio-Rad, Hercules, CA, USA; SKU 1706515, lot 64230791).
 Blots were incubated in Amersham ECL Select chemiluminescent substrate (Danaher, Washington, DC, USA) and imaged in a Bio-Rad VersaDoc imager (Bio-Rad, Hercules, CA, USA).
@@
 
-# Results and discussion {.unnumbered}
+# Results and Discussion {.unnumbered}
 
@@
 
-## Discussion PAR and growth trends {.unnumbered}
-
-The purpose of this study was to determine the interactive effects of
-photoperiod, PAR level, spectral bandwidth and dissolved [O~2~] regimes
-on the growth of *P. marinus*, under simulated present day and
-hypothetical future ecological niches.
-
-### Photoperiod {.unnumbered}
+### Growth Responses to Photoperiod {.unnumbered}
 
 The representative of HLI clade, *P. marinus* MED4, was completely
-excluded from growth under the 4 h photoperiod, and then showed
-increasing growth rate with increasing photoperiod. Thus, MED4 can
+excluded from growth under the 4 h photoperiod, andshowed
+increasing growth rates with increasing photoperiod. Thus, MED4 can
 potentially exploit longer summer photoperiods in temperate zones, but
-will remain excluded from growth in winter through its requirement for
-more than 4 h of light per day.
+will likely remain excluded from growth in winter through its requirement for
+more than 4 h of light per day, even if water temperature warms into the Clade HLI tolerance range.
 
@@
 Therefore, SS120 can potentially exploit the longer summer photoperiods
-in temperate zones but cannot sustain growth in winter through its
-requirement for more than 4 h of light per day.
+in temperate zones but again cannot sustain growth in winter through its
+requirement for more than 4 h of light per day, even if water temperature warms into the Clade LLIII tolerance range.
 
@@
 
-### PAR Levels {.unnumbered}
+### Growth Responses to Peak PAR Responses {.unnumbered}
 
@@
 under all PAR levels, so long as the photoperiod was longer than 4 h,
-although growth rate were slower under the lowest PAR level of 30 µmol
+although growth rates were slow under the lowest PAR level of 30 µmol
 photons m^-2^ s^-1^. Considering the range of PAR levels that MED4 can
@@
 characterized by lower light levels, subject to the limitation of a
-photoperiod of at least 4 h even after depth attenuation. The photo
+photoperiod of at least 4 h even after depth attenuation of light. The photo
 regimes of winter temperate zones, due to shorter photoperiods, exclude
@@
 The representative of HLI clade, *P. marinus* MED4, grew under all
-spectral wavebands, but grew slower under green light. Growth rates were
+tested spectral wavebands. Growth rates were
 generally comparable under blue, white LED and red lights when exposed
@@
 wavebands. Generally, growth was strongly inhibited under PAR of 180
-µmol photons m^-2^ s^-1^ for all spectral wavebands except for green 16
-h photoperiod. The ability of SS120 to grow under low blue light and
-longer photoperiods, makes the deep ocean waters of the temperate zone a
-viable potential habitat. SS120 is constrained to deeper ocean waters
-through its intolerance of higher blue PAR levels.
+µmol photons m^-2^ s^-1^ for all spectral wavebands.
+The ability of SS120 to grow under low blue light and longer photoperiods, makes the deep ocean waters of the temperate zone a viable potential habitat.
+Under 250 µM O~2~ SS120 is constrained to deeper ocean waters through its intolerance of higher blue PAR levels.
 
@@
 m^-2^ s^-1^ for all spectral wavebands except blue light. MIT9313 can
-thus exploit blue light in deep waters of temperate zones and can even
+thus exploit blue light in deeper waters of temperate zones and can even
 tolerate moderate depths to exploit higher blue light levels, as long as
@@
 
-The representative of HLI clade, *P. marinus* MED4, was able to grow
-under both 250 µM and 25 µM O~2~ treatments but was unable to grow under
-the lowest O~2~ level of 2.5 µM. MED4 generally exhibited similar growth
-response trends and growth rate under blue and red light treatments
-under both 25 µM and 250 µM of O~2~. This demonstrated ability to grow
+The representative of HLI clade, *P. marinus* MED4, generally exhibited similar growth
+response trends and growth rates under blue and red light treatments
+under both 25 µM and 250 µM of O~2~,  but was unable to grow under
+the lowest O~2~ level of 2.5 µM. MED4  This demonstrated ability to grow
 under 25 µM O~2~, coupled with its ability to grow under lower PAR
@@
 regions. Our findings were also consistent with
-@mattisonPhotosyntheticStrategiesWild2020 who analyzed the OceansMap
+FIGURE REFERENCE who analyzed the OceansMap
 Protein Portal (OPP) [@saitoDevelopmentOceanProtein2021] for proteins
@@
 
-The LLIII clade, *P. marinus* SS120, was able to grow under both 250 µM
-and 25 µM O~2~ treatments but only grew under 2.5 µM O~2~ with a red
-light photoperiod of 12 h. The growth responses under 250 µM and 25 µM
+The LLIII clade, *P. marinus* SS120 grew under both 250 µM
+and 25 µM O~2~ treatments. The growth responses under 250 µM and 25 µM
 O~2~ were very different under the higher PAR level treatments. As
@@
 under the 25 µM O~2~ treatments for all tested spectral wavebands and
-even grew under the highest PAR level of 180 µmol photons m^-2^ s^-1^,
+even grew under the highest peak PAR level of 180 µmol photons m^-2^ s^-1^,
 in contrast to growth inhibition under 250 µM O~2~ and 180 µmol photons
@@
 O~2~ of 25 µM, MIT9313 was able to grow under all blue light with
-photoperiods up to 12 h, along with growth under 2.5 µM O~2~ and some
-combinations of red and green light, across photoperiods. Given that
+photoperiods up to 12 h, along with growth under some
+combinations of red peak PAR, across photoperiods. Given that
 MIT9313 can grow under all photoperiods at the lowest blue light PAR of
 30 µmol photons m^-2^ s^-1^, all seasons in the temperate zones are
-potentially viable niches. Like SS120, MIT9313 has the capability to
-exploit different ocean water layers through its tolerance of higher
-light levels under lower [O~2~]. MIT9313 has a remarkable ability to
-thrive under very low [O~2~], potentially allowing it to expand into
-broader ecological niches. These results support the findings of
-@mattisonPhotosyntheticStrategiesWild2020 where PSI protein subunits
+potentially viable niches, if temperature rises into the Clade LLIV tolerance range.
+Like SS120, MIT9313 has the capability to exploit different ocean water layers through its tolerance of higher light levels under lower [O~2~].
+MIT9313 has a remarkable ability to thrive under very low [O~2~], potentially allowing it to expand into
+broader ecological niches. These results support 
+FIGUREXXXX where PSI protein subunits
 annotated as derived from MIT9313 were detected at depths \> 120 m,
@@
 when subjected to the highest PAR of 180 µmol photons m^-2^ s^-1^,
-MIT9313 grew when treated under white LED, red and green light and SS120
-grew under white LED and green light treatments. However, neither of
-these strains exhibited any growth under blue light conditions. Growth
+MIT9313 grew when treated under white LED and red light and SS120
+grew under white LED light. However, 
+these strains were excluded from growth under high blue peak PAR. Growth
 studies have demonstrated that LL clades experience growth inhibition at
 PAR levels between 150 and 200 µmol photons m^-2^ s^-1^
-[@moorePhotophysiologyMarineCyanobacterium1999]. In the subsequent
-chapter, we explore the physiological factors contributing to these
-divergent growth responses to different spectral wavebands.
+[@moorePhotophysiologyMarineCyanobacterium1999].
 
@@
 
-### Results PUR and growth trends {.unnumbered}
+## PUR and growth responses {.unnumbered}
 
 Cumulative diel absorbed PUR can potentially collapse photoperiod, PAR and spectral wavebands to a common metric of absorbed light.
-We then plot observed growth rate vs.
+We plot observed growth rate vs.
 cumulative diel absorbed PUR to determine whether growth is a simple response to absorbed light per day across imposed photoperiods and spectral wavebands, or whether photoperiod or spectral wavebands have specific or interactive influences on growth of each ecotype.
@@
 Due to the highly effective absorption of pigments in the blue spectral waveband range for all ecotypes, the maximum imposed cumulative diel absorbed PUR under blue light treatment is almost 3 times that of white LED light and about 6 times the red light treatment, despite being derived from the same imposed photoperiods and PUR regimes.
-As such, only growths rates treated under blue light extend beyond absorbed PUR of ~ 2 x 10^6^ µmol photons m^-2^ d^-1^.
-A full list of cumulative diel absorbed PUR (µmol photons m^-2^ d^-1^) for all imposed spectral wavebands, PAR and photoperiod regimes can be found in Table \@ref(tab:DailyPURTable).
-
-#### MED4 {.unnumbered}
-
-The representative of HLI clade, *P. marinus* MED4, showed no growth under any 4 h photoperiod treatments, even when a 4 h photoperiod delivered cumulative die
-equivalent to other photoperiod treatments.
-In parallel MED4 showed no growth under 2.5 µM O~2~, under the same level of diel cumulative absorbed PUR. 
-In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 showed a simple saturating response of growth to increasing cumulative diel absorbed PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:AllStrainPurFitsPlots)A).
-
-#### SS120 {.unnumbered}
+As such, only growths rates under blue light extend beyond absorbed PUR of ~ 2 x 10^6^ µmol photons m^-2^ d^-1^.
+
+#### MED4 Clade HLI {.unnumbered}
+
+The representative of HLI clade, *P. marinus* MED4, showed no growth under any 4 h photoperiod treatments, even when a 4 h photoperiod delivered cumulative diel PUR
+equivalent to other photoperiod treatments. In parallel MED4 showed no growth under 2.5 µM O~2~, no matter the level of diel cumulative absorbed PUR. 
+In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth was well described by a simple saturating response of growth to increasing cumulative diel absorbed PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:AllStrainPurFitsPlots)A).
+XXXXDISTINCT PHOTOPERIOD FITSXXXXX
+
+#### SS120 Clade LLIII {.unnumbered}
 
@@
 marinus* SS120 showed almost no growth under 2.5 µM O~2~ experiments.
-A majority of the 4 h photoperiod treatments did not grow under 250 µM O~2~ experiments despite having the same absorbed PUR dose as other experimental treatments.
-SS120 did not grow when exposed to more than about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of absorbed PUR under any spectral waveband or photoperiod combination under 250 µM O~2~ experiments(Figure \@ref(fig:AllStrainPurFitsPlots)B).
-
-Under both 25 or 250 µM O~2~ experiments, SS120 growth plateaued by about 5.0 x 10^5^ µmol photons m^-2^ d^-1^, with some scatter among photoperiod and spectral waveband regimes.
+A majority of the 4 h photoperiod treatments did not grow under 250 µM O~2~ experiments even when a 4 h photoperiod delivered the cumulative diel PUR equivalent to other as other photoperiod treatments.
+SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ experiments(Figure \@ref(fig:AllStrainPurFitsPlots)B).
+
+Under both 25 or 250 µM O~2~ experiments, SS120 growth plateaued by about 5.0 x 10^5^ µmol photons m^-2^ d^-1^ diel PUR, with some scatter among photoperiod and spectral waveband regimes.
 The onset of growth inhibition extended to higher cumulative diel absorbed PUR for cultures growing under 25 µM O~2~.
-
-#### MIT9313  {.unnumbered}
+XXXXDISTINCT PHOTOPERIOD FITSXXXXX
+
+#### MIT9313 Clade LLIV {.unnumbered}
 
 The LLIV clade, *P.
-marinus* MIT9313, showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of absorbed PUR, with higher growth rate at over a narrower plateau under 25 and 250 µM O~2~, compared to a wider, flatter response to cumulative diel absorbed PUR under 2.5 µM O~2~.
-Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of absorbed PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands.
-In contrast, under 25 µM O~2~, MIT9313 showed a greatly extended exploitation of higher cumulative diel absorbed PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^.
-Similarly, under 2.5 µM O~2~, MIT9313 grew more slowly, but only showed full growth inhibition above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Figure \@ref(fig:AllStrainPurFitsPlots)C).
+marinus* MIT9313, showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR, with higher growth rates over a narrower plateau under 25 and 250 µM O~2~, compared to a wider, flatter response to cumulative diel  PUR under 2.5 µM O~2~.
+Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands.
+In contrast, under 25 µM O~2~, MIT9313 showed a greatly extended exploitation of higher cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^.
+Similarly, under 2.5 µM O~2~, MIT9313 grew more slowly, but only showed full growth inhibition above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:AllStrainPurFitsPlots)C).
+XXXXDISTINCT PHOTOPERIOD FITSXXXXX
 
@@
 The high Chl a~2~/Chl b~2~ ratio we observed for MED4 is characteristic of the HL clades and the lower Chl a~2~/Chl b~2~ ratios we observed for SS120 and MIT9313 are typical of the LL clades [@moorePhotophysiologyMarineCyanobacterium1999].
-The lower amounts of  absorbed PUR in the white LED and green waveband regions for MED4, in comparison to SS120 and MIT9313, are the result of higher Chl a~2~/Chl b~2~ content.
-Subsequently, calculating absorbed PUR allows direct and meaningful comparison of the energy absorbed by cells on a per photon basis across different wavebands.
-
-In the previous chapter, under 250 µM O~2~ treatments and all PAR of 90 and 180 µmol photons m^-2^ s^-1^ blue light treatments, *P.
+The lower PUR for the white LED waveband for MED4, in comparison to SS120 and MIT9313, are the result of higher Chl a~2~/Chl b~2~ content.
+Subsequently, estimating  PUR allows direct comparison of the energy absorbed by cells on a per photon basis across different wavebands.
+
+Under 250 µM O~2~ treatments and all PAR of 90 and 180 µmol photons m^-2^ s^-1^ blue light treatments, *P.
 marinus* SS120, exhibited growth inhibition but was able to exploit all other spectral wavebands under some photoperiods at these PAR levels.
@@
 
-In chapter 2, we analyzed  growth rates to determine the viability of *P. marinus* MED4, a clade HLI ecotype found at depths near the ocean surface,
+We analyzed  growth rates to determine the viability of *P. marinus* MED4, a clade HLI ecotype found at depths near the ocean surface,
 *P.
@@
 
-In chapter 3, we determined the Photosynthetic Usable Radiation (PUR), the portion of light radiation absorbed differentially by the pigments of the photosynthetic organism [@morelAvailableUsableStored1978] and expressed growth response in terms of cumulative diel PUR.
+We determined the Photosynthetic Usable Radiation (PUR), the portion of light radiation absorbed differentially by the pigments of the photosynthetic organism [@morelAvailableUsableStored1978] and expressed growth response in terms of cumulative diel PUR.
 We found that approximately 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of PUR is the maximum dosage that the representative LL clades, SS120 and MIT9313 can tolerate under 25 µM O~2~, in contrast to the representative HL clade, MED4 which exhibited growth saturation at the same cumulative diel PUR of 1.0 x 10^6^ µmol photons m^-2^ d^-1^.
@@
 
-XXXX Mireille to finish Fig. caption when figure is complete. Add color ? Remove []? XXX
+XXXX Mireille to finish Fig. caption  XXX
 ```{r MED4ProteinAnnotated, fig.cap = MED4ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
@@
 
-XXXX Mireille to finish Fig. caption when figure is complete. Add color ? Remove []? XXX
+XXXX Mireille to finish Fig. caption  XXX
 ```{r MIT9313ProteinAnnotated, fig.cap = MIT9313ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
@@
 MIT9313ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade).  **",
+
                     "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",

### 2024-02-21 Code/Manuscript_O2.Rmd

@@
 
-# Results and Discussion {.unnumbered}
-
-## Detection of *Prochlorococcus* proteins across O~2~ and light niches in the ocean
+# Results and discussion {.unnumbered}
+
+## Detection of *Prochlorococcus* proteins across O~2~ and light niches in the ocean  {.unnumbered}
 

### 2024-02-21 Code/Manuscript_O2.Rmd
Added more citations, fixed order of results figures

@@
 Some as yet uncultured *P.
-marinus* strains in clades LLV and LLVI thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021] (Lavin et al., 2010) ADDITIONAL REFS XXXX.
-(Johnson et al., 1999).
-@goerickeNovelNicheProchlorococcus2000
-[@garcia-robledoCrypticOxygenCycling2017a]. *P. marinus* LL ecotypes may indeed dominate the phytoplankton wihthin OMZ
+marinus* strains in clades LLV and LLVI thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021; @@lavinNovelLineagesProchlorococcus2010; @goerickeNovelNicheProchlorococcus2000; @garcia-robledoCrypticOxygenCycling2017a] (Johnson et al., 1999).
+*P.
+marinus* LL ecotypes may indeed dominate the phytoplankton within OMZ
 [@lavinNovelLineagesProchlorococcus2010;
-@ulloaCyanobacteriumProchlorococcusHas2021]
-[@partenskyProchlorococcusAdvantagesLimits2010].
+@ulloaCyanobacteriumProchlorococcusHas2021; @partenskyProchlorococcusAdvantagesLimits2010].
 
@@
 High-Light clades are  typically dominant picophytoplankton in near-surface, oligotrophic waters, characterized by high light levels.
-Clade HLI, including cultured strain MED4,is adapted to higher iron, and lower temperatures, and originated from the Mediterranean Sea, just 5 m below the surface (Partensky et al., 1999).
-Clade HLII adapted to higher iron, and higher temperatures, is the most abundant group in the North Atlantic and North Pacific Oceans, often constituting over 90% of the total population (Partensky et al., 1999),  and are most numerous around 50 m depth (Partensky et al., 1999).
+Clade HLI, including cultured strain MED4,is adapted to higher iron, and lower temperatures, and originated from the Mediterranean Sea, just 5 m below the surface [@partenskyProchlorococcusMarinePhotosynthetic1999].
+Clade HLII adapted to higher iron, and higher temperatures, is the most abundant group in the North Atlantic and North Pacific Oceans, often constituting over 90% of the total population [@partenskyProchlorococcusMarinePhotosynthetic1999],  and are most numerous around 50 m depth [@partenskyProchlorococcusMarinePhotosynthetic1999].
 Clade HLIII/IV is adapted to lower iron [@kentParallelPhylogeographyProchlorococcus2019; @johnsonNichePartitioningProchlorococcus2006; @zinserInfluenceLightTemperature2007].
 
-*P. marinus* clades are found  in environments beyond their optimal habitats. HL clades inhabit depths overlapping with LL ecotypes
+*Prochlorococcus marinus* clades are found  in environments beyond their optimal habitats. HL clades inhabit depths overlapping with LL ecotypes
 [@westNichePartitioningProchlorococcusPopulationsStratified1999;
@@
 We also aimed to detect whether growth responses are driven simply by cumulative diel absorbed PUR, or whether specific photoperiods, spectral bands or PAR levels have independent, albeit interacting, effects on growth.
-
-\newpage
-
-## Photosystem II maintenance as a limitation on *Prochlorococcus* growth {.unnumbered}
-
-*Prochlorococcus* remain challenging to culture, as their reduced genomes – the smallest of any known oxyphototroph – render them partially dependent upon mutualistic heterotrophic bacteria to  detoxify reactive oxygen species (Moore et al., 2007; Morris et al., 2008).
-MED4, SS120 and MIT9313 have been successfully cultured in laboratories, and used to show that ecotypic classifications correspond to biochemical differences among strains.
-CITATONS OUR LAB and OTHERS.
-
-Under full atmospheric [O~2~], LL clades of *Prochlorococcus* are restricted to growth under low light, in part because they suffer photoinhibition of Photosystem II (PSII) through several paths, including direct absorbance of UV or blue light, in parallel with generation of Reactive Oxygen Species (ROS) if the electron flow is slowed, [@aroPhotoinhibitionPhotosystemII1993], producing  damaging singlet oxygen (^1^O~2~).
-[@aroPhotoinhibitionPhotosystemII1993; @soitamoPhotoinhibitionMarinePicocyanobacteria2017] [@murphyPhotoinactivationPhotosystemII2017][@hakalaEvidenceRoleOxygenevolving2005].
-Repair of inhibited PSII process relies on the removal of damaged PsbA (Mann et al., 2000; Adam et al., 2005), followed by reassembly with newly synthesized PsbA [@nixonRecentAdvancesUnderstanding2010].
-Thus, degradation of PsbA is a rate-limiting step in recovery from photoinhibition (Kanervo et al., 1993), mediated largely by a heterohexamer of (FtsH12)3, a membrane-bound (Sacharz et al., 2015)(Zak et al., 2001) metalloprotease  (Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
-(Adam et al., 2005; Boehm et al., 2012) (Nixon et al.
-(2010)) (Komenda et al., 2007).
-(Pisareva et al., 2007; Sacharz et al., 2015),  (Mann et al., 2000), (AMANDA REF from ALGATECH).
-
-*Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4, homologous to the characterized FtsH isoforms of the model cyanobacterium *Synechocystis* FtsH, with presumably parallel functions (Table 1).
-Upon a shift to higher light HLIII MED4 upregulated expression of FtsH1 and FtsH2 (Bonisteel et al.
-(2018)), homologs to the *Synechocystis* slr0228 and slr1604, implicated in PSII repair.
-In contrast representative LLIV strain MIT9313 showed less overall expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem.
-Furthermore MIT9313 expressed primarily FtsH3, homologous to Sll1463 involved in PSI biogenesis, and FtsH expression did not increase in response to light stress.
-Through adaptation to steady low light, LLIV *Prochlorococcus* instead allocates resources processes other than dynamic regulation of PSII repair.
-
-```{r BuildFtsHtable, echo = FALSE}
-
-FtsHTable <- tibble(Organism = c("*Prochlorococcus marinus*", "*Synechocystis sp. PCC6803*", "Function"),
-                    FtsH1 = c("FtsH1", "SlrO22", "PSII Repair"),
-                    FtsH2 = c("FtsH2", "Slr1604", "PSII Repair"),
-                    FtsH3 = c("FtsH3", "Slr1463", "PSI biogenesis"),
-                    FtsH4 = c("FtsH4", "Slr1390", "Cell viability")
-                    )
-
-```
-
-```{r FtsHTable, fig.height = 6, fig.width = 10, include = TRUE, echo = FALSE}
-
-knitr::kable(FtsHTable,
-             caption = "FtsH protease homologs in *Prochlorococcus marinus* and the model cyanobacterium *Synechocystis* sp.
-PCC6803.
-Protein homology determined by multiple sequence alignment with MUSCLE followed by construction of maximum likelihood phylogenetic tree using 1000 bootstrap replicates in MEGAX.",
-              col.names =  c("Organism",
-                          "Homolog 1",
-                          "Homolog 2",
-                          "Homolog 3",
-                          "Homolog 4"),
-               align = "lcccc"
-             )
-```
 
@@
 
-```{r LabeledMC, fig.cap = LabeledMC_cap , fig.height = 8, fig.width = 6, echo = FALSE}
-
-LabeledMC_cap <- glue("**PSI MCMIX-OD Multicultivator.**",
-                      "Spectral wavebands and light levels are individually controlled for each culture tube.",
-                      "Real time Optical Density (OD) measurements eliminate intrusive subsampling of sterile cultures.",
-                      "The temperature of culture tubes are collectively controlled via heating or cooling of the aquarium water.",
-                      "Gas with specific oxygen concentrations is bubbled through a humidifier and passed through a 0.2 um filter.",
-
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "LabeledMC.png"))
-```
-
-\newpage
-
 ## MetaProteomics bioinformatic analyses and limitations  {.unnumbered}
@@
 ## Growth data management and analysis {.unnumbered}
-Data files (.csv) saved from the Multicultivator software were imported into R-Studio [@R-Studio] for data management [@R-tidyverse], growth rate calculations CITATION, comparisons of model fits CITATION, and generation of
+Data files (.csv) saved from the Multicultivator software were imported into R-Studio [@R-Studio] for data management [@R-tidyverse], growth rate calculations CITATION, comparisons of model fits (get Platt CITATION), and generation of
 figures using `ggplot2` [@R-ggplot2]. The chlorophyll proxy
@@
 
+\newpage
+
 ```{r PurParPlot, fig.cap = PurParPlot_cap , fig.height = 20, fig.width = 10, echo = FALSE}
@@
 PurParPlot_cap <- glue("**Absorbed peak Photosynthetically Usable Radiation (PUR) (µmol photons m^-2^ s^-1^) vs. peak Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^).**",
-                       "The correlation between PAR, plotted on the x-axis and absorbed PUR, plotted on the y-axis, are colored for each growth spectral waveband; blue for 450 nm, red for 660 nm and black for white LED full spectrum light.",
+                       "The correlation between PAR, plotted on the x-axis and absorbed PUR, plotted on the y-axis, are colored for each growth spectral waveband; 450 nm (blue circles), 660 nm (red circles) and white LED (black circles).",
                        "The grey dashed line represents a hypothetical one to one correlation.",
@@
 
-# Results and discussion {.unnumbered}
+# Results {.unnumbered}
 
@@
 spectrum, and light level, is poorly described.
+
+\newpage
 
@@
 
+XXX Fig letters do not match as now we have red GAMs. Below is results for Blue GAMsXXXX
+
+We employed GAM to summarize and visualize th complex responses of growth to the interactions of peak PAR, oxygen, photoperiod and blue vs. red spectral bands
+
+### MED4 Clade HLI  {.unnumbered}
+The GAM model in Figure \@ref(fig:MED4GAM) shows MED4 growth in response to red (A) or blue (B) peak PAR and photoperiod across 2 imposed oxygen concentrations.
+Under 250 µM O~2~ MED4 achieved fastest growth rates above peak blue light of ~180 µmol photons m^-2^ s^-1^, and the longest photoperiod of 16, indicated by the 0.69 d^-1^ contour line representing the
+90^th^ percentile of maximum achieved growth rate.
+Growth decreased with decreasing photoperiod and peak PAR.
+Under red light growth was generally slower but the pattern of growth responses to photoperiod and PAR waas similar.
+We again note the exclusion of MED4 from growth under 4 h photoperiod.
+Under 25 µM O~2~ MED4 showed similar growth responses, but was excluded from both 4 and 8 h photoperiods.
+
+\newpage
+
+```{r MED4GAM,  fig.cap = MED4GAM_cap, fig.height = 10, fig.width = 10, echo = FALSE}
+
+MED4GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 grown under 660 nm (red) or 450 nm (blue) light.**",
+                    "X-axis is photoperiod (h).",
+                    "Y-axis is actinic Photosynethetic Active Radiation (PAR, µmol photons m^-2^ s^-1^).",
+                    "**A.** represents the model under 250 µM of O~2~ and red light.",
+                    "**B.** represents the model under 25 µM of O~2~ and red light.",
+                    "**C.** represents the model under 250 µM of O~2~ and blue light.",
+                    "**D.** represents the model under 25 µM of O~2~ and blue light.",
+                    "Legends represent a colour gradient of growth rate from no growth (white) to 1.00 d^-1^ (dark red or dark blue).",
+                    "Labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "PICO_Hypervolume_GAM_MED4_Oxy_.png"))
+
+```
+
+\newpage
+
 ### SS120 Clade LLIII {.unnumbered}
@@
 \newpage
-
-### MIT9313 Clade LLIV {.unnumbered}
-
-#### High oxygen environment {.unnumbered}
-
-The growth rates of *P. marinus* MIT9313, Clade LLIV increased with longer
-photoperiods under low 30 µmol photons m^-2^ s^-1^ peak PAR, under 250 µM O~2~ (Figure
-\@ref(fig:MIT9313PAR)).
-Under intermediate 90 µmol photons m^-2^ s^-1^ peak PAR growth rates decreased with increasing blue light photoperiod.
-Blue light did not induce growth at 180 µmol photons m^-2^ s^-1^ peak PAR, while cells shows only marginal growth under white LED and red light under the 8 h photoperiod .
-The µ~max~
-was
-`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
-d^-1^ achieved under 30 µmol photons
-m^-2^ s^-1^ blue light and 16 h photoperiod.
-
-#### Intermediate oxygen environment {.unnumbered}
-
-For MIT9313 maintained at 25 µM O~2~ growth rate increased with increasing photoperiods for all spectral wavebands tested (Figure \@ref(fig:MIT9313PAR)).
-Under peak PAR of 90 µmol photons m^-2^ s^-1^ growth rate increased with
-longer photoperiods, with the fastest overall growth rate for MIT9313 
-`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "25", Photoperiod == 16, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 16 h blue light
-photoperiod. In contrast to the 250 µM O~2~ growth experiments,
-MIT9313 grew when exposed to peak PAR of 180 µmol photons m^-2^
-s^-1^ and blue light under all photoperiods except 16 h; additionally,
-white LED and red light treatments induced growth across all tested
-photoperiods under 25 µM O~2~. The 25 µM O~2~, 4 h photoperiod experiments under white LED light and were not performed due to time constraints.
-
-#### Low oxygen environment {.unnumbered}
-
-Under 2.5 µM O~2~  MIT9313 showed growth, particularly under blue LED light, albeit
-generally slower than under the parallel 25 µM O~2~ experiments (Figure
-\@ref(fig:MIT9313PAR)).
-Growth estimates did, however, show scatter among replicates, suggesting the 2.5 µM O~2~  was near the tolerance limit for growth of  MIT9313.
-Growth rates increased with longer photoperiods under blue
-light treatments under peak PAR of 90 µmol photons m^-2^ s^-1^ . Growth 
-for MIT9313 under PAR of 180 µmol photons m^-2^ s^-1^ and blue light
-treatment decreased with increasing photoperiods with full growth inhibition
-under a 16 h photoperiod. The red light peak PAR of 180 µmol
-photons m^-2^ s^-1^ showed similar growth rates for 8 and 12 h
-photoperiods. The µ~max~ was
-`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "2.5", Photoperiod == 4, Par_ue == 180) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 4 h blue light
-photoperiod and PAR of 180 µmol photons m^-2^ s^-1^.  XXXXTHIS DOES NOT LOOK correct; 12 h, 90 uE photons blue light looks higher.
-
-The 2.5 µM O~2~ white LED treatments under 4, 8 and 16 h photoperiods
-and red light under 4 and 16 h photoperiods were not performed due to
-time constraints.
-
-```{r MIT9313PAR, fig.cap = MIT9313PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}
-
-MIT9313PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
-                       "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                       "Columns show 3 levels of growth Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^",
-                    "Colors represent the actinic spectral waveband (nm).",
-                    "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
-
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "MIT9313PAR.png"))
-
-```
-
-\newpage
-
-## Generalized Additive Models (GAM) of *Prochlorococcus marinus* growth responses to photoperiod, PAR, spectal bands and O~2~   {.unnumbered}
-
-XXX Fig letters do not match as now we have red GAMs. Below is results for Blue GAMsXXXX
-
-We employed GAM to summarize and visualize th complex responses of growth to the interactions of peak PAR, oxygen, photoperiod and blue vs. red spectral bands
-
-### MED4 Clade HLI  {.unnumbered}
-The GAM model in Figure \@ref(fig:MED4GAM) shows MED4 growth in response to red (A) or blue (B) peak PAR and photoperiod across 2 imposed oxygen concentrations.
-Under 250 µM O~2~ MED4 achieved fastest growth rates above peak blue light of ~180 µmol photons m^-2^ s^-1^, and the longest photoperiod of 16, indicated by the 0.69 d^-1^ contour line representing the
-90^th^ percentile of maximum achieved growth rate.
-Growth decreased with decreasing photoperiod and peak PAR.
-Under red light growth was generally slower but the pattern of growth responses to photoperiod and PAR waas similar.
-We again note the exclusion of MED4 from growth under 4 h photoperiod.
-Under 25 µM O~2~ MED4 showed similar growth responses, but was excluded from both 4 and 8 h photoperiods.
-
-\newpage
-
-```{r MED4GAM,  fig.cap = MED4GAM_cap, fig.height = 10, fig.width = 10, echo = FALSE}
-
-MED4GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 grown under 660 nm (red) or 450 nm (blue) light.**",
-                    "X-axis is photoperiod (h).",
-                    "Y-axis is actinic Photosynethetic Active Radiation (PAR, µmol photons m^-2^ s^-1^).",
-                    "**A.** represents the model under 250 µM of O~2~ and red light.",
-                    "**B.** represents the model under 25 µM of O~2~ and red light.",
-                    "**C.** represents the model under 250 µM of O~2~ and blue light.",
-                    "**D.** represents the model under 25 µM of O~2~ and blue light.",
-                    "Legends represent a colour gradient of growth rate from no growth (white) to 1.00 d^-1^ (dark red or dark blue).",
-                    "Labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",
-
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "PICO_Hypervolume_GAM_MED4_Oxy_.png"))
-
-```
-
-\newpage
-
-### SS120 Clade Clade LLIII  {.unnumbered}
 
@@
 
+#### High oxygen environment {.unnumbered}
+
+The growth rates of *P. marinus* MIT9313, Clade LLIV increased with longer
+photoperiods under low 30 µmol photons m^-2^ s^-1^ peak PAR, under 250 µM O~2~ (Figure
+\@ref(fig:MIT9313PAR)).
+Under intermediate 90 µmol photons m^-2^ s^-1^ peak PAR growth rates decreased with increasing blue light photoperiod.
+Blue light did not induce growth at 180 µmol photons m^-2^ s^-1^ peak PAR, while cells shows only marginal growth under white LED and red light under the 8 h photoperiod .
+The µ~max~
+was
+`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+d^-1^ achieved under 30 µmol photons
+m^-2^ s^-1^ blue light and 16 h photoperiod.
+
+#### Intermediate oxygen environment {.unnumbered}
+
+For MIT9313 maintained at 25 µM O~2~ growth rate increased with increasing photoperiods for all spectral wavebands tested (Figure \@ref(fig:MIT9313PAR)).
+Under peak PAR of 90 µmol photons m^-2^ s^-1^ growth rate increased with
+longer photoperiods, with the fastest overall growth rate for MIT9313 
+`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "25", Photoperiod == 16, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 16 h blue light
+photoperiod. In contrast to the 250 µM O~2~ growth experiments,
+MIT9313 grew when exposed to peak PAR of 180 µmol photons m^-2^
+s^-1^ and blue light under all photoperiods except 16 h; additionally,
+white LED and red light treatments induced growth across all tested
+photoperiods under 25 µM O~2~. The 25 µM O~2~, 4 h photoperiod experiments under white LED light and were not performed due to time constraints.
+
+#### Low oxygen environment {.unnumbered}
+
+Under 2.5 µM O~2~  MIT9313 showed growth, particularly under blue LED light, albeit
+generally slower than under the parallel 25 µM O~2~ experiments (Figure
+\@ref(fig:MIT9313PAR)).
+Growth estimates did, however, show scatter among replicates, suggesting the 2.5 µM O~2~  was near the tolerance limit for growth of  MIT9313.
+Growth rates increased with longer photoperiods under blue
+light treatments under peak PAR of 90 µmol photons m^-2^ s^-1^ . Growth 
+for MIT9313 under PAR of 180 µmol photons m^-2^ s^-1^ and blue light
+treatment decreased with increasing photoperiods with full growth inhibition
+under a 16 h photoperiod. The red light peak PAR of 180 µmol
+photons m^-2^ s^-1^ showed similar growth rates for 8 and 12 h
+photoperiods. The µ~max~ was
+`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "2.5", Photoperiod == 4, Par_ue == 180) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 4 h blue light
+photoperiod and PAR of 180 µmol photons m^-2^ s^-1^.  XXXXTHIS DOES NOT LOOK correct; 12 h, 90 uE photons blue light looks higher.
+
+The 2.5 µM O~2~ white LED treatments under 4, 8 and 16 h photoperiods
+and red light under 4 and 16 h photoperiods were not performed due to
+time constraints.
+
+\newpage
+
+```{r MIT9313PAR, fig.cap = MIT9313PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+
+MIT9313PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
+                       "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
+                       "Columns show 3 levels of growth Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^",
+                    "Colors represent the actinic spectral waveband (nm).",
+                    "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "MIT9313PAR.png"))
+
+```
+
+\newpage
+
 The GAM model in Figure \@ref(fig:MIT9313GAM) shows MIT9313 growth responses to red (A) or blue (B) peak PAR and photoperiod. Under 250 µM O~2~,  Figure \@ref(fig:MIT9313GAM)A shows MIT9313 achieves
@@
 
+## PUR and growth responses {.unnumbered}
+
+Cumulative diel absorbed PUR can potentially collapse photoperiod, PAR and spectral wavebands to a common metric of absorbed light.
+We plot observed growth rate vs.
+cumulative diel absorbed PUR to determine whether growth is a simple response to absorbed light per day across imposed photoperiods and spectral wavebands, or whether photoperiod or spectral wavebands have specific or interactive influences on growth of each ecotype.
+Cumulative daily absorbed PUR dose (µmol photons m^-2^ d^-1^) was calculated from the imposed absorbed PUR (µmol photons m^-2^ s^-1^) and photoperiod (h).
+
+Due to the highly effective absorption of pigments in the blue spectral waveband range for all ecotypes, the maximum imposed cumulative diel absorbed PUR under blue light treatment is almost 3 times that of white LED light and about 6 times the red light treatment, despite being derived from the same imposed photoperiods and PUR regimes.
+As such, only growths rates under blue light extend beyond absorbed PUR of ~ 2 x 10^6^ µmol photons m^-2^ d^-1^.
+
+### MED4 Clade HLI {.unnumbered}
+
+The representative of HLI clade, *P. marinus* MED4, showed no growth under any 4 h photoperiod treatments, even when a 4 h photoperiod delivered cumulative diel PUR
+equivalent to other photoperiod treatments. In parallel MED4 showed no growth under 2.5 µM O~2~, no matter the level of diel cumulative absorbed PUR. 
+In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth was well described by a simple saturating response of growth to increasing cumulative diel absorbed PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:AllStrainPurFitsPlots)A).
+XXXXDISTINCT PHOTOPERIOD FITSXXXXX
+
+### SS120 Clade LLIII {.unnumbered}
+
+The representative of the LLIII clade, *P.
+marinus* SS120 showed almost no growth under 2.5 µM O~2~ experiments.
+A majority of the 4 h photoperiod treatments did not grow under 250 µM O~2~ experiments even when a 4 h photoperiod delivered the cumulative diel PUR equivalent to other as other photoperiod treatments.
+SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ experiments(Figure \@ref(fig:AllStrainPurFitsPlots)B).
+
+Under both 25 or 250 µM O~2~ experiments, SS120 growth plateaued by about 5.0 x 10^5^ µmol photons m^-2^ d^-1^ diel PUR, with some scatter among photoperiod and spectral waveband regimes.
+The onset of growth inhibition extended to higher cumulative diel absorbed PUR for cultures growing under 25 µM O~2~.
+XXXXDISTINCT PHOTOPERIOD FITSXXXXX
+
+### MIT9313 Clade LLIV {.unnumbered}
+
+The LLIV clade, *P.
+marinus* MIT9313, showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR, with higher growth rates over a narrower plateau under 25 and 250 µM O~2~, compared to a wider, flatter response to cumulative diel  PUR under 2.5 µM O~2~.
+Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands.
+In contrast, under 25 µM O~2~, MIT9313 showed a greatly extended exploitation of higher cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^.
+Similarly, under 2.5 µM O~2~, MIT9313 grew more slowly, but only showed full growth inhibition above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:AllStrainPurFitsPlots)C).
+XXXXDISTINCT PHOTOPERIOD FITSXXXXX
+
+\newpage
+
+```{r AllStrainPurFitsPlots,  fig.cap = AllStrainPurFitsPlots_cap, fig.height = 10, fig.width = 10, echo = FALSE}
+
+AllStrainPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
+                    "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
+                    "Columns are strains; MED4, SS120 and MIT9313.",
+                    "Shapes show the imposed photoperiod (h); 4 h (hollow inverted triangle),  8 h (solid diamond), 12 h (solid circle), 16 h (solid upright triangle).",
+                      "Symbol colours show the spectral waveband for growth; white LED (black symbols), 660 nm (red symbols), and 450 nm (blue symbols).",
+                      "Large symbols show mean of growth rate from logistic curve fits; small symbols show values for replicate determinations, if any.",
+                    "Platt (add Platt citation here) 4 parameter model fit to data pooled for each combination of strain and dissolved oxygen shown with solid lines.
+Seperate models fit to photoperiod data and shown if significantly different from the pooled model; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).",
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "AllStrainPurFitsPlots.png"))
+
+```
+
+\newpage
+
+## Photosystem II maintenance as a limitation on *Prochlorococcus* growth {.unnumbered}
+
+*Prochlorococcus* remain challenging to culture, as their reduced genomes – the smallest of any known oxyphototroph – render them partially dependent upon mutualistic heterotrophic bacteria to  detoxify reactive oxygen species (Moore et al., 2007; Morris et al., 2008).
+MED4, SS120 and MIT9313 have been successfully cultured in laboratories, and used to show that ecotypic classifications correspond to biochemical differences among strains.
+CITATONS OUR LAB and OTHERS.
+
+Under full atmospheric [O~2~], LL clades of *Prochlorococcus* are restricted to growth under low light, in part because they suffer photoinhibition of Photosystem II (PSII) through several paths, including direct absorbance of UV or blue light, in parallel with generation of Reactive Oxygen Species (ROS) if the electron flow is slowed, [@aroPhotoinhibitionPhotosystemII1993], producing  damaging singlet oxygen (^1^O~2~) [@aroPhotoinhibitionPhotosystemII1993; @soitamoPhotoinhibitionMarinePicocyanobacteria2017; @murphyPhotoinactivationPhotosystemII2017; @hakalaEvidenceRoleOxygenevolving2005].
+Repair of inhibited PSII process relies on the removal of damaged PsbA (Mann et al., 2000; Adam et al., 2005), followed by reassembly with newly synthesized PsbA [@nixonRecentAdvancesUnderstanding2010].
+Thus, degradation of PsbA is a rate-limiting step in recovery from photoinhibition (Kanervo et al., 1993), mediated largely by a heterohexamer of (FtsH12)3, a membrane-bound (Sacharz et al., 2015)(Zak et al., 2001) metalloprotease  (Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
+(Adam et al., 2005; Boehm et al., 2012) (Nixon et al.
+(2010)) (Komenda et al., 2007).
+(Pisareva et al., 2007; Sacharz et al., 2015),  (Mann et al., 2000), (AMANDA REF from ALGATECH).
+
+*Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4, homologous to the characterized FtsH isoforms of the model cyanobacterium *Synechocystis* FtsH, with presumably parallel functions (table \@ref(tab:FtsHTable)).
+Upon a shift to higher light HLIII MED4 upregulated expression of FtsH1 and FtsH2 [@bonisteelStrainSpecificDifferences2018], homologs to the *Synechocystis* slr0228 and slr1604, implicated in PSII repair.
+In contrast representative LLIV strain MIT9313 showed less overall expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem.
+Furthermore MIT9313 expressed primarily FtsH3, homologous to Sll1463 involved in PSI biogenesis, and FtsH expression did not increase in response to light stress.
+Through adaptation to steady low light, LLIV *Prochlorococcus* instead allocates resources processes other than dynamic regulation of PSII repair.
+
+\newpage
+
+```{r BuildFtsHtable, echo = FALSE}
+
+FtsHTable <- tibble(Organism = c("*Prochlorococcus marinus*", "*Synechocystis sp. PCC6803*", "Function"),
+                    FtsH1 = c("FtsH1", "SlrO22", "PSII Repair"),
+                    FtsH2 = c("FtsH2", "Slr1604", "PSII Repair"),
+                    FtsH3 = c("FtsH3", "Slr1463", "PSI biogenesis"),
+                    FtsH4 = c("FtsH4", "Slr1390", "Cell viability")
+                    )
+
+```
+
+```{r FtsHTable, fig.height = 6, fig.width = 10, include = TRUE, echo = FALSE}
+
+knitr::kable(FtsHTable,
+             caption = "FtsH protease homologs in *Prochlorococcus marinus* and the model cyanobacterium *Synechocystis* sp.
+PCC6803.
+Protein homology determined by multiple sequence alignment with MUSCLE followed by construction of maximum likelihood phylogenetic tree using 1000 bootstrap replicates in MEGAX.",
+              col.names =  c("Organism",
+                          "Homolog 1",
+                          "Homolog 2",
+                          "Homolog 3",
+                          "Homolog 4"),
+               align = "lcccc"
+             )
+```
+
+\newpage
+
+```{r ProchloroProteinMetabDepthO2, fig.cap = ProchloroProteinMetabDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
+
+ProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein metabolism complexes.**", 
+                       "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
+                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4, SS120 and MIT9313.",
+                       "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome).",
+                       "Culture growth experimental conditions indicated by horizontal grey lines for depths approximating Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) and vertical grey lines for O~2~ (µM).",
+                       "Point colours identify *Prochlorococcus* clade assignments",
+                       "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",
+ .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "ProchloroProteinMetabDepthO2.png"))
+```
+
+\newpage
+
+XXXX Mireille to finish Fig. caption when figure is complete. Add color ? Remove []? XXX
+```{r MED4ProteinAnnotated, fig.cap = MED4ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+
+MED4ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade).**",
+
+                    "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",
+                    "Numbers over each bar are fmole target protein per ug total protein.",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "MED4ProteinAnnotated.png"))
+```
+
+\newpage
+
+XXXX Mireille to finish Fig. caption when figure is complete. Add color ? Remove []? XXX
+```{r MIT9313ProteinAnnotated, fig.cap = MIT9313ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+
+MIT9313ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade).  **",
+                                    "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",
+                    "Numbers over each bar are fmole target protein per ug total protein.",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "MIT9313ProteinAnnotated.png"))
+```
+
+\newpage
+
+# Discussion {.unnumbered}
+
 ### Growth Responses to Photoperiod {.unnumbered}
@@
 The representative of HLI clade, *P. marinus* MED4, was completely
-excluded from growth under the 4 h photoperiod, andshowed
+excluded from growth under the 4 h photoperiod, and showed
 increasing growth rates with increasing photoperiod. Thus, MED4 can
@@
 
-\newpage
-
-## PUR and growth responses {.unnumbered}
-
-Cumulative diel absorbed PUR can potentially collapse photoperiod, PAR and spectral wavebands to a common metric of absorbed light.
-We plot observed growth rate vs.
-cumulative diel absorbed PUR to determine whether growth is a simple response to absorbed light per day across imposed photoperiods and spectral wavebands, or whether photoperiod or spectral wavebands have specific or interactive influences on growth of each ecotype.
-Cumulative daily absorbed PUR dose (µmol photons m^-2^ d^-1^) was calculated from the imposed absorbed PUR (µmol photons m^-2^ s^-1^) and photoperiod (h).
-
-Due to the highly effective absorption of pigments in the blue spectral waveband range for all ecotypes, the maximum imposed cumulative diel absorbed PUR under blue light treatment is almost 3 times that of white LED light and about 6 times the red light treatment, despite being derived from the same imposed photoperiods and PUR regimes.
-As such, only growths rates under blue light extend beyond absorbed PUR of ~ 2 x 10^6^ µmol photons m^-2^ d^-1^.
-
-#### MED4 Clade HLI {.unnumbered}
-
-The representative of HLI clade, *P. marinus* MED4, showed no growth under any 4 h photoperiod treatments, even when a 4 h photoperiod delivered cumulative diel PUR
-equivalent to other photoperiod treatments. In parallel MED4 showed no growth under 2.5 µM O~2~, no matter the level of diel cumulative absorbed PUR. 
-In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth was well described by a simple saturating response of growth to increasing cumulative diel absorbed PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:AllStrainPurFitsPlots)A).
-XXXXDISTINCT PHOTOPERIOD FITSXXXXX
-
-#### SS120 Clade LLIII {.unnumbered}
-
-The representative of the LLIII clade, *P.
-marinus* SS120 showed almost no growth under 2.5 µM O~2~ experiments.
-A majority of the 4 h photoperiod treatments did not grow under 250 µM O~2~ experiments even when a 4 h photoperiod delivered the cumulative diel PUR equivalent to other as other photoperiod treatments.
-SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ experiments(Figure \@ref(fig:AllStrainPurFitsPlots)B).
-
-Under both 25 or 250 µM O~2~ experiments, SS120 growth plateaued by about 5.0 x 10^5^ µmol photons m^-2^ d^-1^ diel PUR, with some scatter among photoperiod and spectral waveband regimes.
-The onset of growth inhibition extended to higher cumulative diel absorbed PUR for cultures growing under 25 µM O~2~.
-XXXXDISTINCT PHOTOPERIOD FITSXXXXX
-
-#### MIT9313 Clade LLIV {.unnumbered}
-
-The LLIV clade, *P.
-marinus* MIT9313, showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR, with higher growth rates over a narrower plateau under 25 and 250 µM O~2~, compared to a wider, flatter response to cumulative diel  PUR under 2.5 µM O~2~.
-Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands.
-In contrast, under 25 µM O~2~, MIT9313 showed a greatly extended exploitation of higher cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^.
-Similarly, under 2.5 µM O~2~, MIT9313 grew more slowly, but only showed full growth inhibition above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:AllStrainPurFitsPlots)C).
-XXXXDISTINCT PHOTOPERIOD FITSXXXXX
-
-## Discussion PUR and growth trends {.unnumbered}
+### Discussion PUR and growth trends {.unnumbered}
 
@@
 
-## Discussion from Mireille' Thesis General Discussion section {.unnumbered}
+### Discussion from Mireille' Thesis General Discussion section {.unnumbered}
 
@@
 
-@flombaumPresentFutureGlobal2013 modeled a 29% increase of net cell abundance of *Prochlorococcus* by the end of this century and predicts that there will be poleward latitudinal shifts of at least 10° in marine phytoplankton habitats.
-Consequently, *P.
-marinus* will encounter new combinations of photoperiod, seasonal patterns, and altered spectral regimes as they move towards the poles, where solar incidence angles are lower and photoperiod seasonality is more pronounced [@bartonAnthropogenicClimateChange2016].
-The predicted poleward shifts of  *P.
-marinus* niches and the estimated increase in their cell abundances was modeled using climate model projections of sea surface temperatures and greenhouse gases equivalent to 650 ppm CO~2~ for the end of this century [@flombaumPresentFutureGlobal2013].
-While these models suggest that *P.
-marinus* could hypothetically expand into poleward regions by the end of this century, it remains uncertain whether *P.
-marinus* can actually tolerate the longer, and shorter, day lengths of temperate region seasons.
-To our knowledge, no other study has as yet addressed *P.
-marinus* growth responses in relation to a wide range of photoperiods.
-
-The lack of photoperiod growth studies is not surprising, given that higher cell abundances of *P.
-marinus* are currently  concentrated between 30°N and 30°S.
-At 30°N, the photoperiod seasonality ranges from 12 to 14 hours at the ocean surface between the winter and summer solstices, while it remains consistently 12 hours throughout the year at the equator.
-Therefore, growth response studies to date have generally been conducted under either a 12 or 14 hour (h) photoperiod.
-However, the photoperiod at the ocean surface is not fully representative of the photoperiod underwater, as solar radiation is reflected off the surface when the solar incident angle is less than 20°.
-This discrepancy between the duration of daylight hours above water and the effective duration of light exposure underwater is often overlooked in the experimental design of *P.
-marinus* growth studies, even when considering photoperiod.
-
-Current niches of *P. marinus* span across vertical ocean water columns
-[@chisholmNovelFreelivingProchlorophyte1988; @veldhuisVerticalDistributionPigment1990; @partenskyProchlorococcusMarinePhotosynthetic1999] and extend into regions with varying dissolved oxygen concentrations
-[@partenskyProchlorococcusAdvantagesLimits2010; @goerickeNovelNicheProchlorococcus2000] and even into anoxic oceans [@lavinNovelLineagesProchlorococcus2010], [@ulloaCyanobacteriumProchlorococcusHas2021; @garcia-robledoCrypticOxygenCycling2017a].
-Climate change is drastically altering the dissolved oxygen concentrations ([O~2~]) of our ocean waters.
-Research indicates that the oxygen minimum zones (OMZs) in the Pacific and Indian Oceans are expanding [@garcia-sotoOverviewOceanClimate2021; @buseckeDivergingFatesPacific2022] and that the levels of dissolved oxygen (O~2~) in our global oceans are generally decreasing [@matearLongtermChangesDissolved2003; @garcia-sotoOverviewOceanClimate2021], with significant decreases observed toward the poles [@helmObservedDecreasesOxygen2011].
-
-In chapter 2, we analyzed  growth rates to determine the viability of *P. marinus* MED4, a clade HLI ecotype found at depths near the ocean surface,
-*P.
-marinus* SS120, a clade LLIII ecotype found deep in the water column, and *P.
-marinus* MIT9313, a clade LLIV ecotype also found in deep oceans, under present day and hypothetical future niche conditions.
-We designed our study to account for light attenuation through ocean waters, recognizing that low light levels of the blue spectral waveband ultimately prevail in deep ocean waters [@morelAvailableUsableStored1978; @holtropVibrationalModesWater2021] and that the solar incidence angle also attenuates the photoperiod or hours of light exposure beneath the ocean surface.
-We also tested the growth response of *P.
-marinus* to varying [O~2~] under the matrix of light parameters to determine if *P.
-marinus* can cope with  diverse  ecosystem scenarios.
-
-We found that *P.
-marinus* MED4, can grow under near surface O~2~ saturation levels of 250 µM and high light levels, conditions representative of its current ecotype classification [@moorePhysiologyMolecularPhylogeny1998].
-MED4 can also grow under O~2~ of 25 µM, and under all tested levels of light in the blue spectral waveband, so long as the photoperiod is longer than 4 h (Figure \@ref(fig:MED4PAR)).
-Consequently, MED4 can potentially inhabit different ecological niches through its ability to  exploit a wide range of light levels, from the surface to the deep ocean, along with varying levels of dissolved oxygen throughout the water column.
-These findings are supported by evidence of HL ecotype presence even in the OMZ [@mattisonPhotosyntheticStrategiesWild2020] and in deeper regions of the ocean [@mattisonPhotosyntheticStrategiesWild2020; @delmontLinkingPangenomesMetagenomes2018].
-With predicted future ocean warming [@wijffelsOceanTemperaturesChronicle2016], MED4 shows potential to harness the photoregimes prevalent in temperate spring, summer, and fall zones when the duration of blue spectral waveband in the water column exceeds 4 hours.
-
-*Prochlorococcus marinus* SS120 prefers the deeper ocean where blue spectral waveband dominates at low levels, through its demonstrated ability to exploit only the lowest blue spectral waveband levels PAR of 30 µmol photons m^-2^ s^-1^ under 250 µM O~2~.
-However, we found *P.
-marinus* SS120 can exploit more diverse ecological niches within the ocean layers, even in regions with high levels of blue spectral waveband,  but only under O~2~ of 25 µM (Figure \@ref(fig:SS120PAR)).
-@mattisonPhotosyntheticStrategiesWild2020 and @lavinNovelLineagesProchlorococcus2010 show evidence of LLIII ecotypes at varying depths from 20 to 200 m and under all [O~2~] in the oxygen minimum zone (OMZ) of the tropical North Pacific Ocean, illustrating its tolerance of high light levels under low O~2~.
-SS120 has the potential to thrive in deep temperate zones, specifically during the spring, summer, and fall seasons when the duration of daylight exceeds 4 h, if O~2~ are near surface saturation of about 250 µM.
-Under lower oxygen levels of 25 µM, SS120 can also exploit a 4 h photoperiod in the blue waveband, and thus has the potential to inhabit a warmed, deep, temperate region during the winter season.
-
-*Prochlorococcus marinus* MIT9313 shows the potential to inhabit future warmed temperate zones year-round, as it exhibits the ability to grow under a 4 h photoperiod.
-MIT9313 demonstrates an unexpected tolerance to higher light levels,  but only under low oxygen conditions of 25 µM and 2.5 µM (Figure \@ref(fig:MIT9313PAR)).
-The ability to utilize higher levels of blue spectral waveband under 25 µM or 2.5 µM O~2~ enables MIT9313 to grow in regions like the OMZ and even at depths closer to the surface.
-
-We found our experimental growth rates agreed with those from @mooreComparativePhysiologySynechococcus1995, grown under white LED and 250 µM O~2~.
-However, growth response studies are scarce for comparison, especially under varying [O~2~] and even under different spectral wavebands and photoperiods.
-As far as we know, our study is the first to analyze the interactive growth responses of *Prochlorococcus*  to varying [O~2~], spectral wavebands and photoperiods.
-
-The potential expansion of  *P.
-marinus*  polewards will contribute to the primary food base of an aquatic ecosystem that has already undergone changes in Canadian waters; commercial fish populations are shifting with new species immigrating  [@zellerCheungZellerPauly2011], endangered whales actively searching for food sources are becoming more prevalent [@meyer-gutbrodMarineSpeciesRange2018] and the white shark seasonal presence is increasing  either due to rising ocean temperatures or following marine prey [@bastienInconspicuousRecoveringNorthward2020].
-While the exact impact of the presence of *P.
-marinus*  on the species distribution of marine wildlife in Atlantic Canadian waters is unknown, there is little doubt that *Prochlorococcus* will play a significant role in shaping this distribution.
-The shifting dynamics of the aquatic ecosystem in the Atlantic Canadian waters may have consequences for our commercial fishing and shipping sectors, as adjustments to shipping routes and regulations are made to safeguard endangered whales.
-
-In chapter 3, we determined the Photosynthetic Usable Radiation (PUR), the portion of light radiation absorbed differentially by the pigments of the photosynthetic organism [@morelAvailableUsableStored1978] and expressed growth response in terms of cumulative diel PUR.
-We found that approximately 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of PUR is the maximum dosage that the representative LL clades, SS120 and MIT9313 can tolerate under 25 µM O~2~, in contrast to the representative HL clade, MED4 which exhibited growth saturation at the same cumulative diel PUR of 1.0 x 10^6^ µmol photons m^-2^ d^-1^.
-Growth under lower O~2~ allowed MIT9313 to substantially increase its exploitation of higher diel PUR.
-
-To gain insights into the variations we observed in growth responses across strains, particularly the responses to different oxygen levels [O~2~], we used a subset of the dataset of annotated phytoplankton genomes from @omarAnnotationGenesEncoding2023.
-This subset contains annotated phytoplankton gene sequences, with a focus on genes encoding enzymes involved in oxygen metabolism (Figure \@ref(fig:ProchlorococcusEnzymeKms)) or DNA repair (Figure \@ref(fig:DNARepairFig)).
-According to figure \@ref(fig:ProchlorococcusEnzymeKms), we see that *P.
-marinus* MED4 has the gene encoding ubiquinol oxidase (non electrogenic) enzyme, whereas SS120 and MIT9313 do not.
-The ubiquinol oxidase (non electrogenic) enzyme is involved in dissipating excess electrons [@InformationEC10] generated under high light exposure, thereby reducing stress on the electron transport system.
-The O~2~ substrate K~m~ value of approximately 25 µM  for ubiquinol oxidase  may explain why *P.
-marinus* MED4 can grow under 25 µM of O~2~ but not under 2.5 µM of O~2~, since growth under 2.5 µM of O~2~ would suppress use of ubiquinol oxidase to balance electron transport.
-The demonstrated ability of *P.
-marinus* MIT9313 to grow when exposed to high blue light under 2.5 µM and 25 µM O~2~ treatments may be explained by the presence of the gene encoding enzyme 2-hydroxy-acid oxidase (Figure \@ref(fig:ProchlorococcusEnzymeKms)).
-The enzyme 2-hydroxy-acid oxidase, with an O~2~ substrate K~m~ value of approximately 250 µM (Figure \@ref(fig:ProchlorococcusEnzymeKms)), catalyzes the reaction of 2-hydroxy acid with O~2~ to produce toxic hydrogen peroxide [@InformationEC15].
-We hypothesize that under our 250 µM O~2~ and high blue light experiments, *P.
-marinus* MIT9313 exhibited photoinhibition, resulting from the inactivation of PSII caused by the production of the reactive oxygen species, hydrogen peroxide.
-This inhibition was further compounded by the limited induced repair mechanism for PSII, due to the absence of FtsH 2 and 3  proteins in *P.
-marinus* MIT9313 [@bonisteelStrainSpecificDifferences2018].
-We hypothesize that under the conditions of our high light and 2.5 µM and 25 µM O~2~ experiments, the activity of the 2-hydroxy-acid oxidase enzyme is suppressed.
-As a result, the catalyzed production of hydrogen peroxide is inhibited, leading to minimal PSII damage, allowing MIT9313 to avoid photohibition and circumvent limitations on PSII repair.
-Figure \@ref(fig:ProchlorococcusEnzymeKms) also shows that *P.
-marinus* SS120 is the only tested ecotype to lack the pyridoxal 5'-phosphate synthase enzyme.
-The pyridoxal 5'-phosphate synthase enzyme is an important cofactor in the biosynthesis of vitamin B~6~ [@sangIdentificationPyridoxinePyridoxamine2007].
-Vitamin B~6~ is a potential antioxidant and can effectively quench singlet oxygen [@bilskiVitaminB6Pyridoxine2000].
-The absence of the pyridoxal 5'-phosphate synthase enzyme may explain why *P.
-marinus* SS120 does not grow as well as *P.
-marinus* MIT9313 when exposed to high light stress under 25 µM O~2~ and not at all under 2.5 µM O~2~.
-
-XXX ProchlorococcusEnzymeKms figure was here XXX
-
-\newpage
-
-Figure \@ref(fig:DNARepairFig) displays the genes encoding DNA repair for the three *P.
-marinus* strains examined in this study.
-As expected,  *P.
-marinus* MED4 possesses the largest and most complete suite of genes encoding DNA repair enzymes, followed by *P.
-marinus* MIT9313.
-Conversely, *P.
-marinus* SS120 demonstrates the smallest genomic capacity for DNA repair.
-*Prochlorococcus marinus* MED4 was the only strain out of the three strains in this study to possess the gene encoding deoxyribodipyrimidine photolyase, which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003].
-*Prochlorococcus marinus* MED4 was also the only strain to possesses the gene encoding DNA ligase, which uses ATP as a cofactor for DNA repair.
-The absence of the genes encoding deoxyribodipyrimidine photolyase and DNA ligase (ATP) in *P.
-marinus* MIT9313 and *P.
-marinus* SS120 explains why these two strains cannot tolerate the high light levels found at the ocean surface where  *P.
-marinus* MED4 inhabits.
-
-XXX DNARepairFig was here XXX
-
-\newpage
-
-@westNichePartitioningProchlorococcusPopulationsStratified1999 and
-@malmstromTemporalDynamicsProchlorococcus2010 found that decreased
-abundances of the LL ecotypes corresponded to increased depth of the
-surface mixed layer, which thus influences the vertical distribution of
-HL and LL ecotypes. @malmstromTemporalDynamicsProchlorococcus2010
-attributes the transport of LL ecotypes to the surface and exposure to
-photoinhibitory high light levels as the reason for low cell abundances.
-@westNichePartitioningProchlorococcusPopulationsStratified1999 found
-the depth of the mixed layer strongly influenced the depth transition
-from HL to LL ecotypes and that additional factors other than light
-levels may influence the variations in the upper and lower depth limits
-of these ecotypes. Based on our findings, we hypothesize that low cell abundances of LL ecotypes in the mixed layer is likely due to increased [O~2~] at
-those depths and it is [O~2~] that determines the prevalence of the LL
-ecotypes to certain depths, not necessarily the light level.
-
-We have demonstrated that *P.
-marinus*  can exploit the photoregimes of the temperate zone, both at the surface and deep in the water column.
-Additionally, we  confirmed that the *P.
-marinus* strains we tested can survive in significantly lower oxygen environments as is represented in the OMZ and that the LL ecotypes we tested can be labeled as HL strains in oxygen environments of 25 µM and as low as 2.5 µM in the case of MIT9313.
-@billerProchlorococcusStructureFunction2015 has described *Prochlorococcus* as a 'federation' of diverse cells through their extensive genomic and phenotypic diversity.
-They underscore the importance of its diverse members and how this diversity contributes to their wide distribution, stability, and abundance in oceans.
-I like to envision a ‘federation’ of  *Prochlorococcus* cells in perfect floating order, like an army of soldiers  diligently engaging in their expertise: photosynthesis.
-
-\newpage
-
-```{r AllStrainPurFitsPlots,  fig.cap = AllStrainPurFitsPlots_cap, fig.height = 10, fig.width = 10, echo = FALSE}
-
-AllStrainPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
-                    "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                    "Columns are strains; MED4, SS120 and MIT9313.",
-                    "Shapes show the imposed photoperiod (h); 4 h (hollow inverted triangle),  8 h (solid diamond), 12 h (solid circle), 16 h (solid upright triangle).",
-                      "Symbol colours show the spectral waveband for growth; white LED (black symbols), 660 nm (red symbols), and 450 nm (blue symbols).",
-                      "Large symbols show mean of growth rate from logistic curve fits; small symbols show values for replicate determinations, if any.",
-                    "Platt (add Platt citation here) 4 parameter model fit to data pooled for each combination of strain and dissolved oxygen shown with solid lines.
-Seperate models fit to photoperiod data and shown if significantly different from the pooled model; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).",
+# Supplemental {.unnumbered}
+
+```{r LabeledMC, fig.cap = LabeledMC_cap , fig.height = 8, fig.width = 6, echo = FALSE}
+
+LabeledMC_cap <- glue("**PSI MCMIX-OD Multicultivator.**",
+                      "Spectral wavebands and light levels are individually controlled for each culture tube.",
+                      "Real time Optical Density (OD) measurements eliminate intrusive subsampling of sterile cultures.",
+                      "The temperature of culture tubes are collectively controlled via heating or cooling of the aquarium water.",
+                      "Gas with specific oxygen concentrations is bubbled through a humidifier and passed through a 0.2 um filter.",
+
                        .sep = " ")
 
-knitr::include_graphics(file.path(FiguresIn, "AllStrainPurFitsPlots.png"))
-
-```
-
-\newpage
-
-%%%% OceanFtsHRibosomeProteins figure from OceanPortal repository  %%%
-
-```{r ProchloroProteinMetabDepthO2, fig.cap = ProchloroProteinMetabDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
-
-ProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein metabolism complexes.**", 
-                       "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
-                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4, SS120 and MIT9313.",
-                       "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome).",
-                       "Culture growth experimental conditions indicated by horizontal grey lines for depths approximating Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) and vertical grey lines for O~2~ (µM).",
-                       "Point colours identify *Prochlorococcus* clade assignments",
-                       "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",
- .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "ProchloroProteinMetabDepthO2.png"))
-```
-
-XXXX Mireille to finish Fig. caption when figure is complete. Add color ? Remove []? XXX
-```{r MED4ProteinAnnotated, fig.cap = MED4ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
-
-MED4ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade).**",
-
-                    "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",
-                    "Numbers over each bar are fmole target protein per ug total protein.",
-
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "MED4ProteinAnnotated.png"))
-```
-
-\newpage
-
-XXXX Mireille to finish Fig. caption when figure is complete. Add color ? Remove []? XXX
-```{r MIT9313ProteinAnnotated, fig.cap = MIT9313ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
-
-MIT9313ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade).  **",
-                                    "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",
-                    "Numbers over each bar are fmole target protein per ug total protein.",
-
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "MIT9313ProteinAnnotated.png"))
-```
-
-\newpage
-
-# Supplemental {.unnumbered}
+knitr::include_graphics(file.path(FiguresIn, "LabeledMC.png"))
+```
+
+\newpage
 

### 2024-02-21 Code/Import_MetaData.Rmd
Added missing data and reprocessed run #78. Regnerated GAM and plots

--- 2024-01-18 Code/Import_MetaData.Rmd
@@
 DataOut <- file.path("..","Data")
-ProjectRows <- c("MiSa|JuNa|SaAr")
+ProjectRows <- c("MiSa|JuNa|SaAr|MaBe|LaGe")
 ProjectCols <- c("PrimaryOperator", "SampleID", "Run", "Strain", "ExpCul", "ExpDate", "ExpStartTime", "Par_ue", "Photoperiod", "Temp_c", "MC", "Tube","O2", "O2_Category", "WL","LightShape", "Optode","OptodeCh","OptodeMeasure", "ExpEndDate")

### 2024-02-21 Code/Manuscript_O2.Rmd
Corrected spelling

@@
 To estimate the Photosynthetic Usable Radiation (PUR), a proxy of incident photons absorbed by the cells, for each *P. marinus* ecotype, the imposed Photosynthetic Active
-Radiation (PAR) was first determined using the reported delivery of sinuisoidal diel PAR regimes by the Multicultivators, point validated using an XXXXXcitation of PAR meterXXX.
+Radiation (PAR) was first determined using the reported delivery of sinusoidal diel PAR regimes by the Multicultivators, point validated using an XXXXXcitation of PAR meterXXX.
 An emission profile from 400 nm to 700 nm of each colored LED
@@
 Growth decreased with decreasing photoperiod and peak PAR.
-Under red light growth was generally slower but the pattern of growth responses to photoperiod and PAR waas similar.
+Under red light growth was generally slower but the pattern of growth responses to photoperiod and PAR was similar.
 We again note the exclusion of MED4 from growth under 4 h photoperiod.
@@
 photons m^-2^ s^-1^ experiments, SS120 maintained at 25 µM O~2~ showed no
-growthunder a 4 h photoperiod for imposed red spectral
+growth under a 4 h photoperiod for imposed red spectral
 waveband, however under blue light, SS120 was able to grow (Figure
@@
 Note the disjunct regions of the plots, resulting from variable growth successes of SS120 under 250 µM O~2~.
-Growth rate patterns under red light were similar, although somehwat faster.
-In contrast, under 25 µM O~2~ and a photoperiod of 8 h SS120 exploited all blue peak PAR levels, achieving faster growth ratesat a higher PAR of \~100 µmol photons
+Growth rate patterns under red light were similar, although somewhat faster.
+In contrast, under 25 µM O~2~ and a photoperiod of 8 h SS120 exploited all blue peak PAR levels, achieving faster growth rates at a higher PAR of \~100 µmol photons
 m^-2^ s^-1^, indicated by the contour line labeled 0.5 d^-1^
@@
 the 90^th^ percentile fastest growth rates under 250 µM O~2~.
-Under red light and 25 µM O~2~ light SS120 grew across most conditions of peak PAR and photoperiod, achieving fastest growhth under long photoperiods and peak PAR below 50 \~100 µmol photons
+Under red light and 25 µM O~2~ light SS120 grew across most conditions of peak PAR and photoperiod, achieving fastest growth under long photoperiods and peak PAR below 50 \~100 µmol photons
 m^-2^ s^-1^.  Thus, the designation of SS120 as a LL strain is dependent upon the [O~2]. SS120 did not, however,  grow under tested conditions at 2.5 µM O~2~.
@@
                     "Platt (add Platt citation here) 4 parameter model fit to data pooled for each combination of strain and dissolved oxygen shown with solid lines.
-Seperate models fit to photoperiod data and shown if significantly different from the pooled model; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).",
+Separate models fit to photoperiod data and shown if significantly different from the pooled model; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).",
                        .sep = " ")
@@
 We hypothesize that under the conditions of our high light and 2.5 µM and 25 µM O~2~ experiments, the activity of the 2-hydroxy-acid oxidase enzyme is suppressed.
-As a result, the catalyzed production of hydrogen peroxide is inhibited, leading to minimal PSII damage, allowing MIT9313 to avoid photohibition and circumvent limitations on PSII repair.
+As a result, the catalyzed production of hydrogen peroxide is inhibited, leading to minimal PSII damage, allowing MIT9313 to avoid photoinhibition and circumvent limitations on PSII repair.
 Figure \@ref(fig:ProchlorococcusEnzymeKms) also shows that *P.

### 2024-02-22 Code/Manuscript_O2.Rmd
edits to subheadings

@@
 
-### MED4 Clade HLI  {.unnumbered}
-The GAM model in Figure \@ref(fig:MED4GAM) shows MED4 growth in response to red (A) or blue (B) peak PAR and photoperiod across 2 imposed oxygen concentrations.
+The GAM model in Figure \@ref(fig:MED4GAM) summarizes MED4 growth in response to red (A) or blue (B) peak PAR and photoperiod across 2 imposed oxygen concentrations.
 Under 250 µM O~2~ MED4 achieved fastest growth rates above peak blue light of ~180 µmol photons m^-2^ s^-1^, and the longest photoperiod of 16, indicated by the 0.69 d^-1^ contour line representing the
@@
 
-The GAM model in Figure \@ref(fig:SS120GAM) shows growth
+The GAM model in Figure \@ref(fig:SS120GAM) summarizes growth
 responses of SS120 red (A) or blue (B) peak PAR and photoperiod,
@@
 
-The GAM model in Figure \@ref(fig:MIT9313GAM) shows MIT9313 growth responses to red (A) or blue (B) peak PAR and photoperiod. Under 250 µM O~2~,  Figure \@ref(fig:MIT9313GAM)A shows MIT9313 achieves
+The GAM model in Figure \@ref(fig:MIT9313GAM) summarizes MIT9313 growth responses to red (A) or blue (B) peak PAR and photoperiod.
+Under 250 µM O~2~,  Figure \@ref(fig:MIT9313GAM)A shows MIT9313 achieves
 fastest growth rates between blue peak PAR of 30 µmol photons m^-2^
@@
 ```
+
+\newpage
+
+## **Prochlorococcus* genomic capacities for electron dissipation and DNA repair
+NAAMAN FIGURE
+Zotero BERG citation
 

### 2024-02-22 Code/Manuscript_O2.Rmd
Edits to protein materials and methods

@@
 *P.
-marinus* growth is currently constrained to between latitudes of 40°N to 40°S in open ocean waters, from surface to 300 m  depth, thus spanning 3 orders of magnitudes of light (Partensky et al., 1999) (Chisholm et al., 1992)  [@partenskyProchlorococcusMarinePhotosynthetic1999].
+marinus* growth is currently constrained to between latitudes of 40°N to 40°S in open ocean waters, from surface to 300 m  depth, thus spanning 3 orders of magnitudes of light [@partenskyProchlorococcusMarinePhotosynthetic1999; @chisholmProchlorococcusMarinusNov1992 ].
 
@@
 Some as yet uncultured *P.
-marinus* strains in clades LLV and LLVI thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021; @@lavinNovelLineagesProchlorococcus2010; @goerickeNovelNicheProchlorococcus2000; @garcia-robledoCrypticOxygenCycling2017a] (Johnson et al., 1999).
+marinus* strains in clades LLV and LLVI thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021; @lavinNovelLineagesProchlorococcus2010; @goerickeNovelNicheProchlorococcus2000; @robledoCrypticOxygenCycling2017] (Johnson et al., 1999).
 *P.
@@
 Blots were blocked overnight in 2% ECL blocking solution as described by @brownFluxCapacitiesAcclimation2008.
-The following morning, each blot was incubated in their appropriate antibody obtained from Agrisera (Vännäs, Sweden; FtsH  1:5,000 dilution, AS11 1789; PsbA  1:10000 dilution, AS05 084; PetC 1:XXXXX dilution, AS08 330; PsaC 1:XXXXXX dilution, AS10 939; RbcL 1:10000 dilution, AS03 037) and a 1:15000 dilution of the secondary antibody, goat anti-rabbit HRP conjugated (Bio-Rad, Hercules, CA, USA; SKU 1706515, lot 64230791).
+The following morning, each blot was incubated in their appropriate antibody obtained from Agrisera (Vännäs, Sweden; FtsH  1:5000 dilution, AS11 1789; PsbA  1:10000 dilution, AS05 084; PetC 1:10000 dilution, AS08 330; PsaC 1:5000 dilution, AS10 939; RbcL 1:10000 dilution, AS03 037) and a 1:15000 dilution of the secondary antibody, goat anti-rabbit HRP conjugated (Bio-Rad, Hercules, CA, USA; SKU 1706515, lot 64230791).
 Blots were incubated in Amersham ECL Select chemiluminescent substrate (Danaher, Washington, DC, USA) and imaged in a Bio-Rad VersaDoc imager (Bio-Rad, Hercules, CA, USA).

### 2024-02-22 Code/Manuscript_O2.Rmd
Knit changes

@@
 able to grow under the lowest PAR treatment of 30 µmol photons m^-2^
-s^-1^ but only when the blue light photoperiod was longer than 4 h; the
-white LED light photoperiod was longer than 8 h; or when the red light
-photoperiod was longer than 16 h. Growth rate increased
+s^-1^ but only when the blue light photoperiod was longer than 4 h and the white LED and red light photoperiod was longer than 8 h. Growth rate increased
 with increasing photoperiods for all spectral wavebands when exposed to
@@
 generally similar growth rates as the 250 µM O~2~ growth experiments,
-with the interesting exception that growth rates increased by 40% under
-25 µM O~2~ at PAR of 30 µmol photons m^-2^ s^-1^ and 16 h photoperiod,
-and even showed growth under 12 h red light photoperiod, in contrast to
+with the interesting exception that growth rates increased by 40 % under
+25 µM O~2~ at PAR of 30 µmol photons m^-2^ s^-1^ and 16 h blue photoperiod and increased by 55 % under 16 h red photoperiod, in contrast to
 the 250 µM O~2~ growth experiments. White LED light treatments grew
-slower, if at all, under 25 µM O~2~, only growing under higher PAR of 90
-and 180 µmol photons m^-2^ s^-1^ and longer photoperiods of 12 and 16 h.
+slower, if at all, under 25 µM O~2~, only growing under higher PAR of 90 µmol photons m^-2^ s^-1^ and 16 h photoperiod and 180 µmol photons m^-2^ s^-1^ and 12 and 16 h photoperiods.
 As under 250 µM O~2~, the fastest growth rate observed for each spectral

### 2024-02-22 Code/ManuscriptFigures.Rmd
Added representative growth fits figures

@@
 
+```
+
+```{r LogisticFitPlot, fig.height= 10, fig.width= 10 }
+maxOD_x = 500
+maxOD_y = 0.165
+
+minOD_x =500
+minOD_y = 0.005
+
+time_x = 300
+time_y = -0.005
+
+Predict_x = 4
+Predict_y = 0.06
+
+deltaODLogGrowthPlot <- PURPARFits %>%
+  filter(Run == 114) %>% 
+  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
+         OxygenLabel_title = "Oxygen Concentration",
+         Oxygen_label = case_when(O2_uM %in% c(2.5, 25, 250) ~ paste("[Oxygen]", O2_uM, "µM", sep = " ")),
+         WL_label_title = "Growth Wavelength",
+         WL_label = case_when(WL %in% c(450, 530, 660) ~ paste(WL, "nm", sep = " "),
+                              WL %in% c("WW") ~ paste("White LED", sep = " ")),
+         Par_label = case_when(Par_ue %in% c(30, 90, 180) ~ paste(Par_ue, "µE", sep = " ")),
+         PhotoLabel = case_when(Photoperiod == 16 ~ "16 h Photoperiod", 
+                                 Photoperiod == 12 ~ "12 h Photoperiod",
+                                 Photoperiod == 8 ~ "8 h Photoperiod",
+                                 Photoperiod == 4 ~ "4 h Photoperiod")) %>%
+  # mutate(deltaOD_logistic_predict = map(deltaOD_logistic, possibly(augment, otherwise = NULL))) %>%
+  unnest(cols = c(tubedata, deltaOD_logistic_predict),names_sep = "_", keep_empty = TRUE) %>%
+  ggplot() +
+  geom_point(aes(x = tubedata_time, y = tubedata_deltaOD), colour = "darkgreen", size = 0.1) +
+  scale_colour_manual(values = MCMIXColours) +
+  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.fitted), colour = "black", size = 0.1) +
+  geom_point(aes(x = tubedata_time, y = deltaOD_logistic_predict_.resid), colour = "gold", size = 0.05) +
+  geom_point(aes(x = tubedata_time, y = tubedata_Actinic_par/5000, colour = as.factor(WL)), size = 0.25, alpha = 1.0) +
+   scale_y_continuous(name="Chlorophyll proxy (ΔOD)", sec.axis=sec_axis(~.*5000, name = Actinic ~PAR~(µmol~photons~m^{-2}~s^{-1}))) +
+  #coord_cartesian(xlim = c(-5, 675)) +
+  #scale_x_continuous(breaks=seq(0, 675, by = 125)) +
+  # facet_grid(rows = vars(O2), cols = vars(Tube, WL, Par_ue, Strain, Photoperiod)) +
+   # ggh4x::facet_nested(cols = vars(Tube, Strain,Photoperiod, Oxygen_label, WL_label, Par_label), 
+   #                  labeller = labeller(Tube = label_both, WL_label = label_value, WL = label_value, Strain = label_value, OxygenLabel_title = label_value,Oxygen_label = label_value, OxygenLabel = label_value, Photoperiod = label_both, Par_label = label_value))+
+   ggh4x::facet_nested(cols = vars(PhotoLabel, Oxygen_label, Tube, SampleID,  Strain, WL_label, Par_label), 
+                    labeller = labeller(Tube = label_both, WL_label = label_value, WL = label_value, Strain = label_value, OxygenLabel_title = label_value,Oxygen_label = label_value, OxygenLabel = label_value, Photoperiod = label_both, Par_label = label_value, SampleID = label_value))+
+  labs(y = "Chlorophyll proxy (ΔOD)" , x = "Elapsed Time (h)") +
+   guides(colour = "none") +
+  theme_bw() +
+  theme( strip.text = element_text(size = 11),
+        axis.title = element_text(size = 20, color = "black"),
+        axis.text.x = element_text(size = 15, color = "black", angle = 60, hjust = 1.0),
+        axis.text.y = element_text(size = 15, color = "black", angle = 0, hjust = 1.0),
+        # strip.background=element_rect(color="grey", fill = "grey"),
+        strip.background=element_rect(fill = "grey"),
+        legend.key.size = unit(1, 'cm'), #change legend key size
+        legend.key.height = unit(1, 'cm'), #change legend key height
+        legend.key.width = unit(0.5, 'cm'), #change legend key width
+        legend.title = element_text(size = 20),  #change legend title font size
+        legend.text = element_text(size = 20),   #change legend text font size
+        legend.position = "top")
+
+deltaODLogGrowthPlot
+
+```
+
+```{r save deltaODLogGrowthPlot}
+
+ggsave(file = file.path(PlotsOut, paste("deltaODLogGrowthPlot",".png",sep = "")), plot = deltaODLogGrowthPlot, device = NULL, scale = 1, height=20, width= 30, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+# ggsave(file = file.path(PlotsPath, paste("deltaODLogGrowthPlotExpand",".png",sep = "")), plot = deltaODLogGrowthPlotExpand, device = NULL, scale = 1, height=25, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)
+# 
+# ggsave(file = file.path(PlotsPath, paste("deltaODGrowthRatesPlot",".png",sep = "")), plot = deltaODGrowthRatesPlot, device = NULL, scale = 1, height=25, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)
 ```

### 2024-02-22 Code/Manuscript_O2.Rmd
editing introduction

@@
 
-## *Prochlorococcus* evolutionary and functional diversity {.unnumbered}
-
-*Prochlorococcus marinus*, a genus of the phylum Cyanobacteria, is the smallest known photosynthetic prokaryote, with cell diameters ranging from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992].
+*Prochlorococcus marinus*, a genus of Cyanobacteria, is the smallest known photosynthetic prokaryote, with cell diameters ranging from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992].
 Despite small cell size, *P.
@@
 *P.
-marinus* growth is currently constrained to between latitudes of 40°N to 40°S in open ocean waters, from surface to 300 m  depth, thus spanning 3 orders of magnitudes of light [@partenskyProchlorococcusMarinePhotosynthetic1999; @chisholmProchlorococcusMarinusNov1992 ].
-
-*Prochlorococcus marinus* is functionally differentiated from other cyanobacteria primarily by the absence of phycobilisomes [@chisholmProchlorococcusMarinusNov1992].
-Instead, *Prochlorococcus*  utilizes intra-membrane Prochlorophyte Chlorophyll Binding (Pcb) proteins bound to divinylchlorophyll a (Chl a2), and α-carotene, as the major light harvesting complex [@goerickePigmentsProchlorococcusMarinus1992]; [@larocheIndependentEvolutionProchlorophyte1996], with diversity in the number of genes encoding Pcb, expression of Pcb under changing light [@garczarekMultiplicationAntennaGenes2000]  [@rocapGenomeDivergenceTwo2003] [@garczarekMultiplicationAntennaGenes2000], and in thylakoid organization [@partenskyProchlorococcusMarinePhotosynthetic1999].
-The genes encoding most of the rest of the photosynthetic apparatus is highly conserved in *Prochlorococcus* [@kettlerPatternsImplicationsGene2007], though the photosynthetic efficiency may vary among clades [@hessPhotosyntheticApparatusProchlorococcus2001; @moorePhotophysiologyMarineCyanobacterium1999].
-
-*Prochlorococcus marinus* comprises many strains, organized into clades, defined by 16S-23S intergenic transcribed ribosomal sequence signatures (Rocap et al., 2003).
+marinus* growth is currently constrained between latitudes of 40°N to 40°S in open ocean waters, from surface to 300 m depth, thus spanning 3 orders of magnitudes of light [@partenskyProchlorococcusMarinePhotosynthetic1999; @chisholmProchlorococcusMarinusNov1992 ].
+
+*P.
+marinus* is functionally differentiated from other cyanobacteria primarily by the absence of phycobilisomes [@chisholmProchlorococcusMarinusNov1992].
+Instead, *Prochlorococcus*  uses intra-membrane Prochlorophyte Chlorophyll Binding (Pcb) proteins binding divinylchlorophyll a (Chl a2), and α-carotene, as major light harvesting complexes [@goerickePigmentsProchlorococcusMarinus1992]; [@larocheIndependentEvolutionProchlorophyte1996], with diversity in the number of genes encoding Pcb, expression of Pcb under changing light [@garczarekMultiplicationAntennaGenes2000]  [@rocapGenomeDivergenceTwo2003] [@garczarekMultiplicationAntennaGenes2000], and in thylakoid organization [@partenskyProchlorococcusMarinePhotosynthetic1999].
+The genes encoding much of the photosynthetic apparatus is highly conserved in *Prochlorococcus* [@kettlerPatternsImplicationsGene2007], though the photosynthetic efficiency may vary among clades [@hessPhotosyntheticApparatusProchlorococcus2001; @moorePhotophysiologyMarineCyanobacterium1999].
+
+*P.
+marinus* comprises many strains, organized into clades, defined by 16S-23S intergenic transcribed ribosomal sequence signatures (Rocap et al., 2003).
 The clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined by Low-Light (LL) or High-Light (HL).
@@
 
-XXXXMIREILLE Check strain descriptions for accuracyXXXX
-Low-Light clades thrive in deeper ocean waters, extending beyond 200 m in depth [@partenskyProchlorococcusMarinePhotosynthetic1999], where only ~1% of the surface irradiance penetrates, primarily in the blue (450 nm) to green (520 nm) spectral ranges [@holtropVibrationalModesWater2021].
-Clade LLIV, including cultured strain MIT9313, falls near the base of the *Prochlorococcus* radiation, and is characterized by preference for low light, at depths from 120 m and 200 m (Partensky et al., 1999).
-LLIV members are, as yet, the only cultured strains found in Oxygen Minimum Zones (OMZ).
+Low-Light clades thrive in deeper ocean waters, extending beyond 200 m in depth [@partenskyProchlorococcusMarinePhotosynthetic1999], where only ~1% of the surface irradiance penetrates, primarily in the blue (450 nm) to green (520 nm) spectral range [@holtropVibrationalModesWater2021].
+Clade LLIV, including cultured strain MIT9313, falls near the base of the *Prochlorococcus* radiation, and is characterized by preference for low light, typical of depths from 120 m to 200 m (Partensky et al., 1999).
+LLIV members are, as yet, the only cultured strains to have been found in Oxygen Minimum Zones (OMZ).
 Some as yet uncultured *P.
-marinus* strains in clades LLV and LLVI thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021; @lavinNovelLineagesProchlorococcus2010; @goerickeNovelNicheProchlorococcus2000; @robledoCrypticOxygenCycling2017] (Johnson et al., 1999).
+marinus* strains in clades LLV and LLVI also thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021; @lavinNovelLineagesProchlorococcus2010; @goerickeNovelNicheProchlorococcus2000; @robledoCrypticOxygenCycling2017] (Johnson et al., 1999).
 *P.
@@
 [@lavinNovelLineagesProchlorococcus2010;
-@ulloaCyanobacteriumProchlorococcusHas2021; @partenskyProchlorococcusAdvantagesLimits2010].
-
-Clades LLII and LLIII are often grouped together as the second oldest phylogenetic lineages in the *Prochlorococcus* radiation, and share an affinity for low light; LLIII cultured strain SS120, was isolated from 135 m depth in the Sargasso Sea.
-
-Clade LLI  includes cultured strains NATL1A and NATL2A, which prefer moderate irradiances found between 30 and 100 m depth.
+@ulloaCyanobacteriumProchlorococcusHas2021; @partenskyProchlorococcusAdvantagesLimits2010], and may be net O~2~ consumers (2018, Partensky et al. 2018).
+
+Clades LLII and LLIII are grouped together as the second oldest phylogenetic lineages diversifying in the *Prochlorococcus* radiation, and share an affinity for low light; LLIII cultured strain SS120, was isolated from 135 m depth in the Sargasso Sea.
+
+Clade LLI  includes cultured strains NATL1A and NATL2A, which prefer moderate irradiances typical between 30 and 100 m depth.
 

### 2024-02-22 Code/Manuscript_O2.Rmd
working on introduction

@@
 
+## *Prochlorococcus marinus* diversity
 *Prochlorococcus marinus*, a genus of Cyanobacteria, is the smallest known photosynthetic prokaryote, with cell diameters ranging from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992].
@@
 
-Clades LLII and LLIII are grouped together as the second oldest phylogenetic lineages diversifying in the *Prochlorococcus* radiation, and share an affinity for low light; LLIII cultured strain SS120, was isolated from 135 m depth in the Sargasso Sea.
+Clades LLII and LLIII are grouped together as the second oldest phylogenetic lineages diversifying in the *P.
+marinus* radiation, and share an affinity for low light; LLIII cultured strain SS120, was isolated from 135 m depth in the Sargasso Sea.
 
@@
 HL clades are the most recently evolved lineages, with reduced genome sizes in comparison to LL ecotypes.
-High-Light clades are  typically dominant picophytoplankton in near-surface, oligotrophic waters, characterized by high light levels.
+High-Light clades are typically dominant picophytoplankters in near-surface, oligotrophic waters, characterized by high light levels.
 Clade HLI, including cultured strain MED4,is adapted to higher iron, and lower temperatures, and originated from the Mediterranean Sea, just 5 m below the surface [@partenskyProchlorococcusMarinePhotosynthetic1999].
-Clade HLII adapted to higher iron, and higher temperatures, is the most abundant group in the North Atlantic and North Pacific Oceans, often constituting over 90% of the total population [@partenskyProchlorococcusMarinePhotosynthetic1999],  and are most numerous around 50 m depth [@partenskyProchlorococcusMarinePhotosynthetic1999].
+Clade HLII adapted to higher iron, and higher temperatures, is the most abundant *P.
+marinus* clade in the North Atlantic and North Pacific Oceans, often constituting over 90% of the total population [@partenskyProchlorococcusMarinePhotosynthetic1999],  and are most numerous around 50 m depth [@partenskyProchlorococcusMarinePhotosynthetic1999].
 Clade HLIII/IV is adapted to lower iron [@kentParallelPhylogeographyProchlorococcus2019; @johnsonNichePartitioningProchlorococcus2006; @zinserInfluenceLightTemperature2007].
 
-*Prochlorococcus marinus* clades are found  in environments beyond their optimal habitats. HL clades inhabit depths overlapping with LL ecotypes
+*P. marinus* clades are nonetheless found  in environments beyond their optimal habitats. HL clades inhabit depths overlapping with LL ecotypes
 [@westNichePartitioningProchlorococcusPopulationsStratified1999;
@@
 [@moorePhotophysiologyMarineCyanobacterium1999]. 
-@lavinNovelLineagesProchlorococcus2010 and
-@mattisonPhotosyntheticStrategiesWild2020 show that LL ecotypes
-can occupy regions in the OMZ at depths above 40 m, reaching ambient light levels above what LL clades were thought to tolerate.
+@lavinNovelLineagesProchlorococcus2010, while LL ecotypes can occupy regions in OMZ at depths above 40 m, exploiting ambient light levels above what LL clades were thought to tolerate.
 
@@
 
-Our changing climate, characterized by warming ocean waters, is rapidly altering conditions for these highly specialized strains of marine picophytoplankton.
+Our changing climate, characterized by warming ocean waters, is rapidly altering conditions for these specialized clades of marine picophytoplankton.
 Predictions indicate a net global increase of *P.
-marinus* cell abundances of 29%, along with  poleward latitudinal shifts of at least 10° in marine phytoplankton niches by the end of this century [@flombaumPresentFutureGlobal2013] in response to warming waters, with increases in *Prochlorococcus* of approximately 50% in the more poleward regions.
-As the solar incidence angles are lower and photoperiod seasonality is more pronounced at higher latitudes, this shift will carry these phytoplankters into new combinations of photoperiod, seasonal regimes and changing spectral regimes [@bartonAnthropogenicClimateChange2016].
-A 10° poleward shift of *P.
-marinus*, coupled with a dramatic increase in cell abundance between 40°N and 50°N,  could have a large impact on ocean ecosystems and global biogeochemical cycles [@flombaumPresentFutureGlobal2013], and thus will undoubtedly impact the ecosystem balance off Canadian waters.
-
-Global warming is also rapidly changing the chemistry of our oceans.
-By the end of this century, surface ocean pH is projected to decline by 0.1 to 0.4  due to  projected increases in carbon dioxide concentrations [@garcia-sotoOverviewOceanClimate2021].
+marinus* cell abundances of 29%, along with  poleward latitudinal shifts of at least 10° in marine phytoplankton niches by the end of this century [@flombaumPresentFutureGlobal2013] in response to warming waters, with increases in *P.
+marinus* of approximately 50% in the more poleward regions of their distributions.
+As solar incidence angles are lower, and photoperiod seasonality is more pronounced, at higher latitudes, polewards shifts will carry these phytoplankters into new combinations of photoperiod, seasonal regimes and changing spectral regimes [@bartonAnthropogenicClimateChange2016].
+
+Global warming is also rapidly changing ocean chemistry.
+By the end of this century, surface ocean pH is projected to decline by 0.1 to 0.4  due toprojected increases in carbon dioxide concentrations [@garcia-sotoOverviewOceanClimate2021].
 Moreover, substantial changes in the global water cycle, leading to extensive changes in worldwide precipitation patterns, are affecting ocean salinity levels on a global scale, and ice melts due to rising temperatures are impacting salinity levels in the Arctic and Northwest Atlantic oceans [@leeRecognizingSalinityThreats2022].

### 2024-02-22 Code/Manuscript_O2.Rmd
Added figures

--- 2024-02-22 Code/Manuscript_O2.Rmd
@@
 
-We employed GAM to summarize and visualize th complex responses of growth to the interactions of peak PAR, oxygen, photoperiod and blue vs. red spectral bands
-
-The GAM model in Figure \@ref(fig:MED4GAM) summarizes MED4 growth in response to red (A) or blue (B) peak PAR and photoperiod across 2 imposed oxygen concentrations.
-Under 250 µM O~2~ MED4 achieved fastest growth rates above peak blue light of ~180 µmol photons m^-2^ s^-1^, and the longest photoperiod of 16, indicated by the 0.69 d^-1^ contour line representing the
-90^th^ percentile of maximum achieved growth rate.
+We employed GAM to summarize and visualize the complex responses of growth to the interactions of peak PAR, oxygen, photoperiod and blue vs. red spectral bands
+
+The GAM model in Figure \@ref(fig:MED4GAM) summarizes MED4 growth in response to red (A,B) or blue (C,D) peak PAR and photoperiod across 2 imposed oxygen concentrations.
+Under 250 µM O~2~ MED4 achieved fastest growth rates above peak blue light of ~180 µmol photons m^-2^ s^-1^, and the longest photoperiod of 16, indicated by the 0.64 d^-1^ contour line representing the
+90^th^ percentile of maximum achieved growth rate (Figure \@ref(fig:MED4GAM)C).
 Growth decreased with decreasing photoperiod and peak PAR.
-Under red light growth was generally slower but the pattern of growth responses to photoperiod and PAR was similar.
-We again note the exclusion of MED4 from growth under 4 h photoperiod.
-Under 25 µM O~2~ MED4 showed similar growth responses, but was excluded from both 4 and 8 h photoperiods.
+Under red light growth was generally slower but the pattern of growth responses to photoperiod and PAR was similar (Figure \@ref(fig:MED4GAM)A).
+We again note the exclusion of MED4 from growth under 4 h photoperiod under both red and blue light (Figure \@ref(fig:MED4GAM)A,C).
+Under 25 µM O~2~ MED4 showed similar growth responses, but was excluded from both 4 and 8 h photoperiods XXX GAM changed after removing 1 bad run XXX and does not reflect true pattern at higher photoperiod and light MIrielle to fix.
 

### 2024-02-22 Code/Manuscript_O2.Rmd
introduction edits

--- 2024-02-22 Code/Manuscript_O2.Rmd
@@
 
-## *Prochlorococcus* responses to changing niches {.unnumbered}
+## *Prochlorococcus* and changing niches {.unnumbered}
 
@@
 Predictions indicate a net global increase of *P.
-marinus* cell abundances of 29%, along with  poleward latitudinal shifts of at least 10° in marine phytoplankton niches by the end of this century [@flombaumPresentFutureGlobal2013] in response to warming waters, with increases in *P.
+marinus* cell abundances of 29%, along with  poleward latitudinal shifts of at least 10° in marine phytoplankton niches by the end of this century [@flombaumPresentFutureGlobal2013][@bartonAnthropogenicClimateChange2016] in response to warming waters, with increases in *P.
 marinus* of approximately 50% in the more poleward regions of their distributions.
-As solar incidence angles are lower, and photoperiod seasonality is more pronounced, at higher latitudes, polewards shifts will carry these phytoplankters into new combinations of photoperiod, seasonal regimes and changing spectral regimes [@bartonAnthropogenicClimateChange2016].
-
-Global warming is also rapidly changing ocean chemistry.
-By the end of this century, surface ocean pH is projected to decline by 0.1 to 0.4  due toprojected increases in carbon dioxide concentrations [@garcia-sotoOverviewOceanClimate2021].
+
+Near the equator, photoperiod remains relatively constant at the ocean surface, approximately 12 hours (h) of daylight and 12 h of darkness throughout the year.
+The effective length of the photoperiod does, however attentuate with depth as dawn and dusk light at depth drops below the level needed for biological processes.
+As *P.
+marinus* potentially expands its temperature-permissive niches poleward into temperate regions  [@flombaumPresentFutureGlobal2013; @bartonAnthropogenicClimateChange2016], it will encounter more
+pronounced seasonal variations in photoperiod regimes both at surface and at depth, with potentially complex effects upon viable growth niches @liDiatomGrowthResponses2017 @prezelinDielPeriodicityPhytoplankton1992.
+For example, @vaulotGrowthProchlorococcusPhotosynthetic1995 showed that *Prochlorococcus* replication of DNA occurs in the afternoon, while cell division occurs at night.
+
+Climate change is also rapidly changing ocean chemistry.
+By the end of this century, surface ocean pH is projected to decline by 0.1 to 0.4  due to projected increases in carbon dioxide concentrations [@garcia-sotoOverviewOceanClimate2021].
 Moreover, substantial changes in the global water cycle, leading to extensive changes in worldwide precipitation patterns, are affecting ocean salinity levels on a global scale, and ice melts due to rising temperatures are impacting salinity levels in the Arctic and Northwest Atlantic oceans [@leeRecognizingSalinityThreats2022].
-Increasing sea temperatures are also causing a decrease in [O~2~] across our global oceans [@matearLongtermChangesDissolved2003], with significant declines in [O~2~] observed toward the poles in both hemispheres [@helmObservedDecreasesOxygen2011].
+Increasing sea temperatures are also causing decreases in [O~2~] across global oceans [@matearLongtermChangesDissolved2003], particularly toward the poles [@helmObservedDecreasesOxygen2011].
 Warmer ocean waters increase stratification, and decrease oxygen solubility at the surface, which in turn decreases oxygen mixing downwards by ocean currents [@garcia-sotoOverviewOceanClimate2021].
-Models predict that the OMZ in the Pacific and Indian Oceans are expanding [@garcia-sotoOverviewOceanClimate2021; @buseckeDivergingFatesPacific2022].
-In light of these expanding OMZ, a recent study by @buseckeDivergingFatesPacific2022 highlights an intriguing finding; the cores of the OMZ, where the oxygen levels are lowest, is projected to contract.
-Given the predicted decrease in overall oceanic [O~2~], projected expansion of OMZs, and possible decline in the OMZ core volumes, we set forth to examine the influence of [O~2~] on *P.
-marinus* growth, as this area of research has been relatively understudied.
-
-Near the equator, photoperiod remains relatively constant at the ocean surface, approximately 12 hours (h) of daylight and 12 h of darkness throughout the entire year.
-The effective length of the photoperiod does, however attentuate with depth as dawn and dusk light drops below the level needed for biological processes.
-As *P.
-marinus* potentially expands its temperature-permissive niches poleward into temperate regions
-[@flombaumPresentFutureGlobal2013; @bartonAnthropogenicClimateChange2016], it will encounter more
-pronounced seasonal variations in photoperiod regimes at surface and at depth.
-With the influence of light attenuation with depth, temperate regions exhibit more combinations of photoperiod, compared to equatorial regions, with potentially complex effects upon viable growth niches @liDiatomGrowthResponses2017 @prezelinDielPeriodicityPhytoplankton1992.
-@vaulotGrowthProchlorococcusPhotosynthetic1995 showed that *Prochlorococcus* replication of DNA occurs in the afternoon, while cell division occurs at night.
-
-We therefore analyzed the growth and physiological responses of representative strains from three clades under a matrix of [O~2~], light levels, spectral waveband ranges, and photoperiods,  to approximate eco-physiological conditions representative of current and hypothetical future ocean zones.
+Models predict that OMZ in the Pacific and Indian Oceans are expanding [@garcia-sotoOverviewOceanClimate2021; @buseckeDivergingFatesPacific2022].
+In spite of these expanding OMZ @buseckeDivergingFatesPacific2022 highlight that the cores of the OMZ, where the oxygen levels are lowest, are actually projected to contract.
+
+We therefore analyzed the growth and physiological responses of representative strains from three clades ofr *P.
+marinus* under a matrix of [O~2~], light levels, spectral waveband ranges, and photoperiods, to approximate eco-physiological conditions representative of current and hypothetical future ocean zones.
 *P.
-marinus* MED4, a clade HLI strain (Figure \@ref(fig:PhylogenyTreeYan2018edit)), was isolated near the ocean surface (5m depth) of the Mediterranean Sea where [O~2~] is near saturation, light levels are high and spectral bias from full solar irradiance is minimal.
+marinus* MED4, a clade HLI strain, was isolated near the ocean surface (5m depth) of the Mediterranean Sea where [O~2~] is near saturation, light levels are high and spectral bias from full solar irradiance is minimal.
 *P.
-marinus* SS120, a clade LLIII (Figure \@ref(fig:PhylogenyTreeYan2018edit)), was isolated from the Sargasso Sea at a depth of 120 m, while *P.
-marinus* MIT9313, a clade LLIV (Figure \@ref(fig:PhylogenyTreeYan2018edit)), was isolated from the North Atlantic Gulf Stream at a depth of 135 m.
-At these depths, light attenuation and spectral shifts occur, resulting in low blue and green light levels, while [O~2~] varies from near-surface saturation levels to decreased concentrations, but does not necessarily decrease systematically with depth [@billheimerOxygenSeasonalityUtilization2021].
+marinus* SS120, a clade LLIII strain, was isolated from the Sargasso Sea at a depth of 120 m, while *P.
+marinus* MIT9313, a clade LLIV strain, was isolated from the North Atlantic Gulf Stream at a depth of 135 m.
+At these depths, light attenuation and spectral shifts occur, resulting in low blue and green light, while [O~2~] varies from near-surface saturation levels to decreased concentrations, but does not necessarily decrease systematically with depth [@billheimerOxygenSeasonalityUtilization2021].
 
 We then analyzed growth rates in terms of cumulative diel Photosynthetically Usable Radiation (PUR).
-Photosynthetic organisms rely on absorbing light energy within the Photosynthetically Active Radiation (PAR) range, 350 to 700 nm, for photosynthesis [@morelAvailableUsableStored1978].
-PUR represents the fraction of PAR that is absorbed by the pigments of photosynthetic organisms [@morelAvailableUsableStored1978].
-PUR, therefore, takes into account the pigment composition of photosynthetic organisms and the specific spectral wavebands these pigments absorb.
-*Prochlorococcus marinus* light-harvesting complexes, [@chisholmProchlorococcusMarinusNov1992;
+Photosynthetic organisms absorb light energy within the Photosynthetically Active Radiation (PAR) range, 350 to 700 nm, for photosynthesis [@morelAvailableUsableStored1978].
+PUR represents the fraction of PAR that is absorbed by the pigments of a given photosynthetic organism [@morelAvailableUsableStored1978], taking into account the specific spectral wavebands these pigments absorb.
+*P.
+marinus* light-harvesting complexes, [@chisholmProchlorococcusMarinusNov1992;
 @goerickePigmentsProchlorococcusMarinus1992], show an absorption maxima
@@
 habitats, where only blue spectral wavelengths prevail [@holtropVibrationalModesWater2021].
-In *Prochlorococcus* small cell diameters, from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992], and simple cell structures, minimize the complication of pigment package effect or intracellular self-shading [@morelProchlorococcusSynechococcusComparative1993].
+In *P.
+marinus* small cell diameters, from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992], and simple cell structures, minimize the complication of pigment package effect or intracellular self-shading [@morelProchlorococcusSynechococcusComparative1993].
 Given the different spectral light regimes typical of the niches of different ecotypes, expressing growth rates in terms of cumulative diel absorbed PUR might simplify different photoperiods, spectral bands, and PAR levels into a common parameter, making growth response comparisons across strains and different oxygen levels more accessible.

### 2024-02-22 Code/Manuscript_O2.Rmd
Added DNA repair

--- 2024-02-22 Code/Manuscript_O2.Rmd
@@
 
+```{r ProchlorococcusEnzymeKms, fig.cap = ProchlorococcusEnzymeKms_cap, fig.height = 15, fig.width = 15, echo = FALSE}
+
+ProchlorococcusEnzymeKms_cap <- glue("**K~m~ values for oxygen metabolizing enzymes.**" ,
+                                     "The y-axis represents the log10 concentration of oxygen substrate (mM).",
+                                     "The x-axis represents the oxygen metabolizing enzymes encoded in at least one of the *Prochlorococcus marinus* strains in this study.",
+                                     "The *Prochlorococcus marinus* strains are indicated in rows." ,
+                                     "The solid circles represent K~m~ values from literature and the asterisks represent predicted values.",
+                                     "Colors represent the gene counts.",
+                                     "The red shaded area denotes a K~m~ oxygen concentration range from 230 to 280 µM.",
+                                     "The green shaded area denotes a K~m~ oxygen concentration range from 5 to 50 µM . ",
+                                     "The blue shaded area denotes a K~m~ oxygen concentration range from 0.5 to 5 µM.  ",
+                                     "The black bars show the minimum and maximum K~m~ values.",
+                       "Figure was generated using a filtered subset of the annotated phytoplankton gene sequences dataset from @omarAnnotationGenesEncoding2023.",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "ProchlorococcusEnzymeKms.png"))
+
+```
+
+\newpage
+
+Figure \@ref(fig:DNARepairFig) displays the genes encoding DNA repair for the three *P.
+marinus* strains examined in this study.
+As expected,  *P.
+marinus* MED4 possesses the largest and most complete suite of genes encoding DNA repair enzymes, followed by *P.
+marinus* MIT9313.
+Conversely, *P.
+marinus* SS120 demonstrates the smallest genomic capacity for DNA repair.
+*Prochlorococcus marinus* MED4 was the only strain out of the three strains in this study to possess the gene encoding deoxyribodipyrimidine photolyase, which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003].
+*Prochlorococcus marinus* MED4 was also the only strain to possesses the gene encoding DNA ligase, which uses ATP as a cofactor for DNA repair.
+The absence of the genes encoding deoxyribodipyrimidine photolyase and DNA ligase (ATP) in *P.
+marinus* MIT9313 and *P.
+marinus* SS120 explains why these two strains cannot tolerate the high light levels found at the ocean surface where  *P.
+marinus* MED4 inhabits.
+
+\newpage
+
+```{r DNARepairFig, fig.cap = DNARepairFig_cap, fig.height = 10, fig.width = 10, echo = FALSE}
+
+DNARepairFig_cap <- glue("**Genes encoding DNA repair enzymes.**" ,
+                         "The y-axis represents  *Prochlorococcus marinus* strains.",
+                         "The x-axis represents enzymes encoded for DNA repair found in at least one *Prochlorococcus marinus* strain in this study.",
+                         "The red solid circles represent a gene count of 1.",
+                         "The green solid circles represent a gene count of 2.",
+                         "The blue solid circles represent a gene count of 3.",
+                       "Figure was generated using a filtered subset of the annotated phytoplankton gene sequences dataset from @omarAnnotationGenesEncoding2023.",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "DNARepairFig.png"))
+
+```
+
+\newpage
 \newpage
@@
 
+\newpage
+
+```{r deltaODLogGrowthPlot, fig.cap = deltaODLogGrowthPlot_cap , fig.height = 8, fig.width = 6, echo = FALSE}
+
+deltaODLogGrowthPlot_cap <- glue("**Fitting chlorophyll proxy growth rate for each tube in the Multicultivator.**",
+                      "The left y-axis is $\\Delta$OD (OD680 - OD720).",
+                      "The right y-axis is actinic PAR levels (µmol photons m^-2^ s^-1^).",
+                      "The x-axis is time in hours (h).",
+                      "The green points are $\\Delta$OD measurements taken every 5 minutes.",
+                      "The black lines are logistic growth curves fit using a nonlinear model regression (R package, minpack.lm). ",
+                      "The gold points are the residuals of the fit.",
+                      "The blue or orange points represent the actinic spectral waveband under 450 nm or 660 nm, showing the imposed PAR level (µmol photons m^-2^ s^-1^) and photoperiod (h).",
+                      "Meta data associated with each Multicultivator tube are in columns.",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "deltaODLogGrowthPlot.png"))
+```
+
+\newpage
+
 ```{r LabeledMC, fig.cap = LabeledMC_cap , fig.height = 8, fig.width = 6, echo = FALSE}

### 2024-02-22 Code/Manuscript_O2.Rmd
introduction edits

--- 2024-02-22 Code/Manuscript_O2.Rmd
@@
 
+We used the OceansMap Protein Portal (OPP; https://proteinportal.whoi.edu/) to analyze the distribution of proteins from clades of *P.
+marinus* in samples tanken across a range of [O~2~] and depth, which in turn correlates to peak light at the site of sampling.
 We therefore analyzed the growth and physiological responses of representative strains from three clades ofr *P.
@@
 We also aimed to detect whether growth responses are driven simply by cumulative diel absorbed PUR, or whether specific photoperiods, spectral bands or PAR levels have independent, albeit interacting, effects on growth.
+
+We discuss our findings in relation to analyses of genomic sequences CITATIONS across clades of *P.
+marinus*, showing that differences in the presence of genes encoding oxygen-dependent enzymes, and DNA repair enzymes, can help explain differential growth responses of strains under the matrix of light and [O~2~].
 

### 2024-02-22 Code/Manuscript_O2.Rmd
Materials & Methods edits

@@
 
+## MetaProteomics bioinformatic analyses  {.unnumbered}
+
+Metaproteomic datasets were obtained from the KM1128 entry in the BCO-DMO database (https://www.bco-dmo.org/deployment/59053) accessed via the OPP in June 2019. Datasets contained:
+	i) Peptide sequences and sample identification (ID) number;
+	ii) Sample ID number, station, depth in meters below the surface the sample was collected at, best-hit BLASTP protein and species annotation and the corresponding Uniprot Entry number for the identified proteins;
+	iii) Sample station depth and [O~2~].  
+	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using the Tidyverse package [@R-tidyverse] in RStudio v1.2.5019 (https://rstudio.com/)  (LOCATION OF CODE ON GITHUBO.
+The resulting merged dataset was filtered for those *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b6f (Cytb6f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Terminal Oxidase (PTOX); plastocyanin (PC); ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  ATP Synthase;  FtsH proteases (FtsH) or ribosomes.
+	Detected peptides were re-annotated for consistency and labelled, where feasible, according to strain, clade, subunit and protein complex.
+Full protein sequences corresponding to detected proteins were obtained from UniProt (https://www.uniprot.org/) and analyzed in Molecular Evolution and Genetic Analyses X (MEGAX) software  (https://www.megasoftware.net/).
+Sequences for proteins for each of the thirteen Prochlorococcus strains identified in the dataset were aligned with MUSCLE using UPGMA cluster method and a lambda of 24 with a -2.9 gap open penalty and 1.20 hydrophobicity multiplier.
+Overall mean pairwise distance between protein sequences was determined using bootstrap variance estimation methods.
+Maximum likelihood phylogenetic trees were assembled using 1000 bootstrap replications with a 95% site coverage cut off.
+*Prochlorococcus* FtsH isoform identities, and functions, were inferred by sequence comparisons to the characterized four isoforms of FtsH protease of *Synechocystis* sp.
+PCC6803 (CITATONS).
+Data for each strain was plotted against depth and  [O~2~] and sampling station.
+
+When assessing the presence of a particular protein complex at a sampling location, all peptides belonging to all subunits of the complex were included to give the greatest number of data points.
+As this data was acquired on a discovery mission rather than through targeted peptide approaches, it is difficult to discern accuracies of strain assignment annotations, particularly as the proteins of interest in this study are highly conserved across strains.
+We are, however, confident in clade classifications for each protein examined.
+A caveat to interpretation of this data is the peptide detection bias inherent to mass spectrometry CITATION.
+The data is also limited by the number and nature of protein spectra in the SEQUEST database: a peptide sequence was not determined unless there is already a known spectrum for that peptide in the SEQUEST database, hence some peptides of interest may not be identifiable.
+Furthermore, a peptide must be detected above a certain threshold abundance in order to be considered an accurate ‘hit’.
+
 ## *Prochlorococcus* culturing and experimental design {.unnumbered}
@@
 
-## MetaProteomics bioinformatic analyses and limitations  {.unnumbered}
-
-Metaproteomic datasets were obtained from the KM1128 entry in the BCO-DMO database (https://www.bco-dmo.org/deployment/59053) accessed via the OPP in June 2019. Datasets contained:
-	i) Peptide sequences and sample identification (ID) number;
-	ii) Sample ID number, station, depth in meters below the surface the sample was collected at, best-hit BLASTP protein and species annotation and the corresponding Uniprot Entry number for the identified proteins;
-	iii) Sample station depth and [O~2~].  
-	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using the Tidyverse package [@R-tidyverse] in RStudio v1.2.5019 (https://rstudio.com/)  (LOCATION OF CODE ON GITHUBO.
-The resulting merged dataset was filtered for those *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b6f (Cytb6f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Terminal Oxidase (PTOX); plastocyanin (PC); ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  ATP Synthase;  FtsH proteases (FtsH) or ribosomes.
-	Detected peptides were re-annotated for consistency and labelled, where feasible, according to strain, clade, subunit and protein complex .
-Full protein sequences corresponding to detected proteins were obtained from UniProt (https://www.uniprot.org/) and analyzed in Molecular Evolution and Genetic Analyses X (MEGAX) software  (https://www.megasoftware.net/).
-Sequences for proteins for each of the thirteen Prochlorococcus strains identified in the dataset were aligned with MUSCLE using UPGMA cluster method and a lambda of 24 with a -2.9 gap open penalty and 1.20 hydrophobicity multiplier.
-Overall mean pairwise distance between protein sequences was determined using bootstrap variance estimation methods.
-Maximum likelihood phylogenetic trees were assembled using 1000 bootstrap replications with a 95% site coverage cut off.
-*Prochlorococcus* FtsH isoform identities, and inferred functions, were specified by phylogenetic comparison to the characterized FtsH proteases of Synechocystis sp.
-PCC6803 (CITATONS).
-Data for each strain was plotted against depth and  [O~2~] and sampling station.
-
-When assessing the presence of a particular protein complex at a sampling location, all peptides belonging to all subunits of the complex were included to give the greatest number of data points.
-As this data was acquired on a discovery mission rather than through targeted peptide approaches, it is difficult to discern accuracies of strain assignment annotations, particularly as the proteins of interest in this study are highly conserved across strains.
-We are, however, confident in clade classifications for each protein examined.
-Another caveat to interpretation of this data is the peptide detection bias inherent to mass spectrometry CITATION.
-The data is also limited by the number and nature of protein spectra in the SEQUEST database: a peptide sequence was not determined unless there is already a known spectrum for that peptide in the SEQUEST database, hence some peptides of interest may not be identifiable.
-Furthermore, a peptide must be detected above a certain threshold abundance in order to be considered an accurate ‘hit’.
-
-## Growth data management and analysis {.unnumbered}
+## Growth rate analysis {.unnumbered}
 Data files (.csv) saved from the Multicultivator software were imported into R-Studio [@R-Studio] for data management [@R-tidyverse], growth rate calculations CITATION, comparisons of model fits (get Platt CITATION), and generation of
@@
 
-OTHER MOREXXXXXX
-
-```{=tex}
-\begin{equation}
-  µ = \frac{ΔOD_{max} × ΔOD_{min} × exp^{(µ × t)}}{ΔOD_{max} + (ΔOD_{min} × exp^{((µ × t) - 1)})}
-  (\#eq:GrowthRate)
-\end{equation}
-```
-
-### Generalized additive model of growth responses {.unnumbered}
+## Generalized additive model of growth responses {.unnumbered}
 
@@
 
-### Estimation of photosynthetically usable radiation {.unnumbered}
+## Estimation of photosynthetically usable radiation {.unnumbered}
 
@@
 
+```{=tex}
+\begin{equation}
+  µ = \frac{ΔOD_{max} × ΔOD_{min} × exp^{(µ × t)}}{ΔOD_{max} + (ΔOD_{min} × exp^{((µ × t) - 1)})}
+  (\#eq:GrowthRate)
+\end{equation}
+```
+
 \newpage
@@
 
-### Quantitative protein immunoblotting {.unnumbered}
+## Quantitative protein immunoblotting {.unnumbered}
 
@@
 
+## Naaman GENOMICS METHODS
+XXX
+
+\newpage
+
 # Results {.unnumbered}
@@
 
+XXXMore TextXXX from AuroraXXX
 Proteins derived from Clade HLXXX ecotypes of *P. marinus* were detected in OMZ at depths up to 200 meters,  with O~2~ of 15 µM. The extent to which [O~2~] defines
@@
 
-## *Prochlorococcus marinus* growth responses to photoperiod, PAR, spectral bands,  and O~2~  {.unnumbered}
+## *Prochlorococcus marinus* growth responses to photoperiod, PAR, spectral band, and [O~2~]  {.unnumbered}
 

### 2024-02-22 Code/Manuscript_O2.Rmd
edits to results & discussion

@@
 For example, @vaulotGrowthProchlorococcusPhotosynthetic1995 showed that *Prochlorococcus* replication of DNA occurs in the afternoon, while cell division occurs at night.
+To our knowledge, no study has as yet addressed *P.
+marinus* growth responses in relation to a  range of photoperiods.
 
@@
 
-# Results {.unnumbered}
+# Results and discussion {.unnumbered}
 
@@
                        "Columns show detections of proteins annotated as  Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
-                       "For comparison culture growth experimental conditions are indicated by horizontal grey lines for depths approximating imposed peak Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^); and vertical grey lines for O~2~ (µM).",
+                       "For comparison culture growth experimental conditions are indicated by horizontal grey lines for depths approximating imposed peak Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^); and vertical grey lines for [O~2~] (µM).",
                        "Point colours identify *Prochlorococcus* clade assignments",
@@
 The growth rates of *P. marinus* MED4, Clade HLI, increased with higher imposed PAR and longer photoperiods
-(Figure \@ref(fig:MED4PAR)), under 250 µM O~2~. No growth was
-observed under any imposed conditions under a 4 h photoperiod. MED4 was
-able to grow under the lowest PAR treatment of 30 µmol photons m^-2^
-s^-1^ but only when the blue light photoperiod was longer than 4 h and the white LED and red light photoperiod was longer than 8 h. Growth rate increased
-with increasing photoperiods for all spectral wavebands when exposed to
-PAR of 90 and 180 µmol photons m^-2^ s^-1^. MED4 grew fastest for each
-spectral waveband under 16 h photoperiods. The maximum growth rate
+(Figure \@ref(fig:MED4PAR)), under 250 µM O~2~, across all spectral wavebands. No growth was
+observed under any imposed conditions under a 4 h photoperiod.The maximum growth rate
 (µ~max~) was
 `r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
-d^-1^ achieved under 180 uE blue
-light and 16 h photoperiod.
+d^-1^ achieved under 180 uE blue light and 16 h photoperiod.
 
@@
 photoperiod was 16 h for each spectral waveband, across PAR levels
-(Figure \@ref(fig:MED4PAR)). The 25 µM O~2~ growth experiments showed
-generally similar growth rates as the 250 µM O~2~ growth experiments,
-with the interesting exception that growth rates increased by 40 % under
-25 µM O~2~ at PAR of 30 µmol photons m^-2^ s^-1^ and 16 h blue photoperiod and increased by 55 % under 16 h red photoperiod, in contrast to
-the 250 µM O~2~ growth experiments. White LED light treatments grew
-slower, if at all, under 25 µM O~2~, only growing under higher PAR of 90 µmol photons m^-2^ s^-1^ and 16 h photoperiod and 180 µmol photons m^-2^ s^-1^ and 12 and 16 h photoperiods.
-As under 250 µM O~2~, the fastest growth rate observed for each spectral
-waveband at each imposed PAR were greatest under the 16 h photoperiod.
-The µ~max~ was
-`r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "25", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+(Figure \@ref(fig:MED4PAR)).
+The µ~max~ was `r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "25", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
 d^-1^  achieved under 180 µmol photons
@@
 experiments under white LED light were not performed because no growth
-was achieved when grown under an 8 h photoperiod.
+was achieved when grown under an 8 h photoperiod of white LED light.
 
@@
 
-XXX Fig letters do not match as now we have red GAMs. Below is results for Blue GAMsXXXX
-
-We employed GAM to summarize and visualize the complex responses of growth to the interactions of peak PAR, oxygen, photoperiod and blue vs. red spectral bands
-
-The GAM model in Figure \@ref(fig:MED4GAM) summarizes MED4 growth in response to red (A,B) or blue (C,D) peak PAR and photoperiod across 2 imposed oxygen concentrations.
+The GAM model in Figure \@ref(fig:MED4GAM) summarizes MED4 growth responses to red (A,B) or blue (C,D) peak PAR and photoperiod across 2 imposed oxygen concentrations.
 Under 250 µM O~2~ MED4 achieved fastest growth rates above peak blue light of ~180 µmol photons m^-2^ s^-1^, and the longest photoperiod of 16, indicated by the 0.64 d^-1^ contour line representing the
 90^th^ percentile of maximum achieved growth rate (Figure \@ref(fig:MED4GAM)C).
-Growth decreased with decreasing photoperiod and peak PAR.
+Growth decreased with decreasing photoperiod and decreasing peak PAR.
 Under red light growth was generally slower but the pattern of growth responses to photoperiod and PAR was similar (Figure \@ref(fig:MED4GAM)A).
-We again note the exclusion of MED4 from growth under 4 h photoperiod under both red and blue light (Figure \@ref(fig:MED4GAM)A,C).
-Under 25 µM O~2~ MED4 showed similar growth responses, but was excluded from both 4 and 8 h photoperiods XXX GAM changed after removing 1 bad run XXX and does not reflect true pattern at higher photoperiod and light MIrielle to fix.
+Note the exclusion of MED4 from growth under 4 h photoperiod under both red and blue light (Figure .
+Under 25 µM O~2~ MED4 showed similar growth responses, but was excluded from both 4 and 8 h photoperiods.
+MED4 did not grow under 25 µM O~2~, so no GAM model was run.
+
+The representative of HLI clade, *P. marinus* MED4, was completely
+excluded from growth under the 4 h photoperiod \@ref(fig:MED4GAM)A,C), and showed
+increasing growth rates with increasing photoperiod. Thus, MED4 can
+potentially exploit longer summer photoperiods in temperate zones, but
+will likely remain excluded from growth in winter through its requirement for
+more than 4 h of light per day, even if water temperature warms into the Clade HLI tolerance range.
+
+MED4 grew under all PAR levels, so long as the photoperiod was longer than 4 h,
+although growth rates were slow under the lowest PAR level of 30 µmol
+photons m^-2^ s^-1^. Considering the range of PAR levels that MED4 can
+utilize, it is reasonable to suggest that MED4 can inhabit not just
+shallow depths, where light levels are high, but also deeper regions
+characterized by lower light levels, subject to the limitation of a
+photoperiod of at least 4 h even after depth attenuation of light. The photo
+regimes of winter temperate zones, due to shorter photoperiods, exclude
+MED4 from growth at all depths, however temperate photoperiods and light
+levels for the remainder of the year are adequate to support growth.
+
+MED4, grew under all tested spectral wavebands. Growth rates were
+generally comparable under blue, white LED and red lights when exposed
+to PAR levels greater than 30 µmol photons m^-2^ s^-1^ for each
+photoperiod. At the lower PAR of 30 µmol photons m^-2^ s^-1^, MED4 grew
+better under blue light. All growth rates for each spectral waveband
+increased with increasing photoperiod. The ability to utilize all
+spectral wavebands at high PAR levels and longer photoperiods make the
+near surface temperate zones available niches for MED4. MED4 ability to
+exploit blue light under low PAR levels and variable photoperiods
+greater than 4 h allow MED4 to exploit deeper regions in these temperate
+zones, where blue light prevails.
 
@@
 marinus* SS120, Clade LLIII, increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^ peak PAR and 250 µM O~2~ (Figure \@ref(fig:SS120PAR)).
-No growth was observed under any blue light photoperiods when
-exposed to peak PAR of 90 µmol photons m^-2^ s^-1^ or greater. Growth rate increased
-with increasing photoperiods for white and red light under peak PAR of 90 µmol photons m^-2^ s^-1^; however, no growth was observed
-when the red light photoperiod was 16 h. Experiments under peak PAR
-of 180 µmol photons m^-2^ s^-1^ showed no growth under blue nor
-red lights. Growth rate decreased with longer photoperiods and showed
-growth inhibition at 12 and 16 h photoperiods under PAR of 180 µmol
-photons m^-2^ s^-1^  white LED light.  The µ~max~ was
-`r PURPARFits %>% filter(Strain == "SS120", WL == "WW", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
-d^-1^  achieved under 90 µmol photons
-m^-2^ s^-1^ white LED light and 16 h photoperiod.
+No growth was observed under any blue light photoperiods when exposed to peak PAR of 90 µmol photons m^-2^ s^-1^ or greater.
+Growth rate increased with increasing photoperiods for white and red light under peak PAR of 90 µmol photons m^-2^ s^-1^; however, no growth was observed when the red light photoperiod was 16 h.
+Experiments under peak PAR
+of 180 µmol photons m^-2^ s^-1^ showed no growth under blue nor red lights.
+Growth rate decreased with longer photoperiods and showed growth inhibition at 12 and 16 h photoperiods under PAR of 180 µmol
+photons m^-2^ s^-1^  white LED light.
+The µ~max~ was `r PURPARFits %>% filter(Strain == "SS120", WL == "WW", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^  achieved under 90 µmol photons m^-2^ s^-1^ white LED light and 16 h photoperiod.
 
@@
 
-XXX Fig letters do not match as now we have red GAMs. Below is results for Blue GAMsXXXX
-
 The GAM model in Figure \@ref(fig:SS120GAM) summarizes growth
-responses of SS120 red (A) or blue (B) peak PAR and photoperiod,
+responses of SS120 to red (A) or blue (B) peak PAR and photoperiod,
 across the 2 imposed oxygen concentrations. Under 250 µM O~2~,
 Figure \@ref(fig:SS120GAM)A showed highest growth
-rates achieved below PAR of 50 µmol photons m^-2^ s^-1^ and
+rates below PAR of 50 µmol photons m^-2^ s^-1^ and
 photoperiods between 8 and 12 h, indicated by the contour line labeled
 0.29 d^-1^ (representing the 90^th^ percentile of achieved growth rate).
-Note the disjunct regions of the plots, resulting from variable growth successes of SS120 under 250 µM O~2~.
+The disjunct regions of the GAM plot results from variable growth success of SS120 under 250 µM O~2~.
 Growth rate patterns under red light were similar, although somewhat faster.
@@
 Under red light and 25 µM O~2~ light SS120 grew across most conditions of peak PAR and photoperiod, achieving fastest growth under long photoperiods and peak PAR below 50 \~100 µmol photons
-m^-2^ s^-1^.  Thus, the designation of SS120 as a LL strain is dependent upon the [O~2]. SS120 did not, however,  grow under tested conditions at 2.5 µM O~2~.
+m^-2^ s^-1^.  Thus, the designation of SS120 as a LL strain is dependent upon the [O~2]. SS120 did not, however, grow reliably under tested conditions at 2.5 µM O~2~.
+
+The LLIII clade, *P. marinus* SS120, grew under photoperiods longer than
+4 h and showed increasing growth rate with increasing photoperiods.
+Therefore, SS120 can potentially exploit the longer summer photoperiods
+in temperate zones but again cannot sustain growth in winter through its
+requirement for more than 4 h of light per day, even if water temperature warms into the Clade LLIII tolerance range.
+
+SS120, grew under a PAR of 30 µmol photons m^-2^ s^-1^, and under some conditions at PAR of 90 µmol photons m^-2^ s^-1^, but growth was generally inhibited under PAR of 180 µmol photons
+m^-2^ s^-1^. These findings align with the results reported by
+@mooreComparativePhysiologySynechococcus1995 and are expected for a low
+light clade. Given that SS120 can tolerate longer photoperiods and low
+PAR levels, the deep ocean temperate zones are a viable habitat but not
+during temperate winter due to shorter photoperiods.
+
+SS120 exhibited different growth responses to spectral wavebands
+under varying O~2~ conditions, as such, this section will address the
+growth response under 250 µM O~2~ experiments, while the interactions of
+spectral wavebands under all O~2~ treatments will be discussed in the
+next section. SS120, grew under all spectral wavebands at a PAR of 30
+µmol photons m^-2^ s^-1^. Growth was completely inhibited under blue
+light at PAR levels of 90 and 180 µmol photons m^-2^ s^-1^, but growth
+occurred at PAR of 90 µmol photons m^-2^ s^-1^ under all other spectral
+wavebands. Generally, growth was strongly inhibited under PAR of 180
+µmol photons m^-2^ s^-1^ for all spectral wavebands.
+The ability of SS120 to grow under low blue light and longer photoperiods, makes the deep ocean waters of the temperate zone a viable potential habitat.
+Under 250 µM O~2~ SS120 is constrained to deeper ocean waters through its intolerance of higher blue PAR levels.
 
@@
 Under intermediate 90 µmol photons m^-2^ s^-1^ peak PAR growth rates decreased with increasing blue light photoperiod.
-Blue light did not induce growth at 180 µmol photons m^-2^ s^-1^ peak PAR, while cells shows only marginal growth under white LED and red light under the 8 h photoperiod .
-The µ~max~
-was
-`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
-d^-1^ achieved under 30 µmol photons
-m^-2^ s^-1^ blue light and 16 h photoperiod.
+Blue light did not induce growth at 180 µmol photons m^-2^ s^-1^ peak PAR, while MIT9313 showed only marginal growth under white LED and red light under the 8 h photoperiod .
+The µ~max~ was `r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 30 µmol photons m^-2^ s^-1^ blue light and 16 h photoperiod.
 
@@
 For MIT9313 maintained at 25 µM O~2~ growth rate increased with increasing photoperiods for all spectral wavebands tested (Figure \@ref(fig:MIT9313PAR)).
-Under peak PAR of 90 µmol photons m^-2^ s^-1^ growth rate increased with
-longer photoperiods, with the fastest overall growth rate for MIT9313 
-`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "25", Photoperiod == 16, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 16 h blue light
-photoperiod. In contrast to the 250 µM O~2~ growth experiments,
-MIT9313 grew when exposed to peak PAR of 180 µmol photons m^-2^
-s^-1^ and blue light under all photoperiods except 16 h; additionally,
-white LED and red light treatments induced growth across all tested
-photoperiods under 25 µM O~2~. The 25 µM O~2~, 4 h photoperiod experiments under white LED light and were not performed due to time constraints.
+Under peak PAR of 90 µmol photons m^-2^ s^-1^ growth rate increased with longer photoperiods, with the fastest overall growth rate for MIT9313
+`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "25", Photoperiod == 16, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 16 h blue light photoperiod.
+In contrast to the 250 µM O~2~ growth experiments, MIT9313 grew when exposed to peak PAR of 180 µmol photons m^-2^ s^-1^ and blue light under all photoperiods except 16 h; additionally,
+white LED and red light treatments induced growth across all tested photoperiods under 25 µM O~2~.
+The 25 µM O~2~, 4 h photoperiod experiments under white LED light and were not performed due to time constraints.
 
@@
 
-Under 2.5 µM O~2~  MIT9313 showed growth, particularly under blue LED light, albeit
-generally slower than under the parallel 25 µM O~2~ experiments (Figure
+MIT9313 grew under 2.5 µM O~2~  particularly under blue LED light, albeit
+generally slower than under the parallel experiments at 25 µM O~2~  (Figure
 \@ref(fig:MIT9313PAR)).
-Growth estimates did, however, show scatter among replicates, suggesting the 2.5 µM O~2~  was near the tolerance limit for growth of  MIT9313.
+Growth estimates did show scatter among replicates, suggesting  2.5 µM O~2~  is near the tolerance limit for growth of MIT9313.
 Growth rates increased with longer photoperiods under blue
-light treatments under peak PAR of 90 µmol photons m^-2^ s^-1^ . Growth 
-for MIT9313 under PAR of 180 µmol photons m^-2^ s^-1^ and blue light
-treatment decreased with increasing photoperiods with full growth inhibition
-under a 16 h photoperiod. The red light peak PAR of 180 µmol
-photons m^-2^ s^-1^ showed similar growth rates for 8 and 12 h
-photoperiods. The µ~max~ was
-`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "2.5", Photoperiod == 4, Par_ue == 180) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 4 h blue light
-photoperiod and PAR of 180 µmol photons m^-2^ s^-1^.  XXXXTHIS DOES NOT LOOK correct; 12 h, 90 uE photons blue light looks higher.
-
-The 2.5 µM O~2~ white LED treatments under 4, 8 and 16 h photoperiods
-and red light under 4 and 16 h photoperiods were not performed due to
-time constraints.
+light treatments under peak PAR of 90 µmol photons m^-2^ s^-1^ .
+Growth  for MIT9313 under PAR of 180 µmol photons m^-2^ s^-1^ and blue light treatment decreased with increasing photoperiods with full growth inhibition under a 16 h photoperiod.
+The red light peak PAR of 180 µmol photons m^-2^ s^-1^ showed similar growth rates for 8 and 12 h photoperiods.
+The µ~max~ was `r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "2.5", Photoperiod == 4, Par_ue == 180) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 4 h blue light photoperiod and PAR of 180 µmol photons m^-2^ s^-1^.
+XXXXTHIS DOES NOT LOOK correct; 12 h, 90 uE photons blue light looks higher.
+The 2.5 µM O~2~ white LED treatments under 4, 8 and 16 h photoperiods and red light under 4 and 16 h photoperiods were not performed due to time constraints.
 
@@
 with longer photoperiods, as long as the blue peak PAR levels remain below 50 µmol
-photons m^-2^ s^-1^.
-In contrast, under red light and 250 µM O~2~ MIT9313 grows faster while exploiting higher peak PAR and longer photoperiods.
-Thus the designation of MIT9313 as a LL clade is dependent upon [O2].
-(Figure \@ref(fig:MIT9313GAM)B).  Figure \@ref(fig:MIT9313GAM)C
-shows that MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 4 and 8 h and peak blue PAR between 50 to 10 µmol photons
-m^-2^ s^-1^ PAR (Figure \@ref(fig:MIT9313GAM)C).
+photons m^-2^ s^-1^.  In contrast, under red light and 250 µM O~2~ MIT9313 grows faster while exploiting higher peak PAR and longer photoperiods.  Figure \@ref(fig:MIT9313GAM)C
+shows that MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 4 and 8 h and peak blue PAR between 50 to 10 µmol photons m^-2^ s^-1^ PAR (Figure \@ref(fig:MIT9313GAM)C).
+Thus the designation of MIT9313 as a LL clade is dependent upon [O2] and light spectra.
+(Figure \@ref(fig:MIT9313GAM)B).
+
+The LLIV clade, *P. marinus* MIT9313, exploited all tested photoperiods,
+and showed increasing growth rate with increasing photoperiods. Hence,
+MIT9313 can potentially inhabit temperate zones with shorter winter and
+longer summer photoperiods, and exploit habitats at depth subject to
+photoperiod attenuation.
+
+MIT9313, sometimes grew under all PAR levels but generally exhibited slower growth rate under PAR of 180 µmol photons m^-2^ s^-1^ and then only under some conditions.
+MIT9313 is well suited to inhabit the deep ocean in temperate zones with wide tolerance for photoperiod yet can also tolerate depths closer to the surface through its partial tolerance of higher PAR levels.
+
+MIT9313, under 250 µM O~2~ grew under all spectral wavebands when exposed to PAR of 30 µmol photons m^-2^ s^-1^ and 90 µmol photons m^-2^ s^-1^ and was even able to grow under PAR of 180 µmol photons
+m^-2^ s^-1^ for all spectral wavebands except blue light. MIT9313 can
+thus exploit blue light in deeper waters of temperate zones and can even
+tolerate moderate depths to exploit higher blue light levels, as long as
+the photoperiod is shorter than 12 h.
 
@@
 
-Cumulative diel absorbed PUR can potentially collapse photoperiod, PAR and spectral wavebands to a common metric of absorbed light.
-We plot observed growth rate vs.
-cumulative diel absorbed PUR to determine whether growth is a simple response to absorbed light per day across imposed photoperiods and spectral wavebands, or whether photoperiod or spectral wavebands have specific or interactive influences on growth of each ecotype.
+Cumulative diel absorbed PUR can potentially collapse photoperiod, PAR and spectral wavebands to a common metric of photosynthetically active light absorbed per day.
 Cumulative daily absorbed PUR dose (µmol photons m^-2^ d^-1^) was calculated from the imposed absorbed PUR (µmol photons m^-2^ s^-1^) and photoperiod (h).
-
-Due to the highly effective absorption of pigments in the blue spectral waveband range for all ecotypes, the maximum imposed cumulative diel absorbed PUR under blue light treatment is almost 3 times that of white LED light and about 6 times the red light treatment, despite being derived from the same imposed photoperiods and PUR regimes.
-As such, only growths rates under blue light extend beyond absorbed PUR of ~ 2 x 10^6^ µmol photons m^-2^ d^-1^.
+We plotted growth rates vs.
+cumulative diel absorbed PUR to determine whether growth is a simple response to diel PUR, across imposed photoperiods and spectral wavebands, or whether photoperiod or spectral wavebands have specific or interactive influences on growth.
+
+Due to the absorption of *P.
+marinus* pigments in the blue spectral waveband range, the maximum imposed cumulative diel absorbed PUR under blue light is almost 3 times that of white LED light, and about 6 times the red light treatment, despite being derived from the same imposed photoperiods and peak PAR regimes.
+As such, only blue light experiments extend beyond cumulative diel PUR of ~ 2 x 10^6^ µmol photons m^-2^ d^-1^.
 
@@
 
-The representative of HLI clade, *P. marinus* MED4, showed no growth under any 4 h photoperiod treatments, even when a 4 h photoperiod delivered cumulative diel PUR
-equivalent to other photoperiod treatments. In parallel MED4 showed no growth under 2.5 µM O~2~, no matter the level of diel cumulative absorbed PUR. 
-In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth was well described by a simple saturating response of growth to increasing cumulative diel absorbed PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:AllStrainPurFitsPlots)A).
+The representative of HLI clade, *P.
+marinus* MED4, showed no growth under any 4 h photoperiod treatments, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments.
+In parallel MED4 showed no growth under 2.5 µM O~2~, no matter the level of diel cumulative PUR.
+In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth was well described by a saturating response (REFERENCE for EQUATION) of growth to increasing cumulative diel PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:AllStrainPurFitsPlots)A), and no evidence of inhibition of growth at any achieved cumulative diel PUR.
 XXXXDISTINCT PHOTOPERIOD FITSXXXXX
@@
 marinus* SS120 showed almost no growth under 2.5 µM O~2~ experiments.
-A majority of the 4 h photoperiod treatments did not grow under 250 µM O~2~ experiments even when a 4 h photoperiod delivered the cumulative diel PUR equivalent to other as other photoperiod treatments.
+A majority of the 4 h photoperiod treatments did not grow under 250 µM O~2~ experiments, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments.
 SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ experiments(Figure \@ref(fig:AllStrainPurFitsPlots)B).
@@
 Under both 25 or 250 µM O~2~ experiments, SS120 growth plateaued by about 5.0 x 10^5^ µmol photons m^-2^ d^-1^ diel PUR, with some scatter among photoperiod and spectral waveband regimes.
-The onset of growth inhibition extended to higher cumulative diel absorbed PUR for cultures growing under 25 µM O~2~.
+The onset of growth inhibition extended to higher cumulative diel PUR for cultures under 25 µM O~2~, showing that SS120 is partially protected from photoinhibition of growth by 25 µM O~2~.
 XXXXDISTINCT PHOTOPERIOD FITSXXXXX
@@
 
-The LLIV clade, *P.
+The LLIV clade representative, *P.
 marinus* MIT9313, showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR, with higher growth rates over a narrower plateau under 25 and 250 µM O~2~, compared to a wider, flatter response to cumulative diel PUR under 2.5 µM O~2~.
@@
 
-## Photosystem II maintenance as a limitation on *Prochlorococcus* growth {.unnumbered}
+## Photosystem II maintenance, oxygen metabolism, and DNA repair as limitations on *Prochlorococcus* growth {.unnumbered}
 
@@
 
-Under full atmospheric [O~2~], LL clades of *Prochlorococcus* are restricted to growth under low light, in part because they suffer photoinhibition of Photosystem II (PSII) through several paths, including direct absorbance of UV or blue light, in parallel with generation of Reactive Oxygen Species (ROS) if the electron flow is slowed, [@aroPhotoinhibitionPhotosystemII1993], producing  damaging singlet oxygen (^1^O~2~) [@aroPhotoinhibitionPhotosystemII1993; @soitamoPhotoinhibitionMarinePicocyanobacteria2017; @murphyPhotoinactivationPhotosystemII2017; @hakalaEvidenceRoleOxygenevolving2005].
+Under full atmospheric [O~2~] and bluelight, LL clades of *Prochlorococcus* are restricted to growth under low light, in part because they suffer photoinhibition of Photosystem II (PSII) through several paths, including direct absorbance of UV or blue light, in parallel with generation of Reactive Oxygen Species (ROS) if the electron flow is slowed, [@aroPhotoinhibitionPhotosystemII1993], producing  damaging singlet oxygen (^1^O~2~) [@aroPhotoinhibitionPhotosystemII1993; @soitamoPhotoinhibitionMarinePicocyanobacteria2017; @murphyPhotoinactivationPhotosystemII2017; @hakalaEvidenceRoleOxygenevolving2005].
 Repair of inhibited PSII process relies on the removal of damaged PsbA (Mann et al., 2000; Adam et al., 2005), followed by reassembly with newly synthesized PsbA [@nixonRecentAdvancesUnderstanding2010].
-Thus, degradation of PsbA is a rate-limiting step in recovery from photoinhibition (Kanervo et al., 1993), mediated largely by a heterohexamer of (FtsH12)3, a membrane-bound (Sacharz et al., 2015)(Zak et al., 2001) metalloprotease  (Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
+Degradation of PsbA is a rate-limiting step in recovery from photoinhibition (Kanervo et al., 1993), mediated largely by a heterohexamer of (FtsH12)3, a membrane-bound (Sacharz et al., 2015)(Zak et al., 2001) metalloprotease  (Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
 (Adam et al., 2005; Boehm et al., 2012) (Nixon et al.
@@
 
-*Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4, homologous to the characterized FtsH isoforms of the model cyanobacterium *Synechocystis* FtsH, with presumably parallel functions (table \@ref(tab:FtsHTable)).
+*Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4, homologs to the characterized FtsH isoforms of the model cyanobacterium *Synechocystis* FtsH, and with presumably parallel functions (table \@ref(tab:FtsHTable)).
 Upon a shift to higher light HLIII MED4 upregulated expression of FtsH1 and FtsH2 [@bonisteelStrainSpecificDifferences2018], homologs to the *Synechocystis* slr0228 and slr1604, implicated in PSII repair.
@@
 
+Ocean detections of proteins mediating protein metabolism support this interpretation of distinct FtsH function across clades of *P.
+marinus*.
+Ribosome proteins from Clade HLI MED4, Clade LLIII SS120 and Clade LLIV MIT9313 show generally similar patterns vs.
+[O~2~] and depth, a proxy for peak PAR.
+FtsH3, inferred to mediate PSI assembly, likewise shows a similar pattern between MED4 and MIT9313.
+But only MED4 shows detected presence of the FtsH1 & FtsH2 isoforms inferred to mediate PSII repair, and then only in near-surface samples subject to higher light.
+Furthermore, even though MIT9313 grows \@ref(fig:MIT9313GAM), and is detected in the ocean at low [O~2~] \ref@(fig:ProchloroPhotosynthDepthO2), no  FtsH from MIT9313 is detected at low [O~2~], showing limited requirement for protein turnover under low [O~2~].
+
 ```{r ProchloroProteinMetabDepthO2, fig.cap = ProchloroProteinMetabDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
@@
                        "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome).",
-                       "Culture growth experimental conditions indicated by horizontal grey lines for depths approximating Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) and vertical grey lines for O~2~ (µM).",
+                       "Culture growth experimental conditions indicated by horizontal grey lines for depths approximating Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) and vertical grey lines for [O~2~] (µM).",
                        "Point colours identify *Prochlorococcus* clade assignments",
@@
 NAAMAN FIGURE
-Zotero BERG citation
+Add Clade Code
+Make visual grammar consistent.
+Drop 'title'
+X axis scale annotated in mMol O2, lines in uM, make consistent.
+
+Figure \@ref(fig:ProchlorococcusEnzymeKms) shows genes encoding enzymes for  *P.
+marinus* strains from Clades HLI, LLII, LLIII and LLII [@omarAnnotationGenesEncoding2023], compared to the measured or inferred K~M~ for [O~2~] for each enzyme CITATIONS.
+[@bergResponsesPsbAHli2011] previously found that MED4 increases expression of alternative oxidase ('ubiquinol oxidase (non electrogenic)')  to cope with changes in light by dissipating electrons from the inter-system transport chain, while the genome scan shows SS120 and MIT9313 lack this gene, and therefore, lack an oxygen-dependent path to cope with changing excitation.
+The approximate K~M~ for [O~2~] of ~ 25 µM for ubiquinol oxidase (non electrogenic) is comparable to the lower limit for growth of MED4 in our experiments.
+We suggest that dependence upon this enzyme excludes MED4 from low oxygen zones.
+Conversely, a gene encoding (S)-2-hydroxy-acid oxidase is encoded in the MIT9313 genome.
+(S)-2-hydroxy-acid oxidase catalyzes the reaction of 2-hydroxy acid with O~2~ to produce toxic H~2~O~2~ [@InformationEC15].
+(S)-2-hydroxy-acid oxidase has an approximate K~M~ for [O~2~] of ~ 250 µM, and produces H~2~O~2~, so growth at lower [O~2~] may protect MIT9313 from auto-intoxication from production of H~2~O~2~.
+We hypothesize that under our 250 µM O~2~ and higher blue light, *P.
+marinus* MIT9313 exhibited photoinhibition, resulting from the inactivation of PSII caused by the production of the reactive oxygen species, hydrogen peroxide.
+This photoinhibition is further compounded by the limited inducible repair mechanism for PSII, due to the absence of FtsH 2 and 3  expression in *P.
+marinus* MIT9313 [@bonisteelStrainSpecificDifferences2018].
+We hypothesize that under the conditions of our high light and 2.5 µM and 25 µM O~2~ experiments, the activity of the 2-hydroxy-acid oxidase enzyme is suppressed.
+As a result, the catalyzed production of hydrogen peroxide is inhibited, leading to minimal PSII damage, allowing MIT9313 to avoid photoinhibition and circumvent limitations on PSII repair.
+Figure \@ref(fig:ProchlorococcusEnzymeKms) also shows that *P.
+marinus* SS120 is the only tested ecotype to lack the pyridoxal 5'-phosphate synthase enzyme.
+The pyridoxal 5'-phosphate synthase enzyme is an important cofactor in the biosynthesis of vitamin B~6~ [@sangIdentificationPyridoxinePyridoxamine2007].
+Vitamin B~6~ is a potential antioxidant and can effectively quench singlet oxygen [@bilskiVitaminB6Pyridoxine2000].
+The absence of the pyridoxal 5'-phosphate synthase enzyme may explain why *P.
+marinus* SS120 does not grow as well as *P.
+marinus* MIT9313 when exposed to high light stress under 25 µM O~2~ and not at all under 2.5 µM O~2~.
 
@@
 
-Figure \@ref(fig:DNARepairFig) displays the genes encoding DNA repair for the three *P.
-marinus* strains examined in this study.
+Figure \@ref(fig:DNARepairFig) shows genes encoding DNA repair for *P.
+marinus* strains.
 As expected,  *P.
@@
 marinus* SS120 demonstrates the smallest genomic capacity for DNA repair.
-*Prochlorococcus marinus* MED4 was the only strain out of the three strains in this study to possess the gene encoding deoxyribodipyrimidine photolyase, which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003].
+*Prochlorococcus marinus* MED4 was the only strain to possess the gene encoding deoxyribodipyrimidine photolyase, which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003].
 *Prochlorococcus marinus* MED4 was also the only strain to possesses the gene encoding DNA ligase, which uses ATP as a cofactor for DNA repair.
@@
 marinus* MIT9313 and *P.
-marinus* SS120 explains why these two strains cannot tolerate the high light levels found at the ocean surface where  *P.
-marinus* MED4 inhabits.
+marinus* SS120 helps explain why these two strains cannot tolerate growth under full [O~2~] and high light found at the ocean surface where.
+Furthermore, the protective effect of lower [O~2~], allowing these strains to grow at higher light, may relate in part to suppression of DNA damage when generation of Reactive Oxygen Species is suppressed at lower [O~2~].
 
@@
 \newpage
-\newpage
-
-# Discussion {.unnumbered}
-
-### Growth Responses to Photoperiod {.unnumbered}
-
-The representative of HLI clade, *P. marinus* MED4, was completely
-excluded from growth under the 4 h photoperiod, and showed
-increasing growth rates with increasing photoperiod. Thus, MED4 can
-potentially exploit longer summer photoperiods in temperate zones, but
-will likely remain excluded from growth in winter through its requirement for
-more than 4 h of light per day, even if water temperature warms into the Clade HLI tolerance range.
-
-The LLIII clade, *P. marinus* SS120, grew under photoperiods longer than
-4 h and showed increasing growth rate with increasing photoperiods.
-Therefore, SS120 can potentially exploit the longer summer photoperiods
-in temperate zones but again cannot sustain growth in winter through its
-requirement for more than 4 h of light per day, even if water temperature warms into the Clade LLIII tolerance range.
-
-The LLIV clade, *P. marinus* MIT9313, exploited all tested photoperiods,
-and showed increasing growth rate with increasing photoperiods. Hence,
-MIT9313 can potentially inhabit temperate zones with shorter winter and
-longer summer photoperiods, and exploit habitats at depth subject to
-photoperiod attenuation.
-
-### Growth Responses to Peak PAR Responses {.unnumbered}
-
-The representative of HLI clade, *P. marinus* MED4, was able to grow
-under all PAR levels, so long as the photoperiod was longer than 4 h,
-although growth rates were slow under the lowest PAR level of 30 µmol
-photons m^-2^ s^-1^. Considering the range of PAR levels that MED4 can
-utilize, it is reasonable to suggest that MED4 can inhabit not just
-shallow depths, where light levels are high, but also deeper regions
-characterized by lower light levels, subject to the limitation of a
-photoperiod of at least 4 h even after depth attenuation of light. The photo
-regimes of winter temperate zones, due to shorter photoperiods, exclude
-MED4 from growth at all depths, however temperate photoperiods and light
-levels for the remainder of the year are adequate to support growth.
-
-The LLIII clade, *P. marinus* SS120, grew under a PAR of 30 µmol photons
-m^-2^ s^-1^, and under some conditions at PAR of 90 µmol photons m^-2^
-s^-1^, but growth was generally inhibited under PAR of 180 µmol photons
-m^-2^ s^-1^. These findings align with the results reported by
-@mooreComparativePhysiologySynechococcus1995 and are expected for a low
-light clade. Given that SS120 can tolerate longer photoperiods and low
-PAR levels, the deep ocean temperate zones are a viable habitat but not
-during temperate winter due to shorter photoperiods.
-
-The LLIV clade, *P. marinus* MIT9313, sometimes grew under all PAR
-levels but generally exhibited slower growth rate under PAR of 180 µmol
-photons m^-2^ s^-1^ and then only under some conditions. MIT9313 is well
-suited to inhabit the deep ocean in temperate zones with wide tolerance
-for photoperiod yet can also tolerate depths closer to the surface
-through its partial tolerance of higher PAR levels.
-
-### Spectral Waveband {.unnumbered}
-
-The representative of HLI clade, *P. marinus* MED4, grew under all
-tested spectral wavebands. Growth rates were
-generally comparable under blue, white LED and red lights when exposed
-to PAR levels greater than 30 µmol photons m^-2^ s^-1^ for each
-photoperiod. At the lower PAR of 30 µmol photons m^-2^ s^-1^, MED4 grew
-better under blue light. All growth rates for each spectral waveband
-increased with increasing photoperiod. The ability to utilize all
-spectral wavebands at high PAR levels and longer photoperiods make the
-near surface temperate zones available niches for MED4. MED4 ability to
-exploit blue light under low PAR levels and variable photoperiods
-greater than 4 h allow MED4 to exploit deeper regions in these temperate
-zones, where blue light prevails.
-
-The LLIII clade, *P. marinus* SS120 and the LLIV clade, *P. marinus*
-MIT9313, exhibited different growth responses to spectral wavebands
-under varying O~2~ conditions, as such, this section will address the
-growth response under 250 µM O~2~ experiments, while the interactions of
-spectral wavebands under all O~2~ treatments will be discussed in the
-next section. SS120, grew under all spectral wavebands at a PAR of 30
-µmol photons m^-2^ s^-1^. Growth was completely inhibited under blue
-light at PAR levels of 90 and 180 µmol photons m^-2^ s^-1^, but growth
-occurred at PAR of 90 µmol photons m^-2^ s^-1^ under all other spectral
-wavebands. Generally, growth was strongly inhibited under PAR of 180
-µmol photons m^-2^ s^-1^ for all spectral wavebands.
-The ability of SS120 to grow under low blue light and longer photoperiods, makes the deep ocean waters of the temperate zone a viable potential habitat.
-Under 250 µM O~2~ SS120 is constrained to deeper ocean waters through its intolerance of higher blue PAR levels.
-
-The LLIV clade, *P. marinus* MIT9313, grew under all spectral wavebands
-when exposed to PAR of 30 µmol photons m^-2^ s^-1^ and 90 µmol photons
-m^-2^ s^-1^ and was even able to grow under PAR of 180 µmol photons
-m^-2^ s^-1^ for all spectral wavebands except blue light. MIT9313 can
-thus exploit blue light in deeper waters of temperate zones and can even
-tolerate moderate depths to exploit higher blue light levels, as long as
-the photoperiod is shorter than 12 h.
-
-### Oxygen {.unnumbered}
 
@@
 
-Furthermore, our data might support suggestive patterns of enhanced growth under conditions of low cumulative diel absorbed PUR and 660 nm (red) spectral bandwidth, as supported by [@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue wavebands.
-
-### Discussion from Mireille' Thesis General Discussion section {.unnumbered}
-
-@flombaumPresentFutureGlobal2013 modeled a 29% increase of net cell abundance of *Prochlorococcus* by the end of this century and predicts that there will be poleward latitudinal shifts of at least 10° in marine phytoplankton habitats.
-Consequently, *P.
-marinus* will encounter new combinations of photoperiod, seasonal patterns, and altered spectral regimes as they move towards the poles, where solar incidence angles are lower and photoperiod seasonality is more pronounced [@bartonAnthropogenicClimateChange2016].
-The predicted poleward shifts of  *P.
-marinus* niches and the estimated increase in their cell abundances was modeled using climate model projections of sea surface temperatures and greenhouse gases equivalent to 650 ppm CO~2~ for the end of this century [@flombaumPresentFutureGlobal2013].
-While these models suggest that *P.
-marinus* could hypothetically expand into poleward regions by the end of this century, it remains uncertain whether *P.
-marinus* can actually tolerate the longer, and shorter, day lengths of temperate region seasons.
-To our knowledge, no other study has as yet addressed *P.
-marinus* growth responses in relation to a wide range of photoperiods.
+Furthermore, our data support enhanced growth under conditions of low cumulative diel absorbed PUR and 660 nm (red) spectral bandwidth, as supported by [@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue wavebands.
 
@@
 
-To gain insights into the variations we observed in growth responses across strains, particularly the responses to different oxygen levels [O~2~], we used a subset of the dataset of annotated phytoplankton genomes from @omarAnnotationGenesEncoding2023.
-This subset contains annotated phytoplankton gene sequences, with a focus on genes encoding enzymes involved in oxygen metabolism (Figure \@ref(fig:ProchlorococcusEnzymeKms)) or DNA repair (Figure \@ref(fig:DNARepairFig)).
-According to figure \@ref(fig:ProchlorococcusEnzymeKms), we see that *P.
-marinus* MED4 has the gene encoding ubiquinol oxidase (non electrogenic) enzyme, whereas SS120 and MIT9313 do not.
-The ubiquinol oxidase (non electrogenic) enzyme is involved in dissipating excess electrons [@InformationEC10] generated under high light exposure, thereby reducing stress on the electron transport system.
-The O~2~ substrate K~m~ value of approximately 25 µM  for ubiquinol oxidase  may explain why *P.
-marinus* MED4 can grow under 25 µM of O~2~ but not under 2.5 µM of O~2~, since growth under 2.5 µM of O~2~ would suppress use of ubiquinol oxidase to balance electron transport.
-The demonstrated ability of *P.
-marinus* MIT9313 to grow when exposed to high blue light under 2.5 µM and 25 µM O~2~ treatments may be explained by the presence of the gene encoding enzyme 2-hydroxy-acid oxidase (Figure \@ref(fig:ProchlorococcusEnzymeKms)).
-The enzyme 2-hydroxy-acid oxidase, with an O~2~ substrate K~m~ value of approximately 250 µM (Figure \@ref(fig:ProchlorococcusEnzymeKms)), catalyzes the reaction of 2-hydroxy acid with O~2~ to produce toxic hydrogen peroxide [@InformationEC15].
-We hypothesize that under our 250 µM O~2~ and high blue light experiments, *P.
-marinus* MIT9313 exhibited photoinhibition, resulting from the inactivation of PSII caused by the production of the reactive oxygen species, hydrogen peroxide.
-This inhibition was further compounded by the limited induced repair mechanism for PSII, due to the absence of FtsH 2 and 3  proteins in *P.
-marinus* MIT9313 [@bonisteelStrainSpecificDifferences2018].
-We hypothesize that under the conditions of our high light and 2.5 µM and 25 µM O~2~ experiments, the activity of the 2-hydroxy-acid oxidase enzyme is suppressed.
-As a result, the catalyzed production of hydrogen peroxide is inhibited, leading to minimal PSII damage, allowing MIT9313 to avoid photoinhibition and circumvent limitations on PSII repair.
-Figure \@ref(fig:ProchlorococcusEnzymeKms) also shows that *P.
-marinus* SS120 is the only tested ecotype to lack the pyridoxal 5'-phosphate synthase enzyme.
-The pyridoxal 5'-phosphate synthase enzyme is an important cofactor in the biosynthesis of vitamin B~6~ [@sangIdentificationPyridoxinePyridoxamine2007].
-Vitamin B~6~ is a potential antioxidant and can effectively quench singlet oxygen [@bilskiVitaminB6Pyridoxine2000].
-The absence of the pyridoxal 5'-phosphate synthase enzyme may explain why *P.
-marinus* SS120 does not grow as well as *P.
-marinus* MIT9313 when exposed to high light stress under 25 µM O~2~ and not at all under 2.5 µM O~2~.
-
-\newpage
-
-XXX ProchlorococcusEnzymeKms figure goes here XXX
-
-\newpage
-
-Figure \@ref(fig:DNARepairFig) displays the genes encoding DNA repair for the three *P.
-marinus* strains examined in this study.
-As expected,  *P.
-marinus* MED4 possesses the largest and most complete suite of genes encoding DNA repair enzymes, followed by *P.
-marinus* MIT9313.
-Conversely, *P.
-marinus* SS120 demonstrates the smallest genomic capacity for DNA repair.
-*Prochlorococcus marinus* MED4 was the only strain out of the three strains in this study to possess the gene encoding deoxyribodipyrimidine photolyase, which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003].
-*Prochlorococcus marinus* MED4 was also the only strain to possesses the gene encoding DNA ligase, which uses ATP as a cofactor for DNA repair.
-The absence of the genes encoding deoxyribodipyrimidine photolyase and DNA ligase (ATP) in *P.
-marinus* MIT9313 and *P.
-marinus* SS120 explains why these two strains cannot tolerate the high light levels found at the ocean surface where  *P.
-marinus* MED4 inhabits.
-
-\newpage
-
-XXX DNARepairFig goes here XXX
-
-\newpage
-
-@westNichePartitioningProchlorococcusPopulationsStratified1999 and
-@malmstromTemporalDynamicsProchlorococcus2010 found that decreased
-abundances of the LL ecotypes corresponded to increased depth of the
-surface mixed layer, which thus influences the vertical distribution of
-HL and LL ecotypes. @malmstromTemporalDynamicsProchlorococcus2010
-attributes the transport of LL ecotypes to the surface and exposure to
-photoinhibitory high light levels as the reason for low cell abundances.
-@westNichePartitioningProchlorococcusPopulationsStratified1999 found
-the depth of the mixed layer strongly influenced the depth transition
-from HL to LL ecotypes and that additional factors other than light
-levels may influence the variations in the upper and lower depth limits
-of these ecotypes. Based on our findings, we hypothesize that low cell abundances of LL ecotypes in the mixed layer is likely due to increased [O~2~] at
-those depths and it is [O~2~] that determines the prevalence of the LL
-ecotypes to certain depths, not necessarily the light level.
-
-We have demonstrated that *P.
-marinus*  can exploit the photoregimes of the temperate zone, both at the surface and deep in the water column.
-Additionally, we  confirmed that the *P.
-marinus* strains we tested can survive in significantly lower oxygen environments as is represented in the OMZ and that the LL ecotypes we tested can be labeled as HL strains in oxygen environments of 25 µM and as low as 2.5 µM in the case of MIT9313.
-@billerProchlorococcusStructureFunction2015 has described *Prochlorococcus* as a 'federation' of diverse cells through their extensive genomic and phenotypic diversity.
-They underscore the importance of its diverse members and how this diversity contributes to their wide distribution, stability, and abundance in oceans.
-I like to envision a ‘federation’ of  *Prochlorococcus* cells in perfect floating order, like an army of soldiers  diligently engaging in their expertise: photosynthesis.
+@westNichePartitioningProchlorococcusPopulationsStratified1999 and @malmstromTemporalDynamicsProchlorococcus2010 found that decreased abundances of the LL clades corresponded to increased depth of the surface mixed layer.
+@malmstromTemporalDynamicsProchlorococcus2010
+attributes the transport of LL ecotypes to the surface and consequent exposure to photoinhibitory high light levels as the reason for low cell abundances with increased mixed layer depth.
+@westNichePartitioningProchlorococcusPopulationsStratified1999 found the depth of the mixed layer strongly influenced the depth transition from HL to LL clades, but that factors other than light levels may influence the variations in the upper and lower depth limits of these ecotypes.
+We hypothesize that low cell abundances of LL ecotypes in the mixed layer is likely driven in part by increased [O~2~],  and it is [O~2~] that constrains LL clades to deeper waters, not necessarily the light level.
+
+*P.
+marinus* strains differentially exploit potential photoregimes of the temperate zone, both at the surface and deep in the water column.
+Some *P.
+marinus* strains grow under  low oxygen environments, similar to OMZ and that the LL clades we tested can be labeled as 'HL'  in oxygen environments of 25 µM and as low as 2.5 µM in the case of MIT9313.
+@billerProchlorococcusStructureFunction2015 has described *Prochlorococcus* as a 'federation' of diverse cells whose extensive genomic and phenotypic diversity contributes to their wide distribution, stability, and abundance in oceans.
 

### 2024-02-22 Code/Manuscript_O2.Rmd
results and discussion edits

@@
 
+XXXXXCHECK WHEN MIREILLE ADDS Colour specific fitsXXX This inhibition initially suggested that blue wavebands triggered photoinhibition at significantly lower levels of Photosynthetically Active Radiation (PAR) compared to other spectral wavebands.
+However, considering the equivalent cumulative diel absorbed PUR of the blue waveband, all treatments including blue, white LED, red and green waveband exhibited approximately the same growth saturation.
+XXXX
+
+Our data support enhanced growth under conditions of low cumulative diel  PUR and 660 nm (red) spectral bandwidth, as supported by [@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue wavebands.
+
 \newpage
@@
 Furthermore, the protective effect of lower [O~2~], allowing these strains to grow at higher light, may relate in part to suppression of DNA damage when generation of Reactive Oxygen Species is suppressed at lower [O~2~].
+*Prochlorococcus* are highly susceptible to hydrogen peroxide (H~2~O~2~) toxicity as they lack genes which scavenge H~2~O~2~ molecules [@morrisFacilitationRobustGrowth2008].
+The small cell size of *Prochlorococcus* allow the reactive oxygen species (ROS), H~2~O~2~, to cross the cell membrane; however, the accumulation of extracellular H~2~O~2~ can also be toxic to *Prochlorococcus* [@morrisFacilitationRobustGrowth2008,  @morrisDependenceCyanobacteriumProchlorococcus2011].
 
@@
 
-### Discussion PUR and growth trends {.unnumbered}
-
-The absorption maxima of Chl a~2~ and Chl b~2~ are 442 nm and 478 nm, respectively [@goerickePigmentsProchlorococcusMarinus1992].
-At these spectral wavelengths, *P.
-marinus* efficiently harvests the light energy present in the blue and green waveband range, 400 nm to 525 nm [@morelAvailableUsableStored1978] that penetrates the deep ocean waters.
-The high Chl a~2~/Chl b~2~ ratio we observed for MED4 is characteristic of the HL clades and the lower Chl a~2~/Chl b~2~ ratios we observed for SS120 and MIT9313 are typical of the LL clades [@moorePhotophysiologyMarineCyanobacterium1999].
-The lower PUR for the white LED waveband for MED4, in comparison to SS120 and MIT9313, are the result of higher Chl a~2~/Chl b~2~ content.
-Subsequently, estimating  PUR allows direct comparison of the energy absorbed by cells on a per photon basis across different wavebands.
-
-Under 250 µM O~2~ treatments and all PAR of 90 and 180 µmol photons m^-2^ s^-1^ blue light treatments, *P.
-marinus* SS120, exhibited growth inhibition but was able to exploit all other spectral wavebands under some photoperiods at these PAR levels.
-Similarly, *P.
-marinus* MIT9313, showed complete growth inhibition under all PAR 180 µmol photons m^-2^ s^-1^ blue light treatments and only grew under a 90 µmol photons m^-2^ s^-1^, 4 and 8 h blue light photoperiods, yet was able to grow under all other spectral wavebands to varying degrees at these PAR levels.
-This inhibition initially suggested that blue wavebands triggered photoinhibition at significantly lower levels of Photosynthetically Active Radiation (PAR) compared to other spectral wavebands.
-However, considering the equivalent cumulative diel absorbed PUR of the blue waveband, all treatments including blue, white LED, red and green waveband exhibited approximately the same growth saturation.
-
-*Prochlorococcus marinus* MED4 has a physiological requirement for more than 4 h of light per day, and thus this strain will not exploit habitats with short photoperiods.
-MED4 is also excluded from the lowest oxygen habitats, equivalent to our 2.5 µM O~2~ experimental conditions; however, MED4 can inhabit regions with slightly higher O~2~, as was demonstrated by the growth responses observed under our 25 µM O~2~ experiments.
-
-*Prochlorococcus marinus* SS120, categorized as a LLIII clade representative, showed an interactive growth inhibition between oxygen and cumulative diel absorbed PUR, with a higher tolerance for higher cumulative diel absorbed PUR under 25 µM O~2~, compared to 250 µM O~2~.
-Thus, SS120 can exploit habitats with O~2~ levels spanning 25 µM O~2~ to 250 µM O~2~.
-
-*Prochlorococcus marinus* MIT9313 is categorized as a LLIV clade representative, but under 25 or 2.5 µM O~2~, MIT9313 can actually exploit cumulative diel absorbed PUR comparably to *P.
-marinus* HLI clade MED4.
-Therefore, lower oxygen habitats extending to near the surface could potentially be exploited by MIT9313.
-
-*Prochlorococcus* are highly susceptible to hydrogen peroxide (H~2~O~2~) toxicity as they lack genes which scavenge H~2~O~2~ molecules [@morrisFacilitationRobustGrowth2008].
-The small cell size of *Prochlorococcus* allow the reactive oxygen species (ROS), H~2~O~2~, to cross the cell membrane; however, the accumulation of extracellular H~2~O~2~ can also be toxic to *Prochlorococcus* [@morrisFacilitationRobustGrowth2008].
-In the marine environment and in isolated cultures, @morrisDependenceCyanobacteriumProchlorococcus2011 showed that *Prochlorococcus* rely on catalase-positive heterotrophs to scavenge H~2~O~2~.
-Beyond the scope of our study, the three *Prochlorococcus* strains we examined were likely accompanied by different communities of co-occurring heterotrophs which could confer differential protection against reactive oxygen species [@zinserCrossprotectionHydrogenPeroxide2018a; @zinserMicrobialContributionReactive2018].
-
-Furthermore, our data support enhanced growth under conditions of low cumulative diel absorbed PUR and 660 nm (red) spectral bandwidth, as supported by [@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue wavebands.
-
-The lack of photoperiod growth studies is not surprising, given that higher cell abundances of *P.
+The lack of photoperiod growth studies for *P.
+marinus* is not surprising, given that higher cell abundances of *P.
 marinus* are currently  concentrated between 30°N and 30°S.
@@
 @billerProchlorococcusStructureFunction2015 has described *Prochlorococcus* as a 'federation' of diverse cells whose extensive genomic and phenotypic diversity contributes to their wide distribution, stability, and abundance in oceans.
+
+*Prochlorococcus marinus* MED4 has a physiological requirement for more than 4 h of light per day, and thus this strain will not exploit habitats with short photoperiods.
+MED4 is also excluded from the lowest oxygen habitats, equivalent to our 2.5 µM O~2~ experimental conditions; however, MED4 can inhabit regions with slightly higher O~2~, as was demonstrated by the growth responses observed under our 25 µM O~2~ experiments.
+
+*Prochlorococcus marinus* SS120, categorized as a LLIII clade representative, showed an interactive growth inhibition between oxygen and cumulative diel absorbed PUR, with a higher tolerance for higher cumulative diel absorbed PUR under 25 µM O~2~, compared to 250 µM O~2~.
+Thus, SS120 can exploit habitats with O~2~ levels spanning 25 µM O~2~ to 250 µM O~2~.
+
+*Prochlorococcus marinus* MIT9313 is categorized as a LLIV clade representative, but under 25 or 2.5 µM O~2~, MIT9313 can actually exploit cumulative diel absorbed PUR comparably to *P.
+marinus* HLI clade MED4.
+Therefore, lower oxygen habitats extending to near the surface could potentially be exploited by MIT9313.
 

### 2024-02-22 Code/ManuscriptPURFits.Rmd
Generated WL ANOVA figure

@@
 
-# # model with dummy dark, 0 PAR,  growth rates 
-# PURPARStrainO2WLNestModels <- PURPARFits_dummy |>
-#   nest(data = -c("Strain","O2_uM", "WL")) |>
-#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
-#                               data = .x,
-#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1),
-#                               lower = c(0, 0, 0),
-#                               upper = c(1,1,100),
-#                               control = list(maxiter = 500)
-#                          ), NULL)
-#                          )
-#          ) |>
-#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
-#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
-#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
-#          )|>
-#   mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
-#                               data = .x,
-#                               start = LinEqnStart
-#                          ), NULL)
-#                          )
-#          ) |>
-#   mutate(GRClm_Param = map(GRClm_Model, tidy),
-#          GRClm_Predict = map(GRClm_Model, possibly(augment)),
-#          GRClm_Glance = map(GRClm_Model, possibly(glance))
-#          )
-# 
+# model with dummy dark, 0 PAR,  growth rates
+PURPARStrainO2WLNestModels <- PURPARFits_dummy |>
+  nest(data = -c("Strain","O2_uM", "WL")) |>
+  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
+                              data = .x,
+                              start = list(a = 1e-7, b = 1e-8, Pmax = 1),
+                              lower = c(0, 0, 0),
+                              upper = c(1,1,100),
+                              control = list(maxiter = 500)
+                         ), NULL)
+                         )
+         ) |>
+  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
+         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
+         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
+         )|>
+  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
+                              data = .x,
+                              start = LinEqnStart
+                         ), NULL)
+                         )
+         ) |>
+  mutate(GRClm_Param = map(GRClm_Model, tidy),
+         GRClm_Predict = map(GRClm_Model, possibly(augment)),
+         GRClm_Glance = map(GRClm_Model, possibly(glance))
+         )
+
 # 
@@
 
+PURPARStrainO2WLNestModels|>
+  filter(!map_lgl(GRCplatt_Model, is.null)) |>
+  unnest(GRCplatt_Predict, data) |>
+   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
+         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
+  ggplot() +
+  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
+  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
+   scale_colour_manual(values = MCMIXColours) +
+  facet_grid(rows = vars(O2_uM, WL), cols = vars(Strain)) +
+    labs(title = "PURPARStrainO2WLNestModels Linear Model") +
+  theme_bw()
+
+PURPARStrainO2WLNestModels|>
+  filter(!map_lgl(GRClm_Model, is.null)) |>
+  unnest(GRClm_Predict, data) |>
+   mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
+         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
+  ggplot() +
+  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
+  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
+   scale_colour_manual(values = MCMIXColours) +
+  facet_grid(rows = vars(O2_uM, WL), cols = vars(Strain)) +
+    labs(title = "PURPARStrainO2WLNestModels Linear Model") +
+  theme_bw()
+
 ```
@@
   mutate(fourvsAll = map(map2(four, All, possibly(anova, otherwise = NULL)), tidy),
-         eightvsAll = map(map2(eight, All, possibly(anova, otherwise = NULL)), tidy),
+         eightvsAll = map(map2(eight, All, possibly(anova, otherwise = NA)), tidy),
          twelvevsAll = map(map2(twelve, All, possibly(anova, otherwise = NULL)), tidy),
@@
   filter(is.na(term) & is.na(p.value) |
-           !is.na(term) & !is.na(p.value)) %>%
+           !is.na(term) & !is.na(p.value) | is.nan(p.value)) %>%
   select(Strain, O2_uM, name, p.value) %>% 
@@
 
+```{r PhotoperiodAnovaTable, include = FALSE}
+
+PhotoperiodAnovaTable <- ANOVA_AllPhotoperiods %>% 
+  mutate(Photoperiod = as.numeric(case_when(Photoperiod1 == 'four' ~ 4,
+                                  Photoperiod1 == 'eight' ~ 8,
+                                  Photoperiod1 == 'twelve' ~ 12,
+                                  Photoperiod1 == 'sixteen' ~ 16)),
+         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
+         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) %>% 
+  select(-c(Photoperiod1, p.value, AllPhotoperiod))  %>%
+  relocate(Photoperiod, .after = O2_uM) %>%
+  arrange(Strain, O2_uM,Photoperiod)
+
+```
+
+```{r PhotoperiodAnovaTable, fig.height = 6, fig.width = 8, echo = FALSE }
+
+knitr::kable(PhotoperiodAnovaTable,
+             caption = "pvalues for each photoperiod from ANOVA comparison with a fit of pooled photoperiods in each O~2~ experiment for each strain.",
+            col.names =  c("Strain",
+                           "[O~2~] (µM)",
+                          "Photoperiod (h)",
+                          "pvalue"),
+              align = "lccc"
+             )
+```
+
+# This figure is a 3 panel figure faceted by strain in columns and O2 in rows. Too stretched.
 # Fits are added that are not sig different individually,  next add fits that were sig different dynamically
@@
 
-```{r Pur plot strain facetted in columns}
+```{r Pur plot strain faceted in columns}
 scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
@@
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.75, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) + 
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotdash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "SS120")) +
    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
@@
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotdash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM == 25, Strain == "MIT9313")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 25, Strain == "MIT9313")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +
@@
 ```
+
+# WL models for each strain for each O2 experiment
+```{r Generate platt and lm for WL}
+
+# model with dummy dark, 0 PAR,  growth rates.
+Also removed data if no growth occurred for an O2 and photoperiod combination so that the model including all photoperiods would not be skewed towards zero.
+StrainO2NestModels <- PURPARFits_dummy |>
+  nest(data = -c("Strain","O2_uM")) |>
+  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
+                              data = .x,
+                              start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
+                              lower = c(0, 0, 0),
+                              upper = c(1,1,100),
+                              control = list(maxiter = 500)
+                         ), NULL)
+                         )
+         ) |>
+  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
+         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
+         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
+         ) |>
+  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
+                              data = .x,
+                              start = LinEqnStart
+                         ), NULL)
+                         )
+         ) |>
+  mutate(GRClm_Param = map(GRClm_Model, tidy),
+         GRClm_Predict = map(GRClm_Model, possibly(augment)),
+         GRClm_Glance = map(GRClm_Model, possibly(glance))
+         )
+
+# nest unfiltered data and join with filtered data to have all data to plot later 
+AllData <- PURPARFits_dummy |>
+    nest(Data_all = -c("Strain","O2_uM"))
+
+StrainO2NestModels <- full_join(StrainO2NestModels, AllData)
+
+# model with dummy dark, 0 PAR,  growth rates
+PURPARStrainO2WLNestModels <- PURPARFits_dummy |>
+  nest(data = -c("Strain","O2_uM", "WL")) |>
+  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
+                              data = .x,
+                              start = list(a = 1e-7, b = 1e-8, Pmax = 1),
+                              lower = c(0, 0, 0),
+                              upper = c(1,1,100),
+                              control = list(maxiter = 500)
+                         ), NULL)
+                         )
+         ) |>
+  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
+         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
+         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
+         )|>
+  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
+                              data = .x,
+                              start = LinEqnStart
+                         ), NULL)
+                         )
+         ) |>
+  mutate(GRClm_Param = map(GRClm_Model, tidy),
+         GRClm_Predict = map(GRClm_Model, possibly(augment)),
+         GRClm_Glance = map(GRClm_Model, possibly(glance))
+         )
+
+remove(AllData)
+
+```
+
+# Want platt model for all fits that did not fail and lm for platt models that returned a NULL
+```{r models for WL}
+# O2 and WL nested data frame containing the fits for each WL for each strain
+#filter to keep platt models
+KeepPlattModel <- PURPARStrainO2WLNestModels|>
+  select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
+   filter(!map_lgl(GRCplatt_Model, is.null))
+
+#filter to keep only the models that failed to fit a platt model, fits by lm remains. 
+KeepLmModel <- PURPARStrainO2WLNestModels|>
+  filter(map_lgl(GRCplatt_Model, is.null)) |>
+ select(-c(GRCplatt_Glance, GRCplatt_Model, GRCplatt_Param, GRCplatt_Predict))
+
+# Join  
+StrainO2WL_AllModels <- bind_rows(KeepPlattModel, KeepLmModel)
+
+ remove(KeepPlattModel)
+ remove(KeepLmModel)
+
+# O2 and WL nested data frame containing the fits for each WL for each strain
+ StrainO2WL_PlattLmModel <- StrainO2WL_AllModels |>
+   pivot_longer(cols = -c(Strain, O2_uM, WL, data)) |>
+  drop_na(value) |>
+  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param") | str_detect(name, pattern = "Predict")) |>
+  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
+  pivot_wider(names_from = Output, values_from = value) |>
+filter(!map_lgl(Model, is.null)) |>
+  filter(!map_lgl(Glance, is.null)) |>
+  mutate(AIC = map_dbl(Glance, ~ as.numeric(pluck(.x, "AIC")))) |>
+  group_by(Strain, O2_uM, WL) |>
+  filter(AIC == min(AIC)) |>
+  ungroup() |>
+  select(-c(Glance)) |>
+  unnest(Param) |>
+  select(-c(statistic)) |>
+  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
+
+# O2 nested data frame containing the single fit of pooled WL
+ #filter to keep platt models
+KeepPlattModel <- StrainO2NestModels|>
+  select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
+   filter(!map_lgl(GRCplatt_Model, is.null))
+
+#filter to keep only the models that failed to fit a platt model, fits by lm remains. 
+KeepLmModel <- StrainO2NestModels|>
+  filter(map_lgl(GRCplatt_Model, is.null)) |>
+ select(-c(GRCplatt_Glance, GRCplatt_Model, GRCplatt_Param, GRCplatt_Predict))
+
+# Join  
+StrainO2_AllModels <- full_join(KeepPlattModel, KeepLmModel)
+
+# O2 nested data frame containing the single fit of pooled WLs 
+ StrainO2_PlattLmModel <- StrainO2_AllModels|>
+  # select(-c(data)) |>
+  pivot_longer(cols = -c(Strain, O2_uM, data, Data_all)) |>
+  drop_na(value) |>
+  filter(str_detect(name, pattern = "Model") | str_detect(name, pattern = "Glance") | str_detect(name, pattern = "Param") | str_detect(name, pattern = "Predict")) |>
+  separate(col = name , into = c("ModelType", "Output"), sep = "_") |>
+  pivot_wider(names_from = Output, values_from = value) |>
+  filter(!map_lgl(Model, is.null)) |>
+  filter(!map_lgl(Glance, is.null)) |>
+  mutate(AIC = map_dbl(Glance, possibly(~ as.numeric(pluck(.x, "AIC"))))) |>
+  group_by(Strain, O2_uM) |>
+  filter(AIC == min(AIC)) |>
+  ungroup() |>
+  select(-c(Glance))|>
+  unnest(Param) |>
+  select(-c(statistic)) |>
+  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
+
+ remove(KeepPlattModel)
+ remove(KeepLmModel)
+ # remove(StrainO2WL_AllModels)
+ # remove(StrainO2_AllModels)
+
+```
+
+Linear models do not have alpha, beta and pmax so inf and NA are generated. Change them to 0.
+```{r lm platt parameters set to zero}
+
+# O2 nested data frame containing the single fit of pooled photoperiods for each strain 
+StrainO2_PlattLmModel <- StrainO2_PlattLmModel|>
+  mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
+         estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
+         estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
+         AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC))
+
+StrainO2_PlattLmModel
+
+# O2 and Photoperiod nested data frame containing the fits for each photoperiod for each strain
+StrainO2WL_PlattLmModel <- StrainO2WL_PlattLmModel|>
+  mutate(estimate_a = if_else(ModelType == "GRClm", 0, estimate_a),
+         estimate_b = if_else(ModelType == "GRClm", 0, estimate_b),
+         estimate_Pmax = if_else(ModelType == "GRClm", 0, estimate_Pmax),
+         AIC = if_else(ModelType == "GRClm" & is.infinite(AIC), 0, AIC))
+
+StrainO2WL_PlattLmModel
+
+```
+
+```{r plot WL models}
+
+# O2 nested data frame containing the single fit of pooled photoperiods for each strain
+StrainO2_PlattLmModel |>
+  unnest(Predict, data) |>
+  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         WL= factor(WL, levels = c("WW", 660, 450)),
+         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
+         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4"))) |>
+  ggplot() +
+  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL))) +
+  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
+   geom_text(aes(x = 500000, y = 0.75, label = paste(ModelType), show.legend = FALSE)
+  ) +
+     scale_colour_manual(values = MCMIXColours) +
+   scale_shape_manual(values = PhotoperiodShapes)  +
+  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
+    labs(title = "Single fit for each strain in each [O2]- all WL ") +
+  theme_bw()
+
+# O2 and Photoperiod nested data frame containing the fits for each photoperiod for each strain
+StrainO2WL_PlattLmModel |>
+  unnest(Predict, data) |>
+  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
+         Photoperiod = factor(Photoperiod, levels = c(16, 12, 8, 4))) |>
+  ggplot() +
+  geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
+  geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) + 
+   geom_text(aes(x = 500000, y = 0.75, label = paste(ModelType), show.legend = FALSE)
+  ) +
+     scale_colour_manual(values = MCMIXColours) +
+  facet_grid(rows = vars(O2_uM, WL), cols = vars(Strain)) +
+    labs(title = "Fits to be used for ANOVA comparison to single fit across each strain and [O2]") +
+  theme_bw()
+
+```
+
+# ANOVA comparison of red light to blue light for each strain and [O2]. 
+```{r compare 1 red and blue light fits}
+
+# make wider to join with DF that contains the 1 fit through all photoperiods
+Wider_WL <- StrainO2WL_PlattLmModel %>% 
+  select(Strain, WL, O2_uM, Model, Predict) %>% 
+  pivot_wider(names_from = WL, values_from = c(Model, Predict))
+
+# this contains 1 fit through all WL.
+AllWL <- StrainO2_PlattLmModel %>% 
+  select(Strain, O2_uM, Model, Predict, Data_all) %>% 
+ rename(All = 'Model',
+        Predict_pooled = 'Predict')
+
+AllFitsCombinedWL <- left_join(Wider_WL, AllWL)
+
+ANOVA_AllWL <- AllFitsCombinedWL %>% 
+  mutate(Blue = `Model_450`,
+         Red = `Model_660`,
+         White = `Model_WW`,
+         Pooled = `All`) %>%
+  mutate(BluevsPooled = map(map2(Blue, Pooled, possibly(anova, otherwise = NULL)), tidy),
+         RedvsPooled = map(map2(Red, Pooled, possibly(anova, otherwise = NA)), tidy),
+         WhitevsPooled = map(map2(White, Pooled, possibly(anova, otherwise = NULL)), tidy),
+         BluevsRed = map(map2(Blue, Red, possibly(anova, otherwise = NULL)), tidy)) %>% 
+  select(Strain, O2_uM, BluevsPooled, RedvsPooled, WhitevsPooled, BluevsRed) %>% 
+  pivot_longer(cols = c(BluevsPooled, RedvsPooled, WhitevsPooled, BluevsRed)) %>% 
+  unnest(value, keep_empty = TRUE) %>% 
+  filter(is.na(term) & is.na(p.value) |
+           !is.na(term) & !is.na(p.value) | is.nan(p.value)) %>%
+  select(Strain, O2_uM, name, p.value) %>% 
+  separate(name, into = c("WL1", "WL2"), sep = "vs") %>% 
+  mutate(pvalue = signif(`p.value`, digits = 2))
+
+# %>% 
+#   mutate(p.value = case_when(is.na(p.value) ~ 0,
+#                              TRUE ~ p.value)) # Changed all failed fits to p.value = 0
+  # mutate(pval = pluck(value, "p.value", 2))
+
+ANOVA_AllWL %>% 
+  mutate(O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
+    # mutate(Photoperiod1 = factor(Photoperiod1, levels = c('four','eight', 'twelve', 'sixteen'))) %>% 
+  ggplot() +
+  geom_text(aes(x = WL1, y = WL2, label = pvalue), data = . %>% filter(pvalue < 0.05), size = 2.5) +
+  geom_text(aes(x = WL1, y = WL2), data = . %>% filter(pvalue > 0.05), label = "ns") +
+  geom_text(aes(x = WL1, y = WL2), data = . %>% filter(is.na(pvalue)), label = "NA") +
+  facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
+  labs(title = "ANOVA compare all models",
+       caption = "NA = atleast one model did not fit due to lack of data points; 
+       ns = not significantly different from WL model (p value > 0.05); 
+       numbers = significantly different pvalues from all WL model (p value < 0.05)")
+
+remove(Wider_WL)
+remove(AllWL)
+
+```
+
+```{r Pur plot strain faceted in columns}
+scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
+
+WLvsPooledPurFitsPlots <- AllFitsCombinedWL |>
+  unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
+  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
+         OxygenLabel = "Oxygen Concentration (µM)",
+         Photoperiod = factor(Data_all_Photoperiod, levels = c(16, 12, 8, 4)),
+         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         WL = factor(Data_all_WL, levels = c("WW", 660, 450)),
+         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
+  ggplot() +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.7) +
+    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.0, alpha = 0.5) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_450) %>%  filter(O2_uM == 2.5, Strain == "MED4",  WL == 450)) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MED4", WL == 660))+
+    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MED4", WL == "WW")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 450)) +
+ geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "SS120", O2_uM != 250, WL == "WW")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 660))+
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MIT9313", O2_uM == 2.5, WL == "WW")) +
+ labs(title = "Anova fit comparisons of WL to pooled", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
+  scale_x_continuous(label=scientific_10) +
+  scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
+  scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
+  # scale_linetype_manual(values = MyLineTypes, labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
+  scale_shape_manual(values = PhotoperiodShapes)  +
+  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), cols = vars(Strain), 
+                    labeller = labeller(Strain = label_value, O2_uM = label_value, OxygenLabel = label_value)) +
+ guides(linetype = guide_legend(nrow = 1),
+        fill = "none",
+        color = guide_legend(nrow = 1)) +
+ guides(shape = guide_legend(nrow = 1)) +
+  theme_bw() +
+   theme( strip.text = element_text(size = 25),
+        axis.title.y = element_text(color = "black", size = 30,  hjust = 0.40),
+        axis.title.x = element_text(color = "black", size = 30),
+        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
+        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
+        # strip.background=element_rect(color="grey87", fill = "grey82"),
+        # strip.background=element_rect(fill = "white"), 
+        legend.key.size = unit(0.1, 'cm'), #change legend key size
+        legend.key.height = unit(0.1, 'cm'), #change legend key height
+        legend.key.width = unit(0.1, 'cm'), #change legend key width
+        legend.title =  element_text(size = 25),  #change legend title font size
+        legend.text = element_text(size = 25),   #change legend text font size
+        legend.position = "top") +
+  labs( shape = "Photoperiod (h)",
+        color = "Growth Waveband (nm)",
+       linetype = "Photoperiod lines"
+      )
+
+WLvsPooledPurFitsPlots
+
+# This labels each pane with a letter but turns of the facet labels
+# AllStrainPurFitsPlots <- tag_facet(AllStrainPurFitsPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
+
+BluevsRedPurFitsPlots <- AllFitsCombinedWL |>
+  unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
+  filter(Data_all_WL %in% c(450,660)) %>% 
+  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
+         OxygenLabel = "Oxygen Concentration (µM)",
+         Photoperiod = factor(Data_all_Photoperiod, levels = c(16, 12, 8, 4)),
+         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         WL = factor(Data_all_WL, levels = c(660, 450)),
+         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
+  ggplot() +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.7) +
+    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.0, alpha = 0.5) +
+ #  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_450) %>%  filter(Strain == "MED4",  WL == 450)) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MED4", WL == 660)) +
+ #    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MED4", WL == "WW")) +
+ #   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM == 25, WL == 450)) +
+ geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_660) %>%  filter(Strain == "SS120", O2_uM == 25, WL == 660)) +
+   # geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 660))+
+    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_450) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 450))+
+ #  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MIT9313", O2_uM == 2.5, WL == "WW")) +
+ labs(title = "Sig diff fits are indicated by the fit drawn. No lines, no diff bt 660 & 450", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
+  scale_x_continuous(label=scientific_10) +
+  scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
+  scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
+  # scale_linetype_manual(values = MyLineTypes, labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
+  scale_shape_manual(values = PhotoperiodShapes)  +
+  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), cols = vars(Strain), 
+                    labeller = labeller(Strain = label_value, O2_uM = label_value, OxygenLabel = label_value)) +
+ guides(linetype = guide_legend(nrow = 1),
+        fill = "none",
+        color = guide_legend(nrow = 1)) +
+ guides(shape = guide_legend(nrow = 1)) +
+  theme_bw() +
+   theme( strip.text = element_text(size = 25),
+        axis.title.y = element_text(color = "black", size = 30,  hjust = 0.40),
+        axis.title.x = element_text(color = "black", size = 30),
+        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
+        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
+        # strip.background=element_rect(color="grey87", fill = "grey82"),
+        # strip.background=element_rect(fill = "white"), 
+        legend.key.size = unit(0.1, 'cm'), #change legend key size
+        legend.key.height = unit(0.1, 'cm'), #change legend key height
+        legend.key.width = unit(0.1, 'cm'), #change legend key width
+        legend.title =  element_text(size = 25),  #change legend title font size
+        legend.text = element_text(size = 25),   #change legend text font size
+        legend.position = "top") +
+  labs( shape = "Photoperiod (h)",
+        color = "Growth Waveband (nm)",
+       linetype = "Photoperiod lines"
+      )
+
+BluevsRedPurFitsPlots
+
+```

### 2024-02-23 Code/ManuscriptPURFits.Rmd
regenerated PURFit for Photoperiod figure

@@
 
-# ggsave(file = file.path(PlotsOut, paste("MED4PURFITPlot",".png",sep = "")), plot = MED4PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-# 
-# ggsave(file = file.path(PlotsOut, paste("SS120PURFITPlot",".png",sep = "")), plot = SS120PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-# 
-# ggsave(file = file.path(PlotsOut, paste("MIT9313PURFITPlot",".png",sep = "")), plot = MIT9313PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-# 
-# ggsave(file = file.path(PlotsOut, paste("MED4PURFITPlot",".tiff",sep = "")), plot = MED4PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-# 
-# ggsave(file = file.path(PlotsOut, paste("SS120PURFITPlot",".tiff",sep = "")), plot = SS120PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-# 
-# ggsave(file = file.path(PlotsOut, paste("MIT9313PURFITPlot",".tiff",sep = "")), plot = MIT9313PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-
 ```
@@
 ```
+
+```{r, save PURWLFitPlots}
+
+ggsave(file = file.path(PlotsOut, paste("BluevsRedPurFitsPlots",".png",sep = "")), plot = BluevsRedPurFitsPlots, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+# ggsave(file = file.path(PlotsOut, paste("BluevsRedPurFitsPlots",".tiff",sep = "")), plot = BluevsRedPurFitsPlots, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+```

### 2024-02-23 Code/Manuscript_O2.Rmd
Fixed citations

@@
 Some as yet uncultured *P.
-marinus* strains in clades LLV and LLVI also thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021; @lavinNovelLineagesProchlorococcus2010; @goerickeNovelNicheProchlorococcus2000; @robledoCrypticOxygenCycling2017] (Johnson et al., 1999).
+marinus* strains in clades LLV and LLVI also thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021; @lavinNovelLineagesProchlorococcus2010; @goerickeNovelNicheProchlorococcus2000; @garcia-robledoCrypticOxygenCycling2017] (Johnson et al., 1999).
 *P.
@@
 [@chisholmNovelFreelivingProchlorophyte1988; @veldhuisVerticalDistributionPigment1990; @partenskyProchlorococcusMarinePhotosynthetic1999] and extend into regions with varying dissolved oxygen concentrations
-[@partenskyProchlorococcusAdvantagesLimits2010; @goerickeNovelNicheProchlorococcus2000] and even into anoxic oceans [@lavinNovelLineagesProchlorococcus2010], [@ulloaCyanobacteriumProchlorococcusHas2021; @garcia-robledoCrypticOxygenCycling2017a].
+[@partenskyProchlorococcusAdvantagesLimits2010; @goerickeNovelNicheProchlorococcus2000] and even into anoxic oceans [@lavinNovelLineagesProchlorococcus2010], [@ulloaCyanobacteriumProchlorococcusHas2021; @garcia-robledoCrypticOxygenCycling2017].
 Climate change is drastically altering the dissolved oxygen concentrations ([O~2~]) of our ocean waters.

### 2024-02-23 Code/Manuscript_O2.Rmd
removed green data from 1 line in results section. knit to .docx

@@
 XXXXXCHECK WHEN MIREILLE ADDS Colour specific fitsXXX This inhibition initially suggested that blue wavebands triggered photoinhibition at significantly lower levels of Photosynthetically Active Radiation (PAR) compared to other spectral wavebands.
-However, considering the equivalent cumulative diel absorbed PUR of the blue waveband, all treatments including blue, white LED, red and green waveband exhibited approximately the same growth saturation.
+However, considering the equivalent cumulative diel absorbed PUR of the blue waveband, all treatments including white LED, red, and blue waveband exhibited approximately the same growth saturation.
 XXXX

### 2024-02-23 Code/ManuscriptPURFits.Rmd
ADDED DASHED LINES TO FITS OF NO SIGNIF DIFF

@@
     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.0, alpha = 0.5) +
- #  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_450) %>%  filter(Strain == "MED4",  WL == 450)) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MED4", WL == 660)) +
- #    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MED4", WL == "WW")) +
- #   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) +
    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM == 25, WL == 450)) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_660) %>%  filter(Strain == "SS120", O2_uM == 25, WL == 660)) +
-   # geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 450)) +
+ geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, linetype = "dashed",  data = . %>% unnest(Predict_660) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 660)) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 660))+
     geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_450) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 450))+
- #  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MIT9313", O2_uM == 2.5, WL == "WW")) +
- labs(title = "Sig diff fits are indicated by the fit drawn. No lines, no diff bt 660 & 450", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, linetype = "dashed", data = .
+%>% unnest(Predict_450) %>%  filter(Strain == "MIT9313", O2_uM == 250, WL == 450)) +
+ geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, linetype = "dashed",  data = .
+%>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM == 250, WL == 660)) +
+ labs(y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
   scale_x_continuous(label=scientific_10) +

### 2024-02-23 Code/Manuscript_O2.Rmd
ordered figures
Added WL PUR fits figure and caption

--- 2024-02-23 Code/Manuscript_O2.Rmd
@@
 
-```{r AllStrainPurFitsPlots,  fig.cap = AllStrainPurFitsPlots_cap, fig.height = 10, fig.width = 10, echo = FALSE}
-
-AllStrainPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
+```{r BluevsRedPurFitsPlots, fig.cap = BluevsRedPurFitsPlots_cap , fig.height = 10, fig.width = 10, echo = FALSE}
+
+ BluevsRedPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
                     "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
@@
                     "Shapes show the imposed photoperiod (h); 4 h (hollow inverted triangle),  8 h (solid diamond), 12 h (solid circle), 16 h (solid upright triangle).",
-                      "Symbol colours show the spectral waveband for growth; white LED (black symbols), 660 nm (red symbols), and 450 nm (blue symbols).",
+                      "Symbol colours show the spectral waveband for growth; 660 nm (red symbols), and 450 nm (blue symbols).",
                       "Large symbols show mean of growth rate from logistic curve fits; small symbols show values for replicate determinations, if any.",
-                    "Platt (add Platt citation here) 4 parameter model fit to data pooled for each combination of strain and dissolved oxygen shown with solid lines.
-Separate models fit to photoperiod data and shown if significantly different from the pooled model; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).",
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "AllStrainPurFitsPlots.png"))
+                    "Platt (add Platt citation here) 4 parameter model fit to 660 nm (red lines) and 450 nm (blue lines) growth data for each combination of strain and dissolved oxygen shown with solid lines (significantly different fits, pvalue < 0.05) or dashed lines (not significantly different fits, pvalue > 0.05).",
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "BluevsRedPurFitsPlots.png"))
 
@@
 
+```{r LabeledMC, fig.cap = LabeledMC_cap , fig.height = 8, fig.width = 6, echo = FALSE}
+
+LabeledMC_cap <- glue("**PSI MCMIX-OD Multicultivator.**",
+                      "Spectral wavebands and light levels are individually controlled for each culture tube.",
+                      "Real time Optical Density (OD) measurements eliminate intrusive subsampling of sterile cultures.",
+                      "The temperature of culture tubes are collectively controlled via heating or cooling of the aquarium water.",
+                      "Gas with specific oxygen concentrations is bubbled through a humidifier and passed through a 0.2 um filter.",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "LabeledMC.png"))
+```
+
+\newpage
+
 ```{r deltaODLogGrowthPlot, fig.cap = deltaODLogGrowthPlot_cap , fig.height = 8, fig.width = 6, echo = FALSE}
@@
 
-```{r LabeledMC, fig.cap = LabeledMC_cap , fig.height = 8, fig.width = 6, echo = FALSE}
-
-LabeledMC_cap <- glue("**PSI MCMIX-OD Multicultivator.**",
-                      "Spectral wavebands and light levels are individually controlled for each culture tube.",
-                      "Real time Optical Density (OD) measurements eliminate intrusive subsampling of sterile cultures.",
-                      "The temperature of culture tubes are collectively controlled via heating or cooling of the aquarium water.",
-                      "Gas with specific oxygen concentrations is bubbled through a humidifier and passed through a 0.2 um filter.",
-
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "LabeledMC.png"))
+```{r AllStrainPurFitsPlots,  fig.cap = AllStrainPurFitsPlots_cap, fig.height = 10, fig.width = 10, echo = FALSE}
+
+AllStrainPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
+                    "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
+                    "Columns are strains; MED4, SS120 and MIT9313.",
+                    "Shapes show the imposed photoperiod (h); 4 h (hollow inverted triangle),  8 h (solid diamond), 12 h (solid circle), 16 h (solid upright triangle).",
+                      "Symbol colours show the spectral waveband for growth; white LED (black symbols), 660 nm (red symbols), and 450 nm (blue symbols).",
+                      "Large symbols show mean of growth rate from logistic curve fits; small symbols show values for replicate determinations, if any.",
+                    "Platt (add Platt citation here) 4 parameter model fit to data pooled for each combination of strain and dissolved oxygen shown with solid lines.
+Separate models fit to photoperiod data and shown if significantly different from the pooled model; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).",
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "AllStrainPurFitsPlots.png"))
+
 ```

### 2024-02-23 Code/ManuscriptPURFits.Rmd
Added table of pvalues Ask how to import to manuscript

@@
 ```
+
+```{r WLAnovaTable, include = FALSE}
+
+WLAnovaTable <- ANOVA_AllWL %>% 
+  filter(WL2 == "Red") %>% 
+  mutate(Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
+         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) %>% 
+  select(-c(p.value)) %>% 
+  arrange(Strain, O2_uM)
+
+```
+
+```{r WLAnovaTable, fig.height = 6, fig.width = 8, echo = FALSE }
+
+knitr::kable(WLAnovaTable,
+             caption = "pvalues for each ANOVA comparison of fit of red and blue light in each O~2~ experiment for each strain.",
+            col.names =  c("Strain",
+                           "[O~2~] (µM)",
+                          "WL1",
+                          "WL2",
+                          "pvalue"),
+              align = "lcccc"
+             )
+```

### 2024-02-23 Code/ManuscriptFigures.Rmd
Generated PUR estimate figures

@@
 
-# ggsave(file = file.path(PlotsOut, paste("MED4OverlayPlots",".png",sep = "")), plot = MED4OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
-# 
-# ggsave(file = file.path(PlotsOut, paste("MED4WWOverlayPlots",".png",sep = "")), plot = MED4WWOverlayPlots, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("MED4OverlayPlots",".png",sep = "")), plot = MED4OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
 
-# MIT9313OverlayPlots <- PURPARFits %>%
-PURPARFits %>%
+MIT9313OverlayPlots <- PURPARFits %>%
    filter(Strain == "MIT9313",
@@
 
- # MIT9313OverlayPlots <- tag_facet(MIT9313OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
- # 
- # MIT9313OverlayPlots
+ MIT9313OverlayPlots <- tag_facet(MIT9313OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
+
+ MIT9313OverlayPlots
 ```
@@
 
-# ggsave(file = file.path(PlotsOut, paste("MIT9313OverlayPlots",".png",sep = "")), plot = MIT9313OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("MIT9313OverlayPlots",".png",sep = "")), plot = MIT9313OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
 ```{r SS120 PUR overlay with legend,  fig.height = 10, fig.width = 10}
-# SS120OverlayPlots <- PURPARFits %>%
-PURPARFits %>%
+
+ SS120OverlayPlots <- PURPARFits %>%
    filter(Strain == "SS120",
@@
 
- # SS120OverlayPlots <- tag_facet(SS120OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
- # 
- # SS120OverlayPlots
+ SS120OverlayPlots <- tag_facet(SS120OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
+
+ SS120OverlayPlots
 
@@
 
-# ggsave(file = file.path(PlotsOut, paste("SS120OverlayPlots",".png",sep = "")), plot = SS120OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("SS120OverlayPlots",".png",sep = "")), plot = SS120OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 

### 2024-02-23 Code/Manuscript_O2.Rmd
added PUR estimate figures and captions

@@
 
+```{r MED4OverlayPlots, fig.cap = MED4OverlayPlots_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+
+MED4OverlayPlots_cap <- glue("**Normalized absorbance and Photosynthetically Usable Radiation for *Prochlorococcus marinus* MED4 grown under three emission wavebands.**",
+                       "**A.** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated absorbed PUR spectra (solid black line and shaded grey).",
+                       "**B.** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated absorbed PUR spectra (solid black line and shaded red).",
+                       "**C.**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated absorbed PUR spectra (solid black line and shaded blue).",
+
+                       "Actinic PAR (µmol photons m^-2^ s^-1^) and calculated absorbed PUR (µmol photons m^-2^ s^-1^) levels are indicated.",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "MED4OverlayPlots.png"))
+
+```
+
+\newpage
+
+```{r SS120OverlayPlots, fig.cap = SS120OverlayPlots_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+
+SS120OverlayPlots_cap <- glue("**Normalized absorbance and Photosynthetically Usable Radiation for *Prochlorococcus marinus* SS120 grown under three emission wavebands.",
+                       "**A.** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated absorbed PUR spectra (solid black line and shaded grey).",
+                       "**B.** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated absorbed PUR spectra (solid black line and shaded red).",
+                       "**C.**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated absorbed PUR spectra (solid black line and shaded blue).",
+                       "Actinic PAR (µmol photons m^-2^ s^-1^) and calculated absorbed PUR (µmol photons m^-2^ s^-1^) levels are indicated.",
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "SS120OverlayPlots.png"))
+
+```
+
+\newpage
+
+```{r MIT9313OverlayPlots, fig.cap = MIT9313OverlayPlots_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+
+MIT9313OverlayPlots_cap <- glue("**Normalized absorbance and Photosynthetically Usable Radiation for *Prochlorococcus marinus* MIT9313 grown under three emission wavebands.**",
+                                "**A.** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated absorbed PUR spectra (solid black line and shaded grey).",
+                       "**B.** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated absorbed PUR spectra (solid black line and shaded red).",
+                       "**C.**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated absorbed PUR spectra (solid black line and shaded blue).",
+                       "Actinic PAR (µmol photons m^-2^ s^-1^) and calculated absorbed PUR (µmol photons m^-2^ s^-1^) levels are indicated.",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "MIT9313OverlayPlots.png"))
+
+```
+
+\newpage
+
 ```{r AllStrainPurFitsPlots,  fig.cap = AllStrainPurFitsPlots_cap, fig.height = 10, fig.width = 10, echo = FALSE}

### 2024-02-23 Code/Manuscript_O2.Rmd
Added max growth table in each O2 condition for  each strain

@@
 
+```{r Generate GrowthTable, include = FALSE }
+
+MaxGrowthTable <- PURPARFits %>%
+  filter(Par_ue %in% c(30,90,180),
+         Strain %in% c("MED4", "SS120" ,"MIT9313")) %>%
+  select(Strain, O2_uM, ReplicateMean_deltaOD_Lmu_corr_day, Photoperiod, Par_ue, WL ) %>%
+  group_by(Strain, O2_uM) %>%
+  summarize(MaxGrowth = round(max(ReplicateMean_deltaOD_Lmu_corr_day), 2), 
+            Photoperiod = Photoperiod[which.max(ReplicateMean_deltaOD_Lmu_corr_day)], 
+            Par_ue = Par_ue[which.max(ReplicateMean_deltaOD_Lmu_corr_day)], 
+            WL= WL[which.max(ReplicateMean_deltaOD_Lmu_corr_day)]) %>%
+  ungroup %>% 
+ mutate(Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
+         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         WL = case_when(WL %in% c(450, 530, 660) ~ WL,
+                              WL %in% c("WW") ~ paste("White LED", sep = " "))) %>% 
+  mutate(Photoperiod = ifelse(MaxGrowth != 0, Photoperiod,  paste("All tested", sep = " ")),
+         Par_ue = ifelse(MaxGrowth != 0, Par_ue, paste("All tested", sep = " ")),
+          WL = ifelse(MaxGrowth != 0, WL, paste("All tested", sep = " "))) %>% 
+   relocate(WL, .after = Par_ue) %>%
+   relocate(MaxGrowth, .after = WL) %>% 
+   relocate(O2_uM, .after = WL) %>% 
+  arrange(Strain, O2_uM)
+
+```
+
+```{r MaxGrowthTable, fig.height = 6, fig.width = 8, echo = FALSE }
+
+knitr::kable(MaxGrowthTable,
+             caption = "The maximum growth rate, µ~max~ (d^-1^) in each O~2~ experiment for each strain. The corresponding photoperiod, PAR level and spectral waveband are indicated.",
+            col.names =  c("Strain",
+                          "Photoperiod (h)",
+                          "PAR (µmol photons m^-2^ s^-1^)",
+                          "Spectral waveband (nm)",
+                          "[O~2~] (µM)",
+                          "µ~max~ (d^-1^)"),
+              align = "lccccc"
+             )
+```
+
 \newpage

### 2024-02-23 Code/Manuscript_O2.Rmd
moved growth equation to growth section

@@
 [@R-minpack.lm], to fit a logistic
-equation \@ref(eq:GrowthRate) where ΔOD~max~ is maximum ΔOD, ΔOD~min~ is minimum ΔOD, t is time
+equation \@ref(eq:GrowthRate)
+
+```{=tex}
+\begin{equation}
+  µ = \frac{ΔOD_{max} × ΔOD_{min} × exp^{(µ × t)}}{ΔOD_{max} + (ΔOD_{min} × exp^{((µ × t) - 1)})}
+  (\#eq:GrowthRate)
+\end{equation}
+```
+
+where ΔOD~max~ is maximum ΔOD, ΔOD~min~ is minimum ΔOD, t is time
 duration over the growth trajectory.  Annotated code for data import, transformations and analyses is available at XXXXX 
@@
 
-```{=tex}
-\begin{equation}
-  µ = \frac{ΔOD_{max} × ΔOD_{min} × exp^{(µ × t)}}{ΔOD_{max} + (ΔOD_{min} × exp^{((µ × t) - 1)})}
-  (\#eq:GrowthRate)
-\end{equation}
-```
+Figures \@ref(fig:MED4OverlayPlots), \@ref(fig:SS120OverlayPlots) and
+\@ref(fig:MIT9313OverlayPlots) provide visual representations of the Photosynthetic Usable Radiation (PUR), the black solid line and shaded area, in relation to the imposed Photosynthetic Active
+Radiation (PAR), the dotted line, under each imposed spectral wavebands for *P.
+marinus* MED4, SS120 and MIT9313, respectively.
+A complete list of absorbed PUR (µmol photons m^-2^ s^-1^) for all imposed spectral wavebands, PAR and photoperiod regimes, can be found in Table \@ref(tab:PURTable).
 

### 2024-02-23 Code/OceanProteinPlots.Rmd
remove ggplot titles from Ocean Protein plots

@@
   facet_grid(factor(strain, levels = c("MED4", "SS120", "MIT9313")) ~ factor(complex, levels = c("psii", "cytb6f", "psi", "rubisco", "atp"), labels = PhotosynthLabels)) +
-  labs(title = expression('Ocean detection of' ~italic(Prochlorococcus)~ 'photosynthesis complexes'),
-       y = "Depth (m)",
+  labs(y = "Depth (m)",
        x = expression("O"[2] ~ "(µM)")) +
@@
    labs(y = "Depth (m)",
-        x = expression("O"[2] ~ "(µM)"),
-        title = expression('Ocean detection of' ~italic(Prochlorococcus)~ 'protein metabolism complexes')) +
+        x = expression("O"[2] ~ "(µM)")) +
   theme_bw()

### 2024-02-23 Code/Manuscript_O2.Rmd
Added reference link to PURPAR figure
edit text

@@
 Figures \@ref(fig:MED4OverlayPlots), \@ref(fig:SS120OverlayPlots) and
-\@ref(fig:MIT9313OverlayPlots) provide visual representations of the Photosynthetic Usable Radiation (PUR), the black solid line and shaded area, in relation to the imposed Photosynthetic Active
-Radiation (PAR), the dotted line, under each imposed spectral wavebands for *P.
+\@ref(fig:MIT9313OverlayPlots) provide visual representations of PUR, the black solid line and shaded area, in relation to the imposed PAR, the dotted line, under each imposed spectral wavebands for *P.
 marinus* MED4, SS120 and MIT9313, respectively.
-A complete list of absorbed PUR (µmol photons m^-2^ s^-1^) for all imposed spectral wavebands, PAR and photoperiod regimes, can be found in Table \@ref(tab:PURTable).
+Figure (\@ref(fig:PurParPlot)) shows the relationship between calculated absorbed PUR versus imposed PAR for each *P.
+marinus* and each spectral waveband.
 

### 2024-02-23 Code/ManuscriptTargetProtein.Rmd
Cleaned Protein fig

@@
 # library(strucchange)
-
+library(photobiology)
 library(dplyr)
@@
 TargetProtein <- TargetProtein %>%
-  rename(SampleID = "Sample")
+  rename(SampleID = "ï..Sample")
 
@@
 ```{r set colours}
-MyWavelengths = c(405, 450, 475, 530, 615, 660, 730, "WW")
-MCMIXColours = c("violet", "darkblue", "dodgerblue", "darkgreen","orange","red","purple", "black")
+
+# MyWavelengths = c(450, 530, 660, "WW")
+# MCMIXColours = c(w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "black")
+
+MyWavelengths = c("WW", 660, 530, 450)
+MCMIXColours = c("black",  w_length2rgb(660), w_length2rgb(530),  w_length2rgb(450))
 
@@
 MCMIXColours
+
+ColoursStrain = c(MIT9313 = "#E69F00", SS120 = "#F0E442", MED4 = "#CC79A7" )
+
+MyOxygen = c(2.5, 25, 250 )
+# ColourOxygen = c("#99CCFF", "dodgerblue", "blue1")
+ColourOxygen = c("#FFCC00", "#FF9900", "#663300")
+names(ColourOxygen) <- MyOxygen
+ColourOxygen
+
+MyOxygen = c(2.5, 25, 250 )
+LineTypeOxygen = c("dotted", "longdash", "solid")
+names(LineTypeOxygen) <- MyOxygen
+LineTypeOxygen
+
+MyPhotoperiods = as.factor(c(4, 8, 12, 16))
+ColoursPhotoperiod = c("gray88", "lightcyan3", "gray47", "gray8")
+names(ColoursPhotoperiod) <- MyPhotoperiods
+ColoursPhotoperiod
+
 ```
@@
 TargetProtein  <- TargetProtein %>% 
- mutate(Target = factor(Target, levels = c("FtsH", "PsbA", "PetC", "PsaC", "RbcL")))
+ mutate(Target = factor(Target, levels = c("FtsH", "PsbA", "PetC", "PsaC", "RbcL")),
+        O2_uM = case_when(O2 == 0 ~ 2.5,
+                          O2 == 2 ~ 25,
+                          O2 == 21 ~ 250),
+        O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         WL= factor(WL, levels = c("WW", 660, 530, 450)))
 
@@
 
-```{r explore plots}
-TargetProtein %>%
-   filter(Strain == "MIT9313") %>%
-  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
-  geom_col() +
-  # ggplot() +
-  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
-  # scale_fill_viridis_d(fill = "f68060") %>% 
-  # scale_colour_manual(values = MCMIXColours) +
- ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
-                    labeller = labeller(WL = label_both, O2 = label_both, Strain = label_both)) +
-  theme_bw()
-
-TargetProtein %>%
-   filter(Strain == "MED4") %>%
-  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
-  geom_col() +
-  # ggplot() +
-  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
-  # scale_fill_viridis_d(fill = "f68060") %>% 
-  # scale_colour_manual(values = MCMIXColours) +
- ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
-                    labeller = labeller(WL = label_both, O2 = label_both, Strain = label_both)) +
-  theme_bw()
-
-TargetProtein %>%
-   filter(Strain == "MIT9313",
-          O2 == 21) %>%
-  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
-  geom_col() +
-  # ggplot() +
-  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
-  # scale_fill_viridis_d(fill = "f68060") %>% 
-  # scale_colour_manual(values = MCMIXColours) +
- ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
-                    labeller = labeller(WL = label_both, O2 = label_both, Strain = label_both)) +
-  theme_bw()
-
-TargetProtein %>%
-   filter(Strain == "MED4",
-          O2 == 21) %>%
-  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
-  geom_col() +
-  # ggplot() +
-  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
-  # scale_fill_viridis_d(fill = "f68060") %>% 
-  # scale_colour_manual(values = MCMIXColours) +
- ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
-                    labeller = labeller(WL = label_both, O2 = label_both, Strain = label_both)) +
-  theme_bw()
-
-TargetProtein %>%
-   filter(Strain == "MIT9313",
-          O2 == 0) %>%
-  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
-  geom_col() +
-  # ggplot() +
-  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
-  # scale_fill_viridis_d(fill = "f68060") %>% 
-  # scale_colour_manual(values = MCMIXColours) +
- ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
-                    labeller = labeller(WL = label_both, O2 = label_both, Strain = label_both)) +
-  theme_bw()
-
-TargetProtein %>%
-   filter(Strain == "MED4",
-          O2 == 0) %>%
-  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
-  geom_col() +
-  # ggplot() +
-  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
-  # scale_fill_viridis_d(fill = "f68060") %>% 
-  # scale_colour_manual(values = MCMIXColours) +
- ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
-                    labeller = labeller(WL = label_both, O2 = label_both, Strain = label_both)) +
-  theme_bw()
+```{r Protein plots}
 
@@
   filter( Strain == "MIT9313") %>% 
+   mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste(WL, "nm", sep = " "),
+                              WL %in% c("WW") ~ paste("White LED", sep = " ")),
+        WL_label = factor(WL_label, levels= c("White LED", "660 nm", "530 nm", "450 nm")),
+         Oxygen_Label = case_when(O2_uM %in% c(250, 25, 2.5) ~ paste(O2_uM, "µM", sep = " ")),
+         Par_Label = case_when(Par_ue %in% c(30, 90, 100, 180) ~ paste(Par_ue, "µE", sep = " "))) %>% 
   ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
   geom_col() +
-   geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.6, position = "stack", check_overlap = T), color = "Black") +
-  # ggplot() +
-  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
-  # scale_fill_viridis_d(fill = "f68060") %>% 
-  # scale_colour_manual(values = MCMIXColours) +
- ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
-                    labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_both)) +
+   geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black") +
+ labs(y = "Concentration" ~  " (fmole µg"  ~ protein^-1~")", x = "Protein") +
+  # scale_fill_manual(fill = (O2_uM)) %>% 
+  # scale_colour_manual(values = ColourOxygen) +
+ ggh4x::facet_nested(cols = vars(Strain, Oxygen_Label), rows = vars(WL_label, Par_Label), 
+                    labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_value)) +
+ # guides(fill = "none") +
   theme_bw()
@@
   filter( Strain == "MED4") %>% 
+   mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste(WL, "nm", sep = " "),
+                              WL %in% c("WW") ~ paste("White LED", sep = " ")),
+        WL_label = factor(WL_label, levels= c("White LED", "660 nm", "530 nm", "450 nm")),
+         Oxygen_Label = case_when(O2_uM %in% c(250, 25, 2.5) ~ paste(O2_uM, "µM", sep = " ")),
+         Par_Label = case_when(Par_ue %in% c(30, 90, 100, 180) ~ paste(Par_ue, "µE", sep = " "))) %>% 
   ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
@@
    geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black") +
-  # ggplot() +
-  # geom_point(aes(x = Par_ue, y = Target_TotalProtein_fmole_ug, colour = as.factor(WL)), size = 3, alpha = 0.4) +
-  # scale_fill_viridis_d(fill = "f68060") %>% 
-  # scale_colour_manual(values = MCMIXColours) +
- ggh4x::facet_nested(cols = vars(Strain, O2), rows = vars(WL,Par_ue), 
-                    labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_both)) +
+ labs(y = "Concentration" ~  " (fmole µg"  ~ protein^-1~")", x = "Protein") +
+  # scale_fill_manual(fill = (O2_uM)) %>% 
+  # scale_colour_manual(values = ColourOxygen) +
+ ggh4x::facet_nested(cols = vars(Strain, Oxygen_Label), rows = vars(WL_label, Par_Label), 
+                    labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_value)) +
+ # guides(fill = "none") +
   theme_bw()

### 2024-02-23 Code/Manuscript_O2.Rmd
edits to Results & Discussion & Summary

@@
     keep_md: yes
-    toc: TRUE
+    toc: FALSE
     toc_depth: 6
@@
 # libraries; Note check actual dependencies
-
-library(lubridate)
+# Naaman add packages?
+library(knitr)
+library(tidyverse)
 library(broom)
-library(knitr)
 library(grid)
@@
 library(ggpubr)
-# library(RColorBrewer)
-library(tidyverse)
+
 library(png)
@@
 
-knitr::write_bib(c("tidyverse", "ggplot2", "Studio", "lubridate","knitr",  "broom", "zoo", "photobiologyWavebands", "RColorBrewer", "data.table","googlesheets4",  "grid", "glue", "bookdown", "photobiology", "mgcv", "minpack.lm", "ggh4x", "cowplot", "egg"), 'RPackages.bib')
+knitr::write_bib(c("knitr", "tidyverse", "lubridate", "ggplot2", "broom", "grid", "bookdown", "glue", "cowplot", "ggpubr", "ggh4x", "png", "Studio", "zoo", "photobiology", "photobiologyWavebands", "data.table", "googlesheets4",  "mgcv", "minpack.lm",  "egg", 'RPackages.bib'))
 
@@
 
-## *Prochlorococcus marinus* diversity
+## *Prochlorococcus marinus* diversity {.unnumbered}
 *Prochlorococcus marinus*, a genus of Cyanobacteria, is the smallest known photosynthetic prokaryote, with cell diameters ranging from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992].
@@
 ## *Prochlorococcus* and changing niches {.unnumbered}
+
+Current niches of *P. marinus* span ocean water columns
+[@chisholmNovelFreelivingProchlorophyte1988; @veldhuisVerticalDistributionPigment1990; @partenskyProchlorococcusMarinePhotosynthetic1999] and extend into regions with varying dissolved oxygen concentrations
+[@partenskyProchlorococcusAdvantagesLimits2010; @goerickeNovelNicheProchlorococcus2000] and even into anoxic oceans [@lavinNovelLineagesProchlorococcus2010], [@ulloaCyanobacteriumProchlorococcusHas2021; @garcia-robledoCrypticOxygenCycling2017].
 
@@
 
-XXX Mireille to confirm and summarise XXX
-
 Quantitative protein immunoblots were used to determine the concentrations of 5 target proteins; FtsH, PsbA, PetC, PsaC and RbcL in *P.
@@
 
-## Naaman GENOMICS METHODS
-XXX
+## *Prochlorococcus* comparative genomics {.unnumbered}
+
+NAAMAN
 
@@
 
-XXXMore TextXXX from AuroraXXX
-Proteins derived from Clade HLXXX ecotypes of *P. marinus* were detected in OMZ at depths up to 200 meters,  with O~2~ of 15 µM. The extent to which [O~2~] defines
-the niches occupied by different *P. marinus* ecotypes, as compared to
-potentially covarying environmental variables like photoperiod, light
-spectrum, and light level, is poorly described.
+XXXMore TextXXX from Amanda & AuroraXXX
+Proteins derived from Clade HLXXX ecotypes of *P.
+marinus* were detected in OMZ at depths up to 200 meters,  with O~2~ of 15 µM.
+The extent to which [O~2~] defines the niches occupied by different *P.
+marinus* ecotypes, as compared to potentially covarying environmental variables like photoperiod, light spectrum, and light level, is poorly described.
 
@@
 
+Guided by the evidence of ocean distributions of proteins from *Prochlorococcus* we set up a matrix of photoperiods, PAR, spectral bands, and [O~2~] to approximate current, and potential future, latitudinal, depth and seasonal niches for *Prochlorococcus* strains.
+We earlier found [@murphyPhotoinactivationPhotosystemII2017] that growth under red light could prove mechanistically informative as to factors limiting *Prochlorococcus* growth, so we included that spectral band even though it is not characteristic of representative *Prochlorococcus* niches.
+Although *Prochlorococcus* is currently limited to a narrow range of surface photoperiods, potential poleward latitudinal expansions, in combination with attenuation of light with depth, mean *Prochlorococcus* currently, or potentially, encounters a wide range of photoperiods.
+Our growth rate determinations generally agreed with those from @mooreComparativePhysiologySynechococcus1995, for white LED and 250 µM O~2~, but our study is, we believe, the first to analyze the interactive growth responses of *Prochlorococcus* strains to varying [O~2~], spectral wavebands and photoperiods.
+
 ### MED4 Clade HLI {.unnumbered}
 
-#### High oxygen environment {.unnumbered}
-
-The growth rates of *P. marinus* MED4, Clade HLI, increased with higher imposed PAR and longer photoperiods
-(Figure \@ref(fig:MED4PAR)), under 250 µM O~2~, across all spectral wavebands. No growth was
-observed under any imposed conditions under a 4 h photoperiod.The maximum growth rate
-(µ~max~) was
-`r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
-d^-1^ achieved under 180 uE blue light and 16 h photoperiod.
-
-#### Intermediate oxygen environment {.unnumbered}
-
-Similar to the growth trends under 250 µM O~2~, MED4
-maintained at 25 µM O~2~ showed the fastest growth rates when the
-photoperiod was 16 h for each spectral waveband, across PAR levels
-(Figure \@ref(fig:MED4PAR)).
-The µ~max~ was `r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "25", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
-d^-1^  achieved under 180 µmol photons
-m^-2^ s^-1^ blue light and 16 h photoperiod. The 4 h photoperiod
-experiments under white LED light were not performed because no growth
-was achieved when grown under an 8 h photoperiod of white LED light.
-
-#### Low oxygen environment {.unnumbered}
-
-MED4 did not grow under when sparged to the lowest O~2~
-of 2.5 µM (Figure \@ref(fig:MED4PAR)). 2.5 µM O~2~ growth experiments
-were not conducted for 4 and 16 h photoperiods, as no reproducible growth occurred
-when MED4 was exposed to 8 and 12 h photoperiods.
+Under 250 µM O~2~ the growth rates of *P. marinus* MED4, Clade HLI, increased with higher imposed PAR and longer photoperiods
+(Figure \@ref(fig:MED4PAR)), across all spectral wavebands.
+No growth was observed under any imposed conditions under a 4 h photoperiod.
+The maximum growth rate (µ~max~) was `r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 180 uE blue light and 16 h photoperiod.
+
+Similar to growth trends under 250 µM O~2~, MED4 maintained at 25 µM O~2~ showed fastest growth when the
+photoperiod was 16 h for each spectral waveband, across PAR levels (Figure \@ref(fig:MED4PAR)).
+The µ~max~ was `r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "25", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^  achieved under 180 µmol photons m^-2^ s^-1^ blue light and 16 h photoperiod.
+The 4 h photoperiod
+experiments under white LED light were not performed because no growth was achieved when grown under an 8 h photoperiod of white LED light.
+
+MED4 did not grow under when sparged to the lowest [O~2~] of 2.5 µM (Figure \@ref(fig:MED4PAR)). 2.5 µM O~2~ growth experiments
+were not conducted for 4 and 16 h photoperiods, as no reproducible growth occurred when MED4 was exposed to 8 and 12 h photoperiods.
 
@@
 The GAM model in Figure \@ref(fig:MED4GAM) summarizes MED4 growth responses to red (A,B) or blue (C,D) peak PAR and photoperiod across 2 imposed oxygen concentrations.
-Under 250 µM O~2~ MED4 achieved fastest growth rates above peak blue light of ~180 µmol photons m^-2^ s^-1^, and the longest photoperiod of 16, indicated by the 0.64 d^-1^ contour line representing the
-90^th^ percentile of maximum achieved growth rate (Figure \@ref(fig:MED4GAM)C).
+Under 250 µM O~2~ MED4 achieved fastest growth rates above peak blue light of ~180 µmol photons m^-2^ s^-1^, and the longest photoperiod of 16, indicated by the 0.64 d^-1^ contour line representing the 90^th^ percentile of maximum achieved growth rate (Figure \@ref(fig:MED4GAM)C).
 Growth decreased with decreasing photoperiod and decreasing peak PAR.
 Under red light growth was generally slower but the pattern of growth responses to photoperiod and PAR was similar (Figure \@ref(fig:MED4GAM)A).
-Note the exclusion of MED4 from growth under 4 h photoperiod under both red and blue light (Figure .
+Note the exclusion of MED4 from growth under 4 h photoperiod under both red and blue light \@ref(fig:MED4GAM).
 Under 25 µM O~2~ MED4 showed similar growth responses, but was excluded from both 4 and 8 h photoperiods.
 MED4 did not grow under 25 µM O~2~, so no GAM model was run.
-
-The representative of HLI clade, *P. marinus* MED4, was completely
-excluded from growth under the 4 h photoperiod \@ref(fig:MED4GAM)A,C), and showed
-increasing growth rates with increasing photoperiod. Thus, MED4 can
-potentially exploit longer summer photoperiods in temperate zones, but
-will likely remain excluded from growth in winter through its requirement for
-more than 4 h of light per day, even if water temperature warms into the Clade HLI tolerance range.
-
-MED4 grew under all PAR levels, so long as the photoperiod was longer than 4 h,
-although growth rates were slow under the lowest PAR level of 30 µmol
-photons m^-2^ s^-1^. Considering the range of PAR levels that MED4 can
-utilize, it is reasonable to suggest that MED4 can inhabit not just
-shallow depths, where light levels are high, but also deeper regions
-characterized by lower light levels, subject to the limitation of a
-photoperiod of at least 4 h even after depth attenuation of light. The photo
-regimes of winter temperate zones, due to shorter photoperiods, exclude
-MED4 from growth at all depths, however temperate photoperiods and light
-levels for the remainder of the year are adequate to support growth.
-
-MED4, grew under all tested spectral wavebands. Growth rates were
-generally comparable under blue, white LED and red lights when exposed
-to PAR levels greater than 30 µmol photons m^-2^ s^-1^ for each
-photoperiod. At the lower PAR of 30 µmol photons m^-2^ s^-1^, MED4 grew
-better under blue light. All growth rates for each spectral waveband
-increased with increasing photoperiod. The ability to utilize all
-spectral wavebands at high PAR levels and longer photoperiods make the
-near surface temperate zones available niches for MED4. MED4 ability to
-exploit blue light under low PAR levels and variable photoperiods
-greater than 4 h allow MED4 to exploit deeper regions in these temperate
-zones, where blue light prevails.
+Considering the range of PAR levels, and spectral bands that MED4 can utilize, MED4 can inhabit not just shallow depths, where light levels are high, but also deeper regions, characterized by lower level of blue light, subject to the limitation of a photoperiod of more than 4 h, even after depth attenuation of light.
+The photoregimes of winter temperate zones, due to shorter photoperiods, exclude MED4 from growth at any depth, however temperate photoperiods and light levels for the remainder of the year are potentially adequate to support MED4 growth, if water temperatures warm into the Clade HLI tolerance range.
 
@@
 
-#### High oxygen environment {.unnumbered}
-
-The growth rates of *P.
-marinus* SS120, Clade LLIII, increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^ peak PAR and 250 µM O~2~ (Figure \@ref(fig:SS120PAR)).
+Under 250 µM O~2~ growth rates of *P.
+marinus* SS120, Clade LLIII, increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^ peak PAR and (Figure \@ref(fig:SS120PAR)).
 No growth was observed under any blue light photoperiods when exposed to peak PAR of 90 µmol photons m^-2^ s^-1^ or greater.
-Growth rate increased with increasing photoperiods for white and red light under peak PAR of 90 µmol photons m^-2^ s^-1^; however, no growth was observed when the red light photoperiod was 16 h.
-Experiments under peak PAR
-of 180 µmol photons m^-2^ s^-1^ showed no growth under blue nor red lights.
-Growth rate decreased with longer photoperiods and showed growth inhibition at 12 and 16 h photoperiods under PAR of 180 µmol
-photons m^-2^ s^-1^  white LED light.
+Growth rate increased with increasing photoperiods for white and red light under peak PAR of 90 µmol photons m^-2^ s^-1^.
+Growth rate decreased with longer photoperiods and showed growth inhibition at 12 and 16 h photoperiods under PAR of 180 µmol photons m^-2^ s^-1^  white, red or blue LED light.
 The µ~max~ was `r PURPARFits %>% filter(Strain == "SS120", WL == "WW", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^  achieved under 90 µmol photons m^-2^ s^-1^ white LED light and 16 h photoperiod.
 
-#### Intermediate oxygen environment {.unnumbered}
-
-Similar to the growth trends under the 250 µM O~2~ and PAR of 30 µmol
-photons m^-2^ s^-1^ experiments, SS120 maintained at 25 µM O~2~ showed no
-growth under a 4 h photoperiod for imposed red spectral
-waveband, however under blue light, SS120 was able to grow (Figure
-\@ref(fig:SS120PAR)). In contrast to the growth trends of the 250 µM
-O~2~ and PAR of 90 µmol photons m^-2^ s^-1^ experiments, SS120 grew
-under 4 and 8 h blue light and 16 h red light photoperiods. The growth
-rate decreased with increasing photoperiod under PAR of 90 µmol photons
-m^-2^ s^-1^ white LED light treatments. Blue light treatments under PAR
-of 180 µmol photons m^-2^ s^-1^ showed growth only under an 8 h
-photoperiod. The µ~max~ was
-`r PURPARFits %>% filter(Strain == "SS120", WL == "450", O2_uM == "25", Photoperiod == 8) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
-d^-1^ (Table. \@ref(tab:MaxGrowthTable)) achieved under 90 µmol photons
-m^-2^ s^-1^ blue light and 8 h photoperiod.
-
-The 25 µM O~2~, less than 16 h photoperiod and 180 µmol photons m^-2^ s^-1^  under white LED light experiments were not performed due to time constraints.
-
-#### Low oxygen environment {.unnumbered}
-
-SS120 did not reproducibly grow when sparged to the lowest O~2~ of 2.5 µM (Figure
-\@ref(fig:SS120PAR)). 2.5 µM O~2~ growth experiments were not conducted for 4 and
-16 h photoperiods under PAR of 180 µmol photons m^-2^ s^-1^, as no
-growth occurred when SS120 was exposed to 8 and 12 h photoperiods. Red
-light 16 h photoperiod experiments were not performed due to time constraints.
+Under 25 µM O~2~ and PAR of 30 µmol photons m^-2^ s^-1^growth trends were similar to 250 µM O~2~. SS120 maintaine showed no
+growth under a 4 h photoperiod for red spectral waveband, however under blue light, SS120 was able to grow under a 4 h photoperiod (Figure
+\@ref(fig:SS120PAR)).
+In contrast to the growth trends of the 250 µM O~2~ and PAR of 90 µmol photons m^-2^ s^-1^ experiments, SS120 grew under 4 and 8 h blue light and 16 h red light photoperiods.
+The growth rate decreased with increasing photoperiod under PAR of 90 µmol photons
+m^-2^ s^-1^ white LED light treatments. Blue light treatments under PAR of 180 µmol photons m^-2^ s^-1^ showed growth only under an 8 h
+photoperiod.
+The µ~max~ was `r PURPARFits %>% filter(Strain == "SS120", WL == "450", O2_uM == "25", Photoperiod == 8) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ (Table.
+\@ref(tab:MaxGrowthTable)) achieved under 90 µmol photons
+m^-2^ s^-1^ blue light and 8 h photoperiod. The 25 µM O~2~, less than 16 h photoperiod and 180 µmol photons m^-2^ s^-1^  under white LED light experiments were not performed due to time constraints.
+
+SS120 did not reproducibly grow when sparged to the lowest O~2~ of 2.5 µM (Figure \@ref(fig:SS120PAR)).
+2.5 µM O~2~ growth experiments were not conducted for 4 and 16 h photoperiods under PAR of 180 µmol photons m^-2^ s^-1^, as no growth occurred when SS120 was exposed to 8 and 12 h photoperiods.
+Red light 16 h photoperiod experiments were not performed due to time constraints.
 
@@
 Under intermediate 90 µmol photons m^-2^ s^-1^ peak PAR growth rates decreased with increasing blue light photoperiod.
-Blue light did not induce growth at 180 µmol photons m^-2^ s^-1^ peak PAR, while MIT9313 showed only marginal growth under white LED and red light under the 8 h photoperiod .
+Blue light did not induce growth at 180 µmol photons m^-2^ s^-1^ peak PAR, while MIT9313 showed only marginal growth under white LED and red light under the 8 h photoperiod, consistent with [@moorePhotophysiologyMarineCyanobacterium1999].
 The µ~max~ was `r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 30 µmol photons m^-2^ s^-1^ blue light and 16 h photoperiod.
@@
 
-*Prochlorococcus* remain challenging to culture, as their reduced genomes – the smallest of any known oxyphototroph – render them partially dependent upon mutualistic heterotrophic bacteria to  detoxify reactive oxygen species (Moore et al., 2007; Morris et al., 2008).
-MED4, SS120 and MIT9313 have been successfully cultured in laboratories, and used to show that ecotypic classifications correspond to biochemical differences among strains.
-CITATONS OUR LAB and OTHERS.
+*Prochlorococcus* remain challenging to culture, as their reduced genomes – the smallest of any known oxyphototroph – render them partially dependent upon mutualistic heterotrophic bacteria to  detoxify reactive oxygen species [@morrisFacilitationRobustGrowth2008; @morrisDependenceCyanobacteriumProchlorococcus2011].
+MED4, SS120 and MIT9313 have been successfully cultured in laboratories  [@mooreComparativePhysiologySynechococcus1995; @mooreCulturingMarineCyanobacterium2007], and used to show that ecotypic classifications correspond to biochemical differences among strains [@bonisteelStrainSpecificDifferences2018].
+CITATONS OTHERS.
 
 Under full atmospheric [O~2~] and bluelight, LL clades of *Prochlorococcus* are restricted to growth under low light, in part because they suffer photoinhibition of Photosystem II (PSII) through several paths, including direct absorbance of UV or blue light, in parallel with generation of Reactive Oxygen Species (ROS) if the electron flow is slowed, [@aroPhotoinhibitionPhotosystemII1993], producing damaging singlet oxygen (^1^O~2~) [@aroPhotoinhibitionPhotosystemII1993; @soitamoPhotoinhibitionMarinePicocyanobacteria2017; @murphyPhotoinactivationPhotosystemII2017; @hakalaEvidenceRoleOxygenevolving2005].
-Repair of inhibited PSII process relies on the removal of damaged PsbA (Mann et al., 2000; Adam et al., 2005), followed by reassembly with newly synthesized PsbA [@nixonRecentAdvancesUnderstanding2010].
+Repair of photoinactivated PSII relies on the removal of damaged PsbA (Mann et al., 2000; Adam et al., 2005), followed by reassembly with newly synthesized PsbA [@nixonRecentAdvancesUnderstanding2010].
 Degradation of PsbA is a rate-limiting step in recovery from photoinhibition (Kanervo et al., 1993), mediated largely by a heterohexamer of (FtsH12)3, a membrane-bound (Sacharz et al., 2015)(Zak et al., 2001) metalloprotease  (Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
@@
 In contrast representative LLIV strain MIT9313 showed less overall expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem.
-Furthermore MIT9313 expressed primarily FtsH3, homologous to Sll1463 involved in PSI biogenesis, and FtsH expression did not increase in response to light stress.
-Through adaptation to steady low light, LLIV *Prochlorococcus* instead allocates resources processes other than dynamic regulation of PSII repair.
+Furthermore, MIT9313 expressed primarily FtsH3, homologous to *Synechocystis* slr1463 involved in PSI biogenesis, and  FtsH expression did not increase in response to light stress in MIT9313.
+Through adaptation to steady low light, Clade LLIV *Prochlorococcus* instead allocate resources to processes other than dynamic regulation of PSII repair.
 
@@
 ## **Prochlorococcus* genomic capacities for electron dissipation and DNA repair
-NAAMAN FIGURE
-Add Clade Code
-Make visual grammar consistent.
-Drop 'title'
-X axis scale annotated in mMol O2, lines in uM, make consistent.
 
@@
 marinus* strains from Clades HLI, LLII, LLIII and LLII [@omarAnnotationGenesEncoding2023], compared to the measured or inferred K~M~ for [O~2~] for each enzyme CITATIONS.
-[@bergResponsesPsbAHli2011] previously found that MED4 increases expression of alternative oxidase ('ubiquinol oxidase (non electrogenic)')  to cope with changes in light by dissipating electrons from the inter-system transport chain, while the genome scan shows SS120 and MIT9313 lack this gene, and therefore, lack an oxygen-dependent path to cope with changing excitation.
+MED4 increases expression of alternative oxidase ('ubiquinol oxidase (non electrogenic)')  to cope with changes in light [@bergResponsesPsbAHli2011], by dissipating electrons from the inter-system transport chain.
 The approximate K~M~ for [O~2~] of ~ 25 µM for ubiquinol oxidase (non electrogenic) is comparable to the lower limit for growth of MED4 in our experiments.
 We suggest that dependence upon this enzyme excludes MED4 from low oxygen zones.
+The genome scan shows SS120 and MIT9313 lack this gene, and therefore, lack this oxygen-dependent path to cope with changing excitation.
 Conversely, a gene encoding (S)-2-hydroxy-acid oxidase is encoded in the MIT9313 genome.
@@
 (S)-2-hydroxy-acid oxidase has an approximate K~M~ for [O~2~] of ~ 250 µM, and produces H~2~O~2~, so growth at lower [O~2~] may protect MIT9313 from auto-intoxication from production of H~2~O~2~.
-We hypothesize that under our 250 µM O~2~ and higher blue light, *P.
-marinus* MIT9313 exhibited photoinhibition, resulting from the inactivation of PSII caused by the production of the reactive oxygen species, hydrogen peroxide.
-This photoinhibition is further compounded by the limited inducible repair mechanism for PSII, due to the absence of FtsH 2 and 3  expression in *P.
+We hypothesize that under 250 µM O~2~ and higher blue light, *P.
+marinus* MIT9313 suffered photoinhibition, resulting from the inactivation of PSII caused by the production of the reactive oxygen species, hydrogen peroxide.
+This photoinhibition is compounded by the limited inducible repair mechanism for PSII, due to the absence of FtsH 2 and 3  expression in *P.
 marinus* MIT9313 [@bonisteelStrainSpecificDifferences2018].
-We hypothesize that under the conditions of our high light and 2.5 µM and 25 µM O~2~ experiments, the activity of the 2-hydroxy-acid oxidase enzyme is suppressed.
-As a result, the catalyzed production of hydrogen peroxide is inhibited, leading to minimal PSII damage, allowing MIT9313 to avoid photoinhibition and circumvent limitations on PSII repair.
+We hypothesize that under the conditions of our high light and 2.5 µM and 25 µM O~2~ experiments, the activity of the (S)-2-hydroxy-acid oxidase enzyme is suppressed.
+As a result, the catalyzed production of hydrogen peroxide is inhibited, leading to less PSII damage, allowing MIT9313 to avoid photoinhibition and circumvent its limitations on PSII repair.
 Figure \@ref(fig:ProchlorococcusEnzymeKms) also shows that *P.
@@
 marinus* SS120 does not grow as well as *P.
-marinus* MIT9313 when exposed to high light stress under 25 µM O~2~ and not at all under 2.5 µM O~2~.
+marinus* MIT9313, when exposed to high light stress under 25 µM O~2~ and not at all under 2.5 µM O~2~.
 
@@
 As expected,  *P.
-marinus* MED4 possesses the largest and most complete suite of genes encoding DNA repair enzymes, followed by *P.
+marinus* MED4 possesses the largest, most complete suite of genes encoding DNA repair enzymes, followed by *P.
 marinus* MIT9313.
@@
 marinus* SS120 demonstrates the smallest genomic capacity for DNA repair.
-*Prochlorococcus marinus* MED4 was the only strain to possess the gene encoding deoxyribodipyrimidine photolyase, which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003].
-*Prochlorococcus marinus* MED4 was also the only strain to possesses the gene encoding DNA ligase, which uses ATP as a cofactor for DNA repair.
-The absence of the genes encoding deoxyribodipyrimidine photolyase and DNA ligase (ATP) in *P.
+*Prochlorococcus marinus* MED4 was the only strain to possess a gene encoding deoxyribodipyrimidine photolyase, which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003].
+*Prochlorococcus marinus* MED4 was also the only strain to possesses a gene encoding DNA ligase, which uses ATP as a cofactor for DNA repair.
+The absence of  genes encoding deoxyribodipyrimidine photolyase and DNA ligase (ATP) in *P.
 marinus* MIT9313 and *P.
-marinus* SS120 helps explain why these two strains cannot tolerate growth under full [O~2~] and high light found at the ocean surface where.
+marinus* SS120 helps explain why these two strains cannot tolerate growth under full [O~2~] and high light, found at the ocean surface.
 Furthermore, the protective effect of lower [O~2~], allowing these strains to grow at higher light, may relate in part to suppression of DNA damage when generation of Reactive Oxygen Species is suppressed at lower [O~2~].
 *Prochlorococcus* are highly susceptible to hydrogen peroxide (H~2~O~2~) toxicity as they lack genes which scavenge H~2~O~2~ molecules [@morrisFacilitationRobustGrowth2008].
-The small cell size of *Prochlorococcus* allow the reactive oxygen species (ROS), H~2~O~2~, to cross the cell membrane; however, the accumulation of extracellular H~2~O~2~ can also be toxic to *Prochlorococcus* [@morrisFacilitationRobustGrowth2008,  @morrisDependenceCyanobacteriumProchlorococcus2011].
+The small cell size of *Prochlorococcus* allow the reactive oxygen species (ROS), H~2~O~2~, to cross the cell membrane [@omarGenomicCapacitiesReactive2023]; however, accumulation of extracellular H~2~O~2~ remains toxic to *Prochlorococcus* [@morrisFacilitationRobustGrowth2008,  @morrisDependenceCyanobacteriumProchlorococcus2011].
 
@@
 \newpage
-
-The representative of HLI clade, *P. marinus* MED4, generally exhibited similar growth
-response trends and growth rates under blue and red light treatments
-under both 25 µM and 250 µM of O~2~,  but was unable to grow under
-the lowest O~2~ level of 2.5 µM. MED4  This demonstrated ability to grow
-under 25 µM O~2~, coupled with its ability to grow under lower PAR
-levels, enables MED4 to potentially inhabit deeper regions where [O~2~]
-may vary and low blue light is present, as long as the photoperiod
-exceeds 4 h. Our findings are supported by the analysis of TARA Oceans
-Project data conducted by @delmontLinkingPangenomesMetagenomes2018 who
-reported the presence of *P. marinus* MED4-like genomes at depths
-ranging from 5 m to 90 m, representing high to low blue light levels, in
-the Pacific South East Ocean. @delmontLinkingPangenomesMetagenomes2018
-did not analyze data from depths beyond the subsurface chlorophyll
-maximum layer, the layer in the water column where the chlorophyll a
-concentration peaks, nor did they report the [O~2~] at those depths but
-we have shown, in this study, that MED4 can potentially grow in these
-regions. Our findings were also consistent with
-FIGURE REFERENCE who analyzed the OceansMap
-Protein Portal (OPP) [@saitoDevelopmentOceanProtein2021] for proteins
-expressed by vertically stratified *P. marinus* strains at varying
-depths and [O~2~], in the ocean minimal zone of the tropical North
-Pacific Ocean, and found PSII proteins annotated as MED4 expressed at
-depths up to 200 meters with O~2~ of 15 µM.
 
@@
 MIT9313 has a remarkable ability to thrive under very low [O~2~], potentially allowing it to expand into
-broader ecological niches. These results support 
-FIGUREXXXX where PSI protein subunits
-annotated as derived from MIT9313 were detected at depths \> 120 m,
-along with PSII subunits at depths from 50 m to 200 m in regions where
+broader ecological niches. These results are supported by \@ref(fig:ProchloroPhotosynthDepthO2) showing PSI protein subunits
+annotated as derived from MIT9313 wdetected at depths \> 120 m, along with PSII subunits at depths from 50 m to 200 m in regions where
 O~2~ was 15 µM.
 
-Under the 250 µM O~2~ growth experiments and under some photoperiods,
-when subjected to the highest PAR of 180 µmol photons m^-2^ s^-1^,
-MIT9313 grew when treated under white LED and red light and SS120
-grew under white LED light. However, 
-these strains were excluded from growth under high blue peak PAR. Growth
-studies have demonstrated that LL clades experience growth inhibition at
-PAR levels between 150 and 200 µmol photons m^-2^ s^-1^
-[@moorePhotophysiologyMarineCyanobacterium1999].
-
-Our growth rate maximums under white LED and 250 µM O~2~, for MED4,
-`r PURPARFits %>% filter(Strain == "MED4", WL == "WW", O2_uM == "250") %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
-d^-1^ and SS120,
-`r PURPARFits %>% filter(Strain == "SS120", WL == "WW", O2_uM == "250") %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
-d^-1^, compare well with @mooreComparativePhysiologySynechococcus1995,
-who found white light saturated growth rate maximums of 0.63 ± 0.06
-d^-1^ and 0.53 ± 0.06 d^-1^ for MED4 and SS120, respectively.
-
-For each strain of *P. marinus*, Table \@ref(tab:NichesTable) provides a
-summary of our findings for potential temperate growth niches, as
-defined by photoperiod, light level and oxygen level, characteristic of
-different seasons, depths, and oxygen zones. The potential for niche
-expansion into temperate regions by *P. marinus* varies depending on the
-season, which influences achieved underwater photoperiods and light
-levels. Temperate summer delivers 11 hours of blue waveband light
-underwater, above the photic threshold of 20 µmol photons m^-2^ s^-1^,
-while temperate spring/fall delivers 8 hours of blue waveband light
-underwater, photoperiod ranges which are permissive for growth of all
-three *P. marinus*. In contrast temperate winter delivers only about 2 h
-of blue waveband light underwater above the photic threshold (Figure \@ref(fig:CardinalSeasons)), which
-precludes growth of MED4 and SS120, even if winter waters reached
-permissive temperatures. MIT9313 and SS120 will be excluded from
-near-surface growth niches by high PAR, unless OMZ zones extend to the
-near surface.
-
-The lack of photoperiod growth studies for *P.
-marinus* is not surprising, given that higher cell abundances of *P.
-marinus* are currently  concentrated between 30°N and 30°S.
-At 30°N, the photoperiod seasonality ranges from 12 to 14 hours at the ocean surface between the winter and summer solstices, while it remains consistently 12 hours throughout the year at the equator.
-Therefore, growth response studies to date have generally been conducted under either a 12 or 14 hour (h) photoperiod.
-However, the photoperiod at the ocean surface is not fully representative of the photoperiod underwater, as solar radiation is reflected off the surface when the solar incident angle is less than 20°.
-This discrepancy between the duration of daylight hours above water and the effective duration of light exposure underwater is often overlooked in the experimental design of *P.
-marinus* growth studies, even when considering photoperiod.
-
-Current niches of *P. marinus* span across vertical ocean water columns
-[@chisholmNovelFreelivingProchlorophyte1988; @veldhuisVerticalDistributionPigment1990; @partenskyProchlorococcusMarinePhotosynthetic1999] and extend into regions with varying dissolved oxygen concentrations
-[@partenskyProchlorococcusAdvantagesLimits2010; @goerickeNovelNicheProchlorococcus2000] and even into anoxic oceans [@lavinNovelLineagesProchlorococcus2010], [@ulloaCyanobacteriumProchlorococcusHas2021; @garcia-robledoCrypticOxygenCycling2017].
-Climate change is drastically altering the dissolved oxygen concentrations ([O~2~]) of our ocean waters.
-Research indicates that the oxygen minimum zones (OMZs) in the Pacific and Indian Oceans are expanding [@garcia-sotoOverviewOceanClimate2021; @buseckeDivergingFatesPacific2022] and that the levels of dissolved oxygen (O~2~) in our global oceans are generally decreasing [@matearLongtermChangesDissolved2003; @garcia-sotoOverviewOceanClimate2021], with significant decreases observed toward the poles [@helmObservedDecreasesOxygen2011].
+Table \@ref(tab:NichesTable) summarizes our findings for potential growth niches, as defined by photoperiod, light level and oxygen level, characteristic of different seasons, depths, and oxygen zones.
+The potential for niche expansion into temperate regions by *P.
+marinus* varies depending on the season, which influences achieved underwater photoperiods and light levels.
+Temperate summer delivers 11 hours of blue waveband light
+underwater, above the photic threshold of 20 µmol photons m^-2^ s^-1^, while temperate spring/fall delivers 8 hours of blue waveband light
+underwater, photoperiod ranges which are permissive for growth of all three *P. marinus*. In contrast temperate winter delivers only about 2 h
+of blue waveband light underwater above the photic threshold, which precludes growth of MED4 and SS120, even if winter waters reached
+permissive temperatures. MIT9313 and SS120 will be excluded from near-surface growth niches by high PAR, unless OMZ zones extend to the near surface.
+
+Diverse *P.
+marinus* strains  @billerProchlorococcusStructureFunction2015 differentially exploit potential photoregimes, both at the surface and deep in the water column.
+Some *P.
+marinus* strains grow under low oxygen environments, similar to OMZ.
+The LL clades we tested can function as 'HL'  in oxygen environments of 25 µM, and as low as 2.5 µM, in the case of MIT9313.
+
+@westNichePartitioningProchlorococcusPopulationsStratified1999 and @malmstromTemporalDynamicsProchlorococcus2010 found that decreased abundances of the LL clades corresponded to increased depth of the surface mixed layer.
+@malmstromTemporalDynamicsProchlorococcus2010 attributes the transport of LL ecotypes to the surface and consequent exposure to photoinhibitory high light levels as the reason for low cell abundances with increased mixed layer depth.
+@westNichePartitioningProchlorococcusPopulationsStratified1999 found the depth of the mixed layer strongly influenced the depth transition from HL to LL clades, but that factors other than light levels may influence the variations in the upper and lower depth limits of these ecotypes.
+We hypothesize that low cell abundances of LL ecotypes in the mixed layer is likely driven in part by increased [O~2~],  and it is [O~2~] that constrains LL clades to deeper waters, not necessarily the light level.
+We found that under 25 µM O~2~ representatives of 'LL' clades, SS120 and MIT9313, actually tolerate approximately 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of PUR [@morelAvailableUsableStored1978],  comparable to the representative HL clade, MED4 which also exhibited growth saturation at the same cumulative diel PUR of 1.0 x 10^6^ µmol photons m^-2^ d^-1^.
+Growth under lower O~2~ allowed MIT9313 to substantially increase its exploitation of higher diel PUR.
+
+# Summary and Conclusions {.unnumbered}
 
@@
 marinus* to varying [O~2~] under the matrix of light parameters to determine if *P.
-marinus* can cope with  diverse  ecosystem scenarios.
-
-We found that *P.
-marinus* MED4, can grow under near surface O~2~ saturation levels of 250 µM and high light levels, conditions representative of its current ecotype classification [@moorePhysiologyMolecularPhylogeny1998].
-MED4 can also grow under O~2~ of 25 µM, and under all tested levels of light in the blue spectral waveband, so long as the photoperiod is longer than 4 h (Figure \@ref(fig:MED4PAR)).
-Consequently, MED4 can potentially inhabit different ecological niches through its ability to  exploit a wide range of light levels, from the surface to the deep ocean, along with varying levels of dissolved oxygen throughout the water column.
-These findings are supported by evidence of HL ecotype presence even in the OMZ [@mattisonPhotosyntheticStrategiesWild2020] and in deeper regions of the ocean [@mattisonPhotosyntheticStrategiesWild2020; @delmontLinkingPangenomesMetagenomes2018].
-With predicted future ocean warming [@wijffelsOceanTemperaturesChronicle2016], MED4 shows potential to harness the photoregimes prevalent in temperate spring, summer, and fall zones when the duration of blue spectral waveband in the water column exceeds 4 hours.
+marinus* strains can cope with  diverse  ecosystem scenarios.
+
+*Prochlorococcus marinus* MED4 has a physiological requirement for more than 4 h of light per day, and thus this strain will not exploit habitats with short photoperiods, typical of winter or light attenuated depths.
+MED4 is also excluded from the lowest oxygen habitats, equivalent to our 2.5 µM O~2~ experimental conditions.
+MED4 can, however, grow under OMZ regions with slightly higher [O~2~], as by the growth under our 25 µM O~2~ experiments.
+Genomic analyses  \@ref(fig:ProchlorococcusEnzymeKms)  and previous transcriptional analyses [@bergResponsesPsbAHli2011]  suggests MED4 is excluded from growth below ~ 25 µM O~2~ because it relies upon a ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction balance in the intersystem electron transport chain.
+On the other hand, MED4 shows inducible expression of FtsH isoforms [@bonisteelStrainSpecificDifferences2018], to counter photoinactivation of PSII under higher PAR and [O~2] environments.
+Photoinactivation, does, however, impose an increased cost of growth upon MED4, since growth under red light, to lower the rate of photoinactivation of PSII [@murphyPhotoinactivationPhotosystemII2017], allows MED4 to achieve faster growth per absorbed photon than growth under red light.
+TARA Oceans
+Project data [@delmontLinkingPangenomesMetagenomes2018] indeed reported presence of *P.
+marinus* MED4-like genomes at depths ranging from 5 m to 90 m, representing high to low blue light levels, in the Pacific South East Ocean.
+@delmontLinkingPangenomesMetagenomes2018 did not analyze data from depths beyond the subsurface chlorophyll maximum layer, the layer in the water column where the chlorophyll a concentration peaks, nor did they report the [O~2~] at those depths.
+Our growth findings are also consistent with Figure \@ref(fig:ProchloroPhotosynthDepthO2) showing PSII proteins annotated as MED4, at depths up to 200 meters with O~2~ of 15 µM.
+
+*Prochlorococcus marinus* SS120, a LLIII clade representative, showed an interactive inhibition of growth by oxygen and cumulative diel PUR, with a higher tolerance for higher cumulative diel absorbed PUR under 25 µM O~2~, compared to 250 µM O~2~.
+Thus, SS120 can exploit habitats with O~2~ levels spanning 25 µM O~2~ to 250 µM O~2~, including high PAR environments within OMZ.
+SS120 is likely excluded from higher [O~2~] and higher PAR because of genomic limitations on capacity for DNA repair \@ref(fig:DNARepairFig), and possibly by limited capacity for synthesis of reactive oxygen quenchers  \@ref(fig:ProchlorococcusEnzymeKms).
 
@@
 
-*Prochlorococcus marinus* MIT9313 shows the potential to inhabit future warmed temperate zones year-round, as it exhibits the ability to grow under a 4 h photoperiod.
-MIT9313 demonstrates an unexpected tolerance to higher light levels,  but only under low oxygen conditions of 25 µM and 2.5 µM (Figure \@ref(fig:MIT9313PAR)).
-The ability to utilize higher levels of blue spectral waveband under 25 µM or 2.5 µM O~2~ enables MIT9313 to grow in regions like the OMZ and even at depths closer to the surface.
-
-We found our experimental growth rates agreed with those from @mooreComparativePhysiologySynechococcus1995, grown under white LED and 250 µM O~2~.
-However, growth response studies are scarce for comparison, especially under varying [O~2~] and even under different spectral wavebands and photoperiods.
-As far as we know, our study is the first to analyze the interactive growth responses of *Prochlorococcus*  to varying [O~2~], spectral wavebands and photoperiods.
-
-The potential expansion of  *P.
-marinus*  polewards will contribute to the primary food base of an aquatic ecosystem that has already undergone changes in Canadian waters; commercial fish populations are shifting with new species immigrating  [@zellerCheungZellerPauly2011], endangered whales actively searching for food sources are becoming more prevalent [@meyer-gutbrodMarineSpeciesRange2018] and the white shark seasonal presence is increasing  either due to rising ocean temperatures or following marine prey [@bastienInconspicuousRecoveringNorthward2020].
-While the exact impact of the presence of *P.
-marinus*  on the species distribution of marine wildlife in Atlantic Canadian waters is unknown, there is little doubt that *Prochlorococcus* will play a significant role in shaping this distribution.
-The shifting dynamics of the aquatic ecosystem in the Atlantic Canadian waters may have consequences for our commercial fishing and shipping sectors, as adjustments to shipping routes and regulations are made to safeguard endangered whales.
-
-We determined the Photosynthetic Usable Radiation (PUR), the portion of light radiation absorbed differentially by the pigments of the photosynthetic organism [@morelAvailableUsableStored1978] and expressed growth response in terms of cumulative diel PUR.
-We found that approximately 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of PUR is the maximum dosage that the representative LL clades, SS120 and MIT9313 can tolerate under 25 µM O~2~, in contrast to the representative HL clade, MED4 which exhibited growth saturation at the same cumulative diel PUR of 1.0 x 10^6^ µmol photons m^-2^ d^-1^.
-Growth under lower O~2~ allowed MIT9313 to substantially increase its exploitation of higher diel PUR.
-
-@westNichePartitioningProchlorococcusPopulationsStratified1999 and @malmstromTemporalDynamicsProchlorococcus2010 found that decreased abundances of the LL clades corresponded to increased depth of the surface mixed layer.
-@malmstromTemporalDynamicsProchlorococcus2010
-attributes the transport of LL ecotypes to the surface and consequent exposure to photoinhibitory high light levels as the reason for low cell abundances with increased mixed layer depth.
-@westNichePartitioningProchlorococcusPopulationsStratified1999 found the depth of the mixed layer strongly influenced the depth transition from HL to LL clades, but that factors other than light levels may influence the variations in the upper and lower depth limits of these ecotypes.
-We hypothesize that low cell abundances of LL ecotypes in the mixed layer is likely driven in part by increased [O~2~],  and it is [O~2~] that constrains LL clades to deeper waters, not necessarily the light level.
-
-*P.
-marinus* strains differentially exploit potential photoregimes of the temperate zone, both at the surface and deep in the water column.
-Some *P.
-marinus* strains grow under  low oxygen environments, similar to OMZ and that the LL clades we tested can be labeled as 'HL'  in oxygen environments of 25 µM and as low as 2.5 µM in the case of MIT9313.
-@billerProchlorococcusStructureFunction2015 has described *Prochlorococcus* as a 'federation' of diverse cells whose extensive genomic and phenotypic diversity contributes to their wide distribution, stability, and abundance in oceans.
-
-*Prochlorococcus marinus* MED4 has a physiological requirement for more than 4 h of light per day, and thus this strain will not exploit habitats with short photoperiods.
-MED4 is also excluded from the lowest oxygen habitats, equivalent to our 2.5 µM O~2~ experimental conditions; however, MED4 can inhabit regions with slightly higher O~2~, as was demonstrated by the growth responses observed under our 25 µM O~2~ experiments.
-
-*Prochlorococcus marinus* SS120, categorized as a LLIII clade representative, showed an interactive growth inhibition between oxygen and cumulative diel absorbed PUR, with a higher tolerance for higher cumulative diel absorbed PUR under 25 µM O~2~, compared to 250 µM O~2~.
-Thus, SS120 can exploit habitats with O~2~ levels spanning 25 µM O~2~ to 250 µM O~2~.
-
-*Prochlorococcus marinus* MIT9313 is categorized as a LLIV clade representative, but under 25 or 2.5 µM O~2~, MIT9313 can actually exploit cumulative diel absorbed PUR comparably to *P.
-marinus* HLI clade MED4.
-Therefore, lower oxygen habitats extending to near the surface could potentially be exploited by MIT9313.
+*Prochlorococcus marinus* MIT9313, a LLIV clade representative, shows the potential to inhabit future warmer temperate zones year-round, as it grows under a 4 h photoperiod, expected in winter or at light-attenuated depths.
+MIT9313 demonstrates an unexpected tolerance to higher light levels and cumulative diel PUR,  but only under low oxygen conditions of 25 µM and 2.5 µM (Figure \@ref(fig:MIT9313PAR)).
+The ability to utilize higher PAR and higher cumulative diel PUR under 25 µM or 2.5 µM O~2~ enables MIT9313 to grow in OMZ, even at depths closer to the surface.
+MIT9313 carries a gene encoding (S)-2-hydroxy-acid oxidase [@InformationEC15],  with a K~M~ for [O~2~] of ~ 250 µM \@ref(fig:ProchlorococcusEnzymeKms), which produces H~2~O~2~.
+Growth at lower [O~2~] may protect MIT9313 from auto-intoxication from production of H~2~O~2~.
+We hypothesize that under 250 µM O~2~ and higher blue light, *P.
+marinus* MIT9313 suffers photoinhibition, resulting from the inactivation of PSII caused by the production of H~2~O~2~.
+This photoinhibition is compounded by the limited inducible repair for PSII, due to the absence of FtsH 2 and 3  expression in *P.
+marinus* MIT9313 [@bonisteelStrainSpecificDifferences2018].
 
@@
 # Acknowledgements  {.unnumbered}
-Jonah Sheinin assisted with growth of some cultures for protein analyses, while Carlie Barnhill assisted with code for import of multicultivator growth data files.
+Jonah Sheinin (Mount Allison Student) assisted with growth of some cultures for protein analyses, while Carlie Barnhill (Mount Allison Student) assisted with code for import of multicultivator growth data files.
 

### 2024-02-23 Code/Manuscript_O2.Rmd
Edits to Results & Discussion

@@
 marinus* small cell diameters, from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992], and simple cell structures, minimize the complication of pigment package effect or intracellular self-shading [@morelProchlorococcusSynechococcusComparative1993].
-Given the different spectral light regimes typical of the niches of different ecotypes, expressing growth rates in terms of cumulative diel absorbed PUR might simplify different photoperiods, spectral bands, and PAR levels into a common parameter, making growth response comparisons across strains and different oxygen levels more accessible.
-We also aimed to detect whether growth responses are driven simply by cumulative diel absorbed PUR, or whether specific photoperiods, spectral bands or PAR levels have independent, albeit interacting, effects on growth.
+Given the different spectral light regimes typical of the niches of different ecotypes, expressing growth rates in terms of cumulative diel PUR might simplify different photoperiods, spectral bands, and PAR levels into a common parameter, making growth response comparisons across strains and different oxygen levels more accessible.
+We also aimed to detect whether growth responses are driven simply by cumulative diel PUR, or whether specific photoperiods, spectral bands or PAR levels have independent, albeit interacting, effects on growth.
 
@@
 
-Actinic absorbed PUR levels (µmol photons m^-2^ s^-1^) were calculated from actinic PAR (µmol photons m^-2^ s^-1^) levels using the equation \@ref(eq:PUR) from [@morelAvailableUsableStored1978],
+Actinic PUR levels (µmol photons m^-2^ s^-1^) were calculated from actinic PAR (µmol photons m^-2^ s^-1^) levels using the equation \@ref(eq:PUR) from [@morelAvailableUsableStored1978],
 
@@
 The applied photoperiods were delivered using the sine circadian light function of the PSI Multicultivator to simulate light exposure approximating sun rise through to sunset.
-The area under the sinusoidal curves is equivalent to the area of a triangular photoregime of equivalent photoperiod (Campbell, unpub), therefore the equation to determine the cumulative diel absorbed PUR (µmol photons m^-2^ d^-1^) is one half of the base (photoperiod) multiplied by the height (PUR) (equation \@ref(eq:SumPURDay)),
+The area under the sinusoidal curves is equivalent to the area of a triangular photoregime of equivalent photoperiod (Campbell, unpub), therefore the equation to determine the cumulative diel PUR (µmol photons m^-2^ d^-1^) is one half of the base (photoperiod) multiplied by the height (PUR) (equation \@ref(eq:SumPURDay)),
 
 \begin{equation}
-  Cumulative diel absorbed PUR = \frac{PUR × 3600 × Photoperiod}{2}
+  Cumulative diel PUR = \frac{PUR × 3600 × Photoperiod}{2}
   (\#eq:SumPURDay)
@@
 marinus* MED4, SS120 and MIT9313, respectively.
-Figure (\@ref(fig:PurParPlot)) shows the relationship between calculated absorbed PUR versus imposed PAR for each *P.
+Figure (\@ref(fig:PurParPlot)) shows the relationship between calculated PUR versus imposed PAR for each *P.
 marinus* and each spectral waveband.
@@
 PurParPlot_cap <- glue("**Absorbed peak Photosynthetically Usable Radiation (PUR) (µmol photons m^-2^ s^-1^) vs. peak Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^).**",
-                       "The correlation between PAR, plotted on the x-axis and absorbed PUR, plotted on the y-axis, are colored for each growth spectral waveband; 450 nm (blue circles), 660 nm (red circles) and white LED (black circles).",
+                       "The correlation between PAR, plotted on the x-axis and PUR, plotted on the y-axis, are colored for each growth spectral waveband; 450 nm (blue circles), 660 nm (red circles) and white LED (black circles).",
                        "The grey dashed line represents a hypothetical one to one correlation.",
@@
 No growth was observed under any blue light photoperiods when exposed to peak PAR of 90 µmol photons m^-2^ s^-1^ or greater.
-Growth rate increased with increasing photoperiods for white and red light under peak PAR of 90 µmol photons m^-2^ s^-1^.
+Growth rate, however increased with increasing photoperiods for white and red light under peak PAR of 90 µmol photons m^-2^ s^-1^.
 Growth rate decreased with longer photoperiods and showed growth inhibition at 12 and 16 h photoperiods under PAR of 180 µmol photons m^-2^ s^-1^  white, red or blue LED light.
@@
 
-Under 25 µM O~2~ and PAR of 30 µmol photons m^-2^ s^-1^growth trends were similar to 250 µM O~2~. SS120 maintaine showed no
+Under 25 µM O~2~ and PAR of 30 µmol photons m^-2^ s^-1^ growth trends were similar to 250 µM O~2~. SS120 showed no
 growth under a 4 h photoperiod for red spectral waveband, however under blue light, SS120 was able to grow under a 4 h photoperiod (Figure
@@
 In contrast to the growth trends of the 250 µM O~2~ and PAR of 90 µmol photons m^-2^ s^-1^ experiments, SS120 grew under 4 and 8 h blue light and 16 h red light photoperiods.
-The growth rate decreased with increasing photoperiod under PAR of 90 µmol photons
-m^-2^ s^-1^ white LED light treatments. Blue light treatments under PAR of 180 µmol photons m^-2^ s^-1^ showed growth only under an 8 h
-photoperiod.
+The growth rate decreased with increasing photoperiod under PAR of 90 µmol photons m^-2^ s^-1^ white LED light treatments.
+Blue light treatments under PAR of 180 µmol photons m^-2^ s^-1^ showed growth only under an 8 h photoperiod.
 The µ~max~ was `r PURPARFits %>% filter(Strain == "SS120", WL == "450", O2_uM == "25", Photoperiod == 8) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ (Table.
-\@ref(tab:MaxGrowthTable)) achieved under 90 µmol photons
-m^-2^ s^-1^ blue light and 8 h photoperiod. The 25 µM O~2~, less than 16 h photoperiod and 180 µmol photons m^-2^ s^-1^  under white LED light experiments were not performed due to time constraints.
+\@ref(tab:MaxGrowthTable)) achieved under 90 µmol photons m^-2^ s^-1^ blue light and 8 h photoperiod.
+The 25 µM O~2~, less than 16 h photoperiod and 180 µmol photons m^-2^ s^-1^  under white LED light experiments were not performed due to time constraints.
 
@@
 Red light 16 h photoperiod experiments were not performed due to time constraints.
-
 \newpage
@@
 
-The GAM model in Figure \@ref(fig:SS120GAM) summarizes growth
-responses of SS120 to red (A) or blue (B) peak PAR and photoperiod,
-across the 2 imposed oxygen concentrations. Under 250 µM O~2~,
-Figure \@ref(fig:SS120GAM)A showed highest growth
-rates below PAR of 50 µmol photons m^-2^ s^-1^ and
-photoperiods between 8 and 12 h, indicated by the contour line labeled
-0.29 d^-1^ (representing the 90^th^ percentile of achieved growth rate).
+The GAM model in Figure \@ref(fig:SS120GAM) summarizes growth responses of SS120 to red (A) or blue (B) peak PAR and photoperiod, across the 2 imposed oxygen concentrations.
+Under 250 µM O~2~, Figure \@ref(fig:SS120GAM)A showed highest growth rates below PAR of 50 µmol photons m^-2^ s^-1^ and photoperiods between 8 and 12 h, indicated by the contour line labeled 0.29 d^-1^ (representing the 90^th^ percentile of achieved growth rate).
+Under 250 µM O~2~ SS120 is constrained to deeper ocean waters through its intolerance of higher blue PAR levels.
+These findings align with @mooreComparativePhysiologySynechococcus1995 and are expected for a low light clade.
 The disjunct regions of the GAM plot results from variable growth success of SS120 under 250 µM O~2~.
 Growth rate patterns under red light were similar, although somewhat faster.
-In contrast, under 25 µM O~2~ and a photoperiod of 8 h SS120 exploited all blue peak PAR levels, achieving faster growth rates at a higher PAR of \~100 µmol photons
-m^-2^ s^-1^, indicated by the contour line labeled 0.5 d^-1^
-(representing the 90^th^ percentile of achieved growth rate), out pacing
-the 90^th^ percentile fastest growth rates under 250 µM O~2~.
-Under red light and 25 µM O~2~ light SS120 grew across most conditions of peak PAR and photoperiod, achieving fastest growth under long photoperiods and peak PAR below 50 \~100 µmol photons
-m^-2^ s^-1^.  Thus, the designation of SS120 as a LL strain is dependent upon the [O~2]. SS120 did not, however, grow reliably under tested conditions at 2.5 µM O~2~.
-
-The LLIII clade, *P. marinus* SS120, grew under photoperiods longer than
-4 h and showed increasing growth rate with increasing photoperiods.
-Therefore, SS120 can potentially exploit the longer summer photoperiods
-in temperate zones but again cannot sustain growth in winter through its
-requirement for more than 4 h of light per day, even if water temperature warms into the Clade LLIII tolerance range.
-
-SS120, grew under a PAR of 30 µmol photons m^-2^ s^-1^, and under some conditions at PAR of 90 µmol photons m^-2^ s^-1^, but growth was generally inhibited under PAR of 180 µmol photons
-m^-2^ s^-1^. These findings align with the results reported by
-@mooreComparativePhysiologySynechococcus1995 and are expected for a low
-light clade. Given that SS120 can tolerate longer photoperiods and low
-PAR levels, the deep ocean temperate zones are a viable habitat but not
-during temperate winter due to shorter photoperiods.
-
-SS120 exhibited different growth responses to spectral wavebands
-under varying O~2~ conditions, as such, this section will address the
-growth response under 250 µM O~2~ experiments, while the interactions of
-spectral wavebands under all O~2~ treatments will be discussed in the
-next section. SS120, grew under all spectral wavebands at a PAR of 30
-µmol photons m^-2^ s^-1^. Growth was completely inhibited under blue
-light at PAR levels of 90 and 180 µmol photons m^-2^ s^-1^, but growth
-occurred at PAR of 90 µmol photons m^-2^ s^-1^ under all other spectral
-wavebands. Generally, growth was strongly inhibited under PAR of 180
-µmol photons m^-2^ s^-1^ for all spectral wavebands.
-The ability of SS120 to grow under low blue light and longer photoperiods, makes the deep ocean waters of the temperate zone a viable potential habitat.
-Under 250 µM O~2~ SS120 is constrained to deeper ocean waters through its intolerance of higher blue PAR levels.
+In contrast, under 25 µM O~2~ and a photoperiod of 8 h SS120 exploited all blue peak PAR levels, achieving faster growth rates at a higher PAR of \~100 µmol photons m^-2^ s^-1^, indicated by the contour line labeled 0.5 d^-1^ (representing the 90^th^ percentile of achieved growth rate), out pacing the 90^th^ percentile fastest growth rates under 250 µM O~2~.
+Under red light and 25 µM O~2~ light SS120 grew across most conditions of peak PAR and photoperiod, achieving fastest growth under long photoperiods and peak PAR below 50 \~100 µmol photons m^-2^ s^-1^.
+Thus, the designation of SS120 as a LL strain is dependent upon the [O~2].
+SS120 did not, however, grow reliably under tested conditions at 2.5 µM O~2~.
 
@@
 
-#### High oxygen environment {.unnumbered}
-
-The growth rates of *P. marinus* MIT9313, Clade LLIV increased with longer
-photoperiods under low 30 µmol photons m^-2^ s^-1^ peak PAR, under 250 µM O~2~ (Figure
-\@ref(fig:MIT9313PAR)).
+Under 250 µM O~2~ growth rates of *P. marinus* MIT9313, Clade LLIV, increased with longer
+photoperiods, under low 30 µmol photons m^-2^ s^-1^ peak PAR, (Figure \@ref(fig:MIT9313PAR)).
 Under intermediate 90 µmol photons m^-2^ s^-1^ peak PAR growth rates decreased with increasing blue light photoperiod.
-Blue light did not induce growth at 180 µmol photons m^-2^ s^-1^ peak PAR, while MIT9313 showed only marginal growth under white LED and red light under the 8 h photoperiod, consistent with [@moorePhotophysiologyMarineCyanobacterium1999].
+Blue light did not induce growth at 180 µmol photons m^-2^ s^-1^ peak PAR, while MIT9313 showed only marginal growth under white LED and red light at 180 µmol photons m^-2^ s^-1^ peak PAR, under the 8 h photoperiod, consistent with [@moorePhotophysiologyMarineCyanobacterium1999].
 The µ~max~ was `r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 30 µmol photons m^-2^ s^-1^ blue light and 16 h photoperiod.
 
-#### Intermediate oxygen environment {.unnumbered}
-
-For MIT9313 maintained at 25 µM O~2~ growth rate increased with increasing photoperiods for all spectral wavebands tested (Figure \@ref(fig:MIT9313PAR)).
-Under peak PAR of 90 µmol photons m^-2^ s^-1^ growth rate increased with longer photoperiods, with the fastest overall growth rate for MIT9313
-`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "25", Photoperiod == 16, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 16 h blue light photoperiod.
-In contrast to the 250 µM O~2~ growth experiments, MIT9313 grew when exposed to peak PAR of 180 µmol photons m^-2^ s^-1^ and blue light under all photoperiods except 16 h; additionally,
-white LED and red light treatments induced growth across all tested photoperiods under 25 µM O~2~.
+For MIT9313 under 25 µM O~2~ growth rate increased with increasing photoperiods for all spectral wavebands tested (Figure \@ref(fig:MIT9313PAR)), with the fastest overall growth rate for MIT9313 
+`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "25", Photoperiod == 16, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under peak PAR of 90 µmol photons m^-2^ s^-1^ and 16 h blue light photoperiod.
+In marked contrast to the 250 µM O~2~ growth experiments, MIT9313 grew when exposed to peak PAR of 180 µmol photons m^-2^ s^-1^ and blue light under all photoperiods except 16 h; additionally, white LED and red light treatments induced growth across all tested photoperiods under 25 µM O~2~.
 The 25 µM O~2~, 4 h photoperiod experiments under white LED light and were not performed due to time constraints.
 
-#### Low oxygen environment {.unnumbered}
-
-MIT9313 grew under 2.5 µM O~2~  particularly under blue LED light, albeit
-generally slower than under the parallel experiments at 25 µM O~2~  (Figure
-\@ref(fig:MIT9313PAR)).
-Growth estimates did show scatter among replicates, suggesting  2.5 µM O~2~  is near the tolerance limit for growth of MIT9313.
-Growth rates increased with longer photoperiods under blue
-light treatments under peak PAR of 90 µmol photons m^-2^ s^-1^ .
+MIT9313 grew under 2.5 µM O~2~  particularly under blue LED light, albeit generally slower than under the parallel experiments at 25 µM O~2~  (Figure \@ref(fig:MIT9313PAR)).
+Growth estimates showed scatter among replicates, suggesting  2.5 µM O~2~  is near the tolerance limit for growth of MIT9313.
+Growth rates increased with longer photoperiods under blue light treatments under peak PAR of 90 µmol photons m^-2^ s^-1^ .
 Growth  for MIT9313 under PAR of 180 µmol photons m^-2^ s^-1^ and blue light treatment decreased with increasing photoperiods with full growth inhibition under a 16 h photoperiod.
@@
 The GAM model in Figure \@ref(fig:MIT9313GAM) summarizes MIT9313 growth responses to red (A) or blue (B) peak PAR and photoperiod.
-Under 250 µM O~2~, Figure \@ref(fig:MIT9313GAM)A shows MIT9313 achieves
-fastest growth rates between blue peak PAR of 30 µmol photons m^-2^
-s^-1^ and 50 µmol photons m^-2^ s^-1^ and photoperiods longer than 8 h,
-indicated by the contour line labeled 0.51 d^-1^ representing the
-90^th^ percentile of achieved growth rates. Figure
-\@ref(fig:MIT9313GAM)A also shows that growth rate increases
-with longer photoperiods, as long as the blue peak PAR levels remain below 50 µmol
-photons m^-2^ s^-1^.  In contrast, under red light and 250 µM O~2~ MIT9313 grows faster while exploiting higher peak PAR and longer photoperiods.  Figure \@ref(fig:MIT9313GAM)C
-shows that MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 4 and 8 h and peak blue PAR between 50 to 10 µmol photons m^-2^ s^-1^ PAR (Figure \@ref(fig:MIT9313GAM)C).
+Under 250 µM O~2~, Figure \@ref(fig:MIT9313GAM)A shows MIT9313 achieves fastest growth rates between blue peak PAR of 30 µmol photons m^-2^ s^-1^ and 50 µmol photons m^-2^ s^-1^ and photoperiods longer than 8 h, indicated by the contour line labeled 0.51 d^-1^ representing the 90^th^ percentile of achieved growth rates.
+Figure \@ref(fig:MIT9313GAM)A also shows that growth rate increases with longer photoperiods, as long as the blue peak PAR levels remain below 50 µmol photons m^-2^ s^-1^.
+In contrast, under red light and 250 µM O~2~ MIT9313 grows faster while exploiting higher peak PAR and longer photoperiods.
+Figure \@ref(fig:MIT9313GAM)C shows that MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 4 and 8 h and peak blue PAR between 50 to 10 µmol photons m^-2^ s^-1^ PAR (Figure \@ref(fig:MIT9313GAM)C).
 Thus the designation of MIT9313 as a LL clade is dependent upon [O2] and light spectra.
 (Figure \@ref(fig:MIT9313GAM)B).
-
-The LLIV clade, *P. marinus* MIT9313, exploited all tested photoperiods,
-and showed increasing growth rate with increasing photoperiods. Hence,
-MIT9313 can potentially inhabit temperate zones with shorter winter and
-longer summer photoperiods, and exploit habitats at depth subject to
-photoperiod attenuation.
-
-MIT9313, sometimes grew under all PAR levels but generally exhibited slower growth rate under PAR of 180 µmol photons m^-2^ s^-1^ and then only under some conditions.
-MIT9313 is well suited to inhabit the deep ocean in temperate zones with wide tolerance for photoperiod yet can also tolerate depths closer to the surface through its partial tolerance of higher PAR levels.
-
-MIT9313, under 250 µM O~2~ grew under all spectral wavebands when exposed to PAR of 30 µmol photons m^-2^ s^-1^ and 90 µmol photons m^-2^ s^-1^ and was even able to grow under PAR of 180 µmol photons
-m^-2^ s^-1^ for all spectral wavebands except blue light. MIT9313 can
-thus exploit blue light in deeper waters of temperate zones and can even
-tolerate moderate depths to exploit higher blue light levels, as long as
-the photoperiod is shorter than 12 h.
 
@@
 
-Cumulative diel absorbed PUR can potentially collapse photoperiod, PAR and spectral wavebands to a common metric of photosynthetically active light absorbed per day.
-Cumulative daily absorbed PUR dose (µmol photons m^-2^ d^-1^) was calculated from the imposed absorbed PUR (µmol photons m^-2^ s^-1^) and photoperiod (h).
+Cumulative diel PUR can potentially collapse photoperiod, PAR and spectral wavebands to a common metric of photosynthetically active light absorbed per day.
+Cumulative diel PUR dose (µmol photons m^-2^ d^-1^) was calculated from the imposed PUR (µmol photons m^-2^ s^-1^) and photoperiod (h).
 We plotted growth rates vs.
-cumulative diel absorbed PUR to determine whether growth is a simple response to diel PUR, across imposed photoperiods and spectral wavebands, or whether photoperiod or spectral wavebands have specific or interactive influences on growth.
+cumulative diel PUR to determine whether growth is a simple response to diel PUR, across imposed photoperiods and spectral wavebands, or whether spectral wavebands or photoperiods have specific or interactive influences on growth beyond cumulative diel PUR.
 
 Due to the absorption of *P.
-marinus* pigments in the blue spectral waveband range, the maximum imposed cumulative diel absorbed PUR under blue light is almost 3 times that of white LED light, and about 6 times the red light treatment, despite being derived from the same imposed photoperiods and peak PAR regimes.
+marinus* pigments in the blue spectral waveband range, the maximum imposed cumulative diel PUR under blue light is almost 3 times that of white LED light, and about 6 times the red light treatment, despite being derived from the same imposed photoperiods and peak PAR regimes.
 As such, only blue light experiments extend beyond cumulative diel PUR of ~ 2 x 10^6^ µmol photons m^-2^ d^-1^.
+This bias in the range of data leads to caution in comparing model fits of growth in response cumulative diel PUR under red, vs.
+blue, wavebands.
 
@@
 In parallel MED4 showed no growth under 2.5 µM O~2~, no matter the level of diel cumulative PUR.
-In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth was well described by a saturating response (REFERENCE for EQUATION) of growth to increasing cumulative diel PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:AllStrainPurFitsPlots)A), and no evidence of inhibition of growth at any achieved cumulative diel PUR.
-XXXXDISTINCT PHOTOPERIOD FITSXXXXX
+In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth under blue light was well described by a saturating response (REFERENCE for EQUATION) of growth to increasing cumulative diel blue PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:AllStrainPurFitsPlots)A), and no evidence of inhibition of growth at any achieved cumulative diel PUR.
+Under the 'artificial' growth treatment of red light, MED4 achieved more growth per unit diel cumulative PUR  \@ref(fig:AllStrainPurFitsPlots)A), consistent with [@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for growth under red light, for MED4, because red light provokes less photoinactivation of PSII, than equivalent levels of blue light.
+XXXXDISTINCT PHOTOPERIOD FITS REFER to SupplementalXXXXX
 
@@
 marinus* SS120 showed almost no growth under 2.5 µM O~2~ experiments.
-A majority of the 4 h photoperiod treatments did not grow under 250 µM O~2~ experiments, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments.
+Most 4 h photoperiod treatments of SS120 also did not grow under 250 µM O~2~, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments.
 SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ experiments(Figure \@ref(fig:AllStrainPurFitsPlots)B).
@@
 The onset of growth inhibition extended to higher cumulative diel PUR for cultures under 25 µM O~2~, showing that SS120 is partially protected from photoinhibition of growth by 25 µM O~2~.
+Under 25 µM O~2~ red light again generated more growth of SS120 per unit cumulative diel PUR, than did blue light, again consistent with lower cost of growth through lower photoinactivation under red light.
 XXXXDISTINCT PHOTOPERIOD FITSXXXXX
@@
 The LLIV clade representative, *P.
-marinus* MIT9313, showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR, with higher growth rates over a narrower plateau under 25 and 250 µM O~2~, compared to a wider, flatter response to cumulative diel PUR under 2.5 µM O~2~.
+marinus* MIT9313, showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR, with higher growth rates over a narrower plateau under 25 and 250 µM O~2~, compared to a wider, lower, flatter response to cumulative diel PUR under 2.5 µM O~2~.
 Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands.
@@
 Similarly, under 2.5 µM O~2~, MIT9313 grew more slowly, but only showed full growth inhibition above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:AllStrainPurFitsPlots)C).
+
+Our data support enhanced growth under conditions of low cumulative dielPUR and 660 nm (red) spectral bandwidth, as supported by [@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue wavebands.
+Interestingly, this protective effect of red light disappears for MIT9313 growing under 2.5 µM O~2~, possibly because photoinactivation is strongly suppressed under this low [O~2~].
 XXXXDISTINCT PHOTOPERIOD FITSXXXXX
-
-XXXXXCHECK WHEN MIREILLE ADDS Colour specific fitsXXX This inhibition initially suggested that blue wavebands triggered photoinhibition at significantly lower levels of Photosynthetically Active Radiation (PAR) compared to other spectral wavebands.
-However, considering the equivalent cumulative diel absorbed PUR of the blue waveband, all treatments including white LED, red, and blue waveband exhibited approximately the same growth saturation.
-XXXX
-
-Our data support enhanced growth under conditions of low cumulative diel  PUR and 660 nm (red) spectral bandwidth, as supported by [@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue wavebands.
 
@@
 
-The LLIII clade, *P. marinus* SS120 grew under both 250 µM
-and 25 µM O~2~ treatments. The growth responses under 250 µM and 25 µM
-O~2~ were very different under the higher PAR level treatments. As
-discussed in the spectral waveband section, SS120 did not grow when
-treated with 250 µM O~2~ under PAR of 90 and 180 µmol photons m^-2^
-s^-1^ blue light. However, SS120 did grow under the lower O~2~ of 25 µM,
-photoperiods of 4 and 8 h and PAR of 90 µmol photons m^-2^ s^-1^ blue
-light and photoperiods of 8 h and PAR of 180 µmol photons m^-2^ s^-1^
-blue light. Under 25 µM O~2~, SS120 grew under all tested white LED
-treatments however, did not grow under PAR of 30 µmol photons m^-2^
-s^-1^ and 4 h red light photoperiod nor under photoperiods longer than 8
-h when treated with PAR of 180 µmol photons m^-2^ s^-1^ red light.
-Beyond photoregimes expected of the deep ocean temperate zone waters,
-characterized by low levels of blue light and extended photoperiods,
-SS120 can also exploit regions closer to the surface where blue light
-PAR levels are higher, provided that the [O~2~] are low, as in the OMZ.
-Our laboratory results support field observations reported by
-@lavinNovelLineagesProchlorococcus2010 who found evidence of LLII/III
-and LLIV ecotypes, using terminal restriction fragment length
-polymorphism analyses, at depths above 40 m where light levels are
-higher in the OMZ. @mattisonPhotosyntheticStrategiesWild2020 found PSII
-protein subunits annotated as derived from SS120 at all depths ranging
-from 20 to 200 m and all [O~2~] in the oxygen minimal zone of the
-tropical North Pacific Ocean.
-
-The LLIV clade, *P. marinus* MIT9313, showed enhanced growth responses
-under the 25 µM O~2~ treatments for all tested spectral wavebands and
-even grew under the highest peak PAR level of 180 µmol photons m^-2^ s^-1^,
-in contrast to growth inhibition under 250 µM O~2~ and 180 µmol photons
-m^-2^ s^-1^. Most impressively, MIT9313 has the capacity to grow just as
-well, and in some conditions, even better, under high PAR levels of 90
-and 180 µmol photons m^-2^ s^-1^, as compared to the lowest PAR of 30
-µmol photons m^-2^ s^-1^, when treated with the lower O~2~ of 25 µM, for
-all spectral wavebands tested. Interestingly, while generally the growth
-rate were slower under the lowest imposed O~2~ of 2.5 µM compared to
-O~2~ of 25 µM, MIT9313 was able to grow under all blue light with
-photoperiods up to 12 h, along with growth under some
-combinations of red peak PAR, across photoperiods. Given that
-MIT9313 can grow under all photoperiods at the lowest blue light PAR of
-30 µmol photons m^-2^ s^-1^, all seasons in the temperate zones are
-potentially viable niches, if temperature rises into the Clade LLIV tolerance range.
-Like SS120, MIT9313 has the capability to exploit different ocean water layers through its tolerance of higher light levels under lower [O~2~].
-MIT9313 has a remarkable ability to thrive under very low [O~2~], potentially allowing it to expand into
-broader ecological niches. These results are supported by \@ref(fig:ProchloroPhotosynthDepthO2) showing PSI protein subunits
-annotated as derived from MIT9313 wdetected at depths \> 120 m, along with PSII subunits at depths from 50 m to 200 m in regions where
-O~2~ was 15 µM.
-
 Table \@ref(tab:NichesTable) summarizes our findings for potential growth niches, as defined by photoperiod, light level and oxygen level, characteristic of different seasons, depths, and oxygen zones.
@@
 
-*Prochlorococcus marinus* SS120, a LLIII clade representative, showed an interactive inhibition of growth by oxygen and cumulative diel PUR, with a higher tolerance for higher cumulative diel absorbed PUR under 25 µM O~2~, compared to 250 µM O~2~.
+*Prochlorococcus marinus* SS120, a LLIII clade representative, showed an interactive inhibition of growth by oxygen and cumulative diel PUR, with a higher tolerance for higher cumulative diel PUR under 25 µM O~2~, compared to 250 µM O~2~.
 Thus, SS120 can exploit habitats with O~2~ levels spanning 25 µM O~2~ to 250 µM O~2~, including high PAR environments within OMZ.
 SS120 is likely excluded from higher [O~2~] and higher PAR because of genomic limitations on capacity for DNA repair \@ref(fig:DNARepairFig), and possibly by limited capacity for synthesis of reactive oxygen quenchers  \@ref(fig:ProchlorococcusEnzymeKms).
+Our growth results are supported by @lavinNovelLineagesProchlorococcus2010 who found evidence of LLII/III
+and LLIV ecotypes, using terminal restriction fragment length polymorphism analyses, at depths above 40 m, where light levels are
+higher, within OMZ, and by \ref(fig:ProchloroPhotosynthDepthO2) showing PSII protein subunits annotated as derived from SS120 at all depths ranging
+from 20 to 200 m and all [O~2~] in an OMZ of the tropical North Pacific Ocean.
+SS120, grew under photoperiods longer than 4 h and showed increasing growth rate with increasing photoperiods.
+Therefore, SS120 can potentially exploit the longer summer photoperiods in temperate zones but again cannot sustain growth in winter through its requirement for more than 4 h of light per day, even if water temperature warms into the Clade LLIII tolerance range.
 
@@
 marinus* MIT9313 [@bonisteelStrainSpecificDifferences2018].
+MIT9313 shows remarkable ability to thrive under very low [O~2~], potentially allowing it to expand into broader ecological niches.
+These results are supported by \@ref(fig:ProchloroPhotosynthDepthO2) showing PSI protein subunits annotated as derived from MIT9313 detected at depths \> 120 m, along with PSII subunits at depths from 50 m to 200 m in regions where O~2~ was 15 µM.
 
@@
 MED4OverlayPlots_cap <- glue("**Normalized absorbance and Photosynthetically Usable Radiation for *Prochlorococcus marinus* MED4 grown under three emission wavebands.**",
-                       "**A.** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated absorbed PUR spectra (solid black line and shaded grey).",
-                       "**B.** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated absorbed PUR spectra (solid black line and shaded red).",
-                       "**C.**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated absorbed PUR spectra (solid black line and shaded blue).",
-
-                       "Actinic PAR (µmol photons m^-2^ s^-1^) and calculated absorbed PUR (µmol photons m^-2^ s^-1^) levels are indicated.",
+                       "**A.** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated PUR spectra (solid black line and shaded grey).",
+                       "**B.** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded red).",
+                       "**C.**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded blue).",
+
+                       "Actinic PAR (µmol photons m^-2^ s^-1^) and calculated PUR (µmol photons m^-2^ s^-1^) levels are indicated.",
 
@@
 SS120OverlayPlots_cap <- glue("**Normalized absorbance and Photosynthetically Usable Radiation for *Prochlorococcus marinus* SS120 grown under three emission wavebands.",
-                       "**A.** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated absorbed PUR spectra (solid black line and shaded grey).",
-                       "**B.** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated absorbed PUR spectra (solid black line and shaded red).",
-                       "**C.**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated absorbed PUR spectra (solid black line and shaded blue).",
-                       "Actinic PAR (µmol photons m^-2^ s^-1^) and calculated absorbed PUR (µmol photons m^-2^ s^-1^) levels are indicated.",
+                       "**A.** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated PUR spectra (solid black line and shaded grey).",
+                       "**B.** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded red).",
+                       "**C.**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded blue).",
+                       "Actinic PAR (µmol photons m^-2^ s^-1^) and calculated PUR (µmol photons m^-2^ s^-1^) levels are indicated.",
                        .sep = " ")
@@
 MIT9313OverlayPlots_cap <- glue("**Normalized absorbance and Photosynthetically Usable Radiation for *Prochlorococcus marinus* MIT9313 grown under three emission wavebands.**",
-                                "**A.** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated absorbed PUR spectra (solid black line and shaded grey).",
-                       "**B.** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated absorbed PUR spectra (solid black line and shaded red).",
-                       "**C.**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated absorbed PUR spectra (solid black line and shaded blue).",
-                       "Actinic PAR (µmol photons m^-2^ s^-1^) and calculated absorbed PUR (µmol photons m^-2^ s^-1^) levels are indicated.",
+                                "**A.** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated PUR spectra (solid black line and shaded grey).",
+                       "**B.** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded red).",
+                       "**C.**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded blue).",
+                       "Actinic PAR (µmol photons m^-2^ s^-1^) and calculated PUR (µmol photons m^-2^ s^-1^) levels are indicated.",
 

### 2024-02-23 Code/Manuscript_O2.Rmd
Fixed citations in intro

@@
 *P.
-marinus* comprises many strains, organized into clades, defined by 16S-23S intergenic transcribed ribosomal sequence signatures (Rocap et al., 2003).
+marinus* comprises many strains, organized into clades, defined by 16S-23S intergenic transcribed ribosomal sequence signatures [@rocapGenomeDivergenceTwo2003].
 The clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined by Low-Light (LL) or High-Light (HL).
@@
 Low-Light clades thrive in deeper ocean waters, extending beyond 200 m in depth [@partenskyProchlorococcusMarinePhotosynthetic1999], where only ~1% of the surface irradiance penetrates, primarily in the blue (450 nm) to green (520 nm) spectral range [@holtropVibrationalModesWater2021].
-Clade LLIV, including cultured strain MIT9313, falls near the base of the *Prochlorococcus* radiation, and is characterized by preference for low light, typical of depths from 120 m to 200 m (Partensky et al., 1999).
+Clade LLIV, including cultured strain MIT9313, falls near the base of the *Prochlorococcus* radiation, and is characterized by preference for low light, typical of depths from 120 m to 200 m [@partenskyProchlorococcusMarinePhotosynthetic1999].
 LLIV members are, as yet, the only cultured strains to have been found in Oxygen Minimum Zones (OMZ).
 Some as yet uncultured *P.
-marinus* strains in clades LLV and LLVI also thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021; @lavinNovelLineagesProchlorococcus2010; @goerickeNovelNicheProchlorococcus2000; @garcia-robledoCrypticOxygenCycling2017] (Johnson et al., 1999).
-*P.
-marinus* LL ecotypes may indeed dominate the phytoplankton within OMZ
+marinus* strains in clades LLV and LLVI also thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021; @lavinNovelLineagesProchlorococcus2010; @goerickeNovelNicheProchlorococcus2000; @garcia-robledoCrypticOxygenCycling2017; @johnsonEnergeticsGrowthKinetics1999].
+*Prochlorococcus marinus* LL ecotypes may indeed dominate the phytoplankton within OMZ
 [@lavinNovelLineagesProchlorococcus2010;
-@ulloaCyanobacteriumProchlorococcusHas2021; @partenskyProchlorococcusAdvantagesLimits2010], and may be net O~2~ consumers (2018, Partensky et al. 2018).
+@ulloaCyanobacteriumProchlorococcusHas2021; @partenskyProchlorococcusAdvantagesLimits2010], and may be net O~2~ consumers [@partenskyComparisonPhotosyntheticPerformances2018].
 
@@
 Current niches of *P. marinus* span ocean water columns
-[@chisholmNovelFreelivingProchlorophyte1988; @veldhuisVerticalDistributionPigment1990; @partenskyProchlorococcusMarinePhotosynthetic1999] and extend into regions with varying dissolved oxygen concentrations
-[@partenskyProchlorococcusAdvantagesLimits2010; @goerickeNovelNicheProchlorococcus2000] and even into anoxic oceans [@lavinNovelLineagesProchlorococcus2010], [@ulloaCyanobacteriumProchlorococcusHas2021; @garcia-robledoCrypticOxygenCycling2017].
+[ @veldhuisVerticalDistributionPigment1990; @chisholmNovelFreelivingProchlorophyte1988; @partenskyProchlorococcusMarinePhotosynthetic1999] and extend into regions with varying dissolved oxygen concentrations
+[@partenskyProchlorococcusAdvantagesLimits2010; @goerickeNovelNicheProchlorococcus2000] and even into anoxic oceans [@lavinNovelLineagesProchlorococcus2010, @ulloaCyanobacteriumProchlorococcusHas2021; @garcia-robledoCrypticOxygenCycling2017].
 
@@
 Predictions indicate a net global increase of *P.
-marinus* cell abundances of 29%, along with  poleward latitudinal shifts of at least 10° in marine phytoplankton niches by the end of this century [@flombaumPresentFutureGlobal2013][@bartonAnthropogenicClimateChange2016] in response to warming waters, with increases in *P.
+marinus* cell abundances of 29%, along with  poleward latitudinal shifts of at least 10° in marine phytoplankton niches by the end of this century [@flombaumPresentFutureGlobal2013; @bartonAnthropogenicClimateChange2016] in response to warming waters, with increases in *P.
 marinus* of approximately 50% in the more poleward regions of their distributions.
@@
 marinus* potentially expands its temperature-permissive niches poleward into temperate regions  [@flombaumPresentFutureGlobal2013; @bartonAnthropogenicClimateChange2016], it will encounter more
-pronounced seasonal variations in photoperiod regimes both at surface and at depth, with potentially complex effects upon viable growth niches @liDiatomGrowthResponses2017 @prezelinDielPeriodicityPhytoplankton1992.
-For example, @vaulotGrowthProchlorococcusPhotosynthetic1995 showed that *Prochlorococcus* replication of DNA occurs in the afternoon, while cell division occurs at night.
+pronounced seasonal variations in photoperiod regimes both at surface and at depth, with potentially complex effects upon viable growth niches [@liDiatomGrowthResponses2017; @prezelinDielPeriodicityPhytoplankton1992].
+For example, Vaulot et al.
+@vaulotGrowthProchlorococcusPhotosynthetic1995 showed that *Prochlorococcus* replication of DNA occurs in the afternoon, while cell division occurs at night.
 To our knowledge, no study has as yet addressed *P.
@@
 marinus* in samples tanken across a range of [O~2~] and depth, which in turn correlates to peak light at the site of sampling.
-We therefore analyzed the growth and physiological responses of representative strains from three clades ofr *P.
+We therefore analyzed the growth and physiological responses of representative strains from three clades of *P.
 marinus* under a matrix of [O~2~], light levels, spectral waveband ranges, and photoperiods, to approximate eco-physiological conditions representative of current and hypothetical future ocean zones.

### 2024-02-23 Code/Manuscript_O2.Rmd
Added Naaman's bioinformatic methods

@@
 pronounced seasonal variations in photoperiod regimes both at surface and at depth, with potentially complex effects upon viable growth niches [@liDiatomGrowthResponses2017; @prezelinDielPeriodicityPhytoplankton1992].
-For example, Vaulot et al.
-@vaulotGrowthProchlorococcusPhotosynthetic1995 showed that *Prochlorococcus* replication of DNA occurs in the afternoon, while cell division occurs at night.
+For example, Vaulot *et al*.
+(1995) @vaulotGrowthProchlorococcusPhotosynthetic1995 showed that *Prochlorococcus* replication of DNA occurs in the afternoon, while cell division occurs at night.
 To our knowledge, no study has as yet addressed *P.
@@
 	iii) Sample station depth and [O~2~].  
-	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using the Tidyverse package [@R-tidyverse] in RStudio v1.2.5019 (https://rstudio.com/)  (LOCATION OF CODE ON GITHUBO.
+	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using the Tidyverse package [@R-tidyverse] in RStudio v1.2.5019 (https://rstudio.com/)  (LOCATION OF CODE ON GITHUB).
 The resulting merged dataset was filtered for those *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b6f (Cytb6f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Terminal Oxidase (PTOX); plastocyanin (PC); ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  ATP Synthase;  FtsH proteases (FtsH) or ribosomes.
@@
 duration of the lag phase, if any. All data from the Multicultivator were saved
-as comma separated values file  (CITATION of FILES LOCATION).
+as comma separated values file  (https://github.com/FundyPhytoPhys/prochlorococcus_o2/tree/main/Data/RawData).
 
@@
 
-NAAMAN
+Using the dataset Omar *et al*.
+(2023) [@omarAnnotationGenesEncoding2023], we filtered the dataset for Enzyme Commission Numbers (EC numbers), or Kegg Orthology Numbers (KO numbers) identified by BRENDA  [@changBRENDAELIXIRCore2021] as 'natural substrates' for O~2~ in Prochlorococcus marinus (MED4, MIT9313, SS120, and NATL2A) in order to generate a subset containing only those orthologs encoding enzymes directly mediating O~2~ metabolism.
+We grouped orthologs together by EC number and their KO number (KO number) and determined the occurrences of individual orthologs encoding each EC number, or KO number when EC number was not available, in a given strain.
+We merged the dataset with a list of enzyme Michaelis constant (K~m~) values from other organisms, as K~m~ values from Prochlorococcus were only available in the case of Ribulose bisphosphate carboxylase.
+XXX Possibly add the link to the full list of genes.
+XXXX
 
@@
 
-## **Prochlorococcus* genomic capacities for electron dissipation and DNA repair
+## **Prochlorococcus* genomic capacities for electron dissipation and DNA repair {.unnumbered}
 

### 2024-02-23 Code/Manuscript_O2.Rmd
more edits

@@
   - name: '**Mireille Savoie**'
-    affil: 1
+    institute: mta
     main: true
@@
   - name: Aurora Mattison
-    affil: 1, 2
+    institute: [mta, ubc]
   - name: Julie Nadeau
-    affil: 1
+    institute: mta
   - name: Laurel Genge
-    affil: 1
+    institute: mta
   - name: Sylwia Śliwińska-Wilczewska
-    affil: 1
+    institute: [mta, other]
   - name: Maximilian Berthold
-    affil: 1, 3
+    institute: mta
   - name: Naaman Omar
-    affil: 1
+    institute: mta
   - name: Ondřej Prášil
-    affil: 1, 4
+    institute: [mta, algatech]
     main: false
   - name: Amanda M. Cockshutt
-    affil: 1, 5
+    institute: [mta, sfx]
     main: false
   - name: Douglas A. Campbell
+    institute: mta
     affil: 1
@@
   - mta: 'Department of Biology, Mount Allison University, 63B York St., Sackville NB, Canada, E4L 1G7.'
-  - num: 2
   - ubc: 'Department of Biology, University of British Columbia'
-  - num: 3
-  - umwelt: 'Umweltbundesamtm, Dessau-Roßlau, Germany'
-  - num: 4
-  - alga: 'Algatech, Czech Academy of Science'
-  - num: 5
   - sfx: 'Department of Chemistry, St. Frances Xavier University'
+  - algatech: 'Institute of Microbiology, Center Algatech, Laboratory of Photosynthesis, Novohradska 237, Trebon, CZ 37981, Czech Republic.'
+
 date: "`r format(Sys.Date())`"
@@
 where ΔOD~max~ is maximum ΔOD, ΔOD~min~ is minimum ΔOD, t is time
-duration over the growth trajectory.  Annotated code for data import, transformations and analyses is available at XXXXX 
-CITAtIONS of github locations of code etc. XXXXX
+duration over the growth trajectory.
+
+Figure \@ref(fig:deltaODLogGrowthPlot) is an example of chlorophyll specific
+growth estimates fitted from the high resolution ΔOD measurements for
+each tube in a Multicultivator. The residuals of the logistic growth
+curve fit are shown and the growth spectral waveband is plotted and
+illustrates the imposed PAR (µmol photons m^-2^ s^-1^) and photoperiod
+(h). Annotated code for data import, transformations and analyses is available at https://github.com/FundyPhytoPhys/prochlorococcus_o2/tree/main/Data/RawData
 
@@
 The applied photoperiods were delivered using the sine circadian light function of the PSI Multicultivator to simulate light exposure approximating sun rise through to sunset.
-The area under the sinusoidal curves is equivalent to the area of a triangular photoregime of equivalent photoperiod (Campbell, unpub), therefore the equation to determine the cumulative diel PUR (µmol photons m^-2^ d^-1^) is one half of the base (photoperiod) multiplied by the height (PUR) (equation \@ref(eq:SumPURDay)),
+The area under the sinusoidal curves is equivalent to the area of a triangular photoregime of equivalent photoperiod (Campbell, unpub), therefore the equation to determine the cumulative diel PUR (µmol photons m^-2^ d^-1^) is one half of the base (photoperiod) multiplied by the height (PUR) (Equation \@ref(eq:SumPURDay)),
 
@@
 No growth was observed under any imposed conditions under a 4 h photoperiod.
-The maximum growth rate (µ~max~) was `r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 180 uE blue light and 16 h photoperiod.
+The maximum growth rate (µ~max~) was `r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 180 µE blue light and 16 h photoperiod.
 
@@
 photoperiod was 16 h for each spectral waveband, across PAR levels (Figure \@ref(fig:MED4PAR)).
-The µ~max~ was `r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "25", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^  achieved under 180 µmol photons m^-2^ s^-1^ blue light and 16 h photoperiod.
+The µ~max~ was `r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "25", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ (Table.
+\@ref(tab:MaxGrowthTable)) achieved under 180 µmol photons m^-2^ s^-1^ blue light and 16 h photoperiod.
 The 4 h photoperiod
@@
 Under red light growth was generally slower but the pattern of growth responses to photoperiod and PAR was similar (Figure \@ref(fig:MED4GAM)A).
-Note the exclusion of MED4 from growth under 4 h photoperiod under both red and blue light \@ref(fig:MED4GAM).
+Note the exclusion of MED4 from growth under 4 h photoperiod under both red and blue light (Figure \@ref(fig:MED4GAM)).
 Under 25 µM O~2~ MED4 showed similar growth responses, but was excluded from both 4 and 8 h photoperiods.
-MED4 did not grow under 25 µM O~2~, so no GAM model was run.
+MED4 did not grow under 2.5 µM O~2~, so no GAM model was run.
 Considering the range of PAR levels, and spectral bands that MED4 can utilize, MED4 can inhabit not just shallow depths, where light levels are high, but also deeper regions, characterized by lower level of blue light, subject to the limitation of a photoperiod of more than 4 h, even after depth attenuation of light.
@@
 Growth rate decreased with longer photoperiods and showed growth inhibition at 12 and 16 h photoperiods under PAR of 180 µmol photons m^-2^ s^-1^  white, red or blue LED light.
-The µ~max~ was `r PURPARFits %>% filter(Strain == "SS120", WL == "WW", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^  achieved under 90 µmol photons m^-2^ s^-1^ white LED light and 16 h photoperiod.
+The µ~max~ was `r PURPARFits %>% filter(Strain == "SS120", WL == "WW", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ (Table.
+\@ref(tab:MaxGrowthTable)) achieved under 90 µmol photons m^-2^ s^-1^ white LED light and 16 h photoperiod.
 
@@
 
-The GAM model in Figure \@ref(fig:SS120GAM) summarizes growth responses of SS120 to red (A) or blue (B) peak PAR and photoperiod, across the 2 imposed oxygen concentrations.
-Under 250 µM O~2~, Figure \@ref(fig:SS120GAM)A showed highest growth rates below PAR of 50 µmol photons m^-2^ s^-1^ and photoperiods between 8 and 12 h, indicated by the contour line labeled 0.29 d^-1^ (representing the 90^th^ percentile of achieved growth rate).
+The GAM model in Figure \@ref(fig:SS120GAM) summarizes growth responses of SS120 to red (A,B) or blue (C,D) peak PAR and photoperiod, across the 2 imposed oxygen concentrations.
+Under 250 µM O~2~, Figure \@ref(fig:SS120GAM)C showed highest growth rates below PAR of 50 µmol photons m^-2^ s^-1^ and photoperiods between 8 and 12 h, indicated by the contour line labeled 0.19 d^-1^ (representing the 90^th^ percentile of achieved growth rate).
 Under 250 µM O~2~ SS120 is constrained to deeper ocean waters through its intolerance of higher blue PAR levels.
@@
 Growth rate patterns under red light were similar, although somewhat faster.
-In contrast, under 25 µM O~2~ and a photoperiod of 8 h SS120 exploited all blue peak PAR levels, achieving faster growth rates at a higher PAR of \~100 µmol photons m^-2^ s^-1^, indicated by the contour line labeled 0.5 d^-1^ (representing the 90^th^ percentile of achieved growth rate), out pacing the 90^th^ percentile fastest growth rates under 250 µM O~2~.
-Under red light and 25 µM O~2~ light SS120 grew across most conditions of peak PAR and photoperiod, achieving fastest growth under long photoperiods and peak PAR below 50 \~100 µmol photons m^-2^ s^-1^.
-Thus, the designation of SS120 as a LL strain is dependent upon the [O~2].
+In contrast, under 25 µM O~2~ and a photoperiod of 8 h SS120 exploited all blue peak PAR levels, achieving faster growth rates at a higher PAR of \~100 µmol photons m^-2^ s^-1^, indicated by the contour line labeled 0.4 d^-1^ (representing the 90^th^ percentile of achieved growth rate), out pacing the 90^th^ percentile fastest growth rates under 250 µM O~2~.
+Under red light and 25 µM O~2~ (Figure \@ref(fig:SS120GAM)B) SS120 grew across most conditions of peak PAR and photoperiod, achieving fastest growth under long photoperiods and peak PAR below 50 \~100 µmol photons m^-2^ s^-1^.
+Thus, the designation of SS120 as a LL strain is dependent upon the [O~2~].
 SS120 did not, however, grow reliably under tested conditions at 2.5 µM O~2~.
@@
 For MIT9313 under 25 µM O~2~ growth rate increased with increasing photoperiods for all spectral wavebands tested (Figure \@ref(fig:MIT9313PAR)), with the fastest overall growth rate for MIT9313 
-`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "25", Photoperiod == 16, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under peak PAR of 90 µmol photons m^-2^ s^-1^ and 16 h blue light photoperiod.
+`r PURPARFits %>% filter(Strain == "MIT9313", WL == "WW", O2_uM == "25", Photoperiod == 16, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under peak PAR of 90 µmol photons m^-2^ s^-1^ and 16 h white LED light photoperiod.
 In marked contrast to the 250 µM O~2~ growth experiments, MIT9313 grew when exposed to peak PAR of 180 µmol photons m^-2^ s^-1^ and blue light under all photoperiods except 16 h; additionally, white LED and red light treatments induced growth across all tested photoperiods under 25 µM O~2~.
@@
 The red light peak PAR of 180 µmol photons m^-2^ s^-1^ showed similar growth rates for 8 and 12 h photoperiods.
-The µ~max~ was `r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "2.5", Photoperiod == 4, Par_ue == 180) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 4 h blue light photoperiod and PAR of 180 µmol photons m^-2^ s^-1^.
-XXXXTHIS DOES NOT LOOK correct; 12 h, 90 uE photons blue light looks higher.
+The µ~max~ was `r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "2.5", Photoperiod == 12, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 12 h blue light photoperiod and PAR of 90 µmol photons m^-2^ s^-1^.
 The 2.5 µM O~2~ white LED treatments under 4, 8 and 16 h photoperiods and red light under 4 and 16 h photoperiods were not performed due to time constraints.
@@
 
-The GAM model in Figure \@ref(fig:MIT9313GAM) summarizes MIT9313 growth responses to red (A) or blue (B) peak PAR and photoperiod.
-Under 250 µM O~2~, Figure \@ref(fig:MIT9313GAM)A shows MIT9313 achieves fastest growth rates between blue peak PAR of 30 µmol photons m^-2^ s^-1^ and 50 µmol photons m^-2^ s^-1^ and photoperiods longer than 8 h, indicated by the contour line labeled 0.51 d^-1^ representing the 90^th^ percentile of achieved growth rates.
-Figure \@ref(fig:MIT9313GAM)A also shows that growth rate increases with longer photoperiods, as long as the blue peak PAR levels remain below 50 µmol photons m^-2^ s^-1^.
+The GAM model in Figure \@ref(fig:MIT9313GAM) summarizes MIT9313 growth responses to red (A,B,C) or blue (D,E,F) peak PAR and photoperiod.
+Under 250 µM O~2~, Figure \@ref(fig:MIT9313GAM)D shows MIT9313 achieves fastest growth rates between blue peak PAR of 30 µmol photons m^-2^ s^-1^ and 50 µmol photons m^-2^ s^-1^ and photoperiods longer than 8 h, indicated by the contour line labeled 0.52 d^-1^ representing the 90^th^ percentile of achieved growth rates.
+Figure \@ref(fig:MIT9313GAM)D also shows that growth rate increases with longer photoperiods, as long as the blue peak PAR levels remain below 50 µmol photons m^-2^ s^-1^.
 In contrast, under red light and 250 µM O~2~ MIT9313 grows faster while exploiting higher peak PAR and longer photoperiods.
-Figure \@ref(fig:MIT9313GAM)C shows that MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 4 and 8 h and peak blue PAR between 50 to 10 µmol photons m^-2^ s^-1^ PAR (Figure \@ref(fig:MIT9313GAM)C).
-Thus the designation of MIT9313 as a LL clade is dependent upon [O2] and light spectra.
-(Figure \@ref(fig:MIT9313GAM)B).
+Figure \@ref(fig:MIT9313GAM)F shows that MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 4 and 8 h and peak blue PAR between 50 to 10 µmol photons m^-2^ s^-1^ PAR.
+Thus the designation of MIT9313 as a LL clade is dependent upon [O~2~] and light spectra.
+(Figure \@ref(fig:MIT9313GAM)E).
 
@@
 
-# Summary and Conclusions {.unnumbered}
+# Summary and conclusions {.unnumbered}
 

### 2024-02-23 Code/Manuscript_O2.Rmd
Final knit

@@
   - algatech: 'Institute of Microbiology, Center Algatech, Laboratory of Photosynthesis, Novohradska 237, Trebon, CZ 37981, Czech Republic.'
-
 date: "`r format(Sys.Date())`"
 output:
+  bookdown::word_document2:
+    code_folding: show
+    reference_docx: KnitTemplate.docx
+    keep_md: yes
+    toc: FALSE
+    toc_depth: 6
+    fig_caption: yes
+    pandoc_args: 
+      - '--lua-filter=scholarly-metadata.lua'
+      - '--lua-filter=author-info-blocks.lua'
   bookdown::html_document2:
@@
     toc_float: TRUE
-    toc_depth: 6
-    fig_caption: yes
-    pandoc_args: 
-      - '--lua-filter=scholarly-metadata.lua'
-      - '--lua-filter=author-info-blocks.lua'
-  bookdown::word_document2:
-    code_folding: show
-    reference_docx: KnitTemplate.docx
-    keep_md: yes
-    toc: FALSE
     toc_depth: 6
@@
 In parallel MED4 showed no growth under 2.5 µM O~2~, no matter the level of diel cumulative PUR.
-In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth under blue light was well described by a saturating response (REFERENCE for EQUATION) of growth to increasing cumulative diel blue PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:AllStrainPurFitsPlots)A), and no evidence of inhibition of growth at any achieved cumulative diel PUR.
-Under the 'artificial' growth treatment of red light, MED4 achieved more growth per unit diel cumulative PUR  \@ref(fig:AllStrainPurFitsPlots)A), consistent with [@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for growth under red light, for MED4, because red light provokes less photoinactivation of PSII, than equivalent levels of blue light.
-XXXXDISTINCT PHOTOPERIOD FITS REFER to SupplementalXXXXX
+In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth under blue light was well described by a saturating response (REFERENCE for EQUATION) of growth to increasing cumulative diel blue PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A), and no evidence of inhibition of growth at any achieved cumulative diel PUR.
+Under the 'artificial' growth treatment of red light, MED4 achieved more growth per unit diel cumulative PUR  \@ref(fig:BluevsRedPurFitsPlots)A), consistent with [@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for growth under red light, for MED4, because red light provokes less photoinactivation of PSII, than equivalent levels of blue light.
+For distinct photoperiod fits refer to figure \@ref(fig:AllStrainPurFitsPlots)A.
 
@@
 Most 4 h photoperiod treatments of SS120 also did not grow under 250 µM O~2~, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments.
-SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ experiments(Figure \@ref(fig:AllStrainPurFitsPlots)B).
+SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ experiments(Figure \@ref(fig:BluevsRedPurFitsPlots)B).
 
@@
 Under 25 µM O~2~ red light again generated more growth of SS120 per unit cumulative diel PUR, than did blue light, again consistent with lower cost of growth through lower photoinactivation under red light.
-XXXXDISTINCT PHOTOPERIOD FITSXXXXX
+For distinct photoperiod fits refer to figure \@ref(fig:AllStrainPurFitsPlots)B.
 
@@
 In contrast, under 25 µM O~2~, MIT9313 showed a greatly extended exploitation of higher cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^.
-Similarly, under 2.5 µM O~2~, MIT9313 grew more slowly, but only showed full growth inhibition above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:AllStrainPurFitsPlots)C).
+Similarly, under 2.5 µM O~2~, MIT9313 grew more slowly, but only showed full growth inhibition above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:BluevsRedPurFitsPlots)C).
 
@@
 Interestingly, this protective effect of red light disappears for MIT9313 growing under 2.5 µM O~2~, possibly because photoinactivation is strongly suppressed under this low [O~2~].
-XXXXDISTINCT PHOTOPERIOD FITSXXXXX
+For distinct photoperiod fits refer to figure \@ref(fig:AllStrainPurFitsPlots)C.
 
@@
 Under full atmospheric [O~2~] and bluelight, LL clades of *Prochlorococcus* are restricted to growth under low light, in part because they suffer photoinhibition of Photosystem II (PSII) through several paths, including direct absorbance of UV or blue light, in parallel with generation of Reactive Oxygen Species (ROS) if the electron flow is slowed, [@aroPhotoinhibitionPhotosystemII1993], producing damaging singlet oxygen (^1^O~2~) [@aroPhotoinhibitionPhotosystemII1993; @soitamoPhotoinhibitionMarinePicocyanobacteria2017; @murphyPhotoinactivationPhotosystemII2017; @hakalaEvidenceRoleOxygenevolving2005].
-Repair of photoinactivated PSII relies on the removal of damaged PsbA (Mann et al., 2000; Adam et al., 2005), followed by reassembly with newly synthesized PsbA [@nixonRecentAdvancesUnderstanding2010].
-Degradation of PsbA is a rate-limiting step in recovery from photoinhibition (Kanervo et al., 1993), mediated largely by a heterohexamer of (FtsH12)3, a membrane-bound (Sacharz et al., 2015)(Zak et al., 2001) metalloprotease  (Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
-(Adam et al., 2005; Boehm et al., 2012) (Nixon et al.
-(2010)) (Komenda et al., 2007).
-(Pisareva et al., 2007; Sacharz et al., 2015),  (Mann et al., 2000), (AMANDA REF from ALGATECH).
+Repair of photoinactivated PSII relies on the removal of damaged PsbA [@mannInvolvementFtsHHomologue2000; @adamFtsHProteasesChloroplasts2005], followed by reassembly with newly synthesized PsbA [@nixonRecentAdvancesUnderstanding2010].
+Degradation of PsbA is a rate-limiting step in recovery from photoinhibition [@kanervoD1ProteinDegradation1993], mediated largely by a heterohexamer of (FtsH12)3, a membrane-bound (Sacharz et al., 2015)(Zak et al., 2001) metalloprotease  (Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
+[@adamFtsHProteasesChloroplasts2005; @boehmSubunitOrganizationSynechocystis2012a; @nixonRecentAdvancesUnderstanding2010; @komendaExposedNTerminalTail2007] (Pisareva et al., 2007; Sacharz et al., 2015),  @mannInvolvementFtsHHomologue2000, (AMANDA REF from ALGATECH).
 
@@
 But only MED4 shows detected presence of the FtsH1 & FtsH2 isoforms inferred to mediate PSII repair, and then only in near-surface samples subject to higher light.
-Furthermore, even though MIT9313 grows \@ref(fig:MIT9313GAM), and is detected in the ocean at low [O~2~] \ref@(fig:ProchloroPhotosynthDepthO2), no  FtsH from MIT9313 is detected at low [O~2~], showing limited requirement for protein turnover under low [O~2~].
+Furthermore, even though MIT9313 grows (Figure \@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~] (Figure \@ref(fig:ProchloroPhotosynthDepthO2)), no  FtsH from MIT9313 is detected at low [O~2~], showing limited requirement for protein turnover under low [O~2~].
 
@@
 
-## **Prochlorococcus* genomic capacities for electron dissipation and DNA repair {.unnumbered}
+## *Prochlorococcus* genomic capacities for electron dissipation and DNA repair {.unnumbered}
 
@@
 
-Table \@ref(tab:NichesTable) summarizes our findings for potential growth niches, as defined by photoperiod, light level and oxygen level, characteristic of different seasons, depths, and oxygen zones.
 The potential for niche expansion into temperate regions by *P.
@@
 MED4 can, however, grow under OMZ regions with slightly higher [O~2~], as by the growth under our 25 µM O~2~ experiments.
-Genomic analyses  \@ref(fig:ProchlorococcusEnzymeKms)  and previous transcriptional analyses [@bergResponsesPsbAHli2011]  suggests MED4 is excluded from growth below ~ 25 µM O~2~ because it relies upon a ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction balance in the intersystem electron transport chain.
+Genomic analyses  ( Figure \@ref(fig:ProchlorococcusEnzymeKms))  and previous transcriptional analyses [@bergResponsesPsbAHli2011]  suggests MED4 is excluded from growth below ~ 25 µM O~2~ because it relies upon a ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction balance in the intersystem electron transport chain.
 On the other hand, MED4 shows inducible expression of FtsH isoforms [@bonisteelStrainSpecificDifferences2018], to counter photoinactivation of PSII under higher PAR and [O~2] environments.
@@
 @delmontLinkingPangenomesMetagenomes2018 did not analyze data from depths beyond the subsurface chlorophyll maximum layer, the layer in the water column where the chlorophyll a concentration peaks, nor did they report the [O~2~] at those depths.
-Our growth findings are also consistent with Figure \@ref(fig:ProchloroPhotosynthDepthO2) showing PSII proteins annotated as MED4, at depths up to 200 meters with O~2~ of 15 µM.
+Our growth findings are also consistent with Figure\@ref(fig:ProchloroPhotosynthDepthO2) showing PSII proteins annotated as MED4, at depths up to 200 meters with O~2~ of 15 µM.
 
@@
 Thus, SS120 can exploit habitats with O~2~ levels spanning 25 µM O~2~ to 250 µM O~2~, including high PAR environments within OMZ.
-SS120 is likely excluded from higher [O~2~] and higher PAR because of genomic limitations on capacity for DNA repair \@ref(fig:DNARepairFig), and possibly by limited capacity for synthesis of reactive oxygen quenchers  \@ref(fig:ProchlorococcusEnzymeKms).
+SS120 is likely excluded from higher [O~2~] and higher PAR because of genomic limitations on capacity for DNA repair (Figure \@ref(fig:DNARepairFig)), and possibly by limited capacity for synthesis of reactive oxygen quenchers (Figure  \@ref(fig:ProchlorococcusEnzymeKms)).
 Our growth results are supported by @lavinNovelLineagesProchlorococcus2010 who found evidence of LLII/III
 and LLIV ecotypes, using terminal restriction fragment length polymorphism analyses, at depths above 40 m, where light levels are
-higher, within OMZ, and by \ref(fig:ProchloroPhotosynthDepthO2) showing PSII protein subunits annotated as derived from SS120 at all depths ranging
+higher, within OMZ, and by Figure\ref(fig:ProchloroPhotosynthDepthO2) showing PSII protein subunits annotated as derived from SS120 at all depths ranging
 from 20 to 200 m and all [O~2~] in an OMZ of the tropical North Pacific Ocean.
@@
 The ability to utilize higher PAR and higher cumulative diel PUR under 25 µM or 2.5 µM O~2~ enables MIT9313 to grow in OMZ, even at depths closer to the surface.
-MIT9313 carries a gene encoding (S)-2-hydroxy-acid oxidase [@InformationEC15],  with a K~M~ for [O~2~] of ~ 250 µM \@ref(fig:ProchlorococcusEnzymeKms), which produces H~2~O~2~.
+MIT9313 carries a gene encoding (S)-2-hydroxy-acid oxidase [@InformationEC15],  with a K~M~ for [O~2~] of ~ 250 µM (Figure \@ref(fig:ProchlorococcusEnzymeKms)), which produces H~2~O~2~.
 Growth at lower [O~2~] may protect MIT9313 from auto-intoxication from production of H~2~O~2~.
@@
 MIT9313 shows remarkable ability to thrive under very low [O~2~], potentially allowing it to expand into broader ecological niches.
-These results are supported by \@ref(fig:ProchloroPhotosynthDepthO2) showing PSI protein subunits annotated as derived from MIT9313 detected at depths \> 120 m, along with PSII subunits at depths from 50 m to 200 m in regions where O~2~ was 15 µM.
+These results are supported by Figure \@ref(fig:ProchloroPhotosynthDepthO2) showing PSI protein subunits annotated as derived from MIT9313 detected at depths \> 120 m, along with PSII subunits at depths from 50 m to 200 m in regions where O~2~ was 15 µM.
 

### 2024-02-26 Code/Manuscript_O2.Rmd
added page breaks
Fixed caption not being knitted to WORD for protein figures

@@
 
+\newpage
+
 ```{r ProchloroProteinMetabDepthO2, fig.cap = ProchloroProteinMetabDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
@@
 XXXX Mireille to finish Fig. caption when figure is complete. Add color ? Remove []? XXX
+
 ```{r  MED4ProteinAnnotated, fig.cap = MED4ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
 
-MED4ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade).**",
-
+MED4ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade.  **",
                                     "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",
                                     "Numbers over each bar are fmole target protein per ug total protein.",
-
                                     .sep = " ")
@@
 knitr::include_graphics(file.path(FiguresIn, "MED4ProteinAnnotated.png"))
+
 ```
@@
 XXXX Mireille to finish Fig. caption when figure is complete. Add color ? Remove []? XXX
+
 ```{r  MIT9313ProteinAnnotated, fig.cap = MIT9313ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
@@
                                     "Numbers over each bar are fmole target protein per ug total protein.",
-
                                     .sep = " ")
@@
 knitr::include_graphics(file.path(FiguresIn, "MIT9313ProteinAnnotated.png"))
-```
-
-\newpage
-
-## *Prochlorococcus* genomic capacities for electron dissipation and DNA repair {.unnumbered}
+
+```
+
+\newpage
 
@@
 
+\newpage
+
 ```{r ProchlorococcusEnzymeKms, fig.cap = ProchlorococcusEnzymeKms_cap, fig.height = 15, fig.width = 15, echo = FALSE}

### 2024-02-26 Code/Manuscript_O2.Rmd
Added Sylwia's Poland affliliation

@@
   - name: Sylwia Śliwińska-Wilczewska
-    institute: [mta, other]
+    institute: [mta, ug]
   - name: Maximilian Berthold
@@
   - algatech: 'Institute of Microbiology, Center Algatech, Laboratory of Photosynthesis, Novohradska 237, Trebon, CZ 37981, Czech Republic.'
+  - ug: 'Institute of Oceanography, University of Gdansk, 46 Piłsudskiego St, Gdynia, Poland'
 date: "`r format(Sys.Date())`"

### 2024-02-26 Code/Manuscript_O2.Rmd
changed proxy to specific for deltaODLogGrowthPlot

@@
 
-deltaODLogGrowthPlot_cap <- glue("**Fitting chlorophyll proxy growth rate for each tube in the Multicultivator.**",
+deltaODLogGrowthPlot_cap <- glue("**Fitting chlorophyll specific growth rate for each tube in the Multicultivator.**",
                       "The left y-axis is $\\Delta$OD (OD680 - OD720).",

### 2024-02-26 Code/Manuscript_O2.Rmd
Add OPP citation

@@
 @ulloaCyanobacteriumProchlorococcusHas2021; @partenskyProchlorococcusAdvantagesLimits2010], and may be net O~2~ consumers [@partenskyComparisonPhotosyntheticPerformances2018].
-
 Clades LLII and LLIII are grouped together as the second oldest phylogenetic lineages diversifying in the *P.
 marinus* radiation, and share an affinity for low light; LLIII cultured strain SS120, was isolated from 135 m depth in the Sargasso Sea.
-
-Clade LLI  includes cultured strains NATL1A and NATL2A, which prefer moderate irradiances typical between 30 and 100 m depth.
+Clade LLI  includes cultured strain NATL2A, which prefers moderate irradiance typically between 30 and 100 m depth.
 
@@
 
-We used the OceansMap Protein Portal (OPP; https://proteinportal.whoi.edu/) to analyze the distribution of proteins from clades of *P.
+We used the OceansMap Protein Portal (OPP; https://proteinportal.whoi.edu/) [@saitoDevelopmentOceanProtein2021] to analyze the distribution of proteins from clades of *P.
 marinus* in samples tanken across a range of [O~2~] and depth, which in turn correlates to peak light at the site of sampling.
@@
 
-The OceansMap Protein Portal (OPP; https://proteinportal.whoi.edu/) is an open access online data repository (Woods Hole Oceanographic Institute, WHOI) of mass spectroscopy data on marine microbial peptides, sampled from various depths and locations worldwide.
+The OceansMap Protein Portal is an open access online data repository (Woods Hole Oceanographic Institute, WHOI) of mass spectroscopy data on marine microbial peptides, sampled from various depths and locations worldwide [@saitoDevelopmentOceanProtein2021].
 We screened a subset of the OPP for proteins annotated as from *Prochlorococcus* strains, to identify differential strategies employed by strains living at varying depths and oxygen levels within the marine water column.

### 2024-02-26 Code/Manuscript_O2.Rmd
text edits

@@
 @ulloaCyanobacteriumProchlorococcusHas2021; @partenskyProchlorococcusAdvantagesLimits2010], and may be net O~2~ consumers [@partenskyComparisonPhotosyntheticPerformances2018].
+Clade LLI includes cultured strain NATL2A, which prefers moderate irradiance typically between 30 and 100 m depth.
 Clades LLII and LLIII are grouped together as the second oldest phylogenetic lineages diversifying in the *P.
-marinus* radiation, and share an affinity for low light; LLIII cultured strain SS120, was isolated from 135 m depth in the Sargasso Sea.
-Clade LLI  includes cultured strain NATL2A, which prefers moderate irradiance typically between 30 and 100 m depth.
+marinus* radiation, and share an affinity for low light.
 
@@
 High-Light clades are typically dominant picophytoplankters in near-surface, oligotrophic waters, characterized by high light levels.
-Clade HLI, including cultured strain MED4,is adapted to higher iron, and lower temperatures, and originated from the Mediterranean Sea, just 5 m below the surface [@partenskyProchlorococcusMarinePhotosynthetic1999].
+Clade HLI is adapted to higher iron, and lower temperatures, and originated from the Mediterranean Sea, just 5 m below the surface [@partenskyProchlorococcusMarinePhotosynthetic1999].
 Clade HLII adapted to higher iron, and higher temperatures, is the most abundant *P.
@@
 Near the equator, photoperiod remains relatively constant at the ocean surface, approximately 12 hours (h) of daylight and 12 h of darkness throughout the year.
-The effective length of the photoperiod does, however attentuate with depth as dawn and dusk light at depth drops below the level needed for biological processes.
+The effective length of the photoperiod does, however attenuate with depth as dawn and dusk light at depth drops below the level needed for biological processes.
 As *P.

### 2024-02-26 Code/Manuscript_O2.Rmd
added clade to captions for OceanProtein figures

@@
                        "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
-                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4, SS120 and MIT9313.",
+                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4 (Clade HLI), SS120 (Clade LLIII) and MIT9313 (Clade LLIV).",
                        "Columns show detections of proteins annotated as  Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
@@
                        "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
-                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4, SS120 and MIT9313.",
+                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4 (Clade HLI), SS120 (Clade LLIII) and MIT9313 (Clade LLIV).",
                        "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome).",

### 2024-02-26 Code/OceanProteinPlots.Rmd
added clade to captions for OceanProtein figures

@@
   ggplot() +
-  geom_point(aes(color=clade, x = O2, y= depth)) +
+  geom_point(aes(x = O2, y= depth)) +
   scale_x_continuous(limits = c(0, 260)) +

### 2024-02-26 Code/ManuscriptFigures.Rmd
text edits
Joined 3 overlay plots to 1

@@
    #                  labeller = labeller(Tube = label_both, WL_label = label_value, WL = label_value, Strain = label_value, OxygenLabel_title = label_value,Oxygen_label = label_value, OxygenLabel = label_value, Photoperiod = label_both, Par_label = label_value))+
-   ggh4x::facet_nested(cols = vars(PhotoLabel, Oxygen_label, Tube, SampleID,  Strain, WL_label, Par_label), 
+   ggh4x::facet_nested(cols = vars(PhotoLabel, Oxygen_label, Tube,   Strain, WL_label, Par_label), 
                     labeller = labeller(Tube = label_both, WL_label = label_value, WL = label_value, Strain = label_value, OxygenLabel_title = label_value,Oxygen_label = label_value, OxygenLabel = label_value, Photoperiod = label_both, Par_label = label_value, SampleID = label_value))+
@@
 
+# Overlay whole cell absorbance with emission spectra all strain together
+```{r MED4 All Spectral Emission,  fig.height = 10, fig.width = 10}
+
+MyWavelengths = c("WW", 660, 450)
+OverlayColours = c("black", w_length2rgb(660),  w_length2rgb(450))
+
+names(OverlayColours) <- MyWavelengths
+OverlayColours
+
+OverlayPlots <- PURPARFits %>%
+  filter(WL %in% c("WW", "660", "450")) %>% 
+  mutate(keep = case_when(Strain == "MED4" &  Par_ue == 30 & O2_Category == "High" & WL == 450  ~ 1,
+          Strain == "MED4" &  Par_ue == 30  & WL == "WW"  ~ 1, 
+          Strain == "MED4" &  Par_ue == 30 & WL == "660"& Run == 109 ~ 1,
+          Strain == "MIT9313" & O2_Category == "High" & Par_ue == 30 & Photoperiod == 12 & WL == 450  ~ 1,
+          Strain == "MIT9313" & O2_Category == "High" & Par_ue == 30 & Photoperiod == 12 & WL == 530  ~ 1,
+          Strain == "MIT9313" & O2_Category == "High" & Par_ue == 30 & Photoperiod == 12 & WL == 660  ~ 1,
+          Strain == "MIT9313" & O2_Category == "High" & Par_ue == 30 & Photoperiod == 16 & WL == "WW"  ~ 1,
+          Strain == "SS120" & O2_Category == "High" & Par_ue == 30 & Photoperiod == 8 ~ 1,
+          # Strain == "SS120" & O2_Category == "High" & Par_ue == 30 & Photoperiod == 12 & WL == 530 ~ 1,
+          TRUE ~ 0)) %>% 
+  filter(keep == 1, Run != 113,
+         Run != 112) %>% 
+  mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste("Growth", "Waveband",  WL, "nm", sep = " "),
+        WL %in% c("WW") ~ paste("Growth", "Waveband", "White LED", sep = " ")),
+        Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
+        WL_label = factor(WL_label, levels = c("Growth Waveband White LED", "Growth Waveband 660 nm", "Growth Waveband 450 nm"))) %>% 
+   unnest(cols = c(PurData), names_sep = "_", keep_empty = TRUE) %>%
+  pivot_longer(cols = c(PurData_PURAbsWholeCell_Norm440, PurData_AbsNorm440,  PurData_MC_NormEm), values_to = "Abs_Em_Value", names_to = "Abs_Em_Names") %>%
+ggplot()+
+  geom_area(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, fill = as.factor(WL)), color = "black", 
+            size = 0.5, alpha = 0.7, show.legend = FALSE, 
+            data = . %>% filter(Abs_Em_Names == "PurData_PURAbsWholeCell_Norm440")) +
+  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = Abs_Em_Names,  linetype = Abs_Em_Names), size = 0.85) +
+  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = as.factor(WL),  linetype = Abs_Em_Names), size = 1.0, data = . %>% filter(Abs_Em_Names == "PurData_MC_NormEm")) +
+  scale_color_manual(values = c(MCMIXColours, "PurData_PURAbsWholeCell_Norm440" = "black", "PurData_AbsNorm440" = "darkorchid3", "PurData_MC_NormEm" = "white")) +
+  scale_linetype_manual(values = c("PurData_PURAbsWholeCell_Norm440" = "solid", "PurData_AbsNorm440" = "twodash",  "PurData_MC_NormEm" = "dotted"),
+                        labels = c("Whole cell abs.",  "LED emission", "PUR")) +
+  scale_fill_manual(values = MCMIXColours) +
+ # guides(colour = FALSE) +
+  labs(y = "Normalized Absorbance and Emission", x = "Wavelength (nm)") +
+  labs(linetype = "Spectra Type")+
+  scale_y_continuous(breaks=seq(0, 1.5, by = 0.25)) +
+ # coord_cartesian(ylim = c (0, 0.2)) +
+   facet_grid(rows = vars(WL_label),
+              cols = vars(Strain),
+              labeller = labeller(Strain = label_value, WL_label = label_value, Photoperiod = label_both, Par_ue = label_both, O2_Category = label_both, Pur_ue = label_both)) +
+   geom_text(aes(x = 500, y = 1, label = paste("PAR", "=", Par_ue, "µE",sep = " "), show.legend = FALSE, ),
+    # parse = TRUE,
+    hjust = 0,
+    vjust = 1,
+    size = 5.0
+  )  +
+  geom_text(aes(x = 500, y = 0.90, label = paste("PUR", "=", Pur_ue, "µE", sep = " "), show.legend = FALSE, ),
+    # parse = TRUE,
+    hjust = 0,
+    vjust = 1,
+    size = 5.0
+  )  +
+  guides(color = "none") +
+  theme_bw() +
+ theme(#strip.text = element_blank(),
+       # legend.background = element_rect(color = "transparent", fill = "transparent"),
+      legend.key.size = unit(1, 'cm'), #change legend key size
+        legend.text = element_text(size = 18),
+        legend.title = element_text(size = 20),
+        # legend.position = c(0.94,0.96),
+        legend.position = "top",
+        axis.title = element_text(vjust = 1.0, size = 20),
+        # strip.text.x = element_text(size = 20),
+        axis.text = element_text(size = 15, color = "black"))
+
+# OverlayPlots <- tag_facet(OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
+
+OverlayPlots
+
+TEST <- PURPARFits %>% 
+  filter(Strain == "MED4", WL == 660, )
+
+```
+
+```{r save allinone overlay plot}
+
+ggsave(file = file.path(PlotsOut, paste("OverlayPlots",".png",sep = "")), plot = OverlayPlots, device = NULL, scale = 1, height = 25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+ggsave(file = file.path(PlotsOut, paste("OverlayPlots",".tiff",sep = "")), plot = OverlayPlots, device = NULL, scale = 1, height = 25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+```
+
 # Overlay whole cell absorbance with emission spectra
@@
 
-ggsave(file = file.path(PlotsOut, paste("MED4OverlayPlots",".png",sep = "")), plot = MED4OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsOut, paste("MED4OverlayPlots",".png",sep = "")), plot = MED4OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
 
-ggsave(file = file.path(PlotsOut, paste("MIT9313OverlayPlots",".png",sep = "")), plot = MIT9313OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsOut, paste("MIT9313OverlayPlots",".png",sep = "")), plot = MIT9313OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
 
-ggsave(file = file.path(PlotsOut, paste("SS120OverlayPlots",".png",sep = "")), plot = SS120OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsOut, paste("SS120OverlayPlots",".png",sep = "")), plot = SS120OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 

### 2024-02-26 Code/Process_OlisJazEmData.Rmd
Removed 1 MED4, red light , 30 uE from PUR calculation as it did not grow, skewed PUR results

@@
 OlisJazMetaPUR <- OlisJazMetaPUR %>%
+  filter(SampleID != "MiSa1364") %>% 
   group_by(Strain, WL, Par_ue) %>% 

### 2024-02-26 Code/ManuscriptFigures.Rmd
Changed 4hr photoperiod shape to solid square

@@
 MyPhotoperiods = as.factor(c(4, 8, 12, 16))
-PhotoperiodShapes = c(6, 18, 16, 17)
+PhotoperiodShapes = c(15, 18, 16, 17)
 
@@
    theme( strip.text = element_text(size = 20),
-       axis.title.x.bottom = element_text(size = 30, color = "black", vjust = 1.0),
-      axis.title.y = element_text(size = 30, color = "black", vjust = 1.0),
+       axis.title.x.bottom = element_text(size = 28, color = "black", vjust = 1.0),
+      axis.title.y = element_text(size = 28, color = "black", vjust = 1.0),
        axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
@@
    theme( strip.text = element_text(size = 20),
-       axis.title.x.bottom = element_text(size = 30, color = "black", vjust = 1.0),
-      axis.title.y = element_text(size = 30, color = "black", vjust = 1.0),
-       axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
+       axis.title.x.bottom = element_text(size = 28, color = "black", vjust = 1.0),
+      axis.title.y = element_text(size = 28, color = "black", vjust = 1.0),
+       # axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
        axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
@@
    theme( strip.text = element_text(size = 20),
-       axis.title.x.bottom = element_text(size = 30, color = "black", vjust = 1.0),
-       axis.title.y = element_text(size = 30, color = "black", vjust = 1.0),
+       axis.title.x.bottom = element_text(size = 28, color = "black", vjust = 1.0),
+       axis.title.y = element_text(size = 28, color = "black", vjust = 1.0),
        axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
@@
           Strain == "MED4" &  Par_ue == 30  & WL == "WW"  ~ 1, 
-          Strain == "MED4" &  Par_ue == 30 & WL == "660"& Run == 109 ~ 1,
+          Strain == "MED4" &  Par_ue == 30 & WL == "660"& Run == 99 ~ 1,
           Strain == "MIT9313" & O2_Category == "High" & Par_ue == 30 & Photoperiod == 12 & WL == 450  ~ 1,

### 2024-02-26 Code/Manuscript_O2.Rmd
Knitted

@@
     toc: FALSE
-    toc_depth: 6
-    fig_caption: yes
-    pandoc_args: 
-      - '--lua-filter=scholarly-metadata.lua'
-      - '--lua-filter=author-info-blocks.lua'
-  bookdown::html_document2:
-    code_folding: show
-    keep_md: yes
-    toc: TRUE
-    toc_float: TRUE
     toc_depth: 6

### 2024-02-27 Code/ManuscriptFigures.Rmd
Fixed legend transparency in colors

@@
   ggplot() +
-  geom_point(aes(x = Par_ue, y = Pur_ue, colour = as.factor(WL)), size = 3, alpha = 0.5) +
+  geom_point(aes(x = Par_ue, y = Pur_ue, colour = as.factor(WL)), size = 3, alpha = 1.0) +
  geom_line(aes(x = Par_ue, y = Pur_ue,colour = as.factor(WL)), linewidth = 0.7) +
@@
 ggsave(file = file.path(PlotsOut, paste("PurParPlot",".png",sep = "")), plot = PurParPlot, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-```
-
-```{r PUR per day, fig.height= 10, fig.width= 10 }
-
-scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
-
-# MED4NoPhotoPUR <- PURPARFits %>%
-PURPARFits %>%
-   filter(Strain == "MED4", 
-         Par_ue %in% c(30,90,180)) %>%
-   mutate(PhotoperiodLabel_title = "Photoperiod (h)",
-         OxygenLabel = "Oxygen Concentration (µM)",
-         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
-  ggplot() +
-  geom_point(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
-    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.5, alpha = 0.8) +
- labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
-scale_x_continuous(label=scientific_10) +
-   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660","530", "450" )) +
-   scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
-                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
- guides(linetype = "none",
-        fill = "none",
-        colour = guide_legend(ncol = 4)) +
- guides(shape = guide_legend(nrow = 1)) +
-  theme_bw() +
-   theme( strip.text = element_text(size = 30),
-        axis.title = element_text(size = 30, color = "black"),
-        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
-        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
-        strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"),
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title =  element_text(size = 20),  #change legend title font size
-        legend.text = element_text(size = 20),   #change legend text font size
-        legend.position = "top") +
-  labs(color = "Growth Waveband (nm)",
-       shape = "Photoperiod (h)")
-
-# MED4NoPhotoPUR
-
-# SS120NoPhotoPUR <- PURPARFits %>%
-PURPARFits %>%
-   filter(Strain == "SS120", 
-           Par_ue %in% c(30,90,180)) %>%
-   mutate(PhotoperiodLabel_title = "Photoperiod (h)",
-         OxygenLabel = "Oxygen Concentration (µM)",
-         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
-  ggplot() +
-  geom_point(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
-    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.5, alpha = 0.8) +
- labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
-scale_x_continuous(label=scientific_10) +
-   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660","530", "450" )) +
-   scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
-                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
- guides(linetype = "none",
-        fill = "none",
-        colour = guide_legend(ncol = 4)) +
- guides(shape = guide_legend(nrow = 1)) +
-  theme_bw() +
-   theme( strip.text = element_text(size = 30),
-        axis.title = element_text(size = 30, color = "black"),
-        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
-        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
-        strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"),
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title =  element_text(size = 20),  #change legend title font size
-        legend.text = element_text(size = 20),   #change legend text font size
-        legend.position = "top") +
-  labs(color = "Growth Waveband (nm)",
-       shape = "Photoperiod (h)")
-
-# SS120NoPhotoPUR
-
-# MIT9313NoPhotoPUR <- PURPARFits %>%
-   PURPARFits %>%
-     filter(Strain == "MIT9313", 
-          Par_ue %in% c(30,90,180)) %>%
-  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
-         OxygenLabel = "Oxygen Concentration (µM)",
-         Photoperiod = factor(Photoperiod, levels = c("16", "12", "8", "4" ))) %>%
-  ggplot() +
-  geom_point(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
-    geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.5, alpha = 0.8) +
- # geom_line(aes(x = PURPhotonDose_day, y = ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), linetype = as.factor(WL)), size = 0.5) +
- labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
-scale_x_continuous(label=scientific_10) +
-   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660","530", "450" )) +
-   scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
-                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
- guides(linetype = "none",
-        fill = "none",
-        colour = guide_legend(ncol = 4)) +
- guides(shape = guide_legend(nrow = 1)) +
-  theme_bw() +
-   theme( strip.text = element_text(size = 30),
-        axis.title = element_text(size = 30, color = "black"),
-        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
-        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
-        strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"),
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        legend.title =  element_text(size = 20),  #change legend title font size
-        legend.text = element_text(size = 20),   #change legend text font size
-        legend.position = "top") +
-  labs(color = "Growth Waveband (nm)",
-       shape = "Photoperiod (h)")
-
-# MIT9313NoPhotoPUR
-
-```
-
-```{r, save O2ColorPURPlots}
-
-# ggsave(file = file.path(PlotsOut, paste("MED4NoPhotoPUR",".png",sep = "")), plot = MED4NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-# 
-# ggsave(file = file.path(PlotsOut, paste("MIT9313NoPhotoPUR",".png",sep = "")), plot = MIT9313NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-# 
-# ggsave(file = file.path(PlotsOut, paste("SS120NoPhotoPUR",".png",sep = "")), plot = SS120NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
          OxygenLabel = "Oxygen~Concentration~(µM)",
-         WL_label_title = "Growth~Wavelength",
+         WL_label_title = "Growth~Wavelength~(nm)",
          ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
@@
   ggplot()  +
-  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 0.5) +
- geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5) +
-    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.5) +
+    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.75, show.legend = F) +
+   geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5, show.legend = F) +
+    geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 1) +
  labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
-   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3) +
+   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3, show.legend = F) +
   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
   # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm", "450 nm" )) +
+  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
    scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
@@
         legend.position = "top") +
-  labs(color = "Growth Wavelength",
-       fill = "Growth Wavelength")
+  labs(color = "Growth Wavelength (nm)",
+       fill = "Growth Wavelength (nm)")
 MED4PAR
@@
   ggplot() +
-  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 0.5) +
- geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5) +
-    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.5) +
+    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.75, show.legend = F) +
+   geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5, show.legend = F) +
+    geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 1) +
  labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
-   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3) +
+   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3, show.legend = F) +
   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
   # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm", "450 nm" )) +
+  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
    scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
@@
         legend.position = "top") +
-  labs(color = "Growth Wavelength",
-       fill = "Growth Wavelength")
+  labs(color = "Growth Wavelength (nm)",
+       fill = "Growth Wavelength (nm)")
 
@@
         legend.position = "top") +
-  labs(color = "Growth Wavelength",
-       fill = "Growth Wavelength")
+  labs(color = "Growth Wavelength (nm)",
+       fill = "Growth Wavelength (nm)" )
 

### 2024-02-27 Code/ManuscriptPURFits.Rmd
Changed 4hr photoperiod shape to solid square
Fixed legends

@@
 ```{r Pur plot strain faceted in columns}
+
 scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
@@
   ggplot() +
+  geom_line(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(Photoperiod)), size = 1) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, linetype = PhotoperiodPooled), size = 0.80, data = .
+%>% unnest(Predict_pooled) %>%  filter(Strain == "MED4") %>% mutate(PhotoperiodPooled = "Pooled")) +
+  geom_rect(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, fill = "white") +
   geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 3, alpha = 1.0) +
     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.0, alpha = 0.8) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.75, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.75, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) + 
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotdash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.75, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) + 
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotdash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 25, Strain == "MIT9313")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.80, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.80, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotdash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.80, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotdash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 25, Strain == "MIT9313")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +
  labs(y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
@@
   scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
-  scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
-  scale_linetype_manual(values = MyLineTypes, labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
-  scale_shape_manual(values = PhotoperiodShapes)  +
+  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm", "450 nm")) +
+  scale_linetype_manual(values = c("solid", "dotdash", "dashed", "dotted", "aa"),
+                        labels = c("Pooled", "16 h",  "12 h", "8 h", "4 h")) +
+  scale_shape_manual(values = PhotoperiodShapes, labels = c("16 h",  "12 h", "8 h", "4 h") )  +
   ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), cols = vars(Strain), 
                     labeller = labeller(Strain = label_value, O2_uM = label_value, OxygenLabel = label_value)) +
- guides(linetype = guide_legend(nrow = 1),
-        fill = "none",
-        color = guide_legend(nrow = 1)) +
- guides(shape = guide_legend(nrow = 1)) +
+ guides(linetype = guide_legend(order = 1),
+        fill = "none",) +
+        #color = guide_legend(nrow = 1)) +
+ # guides(shape = guide_legend(nrow = 1)) +
   theme_bw() +
@@
         # strip.background=element_rect(fill = "white"), 
-        legend.key.size = unit(0.1, 'cm'), #change legend key size
-        legend.key.height = unit(0.1, 'cm'), #change legend key height
-        legend.key.width = unit(0.1, 'cm'), #change legend key width
-        legend.title =  element_text(size = 25),  #change legend title font size
-        legend.text = element_text(size = 25),   #change legend text font size
-        legend.position = "top") +
-  labs( shape = "Photoperiod (h)",
-        color = "Growth Waveband (nm)",
-       linetype = "Photoperiod lines"
+        legend.key.size = unit(2, 'cm'), #change legend key size
+        legend.key.height = unit(0.5, 'cm'), #change legend key height
+        # legend.key.width = unit(2.5, 'cm'), #change legend key width
+        legend.background = element_rect(color = "black"),
+        legend.title =  element_text(size = 28),  #change legend title font size
+        legend.title.align = 0.5,
+        legend.text = element_text(size = 29),   #change legend text font size
+        legend.position = "top",
+        legend.direction = "vertical",
+        legend.spacing.x = unit(0.75, 'cm')) +
+  labs( linetype = "Fits",
+        shape = "Photoperiod",
+        color = "Growth Waveband",
+
       )
@@
 
-ggsave(file = file.path(PlotsOut, paste("AllStrainPurFitsPlots",".png",sep = "")), plot = AllStrainPurFitsPlots, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-ggsave(file = file.path(PlotsOut, paste("AllStrainPurFitsPlots",".tiff",sep = "")), plot = AllStrainPurFitsPlots, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("AllStrainPurFitsPlots",".png",sep = "")), plot = AllStrainPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+ggsave(file = file.path(PlotsOut, paste("AllStrainPurFitsPlots",".tiff",sep = "")), plot = AllStrainPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
 ```{r Pur plot strain faceted in columns}
+
 scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
 
-WLvsPooledPurFitsPlots <- AllFitsCombinedWL |>
+AllFitsCombinedWL |>
   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
@@
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_450) %>%  filter(O2_uM == 2.5, Strain == "MED4",  WL == 450)) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MED4", WL == 660))+
-    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MED4", WL == "WW")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_450) %>%  filter(O2_uM == 2.5, Strain == "MED4",  WL == 450)) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MED4", WL == 660))+
+    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MED4", WL == "WW")) +
    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 450)) +
- geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "SS120", O2_uM != 250, WL == "WW")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 450)) +
+ geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "SS120", O2_uM != 250, WL == "WW")) +
    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 660))+
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MIT9313", O2_uM == 2.5, WL == "WW")) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 660))+
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MIT9313", O2_uM == 2.5, WL == "WW")) +
  labs(title = "Anova fit comparisons of WL to pooled", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
@@
 
-WLvsPooledPurFitsPlots
-
 # This labels each pane with a letter but turns of the facet labels
@@
   ggplot() +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.7) +
-    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.0, alpha = 0.5) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_450) %>%  filter(Strain == "MED4",  WL == 450)) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MED4", WL == 660)) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM == 25, WL == 450)) +
- geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5,  data = . %>% unnest(Predict_660) %>%  filter(Strain == "SS120", O2_uM == 25, WL == 660)) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 450)) +
- geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, linetype = "dashed",  data = . %>% unnest(Predict_660) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 660)) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 660))+
-    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, data = . %>% unnest(Predict_450) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 450))+
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, linetype = "dashed", data = .
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 3, alpha = 1.0) +
+    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.0, alpha = 0.8) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = .
+%>% unnest(Predict_450) %>%  filter(Strain == "MED4",  WL == 450), linetype = "solid", show.legend = T) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MED4", WL == 660) , linetype = "solid") +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = .
+%>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM == 25, WL == 450) , linetype = "solid") +
+ geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_660) %>%  filter(Strain == "SS120", O2_uM == 25, WL == 660) , linetype = "solid") +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, linetype = "dashed", data = .
+%>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 450), show.legend = T) +
+ geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, linetype = "dashed",  data = . %>% unnest(Predict_660) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 660)) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = .
+%>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 660) , linetype = "solid")+
+    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = .
+%>% unnest(Predict_450) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 450) , linetype = "solid")+
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, linetype = "dashed", data = .
 %>% unnest(Predict_450) %>%  filter(Strain == "MIT9313", O2_uM == 250, WL == 450)) +
- geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.5, linetype = "dashed",  data = .
+ geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, linetype = "dashed",  data = .
 %>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM == 250, WL == 660)) +
@@
   scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
-  scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
-  # scale_linetype_manual(values = MyLineTypes, labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
+  scale_colour_manual(values = MCMIXColours, labels = c(660, 450)) +
+  scale_linetype_manual(values = c("solid", "dashed"), labels = c("Significantly different", "Not significantly different")) +
   scale_shape_manual(values = PhotoperiodShapes)  +
@@
                     labeller = labeller(Strain = label_value, O2_uM = label_value, OxygenLabel = label_value)) +
- guides(linetype = guide_legend(nrow = 1),
+ guides(linetype = "none",
+        # linetype = guide_legend(nrow = 1),
         fill = "none",
@@
         # strip.background=element_rect(fill = "white"), 
-        legend.key.size = unit(0.1, 'cm'), #change legend key size
+        legend.key.size = unit(0.2, 'cm'), #change legend key size
         legend.key.height = unit(0.1, 'cm'), #change legend key height
         legend.key.width = unit(0.1, 'cm'), #change legend key width
-        legend.title =  element_text(size = 25),  #change legend title font size
-        legend.text = element_text(size = 25),   #change legend text font size
+        legend.title =  element_text(size = 28),  #change legend title font size
+        legend.text = element_text(size = 29),   #change legend text font size
         legend.position = "top") +
@@
         color = "Growth Waveband (nm)",
-       linetype = "Photoperiod lines"
+       linetype = "ANOVA"
       )

### 2024-02-27 Code/Manuscript_O2.Rmd
Fixed legends

@@
 MIT9313 at 30 µmol photons m^-2^ s^-1^ with illumination from Philips Cool White F14T5/841 Alto, 14 watts, fluorescent bulbs. To maintain active growth all strains were
-transferred weekly with 1 to 5 dilution with Pro99 media
+transferred weekly with 1 in 5 dilution with Pro99 media
 [@mooreCulturingMarineCyanobacterium2007] prepared with autoclaved artificial
@@
                     "Columns are strains; MED4, SS120 and MIT9313.",
-                    "Shapes show the imposed photoperiod (h); 4 h (hollow inverted triangle),  8 h (solid diamond), 12 h (solid circle), 16 h (solid upright triangle).",
+                    "Shapes show the imposed photoperiod (h); 4 h (solid square),  8 h (solid diamond), 12 h (solid circle), 16 h (solid upright triangle).",
                       "Symbol colours show the spectral waveband for growth; 660 nm (red symbols), and 450 nm (blue symbols).",
@@
                     "Columns are strains; MED4, SS120 and MIT9313.",
-                    "Shapes show the imposed photoperiod (h); 4 h (hollow inverted triangle),  8 h (solid diamond), 12 h (solid circle), 16 h (solid upright triangle).",
+                    "Shapes show the imposed photoperiod (h); 4 h (solid square),  8 h (solid diamond), 12 h (solid circle), 16 h (solid upright triangle).",
                       "Symbol colours show the spectral waveband for growth; white LED (black symbols), 660 nm (red symbols), and 450 nm (blue symbols).",

### 2024-02-28 Code/ManuscriptPURFits.Rmd
Fixed legend for blue vs. red PUR plot. Need to remove linetype from WL and Photoperiod legend. Ask Naaman for help

@@
   ggplot() +
-  geom_line(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(Photoperiod)), size = 1) +
+  geom_line(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(Photoperiod)), size = 0.01, alpha = 5, show.legend = F) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted, linetype = PhotoperiodPooled), size = 0.80, data = .
@@
     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.0, alpha = 0.8) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.80, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.80, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotdash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.80, linetype = "solid", show.legend = F, data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotted", show.legend = F, data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.80, linetype = "solid", show.legend = F, data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotdash", show.legend = F, data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dashed", show.legend = F, data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotted", show.legend = F, data = . %>% unnest(Predict_8) %>%  filter(Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.80, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotdash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotdash", show.legend = F, data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +
    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 25, Strain == "MIT9313")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotted", show.legend = F, data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +
  labs(y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
@@
                     labeller = labeller(Strain = label_value, O2_uM = label_value, OxygenLabel = label_value)) +
- guides(linetype = guide_legend(order = 1),
+ guides(
+   linetype = guide_legend(order = 1),
         fill = "none",) +
@@
         # strip.background=element_rect(fill = "white"), 
-        legend.key.size = unit(2, 'cm'), #change legend key size
+        legend.key.size = unit(1.8, 'cm'), #change legend key size
         legend.key.height = unit(0.5, 'cm'), #change legend key height
@@
 
-# This labels each pane with a letter but turns of the facet labels
-# AllStrainPurFitsPlots <- tag_facet(AllStrainPurFitsPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
-
 BluevsRedPurFitsPlots <- AllFitsCombinedWL |>
@@
   ggplot() +
+  geom_line(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(WL)), size = 1, show.legend = T) +
+# geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(Photoperiod)), size = 1, show.legend = F) +
+# geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(Data_all_WL)), size = 1, show.legend = F) +
+  geom_rect(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, fill = "white") +
   geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 3, alpha = 1.0) +
@@
    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = .
-%>% unnest(Predict_450) %>%  filter(Strain == "MED4",  WL == 450), linetype = "solid", show.legend = T) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MED4", WL == 660) , linetype = "solid") +
+%>% unnest(Predict_450) %>%  filter(Strain == "MED4",  WL == 450), linetype = "solid", show.legend = F) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = .
-%>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM == 25, WL == 450) , linetype = "solid") +
- geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_660) %>%  filter(Strain == "SS120", O2_uM == 25, WL == 660) , linetype = "solid") +
+%>% unnest(Predict_660) %>%  filter(Strain == "MED4", WL == 660) , linetype = "solid", show.legend = F) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = .
+%>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM == 25, WL == 450) , linetype = "solid", show.legend = F) +
+ geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = .
+%>% unnest(Predict_660) %>%  filter(Strain == "SS120", O2_uM == 25, WL == 660) , linetype = "solid", show.legend = F) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, linetype = "dashed", data = .
-%>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 450), show.legend = T) +
- geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, linetype = "dashed",  data = . %>% unnest(Predict_660) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 660)) +
+%>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 450), show.legend = F) +
+ geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, linetype = "dashed",  data = .
+%>% unnest(Predict_660) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 660), show.legend = F) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = .
-%>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 660) , linetype = "solid")+
+%>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 660) , linetype = "solid", show.legend = F)+
     geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = .
-%>% unnest(Predict_450) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 450) , linetype = "solid")+
+%>% unnest(Predict_450) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 450) , linetype = "solid", show.legend = F)+
   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, linetype = "dashed", data = .
-%>% unnest(Predict_450) %>%  filter(Strain == "MIT9313", O2_uM == 250, WL == 450)) +
+%>% unnest(Predict_450) %>%  filter(Strain == "MIT9313", O2_uM == 250, WL == 450), show.legend = F) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, linetype = "dashed",  data = .
-%>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM == 250, WL == 660)) +
+%>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM == 250, WL == 660), show.legend = F) +
  labs(y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
@@
   scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
-  scale_colour_manual(values = MCMIXColours, labels = c(660, 450)) +
-  scale_linetype_manual(values = c("solid", "dashed"), labels = c("Significantly different", "Not significantly different")) +
-  scale_shape_manual(values = PhotoperiodShapes)  +
+  scale_colour_manual(values = MCMIXColours, labels = c("660 nm", "450 nm")) +
+  scale_linetype_manual(values = c("solid", "dashed"), labels = c("p value < 0.05", "p value > 0.05")) +
+  scale_shape_manual(values = PhotoperiodShapes, labels = c("16 h", "12 h", "8 h", "4 h") )  +
   ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), cols = vars(Strain), 
                     labeller = labeller(Strain = label_value, O2_uM = label_value, OxygenLabel = label_value)) +
- guides(linetype = "none",
-        # linetype = guide_legend(nrow = 1),
-        fill = "none",
-        color = guide_legend(nrow = 1)) +
- guides(shape = guide_legend(nrow = 1)) +
+ guides(
+   linetype = guide_legend(order = 1),
+        fill = "none") +
+ #        color = guide_legend(nrow = 1)) +
+ # guides(shape = guide_legend(nrow = 1)) +
   theme_bw()  +
@@
         # strip.background=element_rect(fill = "white"), 
-        legend.key.size = unit(0.2, 'cm'), #change legend key size
-        legend.key.height = unit(0.1, 'cm'), #change legend key height
-        legend.key.width = unit(0.1, 'cm'), #change legend key width
+        legend.key.size = unit(1.8, 'cm'), #change legend key size
+        legend.key.height = unit(0.5, 'cm'), #change legend key height
+        # legend.key.width = unit(2.5, 'cm'), #change legend key width
+        legend.background = element_rect(color = "black"),
         legend.title =  element_text(size = 28),  #change legend title font size
+        legend.title.align = 0.5,
         legend.text = element_text(size = 29),   #change legend text font size
-        legend.position = "top") +
-  labs( shape = "Photoperiod (h)",
-        color = "Growth Waveband (nm)",
-       linetype = "ANOVA"
+        legend.position = "top",
+        legend.direction = "vertical",
+        legend.spacing.x = unit(0.75, 'cm')) +
+  labs( linetype = "Fits",
+        shape = "Photoperiod",
+        color = "Growth Waveband",
+
       )

### 2024-02-28 Code/ManuscriptPURFits.Rmd
changed figure size on ggsave

@@
 
-ggsave(file = file.path(PlotsOut, paste("BluevsRedPurFitsPlots",".png",sep = "")), plot = BluevsRedPurFitsPlots, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-# ggsave(file = file.path(PlotsOut, paste("BluevsRedPurFitsPlots",".tiff",sep = "")), plot = BluevsRedPurFitsPlots, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("BluevsRedPurFitsPlots",".png",sep = "")), plot = BluevsRedPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+# ggsave(file = file.path(PlotsOut, paste("BluevsRedPurFitsPlots",".tiff",sep = "")), plot = BluevsRedPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)
 

### 2024-02-28 Code/Manuscript_O2.Rmd
minor wording edits to introduction

@@
 *P.
-marinus* growth is currently constrained between latitudes of 40°N to 40°S in open ocean waters, from surface to 300 m depth, thus spanning 3 orders of magnitudes of light [@partenskyProchlorococcusMarinePhotosynthetic1999; @chisholmProchlorococcusMarinusNov1992 ].
+marinus* growth is currently limited to between latitudes of 40°N to 40°S in open ocean waters, from surface to 300 m depth, thus spanning 3 orders of magnitudes of light [@partenskyProchlorococcusMarinePhotosynthetic1999; @chisholmProchlorococcusMarinusNov1992 ].
 
@@
 marinus* is functionally differentiated from other cyanobacteria primarily by the absence of phycobilisomes [@chisholmProchlorococcusMarinusNov1992].
-Instead, *Prochlorococcus*  uses intra-membrane Prochlorophyte Chlorophyll Binding (Pcb) proteins binding divinylchlorophyll a (Chl a2), and α-carotene, as major light harvesting complexes [@goerickePigmentsProchlorococcusMarinus1992]; [@larocheIndependentEvolutionProchlorophyte1996], with diversity in the number of genes encoding Pcb, expression of Pcb under changing light [@garczarekMultiplicationAntennaGenes2000]  [@rocapGenomeDivergenceTwo2003] [@garczarekMultiplicationAntennaGenes2000], and in thylakoid organization [@partenskyProchlorococcusMarinePhotosynthetic1999].
-The genes encoding much of the photosynthetic apparatus is highly conserved in *Prochlorococcus* [@kettlerPatternsImplicationsGene2007], though the photosynthetic efficiency may vary among clades [@hessPhotosyntheticApparatusProchlorococcus2001; @moorePhotophysiologyMarineCyanobacterium1999].
+Instead, *Prochlorococcus*  uses intra-membrane Prochlorophyte Chlorophyll Binding (Pcb) proteins binding divinylchlorophyll a and b, and α-carotene, as major light harvesting complexes [@goerickePigmentsProchlorococcusMarinus1992]; [@larocheIndependentEvolutionProchlorophyte1996], with diversity in the number of genes encoding Pcb, expression of Pcb under changing light [@garczarekMultiplicationAntennaGenes2000]  [@rocapGenomeDivergenceTwo2003] [@garczarekMultiplicationAntennaGenes2000], and in thylakoid organization [@partenskyProchlorococcusMarinePhotosynthetic1999].
+The genes encoding much of the photosynthetic apparatus are highly conserved in *Prochlorococcus* [@kettlerPatternsImplicationsGene2007], though the photosynthetic efficiency may vary among clades [@hessPhotosyntheticApparatusProchlorococcus2001; @moorePhotophysiologyMarineCyanobacterium1999].
 
@@
 The clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined by Low-Light (LL) or High-Light (HL).
-Of at least 12 known *Prochlorococcus* clades only 5 to date have cultured representatives; HLI, HLII, LLI, LLII/III and LIV [@billerProchlorococcusStructureFunction2015].
-
+Of at least 12 known *Prochlorococcus* genetic clades only 5 to date have cultured representatives; HLI, HLII, LLI, LLII/III and LIV [@billerProchlorococcusStructureFunction2015].
+
+Current niches of *P.
+marinus* strains span ocean water columns [ @veldhuisVerticalDistributionPigment1990; @chisholmNovelFreelivingProchlorophyte1988; @partenskyProchlorococcusMarinePhotosynthetic1999] and extend into regions with low dissolved oxygen concentrations [@partenskyProchlorococcusAdvantagesLimits2010; @goerickeNovelNicheProchlorococcus2000; @lavinNovelLineagesProchlorococcus2010, @ulloaCyanobacteriumProchlorococcusHas2021; @garcia-robledoCrypticOxygenCycling2017].
 Low-Light clades thrive in deeper ocean waters, extending beyond 200 m in depth [@partenskyProchlorococcusMarinePhotosynthetic1999], where only ~1% of the surface irradiance penetrates, primarily in the blue (450 nm) to green (520 nm) spectral range [@holtropVibrationalModesWater2021].
@@
 marinus* strains in clades LLV and LLVI also thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021; @lavinNovelLineagesProchlorococcus2010; @goerickeNovelNicheProchlorococcus2000; @garcia-robledoCrypticOxygenCycling2017; @johnsonEnergeticsGrowthKinetics1999].
-*Prochlorococcus marinus* LL ecotypes may indeed dominate the phytoplankton within OMZ
-[@lavinNovelLineagesProchlorococcus2010;
-@ulloaCyanobacteriumProchlorococcusHas2021; @partenskyProchlorococcusAdvantagesLimits2010], and may be net O~2~ consumers [@partenskyComparisonPhotosyntheticPerformances2018].
+*Prochlorococcus marinus* LL ecotypes may dominate the phytoplankton within OMZ [@lavinNovelLineagesProchlorococcus2010; @ulloaCyanobacteriumProchlorococcusHas2021; @partenskyProchlorococcusAdvantagesLimits2010], where they may be net O~2~ consumers [@partenskyComparisonPhotosyntheticPerformances2018].
 Clade LLI includes cultured strain NATL2A, which prefers moderate irradiance typically between 30 and 100 m depth.
-Clades LLII and LLIII are grouped together as the second oldest phylogenetic lineages diversifying in the *P.
-marinus* radiation, and share an affinity for low light.
-
-HL clades are the most recently evolved lineages, with reduced genome sizes in comparison to LL ecotypes.
+Clades LLII and LLIII, including cultured strain SS120, are grouped together as the second oldest phylogenetic lineage diversifying in the *P.
+marinus* radiation, with an affinity for low light.
+
+HL clades are more evolved lineages, with reduced genome sizes in comparison to LL clades.
 High-Light clades are typically dominant picophytoplankters in near-surface, oligotrophic waters, characterized by high light levels.
-Clade HLI is adapted to higher iron, and lower temperatures, and originated from the Mediterranean Sea, just 5 m below the surface [@partenskyProchlorococcusMarinePhotosynthetic1999].
-Clade HLII adapted to higher iron, and higher temperatures, is the most abundant *P.
+Clade HLI, represented by cultured strain MED4, is adapted to higher iron, and lower temperatures, and originated from 5 m depth in the Mediterranean Sea [@partenskyProchlorococcusMarinePhotosynthetic1999].
+Clade HLII, adapted to higher iron, and higher temperatures, is the most abundant *P.
 marinus* clade in the North Atlantic and North Pacific Oceans, often constituting over 90% of the total population [@partenskyProchlorococcusMarinePhotosynthetic1999],  and are most numerous around 50 m depth [@partenskyProchlorococcusMarinePhotosynthetic1999].
@@
 
-*P. marinus* clades are nonetheless found  in environments beyond their optimal habitats. HL clades inhabit depths overlapping with LL ecotypes
-[@westNichePartitioningProchlorococcusPopulationsStratified1999;
-@zinserInfluenceLightTemperature2007;
-@delmontLinkingPangenomesMetagenomes2018] 
-[@moorePhotophysiologyMarineCyanobacterium1999]. 
-@lavinNovelLineagesProchlorococcus2010, while LL ecotypes can occupy regions in OMZ at depths above 40 m, exploiting ambient light levels above what LL clades were thought to tolerate.
+*P.
+marinus* clades are nonetheless found in environments beyond their optimal habitats.
+HL clades inhabit depths overlapping with LL ecotypes [@westNichePartitioningProchlorococcusPopulationsStratified1999; @zinserInfluenceLightTemperature2007; @delmontLinkingPangenomesMetagenomes2018; @moorePhotophysiologyMarineCyanobacterium1999; @lavinNovelLineagesProchlorococcus2010], while LL clades can occupy regions in OMZ at depths shallower than 40 m, exploiting ambient light levels above what LL clades were thought to tolerate.
 
@@
 
-Current niches of *P. marinus* span ocean water columns
-[ @veldhuisVerticalDistributionPigment1990; @chisholmNovelFreelivingProchlorophyte1988; @partenskyProchlorococcusMarinePhotosynthetic1999] and extend into regions with varying dissolved oxygen concentrations
-[@partenskyProchlorococcusAdvantagesLimits2010; @goerickeNovelNicheProchlorococcus2000] and even into anoxic oceans [@lavinNovelLineagesProchlorococcus2010, @ulloaCyanobacteriumProchlorococcusHas2021; @garcia-robledoCrypticOxygenCycling2017].
-
-Our changing climate, characterized by warming ocean waters, is rapidly altering conditions for these specialized clades of marine picophytoplankton.
+Our changing climate is rapidly altering conditions for these specialized clades of marine picophytoplankton.
 Predictions indicate a net global increase of *P.
@@
 
-Near the equator, photoperiod remains relatively constant at the ocean surface, approximately 12 hours (h) of daylight and 12 h of darkness throughout the year.
-The effective length of the photoperiod does, however attenuate with depth as dawn and dusk light at depth drops below the level needed for biological processes.
+Near the equator, photoperiod remains nearly constant at the ocean surface, approximately 12 hours (h) of daylight and 12 h of darkness throughout the year.
+The effective length of the photoperiod does, however attenuate with depth as dawn and dusk light at depth drops below levels needed for biological processes.
 As *P.

### 2024-02-28 Code/ManuscriptTargetProtein.Rmd

@@
          Oxygen_Label = case_when(O2_uM %in% c(250, 25, 2.5) ~ paste(O2_uM, "µM", sep = " ")),
-         Par_Label = case_when(Par_ue %in% c(30, 90, 100, 180) ~ paste(Par_ue, "µE", sep = " "))) %>% 
-  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
-  geom_col() +
-   geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black") +
- labs(y = "Concentration" ~  " (fmole µg"  ~ protein^-1~")", x = "Protein") +
-  # scale_fill_manual(fill = (O2_uM)) %>% 
-  # scale_colour_manual(values = ColourOxygen) +
- ggh4x::facet_nested(cols = vars(Strain, Oxygen_Label), rows = vars(WL_label, Par_Label), 
+         Par_Label = case_when(Par_ue %in% c(30, 90, 100, 180) ~ paste(Par_ue, "µE", sep = " ")),
+        Oxygen_Label = factor(Oxygen_Label, levels = c("250 µM", "2.5 µM")),
+        Par_Label = factor(Par_Label, levels = c("30 µE", "90 µE", "100 µE", "180 µE"))) %>% 
+   ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug, color = as.factor(WL), fill = as.factor(WL))) +
+  geom_col(position="Dodge") +
+   # geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black")  +
+ labs(y = "Protein subunit content" ~   "(fmole µg"  ~ protein^-1~")", x = "Protein") +
+  scale_fill_manual(values = MCMIXColours) +
+  scale_colour_manual(values = MCMIXColours) +
+ ggh4x::facet_nested(cols = vars(Strain, Par_Label ), rows = vars(Oxygen_Label), 
                     labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_value)) +
- # guides(fill = "none") +
+guides(color = "none") +
   theme_bw()
@@
 MED4ProteinAnnotated <- TargetProtein %>%
-  filter( Strain == "MED4") %>% 
+  filter( Strain == "MED4",
+          O2_uM != 2.5) %>% 
    mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste(WL, "nm", sep = " "),
@@
          Oxygen_Label = case_when(O2_uM %in% c(250, 25, 2.5) ~ paste(O2_uM, "µM", sep = " ")),
-         Par_Label = case_when(Par_ue %in% c(30, 90, 100, 180) ~ paste(Par_ue, "µE", sep = " "))) %>% 
-  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
-  geom_col() +
-   geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black") +
- labs(y = "Concentration" ~  " (fmole µg"  ~ protein^-1~")", x = "Protein") +
-  # scale_fill_manual(fill = (O2_uM)) %>% 
-  # scale_colour_manual(values = ColourOxygen) +
- ggh4x::facet_nested(cols = vars(Strain, Oxygen_Label), rows = vars(WL_label, Par_Label), 
+         Par_Label = case_when(Par_ue %in% c(30, 90, 100, 180) ~ paste(Par_ue, "µE", sep = " ")),
+       Oxygen_Label = factor(Oxygen_Label, levels = c("250 µM", "2.5 µM")),
+        Par_Label = factor(Par_Label, levels = c("30 µE", "90 µE", "100 µE", "180 µE"))) %>% 
+  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug, color = as.factor(WL), fill = as.factor(WL))) +
+  geom_col(position="Dodge") +
+   # geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)), na.rm=FALSE ,  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black") +
+ labs(y = "Protein subunit content" ~   "(fmole µg"  ~ protein^-1~")", x = "Protein") +
+  scale_fill_manual(values = MCMIXColours) +
+  scale_colour_manual(values = MCMIXColours) +
+ ggh4x::facet_nested(cols = vars(Strain, Par_Label ), rows = vars(Oxygen_Label), 
                     labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_value)) +
- # guides(fill = "none") +
+guides(color = "none") +
   theme_bw()

### 2024-02-28 Code/Manuscript_O2.Rmd
Fixed strain name

@@
 marinus* contribute 13 to 48% of net primary production in oligotrophic oceans, corresponding to about 30% of global oxygen production [@partenskyProchlorococcusMarinePhotosynthetic1999].
-*P.
-marinus* growth is currently limited to between latitudes of 40°N to 40°S in open ocean waters, from surface to 300 m depth, thus spanning 3 orders of magnitudes of light [@partenskyProchlorococcusMarinePhotosynthetic1999; @chisholmProchlorococcusMarinusNov1992 ].
-
-*P.
-marinus* is functionally differentiated from other cyanobacteria primarily by the absence of phycobilisomes [@chisholmProchlorococcusMarinusNov1992].
+*Prochlorococcus marinus* growth is currently limited to between latitudes of 40°N to 40°S in open ocean waters, from surface to 300 m depth, thus spanning 3 orders of magnitudes of light [@partenskyProchlorococcusMarinePhotosynthetic1999; @chisholmProchlorococcusMarinusNov1992 ].
+
+*Prochlorococcus marinus* is functionally differentiated from other cyanobacteria primarily by the absence of phycobilisomes [@chisholmProchlorococcusMarinusNov1992].
 Instead, *Prochlorococcus*  uses intra-membrane Prochlorophyte Chlorophyll Binding (Pcb) proteins binding divinylchlorophyll a and b, and α-carotene, as major light harvesting complexes [@goerickePigmentsProchlorococcusMarinus1992]; [@larocheIndependentEvolutionProchlorophyte1996], with diversity in the number of genes encoding Pcb, expression of Pcb under changing light [@garczarekMultiplicationAntennaGenes2000]  [@rocapGenomeDivergenceTwo2003] [@garczarekMultiplicationAntennaGenes2000], and in thylakoid organization [@partenskyProchlorococcusMarinePhotosynthetic1999].
@@
 
-*P.
-marinus* comprises many strains, organized into clades, defined by 16S-23S intergenic transcribed ribosomal sequence signatures [@rocapGenomeDivergenceTwo2003].
+*Prochlorococcus marinus* comprises many strains, organized into clades, defined by 16S-23S intergenic transcribed ribosomal sequence signatures [@rocapGenomeDivergenceTwo2003].
 The clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined by Low-Light (LL) or High-Light (HL).
@@
 
-*P.
-marinus* clades are nonetheless found in environments beyond their optimal habitats.
+*Prochlorococcus marinus* clades are nonetheless found in environments beyond their optimal habitats.
 HL clades inhabit depths overlapping with LL ecotypes [@westNichePartitioningProchlorococcusPopulationsStratified1999; @zinserInfluenceLightTemperature2007; @delmontLinkingPangenomesMetagenomes2018; @moorePhotophysiologyMarineCyanobacterium1999; @lavinNovelLineagesProchlorococcus2010], while LL clades can occupy regions in OMZ at depths shallower than 40 m, exploiting ambient light levels above what LL clades were thought to tolerate.
@@
 For example, Vaulot *et al*.
-(1995) @vaulotGrowthProchlorococcusPhotosynthetic1995 showed that *Prochlorococcus* replication of DNA occurs in the afternoon, while cell division occurs at night.
+@vaulotGrowthProchlorococcusPhotosynthetic1995 showed that *Prochlorococcus* replication of DNA occurs in the afternoon, while cell division occurs at night.
 To our knowledge, no study has as yet addressed *P.
@@
 marinus* under a matrix of [O~2~], light levels, spectral waveband ranges, and photoperiods, to approximate eco-physiological conditions representative of current and hypothetical future ocean zones.
-*P.
-marinus* MED4, a clade HLI strain, was isolated near the ocean surface (5m depth) of the Mediterranean Sea where [O~2~] is near saturation, light levels are high and spectral bias from full solar irradiance is minimal.
-*P.
-marinus* SS120, a clade LLIII strain, was isolated from the Sargasso Sea at a depth of 120 m, while *P.
+*Prochlorococcus marinus* MED4, a clade HLI strain, was isolated near the ocean surface (5m depth) of the Mediterranean Sea where [O~2~] is near saturation, light levels are high and spectral bias from full solar irradiance is minimal.
+*Prochlorococcus marinus* SS120, a clade LLIII strain, was isolated from the Sargasso Sea at a depth of 120 m, while *P.
 marinus* MIT9313, a clade LLIV strain, was isolated from the North Atlantic Gulf Stream at a depth of 135 m.
@@
 PUR represents the fraction of PAR that is absorbed by the pigments of a given photosynthetic organism [@morelAvailableUsableStored1978], taking into account the specific spectral wavebands these pigments absorb.
-*P.
-marinus* light-harvesting complexes, [@chisholmProchlorococcusMarinusNov1992;
+*Prochlorococcus marinus* light-harvesting complexes, [@chisholmProchlorococcusMarinusNov1992;
 @goerickePigmentsProchlorococcusMarinus1992], show an absorption maxima

### 2024-02-28 Code/OceanProteinPlots.Rmd
Alternate ocean protein plots with NATL2A

@@
 StrainLabels <- c("MED4", "SS120", "MIT9313")
+AltStrainLabels <- c("MED4", "SS120", "MIT9313", "NATL2A")
 
@@
 
+ poi |>
+  filter(complex %in% ElectronTrans) |>
+  filter(strain %in% AltStrainLabels) |>
+  ggplot() +
+  geom_point(aes(x = O2, y= depth)) +
+  scale_x_continuous(limits = c(0, 260)) +
+  scale_y_reverse(limits = c(260, 0)) +
+  geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.1) +
+  geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.1) +
+  facet_grid(factor(strain, levels = c("MED4", "NATL2A", "SS120", "MIT9313")) ~ factor(complex, levels = c("psii", "cytb6f", "psi", "rubisco", "atp"), labels = PhotosynthLabels)) +
+  labs(y = "Depth (m)",
+       x = expression("O"[2] ~ "(µM)")) +
+    # ) +
+  theme_bw()
+
+ ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "NATLProchloroPhotosynthDepthO2.png")))
+ ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "NATLProchloroPhotosynthDepthO2.tiff")))
+
+poi |>
+  filter(complex %in% ProteinMetab) |>
+  filter(strain %in% AltStrainLabels) |>
+  ggplot() +
+  geom_point(aes(x = O2, y= depth)) +
+  scale_x_continuous(limits = c(0, 260)) +
+  scale_y_reverse(limits = c(260, 0)) +
+  geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.1) +
+  geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.1) +
+  facet_grid(factor(strain, levels = c("MED4", "NATL2A", "SS120", "MIT9313")) ~ factor(complex, levels = c("ftsh1", "ftsh2", "ftsh3", "ftsh4", "ribosome"), labels = ProteinMetabLabels)) +
+   labs(y = "Depth (m)",
+        x = expression("O"[2] ~ "(µM)")) +
+  theme_bw()
+
+ ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "NATLProchloroProteinMetabDepthO2.png")))
+ ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "NATLProchloroProteinMetabDepthO2.tiff")))
+
 ```

### 2024-02-28 Code/Manuscript_O2.Rmd
edits

@@
 author:
-  - name: '**Mireille Savoie**'
+  - name: 'Mireille Savoie'
     institute: mta
@@
     institute: mta
-  - name: Naaman Omar
+  - name: Naaman M. Omar
     institute: mta
@@
 ## *Prochlorococcus marinus* diversity {.unnumbered}
-*Prochlorococcus marinus*, a genus of Cyanobacteria, is the smallest known photosynthetic prokaryote, with cell diameters ranging from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992].
+*Prochlorococcus*, a genus of Cyanobacteria, is the smallest known photosynthetic prokaryote, with cell diameters ranging from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992].
 Despite small cell size, *P.
@@
 *Prochlorococcus marinus* is functionally differentiated from other cyanobacteria primarily by the absence of phycobilisomes [@chisholmProchlorococcusMarinusNov1992].
-Instead, *Prochlorococcus*  uses intra-membrane Prochlorophyte Chlorophyll Binding (Pcb) proteins binding divinylchlorophyll a and b, and α-carotene, as major light harvesting complexes [@goerickePigmentsProchlorococcusMarinus1992]; [@larocheIndependentEvolutionProchlorophyte1996], with diversity in the number of genes encoding Pcb, expression of Pcb under changing light [@garczarekMultiplicationAntennaGenes2000]  [@rocapGenomeDivergenceTwo2003] [@garczarekMultiplicationAntennaGenes2000], and in thylakoid organization [@partenskyProchlorococcusMarinePhotosynthetic1999].
+Instead, *Prochlorococcus*  uses intra-membrane Prochlorophyte Chlorophyll Binding (Pcb) proteins binding divinylchlorophyll *a* and *b*, and α-carotene, as major light harvesting complexes [@goerickePigmentsProchlorococcusMarinus1992]; [@larocheIndependentEvolutionProchlorophyte1996], with diversity in the number of genes encoding Pcb, expression of Pcb under changing light [@garczarekMultiplicationAntennaGenes2000; @rocapGenomeDivergenceTwo2003], and in thylakoid organization [@partenskyProchlorococcusMarinePhotosynthetic1999].
 The genes encoding much of the photosynthetic apparatus are highly conserved in *Prochlorococcus* [@kettlerPatternsImplicationsGene2007], though the photosynthetic efficiency may vary among clades [@hessPhotosyntheticApparatusProchlorococcus2001; @moorePhotophysiologyMarineCyanobacterium1999].
@@
 The path length of the internally reflective cavity of the Olis spectrophotometer was corrected to a 1 cm path length using the Javorfi correction method [@javorfiQuantitativeSpectrophotometryUsing2006] on PRO 99 media subtracted whole cell absorbance spectra.
-The blank-corrected whole cell absorbance spectra were normalized to the absorbance maximum of divinylchlorophyll a (Chl a~2~), determined for each spectra, falling between 400 nm and 460 nm.
+The blank-corrected whole cell absorbance spectra were normalized to the absorbance maximum of divinylchlorophyll *a* (Chl a~2~), determined for each spectra, falling between 400 nm and 460 nm.
 

### 2024-02-28 Code/Manuscript_O2.Rmd
edits to text

@@
   - num: 1
-    address: Department of Biology, Mount Allison University
+    address: Departments of Biology and Chemistry and Biochemistry, Mount Allison University
 institute:
@@
 marinus* contribute 13 to 48% of net primary production in oligotrophic oceans, corresponding to about 30% of global oxygen production [@partenskyProchlorococcusMarinePhotosynthetic1999].
-*Prochlorococcus marinus* growth is currently limited to between latitudes of 40°N to 40°S in open ocean waters, from surface to 300 m depth, thus spanning 3 orders of magnitudes of light [@partenskyProchlorococcusMarinePhotosynthetic1999; @chisholmProchlorococcusMarinusNov1992 ].
+*Prochlorococcus marinus* growth is currently limited to between latitudes of 40°N to 40°S in open ocean waters, from surface to 300 m depth, thus spanning 3 orders of magnitudes of light irradiance [@partenskyProchlorococcusMarinePhotosynthetic1999; @chisholmProchlorococcusMarinusNov1992 ].
 
 *Prochlorococcus marinus* is functionally differentiated from other cyanobacteria primarily by the absence of phycobilisomes [@chisholmProchlorococcusMarinusNov1992].
-Instead, *Prochlorococcus*  uses intra-membrane Prochlorophyte Chlorophyll Binding (Pcb) proteins binding divinylchlorophyll *a* and *b*, and α-carotene, as major light harvesting complexes [@goerickePigmentsProchlorococcusMarinus1992]; [@larocheIndependentEvolutionProchlorophyte1996], with diversity in the number of genes encoding Pcb, expression of Pcb under changing light [@garczarekMultiplicationAntennaGenes2000; @rocapGenomeDivergenceTwo2003], and in thylakoid organization [@partenskyProchlorococcusMarinePhotosynthetic1999].
+Instead, *Prochlorococcus*  uses intra-membrane Prochlorophyte chlorophyll binding (Pcb) proteins binding divinylchlorophyll *a* and *b*, and α-carotene, as major light harvesting complexes [@goerickePigmentsProchlorococcusMarinus1992]; [@larocheIndependentEvolutionProchlorophyte1996], with diversity in the number of genes encoding Pcb, expression of Pcb under changing light [@garczarekMultiplicationAntennaGenes2000; @rocapGenomeDivergenceTwo2003], and in thylakoid organization [@partenskyProchlorococcusMarinePhotosynthetic1999].
 The genes encoding much of the photosynthetic apparatus are highly conserved in *Prochlorococcus* [@kettlerPatternsImplicationsGene2007], though the photosynthetic efficiency may vary among clades [@hessPhotosyntheticApparatusProchlorococcus2001; @moorePhotophysiologyMarineCyanobacterium1999].
@@
 *Prochlorococcus marinus* comprises many strains, organized into clades, defined by 16S-23S intergenic transcribed ribosomal sequence signatures [@rocapGenomeDivergenceTwo2003].
-The clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined by Low-Light (LL) or High-Light (HL).
+The clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined by High-Light (HL) or Low-Light (LL).
 Of at least 12 known *Prochlorococcus* genetic clades only 5 to date have cultured representatives; HLI, HLII, LLI, LLII/III and LIV [@billerProchlorococcusStructureFunction2015].
@@
 Current niches of *P.
-marinus* strains span ocean water columns [ @veldhuisVerticalDistributionPigment1990; @chisholmNovelFreelivingProchlorophyte1988; @partenskyProchlorococcusMarinePhotosynthetic1999] and extend into regions with low dissolved oxygen concentrations [@partenskyProchlorococcusAdvantagesLimits2010; @goerickeNovelNicheProchlorococcus2000; @lavinNovelLineagesProchlorococcus2010, @ulloaCyanobacteriumProchlorococcusHas2021; @garcia-robledoCrypticOxygenCycling2017].
+marinus* strains span ocean water columns [@veldhuisVerticalDistributionPigment1990; @chisholmNovelFreelivingProchlorophyte1988; @partenskyProchlorococcusMarinePhotosynthetic1999] and extend into regions with low dissolved oxygen concentrations [@partenskyProchlorococcusAdvantagesLimits2010; @goerickeNovelNicheProchlorococcus2000; @lavinNovelLineagesProchlorococcus2010, @ulloaCyanobacteriumProchlorococcusHas2021; @garcia-robledoCrypticOxygenCycling2017].
+
 Low-Light clades thrive in deeper ocean waters, extending beyond 200 m in depth [@partenskyProchlorococcusMarinePhotosynthetic1999], where only ~1% of the surface irradiance penetrates, primarily in the blue (450 nm) to green (520 nm) spectral range [@holtropVibrationalModesWater2021].
-Clade LLIV, including cultured strain MIT9313, falls near the base of the *Prochlorococcus* radiation, and is characterized by preference for low light, typical of depths from 120 m to 200 m [@partenskyProchlorococcusMarinePhotosynthetic1999].
-LLIV members are, as yet, the only cultured strains to have been found in Oxygen Minimum Zones (OMZ).
-Some as yet uncultured *P.
-marinus* strains in clades LLV and LLVI also thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021; @lavinNovelLineagesProchlorococcus2010; @goerickeNovelNicheProchlorococcus2000; @garcia-robledoCrypticOxygenCycling2017; @johnsonEnergeticsGrowthKinetics1999].
-*Prochlorococcus marinus* LL ecotypes may dominate the phytoplankton within OMZ [@lavinNovelLineagesProchlorococcus2010; @ulloaCyanobacteriumProchlorococcusHas2021; @partenskyProchlorococcusAdvantagesLimits2010], where they may be net O~2~ consumers [@partenskyComparisonPhotosyntheticPerformances2018].
 Clade LLI includes cultured strain NATL2A, which prefers moderate irradiance typically between 30 and 100 m depth.
@@
 marinus* radiation, with an affinity for low light.
+Clade LLIV, including cultured strain MIT9313, falls near the base of the *Prochlorococcus* radiation, and is characterized by preference for low light, typical of depths from 120 m to 200 m [@partenskyProchlorococcusMarinePhotosynthetic1999].
+LLIV members are, as yet, the only cultured strains to have been found in Oxygen Minimum Zones (OMZ).
+Some, as yet, uncultured *P.
+marinus* strains in clades LLV and LLVI also thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021; @lavinNovelLineagesProchlorococcus2010; @goerickeNovelNicheProchlorococcus2000; @garcia-robledoCrypticOxygenCycling2017; @johnsonEnergeticsGrowthKinetics1999].
+*Prochlorococcus marinus* LL ecotypes may dominate the phytoplankton within OMZ [@lavinNovelLineagesProchlorococcus2010; @ulloaCyanobacteriumProchlorococcusHas2021; @partenskyProchlorococcusAdvantagesLimits2010], where they may be net O~2~ consumers [@partenskyComparisonPhotosyntheticPerformances2018].
 
@@
 Models predict that OMZ in the Pacific and Indian Oceans are expanding [@garcia-sotoOverviewOceanClimate2021; @buseckeDivergingFatesPacific2022].
-In spite of these expanding OMZ @buseckeDivergingFatesPacific2022 highlight that the cores of the OMZ, where the oxygen levels are lowest, are actually projected to contract.
+In spite of these expanding OMZ, Busecke et al.
+[@buseckeDivergingFatesPacific2022] project that the cores of the OMZ, where the oxygen levels are lowest, may actually contract.
 
 We used the OceansMap Protein Portal (OPP; https://proteinportal.whoi.edu/) [@saitoDevelopmentOceanProtein2021] to analyze the distribution of proteins from clades of *P.
-marinus* in samples tanken across a range of [O~2~] and depth, which in turn correlates to peak light at the site of sampling.
+marinus* in samples taken across a range of [O~2~] and depth, which in turn correlates to peak light at the site of sampling.
 We therefore analyzed the growth and physiological responses of representative strains from three clades of *P.
@@
 @goerickePigmentsProchlorococcusMarinus1992], show an absorption maxima
-of 442 nm for divinyl chlorophyll a and 478 nm for divinyl chlorophyll b
+of 442 nm for divinyl divinylchlorophyll *a* and 478 nm for divinyl chlorophyll b
 [@goerickePigmentsProchlorococcusMarinus1992] allowing *P. marinus* to
@@
 
-Collection and treatment of protein samples were performed following Saito et al., [@saitoMultipleNutrientStresses2014; @saitoNeedlesBlueSea2015].
+Collection and treatment of protein samples were performed following Saito et al.
+[@saitoMultipleNutrientStresses2014; @saitoNeedlesBlueSea2015].
 Briefly, samples of seawater from depths of 20, 40, 50, 60, 70, 80, 90, 120, 150, 200, 250, 300, 380, 400, 500, 550, 600, and 800 m below the ocean surface were pumped through a 0.2 µm filter, preserved in RNAlater and frozen at -80°C until extraction.
@@
 
-```{r ProchloroPhotosynthDepthO2, fig.cap = ProchloroPhotosynthDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
-
-ProchloroPhotosynthDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* photosynthesis complexes.**", 
+```{r NATLProchloroPhotosynthDepthO2, fig.cap = NATLProchloroPhotosynthDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
+
+NATLProchloroPhotosynthDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* photosynthesis complexes.**", 
                        "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
@@
 
-knitr::include_graphics(file.path(FiguresIn, "ProchloroPhotosynthDepthO2.png"))
+knitr::include_graphics(file.path(FiguresIn, "NATLProchloroPhotosynthDepthO2.png"))
 ```
@@
                       "Large symbols show mean of growth rate from logistic curve fits; small symbols show values for replicate determinations, if any.",
-                    "Platt (add Platt citation here) 4 parameter model fit to 660 nm (red lines) and 450 nm (blue lines) growth data for each combination of strain and dissolved oxygen shown with solid lines (significantly different fits, pvalue < 0.05) or dashed lines (not significantly different fits, pvalue > 0.05).",
+                    "Platt (add Platt citation here) 3 parameter model fit to 660 nm (red lines) and 450 nm (blue lines) growth data for each combination of strain and dissolved oxygen shown with solid lines (significantly different fits, pvalue < 0.05) or dashed lines (not significantly different fits, pvalue > 0.05).",
                        .sep = " ")
@@
 
-```{r ProchloroProteinMetabDepthO2, fig.cap = ProchloroProteinMetabDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
-
-ProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein metabolism complexes.**", 
+```{r NATLProchloroProteinMetabDepthO2, fig.cap = NATLProchloroProteinMetabDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
+
+NATLProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein metabolism complexes.**", 
                        "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
@@
 
-knitr::include_graphics(file.path(FiguresIn, "ProchloroProteinMetabDepthO2.png"))
+knitr::include_graphics(file.path(FiguresIn, "NATLProchloroProteinMetabDepthO2.png"))
 ```
@@
 marinus* MED4-like genomes at depths ranging from 5 m to 90 m, representing high to low blue light levels, in the Pacific South East Ocean.
-@delmontLinkingPangenomesMetagenomes2018 did not analyze data from depths beyond the subsurface chlorophyll maximum layer, the layer in the water column where the chlorophyll a concentration peaks, nor did they report the [O~2~] at those depths.
+@delmontLinkingPangenomesMetagenomes2018 did not analyze data from depths beyond the subsurface chlorophyll maximum layer, the layer in the water column where the chlorophyll *a* concentration peaks, nor did they report the [O~2~] at those depths.
 Our growth findings are also consistent with Figure\@ref(fig:ProchloroPhotosynthDepthO2) showing PSII proteins annotated as MED4, at depths up to 200 meters with O~2~ of 15 µM.
@@
                       "Large symbols show mean of growth rate from logistic curve fits; small symbols show values for replicate determinations, if any.",
-                    "Platt (add Platt citation here) 4 parameter model fit to data pooled for each combination of strain and dissolved oxygen shown with solid lines.
+                    "Platt (add Platt citation here) 3 parameter model fit to data pooled for each combination of strain and dissolved oxygen shown with solid lines.
 Separate models fit to photoperiod data and shown if significantly different from the pooled model; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).",

### 2024-02-28 Code/Manuscript_O2.Rmd
text edits

@@
 *Prochlorococcus marinus* is functionally differentiated from other cyanobacteria primarily by the absence of phycobilisomes [@chisholmProchlorococcusMarinusNov1992].
-Instead, *Prochlorococcus*  uses intra-membrane Prochlorophyte chlorophyll binding (Pcb) proteins binding divinylchlorophyll *a* and *b*, and α-carotene, as major light harvesting complexes [@goerickePigmentsProchlorococcusMarinus1992]; [@larocheIndependentEvolutionProchlorophyte1996], with diversity in the number of genes encoding Pcb, expression of Pcb under changing light [@garczarekMultiplicationAntennaGenes2000; @rocapGenomeDivergenceTwo2003], and in thylakoid organization [@partenskyProchlorococcusMarinePhotosynthetic1999].
+Instead, *Prochlorococcus*  uses intra-membrane Prochlorophyte chlorophyll binding (Pcb) proteins binding divinyl chlorophyll *a* and *b*, and α-carotene, as major light harvesting complexes [@goerickePigmentsProchlorococcusMarinus1992]; [@larocheIndependentEvolutionProchlorophyte1996], with diversity in the number of genes encoding Pcb, expression of Pcb under changing light [@garczarekMultiplicationAntennaGenes2000; @rocapGenomeDivergenceTwo2003], and in thylakoid organization [@partenskyProchlorococcusMarinePhotosynthetic1999].
 The genes encoding much of the photosynthetic apparatus are highly conserved in *Prochlorococcus* [@kettlerPatternsImplicationsGene2007], though the photosynthetic efficiency may vary among clades [@hessPhotosyntheticApparatusProchlorococcus2001; @moorePhotophysiologyMarineCyanobacterium1999].
@@
 Models predict that OMZ in the Pacific and Indian Oceans are expanding [@garcia-sotoOverviewOceanClimate2021; @buseckeDivergingFatesPacific2022].
-In spite of these expanding OMZ, Busecke et al.
+In spite of these expanding OMZ, Busecke *et al*.
 [@buseckeDivergingFatesPacific2022] project that the cores of the OMZ, where the oxygen levels are lowest, may actually contract.
@@
 marinus* in samples taken across a range of [O~2~] and depth, which in turn correlates to peak light at the site of sampling.
-We therefore analyzed the growth and physiological responses of representative strains from three clades of *P.
+In parallel we analyzed the growth and physiological responses of representative strains from three clades of *P.
 marinus* under a matrix of [O~2~], light levels, spectral waveband ranges, and photoperiods, to approximate eco-physiological conditions representative of current and hypothetical future ocean zones.
@@
 
-We then analyzed growth rates in terms of cumulative diel Photosynthetically Usable Radiation (PUR).
 Photosynthetic organisms absorb light energy within the Photosynthetically Active Radiation (PAR) range, 350 to 700 nm, for photosynthesis [@morelAvailableUsableStored1978].
-PUR represents the fraction of PAR that is absorbed by the pigments of a given photosynthetic organism [@morelAvailableUsableStored1978], taking into account the specific spectral wavebands these pigments absorb.
+Photosynthetically Usable Radiation (PUR) represents the fraction of PAR that is absorbed by the pigments of a given photosynthetic organism [@morelAvailableUsableStored1978], taking into account the specific spectral wavebands these pigments absorb.
 *Prochlorococcus marinus* light-harvesting complexes, [@chisholmProchlorococcusMarinusNov1992;
 @goerickePigmentsProchlorococcusMarinus1992], show an absorption maxima
-of 442 nm for divinyl divinylchlorophyll *a* and 478 nm for divinyl chlorophyll b
+of 442 nm for divinyl chlorophyll *a* and 478 nm for divinyl chlorophyll *b*
 [@goerickePigmentsProchlorococcusMarinus1992] allowing *P. marinus* to
@@
 We also aimed to detect whether growth responses are driven simply by cumulative diel PUR, or whether specific photoperiods, spectral bands or PAR levels have independent, albeit interacting, effects on growth.
+We therefore analyzed growth rates in terms of cumulative diel PUR.
 
 We discuss our findings in relation to analyses of genomic sequences CITATIONS across clades of *P.
-marinus*, showing that differences in the presence of genes encoding oxygen-dependent enzymes, and DNA repair enzymes, can help explain differential growth responses of strains under the matrix of light and [O~2~].
+marinus*, showing that differences in the presence of genes encoding oxygen-dependent enzymes, and DNA repair enzymes, can help explain differential growth responses of strains under the matrix of light and [O~2~] conditions.
 
@@
 
-Collection and treatment of protein samples were performed following Saito et al.
+Collection and treatment of protein samples were performed by Saito *et al*.
 [@saitoMultipleNutrientStresses2014; @saitoNeedlesBlueSea2015].
@@
 duration of the lag phase, if any. All data from the Multicultivator were saved
-as comma separated values file  (https://github.com/FundyPhytoPhys/prochlorococcus_o2/tree/main/Data/RawData).
+as comma separated values files  (https://github.com/FundyPhytoPhys/prochlorococcus_o2/tree/main/Data/RawData).
 
@@
 full spectrum, 660 nm, and 450 nm) were chosen to approximate light
-levels and spectral colors spanning the vertical ocean water column, from
+levels and spectral colours spanning the vertical ocean water column, from
 near-surface to the lower euphotic zone depths. Photoperiods were chosen to approximate diel cycles characteristic of current and hypothetical future
@@
 rate (µ, d^-1^) for each treatment combination.
-We first we used a rolling mean from the RStudio `zoo` package [@R-zoo] to calculate the average ΔOD data over a 1-hour window, to lower influence of outlier points and remove data points collected during post stationary phase, if applicable.
+We first used a rolling mean from the RStudio `zoo` package [@R-zoo] to calculate the average ΔOD data over a 1-hour window to lower influence of outlier points and remove data points collected during post stationary phase, if applicable.
 We used the Levenberg-Marquardt algorithm
@@
 indicate the 90, 50 and 10% quantiles for growth rate across the levels of factors.
-Growth rate estimates with a standard error below 30% of the fitted growth rate were included in the gam modelling.
+Growth rate estimates with a standard error below 30% of the fitted growth rate were included in the GAM modelling.
 Our priority
@@
 Radiation (PAR) was first determined using the reported delivery of sinusoidal diel PAR regimes by the Multicultivators, point validated using an XXXXXcitation of PAR meterXXX.
-An emission profile from 400 nm to 700 nm of each colored LED
+An emission profile from 400 nm to 700 nm of each coloured LED
 light of the MCMIX-OD Multicultivator and the white LED light of the MC1000-OD Multicultivator was obtained using a Jaz spectrometer (Ocean Optics, Inc.,Dunedin, FL, USA) equipped with a fiber
@@
 The path length of the internally reflective cavity of the Olis spectrophotometer was corrected to a 1 cm path length using the Javorfi correction method [@javorfiQuantitativeSpectrophotometryUsing2006] on PRO 99 media subtracted whole cell absorbance spectra.
-The blank-corrected whole cell absorbance spectra were normalized to the absorbance maximum of divinylchlorophyll *a* (Chl a~2~), determined for each spectra, falling between 400 nm and 460 nm.
+The blank-corrected whole cell absorbance spectra were normalized to the absorbance maximum of divinyl chlorophyll *a* (Chl a~2~), determined for each spectra, falling between 400 nm and 460 nm.
 
@@
 PurParPlot_cap <- glue("**Absorbed peak Photosynthetically Usable Radiation (PUR) (µmol photons m^-2^ s^-1^) vs. peak Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^).**",
-                       "The correlation between PAR, plotted on the x-axis and PUR, plotted on the y-axis, are colored for each growth spectral waveband; 450 nm (blue circles), 660 nm (red circles) and white LED (black circles).",
+                       "The correlation between PAR, plotted on the x-axis and PUR, plotted on the y-axis, are coloured for each growth spectral waveband; 450 nm (blue circles), 660 nm (red circles) and white LED (black circles).",
                        "The grey dashed line represents a hypothetical one to one correlation.",
@@
 Using the dataset Omar *et al*.
-(2023) [@omarAnnotationGenesEncoding2023], we filtered the dataset for Enzyme Commission Numbers (EC numbers), or Kegg Orthology Numbers (KO numbers) identified by BRENDA  [@changBRENDAELIXIRCore2021] as 'natural substrates' for O~2~ in Prochlorococcus marinus (MED4, MIT9313, SS120, and NATL2A) in order to generate a subset containing only those orthologs encoding enzymes directly mediating O~2~ metabolism.
+[@omarAnnotationGenesEncoding2023], we filtered the dataset for Enzyme Commission Numbers (EC numbers), or Kegg Orthology Numbers (KO numbers) identified by BRENDA  [@changBRENDAELIXIRCore2021] as 'natural substrates' for O~2~ in Prochlorococcus marinus (MED4, MIT9313, SS120, and NATL2A) in order to generate a subset containing only those orthologs encoding enzymes directly mediating O~2~ metabolism.
 We grouped orthologs together by EC number and their KO number (KO number) and determined the occurrences of individual orthologs encoding each EC number, or KO number when EC number was not available, in a given strain.
@@
                        "Columns show 3 levels of growth Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^",
-                    "Colors represent the actinic spectral waveband (nm).",
+                    "colours represent the actinic spectral waveband (nm).",
                     "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
@@
 
-XXXX Mireille to finish Fig. caption when figure is complete. Add color ? Remove []? XXX
+XXXX Mireille to finish Fig. caption when figure is complete. Add colour ? Remove []? XXX
 
@@
                                      "The solid circles represent K~m~ values from literature and the asterisks represent predicted values.",
-                                     "Colors represent the gene counts.",
+                                     "colours represent the gene counts.",
                                      "The red shaded area denotes a K~m~ oxygen concentration range from 230 to 280 µM.",

### 2024-02-29 Code/ManuscriptFigures.Rmd
Fixed legend for blue vs. red PUR plot. Need to remove linetype from WL and Photoperiod legend. Ask Naaman for help
standardized variable names for ggplot labels across rmds

@@
     geom_abline(slope = 1, intercept = 0, colour = "grey39", linetype = "dashed", linewidth = 1.2) +
-  labs(y = "PUR (µE)" , x = "PAR (µE)") +
+  labs(y = ~PUR~(µmol~photons~m^{-2}~s^{-1}) , x = ~PAR~(µmol~photons~m^{-2}~s^{-1})) +
    scale_x_continuous(breaks=seq(0, 180, by = 30)) +
@@
   filter(Run == 114) %>% 
-  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
+  mutate(PhotoperiodLabelTitle = "Photoperiod (h)",
          OxygenLabel_title = "Oxygen Concentration",
-         Oxygen_label = case_when(O2_uM %in% c(2.5, 25, 250) ~ paste("[Oxygen]", O2_uM, "µM", sep = " ")),
-         WL_label_title = "Growth Wavelength",
+         Oxygen_label = case_when(O2_uM %in% c(2.5, 25, 250) ~ paste("Oxygen Concentration", O2_uM, "µM", sep = " ")),
+         WLlabelTitle = "Growth Wavelength",
          WL_label = case_when(WL %in% c(450, 530, 660) ~ paste(WL, "nm", sep = " "),
@@
           deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
-  mutate(PhotoperiodLabel_title = "Photoperiod~(h)",
+  mutate(PhotoperiodLabelTitle = "Photoperiod~(h)",
          OxygenLabel = "Oxygen~Concentration~(µM)",
-         WL_label_title = "Growth~Wavelength~(nm)",
+         WLlabelTitle = "Growth~Wavelength~(nm)",
          ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
@@
           deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
-   mutate(PhotoperiodLabel_title = "Photoperiod~(h)",
+   mutate(PhotoperiodLabelTitle = "Photoperiod~(h)",
          OxygenLabel = "Oxygen~Concentration~(µM)",
-         WL_label_title = "Growth~Wavelength~(nm)",
+         WLlabelTitle = "Growth~Wavelength~(nm)",
          ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
@@
               labeller = labeller(Strain = label_value, WL_label = label_value, Photoperiod = label_both, Par_ue = label_both, O2_Category = label_both, Pur_ue = label_both)) +
-   geom_text(aes(x = 500, y = 1, label = paste("PAR", "=", Par_ue, "µE",sep = " "), show.legend = FALSE, ),
+   geom_text(aes(x = 500, y = 1, label = paste("PAR", "=", Par_ue, "µE",sep = " "), show.legend = FALSE ),
     # parse = TRUE,

### 2024-02-29 Code/ManuscriptTargetProtein.Rmd
standardized variable names for ggplot labels across rmds

--- 2024-02-23 Code/ManuscriptTargetProtein.Rmd
@@
 MIT9313ProteinAnnotated <- TargetProtein %>%
-  filter( Strain == "MIT9313") %>% 
-   mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste(WL, "nm", sep = " "),
-                              WL %in% c("WW") ~ paste("White LED", sep = " ")),
-        WL_label = factor(WL_label, levels= c("White LED", "660 nm", "530 nm", "450 nm")),
-         Oxygen_Label = case_when(O2_uM %in% c(250, 25, 2.5) ~ paste(O2_uM, "µM", sep = " ")),
-         Par_Label = case_when(Par_ue %in% c(30, 90, 100, 180) ~ paste(Par_ue, "µE", sep = " "))) %>% 
-  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
-  geom_col() +
-   geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black") +
- labs(y = "Concentration" ~  " (fmole µg"  ~ protein^-1~")", x = "Protein") +
-  # scale_fill_manual(fill = (O2_uM)) %>% 
-  # scale_colour_manual(values = ColourOxygen) +
- ggh4x::facet_nested(cols = vars(Strain, Oxygen_Label), rows = vars(WL_label, Par_Label), 
-                    labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_value)) +
- # guides(fill = "none") +
-  theme_bw()
+  filter(Strain == "MIT9313") %>% 
+   mutate(OxygenLabel = "Oxygen Concentration (µM)",
+         ParLabel = case_when(Par_ue %in% c(30, 90, 100, 180) ~ paste(Par_ue, "µE", sep = " ")),
+        O2_uM = factor(O2_uM, levels = c("250", "2.5")),
+        ParLabel = factor(ParLabel, levels = c("30 µE", "90 µE", "100 µE", "180 µE"))) %>% 
+   ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug, color = as.factor(WL), fill = as.factor(WL))) +
+  geom_col(position="Dodge") +
+   # geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black")  +
+ labs(y = "Protein subunit content" ~   "(fmole µg"  ~ protein^-1~")", x = "Protein") +
+  scale_fill_manual(values = MCMIXColours) +
+  scale_colour_manual(values = MCMIXColours) +
+ ggh4x::facet_nested(cols = vars(Strain, ParLabel ), rows = vars(OxygenLabel, O2_uM), 
+                    labeller = labeller(O2_uM = label_value, WL = label_both, O2 = label_both, Strain = label_value)) +
+guides(color = "none") +
+  theme_bw() +
+  theme(legend.position = "top") +
+  labs(fill = "Growth Waveband (nm)")
 
@@
 MED4ProteinAnnotated <- TargetProtein %>%
-  filter( Strain == "MED4") %>% 
-   mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste(WL, "nm", sep = " "),
-                              WL %in% c("WW") ~ paste("White LED", sep = " ")),
-        WL_label = factor(WL_label, levels= c("White LED", "660 nm", "530 nm", "450 nm")),
-         Oxygen_Label = case_when(O2_uM %in% c(250, 25, 2.5) ~ paste(O2_uM, "µM", sep = " ")),
-         Par_Label = case_when(Par_ue %in% c(30, 90, 100, 180) ~ paste(Par_ue, "µE", sep = " "))) %>% 
-  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug)) +
-  geom_col() +
-   geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)),  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black") +
- labs(y = "Concentration" ~  " (fmole µg"  ~ protein^-1~")", x = "Protein") +
-  # scale_fill_manual(fill = (O2_uM)) %>% 
-  # scale_colour_manual(values = ColourOxygen) +
- ggh4x::facet_nested(cols = vars(Strain, Oxygen_Label), rows = vars(WL_label, Par_Label), 
-                    labeller = labeller(Par_ue = label_both, WL = label_both, O2 = label_both, Strain = label_value)) +
- # guides(fill = "none") +
-  theme_bw()
+  filter( Strain == "MED4",
+          O2_uM != 2.5) %>% 
+   mutate(OxygenLabel = "Oxygen Concentration (µM)",
+         ParLabel = case_when(Par_ue %in% c(30, 90, 100, 180) ~ paste(Par_ue, "µE", sep = " ")),
+        O2_uM = factor(O2_uM, levels = c("250", "2.5")),
+        ParLabel = factor(ParLabel, levels = c("30 µE", "90 µE", "100 µE", "180 µE"))) %>% 
+  ggplot(aes(x=Target, y= Target_TotalProtein_fmole_ug, color = as.factor(WL), fill = as.factor(WL))) +
+  geom_col(position="Dodge") +
+   # geom_text(aes(y = 0.05, label = paste(round(Target_TotalProtein_fmole_ug, 0)), na.rm=FALSE ,  hjust = 0.5, vjust = -1.5, position = "stack", check_overlap = T), color = "Black") +
+ labs(y = "Protein subunit content" ~   "(fmole µg"  ~ protein^-1~")", x = "Protein") +
+  scale_fill_manual(values = MCMIXColours) +
+  scale_colour_manual(values = MCMIXColours) +
+  ggh4x::facet_nested(cols = vars(Strain, ParLabel ), rows = vars(OxygenLabel, O2_uM), 
+                    labeller = labeller(O2_uM = label_value, WL = label_both, O2 = label_both, Strain = label_value)) +
+guides(color = "none") +
+  theme_bw() +
+  theme(legend.position = "top") +
+  labs(fill = "Growth Waveband (nm)")
 

### 2024-02-29 Code/Manuscript_O2.Rmd
added more Amanda comments/edits

@@
 Using the dataset Omar *et al*.
-[@omarAnnotationGenesEncoding2023], we filtered the dataset for Enzyme Commission Numbers (EC numbers), or Kegg Orthology Numbers (KO numbers) identified by BRENDA  [@changBRENDAELIXIRCore2021] as 'natural substrates' for O~2~ in Prochlorococcus marinus (MED4, MIT9313, SS120, and NATL2A) in order to generate a subset containing only those orthologs encoding enzymes directly mediating O~2~ metabolism.
+[@omarAnnotationGenesEncoding2023], we filtered the dataset for Enzyme Commission Numbers (EC numbers), or Kegg Orthology Numbers (KO numbers) identified by BRENDA  [@changBRENDAELIXIRCore2021] as 'natural substrates' for O~2~ in *P.
+marinus* (MED4, MIT9313, SS120, and NATL2A) in order to generate a subset containing only those orthologs encoding enzymes directly mediating O~2~ metabolism.
 We grouped orthologs together by EC number and their KO number (KO number) and determined the occurrences of individual orthologs encoding each EC number, or KO number when EC number was not available, in a given strain.
-We merged the dataset with a list of enzyme Michaelis constant (K~m~) values from other organisms, as K~m~ values from Prochlorococcus were only available in the case of Ribulose bisphosphate carboxylase.
+We merged the dataset with a list of enzyme Michaelis constant (K~m~) values from other organisms, as K~m~ values from *Prochlorococcus* were only available in the case of Ribulose bisphosphate carboxylase.
 XXX Possibly add the link to the full list of genes.
@@
 ## Detection of *Prochlorococcus* proteins across O~2~ and light niches in the ocean  {.unnumbered}
+
+Proteins from 13 annotated strains of *P.
+marinus* were detected across depths and oxygen concentrations in the data set analyzed.
+We have focused our analysis here on photosynthetically relevant protein complexes from three strains: HLI MED4; LLIII SS120 and LLIV MIT9313.
+Figure \@ref(fig:NATLProchloroPhotosynthDepthO2) plots the observation of core photosynthetic complexes (Photosystem II, the Cytochromeb6f complex, Phototsystem I, ATP Synthase and Rubisco) in these strains as a function of depth (a proxy for light intensity) and measured [O~2~].
+Photosynthetic complexes from MED4 were detected throughout the water column predominantly at high [O~2~].
+Complexes from LLIII strain SS120 were detected throughout the water column in high [O~2~] and at depth in low [O~2~] samples.
+Photosystem I and II were only detected at low [O~2~].
+The exclusive assignment of ATP Synthase peptides to MIT9313 may result from the high conservation of protein sequence for this complex.
 
@@
 MED4 did not grow under 2.5 µM O~2~, so no GAM model was run.
-Considering the range of PAR levels, and spectral bands that MED4 can utilize, MED4 can inhabit not just shallow depths, where light levels are high, but also deeper regions, characterized by lower level of blue light, subject to the limitation of a photoperiod of more than 4 h, even after depth attenuation of light.
+Considering the range of PAR levels, and spectral bands that MED4 can utilize, MED4 can inhabit not just shallow depths, where light levels are high, but also deeper regions, characterized by a lower level of blue light, subject to the limitation of a photoperiod of more than 4 h, even after depth attenuation of light.
 The photoregimes of winter temperate zones, due to shorter photoperiods, exclude MED4 from growth at any depth, however temperate photoperiods and light levels for the remainder of the year are potentially adequate to support MED4 growth, if water temperatures warm into the Clade HLI tolerance range.
@@
                     "X-axis is photoperiod (h).",
-                    "Y-axis is actinic Photosynethetic Active Radiation (PAR, µmol photons m^-2^ s^-1^).",
+                    "Y-axis is actinic Photosynethetically Active Radiation (PAR, µmol photons m^-2^ s^-1^).",
                     "**A.** represents the model under 250 µM of O~2~ and red light.",
@@
 \@ref(fig:SS120PAR)).
-In contrast to the growth trends of the 250 µM O~2~ and PAR of 90 µmol photons m^-2^ s^-1^ experiments, SS120 grew under 4 and 8 h blue light and 16 h red light photoperiods.
-The growth rate decreased with increasing photoperiod under PAR of 90 µmol photons m^-2^ s^-1^ white LED light treatments.
+In contrast to the growth trends of the 250 µM O~2~ and PAR of 90 µmol photons m^-2^ s^-1^ experiments, SS120 grew under 4 and 8 h blue light and 16 h red light photoperiods, however the growth rate decreased under 12 and 16 h white LED light photoperiod treatments.
 Blue light treatments under PAR of 180 µmol photons m^-2^ s^-1^ showed growth only under an 8 h photoperiod.
@@
 
-*Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4, homologs to the characterized FtsH isoforms of the model cyanobacterium *Synechocystis* FtsH, and with presumably parallel functions (table \@ref(tab:FtsHTable)).
+*Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4, homologs to the characterized FtsH isoforms of the model freshwater cyanobacterium *Synechocystis* FtsH, and with presumably parallel functions (table \@ref(tab:FtsHTable)).
 Upon a shift to higher light HLIII MED4 upregulated expression of FtsH1 and FtsH2 [@bonisteelStrainSpecificDifferences2018], homologs to the *Synechocystis* slr0228 and slr1604, implicated in PSII repair.

### 2024-02-29 Code/Manuscript_O2.Rmd
Finished Amanda's round 1 edits

@@
 MED4 is also excluded from the lowest oxygen habitats, equivalent to our 2.5 µM O~2~ experimental conditions.
-MED4 can, however, grow under OMZ regions with slightly higher [O~2~], as by the growth under our 25 µM O~2~ experiments.
-Genomic analyses  ( Figure \@ref(fig:ProchlorococcusEnzymeKms))  and previous transcriptional analyses [@bergResponsesPsbAHli2011]  suggests MED4 is excluded from growth below ~ 25 µM O~2~ because it relies upon a ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction balance in the intersystem electron transport chain.
-On the other hand, MED4 shows inducible expression of FtsH isoforms [@bonisteelStrainSpecificDifferences2018], to counter photoinactivation of PSII under higher PAR and [O~2] environments.
+MED4 can, however, grow under OMZ regions with slightly higher [O~2~], as demonstrated by the growth under our 25 µM O~2~ experiments.
+Genomic analyses  ( Figure \@ref(fig:ProchlorococcusEnzymeKms))  and previous transcriptional analyses [@bergResponsesPsbAHli2011]  suggest MED4 is excluded from growth below ~ 25 µM O~2~ because it relies upon a ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction balance in the intersystem electron transport chain.
+On the other hand, MED4 shows inducible expression of FtsH isoforms [@bonisteelStrainSpecificDifferences2018], to counter photoinactivation of PSII under higher PAR and [O~2~] environments.
 Photoinactivation, does, however, impose an increased cost of growth upon MED4, since growth under red light, to lower the rate of photoinactivation of PSII [@murphyPhotoinactivationPhotosystemII2017], allows MED4 to achieve faster growth per absorbed photon than growth under red light.

### 2024-02-29 Code/Manuscript_O2.Rmd
minor edits

@@
 *Prochlorococcus marinus* clades are nonetheless found in environments beyond their optimal habitats.
-HL clades inhabit depths overlapping with LL ecotypes [@westNichePartitioningProchlorococcusPopulationsStratified1999; @zinserInfluenceLightTemperature2007; @delmontLinkingPangenomesMetagenomes2018; @moorePhotophysiologyMarineCyanobacterium1999; @lavinNovelLineagesProchlorococcus2010], while LL clades can occupy regions in OMZ at depths shallower than 40 m, exploiting ambient light levels above what LL clades were thought to tolerate.
+HL clades inhabit depths overlapping with LL ecotypes [@westNichePartitioningProchlorococcusPopulationsStratified1999; @zinserInfluenceLightTemperature2007; @delmontLinkingPangenomesMetagenomes2018], while LL clades can occupy regions in OMZ at depths shallower than 40 m [@lavinNovelLineagesProchlorococcus2010], exploiting ambient light levels above what LL clades were thought to tolerate.
 
@@
 [@goerickePigmentsProchlorococcusMarinus1992] allowing *P. marinus* to
-efficiently harvest blue light in the 400 nm
-to 500 nm range [@morelAvailableUsableStored1978] prevailing in deep ocean
-habitats, where only blue spectral wavelengths prevail [@holtropVibrationalModesWater2021].
+efficiently harvest blue light in the 400 nm to 500 nm range [@morelAvailableUsableStored1978] prevailing in deep ocean habitats, where only blue spectral wavelengths prevail [@holtropVibrationalModesWater2021].
 In *P.
@@
 MED4 can, however, grow under OMZ regions with slightly higher [O~2~], as demonstrated by the growth under our 25 µM O~2~ experiments.
-Genomic analyses  ( Figure \@ref(fig:ProchlorococcusEnzymeKms))  and previous transcriptional analyses [@bergResponsesPsbAHli2011]  suggest MED4 is excluded from growth below ~ 25 µM O~2~ because it relies upon a ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction balance in the intersystem electron transport chain.
+Genomic analyses  (Figure \@ref(fig:ProchlorococcusEnzymeKms))  and previous transcriptional analyses [@bergResponsesPsbAHli2011]  suggest MED4 is excluded from growth below ~ 25 µM O~2~ because it relies upon a ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction balance in the intersystem electron transport chain.
 On the other hand, MED4 shows inducible expression of FtsH isoforms [@bonisteelStrainSpecificDifferences2018], to counter photoinactivation of PSII under higher PAR and [O~2~] environments.

### 2024-02-29 Code/Manuscript_O2.Rmd
minor edits

@@
 Photosynthetically Usable Radiation (PUR) represents the fraction of PAR that is absorbed by the pigments of a given photosynthetic organism [@morelAvailableUsableStored1978], taking into account the specific spectral wavebands these pigments absorb.
-*Prochlorococcus marinus* light-harvesting complexes, [@chisholmProchlorococcusMarinusNov1992;
-@goerickePigmentsProchlorococcusMarinus1992], show an absorption maxima
-of 442 nm for divinyl chlorophyll *a* and 478 nm for divinyl chlorophyll *b*
-[@goerickePigmentsProchlorococcusMarinus1992] allowing *P. marinus* to
-efficiently harvest blue light in the 400 nm to 500 nm range [@morelAvailableUsableStored1978] prevailing in deep ocean habitats, where only blue spectral wavelengths prevail [@holtropVibrationalModesWater2021].
+*Prochlorococcus marinus* light-harvesting complexes show an absorption maxima
+of 442 nm for divinyl chlorophyll *a* and 478 nm for divinyl chlorophyll *b* [@goerickePigmentsProchlorococcusMarinus1992] allowing *P.
+marinus* to efficiently harvest blue light in the 400 nm to 500 nm range [@morelAvailableUsableStored1978] where only blue spectral wavelengths prevail in deep ocean habitats [@holtropVibrationalModesWater2021].
 In *P.
-marinus* small cell diameters, from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992], and simple cell structures, minimize the complication of pigment package effect or intracellular self-shading [@morelProchlorococcusSynechococcusComparative1993].
+marinus* small cell diameters, from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992], and simple cell structures, minimize the complication of pigment package effect or intracellular self-shading [@morelProchlorococcusSynechococcusComparative1993] contributing to efficient optical absorption.
 Given the different spectral light regimes typical of the niches of different ecotypes, expressing growth rates in terms of cumulative diel PUR might simplify different photoperiods, spectral bands, and PAR levels into a common parameter, making growth response comparisons across strains and different oxygen levels more accessible.
@@
 
-We discuss our findings in relation to analyses of genomic sequences CITATIONS across clades of *P.
-marinus*, showing that differences in the presence of genes encoding oxygen-dependent enzymes, and DNA repair enzymes, can help explain differential growth responses of strains under the matrix of light and [O~2~] conditions.
+We discuss our findings in relation to analyses of genomic sequences [@changBRENDAELIXIRCore2021] across clades of *P.
+marinus*, showing that differences in the presence of genes encoding oxygen-dependent enzymes, and DNA repair enzymes, can help explain differential growth responses of strains under the matrix of light and [O~2~] conditions of this study.
 
@@
 We screened a subset of the OPP for proteins annotated as from *Prochlorococcus* strains, to identify differential strategies employed by strains living at varying depths and oxygen levels within the marine water column.
-We focussed on proteins mediating photosynthesis and protein metabolism.
+We focused on proteins mediating photosynthesis and protein metabolism.
 The samples for metaproteomic analyses were collected from 12 locations in the tropical North Pacific ocean along 150 W from 18 N of the equator between October 1, 2011 and October 25, 2011 during the voyage of the R/V Kilo Moana MetZyme cruise KM1128 (https://www.rvdata.us/search/cruise/KM1128; original datasets in the Biological and Chemical Oceanography Data Management Office repository; https://www.bco-dmo.org/project/2236).
 
-Collection and treatment of protein samples were performed by Saito *et al*.
+Collection and treatment of protein samples were performed by personnel at the WHOI according to the protocols described by Saito *et al*.
 [@saitoMultipleNutrientStresses2014; @saitoNeedlesBlueSea2015].

### 2024-02-29 Code/Manuscript_O2.Rmd
minor edits

@@
 	iii) Sample station depth and [O~2~].  
-	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using the Tidyverse package [@R-tidyverse] in RStudio v1.2.5019 (https://rstudio.com/)  (LOCATION OF CODE ON GITHUB).
-The resulting merged dataset was filtered for those *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b6f (Cytb6f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Terminal Oxidase (PTOX); plastocyanin (PC); ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  ATP Synthase;  FtsH proteases (FtsH) or ribosomes.
+	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using tidyverse package [@R-tidyverse] running under R vXXX and RStudio v1.2.5019 (https://posit.co/)  (LOCATION OF CODE ON GITHUB).
+The resulting merged dataset was filtered for those *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b~6~f (Cytb~6~f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Plastoquinol Terminal Oxidase (PTOX); Plastocyanin (PC); Ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  ATP Synthase;  FtsH proteases (FtsH) or ribosomes.
 	Detected peptides were re-annotated for consistency and labelled, where feasible, according to strain, clade, subunit and protein complex.

### 2024-02-29 Code/OceanProteinPlots.Rmd
added alternate ocean protein figures facetted by clade

@@
 ```
+
+```{r clade_plots}
+CladeLabels <- c("HLI", "HLII", "LLI", "LLII",  "LLIII", "LLIV")
+
+PhotosynthLabels <- c("PSII", "Cytb6f", "PSI", "ATP Synthase", "RUBISCO")
+ProteinMetabLabels <- c("FtsH1", "FtsH2", "FtsH3", "FtsH4", "Ribosome")
+
+poi |>
+  filter(complex %in% ElectronTrans) |>
+  ggplot() +
+  geom_point(aes(x = O2, y= depth)) +
+  scale_x_continuous(limits = c(0, 260)) +
+  scale_y_reverse(limits = c(260, 0)) +
+  geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.1) +
+  geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.1) +
+  facet_grid(rows = vars(clade), cols = vars(factor(complex, levels = c("psii", "cytb6f", "psi", "rubisco", "atp"), labels = PhotosynthLabels))) +
+  labs(y = "Depth (m)",
+       x = expression("O"[2] ~ "(µM)")) +
+    # ) +
+  theme_bw()
+
+ ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.png")))
+ ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.tiff")))
+
+poi |>
+  filter(complex %in% ProteinMetab) |>
+  ggplot() +
+  geom_point(aes(x = O2, y= depth)) +
+  scale_x_continuous(limits = c(0, 260)) +
+  scale_y_reverse(limits = c(260, 0)) +
+  geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.1) +
+  geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.1) +
+  facet_grid(rows = vars(clade), cols = vars(factor(complex, levels = c("ftsh1", "ftsh2", "ftsh3", "ftsh4", "ribosome"), labels = ProteinMetabLabels))) +
+   labs(y = "Depth (m)",
+        x = expression("O"[2] ~ "(µM)")) +
+  theme_bw()
+
+  ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.png")))
+  ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.tiff")))
+
+```

### 2024-02-29 Code/Manuscript_O2.Rmd
Doug's edits

@@
 In parallel MED4 showed no growth under 2.5 µM O~2~, no matter the level of diel cumulative PUR.
-In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth under blue light was well described by a saturating response (REFERENCE for EQUATION) of growth to increasing cumulative diel blue PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A), and no evidence of inhibition of growth at any achieved cumulative diel PUR.
+In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth under blue light was well described by a saturating response of growth [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] to increasing cumulative diel blue PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A), and no evidence of inhibition of growth at any achieved cumulative diel PUR.
 Under the 'artificial' growth treatment of red light, MED4 achieved more growth per unit diel cumulative PUR  \@ref(fig:BluevsRedPurFitsPlots)A), consistent with [@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for growth under red light, for MED4, because red light provokes less photoinactivation of PSII, than equivalent levels of blue light.
@@
 
-Our data support enhanced growth under conditions of low cumulative dielPUR and 660 nm (red) spectral bandwidth, as supported by [@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue wavebands.
+Our data support enhanced growth under conditions of low cumulative diel PUR and 660 nm (red) spectral bandwidth, as supported by Murphy *et al*.[@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue wavebands.
 Interestingly, this protective effect of red light disappears for MIT9313 growing under 2.5 µM O~2~, possibly because photoinactivation is strongly suppressed under this low [O~2~].
@@
                       "Large symbols show mean of growth rate from logistic curve fits; small symbols show values for replicate determinations, if any.",
-                    "Platt (add Platt citation here) 3 parameter model fit to 660 nm (red lines) and 450 nm (blue lines) growth data for each combination of strain and dissolved oxygen shown with solid lines (significantly different fits, pvalue < 0.05) or dashed lines (not significantly different fits, pvalue > 0.05).",
+                    "Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to 660 nm (red lines) and 450 nm (blue lines) growth data for each combination of strain and dissolved oxygen shown with solid lines (significantly different fits, pvalue < 0.05) or dashed lines (not significantly different fits, pvalue > 0.05).",
                        .sep = " ")
@@
                       "Large symbols show mean of growth rate from logistic curve fits; small symbols show values for replicate determinations, if any.",
-                    "Platt (add Platt citation here) 3 parameter model fit to data pooled for each combination of strain and dissolved oxygen shown with solid lines.
+                    "Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to data pooled for each combination of strain and dissolved oxygen shown with solid lines.
 Separate models fit to photoperiod data and shown if significantly different from the pooled model; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).",

### 2024-02-29 Code/OceanProteinPlots.Rmd
ocean protein figures facetted by clade with LLII_LLIII

@@
 #Read in previously imported and saved data converted from large .csv to smaller .RDS
+#pro_proteins <- readRDS(file.path("..", "Data", "ProcessedData", "ProcessedOceanProtein", "pro_proteins.RDS"))
+
 poi <- readRDS(file.path("..", "Data", "ProcessedData", "ProcessedOceanProtein", "poi.RDS"))
-pro_proteins <- readRDS(file.path("..", "Data", "ProcessedData", "ProcessedOceanProtein", "pro_proteins.RDS"))
+
 ```
@@
 strains_list<-c("MED4","MIT9515","AS9601","MIT9202","MIT9215","MIT9301","MIT9312","NATL1A","NATL2A", "MIT9211","SS120","MIT9303","MIT9313")
+```
+
+```{r clademerge column}
+poi <- poi |>
+  mutate(CladeMerge = case_when(clade ==  "HLI" ~ "HLI",
+                                clade ==  "HLII" ~ "HLII",
+                                clade == "LLI" ~ "LLI",
+                                clade == "LLII" ~ "LII_LLIII",
+                                clade == "LLIII" ~ "LII_LLIII",
+                                 clade == "LLIV" ~ "LLIV")) |>
+  mutate(CladeMergeFactor = factor(CladeMerge, levels = c("HLI", "HLII", "LLI", "LII_LLIII", "LLIV")))
+
+unique(poi$CladeMerge)
+unique(poi$CladeMergeFactor)
 ```
@@
 
-pro_proteins |>
-  ggplot()+
-  geom_point(aes(x = O2, y= depth)) +
-  scale_x_continuous(limits = c(0, 260)) +
-  scale_y_reverse(limits = c(260, 0)) +
-  geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.2) +
-  geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.2) +
-  labs(title = "All detections of Prochlorococcus proteins from OceanProteinPlots.Rmd, from pro_proteins",
-       caption = "Horizontals approximate experimental growth light levels; Verticals indicate experimental growth oxygen levels") +
-  theme_bw()
+# pro_proteins |>
+#   ggplot()+
+#   geom_point(aes(x = O2, y= depth)) +
+#   scale_x_continuous(limits = c(0, 260)) +
+#   scale_y_reverse(limits = c(260, 0)) +
+#   geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.2) +
+#   geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.2) +
+#   labs(title = "All detections of Prochlorococcus proteins from OceanProteinPlots.Rmd, from pro_proteins",
+#        caption = "Horizontals approximate experimental growth light levels; Verticals indicate experimental growth oxygen levels") +
+#   theme_bw()
+# 
+# #ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "ProchloroAllProteinsDepthO2.png")))
+# 
+# pro_proteins |>
+#     filter(strain %in% c("MIT9313","MED4", "SS120")) |>
+#   ggplot()+
+#   geom_point(aes(x = O2, y= depth)) +
+#   scale_x_continuous(limits = c(0, 260)) +
+#   scale_y_reverse(limits = c(260, 0)) +
+#   geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.2) +
+#   geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.2) +
+#   labs(title = "All detections of MIT9313,MED4, SS120 proteins from OceanProteinPlots.Rmd, from pro_proteins",
+#        caption = "Horizontals approximate experimental growth light levels; Verticals indicate experimental growth oxygen levels") +
+#   theme_bw()
 
-#ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "ProchloroAllProteinsDepthO2.png")))
-
-pro_proteins |>
-    filter(strain %in% c("MIT9313","MED4", "SS120")) |>
-  ggplot()+
-  geom_point(aes(x = O2, y= depth)) +
-  scale_x_continuous(limits = c(0, 260)) +
-  scale_y_reverse(limits = c(260, 0)) +
-  geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.2) +
-  geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.2) +
-  labs(title = "All detections of MIT9313,MED4, SS120 proteins from OceanProteinPlots.Rmd, from pro_proteins",
-       caption = "Horizontals approximate experimental growth light levels; Verticals indicate experimental growth oxygen levels") +
-  theme_bw()
-
-poi |>
-  filter(strain %in% c("MIT9313","MED4", "SS120")) |>
-  ggplot()+
-  geom_point(aes(x = O2, y= depth)) +
-  scale_x_continuous(limits = c(0, 260)) +
-  scale_y_reverse(limits = c(260, 0)) +
-  geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.2) +
-  geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.2) +
-  facet_grid(vars(strain)) +
-  theme(panel.grid.minor = element_line(size = 0), panel.grid.major = element_line(size = 2)) +
-  theme_bw()
+# poi |>
+#   filter(strain %in% c("MIT9313","MED4", "SS120")) |>
+#   ggplot()+
+#   geom_point(aes(x = O2, y= depth)) +
+#   scale_x_continuous(limits = c(0, 260)) +
+#   scale_y_reverse(limits = c(260, 0)) +
+#   geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.2) +
+#   geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.2) +
+#   facet_grid(vars(strain)) +
+#   theme(panel.grid.minor = element_line(size = 0), panel.grid.major = element_line(size = 2)) +
+#   theme_bw()
 
@@
 ```
+
+```{r clademerge_plots}
+PhotosynthLabels <- c("PSII", "Cytb6f", "PSI", "ATP Synthase", "RUBISCO")
+ProteinMetabLabels <- c("FtsH1", "FtsH2", "FtsH3", "FtsH4", "Ribosome")
+
+poi |>
+  filter(complex %in% ElectronTrans) |>
+  ggplot() +
+  geom_point(aes(x = O2, y= depth)) +
+  scale_x_continuous(limits = c(0, 260)) +
+  scale_y_reverse(limits = c(260, 0)) +
+  geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.1) +
+  geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.1) +
+  facet_grid(rows = vars(CladeMergeFactor), cols = vars(factor(complex, levels = c("psii", "cytb6f", "psi", "rubisco", "atp"), labels = PhotosynthLabels))) +
+  labs(y = "Depth (m)",
+       x = expression("O"[2] ~ "(µM)")) +
+    # ) +
+  theme_bw()
+
+ ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.png")))
+ ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.tiff")))
+
+poi |>
+  filter(complex %in% ProteinMetab) |>
+  ggplot() +
+  geom_point(aes(x = O2, y= depth)) +
+  scale_x_continuous(limits = c(0, 260)) +
+  scale_y_reverse(limits = c(260, 0)) +
+  geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.1) +
+  geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.1) +
+  facet_grid(rows = vars(CladeMerge), cols = vars(factor(complex, levels = c("ftsh1", "ftsh2", "ftsh3", "ftsh4", "ribosome"), labels = ProteinMetabLabels))) +
+   labs(y = "Depth (m)",
+        x = expression("O"[2] ~ "(µM)")) +
+  theme_bw()
+
+  ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.png")))
+  ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.tiff")))
+
+```

### 2024-02-29 Code/Manuscript_O2.Rmd

@@
 MIT9313 at 30 µmol photons m^-2^ s^-1^ with illumination from Philips Cool White F14T5/841 Alto, 14 watts, fluorescent bulbs. To maintain active growth all strains were
-transferred weekly with 1 in 5 dilution with Pro99 media
+transferred weekly with 1 in 5 dilutions with Pro99 media
 [@mooreCulturingMarineCyanobacterium2007] prepared with autoclaved artificial
@@
 We earlier found [@murphyPhotoinactivationPhotosystemII2017] that growth under red light could prove mechanistically informative as to factors limiting *Prochlorococcus* growth, so we included that spectral band even though it is not characteristic of representative *Prochlorococcus* niches.
-Although *Prochlorococcus* is currently limited to a narrow range of surface photoperiods, potential poleward latitudinal expansions, in combination with attenuation of light with depth, mean *Prochlorococcus* currently, or potentially, encounters a wide range of photoperiods.
+Although *Prochlorococcus* is currently limited to a narrow range of surface photoperiods, potential poleward latitudinal expansions, in combination with attenuation of light with depth, mean *Prochlorococcus* may potentially encounter a wide range of photoperiods.
 Our growth rate determinations generally agreed with those from @mooreComparativePhysiologySynechococcus1995, for white LED and 250 µM O~2~, but our study is, we believe, the first to analyze the interactive growth responses of *Prochlorococcus* strains to varying [O~2~], spectral wavebands and photoperiods.

### 2024-02-29 Code/Manuscript_O2.Rmd
Added Slywia edits

@@
 
-## Generalized additive model of growth responses {.unnumbered}
-
-A Generalized Additive Model (GAM) CITATION was applied to the
+A Generalized Additive Model (GAM) [@woodGeneralizedAdditiveModels2017] was applied to the
 relation between chlorophyll-specific µ, d^-1^  to photoperiod and PAR level,  for each growth [O~2~] level, and for the blue and red wavebands for growth, for each *P.marinus* strain in this study.
-The gam function from the R package `mgcv`
-[@R-mgcv] was used to model the growth rate with smoothing terms, to
-indicate the 90, 50 and 10% quantiles for growth rate across the levels of factors.
-Growth rate estimates with a standard error below 30% of the fitted growth rate were included in the GAM modelling.
-Our priority
-was the effects of ecologically relevant blue light on growth trends.
+The gam function from the R package `mgcv` [@R-mgcv] was used to model the growth rate with smoothing terms and indicate the 90, 50 and 10% quantiles for growth rate across the levels of factors.
+Only growth rate estimates for which the amplitude of standard error was smaller than 30% of the fitted growth rate were included in the GAM modelling.
+Our priority was the effects of ecologically relevant blue light on growth trends.
 We included analyses of growth responses to red light, which is not ecophysiologically relevant, but which might prove mechanistically informative [@murphyPhotoinactivationPhotosystemII2017].
@@
 \newpage
+
+## Statistical analyses {.unnumbered}
+
+We fit the response of chlorophyll specific growth rate to cumulative diel PUR using the equation of Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] across strain and [O~2~] to first compare growth response between 660 nm (red) and 450 nm (blue) growth light and second to compare growth response between specific photoperiods (4 h, 8 h, 12 h, 16 h) and a fit across the pooled photoperiod data.
+To examine statistical differences between the modeled fits, we performed one-way ANOVA comparing the model output parameters assigning significant differences when p < 0.05.
 
@@
                       "Large symbols show mean of growth rate from logistic curve fits; small symbols show values for replicate determinations, if any.",
-                    "Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to 660 nm (red lines) and 450 nm (blue lines) growth data for each combination of strain and dissolved oxygen shown with solid lines (significantly different fits, pvalue < 0.05) or dashed lines (not significantly different fits, pvalue > 0.05).",
+                    "Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to 660 nm (red lines) and 450 nm (blue lines) growth data for each combination of strain and dissolved oxygen shown with solid lines (significantly different fits, pvalue < 0.05) or dashed lines (not significantly different fits, pvalue > 0.05) using one-way ANOVA.",
                        .sep = " ")
@@
                                      "The black bars show the minimum and maximum K~m~ values.",
-                       "Figure was generated using a filtered subset of the annotated phytoplankton gene sequences dataset from @omarAnnotationGenesEncoding2023.",
+                       "Figure was generated using a filtered subset of the annotated phytoplankton gene sequences dataset from Omar *et al*. [@omarAnnotationGenesEncoding2023].",
 
@@
                          "The blue solid circles represent a gene count of 3.",
-                       "Figure was generated using a filtered subset of the annotated phytoplankton gene sequences dataset from @omarAnnotationGenesEncoding2023.",
+                       "Figure was generated using a filtered subset of the annotated phytoplankton gene sequences dataset from Omar *et al*. [@omarAnnotationGenesEncoding2023].",
 
@@
 marinus* SS120 can exploit more diverse ecological niches within the ocean layers, even in regions with high levels of blue spectral waveband,  but only under O~2~ of 25 µM (Figure \@ref(fig:SS120PAR)).
-@mattisonPhotosyntheticStrategiesWild2020 and @lavinNovelLineagesProchlorococcus2010 show evidence of LLIII ecotypes at varying depths from 20 to 200 m and under all [O~2~] in the oxygen minimum zone (OMZ) of the tropical North Pacific Ocean, illustrating its tolerance of high light levels under low O~2~.
+Lavin *et al*.
+[@lavinNovelLineagesProchlorococcus2010] show evidence of LLIII ecotypes at varying depths from 20 to 30 m and from 75 to 200 µM O~2~ in the oxygen minimum zone (OMZ) of the tropical South Pacific Ocean, illustrating its tolerance of high light levels under low O~2~.
 SS120 has the potential to thrive in deep temperate zones, specifically during the spring, summer, and fall seasons when the duration of daylight exceeds 4 h, if O~2~ are near surface saturation of about 250 µM.
@@
                     "Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to data pooled for each combination of strain and dissolved oxygen shown with solid lines.
-Separate models fit to photoperiod data and shown if significantly different from the pooled model; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).",
+Separate models fit to photoperiod data and shown if significantly different from the pooled model using one-way ANOVA; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).",
                        .sep = " ")

### 2024-02-29 Code/Manuscript_O2.Rmd
more minor edits

@@
 
-Controlled growth experiments were performed using PSI Multicultivators (Figure \@ref(fig:LabeledMC); MCMIX-OD or MC1000-OD, Brno, Czech Republic).
+Controlled growth experiments were performed using MCMIX-OD or MC1000-OD PSI Multicultivators (Figure \@ref(fig:LabeledMC); PSI, Drásov, Czech Republic).
 Each multicultivator individually controls 8 tubes at a common temperature of 22°C.
@@
 ## Growth rate analysis {.unnumbered}
-Data files (.csv) saved from the Multicultivator software were imported into R-Studio [@R-Studio] for data management [@R-tidyverse], growth rate calculations CITATION, comparisons of model fits (get Platt CITATION), and generation of
+Data files (.csv) saved from the Multicultivator software were imported into R-Studio [@R-Studio] for data management [@R-tidyverse], growth rate calculations CITATION, comparisons of model fits [@harrisonPhotosynthesisirradianceRelationshipsPolar1986], and generation of
 figures using `ggplot2` [@R-ggplot2]. The chlorophyll proxy
-optical density (OD680 - OD720;  ΔOD) was used to determine the chlorophyll-specific exponential growth
+optical density (OD680 - OD720;  ΔOD) was used to determine the chlorophyll specific growth
 rate (µ, d^-1^) for each treatment combination.
@@
 \begin{equation}
-  Cumulative diel PUR = \frac{PUR × 3600 × Photoperiod}{2}
+  Cumulative~diel~PUR = \frac{PUR × 3600 × Photoperiod}{2}
   (\#eq:SumPURDay)
@@
 
-MED4PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade) vs. photoperiod (h).  **",
+MED4PAR_cap <- glue("**chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade) vs. photoperiod (h).  **",
                     "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
@@
 
-SS120PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low-Light (LLIII) deep ocean clade) vs. photoperiod (h). **",
+SS120PAR_cap <- glue("**chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low-Light (LLIII) deep ocean clade) vs. photoperiod (h). **",
                      "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
@@
 
-MIT9313PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
+MIT9313PAR_cap <- glue("**chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
                        "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
@@
 
- BluevsRedPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
+ BluevsRedPurFitsPlots_cap <- glue("**chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
                     "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
@@
 
-AllStrainPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
+AllStrainPurFitsPlots_cap <- glue("**chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
                     "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",

### 2024-02-29 Code/Manuscript_O2.Rmd
Naaman and Sylwia edits added

@@
 	iii) Sample station depth and [O~2~].  
-	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using tidyverse package [@R-tidyverse] running under R vXXX and RStudio v1.2.5019 (https://posit.co/)  (LOCATION OF CODE ON GITHUB).
+	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using *tidyverse* package [@R-tidyverse] running under R vXXX and RStudio v1.2.5019 (https://posit.co/)  (LOCATION OF CODE ON GITHUB).
 The resulting merged dataset was filtered for those *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b~6~f (Cytb~6~f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Plastoquinol Terminal Oxidase (PTOX); Plastocyanin (PC); Ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  ATP Synthase;  FtsH proteases (FtsH) or ribosomes.
@@
 is from Low-Light adapted (LLIV) clade. Cultures were
-maintained in incubators set to 22°C with a light/dark cycle of 12 h. The PAR level for maintenance cultures reflected Photosynthetically Active Radiation (PAR) in the source
-niche of the ecotype; MED4, of 160 µmol photons m^-2^ s^-1^ with illumination from STANDARD Products Inc. Cool White F24T5/41K/8/HO/PS/G5/STD, 24 watts, fluorescent bulbs; SS120 and
+maintained in incubators set to 22°C with a light/dark cycle of 12 h.
+The PAR level for maintenance cultures reflected PAR)in the source niche of the ecotype; MED4, of 160 µmol photons m^-2^ s^-1^ with illumination from STANDARD Products Inc.
+Cool White F24T5/41K/8/HO/PS/G5/STD, 24 watts, fluorescent bulbs; SS120 and
 MIT9313 at 30 µmol photons m^-2^ s^-1^ with illumination from Philips Cool White F14T5/841 Alto, 14 watts, fluorescent bulbs. To maintain active growth all strains were
@@
 Nitrogen (N~2~), with consistent 0.05% of Carbon Dioxide (CO~2~)
-gas, delivered through a 0.2 μm sterile microfilter via a G400 gas mixing system (Qubit Systems Inc, Kingston, Ontario, Canada). [O~2~] in situ was verified using oxygen optodes (PyroScience,
+gas, delivered through a 0.2 μm sterile microfilter via a G400 gas mixing system (Qubit Systems Inc., Kingston, Ontario, Canada). [O~2~] in situ was verified using oxygen optodes (PyroScience,
 Germany) inserted into tubes for
@@
 *In situ* measurements of Optical Density (OD) 680 nm, a proxy for cell suspension density, cell size dependent scatter and cell chlorophyll content;  and OD 720 nm, a proxy for cell suspension density and cell size dependent scatter, were recorded every 5 minutes over least 8 to 14 days,  depending on the
-duration of the lag phase, if any. All data from the Multicultivator were saved
+duration of the lag phase, if any. All data obtained from the Multicultivator were saved
 as comma separated values files  (https://github.com/FundyPhytoPhys/prochlorococcus_o2/tree/main/Data/RawData).
@@
 ## Growth rate analysis {.unnumbered}
-Data files (.csv) saved from the Multicultivator software were imported into R-Studio [@R-Studio] for data management [@R-tidyverse], growth rate calculations CITATION, comparisons of model fits [@harrisonPhotosynthesisirradianceRelationshipsPolar1986], and generation of
-figures using `ggplot2` [@R-ggplot2]. The chlorophyll proxy
-optical density (OD680 - OD720;  ΔOD) was used to determine the chlorophyll specific growth
+Data files (.csv) saved from the Multicultivator software were imported into R-Studio for data management [@R-tidyverse], growth rate calculations CITATION, comparisons of model fits [@harrisonPhotosynthesisirradianceRelationshipsPolar1986], and visualization.
+The chlorophyll proxy
+optical density (OD~680~ - OD~720~;  ΔOD) was used to determine the chlorophyll specific growth
 rate (µ, d^-1^) for each treatment combination.
-We first used a rolling mean from the RStudio `zoo` package [@R-zoo] to calculate the average ΔOD data over a 1-hour window to lower influence of outlier points and remove data points collected during post stationary phase, if applicable.
+We first used a rolling mean from the R package *`zoo`* [@R-zoo] to calculate the average ΔOD data over a 1-hour window to lower the influence of outlier points and remove data points collected during post stationary phase, when applicable.
 We used the Levenberg-Marquardt algorithm
 [@bellaviaLevenbergMarquardtMethod2018] modification of the non-linear
-least squares,  using the R package `minpack.lm`
+least squares,  using the R package *`minpack.lm`*
 [@R-minpack.lm], to fit a logistic
-equation \@ref(eq:GrowthRate)
-
-```{=tex}
+equation (Equation \@ref(eq:GrowthRate))
+
 \begin{equation}
@@
 \end{equation}
-```
 
@@
 relation between chlorophyll-specific µ, d^-1^  to photoperiod and PAR level,  for each growth [O~2~] level, and for the blue and red wavebands for growth, for each *P.marinus* strain in this study.
-The gam function from the R package `mgcv` [@R-mgcv] was used to model the growth rate with smoothing terms and indicate the 90, 50 and 10% quantiles for growth rate across the levels of factors.
-Only growth rate estimates for which the amplitude of standard error was smaller than 30% of the fitted growth rate were included in the GAM modelling.
+The R package *`mgcv`* [@R-mgcv] was used to model the growth rate with smoothing terms and indicate the 90, 50 and 10% quantiles for growth rate across the levels of factors.
+Only growth rate estimates for which the amplitude of standard error was smaller than 30% of the fitted growth rate were included in the GAM.
 Our priority was the effects of ecologically relevant blue light on growth trends.
@@
 To estimate the Photosynthetic Usable Radiation (PUR), a proxy of incident photons absorbed by the cells, for each *P. marinus* ecotype, the imposed Photosynthetic Active
-Radiation (PAR) was first determined using the reported delivery of sinusoidal diel PAR regimes by the Multicultivators, point validated using an XXXXXcitation of PAR meterXXX.
+Radiation (PAR) was first determined using the reported delivery of sinusoidal diel PAR regimes by the Multicultivators, point validated using a LI-250 quantum sensor (LI-COR Inc.,Lincoln, NE, USA).
 An emission profile from 400 nm to 700 nm of each coloured LED
@@
 An *in-vivo* whole cell absorbance spectrum for each *P. marinus* strain under each spectral growth condition was obtained using the Olis 14 UV/VIS Clarity
-Spectrophotometer (Olis Inc, Bogart, GA, USA) to scan across range of λ = 350 nm to 750 nm at 1 nm intervals.
+Spectrophotometer (Olis Inc., Bogart, GA, USA) to scan across range of λ = 350 nm to 750 nm at 1 nm intervals.
 The path length of the internally reflective cavity of the Olis spectrophotometer was corrected to a 1 cm path length using the Javorfi correction method [@javorfiQuantitativeSpectrophotometryUsing2006] on PRO 99 media subtracted whole cell absorbance spectra.
@@
 
-An integrated weighting Equation \@ref(eq:WeightedPUR) [@morelAvailableUsableStored1978] was used to determine the weighted PUR spectrum P(λ),
+An integrated weighting equation \@ref(eq:WeightedPUR) [@morelAvailableUsableStored1978] was used to determine the weighted PUR spectrum P(λ),
 
@@
 
-Protein samples were thawed and placed in 2 mL FastPrep®-24 bead lysing matrix D vials (MP Biomedicals, Irvine, CA, USA; SKU 116913050) with 200 uL of 1X protein extraction buffer (0.0281 mol L^−1^ TRIS base buffer, 0.0211 mol L^−1^ TRIS HCl buffer, 0.0735 mol L^−1^ lithium dodecyl sulfate, 1.08 mol L^−1^ glycerol, 0.5 mmol L^−1^ ethylenediaminetetraacetic acid, 0.1 mg·mL−1 PefaBloc SC (AEBSF) protease inhibitor) [@brownFluxCapacitiesAcclimation2008]  XXX note we used a low tris PEB recipe not sure where it came from (citation??) XXX.
+Protein samples were thawed and placed in 2 mL FastPrep®-24 bead lysing matrix D vials (MP Biomedicals, Irvine, CA, USA; SKU 116913050) with 200 µL of 1X protein extraction buffer (0.0281 mol L^−1^ TRIS base buffer, 0.0211 mol L^−1^ TRIS HCl buffer, 0.0735 mol L^−1^ lithium dodecyl sulfate, 1.08 mol L^−1^ glycerol, 0.5 mmol L^−1^ ethylenediaminetetraacetic acid, 0.1 mg·mL−1 PefaBloc SC (AEBSF) protease inhibitor) modified from Brown *et al*.
+[@brownFluxCapacitiesAcclimation2008].
 Cells were lysed for 3 cycles of 60 seconds at 6.5m s-1 with 60 second intervals on ice between cycles.
-The lysing vials were centrifuged at 16100g using XXXXXX centrifuge ( reference here    ) for 5 minutes, the supernatant was transferred to a 600 uL microcentrifuge tube and centrifuged again at 16100g for 3 minutes.
+The lysing vials were centrifuged at 16100 x *g* using a tabletop Mikro 20 centrifuge (Andreas Hettich GmbH & Co., Tuttlingen, Germany) for 5 minutes, the supernatant was transferred to a 600 µL microcentrifuge tube and centrifuged again at 16100 x *g* for 3 minutes.
 40 µL of the supernatant were subsampled into labeled vials and stored at -80 °C until analysis.
@@
 marinus* (MED4, MIT9313, SS120, and NATL2A) in order to generate a subset containing only those orthologs encoding enzymes directly mediating O~2~ metabolism.
-We grouped orthologs together by EC number and their KO number (KO number) and determined the occurrences of individual orthologs encoding each EC number, or KO number when EC number was not available, in a given strain.
+We grouped orthologs together by EC number and their KO number and determined the occurrences of individual orthologs encoding each EC number, or KO number when EC number was not available, in a given strain.
 We merged the dataset with a list of enzyme Michaelis constant (K~m~) values from other organisms, as K~m~ values from *Prochlorococcus* were only available in the case of Ribulose bisphosphate carboxylase.
 XXX Possibly add the link to the full list of genes.
-XXXX
+Remove this once added XXXX
 
@@
                        "Point colours identify *Prochlorococcus* clade assignments",
-                       "Data from OceanProteinPortal (https://www.oceanproteinportal.org/).",
+                       "Data obtained from OceanProteinPortal (https://www.oceanproteinportal.org/).",
  .sep = " ")
@@
 Although *Prochlorococcus* is currently limited to a narrow range of surface photoperiods, potential poleward latitudinal expansions, in combination with attenuation of light with depth, mean *Prochlorococcus* may potentially encounter a wide range of photoperiods.
-Our growth rate determinations generally agreed with those from @mooreComparativePhysiologySynechococcus1995, for white LED and 250 µM O~2~, but our study is, we believe, the first to analyze the interactive growth responses of *Prochlorococcus* strains to varying [O~2~], spectral wavebands and photoperiods.
+Our growth rate determinations generally agreed with those from @mooreComparativePhysiologySynechococcus1995, for white LED and 250 µM O~2~, but our study is, to our knowledge, the first to analyze the interactive growth responses of *Prochlorococcus* strains to varying [O~2~], spectral wavebands and photoperiods.
 
@@
 photoperiod was 16 h for each spectral waveband, across PAR levels (Figure \@ref(fig:MED4PAR)).
-The µ~max~ was `r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "25", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ (Table.
-\@ref(tab:MaxGrowthTable)) achieved under 180 µmol photons m^-2^ s^-1^ blue light and 16 h photoperiod.
-The 4 h photoperiod
-experiments under white LED light were not performed because no growth was achieved when grown under an 8 h photoperiod of white LED light.
-
-MED4 did not grow under when sparged to the lowest [O~2~] of 2.5 µM (Figure \@ref(fig:MED4PAR)). 2.5 µM O~2~ growth experiments
+The µ~max~ was `r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "25", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ (Table \@ref(tab:MaxGrowthTable)) achieved under 180 µmol photons m^-2^ s^-1^ blue light and 16 h photoperiod.
+The 4 h photoperiod experiments under white LED light were not performed as no growth was achieved when grown under an 8 h photoperiod of white LED light.
+
+MED4 did not grow when sparged to the lowest [O~2~] of 2.5 µM (Figure \@ref(fig:MED4PAR)). 2.5 µM O~2~ growth experiments
 were not conducted for 4 and 16 h photoperiods, as no reproducible growth occurred when MED4 was exposed to 8 and 12 h photoperiods.
@@
 Growth rate decreased with longer photoperiods and showed growth inhibition at 12 and 16 h photoperiods under PAR of 180 µmol photons m^-2^ s^-1^  white, red or blue LED light.
-The µ~max~ was `r PURPARFits %>% filter(Strain == "SS120", WL == "WW", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ (Table.
-\@ref(tab:MaxGrowthTable)) achieved under 90 µmol photons m^-2^ s^-1^ white LED light and 16 h photoperiod.
+The µ~max~ was `r PURPARFits %>% filter(Strain == "SS120", WL == "WW", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ (Table \@ref(tab:MaxGrowthTable)) achieved under 90 µmol photons m^-2^ s^-1^ white LED light and 16 h photoperiod.
 
@@
 Blue light treatments under PAR of 180 µmol photons m^-2^ s^-1^ showed growth only under an 8 h photoperiod.
-The µ~max~ was `r PURPARFits %>% filter(Strain == "SS120", WL == "450", O2_uM == "25", Photoperiod == 8) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ (Table.
-\@ref(tab:MaxGrowthTable)) achieved under 90 µmol photons m^-2^ s^-1^ blue light and 8 h photoperiod.
+The µ~max~ was `r PURPARFits %>% filter(Strain == "SS120", WL == "450", O2_uM == "25", Photoperiod == 8) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ (Table \@ref(tab:MaxGrowthTable)) achieved under 90 µmol photons m^-2^ s^-1^ blue light and 8 h photoperiod.
 The 25 µM O~2~, less than 16 h photoperiod and 180 µmol photons m^-2^ s^-1^  under white LED light experiments were not performed due to time constraints.
@@
 Most 4 h photoperiod treatments of SS120 also did not grow under 250 µM O~2~, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments.
-SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ experiments(Figure \@ref(fig:BluevsRedPurFitsPlots)B).
+SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ experiments (Figure \@ref(fig:BluevsRedPurFitsPlots)B).
 
@@
                       "Large symbols show mean of growth rate from logistic curve fits; small symbols show values for replicate determinations, if any.",
-                    "Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to 660 nm (red lines) and 450 nm (blue lines) growth data for each combination of strain and dissolved oxygen shown with solid lines (significantly different fits, pvalue < 0.05) or dashed lines (not significantly different fits, pvalue > 0.05) using one-way ANOVA.",
+                    "Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to 660 nm (red lines) and 450 nm (blue lines) growth data for each combination of strain and dissolved oxygen shown with solid lines (significantly different fits, p value < 0.05) or dashed lines (not significantly different fits, p value > 0.05) using one-way ANOVA.",
                        .sep = " ")
@@
 
-Under full atmospheric [O~2~] and bluelight, LL clades of *Prochlorococcus* are restricted to growth under low light, in part because they suffer photoinhibition of Photosystem II (PSII) through several paths, including direct absorbance of UV or blue light, in parallel with generation of Reactive Oxygen Species (ROS) if the electron flow is slowed, [@aroPhotoinhibitionPhotosystemII1993], producing damaging singlet oxygen (^1^O~2~) [@aroPhotoinhibitionPhotosystemII1993; @soitamoPhotoinhibitionMarinePicocyanobacteria2017; @murphyPhotoinactivationPhotosystemII2017; @hakalaEvidenceRoleOxygenevolving2005].
+Under full atmospheric [O~2~] and blue light, LL clades of *Prochlorococcus* are restricted to growth under low light, in part because they suffer photoinhibition of Photosystem II (PSII) through several paths, including direct absorbance of UV or blue light, in parallel with generation of Reactive Oxygen Species (ROS) if the electron flow is slowed [@aroPhotoinhibitionPhotosystemII1993], producing damaging singlet oxygen (^1^O~2~) [@aroPhotoinhibitionPhotosystemII1993; @soitamoPhotoinhibitionMarinePicocyanobacteria2017; @murphyPhotoinactivationPhotosystemII2017; @hakalaEvidenceRoleOxygenevolving2005].
 Repair of photoinactivated PSII relies on the removal of damaged PsbA [@mannInvolvementFtsHHomologue2000; @adamFtsHProteasesChloroplasts2005], followed by reassembly with newly synthesized PsbA [@nixonRecentAdvancesUnderstanding2010].
-Degradation of PsbA is a rate-limiting step in recovery from photoinhibition [@kanervoD1ProteinDegradation1993], mediated largely by a heterohexamer of (FtsH12)3, a membrane-bound (Sacharz et al., 2015)(Zak et al., 2001) metalloprotease  (Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
+Degradation of PsbA is a rate-limiting step in recovery from photoinhibition [@kanervoD1ProteinDegradation1993], mediated largely by a heterohexamer of (FtsH12)~3~, a membrane-bound (Sacharz et al., 2015)(Zak et al., 2001) metalloprotease  (Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
 [@adamFtsHProteasesChloroplasts2005; @boehmSubunitOrganizationSynechocystis2012a; @nixonRecentAdvancesUnderstanding2010; @komendaExposedNTerminalTail2007] (Pisareva et al., 2007; Sacharz et al., 2015),  @mannInvolvementFtsHHomologue2000, (AMANDA REF from ALGATECH).
 
-*Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4, homologs to the characterized FtsH isoforms of the model freshwater cyanobacterium *Synechocystis* FtsH, and with presumably parallel functions (table \@ref(tab:FtsHTable)).
-Upon a shift to higher light HLIII MED4 upregulated expression of FtsH1 and FtsH2 [@bonisteelStrainSpecificDifferences2018], homologs to the *Synechocystis* slr0228 and slr1604, implicated in PSII repair.
-In contrast representative LLIV strain MIT9313 showed less overall expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem.
+*Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4, homologs to the characterized FtsH isoforms of the model freshwater cyanobacterium *Synechocystis* FtsH, and with presumably parallel functions (Table \@ref(tab:FtsHTable)).
+Upon a shift to higher light HLI MED4 upregulated expression of FtsH1 and FtsH2 [@bonisteelStrainSpecificDifferences2018], homologs to the *Synechocystis* slr0228 and slr1604, implicated in PSII repair.
+In contrast, representative LLIV strain MIT9313 showed less overall expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem.
 Furthermore, MIT9313 expressed primarily FtsH3, homologous to *Synechocystis* slr1463 involved in PSI biogenesis, and  FtsH expression did not increase in response to light stress in MIT9313.
@@
 But only MED4 shows detected presence of the FtsH1 & FtsH2 isoforms inferred to mediate PSII repair, and then only in near-surface samples subject to higher light.
-Furthermore, even though MIT9313 grows (Figure \@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~] (Figure \@ref(fig:ProchloroPhotosynthDepthO2)), no  FtsH from MIT9313 is detected at low [O~2~], showing limited requirement for protein turnover under low [O~2~].
+Furthermore, even though MIT9313 grows (Figure \@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~] (Figure \@ref(fig:ProchloroPhotosynthDepthO2)), no FtsH from MIT9313 is detected at low [O~2~], suggesting limited requirement for protein turnover under low [O~2~].
 
@@
 Figure \@ref(fig:ProchlorococcusEnzymeKms) shows genes encoding enzymes for  *P.
-marinus* strains from Clades HLI, LLII, LLIII and LLII [@omarAnnotationGenesEncoding2023], compared to the measured or inferred K~M~ for [O~2~] for each enzyme CITATIONS.
+marinus* strains from Clades HLI, LLI, LLIII and LLIV [@omarAnnotationGenesEncoding2023], compared to the measured or inferred K~M~ for [O~2~] for each enzyme CITATIONS.
 MED4 increases expression of alternative oxidase ('ubiquinol oxidase (non electrogenic)')  to cope with changes in light [@bergResponsesPsbAHli2011], by dissipating electrons from the inter-system transport chain.
@@
 Conversely, a gene encoding (S)-2-hydroxy-acid oxidase is encoded in the MIT9313 genome.
-(S)-2-hydroxy-acid oxidase catalyzes the reaction of 2-hydroxy acid with O~2~ to produce toxic H~2~O~2~ [@InformationEC15].
+(S)-2-hydroxy-acid oxidase catalyzes the reaction of 2-hydroxy acid with O~2~ to produce toxic H~2~O~2~ [@cunaneCrystalStructureAnalysis2005].
 (S)-2-hydroxy-acid oxidase has an approximate K~M~ for [O~2~] of ~ 250 µM, and produces H~2~O~2~, so growth at lower [O~2~] may protect MIT9313 from auto-intoxication from production of H~2~O~2~.
@@
 MED4 can, however, grow under OMZ regions with slightly higher [O~2~], as demonstrated by the growth under our 25 µM O~2~ experiments.
-Genomic analyses  (Figure \@ref(fig:ProchlorococcusEnzymeKms))  and previous transcriptional analyses [@bergResponsesPsbAHli2011]  suggest MED4 is excluded from growth below ~ 25 µM O~2~ because it relies upon a ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction balance in the intersystem electron transport chain.
+Bioinformatic analyses  (Figure \@ref(fig:ProchlorococcusEnzymeKms))  and previous transcriptional analyses [@bergResponsesPsbAHli2011]  suggest MED4 is excluded from growth below ~ 25 µM O~2~ because it relies upon a ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction balance in the intersystem electron transport chain.
 On the other hand, MED4 shows inducible expression of FtsH isoforms [@bonisteelStrainSpecificDifferences2018], to counter photoinactivation of PSII under higher PAR and [O~2~] environments.
@@
 and LLIV ecotypes, using terminal restriction fragment length polymorphism analyses, at depths above 40 m, where light levels are
-higher, within OMZ, and by Figure\ref(fig:ProchloroPhotosynthDepthO2) showing PSII protein subunits annotated as derived from SS120 at all depths ranging
+higher, within OMZ, and by Figure \@ref(fig:ProchloroPhotosynthDepthO2) showing PSII protein subunits annotated as derived from SS120 at all depths ranging
 from 20 to 200 m and all [O~2~] in an OMZ of the tropical North Pacific Ocean.
@@
 The ability to utilize higher PAR and higher cumulative diel PUR under 25 µM or 2.5 µM O~2~ enables MIT9313 to grow in OMZ, even at depths closer to the surface.
-MIT9313 carries a gene encoding (S)-2-hydroxy-acid oxidase [@InformationEC15],  with a K~M~ for [O~2~] of ~ 250 µM (Figure \@ref(fig:ProchlorococcusEnzymeKms)), which produces H~2~O~2~.
+MIT9313 carries a gene encoding (S)-2-hydroxy-acid oxidase [@cunaneCrystalStructureAnalysis2005],  with a K~M~ for [O~2~] of ~ 250 µM (Figure \@ref(fig:ProchlorococcusEnzymeKms)), which produces H~2~O~2~.
 Growth at lower [O~2~] may protect MIT9313 from auto-intoxication from production of H~2~O~2~.

### 2024-02-29 Code/Manuscript_O2.Rmd
Fixed reference to new NATL Km figures

@@
 But only MED4 shows detected presence of the FtsH1 & FtsH2 isoforms inferred to mediate PSII repair, and then only in near-surface samples subject to higher light.
-Furthermore, even though MIT9313 grows (Figure \@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~] (Figure \@ref(fig:ProchloroPhotosynthDepthO2)), no FtsH from MIT9313 is detected at low [O~2~], suggesting limited requirement for protein turnover under low [O~2~].
+Furthermore, even though MIT9313 grows (Figure \@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~] (Figure \@ref(fig:NATLProchloroPhotosynthDepthO2)), no FtsH from MIT9313 is detected at low [O~2~], suggesting limited requirement for protein turnover under low [O~2~].
 
@@
 @delmontLinkingPangenomesMetagenomes2018 did not analyze data from depths beyond the subsurface chlorophyll maximum layer, the layer in the water column where the chlorophyll *a* concentration peaks, nor did they report the [O~2~] at those depths.
-Our growth findings are also consistent with Figure\@ref(fig:ProchloroPhotosynthDepthO2) showing PSII proteins annotated as MED4, at depths up to 200 meters with O~2~ of 15 µM.
+Our growth findings are also consistent with Figure\@ref(fig:NATLProchloroPhotosynthDepthO2) showing PSII proteins annotated as MED4, at depths up to 200 meters with O~2~ of 15 µM.
 
@@
 and LLIV ecotypes, using terminal restriction fragment length polymorphism analyses, at depths above 40 m, where light levels are
-higher, within OMZ, and by Figure \@ref(fig:ProchloroPhotosynthDepthO2) showing PSII protein subunits annotated as derived from SS120 at all depths ranging
+higher, within OMZ, and by Figure \@ref(fig:NATLProchloroPhotosynthDepthO2) showing PSII protein subunits annotated as derived from SS120 at all depths ranging
 from 20 to 200 m and all [O~2~] in an OMZ of the tropical North Pacific Ocean.
@@
 MIT9313 shows remarkable ability to thrive under very low [O~2~], potentially allowing it to expand into broader ecological niches.
-These results are supported by Figure \@ref(fig:ProchloroPhotosynthDepthO2) showing PSI protein subunits annotated as derived from MIT9313 detected at depths \> 120 m, along with PSII subunits at depths from 50 m to 200 m in regions where O~2~ was 15 µM.
+These results are supported by Figure \@ref(fig:NATLProchloroPhotosynthDepthO2) showing PSI protein subunits annotated as derived from MIT9313 detected at depths \> 120 m, along with PSII subunits at depths from 50 m to 200 m in regions where O~2~ was 15 µM.
 

### 2024-03-01 Code/Manuscript_O2.Rmd
Fixed some fig captions and citations

@@
                        "For comparison culture growth experimental conditions are indicated by horizontal grey lines for depths approximating imposed peak Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^); and vertical grey lines for [O~2~] (µM).",
-                       "Point colours identify *Prochlorococcus* clade assignments",
                        "Data obtained from OceanProteinPortal (https://www.oceanproteinportal.org/).",
@@
 Although *Prochlorococcus* is currently limited to a narrow range of surface photoperiods, potential poleward latitudinal expansions, in combination with attenuation of light with depth, mean *Prochlorococcus* may potentially encounter a wide range of photoperiods.
-Our growth rate determinations generally agreed with those from @mooreComparativePhysiologySynechococcus1995, for white LED and 250 µM O~2~, but our study is, to our knowledge, the first to analyze the interactive growth responses of *Prochlorococcus* strains to varying [O~2~], spectral wavebands and photoperiods.
+Our growth rate determinations generally agreed with those from Moore *et al*.
+[@mooreComparativePhysiologySynechococcus1995], for white LED and 250 µM O~2~, but our study is, to our knowledge, the first to analyze the interactive growth responses of *Prochlorococcus* strains to varying [O~2~], spectral wavebands and photoperiods.
 
@@
                        "Culture growth experimental conditions indicated by horizontal grey lines for depths approximating Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) and vertical grey lines for [O~2~] (µM).",
-                       "Point colours identify *Prochlorococcus* clade assignments",
                        "Data obtained from OceanProteinPortal (https://www.oceanproteinportal.org/).",
@@
 ProchlorococcusEnzymeKms_cap <- glue("**K~m~ values for oxygen metabolizing enzymes.**" ,
-                                     "The y-axis represents the log10 concentration of oxygen substrate (mM).",
+                                     "The y-axis represents the log10 concentration of oxygen substrate (µM).",
                                      "The x-axis represents the oxygen metabolizing enzymes encoded in at least one of the *Prochlorococcus marinus* strains in this study.",
@@
 
-@westNichePartitioningProchlorococcusPopulationsStratified1999 and @malmstromTemporalDynamicsProchlorococcus2010 found that decreased abundances of the LL clades corresponded to increased depth of the surface mixed layer.
-@malmstromTemporalDynamicsProchlorococcus2010 attributes the transport of LL ecotypes to the surface and consequent exposure to photoinhibitory high light levels as the reason for low cell abundances with increased mixed layer depth.
+West *et al*.
+[@westNichePartitioningProchlorococcusPopulationsStratified1999] and Malmstrom *et al*.
+[@malmstromTemporalDynamicsProchlorococcus2010] found that decreased abundances of the LL clades corresponded to increased depth of the surface mixed layer.
+Malmstrom *et al*.
+[@malmstromTemporalDynamicsProchlorococcus2010] attributes the transport of LL ecotypes to the surface and consequent exposure to photoinhibitory high light levels as the reason for low cell abundances with increased mixed layer depth.
 @westNichePartitioningProchlorococcusPopulationsStratified1999 found the depth of the mixed layer strongly influenced the depth transition from HL to LL clades, but that factors other than light levels may influence the variations in the upper and lower depth limits of these ecotypes.

### 2024-03-01 Code/Manuscript_O2.Rmd
Added Mireille edits

@@
 
-Under 250 µM O~2~ growth rates of *P.
-marinus* SS120, Clade LLIII, increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^ peak PAR and (Figure \@ref(fig:SS120PAR)).
+Under 250 µM O~2~, growth rates of *P.
+marinus* SS120, Clade LLIII, increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^ peak PAR and across all spectral wavebands (Figure \@ref(fig:SS120PAR)).
 No growth was observed under any blue light photoperiods when exposed to peak PAR of 90 µmol photons m^-2^ s^-1^ or greater.
-Growth rate, however increased with increasing photoperiods for white and red light under peak PAR of 90 µmol photons m^-2^ s^-1^.
-Growth rate decreased with longer photoperiods and showed growth inhibition at 12 and 16 h photoperiods under PAR of 180 µmol photons m^-2^ s^-1^  white, red or blue LED light.
+Growth rate, however increased with increasing photoperiods for white and red light under peak PAR of 90 µmol photons m^-2^ s^-1^ but showed growth inhibition at 16 h red light photoperiod.
+Growth rate decreased with longer photoperiods and showed growth inhibition at 12 and 16 h photoperiods under PAR of 180 µmol photons m^-2^ s^-1^  white LED, red or blue light.
 The µ~max~ was `r PURPARFits %>% filter(Strain == "SS120", WL == "WW", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ (Table \@ref(tab:MaxGrowthTable)) achieved under 90 µmol photons m^-2^ s^-1^ white LED light and 16 h photoperiod.
 
-Under 25 µM O~2~ and PAR of 30 µmol photons m^-2^ s^-1^ growth trends were similar to 250 µM O~2~. SS120 showed no
-growth under a 4 h photoperiod for red spectral waveband, however under blue light, SS120 was able to grow under a 4 h photoperiod (Figure
-\@ref(fig:SS120PAR)).
+Under 25 µM O~2~ and PAR of 30 µmol photons m^-2^ s^-1^ growth trends were similar to 250 µM O~2~.
+SS120 showed no growth under a 4 h photoperiod for red spectral waveband, however under blue light, SS120 was able to grow (Figure \@ref(fig:SS120PAR)).
 In contrast to the growth trends of the 250 µM O~2~ and PAR of 90 µmol photons m^-2^ s^-1^ experiments, SS120 grew under 4 and 8 h blue light and 16 h red light photoperiods, however the growth rate decreased under 12 and 16 h white LED light photoperiod treatments.
@@
 The GAM model in Figure \@ref(fig:SS120GAM) summarizes growth responses of SS120 to red (A,B) or blue (C,D) peak PAR and photoperiod, across the 2 imposed oxygen concentrations.
-Under 250 µM O~2~, Figure \@ref(fig:SS120GAM)C showed highest growth rates below PAR of 50 µmol photons m^-2^ s^-1^ and photoperiods between 8 and 12 h, indicated by the contour line labeled 0.19 d^-1^ (representing the 90^th^ percentile of achieved growth rate).
+Under 250 µM O~2~, Figure \@ref(fig:SS120GAM)C showed highest growth rates below blue light PAR of 50 µmol photons m^-2^ s^-1^ and photoperiods between 8 and 12 h, indicated by the contour line labeled 0.19 d^-1^ (representing the 90^th^ percentile of achieved growth rate).
 Under 250 µM O~2~ SS120 is constrained to deeper ocean waters through its intolerance of higher blue PAR levels.
-These findings align with @mooreComparativePhysiologySynechococcus1995 and are expected for a low light clade.
+These findings align with Moore *et al*.
+[@mooreComparativePhysiologySynechococcus1995] and are expected for a low light clade.
 The disjunct regions of the GAM plot results from variable growth success of SS120 under 250 µM O~2~.
 Growth rate patterns under red light were similar, although somewhat faster.
-In contrast, under 25 µM O~2~ and a photoperiod of 8 h SS120 exploited all blue peak PAR levels, achieving faster growth rates at a higher PAR of \~100 µmol photons m^-2^ s^-1^, indicated by the contour line labeled 0.4 d^-1^ (representing the 90^th^ percentile of achieved growth rate), out pacing the 90^th^ percentile fastest growth rates under 250 µM O~2~.
-Under red light and 25 µM O~2~ (Figure \@ref(fig:SS120GAM)B) SS120 grew across most conditions of peak PAR and photoperiod, achieving fastest growth under long photoperiods and peak PAR below 50 \~100 µmol photons m^-2^ s^-1^.
+In contrast, under 25 µM O~2~ and a photoperiod of 8 h SS120 exploited all blue peak PAR levels, achieving faster growth rates at a higher PAR of \~100 µmol photons m^-2^ s^-1^, indicated by the contour line labeled 0.4 d^-1^ (representing the 90^th^ percentile of achieved growth rate), out pacing the 90^th^ percentile fastest growth rates under 250 µM O~2~ (Figure \@ref(fig:SS120GAM)D).
+Under red light and 25 µM O~2~ (Figure \@ref(fig:SS120GAM)B) SS120 grew across most conditions of peak PAR and photoperiod, achieving fastest growth under long photoperiods and peak PAR between 50 \~100 µmol photons m^-2^ s^-1^.
 Thus, the designation of SS120 as a LL strain is dependent upon the [O~2~].
@@
 photoperiods, under low 30 µmol photons m^-2^ s^-1^ peak PAR, (Figure \@ref(fig:MIT9313PAR)).
-Under intermediate 90 µmol photons m^-2^ s^-1^ peak PAR growth rates decreased with increasing blue light photoperiod.
-Blue light did not induce growth at 180 µmol photons m^-2^ s^-1^ peak PAR, while MIT9313 showed only marginal growth under white LED and red light at 180 µmol photons m^-2^ s^-1^ peak PAR, under the 8 h photoperiod, consistent with [@moorePhotophysiologyMarineCyanobacterium1999].
+Under intermediate 90 µmol photons m^-2^ s^-1^ peak PAR growth rates decreased with increasing blue light photoperiods.
+Blue light did not induce growth at 180 µmol photons m^-2^ s^-1^ peak PAR, while MIT9313 showed only marginal growth under white LED and red light at 180 µmol photons m^-2^ s^-1^ peak PAR, under the 8 h photoperiod, consistent with Moore *et al*.
+[@moorePhotophysiologyMarineCyanobacterium1999].
 The µ~max~ was `r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 30 µmol photons m^-2^ s^-1^ blue light and 16 h photoperiod.
 
-For MIT9313 under 25 µM O~2~ growth rate increased with increasing photoperiods for all spectral wavebands tested (Figure \@ref(fig:MIT9313PAR)), with the fastest overall growth rate for MIT9313 
+For MIT9313 under 25 µM O~2~, growth rate increased with increasing photoperiods for all spectral wavebands tested (Figure \@ref(fig:MIT9313PAR)), with the fastest overall growth rate for MIT9313 
 `r PURPARFits %>% filter(Strain == "MIT9313", WL == "WW", O2_uM == "25", Photoperiod == 16, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under peak PAR of 90 µmol photons m^-2^ s^-1^ and 16 h white LED light photoperiod.
@@
 Growth estimates showed scatter among replicates, suggesting  2.5 µM O~2~  is near the tolerance limit for growth of MIT9313.
-Growth rates increased with longer photoperiods under blue light treatments under peak PAR of 90 µmol photons m^-2^ s^-1^ .
+Growth rates increased with longer photoperiods under blue light treatments and peak PAR of 90 µmol photons m^-2^ s^-1^ but did not grow under 16 h photoperiod.
 Growth  for MIT9313 under PAR of 180 µmol photons m^-2^ s^-1^ and blue light treatment decreased with increasing photoperiods with full growth inhibition under a 16 h photoperiod.
-The red light peak PAR of 180 µmol photons m^-2^ s^-1^ showed similar growth rates for 8 and 12 h photoperiods.
+The red light peak PAR of 180 µmol photons m^-2^ s^-1^ showed similar growth rates to blue light for 8 and 12 h photoperiods.
 The µ~max~ was `r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "2.5", Photoperiod == 12, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 12 h blue light photoperiod and PAR of 90 µmol photons m^-2^ s^-1^.
@@
 In contrast, under red light and 250 µM O~2~ MIT9313 grows faster while exploiting higher peak PAR and longer photoperiods.
-Figure \@ref(fig:MIT9313GAM)F shows that MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 4 and 8 h and peak blue PAR between 50 to 10 µmol photons m^-2^ s^-1^ PAR.
+Figure \@ref(fig:MIT9313GAM)E shows that MIT9313can exploit all blue PAR levels and most photoperiods with 90^th^ percentile of fastest growth rate between 30 to 100 µmol photons m^-2^ s^-1^ PAR.F igure \@ref(fig:MIT9313GAM)F shows that MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 4 and 8 h and peak blue PAR between 50 to 100 µmol photons m^-2^ s^-1^ PAR.
 Thus the designation of MIT9313 as a LL clade is dependent upon [O~2~] and light spectra.
@@
 Cumulative diel PUR can potentially collapse photoperiod, PAR and spectral wavebands to a common metric of photosynthetically active light absorbed per day.
-Cumulative diel PUR dose (µmol photons m^-2^ d^-1^) was calculated from the imposed PUR (µmol photons m^-2^ s^-1^) and photoperiod (h).
+Cumulative diel PUR dose (µmol photons m^-2^ d^-1^) was calculated from the imposed PUR XXX should say imposed PAR??
+or absorbed PUR ??
+XXX (µmol photons m^-2^ s^-1^) and photoperiod (h).
 We plotted growth rates vs.
@@
 Due to the absorption of *P.
-marinus* pigments in the blue spectral waveband range, the maximum imposed cumulative diel PUR under blue light is almost 3 times that of white LED light, and about 6 times the red light treatment, despite being derived from the same imposed photoperiods and peak PAR regimes.
+marinus* pigments in the blue spectral waveband range, the maximum imposed cumulative diel PUR under blue light is almost 3 times that of white LED light, and about 6 times the red light treatment (Figure \@ref(fig:PurParPlot)), despite being derived from the same imposed photoperiods and peak PAR regimes.
 As such, only blue light experiments extend beyond cumulative diel PUR of ~ 2 x 10^6^ µmol photons m^-2^ d^-1^.
-This bias in the range of data leads to caution in comparing model fits of growth in response cumulative diel PUR under red, vs.
-blue, wavebands.
+This bias in the range of data leads to caution in comparing model fits of growth in response to cumulative diel PUR under red vs.
+blue wavebands.
 
@@
 In parallel MED4 showed no growth under 2.5 µM O~2~, no matter the level of diel cumulative PUR.
-In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth under blue light was well described by a saturating response of growth [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] to increasing cumulative diel blue PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A), and no evidence of inhibition of growth at any achieved cumulative diel PUR.
-Under the 'artificial' growth treatment of red light, MED4 achieved more growth per unit diel cumulative PUR  \@ref(fig:BluevsRedPurFitsPlots)A), consistent with [@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for growth under red light, for MED4, because red light provokes less photoinactivation of PSII, than equivalent levels of blue light.
+In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth under blue light was well described by a saturating response of growth [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] to increasing cumulative diel PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A), and no evidence of inhibition of growth at any achieved cumulative diel PUR.
+Under the 'artificial' growth treatment of red light, MED4 achieved more growth per unit diel cumulative PUR (Figure \@ref(fig:BluevsRedPurFitsPlots)A), consistent with Murphy *et al*.
+[@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for growth under red light, for MED4, because red light provokes less photoinactivation of PSII, than equivalent levels of blue light.
 For distinct photoperiod fits refer to figure \@ref(fig:AllStrainPurFitsPlots)A.

### 2024-03-01 Code/Manuscript_O2.Rmd
minor edits

@@
 Three xenic cultures of *P. marinus* were obtained from Bigelow Labs, NCMA
-Maine, US (REFERENCE). MED4 (CCMP1986) is from High-Light adapted (HLI) clade; SS120
+Maine, USA. MED4 (CCMP1986) is from High-Light adapted (HLI) clade; SS120
 (CCMP1375) is from Low-Light adapted (LLIII) clade; and MIT9313 (CCMP2773)
@@
 [@R-minpack.lm], to fit a logistic
-equation (Equation \@ref(eq:GrowthRate))
+equation (Equation \@ref(eq:GrowthRate)); where ΔOD~max~ is maximum ΔOD, ΔOD~min~ is minimum ΔOD, t is time
+duration over the growth trajectory.
 
@@
 \end{equation}
-
-where ΔOD~max~ is maximum ΔOD, ΔOD~min~ is minimum ΔOD, t is time
-duration over the growth trajectory.
 
@@
 
-An integrated weighting equation \@ref(eq:WeightedPUR) [@morelAvailableUsableStored1978] was used to determine the weighted PUR spectrum P(λ),
+An integrated weighting equation \@ref(eq:WeightedPUR) [@morelAvailableUsableStored1978] was used to determine the weighted PUR spectrum P(λ); where A(λ) is the blank subtracted, Chl a~2~ peak normalized whole cell absorbance spectrum for each *P.
+marinus* ecotype, over 400 nm to 700 nm, A(λ); and E(λ) is the peak normalized emission spectrum of the imposed LED growth light, over 400 nm to 700 nm.
 
@@
 
-where A(λ) is the blank subtracted, Chl a~2~ peak normalized whole cell absorbance spectrum for each *P.
-marinus* ecotype, over 400 nm to 700 nm, A(λ); and E(λ) is the peak normalized emission spectrum of the imposed LED growth light, over 400 nm to 700 nm.
-
-Actinic PUR levels (µmol photons m^-2^ s^-1^) were calculated from actinic PAR (µmol photons m^-2^ s^-1^) levels using the equation \@ref(eq:PUR) from [@morelAvailableUsableStored1978],
+Actinic PUR levels (µmol photons m^-2^ s^-1^) were calculated from actinic PAR (µmol photons m^-2^ s^-1^) levels using the equation \@ref(eq:PUR) from [@morelAvailableUsableStored1978]; where P(λ) is the weighted PUR absorbance spectrum from equation \@ref(eq:WeightedPUR), E(λ) is the imposed growth light emission spectrum from equation \@ref(eq:WeightedPUR) and PAR is the imposed peak light level (µmol photons m^-2^ s^-1^).
+Figure (\@ref(fig:PurParPlot)) shows the calculated absorbed peak PUR (µmol photons m^-2^ d^-1^) versus imposed actinic peak PAR (µmol photons m^-2^ s^-1^) for each strain and each spectral waveband (nm).
 
@@
 
-where P(λ) is the weighted PUR absorbance spectrum from equation \@ref(eq:WeightedPUR), E(λ) is the imposed growth light emission spectrum from equation \@ref(eq:WeightedPUR) and PAR is the imposed peak light level (µmol photons m^-2^ s^-1^).
-Figure (\@ref(fig:PurParPlot)) shows the calculated absorbed peak PUR (µmol photons m^-2^ d^-1^) versus imposed actinic peak PAR (µmol photons m^-2^ s^-1^) for each strain and each spectral waveband (nm).
-
 The applied photoperiods were delivered using the sine circadian light function of the PSI Multicultivator to simulate light exposure approximating sun rise through to sunset.
-The area under the sinusoidal curves is equivalent to the area of a triangular photoregime of equivalent photoperiod (Campbell, unpub), therefore the equation to determine the cumulative diel PUR (µmol photons m^-2^ d^-1^) is one half of the base (photoperiod) multiplied by the height (PUR) (Equation \@ref(eq:SumPURDay)),
+The area under the sinusoidal curves is equivalent to the area of a triangular photoregime of equivalent photoperiod (Campbell, unpub), therefore the equation to determine the cumulative diel PUR (µmol photons m^-2^ d^-1^) is one half of the base (photoperiod) multiplied by the height (PUR) (Equation \@ref(eq:SumPURDay)); where PUR is the actinic absorbed light calculated from equation \@ref(eq:PUR) (µmol photons m^-2^ s^-1^), 3600 is the time conversion from seconds to hour and photoperiod is the imposed photoperiod (h).
 
@@
 \end{equation}
-
-where PUR is the actinic absorbed light calculated from equation \@ref(eq:PUR) (µmol photons m^-2^ s^-1^), 3600 is the time conversion from seconds to hour and photoperiod is the imposed photoperiod (h).
 
@@
 
-We fit the response of chlorophyll specific growth rate to cumulative diel PUR using the equation of Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] across strain and [O~2~] to first compare growth response between 660 nm (red) and 450 nm (blue) growth light and second to compare growth response between specific photoperiods (4 h, 8 h, 12 h, 16 h) and a fit across the pooled photoperiod data.
-To examine statistical differences between the modeled fits, we performed one-way ANOVA comparing the model output parameters assigning significant differences when p < 0.05.
+We fit the response of chlorophyll specific growth rate to cumulative diel PUR using the equation of Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] across strain and [O~2~] to compare growth response between 660 nm (red) and 450 nm (blue) growth light and additionally, to compare growth response between specific photoperiods (4 h, 8 h, 12 h, 16 h) and a fit across pooled photoperiod data.
+To examine statistical differences between the modeled fits, we performed one-way ANOVA comparing the model output parameters assigning significant differences when the p value was < 0.05.
 
@@
 Guided by the evidence of ocean distributions of proteins from *Prochlorococcus* we set up a matrix of photoperiods, PAR, spectral bands, and [O~2~] to approximate current, and potential future, latitudinal, depth and seasonal niches for *Prochlorococcus* strains.
-We earlier found [@murphyPhotoinactivationPhotosystemII2017] that growth under red light could prove mechanistically informative as to factors limiting *Prochlorococcus* growth, so we included that spectral band even though it is not characteristic of representative *Prochlorococcus* niches.
+As aforementioned, growth under red light could prove mechanistically informative [@murphyPhotoinactivationPhotosystemII2017] to factors limiting *Prochlorococcus* growth, we therefore included the red spectral waveband even though it is not characteristic of representative *Prochlorococcus* niches.
 Although *Prochlorococcus* is currently limited to a narrow range of surface photoperiods, potential poleward latitudinal expansions, in combination with attenuation of light with depth, mean *Prochlorococcus* may potentially encounter a wide range of photoperiods.
@@
 Figure \@ref(fig:ProchlorococcusEnzymeKms) shows genes encoding enzymes for  *P.
-marinus* strains from Clades HLI, LLI, LLIII and LLIV [@omarAnnotationGenesEncoding2023], compared to the measured or inferred K~M~ for [O~2~] for each enzyme CITATIONS.
+marinus* strains from clades HLI, LLI, LLIII and LLIV [@omarAnnotationGenesEncoding2023], compared to the measured or inferred K~M~ for [O~2~] for each enzyme XXXX CITATION  to Table once added XXXX.
 MED4 increases expression of alternative oxidase ('ubiquinol oxidase (non electrogenic)')  to cope with changes in light [@bergResponsesPsbAHli2011], by dissipating electrons from the inter-system transport chain.
@@
 *Prochlorococcus* are highly susceptible to hydrogen peroxide (H~2~O~2~) toxicity as they lack genes which scavenge H~2~O~2~ molecules [@morrisFacilitationRobustGrowth2008].
-The small cell size of *Prochlorococcus* allow the reactive oxygen species (ROS), H~2~O~2~, to cross the cell membrane [@omarGenomicCapacitiesReactive2023]; however, accumulation of extracellular H~2~O~2~ remains toxic to *Prochlorococcus* [@morrisFacilitationRobustGrowth2008,  @morrisDependenceCyanobacteriumProchlorococcus2011].
+The small cell size of *Prochlorococcus* allow the reactive oxygen species (ROS), H~2~O~2~, to cross the cell membrane [@omarDiffusionalInteractionsMarine2022]; however, accumulation of extracellular H~2~O~2~ remains toxic to *Prochlorococcus* [@morrisFacilitationRobustGrowth2008,  @morrisDependenceCyanobacteriumProchlorococcus2011].
 
@@
 MED4 can, however, grow under OMZ regions with slightly higher [O~2~], as demonstrated by the growth under our 25 µM O~2~ experiments.
-Bioinformatic analyses  (Figure \@ref(fig:ProchlorococcusEnzymeKms))  and previous transcriptional analyses [@bergResponsesPsbAHli2011]  suggest MED4 is excluded from growth below ~ 25 µM O~2~ because it relies upon a ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction balance in the intersystem electron transport chain.
+Genomic analyses (Figure \@ref(fig:ProchlorococcusEnzymeKms))  and previous transcriptional analyses [@bergResponsesPsbAHli2011]  suggest MED4 is excluded from growth below ~ 25 µM O~2~ because it relies upon a ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction balance in the intersystem electron transport chain.
 On the other hand, MED4 shows inducible expression of FtsH isoforms [@bonisteelStrainSpecificDifferences2018], to counter photoinactivation of PSII under higher PAR and [O~2~] environments.

### 2024-03-01 Code/Manuscript_O2.Rmd
minior edit

@@
 marinus* contribute 13 to 48% of net primary production in oligotrophic oceans, corresponding to about 30% of global oxygen production [@partenskyProchlorococcusMarinePhotosynthetic1999].
-*Prochlorococcus marinus* growth is currently limited to between latitudes of 40°N to 40°S in open ocean waters, from surface to 300 m depth, thus spanning 3 orders of magnitudes of light irradiance [@partenskyProchlorococcusMarinePhotosynthetic1999; @chisholmProchlorococcusMarinusNov1992 ].
-
-*Prochlorococcus marinus* is functionally differentiated from other cyanobacteria primarily by the absence of phycobilisomes [@chisholmProchlorococcusMarinusNov1992].
-Instead, *Prochlorococcus*  uses intra-membrane Prochlorophyte chlorophyll binding (Pcb) proteins binding divinyl chlorophyll *a* and *b*, and α-carotene, as major light harvesting complexes [@goerickePigmentsProchlorococcusMarinus1992]; [@larocheIndependentEvolutionProchlorophyte1996], with diversity in the number of genes encoding Pcb, expression of Pcb under changing light [@garczarekMultiplicationAntennaGenes2000; @rocapGenomeDivergenceTwo2003], and in thylakoid organization [@partenskyProchlorococcusMarinePhotosynthetic1999].
-The genes encoding much of the photosynthetic apparatus are highly conserved in *Prochlorococcus* [@kettlerPatternsImplicationsGene2007], though the photosynthetic efficiency may vary among clades [@hessPhotosyntheticApparatusProchlorococcus2001; @moorePhotophysiologyMarineCyanobacterium1999].
+*Prochlorococcus marinus* growth is currently limited to between latitudes of 40°N to 40°S in open ocean waters, from surface to 300 m depth, thus spanning 3 orders of magnitudes of light irradiance [@partenskyProchlorococcusMarinePhotosynthetic1999; @chisholmProchlorococcusMarinusNov1992].
 
@@
 
-Photosynthetic organisms absorb light energy within the Photosynthetically Active Radiation (PAR) range, 350 to 700 nm, for photosynthesis [@morelAvailableUsableStored1978].
+Genes encoding much of the photosynthetic apparatus is highly conserved in *Prochlorococcus* [@kettlerPatternsImplicationsGene2007], Photosynthetic organisms absorb light energy within the Photosynthetically Active Radiation (PAR) range, 350 to 700 nm, for photosynthesis [@morelAvailableUsableStored1978].
 Photosynthetically Usable Radiation (PUR) represents the fraction of PAR that is absorbed by the pigments of a given photosynthetic organism [@morelAvailableUsableStored1978], taking into account the specific spectral wavebands these pigments absorb.
-*Prochlorococcus marinus* light-harvesting complexes show an absorption maxima
-of 442 nm for divinyl chlorophyll *a* and 478 nm for divinyl chlorophyll *b* [@goerickePigmentsProchlorococcusMarinus1992] allowing *P.
-marinus* to efficiently harvest blue light in the 400 nm to 500 nm range [@morelAvailableUsableStored1978] where only blue spectral wavelengths prevail in deep ocean habitats [@holtropVibrationalModesWater2021].
+*Prochlorococcus marinus* light-harvesting complexes show an absorption maxima of 442 nm for divinyl chlorophyll *a* and 478 nm for divinyl chlorophyll *b* [@goerickePigmentsProchlorococcusMarinus1992] allowing *P.
+marinus* to efficiently harvest blue light in the 400 nm to 500 nm range [@morelAvailableUsableStored1978] where only blue spectral wavelengths prevail in deep ocean habitats [@holtropVibrationalModesWater2021], thus photosynthetic efficiency may vary among clades [@hessPhotosyntheticApparatusProchlorococcus2001; @moorePhotophysiologyMarineCyanobacterium1999].
 In *P.
 marinus* small cell diameters, from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992], and simple cell structures, minimize the complication of pigment package effect or intracellular self-shading [@morelProchlorococcusSynechococcusComparative1993] contributing to efficient optical absorption.
+
 Given the different spectral light regimes typical of the niches of different ecotypes, expressing growth rates in terms of cumulative diel PUR might simplify different photoperiods, spectral bands, and PAR levels into a common parameter, making growth response comparisons across strains and different oxygen levels more accessible.
@@
 	iii) Sample station depth and [O~2~].  
-	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using *tidyverse* package [@R-tidyverse] running under R vXXX and RStudio v1.2.5019 (https://posit.co/)  (LOCATION OF CODE ON GITHUB).
+	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using *tidyverse* package [@R-tidyverse] running under R v4.1.3 and RStudio v2023.06.0 XXX Naaman to get location (https://posit.co/)  XXX.
 The resulting merged dataset was filtered for those *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b~6~f (Cytb~6~f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Plastoquinol Terminal Oxidase (PTOX); Plastocyanin (PC); Ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  ATP Synthase;  FtsH proteases (FtsH) or ribosomes.

### 2024-03-01 Code/ManuscriptGenome.Rmd
Create ManuscriptGenome.Rmd

---
title: "R Notebook"
output: html_notebook
---

```{r, import libraries, include = FALSE}
library(tidyverse)
library(glue)

googlesheets4::gs4_deauth()

```

```{r, assign filepaths, include = FALSE}
DataIn <- file.path("..","Data", "CleanData")
Figures <- file.path("..", "Figures")
# BLAST <- file.path("..", "BLAST")
```

```{r define notin}
`%notin%` <- negate(`%in%`)
```

combinedHits can be found on https://doi.org/10.5061/dryad.kh1893284. Filtered to only include Prochlorococcus genomes.
```{r}
# DataIn <- read_csv(file.path(Data, "combinedHits.csv")) %>% 
#   group_by(EC, genome) %>%
#   mutate(Gene_count = n()) %>%
#   ungroup() %>%
#   group_by(genome) %>%
#   mutate(TotalDetectedEnzymes = n()) %>%
#   ungroup()  %>%
#   distinct(genome, EC, .keep_all = TRUE)
# 
# MetaData <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1kXm0GvMdTRbF12cG5Bps-2e_4MTjgUX7iUOjqiu-_c0/edit#gid=0") %>%
#   dplyr::select(c(Genus, species, Strain, FileName, Ome, Taxa, Rad1_um, Rad2_um, Rad3_um, Flagella, GenomeSize_mbp, GeneModels_count, Latitude, Longitude, Marine, PennateCentric, ColonySpecies)) %>% 
#   mutate(Strain = as.character(Strain))
# 
# O2_Enzymes <- read_csv(file.path(Data, "OxygenEnzymes.csv"))
# 
# 
# KOROSEnzymes <- O2_Enzymes %>% 
#   # select(EC, KO, PriSec, ) %>%
#   separate_rows(KO, sep = ";")
# 
# O2_Enzymes_Km <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1wH2PZpsIDyA_WGfMr53Bm_HwmR0z5W93ed-LgRdLPVw/edit#gid=0") %>%
#   group_by(EC) %>%
#   mutate(AvgKm_mM = mean(Km_mM)) %>%
#   ungroup()
# 
# MergedData <- full_join(x = MetaData, y = KOROSEnzymes, by = character()) %>%
#   left_join(., DataIn, by = c("FileName" = "genome", "EC" = "EC")) %>%
#   left_join(., O2_Enzymes_Km, by = c("EC")) %>%
#   filter(!is.na(FileName))# %>%
#   # filter(Taxa == "Prokaryote") #%>%
#   # complete(., nesting(FileName, EC), fill = list(Gene_count = 0))
# 
# # KOCombinedHits <- DataIn %>%
# #   separate_rows(KEGG_ko, sep = ",") %>%
# #   mutate_at("KEGG_ko", str_replace, "ko:", "") %>%
# #   filter(is.na(EC),
# #          !is.na(KEGG_ko),
# #          KEGG_ko != "-") %>%
# #   left_join(., 
# #             O2_Enzymes %>%
# #               select(EC, KO) %>%
# #               separate_rows(KO, sep = ";"), 
# #             by = c("KEGG_ko" = "KO")) %>%
# #   filter(!is.na(EC)) %>%
# #   select(-EC) %>%
# #   rename(EC = EC) %>%
# #   distinct(genome, query_name, EC, .keep_all = FALSE)
# 
# 
# 
# MergedData %<>%
#   mutate(Rad1_um = as.numeric(Rad1_um),
#          Rad2_um = as.numeric(Rad2_um),
#          Rad3_um = as.numeric(Rad3_um),
#          SA_um2 = 4*pi*(((((Rad1_um*Rad2_um)^1.6)+((Rad1_um*Rad3_um)^1.6)+((Rad2_um*Rad3_um)^1.6))/3)^0.625),
#          Volume_um3 = (4/3)*pi*Rad1_um*Rad2_um*Rad3_um,
#          SAVol_um = SA_um2/Volume_um3,
#          Gene_count = as.numeric(Gene_count),
#          #Diameter = as.numeric(Rad1_um*2),
#          # Radius_um = dplyr::rowwise(as.numeric(Rad1_um)) %>% min(.$Rad1_um, .$Rad2_um, .$Rad3_um),
#          Radius_um = as.numeric(Rad1_um),
#          log_Radius_um = log10(as.numeric(Rad1_um)),
#          log_GenomeSize_mbp = log10(as.numeric(GenomeSize_mbp)),
#          log_GeneModels_count = log10(as.numeric(GeneModels_count)),
#          log_Gene_count = log10(as.numeric(Gene_count)+1),
#          Latitude = as.numeric(as.character(Latitude)),
#          abs_Latitude = abs(Latitude),
#          log_Volume_um3 = log10(as.numeric(Volume_um3)),
#          log_SA_um2 = log10(as.numeric(SA_um2)),
#          GeneModels_count = as.numeric(GeneModels_count),
#          log_SAVol_um = log10(as.numeric(SAVol_um)), 
#          Name = interaction(Genus, species, Strain, sep = " ")) %>%
#   filter(Taxa != "Symbiodinium", 
#          Marine == "yes",
#          FileName != "Nitzschia_palea-dna-trans") 
# 
# ProchlorococcusGenomeData <- MergedData %>% 
#   filter(Genus == "Prochlorococcus")
# 
# saveRDS(object = ProchlorococcusGenomeData, file = file.path("..", "Data", "ProchlorococcusGenomeData.Rds"))
```

```{r}
MergedData <- readRDS(file.path(DataIn, "ProchlorococcusGenomeData.Rds"))
```

```{r, , fig.width = 7, fig.height = 5}
MergedData %>%
  filter(!is.na(Gene_count),
         Taxa == "Prokaryote") %>%
  group_by(EC) %>%
  mutate(Km_mM_min = min(Km_mM), 
         Km_mM_max = max(Km_mM)) %>% 
  ggplot() +
  geom_errorbar(aes(x = reorder(EnzymeName, Km_mM), ymin = log10(Km_mM_min), ymax = log10(Km_mM_max))) +
  geom_point(aes(x = reorder(EnzymeName, Km_mM), y = log10(Km_mM), color = log10(Km_mM))) +
  geom_hline(yintercept = log10(1e-3), linetype = "dotted") +
  geom_hline(yintercept = log10(5e-3), linetype = "dotted") +
  geom_hline(yintercept = log10(230e-3), linetype = "dotted", color = "red") +
  geom_hline(yintercept = log10(290e-3), linetype = "dotted", color = "red") +
  scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
  theme_bw() +
  ggpubr::rotate_x_text(angle = 70) 
```

```{r add flv to MergedData}
# Values are according to paper https://doi.org/10.3390/life5010716
MergedData <- MergedData %>% 
  add_row(Strain = "CCMP1375", Ome = "Genome", Taxa = "Prokaryote", EnzymeName = "Flavodiiron (Flv1a/3a)", Gene_count = 1, Estimated = 0, Genus = "Prochlorococcus", Km_mM  = 200/1000) %>% 
  add_row(Strain = "CCMP1986", Ome = "Genome", Taxa = "Prokaryote", EnzymeName = "Flavodiiron (Flv1a/3a)", Gene_count = 1, Estimated = 0, Genus = "Prochlorococcus", Km_mM  = 200/1000) %>% 
  add_row(Strain = "MIT9313", Ome = "Genome", Taxa = "Prokaryote", EnzymeName = "Flavodiiron (Flv1a/3a)", Gene_count = 1, Estimated = 0, Genus = "Prochlorococcus", Km_mM  = 200/1000) %>% 
  add_row(Strain = "NATL2A", Ome = "Genome", Taxa = "Prokaryote", EnzymeName = "Flavodiiron (Flv1a/3a)", Gene_count = 1, Estimated = 0, Genus = "Prochlorococcus", Km_mM  = 200/1000) %>% 
  add_row(Strain = "CCMP1375", Ome = "Genome", Taxa = "Prokaryote", EnzymeName = "Flavodiiron (Flv1a/3a)", Gene_count = 1, Estimated = 0, Genus = "Prochlorococcus", Km_mM  = 2/1000) %>% 
  add_row(Strain = "CCMP1986", Ome = "Genome", Taxa = "Prokaryote", EnzymeName = "Flavodiiron (Flv1a/3a)", Gene_count = 1, Estimated = 0, Genus = "Prochlorococcus", Km_mM  = 2/1000) %>% 
  add_row(Strain = "MIT9313", Ome = "Genome", Taxa = "Prokaryote", EnzymeName = "Flavodiiron (Flv1a/3a)", Gene_count = 1, Estimated = 0, Genus = "Prochlorococcus", Km_mM  = 2/1000) %>% 
  add_row(Strain = "NATL2A", Ome = "Genome", Taxa = "Prokaryote", EnzymeName = "Flavodiiron (Flv1a/3a)", Gene_count = 1, Estimated = 0, Genus = "Prochlorococcus", Km_mM  = 2/1000) %>% 
  add_row(Strain = "CCMP1375", Ome = "Genome", Taxa = "Prokaryote", EnzymeName = "Flavodiiron (Flv1a/3a)", Gene_count = 1, Estimated = 0, Genus = "Prochlorococcus", Km_mM  = 7/1000) %>% 
  add_row(Strain = "CCMP1986", Ome = "Genome", Taxa = "Prokaryote", EnzymeName = "Flavodiiron (Flv1a/3a)", Gene_count = 1, Estimated = 0, Genus = "Prochlorococcus", Km_mM  = 7/1000) %>% 
  add_row(Strain = "MIT9313", Ome = "Genome", Taxa = "Prokaryote", EnzymeName = "Flavodiiron (Flv1a/3a)", Gene_count = 1, Estimated = 0, Genus = "Prochlorococcus", Km_mM  = 7/1000) %>% 
  add_row(Strain = "NATL2A", Ome = "Genome", Taxa = "Prokaryote", EnzymeName = "Flavodiiron (Flv1a/3a)", Gene_count = 1, Estimated = 0, Genus = "Prochlorococcus", Km_mM  = 7/1000)

```

```{r, ProchlorococcusEnzymeKms, fig.cap = ProchlorococcusEnzymeKms_cap, fig.width = 20, fig.height = 10}
ProchlorococcusEnzymeKms_cap <- glue("**Comparison of log~10~(K~m~ for O~2~ in mM) vs.genes encoding O~2~ utilizing enzymes in *Prochlorococcus***, faceted by their respective strains.",
                                     "Symbol color corresponds to number of genes encoding O~2~ utilizing enzymes.",
                                     "Symbol shape corresponds to whether the K~m~ was measured in the respective enzyme, or inferred from the K~m~ of a similar enzyme.",
                                     "Black vertical line corresponds to the range of K~m~ for O~2~.",
                                     "Vertical translucent bars correspond to concentrations of O~2~ in which *Prochlorococcus* strains were grown.",
                                     "K~m~ values were obtained from other organisms, excluding Ribulose bisphosphate carboxylase.",
                                     "Symbol absence means no sequences were detected in the genome."
                                     )

ProchlorococcusEnzymeKms <- MergedData %>%
  filter(!is.na(Gene_count),
         Genus == "Prochlorococcus",
         Strain %in% c("CCMP1375", "CCMP1986", "MIT9313", "NATL2A"),
         !is.na(Estimated),
         Taxa == "Prokaryote") %>% 
  mutate(StrainLabel = case_when(Strain == "CCMP1375" ~ "SS120",
                                 Strain == "CCMP1986" ~ "MED4",
                                 Strain == "MIT9313" ~ "MIT9313",
                                 Strain == "NATL2A" ~ "NATL2A")) %>%
  mutate(StrainLabel = factor(StrainLabel, levels = c("MED4", "NATL2A", "SS120", "MIT9313"))) %>%
  group_by(EC) %>%
  mutate(Km_mM_min = min(Km_mM, na.rm = TRUE), 
         Km_mM_max = max(Km_mM, na.rm = TRUE),
         Gene_count = as.character(Gene_count)) %>%
  mutate(Km_mM = case_when(Genus == "Prochlorococcus" & EC == "4.1.1.39" ~ 1.4,
                           TRUE ~ Km_mM),
         Km_mM_min = case_when(Genus == "Prochlorococcus" & EC == "4.1.1.39" ~ 1.4,
                           TRUE ~ Km_mM_min),
         Km_mM_max = case_when(Genus == "Prochlorococcus" & EC == "4.1.1.39" ~ 1.4,
                           TRUE ~ Km_mM_max)) %>% 
  # mutate(Km_mM = case_when(EnzymeName == "Flavodiiron (Flv1a/3a)" ~ 10/1000,
  #                          TRUE ~ Km_mM)) %>% 
  ungroup() %>% 
  ggplot() +
  geom_errorbar(aes(x = reorder(EnzymeName, Km_mM * 1000), ymin = log10(Km_mM_min* 1000), ymax = log10(Km_mM_max* 1000))) +
  # geom_ribbon(aes(ymin = log10(5e-4), ymax =  log10(5e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "blue") +
  # geom_ribbon(aes(ymax = log10(5e-2), ymin =  log10(5e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "green") +
  # geom_ribbon(aes(ymax = log10(280e-3), ymin =  log10(230e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "#FF0000") +
  annotate(geom = "rect", ymin = log10(5e-4 * 1000), ymax =  log10(5e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "blue") +
  annotate(geom = "rect", ymax = log10(5e-2 * 1000), ymin =  log10(5e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "green") +
  annotate(geom = "rect", ymax = log10(280e-3 * 1000), ymin =  log10(230e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "#FF0000") +
  geom_point(aes(x = reorder(EnzymeName, Km_mM* 1000), y = log10(Km_mM* 1000), shape = as.logical(Estimated), size = Gene_count), stroke = 1) +
  geom_vline(aes(xintercept = reorder(EnzymeName, Km_mM* 1000)), size = 2,  data = . %>% filter(is.na(Km_mM)), linetype = "solid") +
  geom_text(aes(x = 18.5, y = 0.25, label = "[O2] ≈ 2.5 µM"), color = "blue", size = 6) +
  geom_text(aes(x = 18.5, y = 1.2, label = "[O2] ≈ 25 µM"), color = "darkgreen", size = 6) +
  geom_text(aes(x = 18.5, y = 2.5, label = "[O2] ≈ 250 µM"), color = "#FF0000", size = 6) +
  # geom_hline(yintercept = log10(5e-4), linetype = "dotted") +
  # geom_hline(yintercept = log10(5e-3), linetype = "dotted") +
  # geom_hline(yintercept = log10(5e-3), linetype = "dotted", color = "brown") +
  # geom_hline(yintercept = log10(5e-2), linetype = "dotted", color = "brown") +
  # geom_hline(yintercept = log10(230e-3), linetype = "dotted", color = "red") +
  # geom_hline(yintercept = log10(290e-3), linetype = "dotted", color = "red") +
  # scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
  ggh4x::facet_nested(rows = vars(StrainLabel)) +
  theme_bw() +
  ggpubr::rotate_x_text(angle = 80) +
  scale_shape_manual(values = c(19,8), labels = c("FALSE" = "Measured", "TRUE" = "Inferred")) +
  scale_color_brewer(palette="Dark2") +
  labs(# title = ~K[m] ~O[2] ~  "for *Prochlorococcus* Enzymes using Oxygen", # "Estimates of Affinities of *Prochlorococcus* Enzymes for Oxygen" # "Affinities for Phytoplankton Enzymes for Oxygen", 
       x = "Enzyme Name",
       y = ~log[10] ~ "("~K[m] ~O[2] ~"(µM))",
       size = "Gene Count",
       shape = ""~K[m]) +
  guides(shape = guide_legend(override.aes = list(size=5))) +
   theme(axis.title = element_text(size = 45, color = "black"),
         axis.title.x = element_text(vjust=8),
         axis.title.y = element_blank(),
         title = element_text(size = 30),
         axis.text.x = element_text(size = 30, color = "black"),
        axis.text.y = element_text(size = 20, color = "black"),
        strip.text = element_text(size = 30),
        legend.key.size = unit(2, 'cm'), #change legend key size
        # legend.key.height = unit(2, 'cm'), #change legend key height
        # legend.key.width = unit(1, 'cm'), #change legend key width
        legend.title =  element_text(size = 30),  #change legend title font size
        legend.text = element_text(size = 30))   #change legend text font size

ProchlorococcusEnzymeKms
```

```{r, ProchlorococcusEnzymeKms ggsave, include = FALSE} 
ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms.png"), plot = ProchlorococcusEnzymeKms, height = 23, width = 20)
```

```{r, DiatomEnzymeKms, fig.width = 20, fig.height = 20}
DiatomEnzymeKms <- MergedData %>%
  filter(!is.na(Gene_count),
         Taxa == "Diatom",
         !is.na(Estimated)) %>%
  # mutate(StrainLabel = case_when(Strain == "CCMP1375" ~ "SS120",
  #                                Strain == "CCMP1986" ~ "MED4",
  #                                Strain == "MIT9313" ~ "MIT9313",
  #                                Strain == "NATL2A" ~ "NATL2A")) %>%
  # mutate(StrainLabel = factor(StrainLabel, levels = c("MED4", "NATL2A", "SS120", "MIT9313"))) %>%
  group_by(EC) %>%
  mutate(Km_mM_min = min(Km_mM, na.rm = TRUE), 
         Km_mM_max = max(Km_mM, na.rm = TRUE),
         Gene_count = as.character(Gene_count)) %>%
  ungroup() %>%
  mutate(Latitude = case_when(species == "multistrata" & Strain == "B856" ~ 40.485, #https://doi.org/10.1111/nph.14557
                              species == "inconspicua" & Strain == "GAI-293" ~ 21.57, #https://doi.org/10.1038/s41598-021-95106-3
                              species == "robusta" & Strain == "D6" ~ 51.01, #https://bccm.belspo.be/catalogues/dcg-strain-details?ACCESSION_NUMBER=DCG%200498&LIST1=&TEXT1=&LIST2=&TEXT2=&LIST3=&TEXT3=&LIST4=&TEXT4=&LIST5=&TEXT5=&CONJ=
                              TRUE ~ Latitude)) %>% 
  mutate(Polar = case_when(Latitude > 59 ~ "Polar",
                           Latitude < -59 ~ "Polar",
                           is.na(Latitude) ~ "Unknown",
                           TRUE ~ "Non Polar")) %>% 
  filter(Polar != "Unknown") %>% 
  filter(Genus %notin% c("Chaetoceros", "Amphora", "Extubocellulus"),
         species %notin% c("minuscula")) %>% #select(Genus, species, Strain, Polar, Ome) %>% unique()
  ggplot() +
  geom_errorbar(aes(x = reorder(EnzymeName, Km_mM), ymin = log10(Km_mM_min), ymax = log10(Km_mM_max))) +
  # geom_ribbon(aes(ymin = log10(5e-4), ymax =  log10(5e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "blue") +
  # geom_rect(ymin = log10(5e-4), ymax =  log10(5e-3), xmin = -Inf, xmax = Inf, alpha = 0.03, fill = "blue") +
  annotate(geom = "rect", ymin = log10(5e-4), ymax =  log10(5e-3), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "blue") +
  annotate(geom = "rect", ymax = log10(5e-2), ymin =  log10(5e-3), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "green") +
  annotate(geom = "rect", ymax = log10(280e-3), ymin =  log10(230e-3), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "#FF0000") +
  # geom_ribbon(aes(ymax = log10(5e-2), ymin =  log10(5e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "green") +
  # geom_ribbon(aes(ymax = log10(280e-3), ymin =  log10(230e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "#FF0000") +
  geom_point(aes(x = reorder(EnzymeName, Km_mM), y = log10(Km_mM), color = Gene_count, shape = as.logical(Estimated)), size = 5, stroke = 2) +
  geom_text(aes(x = 16.5, y = -2.8, label = "[O2] ≈ 2.5 µM"), color = "blue", size = 6) +
  geom_text(aes(x = 16.5, y = -1.8, label = "[O2] ≈ 25 µM"), color = "darkgreen", size = 6) +
  geom_text(aes(x = 16.5, y = -0.35, label = "[O2] ≈ 250 µM"), color = "#FF0000", size = 6) +
  geom_vline(aes(xintercept = reorder(EnzymeName, Km_mM), color = Gene_count), size = 5,  data = . %>% filter(is.na(Km_mM)), linetype = "solid") +
  ggh4x::facet_nested(rows = vars(Polar, interaction(Genus, species))) +
  theme_bw() +
  ggpubr::rotate_x_text(angle = 80) +
  scale_shape_manual(values = c(19,8), labels = c("FALSE" = "Literature", "TRUE" = "Predicted")) +
  scale_color_brewer(palette="Dark2") +
  # labs(title = "Affinities for Phytoplankton Enzymes for Oxygen", 
  #      x = "Enzyme Name",
  #      y = ~log[10] ~ "("~K[m] ~O[2] ~"(mM))",
  #      colour = "Gene Count",
  #      shape = ""~K[m]) +
   theme(axis.title = element_text(size = 40, color = "black"),
         title = element_text(size = 30),
         axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black"),
        strip.text = element_text(size = 15),
        # legend.key.size = unit(10, 'cm'), #change legend key size
        # legend.key.height = unit(2, 'cm'), #change legend key height
        # legend.key.width = unit(1, 'cm'), #change legend key width
        legend.title =  element_text(size = 30),  #change legend title font size
        legend.text = element_text(size = 30))   #change legend text font size

DiatomEnzymeKms
```

```{r, DiatomEnzymeKms ggsave, include = FALSE} 
ggsave(filename = file.path(Figures, "DiatomEnzymeKms.png"), plot = DiatomEnzymeKms, height = 37, width = 20)
```

```{r, ProchlorococcusEnzyme,  fig.width = 7, fig.height = 5}
ProchlorococcusEnzyme <- MergedData %>%
  filter(!is.na(Gene_count)) %>%
  # filter(PriSec == "Primary") %>%
  filter(FileName == "Prochlorococcus_marinus_MIT9313-aa-gen"| FileName == "Prochlorococcus_marinus_pastoris_CCMP1986-aa-gen" | FileName == "Prochlorococcus_marinus_marinus_CCMP1375-aa-gen") %>%
  # group_by(EC) %>%
  # mutate(ECNumberTotal = sum(Gene_count)) %>%
  # ungroup() %>% View()
  # filter(ECNumberTotal != 0) %>%
  ggplot() +
  geom_point(aes(x = reorder(EnzymeName, Km_mM), y = interaction(Genus, species, Strain, sep = " "), size = Gene_count, color = log10(AvgKm_mM))) +
  facet_grid(rows = vars(Genus), scales = "free", space = "free") +
  scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
  scale_x_discrete(position = "top") +
  scale_radius(breaks = c(1,2,3,4,5), range = c(2.5,5)) +
  theme_bw() +
  ggpubr::rotate_x_text(hjust = 0, angle = 70) +
  labs(x = "Enzyme Name",
       y = "Organism",
       size = "Gene Count", 
       color = "log10(Km (mM))")

ProchlorococcusEnzyme
```

```{r, ProchlorococcusEnzyme ggsave, include = FALSE}
ggsave(filename = file.path(Figures, "ProchlorococcusEnzyme.png"), plot = ProchlorococcusEnzyme, height = 10, width = 10)
```

```{r, DNARepair}
DNARepair <- MetaData %>% 
  left_join(., DataIn, by = c("FileName" = "genome")) %>% 
  filter(Genus == "Prochlorococcus") %>% 
  separate_rows(GOs, sep = ",") %>% 
  filter(Strain %in% c("CCMP1986", "CCMP1375", "MIT9313", "NATL2A")) %>% 
  filter(GOs %in% c("GO:0006281", "GO:0000716", "GO:0000725", "GO:0006284", "GO:0006289", "GO:0006298", "GO:0006302", "GO:0009432", "GO:0006974", "GO:0003904", "GO:0003914") | EC %in% c("4.1.99.3", "4.1.99.13", "1.13.11.33", "3.2.2.17", "5.6.2.3", "6.5.1.1", "6.5.1.2"))

DNARepairFig <- DNARepair %>% 
  mutate(EnzymeName = case_when(EC == "3.2.2.21" ~ "DNA-3-methyladenine glycosylase II",
                                EC == "3.1.22.4" ~ "crossover junction endodeoxyribonuclease",
                                EC == "6.5.1.2" ~ "DNA ligase (NAD+)",
                                EC == "6.5.1.1" ~ "DNA ligase (ATP)",
                                EC == "4.1.99.3" ~ "deoxyribodipyrimidine photo-lyase")) %>% 
  mutate(StrainLabel = case_when(Strain == "CCMP1375" ~ "SS120",
                                 Strain == "CCMP1986" ~ "MED4",
                                 Strain == "MIT9313" ~ "MIT9313",
                                 Strain == "NATL2A" ~ "NATL2A")) %>%
  mutate(StrainLabel = factor(StrainLabel, levels = c("MED4", "NATL2A", "SS120", "MIT9313"))) %>%
  ggplot() +
  geom_point(aes(x = EnzymeName, y = StrainLabel, size = (Gene_count))) + #y = interaction(Genus, species, StrainLabel, sep = " ")
  # facet_grid(rows = vars(Genus), scales = "free", space = "free") +
  # scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
  scale_x_discrete(position = "bottom") +
  scale_radius(breaks = c(1,2,3,4,5), range = c(1,4)) +
  theme_bw() +
  ggpubr::rotate_x_text(hjust = 1, angle = 70)  +
  labs(x = "Enzyme Name",
       #y = "Organism",
       color = "Gene Count",
       size = "Gene Count") +
  facet_grid(rows = vars(StrainLabel), scale = "free") +
   theme(axis.text = element_text(size = 7, color = "black"),
         legend.position = "right",
         axis.text.y = element_blank(),
         axis.title.y = element_blank(),
         axis.title.x = element_text(vjust=10),
        axis.ticks.y = element_blank(),
  # axis.title = element_text(size = 40, color = "black"),
  #        title = element_text(size = 30),
  #     # axis.text.x = element_text(size = 30, color = "black"),
  #       axis.text.y = element_text(size = 30, color = "black"),
        strip.text = element_text(size = 6),
        legend.box.background = element_rect(colour = "black")
  #       # legend.key.size = unit(10, 'cm'), #change legend key size
  #       # legend.key.height = unit(2, 'cm'), #change legend key height
  #       # legend.key.width = unit(1, 'cm'), #change legend key width
  #       legend.title =  element_text(size = 30),  #change legend title font size
  #       legend.text = element_text(size = 30))   #change legend text font size
  )

DNARepairFig
  # ggpubr::rotate_x_text(hjust = 0) 
```

```{r, DNARepairFig ggsave, include = FALSE} 
ggsave(filename = file.path(Figures, "DNARepairFig.png"), plot = DNARepairFig, height =5 , width = 5)
```

```{r import LightEnzymes, include = FALSE}
LightEnzymes <- read_csv(file.path(Data, "LightEnzymes.csv")) %>% 
  select(-c(`...4`, `...5`)) %>% 
  filter(is.na(Remove))
```

```{r LightEnzymes, include=FALSE}
LightEnzymesList <- LightEnzymes$EC
LightEnzymesMerged <- MetaData %>% 
  filter(Genus == "Prochlorococcus" | Taxa == "Diatom") %>% 
  left_join(., DataIn, by = c("FileName" = "genome")) %>% 
  filter(EC %in% LightEnzymesList) %>% 
  left_join(., LightEnzymes, by = c("EC"), relationship = "many-to-many") %>% 
  filter(Description != "KM Value") %>% 
  separate_rows(GOs, sep = ",") %>% 
  mutate(EnzymeName = case_when(EC == "1.3.1.33" ~ "(light-dependent) protochlorophyllide reductase",
                                EC == "2.4.1.14" ~ "sucrose-phosphate synthase",
                                EC == "2.5.1.32" ~ "15-cis-phytoene synthase",
                                EC == "4.6.1.1" ~ "adenylate cyclase",
                                EC == "4.4.1.5" ~ "lactoylglutathione lyase",
                                EC == "4.2.3.5" ~ "chorismate synthase",
                                EC == "2.7.1.148" ~ "4-(cytidine 5'-diphospho)-2-C-methyl-D-erythritol kinase",
                                EC == "4.2.99.18" ~ "DNA-(apurinic or apyrimidinic site) lyase",
                                EC == "3.4.11.1" ~ "leucyl aminopeptidase",
                                EC == "2.4.1.255" ~ "protein O-GlcNAc transferase",
                                EC == "3.1.4.4" ~ "phospholipase D",
                                EC == "1.1.3.20" ~ "long-chain-alcohol oxidase",
                                EC == "1.7.1.1" ~ "nitrate reductase (NADH)",
                                EC == "2.3.1.87" ~ "aralkylamine N-acetyltransferase",
                                EC == "1.3.8.1" ~ "short-chain acyl-CoA dehydrogenase",
                                EC == "3.4.21.19" ~ "glutamyl endopeptidase",
                                EC == "4.6.1.2" ~ "guanylate cyclase",
                                EC == "1.7.7.2" ~ "ferredoxin-nitrate reductase",
                                EC == "4.2.1.84" ~ "nitrile hydratase",
                                EC == "1.10.3.3" ~ "L-ascorbate oxidase",
                                EC == "3.2.1.80" ~ "fructan beta-fructosidase",
                                EC == "2.3.1.37" ~ "5-aminolevulinate synthase",
                                EC == "3.1.4.35" ~ "3',5'-cyclic-GMP phosphodiesterase",
                                EC == "4.1.99.3" ~ "deoxyribodipyrimidine photo-lyase"))

```

```{r LightEnzymesFig, fig.cap = ProchlorococcusLightEnzymesFig_cap, echo = TRUE, fig.height = 5, fig.width = 8}
ProchlorococcusLightEnzymesFig_cap <- glue("**Summary of genes encoding enzymes activated or inhibited by light in *Prochlorococcus*.**",
                                           "Rows correspond to strains of *Prochlorococcus*", 
                                           "Symbol color and size correspond to counts of genes.",
                                           "Symbol absence means no sequences were detected in the genome."
                                           )
ProchlorococcusLightEnzymesFig <- LightEnzymesMerged %>% 
  filter(Strain %in% c("CCMP1986", "CCMP1375", "MIT9313", "NATL2A")) %>% 
  mutate(StrainLabel = case_when(Strain == "CCMP1375" ~ "SS120",
                                 Strain == "CCMP1986" ~ "MED4",
                                 Strain == "MIT9313" ~ "MIT9313",
                                 Strain == "NATL2A" ~ "NATL2A")) %>%
  mutate(StrainLabel = factor(StrainLabel, levels = c("MED4", "NATL2A", "SS120", "MIT9313"))) %>% 
  mutate(Compound = case_when(Compound == "blue-light regulator 2" ~ "light",
                              TRUE ~ Compound)) %>% 
  ggplot() +
  geom_point(aes(x = fct_reorder(EnzymeName, desc(Gene_count)), y = StrainLabel, size = as.character(Gene_count))) +
  ggh4x::facet_nested(cols = vars(Description, Compound),rows = vars(StrainLabel),  scale = "free", space = "free") + #

  labs(x = "Enzyme Name",
       # y = "Organism",
       size = "Gene Count",
       color = "Gene Count") +
  # scale_size_manual(values = c(1,2,3,4), breaks)
  theme_bw() +
  ggpubr::rotate_x_text(hjust = 1, angle = 70) +
  theme(axis.text = element_text(size = 7, color = "black"),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
  # axis.title = element_text(size = 40, color = "black"),
  #        title = element_text(size = 30),
  #     # axis.text.x = element_text(size = 30, color = "black"),
  #       axis.text.y = element_text(size = 30, color = "black"),
        strip.text = element_text(size = 6),
  legend.position = "bottom",
  legend.key.size = unit(1, 'cm'),
  legend.box.background = element_rect(colour = "black")
  #       # legend.key.size = unit(10, 'cm'), #change legend key size
  #       # legend.key.height = unit(2, 'cm'), #change legend key height
  #       # legend.key.width = unit(1, 'cm'), #change legend key width
  #       legend.title =  element_text(size = 30),  #change legend title font size
  #       legend.text = element_text(size = 30))   #change legend text font size
  )

 ProchlorococcusLightEnzymesFig
```

```{r, save ProchlorococcusLightEnzymesFig, ggsave, include = FALSE} 
ggsave(filename = file.path(Figures, "ProchlorococcusLightEnzymesFig.png"), plot = ProchlorococcusLightEnzymesFig, height = 6, width = 8)
```

```{r DiatomLightEnzymesFig, echo = TRUE, fig.height = 10, fig.width = 15}
DiatomBothOmes <- MetaData %>%
  mutate(FullName = interaction(Genus, species, Strain, sep = " ")) %>% 
  filter(Taxa == "Diatom") %>% 
  select(Ome, Genus, species, Strain, FileName) %>% 
  pivot_wider(names_from = Ome, values_from = FileName) %>% 
  mutate(BothOmesPresent = case_when(#!is.na(Genome) ~ "GenomePresent",
                                     #!is.na(Transcriptome) ~ "TranscriptomePresent",
                                     !is.na(Genome) & !is.na(Transcriptome) ~ "BothPresent")) %>% 
  pivot_longer(cols = c(Genome, Transcriptome), values_to = "FileName", names_to = "Ome")  %>% 
  filter(!is.na(FileName)) %>% 
  mutate(BothOmesPresentTranscriptome = case_when(BothOmesPresent == "BothPresent" & Ome == "Transcriptome" ~ 1,
                                                  TRUE ~ 0))

DiatomLightEnzymesFig <- LightEnzymesMerged %>% 
  filter(Taxa == "Diatom",
         ) %>% #Ome == "Genome"
  mutate(Compound = case_when(Compound == "blue-light regulator 2" ~ "light",
                              Compound == "UVB light" ~ "UV light",
                              Compound == "UVB-light" ~ "UV light",
                              TRUE ~ Compound)) %>% 
  mutate(Latitude = case_when(species == "multistrata" & Strain == "B856" ~ 40.485, #https://doi.org/10.1111/nph.14557
                              species == "inconspicua" & Strain == "GAI-293" ~ 21.57, #https://doi.org/10.1038/s41598-021-95106-3
                              species == "robusta" & Strain == "D6" ~ 51.01, #https://bccm.belspo.be/catalogues/dcg-strain-details?ACCESSION_NUMBER=DCG%200498&LIST1=&TEXT1=&LIST2=&TEXT2=&LIST3=&TEXT3=&LIST4=&TEXT4=&LIST5=&TEXT5=&CONJ=
                              TRUE ~ Latitude)) %>% 
  right_join(., DiatomBothOmes, by = c("FileName", "Ome", "Genus", "species", "Strain")) %>% 
    mutate(Polar = case_when(Latitude > 59 ~ "Polar",
                           Latitude < -59 ~ "Polar",
                           is.na(Latitude) ~ "Unknown",
                           TRUE ~ "Non Polar")) %>% 
  mutate(Compound = case_when(Compound == "far red light" ~ "Far red",
                                 Compound == "light" ~ "Visible",
                                 Compound == "UV light" ~ "UV"),
         Description = case_when(Description == "Activating Compound" ~ "Activator",
                                 TRUE ~ Description),
         Genus = case_when(Genus == "Conticribra_Thalassiosira" ~ "Thalassiosira",
                           TRUE ~ Genus)) %>%

  filter(Polar != "Unknown") %>% 
  filter(BothOmesPresentTranscriptome != 1) %>% 
  mutate(TotalEnzyme_count = sum(Gene_count), .by = EnzymeName) %>% 
  ggplot() +
  geom_point(aes(x = fct_reorder(EnzymeName, desc(TotalEnzyme_count)), y = interaction(Genus, species, sep = " "), size = (Gene_count), color = Polar, shape = Ome)) +
  ggh4x::facet_nested(cols = vars(Description, Compound), rows = vars(Polar),  scale = "free", space = "free") + #

  labs(x = "Enzyme Name",
       y = "Diatom",
       size = "Gene Count",
       color = "Isolation Location") +
  # scale_size_manual(values = c(1,2,3,4), breaks)
  theme_bw() +
  ggpubr::rotate_x_text(hjust = 1, angle = 70) +
  theme(axis.text = element_text(size = 10, color = "black"),
        # axis.text.y = element_blank(),
        # axis.ticks.y = element_blank(),
  axis.title = element_text(size = 15, color = "black"),
  #        title = element_text(size = 30),
  #     # axis.text.x = element_text(size = 30, color = "black"),
  #       axis.text.y = element_text(size = 30, color = "black"),
        strip.text = element_text(size = 10),
  # legend.position = "bottom",
  legend.position = c(0.23, -0.51),
  legend.direction = "vertical",
  legend.box = "horizontal",
  legend.box.background = element_rect(colour = "black"),
  legend.title = element_text(size = 13),
  legend.text = element_text(size = 10),
  #       # legend.key.size = unit(10, 'cm'), #change legend key size
  #       # legend.key.height = unit(2, 'cm'), #change legend key height
  #       # legend.key.width = unit(1, 'cm'), #change legend key width
  #       legend.title =  element_text(size = 30),  #change legend title font size
  #       legend.text = element_text(size = 30))   #change legend text font size
  )

DiatomLightEnzymesFig
```

```{r, save DiatomLightEnzymesFig, ggsave, include = FALSE} 
ggsave(filename = file.path(Figures, "DiatomLightEnzymesFig.png"), plot = DiatomLightEnzymesFig, height = 10, width = 15)
```

```{r}
LightGOs <- MergedData %>% 
  separate_rows(GOs, sep = ",") %>% 
  filter(GOs %in% c("GO:0010018", "GO:0009785", "GO:0009882", "GO:0031516", "GO:0031517", "GO:0009883"))

LightKOs <- MergedData %>% 
  separate_rows(KEGG_ko, sep = ",") %>% 
  filter(KEGG_ko %in% c("ko:K02295", "ko:K12120", "ko:K12122", "ko:K12121", "ko:K12123"))
```

```{r, fig.width = 7, fig.height = 7}
MergedData %>%
  filter(!is.na(Gene_count)) %>%
  filter(PriSec == "Primary") %>%
  filter(Genus == "Prochlorococcus") %>%
  # filter(FileName == "Prochlorococcus_marinus_MIT9313-aa-gen"| FileName == "Prochlorococcus_marinus_pastoris_CCMP1986-aa-gen" | FileName == "Prochlorococcus_marinus_marinus_CCMP1375-aa-gen") %>%
  # group_by(EC) %>%
  # mutate(ECNumberTotal = sum(Gene_count)) %>%
  # ungroup() %>% View()
  # filter(ECNumberTotal != 0) %>%
  ggplot() +
  geom_point(aes(x = reorder(EnzymeName, Km_mM), y = FileName, size = Gene_count, color = log10(AvgKm_mM))) +
  facet_grid(rows = vars(Genus), scales = "free", space = "free") +
  scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
  scale_x_discrete(position = "top") +
  scale_radius(breaks = c(1,2,3,4,5), range = c(1,4)) +
  theme_bw() +
  ggpubr::rotate_x_text(hjust = 0) 
```

```{r, fig.width = 7, fig.height = 7}
MergedData %>%
  filter(!is.na(Gene_count)) %>%
  filter(PriSec == "Primary") %>%
  # filter(FileName == "Prochlorococcus_marinus_MIT9313-aa-gen"| FileName == "Prochlorococcus_marinus_pastoris_CCMP1986-aa-gen" | FileName == "Prochlorococcus_marinus_marinus_CCMP1375-aa-gen") %>%
  # group_by(EC) %>%
  # mutate(ECNumberTotal = sum(Gene_count)) %>%
  # ungroup() %>% View()
  # filter(ECNumberTotal != 0) %>%
  ggplot() +
  geom_point(aes(x = reorder(EnzymeName, Km_mM), y = FileName, size = Gene_count, color = log10(AvgKm_mM))) +
  facet_grid(rows = vars(Genus), scales = "free", space = "free") +
  scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
  scale_x_discrete(position = "top") +
  scale_radius(breaks = c(1,2,3,4,5), range = c(1,4)) +
  theme_bw() +
  ggpubr::rotate_x_text(hjust = 0) 
```

```{r}
# Flv_BLAST_files <- list.files(path = BLAST, pattern = "*.tsv", full.names = TRUE)
```

```{r}
# Flv_BLAST <- Flv_BLAST_files %>% 
#   set_names(.) %>%
#   map_dfr(read_tsv, col_names = c("qseqid", "sseqid", "pident", "length", "mismatch", "gapopen", "qstart", "qend", "sstart", "send", "evalue", "bitscore"), .id = "FileName") %>%
#   mutate(FileName = str_remove(FileName, "../BLAST/"),
#          FileName = str_remove(FileName, "_Flv.tsv")) %>% 
#   left_join(., MetaData, by = c("FileName")) %>% 
#   group_by(Strain, qseqid, sseqid) %>% 
#   mutate(Gene_count = n()) %>% 
#   filter(evalue < 1e-10)
```

Using an evalue of 0.05 above
```{r}
# Flv_BLAST %>% 
#   mutate(StrainLabel = case_when(Strain == "CCMP1375" ~ "SS120",
#                                  Strain == "CCMP1986" ~ "MED4",
#                                  Strain == "MIT9313" ~ "MIT9313",
#                                  Strain == "NATL2A" ~ "NATL2A")) %>%
#   mutate(StrainLabel = factor(StrainLabel, levels = c("MED4", "NATL2A", "SS120", "MIT9313"))) %>% 
#   ggplot() +
#   geom_point(aes(x = qseqid, y = sseqid, color = log10(evalue))) +
#   ggh4x::facet_nested(rows = vars(StrainLabel), scales = "free", space = "free") +
#   theme_bw() +
#   ggpubr::rotate_x_text(hjust = 1) 
```

### 2024-03-01 Code/ManuscriptGenome.Rmd
Update ManuscriptGenome.Rmd

@@
 DataIn <- file.path("..","Data", "CleanData")
-Figures <- file.path("..", "Figures")
+Figures <- file.path("..", "Output", "Figures")
 # BLAST <- file.path("..", "BLAST")
@@
 # 
-# MetaData <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1kXm0GvMdTRbF12cG5Bps-2e_4MTjgUX7iUOjqiu-_c0/edit#gid=0") %>%
-#   dplyr::select(c(Genus, species, Strain, FileName, Ome, Taxa, Rad1_um, Rad2_um, Rad3_um, Flagella, GenomeSize_mbp, GeneModels_count, Latitude, Longitude, Marine, PennateCentric, ColonySpecies)) %>%
-#   mutate(Strain = as.character(Strain))
+MetaData <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1kXm0GvMdTRbF12cG5Bps-2e_4MTjgUX7iUOjqiu-_c0/edit#gid=0") %>%
+  dplyr::select(c(Genus, species, Strain, FileName, Ome, Taxa, Rad1_um, Rad2_um, Rad3_um, Flagella, GenomeSize_mbp, GeneModels_count, Latitude, Longitude, Marine, PennateCentric, ColonySpecies)) %>%
+  mutate(Strain = as.character(Strain))
 # 
@@
   add_row(Strain = "NATL2A", Ome = "Genome", Taxa = "Prokaryote", EnzymeName = "Flavodiiron (Flv1a/3a)", Gene_count = 1, Estimated = 0, Genus = "Prochlorococcus", Km_mM  = 7/1000)
-
 ```
@@
                            TRUE ~ Km_mM_max)) %>% 
-  # mutate(Km_mM = case_when(EnzymeName == "Flavodiiron (Flv1a/3a)" ~ 10/1000,
-  #                          TRUE ~ Km_mM)) %>% 
   ungroup() %>% 
@@
   geom_errorbar(aes(x = reorder(EnzymeName, Km_mM * 1000), ymin = log10(Km_mM_min* 1000), ymax = log10(Km_mM_max* 1000))) +
-  # geom_ribbon(aes(ymin = log10(5e-4), ymax =  log10(5e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "blue") +
-  # geom_ribbon(aes(ymax = log10(5e-2), ymin =  log10(5e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "green") +
-  # geom_ribbon(aes(ymax = log10(280e-3), ymin =  log10(230e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "#FF0000") +
   annotate(geom = "rect", ymin = log10(5e-4 * 1000), ymax =  log10(5e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "blue") +
@@
   geom_text(aes(x = 18.5, y = 2.5, label = "[O2] ≈ 250 µM"), color = "#FF0000", size = 6) +
-  # geom_hline(yintercept = log10(5e-4), linetype = "dotted") +
-  # geom_hline(yintercept = log10(5e-3), linetype = "dotted") +
-  # geom_hline(yintercept = log10(5e-3), linetype = "dotted", color = "brown") +
-  # geom_hline(yintercept = log10(5e-2), linetype = "dotted", color = "brown") +
-  # geom_hline(yintercept = log10(230e-3), linetype = "dotted", color = "red") +
-  # geom_hline(yintercept = log10(290e-3), linetype = "dotted", color = "red") +
-  # scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
   ggh4x::facet_nested(rows = vars(StrainLabel)) +
@@
 
-```{r, DiatomEnzymeKms, fig.width = 20, fig.height = 20}
-DiatomEnzymeKms <- MergedData %>%
-  filter(!is.na(Gene_count),
-         Taxa == "Diatom",
-         !is.na(Estimated)) %>%
-  # mutate(StrainLabel = case_when(Strain == "CCMP1375" ~ "SS120",
-  #                                Strain == "CCMP1986" ~ "MED4",
-  #                                Strain == "MIT9313" ~ "MIT9313",
-  #                                Strain == "NATL2A" ~ "NATL2A")) %>%
-  # mutate(StrainLabel = factor(StrainLabel, levels = c("MED4", "NATL2A", "SS120", "MIT9313"))) %>%
-  group_by(EC) %>%
-  mutate(Km_mM_min = min(Km_mM, na.rm = TRUE), 
-         Km_mM_max = max(Km_mM, na.rm = TRUE),
-         Gene_count = as.character(Gene_count)) %>%
-  ungroup() %>%
-  mutate(Latitude = case_when(species == "multistrata" & Strain == "B856" ~ 40.485, #https://doi.org/10.1111/nph.14557
-                              species == "inconspicua" & Strain == "GAI-293" ~ 21.57, #https://doi.org/10.1038/s41598-021-95106-3
-                              species == "robusta" & Strain == "D6" ~ 51.01, #https://bccm.belspo.be/catalogues/dcg-strain-details?ACCESSION_NUMBER=DCG%200498&LIST1=&TEXT1=&LIST2=&TEXT2=&LIST3=&TEXT3=&LIST4=&TEXT4=&LIST5=&TEXT5=&CONJ=
-                              TRUE ~ Latitude)) %>% 
-  mutate(Polar = case_when(Latitude > 59 ~ "Polar",
-                           Latitude < -59 ~ "Polar",
-                           is.na(Latitude) ~ "Unknown",
-                           TRUE ~ "Non Polar")) %>% 
-  filter(Polar != "Unknown") %>% 
-  filter(Genus %notin% c("Chaetoceros", "Amphora", "Extubocellulus"),
-         species %notin% c("minuscula")) %>% #select(Genus, species, Strain, Polar, Ome) %>% unique()
-  ggplot() +
-  geom_errorbar(aes(x = reorder(EnzymeName, Km_mM), ymin = log10(Km_mM_min), ymax = log10(Km_mM_max))) +
-  # geom_ribbon(aes(ymin = log10(5e-4), ymax =  log10(5e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "blue") +
-  # geom_rect(ymin = log10(5e-4), ymax =  log10(5e-3), xmin = -Inf, xmax = Inf, alpha = 0.03, fill = "blue") +
-  annotate(geom = "rect", ymin = log10(5e-4), ymax =  log10(5e-3), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "blue") +
-  annotate(geom = "rect", ymax = log10(5e-2), ymin =  log10(5e-3), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "green") +
-  annotate(geom = "rect", ymax = log10(280e-3), ymin =  log10(230e-3), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "#FF0000") +
-  # geom_ribbon(aes(ymax = log10(5e-2), ymin =  log10(5e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "green") +
-  # geom_ribbon(aes(ymax = log10(280e-3), ymin =  log10(230e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "#FF0000") +
-  geom_point(aes(x = reorder(EnzymeName, Km_mM), y = log10(Km_mM), color = Gene_count, shape = as.logical(Estimated)), size = 5, stroke = 2) +
-  geom_text(aes(x = 16.5, y = -2.8, label = "[O2] ≈ 2.5 µM"), color = "blue", size = 6) +
-  geom_text(aes(x = 16.5, y = -1.8, label = "[O2] ≈ 25 µM"), color = "darkgreen", size = 6) +
-  geom_text(aes(x = 16.5, y = -0.35, label = "[O2] ≈ 250 µM"), color = "#FF0000", size = 6) +
-  geom_vline(aes(xintercept = reorder(EnzymeName, Km_mM), color = Gene_count), size = 5,  data = . %>% filter(is.na(Km_mM)), linetype = "solid") +
-  ggh4x::facet_nested(rows = vars(Polar, interaction(Genus, species))) +
-  theme_bw() +
-  ggpubr::rotate_x_text(angle = 80) +
-  scale_shape_manual(values = c(19,8), labels = c("FALSE" = "Literature", "TRUE" = "Predicted")) +
-  scale_color_brewer(palette="Dark2") +
-  # labs(title = "Affinities for Phytoplankton Enzymes for Oxygen", 
-  #      x = "Enzyme Name",
-  #      y = ~log[10] ~ "("~K[m] ~O[2] ~"(mM))",
-  #      colour = "Gene Count",
-  #      shape = ""~K[m]) +
-   theme(axis.title = element_text(size = 40, color = "black"),
-         title = element_text(size = 30),
-         axis.text.x = element_text(size = 20, color = "black"),
-        axis.text.y = element_text(size = 20, color = "black"),
-        strip.text = element_text(size = 15),
-        # legend.key.size = unit(10, 'cm'), #change legend key size
-        # legend.key.height = unit(2, 'cm'), #change legend key height
-        # legend.key.width = unit(1, 'cm'), #change legend key width
-        legend.title =  element_text(size = 30),  #change legend title font size
-        legend.text = element_text(size = 30))   #change legend text font size
-
-DiatomEnzymeKms
-```
-
-```{r, DiatomEnzymeKms ggsave, include = FALSE} 
-ggsave(filename = file.path(Figures, "DiatomEnzymeKms.png"), plot = DiatomEnzymeKms, height = 37, width = 20)
-```
-
 ```{r, ProchlorococcusEnzyme,  fig.width = 7, fig.height = 5}
-ProchlorococcusEnzyme <- MergedData %>%
-  filter(!is.na(Gene_count)) %>%
-  # filter(PriSec == "Primary") %>%
-  filter(FileName == "Prochlorococcus_marinus_MIT9313-aa-gen"| FileName == "Prochlorococcus_marinus_pastoris_CCMP1986-aa-gen" | FileName == "Prochlorococcus_marinus_marinus_CCMP1375-aa-gen") %>%
-  # group_by(EC) %>%
-  # mutate(ECNumberTotal = sum(Gene_count)) %>%
-  # ungroup() %>% View()
-  # filter(ECNumberTotal != 0) %>%
-  ggplot() +
-  geom_point(aes(x = reorder(EnzymeName, Km_mM), y = interaction(Genus, species, Strain, sep = " "), size = Gene_count, color = log10(AvgKm_mM))) +
-  facet_grid(rows = vars(Genus), scales = "free", space = "free") +
-  scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
-  scale_x_discrete(position = "top") +
-  scale_radius(breaks = c(1,2,3,4,5), range = c(2.5,5)) +
-  theme_bw() +
-  ggpubr::rotate_x_text(hjust = 0, angle = 70) +
-  labs(x = "Enzyme Name",
-       y = "Organism",
-       size = "Gene Count", 
-       color = "log10(Km (mM))")
-
-ProchlorococcusEnzyme
+# ProchlorococcusEnzyme <- MergedData %>%
+#   filter(!is.na(Gene_count)) %>%
+#   # filter(PriSec == "Primary") %>%
+#   filter(FileName == "Prochlorococcus_marinus_MIT9313-aa-gen"| FileName == "Prochlorococcus_marinus_pastoris_CCMP1986-aa-gen" | FileName == "Prochlorococcus_marinus_marinus_CCMP1375-aa-gen") %>%
+#   # group_by(EC) %>%
+#   # mutate(ECNumberTotal = sum(Gene_count)) %>%
+#   # ungroup() %>% View()
+#   # filter(ECNumberTotal != 0) %>%
+#   ggplot() +
+#   geom_point(aes(x = reorder(EnzymeName, Km_mM), y = interaction(Genus, species, Strain, sep = " "), size = Gene_count, color = log10(AvgKm_mM))) +
+#   facet_grid(rows = vars(Genus), scales = "free", space = "free") +
+#   scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
+#   scale_x_discrete(position = "top") +
+#   scale_radius(breaks = c(1,2,3,4,5), range = c(2.5,5)) +
+#   theme_bw() +
+#   ggpubr::rotate_x_text(hjust = 0, angle = 70) +
+#   labs(x = "Enzyme Name",
+#        y = "Organism",
+#        size = "Gene Count", 
+#        color = "log10(Km (mM))")
+# 
+# ProchlorococcusEnzyme
 ```
@@
 ```{r, ProchlorococcusEnzyme ggsave, include = FALSE}
-ggsave(filename = file.path(Figures, "ProchlorococcusEnzyme.png"), plot = ProchlorococcusEnzyme, height = 10, width = 10)
+# ggsave(filename = file.path(Figures, "ProchlorococcusEnzyme.png"), plot = ProchlorococcusEnzyme, height = 10, width = 10)
 ```
@@
         axis.ticks.y = element_blank(),
-  # axis.title = element_text(size = 40, color = "black"),
-  #        title = element_text(size = 30),
-  #     # axis.text.x = element_text(size = 30, color = "black"),
-  #       axis.text.y = element_text(size = 30, color = "black"),
         strip.text = element_text(size = 6),
         legend.box.background = element_rect(colour = "black")
-  #       # legend.key.size = unit(10, 'cm'), #change legend key size
-  #       # legend.key.height = unit(2, 'cm'), #change legend key height
-  #       # legend.key.width = unit(1, 'cm'), #change legend key width
-  #       legend.title =  element_text(size = 30),  #change legend title font size
-  #       legend.text = element_text(size = 30))   #change legend text font size
   )
@@
 DNARepairFig
-  # ggpubr::rotate_x_text(hjust = 0) 
 ```
@@
                                            )
+
 ProchlorococcusLightEnzymesFig <- LightEnzymesMerged %>% 
@@
 ggsave(filename = file.path(Figures, "ProchlorococcusLightEnzymesFig.png"), plot = ProchlorococcusLightEnzymesFig, height = 6, width = 8)
-```
-
-```{r DiatomLightEnzymesFig, echo = TRUE, fig.height = 10, fig.width = 15}
-DiatomBothOmes <- MetaData %>%
-  mutate(FullName = interaction(Genus, species, Strain, sep = " ")) %>% 
-  filter(Taxa == "Diatom") %>% 
-  select(Ome, Genus, species, Strain, FileName) %>% 
-  pivot_wider(names_from = Ome, values_from = FileName) %>% 
-  mutate(BothOmesPresent = case_when(#!is.na(Genome) ~ "GenomePresent",
-                                     #!is.na(Transcriptome) ~ "TranscriptomePresent",
-                                     !is.na(Genome) & !is.na(Transcriptome) ~ "BothPresent")) %>% 
-  pivot_longer(cols = c(Genome, Transcriptome), values_to = "FileName", names_to = "Ome")  %>% 
-  filter(!is.na(FileName)) %>% 
-  mutate(BothOmesPresentTranscriptome = case_when(BothOmesPresent == "BothPresent" & Ome == "Transcriptome" ~ 1,
-                                                  TRUE ~ 0))
-
-DiatomLightEnzymesFig <- LightEnzymesMerged %>% 
-  filter(Taxa == "Diatom",
-         ) %>% #Ome == "Genome"
-  mutate(Compound = case_when(Compound == "blue-light regulator 2" ~ "light",
-                              Compound == "UVB light" ~ "UV light",
-                              Compound == "UVB-light" ~ "UV light",
-                              TRUE ~ Compound)) %>% 
-  mutate(Latitude = case_when(species == "multistrata" & Strain == "B856" ~ 40.485, #https://doi.org/10.1111/nph.14557
-                              species == "inconspicua" & Strain == "GAI-293" ~ 21.57, #https://doi.org/10.1038/s41598-021-95106-3
-                              species == "robusta" & Strain == "D6" ~ 51.01, #https://bccm.belspo.be/catalogues/dcg-strain-details?ACCESSION_NUMBER=DCG%200498&LIST1=&TEXT1=&LIST2=&TEXT2=&LIST3=&TEXT3=&LIST4=&TEXT4=&LIST5=&TEXT5=&CONJ=
-                              TRUE ~ Latitude)) %>% 
-  right_join(., DiatomBothOmes, by = c("FileName", "Ome", "Genus", "species", "Strain")) %>% 
-    mutate(Polar = case_when(Latitude > 59 ~ "Polar",
-                           Latitude < -59 ~ "Polar",
-                           is.na(Latitude) ~ "Unknown",
-                           TRUE ~ "Non Polar")) %>% 
-  mutate(Compound = case_when(Compound == "far red light" ~ "Far red",
-                                 Compound == "light" ~ "Visible",
-                                 Compound == "UV light" ~ "UV"),
-         Description = case_when(Description == "Activating Compound" ~ "Activator",
-                                 TRUE ~ Description),
-         Genus = case_when(Genus == "Conticribra_Thalassiosira" ~ "Thalassiosira",
-                           TRUE ~ Genus)) %>%
-
-  filter(Polar != "Unknown") %>% 
-  filter(BothOmesPresentTranscriptome != 1) %>% 
-  mutate(TotalEnzyme_count = sum(Gene_count), .by = EnzymeName) %>% 
-  ggplot() +
-  geom_point(aes(x = fct_reorder(EnzymeName, desc(TotalEnzyme_count)), y = interaction(Genus, species, sep = " "), size = (Gene_count), color = Polar, shape = Ome)) +
-  ggh4x::facet_nested(cols = vars(Description, Compound), rows = vars(Polar),  scale = "free", space = "free") + #
-
-  labs(x = "Enzyme Name",
-       y = "Diatom",
-       size = "Gene Count",
-       color = "Isolation Location") +
-  # scale_size_manual(values = c(1,2,3,4), breaks)
-  theme_bw() +
-  ggpubr::rotate_x_text(hjust = 1, angle = 70) +
-  theme(axis.text = element_text(size = 10, color = "black"),
-        # axis.text.y = element_blank(),
-        # axis.ticks.y = element_blank(),
-  axis.title = element_text(size = 15, color = "black"),
-  #        title = element_text(size = 30),
-  #     # axis.text.x = element_text(size = 30, color = "black"),
-  #       axis.text.y = element_text(size = 30, color = "black"),
-        strip.text = element_text(size = 10),
-  # legend.position = "bottom",
-  legend.position = c(0.23, -0.51),
-  legend.direction = "vertical",
-  legend.box = "horizontal",
-  legend.box.background = element_rect(colour = "black"),
-  legend.title = element_text(size = 13),
-  legend.text = element_text(size = 10),
-  #       # legend.key.size = unit(10, 'cm'), #change legend key size
-  #       # legend.key.height = unit(2, 'cm'), #change legend key height
-  #       # legend.key.width = unit(1, 'cm'), #change legend key width
-  #       legend.title =  element_text(size = 30),  #change legend title font size
-  #       legend.text = element_text(size = 30))   #change legend text font size
-  )
-
-DiatomLightEnzymesFig
-```
-
-```{r, save DiatomLightEnzymesFig, ggsave, include = FALSE} 
-ggsave(filename = file.path(Figures, "DiatomLightEnzymesFig.png"), plot = DiatomLightEnzymesFig, height = 10, width = 15)
 ```
@@
 ```
-
-```{r}
-# Flv_BLAST_files <- list.files(path = BLAST, pattern = "*.tsv", full.names = TRUE)
-```
-
-```{r}
-# Flv_BLAST <- Flv_BLAST_files %>% 
-#   set_names(.) %>%
-#   map_dfr(read_tsv, col_names = c("qseqid", "sseqid", "pident", "length", "mismatch", "gapopen", "qstart", "qend", "sstart", "send", "evalue", "bitscore"), .id = "FileName") %>%
-#   mutate(FileName = str_remove(FileName, "../BLAST/"),
-#          FileName = str_remove(FileName, "_Flv.tsv")) %>% 
-#   left_join(., MetaData, by = c("FileName")) %>% 
-#   group_by(Strain, qseqid, sseqid) %>% 
-#   mutate(Gene_count = n()) %>% 
-#   filter(evalue < 1e-10)
-```
-
-Using an evalue of 0.05 above
-```{r}
-# Flv_BLAST %>% 
-#   mutate(StrainLabel = case_when(Strain == "CCMP1375" ~ "SS120",
-#                                  Strain == "CCMP1986" ~ "MED4",
-#                                  Strain == "MIT9313" ~ "MIT9313",
-#                                  Strain == "NATL2A" ~ "NATL2A")) %>%
-#   mutate(StrainLabel = factor(StrainLabel, levels = c("MED4", "NATL2A", "SS120", "MIT9313"))) %>% 
-#   ggplot() +
-#   geom_point(aes(x = qseqid, y = sseqid, color = log10(evalue))) +
-#   ggh4x::facet_nested(rows = vars(StrainLabel), scales = "free", space = "free") +
-#   theme_bw() +
-#   ggpubr::rotate_x_text(hjust = 1) 
-```

### 2024-03-01 Code/Manuscript_O2.Rmd
some edits

@@
 Current niches of *P.
-marinus* strains span ocean water columns [@veldhuisVerticalDistributionPigment1990; @chisholmNovelFreelivingProchlorophyte1988; @partenskyProchlorococcusMarinePhotosynthetic1999] and extend into regions with low dissolved oxygen concentrations [@partenskyProchlorococcusAdvantagesLimits2010; @goerickeNovelNicheProchlorococcus2000; @lavinNovelLineagesProchlorococcus2010, @ulloaCyanobacteriumProchlorococcusHas2021; @garcia-robledoCrypticOxygenCycling2017].
+marinus* strains span ocean water columns [@veldhuisVerticalDistributionPigment1990; @chisholmNovelFreelivingProchlorophyte1988; @partenskyProchlorococcusMarinePhotosynthetic1999] and extend into regions with low dissolved oxygen concentrations [@partenskyProchlorococcusAdvantagesLimits2010; @goerickeNovelNicheProchlorococcus2000; @lavinNovelLineagesProchlorococcus2010; @ulloaCyanobacteriumProchlorococcusHas2021; @garcia-robledoCrypticOxygenCycling2017].
 
@@
 We screened a subset of the OPP for proteins annotated as from *Prochlorococcus* strains, to identify differential strategies employed by strains living at varying depths and oxygen levels within the marine water column.
-We focused on proteins mediating photosynthesis and protein metabolism.
+We focused on proteins mediating photosynthesis and protein metabolism from depths of 20 to 200 m below the ocean surface.
 The samples for metaproteomic analyses were collected from 12 locations in the tropical North Pacific ocean along 150 W from 18 N of the equator between October 1, 2011 and October 25, 2011 during the voyage of the R/V Kilo Moana MetZyme cruise KM1128 (https://www.rvdata.us/search/cruise/KM1128; original datasets in the Biological and Chemical Oceanography Data Management Office repository; https://www.bco-dmo.org/project/2236).
-
-Collection and treatment of protein samples were performed by personnel at the WHOI according to the protocols described by Saito *et al*.
+Oxygen concentration levels at the location of sampling were recorded.
+The methodology for sample collection and peptide analysis are described by Saito *et al*.
 [@saitoMultipleNutrientStresses2014; @saitoNeedlesBlueSea2015].
-Briefly, samples of seawater from depths of 20, 40, 50, 60, 70, 80, 90, 120, 150, 200, 250, 300, 380, 400, 500, 550, 600, and 800 m below the ocean surface were pumped through a 0.2 µm filter, preserved in RNAlater and frozen at -80°C until extraction.
-Proteins were extracted from the filter in an SDS-based detergent, embedded in tube gel, alkylated and reduced prior to in-gel trypsin digestion.
-Peptide spectra were generated using a Q-Exactive Orbitrap Mass Spectrometer, searched in the SEQUEST CITATIONXXXX and labelled with the most likely protein and species annotation from Uniprot.
-Oxygen levels at the location of sampling were recorded.
 
@@
 
-## Quantitative protein immunoblotting {.unnumbered}
-
-Quantitative protein immunoblots were used to determine the concentrations of 5 target proteins; FtsH, PsbA, PetC, PsaC and RbcL in *P.
-marinus* MED4 and MIT9313 cultures grown in the PSI Multicultivator under imposed PAR light levels of 30 and 100 µmol photons m^-2^ s^-1^, spectral wavebands of 660 and 450 nm and [O~2~] of 2.5 and 250 µM.
-40 mL of culture were transferred into a 50 mL falcon tube and 40 µL of 10 % Pluronic F68 acid was added to the cell suspension.
-The cell suspension was centrifuged for 30 minutes at 17664 g using a J-26XP centrifuge (Beckman Coulter, Brea, CA, USA) equipped with a J-10 rotor.
-The supernatant was removed and the resulting pellet was flash frozen in liquid nitrogen and stored at -80 °C for later use.
-
-Protein samples were thawed and placed in 2 mL FastPrep®-24 bead lysing matrix D vials (MP Biomedicals, Irvine, CA, USA; SKU 116913050) with 200 µL of 1X protein extraction buffer (0.0281 mol L^−1^ TRIS base buffer, 0.0211 mol L^−1^ TRIS HCl buffer, 0.0735 mol L^−1^ lithium dodecyl sulfate, 1.08 mol L^−1^ glycerol, 0.5 mmol L^−1^ ethylenediaminetetraacetic acid, 0.1 mg·mL−1 PefaBloc SC (AEBSF) protease inhibitor) modified from Brown *et al*.
-[@brownFluxCapacitiesAcclimation2008].
-Cells were lysed for 3 cycles of 60 seconds at 6.5m s-1 with 60 second intervals on ice between cycles.
-The lysing vials were centrifuged at 16100 x *g* using a tabletop Mikro 20 centrifuge (Andreas Hettich GmbH & Co., Tuttlingen, Germany) for 5 minutes, the supernatant was transferred to a 600 µL microcentrifuge tube and centrifuged again at 16100 x *g* for 3 minutes.
-40 µL of the supernatant were subsampled into labeled vials and stored at -80 °C until analysis.
-The bicinchoninic acid (BCA) assay was used for total protein determination using a calibration curve of bovine gamma globulin (BGG; Bio-Rad, Hercules, CA, USA) standard ranging from 0 to 1.0 mg mL^-1^ range.
-
-All samples and appropriate standards were prepared as described in [@brownFluxCapacitiesAcclimation2008].
-Standards were obtained from Agrisera (Vännäs, Sweden; FtsH AS11 1789S; PsbA AS01 016S; PetC AS08 330S; PsaC AS04 042S; RbcL AS01 017S).
-Between 0.1 to 4.0 µg of total protein was loaded onto 15 well Invitrogen Bolt 4-12% acrylamide Bis-Tris gels (ThermoFisher Scientific, Waltham, MA, USA).
-All gels were run for 25 minutes at 200V using Invitrogen Bolt Mini Gel tanks and Invitrogen Bolt MES SDS running buffer (ThermoFisher Scientific, Waltham, MA, USA) and transferred for 60 minutes at 20V onto a PVDF membrane (Bio-Rad, Hercules, CA, USA; SKU 1620177).
-Blots were blocked overnight in 2% ECL blocking solution as described by @brownFluxCapacitiesAcclimation2008.
-The following morning, each blot was incubated in their appropriate antibody obtained from Agrisera (Vännäs, Sweden; FtsH  1:5000 dilution, AS11 1789; PsbA  1:10000 dilution, AS05 084; PetC 1:10000 dilution, AS08 330; PsaC 1:5000 dilution, AS10 939; RbcL 1:10000 dilution, AS03 037) and a 1:15000 dilution of the secondary antibody, goat anti-rabbit HRP conjugated (Bio-Rad, Hercules, CA, USA; SKU 1706515, lot 64230791).
-Blots were incubated in Amersham ECL Select chemiluminescent substrate (Danaher, Washington, DC, USA) and imaged in a Bio-Rad VersaDoc imager (Bio-Rad, Hercules, CA, USA).
-Images were quantitated using the ImageJ2 software (version 1.53c).
-
 ## *Prochlorococcus* comparative genomics {.unnumbered}
@@
 XXXMore TextXXX from Amanda & AuroraXXX
-Proteins derived from Clade HLXXX ecotypes of *P.
+Proteins derived from clade HLXXX ecotypes of *P.
 marinus* were detected in OMZ at depths up to 200 meters,  with O~2~ of 15 µM.
@@
                        "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
-                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4 (Clade HLI), SS120 (Clade LLIII) and MIT9313 (Clade LLIV).",
+                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4 (clade HLI), SS120 (clade LLIII) and MIT9313 (clade LLIV).",
                        "Columns show detections of proteins annotated as  Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
@@
 
-### MED4 Clade HLI {.unnumbered}
-
-Under 250 µM O~2~ the growth rates of *P. marinus* MED4, Clade HLI, increased with higher imposed PAR and longer photoperiods
+### MED4 clade HLI {.unnumbered}
+
+Under 250 µM O~2~ the growth rates of *P. marinus* MED4, clade HLI, increased with higher imposed PAR and longer photoperiods
 (Figure \@ref(fig:MED4PAR)), across all spectral wavebands.
@@
 Considering the range of PAR levels, and spectral bands that MED4 can utilize, MED4 can inhabit not just shallow depths, where light levels are high, but also deeper regions, characterized by a lower level of blue light, subject to the limitation of a photoperiod of more than 4 h, even after depth attenuation of light.
-The photoregimes of winter temperate zones, due to shorter photoperiods, exclude MED4 from growth at any depth, however temperate photoperiods and light levels for the remainder of the year are potentially adequate to support MED4 growth, if water temperatures warm into the Clade HLI tolerance range.
+The photoregimes of winter temperate zones, due to shorter photoperiods, exclude MED4 from growth at any depth, however temperate photoperiods and light levels for the remainder of the year are potentially adequate to support MED4 growth, if water temperatures warm into the clade HLI tolerance range.
 
@@
 
-### SS120 Clade LLIII {.unnumbered}
+### SS120 clade LLIII {.unnumbered}
 
 Under 250 µM O~2~, growth rates of *P.
-marinus* SS120, Clade LLIII, increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^ peak PAR and across all spectral wavebands (Figure \@ref(fig:SS120PAR)).
+marinus* SS120, clade LLIII, increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^ peak PAR and across all spectral wavebands (Figure \@ref(fig:SS120PAR)).
 No growth was observed under any blue light photoperiods when exposed to peak PAR of 90 µmol photons m^-2^ s^-1^ or greater.
@@
 
-### MIT9313 Clade LLIV {.unnumbered}
-
-Under 250 µM O~2~ growth rates of *P. marinus* MIT9313, Clade LLIV, increased with longer
+### MIT9313 clade LLIV {.unnumbered}
+
+Under 250 µM O~2~ growth rates of *P. marinus* MIT9313, clade LLIV, increased with longer
 photoperiods, under low 30 µmol photons m^-2^ s^-1^ peak PAR, (Figure \@ref(fig:MIT9313PAR)).
@@
 
-### MED4 Clade HLI {.unnumbered}
+### MED4 clade HLI {.unnumbered}
 
@@
 
-### SS120 Clade LLIII {.unnumbered}
+### SS120 clade LLIII {.unnumbered}
 
@@
 
-### MIT9313 Clade LLIV {.unnumbered}
+### MIT9313 clade LLIV {.unnumbered}
 
@@
 Under full atmospheric [O~2~] and blue light, LL clades of *Prochlorococcus* are restricted to growth under low light, in part because they suffer photoinhibition of Photosystem II (PSII) through several paths, including direct absorbance of UV or blue light, in parallel with generation of Reactive Oxygen Species (ROS) if the electron flow is slowed [@aroPhotoinhibitionPhotosystemII1993], producing damaging singlet oxygen (^1^O~2~) [@aroPhotoinhibitionPhotosystemII1993; @soitamoPhotoinhibitionMarinePicocyanobacteria2017; @murphyPhotoinactivationPhotosystemII2017; @hakalaEvidenceRoleOxygenevolving2005].
+The presence of NATL2A, a clade LLI, has been found near the ocean surface during deep ocean mixing [@malmstromTemporalDynamicsProchlorococcus2010].
+Malmstrom *et al*.
+attributes NATL2a tolerance to short exposures of high light to the presence of the genes encoding photolyase, a gene found in HL clades which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003].
 Repair of photoinactivated PSII relies on the removal of damaged PsbA [@mannInvolvementFtsHHomologue2000; @adamFtsHProteasesChloroplasts2005], followed by reassembly with newly synthesized PsbA [@nixonRecentAdvancesUnderstanding2010].
@@
 Furthermore, MIT9313 expressed primarily FtsH3, homologous to *Synechocystis* slr1463 involved in PSI biogenesis, and  FtsH expression did not increase in response to light stress in MIT9313.
-Through adaptation to steady low light, Clade LLIV *Prochlorococcus* instead allocate resources to processes other than dynamic regulation of PSII repair.
+Through adaptation to steady low light, clade LLIV *Prochlorococcus* instead allocate resources to processes other than dynamic regulation of PSII repair.
 
@@
 marinus*.
-Ribosome proteins from Clade HLI MED4, Clade LLIII SS120 and Clade LLIV MIT9313 show generally similar patterns vs.
+Ribosome proteins from clade HLI MED4, clade LLIII SS120 and clade LLIV MIT9313 show generally similar patterns vs.
 [O~2~] and depth, a proxy for peak PAR.
@@
                        "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
-                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4 (Clade HLI), SS120 (Clade LLIII) and MIT9313 (Clade LLIV).",
+                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4 (clade HLI), SS120 (clade LLIII) and MIT9313 (clade LLIV).",
                        "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome).",
@@
 knitr::include_graphics(file.path(FiguresIn, "NATLProchloroProteinMetabDepthO2.png"))
-```
-
-\newpage
-
-XXXX Mireille to finish Fig. caption when figure is complete. Add colour ? Remove []? XXX
-
-```{r  MED4ProteinAnnotated, fig.cap = MED4ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
-
-MED4ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade.  **",
-                                    "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",
-                                    "Numbers over each bar are fmole target protein per ug total protein.",
-                                    .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "MED4ProteinAnnotated.png"))
-
-```
-
-\newpage
-
-XXXX Mireille to finish Fig. caption when figure is complete. Add colour ? Remove []? XXX
-
-```{r  MIT9313ProteinAnnotated, fig.cap = MIT9313ProteinAnnotated_cap, fig.height = 6, fig.width = 8, echo = FALSE}
-
-MIT9313ProteinAnnotated_cap <- glue("**Bar graph indicating protein concentrations determined from lab grown *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade).  **",
-                                    "Growth Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^) and spectral wavelength are in rows;  2 levels of imposed growth dissolved O~2~ concentrations (µM) are in columns.",
-                                    "Numbers over each bar are fmole target protein per ug total protein.",
-                                    .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "MIT9313ProteinAnnotated.png"))
-
 ```
@@
 SS120, grew under photoperiods longer than 4 h and showed increasing growth rate with increasing photoperiods.
-Therefore, SS120 can potentially exploit the longer summer photoperiods in temperate zones but again cannot sustain growth in winter through its requirement for more than 4 h of light per day, even if water temperature warms into the Clade LLIII tolerance range.
+Therefore, SS120 can potentially exploit the longer summer photoperiods in temperate zones but again cannot sustain growth in winter through its requirement for more than 4 h of light per day, even if water temperature warms into the clade LLIII tolerance range.
 

### 2024-03-01 Code/Manuscript_O2.Rmd
Added Amanda's MIT9313 explanation for O2 and respiration

@@
 Repair of photoinactivated PSII relies on the removal of damaged PsbA [@mannInvolvementFtsHHomologue2000; @adamFtsHProteasesChloroplasts2005], followed by reassembly with newly synthesized PsbA [@nixonRecentAdvancesUnderstanding2010].
-Degradation of PsbA is a rate-limiting step in recovery from photoinhibition [@kanervoD1ProteinDegradation1993], mediated largely by a heterohexamer of (FtsH12)~3~, a membrane-bound (Sacharz et al., 2015)(Zak et al., 2001) metalloprotease  (Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
+Degradation of PsbA is a rate-limiting step in recovery from photoinhibition [@kanervoD1ProteinDegradation1993], mediated largely by a heterohexamer of (FtsH12)~3~, a membrane-bound [@sacharzSubCellularLocation2015; @zakInitialStepsBiogenesis2001] metalloprotease  [(Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
 [@adamFtsHProteasesChloroplasts2005; @boehmSubunitOrganizationSynechocystis2012a; @nixonRecentAdvancesUnderstanding2010; @komendaExposedNTerminalTail2007] (Pisareva et al., 2007; Sacharz et al., 2015),  @mannInvolvementFtsHHomologue2000, (AMANDA REF from ALGATECH).
@@
 [@malmstromTemporalDynamicsProchlorococcus2010] attributes the transport of LL ecotypes to the surface and consequent exposure to photoinhibitory high light levels as the reason for low cell abundances with increased mixed layer depth.
-@westNichePartitioningProchlorococcusPopulationsStratified1999 found the depth of the mixed layer strongly influenced the depth transition from HL to LL clades, but that factors other than light levels may influence the variations in the upper and lower depth limits of these ecotypes.
+West *et al*.
+[@westNichePartitioningProchlorococcusPopulationsStratified1999] found the depth of the mixed layer strongly influenced the depth transition from HL to LL clades, but that factors other than light levels may influence the variations in the upper and lower depth limits of these ecotypes.
 We hypothesize that low cell abundances of LL ecotypes in the mixed layer is likely driven in part by increased [O~2~],  and it is [O~2~] that constrains LL clades to deeper waters, not necessarily the light level.
@@
 These results are supported by Figure \@ref(fig:NATLProchloroPhotosynthDepthO2) showing PSI protein subunits annotated as derived from MIT9313 detected at depths \> 120 m, along with PSII subunits at depths from 50 m to 200 m in regions where O~2~ was 15 µM.
+
+MIT9313 is not “using” photosynthesis in low O~2~ environments to do CO~2~ fixation so much as to generate oxygen locally in an environment that is low enough to limit the ability to do respiration.
+The deep water environments that we see MIT 9313 are relatively nutrient rich and there is evidence in the literature of *Prochlorococcus* have  been observed to take up and metabolise various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017] and amino acids (Zubkov et al., 2004).
+They may be using photosynthesis to generate O~2~ to act as an electron sink for respiration.
+And maybe using ATP to take up food from the surroundings.
+Partensky *et al*.
+[@partenskyComparisonPhotosyntheticPerformances2018] found that in the low-light conditions found in the OMZ, MED4, SS120 and MIT9313 all became net O~2~ consumers, suggesting that the low light levels caused the respiratory chain to consume more O~2~ than the photosynthetic electron transport chain could generate and could potentially be contributing to the maintenance of the low O~2~ environment
 

### 2024-03-01 Code/Manuscript_O2.Rmd
Added proper citations

@@
 MIT9313 is not “using” photosynthesis in low O~2~ environments to do CO~2~ fixation so much as to generate oxygen locally in an environment that is low enough to limit the ability to do respiration.
-The deep water environments that we see MIT 9313 are relatively nutrient rich and there is evidence in the literature of *Prochlorococcus* have  been observed to take up and metabolise various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017] and amino acids (Zubkov et al., 2004).
+The deep water environments that we see MIT 9313 are relatively nutrient rich and there is evidence in the literature of *Prochlorococcus* have  been observed to take up and metabolise various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017; @munoz-marinProchlorococcusCanUse2013] and amino acids [@zubkovDepthRelatedAmino2004].
 They may be using photosynthesis to generate O~2~ to act as an electron sink for respiration.
@@
 Partensky *et al*.
-[@partenskyComparisonPhotosyntheticPerformances2018] found that in the low-light conditions found in the OMZ, MED4, SS120 and MIT9313 all became net O~2~ consumers, suggesting that the low light levels caused the respiratory chain to consume more O~2~ than the photosynthetic electron transport chain could generate and could potentially be contributing to the maintenance of the low O~2~ environment
+[@partenskyComparisonPhotosyntheticPerformances2018] found that in the low-light conditions found in the OMZ, MED4, SS120 and MIT9313 all became net O~2~ consumers, suggesting that the low light levels caused the respiratory chain to consume more O~2~ than the photosynthetic electron transport chain could generate and could potentially be contributing to the maintenance of the low O~2~ environment.
 

### 2024-03-01 Code/Manuscript_O2.Rmd
doug scan of Manuscript_O2.Rmd edits, notes on edits missing

--- 2024-03-01 Code/Manuscript_O2.Rmd
@@
 *Prochlorococcus marinus* comprises many strains, organized into clades, defined by 16S-23S intergenic transcribed ribosomal sequence signatures [@rocapGenomeDivergenceTwo2003].
-The clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined by High-Light (HL) or Low-Light (LL).
+The clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined as High-Light (HL) or Low-Light (LL).
 Of at least 12 known *Prochlorococcus* genetic clades only 5 to date have cultured representatives; HLI, HLII, LLI, LLII/III and LIV [@billerProchlorococcusStructureFunction2015].
-
 Current niches of *P.
@@
 Low-Light clades thrive in deeper ocean waters, extending beyond 200 m in depth [@partenskyProchlorococcusMarinePhotosynthetic1999], where only ~1% of the surface irradiance penetrates, primarily in the blue (450 nm) to green (520 nm) spectral range [@holtropVibrationalModesWater2021].
-Clade LLI includes cultured strain NATL2A, which prefers moderate irradiance typically between 30 and 100 m depth.
+Clade LLI includes cultured strain NATL2A, which prefers moderate irradiances typical of between 30 and 100 m depth.
 Clades LLII and LLIII, including cultured strain SS120, are grouped together as the second oldest phylogenetic lineage diversifying in the *P.
@@
 marinus* strains in clades LLV and LLVI also thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021; @lavinNovelLineagesProchlorococcus2010; @goerickeNovelNicheProchlorococcus2000; @garcia-robledoCrypticOxygenCycling2017; @johnsonEnergeticsGrowthKinetics1999].
-*Prochlorococcus marinus* LL ecotypes may dominate the phytoplankton within OMZ [@lavinNovelLineagesProchlorococcus2010; @ulloaCyanobacteriumProchlorococcusHas2021; @partenskyProchlorococcusAdvantagesLimits2010], where they may be net O~2~ consumers [@partenskyComparisonPhotosyntheticPerformances2018].
-
-HL clades are more evolved lineages, with reduced genome sizes in comparison to LL clades.
+*P.
+marinus* LL ecotypes may indeed dominate the phytoplankton within OMZ [@lavinNovelLineagesProchlorococcus2010; @ulloaCyanobacteriumProchlorococcusHas2021; @partenskyProchlorococcusAdvantagesLimits2010], where they may be net O~2~ consumers [@partenskyComparisonPhotosyntheticPerformances2018].
+
+HL clades are more recently branching lineages, with reduced genome sizes in comparison to LL clades.
 High-Light clades are typically dominant picophytoplankters in near-surface, oligotrophic waters, characterized by high light levels.
@@
 Predictions indicate a net global increase of *P.
-marinus* cell abundances of 29%, along with  poleward latitudinal shifts of at least 10° in marine phytoplankton niches by the end of this century [@flombaumPresentFutureGlobal2013; @bartonAnthropogenicClimateChange2016] in response to warming waters, with increases in *P.
+marinus* cell abundances of 29% [@flombaumPresentFutureGlobal2013{}, along with  poleward latitudinal shifts of at least 10° in marine phytoplankton niches by the end of this century  [@bartonAnthropogenicClimateChange2016] in response to warming waters, with increases in *P.
 marinus* of approximately 50% in the more poleward regions of their distributions.
@@
 Near the equator, photoperiod remains nearly constant at the ocean surface, approximately 12 hours (h) of daylight and 12 h of darkness throughout the year.
-The effective length of the photoperiod does, however attenuate with depth as dawn and dusk light at depth drops below levels needed for biological processes.
+The effective length of the photoperiod does, however, attenuate with depth as dawn and dusk light at depth drops below levels needed for biological processes.
 As *P.
@@
 Increasing sea temperatures are also causing decreases in [O~2~] across global oceans [@matearLongtermChangesDissolved2003], particularly toward the poles [@helmObservedDecreasesOxygen2011].
-Warmer ocean waters increase stratification, and decrease oxygen solubility at the surface, which in turn decreases oxygen mixing downwards by ocean currents [@garcia-sotoOverviewOceanClimate2021].
-Models predict that OMZ in the Pacific and Indian Oceans are expanding [@garcia-sotoOverviewOceanClimate2021; @buseckeDivergingFatesPacific2022].
-In spite of these expanding OMZ, Busecke *et al*.
-[@buseckeDivergingFatesPacific2022] project that the cores of the OMZ, where the oxygen levels are lowest, may actually contract.
+Warmer ocean waters decrease oxygen solubility at the surface, and increase stratification, which in turn decreases oxygen mixing downwards by ocean currents [@garcia-sotoOverviewOceanClimate2021].
+Models predict that OMZ in the Pacific and Indian Oceans are expanding [@garcia-sotoOverviewOceanClimate2021; @buseckeDivergingFatesPacific2022], although the cores of the OMZ, where the oxygen levels are lowest, may actually contract  [@buseckeDivergingFatesPacific2022].
 
@@
 marinus* MIT9313, a clade LLIV strain, was isolated from the North Atlantic Gulf Stream at a depth of 135 m.
-At these depths, light attenuation and spectral shifts occur, resulting in low blue and green light, while [O~2~] varies from near-surface saturation levels to decreased concentrations, but does not necessarily decrease systematically with depth [@billheimerOxygenSeasonalityUtilization2021].
-
-Genes encoding much of the photosynthetic apparatus is highly conserved in *Prochlorococcus* [@kettlerPatternsImplicationsGene2007], Photosynthetic organisms absorb light energy within the Photosynthetically Active Radiation (PAR) range, 350 to 700 nm, for photosynthesis [@morelAvailableUsableStored1978].
+At these depths, light attenuation and spectral shifts occur, resulting in low blue light, while [O~2~] varies from near-surface saturation levels to decreased concentrations, but does not necessarily decrease systematically with depth [@billheimerOxygenSeasonalityUtilization2021].
+
+Photosynthetic organisms absorb light energy within the Photosynthetically Active Radiation (PAR) range, 350 to 700 nm, for photosynthesis [@morelAvailableUsableStored1978].
 Photosynthetically Usable Radiation (PUR) represents the fraction of PAR that is absorbed by the pigments of a given photosynthetic organism [@morelAvailableUsableStored1978], taking into account the specific spectral wavebands these pigments absorb.
-*Prochlorococcus marinus* light-harvesting complexes show an absorption maxima of 442 nm for divinyl chlorophyll *a* and 478 nm for divinyl chlorophyll *b* [@goerickePigmentsProchlorococcusMarinus1992] allowing *P.
-marinus* to efficiently harvest blue light in the 400 nm to 500 nm range [@morelAvailableUsableStored1978] where only blue spectral wavelengths prevail in deep ocean habitats [@holtropVibrationalModesWater2021], thus photosynthetic efficiency may vary among clades [@hessPhotosyntheticApparatusProchlorococcus2001; @moorePhotophysiologyMarineCyanobacterium1999].
+*Prochlorococcus marinus* Pcb light-harvesting complexes show an absorption maxima of 442 nm for divinyl chlorophyll *a* and 478 nm for divinyl chlorophyll *b* [@goerickePigmentsProchlorococcusMarinus1992] allowing *P.
+marinus* to efficiently harvest blue light in the 400 nm to 500 nm range [@morelAvailableUsableStored1978] corresponding to blue spectral wavelengths prevailing in deep ocean habitats [@holtropVibrationalModesWater2021].
 In *P.
-marinus* small cell diameters, from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992], and simple cell structures, minimize the complication of pigment package effect or intracellular self-shading [@morelProchlorococcusSynechococcusComparative1993] contributing to efficient optical absorption.
+marinus* small cell diameters, from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992], and simple cell structures, minimize the complication of pigment package effect or intracellular self-shading [@morelProchlorococcusSynechococcusComparative1993] contributing to efficient optical absorption, although photosynthetic efficiency may vary among clades [@hessPhotosyntheticApparatusProchlorococcus2001; @moorePhotophysiologyMarineCyanobacterium1999].
 
 Given the different spectral light regimes typical of the niches of different ecotypes, expressing growth rates in terms of cumulative diel PUR might simplify different photoperiods, spectral bands, and PAR levels into a common parameter, making growth response comparisons across strains and different oxygen levels more accessible.
-We also aimed to detect whether growth responses are driven simply by cumulative diel PUR, or whether specific photoperiods, spectral bands or PAR levels have independent, albeit interacting, effects on growth.
+We  aimed to detect whether growth responses are driven simply by cumulative diel PUR, or whether specific photoperiods, spectral bands or PAR levels have independent, albeit interacting, effects on growth.
 We therefore analyzed growth rates in terms of cumulative diel PUR.
@@
 We discuss our findings in relation to analyses of genomic sequences [@changBRENDAELIXIRCore2021] across clades of *P.
-marinus*, showing that differences in the presence of genes encoding oxygen-dependent enzymes, and DNA repair enzymes, can help explain differential growth responses of strains under the matrix of light and [O~2~] conditions of this study.
+marinus*, showing that differences in the expression and presence of genes encoding protein turnover, oxygen-dependent enzymes, and DNA repair enzymes, can explain the differential growth responses of strains under the matrix of light and [O~2~] conditions of this study.
 
@@
 Full protein sequences corresponding to detected proteins were obtained from UniProt (https://www.uniprot.org/) and analyzed in Molecular Evolution and Genetic Analyses X (MEGAX) software  (https://www.megasoftware.net/).
-Sequences for proteins for each of the thirteen Prochlorococcus strains identified in the dataset were aligned with MUSCLE using UPGMA cluster method and a lambda of 24 with a -2.9 gap open penalty and 1.20 hydrophobicity multiplier.
+Sequences for proteins for each of the thirteen *Prochlorococcus* strains identified in the dataset were aligned with MUSCLE using UPGMA cluster method and a lambda of 24 with a -2.9 gap open penalty and 1.20 hydrophobicity multiplier.
 Overall mean pairwise distance between protein sequences was determined using bootstrap variance estimation methods.
@@
 
-Three xenic cultures of *P. marinus* were obtained from Bigelow Labs, NCMA
-Maine, USA. MED4 (CCMP1986) is from High-Light adapted (HLI) clade; SS120
-(CCMP1375) is from Low-Light adapted (LLIII) clade; and MIT9313 (CCMP2773)
-is from Low-Light adapted (LLIV) clade. Cultures were
-maintained in incubators set to 22°C with a light/dark cycle of 12 h.
+Three xenic cultures of *P.
+marinus* were obtained from Bigelow Labs, NCMA Maine, USA.
+MED4 (CCMP1986) is from High-Light adapted (HLI) clade; SS120 (CCMP1375) is from Low-Light adapted (LLIII) clade; and MIT9313 (CCMP2773) is from Low-Light adapted (LLIV) clade.
+Cultures were maintained in incubators set to 22°C with a light/dark cycle of 12 h.
 The PAR level for maintenance cultures reflected PAR)in the source niche of the ecotype; MED4, of 160 µmol photons m^-2^ s^-1^ with illumination from STANDARD Products Inc.
-Cool White F24T5/41K/8/HO/PS/G5/STD, 24 watts, fluorescent bulbs; SS120 and
-MIT9313 at 30 µmol photons m^-2^ s^-1^ with illumination from Philips Cool White F14T5/841 Alto, 14 watts, fluorescent bulbs. To maintain active growth all strains were
-transferred weekly with 1 in 5 dilutions with Pro99 media
-[@mooreCulturingMarineCyanobacterium2007] prepared with autoclaved artificial
-seawater [@bergesEvolutionArtificialSeawater2001].
+Cool White F24T5/41K/8/HO/PS/G5/STD, 24 watts, fluorescent bulbs; SS120 and MIT9313 at 30 µmol photons m^-2^ s^-1^ with illumination from Philips Cool White F14T5/841 Alto, 14 watts, fluorescent bulbs.
+To maintain active growth all strains were transferred weekly with 1 in 5 dilutions with Pro99 media [@mooreCulturingMarineCyanobacterium2007] prepared with autoclaved artificial seawater [@bergesEvolutionArtificialSeawater2001].
 
@@
 [O~2~] levels (2.5 µM, 25 µM, 250 µM) were imposed by bubbling tubes with varying ratios of air and
-Nitrogen (N~2~), with consistent 0.05% of Carbon Dioxide (CO~2~)
-gas, delivered through a 0.2 μm sterile microfilter via a G400 gas mixing system (Qubit Systems Inc., Kingston, Ontario, Canada). [O~2~] in situ was verified using oxygen optodes (PyroScience,
-Germany) inserted into tubes for
-real-time measurements, with a temperature probe in
-the aquarium of the bioreactor to correct [O~2~] measures for temperature
-fluctuations. In addition, the Pyroscience software corrected [O~2~] based on the
-salinity of the media (32 ppt).
+Nitrogen (N~2~), with consistent 0.05% of Carbon Dioxide (CO~2~) gas, delivered through a 0.2 μm sterile microfilter via a G400 gas mixing system (Qubit Systems Inc., Kingston, Ontario, Canada).
+[O~2~] in situ was verified using oxygen optodes (PyroScience, Germany) inserted into tubes for real-time measurements, with a temperature probe in
+the bath of the bioreactor to correct [O~2~] measures for temperature fluctuations.
+In addition, the Pyroscience software corrected [O~2~] based on the salinity of the media (32 ppt).
 The flow rate of the gas mixture was controlled, but variations in bubbling speed, PAR and culture density affected the [O~2~] achieved in each tube.
-A low [O~2~] of 0.5 µM - 5 µM (reported as 2.5 µM hereafter),  was achieved by sparging with a gas mixture containing 99.95% N~2~ and 0.05%
-CO~2~.
+A low [O~2~] of 0.5 µM - 5 µM (reported as 2.5 µM hereafter),  was achieved by sparging with a gas mixture containing 99.95% N~2~ and 0.05% CO~2~.
 An intermediate [O~2~] of 10 - 25 µM (reported hereafter as 25 µM) was achieved by sparging with a gas mixture containing 98.95% N~2~, 0.05% CO~2~ and 1% O~2~.
@@
 
-*In situ* measurements of Optical Density (OD) 680 nm, a proxy for cell suspension density, cell size dependent scatter and cell chlorophyll content;  and OD 720 nm, a proxy for cell suspension density and cell size dependent scatter, were recorded every 5 minutes over least 8 to 14 days,  depending on the
-duration of the lag phase, if any. All data obtained from the Multicultivator were saved
-as comma separated values files  (https://github.com/FundyPhytoPhys/prochlorococcus_o2/tree/main/Data/RawData).
-
-PAR of 180, 90 or 30 µmol photons m^-2^ s^-1^, and spectral wavebands (white LED
-full spectrum, 660 nm, and 450 nm) were chosen to approximate light
-levels and spectral colours spanning the vertical ocean water column, from
-near-surface to the lower euphotic zone depths. Photoperiods were chosen to approximate diel cycles characteristic of current and hypothetical future
-niches of *P. marinus*; 16 h represents
-temperate (45°N) summer at the ocean surface; 12 h for equatorial (0°N)
-ocean surface or temperate (45°N) spring and fall ocean surface or
-temperate (45°N) summer at deeper ocean depths; 8 h for temperate (45°N)
-winter at the surface or at temperate (45°N) spring and fall at depth
-and equatorial (0°N) deep ocean depths; and 4 h for temperate (45°N)
-winter or deep ocean depths during temperate (45°N) spring and fall.
+*In situ* measurements of Optical Density (OD) 680 nm, a proxy for cell suspension density, cell size dependent scatter and cell chlorophyll content;  and OD 720 nm, a proxy for cell suspension density and cell size dependent scatter, were recorded every 5 minutes over least 8 to 14 days,  depending on the duration of the lag phase, if any.
+All data obtained from the Multicultivator were saved as comma separated values files  (https://github.com/FundyPhytoPhys/prochlorococcus_o2/).
+
+PAR of 180, 90 or 30 µmol photons m^-2^ s^-1^, and spectral wavebands (white LED full spectrum, 660 nm, and 450 nm) were chosen to approximate light
+levels and spectral colours spanning the vertical ocean water column, from near-surface to the lower euphotic zone depths.
+Photoperiods were chosen to approximate diel cycles characteristic of current and hypothetical future niches of *P.
+marinus*; 16 h represents temperate (45°N) summer at the ocean surface; 12 h for equatorial (0°N)
+ocean surface or temperate (45°N) spring and fall ocean surface or temperate (45°N) summer at deeper ocean depths; 8 h for temperate (45°N) winter at the surface or at temperate (45°N) spring and fall at depth and equatorial (0°N) deep ocean depths; and 4 h for temperate (45°N) winter or deep ocean depths during temperate (45°N) spring and fall.
 
@@
 Data files (.csv) saved from the Multicultivator software were imported into R-Studio for data management [@R-tidyverse], growth rate calculations CITATION, comparisons of model fits [@harrisonPhotosynthesisirradianceRelationshipsPolar1986], and visualization.
-The chlorophyll proxy
-optical density (OD~680~ - OD~720~;  ΔOD) was used to determine the chlorophyll specific growth
-rate (µ, d^-1^) for each treatment combination.
+The chlorophyll proxy optical density (OD~680~ - OD~720~;  ΔOD) was used to determine the chlorophyll specific growth rate (µ, d^-1^) for each treatment combination.
 We first used a rolling mean from the R package *`zoo`* [@R-zoo] to calculate the average ΔOD data over a 1-hour window to lower the influence of outlier points and remove data points collected during post stationary phase, when applicable.
-We used the Levenberg-Marquardt algorithm
-[@bellaviaLevenbergMarquardtMethod2018] modification of the non-linear
-least squares,  using the R package *`minpack.lm`*
-[@R-minpack.lm], to fit a logistic
-equation (Equation \@ref(eq:GrowthRate)); where ΔOD~max~ is maximum ΔOD, ΔOD~min~ is minimum ΔOD, t is time
+We used the Levenberg-Marquardt algorithm [@bellaviaLevenbergMarquardtMethod2018] modification of the non-linear least squares,  using the R package *`minpack.lm`*
+[@R-minpack.lm], to fit a logistic equation (Equation \@ref(eq:GrowthRate)); where ΔOD~max~ is maximum ΔOD, ΔOD~min~ is minimum ΔOD, t is time
 duration over the growth trajectory.
@@
 
-Figure \@ref(fig:deltaODLogGrowthPlot) is an example of chlorophyll specific
-growth estimates fitted from the high resolution ΔOD measurements for
-each tube in a Multicultivator. The residuals of the logistic growth
-curve fit are shown and the growth spectral waveband is plotted and
-illustrates the imposed PAR (µmol photons m^-2^ s^-1^) and photoperiod
-(h). Annotated code for data import, transformations and analyses is available at https://github.com/FundyPhytoPhys/prochlorococcus_o2/tree/main/Data/RawData
-
-A Generalized Additive Model (GAM) [@woodGeneralizedAdditiveModels2017] was applied to the
-relation between chlorophyll-specific µ, d^-1^  to photoperiod and PAR level,  for each growth [O~2~] level, and for the blue and red wavebands for growth, for each *P.marinus* strain in this study.
+Figure \@ref(fig:deltaODLogGrowthPlot) is an example of chlorophyll specific growth estimates fitted from the high resolution ΔOD measurements for each tube in a Multicultivator.
+The residuals of the logistic growth curve fit are shown and the growth spectral waveband is plotted and illustrates the imposed PAR (µmol photons m^-2^ s^-1^) and photoperiod
+(h). Annotated code for data import, transformations and analyses is available at https://github.com/FundyPhytoPhys/prochlorococcus_o2/  MAKE SURE RePOSTIORY IS PUBLICXXXX
+
+A Generalized Additive Model (GAM) [@woodGeneralizedAdditiveModels2017] was applied to the relation of chlorophyll-specific µ, d^-1^  to photoperiod and PAR level,  for each growth [O~2~] level, and for the blue and red wavebands for growth, for each *P.marinus* strain in this study.
 The R package *`mgcv`* [@R-mgcv] was used to model the growth rate with smoothing terms and indicate the 90, 50 and 10% quantiles for growth rate across the levels of factors.
@@
 Our priority was the effects of ecologically relevant blue light on growth trends.
-We included analyses of growth responses to red light, which is not ecophysiologically relevant, but which might prove mechanistically informative [@murphyPhotoinactivationPhotosystemII2017].
+We also included GAM analyses of growth responses to red light, which is not ecophysiologically relevant, but which might prove mechanistically informative [@murphyPhotoinactivationPhotosystemII2017].
 
@@
 Radiation (PAR) was first determined using the reported delivery of sinusoidal diel PAR regimes by the Multicultivators, point validated using a LI-250 quantum sensor (LI-COR Inc.,Lincoln, NE, USA).
-An emission profile from 400 nm to 700 nm of each coloured LED
-light of the MCMIX-OD Multicultivator and the white LED light of the MC1000-OD Multicultivator was obtained using a Jaz spectrometer (Ocean Optics, Inc.,Dunedin, FL, USA) equipped with a fiber
-optic cable, HH2 FiberOpticJmp (Part number A901073, Malvern Panalytical
-Ltd, Malvern, UK). Each LED spectrum was then normalized to its emission maximum.
-An *in-vivo* whole cell absorbance spectrum for each *P. marinus* strain under each spectral growth condition was obtained using the Olis 14 UV/VIS Clarity
-Spectrophotometer (Olis Inc., Bogart, GA, USA) to scan across range of λ = 350 nm to 750 nm at 1 nm intervals.
+An emission profile from 400 nm to 700 nm of each coloured LED light of the MCMIX-OD Multicultivator and the white LED light of the MC1000-OD Multicultivator was obtained using a Jaz spectrometer (Ocean Optics, Inc.,Dunedin, FL, USA) equipped with a fiber optic cable, HH2 FiberOpticJmp (Part number A901073, Malvern Panalytical Ltd, Malvern, UK).
+Each LED spectrum was then normalized to its emission maximum.
+An *in-vivo* whole cell absorbance spectrum for each *P.
+marinus* strain under each spectral growth condition was obtained using the Olis 14 UV/VIS Clarity Spectrophotometer (Olis Inc., Bogart, GA, USA) to scan across range of λ = 350 nm to 750 nm at 1 nm intervals.
 The path length of the internally reflective cavity of the Olis spectrophotometer was corrected to a 1 cm path length using the Javorfi correction method [@javorfiQuantitativeSpectrophotometryUsing2006] on PRO 99 media subtracted whole cell absorbance spectra.
@@
 
-The applied photoperiods were delivered using the sine circadian light function of the PSI Multicultivator to simulate light exposure approximating sun rise through to sunset.
+The applied photoperiods were delivered using the sinusoidal circadian light function of the PSI Multicultivator to simulate light exposure approximating sun rise through to sunset.
 The area under the sinusoidal curves is equivalent to the area of a triangular photoregime of equivalent photoperiod (Campbell, unpub), therefore the equation to determine the cumulative diel PUR (µmol photons m^-2^ d^-1^) is one half of the base (photoperiod) multiplied by the height (PUR) (Equation \@ref(eq:SumPURDay)); where PUR is the actinic absorbed light calculated from equation \@ref(eq:PUR) (µmol photons m^-2^ s^-1^), 3600 is the time conversion from seconds to hour and photoperiod is the imposed photoperiod (h).
@@
 marinus* and each spectral waveband.
+
+We fit the response of chlorophyll specific growth rate to cumulative diel PUR using the equation of Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] across strain and [O~2~] to compare growth response between 660 nm (red) and 450 nm (blue) growth light and additionally, to compare growth response between specific photoperiods (4 h, 8 h, 12 h, 16 h) and a fit across pooled photoperiod data.
+To examine statistical differences between the modeled fits, we performed one-way ANOVA comparing the model output parameters assigning significant differences when the p value was < 0.05.
 
@@
 
-## Statistical analyses {.unnumbered}
-
-We fit the response of chlorophyll specific growth rate to cumulative diel PUR using the equation of Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] across strain and [O~2~] to compare growth response between 660 nm (red) and 450 nm (blue) growth light and additionally, to compare growth response between specific photoperiods (4 h, 8 h, 12 h, 16 h) and a fit across pooled photoperiod data.
-To examine statistical differences between the modeled fits, we performed one-way ANOVA comparing the model output parameters assigning significant differences when the p value was < 0.05.
-
 ## *Prochlorococcus* comparative genomics {.unnumbered}
 
-Using the dataset Omar *et al*.
-[@omarAnnotationGenesEncoding2023], we filtered the dataset for Enzyme Commission Numbers (EC numbers), or Kegg Orthology Numbers (KO numbers) identified by BRENDA  [@changBRENDAELIXIRCore2021] as 'natural substrates' for O~2~ in *P.
-marinus* (MED4, MIT9313, SS120, and NATL2A) in order to generate a subset containing only those orthologs encoding enzymes directly mediating O~2~ metabolism.
+ We filtered the dataset of Omar *et al*.
+[@omarAnnotationGenesEncoding2023], for Enzyme Commission Numbers (EC numbers), or Kegg Orthology Numbers (KO numbers) identified by BRENDA  [@changBRENDAELIXIRCore2021] as 'natural substrates' for O~2~ in *P.
+marinus* strains (MED4, MIT9313, SS120, and NATL2A).
 We grouped orthologs together by EC number and their KO number and determined the occurrences of individual orthologs encoding each EC number, or KO number when EC number was not available, in a given strain.
@@
 Remove this once added XXXX
+ XXXXADD METHODS for DNA REpair and for light dependent EnzymesXXXX
 
@@
 Proteins from 13 annotated strains of *P.
-marinus* were detected across depths and oxygen concentrations in the data set analyzed.
-We have focused our analysis here on photosynthetically relevant protein complexes from three strains: HLI MED4; LLIII SS120 and LLIV MIT9313.
-Figure \@ref(fig:NATLProchloroPhotosynthDepthO2) plots the observation of core photosynthetic complexes (Photosystem II, the Cytochromeb6f complex, Phototsystem I, ATP Synthase and Rubisco) in these strains as a function of depth (a proxy for light intensity) and measured [O~2~].
-Photosynthetic complexes from MED4 were detected throughout the water column predominantly at high [O~2~].
-Complexes from LLIII strain SS120 were detected throughout the water column in high [O~2~] and at depth in low [O~2~] samples.
+marinus* were detected across depths and oxygen concentrations in the ocean proteins data set analyzed.
+We focused our analysis here on photosynthetic protein complexes, grouped by clade.
+Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) plots the observation of core photosynthetic complexes (Photosystem II, the Cytochromeb6f complex, Phototsystem I, ATP Synthase and Rubisco) across clades, as a function of depth (a proxy for light intensity) and measured [O~2~].
+Photosynthetic complexes from HLI (ex.
+MED4) were detected throughout the water column, predominantly at high [O~2~].
+Complexes from Clade LLIII (ex.
+SS120) were detected throughout the water column in high [O~2~] and at depth in low [O~2~] samples.
 Photosystem I and II were only detected at low [O~2~].
-The exclusive assignment of ATP Synthase peptides to MIT9313 may result from the high conservation of protein sequence for this complex.
+The exclusive assignment of ATP Synthase peptides to Clade IV (ex.
+MIT9313) may result from the high conservation of protein sequence for this complex.
+
+XXXXCheck text for figureXXXX
 
@@
 
+XXXRewrite caption if we change figure versionXXX
 ```{r NATLProchloroPhotosynthDepthO2, fig.cap = NATLProchloroPhotosynthDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
@@
 Guided by the evidence of ocean distributions of proteins from *Prochlorococcus* we set up a matrix of photoperiods, PAR, spectral bands, and [O~2~] to approximate current, and potential future, latitudinal, depth and seasonal niches for *Prochlorococcus* strains.
-As aforementioned, growth under red light could prove mechanistically informative [@murphyPhotoinactivationPhotosystemII2017] to factors limiting *Prochlorococcus* growth, we therefore included the red spectral waveband even though it is not characteristic of representative *Prochlorococcus* niches.
+As mentioned, growth under red light could prove mechanistically informative [@murphyPhotoinactivationPhotosystemII2017] to factors limiting *Prochlorococcus* growth, we therefore included the red spectral waveband even though it is not representative of *Prochlorococcus* niches.
 Although *Prochlorococcus* is currently limited to a narrow range of surface photoperiods, potential poleward latitudinal expansions, in combination with attenuation of light with depth, mean *Prochlorococcus* may potentially encounter a wide range of photoperiods.
-Our growth rate determinations generally agreed with those from Moore *et al*.
+Our growth rate determinations generally agree with those from Moore *et al*.
 [@mooreComparativePhysiologySynechococcus1995], for white LED and 250 µM O~2~, but our study is, to our knowledge, the first to analyze the interactive growth responses of *Prochlorococcus* strains to varying [O~2~], spectral wavebands and photoperiods.
 
-### MED4 clade HLI {.unnumbered}
-
-Under 250 µM O~2~ the growth rates of *P. marinus* MED4, clade HLI, increased with higher imposed PAR and longer photoperiods
+*P. marinus* MED4, clade HLI, growth under 250 µM O~2~ increased with higher imposed PAR and longer photoperiods
 (Figure \@ref(fig:MED4PAR)), across all spectral wavebands.
@@
 
-### SS120 clade LLIII {.unnumbered}
-
-Under 250 µM O~2~, growth rates of *P.
-marinus* SS120, clade LLIII, increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^ peak PAR and across all spectral wavebands (Figure \@ref(fig:SS120PAR)).
+*P.
+marinus* SS120 clade LLIII,  growth under 250 µM O~2~ increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^ peak PAR and across all spectral wavebands (Figure \@ref(fig:SS120PAR)).
 No growth was observed under any blue light photoperiods when exposed to peak PAR of 90 µmol photons m^-2^ s^-1^ or greater.
@@
 
-### MIT9313 clade LLIV {.unnumbered}
-
-Under 250 µM O~2~ growth rates of *P. marinus* MIT9313, clade LLIV, increased with longer
+*P. marinus* MIT9313, clade LLIV, growth under 250 µM O~2~ increased with longer
 photoperiods, under low 30 µmol photons m^-2^ s^-1^ peak PAR, (Figure \@ref(fig:MIT9313PAR)).
@@
 Cumulative diel PUR can potentially collapse photoperiod, PAR and spectral wavebands to a common metric of photosynthetically active light absorbed per day.
-Cumulative diel PUR dose (µmol photons m^-2^ d^-1^) was calculated from the imposed PUR XXX should say imposed PAR??
-or absorbed PUR ??
-XXX (µmol photons m^-2^ s^-1^) and photoperiod (h).
+Cumulative diel PUR dose (µmol photons m^-2^ d^-1^) was calculated from the imposed PUR (µmol photons m^-2^ s^-1^) and photoperiod (h).
 We plotted growth rates vs.
@@
 Due to the absorption of *P.
-marinus* pigments in the blue spectral waveband range, the maximum imposed cumulative diel PUR under blue light is almost 3 times that of white LED light, and about 6 times the red light treatment (Figure \@ref(fig:PurParPlot)), despite being derived from the same imposed photoperiods and peak PAR regimes.
+marinus* pigments in the blue spectral waveband range, the maximum cumulative diel PUR under blue light is almost 3 times that of white LED light, and about 6 times the red light treatment (Figure \@ref(fig:PurParPlot)), despite being derived from the same photoperiods and peak PAR regimes.
 As such, only blue light experiments extend beyond cumulative diel PUR of ~ 2 x 10^6^ µmol photons m^-2^ d^-1^.
-This bias in the range of data leads to caution in comparing model fits of growth in response to cumulative diel PUR under red vs.
+This bias in the range of data leads us to caution in comparing model fits of growth in response to cumulative diel PUR under red vs.
 blue wavebands.
@@
 ### MED4 clade HLI {.unnumbered}
+
+XXXXCHECK figure references here; not sure White Light data is shown on the bluered figure; refer to Supplemental?XXXX
 
@@
 [@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for growth under red light, for MED4, because red light provokes less photoinactivation of PSII, than equivalent levels of blue light.
-For distinct photoperiod fits refer to figure \@ref(fig:AllStrainPurFitsPlots)A.
+For distinct fits for different photoperiods refer to figure \@ref(fig:AllStrainPurFitsPlots)A.
 
@@
 Under 25 µM O~2~ red light again generated more growth of SS120 per unit cumulative diel PUR, than did blue light, again consistent with lower cost of growth through lower photoinactivation under red light.
-For distinct photoperiod fits refer to figure \@ref(fig:AllStrainPurFitsPlots)B.
+For distinct fits for different photoperiods refer to figure \@ref(fig:AllStrainPurFitsPlots)B.
 
@@
 
-Our data support enhanced growth under conditions of low cumulative diel PUR and 660 nm (red) spectral bandwidth, as supported by Murphy *et al*.[@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue wavebands.
+Our data again support enhanced growth under conditions of low cumulative diel PUR and 660 nm (red) spectral bandwidth, consistent with Murphy *et al*.[@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue, wavebands.
 Interestingly, this protective effect of red light disappears for MIT9313 growing under 2.5 µM O~2~, possibly because photoinactivation is strongly suppressed under this low [O~2~].
-For distinct photoperiod fits refer to figure \@ref(fig:AllStrainPurFitsPlots)C.
+For distinct fits for different photoperiod fits refer to figure \@ref(fig:AllStrainPurFitsPlots)C.
 
@@
 MED4, SS120 and MIT9313 have been successfully cultured in laboratories  [@mooreComparativePhysiologySynechococcus1995; @mooreCulturingMarineCyanobacterium2007], and used to show that ecotypic classifications correspond to biochemical differences among strains [@bonisteelStrainSpecificDifferences2018].
-CITATONS OTHERS.
 
 Under full atmospheric [O~2~] and blue light, LL clades of *Prochlorococcus* are restricted to growth under low light, in part because they suffer photoinhibition of Photosystem II (PSII) through several paths, including direct absorbance of UV or blue light, in parallel with generation of Reactive Oxygen Species (ROS) if the electron flow is slowed [@aroPhotoinhibitionPhotosystemII1993], producing damaging singlet oxygen (^1^O~2~) [@aroPhotoinhibitionPhotosystemII1993; @soitamoPhotoinhibitionMarinePicocyanobacteria2017; @murphyPhotoinactivationPhotosystemII2017; @hakalaEvidenceRoleOxygenevolving2005].
-The presence of NATL2A, a clade LLI, has been found near the ocean surface during deep ocean mixing [@malmstromTemporalDynamicsProchlorococcus2010].
-Malmstrom *et al*.
-attributes NATL2a tolerance to short exposures of high light to the presence of the genes encoding photolyase, a gene found in HL clades which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003].
 Repair of photoinactivated PSII relies on the removal of damaged PsbA [@mannInvolvementFtsHHomologue2000; @adamFtsHProteasesChloroplasts2005], followed by reassembly with newly synthesized PsbA [@nixonRecentAdvancesUnderstanding2010].
@@
 In contrast, representative LLIV strain MIT9313 showed less overall expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem.
-Furthermore, MIT9313 expressed primarily FtsH3, homologous to *Synechocystis* slr1463 involved in PSI biogenesis, and  FtsH expression did not increase in response to light stress in MIT9313.
+Furthermore, MIT9313 expressed primarily FtsH3, homologous to *Synechocystis* slr1463 involved in PSI biogenesis, andFtsH expression did not increase in response to light stress in MIT9313.
 Through adaptation to steady low light, clade LLIV *Prochlorococcus* instead allocate resources to processes other than dynamic regulation of PSII repair.
@@
 \newpage
-
+XXXXEdit text depending upon which ocean protein figures we useXXXXX
 Ocean detections of proteins mediating protein metabolism support this interpretation of distinct FtsH function across clades of *P.
@@
 marinus* MIT9313 suffered photoinhibition, resulting from the inactivation of PSII caused by the production of the reactive oxygen species, hydrogen peroxide.
-This photoinhibition is compounded by the limited inducible repair mechanism for PSII, due to the absence of FtsH 2 and 3  expression in *P.
+This photoinhibition is compounded by the limited inducible repair mechanism for PSII, due to the absence of FtsH 2 and 3 XXXXCHECK TERMINOLOGYXXXX expression in *P.
 marinus* MIT9313 [@bonisteelStrainSpecificDifferences2018].
-We hypothesize that under the conditions of our high light and 2.5 µM and 25 µM O~2~ experiments, the activity of the (S)-2-hydroxy-acid oxidase enzyme is suppressed.
-As a result, the catalyzed production of hydrogen peroxide is inhibited, leading to less PSII damage, allowing MIT9313 to avoid photoinhibition and circumvent its limitations on PSII repair.
+We hypothesize that under the conditions of our high light and 2.5 µM or 25 µM O~2~ experiments, the activity of the (S)-2-hydroxy-acid oxidase enzyme is suppressed.
+As a result, the catalyzed production of hydrogen peroxide is inhibited, leading to less PSII damage, allowing MIT9313 to avoid photoinhibition and circumvent its limitations on PSII repair to exploit higher light.
 Figure \@ref(fig:ProchlorococcusEnzymeKms) also shows that *P.
@@
 Furthermore, the protective effect of lower [O~2~], allowing these strains to grow at higher light, may relate in part to suppression of DNA damage when generation of Reactive Oxygen Species is suppressed at lower [O~2~].
+NATL2A, a clade LLI, has been found near the ocean surface during deep ocean mixing [@malmstromTemporalDynamicsProchlorococcus2010].
+Malmstrom *et al*.
+attributes NATL2a tolerance to short exposures of high light to the presence of the genes encoding photolyase, a gene found in HL clades which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003].
 *Prochlorococcus* are highly susceptible to hydrogen peroxide (H~2~O~2~) toxicity as they lack genes which scavenge H~2~O~2~ molecules [@morrisFacilitationRobustGrowth2008].
@@
 marinus* varies depending on the season, which influences achieved underwater photoperiods and light levels.
-Temperate summer delivers 11 hours of blue waveband light
-underwater, above the photic threshold of 20 µmol photons m^-2^ s^-1^, while temperate spring/fall delivers 8 hours of blue waveband light
-underwater, photoperiod ranges which are permissive for growth of all three *P. marinus*. In contrast temperate winter delivers only about 2 h
-of blue waveband light underwater above the photic threshold, which precludes growth of MED4 and SS120, even if winter waters reached
-permissive temperatures. MIT9313 and SS120 will be excluded from near-surface growth niches by high PAR, unless OMZ zones extend to the near surface.
+Temperate summer delivers 11 hours of blue waveband light underwater, above the photic threshold of 20 µmol photons m^-2^ s^-1^, while temperate spring/fall delivers 8 hours of blue waveband light underwater, photoperiod ranges which are permissive for growth of all three *P.
+marinus*.
+In contrast temperate winter delivers only about 2 h
+of blue waveband light underwater above the photic threshold, which precludes growth of MED4 and SS120, even if winter waters reached permissive temperatures.
+MIT9313 and SS120 will be excluded from near-surface growth niches by high PAR, unless OMZ zones extend to the near surface.
 
@@
 
-MIT9313 is not “using” photosynthesis in low O~2~ environments to do CO~2~ fixation so much as to generate oxygen locally in an environment that is low enough to limit the ability to do respiration.
-The deep water environments that we see MIT 9313 are relatively nutrient rich and there is evidence in the literature of *Prochlorococcus* have  been observed to take up and metabolise various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017] and amino acids (Zubkov et al., 2004).
-They may be using photosynthesis to generate O~2~ to act as an electron sink for respiration.
-And maybe using ATP to take up food from the surroundings.
+In future work we aim to test whether MIT9313 is not “using” photosynthesis in low O~2~ environments to drive CO~2~ fixation, so much as to generate oxygen locally to support  respiration.
+The deep water environments typical for MIT 9313 are relatively nutrient rich and  *Prochlorococcus* take up and metabolise various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017; @munoz-marinProchlorococcusCanUse2013] and amino acids [@zubkovDepthRelatedAmino2004].
+They may be using photosynthesis to generate O~2~ to act as an electron sink for respiration, to generate using ATP for maintenance and to take up nutrients from the surroundings.
 Partensky *et al*.
-[@partenskyComparisonPhotosyntheticPerformances2018] found that in the low-light conditions found in the OMZ, MED4, SS120 and MIT9313 all became net O~2~ consumers, suggesting that the low light levels caused the respiratory chain to consume more O~2~ than the photosynthetic electron transport chain could generate and could potentially be contributing to the maintenance of the low O~2~ environment
+[@partenskyComparisonPhotosyntheticPerformances2018] found that in the low-light conditions found in the OMZ, MED4, SS120 and MIT9313 all became net O~2~ consumers, suggesting that the low light levels cause the respiratory chain to consume more O~2~ than the photosynthetic electron transport chain generates, and c contributing to maintenance of the low O~2~ environment.
 

### 2024-03-01 Code/ManuscriptFigures.Rmd
Changed red light to lighter shade

@@
 
-MCMIXColours = c("black", w_length2rgb(660), w_length2rgb(450))
+MCMIXColours = c("black", "#f40d30", w_length2rgb(450))
 
@@
 
-MyWavelengths = c("WW", 660, 450)
-OverlayColours = c("black", w_length2rgb(660),  w_length2rgb(450))
-
-names(OverlayColours) <- MyWavelengths
-OverlayColours
-
 OverlayPlots <- PURPARFits %>%
@@
         # strip.text.x = element_text(size = 20),
-        axis.text = element_text(size = 15, color = "black"))
+        axis.text = element_text(size = 15, color = "black"),
+        panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank())
 
@@
 OverlayPlots
-
-TEST <- PURPARFits %>% 
-  filter(Strain == "MED4", WL == 660, )
 
@@
 ```{r MED4 All Spectral Emission,  fig.height = 10, fig.width = 10}
-
-MyWavelengths = c("WW", 660, 450)
-OverlayColours = c("black", w_length2rgb(660),  w_length2rgb(450))
-
-names(OverlayColours) <- MyWavelengths
-OverlayColours
 

### 2024-03-01 Code/Manuscript_O2.Rmd
Fixed reference to PUR section.

@@
 output:
+  bookdown::word_document2:
+    code_folding: show
+    reference_docx: KnitTemplate.docx
+    keep_md: yes
+    toc: FALSE
+    toc_depth: 6
+    fig_caption: yes
+    pandoc_args: 
+      - '--lua-filter=scholarly-metadata.lua'
+      - '--lua-filter=author-info-blocks.lua'
   bookdown::html_document2:
@@
 Cultures were maintained in incubators set to 22°C with a light/dark cycle of 12 h.
-The PAR level for maintenance cultures reflected PAR)in the source niche of the ecotype; MED4, of 160 µmol photons m^-2^ s^-1^ with illumination from STANDARD Products Inc.
+The PAR level for maintenance cultures reflected PAR in the source niche of the ecotype; MED4, of 160 µmol photons m^-2^ s^-1^ with illumination from STANDARD Products Inc.
 Cool White F24T5/41K/8/HO/PS/G5/STD, 24 watts, fluorescent bulbs; SS120 and MIT9313 at 30 µmol photons m^-2^ s^-1^ with illumination from Philips Cool White F14T5/841 Alto, 14 watts, fluorescent bulbs.
@@
 
+XXX Some text is relevant when referring to original NATLProchlorPhotosynDepthO2 figure, not with this figureXXX
 Proteins from 13 annotated strains of *P.
@@
 SS120) were detected throughout the water column in high [O~2~] and at depth in low [O~2~] samples.
-Photosystem I and II were only detected at low [O~2~].
+Photosystem I and II were only detected at low [O~2~] XXX This is evident when referring to original NATLProchlorPhotosynDepthO2 figure, not with this figureXXX.
 The exclusive assignment of ATP Synthase peptides to Clade IV (ex.
@@
 XXXRewrite caption if we change figure versionXXX
-```{r NATLProchloroPhotosynthDepthO2, fig.cap = NATLProchloroPhotosynthDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
-
-NATLProchloroPhotosynthDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* photosynthesis complexes.**", 
+XXX Figure changed- need to rewrite caption if keeping this figure XXX
+```{r CladeProchloroPhotosynthDepthO2, fig.cap = CladeProchloroPhotosynthDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
+
+CladeProchloroPhotosynthDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* photosynthesis complexes.**", 
                        "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
@@
 
-knitr::include_graphics(file.path(FiguresIn, "NATLProchloroPhotosynthDepthO2.png"))
+knitr::include_graphics(file.path(FiguresIn, "CladeProchloroPhotosynthDepthO2.png"))
 ```
@@
 The representative of HLI clade, *P.
-marinus* MED4, showed no growth under any 4 h photoperiod treatments, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments.
+marinus* MED4, showed no growth under any 4 h photoperiod treatments, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments (Figure \@ref(fig:AllStrainPurFitsPlots)A).
 In parallel MED4 showed no growth under 2.5 µM O~2~, no matter the level of diel cumulative PUR.
-In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth under blue light was well described by a saturating response of growth [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] to increasing cumulative diel PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A), and no evidence of inhibition of growth at any achieved cumulative diel PUR.
+In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth under blue light was well described by a saturating response of growth [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] to increasing cumulative diel PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A), and no evidence of inhibition of growth at any achieved cumulative diel PUR (Figure \@ref(fig:AllStrainPurFitsPlots)A).
 Under the 'artificial' growth treatment of red light, MED4 achieved more growth per unit diel cumulative PUR (Figure \@ref(fig:BluevsRedPurFitsPlots)A), consistent with Murphy *et al*.
@@
 The representative of the LLIII clade, *P.
-marinus* SS120 showed almost no growth under 2.5 µM O~2~ experiments.
-Most 4 h photoperiod treatments of SS120 also did not grow under 250 µM O~2~, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments.
-SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ experiments (Figure \@ref(fig:BluevsRedPurFitsPlots)B).
+marinus* SS120 showed almost no growth under 2.5 µM O~2~ experiments (Figure \@ref(fig:AllStrainPurFitsPlots)B).
+Most 4 h photoperiod treatments of SS120 also did not grow under 250 µM O~2~, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments (Figure \@ref(fig:AllStrainPurFitsPlots)B).
+SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ experiments (Figure \@ref(fig:AllStrainPurFitsPlots)B).
 
@@
 The onset of growth inhibition extended to higher cumulative diel PUR for cultures under 25 µM O~2~, showing that SS120 is partially protected from photoinhibition of growth by 25 µM O~2~.
-Under 25 µM O~2~ red light again generated more growth of SS120 per unit cumulative diel PUR, than did blue light, again consistent with lower cost of growth through lower photoinactivation under red light.
+Under 25 µM O~2~, red light again generated more growth of SS120 per unit cumulative diel PUR, than did blue light, again consistent with lower cost of growth through lower photoinactivation under red light (Figure \@ref(fig:BluevsRedPurFitsPlots)B).
 For distinct fits for different photoperiods refer to figure \@ref(fig:AllStrainPurFitsPlots)B.
@@
 The LLIV clade representative, *P.
-marinus* MIT9313, showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR, with higher growth rates over a narrower plateau under 25 and 250 µM O~2~, compared to a wider, lower, flatter response to cumulative diel PUR under 2.5 µM O~2~.
-Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands.
+marinus* MIT9313, showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR, with higher growth rates over a narrower plateau under 25 and 250 µM O~2~, compared to a wider, lower, flatter response to cumulative diel PUR under 2.5 µM O~2~ (Figure \@ref(fig:AllStrainPurFitsPlots)C).
+Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands(Figure \@ref(fig:AllStrainPurFitsPlots)C).
 In contrast, under 25 µM O~2~, MIT9313 showed a greatly extended exploitation of higher cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^.
-Similarly, under 2.5 µM O~2~, MIT9313 grew more slowly, but only showed full growth inhibition above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:BluevsRedPurFitsPlots)C).
-
-Our data again support enhanced growth under conditions of low cumulative diel PUR and 660 nm (red) spectral bandwidth, consistent with Murphy *et al*.[@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue, wavebands.
+Similarly, under 2.5 µM O~2~, MIT9313 grew more slowly, but only showed full growth inhibition above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:AllStrainPurFitsPlots)C).
+
+Our data again support enhanced growth under conditions of low cumulative diel PUR and 660 nm (red) spectral bandwidth, consistent with Murphy *et al*.[@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue, wavebands (Figure \@ref(fig:BluevsRedPurFitsPlots)C).
 Interestingly, this protective effect of red light disappears for MIT9313 growing under 2.5 µM O~2~, possibly because photoinactivation is strongly suppressed under this low [O~2~].
@@
 But only MED4 shows detected presence of the FtsH1 & FtsH2 isoforms inferred to mediate PSII repair, and then only in near-surface samples subject to higher light.
-Furthermore, even though MIT9313 grows (Figure \@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~] (Figure \@ref(fig:NATLProchloroPhotosynthDepthO2)), no FtsH from MIT9313 is detected at low [O~2~], suggesting limited requirement for protein turnover under low [O~2~].
+Furthermore, even though MIT9313 grows (Figure \@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~] (Figure \@ref(fig:CladeProchloroPhotosynthDepthO2)), no FtsH from MIT9313 is detected at low [O~2~], suggesting limited requirement for protein turnover under low [O~2~].
 
@@
 @delmontLinkingPangenomesMetagenomes2018 did not analyze data from depths beyond the subsurface chlorophyll maximum layer, the layer in the water column where the chlorophyll *a* concentration peaks, nor did they report the [O~2~] at those depths.
-Our growth findings are also consistent with Figure\@ref(fig:NATLProchloroPhotosynthDepthO2) showing PSII proteins annotated as MED4, at depths up to 200 meters with O~2~ of 15 µM.
+Our growth findings are also consistent with Figure\@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSII proteins annotated as MED4, clade HLI, at depths up to 200 meters with O~2~ of 15 µM.
 
@@
 and LLIV ecotypes, using terminal restriction fragment length polymorphism analyses, at depths above 40 m, where light levels are
-higher, within OMZ, and by Figure \@ref(fig:NATLProchloroPhotosynthDepthO2) showing PSII protein subunits annotated as derived from SS120 at all depths ranging
+higher, within OMZ, and by Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSII protein subunits annotated as derived from SS120 at all depths ranging
 from 20 to 200 m and all [O~2~] in an OMZ of the tropical North Pacific Ocean.
@@
 MIT9313 shows remarkable ability to thrive under very low [O~2~], potentially allowing it to expand into broader ecological niches.
-These results are supported by Figure \@ref(fig:NATLProchloroPhotosynthDepthO2) showing PSI protein subunits annotated as derived from MIT9313 detected at depths \> 120 m, along with PSII subunits at depths from 50 m to 200 m in regions where O~2~ was 15 µM.
+These results are supported by Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSI protein subunits annotated as derived from MIT9313 detected at depths \> 120 m, along with PSII subunits at depths from 50 m to 200 m in regions where O~2~ was 15 µM.
 
 In future work we aim to test whether MIT9313 is not “using” photosynthesis in low O~2~ environments to drive CO~2~ fixation, so much as to generate oxygen locally to support  respiration.
-The deep water environments typical for MIT 9313 are relatively nutrient rich and  *Prochlorococcus* take up and metabolise various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017; @munoz-marinProchlorococcusCanUse2013] and amino acids [@zubkovDepthRelatedAmino2004].
+The deep water environments typical for MIT 9313 are relatively nutrient rich and  *Prochlorococcus* take up and metabolize various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017; @munoz-marinProchlorococcusCanUse2013] and amino acids [@zubkovDepthRelatedAmino2004].
 They may be using photosynthesis to generate O~2~ to act as an electron sink for respiration, to generate using ATP for maintenance and to take up nutrients from the surroundings.

### 2024-03-01 Code/Manuscript_O2.Rmd
Renamed AllStrainPURFitsPlots to PhotoperiodPURFitsPlots

@@
 The representative of HLI clade, *P.
-marinus* MED4, showed no growth under any 4 h photoperiod treatments, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments (Figure \@ref(fig:AllStrainPurFitsPlots)A).
+marinus* MED4, showed no growth under any 4 h photoperiod treatments, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments (Figure \@ref(fig:PhotoperiodPurFitsPlots)A).
 In parallel MED4 showed no growth under 2.5 µM O~2~, no matter the level of diel cumulative PUR.
-In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth under blue light was well described by a saturating response of growth [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] to increasing cumulative diel PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A), and no evidence of inhibition of growth at any achieved cumulative diel PUR (Figure \@ref(fig:AllStrainPurFitsPlots)A).
+In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth under blue light was well described by a saturating response of growth [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] to increasing cumulative diel PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A), and no evidence of inhibition of growth at any achieved cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)A).
 Under the 'artificial' growth treatment of red light, MED4 achieved more growth per unit diel cumulative PUR (Figure \@ref(fig:BluevsRedPurFitsPlots)A), consistent with Murphy *et al*.
 [@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for growth under red light, for MED4, because red light provokes less photoinactivation of PSII, than equivalent levels of blue light.
-For distinct fits for different photoperiods refer to figure \@ref(fig:AllStrainPurFitsPlots)A.
+For distinct fits for different photoperiods refer to figure \@ref(fig:PhotoperiodPurFitsPlots)A.
 
@@
 The representative of the LLIII clade, *P.
-marinus* SS120 showed almost no growth under 2.5 µM O~2~ experiments (Figure \@ref(fig:AllStrainPurFitsPlots)B).
-Most 4 h photoperiod treatments of SS120 also did not grow under 250 µM O~2~, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments (Figure \@ref(fig:AllStrainPurFitsPlots)B).
-SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ experiments (Figure \@ref(fig:AllStrainPurFitsPlots)B).
+marinus* SS120 showed almost no growth under 2.5 µM O~2~ experiments (Figure \@ref(fig:PhotoperiodPurFitsPlots)B).
+Most 4 h photoperiod treatments of SS120 also did not grow under 250 µM O~2~, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments (Figure \@ref(fig:PhotoperiodPurFitsPlots)B).
+SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ experiments (Figure \@ref(fig:PhotoperiodPurFitsPlots)B).
 
@@
 Under 25 µM O~2~, red light again generated more growth of SS120 per unit cumulative diel PUR, than did blue light, again consistent with lower cost of growth through lower photoinactivation under red light (Figure \@ref(fig:BluevsRedPurFitsPlots)B).
-For distinct fits for different photoperiods refer to figure \@ref(fig:AllStrainPurFitsPlots)B.
+For distinct fits for different photoperiods refer to figure \@ref(fig:PhotoperiodPurFitsPlots)B.
 
@@
 The LLIV clade representative, *P.
-marinus* MIT9313, showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR, with higher growth rates over a narrower plateau under 25 and 250 µM O~2~, compared to a wider, lower, flatter response to cumulative diel PUR under 2.5 µM O~2~ (Figure \@ref(fig:AllStrainPurFitsPlots)C).
-Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands(Figure \@ref(fig:AllStrainPurFitsPlots)C).
+marinus* MIT9313, showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR, with higher growth rates over a narrower plateau under 25 and 250 µM O~2~, compared to a wider, lower, flatter response to cumulative diel PUR under 2.5 µM O~2~ (Figure \@ref(fig:PhotoperiodPurFitsPlots)C).
+Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands(Figure \@ref(fig:PhotoperiodPurFitsPlots)C).
 In contrast, under 25 µM O~2~, MIT9313 showed a greatly extended exploitation of higher cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^.
-Similarly, under 2.5 µM O~2~, MIT9313 grew more slowly, but only showed full growth inhibition above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:AllStrainPurFitsPlots)C).
+Similarly, under 2.5 µM O~2~, MIT9313 grew more slowly, but only showed full growth inhibition above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)C).
 
@@
 Interestingly, this protective effect of red light disappears for MIT9313 growing under 2.5 µM O~2~, possibly because photoinactivation is strongly suppressed under this low [O~2~].
-For distinct fits for different photoperiod fits refer to figure \@ref(fig:AllStrainPurFitsPlots)C.
+For distinct fits for different photoperiod fits refer to figure \@ref(fig:PhotoperiodPurFitsPlots)C.
 
@@
 
-```{r AllStrainPurFitsPlots,  fig.cap = AllStrainPurFitsPlots_cap, fig.height = 10, fig.width = 10, echo = FALSE}
-
-AllStrainPurFitsPlots_cap <- glue("**chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
+```{r PhotoperiodPurFitsPlots,  fig.cap = PhotoperiodPurFitsPlots_cap, fig.height = 10, fig.width = 10, echo = FALSE}
+
+PhotoperiodPurFitsPlots_cap <- glue("**chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
                     "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
@@
 
-knitr::include_graphics(file.path(FiguresIn, "AllStrainPurFitsPlots.png"))
+knitr::include_graphics(file.path(FiguresIn, "PhotoperiodPurFitsPlots.png"))
 

### 2024-03-01 Code/ManuscriptPURFits.Rmd
standardized variable names for ggplot labels across rmds
Renamed plot to be consistent with other plot names

@@
 MyWavelengths = c("WW", 660, 530, 450)
-MCMIXColours = c("black", w_length2rgb(660), w_length2rgb(530),  w_length2rgb(450))
+MCMIXColours = c("black", "#f40d30", w_length2rgb(530),  w_length2rgb(450))
 
@@
 #   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
-#   mutate(PhotoperiodLabel_title = "Photoperiod (h)",
+#   mutate(PhotoperiodLabelTitle = "Photoperiod (h)",
 #          OxygenLabel = "Oxygen Concentration (µM)",
@@
 
-# AllStrainPurFitsPlots <- plot_grid(MED4PURFITPlot, SS120PURFITPlot, MIT9313PURFITPlot, ncol = 1)
+# PhotoperiodPurFitsPlots <- plot_grid(MED4PURFITPlot, SS120PURFITPlot, MIT9313PURFITPlot, ncol = 1)
 # 
@@
 # #add to plot
-# AllStrainPurFitsPlots <- grid.arrange(arrangeGrob(AllStrainPurFitsPlots, left = y.grob))
+# PhotoperiodPurFitsPlots <- grid.arrange(arrangeGrob(PhotoperiodPurFitsPlots, left = y.grob))
 
@@
 
-AllStrainPurFitsPlots <- AllFitsCombined |>
+PhotoperiodPurFitsPlots <- AllFitsCombined |>
   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
-  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
+  mutate(PhotoperiodLabelTitle = "Photoperiod (h)",
          OxygenLabel = "Oxygen Concentration (µM)",
@@
 
-AllStrainPurFitsPlots
+PhotoperiodPurFitsPlots
 
 # This labels each pane with a letter but turns of the dacet labels
-# AllStrainPurFitsPlots <- tag_facet(AllStrainPurFitsPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
+# PhotoperiodPurFitsPlots <- tag_facet(PhotoperiodPurFitsPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
 
@@
 
-ggsave(file = file.path(PlotsOut, paste("AllStrainPurFitsPlots",".png",sep = "")), plot = AllStrainPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-ggsave(file = file.path(PlotsOut, paste("AllStrainPurFitsPlots",".tiff",sep = "")), plot = AllStrainPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("PhotoperiodPurFitsPlots",".png",sep = "")), plot = PhotoperiodPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+ggsave(file = file.path(PlotsOut, paste("PhotoperiodPurFitsPlots",".tiff",sep = "")), plot = PhotoperiodPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
-  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
+  mutate(PhotoperiodLabelTitle = "Photoperiod (h)",
          OxygenLabel = "Oxygen Concentration (µM)",
@@
   filter(Data_all_WL %in% c(450,660)) %>% 
-  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
+  mutate(PhotoperiodLabelTitle = "Photoperiod (h)",
          OxygenLabel = "Oxygen Concentration (µM)",

### 2024-03-03 Code/Manuscript_O2.Rmd
Added more ref to figures

@@
 
-Our data again support enhanced growth under conditions of low cumulative diel PUR and 660 nm (red) spectral bandwidth, consistent with Murphy *et al*.[@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue, wavebands (Figure \@ref(fig:BluevsRedPurFitsPlots)C).
+As with MED4 and SS120, our data again support enhanced growth under conditions of low cumulative diel PUR and 660 nm (red) spectral bandwidth, consistent with Murphy *et al*.[@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue, wavebands (Figure \@ref(fig:BluevsRedPurFitsPlots)C).
 Interestingly, this protective effect of red light disappears for MIT9313 growing under 2.5 µM O~2~, possibly because photoinactivation is strongly suppressed under this low [O~2~].
@@
 Ribosome proteins from clade HLI MED4, clade LLIII SS120 and clade LLIV MIT9313 show generally similar patterns vs.
-[O~2~] and depth, a proxy for peak PAR.
-FtsH3, inferred to mediate PSI assembly, likewise shows a similar pattern between MED4 and MIT9313.
+[O~2~] and depth, a proxy for peak PAR  (Figure \@ref(fig:NATLProchloroProteinMetabDepthO2)).
+FtsH3, inferred to mediate PSI assembly, likewise shows a similar pattern between MED4 and MIT9313 (Figure \@ref(fig:NATLProchloroProteinMetabDepthO2)).
 But only MED4 shows detected presence of the FtsH1 & FtsH2 isoforms inferred to mediate PSII repair, and then only in near-surface samples subject to higher light.
-Furthermore, even though MIT9313 grows (Figure \@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~] (Figure \@ref(fig:CladeProchloroPhotosynthDepthO2)), no FtsH from MIT9313 is detected at low [O~2~], suggesting limited requirement for protein turnover under low [O~2~].
+Furthermore, even though MIT9313 grows (Figure \@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~] (Figure \@ref(fig:CladeProchloroPhotosynthDepthO2)), no FtsH from MIT9313 is detected at low [O~2~] (Figure \@ref(fig:NATLProchloroProteinMetabDepthO2)), suggesting limited requirement for protein turnover under low [O~2~].
 

### 2024-03-03 Code/Manuscript_O2.Rmd
Reworded first line introducing Km and gene encoding enzymes

@@
 
-Figure \@ref(fig:ProchlorococcusEnzymeKms) shows genes encoding enzymes for  *P.
-marinus* strains from clades HLI, LLI, LLIII and LLIV [@omarAnnotationGenesEncoding2023], compared to the measured or inferred K~M~ for [O~2~] for each enzyme XXXX CITATION  to Table once added XXXX.
+Figure \@ref(fig:ProchlorococcusEnzymeKms) shows the measured or inferred K~M~ for [O~2~] for genes encoding enzymes [@omarAnnotationGenesEncoding2023] for  *P.
+marinus* strains from clades HLI, LLI, LLIII and LLIV.
+XXXX CITATION  to Table once added XXXX.
 MED4 increases expression of alternative oxidase ('ubiquinol oxidase (non electrogenic)')  to cope with changes in light [@bergResponsesPsbAHli2011], by dissipating electrons from the inter-system transport chain.

### 2024-03-03 Code/Manuscript_O2.Rmd
Fixed reference to FtsH 2 and 3 to FtsH 1 and 2

@@
 MED4 increases expression of alternative oxidase ('ubiquinol oxidase (non electrogenic)')  to cope with changes in light [@bergResponsesPsbAHli2011], by dissipating electrons from the inter-system transport chain.
-The approximate K~M~ for [O~2~] of ~ 25 µM for ubiquinol oxidase (non electrogenic) is comparable to the lower limit for growth of MED4 in our experiments.
+The approximate K~M~ for [O~2~] of ~ 25 µM for ubiquinol oxidase (non electrogenic) (Figure \@ref(fig:ProchlorococcusEnzymeKms)) is comparable to the lower limit for growth of MED4 in our experiments (Figure \@ref(fig:MED4GAM)).
 We suggest that dependence upon this enzyme excludes MED4 from low oxygen zones.
-The genome scan shows SS120 and MIT9313 lack this gene, and therefore, lack this oxygen-dependent path to cope with changing excitation.
-Conversely, a gene encoding (S)-2-hydroxy-acid oxidase is encoded in the MIT9313 genome.
+The genome scan shows SS120 and MIT9313 lack this gene (Figure \@ref(fig:ProchlorococcusEnzymeKms)), and therefore, lack this oxygen-dependent path to cope with changing excitation.
+Conversely, a gene encoding (S)-2-hydroxy-acid oxidase is encoded in the MIT9313 genome (Figure \@ref(fig:ProchlorococcusEnzymeKms)).
 (S)-2-hydroxy-acid oxidase catalyzes the reaction of 2-hydroxy acid with O~2~ to produce toxic H~2~O~2~ [@cunaneCrystalStructureAnalysis2005].
@@
 marinus* MIT9313 suffered photoinhibition, resulting from the inactivation of PSII caused by the production of the reactive oxygen species, hydrogen peroxide.
-This photoinhibition is compounded by the limited inducible repair mechanism for PSII, due to the absence of FtsH 2 and 3 XXXXCHECK TERMINOLOGYXXXX expression in *P.
+This photoinhibition is compounded by the limited inducible repair mechanism for PSII, due to the absence of FtsH 1 and 2 XXXXCHECK TERMINOLOGYXXXX expression in *P.
 marinus* MIT9313 [@bonisteelStrainSpecificDifferences2018].
@@
 marinus* MIT9313 suffers photoinhibition, resulting from the inactivation of PSII caused by the production of H~2~O~2~.
-This photoinhibition is compounded by the limited inducible repair for PSII, due to the absence of FtsH 2 and 3  expression in *P.
+This photoinhibition is compounded by the limited inducible repair for PSII, due to the absence of FtsH 1 and 2  expression in *P.
 marinus* MIT9313 [@bonisteelStrainSpecificDifferences2018].

### 2024-03-03 Code/Manuscript_O2.Rmd
Added to DNA discussion re: NATL2A and DNA repair

@@
 marinus* SS120 does not grow as well as *P.
-marinus* MIT9313, when exposed to high light stress under 25 µM O~2~ and not at all under 2.5 µM O~2~.
+marinus* MIT9313, when exposed to high light stress under 25 µM O~2~ and not at all under 2.5 µM O~2~ (Figure \@ref(fig:SS120PAR)).
 
@@
 marinus* SS120 demonstrates the smallest genomic capacity for DNA repair.
-*Prochlorococcus marinus* MED4 was the only strain to possess a gene encoding deoxyribodipyrimidine photolyase, which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003].
+*Prochlorococcus marinus* MED4 and NATL2A were the only strains to possess a gene encoding deoxyribodipyrimidine photolyase, which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003].
 *Prochlorococcus marinus* MED4 was also the only strain to possesses a gene encoding DNA ligase, which uses ATP as a cofactor for DNA repair.
@@
 marinus* MIT9313 and *P.
-marinus* SS120 helps explain why these two strains cannot tolerate growth under full [O~2~] and high light, found at the ocean surface.
+marinus* SS120 explain why these two strains cannot tolerate growth under full [O~2~] and high light, found at the ocean surface.
 Furthermore, the protective effect of lower [O~2~], allowing these strains to grow at higher light, may relate in part to suppression of DNA damage when generation of Reactive Oxygen Species is suppressed at lower [O~2~].
@@
 Malmstrom *et al*.
-attributes NATL2a tolerance to short exposures of high light to the presence of the genes encoding photolyase, a gene found in HL clades which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003].
+attributes NATL2A tolerance to short exposures of high light to the presence of the genes encoding photolyase, a gene found in HL clades.
+The presence of deoxyribodipyrimidine photolyase and absence of DNA ligase (ATP) supports why NATL2A tolerates limited exposure to high light and why NATL2A is unable to fully repair damaged DNA.
 *Prochlorococcus* are highly susceptible to hydrogen peroxide (H~2~O~2~) toxicity as they lack genes which scavenge H~2~O~2~ molecules [@morrisFacilitationRobustGrowth2008].
-The small cell size of *Prochlorococcus* allow the reactive oxygen species (ROS), H~2~O~2~, to cross the cell membrane [@omarDiffusionalInteractionsMarine2022]; however, accumulation of extracellular H~2~O~2~ remains toxic to *Prochlorococcus* [@morrisFacilitationRobustGrowth2008,  @morrisDependenceCyanobacteriumProchlorococcus2011].
+The small cell size of *Prochlorococcus* allow the reactive oxygen species (ROS), H~2~O~2~, to cross the cell membrane [@omarDiffusionalInteractionsMarine2022]; however, accumulation of extracellular H~2~O~2~ remains toxic to *Prochlorococcus* [@morrisFacilitationRobustGrowth2008;  @morrisDependenceCyanobacteriumProchlorococcus2011].
 

### 2024-03-03 Code/Manuscript_O2.Rmd
added more reference to figures and changed red light to blue light in conclusion section where comaparing red to blue (not red to red)

@@
 We hypothesize that low cell abundances of LL ecotypes in the mixed layer is likely driven in part by increased [O~2~],  and it is [O~2~] that constrains LL clades to deeper waters, not necessarily the light level.
-We found that under 25 µM O~2~ representatives of 'LL' clades, SS120 and MIT9313, actually tolerate approximately 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of PUR [@morelAvailableUsableStored1978],  comparable to the representative HL clade, MED4 which also exhibited growth saturation at the same cumulative diel PUR of 1.0 x 10^6^ µmol photons m^-2^ d^-1^.
-Growth under lower O~2~ allowed MIT9313 to substantially increase its exploitation of higher diel PUR.
+We found that under 25 µM O~2~ representatives of 'LL' clades, SS120 and MIT9313, actually tolerate approximately 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)B,C), comparable to the representative HL clade, MED4 which also exhibited growth saturation at the same cumulative diel PUR of 1.0 x 10^6^ µmol photons m^-2^ d^-1^ (Figure \@ref(fig:PhotoperiodPurFitsPlots)A).
+Growth under lower O~2~ allowed MIT9313 to substantially increase its exploitation of higher diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)C).
 
@@
 On the other hand, MED4 shows inducible expression of FtsH isoforms [@bonisteelStrainSpecificDifferences2018], to counter photoinactivation of PSII under higher PAR and [O~2~] environments.
-Photoinactivation, does, however, impose an increased cost of growth upon MED4, since growth under red light, to lower the rate of photoinactivation of PSII [@murphyPhotoinactivationPhotosystemII2017], allows MED4 to achieve faster growth per absorbed photon than growth under red light.
+Photoinactivation, does, however, impose an increased cost of growth upon MED4, since growth under red light, to lower the rate of photoinactivation of PSII [@murphyPhotoinactivationPhotosystemII2017], allows MED4 to achieve faster growth per absorbed photon than growth under blue light.
 TARA Oceans

### 2024-03-03 Code/Manuscript_O2.Rmd
Added comment to check Bagby and Chisholm re CO2:O2 experiments and their explanation  re respiration.

@@
 marinus* MED4-like genomes at depths ranging from 5 m to 90 m, representing high to low blue light levels, in the Pacific South East Ocean.
-@delmontLinkingPangenomesMetagenomes2018 did not analyze data from depths beyond the subsurface chlorophyll maximum layer, the layer in the water column where the chlorophyll *a* concentration peaks, nor did they report the [O~2~] at those depths.
+Delmont and Eren [@delmontLinkingPangenomesMetagenomes2018] did not analyze data from depths beyond the subsurface chlorophyll maximum layer, the layer in the water column where the chlorophyll *a* concentration peaks, nor did they report the [O~2~] at those depths.
 Our growth findings are also consistent with Figure\@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSII proteins annotated as MED4, clade HLI, at depths up to 200 meters with O~2~ of 15 µM.
@@
 SS120 is likely excluded from higher [O~2~] and higher PAR because of genomic limitations on capacity for DNA repair (Figure \@ref(fig:DNARepairFig)), and possibly by limited capacity for synthesis of reactive oxygen quenchers (Figure  \@ref(fig:ProchlorococcusEnzymeKms)).
-Our growth results are supported by @lavinNovelLineagesProchlorococcus2010 who found evidence of LLII/III
+Our growth results are supported by Lavin *et al*.
+[@lavinNovelLineagesProchlorococcus2010] who found evidence of LLII/III
 and LLIV ecotypes, using terminal restriction fragment length polymorphism analyses, at depths above 40 m, where light levels are
@@
 SS120, grew under photoperiods longer than 4 h and showed increasing growth rate with increasing photoperiods.
-Therefore, SS120 can potentially exploit the longer summer photoperiods in temperate zones but again cannot sustain growth in winter through its requirement for more than 4 h of light per day, even if water temperature warms into the clade LLIII tolerance range.
+Therefore, SS120 can potentially exploit the longer summer photoperiods in temperate zones however, like MED4, cannot sustain growth in winter through its requirement for more than 4 h of light per day, even if water temperature warms into the clade LLIII tolerance range.
 
@@
 
+XXX Check Bagby and Chisholm for discussion on respiration as they limited CO2 and O2 XXXXX 
 In future work we aim to test whether MIT9313 is not “using” photosynthesis in low O~2~ environments to drive CO~2~ fixation, so much as to generate oxygen locally to support  respiration.

### 2024-03-03 Code/Manuscript_O2.Rmd
Knitted

@@
 
-XXX Check Bagby and Chisholm for discussion on respiration as they limited CO2 and O2 XXXXX 
+XXX Check Bagby and Chisholm for discussion on respiration as they limited CO2 and O2. Mirielle has notes, will add if relevant XXXXX 
 In future work we aim to test whether MIT9313 is not “using” photosynthesis in low O~2~ environments to drive CO~2~ fixation, so much as to generate oxygen locally to support  respiration.

### 2024-03-04 Code/Manuscript_O2.Rmd
Added Data availability section- moved text there

@@
 *In situ* measurements of Optical Density (OD) 680 nm, a proxy for cell suspension density, cell size dependent scatter and cell chlorophyll content;  and OD 720 nm, a proxy for cell suspension density and cell size dependent scatter, were recorded every 5 minutes over least 8 to 14 days,  depending on the duration of the lag phase, if any.
-All data obtained from the Multicultivator were saved as comma separated values files  (https://github.com/FundyPhytoPhys/prochlorococcus_o2/).
 
@@
 The residuals of the logistic growth curve fit are shown and the growth spectral waveband is plotted and illustrates the imposed PAR (µmol photons m^-2^ s^-1^) and photoperiod
-(h). Annotated code for data import, transformations and analyses is available at https://github.com/FundyPhytoPhys/prochlorococcus_o2/  MAKE SURE RePOSTIORY IS PUBLICXXXX
+(h).
 
@@
 
+# Data availability  {.unnumbered}
+All data obtained from the Multicultivator were saved as comma separated values files and are available at https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData.
+Annotated code for data import, transformations and analyses are available at https://github.com/FundyPhytoPhys/prochlorococcus_o2/Code.
+
 # Acknowledgements  {.unnumbered}
-Jonah Sheinin (Mount Allison Student) assisted with growth of some cultures for protein analyses, while Carlie Barnhill (Mount Allison Student) assisted with code for import of multicultivator growth data files.
-
+Carlie Barnhill (Mount Allison Student) assisted with code for import of multicultivator growth data files.
+
+XXX PLOS requires grant numbers XXX
 # Funding  {.unnumbered}

### 2024-03-04 Code/ManuscriptGenome.Rmd
Update ManuscriptGenome.Rmd

@@
 title: "R Notebook"
-output: html_notebook
 ---
@@
 ```{r}
-LightGOs <- MergedData %>% 
-  separate_rows(GOs, sep = ",") %>% 
-  filter(GOs %in% c("GO:0010018", "GO:0009785", "GO:0009882", "GO:0031516", "GO:0031517", "GO:0009883"))
-
-LightKOs <- MergedData %>% 
-  separate_rows(KEGG_ko, sep = ",") %>% 
-  filter(KEGG_ko %in% c("ko:K02295", "ko:K12120", "ko:K12122", "ko:K12121", "ko:K12123"))
+# LightGOs <- MergedData %>% 
+#   separate_rows(GOs, sep = ",") %>% 
+#   filter(GOs %in% c("GO:0010018", "GO:0009785", "GO:0009882", "GO:0031516", "GO:0031517", "GO:0009883"))
+# 
+# LightKOs <- MergedData %>% 
+#   separate_rows(KEGG_ko, sep = ",") %>% 
+#   filter(KEGG_ko %in% c("ko:K02295", "ko:K12120", "ko:K12122", "ko:K12121", "ko:K12123"))
 ```
@@
 ```{r, fig.width = 7, fig.height = 7}
-MergedData %>%
-  filter(!is.na(Gene_count)) %>%
-  filter(PriSec == "Primary") %>%
-  filter(Genus == "Prochlorococcus") %>%
-  # filter(FileName == "Prochlorococcus_marinus_MIT9313-aa-gen"| FileName == "Prochlorococcus_marinus_pastoris_CCMP1986-aa-gen" | FileName == "Prochlorococcus_marinus_marinus_CCMP1375-aa-gen") %>%
-  # group_by(EC) %>%
-  # mutate(ECNumberTotal = sum(Gene_count)) %>%
-  # ungroup() %>% View()
-  # filter(ECNumberTotal != 0) %>%
-  ggplot() +
-  geom_point(aes(x = reorder(EnzymeName, Km_mM), y = FileName, size = Gene_count, color = log10(AvgKm_mM))) +
-  facet_grid(rows = vars(Genus), scales = "free", space = "free") +
-  scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
-  scale_x_discrete(position = "top") +
-  scale_radius(breaks = c(1,2,3,4,5), range = c(1,4)) +
-  theme_bw() +
-  ggpubr::rotate_x_text(hjust = 0) 
+# MergedData %>%
+#   filter(!is.na(Gene_count)) %>%
+#   filter(PriSec == "Primary") %>%
+#   filter(Genus == "Prochlorococcus") %>%
+#   # filter(FileName == "Prochlorococcus_marinus_MIT9313-aa-gen"| FileName == "Prochlorococcus_marinus_pastoris_CCMP1986-aa-gen" | FileName == "Prochlorococcus_marinus_marinus_CCMP1375-aa-gen") %>%
+#   # group_by(EC) %>%
+#   # mutate(ECNumberTotal = sum(Gene_count)) %>%
+#   # ungroup() %>% View()
+#   # filter(ECNumberTotal != 0) %>%
+#   ggplot() +
+#   geom_point(aes(x = reorder(EnzymeName, Km_mM), y = FileName, size = Gene_count, color = log10(AvgKm_mM))) +
+#   facet_grid(rows = vars(Genus), scales = "free", space = "free") +
+#   scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
+#   scale_x_discrete(position = "top") +
+#   scale_radius(breaks = c(1,2,3,4,5), range = c(1,4)) +
+#   theme_bw() +
+#   ggpubr::rotate_x_text(hjust = 0) 
 ```
@@
 ```{r, fig.width = 7, fig.height = 7}
-MergedData %>%
-  filter(!is.na(Gene_count)) %>%
-  filter(PriSec == "Primary") %>%
-  # filter(FileName == "Prochlorococcus_marinus_MIT9313-aa-gen"| FileName == "Prochlorococcus_marinus_pastoris_CCMP1986-aa-gen" | FileName == "Prochlorococcus_marinus_marinus_CCMP1375-aa-gen") %>%
-  # group_by(EC) %>%
-  # mutate(ECNumberTotal = sum(Gene_count)) %>%
-  # ungroup() %>% View()
-  # filter(ECNumberTotal != 0) %>%
-  ggplot() +
-  geom_point(aes(x = reorder(EnzymeName, Km_mM), y = FileName, size = Gene_count, color = log10(AvgKm_mM))) +
-  facet_grid(rows = vars(Genus), scales = "free", space = "free") +
-  scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
-  scale_x_discrete(position = "top") +
-  scale_radius(breaks = c(1,2,3,4,5), range = c(1,4)) +
-  theme_bw() +
-  ggpubr::rotate_x_text(hjust = 0) 
+# MergedData %>%
+#   filter(!is.na(Gene_count)) %>%
+#   filter(PriSec == "Primary") %>%
+#   # filter(FileName == "Prochlorococcus_marinus_MIT9313-aa-gen"| FileName == "Prochlorococcus_marinus_pastoris_CCMP1986-aa-gen" | FileName == "Prochlorococcus_marinus_marinus_CCMP1375-aa-gen") %>%
+#   # group_by(EC) %>%
+#   # mutate(ECNumberTotal = sum(Gene_count)) %>%
+#   # ungroup() %>% View()
+#   # filter(ECNumberTotal != 0) %>%
+#   ggplot() +
+#   geom_point(aes(x = reorder(EnzymeName, Km_mM), y = FileName, size = Gene_count, color = log10(AvgKm_mM))) +
+#   facet_grid(rows = vars(Genus), scales = "free", space = "free") +
+#   scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
+#   scale_x_discrete(position = "top") +
+#   scale_radius(breaks = c(1,2,3,4,5), range = c(1,4)) +
+#   theme_bw() +
+#   ggpubr::rotate_x_text(hjust = 0) 
 ```

### 2024-03-04 Code/Manuscript_O2.Rmd
minor edits

@@
 *Prochlorococcus marinus* MED4, a clade HLI strain, was isolated near the ocean surface (5m depth) of the Mediterranean Sea where [O~2~] is near saturation, light levels are high and spectral bias from full solar irradiance is minimal.
-*Prochlorococcus marinus* SS120, a clade LLIII strain, was isolated from the Sargasso Sea at a depth of 120 m, while *P.
+*Prochlorococcus marinus* SS120, a clade LLII/III strain, was isolated from the Sargasso Sea at a depth of 120 m, while *P.
 marinus* MIT9313, a clade LLIV strain, was isolated from the North Atlantic Gulf Stream at a depth of 135 m.
@@
 marinus* were obtained from Bigelow Labs, NCMA Maine, USA.
-MED4 (CCMP1986) is from High-Light adapted (HLI) clade; SS120 (CCMP1375) is from Low-Light adapted (LLIII) clade; and MIT9313 (CCMP2773) is from Low-Light adapted (LLIV) clade.
+MED4 (CCMP1986) is from High-Light adapted (HLI) clade; SS120 (CCMP1375) is from Low-Light adapted (LLII/III) clade; and MIT9313 (CCMP2773) is from Low-Light adapted (LLIV) clade.
 Cultures were maintained in incubators set to 22°C with a light/dark cycle of 12 h.
@@
 ## Growth rate analysis {.unnumbered}
-Data files (.csv) saved from the Multicultivator software were imported into R-Studio for data management [@R-tidyverse], growth rate calculations CITATION, comparisons of model fits [@harrisonPhotosynthesisirradianceRelationshipsPolar1986], and visualization.
+Data files (.csv) saved from the Multicultivator software were imported into R-Studio for data management [@R-tidyverse], growth rate calculations, comparisons of model fits [@harrisonPhotosynthesisirradianceRelationshipsPolar1986], and visualization.
 The chlorophyll proxy optical density (OD~680~ - OD~720~;  ΔOD) was used to determine the chlorophyll specific growth rate (µ, d^-1^) for each treatment combination.
@@
 
-XXX Some text is relevant when referring to original NATLProchlorPhotosynDepthO2 figure, not with this figureXXX
 Proteins from 13 annotated strains of *P.
@@
 MED4) were detected throughout the water column, predominantly at high [O~2~].
-Complexes from Clade LLIII (ex.
-SS120) were detected throughout the water column in high [O~2~] and at depth in low [O~2~] samples.
-Photosystem I and II were only detected at low [O~2~] XXX This is evident when referring to original NATLProchlorPhotosynDepthO2 figure, not with this figureXXX.
+Complexes from clade LLII/III (ex.
+SS120) and clade LLIV (ex.
+MIT9313) were detected throughout the water column in high [O~2~] and at depth in low [O~2~] samples.
 The exclusive assignment of ATP Synthase peptides to Clade IV (ex.
@@
                        "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
-                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4 (clade HLI), SS120 (clade LLIII) and MIT9313 (clade LLIV).",
+                       "Rows separate data annotated as from *Prochlorococcus* clades: HLI (includes *P.
+marinus* MED4), HLII, LLI, LLII/III (includes P.
+marinus* SS120) and LLIV (includes *P.
+marinus* MIT9313).",
                        "Columns show detections of proteins annotated as  Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
@@
 *P.
-marinus* SS120 clade LLIII,  growth under 250 µM O~2~ increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^ peak PAR and across all spectral wavebands (Figure \@ref(fig:SS120PAR)).
+marinus* SS120 clade LLII/III,  growth under 250 µM O~2~ increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^ peak PAR and across all spectral wavebands (Figure \@ref(fig:SS120PAR)).
 No growth was observed under any blue light photoperiods when exposed to peak PAR of 90 µmol photons m^-2^ s^-1^ or greater.
@@
 
-SS120PAR_cap <- glue("**chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low-Light (LLIII) deep ocean clade) vs. photoperiod (h). **",
+SS120PAR_cap <- glue("**chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low-Light (LLII/III) deep ocean clade) vs. photoperiod (h). **",
                      "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
@@
 
-XXXXCHECK figure references here; not sure White Light data is shown on the bluered figure; refer to Supplemental?XXXX
-
 The representative of HLI clade, *P.
@@
 
-### SS120 clade LLIII {.unnumbered}
-
-The representative of the LLIII clade, *P.
+### SS120 clade LLII/III {.unnumbered}
+
+The representative of the LLII/III clade, *P.
 marinus* SS120 showed almost no growth under 2.5 µM O~2~ experiments (Figure \@ref(fig:PhotoperiodPurFitsPlots)B).
@@
 marinus*.
-Ribosome proteins from clade HLI MED4, clade LLIII SS120 and clade LLIV MIT9313 show generally similar patterns vs.
+Ribosome proteins from clade HLI MED4, clade LLII/III SS120 and clade LLIV MIT9313 show generally similar patterns vs.
 [O~2~] and depth, a proxy for peak PAR  (Figure \@ref(fig:NATLProchloroProteinMetabDepthO2)).
@@
                        "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
-                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4 (clade HLI), SS120 (clade LLIII) and MIT9313 (clade LLIV).",
+                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4 (clade HLI), SS120 (clade LLII/III) and MIT9313 (clade LLIV).",
                        "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome).",
@@
 Figure \@ref(fig:ProchlorococcusEnzymeKms) shows the measured or inferred K~M~ for [O~2~] for genes encoding enzymes [@omarAnnotationGenesEncoding2023] for  *P.
-marinus* strains from clades HLI, LLI, LLIII and LLIV.
+marinus* strains from clades HLI, LLI, LLII/III and LLIV.
 XXXX CITATION  to Table once added XXXX.
@@
                          "The x-axis represents enzymes encoded for DNA repair found in at least one *Prochlorococcus marinus* strain in this study.",
-                         "The red solid circles represent a gene count of 1.",
-                         "The green solid circles represent a gene count of 2.",
-                         "The blue solid circles represent a gene count of 3.",
+                         "Point size indicate gene counts.",
                        "Figure was generated using a filtered subset of the annotated phytoplankton gene sequences dataset from Omar *et al*. [@omarAnnotationGenesEncoding2023].",
@@
 *P.
-marinus* SS120, a clade LLIII ecotype found deep in the water column, and *P.
+marinus* SS120, a clade LLII/III ecotype found deep in the water column, and *P.
 marinus* MIT9313, a clade LLIV ecotype also found in deep oceans, under present day and hypothetical future niche conditions.
@@
 
-*Prochlorococcus marinus* SS120, a LLIII clade representative, showed an interactive inhibition of growth by oxygen and cumulative diel PUR, with a higher tolerance for higher cumulative diel PUR under 25 µM O~2~, compared to 250 µM O~2~.
+*Prochlorococcus marinus* SS120, a LLII/III clade representative, showed an interactive inhibition of growth by oxygen and cumulative diel PUR, with a higher tolerance for higher cumulative diel PUR under 25 µM O~2~, compared to 250 µM O~2~.
 Thus, SS120 can exploit habitats with O~2~ levels spanning 25 µM O~2~ to 250 µM O~2~, including high PAR environments within OMZ.
@@
 SS120, grew under photoperiods longer than 4 h and showed increasing growth rate with increasing photoperiods.
-Therefore, SS120 can potentially exploit the longer summer photoperiods in temperate zones however, like MED4, cannot sustain growth in winter through its requirement for more than 4 h of light per day, even if water temperature warms into the clade LLIII tolerance range.
+Therefore, SS120 can potentially exploit the longer summer photoperiods in temperate zones however, like MED4, cannot sustain growth in winter through its requirement for more than 4 h of light per day, even if water temperature warms into the clade LLII/III tolerance range.
 
@@
 Lavin *et al*.
-[@lavinNovelLineagesProchlorococcus2010] show evidence of LLIII ecotypes at varying depths from 20 to 30 m and from 75 to 200 µM O~2~ in the oxygen minimum zone (OMZ) of the tropical South Pacific Ocean, illustrating its tolerance of high light levels under low O~2~.
+[@lavinNovelLineagesProchlorococcus2010] show evidence of LLII/III ecotypes at varying depths from 20 to 30 m and from 75 to 200 µM O~2~ in the oxygen minimum zone (OMZ) of the tropical South Pacific Ocean, illustrating its tolerance of high light levels under low O~2~.
 SS120 has the potential to thrive in deep temperate zones, specifically during the spring, summer, and fall seasons when the duration of daylight exceeds 4 h, if O~2~ are near surface saturation of about 250 µM.
@@
 ```
+
+```{r PhotoperiodPurFitsPlots,  fig.cap = PhotoperiodPurFitsPlots_cap, fig.height = 10, fig.width = 10, echo = FALSE}
+
+PhotoperiodPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
+                    "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
+                    "Columns are strains; MED4, SS120 and MIT9313.",
+                    "Shapes show the imposed photoperiod (h); 4 h (solid square),  8 h (solid diamond), 12 h (solid circle), 16 h (solid upright triangle).",
+                      "Symbol colours show the spectral waveband for growth; white LED (black symbols), 660 nm (red symbols), and 450 nm (blue symbols).",
+                      "Large symbols show mean of growth rate from logistic curve fits; small symbols show values for replicate determinations, if any.",
+                    "Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to data pooled for each combination of strain and dissolved oxygen shown with solid lines.
+Separate models fit to photoperiod data and shown if significantly different from the pooled model using one-way ANOVA; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).",
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "PhotoperiodPurFitsPlots.png"))
+
+```
+
+\newpage
+
+```{r ProchlorococcusLightEnzymes, fig.cap = ProchlorococcusLightEnzymes_cap, fig.height = 10, fig.width = 10, echo = FALSE}
+
+ProchlorococcusLightEnzymes_cap <- glue("**Genes encoding enzymes activated or inhibited by light.**",
+                         "The y-axis represents  *Prochlorococcus marinus* strains.",
+                         "The x-axis represents enzymes encoded for DNA repair found in at least one *Prochlorococcus marinus* strain in this study.",
+                         "Point size indicate gene counts.",
+                       "Figure was generated using a filtered subset of the annotated phytoplankton gene sequences dataset from Omar *et al*. [@omarAnnotationGenesEncoding2023].",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "ProchlorococcusLightEnzymes.png"))
+
+```
+
+\newpage
 
@@
 
-```{r PhotoperiodPurFitsPlots,  fig.cap = PhotoperiodPurFitsPlots_cap, fig.height = 10, fig.width = 10, echo = FALSE}
-
-PhotoperiodPurFitsPlots_cap <- glue("**chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
-                    "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                    "Columns are strains; MED4, SS120 and MIT9313.",
-                    "Shapes show the imposed photoperiod (h); 4 h (solid square),  8 h (solid diamond), 12 h (solid circle), 16 h (solid upright triangle).",
-                      "Symbol colours show the spectral waveband for growth; white LED (black symbols), 660 nm (red symbols), and 450 nm (blue symbols).",
-                      "Large symbols show mean of growth rate from logistic curve fits; small symbols show values for replicate determinations, if any.",
-                    "Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to data pooled for each combination of strain and dissolved oxygen shown with solid lines.
-Separate models fit to photoperiod data and shown if significantly different from the pooled model using one-way ANOVA; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).",
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "PhotoperiodPurFitsPlots.png"))
-
-```
-
-\newpage
-
 # Data availability  {.unnumbered}

### 2024-03-04 Code/OceanProteinPlots.Rmd
add alpha to non-target strains in same Clade

@@
 unique(poi$CladeMergeFactor)
+```
+
+```{r labels}
+PhotosynthLabels <- c("PSII", "Cytb6f", "PSI", "ATP Synthase", "RUBISCO")
+ProteinMetabLabels <- c("FtsH1", "FtsH2", "FtsH3", "FtsH4", "Ribosome")
+StrainLabels <- c("MED4", "SS120", "MIT9313")
+AltStrainLabels <- c("MED4", "SS120", "MIT9313", "NATL2A")
+
+ElectronTrans <- c("psii", "cytb6f", "psi", "rubisco", "atp")
+
+ProteinMetab <- c("ftsh1", "ftsh2", "ftsh3", "ftsh4", "ribosome")
+
 ```
@@
 #https://stackoverflow.com/questions/32555531/how-to-italicize-part-one-or-two-words-of-an-axis-title
-
-PhotosynthLabels <- c("PSII", "Cytb6f", "PSI", "ATP Synthase", "RUBISCO")
-ProteinMetabLabels <- c("FtsH1", "FtsH2", "FtsH3", "FtsH4", "Ribosome")
-StrainLabels <- c("MED4", "SS120", "MIT9313")
-AltStrainLabels <- c("MED4", "SS120", "MIT9313", "NATL2A")
-
-ElectronTrans <- c("psii", "cytb6f", "psi", "rubisco", "atp")
-
-ProteinMetab <- c("ftsh1", "ftsh2", "ftsh3", "ftsh4", "ribosome")
 
@@
 ```{r clademerge_plots}
-PhotosynthLabels <- c("PSII", "Cytb6f", "PSI", "ATP Synthase", "RUBISCO")
-ProteinMetabLabels <- c("FtsH1", "FtsH2", "FtsH3", "FtsH4", "Ribosome")
+# PhotosynthLabels <- c("PSII", "Cytb6f", "PSI", "ATP Synthase", "RUBISCO")
+# ProteinMetabLabels <- c("FtsH1", "FtsH2", "FtsH3", "FtsH4", "Ribosome")
+
+poi <- poi |>
+  mutate(StrainAlpha = if_else(strain %in% AltStrainLabels, 1, 0.1))
 
@@
   ggplot() +
-  geom_point(aes(x = O2, y= depth)) +
+  geom_point(aes(x = O2, y= depth, alpha = StrainAlpha)) +
   scale_x_continuous(limits = c(0, 260)) +
@@
   geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.1) +
+  guides(alpha = 'none') +
   facet_grid(rows = vars(CladeMergeFactor), cols = vars(factor(complex, levels = c("psii", "cytb6f", "psi", "rubisco", "atp"), labels = PhotosynthLabels))) +
@@
   geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.1) +
+  guides(alpha = 'none') +
   facet_grid(rows = vars(CladeMerge), cols = vars(factor(complex, levels = c("ftsh1", "ftsh2", "ftsh3", "ftsh4", "ribosome"), labels = ProteinMetabLabels))) +

### 2024-03-04 Code/OceanProteinPlots.Rmd
filter out Clade HLII from CladeMergePlots

@@
   filter(complex %in% ElectronTrans) |>
+  filter(CladeMerge != "HLII") |>
   ggplot() +
@@
   filter(complex %in% ProteinMetab) |>
+  filter(CladeMerge != "HLII") |>
   ggplot() +

### 2024-03-04 Code/OceanProteinPlots.Rmd
fix CladeMerge

@@
                                 clade == "LLI" ~ "LLI",
-                                clade == "LLII" ~ "LII_LLIII",
-                                clade == "LLIII" ~ "LII_LLIII",
+                                clade == "LLII" ~ "LLII_LLIII",
+                                clade == "LLIII" ~ "LLII_LLIII",
                                  clade == "LLIV" ~ "LLIV")) |>
-  mutate(CladeMergeFactor = factor(CladeMerge, levels = c("HLI", "HLII", "LLI", "LII_LLIII", "LLIV")))
+  mutate(CladeMergeFactor = factor(CladeMerge, levels = c("HLI", "HLII", "LLI", "LLII_LLIII", "LLIV")))
 

### 2024-03-04 Code/Manuscript_O2.Rmd

@@
 
-Figures \@ref(fig:MED4OverlayPlots), \@ref(fig:SS120OverlayPlots) and
-\@ref(fig:MIT9313OverlayPlots) provide visual representations of PUR, the black solid line and shaded area, in relation to the imposed PAR, the dotted line, under each imposed spectral wavebands for *P.
+Figures \@ref(fig:OverlayPlots) provide visual representations of PUR, the black solid line and shaded area, in relation to the imposed PAR, the dotted line, under each imposed spectral wavebands for *P.
 marinus* MED4, SS120 and MIT9313, respectively.
@@
 
-```{r MED4OverlayPlots, fig.cap = MED4OverlayPlots_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+```{r OverlayPlots, fig.cap = OverlayPlots_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+
+OverlayPlots_cap <- glue("**Normalized absorbance and Photosynthetically Usable Radiation for *Prochlorococcus marinus* MED4 (A,B,C); SS120 (D,E,F); MIT9313 (G,H,I) grown under three emission wavebands.**",
+                       "**(A,D,G)** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated PUR spectra (solid black line and shaded grey).",
+                       "**(B,E,H)** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded red).",
+                       "**(C,F,I)**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded blue).",
+
+                       "Actinic PAR (µmol photons m^-2^ s^-1^) and calculated PUR (µmol photons m^-2^ s^-1^) levels are indicated.",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "OverlayPlots.png"))
+
+```
+
+```{r MED4OverlayPlots, fig.cap = MED4OverlayPlots_cap, fig.height = 6, fig.width = 8, include = FALSE}
 
@@
 
-```{r SS120OverlayPlots, fig.cap = SS120OverlayPlots_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+```{r SS120OverlayPlots, fig.cap = SS120OverlayPlots_cap, fig.height = 6, fig.width = 8, include = FALSE}
 
@@
 
-```{r MIT9313OverlayPlots, fig.cap = MIT9313OverlayPlots_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+```{r MIT9313OverlayPlots, fig.cap = MIT9313OverlayPlots_cap, fig.height = 6, fig.width = 8, include = FALSE}
 
@@
 
-```{r MaxGrowthTable, fig.height = 6, fig.width = 8, echo = FALSE }
+```{r MaxGrowthTable, echo = FALSE }
 
@@
 
+```{r ProchlorococcusEnzymeTable, echo = FALSE }
+
+readRDS(file.path(DataIn,"ProchlorococcusEnzymeTable.Rds")) %>% 
+  knitr::kable(.,
+             caption = "Enzyme Commission numbers (EC) and corresponsing enzyme names.",
+            col.names =  c("EC",
+                          "Enzyme Name")
+             )
+
+```
+
 # Data availability  {.unnumbered}

### 2024-03-04 Code/Manuscript_O2.Rmd
edit FtsH table and text

@@
 In contrast, representative LLIV strain MIT9313 showed less overall expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem.
-Furthermore, MIT9313 expressed primarily FtsH3, homologous to *Synechocystis* slr1463 involved in PSI biogenesis, andFtsH expression did not increase in response to light stress in MIT9313.
+Furthermore, MIT9313 expressed primarily FtsH3, homologous to *Synechocystis* slr1463, possibly involved in PSI biogenesis, and FtsH expression did not increase in response to light stress in MIT9313.
 Through adaptation to steady low light, clade LLIV *Prochlorococcus* instead allocate resources to processes other than dynamic regulation of PSII repair.
@@
 FtsHTable <- tibble(Organism = c("*Prochlorococcus marinus*", "*Synechocystis sp. PCC6803*", "Function"),
-                    FtsH1 = c("FtsH1", "SlrO22", "PSII Repair"),
+                    FtsH1 = c("FtsH1", "SlrO228", "PSII Repair"),
                     FtsH2 = c("FtsH2", "Slr1604", "PSII Repair"),
-                    FtsH3 = c("FtsH3", "Slr1463", "PSI biogenesis"),
+                    FtsH3 = c("FtsH3", "Slr1463", "PSI biogenesis?"),
                     FtsH4 = c("FtsH4", "Slr1390", "Cell viability")

### 2024-03-04 Code/Manuscript_O2.Rmd
edited summary section

@@
 
-We analyzed  growth rates to determine the viability of *P. marinus* MED4, a clade HLI ecotype found at depths near the ocean surface,
+We analyzed  growth rates to determine the viability of *P. marinus* MED4, a clade HLI ecotype found near the ocean surface,
 *P.
 marinus* SS120, a clade LLII/III ecotype found deep in the water column, and *P.
-marinus* MIT9313, a clade LLIV ecotype also found in deep oceans, under present day and hypothetical future niche conditions.
-We designed our study to account for light attenuation through ocean waters, recognizing that low light levels of the blue spectral waveband ultimately prevail in deep ocean waters [@morelAvailableUsableStored1978; @holtropVibrationalModesWater2021] and that the solar incidence angle also attenuates the photoperiod or hours of light exposure beneath the ocean surface.
-We also tested the growth response of *P.
-marinus* to varying [O~2~] under the matrix of light parameters to determine if *P.
-marinus* strains can cope with  diverse  ecosystem scenarios.
-
-*Prochlorococcus marinus* MED4 has a physiological requirement for more than 4 h of light per day, and thus this strain will not exploit habitats with short photoperiods, typical of winter or light attenuated depths.
-MED4 is also excluded from the lowest oxygen habitats, equivalent to our 2.5 µM O~2~ experimental conditions.
+marinus* MIT9313, a clade LLIV ecotype also found in deep oceans including OMZ, under a matrix of spectral, light level, photoperiod and oxygen conditions approxmating present day and hypothetical future niches.
+Low light levels in the blue spectral waveband prevail in deep ocean waters [@morelAvailableUsableStored1978; @holtropVibrationalModesWater2021], while solar incidence angle and light attenuation also progressively attenuate the photoperiod with depth beneath the ocean surface.
+
+*Prochlorococcus marinus* MED4 has a physiological requirement for more than 4 h of light per day; thus this strain will not exploit habitats with short photoperiods, typical of temperate winter or light attenuated depths, even if water temperature warms into the clade LLII/III tolerance range.
+MED4 is also excluded from the lowest oxygen habitats, represented by our 2.5 µM O~2~ experimental conditions.
 MED4 can, however, grow under OMZ regions with slightly higher [O~2~], as demonstrated by the growth under our 25 µM O~2~ experiments.
@@
 Photoinactivation, does, however, impose an increased cost of growth upon MED4, since growth under red light, to lower the rate of photoinactivation of PSII [@murphyPhotoinactivationPhotosystemII2017], allows MED4 to achieve faster growth per absorbed photon than growth under blue light.
-TARA Oceans
-Project data [@delmontLinkingPangenomesMetagenomes2018] indeed reported presence of *P.
+TARA Oceans Project data [@delmontLinkingPangenomesMetagenomes2018] indeed reported presence of *P.
 marinus* MED4-like genomes at depths ranging from 5 m to 90 m, representing high to low blue light levels, in the Pacific South East Ocean.
@@
 *Prochlorococcus marinus* SS120, a LLII/III clade representative, showed an interactive inhibition of growth by oxygen and cumulative diel PUR, with a higher tolerance for higher cumulative diel PUR under 25 µM O~2~, compared to 250 µM O~2~.
-Thus, SS120 can exploit habitats with O~2~ levels spanning 25 µM O~2~ to 250 µM O~2~, including high PAR environments within OMZ.
-SS120 is likely excluded from higher [O~2~] and higher PAR because of genomic limitations on capacity for DNA repair (Figure \@ref(fig:DNARepairFig)), and possibly by limited capacity for synthesis of reactive oxygen quenchers (Figure  \@ref(fig:ProchlorococcusEnzymeKms)).
+Thus, SS120 can exploit habitats with O~2~ levels spanning 25 µM O~2~ to 250 µM O~2~, including higher PAR environments within OMZ.
+SS120 is likely excluded from the combination of higher [O~2~] and higher PAR by genomic limitations on capacity for DNA repair (Figure \@ref(fig:DNARepairFig)), and possibly by limited capacity for synthesis of reactive oxygen quenchers (Figure  \@ref(fig:ProchlorococcusEnzymeKms)).
 Our growth results are supported by Lavin *et al*.
@@
 from 20 to 200 m and all [O~2~] in an OMZ of the tropical North Pacific Ocean.
-SS120, grew under photoperiods longer than 4 h and showed increasing growth rate with increasing photoperiods.
-Therefore, SS120 can potentially exploit the longer summer photoperiods in temperate zones however, like MED4, cannot sustain growth in winter through its requirement for more than 4 h of light per day, even if water temperature warms into the clade LLII/III tolerance range.
-
-*Prochlorococcus marinus* SS120 prefers the deeper ocean where blue spectral waveband dominates at low levels, through its demonstrated ability to exploit only the lowest blue spectral waveband levels PAR of 30 µmol photons m^-2^ s^-1^ under 250 µM O~2~.
+SS120 grew under photoperiods longer than 4 h and showed increasing growth rate with increasing photoperiods.
 However, we found *P.
-marinus* SS120 can exploit more diverse ecological niches within the ocean layers, even in regions with high levels of blue spectral waveband,  but only under O~2~ of 25 µM (Figure \@ref(fig:SS120PAR)).
+marinus* SS120 can potentially exploit more diverse ecological niches within the ocean layers, even in regions with higher levels of blue spectral waveband, but only under O~2~ of 25 µM (Figure \@ref(fig:SS120PAR)).
 Lavin *et al*.
@@
 SS120 has the potential to thrive in deep temperate zones, specifically during the spring, summer, and fall seasons when the duration of daylight exceeds 4 h, if O~2~ are near surface saturation of about 250 µM.
-Under lower oxygen levels of 25 µM, SS120 can also exploit a 4 h photoperiod in the blue waveband, and thus has the potential to inhabit a warmed, deep, temperate region during the winter season.
-
-*Prochlorococcus marinus* MIT9313, a LLIV clade representative, shows the potential to inhabit future warmer temperate zones year-round, as it grows under a 4 h photoperiod, expected in winter or at light-attenuated depths.
-MIT9313 demonstrates an unexpected tolerance to higher light levels and cumulative diel PUR,  but only under low oxygen conditions of 25 µM and 2.5 µM (Figure \@ref(fig:MIT9313PAR)).
-The ability to utilize higher PAR and higher cumulative diel PUR under 25 µM or 2.5 µM O~2~ enables MIT9313 to grow in OMZ, even at depths closer to the surface.
+Under lower oxygen levels of 25 µM, SS120 can also potentially exploit a 4 h photoperiod in the blue waveband, and thus has the potential to inhabit a potential warmed, deep, temperate OMZ, during the winter season.
+
+*Prochlorococcus marinus* MIT9313, a LLIV clade representative, shows potential to inhabit future warmer temperate zones year-round, as it grows under a 4 h photoperiod, expected in winter, or at light-attenuated depths.
+MIT9313 demonstrates an unexpected tolerance to higher light levels and cumulative diel PUR, but only under low oxygen conditions of 25 µM and 2.5 µM (Figure \@ref(fig:MIT9313PAR)), enabling MIT9313 to grow in OMZ, even at depths closer to the surface.
 MIT9313 carries a gene encoding (S)-2-hydroxy-acid oxidase [@cunaneCrystalStructureAnalysis2005],  with a K~M~ for [O~2~] of ~ 250 µM (Figure \@ref(fig:ProchlorococcusEnzymeKms)), which produces H~2~O~2~.
@@
 These results are supported by Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSI protein subunits annotated as derived from MIT9313 detected at depths \> 120 m, along with PSII subunits at depths from 50 m to 200 m in regions where O~2~ was 15 µM.
-
-XXX Check Bagby and Chisholm for discussion on respiration as they limited CO2 and O2. Mirielle has notes, will add if relevant XXXXX 
-In future work we aim to test whether MIT9313 is not “using” photosynthesis in low O~2~ environments to drive CO~2~ fixation, so much as to generate oxygen locally to support  respiration.
-The deep water environments typical for MIT 9313 are relatively nutrient rich and  *Prochlorococcus* take up and metabolize various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017; @munoz-marinProchlorococcusCanUse2013] and amino acids [@zubkovDepthRelatedAmino2004].
-They may be using photosynthesis to generate O~2~ to act as an electron sink for respiration, to generate using ATP for maintenance and to take up nutrients from the surroundings.
+XXX Check Bagby and Chisholm for discussion on respiration as they limited CO2 and O2.
+Mirielle has notes, will add if relevant XXXXX  The deep water environments typical for MIT 9313 are relatively nutrient rich, and *Prochlorococcus* take up and metabolize various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017; @munoz-marinProchlorococcusCanUse2013] and amino acids [@zubkovDepthRelatedAmino2004].
+In future work we aim to test whether MIT9313 is using photosynthesis to drive CO~2~ fixation in low O~2~ environments, or whether PSII generation of O~2~ acts as an electron sink for respiration, to generate using ATP for maintenance and to take up nutrients from the surroundings.
 Partensky *et al*.
-[@partenskyComparisonPhotosyntheticPerformances2018] found that in the low-light conditions found in the OMZ, MED4, SS120 and MIT9313 all became net O~2~ consumers, suggesting that the low light levels cause the respiratory chain to consume more O~2~ than the photosynthetic electron transport chain generates, and c contributing to maintenance of the low O~2~ environment.
+[@partenskyComparisonPhotosyntheticPerformances2018] found that in the low-light conditions found in the OMZ, MED4, SS120 and MIT9313 all became net O~2~ consumers, suggesting that the low light levels cause the respiratory chain to consume more O~2~ than the photosynthetic electron transport chain generates, thus contributing to maintenance of the low O~2~ environment.
 

### 2024-03-04 Code/Manuscript_O2.Rmd
knitted to html

@@
 always_allow_html: true
-bibliography: [Manuscript_O2.bib, RPackages.bib]
+bibliography: [Manuscript_O2.bib, RPackages.bib, FaultyCitations.bib]
 csl: plos-one.csl
@@
             col.names =  c("EC",
-                          "Enzyme Name")
+                          "Enzyme Name",
+                          "Kegg Orthology")
              )

### 2024-03-04 Code/ManuscriptPURFits.Rmd
Added letters to PUR figures

@@
 
-```{r Pur plot strain faceted in columns}
+```{r Pur plot strain faceted in columns, fig.height=10, fig.width=10}
 
@@
         legend.direction = "vertical",
-        legend.spacing.x = unit(0.75, 'cm')) +
+        legend.spacing.x = unit(0.75, 'cm'),
+        tagger.panel.tag.background = element_blank()) +
   labs( linetype = "Fits",
@@
 
-      )
+      ) +
+  tagger::tag_facets(tag_levels  = c("A", "I"), tag_suffix = "")
 
@@
 # PhotoperiodPurFitsPlots <- tag_facet(PhotoperiodPurFitsPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
-
-```
-
-Would like to add Compact Letter Displays (cld) but do not know how. Some examples:
+# 
+# PhotoperiodPurFitsPlots
+```
+
+Would like to add Compact Letter Displays (cld). Some examples:
 https://stackoverflow.com/questions/70854552/any-other-options-besides-the-traditional-cld-bar-graph/70863531#70863531
@@
 
-ggsave(file = file.path(PlotsOut, paste("PhotoperiodPurFitsPlots",".tiff",sep = "")), plot = PhotoperiodPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsOut, paste("PhotoperiodPurFitsPlots",".tiff",sep = "")), plot = PhotoperiodPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
 
-```{r Pur plot strain faceted in columns}
+```{r Pur plot strain faceted in columns , fig.height=10, fig.width=10}
 
@@
 
-AllFitsCombinedWL |>
-  unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
-  mutate(PhotoperiodLabelTitle = "Photoperiod (h)",
-         OxygenLabel = "Oxygen Concentration (µM)",
-         Photoperiod = factor(Data_all_Photoperiod, levels = c(16, 12, 8, 4)),
-         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         WL = factor(Data_all_WL, levels = c("WW", 660, 450)),
-         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
-  ggplot() +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.7) +
-    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.0, alpha = 0.5) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_450) %>%  filter(O2_uM == 2.5, Strain == "MED4",  WL == 450)) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MED4", WL == 660))+
-    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MED4", WL == "WW")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 450)) +
- geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "SS120", O2_uM != 250, WL == "WW")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 660))+
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MIT9313", O2_uM == 2.5, WL == "WW")) +
- labs(title = "Anova fit comparisons of WL to pooled", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
-  scale_x_continuous(label=scientific_10) +
-  scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
-  scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
-  # scale_linetype_manual(values = MyLineTypes, labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
-  scale_shape_manual(values = PhotoperiodShapes)  +
-  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), cols = vars(Strain), 
-                    labeller = labeller(Strain = label_value, O2_uM = label_value, OxygenLabel = label_value)) +
- guides(linetype = guide_legend(nrow = 1),
-        fill = "none",
-        color = guide_legend(nrow = 1)) +
- guides(shape = guide_legend(nrow = 1)) +
-  theme_bw() +
-   theme( strip.text = element_text(size = 25),
-        axis.title.y = element_text(color = "black", size = 30,  hjust = 0.40),
-        axis.title.x = element_text(color = "black", size = 30),
-        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
-        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
-        # strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"), 
-        legend.key.size = unit(0.1, 'cm'), #change legend key size
-        legend.key.height = unit(0.1, 'cm'), #change legend key height
-        legend.key.width = unit(0.1, 'cm'), #change legend key width
-        legend.title =  element_text(size = 25),  #change legend title font size
-        legend.text = element_text(size = 25),   #change legend text font size
-        legend.position = "top") +
-  labs( shape = "Photoperiod (h)",
-        color = "Growth Waveband (nm)",
-       linetype = "Photoperiod lines"
-      )
+# AllFitsCombinedWL |>
+#   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
+#   mutate(PhotoperiodLabelTitle = "Photoperiod (h)",
+#          OxygenLabel = "Oxygen Concentration (µM)",
+#          Photoperiod = factor(Data_all_Photoperiod, levels = c(16, 12, 8, 4)),
+#          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+#          WL = factor(Data_all_WL, levels = c("WW", 660, 450)),
+#          Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
+#   ggplot() +
+#   geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.7) +
+#     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.0, alpha = 0.5) +
+#   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
+#    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_450) %>%  filter(O2_uM == 2.5, Strain == "MED4",  WL == 450)) +
+#   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MED4", WL == 660))+
+#     geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MED4", WL == "WW")) +
+#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) +
+#    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 450)) +
+#  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "SS120", O2_uM != 250, WL == "WW")) +
+#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) +
+#   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 660))+
+#   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MIT9313", O2_uM == 2.5, WL == "WW")) +
+#  labs(title = "Anova fit comparisons of WL to pooled", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
+#   scale_x_continuous(label=scientific_10) +
+#   scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
+#   scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
+#   # scale_linetype_manual(values = MyLineTypes, labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
+#   scale_shape_manual(values = PhotoperiodShapes)  +
+#   ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), cols = vars(Strain), 
+#                     labeller = labeller(Strain = label_value, O2_uM = label_value, OxygenLabel = label_value)) +
+#  guides(linetype = guide_legend(nrow = 1),
+#         fill = "none",
+#         color = guide_legend(nrow = 1)) +
+#  guides(shape = guide_legend(nrow = 1)) +
+#   theme_bw() +
+#    theme( strip.text = element_text(size = 25),
+#         axis.title.y = element_text(color = "black", size = 30,  hjust = 0.40),
+#         axis.title.x = element_text(color = "black", size = 30),
+#         axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
+#         axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
+#         # strip.background=element_rect(color="grey87", fill = "grey82"),
+#         # strip.background=element_rect(fill = "white"), 
+#         legend.key.size = unit(0.1, 'cm'), #change legend key size
+#         legend.key.height = unit(0.1, 'cm'), #change legend key height
+#         legend.key.width = unit(0.1, 'cm'), #change legend key width
+#         legend.title =  element_text(size = 25),  #change legend title font size
+#         legend.text = element_text(size = 25),   #change legend text font size
+#         legend.position = "top") +
+#   labs( shape = "Photoperiod (h)",
+#         color = "Growth Waveband (nm)",
+#        linetype = "Photoperiod lines"
+#       )
 
@@
         color = "Growth Waveband",
-
-      )
+      ) +
+  tagger::tag_facets(tag_levels  = c("A", "I"), tag_suffix = "")
 

### 2024-03-04 Code/Manuscript_O2.Rmd
Added letters to PUR figures

@@
 
-knitr::write_bib(c("knitr", "tidyverse", "lubridate", "ggplot2", "broom", "grid", "bookdown", "glue", "cowplot", "ggpubr", "ggh4x", "png", "Studio", "zoo", "photobiology", "photobiologyWavebands", "data.table", "googlesheets4",  "mgcv", "minpack.lm",  "egg", 'RPackages.bib'))
+knitr::write_bib(c("knitr", "tidyverse", "lubridate", "ggplot2", "broom", "grid", "bookdown", "glue", "cowplot", "ggpubr", "ggh4x", "png", "Studio", "zoo", "photobiology", "photobiologyWavebands", "data.table", "googlesheets4",  "mgcv", "minpack.lm",  "tagger", 'RPackages.bib'))
 
@@
 marinus* SS120, a clade LLII/III ecotype found deep in the water column, and *P.
-marinus* MIT9313, a clade LLIV ecotype also found in deep oceans including OMZ, under a matrix of spectral, light level, photoperiod and oxygen conditions approxmating present day and hypothetical future niches.
+marinus* MIT9313, a clade LLIV ecotype also found in deep oceans including OMZ, under a matrix of spectral, light level, photoperiod and oxygen conditions approximating present day and hypothetical future niches.
 Low light levels in the blue spectral waveband prevail in deep ocean waters [@morelAvailableUsableStored1978; @holtropVibrationalModesWater2021], while solar incidence angle and light attenuation also progressively attenuate the photoperiod with depth beneath the ocean surface.
 
-*Prochlorococcus marinus* MED4 has a physiological requirement for more than 4 h of light per day; thus this strain will not exploit habitats with short photoperiods, typical of temperate winter or light attenuated depths, even if water temperature warms into the clade LLII/III tolerance range.
+*Prochlorococcus marinus* MED4 has a physiological requirement for more than 4 h of light per day; thus this strain will not exploit habitats with short photoperiods, typical of temperate winter or light attenuated depths, even if water temperature warms into the clade HLI tolerance range.
 MED4 is also excluded from the lowest oxygen habitats, represented by our 2.5 µM O~2~ experimental conditions.
@@
 XXX PLOS requires grant numbers XXX
+
 # Funding  {.unnumbered}
+
 To Be Entered through PLoSONe system and deleted here

### 2024-03-04 Code/ManuscriptFigures.Rmd
Added letters to overlay plot

@@
   theme_bw() +
- theme(#strip.text = element_blank(),
+ theme( strip.text = element_text(size = 13),
        # legend.background = element_rect(color = "transparent", fill = "transparent"),
@@
         panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank())
+        panel.grid.major = element_blank(),
+        tagger.panel.tag.background = element_blank()) +
+  tagger::tag_facets(tag_levels  = c("A", "I"), tag_suffix = "")
 
@@
 
-ggsave(file = file.path(PlotsOut, paste("OverlayPlots",".tiff",sep = "")), plot = OverlayPlots, device = NULL, scale = 1, height = 25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsOut, paste("OverlayPlots",".tiff",sep = "")), plot = OverlayPlots, device = NULL, scale = 1, height = 25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 

### 2024-03-04 Code/Manuscript_O2.Rmd
fixed fig caption overlay plot

@@
 
-OverlayPlots_cap <- glue("**Normalized absorbance and Photosynthetically Usable Radiation for *Prochlorococcus marinus* MED4 (A,B,C); SS120 (D,E,F); MIT9313 (G,H,I) grown under three emission wavebands.**",
-                       "**(A,D,G)** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated PUR spectra (solid black line and shaded grey).",
-                       "**(B,E,H)** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded red).",
-                       "**(C,F,I)**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded blue).",
+OverlayPlots_cap <- glue("**Normalized absorbance and Photosynthetically Usable Radiation for *Prochlorococcus marinus* MED4 (A,D,G); SS120 (B,E,H); MIT9313 (C,F,I) grown under three emission wavebands.**",
+                       "**(A,B,C)** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated PUR spectra (solid black line and shaded grey).",
+                       "**(D,E,F)** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded red).",
+                       "**(G,H,I)**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded blue).",
 

### 2024-03-04 Code/Manuscript_O2.Rmd
edits

@@
 
-knitr::write_bib(c("knitr", "tidyverse", "lubridate", "ggplot2", "broom", "grid", "bookdown", "glue", "cowplot", "ggpubr", "ggh4x", "png", "Studio", "zoo", "photobiology", "photobiologyWavebands", "data.table", "googlesheets4",  "mgcv", "minpack.lm",  "tagger", 'RPackages.bib'))
+knitr::write_bib(c("knitr", "tidyverse", "lubridate", "ggplot2", "broom", "grid", "bookdown", "glue", "cowplot", "ggpubr", "ggh4x", "png", "zoo", "photobiology", "photobiologyWavebands", "data.table", "googlesheets4",  "mgcv", "minpack.lm"), 'RPackages.bib')
 
@@
 	iii) Sample station depth and [O~2~].  
-	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using *tidyverse* package [@R-tidyverse] running under R v4.1.3 and RStudio v2023.06.0 XXX Naaman to get location (https://posit.co/)  XXX.
+	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using *tidyverse* package [@R-tidyverse] running under R v4.1.3 and RStudio v2023.06.0 [@RStudio].
 The resulting merged dataset was filtered for those *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b~6~f (Cytb~6~f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Plastoquinol Terminal Oxidase (PTOX); Plastocyanin (PC); Ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  ATP Synthase;  FtsH proteases (FtsH) or ribosomes.
@@
 *Prochlorococcus* FtsH isoform identities, and functions, were inferred by sequence comparisons to the characterized four isoforms of FtsH protease of *Synechocystis* sp.
-PCC6803 (CITATONS).
+PCC6803 [@bonisteelStrainSpecificDifferences2018].
 Data for each strain was plotted against depth and  [O~2~] and sampling station.
@@
 We are, however, confident in clade classifications for each protein examined.
-A caveat to interpretation of this data is the peptide detection bias inherent to mass spectrometry CITATION.
+A caveat to interpretation of this data is the peptide detection bias inherent to mass spectrometry XXX Aurora CITATION XXX.
 The data is also limited by the number and nature of protein spectra in the SEQUEST database: a peptide sequence was not determined unless there is already a known spectrum for that peptide in the SEQUEST database, hence some peptides of interest may not be identifiable.
@@
 Nitrogen (N~2~), with consistent 0.05% of Carbon Dioxide (CO~2~) gas, delivered through a 0.2 μm sterile microfilter via a G400 gas mixing system (Qubit Systems Inc., Kingston, Ontario, Canada).
-[O~2~] in situ was verified using oxygen optodes (PyroScience, Germany) inserted into tubes for real-time measurements, with a temperature probe in
+[O~2~] *in situ* was verified using oxygen optodes (PyroScience, Germany) inserted into tubes for real-time measurements, with a temperature probe in
 the bath of the bioreactor to correct [O~2~] measures for temperature fluctuations.
@@
 
-Figures \@ref(fig:OverlayPlots) provide visual representations of PUR, the black solid line and shaded area, in relation to the imposed PAR, the dotted line, under each imposed spectral wavebands for *P.
-marinus* MED4, SS120 and MIT9313, respectively.
+Figure \@ref(fig:OverlayPlots) provide visual representations of PUR, the black solid line and shaded area, in relation to the imposed PAR, the dotted line, under each imposed spectral wavebands for *P.
+marinus* MED4 (A,B,C), SS120 (D,E,F) and MIT9313 (G,H,I).
 Figure (\@ref(fig:PurParPlot)) shows the relationship between calculated PUR versus imposed PAR for each *P.
@@
 We filtered the dataset of Omar *et al*.
-[@omarAnnotationGenesEncoding2023], for Enzyme Commission Numbers (EC numbers), or Kegg Orthology Numbers (KO numbers) identified by BRENDA  [@changBRENDAELIXIRCore2021] as 'natural substrates' for O~2~ in *P.
+[@omarAnnotationGenesEncoding2023], for Enzyme Commission Numbers (EC numbers), or Kegg Orthology Numbers (KO numbers) identified by BRENDA  [@changBRENDAELIXIRCore2021] as 'natural substrates' for O~2~; EC numbers identified by BRENDA as being activated, or inhibited by light; and EC numbers annotated by BioCyc [@karpBioCycCollectionMicrobial2019] as corresponding to the Gene Ontology Term (GO:0006281 - DNA repair), in *P.
 marinus* strains (MED4, MIT9313, SS120, and NATL2A).
@@
 We merged the dataset with a list of enzyme Michaelis constant (K~m~) values from other organisms, as K~m~ values from *Prochlorococcus* were only available in the case of Ribulose bisphosphate carboxylase.
-XXX Possibly add the link to the full list of genes.
-Remove this once added XXXX
- XXXXADD METHODS for DNA REpair and for light dependent EnzymesXXXX
+Gene counts for Flavodiirons were obtained from Allahverdiyeva *et al*.
+[@allahverdiyevaCyanobacterialOxygenicPhotosynthesis2015a], as they do not have allocated EC numbers.
+A full list of enzymes and corresponding EC and KO numbers can be found in Table \@ref(tab:ProchlorococcusEnzymeTable).
 
@@
 MIT9313) were detected throughout the water column in high [O~2~] and at depth in low [O~2~] samples.
-The exclusive assignment of ATP Synthase peptides to Clade IV (ex.
+The exclusive assignment of ATP Synthase peptides to clade LLIV (ex.
 MIT9313) may result from the high conservation of protein sequence for this complex.
-
-XXXXCheck text for figureXXXX
 
@@
 
-XXXRewrite caption if we change figure versionXXX
-XXX Figure changed- need to rewrite caption if keeping this figure XXX
 ```{r CladeProchloroPhotosynthDepthO2, fig.cap = CladeProchloroPhotosynthDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
@@
                        "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
-                       "Rows separate data annotated as from *Prochlorococcus* clades: HLI (includes *P.
-marinus* MED4), HLII, LLI, LLII/III (includes P.
-marinus* SS120) and LLIV (includes *P.
-marinus* MIT9313).",
+                       "Rows separate data annotated as from *Prochlorococcus* clades: HLI (represents *P.
+marinus* MED4 annotated with solid black circles), LLI, LLII/III (represents *P.
+marinus* SS120 annotated with solid black circles) and LLIV (represents *P.
+marinus* MIT9313 annotated with solid black circles).",
                        "Columns show detections of proteins annotated as  Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
@@
 Due to the absorption of *P.
-marinus* pigments in the blue spectral waveband range, the maximum cumulative diel PUR under blue light is almost 3 times that of white LED light, and about 6 times the red light treatment (Figure \@ref(fig:PurParPlot)), despite being derived from the same photoperiods and peak PAR regimes.
+marinus* pigments in the blue spectral waveband range, the maximum cumulative diel PUR under blue light is almost 3 times that of white LED light, and about 5 times the red light treatment (Figure \@ref(fig:PurParPlot)), despite being derived from the same photoperiods and peak PAR regimes.
 As such, only blue light experiments extend beyond cumulative diel PUR of ~ 2 x 10^6^ µmol photons m^-2^ d^-1^.
@@
 The representative of HLI clade, *P.
-marinus* MED4, showed no growth under any 4 h photoperiod treatments, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments (Figure \@ref(fig:PhotoperiodPurFitsPlots)A).
+marinus* MED4, showed no growth under any 4 h photoperiod treatments, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments (Figure \@ref(fig:PhotoperiodPurFitsPlots)A,B,C).
 In parallel MED4 showed no growth under 2.5 µM O~2~, no matter the level of diel cumulative PUR.
-In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth under blue light was well described by a saturating response of growth [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] to increasing cumulative diel PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A), and no evidence of inhibition of growth at any achieved cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)A).
-Under the 'artificial' growth treatment of red light, MED4 achieved more growth per unit diel cumulative PUR (Figure \@ref(fig:BluevsRedPurFitsPlots)A), consistent with Murphy *et al*.
+In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth under blue light was well described by a saturating response of growth [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] to increasing cumulative diel PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A,B), and no evidence of inhibition of growth at any achieved cumulative diel PUR.
+Under the 'artificial' growth treatment of red light, MED4 achieved more growth per unit diel cumulative PUR (Figure \@ref(fig:BluevsRedPurFitsPlots)A,B), consistent with Murphy *et al*.
 [@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for growth under red light, for MED4, because red light provokes less photoinactivation of PSII, than equivalent levels of blue light.
-For distinct fits for different photoperiods refer to figure \@ref(fig:PhotoperiodPurFitsPlots)A.
+For distinct fits for different photoperiods refer to figure \@ref(fig:PhotoperiodPurFitsPlots)A,B and C.
 
@@
 The representative of the LLII/III clade, *P.
-marinus* SS120 showed almost no growth under 2.5 µM O~2~ experiments (Figure \@ref(fig:PhotoperiodPurFitsPlots)B).
-Most 4 h photoperiod treatments of SS120 also did not grow under 250 µM O~2~, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments (Figure \@ref(fig:PhotoperiodPurFitsPlots)B).
-SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ experiments (Figure \@ref(fig:PhotoperiodPurFitsPlots)B).
+marinus* SS120 showed almost no growth under 2.5 µM O~2~ experiments (Figure \@ref(fig:PhotoperiodPurFitsPlots)F).
+Most 4 h photoperiod treatments of SS120 also did not grow under 250 µM O~2~, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments (Figure \@ref(fig:PhotoperiodPurFitsPlots)F).
+SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ experiments (Figure \@ref(fig:PhotoperiodPurFitsPlots)F).
 
@@
 The onset of growth inhibition extended to higher cumulative diel PUR for cultures under 25 µM O~2~, showing that SS120 is partially protected from photoinhibition of growth by 25 µM O~2~.
-Under 25 µM O~2~, red light again generated more growth of SS120 per unit cumulative diel PUR, than did blue light, again consistent with lower cost of growth through lower photoinactivation under red light (Figure \@ref(fig:BluevsRedPurFitsPlots)B).
-For distinct fits for different photoperiods refer to figure \@ref(fig:PhotoperiodPurFitsPlots)B.
+Under 25 µM O~2~, red light again generated more growth of SS120 per unit cumulative diel PUR, than did blue light, again consistent with lower cost of growth through lower photoinactivation under red light (Figure \@ref(fig:BluevsRedPurFitsPlots)E).
+For distinct fits for different photoperiods refer to figure \@ref(fig:PhotoperiodPurFitsPlots)D,E and F.
 
@@
 The LLIV clade representative, *P.
-marinus* MIT9313, showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR, with higher growth rates over a narrower plateau under 25 and 250 µM O~2~, compared to a wider, lower, flatter response to cumulative diel PUR under 2.5 µM O~2~ (Figure \@ref(fig:PhotoperiodPurFitsPlots)C).
-Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands(Figure \@ref(fig:PhotoperiodPurFitsPlots)C).
-In contrast, under 25 µM O~2~, MIT9313 showed a greatly extended exploitation of higher cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^.
-Similarly, under 2.5 µM O~2~, MIT9313 grew more slowly, but only showed full growth inhibition above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)C).
-
-As with MED4 and SS120, our data again support enhanced growth under conditions of low cumulative diel PUR and 660 nm (red) spectral bandwidth, consistent with Murphy *et al*.[@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue, wavebands (Figure \@ref(fig:BluevsRedPurFitsPlots)C).
-Interestingly, this protective effect of red light disappears for MIT9313 growing under 2.5 µM O~2~, possibly because photoinactivation is strongly suppressed under this low [O~2~].
-For distinct fits for different photoperiod fits refer to figure \@ref(fig:PhotoperiodPurFitsPlots)C.
+marinus* MIT9313, showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR, with higher growth rates over a narrower plateau under 25 and 250 µM O~2~, compared to a wider, lower, flatter response to cumulative diel PUR under 2.5 µM O~2~ (Figure \@ref(fig:PhotoperiodPurFitsPlots)G,H).
+Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands (Figure \@ref(fig:PhotoperiodPurFitsPlots)G).
+In contrast, under 25 µM O~2~, MIT9313 showed a greatly extended exploitation of higher cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Figure \@ref(fig:PhotoperiodPurFitsPlots)H).
+Similarly, under 2.5 µM O~2~, MIT9313 grew more slowly, but only showed full growth inhibition above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).
+
+As with MED4 and SS120, our data again support enhanced growth under conditions of low cumulative diel PUR and 660 nm (red) spectral bandwidth, consistent with Murphy *et al*.[@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue, wavebands (Figure \@ref(fig:BluevsRedPurFitsPlots)G,H).
+Interestingly, this protective effect of red light disappears for MIT9313 growing under 2.5 µM O~2~, possibly because photoinactivation is strongly suppressed under this low [O~2~] (Figure \@ref(fig:BluevsRedPurFitsPlots)I).
+For distinct fits for different photoperiod fits refer to figure \@ref(fig:PhotoperiodPurFitsPlots)G,H and I.
 
@@
                     "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                    "Columns are strains; MED4, SS120 and MIT9313.",
+                    "Columns are strains; MED4 (A,B,C), SS120 (D,E,F) and MIT9313 (G,H,I).",
                     "Shapes show the imposed photoperiod (h); 4 h (solid square),  8 h (solid diamond), 12 h (solid circle), 16 h (solid upright triangle).",
@@
 *Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4, homologs to the characterized FtsH isoforms of the model freshwater cyanobacterium *Synechocystis* FtsH, and with presumably parallel functions (Table \@ref(tab:FtsHTable)).
-Upon a shift to higher light HLI MED4 upregulated expression of FtsH1 and FtsH2 [@bonisteelStrainSpecificDifferences2018], homologs to the *Synechocystis* slr0228 and slr1604, implicated in PSII repair.
+Upon a shift to higher light HLI MED4 upregulated expression of FtsH1 and FtsH2 [@bonisteelStrainSpecificDifferences2018], homologs to the *Synechocystis* *slr*0228 and *slr*1604, implicated in PSII repair.
 In contrast, representative LLIV strain MIT9313 showed less overall expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem.
-Furthermore, MIT9313 expressed primarily FtsH3, homologous to *Synechocystis* slr1463, possibly involved in PSI biogenesis, and FtsH expression did not increase in response to light stress in MIT9313.
+Furthermore, MIT9313 expressed primarily FtsH3, homologous to *Synechocystis* *slr*1463, possibly involved in PSI biogenesis, and FtsH expression did not increase in response to light stress in MIT9313.
 Through adaptation to steady low light, clade LLIV *Prochlorococcus* instead allocate resources to processes other than dynamic regulation of PSII repair.
@@
 FtsHTable <- tibble(Organism = c("*Prochlorococcus marinus*", "*Synechocystis sp. PCC6803*", "Function"),
-                    FtsH1 = c("FtsH1", "SlrO228", "PSII Repair"),
-                    FtsH2 = c("FtsH2", "Slr1604", "PSII Repair"),
-                    FtsH3 = c("FtsH3", "Slr1463", "PSI biogenesis?"),
-                    FtsH4 = c("FtsH4", "Slr1390", "Cell viability")
+                    FtsH1 = c("FtsH1", "*Slr*0228", "PSII Repair"),
+                    FtsH2 = c("FtsH2", "*Slr*1604", "PSII Repair"),
+                    FtsH3 = c("FtsH3", "*Sll*1463", "PSI biogenesis?"),
+                    FtsH4 = c("FtsH4", "*Slr*1390", "Cell viability")
                     )
@@
 \newpage
-XXXXEdit text depending upon which ocean protein figures we useXXXXX
+
 Ocean detections of proteins mediating protein metabolism support this interpretation of distinct FtsH function across clades of *P.
 marinus*.
-Ribosome proteins from clade HLI MED4, clade LLII/III SS120 and clade LLIV MIT9313 show generally similar patterns vs.
-[O~2~] and depth, a proxy for peak PAR  (Figure \@ref(fig:NATLProchloroProteinMetabDepthO2)).
-FtsH3, inferred to mediate PSI assembly, likewise shows a similar pattern between MED4 and MIT9313 (Figure \@ref(fig:NATLProchloroProteinMetabDepthO2)).
+Ribosome proteins from clade HLI MED4, clade LLI NATL2A, clade LLII/III SS120 and clade LLIV MIT9313 show generally similar patterns vs.
+[O~2~] and depth, a proxy for peak PAR  (Figure \@ref(fig:CladeProchloroProteinMetabDepthO2)).
+FtsH3, inferred to mediate PSI assembly, likewise shows a similar pattern between MED4 and MIT9313 (Figure \@ref(fig:CladeProchloroProteinMetabDepthO2)).
 But only MED4 shows detected presence of the FtsH1 & FtsH2 isoforms inferred to mediate PSII repair, and then only in near-surface samples subject to higher light.
-Furthermore, even though MIT9313 grows (Figure \@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~] (Figure \@ref(fig:CladeProchloroPhotosynthDepthO2)), no FtsH from MIT9313 is detected at low [O~2~] (Figure \@ref(fig:NATLProchloroProteinMetabDepthO2)), suggesting limited requirement for protein turnover under low [O~2~].
-
-\newpage
-
-```{r NATLProchloroProteinMetabDepthO2, fig.cap = NATLProchloroProteinMetabDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
-
-NATLProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein metabolism complexes.**", 
+Furthermore, even though MIT9313 grows (Figure \@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~] (Figure \@ref(fig:CladeProchloroPhotosynthDepthO2)), no FtsH from MIT9313 is detected at low [O~2~] (Figure \@ref(fig:CladeProchloroProteinMetabDepthO2)), suggesting limited requirement for protein turnover under low [O~2~].
+
+\newpage
+
+```{r CladeProchloroProteinMetabDepthO2, fig.cap = CladeProchloroProteinMetabDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
+
+CladeProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein metabolism complexes.**", 
                        "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
@@
 
-knitr::include_graphics(file.path(FiguresIn, "NATLProchloroProteinMetabDepthO2.png"))
+knitr::include_graphics(file.path(FiguresIn, "CladeProchloroProteinMetabDepthO2.png"))
 ```
@@
 marinus* strains from clades HLI, LLI, LLII/III and LLIV.
-XXXX CITATION  to Table once added XXXX.
 MED4 increases expression of alternative oxidase ('ubiquinol oxidase (non electrogenic)')  to cope with changes in light [@bergResponsesPsbAHli2011], by dissipating electrons from the inter-system transport chain.
@@
 marinus* MIT9313 suffered photoinhibition, resulting from the inactivation of PSII caused by the production of the reactive oxygen species, hydrogen peroxide.
-This photoinhibition is compounded by the limited inducible repair mechanism for PSII, due to the absence of FtsH 1 and 2 XXXXCHECK TERMINOLOGYXXXX expression in *P.
+This photoinhibition is compounded by the limited inducible repair mechanism for PSII, due to the absence of FtsH 1 and 2 expression in *P.
 marinus* MIT9313 [@bonisteelStrainSpecificDifferences2018].
@@
 These results are supported by Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSI protein subunits annotated as derived from MIT9313 detected at depths \> 120 m, along with PSII subunits at depths from 50 m to 200 m in regions where O~2~ was 15 µM.
-XXX Check Bagby and Chisholm for discussion on respiration as they limited CO2 and O2.
-Mirielle has notes, will add if relevant XXXXX  The deep water environments typical for MIT 9313 are relatively nutrient rich, and *Prochlorococcus* take up and metabolize various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017; @munoz-marinProchlorococcusCanUse2013] and amino acids [@zubkovDepthRelatedAmino2004].
+The deep water environments typical for MIT 9313 are relatively nutrient rich, and *Prochlorococcus* take up and metabolize various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017; @munoz-marinProchlorococcusCanUse2013] and amino acids [@zubkovDepthRelatedAmino2004].
 In future work we aim to test whether MIT9313 is using photosynthesis to drive CO~2~ fixation in low O~2~ environments, or whether PSII generation of O~2~ acts as an electron sink for respiration, to generate using ATP for maintenance and to take up nutrients from the surroundings.
@@
                     "Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to data pooled for each combination of strain and dissolved oxygen shown with solid lines.
-Separate models fit to photoperiod data and shown if significantly different from the pooled model using one-way ANOVA; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).",
+Separate models fit to photoperiod data and shown if significantly different (p value < 0.05) from the pooled model using one-way ANOVA; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).",
                        .sep = " ")
@@
 
-ProchlorococcusLightEnzymes_cap <- glue("**Genes encoding enzymes activated or inhibited by light.**",
+ProchlorococcusLightEnzymes_cap <- glue("***Prochlorococcus* Genes encoding enzymes activated or inhibited by light.**",
                          "The y-axis represents *Prochlorococcus marinus* strains.",
-                         "The x-axis represents enzymes encoded for DNA repair found in at least one *Prochlorococcus marinus* strain in this study.",
+                         "The x-axis represents enzymes encoding light-dependent enzymes found in at least one *Prochlorococcus marinus* strain in this study.",
                          "Point size indicate gene counts.",
@@
 readRDS(file.path(DataIn,"ProchlorococcusEnzymeTable.Rds")) %>% 
+  select(EnzymeName, EC, KO) %>% 
   knitr::kable(.,
-             caption = "Enzyme Commission numbers (EC) and corresponsing enzyme names.",
-            col.names =  c("EC",
+             caption = "Enzymes shown in Figures \\@ref(fig:ProchlorococcusEnzymeKms),  \\@ref(fig:DNARepairFig) and \\@ref(fig:ProchlorococcusLightEnzymes) with their Enzyme Commission numbers (EC) and Kegg Orthology (KO).",
+            col.names =  c(
                           "Enzyme Name",
+                          "EC",
                           "Kegg Orthology")
@@
 Carlie Barnhill (Mount Allison Student) assisted with code for import of multicultivator growth data files.
-
-XXX PLOS requires grant numbers XXX
 
@@
 
+XXX PLOS requires grant numbers XXX
+
 # References {.unnumbered}

### 2024-03-04 Code/Manuscript_O2.Rmd
knit

--- 2024-03-04 Code/Manuscript_O2.Rmd
@@
 Predictions indicate a net global increase of *P.
-marinus* cell abundances of 29% [@flombaumPresentFutureGlobal2013{}, along with  poleward latitudinal shifts of at least 10° in marine phytoplankton niches by the end of this century  [@bartonAnthropogenicClimateChange2016] in response to warming waters, with increases in *P.
+marinus* cell abundances of 29% [@flombaumPresentFutureGlobal2013], along with  poleward latitudinal shifts of at least 10° in marine phytoplankton niches by the end of this century  [@bartonAnthropogenicClimateChange2016] in response to warming waters, with increases in *P.
 marinus* of approximately 50% in the more poleward regions of their distributions.

### 2024-03-05 Code/Manuscript_O2.Rmd
Fixed figure caption and figure references

--- 2024-03-04 Code/Manuscript_O2.Rmd
@@
 
-A Generalized Additive Model (GAM) [@woodGeneralizedAdditiveModels2017] was applied to the relation of chlorophyll-specific µ, d^-1^  to photoperiod and PAR level,  for each growth [O~2~] level, and for the blue and red wavebands for growth, for each *P.marinus* strain in this study.
+A Generalized Additive Model (GAM) [@woodGeneralizedAdditiveModels2017] was applied to the relation of chlorophyll-specific µ, d^-1^  to photoperiod and PAR level,  for each growth [O~2~] level, and for the blue and red wavebands for growth, for each *P.
+marinus* strain in this study.
 The R package *`mgcv`* [@R-mgcv] was used to model the growth rate with smoothing terms and indicate the 90, 50 and 10% quantiles for growth rate across the levels of factors.
@@
                        "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
-                       "Rows separate data annotated as from *Prochlorococcus* clades: HLI (represents *P.
-marinus* MED4 annotated with solid black circles), LLI, LLII/III (represents *P.
-marinus* SS120 annotated with solid black circles) and LLIV (represents *P.
+                       "Rows separate data annotated as from *Prochlorococcus* clades: HLI (*P.
+marinus* MED4 annotated with solid black circles), LLI (*P.
+marinus* NATL2A annotated with solid black circles), LLII/III (*P.
+marinus* SS120 annotated with solid black circles) and LLIV (*P.
 marinus* MIT9313 annotated with solid black circles).",
@@
 marinus* SS120 showed almost no growth under 2.5 µM O~2~ experiments (Figure \@ref(fig:PhotoperiodPurFitsPlots)F).
-Most 4 h photoperiod treatments of SS120 also did not grow under 250 µM O~2~, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments (Figure \@ref(fig:PhotoperiodPurFitsPlots)F).
-SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ experiments (Figure \@ref(fig:PhotoperiodPurFitsPlots)F).
-
-Under both 25 or 250 µM O~2~ experiments, SS120 growth plateaued by about 5.0 x 10^5^ µmol photons m^-2^ d^-1^ diel PUR, with some scatter among photoperiod and spectral waveband regimes.
+Most 4 h photoperiod treatments of SS120 also did not grow under 250 µM O~2~, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments (Figure \@ref(fig:PhotoperiodPurFitsPlots)D).
+SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ experiments (Figure \@ref(fig:PhotoperiodPurFitsPlots)D).
+
+Under both 25 and 250 µM O~2~ experiments, SS120 growth plateaued by about 5.0 x 10^5^ µmol photons m^-2^ d^-1^ diel PUR, with some scatter among photoperiod and spectral waveband regimes.
 The onset of growth inhibition extended to higher cumulative diel PUR for cultures under 25 µM O~2~, showing that SS120 is partially protected from photoinhibition of growth by 25 µM O~2~.
@@
 The LLIV clade representative, *P.
-marinus* MIT9313, showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR, with higher growth rates over a narrower plateau under 25 and 250 µM O~2~, compared to a wider, lower, flatter response to cumulative diel PUR under 2.5 µM O~2~ (Figure \@ref(fig:PhotoperiodPurFitsPlots)G,H).
+marinus* MIT9313, showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR, with higher growth rates over a narrower plateau under 25 and 250 µM O~2~ (Figure \@ref(fig:PhotoperiodPurFitsPlots)H,G), compared to a wider, lower, flatter response to cumulative diel PUR under 2.5 µM O~2~ (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).
 Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands (Figure \@ref(fig:PhotoperiodPurFitsPlots)G).
@@
 Repair of photoinactivated PSII relies on the removal of damaged PsbA [@mannInvolvementFtsHHomologue2000; @adamFtsHProteasesChloroplasts2005], followed by reassembly with newly synthesized PsbA [@nixonRecentAdvancesUnderstanding2010].
-Degradation of PsbA is a rate-limiting step in recovery from photoinhibition [@kanervoD1ProteinDegradation1993], mediated largely by a heterohexamer of (FtsH12)~3~, a membrane-bound [@sacharzSubCellularLocation2015; @zakInitialStepsBiogenesis2001] metalloprotease  [(Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
+Degradation of PsbA is a rate-limiting step in recovery from photoinhibition [@kanervoD1ProteinDegradation1993], mediated largely by a heterohexamer of (FtsH1-FtsH2)~3~, a membrane-bound [@sacharzSubCellularLocation2015; @zakInitialStepsBiogenesis2001] metalloprotease  [(Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
 [@adamFtsHProteasesChloroplasts2005; @boehmSubunitOrganizationSynechocystis2012a; @nixonRecentAdvancesUnderstanding2010; @komendaExposedNTerminalTail2007] (Pisareva et al., 2007; Sacharz et al., 2015),  @mannInvolvementFtsHHomologue2000, (AMANDA REF from ALGATECH).
@@
 In contrast, representative LLIV strain MIT9313 showed less overall expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem.
-Furthermore, MIT9313 expressed primarily FtsH3, homologous to *Synechocystis* *slr*1463, possibly involved in PSI biogenesis, and FtsH expression did not increase in response to light stress in MIT9313.
+Furthermore, MIT9313 expressed primarily FtsH3, homologous to *Synechocystis* *slr*1463, possibly involved in PSI biogenesis, and FtsH expression did not increase in response to light stress in MIT9313 [@bonisteelStrainSpecificDifferences2018].
 Through adaptation to steady low light, clade LLIV *Prochlorococcus* instead allocate resources to processes other than dynamic regulation of PSII repair.
@@
                        "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
-                       "Rows separate data annotated as from *Prochlorococcus marinus* strains MED4 (clade HLI), SS120 (clade LLII/III) and MIT9313 (clade LLIV).",
-                       "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome).",
+                       "Rows separate data annotated as from *Prochlorococcus* clades: HLI (*P.
+marinus* MED4 annotated with solid black circles), LLI (*P.
+marinus* NATL2A annotated with solid black circles), LLII/III (*P.
+marinus* SS120 annotated with solid black circles) and LLIV (*P.
+marinus* MIT9313 annotated with solid black circles).",
+                       "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome.",
                        "Culture growth experimental conditions indicated by horizontal grey lines for depths approximating Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) and vertical grey lines for [O~2~] (µM).",
@@
 We hypothesize that low cell abundances of LL ecotypes in the mixed layer is likely driven in part by increased [O~2~],  and it is [O~2~] that constrains LL clades to deeper waters, not necessarily the light level.
-We found that under 25 µM O~2~ representatives of 'LL' clades, SS120 and MIT9313, actually tolerate approximately 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)B,C), comparable to the representative HL clade, MED4 which also exhibited growth saturation at the same cumulative diel PUR of 1.0 x 10^6^ µmol photons m^-2^ d^-1^ (Figure \@ref(fig:PhotoperiodPurFitsPlots)A).
-Growth under lower O~2~ allowed MIT9313 to substantially increase its exploitation of higher diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)C).
+We found that under 25 µM O~2~ representatives of 'LL' clades, SS120 and MIT9313, actually tolerate approximately 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)E,H), comparable to the representative HL clade, MED4 which also exhibited growth saturation at the same cumulative diel PUR of 1.0 x 10^6^ µmol photons m^-2^ d^-1^ (Figure \@ref(fig:PhotoperiodPurFitsPlots)A,B).
+Growth under lower O~2~ allowed MIT9313 to substantially increase its exploitation of higher diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).
 
@@
 marinus* SS120, a clade LLII/III ecotype found deep in the water column, and *P.
-marinus* MIT9313, a clade LLIV ecotype also found in deep oceans including OMZ, under a matrix of spectral, light level, photoperiod and oxygen conditions approximating present day and hypothetical future niches.
+marinus* MIT9313, a clade LLIV ecotype also found in deep oceans including OMZ, under a matrix of spectral waveband, light level, photoperiod and oxygen conditions approximating present day and hypothetical future niches.
 Low light levels in the blue spectral waveband prevail in deep ocean waters [@morelAvailableUsableStored1978; @holtropVibrationalModesWater2021], while solar incidence angle and light attenuation also progressively attenuate the photoperiod with depth beneath the ocean surface.
@@
 Delmont and Eren [@delmontLinkingPangenomesMetagenomes2018] did not analyze data from depths beyond the subsurface chlorophyll maximum layer, the layer in the water column where the chlorophyll *a* concentration peaks, nor did they report the [O~2~] at those depths.
-Our growth findings are also consistent with Figure\@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSII proteins annotated as MED4, clade HLI, at depths up to 200 meters with O~2~ of 15 µM.
+Our growth findings are also consistent with Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSII proteins annotated as MED4, clade HLI, at depths up to 200 meters with O~2~ of 15 µM.
 
@@
 [@lavinNovelLineagesProchlorococcus2010] show evidence of LLII/III ecotypes at varying depths from 20 to 30 m and from 75 to 200 µM O~2~ in the oxygen minimum zone (OMZ) of the tropical South Pacific Ocean, illustrating its tolerance of high light levels under low O~2~.
-SS120 has the potential to thrive in deep temperate zones, specifically during the spring, summer, and fall seasons when the duration of daylight exceeds 4 h, if O~2~ are near surface saturation of about 250 µM.
+SS120 has the potential to thrive in deep temperate zones, specifically during the spring, summer, and fall seasons when the duration of daylight exceeds 4 h, if [O~2~] are near surface saturation of about 250 µM.
 Under lower oxygen levels of 25 µM, SS120 can also potentially exploit a 4 h photoperiod in the blue waveband, and thus has the potential to inhabit a potential warmed, deep, temperate OMZ, during the winter season.
@@
 These results are supported by Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSI protein subunits annotated as derived from MIT9313 detected at depths \> 120 m, along with PSII subunits at depths from 50 m to 200 m in regions where O~2~ was 15 µM.
-The deep water environments typical for MIT 9313 are relatively nutrient rich, and *Prochlorococcus* take up and metabolize various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017; @munoz-marinProchlorococcusCanUse2013] and amino acids [@zubkovDepthRelatedAmino2004].
-In future work we aim to test whether MIT9313 is using photosynthesis to drive CO~2~ fixation in low O~2~ environments, or whether PSII generation of O~2~ acts as an electron sink for respiration, to generate using ATP for maintenance and to take up nutrients from the surroundings.
+The deep water environments typical for MIT9313 are relatively nutrient rich, and *Prochlorococcus* take up and metabolize various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017; @munoz-marinProchlorococcusCanUse2013] and amino acids [@zubkovDepthRelatedAmino2004].
+In future work we aim to test whether MIT9313 is using photosynthesis to drive CO~2~ fixation in low O~2~ environments, or whether PSII generation of O~2~ acts as an electron sink for respiration, using ATP for maintenance and to take up nutrients from the surroundings.
 Partensky *et al*.

### 2024-03-05 Code/Manuscript_O2.Rmd
Adedd Bagby citation re CO2 and O2

@@
 These results are supported by Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSI protein subunits annotated as derived from MIT9313 detected at depths \> 120 m, along with PSII subunits at depths from 50 m to 200 m in regions where O~2~ was 15 µM.
+Bagby and Chisholm [@bagbyResponseProchlorococcusVarying2015] suggest that O~2~ has a protective role in *Prochlorococcus* under lower carbon dioxide environments when carbon fixation is limited.
 The deep water environments typical for MIT9313 are relatively nutrient rich, and *Prochlorococcus* take up and metabolize various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017; @munoz-marinProchlorococcusCanUse2013] and amino acids [@zubkovDepthRelatedAmino2004].

### 2024-03-05 Code/Manuscript_O2.Rmd
Changed order of Tables in Supp to relect order of mention

--- 2024-03-05 Code/Manuscript_O2.Rmd
@@
 
-```{r MED4OverlayPlots, fig.cap = MED4OverlayPlots_cap, fig.height = 6, fig.width = 8, include = FALSE}
-
-MED4OverlayPlots_cap <- glue("**Normalized absorbance and Photosynthetically Usable Radiation for *Prochlorococcus marinus* MED4 grown under three emission wavebands.**",
-                       "**A.** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated PUR spectra (solid black line and shaded grey).",
-                       "**B.** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded red).",
-                       "**C.**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded blue).",
-
-                       "Actinic PAR (µmol photons m^-2^ s^-1^) and calculated PUR (µmol photons m^-2^ s^-1^) levels are indicated.",
-
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "MED4OverlayPlots.png"))
-
-```
-
-\newpage
-
-```{r SS120OverlayPlots, fig.cap = SS120OverlayPlots_cap, fig.height = 6, fig.width = 8, include = FALSE}
-
-SS120OverlayPlots_cap <- glue("**Normalized absorbance and Photosynthetically Usable Radiation for *Prochlorococcus marinus* SS120 grown under three emission wavebands.",
-                       "**A.** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated PUR spectra (solid black line and shaded grey).",
-                       "**B.** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded red).",
-                       "**C.**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded blue).",
-                       "Actinic PAR (µmol photons m^-2^ s^-1^) and calculated PUR (µmol photons m^-2^ s^-1^) levels are indicated.",
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "SS120OverlayPlots.png"))
-
-```
-
-\newpage
-
-```{r MIT9313OverlayPlots, fig.cap = MIT9313OverlayPlots_cap, fig.height = 6, fig.width = 8, include = FALSE}
-
-MIT9313OverlayPlots_cap <- glue("**Normalized absorbance and Photosynthetically Usable Radiation for *Prochlorococcus marinus* MIT9313 grown under three emission wavebands.**",
-                                "**A.** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated PUR spectra (solid black line and shaded grey).",
-                       "**B.** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded red).",
-                       "**C.**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded blue).",
-                       "Actinic PAR (µmol photons m^-2^ s^-1^) and calculated PUR (µmol photons m^-2^ s^-1^) levels are indicated.",
-
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "MIT9313OverlayPlots.png"))
-
-```
+\newpage
 
@@
 knitr::include_graphics(file.path(FiguresIn, "ProchlorococcusLightEnzymes.png"))
+
+```
+
+\newpage
+
+```{r ProchlorococcusEnzymeTable, echo = FALSE }
+
+readRDS(file.path(DataIn,"ProchlorococcusEnzymeTable.Rds")) %>% 
+  select(EnzymeName, EC, KO) %>% 
+  knitr::kable(.,
+             caption = "Enzymes shown in Figures \\@ref(fig:ProchlorococcusEnzymeKms),  \\@ref(fig:DNARepairFig) and \\@ref(fig:ProchlorococcusLightEnzymes) with their Enzyme Commission numbers (EC) and Kegg Orthology (KO).",
+            col.names =  c(
+                          "Enzyme Name",
+                          "EC",
+                          "Kegg Orthology")
+             )
 
@@
 
-```{r ProchlorococcusEnzymeTable, echo = FALSE }
-
-readRDS(file.path(DataIn,"ProchlorococcusEnzymeTable.Rds")) %>% 
-  select(EnzymeName, EC, KO) %>% 
-  knitr::kable(.,
-             caption = "Enzymes shown in Figures \\@ref(fig:ProchlorococcusEnzymeKms),  \\@ref(fig:DNARepairFig) and \\@ref(fig:ProchlorococcusLightEnzymes) with their Enzyme Commission numbers (EC) and Kegg Orthology (KO).",
-            col.names =  c(
-                          "Enzyme Name",
-                          "EC",
-                          "Kegg Orthology")
-             )
-
-```
-
 # Data availability  {.unnumbered}

### 2024-03-05 Code/Manuscript_O2.Rmd
Removed some extra FtsH citations

@@
 
-XXXMore TextXXX from Amanda & AuroraXXX
+XXX More Text XXX from Amanda & Aurora XXX
 Proteins derived from clade HLXXX ecotypes of *P.
@@
 Repair of photoinactivated PSII relies on the removal of damaged PsbA [@mannInvolvementFtsHHomologue2000; @adamFtsHProteasesChloroplasts2005], followed by reassembly with newly synthesized PsbA [@nixonRecentAdvancesUnderstanding2010].
-Degradation of PsbA is a rate-limiting step in recovery from photoinhibition [@kanervoD1ProteinDegradation1993], mediated largely by a heterohexamer of (FtsH1-FtsH2)~3~, a membrane-bound [@sacharzSubCellularLocation2015; @zakInitialStepsBiogenesis2001] metalloprotease  [(Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014).
-[@adamFtsHProteasesChloroplasts2005; @boehmSubunitOrganizationSynechocystis2012a; @nixonRecentAdvancesUnderstanding2010; @komendaExposedNTerminalTail2007] (Pisareva et al., 2007; Sacharz et al., 2015),  @mannInvolvementFtsHHomologue2000, (AMANDA REF from ALGATECH).
+Degradation of PsbA is a rate-limiting step in recovery from photoinhibition [@kanervoD1ProteinDegradation1993], mediated largely by a heterohexamer of (FtsH1-FtsH2)~3~, a membrane-bound [@sacharzSubCellularLocation2015; @zakInitialStepsBiogenesis2001] metalloprotease  [(Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014),  @boehmSubunitOrganizationSynechocystis2012a;  @komendaExposedNTerminalTail2007],  XXX (AMANDA REF from ALGATECH) XXX.
 

### 2024-03-05 Code/Manuscript_O2.Rmd
minor edit

@@
 [@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for growth under red light, for MED4, because red light provokes less photoinactivation of PSII, than equivalent levels of blue light.
-For distinct fits for different photoperiods refer to figure \@ref(fig:PhotoperiodPurFitsPlots)A,B and C.
+For distinct fits for different photoperiods refer to Figure \@ref(fig:PhotoperiodPurFitsPlots) A,B and C.
 
@@
 Under 25 µM O~2~, red light again generated more growth of SS120 per unit cumulative diel PUR, than did blue light, again consistent with lower cost of growth through lower photoinactivation under red light (Figure \@ref(fig:BluevsRedPurFitsPlots)E).
-For distinct fits for different photoperiods refer to figure \@ref(fig:PhotoperiodPurFitsPlots)D,E and F.
+For distinct fits for different photoperiods refer to Figure \@ref(fig:PhotoperiodPurFitsPlots) D,E and F.
 
@@
 Interestingly, this protective effect of red light disappears for MIT9313 growing under 2.5 µM O~2~, possibly because photoinactivation is strongly suppressed under this low [O~2~] (Figure \@ref(fig:BluevsRedPurFitsPlots)I).
-For distinct fits for different photoperiod fits refer to figure \@ref(fig:PhotoperiodPurFitsPlots)G,H and I.
+For distinct fits for different photoperiod fits refer to Figure \@ref(fig:PhotoperiodPurFitsPlots) G,H and I.
 

### 2024-03-05 Code/Manuscript_O2.Rmd
minor edit in fig caption

@@
 
-ProchlorococcusLightEnzymes_cap <- glue("***Prochlorococcus* Genes encoding enzymes activated or inhibited by light.**",
+ProchlorococcusLightEnzymes_cap <- glue("***Prochlorococcus* genes encoding enzymes activated or inhibited by light.**",
                          "The y-axis represents *Prochlorococcus marinus* strains.",

### 2024-03-05 Code/Plots_OceanProtein.Rmd
Renamed rmd OceanProteinPlots

--- 2024-03-04 Code/OceanProteinPlots.Rmd
@@
 
-poi <- poi |>
-  mutate(StrainAlpha = if_else(strain %in% AltStrainLabels, 1, 0.1))
+# poi <- poi |>
+#   mutate(StrainAlpha = if_else(strain %in% AltStrainLabels, 1, 0.1))
+`%notin%` <- negate(`%in%`)
 
@@
   ggplot() +
-  geom_point(aes(x = O2, y= depth, alpha = StrainAlpha)) +
+  geom_point(aes(x = O2, y= depth), data = . %>% filter(strain %notin% AltStrainLabels)) +
+  annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, alpha = 0.75, fill = "white") +
+  geom_point(aes(x = O2, y= depth), data = . %>% filter(strain %in% AltStrainLabels)) +
+  # geom_point(aes(x = O2, y= depth, alpha = StrainAlpha)) +
   scale_x_continuous(limits = c(0, 260)) +

### 2024-03-05 Code/Manuscript_O2.Rmd
Adedd acknowledgement Sarah Arthur
Changed P .marinus with *Prochlorococcus marinus* when starts sentence.

@@
 marinus* strains in clades LLV and LLVI also thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021; @lavinNovelLineagesProchlorococcus2010; @goerickeNovelNicheProchlorococcus2000; @garcia-robledoCrypticOxygenCycling2017; @johnsonEnergeticsGrowthKinetics1999].
-*P.
-marinus* LL ecotypes may indeed dominate the phytoplankton within OMZ [@lavinNovelLineagesProchlorococcus2010; @ulloaCyanobacteriumProchlorococcusHas2021; @partenskyProchlorococcusAdvantagesLimits2010], where they may be net O~2~ consumers [@partenskyComparisonPhotosyntheticPerformances2018].
+*Prochlorococcus marinus* LL ecotypes may indeed dominate the phytoplankton within OMZ [@lavinNovelLineagesProchlorococcus2010; @ulloaCyanobacteriumProchlorococcusHas2021; @partenskyProchlorococcusAdvantagesLimits2010], where they may be net O~2~ consumers [@partenskyComparisonPhotosyntheticPerformances2018].
 
@@
 
-*P. marinus* MED4, clade HLI, growth under 250 µM O~2~ increased with higher imposed PAR and longer photoperiods
+*Prochlorococcus marinus* MED4, clade HLI, growth under 250 µM O~2~ increased with higher imposed PAR and longer photoperiods
 (Figure \@ref(fig:MED4PAR)), across all spectral wavebands.
@@
 
-*P.
-marinus* SS120 clade LLII/III,  growth under 250 µM O~2~ increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^ peak PAR and across all spectral wavebands (Figure \@ref(fig:SS120PAR)).
+*Prochlorococcus marinus* SS120 clade LLII/III,  growth under 250 µM O~2~ increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^ peak PAR and across all spectral wavebands (Figure \@ref(fig:SS120PAR)).
 No growth was observed under any blue light photoperiods when exposed to peak PAR of 90 µmol photons m^-2^ s^-1^ or greater.
@@
 
-*P. marinus* MIT9313, clade LLIV, growth under 250 µM O~2~ increased with longer
+*Prochlorococcus marinus* MIT9313, clade LLIV, growth under 250 µM O~2~ increased with longer
 photoperiods, under low 30 µmol photons m^-2^ s^-1^ peak PAR, (Figure \@ref(fig:MIT9313PAR)).
@@
 Carlie Barnhill (Mount Allison Student) assisted with code for import of multicultivator growth data files.
+Sarah Arthur (Mount Allison Student) assisted with culturing and setting up Multicultivator runs.
 

### 2024-03-05 Code/Manuscript_O2.Rmd
caption wording

--- 2024-03-05 Code/Manuscript_O2.Rmd
@@
 LabeledMC_cap <- glue("**PSI MCMIX-OD Multicultivator.**",
-                      "Spectral wavebands and light levels are individually controlled for each culture tube.",
-                      "Real time Optical Density (OD) measurements eliminate intrusive subsampling of sterile cultures.",
+                      "Spectral waveband, light level and photoperiod are individually controlled for each culture tube.",
+                      "Real time Optical Density (OD) measurements eliminate intrusive subsampling of cultures.",
                       "The temperature of culture tubes are collectively controlled via heating or cooling of the aquarium water.",
@@
 knitr::kable(MaxGrowthTable,
-             caption = "The maximum growth rate, µ~max~ (d^-1^) in each O~2~ experiment for each strain. The corresponding photoperiod, PAR level and spectral waveband are indicated.",
+             caption = "The maximum growth rate, µ~max~ (d^-1^) achieved for each O~2~ experiment, for each strain, with the corresponding photoperiod, PAR level and spectral waveband.",
             col.names =  c("Strain",
@@
 To Be Entered through PLoSONe system and deleted here
-Czech Academy of Science visiting fellowship supporting DAC work at AlgaTech (OP)
+Czech Academy of Science (OP) visiting fellowship supporting DAC work at AlgaTech
 Canada Research Chair in Phytoplankton Ecophysiology (DAC)

### 2024-03-06 Code/Plots_GAM.Rmd

--- 2024-02-05 Code/ManuscriptGAM.Rmd
@@
 library(faraway) # LM package
+library(grid)
 library(gridExtra)
@@
     #facet_grid(cols = vars(O2_uM)) +
-    labs(title = bquote("  C.   " ~ .(GamStrain) ~ '    2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
+    labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
     theme_classic() +
@@
     #facet_grid(cols = vars(O2_uM)) +
-    labs(title = bquote("  B.   " ~ .(GamStrain) ~ '    25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
+    labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
    theme_classic() +
@@
     #facet_grid(cols = vars(O2_uM)) +
-    labs(title = bquote("  A.   " ~ .(GamStrain) ~ '    250 µM' ~ "[" ~ O[2]~ "]")) +  #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+    labs(title = bquote("A.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +  #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
     theme_classic() +
@@
 (g_dummy1 <- ggplot(subset(HyperChlPlotLow, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
++ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
   limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
@@
                      c(2, 2, 2, 2, 5),
-                     c(2, 2, 2, 2, 5),
+                     c(2, 2, 2, 2, 5)
+                     ,
                      c(1, 1, 1, 1, 4),
@@
 
-p3 <- grid.arrange(ContourLowO2 + theme(legend.position = 'none'), ContourIntO2 + theme(legend.position = 'none'), ContourHighO2 + theme(legend.position = 'none'), legend1, legend2, legend3, layout_matrix = LayoutNiche)
+p3_Red <- grid.arrange(ContourLowO2 + theme(legend.position = 'none'), ContourIntO2 + theme(legend.position = 'none'), ContourHighO2 + theme(legend.position = 'none'), legend1, legend2, legend3, layout_matrix = LayoutNiche)
 
@@
 #  for thesis
-  # ggsave(file = file.path(paste(FP1, "Plots", sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3,  height = 10, width = 6)
+  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Red,  height = 10, width = 6 )
 
 # for presentation
-  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3,  height = 7.6, width = 6)
+  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Red,  height = 7.6, width = 6)
 
@@
 
-# Plot blue light GAM, must change GAMStrain and rerun chunk to generate plot of each strain
+# Plot blue light GAM, must change GAMStrain and rerun chunk to generate plot for each strain
 ``` {r GAM Plot Blue WL}
@@
     #facet_grid(cols = vars(O2_uM)) +
-    labs(title = bquote("  C.   " ~ .(GamStrain) ~ '    2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
+    labs(title = bquote("F.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
     theme_classic() +
@@
           axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35)))# change to 25 and 30 for thesis
-          # axis.title.y = element_blank()))
+           axis.title.y = element_text(size=35),
+          axis.text.y = element_blank(),
+          axis.line.y = element_blank(),
+          axis.ticks.y = element_blank()))
 
@@
     #facet_grid(cols = vars(O2_uM)) +
-    labs(title = bquote("  B.   " ~ .(GamStrain) ~ '    25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
+    labs(title = bquote("E.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
    theme_classic() +
@@
           axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=23)))# change to 25 and 30 for thesis
-          # axis.title.y = element_blank()))
+           axis.title.y = element_text(size=23),
+          axis.text.y = element_blank(),
+          axis.line.y = element_blank(),
+          axis.ticks.y = element_blank()))
 
@@
     #facet_grid(cols = vars(O2_uM)) +
-    labs(title = bquote("  A.   " ~ .(GamStrain) ~ '    250 µM' ~ "[" ~ O[2]~ "]")) +  #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+    labs(title = bquote("D.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +  #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
     theme_classic() +
@@
 
-p3 <- grid.arrange(ContourLowO2 + theme(legend.position = 'none'), ContourIntO2 + theme(legend.position = 'none'), ContourHighO2 + theme(legend.position = 'none'), legend1, legend2, legend3, layout_matrix = LayoutNiche)
+p3_Blue <- grid.arrange(ContourLowO2 + theme(legend.position = 'none'), ContourIntO2 + theme(legend.position = 'none'), ContourHighO2 + theme(legend.position = 'none'), legend1, legend2, legend3, layout_matrix = LayoutNiche)
 
@@
 #  for thesis
-  # ggsave(file = file.path(paste(FP1, "Plots", sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3,  height = 10, width = 6)
+  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Blue,  height = 10, width = 6)
 
 # for presentation
-  ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3,  height = 7.6, width = 6)
+  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Blue,  height = 7.6, width = 6)
 
@@
 
-``` {r GAM PUR comparison}
+```{r combine red and blue light GAM plots}
 
-GamWL = c("deltaOD") #deltaOD OD720
-Proxy= "[~Chl]" #~Chl ~Cells 
-GamParaMod = "Lmu"
-#GamVar = c("450")# 450 660 WW
-GamStrain = "MED4" # MIT9313 MED4 SS120
-# ErrorTol = 20
-OxyLev = 250
+CombinedGAM <- plot_grid(p3_Red, p3_Blue)
 
-################ check smooth terms #https://fromthebottomoftheheap.net/2017/12/14/difference-splines-ii/
-#https://stackoverflow.com/questions/70922283/gam-smooths-interaction-differences-calculate-p-value-using-mgcv-and-gratia-0
-PurGAM <- ComGrowthFits %>%
-  mutate(ordPP = ordered(Photoperiod, levels = c('4', '8', '12', '16')),
-         Lmu_seFlag = case_when(se/estimate*100 < ErrorTolGrowth ~ 1, #filters faulty data where Standarderror larger +/- Errortolerance
-                         FALSE ~ 0)) %>%
-  ungroup() %>%
-  dplyr::filter(
-                Photoperiod != 4, 
-                Lmu_seFlag == 1,
-                term %in% GamParaMod,
-                Wavelength %in% GamWL,
-                Strain %in% GamStrain,
-                O2_uM %in% OxyLev) %>%
-  mutate(estimate = estimate*24,
-         se = se*24)
+x.grob <- textGrob("Photoperiod (h)", 
+                   gp = gpar(fontface="bold", fontsize = 20))
 
-m_PUR_gam <- gamm(estimate ~ s(PURPhotonDose_day, k = -1) + s(PURPhotonDose_day, by = ordPP), random=list(WL=~1), data = PurGAM, method = "REML")
-m_PUR_gam <- m_PUR_gam$gam
+y.grob <- textGrob("PAR (µmol photons"~ m^-2~ ~s^-1~ ")", 
+                   gp = gpar(fontface="bold", fontsize = 20), rot = 90)
 
-plot(m_PUR_gam, shade = TRUE, pages = 1, scale = 0, seWithMean = TRUE)
-summary(m_PUR_gam)
+#add to plot
 
-# zoom_Chl_TreatCheck <- zoom_log %>%
-#   filter(Group != "ES") %>%
-#   mutate(ordGroup = ordered(Group, levels = c('ES', 'Fish', 'noFish')))
-# 
-# m_Chl_Treatgam <- gamm(Chla_ugL ~ Group +  s(DayFrFrst) +s(DayFrFrst, by = ordGroup), random=list(SampleYear=~1), data = zoom_Chl_TreatCheck, method = "REML")
-# m_Chl_Treatgam <- m_Chl_Treatgam$gam
-# 
-# plot(m_Chl_Treatgam, shade = TRUE, pages = 1, scale = 0, seWithMean = TRUE)
-# summary(m_Chl_Treatgam)
-
-# PurGAM <- ComGrowthFits %>% 
-#   ungroup() %>%
-#   dplyr::filter(Lmu_seFlag == 1, 
-#                 term %in% GamParaMod, 
-#                 Wavelength %in% GamWL,
-#                 strain %in% GamStrain) %>%
-#   mutate(estimate = estimate*24,
-#          se = se*24) %>%
-#   group_by(Strain, Wavelength, O2_uM, Photoperiod) %>%
-#   nest() %>%
-#   dplyr::arrange(Strain, Wavelength, O2_uM) %>%
-#   mutate(GamModel = map(data, ~possibGAM(estimate ~ s(PUR_day, k = 3) + s(Photoperiod, k = 3) + ti(Photoperiod, Par_ue, k = 3),  data = .x,
-#                                     family = "gaussian"(link = "log"), 
-#                                     method = "REML")),
-#          predicted = map(GamModel, ~possibPRED(.x, newdata = PAR_Photoperiod_Model_predi, type = 'response', se.fit=TRUE)),
-#          augmented = map(GamModel, ~augment(.x))
-#          )
-# 
-# PicoGAM_Pred <- PicoGAM %>%
-#   dplyr::select(Strain, Wavelength, WL, O2_uM, predicted) %>%
-#   dplyr::filter(predicted != "NULL") %>%
-#   rowwise() %>%
-#   mutate(db = list(cbind(predicted, PAR_Photoperiod_Model_predi))) %>%
-#   dplyr::select(-predicted) %>%
-#   unnest(col = db) %>%
-#   group_by(Strain, Wavelength, WL, O2_uM) %>%
-#   dplyr::filter(fit < 1) %>% #with two expections, growth rates were never higher than 0.06; GAM model creates some unrealistic high growth rates due to low data availability
-#   mutate(
-#     fit = case_when(se.fit/fit*100 < ErrorTol ~ fit*1, #filters faulty data where Standarderror larger +/- Errortolerance
-#                          FALSE ~ fit)
-#   # ,fit = case_when(fit >= quantile(fit, 0.75, na.rm = TRUE) ~ fit*1, #leaves only top-10%, that means fastest growth rates in the dataframe
-#   #                 FALSE ~ fit)
-#   )
+LabelledCombinedGam <- grid.arrange(arrangeGrob(CombinedGAM, left = y.grob, bottom = x.grob))
 
 ```
+
+```{r save png}
+ ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = LabelledCombinedGam,  height = 10, width = 10)
+```

### 2024-03-06 Code/Manuscript_O2.Rmd
minor edits to readme and manuscript

@@
 
+XXX DOI pending from BOREALIS? or DRYAD? XXX
+
 # Acknowledgements  {.unnumbered}
@@
 New Brunswick Foundation for Innovation (DAC)
-Rice Graduate Fellowship (MS)
+Rice Graduate Fellowship 2021 and 2022 (MS)
 

### 2024-03-06 Code/Manuscript_O2.Rmd
fixed fig caption

@@
 CladeProchloroPhotosynthDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* photosynthesis complexes.**", 
-                       "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
+                       "Protein detections (annotated as solid grey circles) are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
                        "Rows separate data annotated as from *Prochlorococcus* clades: HLI (*P.
@@
 CladeProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein metabolism complexes.**", 
-                       "Protein detections are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
+                       "Protein detections (annotated as solid grey circles) are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
                        "Rows separate data annotated as from *Prochlorococcus* clades: HLI (*P.

### 2024-03-06 Code/Import_MCData.Rmd
Uncommented chunk
removed from library load 'data.table' -redundant

@@
 library(zoo)
-library(data.table)
 library(photobiologyWavebands)
@@
 
-TargetFile <- "20220824_PICO_MC257_RUN86.csv"
+TargetFile <- "20220701_PICO_MCMIX006_RUN80.csv"
 
@@
 
-TargetDataMeta <- TargetDataMeta %>%
-mutate(OD680 = if_else(Tube == 5, 0.005, OD680),
-       OD720 = if_else(Tube == 5, 0.003, OD720))
+# TargetDataMeta <- TargetDataMeta %>%
+# mutate(OD680 = if_else(Tube == 5, 0.005, OD680),
+#        OD720 = if_else(Tube == 5, 0.003, OD720))
 
@@
 
+TargetDataMetaFilter
+
 ```

### 2024-03-06 Code/Import_MCData.Rmd
minor edit

@@
 widely, aberrant when a bubble interrupts the measurement, and if the
-MultiCultivator is running properly these bubble aberration events are
+Multicultivator is running properly these bubble aberration events are
 rare.

### 2024-03-06 Code/Plots_PURFits.Rmd
Removed redundant packages, removed a lot of commented chunks

--- 2024-03-04 Code/ManuscriptPURFits.Rmd
@@
 library(lubridate)
-#library(stringr)
 library(broom)
@@
 library(zoo)
-#library(AICcmodavg)
-# library(RColorBrewer)
 library(grid)
 library(gridExtra)
-# library(bookdown)
-# library(glue)
 library(egg)
-# library(ggspectra)
-# library(photobiologyWavebands)
-# library(photobiology)
-#library(ggpubr)
-#library(ggh4x)
-library(cowplot)
-#library(jmv)
-# library(pgirmess) # for the post hoc kruskalalmc test
-#library(rcompanion) # for Scheirer-Ray-Hare non-parametric 2 way test, derived from Kruskal-Wallis
-# library(FSA) # for Dunn test
-#library(dunn.test)
-# library(rstatix)
+library(photobiology)
 library(minpack.lm)
@@
 ```{r set colours and shapes}
-
-library(photobiology)
 
@@
 
-# This figure is a 3 panel figure faceted by strain in columns and O2 in rows. Too stretched.
 # Fits are added that are not sig different individually,  next add fits that were sig different dynamically
-```{r Plot fits, fig.height= 20, fig.width= 20 }
-
-# scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
-# 
-# 
-# MED4PURFITPlot <- AllFitsCombined |>
-#     filter(Strain == "MED4") |>
-#   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
-#   mutate(PhotoperiodLabelTitle = "Photoperiod (h)",
-#          OxygenLabel = "Oxygen Concentration (µM)",
-#          Photoperiod = factor(Data_all_Photoperiod, levels = c(16, 12, 8, 4)),
-#          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-#          WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
-#   ggplot() +
-#   geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 4, alpha = 1.0) +
-#     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
-#   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
-#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
-#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
-#  geom_text(aes(x = 1000, y = 0.75, label= "A     MED4 HLI"), data = . %>% filter(O2_uM == 250, Strain == "MED4"), size = 4, hjust = 0, vjust = 0) +
-#   scale_x_continuous(label=scientific_10) +
-#    scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
-#   scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
-#   scale_linetype_manual(values = MyLineTypes, labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
-#    scale_shape_manual(values = PhotoperiodShapes)  +
-#   ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
-#                     labeller = labeller(Strain = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
-#  guides(linetype = guide_legend(nrow = 1),
-#         fill = "none",
-#         color = guide_legend(nrow = 1)) +
-#  guides(shape = guide_legend(nrow = 1)) +
-#   theme_bw() +
-#    theme( strip.text = element_text(size = 10),
-#         axis.title.y = element_blank(),
-#         axis.title.x.bottom = element_blank(),
-#         axis.text.x = element_blank(),
-#         axis.text.y = element_text(size = 9, color = "black", angle = 0, hjust = 1.0),
-#         strip.background=element_rect(color="grey87", fill = "grey82"),
-#         # strip.background=element_rect(fill = "white"),
-#         legend.key.size = unit(1, 'cm'), #change legend key size
-#         legend.key.height = unit(1, 'cm'), #change legend key height
-#         legend.key.width = unit(0.5, 'cm'), #change legend key width
-#         legend.title =  element_text(size = 15),  #change legend title font size
-#         legend.text = element_text(size = 15),   #change legend text font size
-#         legend.position = "top") +
-#   labs( shape = "Photoperiod (h)",
-#         color = "Growth Waveband (nm)",
-#        linetype = "Photoperiod lines"
-#       )
-# MED4PURFITPlot
-# 
-# SS120PURFITPlot <- AllFitsCombined |>
-#     filter(Strain == "SS120") |>
-#   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
-#   mutate(PhotoperiodLabelTitle = "Photoperiod (h)",
-#          OxygenLabel = "Oxygen Concentration (µM)",
-#          Photoperiod = factor(Data_all_Photoperiod, levels = c(16, 12, 8, 4)),
-#          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-#          WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
-#   ggplot() +
-#   geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 4, alpha = 1.0) +
-#     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
-#   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) + 
-#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
-#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(Strain == "SS120")) +
-#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
-#  geom_text(aes(x = 1000, y = 0.75, label= "B     SS120 LLII/III"), data = . %>% filter(O2_uM == 250, Strain == "SS120"), size = 4, hjust = 0, vjust = 0) +
-#   scale_x_continuous(label=scientific_10) +
-#    scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
-#   scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
-#   scale_linetype_manual(values = c("dotdash","dashed", "dotted", "aa"), labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
-#    scale_shape_manual(values = PhotoperiodShapes)  +
-#   ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
-#                     labeller = labeller(Strain = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
-#  # guides(linetype = guide_legend(nrow = 4),
-#  #        fill = "none",
-#  #        colour = guide_legend(nrow = 4)) +
-#  # guides(shape = guide_legend(nrow = 4)) +
-#   theme_bw() +
-#    theme( strip.text = element_text(size = 10),
-#         axis.title.y = element_blank(),
-#         axis.title.x.bottom = element_blank(),
-#         axis.text.x = element_blank(),
-#         axis.text.y = element_text(size = 10, color = "black", angle = 0, hjust = 1.0),
-#         strip.background=element_rect(color="grey87", fill = "grey82"),
-#         # strip.background=element_rect(fill = "white"),
-#         legend.key.size = unit(1, 'cm'), #change legend key size
-#         legend.key.height = unit(1, 'cm'), #change legend key height
-#         legend.key.width = unit(0.5, 'cm'), #change legend key width
-#         # legend.title =  element_text(size = 20),  #change legend title font size
-#         # legend.text = element_text(size = 20),   #change legend text font size
-#         legend.position = "none") +
-#   labs( shape = "Photoperiod (h)",
-#         color = "Growth Waveband (nm)",
-#        linetype = "Photoperiod (h) "
-#       )
-#    SS120PURFITPlot
-# 
-# MIT9313PURFITPlot <- AllFitsCombined |>
-#    filter(Strain == "MIT9313") |>
-#   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
-#   mutate(PhotoperiodLabelTitle = "Photoperiod (h)",
-#          OxygenLabel = "Oxygen Concentration (µM)",
-#          Photoperiod = factor(Data_all_Photoperiod, levels = c(16, 12, 8, 4)),
-#          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-#          WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
-#   ggplot() +
-#   geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 4, alpha = 1.0) +
-#     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
-#   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) + 
-#   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotdash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +
-#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
-#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM == 25, Strain == "MIT9313")) +
-#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +
-#   labs(x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
-#  geom_text(aes(x = 1000, y = 0.75, label= "C     MIT9313 LLIV"), data = . %>% filter(O2_uM == 250, Strain == "MIT9313"), size = 4, hjust = 0, vjust = 0) +
-#   scale_x_continuous(breaks = c(0, 1000000,2000000, 3000000, 4000000),label=scientific_10, limits = c (-100, 5000000)) +
-#    scale_y_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
-#   scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
-#   scale_linetype_manual(values = c("solid","dotdash","dashed", "dotted", "aa"), labels = c("Pooled","16 hr", "12 hr", "8 hr", "4 hr")) +
-#    scale_shape_manual(values = PhotoperiodShapes)  +
-#   ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
-#                     labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
-#  guides(linetype = guide_legend(nrow = 4),
-#         fill = "none",
-#         colour = guide_legend(nrow = 4)) +
-#  guides(shape = guide_legend(nrow = 4)) +
-#   theme_bw() +
-#    theme( strip.text = element_text(size = 10),
-#           axis.title.y = element_blank(),
-#           axis.title.x = element_text(size = 15, color = "black"),
-#           axis.text.x = element_text(size = 10, color = "black", angle = 0, hjust = 1.0),
-#           axis.text.y = element_text(size = 10, color = "black", angle = 0, hjust = 1.0),
-#         strip.background=element_rect(color="grey87", fill = "grey82"),
-#         # strip.background=element_rect(fill = "white"),
-#         legend.key.size = unit(1, 'cm'), #change legend key size
-#         legend.key.height = unit(1, 'cm'), #change legend key height
-#         legend.key.width = unit(0.5, 'cm'), #change legend key width
-#         # legend.title =  element_text(size = 20),  #change legend title font size
-#         # legend.text = element_text(size = 20),   #change legend text font size
-#         legend.position = "none") +
-#   labs( shape = "Photoperiod (h)",
-#         color = "Growth Waveband (nm)",
-#        linetype = "Photoperiod (h) "
-#       )
-# MIT9313PURFITPlot
-
-```
-
-# Combine the 3 strains into 1 plot 
-```{r combine plots}
-
-# PhotoperiodPurFitsPlots <- plot_grid(MED4PURFITPlot, SS120PURFITPlot, MIT9313PURFITPlot, ncol = 1)
-# 
-# #create common x and y labels
-# y.grob <- textGrob("Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")",
-#                    gp = gpar(col="black", fontsize = 15), rot = 90)
-# 
-# #add to plot
-# PhotoperiodPurFitsPlots <- grid.arrange(arrangeGrob(PhotoperiodPurFitsPlots, left = y.grob))
-
-```
-
 ```{r Pur plot strain faceted in columns, fig.height=10, fig.width=10}
@@
 
-# This labels each pane with a letter but turns of the dacet labels
-# PhotoperiodPurFitsPlots <- tag_facet(PhotoperiodPurFitsPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
-# 
-# PhotoperiodPurFitsPlots
 ```
@@
 scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
-
-# AllFitsCombinedWL |>
-#   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
-#   mutate(PhotoperiodLabelTitle = "Photoperiod (h)",
-#          OxygenLabel = "Oxygen Concentration (µM)",
-#          Photoperiod = factor(Data_all_Photoperiod, levels = c(16, 12, 8, 4)),
-#          O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-#          WL = factor(Data_all_WL, levels = c("WW", 660, 450)),
-#          Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
-#   ggplot() +
-#   geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.7) +
-#     geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.0, alpha = 0.5) +
-#   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
-#    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_450) %>%  filter(O2_uM == 2.5, Strain == "MED4",  WL == 450)) +
-#   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MED4", WL == 660))+
-#     geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MED4", WL == "WW")) +
-#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) +
-#    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_450) %>%  filter(Strain == "SS120", O2_uM != 25, WL == 450)) +
-#  geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "SS120", O2_uM != 250, WL == "WW")) +
-#    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.0, alpha = 0.3, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) +
-#   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = . %>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM != 250, WL == 660))+
-#   geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6,  data = . %>% unnest(Predict_WW) %>%  filter(Strain == "MIT9313", O2_uM == 2.5, WL == "WW")) +
-#  labs(title = "Anova fit comparisons of WL to pooled", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
-#   scale_x_continuous(label=scientific_10) +
-#   scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
-#   scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
-#   # scale_linetype_manual(values = MyLineTypes, labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
-#   scale_shape_manual(values = PhotoperiodShapes)  +
-#   ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), cols = vars(Strain), 
-#                     labeller = labeller(Strain = label_value, O2_uM = label_value, OxygenLabel = label_value)) +
-#  guides(linetype = guide_legend(nrow = 1),
-#         fill = "none",
-#         color = guide_legend(nrow = 1)) +
-#  guides(shape = guide_legend(nrow = 1)) +
-#   theme_bw() +
-#    theme( strip.text = element_text(size = 25),
-#         axis.title.y = element_text(color = "black", size = 30,  hjust = 0.40),
-#         axis.title.x = element_text(color = "black", size = 30),
-#         axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
-#         axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
-#         # strip.background=element_rect(color="grey87", fill = "grey82"),
-#         # strip.background=element_rect(fill = "white"), 
-#         legend.key.size = unit(0.1, 'cm'), #change legend key size
-#         legend.key.height = unit(0.1, 'cm'), #change legend key height
-#         legend.key.width = unit(0.1, 'cm'), #change legend key width
-#         legend.title =  element_text(size = 25),  #change legend title font size
-#         legend.text = element_text(size = 25),   #change legend text font size
-#         legend.position = "top") +
-#   labs( shape = "Photoperiod (h)",
-#         color = "Growth Waveband (nm)",
-#        linetype = "Photoperiod lines"
-#       )
 

### 2024-03-06 Code/Import_MCData.Rmd
Put data.table back in. I don't think it is redundant
New file path to Culture Catalog

@@
 library(broom)
+library(data.table)
 library(zoo)
@@
 
-CultureCatalog <- readRDS(file = file.path("..", "Data","CultureCatalog.Rds"))
+CultureCatalog <- readRDS(file = file.path("..", "Data",  "RawData","CultureCatalog.Rds"))
 

### 2024-03-06 Code/Import_MCData.Rmd
Annotated some chunks. Deleted some commented codes.

@@
 Project <- "PICO"
+
+# Multiculti data files are too large to upload in a single .zip so uploaded 3 .zipped folders. Uncomment the 'DataIn' line with the folder name containing the intended files for import.   
  # DataIn <- file.path("..", "Data", "RawData", "MultiCultiData1.zip")
@@
 ```{r set colours}
+# Set colour codes for each WL of the Multicultivator. These colours are matched to WL using the Photobiology package. Colour codes used for visualization of spectral settings used in Muticulti run.
+
 MyWavelengths = c(405, 450, 470, 530, 620, 660, 730, "WW")
 MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(450), w_length2rgb(470), w_length2rgb(530),            w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black"))
-
-# MyWavelengths = c(450, 530, 660, "WW")
-# MCMIXColours = c(w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "black")
 
@@
 TargetData <- TargetData %>%
-  # filter(key != "thermo.temperature",
-  #        key !="thermo.thermo-reg",
-  #        key != "mc-airpump.airpump") %>%
   filter(str_detect(key, "od-720|od-680|actinic-lights.light"))
@@
   filter(grepl("od-", key)) %>%
-  #filter(grepl("od-sensors-", key)) %>%
   ggplot(data = .) +
   geom_point(aes(x = time, y = value, colour = as.factor(str_detect(key, "680"))), size = 0.5) +
-  #scale_x_continuous(breaks=seq(0, 800, by = 125)) + 
-  #coord_cartesian(xlim = c(-5, 800)) +
   geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
@@
 
-# "actinic-lights.light"
-
 #rm(TargetDataMeta)
@@
   geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
-  #geom_point(aes(x = time, y = Actinic_par/1000),  colour = "orange", size = 0.0001) +
- # geom_point(aes(x = time, y = IsMovAvgOutlier680)) +
-#scale_x_continuous(limits = c(0,100))+
-  #scale_x_continuous(breaks=seq(0, 800, by = 125)) +
-  #coord_cartesian(xlim = c(-10, 800)) +
   scale_colour_manual(values = MCMIXColours) +

### 2024-03-07 Code/Manuscript_O2.Rmd
minor edits

@@
 library(ggpubr)
-
 library(png)
@@
 The clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined as High-Light (HL) or Low-Light (LL).
-Of at least 12 known *Prochlorococcus* genetic clades only 5 to date have cultured representatives; HLI, HLII, LLI, LLII/III and LIV [@billerProchlorococcusStructureFunction2015].
+Only 5 out of 12 known *Prochlorococcus* genetic clades have cultured representatives to date; HLI, HLII, LLI, LLII/III and LIV [@billerProchlorococcusStructureFunction2015].
 Current niches of *P.
@@
 HL clades are more recently branching lineages, with reduced genome sizes in comparison to LL clades.
-High-Light clades are typically dominant picophytoplankters in near-surface, oligotrophic waters, characterized by high light levels.
-Clade HLI, represented by cultured strain MED4, is adapted to higher iron, and lower temperatures, and originated from 5 m depth in the Mediterranean Sea [@partenskyProchlorococcusMarinePhotosynthetic1999].
-Clade HLII, adapted to higher iron, and higher temperatures, is the most abundant *P.
+High-Light clades are typically dominant picophytoplankters in near-surface, oligotrophic waters, characterized by high light levels and subdivided into clades based on iron adaptation [@johnsonNichePartitioningProchlorococcus2006; @zinserInfluenceLightTemperature2007; @kentParallelPhylogeographyProchlorococcus2019].
+Clade HLI, represented by cultured strain MED4, is adapted to high iron, and low temperatures, and originated from 5 m depth in the Mediterranean Sea [@partenskyProchlorococcusMarinePhotosynthetic1999].
+Clade HLII, adapted to high iron, and high temperatures, is the most abundant *P.
 marinus* clade in the North Atlantic and North Pacific Oceans, often constituting over 90% of the total population [@partenskyProchlorococcusMarinePhotosynthetic1999], and are most numerous around 50 m depth [@partenskyProchlorococcusMarinePhotosynthetic1999].
-Clade HLIII/IV is adapted to lower iron [@kentParallelPhylogeographyProchlorococcus2019; @johnsonNichePartitioningProchlorococcus2006; @zinserInfluenceLightTemperature2007].
+Clade HLIII/IV is adapted to low iron [@kentParallelPhylogeographyProchlorococcus2019; @johnsonNichePartitioningProchlorococcus2006; @zinserInfluenceLightTemperature2007].
 
@@
 *Prochlorococcus marinus* SS120, a clade LLII/III strain, was isolated from the Sargasso Sea at a depth of 120 m, while *P.
-marinus* MIT9313, a clade LLIV strain, was isolated from the North Atlantic Gulf Stream at a depth of 135 m.
+marinus* MIT9313, a clade LLIV strain, was isolated from the North Atlantic Gulf Stream at a depth of 135 m [@moorePhotophysiologyMarineCyanobacterium1999].
 At these depths, light attenuation and spectral shifts occur, resulting in low blue light, while [O~2~] varies from near-surface saturation levels to decreased concentrations, but does not necessarily decrease systematically with depth [@billheimerOxygenSeasonalityUtilization2021].
@@
 
-PAR of 180, 90 or 30 µmol photons m^-2^ s^-1^, and spectral wavebands (white LED full spectrum, 660 nm, and 450 nm) were chosen to approximate light
+PAR of 180, 90 or 30 µmol photons m^-2^ s^-1^, and spectral wavebands (white LED full spectrum, 660 nm (red light), and 450 nm (blue light)) were chosen to approximate light
 levels and spectral colours spanning the vertical ocean water column, from near-surface to the lower euphotic zone depths.

### 2024-03-07 Code/Manuscript_O2.Rmd
minor edits

@@
 The path length of the internally reflective cavity of the Olis spectrophotometer was corrected to a 1 cm path length using the Javorfi correction method [@javorfiQuantitativeSpectrophotometryUsing2006] on PRO 99 media subtracted whole cell absorbance spectra.
-The blank-corrected whole cell absorbance spectra were normalized to the absorbance maximum of divinyl chlorophyll *a* (Chl a~2~), determined for each spectra, falling between 400 nm and 460 nm.
-
-An integrated weighting equation \@ref(eq:WeightedPUR) [@morelAvailableUsableStored1978] was used to determine the weighted PUR spectrum P(λ); where A(λ) is the blank subtracted, Chl a~2~ peak normalized whole cell absorbance spectrum for each *P.
+The blank-corrected whole cell absorbance spectra were normalized to the absorbance maximum of divinyl chlorophyll *a* (Chl *a*~2~), determined for each spectra, falling between 400 nm and 460 nm.
+
+An integrated weighting equation \@ref(eq:WeightedPUR) [@morelAvailableUsableStored1978] was used to determine the weighted PUR spectrum P(λ); where A(λ) is the blank subtracted, Chl *a*~2~ peak normalized whole cell absorbance spectrum for each *P.
 marinus* ecotype, over 400 nm to 700 nm, A(λ); and E(λ) is the peak normalized emission spectrum of the imposed LED growth light, over 400 nm to 700 nm.
@@
 Malmstrom *et al*.
-attributes NATL2A tolerance to short exposures of high light to the presence of the genes encoding photolyase, a gene found in HL clades.
+[@malmstromTemporalDynamicsProchlorococcus2010] attributes NATL2A tolerance to short exposures of high light to the presence of the genes encoding photolyase, a gene found in HL clades.
 The presence of deoxyribodipyrimidine photolyase and absence of DNA ligase (ATP) supports why NATL2A tolerates limited exposure to high light and why NATL2A is unable to fully repair damaged DNA.

### 2024-03-07 Code/Manuscript_O2.Rmd
Fixed figure cap for OPP figures stating what grey and black mean more clearly

@@
                        "Rows separate data annotated as from *Prochlorococcus* clades: HLI (*P.
-marinus* MED4 annotated with solid black circles), LLI (*P.
-marinus* NATL2A annotated with solid black circles), LLII/III (*P.
-marinus* SS120 annotated with solid black circles) and LLIV (*P.
-marinus* MIT9313 annotated with solid black circles).",
+marinus* MED4 protein detection annotated as solid black circles), LLI (*P.
+marinus* NATL2A protein detection annotated as solid black circles), LLII/III (*P.
+marinus* SS120 protein detection annotated as solid black circles) and LLIV (*P.
+marinus* MIT9313 protein detection annotated as solid black circles).",
                        "Columns show detections of proteins annotated as  Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
@@
 In contrast, under red light and 250 µM O~2~ MIT9313 grows faster while exploiting higher peak PAR and longer photoperiods.
-Figure \@ref(fig:MIT9313GAM)E shows that MIT9313can exploit all blue PAR levels and most photoperiods with 90^th^ percentile of fastest growth rate between 30 to 100 µmol photons m^-2^ s^-1^ PAR.F igure \@ref(fig:MIT9313GAM)F shows that MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 4 and 8 h and peak blue PAR between 50 to 100 µmol photons m^-2^ s^-1^ PAR.
+Figure \@ref(fig:MIT9313GAM)E shows that MIT9313can exploit all blue PAR levels and most photoperiods with 90^th^ percentile of fastest growth rate between 30 to 100 µmol photons m^-2^ s^-1^ PAR.
+Figure \@ref(fig:MIT9313GAM)F shows that MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 4 and 8 h and peak blue PAR between 50 to 100 µmol photons m^-2^ s^-1^ PAR.
 Thus the designation of MIT9313 as a LL clade is dependent upon [O~2~] and light spectra.
@@
                        "Rows separate data annotated as from *Prochlorococcus* clades: HLI (*P.
-marinus* MED4 annotated with solid black circles), LLI (*P.
-marinus* NATL2A annotated with solid black circles), LLII/III (*P.
-marinus* SS120 annotated with solid black circles) and LLIV (*P.
-marinus* MIT9313 annotated with solid black circles).",
+marinus* MED4 protein detection annotated as solid black circles), LLI (*P.
+marinus* NATL2A protein detection annotated as solid black circles), LLII/III (*P.
+marinus* SS120 protein detection annotated as solid black circles) and LLIV (*P.
+marinus* MIT9313 protein detection annotated as solid black circles).",
                        "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome.",

### 2024-03-07 Code/Manuscript_O2.Rmd
minor edits
fixed a citation

@@
 *Prochlorococcus marinus* clades are nonetheless found in environments beyond their optimal habitats.
-HL clades inhabit depths overlapping with LL ecotypes [@westNichePartitioningProchlorococcusPopulationsStratified1999; @zinserInfluenceLightTemperature2007; @delmontLinkingPangenomesMetagenomes2018], while LL clades can occupy regions in OMZ at depths shallower than 40 m [@lavinNovelLineagesProchlorococcus2010], exploiting ambient light levels above what LL clades were thought to tolerate.
+HL clades inhabit depths overlapping with LL ecotypes [@westNichePartitioningProchlorococcusPopulations1999; @zinserInfluenceLightTemperature2007; @delmontLinkingPangenomesMetagenomes2018], while LL clades can occupy regions in OMZ at depths shallower than 40 m [@lavinNovelLineagesProchlorococcus2010], exploiting ambient light levels above what LL clades were thought to tolerate.
 
@@
 MED4 (CCMP1986) is from High-Light adapted (HLI) clade; SS120 (CCMP1375) is from Low-Light adapted (LLII/III) clade; and MIT9313 (CCMP2773) is from Low-Light adapted (LLIV) clade.
-Cultures were maintained in incubators set to 22°C with a light/dark cycle of 12 h.
+Cultures were maintained in incubators set to 22°C with an on/off light/dark cycle of 12 h.
 The PAR level for maintenance cultures reflected PAR in the source niche of the ecotype; MED4, of 160 µmol photons m^-2^ s^-1^ with illumination from STANDARD Products Inc.

### 2024-03-07 Code/Manuscript_O2.Rmd
Moved a paragraph to Mat and Methods under Culturing and experimental design
edsits to PUR ersults

@@
 
+*Prochlorococcus* remain challenging to culture, as their reduced genomes – the smallest of any known oxyphototroph – render them partially dependent upon mutualistic heterotrophic bacteria to detoxify reactive oxygen species [@morrisFacilitationRobustGrowth2008; @morrisDependenceCyanobacteriumProchlorococcus2011].
+MED4, SS120 and MIT9313 have been successfully cultured in laboratories [@mooreComparativePhysiologySynechococcus1995; @mooreCulturingMarineCyanobacterium2007], and used to show that ecotypic classifications correspond to biochemical differences among strains [@bonisteelStrainSpecificDifferences2018].
 Three xenic cultures of *P.
@@
 We focused our analysis here on photosynthetic protein complexes, grouped by clade.
-Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) plots the observation of core photosynthetic complexes (Photosystem II, the Cytochromeb6f complex, Phototsystem I, ATP Synthase and Rubisco) across clades, as a function of depth (a proxy for light intensity) and measured [O~2~].
+Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) plots the observation of core photosynthetic complexes (Photosystem II, the Cytochromeb6f complex, Photosystem I, ATP Synthase and Rubisco) across clades, as a function of depth (a proxy for light intensity) and measured [O~2~].
 Photosynthetic complexes from HLI (ex.
@@
 CladeProchloroPhotosynthDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* photosynthesis complexes.**", 
-                       "Protein detections (annotated as solid grey circles) are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
-                       "Rows separate data annotated as from *Prochlorococcus* clades: HLI (*P.
-marinus* MED4 protein detection annotated as solid black circles), LLI (*P.
-marinus* NATL2A protein detection annotated as solid black circles), LLII/III (*P.
-marinus* SS120 protein detection annotated as solid black circles) and LLIV (*P.
-marinus* MIT9313 protein detection annotated as solid black circles).",
+                       "Protein detections (circles) are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
+                       "Rows separate data annotated as from *Prochlorococcus* clades: HLI (including *P.
+marinus* MED4, solid black circles), LLI (including *P.
+marinus* NATL2A, solid black circles), LLII/III (including *P.
+marinus* SS120, solid black circles) and LLIV (including *P.
+marinus* MIT9313, solid black circles).",
                        "Columns show detections of proteins annotated as  Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
-                       "For comparison culture growth experimental conditions are indicated by horizontal grey lines for depths approximating imposed peak Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^); and vertical grey lines for [O~2~] (µM).",
+                       "For comparison culture growth experimental conditions are indicated by horizontal grey lines for depths approximating imposed peak Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^); and vertical grey lines for imposed [O~2~] (µM).",
                        "Data obtained from OceanProteinPortal (https://www.oceanproteinportal.org/).",
@@
 
-Guided by the evidence of ocean distributions of proteins from *Prochlorococcus* we set up a matrix of photoperiods, PAR, spectral bands, and [O~2~] to approximate current, and potential future, latitudinal, depth and seasonal niches for *Prochlorococcus* strains.
+Guided in part by the evidence of ocean distributions of proteins from *Prochlorococcus* we set up a matrix of photoperiods, PAR, spectral bands, and [O~2~] to approximate current, and potential future, latitudinal, depth and seasonal niches for *Prochlorococcus* strains.
 As mentioned, growth under red light could prove mechanistically informative [@murphyPhotoinactivationPhotosystemII2017] to factors limiting *Prochlorococcus* growth, we therefore included the red spectral waveband even though it is not representative of *Prochlorococcus* niches.
@@
 
-MED4PAR_cap <- glue("**chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade) vs. photoperiod (h).  **",
+MED4PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade) vs. photoperiod (h).  **",
                     "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
@@
 
-SS120PAR_cap <- glue("**chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low-Light (LLII/III) deep ocean clade) vs. photoperiod (h). **",
+SS120PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low-Light (LLII/III) deep ocean clade) vs. photoperiod (h). **",
                      "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
@@
 
-MIT9313PAR_cap <- glue("**chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
+MIT9313PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
                        "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
@@
 
-Cumulative diel PUR can potentially collapse photoperiod, PAR and spectral wavebands to a common metric of photosynthetically active light absorbed per day.
-Cumulative diel PUR dose (µmol photons m^-2^ d^-1^) was calculated from the imposed PUR (µmol photons m^-2^ s^-1^) and photoperiod (h).
+Cumulative diel PUR can potentially collapse photoperiod, PAR and spectral wavebands to a common metric of usable photosynthetically active light per day.
+Cumulative diel PUR (µmol photons m^-2^ d^-1^) was calculated from the imposed PUR (µmol photons m^-2^ s^-1^) and photoperiod (h).
 We plotted growth rates vs.
-cumulative diel PUR to determine whether growth is a simple response to diel PUR, across imposed photoperiods and spectral wavebands, or whether spectral wavebands or photoperiods have specific or interactive influences on growth beyond cumulative diel PUR.
+cumulative diel PUR to determine whether growth is a simple response to diel PUR, across imposed spectral wavebands, and photoperiods, or whether spectral wavebands or photoperiods have specific or interactive influences on growth, beyond cumulative diel PUR.
 
 Due to the absorption of *P.
-marinus* pigments in the blue spectral waveband range, the maximum cumulative diel PUR under blue light is almost 3 times that of white LED light, and about 5 times the red light treatment (Figure \@ref(fig:PurParPlot)), despite being derived from the same photoperiods and peak PAR regimes.
-As such, only blue light experiments extend beyond cumulative diel PUR of ~ 2 x 10^6^ µmol photons m^-2^ d^-1^.
-This bias in the range of data leads us to caution in comparing model fits of growth in response to cumulative diel PUR under red vs.
+marinus* pigments in the blue spectral waveband range, the maximum cumulative diel PUR under blue light is almost 3 times that of white LED light, and about 5 times that of the red light (Figure \@ref(fig:PurParPlot)), despite being derived from the same photoperiods and peak PAR regimes.
+As such, only blue light experiments extend beyond a cumulative diel PUR of ~ 2 x 10^6^ µmol photons m^-2^ d^-1^.
+This spectral bias in the range of PUR leads us to caution in comparing model fits of growth in response to cumulative diel PUR under red vs.
 blue wavebands.
-
-### MED4 clade HLI {.unnumbered}
+Furthermore, we found some distinct model fits for specific photoperiods, contributing to scatter within the red vs.
+blue data sets.
 
@@
 In parallel MED4 showed no growth under 2.5 µM O~2~, no matter the level of diel cumulative PUR.
-In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth under blue light was well described by a saturating response of growth [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] to increasing cumulative diel PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A,B), and no evidence of inhibition of growth at any achieved cumulative diel PUR.
+In contrast, under 250 or 25  µM O~2~, and including photoperiods greater than 4 h, MED4 growth under blue light was described by a saturating response of growth [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] to increasing cumulative diel PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A,B), and no evidence of inhibition of growth at any achieved cumulative diel PUR.
 Under the 'artificial' growth treatment of red light, MED4 achieved more growth per unit diel cumulative PUR (Figure \@ref(fig:BluevsRedPurFitsPlots)A,B), consistent with Murphy *et al*.
@@
 
-### SS120 clade LLII/III {.unnumbered}
-
 The representative of the LLII/III clade, *P.
 marinus* SS120 showed almost no growth under 2.5 µM O~2~ experiments (Figure \@ref(fig:PhotoperiodPurFitsPlots)F).
-Most 4 h photoperiod treatments of SS120 also did not grow under 250 µM O~2~, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments (Figure \@ref(fig:PhotoperiodPurFitsPlots)D).
-SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ experiments (Figure \@ref(fig:PhotoperiodPurFitsPlots)D).
+Most 4 h photoperiod treatments of SS120 also did not grow under 250 µM O~2~ , even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments (Figure \@ref(fig:PhotoperiodPurFitsPlots)D).
+Again using [@harrisonPhotosynthesisirradianceRelationshipsPolar1986], SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ (Figure \@ref(fig:PhotoperiodPurFitsPlots)D).
 
@@
 The onset of growth inhibition extended to higher cumulative diel PUR for cultures under 25 µM O~2~, showing that SS120 is partially protected from photoinhibition of growth by 25 µM O~2~.
-Under 25 µM O~2~, red light again generated more growth of SS120 per unit cumulative diel PUR, than did blue light, again consistent with lower cost of growth through lower photoinactivation under red light (Figure \@ref(fig:BluevsRedPurFitsPlots)E).
+Under 25 µM O~2~, red light again generated more growth of SS120 per unit cumulative diel PUR, than did blue light, consistent with lower cost of growth through lower photoinactivation under red light (Figure \@ref(fig:BluevsRedPurFitsPlots)E) [@murphyPhotoinactivationPhotosystemII2017].
 For distinct fits for different photoperiods refer to Figure \@ref(fig:PhotoperiodPurFitsPlots) D,E and F.
 
-### MIT9313 clade LLIV {.unnumbered}
-
 The LLIV clade representative, *P.
-marinus* MIT9313, showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR, with higher growth rates over a narrower plateau under 25 and 250 µM O~2~ (Figure \@ref(fig:PhotoperiodPurFitsPlots)H,G), compared to a wider, lower, flatter response to cumulative diel PUR under 2.5 µM O~2~ (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).
+marinus* MIT9313, under 250 µM O~2~ showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR, with higher growth rates over a wider plateau under 25 µM O~2~ (Figure \@ref(fig:PhotoperiodPurFitsPlots)H,G).
+In contrast, growth under 2.5 µM O~2~ showed a wider, lower, flatter response to cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).
 Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands (Figure \@ref(fig:PhotoperiodPurFitsPlots)G).
@@
 
- BluevsRedPurFitsPlots_cap <- glue("**chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
+ BluevsRedPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
                     "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                    "Columns are strains; MED4 (A,B,C), SS120 (D,E,F) and MIT9313 (G,H,I).",
+                    "Columns separate data from strains; MED4 (A,B,C), SS120 (D,E,F) and MIT9313 (G,H,I).",
                     "Shapes show the imposed photoperiod (h); 4 h (solid square),  8 h (solid diamond), 12 h (solid circle), 16 h (solid upright triangle).",
                       "Symbol colours show the spectral waveband for growth; 660 nm (red symbols), and 450 nm (blue symbols).",
-                      "Large symbols show mean of growth rate from logistic curve fits; small symbols show values for replicate determinations, if any.",
-                    "Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to 660 nm (red lines) and 450 nm (blue lines) growth data for each combination of strain and dissolved oxygen shown with solid lines (significantly different fits, p value < 0.05) or dashed lines (not significantly different fits, p value > 0.05) using one-way ANOVA.",
+                      "Large symbols show mean of growth rate from logistic curve fits; small symbols show values from replicates, if any.",
+                    "Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to 660 nm (red lines) or 450 nm (blue lines) growth data for each combination of strain and dissolved oxygen shown with solid lines (red significantly different from blue, p value < 0.05) or dashed lines (red not significantly different from blue, p value > 0.05) tested using one-way ANOVA comparisons of fits.",
                        .sep = " ")
@@
 ## Photosystem II maintenance, oxygen metabolism, and DNA repair as limitations on *Prochlorococcus* growth {.unnumbered}
-
-*Prochlorococcus* remain challenging to culture, as their reduced genomes – the smallest of any known oxyphototroph – render them partially dependent upon mutualistic heterotrophic bacteria to detoxify reactive oxygen species [@morrisFacilitationRobustGrowth2008; @morrisDependenceCyanobacteriumProchlorococcus2011].
-MED4, SS120 and MIT9313 have been successfully cultured in laboratories  [@mooreComparativePhysiologySynechococcus1995; @mooreCulturingMarineCyanobacterium2007], and used to show that ecotypic classifications correspond to biochemical differences among strains [@bonisteelStrainSpecificDifferences2018].
 

### 2024-03-07 Code/Manuscript_O2.Rmd
PUR edits

@@
 The LLIV clade representative, *P.
-marinus* MIT9313, under 250 µM O~2~ showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR, with higher growth rates over a wider plateau under 25 µM O~2~ (Figure \@ref(fig:PhotoperiodPurFitsPlots)H,G).
-In contrast, growth under 2.5 µM O~2~ showed a wider, lower, flatter response to cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).
+marinus* MIT9313, under 250 µM O~2~ showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR.
 Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands (Figure \@ref(fig:PhotoperiodPurFitsPlots)G).
-In contrast, under 25 µM O~2~, MIT9313 showed a greatly extended exploitation of higher cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Figure \@ref(fig:PhotoperiodPurFitsPlots)H).
-Similarly, under 2.5 µM O~2~, MIT9313 grew more slowly, but only showed full growth inhibition above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).
+Under 25 µM O~2~ MIT9313 showed higher growth rates over a wider plateau (Figure \@ref(fig:PhotoperiodPurFitsPlots)H,G), with a greatly extended exploitation of higher cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Figure \@ref(fig:PhotoperiodPurFitsPlots)H).
+MIT9313 growth under 2.5 µM O~2~ showed a wider, lower, flatter response to cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I), with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).
 

### 2024-03-07 Code/Manuscript_O2.Rmd
edits to summary

@@
 marinus* MIT9313, a clade LLIV ecotype also found in deep oceans including OMZ, under a matrix of spectral waveband, light level, photoperiod and oxygen conditions approximating present day and hypothetical future niches.
-Low light levels in the blue spectral waveband prevail in deep ocean waters [@morelAvailableUsableStored1978; @holtropVibrationalModesWater2021], while solar incidence angle and light attenuation also progressively attenuate the photoperiod with depth beneath the ocean surface.
-
-*Prochlorococcus marinus* MED4 has a physiological requirement for more than 4 h of light per day; thus this strain will not exploit habitats with short photoperiods, typical of temperate winter or light attenuated depths, even if water temperature warms into the clade HLI tolerance range.
-MED4 is also excluded from the lowest oxygen habitats, represented by our 2.5 µM O~2~ experimental conditions.
-MED4 can, however, grow under OMZ regions with slightly higher [O~2~], as demonstrated by the growth under our 25 µM O~2~ experiments.
-Genomic analyses (Figure \@ref(fig:ProchlorococcusEnzymeKms))  and previous transcriptional analyses [@bergResponsesPsbAHli2011]  suggest MED4 is excluded from growth below ~ 25 µM O~2~ because it relies upon a ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction balance in the intersystem electron transport chain.
+
+*Prochlorococcus marinus* MED4 requires more than 4 h of light per day; thus this strain will not exploit habitats with short photoperiods, typical of temperate winter or light attenuated depths, even if water temperature warms into the clade HLI tolerance range.
+MED4 is also excluded from the lowest oxygen habitats of 2.5 µM O~2~.
+MED4 can, however, grow under OMZ regions with 25 µM O~2~.
+Genomic analyses (Figure \@ref(fig:ProchlorococcusEnzymeKms))  and transcriptional analyses [@bergResponsesPsbAHli2011]  suggest MED4 is excluded from growth below ~ 25 µM O~2~ because it relies upon a ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction balance in the intersystem electron transport chain.
 On the other hand, MED4 shows inducible expression of FtsH isoforms [@bonisteelStrainSpecificDifferences2018], to counter photoinactivation of PSII under higher PAR and [O~2~] environments.
@@
 
-*Prochlorococcus marinus* SS120, a LLII/III clade representative, showed an interactive inhibition of growth by oxygen and cumulative diel PUR, with a higher tolerance for higher cumulative diel PUR under 25 µM O~2~, compared to 250 µM O~2~.
+*Prochlorococcus marinus* SS120, a LLII/III clade representative, showed an interactive inhibition of growth by oxygen and cumulative diel PUR, with a higher tolerance for higher cumulative diel PUR under 25 µM O~2~, compared to 250 µM O~2~ (Figure \@ref(fig:PhotoperiodPurFitsPlots)).
 Thus, SS120 can exploit habitats with O~2~ levels spanning 25 µM O~2~ to 250 µM O~2~, including higher PAR environments within OMZ.
@@
 SS120 grew under photoperiods longer than 4 h and showed increasing growth rate with increasing photoperiods.
-However, we found *P.
-marinus* SS120 can potentially exploit more diverse ecological niches within the ocean layers, even in regions with higher levels of blue spectral waveband, but only under O~2~ of 25 µM (Figure \@ref(fig:SS120PAR)).
-Lavin *et al*.
-[@lavinNovelLineagesProchlorococcus2010] show evidence of LLII/III ecotypes at varying depths from 20 to 30 m and from 75 to 200 µM O~2~ in the oxygen minimum zone (OMZ) of the tropical South Pacific Ocean, illustrating its tolerance of high light levels under low O~2~.
 SS120 has the potential to thrive in deep temperate zones, specifically during the spring, summer, and fall seasons when the duration of daylight exceeds 4 h, if [O~2~] are near surface saturation of about 250 µM.

### 2024-03-07 Code/Manuscript_O2.Rmd
Summary edits and Abstract draft 248 words

@@
 
+*Prochlorococcus marinus*, the smallest picocyanobacterium, comprises multiple clades with distinct niches across tropical and sub-tropical oligotrophic ocean regions, including Oxygen Minimum Zones.
+Ocean warming may open permissive temperatures in  new, poleward photic regimes, along with expanded Oxygen Minimum Zones.
+We used ocean protein data [CITATION] to help guide testing of *Prochlorococcus marinus* growth across a matrix of peak irradiances, photoperiods, spectral bands and dissolved oxygen.
+MED4 from Clade HLI requires greater than 4 h photoperiod, grows at 25 µmol O~2~ L^-1^ and above, and exploits high cumulative diel photon doses, yet shows accelerated growth when the cost of photoinactivation is lowered under red, vs.
+blue, actinic light.
+MED4 relies upon an alternative oxidase to balance electron transport, which may exclude it from growth under our lowest 2.5 µmol O~2~ L^-1^ condition.
+SS120 from Clade LLIII is restricted to low light under full 250 µmol O~2~ L^-1^ , shows expanded light exploitation under  25 µmol O~2~ L^-1^, but is excluded from growth under  2.5 µmol O~2~ L^-1^.
+Intermediate oxygen suppresses the cost of PSII photoinactivation, and enzymatic production of H~2~O~2~ in SS120, which has limited genomic capacity for PSII and DNA repair.
+MIT9313 from Clade LLIV is restricted to low blue irradiance under 250 µmol O~2~ L^-1^, but exploits much higher irradiance under red light, or under lower [O~2~], conditions which slow photoinactivation of PSII and production of reactive oxygen species.
+
 \newpage
@@
 
-We analyzed  growth rates to determine the viability of *P. marinus* MED4, a clade HLI ecotype found near the ocean surface,
-*P.
-marinus* SS120, a clade LLII/III ecotype found deep in the water column, and *P.
-marinus* MIT9313, a clade LLIV ecotype also found in deep oceans including OMZ, under a matrix of spectral waveband, light level, photoperiod and oxygen conditions approximating present day and hypothetical future niches.
-
-*Prochlorococcus marinus* MED4 requires more than 4 h of light per day; thus this strain will not exploit habitats with short photoperiods, typical of temperate winter or light attenuated depths, even if water temperature warms into the clade HLI tolerance range.
-MED4 is also excluded from the lowest oxygen habitats of 2.5 µM O~2~.
-MED4 can, however, grow under OMZ regions with 25 µM O~2~.
-Genomic analyses (Figure \@ref(fig:ProchlorococcusEnzymeKms))  and transcriptional analyses [@bergResponsesPsbAHli2011]  suggest MED4 is excluded from growth below ~ 25 µM O~2~ because it relies upon a ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction balance in the intersystem electron transport chain.
+We analyzed growth rates for  *P.
+marinus* clade HLI found near the ocean surface; clade LLII/III found deep in the water column; and clade LLIV also found in deep oceans, including OMZ, under a matrix of spectral wavebands, irradiances, photoperiods and oxygen concentrations approximating present day and hypothetical future niches.
+
+*Prochlorococcus marinus* MED4 requires more than 4 h of light per day; thus this strain will not exploit habitats typical of temperate winter or light attenuated depths, even if water temperatures warm into the clade HLI tolerance range.
+MED4 is also excluded from the lowest oxygen habitats of 2.5 µM O~2~, but can, grow under OMZ regions with 25 µM O~2~.
+Genomic (Figure \@ref(fig:ProchlorococcusEnzymeKms)) and transcriptional analyses [@bergResponsesPsbAHli2011]  suggest MED4 is excluded from growth below ~ 25 µM O~2~ because it relies upon a ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction balance in the intersystem electron transport chain, with a K~M~ for  [O~2~] of ~25 µM O~2~.
 On the other hand, MED4 shows inducible expression of FtsH isoforms [@bonisteelStrainSpecificDifferences2018], to counter photoinactivation of PSII under higher PAR and [O~2~] environments.
-Photoinactivation, does, however, impose an increased cost of growth upon MED4, since growth under red light, to lower the rate of photoinactivation of PSII [@murphyPhotoinactivationPhotosystemII2017], allows MED4 to achieve faster growth per absorbed photon than growth under blue light.
+Photoinactivation, does, however, impose an increased cost of growth upon MED4, since growth under red light, to lower photoinactivation of PSII [@murphyPhotoinactivationPhotosystemII2017], allows MED4 to achieve faster growth per absorbed photon than growth under blue light.
 TARA Oceans Project data [@delmontLinkingPangenomesMetagenomes2018] indeed reported presence of *P.
 marinus* MED4-like genomes at depths ranging from 5 m to 90 m, representing high to low blue light levels, in the Pacific South East Ocean.
-Delmont and Eren [@delmontLinkingPangenomesMetagenomes2018] did not analyze data from depths beyond the subsurface chlorophyll maximum layer, the layer in the water column where the chlorophyll *a* concentration peaks, nor did they report the [O~2~] at those depths.
-Our growth findings are also consistent with Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSII proteins annotated as MED4, clade HLI, at depths up to 200 meters with O~2~ of 15 µM.
+Delmont and Eren [@delmontLinkingPangenomesMetagenomes2018] did not analyze data from depths beyond the subsurface chlorophyll maximum layer, nor did they report[O~2~] at depth.
+Our growth findings are  consistent with Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSII proteins annotated as MED4, clade HLI, at depths up to 200 meters, with O~2~ of ~15 µM.
 
 *Prochlorococcus marinus* SS120, a LLII/III clade representative, showed an interactive inhibition of growth by oxygen and cumulative diel PUR, with a higher tolerance for higher cumulative diel PUR under 25 µM O~2~, compared to 250 µM O~2~ (Figure \@ref(fig:PhotoperiodPurFitsPlots)).
-Thus, SS120 can exploit habitats with O~2~ levels spanning 25 µM O~2~ to 250 µM O~2~, including higher PAR environments within OMZ.
+Thus, SS120 can exploit higher PAR environments, within OMZ.
 SS120 is likely excluded from the combination of higher [O~2~] and higher PAR by genomic limitations on capacity for DNA repair (Figure \@ref(fig:DNARepairFig)), and possibly by limited capacity for synthesis of reactive oxygen quenchers (Figure  \@ref(fig:ProchlorococcusEnzymeKms)).
 Our growth results are supported by Lavin *et al*.
-[@lavinNovelLineagesProchlorococcus2010] who found evidence of LLII/III
-and LLIV ecotypes, using terminal restriction fragment length polymorphism analyses, at depths above 40 m, where light levels are
-higher, within OMZ, and by Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSII protein subunits annotated as derived from SS120 at all depths ranging
-from 20 to 200 m and all [O~2~] in an OMZ of the tropical North Pacific Ocean.
-SS120 grew under photoperiods longer than 4 h and showed increasing growth rate with increasing photoperiods.
-SS120 has the potential to thrive in deep temperate zones, specifically during the spring, summer, and fall seasons when the duration of daylight exceeds 4 h, if [O~2~] are near surface saturation of about 250 µM.
+[@lavinNovelLineagesProchlorococcus2010] who found evidence of LLII/III and LLIV ecotypes, using terminal restriction fragment length polymorphism analyses, at depths above 40 m, where light levels are higher, within OMZ, and by Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSII protein subunits annotated as derived from SS120 at all depths ranging from 20 to 200 m and all [O~2~] in an OMZ of the tropical North Pacific Ocean.
+SS120 grew under photoperiods longer than 4 h and showed increasing growth rate with increasing photoperiods, and so has the potential to thrive in deep temperate zones, specifically during the spring, summer, and fall seasons when the duration of daylight exceeds 4 h, if [O~2~] are near surface saturation of about 250 µM.
 Under lower oxygen levels of 25 µM, SS120 can also potentially exploit a 4 h photoperiod in the blue waveband, and thus has the potential to inhabit a potential warmed, deep, temperate OMZ, during the winter season.
@@
 We hypothesize that under 250 µM O~2~ and higher blue light, *P.
-marinus* MIT9313 suffers photoinhibition, resulting from the inactivation of PSII caused by the production of H~2~O~2~.
-This photoinhibition is compounded by the limited inducible repair for PSII, due to the absence of FtsH 1 and 2  expression in *P.
+marinus* MIT9313 suffers photoinhibition, resulting in part from the inactivation of PSII caused by the production of H~2~O~2~.
+This photoinhibition is compounded by limited inducible repair for PSII, due to the absence of FtsH 1 and 2  expression in *P.
 marinus* MIT9313 [@bonisteelStrainSpecificDifferences2018].
@@
 Partensky *et al*.
-[@partenskyComparisonPhotosyntheticPerformances2018] found that in the low-light conditions found in the OMZ, MED4, SS120 and MIT9313 all became net O~2~ consumers, suggesting that the low light levels cause the respiratory chain to consume more O~2~ than the photosynthetic electron transport chain generates, thus contributing to maintenance of the low O~2~ environment.
+[@partenskyComparisonPhotosyntheticPerformances2018] indeed found that in the low-light conditions found in the OMZ, MED4, SS120 and MIT9313 all became net O~2~ consumers, suggesting that the low light levels cause the respiratory chain to consume more O~2~ than the photosynthetic electron transport chain generates, thus contributing to maintenance of the low O~2~ environment.
 
@@
 
-XXX DOI pending from BOREALIS? or DRYAD? XXX
-
 # Acknowledgements  {.unnumbered}
 Carlie Barnhill (Mount Allison Student) assisted with code for import of multicultivator growth data files.
-Sarah Arthur (Mount Allison Student) assisted with culturing and setting up Multicultivator runs.
+Sarah Arthur & Daytona McMackin (Mount Allison Students) assisted with culturing and setting up Multicultivator runs.
 

### 2024-03-07 Code/Manuscript_O2.Rmd
Added OPP dataset citations

@@
 Ocean warming may open permissive temperatures in new, poleward photic regimes, along with expanded Oxygen Minimum Zones.
-We used ocean protein data [CITATION] to help guide testing of *Prochlorococcus marinus* growth across a matrix of peak irradiances, photoperiods, spectral bands and dissolved oxygen.
+We used ocean protein data [@saitoPeptidesTheirSpectral2018; @saitoDevelopmentOceanProtein2021] to help guide testing of *Prochlorococcus marinus* growth across a matrix of peak irradiances, photoperiods, spectral bands and dissolved oxygen.
 MED4 from Clade HLI requires greater than 4 h photoperiod, grows at 25 µmol O~2~ L^-1^ and above, and exploits high cumulative diel photon doses, yet shows accelerated growth when the cost of photoinactivation is lowered under red, vs.
@@
 Intermediate oxygen suppresses the cost of PSII photoinactivation, and enzymatic production of H~2~O~2~ in SS120, which has limited genomic capacity for PSII and DNA repair.
-MIT9313 from Clade LLIV is restricted to low blue irradiance under 250 µmol O~2~ L^-1^, but exploits much higher irradiance under red light, or under lower [O~2~], conditions which slow photoinactivation of PSII and production of reactive oxygen species.
+MIT9313 from Clade LLIV is restricted to low blue irradiance under 250 µmol O~2~ L^-1^, but exploits much higher irradiance under red light, or under lower O~2~ concentrations, conditions which slow photoinactivation of PSII and production of reactive oxygen species.
 

### 2024-03-07 Code/Manuscript_O2.Rmd
fixed citation west et al

@@
 We focused on proteins mediating photosynthesis and protein metabolism from depths of 20 to 200 m below the ocean surface.
-The samples for metaproteomic analyses were collected from 12 locations in the tropical North Pacific ocean along 150 W from 18 N of the equator between October 1, 2011 and October 25, 2011 during the voyage of the R/V Kilo Moana MetZyme cruise KM1128 (https://www.rvdata.us/search/cruise/KM1128; original datasets in the Biological and Chemical Oceanography Data Management Office repository; https://www.bco-dmo.org/project/2236).
+The samples for metaproteomic analyses were collected from 12 locations in the tropical North Pacific ocean along 150 W from 18 N of the equator between October 1, 2011 and October 25, 2011 during the voyage of the R/V Kilo Moana MetZyme cruise [@rollingdecktorepositoryCruiseKM1128RV2015]; original datasets in the Biological and Chemical Oceanography Data Management Office repository [@saitoPeptidesTheirSpectral2018; @saitoDevelopmentOceanProtein2021].
 Oxygen concentration levels at the location of sampling were recorded.
@@
 West *et al*.
-[@westNichePartitioningProchlorococcusPopulationsStratified1999] and Malmstrom *et al*.
+[@westNichePartitioningProchlorococcusPopulations1999] and Malmstrom *et al*.
 [@malmstromTemporalDynamicsProchlorococcus2010] found that decreased abundances of the LL clades corresponded to increased depth of the surface mixed layer.
@@
 West *et al*.
-[@westNichePartitioningProchlorococcusPopulationsStratified1999] found the depth of the mixed layer strongly influenced the depth transition from HL to LL clades, but that factors other than light levels may influence the variations in the upper and lower depth limits of these ecotypes.
+[@westNichePartitioningProchlorococcusPopulations1999] found the depth of the mixed layer strongly influenced the depth transition from HL to LL clades, but that factors other than light levels may influence the variations in the upper and lower depth limits of these ecotypes.
 We hypothesize that low cell abundances of LL ecotypes in the mixed layer is likely driven in part by increased [O~2~],  and it is [O~2~] that constrains LL clades to deeper waters, not necessarily the light level.

### 2024-03-07 Code/Manuscript_O2.Rmd
Fixed OPP dataset citation in fig.cap

@@
 Ocean warming may open permissive temperatures in new, poleward photic regimes, along with expanded Oxygen Minimum Zones.
-We used ocean protein data [@saitoPeptidesTheirSpectral2018; @saitoDevelopmentOceanProtein2021] to help guide testing of *Prochlorococcus marinus* growth across a matrix of peak irradiances, photoperiods, spectral bands and dissolved oxygen.
+We used ocean protein data [@saitoPeptidesTheirSpectral2018] to help guide testing of *Prochlorococcus marinus* growth across a matrix of peak irradiances, photoperiods, spectral bands and dissolved oxygen.
 MED4 from Clade HLI requires greater than 4 h photoperiod, grows at 25 µmol O~2~ L^-1^ and above, and exploits high cumulative diel photon doses, yet shows accelerated growth when the cost of photoinactivation is lowered under red, vs.
@@
 We focused on proteins mediating photosynthesis and protein metabolism from depths of 20 to 200 m below the ocean surface.
-The samples for metaproteomic analyses were collected from 12 locations in the tropical North Pacific ocean along 150 W from 18 N of the equator between October 1, 2011 and October 25, 2011 during the voyage of the R/V Kilo Moana MetZyme cruise [@rollingdecktorepositoryCruiseKM1128RV2015]; original datasets in the Biological and Chemical Oceanography Data Management Office repository [@saitoPeptidesTheirSpectral2018; @saitoDevelopmentOceanProtein2021].
+The samples for metaproteomic analyses were collected from 12 locations in the tropical North Pacific ocean along 150 W from 18 N of the equator between October 1, 2011 and October 25, 2011 during the voyage of the R/V Kilo Moana MetZyme cruise [@rollingdecktorepositoryCruiseKM1128RV2015]; original datasets in the Biological and Chemical Oceanography Data Management Office repository [@saitoPeptidesTheirSpectral2018].
 Oxygen concentration levels at the location of sampling were recorded.
@@
 
-Metaproteomic datasets were obtained from the KM1128 entry in the BCO-DMO database (https://www.bco-dmo.org/deployment/59053) accessed via the OPP in June 2019. Datasets contained:
+Metaproteomic datasets were obtained from the KM1128 entry in the BCO-DMO database [@saitoPeptidesTheirSpectral2018] accessed via the OPP in June 2019. Datasets contained:
 	i) Peptide sequences and sample identification (ID) number;
@@
                        "For comparison culture growth experimental conditions are indicated by horizontal grey lines for depths approximating imposed peak Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^); and vertical grey lines for imposed [O~2~] (µM).",
-                       "Data obtained from OceanProteinPortal (https://www.oceanproteinportal.org/).",
+                       "Data obtained from the Biological and Chemical Oceanography Data Management Office repository [@saitoPeptidesTheirSpectral2018].",
  .sep = " ")
@@
                     "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                       "Columns show 3 levels of growth Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^",
-                    "colours represent the actinic spectral waveband (nm).",
+                       "Columns show 3 levels of growth Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
+                    "Colours represent the actinic spectral waveband (nm).",
                     "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
@@
                      "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                       "Columns show 3 levels of growth Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^",
-                    "colours represent the actinic spectral waveband (nm).",
+                       "Columns show 3 levels of growth Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
+                    "Colours represent the actinic spectral waveband (nm).",
                     "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
@@
                        "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                       "Columns show 3 levels of growth Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^",
-                    "colours represent the actinic spectral waveband (nm).",
+                       "Columns show 3 levels of growth Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
+                    "Colours represent the actinic spectral waveband (nm).",
                     "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
@@
                        "Culture growth experimental conditions indicated by horizontal grey lines for depths approximating Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) and vertical grey lines for [O~2~] (µM).",
-                       "Data obtained from OceanProteinPortal (https://www.oceanproteinportal.org/).",
+                       "Data obtained from the Biological and Chemical Oceanography Data Management Office repository [@saitoPeptidesTheirSpectral2018].",
  .sep = " ")

### 2024-03-07 Code/Manuscript_O2.Rmd
Changed number of sample collection  locations from 12 to 7 as per OPP site (KM1128 cruise) and the 'stations_info.txt' file in OceanProteinProchloro github repository (RawData).

@@
 We focused on proteins mediating photosynthesis and protein metabolism from depths of 20 to 200 m below the ocean surface.
-The samples for metaproteomic analyses were collected from 12 locations in the tropical North Pacific ocean along 150 W from 18 N of the equator between October 1, 2011 and October 25, 2011 during the voyage of the R/V Kilo Moana MetZyme cruise [@rollingdecktorepositoryCruiseKM1128RV2015]; original datasets in the Biological and Chemical Oceanography Data Management Office repository [@saitoPeptidesTheirSpectral2018].
+The samples for metaproteomic analyses were collected from 7 locations in the tropical North Pacific ocean along 150 W from 18 N of the equator between October 1, 2011 and October 25, 2011 during the voyage of the R/V Kilo Moana MetZyme cruise [@rollingdecktorepositoryCruiseKM1128RV2015]; original datasets in the Biological and Chemical Oceanography Data Management Office repository [@saitoPeptidesTheirSpectral2018].
 Oxygen concentration levels at the location of sampling were recorded.

### 2024-03-08 Code/Manuscript_O2.Rmd
Added ANOVA blurb. Fixed  1 reference to a figure

@@
 
-We fit the response of chlorophyll specific growth rate to cumulative diel PUR using the equation of Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] across strain and [O~2~] to compare growth response between 660 nm (red) and 450 nm (blue) growth light and additionally, to compare growth response between specific photoperiods (4 h, 8 h, 12 h, 16 h) and a fit across pooled photoperiod data.
-To examine statistical differences between the modeled fits, we performed one-way ANOVA comparing the model output parameters assigning significant differences when the p value was < 0.05.
+We performed one-way ANOVA to examine statistical differences between Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to 660 nm (red light) and 450 nm (blue light) growth data for each combination of strain and [O~2~].
+We also performed one-way ANOVA to examine statistical differences between Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to each photoperiod (4 h, 8 h, 12 h, 16 h) and pooled photoperiod growth data for each combination of strain and [O~2~].
+Photoperiod growth data that showed complete growth inhibition for each combination of strain, [O~2~] and imposed spectral waveband were omitted from the pooled photoperiod model.
+Statistical differences were determined at p < 0.05.
 
@@
 Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands (Figure \@ref(fig:PhotoperiodPurFitsPlots)G).
-Under 25 µM O~2~ MIT9313 showed higher growth rates over a wider plateau (Figure \@ref(fig:PhotoperiodPurFitsPlots)H,G), with a greatly extended exploitation of higher cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Figure \@ref(fig:PhotoperiodPurFitsPlots)H).
-MIT9313 growth under 2.5 µM O~2~ showed a wider, lower, flatter response to cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I), with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).
+Under 25 µM O~2~ MIT9313 showed higher growth rates over a wider plateau, with a greatly extended exploitation of higher cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Figure \@ref(fig:PhotoperiodPurFitsPlots)H).
+MIT9313 growth under 2.5 µM O~2~ showed a wider, lower, flatter response to cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).
 

### 2024-03-08 Code/Manuscript_O2.Rmd
minor edit

@@
 We focused on proteins mediating photosynthesis and protein metabolism from depths of 20 to 200 m below the ocean surface.
-The samples for metaproteomic analyses were collected from 7 locations in the tropical North Pacific ocean along 150 W from 18 N of the equator between October 1, 2011 and October 25, 2011 during the voyage of the R/V Kilo Moana MetZyme cruise [@rollingdecktorepositoryCruiseKM1128RV2015]; original datasets in the Biological and Chemical Oceanography Data Management Office repository [@saitoPeptidesTheirSpectral2018].
+The samples for metaproteomic analyses were collected from 7 locations in the tropical North Pacific ocean along 150 W from 18 N of the equator between October 1, 2011 and October 25, 2011 during the voyage of the R/V Kilo Moana MetZyme cruise [@rollingdecktorepositoryCruiseKM1128RV2015]; original datasets in the Biological and Chemical Oceanography Data Management Office (BCO-DMO) repository [@saitoPeptidesTheirSpectral2018].
 Oxygen concentration levels at the location of sampling were recorded.

### 2024-03-08 Code/Manuscript_O2.Rmd
minor edits

@@
 Photosynthetic organisms absorb light energy within the Photosynthetically Active Radiation (PAR) range, 350 to 700 nm, for photosynthesis [@morelAvailableUsableStored1978].
-Photosynthetically Usable Radiation (PUR) represents the fraction of PAR that is absorbed by the pigments of a given photosynthetic organism [@morelAvailableUsableStored1978], taking into account the specific spectral wavebands these pigments absorb.
+Photosynthetically Usable Radiation (PUR) represents the fraction of PAR that can be absorbed by the pigments of a given photosynthetic organism [@morelAvailableUsableStored1978], taking into account the specific spectral wavebands these pigments absorb.
 *Prochlorococcus marinus* Pcb light-harvesting complexes show an absorption maxima of 442 nm for divinyl chlorophyll *a* and 478 nm for divinyl chlorophyll *b* [@goerickePigmentsProchlorococcusMarinus1992] allowing *P.
@@
 
-To estimate the Photosynthetic Usable Radiation (PUR), a proxy of incident photons absorbed by the cells, for each *P. marinus* ecotype, the imposed Photosynthetic Active
+To estimate the Photosynthetic Usable Radiation (PUR), a proxy of incident photons that can be absorbed by the cells, for each *P. marinus* ecotype, the imposed Photosynthetic Active
 Radiation (PAR) was first determined using the reported delivery of sinusoidal diel PAR regimes by the Multicultivators, point validated using a LI-250 quantum sensor (LI-COR Inc.,Lincoln, NE, USA).
@@
 Actinic PUR levels (µmol photons m^-2^ s^-1^) were calculated from actinic PAR (µmol photons m^-2^ s^-1^) levels using the equation \@ref(eq:PUR) from [@morelAvailableUsableStored1978]; where P(λ) is the weighted PUR absorbance spectrum from equation \@ref(eq:WeightedPUR), E(λ) is the imposed growth light emission spectrum from equation \@ref(eq:WeightedPUR) and PAR is the imposed peak light level (µmol photons m^-2^ s^-1^).
-Figure (\@ref(fig:PurParPlot)) shows the calculated absorbed peak PUR (µmol photons m^-2^ d^-1^) versus imposed actinic peak PAR (µmol photons m^-2^ s^-1^) for each strain and each spectral waveband (nm).
+Figure (\@ref(fig:PurParPlot)) shows the calculated peak PUR (µmol photons m^-2^ d^-1^) versus imposed actinic peak PAR (µmol photons m^-2^ s^-1^) for each strain and each spectral waveband (nm).
 
@@
 The applied photoperiods were delivered using the sinusoidal circadian light function of the PSI Multicultivator to simulate light exposure approximating sun rise through to sunset.
-The area under the sinusoidal curves is equivalent to the area of a triangular photoregime of equivalent photoperiod (Campbell, unpub), therefore the equation to determine the cumulative diel PUR (µmol photons m^-2^ d^-1^) is one half of the base (photoperiod) multiplied by the height (PUR) (Equation \@ref(eq:SumPURDay)); where PUR is the actinic absorbed light calculated from equation \@ref(eq:PUR) (µmol photons m^-2^ s^-1^), 3600 is the time conversion from seconds to hour and photoperiod is the imposed photoperiod (h).
+The area under the sinusoidal curves is equivalent to the area of a triangular photoregime of equivalent photoperiod (Campbell, unpub), therefore the equation to determine the cumulative diel PUR (µmol photons m^-2^ d^-1^) is one half of the base (photoperiod) multiplied by the height (PUR) (Equation \@ref(eq:SumPURDay)); where PUR is the actinic light calculated from equation \@ref(eq:PUR) (µmol photons m^-2^ s^-1^), 3600 is the time conversion from seconds to hour and photoperiod is the imposed photoperiod (h).
 
@@
 
-PurParPlot_cap <- glue("**Absorbed peak Photosynthetically Usable Radiation (PUR) (µmol photons m^-2^ s^-1^) vs. peak Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^).**",
+PurParPlot_cap <- glue("**Peak Photosynthetically Usable Radiation (PUR) (µmol photons m^-2^ s^-1^) vs. peak Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^).**",
                        "The correlation between PAR, plotted on the x-axis and PUR, plotted on the y-axis, are coloured for each growth spectral waveband; 450 nm (blue circles), 660 nm (red circles) and white LED (black circles).",
@@
 On the other hand, MED4 shows inducible expression of FtsH isoforms [@bonisteelStrainSpecificDifferences2018], to counter photoinactivation of PSII under higher PAR and [O~2~] environments.
-Photoinactivation, does, however, impose an increased cost of growth upon MED4, since growth under red light, to lower photoinactivation of PSII [@murphyPhotoinactivationPhotosystemII2017], allows MED4 to achieve faster growth per absorbed photon than growth under blue light.
+However, photoinactivation, does impose an increased cost of growth upon MED4, since growth under red light, to lower photoinactivation of PSII [@murphyPhotoinactivationPhotosystemII2017], allows MED4 to achieve faster growth per absorbed photon than growth under blue light.
 TARA Oceans Project data [@delmontLinkingPangenomesMetagenomes2018] indeed reported presence of *P.

### 2024-03-08 Code/Manuscript_O2.Rmd
added orcid numbersin readme

@@
 
-HL clades are more recently branching lineages, with reduced genome sizes in comparison to LL clades.
+High-Light clades are more recently branching lineages, with reduced genome sizes in comparison to LL clades.
 High-Light clades are typically dominant picophytoplankters in near-surface, oligotrophic waters, characterized by high light levels and subdivided into clades based on iron adaptation [@johnsonNichePartitioningProchlorococcus2006; @zinserInfluenceLightTemperature2007; @kentParallelPhylogeographyProchlorococcus2019].
@@
 *Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4, homologs to the characterized FtsH isoforms of the model freshwater cyanobacterium *Synechocystis* FtsH, and with presumably parallel functions (Table \@ref(tab:FtsHTable)).
-Upon a shift to higher light HLI MED4 upregulated expression of FtsH1 and FtsH2 [@bonisteelStrainSpecificDifferences2018], homologs to the *Synechocystis* *slr*0228 and *slr*1604, implicated in PSII repair.
+Upon a shift to higher light, HLI MED4 upregulated expression of FtsH1 and FtsH2 [@bonisteelStrainSpecificDifferences2018], homologs to the *Synechocystis* *slr*0228 and *slr*1604, implicated in PSII repair.
 In contrast, representative LLIV strain MIT9313 showed less overall expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem.
@@
 On the other hand, MED4 shows inducible expression of FtsH isoforms [@bonisteelStrainSpecificDifferences2018], to counter photoinactivation of PSII under higher PAR and [O~2~] environments.
-However, photoinactivation, does impose an increased cost of growth upon MED4, since growth under red light, to lower photoinactivation of PSII [@murphyPhotoinactivationPhotosystemII2017], allows MED4 to achieve faster growth per absorbed photon than growth under blue light.
+However, photoinactivation imposes an increased cost of growth upon MED4, since growth under red light, to lower photoinactivation of PSII [@murphyPhotoinactivationPhotosystemII2017], allows MED4 to achieve faster growth per absorbed photon than growth under blue light.
 TARA Oceans Project data [@delmontLinkingPangenomesMetagenomes2018] indeed reported presence of *P.

### 2024-03-08 Code/Manuscript_O2.Rmd
minor edits

@@
     institute: [mta, ubc]
+  - name: Laurel Genge
+    institute: [mta, dfo]
   - name: Julie Nadeau
-    institute: mta
-  - name: Laurel Genge
     institute: mta
@@
 institute:
-  - mta: 'Department of Biology, Mount Allison University, 63B York St., Sackville NB, Canada, E4L 1G7.'
+  - mta: 'Department of Biology, Mount Allison University, 63B York St., Sackville NB, Canada, E4L 1G7'
   - ubc: 'Department of Biology, University of British Columbia'
+  - dfo: 'Fisheries and Oceans Canada, Ecosystems Management Branch, Dartmouth NS'
   - sfx: 'Department of Chemistry, St. Frances Xavier University'

### 2024-03-08 Code/Manuscript_O2.Rmd
defined ATP

@@
 	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using *tidyverse* package [@R-tidyverse] running under R v4.1.3 and RStudio v2023.06.0 [@RStudio].
-The resulting merged dataset was filtered for those *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b~6~f (Cytb~6~f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Plastoquinol Terminal Oxidase (PTOX); Plastocyanin (PC); Ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  ATP Synthase;  FtsH proteases (FtsH) or ribosomes.
+The resulting merged dataset was filtered for those *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b~6~f (Cytb~6~f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Plastoquinol Terminal Oxidase (PTOX); Plastocyanin (PC); Ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  Adenosine triphosphate (ATP) Synthase;  FtsH proteases (FtsH) or ribosomes.
 Detected peptides were re-annotated for consistency and labelled, where feasible, according to strain, clade, subunit and protein complex.

### 2024-03-08 Code/Manuscript_O2.Rmd
edited mumax supplemental table

@@
           WL = ifelse(MaxGrowth != 0, WL, paste("All tested", sep = " "))) %>%
-   relocate(WL, .after = Par_ue) %>%
-   relocate(MaxGrowth, .after = WL) %>% 
-   relocate(O2_uM, .after = WL) %>% 
   arrange(Strain, O2_uM)
 
+  MaxGrowthTable
+
 ```
@@
 knitr::kable(MaxGrowthTable,
-             caption = "The maximum growth rate, µ~max~ (d^-1^) achieved for each O~2~ experiment, for each strain, with the corresponding photoperiod, PAR level and spectral waveband.",
+             caption = "The maximum growth rate, µ~max~ (d^-1^) achieved for each strain under each [O~2~], with the corresponding photoperiod, PAR level and spectral waveband.",
             col.names =  c("Strain",
+                          "[O~2~] (µM)",
+                          "µ~max~ (d^-1^)",
                           "Photoperiod (h)",
                           "PAR (µmol photons m^-2^ s^-1^)",
-                          "Spectral waveband (nm)",
-                          "[O~2~] (µM)",
-                          "µ~max~ (d^-1^)"),
+                          "Spectral waveband (nm)"),
               align = "lccccc"

### 2024-03-08 Code/Manuscript_O2.Rmd
defined ATP
Added Miranda in Acknowledgement

--- 2024-03-08 Code/Manuscript_O2.Rmd
@@
 marinus* SS120 demonstrates the smallest genomic capacity for DNA repair.
-*Prochlorococcus marinus* MED4 and NATL2A were the only strains to possess a gene encoding deoxyribodipyrimidine photolyase, which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003].
+*Prochlorococcus marinus* MED4 and NATL2A were the only strains to possess a gene encoding deoxyribodipyrimidine photolyase (Figure \@ref(fig:DNARepairFig) and \@ref(fig:ProchlorococcusLightEnzymes)), which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003].
 *Prochlorococcus marinus* MED4 was also the only strain to possesses a gene encoding DNA ligase, which uses ATP as a cofactor for DNA repair.
@@
 # Acknowledgements  {.unnumbered}
+Miranda Corkum maintained cultures and trained personnel in culture handling.
 Carlie Barnhill (Mount Allison Student) assisted with code for import of multicultivator growth data files.

### 2024-03-08 Code/Manuscript_O2.Rmd
merged changes to table

--- 2024-03-08 Code/Manuscript_O2.Rmd
@@
 MaxGrowthTable
-
 ```

### 2024-03-08 Code/Manuscript_O2.Rmd
working on FtsH terminology

@@
 We are, however, confident in clade classifications for each protein examined.
-A caveat to interpretation of this data is the peptide detection bias inherent to mass spectrometry XXX Aurora CITATION XXX.
-The data is also limited by the number and nature of protein spectra in the SEQUEST database: a peptide sequence was not determined unless there is already a known spectrum for that peptide in the SEQUEST database, hence some peptides of interest may not be identifiable.
+The data is also limited because a peptide sequence was not determined unless there was already a known spectrum for that peptide in the SEQUEST database, hence some peptides of interest may not be identifiable.
 Furthermore, a peptide must be detected above a certain threshold abundance in order to be considered an accurate ‘hit’.
@@
 marinus* were detected across depths and oxygen concentrations in the ocean proteins data set analyzed.
-We focused our analysis here on photosynthetic protein complexes, grouped by clade.
-Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) plots the observation of core photosynthetic complexes (Photosystem II, the Cytochromeb6f complex, Photosystem I, ATP Synthase and Rubisco) across clades, as a function of depth (a proxy for light intensity) and measured [O~2~].
-Photosynthetic complexes from HLI (ex.
-MED4) were detected throughout the water column, predominantly at high [O~2~].
+We focused our analysis here on core photosynthetic protein complexes, for clades HL, LLI, LLIII and LLIV (Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) as a function of depth (a proxy for light intensity) and measured [O~2~].
+Photosynthetic complexes from HLI (including strain MED4) were detected throughout the water column, predominantly at high [O~2~].
+The  absence of proteins annotated for the key ATP Synthase complex for Clade HLI, compared to annotated detections of ATP Synthase across the other three clades suggests limitations in the annotation process for highly conserved protein sequences.
+Complexes from Clades LLI (including strain NATL2A) were also present across the depth/light axes, with more representation at lower [O~2], and fewer near surface detections.
 Complexes from clade LLII/III (ex.
-SS120) and clade LLIV (ex.
-MIT9313) were detected throughout the water column in high [O~2~] and at depth in low [O~2~] samples.
-The exclusive assignment of ATP Synthase peptides to clade LLIV (ex.
-MIT9313) may result from the high conservation of protein sequence for this complex.
-
-XXX More Text XXX from Amanda & Aurora XXX
-Proteins derived from clade HLXXX ecotypes of *P.
-marinus* were detected in OMZ at depths up to 200 meters,  with O~2~ of 15 µM.
-The extent to which [O~2~] defines the niches occupied by different *P.
-marinus* ecotypes, as compared to potentially covarying environmental variables like photoperiod, light spectrum, and light level, is poorly described.
+SS120) were also detected across the depth/light and [O~2~] ranges, with more detections at deeper, darker depths.
+Clade LLIV (ex.
+MIT9313) photosynthetic complexes were also were detected throughout the depth/light and [O~2~], ranges, with the most frequent detections at depth and at low [O~2~], compared to other strains.
 
@@
 Repair of photoinactivated PSII relies on the removal of damaged PsbA [@mannInvolvementFtsHHomologue2000; @adamFtsHProteasesChloroplasts2005], followed by reassembly with newly synthesized PsbA [@nixonRecentAdvancesUnderstanding2010].
-Degradation of PsbA is a rate-limiting step in recovery from photoinhibition [@kanervoD1ProteinDegradation1993], mediated largely by a heterohexamer of (FtsH1-FtsH2)~3~, a membrane-bound [@sacharzSubCellularLocation2015; @zakInitialStepsBiogenesis2001] metalloprotease  [(Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014),  @boehmSubunitOrganizationSynechocystis2012a;  @komendaExposedNTerminalTail2007],  XXX (AMANDA REF from ALGATECH) XXX.
-
+Degradation of PsbA is a rate-limiting step in recovery from photoinhibition [@kanervoD1ProteinDegradation1993], mediated largely by a heterohexamer of (FtsH1-FtsH2)~3~, a membrane-bound [@sacharzSubCellularLocation2015; @zakInitialStepsBiogenesis2001] metalloprotease  [(Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014),  @boehmSubunitOrganizationSynechocystis2012a;  @komendaExposedNTerminalTail2007].
+
+XXXStillWorkingonFtsH Terminology!XXXX
 *Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4, homologs to the characterized FtsH isoforms of the model freshwater cyanobacterium *Synechocystis* FtsH, and with presumably parallel functions (Table \@ref(tab:FtsHTable)).

### 2024-03-08 Code/Plots_GAM.Rmd

@@
      # xlab("Photoperiod (h)") +
-    # ylab("                                  ") +
       ylab(NULL)+
+    # ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")") +
     # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
@@
           axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35),
-          axis.text.y = element_blank(),
-          axis.line.y = element_blank(),
-          axis.ticks.y = element_blank()))
+           axis.title.y = element_text(size=35)))
 
@@
           axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=23),
-          axis.text.y = element_blank(),
-          axis.line.y = element_blank(),
-          axis.ticks.y = element_blank()))
+           axis.title.y = element_text(size=35)))
 
@@
 
-CombinedGAM <- plot_grid(p3_Red, p3_Blue)
+CombinedGAM <- plot_grid(p3_Red, p3_Blue, nrow = 1)
 
 x.grob <- textGrob("Photoperiod (h)", 
-                   gp = gpar(fontface="bold", fontsize = 20))
+                   gp = gpar(fontsize = 20))
 

### 2024-03-09 Code/Plots_GAM.Rmd
Fixed scaling issue with blue part of GAMs. Cleaned up code so generation of grid arrange plots is prone to less error

@@
 ``` {r GAM Plot Red WL}
-GamStrain = "MIT9313" # MIT9313 MED4 SS120
+GamStrain = "SS120" # MIT9313 MED4 SS120
 GamColor = "Red" 
@@
     #facet_grid(cols = vars(O2_uM)) +
-    labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
+    # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
     theme_classic() +
@@
     #facet_grid(cols = vars(O2_uM)) +
-    labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
+    # labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
    theme_classic() +
@@
     #facet_grid(cols = vars(O2_uM)) +
-    labs(title = bquote("A.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +  #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+    # labs(title = bquote("A.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +  #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
     theme_classic() +
@@
 
+# comment rows that are not included in grid arrange 
 LayoutNiche <- rbind(
-                     c(3, 3, 3, 3, 6),
-                     c(3, 3, 3, 3, 6),
-                     c(2, 2, 2, 2, 5),
-                     c(2, 2, 2, 2, 5)
-                     ,
-                     c(1, 1, 1, 1, 4),
-                     c(1, 1, 1, 1, 4)
+                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2
+                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2
+                     c(2, 2, 2, 2, 5),   # For 25 uM O2
+                     c(2, 2, 2, 2, 5),   # For 25 uM O2
+                     c(1, 1, 1, 1, 4),   # For 250 uM O2
+                     c(1, 1, 1, 1, 4)    # For 250 uM O2
                      )
@@
 
-p3_Red <- grid.arrange(ContourLowO2 + theme(legend.position = 'none'), ContourIntO2 + theme(legend.position = 'none'), ContourHighO2 + theme(legend.position = 'none'), legend1, legend2, legend3, layout_matrix = LayoutNiche)
+p3_Red <- grid.arrange(
+  # ContourLowO2 +   labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
+                         # theme(legend.position = 'none'), 
+                       ContourIntO2 + labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
+                         theme(legend.position = 'none'), 
+                       ContourHighO2 + labs(title = bquote("A.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
+                         theme(legend.position = 'none'), 
+                        legend1, 
+                       # legend2, 
+                        legend3, 
+                       layout_matrix = LayoutNiche)
 
@@
 ``` {r GAM Plot Blue WL}
-GamStrain = "MIT9313" # MIT9313 MED4 SS120
+GamStrain = "SS120" # MIT9313 MED4 SS120
 GamColor = "Blue"
@@
     #facet_grid(cols = vars(O2_uM)) +
-    labs(title = bquote("F.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
+    # labs(title = bquote("F.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
    theme_classic() +
@@
     #facet_grid(cols = vars(O2_uM)) +
-    labs(title = bquote("E.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
+    # labs(title = bquote("E.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
   theme_classic() +
@@
     #facet_grid(cols = vars(O2_uM)) +
-    labs(title = bquote("D.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +  #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+    # labs(title = bquote("D.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +  #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
 theme_classic() +
@@
 
-# remove Photoperiod from aes when plotting 450 (Blue light)
 (g_dummy1 <- ggplot(subset(HyperChlPlotLow, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
@@
 
-p3_Blue <- grid.arrange(ContourLowO2 + theme(legend.position = 'none'), ContourIntO2 + theme(legend.position = 'none'), ContourHighO2 + theme(legend.position = 'none'), legend1, legend2, legend3, layout_matrix = LayoutNiche)
+p3_Blue <- grid.arrange(
+                        # ContourLowO2 +   labs(title = bquote("F.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
+                        #   theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
+                        ContourIntO2 +  labs(title = bquote("D.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
+                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
+                        ContourHighO2 + labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
+                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
+                        # legend1, 
+                        legend2, 
+                        legend3, 
+                        layout_matrix = LayoutNiche)
 
@@
 
+#combine red and blue GAM plots
 CombinedGAM <- plot_grid(p3_Red, p3_Blue, nrow = 1)
 
+# common x-axis title
 x.grob <- textGrob("Photoperiod (h)", 
                    gp = gpar(fontsize = 20))
-
+# common y-axis title
 y.grob <- textGrob("PAR (µmol photons"~ m^-2~ ~s^-1~ ")", 
@@
 
-#add to plot
-
+#add titles to plot
 LabelledCombinedGam <- grid.arrange(arrangeGrob(CombinedGAM, left = y.grob, bottom = x.grob))
@@
 ```{r save png}
- ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = LabelledCombinedGam,  height = 10, width = 10)
+ ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(GamStrain, "GAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = LabelledCombinedGam,  height = 10, width = 10)
 ```

### 2024-03-09 Code/Manuscript_O2.Rmd
Knitted new GAM figures

@@
 
-knitr::include_graphics(file.path(FiguresIn, "PICO_Hypervolume_GAM_MED4_Oxy_.png"))
+knitr::include_graphics(file.path(FiguresIn, "MED4GAM.png"))
 
@@
 
-knitr::include_graphics(file.path(FiguresIn, "PICO_Hypervolume_GAM_SS120_Oxy_.png"))
+knitr::include_graphics(file.path(FiguresIn, "SS120GAM.png"))
 
@@
 
-knitr::include_graphics(file.path(FiguresIn, "PICO_Hypervolume_GAM_MIT9313_Oxy_.png"))
+knitr::include_graphics(file.path(FiguresIn, "MIT9313GAM.png"))
 

### 2024-03-09 Code/Plots_GAM.Rmd
Scaling was still off- Had to reduce the y-axis textsize a bit

@@
 ``` {r GAM Plot Red WL}
-GamStrain = "SS120" # MIT9313 MED4 SS120
+GamStrain = "MIT9313" # MIT9313 MED4 SS120
 GamColor = "Red" 
@@
     theme_classic() +
-    theme(axis.text=element_text(size=20),
+    theme(axis.text=element_text(size=15),
           axis.title.x = element_text(size=20),
@@
    theme_classic() +
-  theme(axis.text=element_text(size=20),
+  theme(axis.text=element_text(size=15),
           axis.title.x = element_text(size=20),
@@
     theme_classic() +
-   theme(axis.text=element_text(size=20),
+   theme(axis.text=element_text(size=15),
           axis.title.x = element_text(size=20),
@@
 LayoutNiche <- rbind(
-                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2
-                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2
+                     c(3, 3, 3, 3, 6), # For 2.5 uM O2
+                     c(3, 3, 3, 3, 6), # For 2.5 uM O2
                      c(2, 2, 2, 2, 5),   # For 25 uM O2
@@
 p3_Red <- grid.arrange(
-  # ContourLowO2 +   labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
-                         # theme(legend.position = 'none'), 
+                       ContourLowO2 +   labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
+                          theme(legend.position = 'none'), 
                        ContourIntO2 + labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
@@
                         legend1, 
-                       # legend2, 
+                        legend2, 
                         legend3, 
@@
 ``` {r GAM Plot Blue WL}
-GamStrain = "SS120" # MIT9313 MED4 SS120
+GamStrain = "MIT9313" # MIT9313 MED4 SS120
 GamColor = "Blue"
@@
    theme_classic() +
-   theme(axis.text=element_text(size=20),
+   theme(axis.text=element_text(size=15),
           axis.title.x = element_text(size=20),
@@
   theme_classic() +
-   theme(axis.text=element_text(size=20),
+   theme(axis.text=element_text(size=15),
           axis.title.x = element_text(size=20),
@@
 theme_classic() +
-   theme(axis.text=element_text(size=20),
+   theme(axis.text=element_text(size=15),
           axis.title.x = element_text(size=20),
@@
 p3_Blue <- grid.arrange(
-                        # ContourLowO2 +   labs(title = bquote("F.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
-                        #   theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
-                        ContourIntO2 +  labs(title = bquote("D.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
+                         ContourLowO2 +   labs(title = bquote("F.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
                            theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
-                        ContourHighO2 + labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
+                        ContourIntO2 +  labs(title = bquote("E.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
                           theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
-                        # legend1, 
+                        ContourHighO2 + labs(title = bquote("D.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
+                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
+                         legend1, 
                         legend2, 
@@
 #combine red and blue GAM plots
-CombinedGAM <- plot_grid(p3_Red, p3_Blue, nrow = 1)
+CombinedGAM <- plot_grid(p3_Red, p3_Blue, nrow = 1, align = "v")
 

### 2024-03-09 Code/Manuscript_O2.Rmd
Amanda edits to FtsH terminology

@@
 
-*Prochlorococcus marinus*, the smallest picocyanobacterium, comprises multiple clades with distinct niches across tropical and sub-tropical oligotrophic ocean regions, including Oxygen Minimum Zones.
-Ocean warming may open permissive temperatures in new, poleward photic regimes, along with expanded Oxygen Minimum Zones.
-We used ocean protein data [@saitoPeptidesTheirSpectral2018] to help guide testing of *Prochlorococcus marinus* growth across a matrix of peak irradiances, photoperiods, spectral bands and dissolved oxygen.
-MED4 from Clade HLI requires greater than 4 h photoperiod, grows at 25 µmol O~2~ L^-1^ and above, and exploits high cumulative diel photon doses, yet shows accelerated growth when the cost of photoinactivation is lowered under red, vs.
-blue, actinic light.
-MED4 relies upon an alternative oxidase to balance electron transport, which may exclude it from growth under our lowest 2.5 µmol O~2~ L^-1^ condition.
-SS120 from Clade LLIII is restricted to low light under full 250 µmol O~2~ L^-1^ , shows expanded light exploitation under  25 µmol O~2~ L^-1^, but is excluded from growth under 2.5 µmol O~2~ L^-1^.
-Intermediate oxygen suppresses the cost of PSII photoinactivation, and enzymatic production of H~2~O~2~ in SS120, which has limited genomic capacity for PSII and DNA repair.
-MIT9313 from Clade LLIV is restricted to low blue irradiance under 250 µmol O~2~ L^-1^, but exploits much higher irradiance under red light, or under lower O~2~ concentrations, conditions which slow photoinactivation of PSII and production of reactive oxygen species.
+*Prochlorococcus marinus*, the smallest picocyanobacterium, comprises
+multiple clades with distinct niches across tropical and sub-tropical
+oligotrophic ocean regions, including Oxygen Minimum Zones. Ocean
+warming may open permissive temperatures in new, poleward photic
+regimes, along with expanded Oxygen Minimum Zones. We used ocean protein
+data [@saitoPeptidesTheirSpectral2018] to help guide testing of
+*Prochlorococcus marinus* growth across a matrix of peak irradiances,
+photoperiods, spectral bands and dissolved oxygen. MED4 from Clade HLI
+requires greater than 4 h photoperiod, grows at 25 µmol O~2~ L^-1^ and
+above, and exploits high cumulative diel photon doses, yet shows
+accelerated growth when the cost of photoinactivation is lowered under
+red, vs. blue, actinic light. MED4 relies upon an alternative oxidase to
+balance electron transport, which may exclude it from growth under our
+lowest 2.5 µmol O~2~ L^-1^ condition. SS120 from Clade LLIII is
+restricted to low light under full 250 µmol O~2~ L^-1^ , shows expanded
+light exploitation under 25 µmol O~2~ L^-1^, but is excluded from growth
+under 2.5 µmol O~2~ L^-1^. Intermediate oxygen suppresses the cost of
+PSII photoinactivation, and enzymatic production of H~2~O~2~ in SS120,
+which has limited genomic capacity for PSII and DNA repair. MIT9313 from
+Clade LLIV is restricted to low blue irradiance under 250 µmol O~2~
+L^-1^, but exploits much higher irradiance under red light, or under
+lower O~2~ concentrations, conditions which slow photoinactivation of
+PSII and production of reactive oxygen species.
 
@@
 ## *Prochlorococcus marinus* diversity {.unnumbered}
-*Prochlorococcus*, a genus of Cyanobacteria, is the smallest known photosynthetic prokaryote, with cell diameters ranging from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992].
-Despite small cell size, *P.
-marinus* contribute 13 to 48% of net primary production in oligotrophic oceans, corresponding to about 30% of global oxygen production [@partenskyProchlorococcusMarinePhotosynthetic1999].
-*Prochlorococcus marinus* growth is currently limited to between latitudes of 40°N to 40°S in open ocean waters, from surface to 300 m depth, thus spanning 3 orders of magnitudes of light irradiance [@partenskyProchlorococcusMarinePhotosynthetic1999; @chisholmProchlorococcusMarinusNov1992].
-
-*Prochlorococcus marinus* comprises many strains, organized into clades, defined by 16S-23S intergenic transcribed ribosomal sequence signatures [@rocapGenomeDivergenceTwo2003].
-The clades inhabit distinct ecological niches [@moorePhysiologyMolecularPhylogeny1998], originally defined as High-Light (HL) or Low-Light (LL).
-Only 5 out of 12 known *Prochlorococcus* genetic clades have cultured representatives to date; HLI, HLII, LLI, LLII/III and LIV [@billerProchlorococcusStructureFunction2015].
-Current niches of *P.
-marinus* strains span ocean water columns [@veldhuisVerticalDistributionPigment1990; @chisholmNovelFreelivingProchlorophyte1988; @partenskyProchlorococcusMarinePhotosynthetic1999] and extend into regions with low dissolved oxygen concentrations [@partenskyProchlorococcusAdvantagesLimits2010; @goerickeNovelNicheProchlorococcus2000; @lavinNovelLineagesProchlorococcus2010; @ulloaCyanobacteriumProchlorococcusHas2021; @garcia-robledoCrypticOxygenCycling2017].
-
-Low-Light clades thrive in deeper ocean waters, extending beyond 200 m in depth [@partenskyProchlorococcusMarinePhotosynthetic1999], where only ~1% of the surface irradiance penetrates, primarily in the blue (450 nm) to green (520 nm) spectral range [@holtropVibrationalModesWater2021].
-Clade LLI includes cultured strain NATL2A, which prefers moderate irradiances typical of between 30 and 100 m depth.
-Clades LLII and LLIII, including cultured strain SS120, are grouped together as the second oldest phylogenetic lineage diversifying in the *P.
-marinus* radiation, with an affinity for low light.
-Clade LLIV, including cultured strain MIT9313, falls near the base of the *Prochlorococcus* radiation, and is characterized by preference for low light, typical of depths from 120 m to 200 m [@partenskyProchlorococcusMarinePhotosynthetic1999].
-LLIV members are, as yet, the only cultured strains to have been found in Oxygen Minimum Zones (OMZ).
-Some, as yet, uncultured *P.
-marinus* strains in clades LLV and LLVI also thrive in OMZ of the subtropical Atlantic and Pacific Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20 µM [@ulloaCyanobacteriumProchlorococcusHas2021; @lavinNovelLineagesProchlorococcus2010; @goerickeNovelNicheProchlorococcus2000; @garcia-robledoCrypticOxygenCycling2017; @johnsonEnergeticsGrowthKinetics1999].
-*Prochlorococcus marinus* LL ecotypes may indeed dominate the phytoplankton within OMZ [@lavinNovelLineagesProchlorococcus2010; @ulloaCyanobacteriumProchlorococcusHas2021; @partenskyProchlorococcusAdvantagesLimits2010], where they may be net O~2~ consumers [@partenskyComparisonPhotosyntheticPerformances2018].
-
-High-Light clades are more recently branching lineages, with reduced genome sizes in comparison to LL clades.
-High-Light clades are typically dominant picophytoplankters in near-surface, oligotrophic waters, characterized by high light levels and subdivided into clades based on iron adaptation [@johnsonNichePartitioningProchlorococcus2006; @zinserInfluenceLightTemperature2007; @kentParallelPhylogeographyProchlorococcus2019].
-Clade HLI, represented by cultured strain MED4, is adapted to high iron, and low temperatures, and originated from 5 m depth in the Mediterranean Sea [@partenskyProchlorococcusMarinePhotosynthetic1999].
-Clade HLII, adapted to high iron, and high temperatures, is the most abundant *P.
-marinus* clade in the North Atlantic and North Pacific Oceans, often constituting over 90% of the total population [@partenskyProchlorococcusMarinePhotosynthetic1999], and are most numerous around 50 m depth [@partenskyProchlorococcusMarinePhotosynthetic1999].
-Clade HLIII/IV is adapted to low iron [@kentParallelPhylogeographyProchlorococcus2019; @johnsonNichePartitioningProchlorococcus2006; @zinserInfluenceLightTemperature2007].
-
-*Prochlorococcus marinus* clades are nonetheless found in environments beyond their optimal habitats.
-HL clades inhabit depths overlapping with LL ecotypes [@westNichePartitioningProchlorococcusPopulations1999; @zinserInfluenceLightTemperature2007; @delmontLinkingPangenomesMetagenomes2018], while LL clades can occupy regions in OMZ at depths shallower than 40 m [@lavinNovelLineagesProchlorococcus2010], exploiting ambient light levels above what LL clades were thought to tolerate.
+
+*Prochlorococcus*, a genus of Cyanobacteria, is the smallest known
+photosynthetic prokaryote, with cell diameters ranging from 0.5 to 0.7
+µm [@chisholmProchlorococcusMarinusNov1992]. Despite small cell size,
+*P. marinus* contribute 13 to 48% of net primary production in
+oligotrophic oceans, corresponding to about 30% of global oxygen
+production [@partenskyProchlorococcusMarinePhotosynthetic1999].
+*Prochlorococcus marinus* growth is currently limited to between
+latitudes of 40°N to 40°S in open ocean waters, from surface to 300 m
+depth, thus spanning 3 orders of magnitudes of light irradiance
+[@partenskyProchlorococcusMarinePhotosynthetic1999;
+@chisholmProchlorococcusMarinusNov1992].
+
+*Prochlorococcus marinus* comprises many strains, organized into clades,
+defined by 16S-23S intergenic transcribed ribosomal sequence signatures
+[@rocapGenomeDivergenceTwo2003]. The clades inhabit distinct ecological
+niches [@moorePhysiologyMolecularPhylogeny1998], originally defined as
+High-Light (HL) or Low-Light (LL). Only 5 out of 12 known
+*Prochlorococcus* genetic clades have cultured representatives to date;
+HLI, HLII, LLI, LLII/III and LIV
+[@billerProchlorococcusStructureFunction2015]. Current niches of *P.
+marinus* strains span ocean water columns
+[@veldhuisVerticalDistributionPigment1990;
+@chisholmNovelFreelivingProchlorophyte1988;
+@partenskyProchlorococcusMarinePhotosynthetic1999] and extend into
+regions with low dissolved oxygen concentrations
+[@partenskyProchlorococcusAdvantagesLimits2010;
+@goerickeNovelNicheProchlorococcus2000;
+@lavinNovelLineagesProchlorococcus2010;
+@ulloaCyanobacteriumProchlorococcusHas2021;
+@garcia-robledoCrypticOxygenCycling2017].
+
+Low-Light clades thrive in deeper ocean waters, extending beyond 200 m
+in depth [@partenskyProchlorococcusMarinePhotosynthetic1999], where only
+\~1% of the surface irradiance penetrates, primarily in the blue (450
+nm) to green (520 nm) spectral range
+[@holtropVibrationalModesWater2021]. Clade LLI includes cultured strain
+NATL2A, which prefers moderate irradiances typical of between 30 and 100
+m depth. Clades LLII and LLIII, including cultured strain SS120, are
+grouped together as the second oldest phylogenetic lineage diversifying
+in the *P. marinus* radiation, with an affinity for low light. Clade
+LLIV, including cultured strain MIT9313, falls near the base of the
+*Prochlorococcus* radiation, and is characterized by preference for low
+light, typical of depths from 120 m to 200 m
+[@partenskyProchlorococcusMarinePhotosynthetic1999]. LLIV members are,
+as yet, the only cultured strains to have been found in Oxygen Minimum
+Zones (OMZ). Some, as yet, uncultured *P. marinus* strains in clades LLV
+and LLVI also thrive in OMZ of the subtropical Atlantic and Pacific
+Oceans, where dissolved oxygen concentrations [O~2~] can be less than 20
+µM [@ulloaCyanobacteriumProchlorococcusHas2021;
+@lavinNovelLineagesProchlorococcus2010;
+@goerickeNovelNicheProchlorococcus2000;
+@garcia-robledoCrypticOxygenCycling2017;
+@johnsonEnergeticsGrowthKinetics1999]. *Prochlorococcus marinus* LL
+ecotypes may indeed dominate the phytoplankton within OMZ
+[@lavinNovelLineagesProchlorococcus2010;
+@ulloaCyanobacteriumProchlorococcusHas2021;
+@partenskyProchlorococcusAdvantagesLimits2010], where they may be net
+O~2~ consumers [@partenskyComparisonPhotosyntheticPerformances2018].
+
+High-Light clades are more recently branching lineages, with reduced
+genome sizes in comparison to LL clades. High-Light clades are typically
+dominant picophytoplankters in near-surface, oligotrophic waters,
+characterized by high light levels and subdivided into clades based on
+iron adaptation [@johnsonNichePartitioningProchlorococcus2006;
+@zinserInfluenceLightTemperature2007;
+@kentParallelPhylogeographyProchlorococcus2019]. Clade HLI, represented
+by cultured strain MED4, is adapted to high iron, and low temperatures,
+and originated from 5 m depth in the Mediterranean Sea
+[@partenskyProchlorococcusMarinePhotosynthetic1999]. Clade HLII, adapted
+to high iron, and high temperatures, is the most abundant *P. marinus*
+clade in the North Atlantic and North Pacific Oceans, often constituting
+over 90% of the total population
+[@partenskyProchlorococcusMarinePhotosynthetic1999], and are most
+numerous around 50 m depth
+[@partenskyProchlorococcusMarinePhotosynthetic1999]. Clade HLIII/IV is
+adapted to low iron [@kentParallelPhylogeographyProchlorococcus2019;
+@johnsonNichePartitioningProchlorococcus2006;
+@zinserInfluenceLightTemperature2007].
+
+*Prochlorococcus marinus* clades are nonetheless found in environments
+beyond their optimal habitats. HL clades inhabit depths overlapping with
+LL ecotypes [@westNichePartitioningProchlorococcusPopulations1999;
+@zinserInfluenceLightTemperature2007;
+@delmontLinkingPangenomesMetagenomes2018], while LL clades can occupy
+regions in OMZ at depths shallower than 40 m
+[@lavinNovelLineagesProchlorococcus2010], exploiting ambient light
+levels above what LL clades were thought to tolerate.
 
@@
 
-Our changing climate is rapidly altering conditions for these specialized clades of marine picophytoplankton.
-Predictions indicate a net global increase of *P.
-marinus* cell abundances of 29% [@flombaumPresentFutureGlobal2013], along with  poleward latitudinal shifts of at least 10° in marine phytoplankton niches by the end of this century  [@bartonAnthropogenicClimateChange2016] in response to warming waters, with increases in *P.
-marinus* of approximately 50% in the more poleward regions of their distributions.
-
-Near the equator, photoperiod remains nearly constant at the ocean surface, approximately 12 hours (h) of daylight and 12 h of darkness throughout the year.
-The effective length of the photoperiod does, however, attenuate with depth as dawn and dusk light at depth drops below levels needed for biological processes.
-As *P.
-marinus* potentially expands its temperature-permissive niches poleward into temperate regions  [@flombaumPresentFutureGlobal2013; @bartonAnthropogenicClimateChange2016], it will encounter more
-pronounced seasonal variations in photoperiod regimes both at surface and at depth, with potentially complex effects upon viable growth niches [@liDiatomGrowthResponses2017; @prezelinDielPeriodicityPhytoplankton1992].
-For example, Vaulot *et al*.
-@vaulotGrowthProchlorococcusPhotosynthetic1995 showed that *Prochlorococcus* replication of DNA occurs in the afternoon, while cell division occurs at night.
-To our knowledge, no study has as yet addressed *P.
-marinus* growth responses in relation to a range of photoperiods.
-
-Climate change is also rapidly changing ocean chemistry.
-By the end of this century, surface ocean pH is projected to decline by 0.1 to 0.4  due to projected increases in carbon dioxide concentrations [@garcia-sotoOverviewOceanClimate2021].
-Moreover, substantial changes in the global water cycle, leading to extensive changes in worldwide precipitation patterns, are affecting ocean salinity levels on a global scale, and ice melts due to rising temperatures are impacting salinity levels in the Arctic and Northwest Atlantic oceans [@leeRecognizingSalinityThreats2022].
-Increasing sea temperatures are also causing decreases in [O~2~] across global oceans [@matearLongtermChangesDissolved2003], particularly toward the poles [@helmObservedDecreasesOxygen2011].
-Warmer ocean waters decrease oxygen solubility at the surface, and increase stratification, which in turn decreases oxygen mixing downwards by ocean currents [@garcia-sotoOverviewOceanClimate2021].
-Models predict that OMZ in the Pacific and Indian Oceans are expanding [@garcia-sotoOverviewOceanClimate2021; @buseckeDivergingFatesPacific2022], although the cores of the OMZ, where the oxygen levels are lowest, may actually contract  [@buseckeDivergingFatesPacific2022].
-
-We used the OceansMap Protein Portal (OPP; https://proteinportal.whoi.edu/) [@saitoDevelopmentOceanProtein2021] to analyze the distribution of proteins from clades of *P.
-marinus* in samples taken across a range of [O~2~] and depth, which in turn correlates to peak light at the site of sampling.
-In parallel we analyzed the growth and physiological responses of representative strains from three clades of *P.
-marinus* under a matrix of [O~2~], light levels, spectral waveband ranges, and photoperiods, to approximate eco-physiological conditions representative of current and hypothetical future ocean zones.
-*Prochlorococcus marinus* MED4, a clade HLI strain, was isolated near the ocean surface (5m depth) of the Mediterranean Sea where [O~2~] is near saturation, light levels are high and spectral bias from full solar irradiance is minimal.
-*Prochlorococcus marinus* SS120, a clade LLII/III strain, was isolated from the Sargasso Sea at a depth of 120 m, while *P.
-marinus* MIT9313, a clade LLIV strain, was isolated from the North Atlantic Gulf Stream at a depth of 135 m [@moorePhotophysiologyMarineCyanobacterium1999].
-At these depths, light attenuation and spectral shifts occur, resulting in low blue light, while [O~2~] varies from near-surface saturation levels to decreased concentrations, but does not necessarily decrease systematically with depth [@billheimerOxygenSeasonalityUtilization2021].
-
-Photosynthetic organisms absorb light energy within the Photosynthetically Active Radiation (PAR) range, 350 to 700 nm, for photosynthesis [@morelAvailableUsableStored1978].
-Photosynthetically Usable Radiation (PUR) represents the fraction of PAR that can be absorbed by the pigments of a given photosynthetic organism [@morelAvailableUsableStored1978], taking into account the specific spectral wavebands these pigments absorb.
-*Prochlorococcus marinus* Pcb light-harvesting complexes show an absorption maxima of 442 nm for divinyl chlorophyll *a* and 478 nm for divinyl chlorophyll *b* [@goerickePigmentsProchlorococcusMarinus1992] allowing *P.
-marinus* to efficiently harvest blue light in the 400 nm to 500 nm range [@morelAvailableUsableStored1978] corresponding to blue spectral wavelengths prevailing in deep ocean habitats [@holtropVibrationalModesWater2021].
-In *P.
-marinus* small cell diameters, from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992], and simple cell structures, minimize the complication of pigment package effect or intracellular self-shading [@morelProchlorococcusSynechococcusComparative1993] contributing to efficient optical absorption, although photosynthetic efficiency may vary among clades [@hessPhotosyntheticApparatusProchlorococcus2001; @moorePhotophysiologyMarineCyanobacterium1999].
-
-Given the different spectral light regimes typical of the niches of different ecotypes, expressing growth rates in terms of cumulative diel PUR might simplify different photoperiods, spectral bands, and PAR levels into a common parameter, making growth response comparisons across strains and different oxygen levels more accessible.
-We  aimed to detect whether growth responses are driven simply by cumulative diel PUR, or whether specific photoperiods, spectral bands or PAR levels have independent, albeit interacting, effects on growth.
-We therefore analyzed growth rates in terms of cumulative diel PUR.
-
-We discuss our findings in relation to analyses of genomic sequences [@changBRENDAELIXIRCore2021] across clades of *P.
-marinus*, showing that differences in the expression and presence of genes encoding protein turnover, oxygen-dependent enzymes, and DNA repair enzymes, can explain the differential growth responses of strains under the matrix of light and [O~2~] conditions of this study.
+Our changing climate is rapidly altering conditions for these
+specialized clades of marine picophytoplankton. Predictions indicate a
+net global increase of *P. marinus* cell abundances of 29%
+[@flombaumPresentFutureGlobal2013], along with poleward latitudinal
+shifts of at least 10° in marine phytoplankton niches by the end of this
+century [@bartonAnthropogenicClimateChange2016] in response to warming
+waters, with increases in *P. marinus* of approximately 50% in the more
+poleward regions of their distributions.
+
+Near the equator, photoperiod remains nearly constant at the ocean
+surface, approximately 12 hours (h) of daylight and 12 h of darkness
+throughout the year. The effective length of the photoperiod does,
+however, attenuate with depth as dawn and dusk light at depth drops
+below levels needed for biological processes. As *P. marinus*
+potentially expands its temperature-permissive niches poleward into
+temperate regions [@flombaumPresentFutureGlobal2013;
+@bartonAnthropogenicClimateChange2016], it will encounter more
+pronounced seasonal variations in photoperiod regimes both at surface
+and at depth, with potentially complex effects upon viable growth niches
+[@liDiatomGrowthResponses2017;
+@prezelinDielPeriodicityPhytoplankton1992]. For example, Vaulot *et al*.
+@vaulotGrowthProchlorococcusPhotosynthetic1995 showed that
+*Prochlorococcus* replication of DNA occurs in the afternoon, while cell
+division occurs at night. To our knowledge, no study has as yet
+addressed *P. marinus* growth responses in relation to a range of
+photoperiods.
+
+Climate change is also rapidly changing ocean chemistry. By the end of
+this century, surface ocean pH is projected to decline by 0.1 to 0.4 due
+to projected increases in carbon dioxide concentrations
+[@garcia-sotoOverviewOceanClimate2021]. Moreover, substantial changes in
+the global water cycle, leading to extensive changes in worldwide
+precipitation patterns, are affecting ocean salinity levels on a global
+scale, and ice melts due to rising temperatures are impacting salinity
+levels in the Arctic and Northwest Atlantic oceans
+[@leeRecognizingSalinityThreats2022]. Increasing sea temperatures are
+also causing decreases in [O~2~] across global oceans
+[@matearLongtermChangesDissolved2003], particularly toward the poles
+[@helmObservedDecreasesOxygen2011]. Warmer ocean waters decrease oxygen
+solubility at the surface, and increase stratification, which in turn
+decreases oxygen mixing downwards by ocean currents
+[@garcia-sotoOverviewOceanClimate2021]. Models predict that OMZ in the
+Pacific and Indian Oceans are expanding
+[@garcia-sotoOverviewOceanClimate2021;
+@buseckeDivergingFatesPacific2022], although the cores of the OMZ, where
+the oxygen levels are lowest, may actually contract
+[@buseckeDivergingFatesPacific2022].
+
+We used the OceansMap Protein Portal (OPP;
+<https://proteinportal.whoi.edu/>) [@saitoDevelopmentOceanProtein2021]
+to analyze the distribution of proteins from clades of *P. marinus* in
+samples taken across a range of [O~2~] and depth, which in turn
+correlates to peak light at the site of sampling. In parallel we
+analyzed the growth and physiological responses of representative
+strains from three clades of *P. marinus* under a matrix of [O~2~],
+light levels, spectral waveband ranges, and photoperiods, to approximate
+eco-physiological conditions representative of current and hypothetical
+future ocean zones. *Prochlorococcus marinus* MED4, a clade HLI strain,
+was isolated near the ocean surface (5m depth) of the Mediterranean Sea
+where [O~2~] is near saturation, light levels are high and spectral bias
+from full solar irradiance is minimal. *Prochlorococcus marinus* SS120,
+a clade LLII/III strain, was isolated from the Sargasso Sea at a depth
+of 120 m, while *P. marinus* MIT9313, a clade LLIV strain, was isolated
+from the North Atlantic Gulf Stream at a depth of 135 m
+[@moorePhotophysiologyMarineCyanobacterium1999]. At these depths, light
+attenuation and spectral shifts occur, resulting in low blue light,
+while [O~2~] varies from near-surface saturation levels to decreased
+concentrations, but does not necessarily decrease systematically with
+depth [@billheimerOxygenSeasonalityUtilization2021].
+
+Photosynthetic organisms absorb light energy within the
+Photosynthetically Active Radiation (PAR) range, 350 to 700 nm, for
+photosynthesis [@morelAvailableUsableStored1978]. Photosynthetically
+Usable Radiation (PUR) represents the fraction of PAR that can be
+absorbed by the pigments of a given photosynthetic organism
+[@morelAvailableUsableStored1978], taking into account the specific
+spectral wavebands these pigments absorb. *Prochlorococcus marinus* Pcb
+light-harvesting complexes show an absorption maxima of 442 nm for
+divinyl chlorophyll *a* and 478 nm for divinyl chlorophyll *b*
+[@goerickePigmentsProchlorococcusMarinus1992] allowing *P. marinus* to
+efficiently harvest blue light in the 400 nm to 500 nm range
+[@morelAvailableUsableStored1978] corresponding to blue spectral
+wavelengths prevailing in deep ocean habitats
+[@holtropVibrationalModesWater2021]. In *P. marinus* small cell
+diameters, from 0.5 to 0.7 µm [@chisholmProchlorococcusMarinusNov1992],
+and simple cell structures, minimize the complication of pigment package
+effect or intracellular self-shading
+[@morelProchlorococcusSynechococcusComparative1993] contributing to
+efficient optical absorption, although photosynthetic efficiency may
+vary among clades [@hessPhotosyntheticApparatusProchlorococcus2001;
+@moorePhotophysiologyMarineCyanobacterium1999].
+
+Given the different spectral light regimes typical of the niches of
+different ecotypes, expressing growth rates in terms of cumulative diel
+PUR might simplify different photoperiods, spectral bands, and PAR
+levels into a common parameter, making growth response comparisons
+across strains and different oxygen levels more accessible. We aimed to
+detect whether growth responses are driven simply by cumulative diel
+PUR, or whether specific photoperiods, spectral bands or PAR levels have
+independent, albeit interacting, effects on growth. We therefore
+analyzed growth rates in terms of cumulative diel PUR.
+
+We discuss our findings in relation to analyses of genomic sequences
+[@changBRENDAELIXIRCore2021] across clades of *P. marinus*, showing that
+differences in the expression and presence of genes encoding protein
+turnover, oxygen-dependent enzymes, and DNA repair enzymes, can explain
+the differential growth responses of strains under the matrix of light
+and [O~2~] conditions of this study.
 
@@
 
-The OceansMap Protein Portal is an open access online data repository (Woods Hole Oceanographic Institute, WHOI) of mass spectroscopy data on marine microbial peptides, sampled from various depths and locations worldwide [@saitoDevelopmentOceanProtein2021].
-We screened a subset of the OPP for proteins annotated as from *Prochlorococcus* strains, to identify differential strategies employed by strains living at varying depths and oxygen levels within the marine water column.
-We focused on proteins mediating photosynthesis and protein metabolism from depths of 20 to 200 m below the ocean surface.
-The samples for metaproteomic analyses were collected from 7 locations in the tropical North Pacific ocean along 150 W from 18 N of the equator between October 1, 2011 and October 25, 2011 during the voyage of the R/V Kilo Moana MetZyme cruise [@rollingdecktorepositoryCruiseKM1128RV2015]; original datasets in the Biological and Chemical Oceanography Data Management Office (BCO-DMO) repository [@saitoPeptidesTheirSpectral2018].
-Oxygen concentration levels at the location of sampling were recorded.
-The methodology for sample collection and peptide analysis are described by Saito *et al*.
+The OceansMap Protein Portal is an open access online data repository
+(Woods Hole Oceanographic Institute, WHOI) of mass spectroscopy data on
+marine microbial peptides, sampled from various depths and locations
+worldwide [@saitoDevelopmentOceanProtein2021]. We screened a subset of
+the OPP for proteins annotated as from *Prochlorococcus* strains, to
+identify differential strategies employed by strains living at varying
+depths and oxygen levels within the marine water column. We focused on
+proteins mediating photosynthesis and protein metabolism from depths of
+20 to 200 m below the ocean surface. The samples for metaproteomic
+analyses were collected from 7 locations in the tropical North Pacific
+ocean along 150 W from 18 N of the equator between October 1, 2011 and
+October 25, 2011 during the voyage of the R/V Kilo Moana MetZyme cruise
+[@rollingdecktorepositoryCruiseKM1128RV2015]; original datasets in the
+Biological and Chemical Oceanography Data Management Office (BCO-DMO)
+repository [@saitoPeptidesTheirSpectral2018]. Oxygen concentration
+levels at the location of sampling were recorded. The methodology for
+sample collection and peptide analysis are described by Saito *et al*.
 [@saitoMultipleNutrientStresses2014; @saitoNeedlesBlueSea2015].
@@
 
-Metaproteomic datasets were obtained from the KM1128 entry in the BCO-DMO database [@saitoPeptidesTheirSpectral2018] accessed via the OPP in June 2019. Datasets contained:
-	i) Peptide sequences and sample identification (ID) number;
-	ii) Sample ID number, station, depth in meters below the surface the sample was collected at, best-hit BLASTP protein and species annotation and the corresponding Uniprot Entry number for the identified proteins;
-	iii) Sample station depth and [O~2~].  
-	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using *tidyverse* package [@R-tidyverse] running under R v4.1.3 and RStudio v2023.06.0 [@RStudio].
-The resulting merged dataset was filtered for those *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b~6~f (Cytb~6~f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Plastoquinol Terminal Oxidase (PTOX); Plastocyanin (PC); Ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  Adenosine triphosphate (ATP) Synthase;  FtsH proteases (FtsH) or ribosomes.
-Detected peptides were re-annotated for consistency and labelled, where feasible, according to strain, clade, subunit and protein complex.
-Full protein sequences corresponding to detected proteins were obtained from UniProt (https://www.uniprot.org/) and analyzed in Molecular Evolution and Genetic Analyses X (MEGAX) software  (https://www.megasoftware.net/).
-Sequences for proteins for each of the thirteen *Prochlorococcus* strains identified in the dataset were aligned with MUSCLE using UPGMA cluster method and a lambda of 24 with a -2.9 gap open penalty and 1.20 hydrophobicity multiplier.
-Overall mean pairwise distance between protein sequences was determined using bootstrap variance estimation methods.
-Maximum likelihood phylogenetic trees were assembled using 1000 bootstrap replications with a 95% site coverage cut off.
-*Prochlorococcus* FtsH isoform identities, and functions, were inferred by sequence comparisons to the characterized four isoforms of FtsH protease of *Synechocystis* sp.
-PCC6803 [@bonisteelStrainSpecificDifferences2018].
-Data for each strain was plotted against depth and [O~2~] and sampling station.
-
-When assessing the presence of a particular protein complex at a sampling location, all peptides belonging to all subunits of the complex were included to give the greatest number of data points.
-As this data was acquired on a discovery mission rather than through targeted peptide approaches, it is difficult to discern accuracies of strain assignment annotations, particularly as the proteins of interest in this study are highly conserved across strains.
-We are, however, confident in clade classifications for each protein examined.
-The data is also limited because a peptide sequence was not determined unless there was already a known spectrum for that peptide in the SEQUEST database, hence some peptides of interest may not be identifiable.
-Furthermore, a peptide must be detected above a certain threshold abundance in order to be considered an accurate ‘hit’.
+Metaproteomic datasets were obtained from the KM1128 entry in the
+BCO-DMO database [@saitoPeptidesTheirSpectral2018] accessed via the OPP
+in June 2019. Datasets contained: i) Peptide sequences and sample
+identification (ID) number; ii) Sample ID number, station, depth in
+meters below the surface the sample was collected at, best-hit BLASTP
+protein and species annotation and the corresponding Uniprot Entry
+number for the identified proteins; iii) Sample station depth and
+[O~2~].\
+The depth and [O~2~] were joined to peptide sequence and BLASTP
+annotations by ID number, depth and station using *tidyverse* package
+[@R-tidyverse] running under R v4.1.3 and RStudio v2023.06.0 [@RStudio].
+The resulting merged dataset was filtered for those *Prochlorococcus*
+peptides, detected from 0 to 300 m below the surface, annotated as a
+subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb);
+Photosystem II (PSII); Cytochrome b~6~f (Cytb~6~f); Photosystem I (PSI);
+NADPH Dehydrogenase (NDH); Plastoquinol Terminal Oxidase (PTOX);
+Plastocyanin (PC); Ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase
+(RUBISCO); Adenosine triphosphate (ATP) Synthase; FtsH proteases (FtsH)
+or ribosomes. Detected peptides were re-annotated for consistency and
+labelled, where feasible, according to strain, clade, subunit and
+protein complex. Full protein sequences corresponding to detected
+proteins were obtained from UniProt (<https://www.uniprot.org/>) and
+analyzed in Molecular Evolution and Genetic Analyses X (MEGAX) software
+(<https://www.megasoftware.net/>). Sequences for proteins for each of
+the thirteen *Prochlorococcus* strains identified in the dataset were
+aligned with MUSCLE using UPGMA cluster method and a lambda of 24 with a
+-2.9 gap open penalty and 1.20 hydrophobicity multiplier. Overall mean
+pairwise distance between protein sequences was determined using
+bootstrap variance estimation methods. Maximum likelihood phylogenetic
+trees were assembled using 1000 bootstrap replications with a 95% site
+coverage cut off. *Prochlorococcus* FtsH isoform identities, and
+functions, were inferred by sequence comparisons to the characterized
+four isoforms of FtsH protease of *Synechocystis* sp. PCC6803
+[@bonisteelStrainSpecificDifferences2018]. Data for each strain was
+plotted against depth and [O~2~] and sampling station.
+
+When assessing the presence of a particular protein complex at a
+sampling location, all peptides belonging to all subunits of the complex
+were included to give the greatest number of data points. As this data
+was acquired on a discovery mission rather than through targeted peptide
+approaches, it is difficult to discern accuracies of strain assignment
+annotations, particularly as the proteins of interest in this study are
+highly conserved across strains. We are, however, confident in clade
+classifications for each protein examined. The data is also limited
+because a peptide sequence was not determined unless there was already a
+known spectrum for that peptide in the SEQUEST database, hence some
+peptides of interest may not be identifiable. Furthermore, a peptide
+must be detected above a certain threshold abundance in order to be
+considered an accurate ‘hit’.
 
@@
 
-*Prochlorococcus* remain challenging to culture, as their reduced genomes – the smallest of any known oxyphototroph – render them partially dependent upon mutualistic heterotrophic bacteria to detoxify reactive oxygen species [@morrisFacilitationRobustGrowth2008; @morrisDependenceCyanobacteriumProchlorococcus2011].
-MED4, SS120 and MIT9313 have been successfully cultured in laboratories [@mooreComparativePhysiologySynechococcus1995; @mooreCulturingMarineCyanobacterium2007], and used to show that ecotypic classifications correspond to biochemical differences among strains [@bonisteelStrainSpecificDifferences2018].
-Three xenic cultures of *P.
-marinus* were obtained from Bigelow Labs, NCMA Maine, USA.
-MED4 (CCMP1986) is from High-Light adapted (HLI) clade; SS120 (CCMP1375) is from Low-Light adapted (LLII/III) clade; and MIT9313 (CCMP2773) is from Low-Light adapted (LLIV) clade.
-Cultures were maintained in incubators set to 22°C with an on/off light/dark cycle of 12 h.
-The PAR level for maintenance cultures reflected PAR in the source niche of the ecotype; MED4, of 160 µmol photons m^-2^ s^-1^ with illumination from STANDARD Products Inc.
-Cool White F24T5/41K/8/HO/PS/G5/STD, 24 watts, fluorescent bulbs; SS120 and MIT9313 at 30 µmol photons m^-2^ s^-1^ with illumination from Philips Cool White F14T5/841 Alto, 14 watts, fluorescent bulbs.
-To maintain active growth all strains were transferred weekly with 1 in 5 dilutions with Pro99 media [@mooreCulturingMarineCyanobacterium2007] prepared with autoclaved artificial seawater [@bergesEvolutionArtificialSeawater2001].
-
-Controlled growth experiments were performed using MCMIX-OD or MC1000-OD PSI Multicultivators (Figure \@ref(fig:LabeledMC); PSI, Drásov, Czech Republic).
-Each multicultivator individually controls 8 tubes at a common temperature of 22°C.
-Each tube containing 70 mL of Pro99 media was inoculated with 10 mL of growing maintenance culture.
-In a factorial matrix design, each tube was then subject to an individual combination of sinusoidal photoperiod (4, 8, 12, 16  h);  reaching a peak PAR (30, 90, 180 µmol photons m^-2^ s^-1^), with defined spectral bandwidth (White LED, 660 nm, 450 nm).
-[O~2~] levels (2.5 µM, 25 µM, 250 µM) were imposed by bubbling tubes with varying ratios of air and
-Nitrogen (N~2~), with consistent 0.05% of Carbon Dioxide (CO~2~) gas, delivered through a 0.2 μm sterile microfilter via a G400 gas mixing system (Qubit Systems Inc., Kingston, Ontario, Canada).
-[O~2~] *in situ* was verified using oxygen optodes (PyroScience, Germany) inserted into tubes for real-time measurements, with a temperature probe in
-the bath of the bioreactor to correct [O~2~] measures for temperature fluctuations.
-In addition, the Pyroscience software corrected [O~2~] based on the salinity of the media (32 ppt).
-The flow rate of the gas mixture was controlled, but variations in bubbling speed, PAR and culture density affected the [O~2~] achieved in each tube.
-A low [O~2~] of 0.5 µM - 5 µM (reported as 2.5 µM hereafter),  was achieved by sparging with a gas mixture containing 99.95% N~2~ and 0.05% CO~2~.
-An intermediate [O~2~] of 10 - 25 µM (reported hereafter as 25 µM) was achieved by sparging with a gas mixture containing 98.95% N~2~, 0.05% CO~2~ and 1% O~2~.
-A high O~2~ of 200 µM - 280 µM (reported hereafter as 250 µM) was achieved by sparging with lab air (78% N~2~, 21% O~2~, 1% Ar and 0.05% CO~2~).
-
-The full crossing of all factor levels would yield 4 x 3 x 3 x 3 = 108 treatments, x 3 strains for 324 possible combinations.
-Consistent absence of growth of some strains under some levels of photoperiod, PAR, or [O~2~] meant we completed 268 growth factor treatment combinations.
-
-*In situ* measurements of Optical Density (OD) 680 nm, a proxy for cell suspension density, cell size dependent scatter and cell chlorophyll content;  and OD 720 nm, a proxy for cell suspension density and cell size dependent scatter, were recorded every 5 minutes over least 8 to 14 days,  depending on the duration of the lag phase, if any.
-
-PAR of 180, 90 or 30 µmol photons m^-2^ s^-1^, and spectral wavebands (white LED full spectrum, 660 nm (red light), and 450 nm (blue light)) were chosen to approximate light
-levels and spectral colours spanning the vertical ocean water column, from near-surface to the lower euphotic zone depths.
-Photoperiods were chosen to approximate diel cycles characteristic of current and hypothetical future niches of *P.
-marinus*; 16 h represents temperate (45°N) summer at the ocean surface; 12 h for equatorial (0°N)
-ocean surface or temperate (45°N) spring and fall ocean surface or temperate (45°N) summer at deeper ocean depths; 8 h for temperate (45°N) winter at the surface or at temperate (45°N) spring and fall at depth and equatorial (0°N) deep ocean depths; and 4 h for temperate (45°N) winter or deep ocean depths during temperate (45°N) spring and fall.
+*Prochlorococcus* remain challenging to culture, as their reduced
+genomes – the smallest of any known oxyphototroph – render them
+partially dependent upon mutualistic heterotrophic bacteria to detoxify
+reactive oxygen species [@morrisFacilitationRobustGrowth2008;
+@morrisDependenceCyanobacteriumProchlorococcus2011]. MED4, SS120 and
+MIT9313 have been successfully cultured in laboratories
+[@mooreComparativePhysiologySynechococcus1995;
+@mooreCulturingMarineCyanobacterium2007], and used to show that ecotypic
+classifications correspond to biochemical differences among strains
+[@bonisteelStrainSpecificDifferences2018]. Three xenic cultures of *P.
+marinus* were obtained from Bigelow Labs, NCMA Maine, USA. MED4
+(CCMP1986) is from High-Light adapted (HLI) clade; SS120 (CCMP1375) is
+from Low-Light adapted (LLII/III) clade; and MIT9313 (CCMP2773) is from
+Low-Light adapted (LLIV) clade. Cultures were maintained in incubators
+set to 22°C with an on/off light/dark cycle of 12 h. The PAR level for
+maintenance cultures reflected PAR in the source niche of the ecotype;
+MED4, of 160 µmol photons m^-2^ s^-1^ with illumination from STANDARD
+Products Inc. Cool White F24T5/41K/8/HO/PS/G5/STD, 24 watts, fluorescent
+bulbs; SS120 and MIT9313 at 30 µmol photons m^-2^ s^-1^ with
+illumination from Philips Cool White F14T5/841 Alto, 14 watts,
+fluorescent bulbs. To maintain active growth all strains were
+transferred weekly with 1 in 5 dilutions with Pro99 media
+[@mooreCulturingMarineCyanobacterium2007] prepared with autoclaved
+artificial seawater [@bergesEvolutionArtificialSeawater2001].
+
+Controlled growth experiments were performed using MCMIX-OD or MC1000-OD
+PSI Multicultivators (Figure \@ref(fig:LabeledMC); PSI, Drásov, Czech
+Republic). Each multicultivator individually controls 8 tubes at a
+common temperature of 22°C. Each tube containing 70 mL of Pro99 media
+was inoculated with 10 mL of growing maintenance culture. In a factorial
+matrix design, each tube was then subject to an individual combination
+of sinusoidal photoperiod (4, 8, 12, 16 h); reaching a peak PAR (30, 90,
+180 µmol photons m^-2^ s^-1^), with defined spectral bandwidth (White
+LED, 660 nm, 450 nm). [O~2~] levels (2.5 µM, 25 µM, 250 µM) were imposed
+by bubbling tubes with varying ratios of air and Nitrogen (N~2~), with
+consistent 0.05% of Carbon Dioxide (CO~2~) gas, delivered through a 0.2
+μm sterile microfilter via a G400 gas mixing system (Qubit Systems Inc.,
+Kingston, Ontario, Canada). [O~2~] *in situ* was verified using oxygen
+optodes (PyroScience, Germany) inserted into tubes for real-time
+measurements, with a temperature probe in the bath of the bioreactor to
+correct [O~2~] measures for temperature fluctuations. In addition, the
+Pyroscience software corrected [O~2~] based on the salinity of the media
+(32 ppt). The flow rate of the gas mixture was controlled, but
+variations in bubbling speed, PAR and culture density affected the
+[O~2~] achieved in each tube. A low [O~2~] of 0.5 µM - 5 µM (reported as
+2.5 µM hereafter), was achieved by sparging with a gas mixture
+containing 99.95% N~2~ and 0.05% CO~2~. An intermediate [O~2~] of 10 -
+25 µM (reported hereafter as 25 µM) was achieved by sparging with a gas
+mixture containing 98.95% N~2~, 0.05% CO~2~ and 1% O~2~. A high O~2~ of
+200 µM - 280 µM (reported hereafter as 250 µM) was achieved by sparging
+with lab air (78% N~2~, 21% O~2~, 1% Ar and 0.05% CO~2~).
+
+The full crossing of all factor levels would yield 4 x 3 x 3 x 3 = 108
+treatments, x 3 strains for 324 possible combinations. Consistent
+absence of growth of some strains under some levels of photoperiod, PAR,
+or [O~2~] meant we completed 268 growth factor treatment combinations.
+
+*In situ* measurements of Optical Density (OD) 680 nm, a proxy for cell
+suspension density, cell size dependent scatter and cell chlorophyll
+content; and OD 720 nm, a proxy for cell suspension density and cell
+size dependent scatter, were recorded every 5 minutes over least 8 to 14
+days, depending on the duration of the lag phase, if any.
+
+PAR of 180, 90 or 30 µmol photons m^-2^ s^-1^, and spectral wavebands
+(white LED full spectrum, 660 nm (red light), and 450 nm (blue light))
+were chosen to approximate light levels and spectral colours spanning
+the vertical ocean water column, from near-surface to the lower euphotic
+zone depths. Photoperiods were chosen to approximate diel cycles
+characteristic of current and hypothetical future niches of *P.
+marinus*; 16 h represents temperate (45°N) summer at the ocean surface;
+12 h for equatorial (0°N) ocean surface or temperate (45°N) spring and
+fall ocean surface or temperate (45°N) summer at deeper ocean depths; 8
+h for temperate (45°N) winter at the surface or at temperate (45°N)
+spring and fall at depth and equatorial (0°N) deep ocean depths; and 4 h
+for temperate (45°N) winter or deep ocean depths during temperate (45°N)
+spring and fall.
 
 ## Growth rate analysis {.unnumbered}
-Data files (.csv) saved from the Multicultivator software were imported into R-Studio for data management [@R-tidyverse], growth rate calculations, comparisons of model fits [@harrisonPhotosynthesisirradianceRelationshipsPolar1986], and visualization.
-The chlorophyll proxy optical density (OD~680~ - OD~720~;  ΔOD) was used to determine the chlorophyll specific growth rate (µ, d^-1^) for each treatment combination.
-We first used a rolling mean from the R package *`zoo`* [@R-zoo] to calculate the average ΔOD data over a 1-hour window to lower the influence of outlier points and remove data points collected during post stationary phase, when applicable.
-We used the Levenberg-Marquardt algorithm [@bellaviaLevenbergMarquardtMethod2018] modification of the non-linear least squares,  using the R package *`minpack.lm`*
-[@R-minpack.lm], to fit a logistic equation (Equation \@ref(eq:GrowthRate)); where ΔOD~max~ is maximum ΔOD, ΔOD~min~ is minimum ΔOD, t is time
-duration over the growth trajectory.
-
+
+Data files (.csv) saved from the Multicultivator software were imported
+into R-Studio for data management [@R-tidyverse], growth rate
+calculations, comparisons of model fits
+[@harrisonPhotosynthesisirradianceRelationshipsPolar1986], and
+visualization. The chlorophyll proxy optical density (OD~680~ - OD~720~;
+ΔOD) was used to determine the chlorophyll specific growth rate (µ,
+d^-1^) for each treatment combination. We first used a rolling mean from
+the R package *`zoo`* [@R-zoo] to calculate the average ΔOD data over a
+1-hour window to lower the influence of outlier points and remove data
+points collected during post stationary phase, when applicable. We used
+the Levenberg-Marquardt algorithm
+[@bellaviaLevenbergMarquardtMethod2018] modification of the non-linear
+least squares, using the R package *`minpack.lm`* [@R-minpack.lm], to
+fit a logistic equation (Equation \@ref(eq:GrowthRate)); where ΔOD~max~
+is maximum ΔOD, ΔOD~min~ is minimum ΔOD, t is time duration over the
+growth trajectory.
+
+```{=tex}
 \begin{equation}
@@
 \end{equation}
-
-Figure \@ref(fig:deltaODLogGrowthPlot) is an example of chlorophyll specific growth estimates fitted from the high resolution ΔOD measurements for each tube in a Multicultivator.
-The residuals of the logistic growth curve fit are shown and the growth spectral waveband is plotted and illustrates the imposed PAR (µmol photons m^-2^ s^-1^) and photoperiod
-(h).
-
-A Generalized Additive Model (GAM) [@woodGeneralizedAdditiveModels2017] was applied to the relation of chlorophyll-specific µ, d^-1^  to photoperiod and PAR level,  for each growth [O~2~] level, and for the blue and red wavebands for growth, for each *P.
-marinus* strain in this study.
-The R package *`mgcv`* [@R-mgcv] was used to model the growth rate with smoothing terms and indicate the 90, 50 and 10% quantiles for growth rate across the levels of factors.
-Only growth rate estimates for which the amplitude of standard error was smaller than 30% of the fitted growth rate were included in the GAM.
-Our priority was the effects of ecologically relevant blue light on growth trends.
-We also included GAM analyses of growth responses to red light, which is not ecophysiologically relevant, but which might prove mechanistically informative [@murphyPhotoinactivationPhotosystemII2017].
+```
+Figure \@ref(fig:deltaODLogGrowthPlot) is an example of chlorophyll
+specific growth estimates fitted from the high resolution ΔOD
+measurements for each tube in a Multicultivator. The residuals of the
+logistic growth curve fit are shown and the growth spectral waveband is
+plotted and illustrates the imposed PAR (µmol photons m^-2^ s^-1^) and
+photoperiod (h).
+
+A Generalized Additive Model (GAM) [@woodGeneralizedAdditiveModels2017]
+was applied to the relation of chlorophyll-specific µ, d^-1^ to
+photoperiod and PAR level, for each growth [O~2~] level, and for the
+blue and red wavebands for growth, for each *P. marinus* strain in this
+study. The R package *`mgcv`* [@R-mgcv] was used to model the growth
+rate with smoothing terms and indicate the 90, 50 and 10% quantiles for
+growth rate across the levels of factors. Only growth rate estimates for
+which the amplitude of standard error was smaller than 30% of the fitted
+growth rate were included in the GAM. Our priority was the effects of
+ecologically relevant blue light on growth trends. We also included GAM
+analyses of growth responses to red light, which is not
+ecophysiologically relevant, but which might prove mechanistically
+informative [@murphyPhotoinactivationPhotosystemII2017].
 
@@
 
-To estimate the Photosynthetic Usable Radiation (PUR), a proxy of incident photons that can be absorbed by the cells, for each *P. marinus* ecotype, the imposed Photosynthetic Active
-Radiation (PAR) was first determined using the reported delivery of sinusoidal diel PAR regimes by the Multicultivators, point validated using a LI-250 quantum sensor (LI-COR Inc.,Lincoln, NE, USA).
-An emission profile from 400 nm to 700 nm of each coloured LED light of the MCMIX-OD Multicultivator and the white LED light of the MC1000-OD Multicultivator was obtained using a Jaz spectrometer (Ocean Optics, Inc.,Dunedin, FL, USA) equipped with a fiber optic cable, HH2 FiberOpticJmp (Part number A901073, Malvern Panalytical Ltd, Malvern, UK).
-Each LED spectrum was then normalized to its emission maximum.
-An *in-vivo* whole cell absorbance spectrum for each *P.
-marinus* strain under each spectral growth condition was obtained using the Olis 14 UV/VIS Clarity Spectrophotometer (Olis Inc., Bogart, GA, USA) to scan across range of λ = 350 nm to 750 nm at 1 nm intervals.
-The path length of the internally reflective cavity of the Olis spectrophotometer was corrected to a 1 cm path length using the Javorfi correction method [@javorfiQuantitativeSpectrophotometryUsing2006] on PRO 99 media subtracted whole cell absorbance spectra.
-The blank-corrected whole cell absorbance spectra were normalized to the absorbance maximum of divinyl chlorophyll *a* (Chl *a*~2~), determined for each spectra, falling between 400 nm and 460 nm.
-
-An integrated weighting equation \@ref(eq:WeightedPUR) [@morelAvailableUsableStored1978] was used to determine the weighted PUR spectrum P(λ); where A(λ) is the blank subtracted, Chl *a*~2~ peak normalized whole cell absorbance spectrum for each *P.
-marinus* ecotype, over 400 nm to 700 nm, A(λ); and E(λ) is the peak normalized emission spectrum of the imposed LED growth light, over 400 nm to 700 nm.
-
+To estimate the Photosynthetic Usable Radiation (PUR), a proxy of
+incident photons that can be absorbed by the cells, for each *P.
+marinus* ecotype, the imposed Photosynthetic Active Radiation (PAR) was
+first determined using the reported delivery of sinusoidal diel PAR
+regimes by the Multicultivators, point validated using a LI-250 quantum
+sensor (LI-COR Inc.,Lincoln, NE, USA). An emission profile from 400 nm
+to 700 nm of each coloured LED light of the MCMIX-OD Multicultivator and
+the white LED light of the MC1000-OD Multicultivator was obtained using
+a Jaz spectrometer (Ocean Optics, Inc.,Dunedin, FL, USA) equipped with a
+fiber optic cable, HH2 FiberOpticJmp (Part number A901073, Malvern
+Panalytical Ltd, Malvern, UK). Each LED spectrum was then normalized to
+its emission maximum. An *in-vivo* whole cell absorbance spectrum for
+each *P. marinus* strain under each spectral growth condition was
+obtained using the Olis 14 UV/VIS Clarity Spectrophotometer (Olis Inc.,
+Bogart, GA, USA) to scan across range of λ = 350 nm to 750 nm at 1 nm
+intervals. The path length of the internally reflective cavity of the
+Olis spectrophotometer was corrected to a 1 cm path length using the
+Javorfi correction method
+[@javorfiQuantitativeSpectrophotometryUsing2006] on PRO 99 media
+subtracted whole cell absorbance spectra. The blank-corrected whole cell
+absorbance spectra were normalized to the absorbance maximum of divinyl
+chlorophyll *a* (Chl *a*~2~), determined for each spectra, falling
+between 400 nm and 460 nm.
+
+An integrated weighting equation \@ref(eq:WeightedPUR)
+[@morelAvailableUsableStored1978] was used to determine the weighted PUR
+spectrum P(λ); where A(λ) is the blank subtracted, Chl *a*~2~ peak
+normalized whole cell absorbance spectrum for each *P. marinus* ecotype,
+over 400 nm to 700 nm, A(λ); and E(λ) is the peak normalized emission
+spectrum of the imposed LED growth light, over 400 nm to 700 nm.
+
+```{=tex}
 \begin{equation}
@@
 \end{equation}
-
-Actinic PUR levels (µmol photons m^-2^ s^-1^) were calculated from actinic PAR (µmol photons m^-2^ s^-1^) levels using the equation \@ref(eq:PUR) from [@morelAvailableUsableStored1978]; where P(λ) is the weighted PUR absorbance spectrum from equation \@ref(eq:WeightedPUR), E(λ) is the imposed growth light emission spectrum from equation \@ref(eq:WeightedPUR) and PAR is the imposed peak light level (µmol photons m^-2^ s^-1^).
-Figure (\@ref(fig:PurParPlot)) shows the calculated peak PUR (µmol photons m^-2^ d^-1^) versus imposed actinic peak PAR (µmol photons m^-2^ s^-1^) for each strain and each spectral waveband (nm).
-
+```
+Actinic PUR levels (µmol photons m^-2^ s^-1^) were calculated from
+actinic PAR (µmol photons m^-2^ s^-1^) levels using the equation
+\@ref(eq:PUR) from [@morelAvailableUsableStored1978]; where P(λ) is the
+weighted PUR absorbance spectrum from equation \@ref(eq:WeightedPUR),
+E(λ) is the imposed growth light emission spectrum from equation
+\@ref(eq:WeightedPUR) and PAR is the imposed peak light level (µmol
+photons m^-2^ s^-1^). Figure (\@ref(fig:PurParPlot)) shows the
+calculated peak PUR (µmol photons m^-2^ d^-1^) versus imposed actinic
+peak PAR (µmol photons m^-2^ s^-1^) for each strain and each spectral
+waveband (nm).
+
+```{=tex}
 \begin{equation}
@@
 \end{equation}
-
-The applied photoperiods were delivered using the sinusoidal circadian light function of the PSI Multicultivator to simulate light exposure approximating sun rise through to sunset.
-The area under the sinusoidal curves is equivalent to the area of a triangular photoregime of equivalent photoperiod (Campbell, unpub), therefore the equation to determine the cumulative diel PUR (µmol photons m^-2^ d^-1^) is one half of the base (photoperiod) multiplied by the height (PUR) (Equation \@ref(eq:SumPURDay)); where PUR is the actinic light calculated from equation \@ref(eq:PUR) (µmol photons m^-2^ s^-1^), 3600 is the time conversion from seconds to hour and photoperiod is the imposed photoperiod (h).
-
+```
+The applied photoperiods were delivered using the sinusoidal circadian
+light function of the PSI Multicultivator to simulate light exposure
+approximating sun rise through to sunset. The area under the sinusoidal
+curves is equivalent to the area of a triangular photoregime of
+equivalent photoperiod (Campbell, unpub), therefore the equation to
+determine the cumulative diel PUR (µmol photons m^-2^ d^-1^) is one half
+of the base (photoperiod) multiplied by the height (PUR) (Equation
+\@ref(eq:SumPURDay)); where PUR is the actinic light calculated from
+equation \@ref(eq:PUR) (µmol photons m^-2^ s^-1^), 3600 is the time
+conversion from seconds to hour and photoperiod is the imposed
+photoperiod (h).
+
+```{=tex}
 \begin{equation}
@@
 \end{equation}
-
-Figure \@ref(fig:OverlayPlots) provide visual representations of PUR, the black solid line and shaded area, in relation to the imposed PAR, the dotted line, under each imposed spectral wavebands for *P.
-marinus* MED4 (A,B,C), SS120 (D,E,F) and MIT9313 (G,H,I).
-Figure (\@ref(fig:PurParPlot)) shows the relationship between calculated PUR versus imposed PAR for each *P.
-marinus* and each spectral waveband.
-
-We performed one-way ANOVA to examine statistical differences between Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to 660 nm (red light) and 450 nm (blue light) growth data for each combination of strain and [O~2~].
-We also performed one-way ANOVA to examine statistical differences between Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to each photoperiod (4 h, 8 h, 12 h, 16 h) and pooled photoperiod growth data for each combination of strain and [O~2~].
-Photoperiod growth data that showed complete growth inhibition for each combination of strain, [O~2~] and imposed spectral waveband were omitted from the pooled photoperiod model.
-Statistical differences were determined at p < 0.05.
+```
+Figure \@ref(fig:OverlayPlots) provide visual representations of PUR,
+the black solid line and shaded area, in relation to the imposed PAR,
+the dotted line, under each imposed spectral wavebands for *P. marinus*
+MED4 (A,B,C), SS120 (D,E,F) and MIT9313 (G,H,I). Figure
+(\@ref(fig:PurParPlot)) shows the relationship between calculated PUR
+versus imposed PAR for each *P. marinus* and each spectral waveband.
+
+We performed one-way ANOVA to examine statistical differences between
+Harrison and Platt
+[@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter
+model fit to 660 nm (red light) and 450 nm (blue light) growth data for
+each combination of strain and [O~2~]. We also performed one-way ANOVA
+to examine statistical differences between Harrison and Platt
+[@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter
+model fit to each photoperiod (4 h, 8 h, 12 h, 16 h) and pooled
+photoperiod growth data for each combination of strain and [O~2~].
+Photoperiod growth data that showed complete growth inhibition for each
+combination of strain, [O~2~] and imposed spectral waveband were omitted
+from the pooled photoperiod model. Statistical differences were
+determined at p \< 0.05.
 
@@
 We filtered the dataset of Omar *et al*.
-[@omarAnnotationGenesEncoding2023], for Enzyme Commission Numbers (EC numbers), or Kegg Orthology Numbers (KO numbers) identified by BRENDA  [@changBRENDAELIXIRCore2021] as 'natural substrates' for O~2~; EC numbers identified by BRENDA as being activated, or inhibited by light; and EC numbers annotated by BioCyc [@karpBioCycCollectionMicrobial2019] as corresponding to the Gene Ontology Term (GO:0006281 - DNA repair), in *P.
-marinus* strains (MED4, MIT9313, SS120, and NATL2A).
-We grouped orthologs together by EC number and their KO number and determined the occurrences of individual orthologs encoding each EC number, or KO number when EC number was not available, in a given strain.
-We merged the dataset with a list of enzyme Michaelis constant (K~m~) values from other organisms, as K~m~ values from *Prochlorococcus* were only available in the case of Ribulose bisphosphate carboxylase.
-Gene counts for Flavodiirons were obtained from Allahverdiyeva *et al*.
-[@allahverdiyevaCyanobacterialOxygenicPhotosynthesis2015a], as they do not have allocated EC numbers.
-A full list of enzymes and corresponding EC and KO numbers can be found in Table \@ref(tab:ProchlorococcusEnzymeTable).
+[@omarAnnotationGenesEncoding2023], for Enzyme Commission Numbers (EC
+numbers), or Kegg Orthology Numbers (KO numbers) identified by BRENDA
+[@changBRENDAELIXIRCore2021] as 'natural substrates' for O~2~; EC
+numbers identified by BRENDA as being activated, or inhibited by light;
+and EC numbers annotated by BioCyc [@karpBioCycCollectionMicrobial2019]
+as corresponding to the Gene Ontology Term (<GO:0006281> - DNA repair),
+in *P. marinus* strains (MED4, MIT9313, SS120, and NATL2A). We grouped
+orthologs together by EC number and their KO number and determined the
+occurrences of individual orthologs encoding each EC number, or KO
+number when EC number was not available, in a given strain. We merged
+the dataset with a list of enzyme Michaelis constant (K~m~) values from
+other organisms, as K~m~ values from *Prochlorococcus* were only
+available in the case of Ribulose bisphosphate carboxylase. Gene counts
+for Flavodiirons were obtained from Allahverdiyeva *et al*.
+[@allahverdiyevaCyanobacterialOxygenicPhotosynthesis2015a], as they do
+not have allocated EC numbers. A full list of enzymes and corresponding
+EC and KO numbers can be found in Table
+\@ref(tab:ProchlorococcusEnzymeTable).
 
@@
 
-Proteins from 13 annotated strains of *P.
-marinus* were detected across depths and oxygen concentrations in the ocean proteins data set analyzed.
-We focused our analysis here on core photosynthetic protein complexes, for clades HL, LLI, LLIII and LLIV (Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) as a function of depth (a proxy for light intensity) and measured [O~2~].
-Photosynthetic complexes from HLI (including strain MED4) were detected throughout the water column, predominantly at high [O~2~].
-The  absence of proteins annotated for the key ATP Synthase complex for Clade HLI, compared to annotated detections of ATP Synthase across the other three clades suggests limitations in the annotation process for highly conserved protein sequences.
-Complexes from Clades LLI (including strain NATL2A) were also present across the depth/light axes, with more representation at lower [O~2], and fewer near surface detections.
-Complexes from clade LLII/III (ex.
-SS120) were also detected across the depth/light and [O~2~] ranges, with more detections at deeper, darker depths.
-Clade LLIV (ex.
-MIT9313) photosynthetic complexes were also were detected throughout the depth/light and [O~2~], ranges, with the most frequent detections at depth and at low [O~2~], compared to other strains.
+Proteins from 13 annotated strains of *P. marinus* were detected across
+depths and oxygen concentrations in the ocean proteins data set
+analyzed. We focused our analysis here on core photosynthetic protein
+complexes, for clades HL, LLI, LLIII and LLIV (Figure
+\@ref(fig:CladeProchloroPhotosynthDepthO2) as a function of depth (a
+proxy for light intensity) and measured [O~2~]. Photosynthetic complexes
+from HLI (including strain MED4) were detected throughout the water
+column, predominantly at high [O~2~]. The absence of proteins annotated
+for the key ATP Synthase complex for Clade HLI, compared to annotated
+detections of ATP Synthase across the other three clades suggests
+limitations in the annotation process for highly conserved protein
+sequences. Complexes from Clades LLI (including strain NATL2A) were also
+present across the depth/light axes, with more representation at lower
+[O\~2], and fewer near surface detections. Complexes from clade LLII/III
+(ex. SS120) were also detected across the depth/light and [O~2~] ranges,
+with more detections at deeper, darker depths. Clade LLIV (ex. MIT9313)
+photosynthetic complexes were also were detected throughout the
+depth/light and [O~2~], ranges, with the most frequent detections at
+depth and at low [O~2~], compared to other strains.
 
@@
 
-Guided in part by the evidence of ocean distributions of proteins from *Prochlorococcus* we set up a matrix of photoperiods, PAR, spectral bands, and [O~2~] to approximate current, and potential future, latitudinal, depth and seasonal niches for *Prochlorococcus* strains.
-As mentioned, growth under red light could prove mechanistically informative [@murphyPhotoinactivationPhotosystemII2017] to factors limiting *Prochlorococcus* growth, we therefore included the red spectral waveband even though it is not representative of *Prochlorococcus* niches.
-Although *Prochlorococcus* is currently limited to a narrow range of surface photoperiods, potential poleward latitudinal expansions, in combination with attenuation of light with depth, mean *Prochlorococcus* may potentially encounter a wide range of photoperiods.
-Our growth rate determinations generally agree with those from Moore *et al*.
-[@mooreComparativePhysiologySynechococcus1995], for white LED and 250 µM O~2~, but our study is, to our knowledge, the first to analyze the interactive growth responses of *Prochlorococcus* strains to varying [O~2~], spectral wavebands and photoperiods.
-
-*Prochlorococcus marinus* MED4, clade HLI, growth under 250 µM O~2~ increased with higher imposed PAR and longer photoperiods
-(Figure \@ref(fig:MED4PAR)), across all spectral wavebands.
-No growth was observed under any imposed conditions under a 4 h photoperiod.
-The maximum growth rate (µ~max~) was `r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 180 µE blue light and 16 h photoperiod.
-
-Similar to growth trends under 250 µM O~2~, MED4 maintained at 25 µM O~2~ showed fastest growth when the
-photoperiod was 16 h for each spectral waveband, across PAR levels (Figure \@ref(fig:MED4PAR)).
-The µ~max~ was `r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "25", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ (Table \@ref(tab:MaxGrowthTable)) achieved under 180 µmol photons m^-2^ s^-1^ blue light and 16 h photoperiod.
-The 4 h photoperiod experiments under white LED light were not performed as no growth was achieved when grown under an 8 h photoperiod of white LED light.
-
-MED4 did not grow when sparged to the lowest [O~2~] of 2.5 µM (Figure \@ref(fig:MED4PAR)). 2.5 µM O~2~ growth experiments
-were not conducted for 4 and 16 h photoperiods, as no reproducible growth occurred when MED4 was exposed to 8 and 12 h photoperiods.
+Guided in part by the evidence of ocean distributions of proteins from
+*Prochlorococcus* we set up a matrix of photoperiods, PAR, spectral
+bands, and [O~2~] to approximate current, and potential future,
+latitudinal, depth and seasonal niches for *Prochlorococcus* strains. As
+mentioned, growth under red light could prove mechanistically
+informative [@murphyPhotoinactivationPhotosystemII2017] to factors
+limiting *Prochlorococcus* growth, we therefore included the red
+spectral waveband even though it is not representative of
+*Prochlorococcus* niches. Although *Prochlorococcus* is currently
+limited to a narrow range of surface photoperiods, potential poleward
+latitudinal expansions, in combination with attenuation of light with
+depth, mean *Prochlorococcus* may potentially encounter a wide range of
+photoperiods. Our growth rate determinations generally agree with those
+from Moore *et al*. [@mooreComparativePhysiologySynechococcus1995], for
+white LED and 250 µM O~2~, but our study is, to our knowledge, the first
+to analyze the interactive growth responses of *Prochlorococcus* strains
+to varying [O~2~], spectral wavebands and photoperiods.
+
+*Prochlorococcus marinus* MED4, clade HLI, growth under 250 µM O~2~
+increased with higher imposed PAR and longer photoperiods (Figure
+\@ref(fig:MED4PAR)), across all spectral wavebands. No growth was
+observed under any imposed conditions under a 4 h photoperiod. The
+maximum growth rate (µ~max~) was
+`r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+d^-1^ achieved under 180 µE blue light and 16 h photoperiod.
+
+Similar to growth trends under 250 µM O~2~, MED4 maintained at 25 µM
+O~2~ showed fastest growth when the photoperiod was 16 h for each
+spectral waveband, across PAR levels (Figure \@ref(fig:MED4PAR)). The
+µ~max~ was
+`r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "25", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+d^-1^ (Table \@ref(tab:MaxGrowthTable)) achieved under 180 µmol photons
+m^-2^ s^-1^ blue light and 16 h photoperiod. The 4 h photoperiod
+experiments under white LED light were not performed as no growth was
+achieved when grown under an 8 h photoperiod of white LED light.
+
+MED4 did not grow when sparged to the lowest [O~2~] of 2.5 µM (Figure
+\@ref(fig:MED4PAR)). 2.5 µM O~2~ growth experiments were not conducted
+for 4 and 16 h photoperiods, as no reproducible growth occurred when
+MED4 was exposed to 8 and 12 h photoperiods.
 
@@
 
-The GAM model in Figure \@ref(fig:MED4GAM) summarizes MED4 growth responses to red (A,B) or blue (C,D) peak PAR and photoperiod across 2 imposed oxygen concentrations.
-Under 250 µM O~2~ MED4 achieved fastest growth rates above peak blue light of ~180 µmol photons m^-2^ s^-1^, and the longest photoperiod of 16, indicated by the 0.64 d^-1^ contour line representing the 90^th^ percentile of maximum achieved growth rate (Figure \@ref(fig:MED4GAM)C).
-Growth decreased with decreasing photoperiod and decreasing peak PAR.
-Under red light growth was generally slower but the pattern of growth responses to photoperiod and PAR was similar (Figure \@ref(fig:MED4GAM)A).
-Note the exclusion of MED4 from growth under 4 h photoperiod under both red and blue light (Figure \@ref(fig:MED4GAM)).
-Under 25 µM O~2~ MED4 showed similar growth responses, but was excluded from both 4 and 8 h photoperiods.
-MED4 did not grow under 2.5 µM O~2~, so no GAM model was run.
-Considering the range of PAR levels, and spectral bands that MED4 can utilize, MED4 can inhabit not just shallow depths, where light levels are high, but also deeper regions, characterized by a lower level of blue light, subject to the limitation of a photoperiod of more than 4 h, even after depth attenuation of light.
-The photoregimes of winter temperate zones, due to shorter photoperiods, exclude MED4 from growth at any depth, however temperate photoperiods and light levels for the remainder of the year are potentially adequate to support MED4 growth, if water temperatures warm into the clade HLI tolerance range.
+The GAM model in Figure \@ref(fig:MED4GAM) summarizes MED4 growth
+responses to red (A,B) or blue (C,D) peak PAR and photoperiod across 2
+imposed oxygen concentrations. Under 250 µM O~2~ MED4 achieved fastest
+growth rates above peak blue light of \~180 µmol photons m^-2^ s^-1^,
+and the longest photoperiod of 16, indicated by the 0.64 d^-1^ contour
+line representing the 90^th^ percentile of maximum achieved growth rate
+(Figure \@ref(fig:MED4GAM)C). Growth decreased with decreasing
+photoperiod and decreasing peak PAR. Under red light growth was
+generally slower but the pattern of growth responses to photoperiod and
+PAR was similar (Figure \@ref(fig:MED4GAM)A). Note the exclusion of MED4
+from growth under 4 h photoperiod under both red and blue light (Figure
+\@ref(fig:MED4GAM)). Under 25 µM O~2~ MED4 showed similar growth
+responses, but was excluded from both 4 and 8 h photoperiods. MED4 did
+not grow under 2.5 µM O~2~, so no GAM model was run. Considering the
+range of PAR levels, and spectral bands that MED4 can utilize, MED4 can
+inhabit not just shallow depths, where light levels are high, but also
+deeper regions, characterized by a lower level of blue light, subject to
+the limitation of a photoperiod of more than 4 h, even after depth
+attenuation of light. The photoregimes of winter temperate zones, due to
+shorter photoperiods, exclude MED4 from growth at any depth, however
+temperate photoperiods and light levels for the remainder of the year
+are potentially adequate to support MED4 growth, if water temperatures
+warm into the clade HLI tolerance range.
 
@@
 
-*Prochlorococcus marinus* SS120 clade LLII/III,  growth under 250 µM O~2~ increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^ peak PAR and across all spectral wavebands (Figure \@ref(fig:SS120PAR)).
-No growth was observed under any blue light photoperiods when exposed to peak PAR of 90 µmol photons m^-2^ s^-1^ or greater.
-Growth rate, however increased with increasing photoperiods for white and red light under peak PAR of 90 µmol photons m^-2^ s^-1^ but showed growth inhibition at 16 h red light photoperiod.
-Growth rate decreased with longer photoperiods and showed growth inhibition at 12 and 16 h photoperiods under PAR of 180 µmol photons m^-2^ s^-1^  white LED, red or blue light.
-The µ~max~ was `r PURPARFits %>% filter(Strain == "SS120", WL == "WW", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ (Table \@ref(tab:MaxGrowthTable)) achieved under 90 µmol photons m^-2^ s^-1^ white LED light and 16 h photoperiod.
-
-Under 25 µM O~2~ and PAR of 30 µmol photons m^-2^ s^-1^ growth trends were similar to 250 µM O~2~.
-SS120 showed no growth under a 4 h photoperiod for red spectral waveband, however under blue light, SS120 was able to grow (Figure \@ref(fig:SS120PAR)).
-In contrast to the growth trends of the 250 µM O~2~ and PAR of 90 µmol photons m^-2^ s^-1^ experiments, SS120 grew under 4 and 8 h blue light and 16 h red light photoperiods, however the growth rate decreased under 12 and 16 h white LED light photoperiod treatments.
-Blue light treatments under PAR of 180 µmol photons m^-2^ s^-1^ showed growth only under an 8 h photoperiod.
-The µ~max~ was `r PURPARFits %>% filter(Strain == "SS120", WL == "450", O2_uM == "25", Photoperiod == 8) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ (Table \@ref(tab:MaxGrowthTable)) achieved under 90 µmol photons m^-2^ s^-1^ blue light and 8 h photoperiod.
-The 25 µM O~2~, less than 16 h photoperiod and 180 µmol photons m^-2^ s^-1^  under white LED light experiments were not performed due to time constraints.
-
-SS120 did not reproducibly grow when sparged to the lowest O~2~ of 2.5 µM (Figure \@ref(fig:SS120PAR)).
-2.5 µM O~2~ growth experiments were not conducted for 4 and 16 h photoperiods under PAR of 180 µmol photons m^-2^ s^-1^, as no growth occurred when SS120 was exposed to 8 and 12 h photoperiods.
-Red light 16 h photoperiod experiments were not performed due to time constraints.
-\newpage
+*Prochlorococcus marinus* SS120 clade LLII/III, growth under 250 µM O~2~
+increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^
+peak PAR and across all spectral wavebands (Figure \@ref(fig:SS120PAR)).
+No growth was observed under any blue light photoperiods when exposed to
+peak PAR of 90 µmol photons m^-2^ s^-1^ or greater. Growth rate, however
+increased with increasing photoperiods for white and red light under
+peak PAR of 90 µmol photons m^-2^ s^-1^ but showed growth inhibition at
+16 h red light photoperiod. Growth rate decreased with longer
+photoperiods and showed growth inhibition at 12 and 16 h photoperiods
+under PAR of 180 µmol photons m^-2^ s^-1^ white LED, red or blue light.
+The µ~max~ was
+`r PURPARFits %>% filter(Strain == "SS120", WL == "WW", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+d^-1^ (Table \@ref(tab:MaxGrowthTable)) achieved under 90 µmol photons
+m^-2^ s^-1^ white LED light and 16 h photoperiod.
+
+Under 25 µM O~2~ and PAR of 30 µmol photons m^-2^ s^-1^ growth trends
+were similar to 250 µM O~2~. SS120 showed no growth under a 4 h
+photoperiod for red spectral waveband, however under blue light, SS120
+was able to grow (Figure \@ref(fig:SS120PAR)). In contrast to the growth
+trends of the 250 µM O~2~ and PAR of 90 µmol photons m^-2^ s^-1^
+experiments, SS120 grew under 4 and 8 h blue light and 16 h red light
+photoperiods, however the growth rate decreased under 12 and 16 h white
+LED light photoperiod treatments. Blue light treatments under PAR of 180
+µmol photons m^-2^ s^-1^ showed growth only under an 8 h photoperiod.
+The µ~max~ was
+`r PURPARFits %>% filter(Strain == "SS120", WL == "450", O2_uM == "25", Photoperiod == 8) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+d^-1^ (Table \@ref(tab:MaxGrowthTable)) achieved under 90 µmol photons
+m^-2^ s^-1^ blue light and 8 h photoperiod. The 25 µM O~2~, less than 16
+h photoperiod and 180 µmol photons m^-2^ s^-1^ under white LED light
+experiments were not performed due to time constraints.
+
+SS120 did not reproducibly grow when sparged to the lowest O~2~ of 2.5
+µM (Figure \@ref(fig:SS120PAR)). 2.5 µM O~2~ growth experiments were not
+conducted for 4 and 16 h photoperiods under PAR of 180 µmol photons
+m^-2^ s^-1^, as no growth occurred when SS120 was exposed to 8 and 12 h
+photoperiods. Red light 16 h photoperiod experiments were not performed
+due to time constraints. \newpage
 
@@
 
-The GAM model in Figure \@ref(fig:SS120GAM) summarizes growth responses of SS120 to red (A,B) or blue (C,D) peak PAR and photoperiod, across the 2 imposed oxygen concentrations.
-Under 250 µM O~2~, Figure \@ref(fig:SS120GAM)C showed highest growth rates below blue light PAR of 50 µmol photons m^-2^ s^-1^ and photoperiods between 8 and 12 h, indicated by the contour line labeled 0.19 d^-1^ (representing the 90^th^ percentile of achieved growth rate).
-Under 250 µM O~2~ SS120 is constrained to deeper ocean waters through its intolerance of higher blue PAR levels.
-These findings align with Moore *et al*.
-[@mooreComparativePhysiologySynechococcus1995] and are expected for a low light clade.
-The disjunct regions of the GAM plot results from variable growth success of SS120 under 250 µM O~2~.
-Growth rate patterns under red light were similar, although somewhat faster.
-In contrast, under 25 µM O~2~ and a photoperiod of 8 h SS120 exploited all blue peak PAR levels, achieving faster growth rates at a higher PAR of \~100 µmol photons m^-2^ s^-1^, indicated by the contour line labeled 0.4 d^-1^ (representing the 90^th^ percentile of achieved growth rate), out pacing the 90^th^ percentile fastest growth rates under 250 µM O~2~ (Figure \@ref(fig:SS120GAM)D).
-Under red light and 25 µM O~2~ (Figure \@ref(fig:SS120GAM)B) SS120 grew across most conditions of peak PAR and photoperiod, achieving fastest growth under long photoperiods and peak PAR between 50 \~100 µmol photons m^-2^ s^-1^.
-Thus, the designation of SS120 as a LL strain is dependent upon the [O~2~].
-SS120 did not, however, grow reliably under tested conditions at 2.5 µM O~2~.
+The GAM model in Figure \@ref(fig:SS120GAM) summarizes growth responses
+of SS120 to red (A,B) or blue (C,D) peak PAR and photoperiod, across the
+2 imposed oxygen concentrations. Under 250 µM O~2~, Figure
+\@ref(fig:SS120GAM)C showed highest growth rates below blue light PAR of
+50 µmol photons m^-2^ s^-1^ and photoperiods between 8 and 12 h,
+indicated by the contour line labeled 0.19 d^-1^ (representing the
+90^th^ percentile of achieved growth rate). Under 250 µM O~2~ SS120 is
+constrained to deeper ocean waters through its intolerance of higher
+blue PAR levels. These findings align with Moore *et al*.
+[@mooreComparativePhysiologySynechococcus1995] and are expected for a
+low light clade. The disjunct regions of the GAM plot results from
+variable growth success of SS120 under 250 µM O~2~. Growth rate patterns
+under red light were similar, although somewhat faster. In contrast,
+under 25 µM O~2~ and a photoperiod of 8 h SS120 exploited all blue peak
+PAR levels, achieving faster growth rates at a higher PAR of \~100 µmol
+photons m^-2^ s^-1^, indicated by the contour line labeled 0.4 d^-1^
+(representing the 90^th^ percentile of achieved growth rate), out pacing
+the 90^th^ percentile fastest growth rates under 250 µM O~2~ (Figure
+\@ref(fig:SS120GAM)D). Under red light and 25 µM O~2~ (Figure
+\@ref(fig:SS120GAM)B) SS120 grew across most conditions of peak PAR and
+photoperiod, achieving fastest growth under long photoperiods and peak
+PAR between 50 \~100 µmol photons m^-2^ s^-1^. Thus, the designation of
+SS120 as a LL strain is dependent upon the [O~2~]. SS120 did not,
+however, grow reliably under tested conditions at 2.5 µM O~2~.
 
@@
 
-*Prochlorococcus marinus* MIT9313, clade LLIV, growth under 250 µM O~2~ increased with longer
-photoperiods, under low 30 µmol photons m^-2^ s^-1^ peak PAR, (Figure \@ref(fig:MIT9313PAR)).
-Under intermediate 90 µmol photons m^-2^ s^-1^ peak PAR growth rates decreased with increasing blue light photoperiods.
-Blue light did not induce growth at 180 µmol photons m^-2^ s^-1^ peak PAR, while MIT9313 showed only marginal growth under white LED and red light at 180 µmol photons m^-2^ s^-1^ peak PAR, under the 8 h photoperiod, consistent with Moore *et al*.
-[@moorePhotophysiologyMarineCyanobacterium1999].
-The µ~max~ was `r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 30 µmol photons m^-2^ s^-1^ blue light and 16 h photoperiod.
-
-For MIT9313 under 25 µM O~2~, growth rate increased with increasing photoperiods for all spectral wavebands tested (Figure \@ref(fig:MIT9313PAR)), with the fastest overall growth rate for MIT9313 
-`r PURPARFits %>% filter(Strain == "MIT9313", WL == "WW", O2_uM == "25", Photoperiod == 16, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under peak PAR of 90 µmol photons m^-2^ s^-1^ and 16 h white LED light photoperiod.
-In marked contrast to the 250 µM O~2~ growth experiments, MIT9313 grew when exposed to peak PAR of 180 µmol photons m^-2^ s^-1^ and blue light under all photoperiods except 16 h; additionally, white LED and red light treatments induced growth across all tested photoperiods under 25 µM O~2~.
-The 25 µM O~2~, 4 h photoperiod experiments under white LED light and were not performed due to time constraints.
-
-MIT9313 grew under 2.5 µM O~2~  particularly under blue LED light, albeit generally slower than under the parallel experiments at 25 µM O~2~  (Figure \@ref(fig:MIT9313PAR)).
-Growth estimates showed scatter among replicates, suggesting  2.5 µM O~2~  is near the tolerance limit for growth of MIT9313.
-Growth rates increased with longer photoperiods under blue light treatments and peak PAR of 90 µmol photons m^-2^ s^-1^ but did not grow under 16 h photoperiod.
-Growth  for MIT9313 under PAR of 180 µmol photons m^-2^ s^-1^ and blue light treatment decreased with increasing photoperiods with full growth inhibition under a 16 h photoperiod.
-The red light peak PAR of 180 µmol photons m^-2^ s^-1^ showed similar growth rates to blue light for 8 and 12 h photoperiods.
-The µ~max~ was `r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "2.5", Photoperiod == 12, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 12 h blue light photoperiod and PAR of 90 µmol photons m^-2^ s^-1^.
-The 2.5 µM O~2~ white LED treatments under 4, 8 and 16 h photoperiods and red light under 4 and 16 h photoperiods were not performed due to time constraints.
+*Prochlorococcus marinus* MIT9313, clade LLIV, growth under 250 µM O~2~
+increased with longer photoperiods, under low 30 µmol photons m^-2^
+s^-1^ peak PAR, (Figure \@ref(fig:MIT9313PAR)). Under intermediate 90
+µmol photons m^-2^ s^-1^ peak PAR growth rates decreased with increasing
+blue light photoperiods. Blue light did not induce growth at 180 µmol
+photons m^-2^ s^-1^ peak PAR, while MIT9313 showed only marginal growth
+under white LED and red light at 180 µmol photons m^-2^ s^-1^ peak PAR,
+under the 8 h photoperiod, consistent with Moore *et al*.
+[@moorePhotophysiologyMarineCyanobacterium1999]. The µ~max~ was
+`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+d^-1^ achieved under 30 µmol photons m^-2^ s^-1^ blue light and 16 h
+photoperiod.
+
+For MIT9313 under 25 µM O~2~, growth rate increased with increasing
+photoperiods for all spectral wavebands tested (Figure
+\@ref(fig:MIT9313PAR)), with the fastest overall growth rate for MIT9313
+`r PURPARFits %>% filter(Strain == "MIT9313", WL == "WW", O2_uM == "25", Photoperiod == 16, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+d^-1^ achieved under peak PAR of 90 µmol photons m^-2^ s^-1^ and 16 h
+white LED light photoperiod. In marked contrast to the 250 µM O~2~
+growth experiments, MIT9313 grew when exposed to peak PAR of 180 µmol
+photons m^-2^ s^-1^ and blue light under all photoperiods except 16 h;
+additionally, white LED and red light treatments induced growth across
+all tested photoperiods under 25 µM O~2~. The 25 µM O~2~, 4 h
+photoperiod experiments under white LED light and were not performed due
+to time constraints.
+
+MIT9313 grew under 2.5 µM O~2~ particularly under blue LED light, albeit
+generally slower than under the parallel experiments at 25 µM O~2~
+(Figure \@ref(fig:MIT9313PAR)). Growth estimates showed scatter among
+replicates, suggesting 2.5 µM O~2~ is near the tolerance limit for
+growth of MIT9313. Growth rates increased with longer photoperiods under
+blue light treatments and peak PAR of 90 µmol photons m^-2^ s^-1^ but
+did not grow under 16 h photoperiod. Growth for MIT9313 under PAR of 180
+µmol photons m^-2^ s^-1^ and blue light treatment decreased with
+increasing photoperiods with full growth inhibition under a 16 h
+photoperiod. The red light peak PAR of 180 µmol photons m^-2^ s^-1^
+showed similar growth rates to blue light for 8 and 12 h photoperiods.
+The µ~max~ was
+`r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "2.5", Photoperiod == 12, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
+d^-1^ achieved under 12 h blue light photoperiod and PAR of 90 µmol
+photons m^-2^ s^-1^. The 2.5 µM O~2~ white LED treatments under 4, 8 and
+16 h photoperiods and red light under 4 and 16 h photoperiods were not
+performed due to time constraints.
 
@@
 
-The GAM model in Figure \@ref(fig:MIT9313GAM) summarizes MIT9313 growth responses to red (A,B,C) or blue (D,E,F) peak PAR and photoperiod.
-Under 250 µM O~2~, Figure \@ref(fig:MIT9313GAM)D shows MIT9313 achieves fastest growth rates between blue peak PAR of 30 µmol photons m^-2^ s^-1^ and 50 µmol photons m^-2^ s^-1^ and photoperiods longer than 8 h, indicated by the contour line labeled 0.52 d^-1^ representing the 90^th^ percentile of achieved growth rates.
-Figure \@ref(fig:MIT9313GAM)D also shows that growth rate increases with longer photoperiods, as long as the blue peak PAR levels remain below 50 µmol photons m^-2^ s^-1^.
-In contrast, under red light and 250 µM O~2~ MIT9313 grows faster while exploiting higher peak PAR and longer photoperiods.
-Figure \@ref(fig:MIT9313GAM)E shows that MIT9313can exploit all blue PAR levels and most photoperiods with 90^th^ percentile of fastest growth rate between 30 to 100 µmol photons m^-2^ s^-1^ PAR.
-Figure \@ref(fig:MIT9313GAM)F shows that MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 4 and 8 h and peak blue PAR between 50 to 100 µmol photons m^-2^ s^-1^ PAR.
-Thus the designation of MIT9313 as a LL clade is dependent upon [O~2~] and light spectra.
+The GAM model in Figure \@ref(fig:MIT9313GAM) summarizes MIT9313 growth
+responses to red (A,B,C) or blue (D,E,F) peak PAR and photoperiod. Under
+250 µM O~2~, Figure \@ref(fig:MIT9313GAM)D shows MIT9313 achieves
+fastest growth rates between blue peak PAR of 30 µmol photons m^-2^
+s^-1^ and 50 µmol photons m^-2^ s^-1^ and photoperiods longer than 8 h,
+indicated by the contour line labeled 0.52 d^-1^ representing the 90^th^
+percentile of achieved growth rates. Figure \@ref(fig:MIT9313GAM)D also
+shows that growth rate increases with longer photoperiods, as long as
+the blue peak PAR levels remain below 50 µmol photons m^-2^ s^-1^. In
+contrast, under red light and 250 µM O~2~ MIT9313 grows faster while
+exploiting higher peak PAR and longer photoperiods. Figure
+\@ref(fig:MIT9313GAM)E shows that MIT9313can exploit all blue PAR levels
+and most photoperiods with 90^th^ percentile of fastest growth rate
+between 30 to 100 µmol photons m^-2^ s^-1^ PAR. Figure
+\@ref(fig:MIT9313GAM)F shows that MIT9313 maintains growth even under
+2.5 µM O~2~, under photoperiods between 4 and 8 h and peak blue PAR
+between 50 to 100 µmol photons m^-2^ s^-1^ PAR. Thus the designation of
+MIT9313 as a LL clade is dependent upon [O~2~] and light spectra.
 (Figure \@ref(fig:MIT9313GAM)E).
@@
 
-Cumulative diel PUR can potentially collapse photoperiod, PAR and spectral wavebands to a common metric of usable photosynthetically active light per day.
-Cumulative diel PUR (µmol photons m^-2^ d^-1^) was calculated from the imposed PUR (µmol photons m^-2^ s^-1^) and photoperiod (h).
-We plotted growth rates vs.
-cumulative diel PUR to determine whether growth is a simple response to diel PUR, across imposed spectral wavebands, and photoperiods, or whether spectral wavebands or photoperiods have specific or interactive influences on growth, beyond cumulative diel PUR.
-
-Due to the absorption of *P.
-marinus* pigments in the blue spectral waveband range, the maximum cumulative diel PUR under blue light is almost 3 times that of white LED light, and about 5 times that of the red light (Figure \@ref(fig:PurParPlot)), despite being derived from the same photoperiods and peak PAR regimes.
-As such, only blue light experiments extend beyond a cumulative diel PUR of ~ 2 x 10^6^ µmol photons m^-2^ d^-1^.
-This spectral bias in the range of PUR leads us to caution in comparing model fits of growth in response to cumulative diel PUR under red vs.
-blue wavebands.
-Furthermore, we found some distinct model fits for specific photoperiods, contributing to scatter within the red vs.
-blue data sets.
-
-The representative of HLI clade, *P.
-marinus* MED4, showed no growth under any 4 h photoperiod treatments, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments (Figure \@ref(fig:PhotoperiodPurFitsPlots)A,B,C).
-In parallel MED4 showed no growth under 2.5 µM O~2~, no matter the level of diel cumulative PUR.
-In contrast, under 250 or 25  µM O~2~, and including photoperiods greater than 4 h, MED4 growth under blue light was described by a saturating response of growth [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] to increasing cumulative diel PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A,B), and no evidence of inhibition of growth at any achieved cumulative diel PUR.
-Under the 'artificial' growth treatment of red light, MED4 achieved more growth per unit diel cumulative PUR (Figure \@ref(fig:BluevsRedPurFitsPlots)A,B), consistent with Murphy *et al*.
-[@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for growth under red light, for MED4, because red light provokes less photoinactivation of PSII, than equivalent levels of blue light.
-For distinct fits for different photoperiods refer to Figure \@ref(fig:PhotoperiodPurFitsPlots) A,B and C.
-
-The representative of the LLII/III clade, *P.
-marinus* SS120 showed almost no growth under 2.5 µM O~2~ experiments (Figure \@ref(fig:PhotoperiodPurFitsPlots)F).
-Most 4 h photoperiod treatments of SS120 also did not grow under 250 µM O~2~ , even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments (Figure \@ref(fig:PhotoperiodPurFitsPlots)D).
-Again using [@harrisonPhotosynthesisirradianceRelationshipsPolar1986], SS120 did not grow when exposed to more than ~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative diel PUR under any spectral waveband or photoperiod combination, under 250 µM O~2~ (Figure \@ref(fig:PhotoperiodPurFitsPlots)D).
-
-Under both 25 and 250 µM O~2~ experiments, SS120 growth plateaued by about 5.0 x 10^5^ µmol photons m^-2^ d^-1^ diel PUR, with some scatter among photoperiod and spectral waveband regimes.
-The onset of growth inhibition extended to higher cumulative diel PUR for cultures under 25 µM O~2~, showing that SS120 is partially protected from photoinhibition of growth by 25 µM O~2~.
-Under 25 µM O~2~, red light again generated more growth of SS120 per unit cumulative diel PUR, than did blue light, consistent with lower cost of growth through lower photoinactivation under red light (Figure \@ref(fig:BluevsRedPurFitsPlots)E) [@murphyPhotoinactivationPhotosystemII2017].
-For distinct fits for different photoperiods refer to Figure \@ref(fig:PhotoperiodPurFitsPlots) D,E and F.
-
-The LLIV clade representative, *P.
-marinus* MIT9313, under 250 µM O~2~ showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^ d^-1^ of cumulative diel PUR.
-Above about 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full inhibition of growth, across photoperiods, and spectral wavebands (Figure \@ref(fig:PhotoperiodPurFitsPlots)G).
-Under 25 µM O~2~ MIT9313 showed higher growth rates over a wider plateau, with a greatly extended exploitation of higher cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Figure \@ref(fig:PhotoperiodPurFitsPlots)H).
-MIT9313 growth under 2.5 µM O~2~ showed a wider, lower, flatter response to cumulative diel PUR, with full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).
-
-As with MED4 and SS120, our data again support enhanced growth under conditions of low cumulative diel PUR and 660 nm (red) spectral bandwidth, consistent with Murphy *et al*.[@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue, wavebands (Figure \@ref(fig:BluevsRedPurFitsPlots)G,H).
-Interestingly, this protective effect of red light disappears for MIT9313 growing under 2.5 µM O~2~, possibly because photoinactivation is strongly suppressed under this low [O~2~] (Figure \@ref(fig:BluevsRedPurFitsPlots)I).
-For distinct fits for different photoperiod fits refer to Figure \@ref(fig:PhotoperiodPurFitsPlots) G,H and I.
+Cumulative diel PUR can potentially collapse photoperiod, PAR and
+spectral wavebands to a common metric of usable photosynthetically
+active light per day. Cumulative diel PUR (µmol photons m^-2^ d^-1^) was
+calculated from the imposed PUR (µmol photons m^-2^ s^-1^) and
+photoperiod (h). We plotted growth rates vs. cumulative diel PUR to
+determine whether growth is a simple response to diel PUR, across
+imposed spectral wavebands, and photoperiods, or whether spectral
+wavebands or photoperiods have specific or interactive influences on
+growth, beyond cumulative diel PUR.
+
+Due to the absorption of *P. marinus* pigments in the blue spectral
+waveband range, the maximum cumulative diel PUR under blue light is
+almost 3 times that of white LED light, and about 5 times that of the
+red light (Figure \@ref(fig:PurParPlot)), despite being derived from the
+same photoperiods and peak PAR regimes. As such, only blue light
+experiments extend beyond a cumulative diel PUR of \~ 2 x 10^6^ µmol
+photons m^-2^ d^-1^. This spectral bias in the range of PUR leads us to
+caution in comparing model fits of growth in response to cumulative diel
+PUR under red vs. blue wavebands. Furthermore, we found some distinct
+model fits for specific photoperiods, contributing to scatter within the
+red vs. blue data sets.
+
+The representative of HLI clade, *P. marinus* MED4, showed no growth
+under any 4 h photoperiod treatments, even when a 4 h photoperiod
+delivered cumulative diel PUR equivalent to other photoperiod treatments
+(Figure \@ref(fig:PhotoperiodPurFitsPlots)A,B,C). In parallel MED4
+showed no growth under 2.5 µM O~2~, no matter the level of diel
+cumulative PUR. In contrast, under 250 or 25 µM O~2~, and including
+photoperiods greater than 4 h, MED4 growth under blue light was
+described by a saturating response of growth
+[@harrisonPhotosynthesisirradianceRelationshipsPolar1986] to increasing
+cumulative diel PUR, with saturation of growth rate achieved around 1.0
+x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A,B),
+and no evidence of inhibition of growth at any achieved cumulative diel
+PUR. Under the 'artificial' growth treatment of red light, MED4 achieved
+more growth per unit diel cumulative PUR (Figure
+\@ref(fig:BluevsRedPurFitsPlots)A,B), consistent with Murphy *et al*.
+[@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for
+growth under red light, for MED4, because red light provokes less
+photoinactivation of PSII, than equivalent levels of blue light. For
+distinct fits for different photoperiods refer to Figure
+\@ref(fig:PhotoperiodPurFitsPlots) A,B and C.
+
+The representative of the LLII/III clade, *P. marinus* SS120 showed
+almost no growth under 2.5 µM O~2~ experiments (Figure
+\@ref(fig:PhotoperiodPurFitsPlots)F). Most 4 h photoperiod treatments of
+SS120 also did not grow under 250 µM O~2~ , even when a 4 h photoperiod
+delivered cumulative diel PUR equivalent to other photoperiod treatments
+(Figure \@ref(fig:PhotoperiodPurFitsPlots)D). Again using
+[@harrisonPhotosynthesisirradianceRelationshipsPolar1986], SS120 did not
+grow when exposed to more than \~1.0 x 10^6^ µmol photons m^-2^ d^-1^ of
+cumulative diel PUR under any spectral waveband or photoperiod
+combination, under 250 µM O~2~ (Figure
+\@ref(fig:PhotoperiodPurFitsPlots)D).
+
+Under both 25 and 250 µM O~2~ experiments, SS120 growth plateaued by
+about 5.0 x 10^5^ µmol photons m^-2^ d^-1^ diel PUR, with some scatter
+among photoperiod and spectral waveband regimes. The onset of growth
+inhibition extended to higher cumulative diel PUR for cultures under 25
+µM O~2~, showing that SS120 is partially protected from photoinhibition
+of growth by 25 µM O~2~. Under 25 µM O~2~, red light again generated
+more growth of SS120 per unit cumulative diel PUR, than did blue light,
+consistent with lower cost of growth through lower photoinactivation
+under red light (Figure \@ref(fig:BluevsRedPurFitsPlots)E)
+[@murphyPhotoinactivationPhotosystemII2017]. For distinct fits for
+different photoperiods refer to Figure
+\@ref(fig:PhotoperiodPurFitsPlots) D,E and F.
+
+The LLIV clade representative, *P. marinus* MIT9313, under 250 µM O~2~
+showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^
+d^-1^ of cumulative diel PUR. Above about 1.0 x 10^6^ µmol photons m^-2^
+d^-1^ of cumulative PUR under 250 µM O~2~, MIT9313 showed full
+inhibition of growth, across photoperiods, and spectral wavebands
+(Figure \@ref(fig:PhotoperiodPurFitsPlots)G). Under 25 µM O~2~ MIT9313
+showed higher growth rates over a wider plateau, with a greatly extended
+exploitation of higher cumulative diel PUR, with full growth inhibition
+only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Figure
+\@ref(fig:PhotoperiodPurFitsPlots)H). MIT9313 growth under 2.5 µM O~2~
+showed a wider, lower, flatter response to cumulative diel PUR, with
+full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^
+d^-1^ cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).
+
+As with MED4 and SS120, our data again support enhanced growth under
+conditions of low cumulative diel PUR and 660 nm (red) spectral
+bandwidth, consistent with Murphy *et
+al*.[@murphyPhotoinactivationPhotosystemII2017] who found a lower cost
+of growth, due to decreased photoinactivation of PSII under red,
+compared to blue, wavebands (Figure
+\@ref(fig:BluevsRedPurFitsPlots)G,H). Interestingly, this protective
+effect of red light disappears for MIT9313 growing under 2.5 µM O~2~,
+possibly because photoinactivation is strongly suppressed under this low
+[O~2~] (Figure \@ref(fig:BluevsRedPurFitsPlots)I). For distinct fits for
+different photoperiod fits refer to Figure
+\@ref(fig:PhotoperiodPurFitsPlots) G,H and I.
 
@@
 
-Under full atmospheric [O~2~] and blue light, LL clades of *Prochlorococcus* are restricted to growth under low light, in part because they suffer photoinhibition of Photosystem II (PSII) through several paths, including direct absorbance of UV or blue light, in parallel with generation of Reactive Oxygen Species (ROS) if the electron flow is slowed [@aroPhotoinhibitionPhotosystemII1993], producing damaging singlet oxygen (^1^O~2~) [@aroPhotoinhibitionPhotosystemII1993; @soitamoPhotoinhibitionMarinePicocyanobacteria2017; @murphyPhotoinactivationPhotosystemII2017; @hakalaEvidenceRoleOxygenevolving2005].
-Repair of photoinactivated PSII relies on the removal of damaged PsbA [@mannInvolvementFtsHHomologue2000; @adamFtsHProteasesChloroplasts2005], followed by reassembly with newly synthesized PsbA [@nixonRecentAdvancesUnderstanding2010].
-Degradation of PsbA is a rate-limiting step in recovery from photoinhibition [@kanervoD1ProteinDegradation1993], mediated largely by a heterohexamer of (FtsH1-FtsH2)~3~, a membrane-bound [@sacharzSubCellularLocation2015; @zakInitialStepsBiogenesis2001] metalloprotease  [(Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto, 2014),  @boehmSubunitOrganizationSynechocystis2012a;  @komendaExposedNTerminalTail2007].
-
-XXXStillWorkingonFtsH Terminology!XXXX
-*Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to as FtsH1-4, homologs to the characterized FtsH isoforms of the model freshwater cyanobacterium *Synechocystis* FtsH, and with presumably parallel functions (Table \@ref(tab:FtsHTable)).
-Upon a shift to higher light, HLI MED4 upregulated expression of FtsH1 and FtsH2 [@bonisteelStrainSpecificDifferences2018], homologs to the *Synechocystis* *slr*0228 and *slr*1604, implicated in PSII repair.
-In contrast, representative LLIV strain MIT9313 showed less overall expression of the FtsH proteases, and thus has fewer FtsH serving each photosystem.
-Furthermore, MIT9313 expressed primarily FtsH3, homologous to *Synechocystis* *slr*1463, possibly involved in PSI biogenesis, and FtsH expression did not increase in response to light stress in MIT9313 [@bonisteelStrainSpecificDifferences2018].
-Through adaptation to steady low light, clade LLIV *Prochlorococcus* instead allocate resources to processes other than dynamic regulation of PSII repair.
+Under full atmospheric [O~2~] and blue light, LL clades of
+*Prochlorococcus* are restricted to growth under low light, in part
+because they suffer photoinhibition of Photosystem II (PSII) through
+several paths, including direct absorbance of UV or blue light, in
+parallel with generation of Reactive Oxygen Species (ROS) if the
+electron flow is slowed [@aroPhotoinhibitionPhotosystemII1993],
+producing damaging singlet oxygen (^1^O~2~)
+[@aroPhotoinhibitionPhotosystemII1993;
+@soitamoPhotoinhibitionMarinePicocyanobacteria2017;
+@murphyPhotoinactivationPhotosystemII2017;
+@hakalaEvidenceRoleOxygenevolving2005]. Repair of photoinactivated PSII
+relies on the removal of damaged PsbA
+[@mannInvolvementFtsHHomologue2000; @adamFtsHProteasesChloroplasts2005],
+followed by reassembly with newly synthesized PsbA
+[@nixonRecentAdvancesUnderstanding2010]. Degradation of PsbA is a
+rate-limiting step in recovery from photoinhibition
+[@kanervoD1ProteinDegradation1993], mediated largely by a heterohexamer,
+termed in *Prochlorococcus* (FtsH1-FtsH2)~3~, a membrane-bound
+[@sacharzSubCellularLocation2015; @zakInitialStepsBiogenesis2001]
+metalloprotease [(Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto,
+2014), @boehmSubunitOrganizationSynechocystis2012a;
+@komendaExposedNTerminalTail2007].
+
+*Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to
+as FtsH1-4, homologs to the characterized FtsH isoforms of the model
+freshwater cyanobacterium *Synechocystis* FtsH, and with presumably
+parallel functions (Table \@ref(tab:FtsHTable)). Upon a shift to higher
+light, HLI MED4 upregulates expression of FtsH1 and FtsH2
+[@bonisteelStrainSpecificDifferences2018], homologs to the
+*Synechocystis* *slr*0228 and *slr*1604, implicated in PSII repair. In
+contrast, representative LLIV strain MIT9313 shows no induction of
+expression of these FtsH protease isoforms when shifted to high light,
+and thus has fewer of these FtsH hexamers serving each photosystem.
+Transcript analysis demonstrates that MIT9313 expressed primarily FtsH3,
+homologous to *Synechocystis* *slr*1463, possibly involved in PSI
+biogenesis [@krynickaFtsH4ProteaseControls2022,
+@konikCyanobacterialFtsH4Protease2024]. This FtsH expression did not
+increase in response to light stress in MIT9313
+[@bonisteelStrainSpecificDifferences2018]. Through adaptation to steady
+low light, clade LLIV *Prochlorococcus* instead allocate resources to
+processes other than dynamic regulation of PSII repair.
 
@@
 
-FtsHTable <- tibble(Organism = c("*Prochlorococcus marinus*", "*Synechocystis sp. PCC6803*", "Function"),
-                    FtsH1 = c("FtsH1", "*Slr*0228", "PSII Repair"),
-                    FtsH2 = c("FtsH2", "*Slr*1604", "PSII Repair"),
-                    FtsH3 = c("FtsH3", "*Sll*1463", "PSI biogenesis?"),
-                    FtsH4 = c("FtsH4", "*Slr*1390", "Cell viability")
+FtsHTable <- tibble(Organism = c("*Prochlorococcus marinus*", "*Synechocystis sp. PCC6803*", "*Synechocystis sp. PCC6803* isoform", "Function"),
+                    FtsH1 = c("FtsH1", "*Slr*0228", "FtsH2", "PSII Repair"),
+                    FtsH2 = c("FtsH2", "*Slr*1604", "FtsH3", "PSII Repair"),
+                    FtsH3 = c("FtsH3", "*Sll*1463", "FtsH4", "PSI biogenesis"),
+                    FtsH4 = c("FtsH4", "*Slr*1390", "FtsH1", "Cell viability")
                     )
@@
 
-Ocean detections of proteins mediating protein metabolism support this interpretation of distinct FtsH function across clades of *P.
-marinus*.
-Ribosome proteins from clade HLI MED4, clade LLI NATL2A, clade LLII/III SS120 and clade LLIV MIT9313 show generally similar patterns vs.
-[O~2~] and depth, a proxy for peak PAR  (Figure \@ref(fig:CladeProchloroProteinMetabDepthO2)).
-FtsH3, inferred to mediate PSI assembly, likewise shows a similar pattern between MED4 and MIT9313 (Figure \@ref(fig:CladeProchloroProteinMetabDepthO2)).
-But only MED4 shows detected presence of the FtsH1 & FtsH2 isoforms inferred to mediate PSII repair, and then only in near-surface samples subject to higher light.
-Furthermore, even though MIT9313 grows (Figure \@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~] (Figure \@ref(fig:CladeProchloroPhotosynthDepthO2)), no FtsH from MIT9313 is detected at low [O~2~] (Figure \@ref(fig:CladeProchloroProteinMetabDepthO2)), suggesting limited requirement for protein turnover under low [O~2~].
+Ocean detections of proteins mediating protein metabolism support this
+interpretation of distinct FtsH function across clades of *P. marinus*.
+Ribosome proteins from clade HLI MED4, clade LLI NATL2A, clade LLII/III
+SS120 and clade LLIV MIT9313 show generally similar patterns vs. [O~2~]
+and depth, a proxy for peak PAR (Figure
+\@ref(fig:CladeProchloroProteinMetabDepthO2)). FtsH3, inferred to
+mediate PSI assembly, likewise shows a similar pattern between MED4 and
+MIT9313 (Figure \@ref(fig:CladeProchloroProteinMetabDepthO2)). But only
+MED4 shows the presence of the FtsH1 & FtsH2 isoforms inferred to
+mediate PSII repair, and then only in near-surface samples subject to
+higher light levels. Furthermore, even though MIT9313 grows (Figure
+\@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~]
+(Figure \@ref(fig:CladeProchloroPhotosynthDepthO2)), no FtsH from
+MIT9313 is detected at low [O~2~] (Figure
+\@ref(fig:CladeProchloroProteinMetabDepthO2)), suggesting limited
+requirement for protein turnover under low [O~2~].
 
@@
 
-Figure \@ref(fig:ProchlorococcusEnzymeKms) shows the measured or inferred K~M~ for [O~2~] for genes encoding enzymes [@omarAnnotationGenesEncoding2023] for  *P.
-marinus* strains from clades HLI, LLI, LLII/III and LLIV.
-MED4 increases expression of alternative oxidase ('ubiquinol oxidase (non electrogenic)')  to cope with changes in light [@bergResponsesPsbAHli2011], by dissipating electrons from the inter-system transport chain.
-The approximate K~M~ for [O~2~] of ~ 25 µM for ubiquinol oxidase (non electrogenic) (Figure \@ref(fig:ProchlorococcusEnzymeKms)) is comparable to the lower limit for growth of MED4 in our experiments (Figure \@ref(fig:MED4GAM)).
-We suggest that dependence upon this enzyme excludes MED4 from low oxygen zones.
-The genome scan shows SS120 and MIT9313 lack this gene (Figure \@ref(fig:ProchlorococcusEnzymeKms)), and therefore, lack this oxygen-dependent path to cope with changing excitation.
-Conversely, a gene encoding (S)-2-hydroxy-acid oxidase is encoded in the MIT9313 genome (Figure \@ref(fig:ProchlorococcusEnzymeKms)).
-(S)-2-hydroxy-acid oxidase catalyzes the reaction of 2-hydroxy acid with O~2~ to produce toxic H~2~O~2~ [@cunaneCrystalStructureAnalysis2005].
-(S)-2-hydroxy-acid oxidase has an approximate K~M~ for [O~2~] of ~ 250 µM, and produces H~2~O~2~, so growth at lower [O~2~] may protect MIT9313 from auto-intoxication from production of H~2~O~2~.
-We hypothesize that under 250 µM O~2~ and higher blue light, *P.
-marinus* MIT9313 suffered photoinhibition, resulting from the inactivation of PSII caused by the production of the reactive oxygen species, hydrogen peroxide.
-This photoinhibition is compounded by the limited inducible repair mechanism for PSII, due to the absence of FtsH 1 and 2 expression in *P.
-marinus* MIT9313 [@bonisteelStrainSpecificDifferences2018].
-We hypothesize that under the conditions of our high light and 2.5 µM or 25 µM O~2~ experiments, the activity of the (S)-2-hydroxy-acid oxidase enzyme is suppressed.
-As a result, the catalyzed production of hydrogen peroxide is inhibited, leading to less PSII damage, allowing MIT9313 to avoid photoinhibition and circumvent its limitations on PSII repair to exploit higher light.
-Figure \@ref(fig:ProchlorococcusEnzymeKms) also shows that *P.
-marinus* SS120 is the only tested ecotype to lack the pyridoxal 5'-phosphate synthase enzyme.
-The pyridoxal 5'-phosphate synthase enzyme is an important cofactor in the biosynthesis of vitamin B~6~ [@sangIdentificationPyridoxinePyridoxamine2007].
-Vitamin B~6~ is a potential antioxidant and can effectively quench singlet oxygen [@bilskiVitaminB6Pyridoxine2000].
-The absence of the pyridoxal 5'-phosphate synthase enzyme may explain why *P.
-marinus* SS120 does not grow as well as *P.
-marinus* MIT9313, when exposed to high light stress under 25 µM O~2~ and not at all under 2.5 µM O~2~ (Figure \@ref(fig:SS120PAR)).
+Figure \@ref(fig:ProchlorococcusEnzymeKms) shows the measured or
+inferred K~M~ for [O~2~] for genes encoding enzymes
+[@omarAnnotationGenesEncoding2023] for *P. marinus* strains from clades
+HLI, LLI, LLII/III and LLIV. MED4 increases expression of alternative
+oxidase ('ubiquinol oxidase (non electrogenic)') to cope with changes in
+light [@bergResponsesPsbAHli2011], by dissipating electrons from the
+inter-system transport chain. The approximate K~M~ for [O~2~] of \~ 25
+µM for ubiquinol oxidase (non electrogenic) (Figure
+\@ref(fig:ProchlorococcusEnzymeKms)) is comparable to the lower limit
+for growth of MED4 in our experiments (Figure \@ref(fig:MED4GAM)). We
+suggest that dependence upon this enzyme excludes MED4 from low oxygen
+zones. The genome scan shows SS120 and MIT9313 lack this gene (Figure
+\@ref(fig:ProchlorococcusEnzymeKms)), and therefore, lack this
+oxygen-dependent path to cope with changing excitation. Conversely, a
+gene encoding (S)-2-hydroxy-acid oxidase is encoded in the MIT9313
+genome (Figure \@ref(fig:ProchlorococcusEnzymeKms)). (S)-2-hydroxy-acid
+oxidase catalyzes the reaction of 2-hydroxy acid with O~2~ to produce
+toxic H~2~O~2~ [@cunaneCrystalStructureAnalysis2005]. (S)-2-hydroxy-acid
+oxidase has an approximate K~M~ for [O~2~] of \~ 250 µM, and produces
+H~2~O~2~, so growth at lower [O~2~] may protect MIT9313 from
+auto-intoxication from production of H~2~O~2~. We hypothesize that under
+250 µM O~2~ and higher blue light, *P. marinus* MIT9313 suffered
+photoinhibition, resulting from the inactivation of PSII caused by the
+production of the reactive oxygen species, hydrogen peroxide. This
+photoinhibition is compounded by the limited inducible repair mechanism
+for PSII, due to the absence of FtsH 1 and 2 expression in *P. marinus*
+MIT9313 [@bonisteelStrainSpecificDifferences2018]. We hypothesize that
+under the conditions of our high light and 2.5 µM or 25 µM O~2~
+experiments, the activity of the (S)-2-hydroxy-acid oxidase enzyme is
+suppressed. As a result, the catalyzed production of hydrogen peroxide
+is inhibited, leading to less PSII damage, allowing MIT9313 to avoid
+photoinhibition and circumvent its limitations on PSII repair to exploit
+higher light. Figure \@ref(fig:ProchlorococcusEnzymeKms) also shows that
+*P. marinus* SS120 is the only tested ecotype to lack the pyridoxal
+5'-phosphate synthase enzyme. The pyridoxal 5'-phosphate synthase enzyme
+is an important cofactor in the biosynthesis of vitamin B~6~
+[@sangIdentificationPyridoxinePyridoxamine2007]. Vitamin B~6~ is a
+potential antioxidant and can effectively quench singlet oxygen
+[@bilskiVitaminB6Pyridoxine2000]. The absence of the pyridoxal
+5'-phosphate synthase enzyme may explain why *P. marinus* SS120 does not
+grow as well as *P. marinus* MIT9313, when exposed to high light stress
+under 25 µM O~2~ and not at all under 2.5 µM O~2~ (Figure
+\@ref(fig:SS120PAR)).
 
@@
 Figure \@ref(fig:DNARepairFig) shows genes encoding DNA repair for *P.
-marinus* strains.
-As expected, *P.
-marinus* MED4 possesses the largest, most complete suite of genes encoding DNA repair enzymes, followed by *P.
-marinus* MIT9313.
-Conversely, *P.
-marinus* SS120 demonstrates the smallest genomic capacity for DNA repair.
-*Prochlorococcus marinus* MED4 and NATL2A were the only strains to possess a gene encoding deoxyribodipyrimidine photolyase (Figure \@ref(fig:DNARepairFig) and \@ref(fig:ProchlorococcusLightEnzymes)), which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003].
-*Prochlorococcus marinus* MED4 was also the only strain to possesses a gene encoding DNA ligase, which uses ATP as a cofactor for DNA repair.
-The absence of genes encoding deoxyribodipyrimidine photolyase and DNA ligase (ATP) in *P.
-marinus* MIT9313 and *P.
-marinus* SS120 explain why these two strains cannot tolerate growth under full [O~2~] and high light, found at the ocean surface.
-Furthermore, the protective effect of lower [O~2~], allowing these strains to grow at higher light, may relate in part to suppression of DNA damage when generation of Reactive Oxygen Species is suppressed at lower [O~2~].
-NATL2A, a clade LLI, has been found near the ocean surface during deep ocean mixing [@malmstromTemporalDynamicsProchlorococcus2010].
-Malmstrom *et al*.
-[@malmstromTemporalDynamicsProchlorococcus2010] attributes NATL2A tolerance to short exposures of high light to the presence of the genes encoding photolyase, a gene found in HL clades.
-The presence of deoxyribodipyrimidine photolyase and absence of DNA ligase (ATP) supports why NATL2A tolerates limited exposure to high light and why NATL2A is unable to fully repair damaged DNA.
-*Prochlorococcus* are highly susceptible to hydrogen peroxide (H~2~O~2~) toxicity as they lack genes which scavenge H~2~O~2~ molecules [@morrisFacilitationRobustGrowth2008].
-The small cell size of *Prochlorococcus* allow the reactive oxygen species (ROS), H~2~O~2~, to cross the cell membrane [@omarDiffusionalInteractionsMarine2022]; however, accumulation of extracellular H~2~O~2~ remains toxic to *Prochlorococcus* [@morrisFacilitationRobustGrowth2008;  @morrisDependenceCyanobacteriumProchlorococcus2011].
+marinus* strains. As expected, *P. marinus* MED4 possesses the largest,
+most complete suite of genes encoding DNA repair enzymes, followed by
+*P. marinus* MIT9313. Conversely, *P. marinus* SS120 demonstrates the
+smallest genomic capacity for DNA repair. *Prochlorococcus marinus* MED4
+and NATL2A were the only strains to possess a gene encoding
+deoxyribodipyrimidine photolyase (Figure \@ref(fig:DNARepairFig) and
+\@ref(fig:ProchlorococcusLightEnzymes)), which, in the presence of blue
+light, is responsible for repairing DNA damaged by UV light
+[@sancarStructureFunctionDNA2003]. *Prochlorococcus marinus* MED4 was
+also the only strain to possesses a gene encoding DNA ligase, which uses
+ATP as a cofactor for DNA repair. The absence of genes encoding
+deoxyribodipyrimidine photolyase and DNA ligase (ATP) in *P. marinus*
+MIT9313 and *P. marinus* SS120 explain why these two strains cannot
+tolerate growth under full [O~2~] and high light, found at the ocean
+surface. Furthermore, the protective effect of lower [O~2~], allowing
+these strains to grow at higher light, may relate in part to suppression
+of DNA damage when generation of Reactive Oxygen Species is suppressed
+at lower [O~2~]. NATL2A, a clade LLI, has been found near the ocean
+surface during deep ocean mixing
+[@malmstromTemporalDynamicsProchlorococcus2010]. Malmstrom *et al*.
+[@malmstromTemporalDynamicsProchlorococcus2010] attributes NATL2A
+tolerance to short exposures of high light to the presence of the genes
+encoding photolyase, a gene found in HL clades. The presence of
+deoxyribodipyrimidine photolyase and absence of DNA ligase (ATP)
+supports why NATL2A tolerates limited exposure to high light and why
+NATL2A is unable to fully repair damaged DNA. *Prochlorococcus* are
+highly susceptible to hydrogen peroxide (H~2~O~2~) toxicity as they lack
+genes which scavenge H~2~O~2~ molecules
+[@morrisFacilitationRobustGrowth2008]. The small cell size of
+*Prochlorococcus* allow the reactive oxygen species (ROS), H~2~O~2~, to
+cross the cell membrane [@omarDiffusionalInteractionsMarine2022];
+however, accumulation of extracellular H~2~O~2~ remains toxic to
+*Prochlorococcus* [@morrisFacilitationRobustGrowth2008;
+@morrisDependenceCyanobacteriumProchlorococcus2011].
 
@@
 
-The potential for niche expansion into temperate regions by *P.
-marinus* varies depending on the season, which influences achieved underwater photoperiods and light levels.
-Temperate summer delivers 11 hours of blue waveband light underwater, above the photic threshold of 20 µmol photons m^-2^ s^-1^, while temperate spring/fall delivers 8 hours of blue waveband light underwater, photoperiod ranges which are permissive for growth of all three *P.
-marinus*.
-In contrast temperate winter delivers only about 2 h
-of blue waveband light underwater above the photic threshold, which precludes growth of MED4 and SS120, even if winter waters reached permissive temperatures.
-MIT9313 and SS120 will be excluded from near-surface growth niches by high PAR, unless OMZ zones extend to the near surface.
-
-Diverse *P.
-marinus* strains  @billerProchlorococcusStructureFunction2015 differentially exploit potential photoregimes, both at the surface and deep in the water column.
-Some *P.
-marinus* strains grow under low oxygen environments, similar to OMZ.
-The LL clades we tested can function as 'HL'  in oxygen environments of 25 µM, and as low as 2.5 µM, in the case of MIT9313.
-
-West *et al*.
-[@westNichePartitioningProchlorococcusPopulations1999] and Malmstrom *et al*.
-[@malmstromTemporalDynamicsProchlorococcus2010] found that decreased abundances of the LL clades corresponded to increased depth of the surface mixed layer.
-Malmstrom *et al*.
-[@malmstromTemporalDynamicsProchlorococcus2010] attributes the transport of LL ecotypes to the surface and consequent exposure to photoinhibitory high light levels as the reason for low cell abundances with increased mixed layer depth.
-West *et al*.
-[@westNichePartitioningProchlorococcusPopulations1999] found the depth of the mixed layer strongly influenced the depth transition from HL to LL clades, but that factors other than light levels may influence the variations in the upper and lower depth limits of these ecotypes.
-We hypothesize that low cell abundances of LL ecotypes in the mixed layer is likely driven in part by increased [O~2~],  and it is [O~2~] that constrains LL clades to deeper waters, not necessarily the light level.
-We found that under 25 µM O~2~ representatives of 'LL' clades, SS120 and MIT9313, actually tolerate approximately 1.0 x 10^6^ µmol photons m^-2^ d^-1^ of PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)E,H), comparable to the representative HL clade, MED4 which also exhibited growth saturation at the same cumulative diel PUR of 1.0 x 10^6^ µmol photons m^-2^ d^-1^ (Figure \@ref(fig:PhotoperiodPurFitsPlots)A,B).
-Growth under lower O~2~ allowed MIT9313 to substantially increase its exploitation of higher diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).
+The potential for niche expansion into temperate regions by *P. marinus*
+varies depending on the season, which influences achieved underwater
+photoperiods and light levels. Temperate summer delivers 11 hours of
+blue waveband light underwater, above the photic threshold of 20 µmol
+photons m^-2^ s^-1^, while temperate spring/fall delivers 8 hours of
+blue waveband light underwater, photoperiod ranges which are permissive
+for growth of all three *P. marinus*. In contrast temperate winter
+delivers only about 2 h of blue waveband light underwater above the
+photic threshold, which precludes growth of MED4 and SS120, even if
+winter waters reached permissive temperatures. MIT9313 and SS120 will be
+excluded from near-surface growth niches by high PAR, unless OMZ zones
+extend to the near surface.
+
+Diverse *P. marinus* strains @billerProchlorococcusStructureFunction2015
+differentially exploit potential photoregimes, both at the surface and
+deep in the water column. Some *P. marinus* strains grow under low
+oxygen environments, similar to OMZ. The LL clades we tested can
+function as 'HL' in oxygen environments of 25 µM, and as low as 2.5 µM,
+in the case of MIT9313.
+
+West *et al*. [@westNichePartitioningProchlorococcusPopulations1999] and
+Malmstrom *et al*. [@malmstromTemporalDynamicsProchlorococcus2010] found
+that decreased abundances of the LL clades corresponded to increased
+depth of the surface mixed layer. Malmstrom *et al*.
+[@malmstromTemporalDynamicsProchlorococcus2010] attributes the transport
+of LL ecotypes to the surface and consequent exposure to photoinhibitory
+high light levels as the reason for low cell abundances with increased
+mixed layer depth. West *et al*.
+[@westNichePartitioningProchlorococcusPopulations1999] found the depth
+of the mixed layer strongly influenced the depth transition from HL to
+LL clades, but that factors other than light levels may influence the
+variations in the upper and lower depth limits of these ecotypes. We
+hypothesize that low cell abundances of LL ecotypes in the mixed layer
+is likely driven in part by increased [O~2~], and it is [O~2~] that
+constrains LL clades to deeper waters, not necessarily the light level.
+We found that under 25 µM O~2~ representatives of 'LL' clades, SS120 and
+MIT9313, actually tolerate approximately 1.0 x 10^6^ µmol photons m^-2^
+d^-1^ of PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)E,H), comparable
+to the representative HL clade, MED4 which also exhibited growth
+saturation at the same cumulative diel PUR of 1.0 x 10^6^ µmol photons
+m^-2^ d^-1^ (Figure \@ref(fig:PhotoperiodPurFitsPlots)A,B). Growth under
+lower O~2~ allowed MIT9313 to substantially increase its exploitation of
+higher diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).
 
@@
 
-We analyzed growth rates for  *P.
-marinus* clade HLI found near the ocean surface; clade LLII/III found deep in the water column; and clade LLIV also found in deep oceans, including OMZ, under a matrix of spectral wavebands, irradiances, photoperiods and oxygen concentrations approximating present day and hypothetical future niches.
-
-*Prochlorococcus marinus* MED4 requires more than 4 h of light per day; thus this strain will not exploit habitats typical of temperate winter or light attenuated depths, even if water temperatures warm into the clade HLI tolerance range.
-MED4 is also excluded from the lowest oxygen habitats of 2.5 µM O~2~, but can, grow under OMZ regions with 25 µM O~2~.
-Genomic (Figure \@ref(fig:ProchlorococcusEnzymeKms)) and transcriptional analyses [@bergResponsesPsbAHli2011]  suggest MED4 is excluded from growth below ~ 25 µM O~2~ because it relies upon a ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction balance in the intersystem electron transport chain, with a K~M~ for  [O~2~] of ~25 µM O~2~.
-On the other hand, MED4 shows inducible expression of FtsH isoforms [@bonisteelStrainSpecificDifferences2018], to counter photoinactivation of PSII under higher PAR and [O~2~] environments.
-However, photoinactivation imposes an increased cost of growth upon MED4, since growth under red light, to lower photoinactivation of PSII [@murphyPhotoinactivationPhotosystemII2017], allows MED4 to achieve faster growth per absorbed photon than growth under blue light.
-TARA Oceans Project data [@delmontLinkingPangenomesMetagenomes2018] indeed reported presence of *P.
-marinus* MED4-like genomes at depths ranging from 5 m to 90 m, representing high to low blue light levels, in the Pacific South East Ocean.
-Delmont and Eren [@delmontLinkingPangenomesMetagenomes2018] did not analyze data from depths beyond the subsurface chlorophyll maximum layer, nor did they report[O~2~] at depth.
-Our growth findings are  consistent with Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSII proteins annotated as MED4, clade HLI, at depths up to 200 meters, with O~2~ of ~15 µM.
-
-*Prochlorococcus marinus* SS120, a LLII/III clade representative, showed an interactive inhibition of growth by oxygen and cumulative diel PUR, with a higher tolerance for higher cumulative diel PUR under 25 µM O~2~, compared to 250 µM O~2~ (Figure \@ref(fig:PhotoperiodPurFitsPlots)).
-Thus, SS120 can exploit higher PAR environments, within OMZ.
-SS120 is likely excluded from the combination of higher [O~2~] and higher PAR by genomic limitations on capacity for DNA repair (Figure \@ref(fig:DNARepairFig)), and possibly by limited capacity for synthesis of reactive oxygen quenchers (Figure  \@ref(fig:ProchlorococcusEnzymeKms)).
-Our growth results are supported by Lavin *et al*.
-[@lavinNovelLineagesProchlorococcus2010] who found evidence of LLII/III and LLIV ecotypes, using terminal restriction fragment length polymorphism analyses, at depths above 40 m, where light levels are higher, within OMZ, and by Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSII protein subunits annotated as derived from SS120 at all depths ranging from 20 to 200 m and all [O~2~] in an OMZ of the tropical North Pacific Ocean.
-SS120 grew under photoperiods longer than 4 h and showed increasing growth rate with increasing photoperiods, and so has the potential to thrive in deep temperate zones, specifically during the spring, summer, and fall seasons when the duration of daylight exceeds 4 h, if [O~2~] are near surface saturation of about 250 µM.
-Under lower oxygen levels of 25 µM, SS120 can also potentially exploit a 4 h photoperiod in the blue waveband, and thus has the potential to inhabit a potential warmed, deep, temperate OMZ, during the winter season.
-
-*Prochlorococcus marinus* MIT9313, a LLIV clade representative, shows potential to inhabit future warmer temperate zones year-round, as it grows under a 4 h photoperiod, expected in winter, or at light-attenuated depths.
-MIT9313 demonstrates an unexpected tolerance to higher light levels and cumulative diel PUR, but only under low oxygen conditions of 25 µM and 2.5 µM (Figure \@ref(fig:MIT9313PAR)), enabling MIT9313 to grow in OMZ, even at depths closer to the surface.
-MIT9313 carries a gene encoding (S)-2-hydroxy-acid oxidase [@cunaneCrystalStructureAnalysis2005],  with a K~M~ for [O~2~] of ~ 250 µM (Figure \@ref(fig:ProchlorococcusEnzymeKms)), which produces H~2~O~2~.
-Growth at lower [O~2~] may protect MIT9313 from auto-intoxication from production of H~2~O~2~.
-We hypothesize that under 250 µM O~2~ and higher blue light, *P.
-marinus* MIT9313 suffers photoinhibition, resulting in part from the inactivation of PSII caused by the production of H~2~O~2~.
-This photoinhibition is compounded by limited inducible repair for PSII, due to the absence of FtsH 1 and 2  expression in *P.
-marinus* MIT9313 [@bonisteelStrainSpecificDifferences2018].
-MIT9313 shows remarkable ability to thrive under very low [O~2~], potentially allowing it to expand into broader ecological niches.
-These results are supported by Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSI protein subunits annotated as derived from MIT9313 detected at depths \> 120 m, along with PSII subunits at depths from 50 m to 200 m in regions where O~2~ was 15 µM.
-Bagby and Chisholm [@bagbyResponseProchlorococcusVarying2015] suggest that O~2~ has a protective role in *Prochlorococcus* under lower carbon dioxide environments when carbon fixation is limited.
-The deep water environments typical for MIT9313 are relatively nutrient rich, and *Prochlorococcus* take up and metabolize various sugars [@gomez-baenaGlucoseUptakeIts2008; @munoz-marinGlucoseUptakeProchlorococcus2017; @munoz-marinProchlorococcusCanUse2013] and amino acids [@zubkovDepthRelatedAmino2004].
-In future work we aim to test whether MIT9313 is using photosynthesis to drive CO~2~ fixation in low O~2~ environments, or whether PSII generation of O~2~ acts as an electron sink for respiration, using ATP for maintenance and to take up nutrients from the surroundings.
-Partensky *et al*.
-[@partenskyComparisonPhotosyntheticPerformances2018] indeed found that in the low-light conditions found in the OMZ, MED4, SS120 and MIT9313 all became net O~2~ consumers, suggesting that the low light levels cause the respiratory chain to consume more O~2~ than the photosynthetic electron transport chain generates, thus contributing to maintenance of the low O~2~ environment.
+We analyzed growth rates for *P. marinus* clade HLI found near the ocean
+surface; clade LLII/III found deep in the water column; and clade LLIV
+also found in deep oceans, including OMZ, under a matrix of spectral
+wavebands, irradiances, photoperiods and oxygen concentrations
+approximating present day and hypothetical future niches.
+
+*Prochlorococcus marinus* MED4 requires more than 4 h of light per day;
+thus this strain will not exploit habitats typical of temperate winter
+or light attenuated depths, even if water temperatures warm into the
+clade HLI tolerance range. MED4 is also excluded from the lowest oxygen
+habitats of 2.5 µM O~2~, but can, grow under OMZ regions with 25 µM
+O~2~. Genomic (Figure \@ref(fig:ProchlorococcusEnzymeKms)) and
+transcriptional analyses [@bergResponsesPsbAHli2011] suggest MED4 is
+excluded from growth below \~ 25 µM O~2~ because it relies upon a
+ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction
+balance in the intersystem electron transport chain, with a K~M~ for
+[O~2~] of \~25 µM O~2~. On the other hand, MED4 shows inducible
+expression of FtsH isoforms [@bonisteelStrainSpecificDifferences2018],
+to counter photoinactivation of PSII under higher PAR and [O~2~]
+environments. However, photoinactivation imposes an increased cost of
+growth upon MED4, since growth under red light, to lower
+photoinactivation of PSII [@murphyPhotoinactivationPhotosystemII2017],
+allows MED4 to achieve faster growth per absorbed photon than growth
+under blue light. TARA Oceans Project data
+[@delmontLinkingPangenomesMetagenomes2018] indeed reported presence of
+*P. marinus* MED4-like genomes at depths ranging from 5 m to 90 m,
+representing high to low blue light levels, in the Pacific South East
+Ocean. Delmont and Eren [@delmontLinkingPangenomesMetagenomes2018] did
+not analyze data from depths beyond the subsurface chlorophyll maximum
+layer, nor did they report[O~2~] at depth. Our growth findings are
+consistent with Figure \@ref(fig:CladeProchloroPhotosynthDepthO2)
+showing PSII proteins annotated as MED4, clade HLI, at depths up to 200
+meters, with O~2~ of \~15 µM.
+
+*Prochlorococcus marinus* SS120, a LLII/III clade representative, showed
+an interactive inhibition of growth by oxygen and cumulative diel PUR,
+with a higher tolerance for higher cumulative diel PUR under 25 µM O~2~,
+compared to 250 µM O~2~ (Figure \@ref(fig:PhotoperiodPurFitsPlots)).
+Thus, SS120 can exploit higher PAR environments, within OMZ. SS120 is
+likely excluded from the combination of higher [O~2~] and higher PAR by
+genomic limitations on capacity for DNA repair (Figure
+\@ref(fig:DNARepairFig)), and possibly by limited capacity for synthesis
+of reactive oxygen quenchers (Figure
+\@ref(fig:ProchlorococcusEnzymeKms)). Our growth results are supported
+by Lavin *et al*. [@lavinNovelLineagesProchlorococcus2010] who found
+evidence of LLII/III and LLIV ecotypes, using terminal restriction
+fragment length polymorphism analyses, at depths above 40 m, where light
+levels are higher, within OMZ, and by Figure
+\@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSII protein subunits
+annotated as derived from SS120 at all depths ranging from 20 to 200 m
+and all [O~2~] in an OMZ of the tropical North Pacific Ocean. SS120 grew
+under photoperiods longer than 4 h and showed increasing growth rate
+with increasing photoperiods, and so has the potential to thrive in deep
+temperate zones, specifically during the spring, summer, and fall
+seasons when the duration of daylight exceeds 4 h, if [O~2~] are near
+surface saturation of about 250 µM. Under lower oxygen levels of 25 µM,
+SS120 can also potentially exploit a 4 h photoperiod in the blue
+waveband, and thus has the potential to inhabit a potential warmed,
+deep, temperate OMZ, during the winter season.
+
+*Prochlorococcus marinus* MIT9313, a LLIV clade representative, shows
+potential to inhabit future warmer temperate zones year-round, as it
+grows under a 4 h photoperiod, expected in winter, or at
+light-attenuated depths. MIT9313 demonstrates an unexpected tolerance to
+higher light levels and cumulative diel PUR, but only under low oxygen
+conditions of 25 µM and 2.5 µM (Figure \@ref(fig:MIT9313PAR)), enabling
+MIT9313 to grow in OMZ, even at depths closer to the surface. MIT9313
+carries a gene encoding (S)-2-hydroxy-acid oxidase
+[@cunaneCrystalStructureAnalysis2005], with a K~M~ for [O~2~] of \~ 250
+µM (Figure \@ref(fig:ProchlorococcusEnzymeKms)), which produces
+H~2~O~2~. Growth at lower [O~2~] may protect MIT9313 from
+auto-intoxication from production of H~2~O~2~. We hypothesize that under
+250 µM O~2~ and higher blue light, *P. marinus* MIT9313 suffers
+photoinhibition, resulting in part from the inactivation of PSII caused
+by the production of H~2~O~2~. This photoinhibition is compounded by
+limited inducible repair for PSII, due to the absence of FtsH 1 and 2
+expression in *P. marinus* MIT9313
+[@bonisteelStrainSpecificDifferences2018]. MIT9313 shows remarkable
+ability to thrive under very low [O~2~], potentially allowing it to
+expand into broader ecological niches. These results are supported by
+Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSI protein
+subunits annotated as derived from MIT9313 detected at depths \> 120 m,
+along with PSII subunits at depths from 50 m to 200 m in regions where
+O~2~ was 15 µM. Bagby and Chisholm
+[@bagbyResponseProchlorococcusVarying2015] suggest that O~2~ has a
+protective role in *Prochlorococcus* under lower carbon dioxide
+environments when carbon fixation is limited. The deep water
+environments typical for MIT9313 are relatively nutrient rich, and
+*Prochlorococcus* take up and metabolize various sugars
+[@gomez-baenaGlucoseUptakeIts2008;
+@munoz-marinGlucoseUptakeProchlorococcus2017;
+@munoz-marinProchlorococcusCanUse2013] and amino acids
+[@zubkovDepthRelatedAmino2004]. In future work we aim to test whether
+MIT9313 is using photosynthesis to drive CO~2~ fixation in low O~2~
+environments, or whether PSII generation of O~2~ acts as an electron
+sink for respiration, using ATP for maintenance and to take up nutrients
+from the surroundings. Partensky *et al*.
+[@partenskyComparisonPhotosyntheticPerformances2018] indeed found that
+in the low-light conditions found in the OMZ, MED4, SS120 and MIT9313
+all became net O~2~ consumers, suggesting that the low light levels
+cause the respiratory chain to consume more O~2~ than the photosynthetic
+electron transport chain generates, thus contributing to maintenance of
+the low O~2~ environment.
 
@@
 # Data availability {.unnumbered}
-All data obtained from the Multicultivator were saved as comma separated values files and are available at https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData.
-Annotated code for data import, transformations and analyses are available at https://github.com/FundyPhytoPhys/prochlorococcus_o2/Code.
+
+All data obtained from the Multicultivator were saved as comma separated
+values files and are available at
+<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData>.
+Annotated code for data import, transformations and analyses are
+available at
+<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Code>.
 
 # Acknowledgements {.unnumbered}
-Miranda Corkum maintained cultures and trained personnel in culture handling.
-Carlie Barnhill (Mount Allison Student) assisted with code for import of multicultivator growth data files.
-Sarah Arthur & Daytona McMackin (Mount Allison Students) assisted with culturing and setting up Multicultivator runs.
+
+Miranda Corkum maintained cultures and trained personnel in culture
+handling. Carlie Barnhill (Mount Allison Student) assisted with code for
+import of multicultivator growth data files. Sarah Arthur & Daytona
+McMackin (Mount Allison Students) assisted with culturing and setting up
+Multicultivator runs.
 
@@
 
-To Be Entered through PLoSONe system and deleted here
-Czech Academy of Science (OP) visiting fellowship supporting DAC work at AlgaTech
-Canada Research Chair in Phytoplankton Ecophysiology (DAC)
-Natural Sciences and Engineering Research Council of Canada, 'Latitude and Light' (DAC)
-Canada Foundation for Innovation (DAC)
-New Brunswick Foundation for Innovation (DAC)
-Rice Graduate Fellowship 2021 and 2022 (MS)
+To Be Entered through PLoSONe system and deleted here Czech Academy of
+Science (OP) visiting fellowship supporting DAC work at AlgaTech Canada
+Research Chair in Phytoplankton Ecophysiology (DAC) Natural Sciences and
+Engineering Research Council of Canada, 'Latitude and Light' (DAC)
+Canada Foundation for Innovation (DAC) New Brunswick Foundation for
+Innovation (DAC) Rice Graduate Fellowship 2021 and 2022 (MS)
 

### 2024-03-09 Code/Manuscript_O2.Rmd
changed slr1463 to sll1463

@@
 Transcript analysis demonstrates that MIT9313 expressed primarily FtsH3,
-homologous to *Synechocystis* *slr*1463, possibly involved in PSI
+homologous to *Synechocystis* *sll*1463, possibly involved in PSI
 biogenesis [@krynickaFtsH4ProteaseControls2022,

### 2024-03-09 Code/Manuscript_O2.Rmd
Fixed fig cap for deltaODLogGrowthPlot

@@
 deltaODLogGrowthPlot_cap <- glue("**Fitting chlorophyll specific growth rate for each tube in the Multicultivator.**",
-                      "The left y-axis is $\\Delta$OD (OD680 - OD720).",
-                      "The right y-axis is actinic PAR levels (µmol photons m^-2^ s^-1^).",
+                      "The left y-axis is chlorophyll proxy optical density (OD~680~ - OD~720~;
+$\\Delta$OD)",
+                      "The right y-axis is actinic PAR levels (µmol photons m^-2^ s^-1^); colours represent the actinic spectral waveband: 450 nm (blue points) or 660 nm (red points).",
                       "The x-axis is time in hours (h).",
@@
                       "The gold points are the residuals of the fit.",
-                      "The blue or orange points represent the actinic spectral waveband under 450 nm or 660 nm, showing the imposed PAR level (µmol photons m^-2^ s^-1^) and photoperiod (h).",
                       "Meta data associated with each Multicultivator tube are in columns.",

### 2024-03-09 Code/Manuscript_O2.Rmd
added 'emission' and 'spectra' to title of overlay graph

@@
 CladeProchloroPhotosynthDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* photosynthesis complexes.**", 
-                       "Protein detections (circles) are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
+                       "Protein detections (circles) are plotted vs. O~2~ (µM) (X-axis) and depth (m) (Y-axis) at sample origin.",
                        "Rows separate data annotated as from *Prochlorococcus* clades: HLI (including *P.
@@
 CladeProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein metabolism complexes.**", 
-                       "Protein detections (annotated as solid grey circles) are plotted vs. O~2~ (µM) (X axis) and depth (m) (Y axis) at sample origin.",
+                       "Protein detections (annotated as solid grey circles) are plotted vs. O~2~ (µM) (X-axis) and depth (m) (Y-axis) at sample origin.",
                        "Rows separate data annotated as from *Prochlorococcus* clades: HLI (*P.
@@
 deltaODLogGrowthPlot_cap <- glue("**Fitting chlorophyll specific growth rate for each tube in the Multicultivator.**",
-                      "The left y-axis is chlorophyll proxy optical density (OD~680~ - OD~720~;
-$\\Delta$OD)",
+                                 "The x-axis is time in hours (h).",
+                                 "The left y-axis is chlorophyll proxy optical density (OD~680~ - OD~720~; $\\Delta$OD)",
                                  "The right y-axis is actinic PAR levels (µmol photons m^-2^ s^-1^); colours represent the actinic spectral waveband: 450 nm (blue points) or 660 nm (red points).",
-                      "The x-axis is time in hours (h).",
                                  "The green points are $\\Delta$OD measurements taken every 5 minutes.",
-                      "The black lines are logistic growth curves fit using a nonlinear model regression (R package, minpack.lm). ",
+                                 "The black lines are logistic growth curves fit using a nonlinear model regression (R package, minpack.lm).",
                                  "The gold points are the residuals of the fit.",
@@
 
-OverlayPlots_cap <- glue("**Normalized absorbance and Photosynthetically Usable Radiation for *Prochlorococcus marinus* MED4 (A,D,G); SS120 (B,E,H); MIT9313 (C,F,I) grown under three emission wavebands.**",
+OverlayPlots_cap <- glue("**Normalized absorbance, emission and Photosynthetically Usable Radiation spectra for *Prochlorococcus marinus* MED4 (A,D,G); SS120 (B,E,H); MIT9313 (C,F,I) grown under three emission wavebands.**",
                        "**(A,B,C)** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated PUR spectra (solid black line and shaded grey).",

### 2024-03-09 Code/Manuscript_O2.Rmd
Changed fig cap for several figures. Used same description format of faceted rows and columns across all figures

@@
 MED4PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade) vs. photoperiod (h).  **",
-                    "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                       "Columns show 3 levels of growth Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
+                    "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
+                    "Columns separate data from 3 levels of actinic Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
                     "Colours represent the actinic spectral waveband (nm).",
@@
 SS120PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low-Light (LLII/III) deep ocean clade) vs. photoperiod (h). **",
-                     "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                       "Columns show 3 levels of growth Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
+                     "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
+                       "Columns separate data from 3 levels of actinic Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
                     "Colours represent the actinic spectral waveband (nm).",
@@
 MIT9313PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
-                       "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                       "Columns show 3 levels of growth Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
+                       "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
+                       "Columns separate data from 3 levels of actinic Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
                     "Colours represent the actinic spectral waveband (nm).",
@@
  BluevsRedPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
-                    "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
+                    "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
                     "Columns separate data from strains; MED4 (A,B,C), SS120 (D,E,F) and MIT9313 (G,H,I).",
@@
 PhotoperiodPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
-                    "Rows show levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                    "Columns are strains; MED4 (A,B,C), SS120 (D,E,F) and MIT9313 (G,H,I).",
+                    "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
+                    "Columns separate data from strains; MED4 (A,B,C), SS120 (D,E,F) and MIT9313 (G,H,I).",
                     "Shapes show the imposed photoperiod (h); 4 h (solid square),  8 h (solid diamond), 12 h (solid circle), 16 h (solid upright triangle).",

### 2024-03-09 Code/Manuscript_O2.Rmd
Fixed wording in text describing deltaODLogGrowth figure

@@
 
-PAR of 180, 90 or 30 µmol photons m^-2^ s^-1^, and spectral wavebands
+Peak PAR of 180, 90 or 30 µmol photons m^-2^ s^-1^, and spectral wavebands
 (white LED full spectrum, 660 nm (red light), and 450 nm (blue light))
@@
 ```
+
 Figure \@ref(fig:deltaODLogGrowthPlot) is an example of chlorophyll
@@
 measurements for each tube in a Multicultivator. The residuals of the
-logistic growth curve fit are shown and the growth spectral waveband is
-plotted and illustrates the imposed PAR (µmol photons m^-2^ s^-1^) and
-photoperiod (h).
+logistic growth curve fit are shown. The actinic PAR (µmol photons m^-2^ s^-1^) are plotted for each tube and illustrates the applied photoperiod (h) regimes.
 
@@
 PurParPlot_cap <- glue("**Peak Photosynthetically Usable Radiation (PUR) (µmol photons m^-2^ s^-1^) vs. peak Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^).**",
-                       "The correlation between PAR, plotted on the x-axis and PUR, plotted on the y-axis, are coloured for each growth spectral waveband; 450 nm (blue circles), 660 nm (red circles) and white LED (black circles).",
+                       "The correlation between PAR, plotted on the x-axis and PUR, plotted on the y-axis, are coloured for each actinic spectral waveband; 450 nm (blue circles), 660 nm (red circles) and white LED (black circles).",
                        "The grey dashed line represents a hypothetical one to one correlation.",
@@
                     "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                    "Columns separate data from 3 levels of actinic Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
+                    "Columns separate data from 3 levels of peak actinic Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
                     "Colours represent the actinic spectral waveband (nm).",
@@
                      "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                       "Columns separate data from 3 levels of actinic Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
+                       "Columns separate data from 3 levels of peak actinic Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
                     "Colours represent the actinic spectral waveband (nm).",
@@
                        "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                       "Columns separate data from 3 levels of actinic Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
+                       "Columns separate data from 3 levels of peak actinic Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
                     "Colours represent the actinic spectral waveband (nm).",

### 2024-03-09 Code/Manuscript_O2.Rmd
Fixed citations in re: FtsH

@@
 relies on the removal of damaged PsbA
-[@mannInvolvementFtsHHomologue2000; @adamFtsHProteasesChloroplasts2005],
+[@mannInvolvementFtsHHomologue2000; @komendaExposedNTerminalTail2007],
 followed by reassembly with newly synthesized PsbA
@@
 [@kanervoD1ProteinDegradation1993], mediated largely by a heterohexamer,
-termed in *Prochlorococcus* (FtsH1-FtsH2)~3~, a membrane-bound
-[@sacharzSubCellularLocation2015; @zakInitialStepsBiogenesis2001]
-metalloprotease [(Chiba et al., 2002) (Yoshioka-Nishimura and Yamamoto,
-2014), @boehmSubunitOrganizationSynechocystis2012a;
-@komendaExposedNTerminalTail2007].
-
-*Prochlorococcus* genomes encode 4 FtsH proteins, henceforth referred to
+termed in *Prochlorococcus* (FtsH1-FtsH2)~3~, a membrane-bound metalloprotease [@chibaMembraneProteinDegradation2002; @boehmSubunitOrganizationSynechocystis2012a; @sacharzSubCellularLocation2015].
+
+*Prochlorococcus* genomes encode 4 FtsH proteins [@mannInvolvementFtsHHomologue2000; @adamFtsHProteasesChloroplasts2005], henceforth referred to
 as FtsH1-4, homologs to the characterized FtsH isoforms of the model
@@
 [@bonisteelStrainSpecificDifferences2018], homologs to the
-*Synechocystis* *slr*0228 and *slr*1604, implicated in PSII repair. In
+*Synechocystis* *slr*0228 and *slr*1604, implicated in PSII repair [@adamFtsHProteasesChloroplasts2005; @boehmSubunitOrganizationSynechocystis2012a]. In
 contrast, representative LLIV strain MIT9313 shows no induction of
 expression of these FtsH protease isoforms when shifted to high light,
-and thus has fewer of these FtsH hexamers serving each photosystem.
+and thus has fewer of these FtsH hexamers serving each photosystem [@bonisteelStrainSpecificDifferences2018].
 Transcript analysis demonstrates that MIT9313 expressed primarily FtsH3,
 homologous to *Synechocystis* *sll*1463, possibly involved in PSI
-biogenesis [@krynickaFtsH4ProteaseControls2022,
+biogenesis [@mannInvolvementFtsHHomologue2000; @krynickaFtsH4ProteaseControls2022,
 @konikCyanobacterialFtsH4Protease2024]. This FtsH expression did not

### 2024-03-09 Code/Manuscript_O2.Rmd
Fixed zotero citation keys

@@
 for Flavodiirons were obtained from Allahverdiyeva *et al*.
-[@allahverdiyevaCyanobacterialOxygenicPhotosynthesis2015a], as they do
+[@allahverdiyevaCyanobacterialOxygenicPhotosynthesis2015], as they do
 not have allocated EC numbers. A full list of enzymes and corresponding
@@
 
-MED4PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade) vs. photoperiod (h).  **",
+MED4PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade) vs. photoperiod (h).**",
                     "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
@@
 [@kanervoD1ProteinDegradation1993], mediated largely by a heterohexamer,
-termed in *Prochlorococcus* (FtsH1-FtsH2)~3~, a membrane-bound metalloprotease [@chibaMembraneProteinDegradation2002; @boehmSubunitOrganizationSynechocystis2012a; @sacharzSubCellularLocation2015].
+termed in *Prochlorococcus* (FtsH1-FtsH2)~3~, a membrane-bound metalloprotease [@chibaMembraneProteinDegradation2002; @boehmSubunitOrganizationSynechocystis2012; @sacharzSubCellularLocation2015].
 
@@
 [@bonisteelStrainSpecificDifferences2018], homologs to the
-*Synechocystis* *slr*0228 and *slr*1604, implicated in PSII repair [@adamFtsHProteasesChloroplasts2005; @boehmSubunitOrganizationSynechocystis2012a]. In
+*Synechocystis* *slr*0228 and *slr*1604, implicated in PSII repair [@adamFtsHProteasesChloroplasts2005; @boehmSubunitOrganizationSynechocystis2012]. In
 contrast, representative LLIV strain MIT9313 shows no induction of
@@
                                      "The red shaded area denotes a K~m~ oxygen concentration range from 230 to 280 µM.",
-                                     "The green shaded area denotes a K~m~ oxygen concentration range from 5 to 50 µM . ",
-                                     "The blue shaded area denotes a K~m~ oxygen concentration range from 0.5 to 5 µM.  ",
+                                     "The green shaded area denotes a K~m~ oxygen concentration range from 5 to 50 µM.",
+                                     "The blue shaded area denotes a K~m~ oxygen concentration range from 0.5 to 5 µM.",
                                      "The black bars show the minimum and maximum K~m~ values.",

### 2024-03-09 Code/Manuscript_O2.Rmd
italicized 'P' in P value

@@
                       "Large symbols show mean of growth rate from logistic curve fits; small symbols show values from replicates, if any.",
-                    "Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to 660 nm (red lines) or 450 nm (blue lines) growth data for each combination of strain and dissolved oxygen shown with solid lines (red significantly different from blue, p value < 0.05) or dashed lines (red not significantly different from blue, p value > 0.05) tested using one-way ANOVA comparisons of fits.",
+                    "Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to 660 nm (red lines) or 450 nm (blue lines) growth data for each combination of strain and dissolved oxygen shown with solid lines (red significantly different from blue, *P* value < 0.05) or dashed lines (red not significantly different from blue, *P* value > 0.05) tested using one-way ANOVA comparisons of fits.",
                        .sep = " ")
@@
                     "Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to data pooled for each combination of strain and dissolved oxygen shown with solid lines.
-Separate models fit to photoperiod data and shown if significantly different (p value < 0.05) from the pooled model using one-way ANOVA; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).",
+Separate models fit to photoperiod data and shown if significantly different (*P* value < 0.05) from the pooled model using one-way ANOVA; 4 h (long dashed line); 8 h (dotted line); 12 h (dashed line); and 16 h (dot dashed line).",
                        .sep = " ")

### 2024-03-09 Code/Plots_PURFits.Rmd
Made points larger, made figure height and width larger

@@
        caption = "NA = atleast one model did not fit due to lack of data points; 
-       ns = not significantly different from all photoperiod model (p value > 0.05); 
-       numbers = significantly different pvalues from all photoperiod model (p value < 0.05)")
+       ns = not significantly different from all photoperiod model (*P* value > 0.05); 
+       numbers = significantly different pvalues from all photoperiod model (*P* value < 0.05)")
 
@@
   geom_rect(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, fill = "white") +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 3, alpha = 1.0) +
-    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.0, alpha = 0.8) +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 3.5, alpha = 1.0) +
+    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2.0, alpha = 0.6) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.80, linetype = "solid", show.legend = F, data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) +
@@
         legend.background = element_rect(color = "black"),
-        legend.title =  element_text(size = 28),  #change legend title font size
+        legend.title =  element_text(size = 25),  #change legend title font size
         legend.title.align = 0.5,
-        legend.text = element_text(size = 29),   #change legend text font size
+        legend.text = element_text(size = 25),   #change legend text font size
         legend.position = "top",
@@
 
-ggsave(file = file.path(PlotsOut, paste("PhotoperiodPurFitsPlots",".png",sep = "")), plot = PhotoperiodPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("PhotoperiodPurFitsPlots",".png",sep = "")), plot = PhotoperiodPurFitsPlots, device = NULL, scale = 1, height=40, width= 54, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
        caption = "NA = atleast one model did not fit due to lack of data points; 
-       ns = not significantly different from WL model (p value > 0.05); 
-       numbers = significantly different pvalues from all WL model (p value < 0.05)")
+       ns = not significantly different from WL model (*P* value > 0.05); 
+       numbers = significantly different pvalues from all WL model (*P* value < 0.05)")
 
@@
   geom_rect(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, fill = "white") +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 3, alpha = 1.0) +
-    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 1.0, alpha = 0.8) +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 3.5, alpha = 1.0) +
+    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.6) +
    geom_line(aes(x = PURPhotonDose_day, y = .fitted, color = as.factor(WL)), size = 0.6, data = .
@@
   scale_colour_manual(values = MCMIXColours, labels = c("660 nm", "450 nm")) +
-  scale_linetype_manual(values = c("solid", "dashed"), labels = c("p value < 0.05", "p value > 0.05")) +
+  scale_linetype_manual(values = c("solid", "dashed"), labels = c("P value < 0.05", "P value > 0.05")) +
   scale_shape_manual(values = PhotoperiodShapes, labels = c("16 h", "12 h", "8 h", "4 h") )  +
@@
 
-ggsave(file = file.path(PlotsOut, paste("BluevsRedPurFitsPlots",".png",sep = "")), plot = BluevsRedPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("BluevsRedPurFitsPlots",".png",sep = "")), plot = BluevsRedPurFitsPlots, device = NULL, scale = 1, height=40, width= 54, units = c("cm"),dpi = 300, limitsize = TRUE)
 

### 2024-03-10 Code/Manuscript_O2.Rmd
added full name for Synechocystis and minor edits

@@
 as FtsH1-4, homologs to the characterized FtsH isoforms of the model
-freshwater cyanobacterium *Synechocystis* FtsH, and with presumably
+freshwater cyanobacterium *Synechocystis sp. PCC6803*, and with presumably
 parallel functions (Table \@ref(tab:FtsHTable)). Upon a shift to higher
@@
 biogenesis [@mannInvolvementFtsHHomologue2000; @krynickaFtsH4ProteaseControls2022,
-@konikCyanobacterialFtsH4Protease2024]. This FtsH expression did not
+@konikCyanobacterialFtsH4Protease2024]. FtsH3 expression did not
 increase in response to light stress in MIT9313

### 2024-03-10 Code/Manuscript_O2.Rmd
Fixed italics for genus Synechocystis

@@
 as FtsH1-4, homologs to the characterized FtsH isoforms of the model
-freshwater cyanobacterium *Synechocystis sp. PCC6803*, and with presumably
+freshwater cyanobacterium *Synechocystis sp.* PCC6803, and with presumably
 parallel functions (Table \@ref(tab:FtsHTable)). Upon a shift to higher
@@
 
-FtsHTable <- tibble(Organism = c("*Prochlorococcus marinus*", "*Synechocystis sp. PCC6803*", "*Synechocystis sp. PCC6803* isoform", "Function"),
+FtsHTable <- tibble(Organism = c("*Prochlorococcus marinus*", "*Synechocystis sp.* PCC6803", "*Synechocystis sp.* PCC6803 isoform", "Function"),
                     FtsH1 = c("FtsH1", "*Slr*0228", "FtsH2", "PSII Repair"),

### 2024-03-10 Code/Manuscript_O2.Rmd
Changed actinic to imposed in fig. cap

@@
                     "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                    "Columns separate data from 3 levels of peak actinic Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
+                    "Columns separate data from 3 levels of peak imposed Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
                     "Colours represent the actinic spectral waveband (nm).",
@@
                      "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                       "Columns separate data from 3 levels of peak actinic Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
+                       "Columns separate data from 3 levels of peak imposed Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
                     "Colours represent the actinic spectral waveband (nm).",
@@
                        "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                       "Columns separate data from 3 levels of peak actinic Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
+                       "Columns separate data from 3 levels of peak imposed Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
                     "Colours represent the actinic spectral waveband (nm).",
@@
 CladeProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein metabolism complexes.**", 
-                       "Protein detections (annotated as solid grey circles) are plotted vs. O~2~ (µM) (X-axis) and depth (m) (Y-axis) at sample origin.",
-                       "Rows separate data annotated as from *Prochlorococcus* clades: HLI (*P.
-marinus* MED4 protein detection annotated as solid black circles), LLI (*P.
-marinus* NATL2A protein detection annotated as solid black circles), LLII/III (*P.
-marinus* SS120 protein detection annotated as solid black circles) and LLIV (*P.
-marinus* MIT9313 protein detection annotated as solid black circles).",
+                       "Protein detections (circles) are plotted vs. O~2~ (µM) (X-axis) and depth (m) (Y-axis) at sample origin.",
+                       "Rows separate data annotated as from *Prochlorococcus* clades: HLI (including *P.
+marinus* MED4, solid black circles), LLI (including *P.
+marinus* NATL2A, solid black circles), LLII/III (including *P.
+marinus* SS120, solid black circles) and LLIV (including *P.
+marinus* MIT9313, solid black circles).",
                        "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome.",
-                       "Culture growth experimental conditions indicated by horizontal grey lines for depths approximating Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^) and vertical grey lines for [O~2~] (µM).",
+                       "For comparison, culture growth experimental conditions are indicated by horizontal grey lines for depths approximating imposed peak Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^); and vertical grey lines for [O~2~] (µM).",
                        "Data obtained from the Biological and Chemical Oceanography Data Management Office repository [@saitoPeptidesTheirSpectral2018].",

### 2024-03-10 Code/Manuscript_O2.Rmd
changed imposed to actinic when referring to PAR or PUR

@@
 To estimate the Photosynthetic Usable Radiation (PUR), a proxy of
-incident photons that can be absorbed by the cells, for each *P.
-marinus* ecotype, the imposed Photosynthetic Active Radiation (PAR) was
+incident photons that can be absorbed by the cells, for each *P. marinus* ecotype, 
+the actinic Photosynthetic Active Radiation (PAR) was
 first determined using the reported delivery of sinusoidal diel PAR
@@
 E(λ) is the imposed growth light emission spectrum from equation
-\@ref(eq:WeightedPUR) and PAR is the imposed peak light level (µmol
+\@ref(eq:WeightedPUR) and PAR is the actinic peak light level (µmol
 photons m^-2^ s^-1^). Figure (\@ref(fig:PurParPlot)) shows the
-calculated peak PUR (µmol photons m^-2^ d^-1^) versus imposed actinic
+calculated peak PUR (µmol photons m^-2^ d^-1^) versus actinic
 peak PAR (µmol photons m^-2^ s^-1^) for each strain and each spectral
@@
 Figure \@ref(fig:OverlayPlots) provide visual representations of PUR,
-the black solid line and shaded area, in relation to the imposed PAR,
-the dotted line, under each imposed spectral wavebands for *P. marinus*
+the black solid line and shaded area, in relation to the actinic PAR,
+the dotted line, under each actinic spectral wavebands for *P. marinus*
 MED4 (A,B,C), SS120 (D,E,F) and MIT9313 (G,H,I). Figure
 (\@ref(fig:PurParPlot)) shows the relationship between calculated PUR
-versus imposed PAR for each *P. marinus* and each spectral waveband.
+versus actinic PAR for each *P. marinus* and each spectral waveband.
 
@@
 Photoperiod growth data that showed complete growth inhibition for each
-combination of strain, [O~2~] and imposed spectral waveband were omitted
+combination of strain, [O~2~] and actinic spectral waveband were omitted
 from the pooled photoperiod model. Statistical differences were
@@
                        "Columns show detections of proteins annotated as  Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
-                       "For comparison culture growth experimental conditions are indicated by horizontal grey lines for depths approximating imposed peak Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^); and vertical grey lines for imposed [O~2~] (µM).",
+                       "For comparison culture growth experimental conditions are indicated by horizontal grey lines for depths approximating actinic peak Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^); and vertical grey lines for imposed [O~2~] (µM).",
                        "Data obtained from the Biological and Chemical Oceanography Data Management Office repository [@saitoPeptidesTheirSpectral2018].",
@@
 *Prochlorococcus marinus* MED4, clade HLI, growth under 250 µM O~2~
-increased with higher imposed PAR and longer photoperiods (Figure
+increased with higher actinic PAR and longer photoperiods (Figure
 \@ref(fig:MED4PAR)), across all spectral wavebands. No growth was
@@
                     "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                    "Columns separate data from 3 levels of peak imposed Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
-                    "Colours represent the actinic spectral waveband (nm).",
+                    "Columns separate data from 3 levels of peak actinic Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
+                    "Colours represent the imposed spectral waveband (nm).",
                     "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
@@
                      "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                       "Columns separate data from 3 levels of peak imposed Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
-                    "Colours represent the actinic spectral waveband (nm).",
+                       "Columns separate data from 3 levels of peak actinic Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
+                    "Colours represent the imposed spectral waveband (nm).",
                     "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
@@
                        "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                       "Columns separate data from 3 levels of peak imposed Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
-                    "Colours represent the actinic spectral waveband (nm).",
+                       "Columns separate data from 3 levels of peak actinic Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
+                    "Colours represent the imposed spectral waveband (nm).",
                     "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
@@
 active light per day. Cumulative diel PUR (µmol photons m^-2^ d^-1^) was
-calculated from the imposed PUR (µmol photons m^-2^ s^-1^) and
-photoperiod (h). We plotted growth rates vs. cumulative diel PUR to
+calculated from the actinic PUR (µmol photons m^-2^ s^-1^) and
+photoperiod (h) (Equation \@ref(eq:SumPURDay)). We plotted growth rates vs. cumulative diel PUR to
 determine whether growth is a simple response to diel PUR, across
@@
                        "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome.",
-                       "For comparison, culture growth experimental conditions are indicated by horizontal grey lines for depths approximating imposed peak Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^); and vertical grey lines for [O~2~] (µM).",
+                       "For comparison, culture growth experimental conditions are indicated by horizontal grey lines for depths approximating actinic peak Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^); and vertical grey lines for [O~2~] (µM).",
                        "Data obtained from the Biological and Chemical Oceanography Data Management Office repository [@saitoPeptidesTheirSpectral2018].",
@@
                                  "The left y-axis is chlorophyll proxy optical density (OD~680~ - OD~720~; $\\Delta$OD)",
-                                 "The right y-axis is actinic PAR levels (µmol photons m^-2^ s^-1^); colours represent the actinic spectral waveband: 450 nm (blue points) or 660 nm (red points).",
+                                 "The right y-axis is actinic PAR levels (µmol photons m^-2^ s^-1^); colours represent the imposed spectral waveband: 450 nm (blue points) or 660 nm (red points).",
                                  "The green points are $\\Delta$OD measurements taken every 5 minutes.",

### 2024-03-10 Code/Manuscript_O2.Rmd
changed 2 versus to vs. in text for consistency

@@
 photons m^-2^ s^-1^). Figure (\@ref(fig:PurParPlot)) shows the
-calculated peak PUR (µmol photons m^-2^ d^-1^) versus actinic
+calculated peak PUR (µmol photons m^-2^ d^-1^) vs. actinic
 peak PAR (µmol photons m^-2^ s^-1^) for each strain and each spectral
@@
 (\@ref(fig:PurParPlot)) shows the relationship between calculated PUR
-versus actinic PAR for each *P. marinus* and each spectral waveband.
+vs. actinic PAR for each *P. marinus* and each spectral waveband.
 

### 2024-03-10 Code/Manuscript_O2.Rmd
changed LLIII to LLII/III in text

@@
 balance electron transport, which may exclude it from growth under our
-lowest 2.5 µmol O~2~ L^-1^ condition. SS120 from Clade LLIII is
+lowest 2.5 µmol O~2~ L^-1^ condition. SS120 from Clade LLII/III is
 restricted to low light under full 250 µmol O~2~ L^-1^ , shows expanded
@@
 analyzed. We focused our analysis here on core photosynthetic protein
-complexes, for clades HL, LLI, LLIII and LLIV (Figure
+complexes, for clades HL, LLI, LLII/III and LLIV (Figure
 \@ref(fig:CladeProchloroPhotosynthDepthO2) as a function of depth (a

### 2024-03-11 Code/Manuscript_O2.Rmd
minor edits

@@
 lowest 2.5 µmol O~2~ L^-1^ condition. SS120 from Clade LLII/III is
-restricted to low light under full 250 µmol O~2~ L^-1^ , shows expanded
+restricted to low light under full 250 µmol O~2~ L^-1^, shows expanded
 light exploitation under 25 µmol O~2~ L^-1^, but is excluded from growth
@@
 in the low-light conditions found in the OMZ, MED4, SS120 and MIT9313
-all became net O~2~ consumers, suggesting that the low light levels
+all became net O~2~ consumers, suggesting that low light levels
 cause the respiratory chain to consume more O~2~ than the photosynthetic

### 2024-03-11 Code/Manuscript_O2.Rmd
wording on O2 dependent enzymes

@@
 Figure \@ref(fig:ProchlorococcusEnzymeKms) shows the measured or
-inferred K~M~ for [O~2~] for genes encoding enzymes
-[@omarAnnotationGenesEncoding2023] for *P. marinus* strains from clades
+inferred K~M~ for [O~2~] for enzymes encoded by genes 
+[@omarAnnotationGenesEncoding2023] from *P. marinus* strains, from clades
 HLI, LLI, LLII/III and LLIV. MED4 increases expression of alternative

### 2024-03-11 Code/Manuscript_O2.Rmd
minor edits

@@
 samples taken across a range of [O~2~] and depth, which in turn
-correlates to peak light at the site of sampling. In parallel we
+correlates to depth attenuated peak light at the site of sampling. In parallel we
 analyzed the growth and physiological responses of representative
@@
 PCC6803.
-Protein homology determined by multiple sequence alignment with MUSCLE followed by construction of maximum likelihood phylogenetic tree using 1000 bootstrap replicates in MEGAX.",
+Protein homologies between *Prochlorococcus* and *Synechocystis* were determined by multiple sequence alignment with MUSCLE followed by construction of maximum likelihood phylogenetic tree using 1000 bootstrap replicates in MEGAX.",
               col.names =  c("Organism",

### 2024-03-11 Code/Manuscript_O2.Rmd
used imposed PAR inplace of actinic PAR.

@@
 measurements for each tube in a Multicultivator. The residuals of the
-logistic growth curve fit are shown. The actinic PAR (µmol photons m^-2^ s^-1^) are plotted for each tube and illustrates the applied photoperiod (h) regimes.
+logistic growth curve fit are shown. The imposed PAR (µmol photons m^-2^ s^-1^) are plotted for each tube and illustrates the applied photoperiod (h) regimes.
 
@@
 incident photons that can be absorbed by the cells, for each *P. marinus* ecotype, 
-the actinic Photosynthetic Active Radiation (PAR) was
+the imposed Photosynthetic Active Radiation (PAR) was
 first determined using the reported delivery of sinusoidal diel PAR
@@
 ```
-Actinic PUR levels (µmol photons m^-2^ s^-1^) were calculated from
-actinic PAR (µmol photons m^-2^ s^-1^) levels using the equation
+PUR levels (µmol photons m^-2^ s^-1^) were calculated from
+imposed PAR (µmol photons m^-2^ s^-1^) levels using the equation
 \@ref(eq:PUR) from [@morelAvailableUsableStored1978]; where P(λ) is the
@@
 E(λ) is the imposed growth light emission spectrum from equation
-\@ref(eq:WeightedPUR) and PAR is the actinic peak light level (µmol
+\@ref(eq:WeightedPUR) and PAR is the imposed peak light level (µmol
 photons m^-2^ s^-1^). Figure (\@ref(fig:PurParPlot)) shows the
-calculated peak PUR (µmol photons m^-2^ d^-1^) vs. actinic
+calculated peak PUR (µmol photons m^-2^ d^-1^) vs. imposed
 peak PAR (µmol photons m^-2^ s^-1^) for each strain and each spectral
@@
 of the base (photoperiod) multiplied by the height (PUR) (Equation
-\@ref(eq:SumPURDay)); where PUR is the actinic light calculated from
-equation \@ref(eq:PUR) (µmol photons m^-2^ s^-1^), 3600 is the time
-conversion from seconds to hour and photoperiod is the imposed
+\@ref(eq:SumPURDay)); where PUR is the usable light (µmol photons m^-2^ s^-1^) calculated from
+equation \@ref(eq:PUR), 3600 is the time conversion from seconds to hour and photoperiod is the imposed
 photoperiod (h).
@@
 Figure \@ref(fig:OverlayPlots) provide visual representations of PUR,
-the black solid line and shaded area, in relation to the actinic PAR,
-the dotted line, under each actinic spectral wavebands for *P. marinus*
+the black solid line and shaded area, in relation to the imposed PAR,
+the dotted line, under each imposed spectral wavebands for *P. marinus*
 MED4 (A,B,C), SS120 (D,E,F) and MIT9313 (G,H,I). Figure
 (\@ref(fig:PurParPlot)) shows the relationship between calculated PUR
-vs. actinic PAR for each *P. marinus* and each spectral waveband.
+vs. imposed PAR for each *P. marinus* and each spectral waveband.
 
@@
 Photoperiod growth data that showed complete growth inhibition for each
-combination of strain, [O~2~] and actinic spectral waveband were omitted
+combination of strain, [O~2~] and imposed spectral waveband were omitted
 from the pooled photoperiod model. Statistical differences were
@@
 
-PurParPlot_cap <- glue("**Peak Photosynthetically Usable Radiation (PUR) (µmol photons m^-2^ s^-1^) vs. peak Photosynthetically Active Radiation (PAR) (µmol photons m^-2^ s^-1^).**",
-                       "The correlation between PAR, plotted on the x-axis and PUR, plotted on the y-axis, are coloured for each actinic spectral waveband; 450 nm (blue circles), 660 nm (red circles) and white LED (black circles).",
+PurParPlot_cap <- glue("**Peak Photosynthetically Usable Radiation (PUR; µmol photons m^-2^ s^-1^) vs. peak Photosynthetically Active Radiation (PAR; µmol photons m^-2^ s^-1^).**",
+                       "The correlation between PAR, plotted on the x-axis and PUR, plotted on the y-axis, are coloured for each imposed spectral waveband; 450 nm (blue circles), 660 nm (red circles) and white LED (black circles).",
                        "The grey dashed line represents a hypothetical one to one correlation.",
@@
                        "Columns show detections of proteins annotated as  Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
-                       "For comparison culture growth experimental conditions are indicated by horizontal grey lines for depths approximating actinic peak Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^); and vertical grey lines for imposed [O~2~] (µM).",
+                       "For comparison culture growth experimental conditions are indicated by horizontal grey lines for depths approximating peak Photosynthetically Active Radiation (PAR; µmol photons m^-2^ s^-1^); and vertical grey lines for imposed [O~2~] (µM).",
                        "Data obtained from the Biological and Chemical Oceanography Data Management Office repository [@saitoPeptidesTheirSpectral2018].",
@@
 *Prochlorococcus marinus* MED4, clade HLI, growth under 250 µM O~2~
-increased with higher actinic PAR and longer photoperiods (Figure
+increased with higher imposed PAR and longer photoperiods (Figure
 \@ref(fig:MED4PAR)), across all spectral wavebands. No growth was
@@
 MED4PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade) vs. photoperiod (h).**",
-                    "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                    "Columns separate data from 3 levels of peak actinic Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
+                    "Rows separate data from levels of imposed dissolved O~2~ concentrations (250 µM, 25 µM and 2.5 µM).",
+                    "Columns separate data from 3 levels of peak imposed Photosynthetically Active Radiation (PAR; 30, 90 and 180 µmol photons m^-2^ s^-1^).",
                     "Colours represent the imposed spectral waveband (nm).",
@@
                     "X-axis is photoperiod (h).",
-                    "Y-axis is actinic Photosynethetically Active Radiation (PAR, µmol photons m^-2^ s^-1^).",
+                    "Y-axis is Photosynethetically Active Radiation (PAR, µmol photons m^-2^ s^-1^).",
                     "**A.** represents the model under 250 µM of O~2~ and red light.",
@@
 SS120PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low-Light (LLII/III) deep ocean clade) vs. photoperiod (h). **",
-                     "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                       "Columns separate data from 3 levels of peak actinic Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
+                    "Rows separate data from levels of imposed dissolved O~2~ concentrations (250 µM, 25 µM and 2.5 µM).",
+                    "Columns separate data from 3 levels of peak imposed Photosynthetically Active Radiation (PAR; 30, 90 and 180 µmol photons m^-2^ s^-1^).",
                     "Colours represent the imposed spectral waveband (nm).",
@@
 MIT9313PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
-                       "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                       "Columns separate data from 3 levels of peak actinic Photosynthetically Active Radiation (PAR); 30, 90 and 180 µmol photons m^-2^ s^-1^.",
+                    "Rows separate data from levels of imposed dissolved O~2~ concentrations (250 µM, 25 µM and 2.5 µM).",
+                    "Columns separate data from 3 levels of peak imposed Photosynthetically Active Radiation (PAR; 30, 90 and 180 µmol photons m^-2^ s^-1^).",
                     "Colours represent the imposed spectral waveband (nm).",
@@
                     "X-axis is photoperiod (h).",
-                    "Y-axis is actinic Photosynthetically Active Radiation (PAR, µmol photons m^-2^ s^-1^).",
+                    "Y-axis is Photosynthetically Active Radiation (PAR; µmol photons m^-2^ s^-1^).",
                     "**A.** represents the model under 250 µM of O~2~ and red light.",
@@
 active light per day. Cumulative diel PUR (µmol photons m^-2^ d^-1^) was
-calculated from the actinic PUR (µmol photons m^-2^ s^-1^) and
+calculated from PUR (µmol photons m^-2^ s^-1^) and
 photoperiod (h) (Equation \@ref(eq:SumPURDay)). We plotted growth rates vs. cumulative diel PUR to
@@
                        "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome.",
-                       "For comparison, culture growth experimental conditions are indicated by horizontal grey lines for depths approximating actinic peak Photosynthetically Active Radiation (µmol photons m^-2^ s^-1^); and vertical grey lines for [O~2~] (µM).",
+                       "For comparison, culture growth experimental conditions are indicated by horizontal grey lines for depths approximating peak Photosynthetically Active Radiation (PAR; µmol photons m^-2^ s^-1^); and vertical grey lines for [O~2~] (µM).",
                        "Data obtained from the Biological and Chemical Oceanography Data Management Office repository [@saitoPeptidesTheirSpectral2018].",
@@
                                  "The left y-axis is chlorophyll proxy optical density (OD~680~ - OD~720~; $\\Delta$OD)",
-                                 "The right y-axis is actinic PAR levels (µmol photons m^-2^ s^-1^); colours represent the imposed spectral waveband: 450 nm (blue points) or 660 nm (red points).",
+                                 "The right y-axis is the Photosynthetically Active Radiation (PAR; µmol photons m^-2^ s^-1^) levels; colours represent the imposed spectral waveband: 450 nm (blue points) or 660 nm (red points).",
                                  "The green points are $\\Delta$OD measurements taken every 5 minutes.",
@@
 
-                       "Actinic PAR (µmol photons m^-2^ s^-1^) and calculated PUR (µmol photons m^-2^ s^-1^) levels are indicated.",
+                       "Photosynthetically Active Radiation (PAR; µmol photons m^-2^ s^-1^) and calculated Photosynthetically Usable Radiation (PUR; µmol photons m^-2^ s^-1^) levels are indicated.",
 

### 2024-03-11 Code/Plots_PURFits.Rmd
made "P" italic in legend

@@
 
-scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
+scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x)))}
 
@@
   scale_colour_manual(values = MCMIXColours, labels = c("660 nm", "450 nm")) +
-  scale_linetype_manual(values = c("solid", "dashed"), labels = c("P value < 0.05", "P value > 0.05")) +
+  scale_linetype_manual(values = c("solid", "dashed"), labels = c(italic("P") ~ "value <0.05", italic("P") ~ "value >0.05")) +
   scale_shape_manual(values = PhotoperiodShapes, labels = c("16 h", "12 h", "8 h", "4 h") )  +

### 2024-03-12 Code/Manuscript_O2.Rmd
minor edit
Added DOug as correspondence

@@
     affil: 1
-    main: false
     orcid: '0000-0001-8996-5463'
     email: 'dcampbel@mta.ca'
+    correspondence: true
 affiliation:
@@
 between 50 to 100 µmol photons m^-2^ s^-1^ PAR. Thus the designation of
-MIT9313 as a LL clade is dependent upon [O~2~] and light spectra.
-(Figure \@ref(fig:MIT9313GAM)E).
+MIT9313 as a LL clade is dependent upon [O~2~] and light spectra (Figure \@ref(fig:MIT9313GAM)E).
 

### 2024-03-12 Code/Manuscript_O2.Rmd
Removed FinguresIN from O2Anaylsis directory

@@
 FiguresIn <- file.path("..","Output", "Figures")
-FigureInO2Analy <- file.path(  "..", "..", "O2Analyses", "Output")
 

### 2024-03-12 Code/Manuscript_O2.Rmd
Moved .bib to "Docs" folder

@@
     pandoc_args: 
-      - '--lua-filter=scholarly-metadata.lua'
-      - '--lua-filter=author-info-blocks.lua'
+      - "--lua-filter=`r file.path('..','Docs', 'scholarly-metadata.lua')`"
+      - "--lua-filter=`r file.path('..','Docs', 'author-info-blocks.lua')`"
 always_allow_html: true
-bibliography: [Manuscript_O2.bib, RPackages.bib, FaultyCitations.bib]
+bibliography: ["`r file.path('..', 'Docs', 'Manuscript_O2.bib')`", "`r file.path('..', 'Docs', 'RPackages.bib')`", "`r file.path('..', 'Docs', 'FaultyCitations.bib')`"]
 csl: plos-one.csl
@@
 
-knitr::write_bib(c("knitr", "tidyverse", "lubridate", "ggplot2", "broom", "grid", "bookdown", "glue", "cowplot", "ggpubr", "ggh4x", "png", "zoo", "photobiology", "photobiologyWavebands", "data.table", "googlesheets4",  "mgcv", "minpack.lm"), 'RPackages.bib')
+knitr::write_bib(c("knitr", "tidyverse", "lubridate", "ggplot2", "broom", "grid", "bookdown", "glue", "cowplot", "ggpubr", "ggh4x", "png", "zoo", "photobiology", "photobiologyWavebands", "data.table", "googlesheets4",  "mgcv", "minpack.lm"), file.path("..", "Docs",'RPackages.bib'))
 

### 2024-03-12 Code/Manuscript_O2.Rmd
moved .csl to "Docs" folder. Moving .lua files did not work when moved out of "Code" folder

@@
     pandoc_args: 
-      - "--lua-filter=`r file.path('..','Docs', 'scholarly-metadata.lua')`"
-      - "--lua-filter=`r file.path('..','Docs', 'author-info-blocks.lua')`"
+      - '--lua-filter=scholarly-metadata.lua'
+      - '--lua-filter=author-info-blocks.lua'
 always_allow_html: true
 bibliography: ["`r file.path('..', 'Docs', 'Manuscript_O2.bib')`", "`r file.path('..', 'Docs', 'RPackages.bib')`", "`r file.path('..', 'Docs', 'FaultyCitations.bib')`"]
-csl: plos-one.csl
+csl: "`r file.path('..', 'Docs', 'plos-one.csl')`"
 editor_options: 

### 2024-03-12 Code/Manuscript_O2.Rmd
removed an empty line
Changed directory for knitted documents to "Output" folder

@@
     wrap: 72
+knit: (function(input, encoding) {
+  rmarkdown::render(input,
+                    output_dir = file.path('..', 'Output'))})
 ---
@@
 knitr::opts_chunk$set(fig.path='Figs/')
+
 ```

### 2024-03-13 Code/Manuscript_O2.Rmd
minor edit
Removed citation in abstract as per PLOS guidelines.

@@
 regimes, along with expanded Oxygen Minimum Zones. We used ocean protein
-data [@saitoPeptidesTheirSpectral2018] to help guide testing of
+data to help guide testing of
 *Prochlorococcus marinus* growth across a matrix of peak irradiances,

### 2024-03-13 Code/Manuscript_O2.Rmd
Renamed Supplemental to "Supporting information" as per PLOS guidelines.
Formulas are not displayed in the knitted .docx now that I moved the knitted output to a different folder. Reverting back to knit to "code" folder

@@
   markdown:
+
     wrap: 72
-knit: (function(input, encoding) {
-  rmarkdown::render(input,
-                    output_dir = file.path('..', 'Output'))})
 ---
@@
 
-# Supplemental {.unnumbered}
+# Supporting information {.unnumbered}
 

### 2024-03-13 Code/Manuscript_O2.Rmd
Copied .rmd from before I started changing the output destination. Still no equations in .docx

--- 2024-03-12 Code/Manuscript_O2.Rmd
@@
     affil: 1
+    main: false
     orcid: '0000-0001-8996-5463'
     email: 'dcampbel@mta.ca'
-    correspondence: true
 affiliation:
@@
 always_allow_html: true
-bibliography: ["`r file.path('..', 'Docs', 'Manuscript_O2.bib')`", "`r file.path('..', 'Docs', 'RPackages.bib')`", "`r file.path('..', 'Docs', 'FaultyCitations.bib')`"]
-csl: "`r file.path('..', 'Docs', 'plos-one.csl')`"
+bibliography: [Manuscript_O2.bib, RPackages.bib, FaultyCitations.bib]
+csl: plos-one.csl
 editor_options: 
@@
     wrap: 72
-knit: (function(input, encoding) {
-  rmarkdown::render(input,
-                    output_dir = file.path('..', 'Output'))})
 ---
@@
 knitr::opts_chunk$set(fig.path='Figs/')
-
 ```
@@
 
-knitr::write_bib(c("knitr", "tidyverse", "lubridate", "ggplot2", "broom", "grid", "bookdown", "glue", "cowplot", "ggpubr", "ggh4x", "png", "zoo", "photobiology", "photobiologyWavebands", "data.table", "googlesheets4",  "mgcv", "minpack.lm"), file.path("..", "Docs",'RPackages.bib'))
+knitr::write_bib(c("knitr", "tidyverse", "lubridate", "ggplot2", "broom", "grid", "bookdown", "glue", "cowplot", "ggpubr", "ggh4x", "png", "zoo", "photobiology", "photobiologyWavebands", "data.table", "googlesheets4",  "mgcv", "minpack.lm"), 'RPackages.bib')
 
@@
 FiguresIn <- file.path("..","Output", "Figures")
+FigureInO2Analy <- file.path(  "..", "..", "O2Analyses", "Output")
 

### 2024-03-13 Code/Manuscript_O2.Rmd
removed  equations out of chunk ```{=tex} ``` Seemed to be the problem

@@
 
-```{=tex}
 \begin{equation}
@@
 \end{equation}
-```
+
 PUR levels (µmol photons m^-2^ s^-1^) were calculated from
@@
 \end{equation}
-```
+
 The applied photoperiods were delivered using the sinusoidal circadian
@@
 \end{equation}
-```
+
 Figure \@ref(fig:OverlayPlots) provide visual representations of PUR,

### 2024-03-13 Code/Manuscript_O2.Rmd
Formatted as per PLOS guidelines. Removed citation in abstract and changed "Supplemental" to "Supporting information"

@@
 from the pooled photoperiod model. Statistical differences were
-determined at p \< 0.05.
+determined at *P* value \< 0.05.
 
@@
 
-\newpage
-
 ```{r BuildFtsHtable, echo = FALSE}
@@
 ```
-
-\newpage
 
@@
 
-# Supplemental {.unnumbered}
-
-\newpage
+\newpage
+
+# Supporting information {.unnumbered}
 
@@
 
-\newpage
-
 # Data availability {.unnumbered}
@@
 
+\newpage
+
 # References {.unnumbered}

### 2024-03-13 Code/Plots_OceanProtein.Rmd
Generated .tiff figures for PLOS submission. Commented out ggsave for redundant .png and .tiff

@@
 
- ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "ProchloroPhotosynthDepthO2.png")))
- ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "ProchloroPhotosynthDepthO2.tiff")))
+ # ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "ProchloroPhotosynthDepthO2.png")))
+ # ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "ProchloroPhotosynthDepthO2.tiff")))
 
@@
 
- ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "ProchloroProteinMetabDepthO2.png")))
- ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "ProchloroProteinMetabDepthO2.tiff")))
+ # ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "ProchloroProteinMetabDepthO2.png")))
+ # ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "ProchloroProteinMetabDepthO2.tiff")))
 
@@
 
- ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "NATLProchloroPhotosynthDepthO2.png")))
- ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "NATLProchloroPhotosynthDepthO2.tiff")))
+ # ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "NATLProchloroPhotosynthDepthO2.png")))
+ # ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "NATLProchloroPhotosynthDepthO2.tiff")))
 
@@
 
- ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "NATLProchloroProteinMetabDepthO2.png")))
- ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "NATLProchloroProteinMetabDepthO2.tiff")))
+ # ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "NATLProchloroProteinMetabDepthO2.png")))
+ # ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "NATLProchloroProteinMetabDepthO2.tiff")))
 
@@
 
- ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.png")))
- ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.tiff")))
+ # ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.png")))
+ # ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.tiff")))
 
@@
 
-  ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.png")))
-  ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.tiff")))
+  # ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.png")))
+  # ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.tiff")))
 
@@
  ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.png")))
- ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.tiff")))
+ ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSFiguresRound1", "Fig10.tiff")))
 
@@
    ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.png")))
-   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.tiff")))
+   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSFiguresRound1", "CladeProchloroProteinMetabDepthO2.tiff")))
 

### 2024-03-13 Code/Plots_OceanProtein.Rmd
Assigned PLOS figure numbers to .tiff

@@
  ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.png")))
- ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSFiguresRound1", "Fig10.tiff")))
+ ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSFiguresRound1", "Fig2.tiff")))
 
@@
    ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.png")))
-   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSFiguresRound1", "CladeProchloroProteinMetabDepthO2.tiff")))
+   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSFiguresRound1", "Fig10.tiff")))
 

### 2024-03-13 Code/Plots_Growth.Rmd
Renamed RMDs for consistent convention
Generated .tiff figures

--- 2024-03-04 Code/ManuscriptFigures.Rmd
@@
 PlotsOut <- file.path("..","Output", "Figures")
-# DataOut <- file.path("..","GrowthAssessData")
+PlotsOutPLOS <- file.path("..", "OutPut", "PLOSFiguresRound1")
 
@@
 
-```{r save ParPurPlots}
+```{r save PurParPlots}
 
 ggsave(file = file.path(PlotsOut, paste("PurParPlot",".png",sep = "")), plot = PurParPlot, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+ggsave(file = file.path(PlotsOutPLOS, "Fig1.tiff"), plot = PurParPlot, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
 
-# ggsave(file = file.path(PlotsPath, paste("deltaODLogGrowthPlotExpand",".png",sep = "")), plot = deltaODLogGrowthPlotExpand, device = NULL, scale = 1, height=25, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)
-# 
-# ggsave(file = file.path(PlotsPath, paste("deltaODGrowthRatesPlot",".png",sep = "")), plot = deltaODGrowthRatesPlot, device = NULL, scale = 1, height=25, width= 25, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOutPLOS, "S2_Fig.tiff"), plot = deltaODLogGrowthPlot, device = NULL, scale = 1, height=20, width= 30, units = c("cm"),dpi = 300, limitsize = TRUE)
+
 ```
@@
 
+ggsave(file = file.path(PlotsOutPLOS, "Fig3.tiff"), plot = MED4PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+
 ggsave(file = file.path(PlotsOut, paste("SS120PAR",".png",sep = "")), plot = SS120PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 
+ggsave(file = file.path(PlotsOutPLOS, "Fig5.tiff"), plot = SS120PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+
 ggsave(file = file.path(PlotsOut, paste("MIT9313PAR",".png",sep = "")), plot = MIT9313PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+
+ggsave(file = file.path(PlotsOutPLOS, "Fig7.tiff"), plot = SS120PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
 # Overlay whole cell absorbance with emission spectra all strain together
-```{r MED4 All Spectral Emission,  fig.height = 10, fig.width = 10}
+```{r allinone overlay plots,  fig.height = 10, fig.width = 10}
 
@@
         tagger.panel.tag.background = element_blank()) +
-  tagger::tag_facets(tag_levels  = c("A", "I"), tag_suffix = "")
+  tagger::tag_facets("panel",position = "tl", tag_pool  = c("A","D", "G", "B","E","H","C","F","I"), tag_suffix = "")
 
@@
 
-# ggsave(file = file.path(PlotsOut, paste("OverlayPlots",".tiff",sep = "")), plot = OverlayPlots, device = NULL, scale = 1, height = 25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOutPLOS, "S3_Fig.tiff"), plot = OverlayPlots, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 

### 2024-03-13 Code/Plots_PURFits.Rmd
ggsave to PlotsOutPLOS folder

@@
 PlotsOut <- file.path("..","Output", "Figures")
+PlotsOutPLOS <- file.path("..", "OutPut", "PLOSFiguresRound1")
 
@@
 
-# ggsave(file = file.path(PlotsOut, paste("PhotoperiodPurFitsPlots",".tiff",sep = "")), plot = PhotoperiodPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOutPLOS, "S4_Fig.tiff"), plot = PhotoperiodPurFitsPlots, device = NULL, scale = 1, height=40, width= 54, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
   geom_line(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(WL)), size = 1, show.legend = T) +
-# geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(Photoperiod)), size = 1, show.legend = F) +
+# geom_line(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(Photoperiod)), size = 1, show.legend = F) +
 # geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(Data_all_WL)), size = 1, show.legend = F) +
@@
   scale_linetype_manual(values = c("solid", "dashed"), labels = c(italic("P") ~ "value <0.05", italic("P") ~ "value >0.05")) +
-  scale_shape_manual(values = PhotoperiodShapes, labels = c("16 h", "12 h", "8 h", "4 h") )  +
+  scale_shape_manual(values = PhotoperiodShapes, labels = c("16 h", "12 h", "8 h", "4 h"))  +
   ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), cols = vars(Strain), 
@@
 
-# ggsave(file = file.path(PlotsOut, paste("BluevsRedPurFitsPlots",".tiff",sep = "")), plot = BluevsRedPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)
+ ggsave(file = file.path(PlotsOutPLOS, paste("Fig9.tiff",sep = "")), plot = BluevsRedPurFitsPlots, device = NULL, scale = 1, height=40, width= 54, units = c("cm"),dpi = 300, limitsize = TRUE)
 

### 2024-03-13 Code/Plots_GAM.Rmd
Generated .tiff for GAMs

@@
 DataOut <- file.path("..","Data", "CleanData")
-PlotsPath <- file.path("..","Output", "Figures")
+PlotsOut <- file.path("..","Output", "Figures")
+PlotsOutPLOS <- file.path("..", "OutPut", "PLOSFiguresRound1")
 
@@
 LayoutNiche <- rbind(
-                     c(3, 3, 3, 3, 6), # For 2.5 uM O2
-                     c(3, 3, 3, 3, 6), # For 2.5 uM O2
+                      # c(3, 3, 3, 3, 6), # For 2.5 uM O2     # remove comment for MIT9313
+                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2    # remove comment for MIT9313
                      c(2, 2, 2, 2, 5),   # For 25 uM O2
@@
 p3_Red <- grid.arrange(
-                       ContourLowO2 +   labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
-                          theme(legend.position = 'none'), 
+                       # ContourLowO2 +   labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + theme(legend.position = 'none'),   # remove comment for MIT9313
                        ContourIntO2 + labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
@@
                          theme(legend.position = 'none'), 
-                        legend1, 
+                        # legend1,   # remove comment for MIT9313
                         legend2, 
@@
 #  for thesis
-  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Red,  height = 10, width = 6 )
+  # ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Red,  height = 10, width = 6 )
 
 # for presentation
-  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Red,  height = 7.6, width = 6)
+  # ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Red,  height = 7.6, width = 6)
 
@@
 LayoutNiche <- rbind(
-                     c(3, 3, 3, 3, 6), # For 2.5 uM O2
-                     c(3, 3, 3, 3, 6), # For 2.5 uM O2
+                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2   # remove comment for MIT9313
+                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2   # remove comment for MIT9313
                      c(2, 2, 2, 2, 5),   # For 25 uM O2
@@
 p3_Blue <- grid.arrange(
-                         ContourLowO2 +   labs(title = bquote("F.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
+                         # ContourLowO2 +   labs(title = bquote("F.
+" ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()),
+                        ContourIntO2 +  labs(title = bquote("D.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
                           theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
-                        ContourIntO2 +  labs(title = bquote("E.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
-                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
-                        ContourHighO2 + labs(title = bquote("D.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
-                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
-                         legend1, 
+                        ContourHighO2 + labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
+                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()),                          # legend1,    # remove comment for MIT9313
                         legend2, 
@@
 #  for thesis
-  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Blue,  height = 10, width = 6)
+  # ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Blue,  height = 10, width = 6)
 
 # for presentation
-  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Blue,  height = 7.6, width = 6)
+  # ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Blue,  height = 7.6, width = 6)
 
@@
 
-```{r save png}
- ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(GamStrain, "GAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = LabelledCombinedGam,  height = 10, width = 10)
+```{r save plots}
+
+ ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "GAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = LabelledCombinedGam,  height = 10, width = 10)
+
+# MED4 GAM is Fig4.tiff
+# SS120 GAM is Fig6.tiff
+# MIT9313 GAM is Fig8.tiff
+ ggsave(file = file.path(PlotsOutPLOS, "Fig6.tiff", fsep = .Platform$file.sep), plot = LabelledCombinedGam, device = NULL, scale = 1,  height = 10, width = 10)
+
 ```

### 2024-03-13 Code/Plots_Growth.Rmd
Generated .tiff

@@
 
-ggsave(file = file.path(PlotsOutPLOS, "Fig7.tiff"), plot = SS120PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOutPLOS, "Fig7.tiff"), plot = MIT9313PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
 

### 2024-03-13 Code/Manuscript_O2.Rmd
Added .tiff names in chunk where the figure was generated for knit

@@
 
+# This is Fig1.tiff
 PurParPlot_cap <- glue("**Peak Photosynthetically Usable Radiation (PUR; µmol photons m^-2^ s^-1^) vs. peak Photosynthetically Active Radiation (PAR; µmol photons m^-2^ s^-1^).**",
@@
 
+# This is Fig2.tiff
 CladeProchloroPhotosynthDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* photosynthesis complexes.**", 
@@
 
+# This is Fig3.tiff
 MED4PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade) vs. photoperiod (h).**",
@@
 
+# This is Fig4.tiff
 MED4GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 grown under 660 nm (red) or 450 nm (blue) light.**",
@@
 
+# This is Fig5.tiff
 SS120PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low-Light (LLII/III) deep ocean clade) vs. photoperiod (h). **",
@@
 
+# This is Fig6.tiff
 SS120GAM_cap <- glue("**Contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 grown under 660 nm (red) or 450 nm (blue) light.**",
@@
 
+# This is Fig7.tiff
 MIT9313PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
@@
 
+# This is Fig8.tiff
 MIT9313GAM_cap <- glue("**Contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 grown under 660 nm (red) or 450 nm (blue) light.**",
@@
 
+# This is Fig9.tiff
  BluevsRedPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
@@
 
+# This is Fig10.tiff
 CladeProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein metabolism complexes.**", 
@@
 
+# This is Fig11.tiff
 ProchlorococcusEnzymeKms_cap <- glue("**K~m~ values for oxygen metabolizing enzymes.**" ,
@@
 
+#  This is Fig12.tiff
 DNARepairFig_cap <- glue("**Genes encoding DNA repair enzymes.**" ,
@@
 
+# This is S1_Fig.tiff 
 LabeledMC_cap <- glue("**PSI MCMIX-OD Multicultivator.**",
@@
 
+# This is S2_Fig.tiff 
 deltaODLogGrowthPlot_cap <- glue("**Fitting chlorophyll specific growth rate for each tube in the Multicultivator.**",
@@
 
+# This is S3_Fig.tiff 
 OverlayPlots_cap <- glue("**Normalized absorbance, emission and Photosynthetically Usable Radiation spectra for *Prochlorococcus marinus* MED4 (A,D,G); SS120 (B,E,H); MIT9313 (C,F,I) grown under three emission wavebands.**",
@@
 
+# This is S4_Fig.tiff 
 PhotoperiodPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
@@
 
+# This is S5_Fig.tiff 
 ProchlorococcusLightEnzymes_cap <- glue("***Prochlorococcus* genes encoding enzymes activated or inhibited by light.**",
@@
 
+# This is S1_Table.csv
 readRDS(file.path(DataIn,"ProchlorococcusEnzymeTable.Rds")) %>% 
@@
 
+# This is S2_Table
 MaxGrowthTable <- PURPARFits %>%
@@
 
+# This is S2_Table
 knitr::kable(MaxGrowthTable,
@@
              )
+
 ```

### 2024-03-14 Code/Plots_Growth.Rmd
Regenerated plots using sentence structure for axis titles and legends

@@
   theme_bw() +
-  labs(colour = "Growth Waveband (nm)") +
+  labs(colour = "Growth waveband (nm)") +
   theme(strip.text = element_blank(),
@@
   mutate(PhotoperiodLabelTitle = "Photoperiod (h)",
-         OxygenLabel_title = "Oxygen Concentration",
-         Oxygen_label = case_when(O2_uM %in% c(2.5, 25, 250) ~ paste("Oxygen Concentration", O2_uM, "µM", sep = " ")),
-         WLlabelTitle = "Growth Wavelength",
+         OxygenLabel_title = "Oxygen concentration",
+         Oxygen_label = case_when(O2_uM %in% c(2.5, 25, 250) ~ paste("Oxygen concentration:", O2_uM, "µM", sep = " ")),
+         WLlabelTitle = "Growth wavelength",
          WL_label = case_when(WL %in% c(450, 530, 660) ~ paste(WL, "nm", sep = " "),
@@
          Par_label = case_when(Par_ue %in% c(30, 90, 180) ~ paste(Par_ue, "µE", sep = " ")),
-         PhotoLabel = case_when(Photoperiod == 16 ~ "16 h Photoperiod", 
-                                 Photoperiod == 12 ~ "12 h Photoperiod",
-                                 Photoperiod == 8 ~ "8 h Photoperiod",
-                                 Photoperiod == 4 ~ "4 h Photoperiod")) %>%
+         PhotoLabel = case_when(Photoperiod == 16 ~ "Photoperiod: 16 h", 
+                                 Photoperiod == 12 ~ "Photoperiod: 12 h",
+                                 Photoperiod == 8 ~ "Photoperiod: 8 h",
+                                 Photoperiod == 4 ~ "Photoperiod: 4 h")) %>%
   # mutate(deltaOD_logistic_predict = map(deltaOD_logistic, possibly(augment, otherwise = NULL))) %>%
@@
                     labeller = labeller(Tube = label_both, WL_label = label_value, WL = label_value, Strain = label_value, OxygenLabel_title = label_value,Oxygen_label = label_value, OxygenLabel = label_value, Photoperiod = label_both, Par_label = label_value, SampleID = label_value))+
-  labs(y = "Chlorophyll proxy (ΔOD)" , x = "Elapsed Time (h)") +
+  labs(y = "Chlorophyll proxy (ΔOD)" , x = "Elapsed time (h)") +
    guides(colour = "none") +
@@
   mutate(PhotoperiodLabelTitle = "Photoperiod~(h)",
-         OxygenLabel = "Oxygen~Concentration~(µM)",
-         WLlabelTitle = "Growth~Wavelength~(nm)",
+         OxygenLabel = "Oxygen~concentration~(µM)",
+         WLlabelTitle = "Growth~wavelength~(nm)",
          ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
@@
     geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 1) +
- labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
+ labs( y = "Chlorophyll specific growth rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
    geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3, show.legend = F) +
@@
         legend.position = "top") +
-  labs(color = "Growth Wavelength (nm)",
-       fill = "Growth Wavelength (nm)")
+  labs(color = "Growth wavelength (nm)",
+       fill = "Growth wavelength (nm)")
 MED4PAR
@@
         legend.position = "top") +
-  labs(color = "Growth Wavelength (nm)",
-       fill = "Growth Wavelength (nm)")
+  labs(color = "Growth wavelength (nm)",
+       fill = "Growth wavelength (nm)")
 
@@
    mutate(PhotoperiodLabelTitle = "Photoperiod~(h)",
-         OxygenLabel = "Oxygen~Concentration~(µM)",
-         WLlabelTitle = "Growth~Wavelength~(nm)",
+         OxygenLabel = "Oxygen~concentration~(µM)",
+         WLlabelTitle = "Growth~wavelength~(nm)",
          ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
@@
         legend.position = "top") +
-  labs(color = "Growth Wavelength (nm)",
-       fill = "Growth Wavelength (nm)" )
+  labs(color = "Growth wavelength (nm)",
+       fill = "Growth wavelength (nm)" )
 
@@
          Run != 112) %>% 
-  mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste("Growth", "Waveband",  WL, "nm", sep = " "),
-        WL %in% c("WW") ~ paste("Growth", "Waveband", "White LED", sep = " ")),
+  mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste("Growth", "waveband",  WL, "nm", sep = " "),
+        WL %in% c("WW") ~ paste("Growth", "waveband", "White LED", sep = " ")),
         Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
-        WL_label = factor(WL_label, levels = c("Growth Waveband White LED", "Growth Waveband 660 nm", "Growth Waveband 450 nm"))) %>% 
+        WL_label = factor(WL_label, levels = c("Growth waveband White LED", "Growth waveband 660 nm", "Growth waveband 450 nm"))) %>% 
    unnest(cols = c(PurData), names_sep = "_", keep_empty = TRUE) %>%
@@
  # guides(colour = FALSE) +
-  labs(y = "Normalized Absorbance and Emission", x = "Wavelength (nm)") +
-  labs(linetype = "Spectra Type")+
+  labs(y = "Normalized absorbance and emission", x = "Wavelength (nm)") +
+  labs(linetype = "Spectra type")+
   scale_y_continuous(breaks=seq(0, 1.5, by = 0.25)) +

### 2024-03-14 Code/Manuscript_O2.Rmd
Formated figure citations as per PLOS guidelines

@@
 the dotted line, under each imposed spectral wavebands for *P. marinus*
-MED4 (A,B,C), SS120 (D,E,F) and MIT9313 (G,H,I). Figure
+MED4 (A-C), SS120 (D-F) and MIT9313 (G-I). Figure
 (\@ref(fig:PurParPlot)) shows the relationship between calculated PUR
@@
 The GAM model in Figure \@ref(fig:MED4GAM) summarizes MED4 growth
-responses to red (A,B) or blue (C,D) peak PAR and photoperiod across 2
+responses to red (A and B) or blue (C and D) peak PAR and photoperiod across 2
 imposed oxygen concentrations. Under 250 µM O~2~ MED4 achieved fastest
@@
 The GAM model in Figure \@ref(fig:SS120GAM) summarizes growth responses
-of SS120 to red (A,B) or blue (C,D) peak PAR and photoperiod, across the
+of SS120 to red (A and B) or blue (C and D) peak PAR and photoperiod, across the
 2 imposed oxygen concentrations. Under 250 µM O~2~, Figure
@@
 The GAM model in Figure \@ref(fig:MIT9313GAM) summarizes MIT9313 growth
-responses to red (A,B,C) or blue (D,E,F) peak PAR and photoperiod. Under
+responses to red (A-C) or blue (D-F) peak PAR and photoperiod. Under
 250 µM O~2~, Figure \@ref(fig:MIT9313GAM)D shows MIT9313 achieves
@@
 delivered cumulative diel PUR equivalent to other photoperiod treatments
-(Figure \@ref(fig:PhotoperiodPurFitsPlots)A,B,C). In parallel MED4
+(Figure \@ref(fig:PhotoperiodPurFitsPlots)A-C). In parallel MED4
 showed no growth under 2.5 µM O~2~, no matter the level of diel
@@
 cumulative diel PUR, with saturation of growth rate achieved around 1.0
-x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A,B),
+x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A and B),
 and no evidence of inhibition of growth at any achieved cumulative diel
@@
 more growth per unit diel cumulative PUR (Figure
-\@ref(fig:BluevsRedPurFitsPlots)A,B), consistent with Murphy *et al*.
+\@ref(fig:BluevsRedPurFitsPlots)A and B), consistent with Murphy *et al*.
 [@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for
@@
 distinct fits for different photoperiods refer to Figure
-\@ref(fig:PhotoperiodPurFitsPlots) A,B and C.
+\@ref(fig:PhotoperiodPurFitsPlots) A-C.
 
@@
 different photoperiods refer to Figure
-\@ref(fig:PhotoperiodPurFitsPlots) D,E and F.
+\@ref(fig:PhotoperiodPurFitsPlots) D-F.
 
@@
 compared to blue, wavebands (Figure
-\@ref(fig:BluevsRedPurFitsPlots)G,H). Interestingly, this protective
+\@ref(fig:BluevsRedPurFitsPlots)G and H). Interestingly, this protective
 effect of red light disappears for MIT9313 growing under 2.5 µM O~2~,
@@
 different photoperiod fits refer to Figure
-\@ref(fig:PhotoperiodPurFitsPlots) G,H and I.
+\@ref(fig:PhotoperiodPurFitsPlots) G-I.
 
@@
                     "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
-                    "Columns separate data from strains; MED4 (A,B,C), SS120 (D,E,F) and MIT9313 (G,H,I).",
+                    "Columns separate data from strains; MED4 (A-C), SS120 (D-F) and MIT9313 (G-I).",
                     "Shapes show the imposed photoperiod (h); 4 h (solid square),  8 h (solid diamond), 12 h (solid circle), 16 h (solid upright triangle).",
@@
 saturation at the same cumulative diel PUR of 1.0 x 10^6^ µmol photons
-m^-2^ d^-1^ (Figure \@ref(fig:PhotoperiodPurFitsPlots)A,B). Growth under
+m^-2^ d^-1^ (Figure \@ref(fig:PhotoperiodPurFitsPlots)A and B). Growth under
 lower O~2~ allowed MIT9313 to substantially increase its exploitation of
@@
 OverlayPlots_cap <- glue("**Normalized absorbance, emission and Photosynthetically Usable Radiation spectra for *Prochlorococcus marinus* MED4 (A,D,G); SS120 (B,E,H); MIT9313 (C,F,I) grown under three emission wavebands.**",
-                       "**(A,B,C)** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated PUR spectra (solid black line and shaded grey).",
-                       "**(D,E,F)** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded red).",
-                       "**(G,H,I)**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded blue).",
+                       "**(A-C)** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated PUR spectra (solid black line and shaded grey).",
+                       "**(D-F)** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded red).",
+                       "**(G-I)**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded blue).",
 

### 2024-03-14 Code/Manuscript_O2.Rmd
Fixed fig caption for overlay plot. Panel reference were wrong.

@@
 # This is S3_Fig.tiff 
-OverlayPlots_cap <- glue("**Normalized absorbance, emission and Photosynthetically Usable Radiation spectra for *Prochlorococcus marinus* MED4 (A,D,G); SS120 (B,E,H); MIT9313 (C,F,I) grown under three emission wavebands.**",
-                       "**(A-C)** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated PUR spectra (solid black line and shaded grey).",
-                       "**(D-F)** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded red).",
-                       "**(G-I)**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded blue).",
+OverlayPlots_cap <- glue("**Normalized absorbance, emission and Photosynthetically Usable Radiation spectra for *Prochlorococcus marinus* MED4 (A-C); SS120 (D-F); MIT9313 (G-I) grown under three emission wavebands.**",
+                       "**(A,D,G)** Growth light emission spectra from the White LED (normalized to 439 nm; dotted black line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line); and calculated PUR spectra (solid black line and shaded grey).",
+                       "**(B,E,H)** Growth light emission spectra at 660 nm (normalized to 647 nm; dotted red line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded red).",
+                       "**(C,F,I)**  Growth light emission spectra at 450 nm (normalized to 441 nm; dotted blue line); whole cell absorbance spectra (normalized to absorbance maxima between 400 nm and 460 nm; dashed purple line);  and calculated PUR spectra (solid black line and shaded blue).",
 

### 2024-03-14 Code/Manuscript_O2.Rmd
Added Mireille as receiving NBIF grant

@@
 Canada Foundation for Innovation (DAC) New Brunswick Foundation for
-Innovation (DAC) Rice Graduate Fellowship 2021 and 2022 (MS)
+Innovation (DAC and MS) Rice Graduate Fellowship 2021 and 2022 (MS)
 

### 2024-03-14 Code/Manuscript_O2.Rmd
Formatted affliations as per PLOS guidelines

@@
 institute:
-  - mta: 'Department of Biology, Mount Allison University, 63B York St., Sackville NB, Canada, E4L 1G7'
-  - ubc: 'Department of Biology, University of British Columbia'
-  - dfo: 'Fisheries and Oceans Canada, Ecosystems Management Branch, Dartmouth NS'
-  - sfx: 'Department of Chemistry, St. Frances Xavier University'
-  - algatech: 'Institute of Microbiology, Center Algatech, Laboratory of Photosynthesis, Novohradska 237, Trebon, CZ 37981, Czech Republic.'
-  - ug: 'Institute of Oceanography, University of Gdansk, 46 Piłsudskiego St, Gdynia, Poland'
+  - mta: 'Department of Biology, Mount Allison University, Sackville, New Brunswick, Canada, E4L 1G7'
+  - ubc: 'Department of Biology, University of British Columbia, Vancouver, British Columbia, Canada'
+  - dfo: 'Fisheries and Oceans Canada, Ecosystems Management Branch, Dartmouth, Nova Scotia, Canada'
+  - sfx: 'Department of Chemistry, St. Frances Xavier University, Antigonish, Nova Scotia, Canada'
+  - algatech: 'Institute of Microbiology, Center Algatech, Laboratory of Photosynthesis, Trebon, Czech Republic'
+  - ug: 'Institute of Oceanography, University of Gdansk, Gdynia, Poland'
 date: "`r format(Sys.Date())`"

### 2024-03-14 Code/Manuscript_O2.Rmd
Compressed .tiff figures for PLOS ONE

@@
   - name: Amanda M. Cockshutt
-    institute: [mta, sfx]
+    institute: [mtachem, sfx]
     main: false
@@
     institute: mta
-    affil: 1
     main: false
@@
     email: 'dcampbel@mta.ca'
-affiliation:
-  - num: 1
-    address: Departments of Biology and Chemistry and Biochemistry, Mount Allison University
 institute:
-  - mta: 'Department of Biology, Mount Allison University, Sackville, New Brunswick, Canada, E4L 1G7'
+  - mta: 'Department of Biology, Mount Allison University, Sackville, New Brunswick, Canada'
+  - mtachem: 'Department of Chemistry and Biochemistry, Mount Allison University, Sackville, New Brunswick, Canada'
   - ubc: 'Department of Biology, University of British Columbia, Vancouver, British Columbia, Canada'

### 2024-03-14 Code/Plots_PURFits.Rmd
regenerated plots using sentence structure in axis titles and legends
Compressed .tiff figures for PLOS ONE

@@
   mutate(PhotoperiodLabelTitle = "Photoperiod (h)",
-         OxygenLabel = "Oxygen Concentration (µM)",
+         OxygenLabel = "Oxygen concentration (µM)",
          Photoperiod = factor(Data_all_Photoperiod, levels = c(16, 12, 8, 4)),
@@
    geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +
- labs(y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
+ labs(y = "Chlorophyll specific growth rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
   scale_x_continuous(label=scientific_10) +
@@
         shape = "Photoperiod",
-        color = "Growth Waveband",
+        color = "Growth waveband",
 
@@
 
-ggsave(file = file.path(PlotsOutPLOS, "S4_Fig.tiff"), plot = PhotoperiodPurFitsPlots, device = NULL, scale = 1, height=40, width= 54, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOutPLOS, "S4_Fig.tiff"), plot = PhotoperiodPurFitsPlots, device = NULL, scale = 1, height=40, width= 54, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)
 
@@
 %>% unnest(Predict_660) %>%  filter(Strain == "MIT9313", O2_uM == 250, WL == 660), show.legend = F) +
- labs(y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
+ labs(y = "Chlorophyll specific growth rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
   scale_x_continuous(label=scientific_10) +
@@
         shape = "Photoperiod",
-        color = "Growth Waveband",
+        color = "Growth waveband",
       ) +
@@
 
- ggsave(file = file.path(PlotsOutPLOS, paste("Fig9.tiff",sep = "")), plot = BluevsRedPurFitsPlots, device = NULL, scale = 1, height=40, width= 54, units = c("cm"),dpi = 300, limitsize = TRUE)
+ ggsave(file = file.path(PlotsOutPLOS, paste("Fig9.tiff",sep = "")), plot = BluevsRedPurFitsPlots, device = NULL, scale = 1, height=40, width= 54, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)
 

### 2024-03-15 Code/Plots_Growth.Rmd
Generated compressed .tiff files

@@
 
-ggsave(file = file.path(PlotsOutPLOS, "Fig1.tiff"), plot = PurParPlot, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOutPLOS, "Fig1.tiff"), plot = PurParPlot, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)
 
@@
 
-ggsave(file = file.path(PlotsOutPLOS, "S2_Fig.tiff"), plot = deltaODLogGrowthPlot, device = NULL, scale = 1, height=20, width= 30, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOutPLOS, "S2_Fig.tiff"), plot = deltaODLogGrowthPlot, device = NULL, scale = 1, height=20, width= 30, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)
 
@@
 
-ggsave(file = file.path(PlotsOutPLOS, "Fig3.tiff"), plot = MED4PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOutPLOS, "Fig3.tiff"), plot = MED4PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)
 
@@
 
-ggsave(file = file.path(PlotsOutPLOS, "Fig5.tiff"), plot = SS120PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOutPLOS, "Fig5.tiff"), plot = SS120PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)
 
@@
 
-ggsave(file = file.path(PlotsOutPLOS, "Fig7.tiff"), plot = MIT9313PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOutPLOS, "Fig7.tiff"), plot = MIT9313PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)
 
@@
 
-ggsave(file = file.path(PlotsOutPLOS, "S3_Fig.tiff"), plot = OverlayPlots, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOutPLOS, "S3_Fig.tiff"), plot = OverlayPlots, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)
 

### 2024-03-15 Code/Plots_GAM.Rmd
changed how plots are generated and saved such that 'run all' is used instead of changing strain name in the chunk that generates and saves plots. Prone to errors.

--- 2024-03-09 Code/Plots_GAM.Rmd
@@
 
-# Plot red light GAM, must change GAMStrain and rerun chunk to generate plot of each strain
-``` {r GAM Plot Red WL}
-GamStrain = "MIT9313" # MIT9313 MED4 SS120
-GamColor = "Red" 
-WL_nm = 660 
-PlotWL <- "deltaOD"
-
-maxMu <- PicoGAM_Pred %>%
-  ungroup() %>%
-  filter(Wavelength %in% PlotWL) %>%
-  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
-maxMu <- maxMu$fit
-
-minMu <- PicoGAM_Pred %>%
-  ungroup() %>%
-  filter(Wavelength %in% PlotWL) %>%
-  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
-  #        fit == min(fit, na.rm = TRUE)) %>%
-  # distinct(fit)
-minMu <- minMu$fit
-
-PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
-  filter(Wavelength %in% PlotWL,
-         Strain %in% GamStrain,
-         WL %in% WL_nm) %>%
-  mutate(
-         # PhotoperiodLabel = "Photoperiod",
-
-         OxygenLabel = "Oxygen Concentration (uM)",
-         O2_level = case_when(O2_uM == 2.5 ~ "low",
-                              O2_uM == 25 ~ "intermediate",
-                              O2_uM == 250 ~ "high"),
-         Color_name = case_when(WL == "450" ~ 'Blue',
-                                WL == "530" ~ 'Green',
-                                WL == "660" ~ 'Red',
-                                WL == "WW" ~ 'White')) %>%
-  unite(WL_O2, Color_name, O2_level, sep = "_", remove = FALSE)
-
-WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
-
-ColourDF <- data.frame(
-  ColorName = c('Blue', 'Green', 'Red', 'White'),
-  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
-) %>%
-  filter(ColorName %in% GamColor) %>%
-  dplyr::select(WL_O2_Colors)
-
-ContourBreaks <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL
-  ) %>%
-  group_by(O2_uM) %>%
-  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
-         median50 = quantile(fit, 0.5, na.rm = TRUE),
-         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
-  ungroup() %>%
-  dplyr::select(O2_uM, upper10, median50, lower10) %>%
-  distinct() %>%
-  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
-  mutate(quantileValue = round(quantileValue, digits = 2))
-
-##############
-###plot
-#https://stackoverflow.com/questions/28775036/ggplot-line-graph-with-na-values
-#https://stackoverflow.com/questions/6906661/ggplot2-make-missing-value-in-geom-tile-not-blank
-#https://stackoverflow.com/questions/24822621/multiple-legends-in-a-plot-with-geom-tile
-#https://stackoverflow.com/questions/43395219/plotting-multiple-layers-with-geom-raster-or-geom-tile-or-geom-rect
-#https://stackoverflow.com/questions/59949635/ggplot-align-grid-lines-with-end-of-geom-tile
-#https://stackoverflow.com/questions/22945651/remove-space-between-plotted-data-and-the-axes
-#https://stackoverflow.com/questions/5293715/how-to-use-greek-symbols-in-ggplot2
-
-HyperChlPlotLow <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         #DM == "Chl",
-         Wavelength %in% PlotWL,
-         O2_uM == "2.5"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "2.5") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
-    #geom_text(x = 4, y = 200, label = "C", size = 5) +
-     xlab(NULL)+
-     # xlab("Photoperiod (h)") +
-      ylab(NULL)+
-    # ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")") +
-    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
-    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
-    #facet_grid(cols = vars(O2_uM)) +
-    # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
-    theme_classic() +
-    theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35)))# change to 25 and 30 for thesis
-          # axis.title.y = element_blank()))
-
-HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         #DM == "Chl",
-         Wavelength %in% PlotWL,
-         O2_uM == "25"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "25") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
-    #geom_text(x = 4, y = 200, label = "B", size = 5) +
-    xlab(NULL)+
-     # xlab("Photoperiod (h)") +
-      ylab(NULL)+
-    # ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")") +
-    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
-    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
-    #facet_grid(cols = vars(O2_uM)) +
-    # labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
-   theme_classic() +
-  theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=23)))# change to 25 and 30 for thesis
-          # axis.title.y = element_blank()))
-
-HyperChlPlotHigh <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         #DM == "Chl",
-         Wavelength %in% PlotWL,
-         O2_uM == "250"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "250") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
-    #geom_text(x = 4, y = 200, label = "A", size = 5) +
-    xlab(NULL)+
-     # xlab("Photoperiod (h)") +
-      ylab(NULL)+
-    # ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")") +
-    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
-    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
-    #facet_grid(cols = vars(O2_uM)) +
-    # labs(title = bquote("A.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +  #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
-    theme_classic() +
-   theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35)))# change to 25 and 30 for thesis
-          # axis.title.y = element_blank()))
-
-g_legend<-function(a.gplot){
-  tmp <- ggplot_gtable(ggplot_build(a.gplot))
-  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
-  legend <- tmp$grobs[[leg]]
-  legend
-}
-
-(g_dummy1 <- ggplot(subset(HyperChlPlotLow, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
-+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
-  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend1 <- g_legend(g_dummy1)
-(g_dummy2 <- ggplot(subset(HyperChlPlotInt, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
-+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
-  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend2 <- g_legend(g_dummy2)
-(g_dummy3 <- ggplot(subset(HyperChlPlotHigh, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
-+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
-  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend3 <- g_legend(g_dummy3)
-
-# comment rows that are not included in grid arrange 
-LayoutNiche <- rbind(
-                     c(3, 3, 3, 3, 6), # For 2.5 uM O2
-                     c(3, 3, 3, 3, 6), # For 2.5 uM O2
-                     c(2, 2, 2, 2, 5),   # For 25 uM O2
-                     c(2, 2, 2, 2, 5),   # For 25 uM O2
-                     c(1, 1, 1, 1, 4),   # For 250 uM O2
-                     c(1, 1, 1, 1, 4)    # For 250 uM O2
-                     )
-
-#LayoutNiche <- rbind(c(1, 1, 1, 2, 2, 2, 3, 3, 3, 4))
-
-p3_Red <- grid.arrange(
-                       ContourLowO2 +   labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
-                          theme(legend.position = 'none'), 
-                       ContourIntO2 + labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
-                         theme(legend.position = 'none'), 
-                       ContourHighO2 + labs(title = bquote("A.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
-                         theme(legend.position = 'none'), 
-                        legend1, 
-                        legend2, 
-                        legend3, 
-                       layout_matrix = LayoutNiche)
-
-                   # ,  left = textGrob("PAR (µmol photons"~ m^-2~ ~s^-1~ ")", rot = 90, vjust = 0.5, hjust = 0.45, gp=gpar(fontsize=30)), bottom = textGrob("Photoperiod (h)", gp=gpar(fontsize=20), vjust = 0.2, hjust = 0.6))
-
-#  for thesis
-  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Red,  height = 10, width = 6 )
-
-# for presentation
-  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Red,  height = 7.6, width = 6)
-
-```
-
 # Generate GAM for blue light conditions for all strains using chlorophyll proxy logistic growth rate. 
@@
 
-# Plot blue light GAM, must change GAMStrain and rerun chunk to generate plot for each strain
-``` {r GAM Plot Blue WL}
-GamStrain = "MIT9313" # MIT9313 MED4 SS120
-GamColor = "Blue"
-WL_nm = 450 
+# Plot red light GAM for MED4
+``` {r MED4GAM Plot Red WL}
+GamStrain = "MED4" 
+GamColor = "Red" 
+WL_nm = 660 
 PlotWL <- "deltaOD"
@@
   mutate(
-
-         # PhotoperiodLabel = "Photoperiod",
-
-         OxygenLabel = "Oxygen Concentration (uM)",
+         OxygenLabel = "Oxygen concentration (uM)",
          O2_level = case_when(O2_uM == 2.5 ~ "low",
@@
          Strain %in% GamStrain,
-         #DM == "Chl",
+         Wavelength %in% PlotWL,
+         O2_uM == "2.5"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "2.5") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
+  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
+    metR::geom_contour2(aes(label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+     xlab(NULL)+
+      ylab(NULL)+
+    theme_classic() +
+    theme(axis.text=element_text(size=15),
+          axis.title.x = element_text(size=20),
+           axis.title.y = element_text(size=35)))
+
+HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "25"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "25") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
+  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
+    metR::geom_contour2(aes(label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+    xlab(NULL)+
+      ylab(NULL)+
+   theme_classic() +
+  theme(axis.text=element_text(size=15),
+          axis.title.x = element_text(size=20),
+           axis.title.y = element_text(size=23)))
+
+HyperChlPlotHigh <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "250"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "250") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
+    metR::geom_contour2(aes(label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+    xlab(NULL)+
+      ylab(NULL)+
+    #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+    theme_classic() +
+   theme(axis.text=element_text(size=15),
+          axis.title.x = element_text(size=20),
+           axis.title.y = element_text(size=35)))
+
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  legend
+}
+
+(g_dummy1 <- ggplot(subset(HyperChlPlotLow, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
++ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
+  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
+legend1 <- g_legend(g_dummy1)
+(g_dummy2 <- ggplot(subset(HyperChlPlotInt, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
++ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
+  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
+legend2 <- g_legend(g_dummy2)
+(g_dummy3 <- ggplot(subset(HyperChlPlotHigh, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
++ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
+  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
+legend3 <- g_legend(g_dummy3)
+
+# comment rows that are not included in grid arrange 
+LayoutNiche <- rbind(
+                      # c(3, 3, 3, 3, 6), # For 2.5 uM O2     # remove comment if want 2.5 uM O2 plotted
+                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2    # remove comment if want 2.5 uM O2 plotted
+                     c(2, 2, 2, 2, 5),   # For 25 uM O2
+                     c(2, 2, 2, 2, 5),   # For 25 uM O2
+                     c(1, 1, 1, 1, 4),   # For 250 uM O2
+                     c(1, 1, 1, 1, 4)    # For 250 uM O2
+                     )
+
+#LayoutNiche <- rbind(c(1, 1, 1, 2, 2, 2, 3, 3, 3, 4))
+
+p3_Red <- grid.arrange(
+                       # ContourLowO2 +   labs(title = bquote("C.
+" ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + theme(legend.position = 'none'),   # remove comment if want 2.5 uM O2 plotted
+                       ContourIntO2 + labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
+                         theme(legend.position = 'none'), 
+                       ContourHighO2 + labs(title = bquote("A.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
+                         theme(legend.position = 'none'),
+                       # legend1,   # remove comment if want 2.5 uM O2 plotted
+                        legend2, 
+                        legend3, 
+                       layout_matrix = LayoutNiche)
+
+```
+
+# Plot blue light GAM for MED4
+``` {r MED4GAM Plot Blue WL}
+GamStrain = "MED4" 
+GamColor = "Blue"
+WL_nm = 450 
+PlotWL <- "deltaOD"
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+  #        fit == min(fit, na.rm = TRUE)) %>%
+  # distinct(fit)
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         OxygenLabel = "Oxygen concentration (uM)",
+         O2_level = case_when(O2_uM == 2.5 ~ "low",
+                              O2_uM == 25 ~ "intermediate",
+                              O2_uM == 250 ~ "high"),
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White')) %>%
+  unite(WL_O2, Color_name, O2_level, sep = "_", remove = FALSE)
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+##############
+###plot
+#https://stackoverflow.com/questions/28775036/ggplot-line-graph-with-na-values
+#https://stackoverflow.com/questions/6906661/ggplot2-make-missing-value-in-geom-tile-not-blank
+#https://stackoverflow.com/questions/24822621/multiple-legends-in-a-plot-with-geom-tile
+#https://stackoverflow.com/questions/43395219/plotting-multiple-layers-with-geom-raster-or-geom-tile-or-geom-rect
+#https://stackoverflow.com/questions/59949635/ggplot-align-grid-lines-with-end-of-geom-tile
+#https://stackoverflow.com/questions/22945651/remove-space-between-plotted-data-and-the-axes
+#https://stackoverflow.com/questions/5293715/how-to-use-greek-symbols-in-ggplot2
+
+HyperChlPlotLow <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
          Wavelength %in% PlotWL,
@@
     scale_y_continuous(limits = c(10, 200)) +
-    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
-    #geom_text(x = 4, y = 200, label = "C", size = 5) +
-    xlab(NULL)+
-     # xlab("Photoperiod (h)") +
+    xlab(NULL)+
       ylab(NULL)+
-    # ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")") +
-    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
-    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
-    #facet_grid(cols = vars(O2_uM)) +
-    # labs(title = bquote("F.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
    theme_classic() +
@@
          Strain %in% GamStrain,
-         #DM == "Chl",
          Wavelength %in% PlotWL,
@@
     scale_y_continuous(limits = c(10, 200)) +
-    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
-    #geom_text(x = 4, y = 200, label = "B", size = 5) +
-    xlab(NULL)+
-     # xlab("Photoperiod (h)") +
+    xlab(NULL)+
       ylab(NULL)+ 
-    # ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")") +
-    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
-    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
-    #facet_grid(cols = vars(O2_uM)) +
-    # labs(title = bquote("E.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
   theme_classic() +
@@
     scale_y_continuous(limits = c(10, 200)) +
-    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
-    #geom_text(x = 4, y = 200, label = "A", size = 5) +
-    xlab(NULL)+
-     # xlab("Photoperiod (h)") +
+    xlab(NULL)+
+      ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+theme_classic() +
+   theme(axis.text=element_text(size=15),
+          axis.title.x = element_text(size=20),
+           axis.title.y = element_text(size=35)))
+
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  legend
+}
+
+(g_dummy1 <- ggplot(subset(HyperChlPlotLow, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
+ + scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"),
+ limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
+legend1 <- g_legend(g_dummy1)
+(g_dummy2 <- ggplot(subset(HyperChlPlotInt, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
+ + scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"),
+  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
+legend2 <- g_legend(g_dummy2)
+(g_dummy3 <- ggplot(subset(HyperChlPlotHigh, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
++ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"),
+  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
+legend3 <- g_legend(g_dummy3)
+
+# comment rows that are not included in grid arrange 
+LayoutNiche <- rbind(
+                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2   # remove comment if want 2.5 uM O2
+                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2   # remove comment if want 2.5 uM O2
+                     c(2, 2, 2, 2, 5),   # For 25 uM O2
+                     c(2, 2, 2, 2, 5),   # For 25 uM O2
+                     c(1, 1, 1, 1, 4),   # For 250 uM O2
+                     c(1, 1, 1, 1, 4)    # For 250 uM O2
+                     )
+
+#LayoutNiche <- rbind(c(1, 1, 1, 2, 2, 2, 3, 3, 3, 4))
+
+p3_Blue <- grid.arrange(
+                         # ContourLowO2 +   labs(title = bquote("F.
+" ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()),
+                        ContourIntO2 +  labs(title = bquote("D.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
+                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
+                        ContourHighO2 + labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
+                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()),
+                        # legend1,    # remove comment if want 2.5 uM O2
+                        legend2, 
+                        legend3, 
+                        layout_matrix = LayoutNiche)
+
+```
+
+```{r combine red and blue light MED4GAM plots}
+
+#combine red and blue GAM plots
+CombinedGAM <- plot_grid(p3_Red, p3_Blue, nrow = 1, align = "v")
+
+# common x-axis title
+x.grob <- textGrob("Photoperiod (h)", 
+                   gp = gpar(fontsize = 20))
+# common y-axis title
+y.grob <- textGrob("PAR (µmol photons"~ m^-2~ ~s^-1~ ")", 
+                   gp = gpar(fontface="bold", fontsize = 20), rot = 90)
+
+# add titles to plot
+LabelledCombinedGam <- grid.arrange(arrangeGrob(CombinedGAM, left = y.grob, bottom = x.grob))
+
+```
+
+```{r save MED4GAM plots}
+# MED4GAM,png for manuscript
+ ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "GAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = LabelledCombinedGam,  height = 10, width = 10)
+
+# MED4GAM is Fig4.tiff for PLOSONE submission
+ ggsave(file = file.path(PlotsOutPLOS, "Fig4.tiff", fsep = .Platform$file.sep), plot = LabelledCombinedGam, device = NULL, scale = 1,  height = 10, width = 10, compression = "lzw")
+
+```
+
+# Plot red light GAM for SS120
+``` {r SS120GAM Plot Red WL}
+GamStrain = "SS120" 
+GamColor = "Red" 
+WL_nm = 660 
+PlotWL <- "deltaOD"
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+  #        fit == min(fit, na.rm = TRUE)) %>%
+  # distinct(fit)
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         OxygenLabel = "Oxygen concentration (uM)",
+         O2_level = case_when(O2_uM == 2.5 ~ "low",
+                              O2_uM == 25 ~ "intermediate",
+                              O2_uM == 250 ~ "high"),
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White')) %>%
+  unite(WL_O2, Color_name, O2_level, sep = "_", remove = FALSE)
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+##############
+###plot
+#https://stackoverflow.com/questions/28775036/ggplot-line-graph-with-na-values
+#https://stackoverflow.com/questions/6906661/ggplot2-make-missing-value-in-geom-tile-not-blank
+#https://stackoverflow.com/questions/24822621/multiple-legends-in-a-plot-with-geom-tile
+#https://stackoverflow.com/questions/43395219/plotting-multiple-layers-with-geom-raster-or-geom-tile-or-geom-rect
+#https://stackoverflow.com/questions/59949635/ggplot-align-grid-lines-with-end-of-geom-tile
+#https://stackoverflow.com/questions/22945651/remove-space-between-plotted-data-and-the-axes
+#https://stackoverflow.com/questions/5293715/how-to-use-greek-symbols-in-ggplot2
+
+HyperChlPlotLow <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "2.5"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "2.5") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
+  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
+    metR::geom_contour2(aes(label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+     xlab(NULL)+
+    theme_classic() +
+    theme(axis.text=element_text(size=15),
+          axis.title.x = element_text(size=20),
+           axis.title.y = element_text(size=35)))
+
+HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "25"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "25") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
+  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
+    metR::geom_contour2(aes(label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+    xlab(NULL)+
       ylab(NULL)+
-    # ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")") +
-    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
-    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
-    #facet_grid(cols = vars(O2_uM)) +
-    # labs(title = bquote("D.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +  #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+   theme_classic() +
+  theme(axis.text=element_text(size=15),
+          axis.title.x = element_text(size=20),
+           axis.title.y = element_text(size=23)))
+
+HyperChlPlotHigh <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "250"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "250") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
+    metR::geom_contour2(aes(label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+    xlab(NULL)+
+      ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+    theme_classic() +
+   theme(axis.text=element_text(size=15),
+          axis.title.x = element_text(size=20),
+           axis.title.y = element_text(size=35)))
+
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  legend
+}
+
+(g_dummy1 <- ggplot(subset(HyperChlPlotLow, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
++ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
+  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
+legend1 <- g_legend(g_dummy1)
+(g_dummy2 <- ggplot(subset(HyperChlPlotInt, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
++ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
+  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
+legend2 <- g_legend(g_dummy2)
+(g_dummy3 <- ggplot(subset(HyperChlPlotHigh, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
++ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
+  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
+legend3 <- g_legend(g_dummy3)
+
+# comment rows that are not included in grid arrange 
+LayoutNiche <- rbind(
+                      # c(3, 3, 3, 3, 6), # For 2.5 uM O2     # remove comment if want 2.5 uM O2
+                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2    # remove comment if want 2.5 uM O2
+                     c(2, 2, 2, 2, 5),   # For 25 uM O2
+                     c(2, 2, 2, 2, 5),   # For 25 uM O2
+                     c(1, 1, 1, 1, 4),   # For 250 uM O2
+                     c(1, 1, 1, 1, 4)    # For 250 uM O2
+                     )
+
+#LayoutNiche <- rbind(c(1, 1, 1, 2, 2, 2, 3, 3, 3, 4))
+
+p3_Red <- grid.arrange(
+                       # ContourLowO2 +   labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + theme(legend.position = 'none'),   # remove comment for MIT9313
+                       ContourIntO2 + labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
+                         theme(legend.position = 'none'), 
+                       ContourHighO2 + labs(title = bquote("A.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
+                         theme(legend.position = 'none'),
+                       # legend1,   # remove comment if want 2.5 uM O2
+                        legend2, 
+                        legend3, 
+                       layout_matrix = LayoutNiche)
+
+```
+
+# Plot blue light SS120GAM
+``` {r GAM Plot Blue WL}
+GamStrain = "SS120"
+GamColor = "Blue"
+WL_nm = 450 
+PlotWL <- "deltaOD"
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+  #        fit == min(fit, na.rm = TRUE)) %>%
+  # distinct(fit)
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         OxygenLabel = "Oxygen concentration (uM)",
+         O2_level = case_when(O2_uM == 2.5 ~ "low",
+                              O2_uM == 25 ~ "intermediate",
+                              O2_uM == 250 ~ "high"),
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White')) %>%
+  unite(WL_O2, Color_name, O2_level, sep = "_", remove = FALSE)
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+##############
+###plot
+#https://stackoverflow.com/questions/28775036/ggplot-line-graph-with-na-values
+#https://stackoverflow.com/questions/6906661/ggplot2-make-missing-value-in-geom-tile-not-blank
+#https://stackoverflow.com/questions/24822621/multiple-legends-in-a-plot-with-geom-tile
+#https://stackoverflow.com/questions/43395219/plotting-multiple-layers-with-geom-raster-or-geom-tile-or-geom-rect
+#https://stackoverflow.com/questions/59949635/ggplot-align-grid-lines-with-end-of-geom-tile
+#https://stackoverflow.com/questions/22945651/remove-space-between-plotted-data-and-the-axes
+#https://stackoverflow.com/questions/5293715/how-to-use-greek-symbols-in-ggplot2
+
+HyperChlPlotLow <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "2.5"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "2.5") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
+    metR::geom_contour2(aes(label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+    xlab(NULL)+
+      ylab(NULL)+
+   theme_classic() +
+   theme(axis.text=element_text(size=15),
+          axis.title.x = element_text(size=20),
+           axis.title.y = element_text(size=35)))
+
+HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "25"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "25") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
+    metR::geom_contour2(aes(label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+    xlab(NULL)+
+      ylab(NULL)+
+  theme_classic() +
+   theme(axis.text=element_text(size=15),
+          axis.title.x = element_text(size=20),
+           axis.title.y = element_text(size=35)))
+
+HyperChlPlotHigh <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         #DM == "Chl",
+         Wavelength %in% PlotWL,
+         O2_uM == "250"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "250") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
+    metR::geom_contour2(aes(label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+    xlab(NULL)+
+      ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+theme_classic() +
+   theme(axis.text=element_text(size=15),
+          axis.title.x = element_text(size=20),
+           axis.title.y = element_text(size=35)))
+
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  legend
+}
+
+(g_dummy1 <- ggplot(subset(HyperChlPlotLow, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
+ + scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"),
+ limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
+legend1 <- g_legend(g_dummy1)
+(g_dummy2 <- ggplot(subset(HyperChlPlotInt, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
+ + scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"),
+  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
+legend2 <- g_legend(g_dummy2)
+(g_dummy3 <- ggplot(subset(HyperChlPlotHigh, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
++ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"),
+  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
+legend3 <- g_legend(g_dummy3)
+
+# comment rows that are not included in grid arrange 
+LayoutNiche <- rbind(
+                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2   # remove comment if want 2.5 uM O2
+                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2   # remove comment if want 2.5 uM O2
+                     c(2, 2, 2, 2, 5),   # For 25 uM O2
+                     c(2, 2, 2, 2, 5),   # For 25 uM O2
+                     c(1, 1, 1, 1, 4),   # For 250 uM O2
+                     c(1, 1, 1, 1, 4)    # For 250 uM O2
+                     )
+
+#LayoutNiche <- rbind(c(1, 1, 1, 2, 2, 2, 3, 3, 3, 4))
+
+p3_Blue <- grid.arrange(
+                         # ContourLowO2 + labs(title = bquote("F.
+" ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()),  # remove comment if want 2.5 uM O2
+                        ContourIntO2 +  labs(title = bquote("D.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
+                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
+                        ContourHighO2 + labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
+                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()),
+                        # legend1,    # remove comment if want 2.5 uM O2
+                        legend2, 
+                        legend3, 
+                        layout_matrix = LayoutNiche)
+
+```
+
+```{r combine red and blue light SS120GAM plots}
+
+#combine red and blue GAM plots
+CombinedGAM <- plot_grid(p3_Red, p3_Blue, nrow = 1, align = "v")
+
+# common x-axis title
+x.grob <- textGrob("Photoperiod (h)", 
+                   gp = gpar(fontsize = 20))
+# common y-axis title
+y.grob <- textGrob("PAR (µmol photons"~ m^-2~ ~s^-1~ ")", 
+                   gp = gpar(fontface="bold", fontsize = 20), rot = 90)
+
+# add titles to plot
+LabelledCombinedGam <- grid.arrange(arrangeGrob(CombinedGAM, left = y.grob, bottom = x.grob))
+
+```
+
+```{r save SS120GAM plots}
+
+# SS120GAM.png for manuscript
+ ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "GAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = LabelledCombinedGam,  height = 10, width = 10)
+
+# SS120GAM is Fig6.tiff for PLOSONE submission
+ ggsave(file = file.path(PlotsOutPLOS, "Fig6.tiff", fsep = .Platform$file.sep), plot = LabelledCombinedGam, device = NULL, scale = 1,  height = 10, width = 10, compression = "lzw")
+
+```
+
+# Plot red light MIT9313 GAM
+``` {r MIT9313GAM Plot Red WL}
+GamStrain = "MIT9313"
+GamColor = "Red" 
+WL_nm = 660 
+PlotWL <- "deltaOD"
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+  #        fit == min(fit, na.rm = TRUE)) %>%
+  # distinct(fit)
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         OxygenLabel = "Oxygen concentration (uM)",
+         O2_level = case_when(O2_uM == 2.5 ~ "low",
+                              O2_uM == 25 ~ "intermediate",
+                              O2_uM == 250 ~ "high"),
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White')) %>%
+  unite(WL_O2, Color_name, O2_level, sep = "_", remove = FALSE)
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+##############
+###plot
+#https://stackoverflow.com/questions/28775036/ggplot-line-graph-with-na-values
+#https://stackoverflow.com/questions/6906661/ggplot2-make-missing-value-in-geom-tile-not-blank
+#https://stackoverflow.com/questions/24822621/multiple-legends-in-a-plot-with-geom-tile
+#https://stackoverflow.com/questions/43395219/plotting-multiple-layers-with-geom-raster-or-geom-tile-or-geom-rect
+#https://stackoverflow.com/questions/59949635/ggplot-align-grid-lines-with-end-of-geom-tile
+#https://stackoverflow.com/questions/22945651/remove-space-between-plotted-data-and-the-axes
+#https://stackoverflow.com/questions/5293715/how-to-use-greek-symbols-in-ggplot2
+
+HyperChlPlotLow <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "2.5"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "2.5") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
+  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
+    metR::geom_contour2(aes(label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+     xlab(NULL)+
+      ylab(NULL)+
+    theme_classic() +
+    theme(axis.text=element_text(size=15),
+          axis.title.x = element_text(size=20),
+           axis.title.y = element_text(size=35)))
+
+HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "25"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "25") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
+  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
+    metR::geom_contour2(aes(label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+    xlab(NULL)+
+      ylab(NULL)+
+   theme_classic() +
+  theme(axis.text=element_text(size=15),
+          axis.title.x = element_text(size=20),
+           axis.title.y = element_text(size=23)))
+
+HyperChlPlotHigh <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "250"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "250") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
+    metR::geom_contour2(aes(label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+    xlab(NULL)+
+      ylab(NULL)+
+    #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+    theme_classic() +
+   theme(axis.text=element_text(size=15),
+          axis.title.x = element_text(size=20),
+           axis.title.y = element_text(size=35)))
+
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  legend
+}
+
+(g_dummy1 <- ggplot(subset(HyperChlPlotLow, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
++ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
+  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
+legend1 <- g_legend(g_dummy1)
+(g_dummy2 <- ggplot(subset(HyperChlPlotInt, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
++ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
+  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
+legend2 <- g_legend(g_dummy2)
+(g_dummy3 <- ggplot(subset(HyperChlPlotHigh, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
++ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
+  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
+legend3 <- g_legend(g_dummy3)
+
+# comment rows that are not included in grid arrange 
+LayoutNiche <- rbind(
+                     c(3, 3, 3, 3, 6), # For 2.5 uM O2    
+                     c(3, 3, 3, 3, 6), # For 2.5 uM O2  
+                     c(2, 2, 2, 2, 5),   # For 25 uM O2
+                     c(2, 2, 2, 2, 5),   # For 25 uM O2
+                     c(1, 1, 1, 1, 4),   # For 250 uM O2
+                     c(1, 1, 1, 1, 4)    # For 250 uM O2
+                     )
+
+#LayoutNiche <- rbind(c(1, 1, 1, 2, 2, 2, 3, 3, 3, 4))
+
+p3_Red <- grid.arrange(
+                       ContourLowO2 + labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
+                         theme(legend.position = 'none'),  
+                       ContourIntO2 + labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
+                         theme(legend.position = 'none'), 
+                       ContourHighO2 + labs(title = bquote("A.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
+                         theme(legend.position = 'none'), 
+                        legend1, 
+                        legend2, 
+                        legend3, 
+                       layout_matrix = LayoutNiche)
+
+```
+
+# Plot blue light MIT9313 GAM
+``` {r MIT9313GAM Plot Blue WL}
+GamStrain = "MIT9313"
+GamColor = "Blue"
+WL_nm = 450 
+PlotWL <- "deltaOD"
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+  #        fit == min(fit, na.rm = TRUE)) %>%
+  # distinct(fit)
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         OxygenLabel = "Oxygen concentration (uM)",
+         O2_level = case_when(O2_uM == 2.5 ~ "low",
+                              O2_uM == 25 ~ "intermediate",
+                              O2_uM == 250 ~ "high"),
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White')) %>%
+  unite(WL_O2, Color_name, O2_level, sep = "_", remove = FALSE)
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+##############
+###plot
+#https://stackoverflow.com/questions/28775036/ggplot-line-graph-with-na-values
+#https://stackoverflow.com/questions/6906661/ggplot2-make-missing-value-in-geom-tile-not-blank
+#https://stackoverflow.com/questions/24822621/multiple-legends-in-a-plot-with-geom-tile
+#https://stackoverflow.com/questions/43395219/plotting-multiple-layers-with-geom-raster-or-geom-tile-or-geom-rect
+#https://stackoverflow.com/questions/59949635/ggplot-align-grid-lines-with-end-of-geom-tile
+#https://stackoverflow.com/questions/22945651/remove-space-between-plotted-data-and-the-axes
+#https://stackoverflow.com/questions/5293715/how-to-use-greek-symbols-in-ggplot2
+
+HyperChlPlotLow <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "2.5"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "2.5") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
+    metR::geom_contour2(aes(label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+    xlab(NULL)+
+      ylab(NULL)+
+   theme_classic() +
+   theme(axis.text=element_text(size=15),
+          axis.title.x = element_text(size=20),
+           axis.title.y = element_text(size=35)))
+
+HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "25"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "25") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
+    metR::geom_contour2(aes(label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+    xlab(NULL)+
+      ylab(NULL)+
+  theme_classic() +
+   theme(axis.text=element_text(size=15),
+          axis.title.x = element_text(size=20),
+           axis.title.y = element_text(size=35)))
+
+HyperChlPlotHigh <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "250"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "250") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
+    metR::geom_contour2(aes(label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+    xlab(NULL)+
+      ylab(NULL)+
+    #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
 theme_classic() +
@@
                         layout_matrix = LayoutNiche)  
-
-# , left = textGrob("PAR (µmol photons"~ m^-2~ ~s^-1~ ")", rot = 90, vjust = 0.5, hjust = 0.45, gp=gpar(fontsize=30)), bottom = textGrob("Photoperiod (h)", gp=gpar(fontsize=20), vjust = 0.2, hjust = 0.6))
-
-#  for thesis
-  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Blue,  height = 10, width = 6)
-
-# for presentation
-  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Blue,  height = 7.6, width = 6)
-
-```
-
-```{r combine red and blue light GAM plots}
+```
+
+```{r combine red and blue light MIT9313GAM plots}
 
@@
                    gp = gpar(fontsize = 20))
+
 # common y-axis title
@@
 
-#add titles to plot
+# add titles to plot
 LabelledCombinedGam <- grid.arrange(arrangeGrob(CombinedGAM, left = y.grob, bottom = x.grob))
@@
 
-```{r save png}
- ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(GamStrain, "GAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = LabelledCombinedGam,  height = 10, width = 10)
-```
+```{r save MIT9313GAM plots}
+
+# MIT9313GAM.png for manuscript
+ ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "GAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = LabelledCombinedGam,  height = 10, width = 10)
+
+# MIT9313 GAM is Fig8.tiff for PLOSONE submission
+ ggsave(file = file.path(PlotsOutPLOS, "Fig8.tiff", fsep = .Platform$file.sep), plot = LabelledCombinedGam, device = NULL, scale = 1,  height = 10, width = 10,  compression = "lzw")
+
+```

### 2024-03-15 Code/Manuscript_O2.Rmd
Minor edits

@@
 50 µmol photons m^-2^ s^-1^ and photoperiods between 8 and 12 h,
-indicated by the contour line labeled 0.19 d^-1^ (representing the
+indicated by the contour line labeled 0.18 d^-1^ (representing the
 90^th^ percentile of achieved growth rate). Under 250 µM O~2~ SS120 is
@@
 PAR levels, achieving faster growth rates at a higher PAR of \~100 µmol
-photons m^-2^ s^-1^, indicated by the contour line labeled 0.4 d^-1^
+photons m^-2^ s^-1^, indicated by the contour line labeled 0.41 d^-1^
 (representing the 90^th^ percentile of achieved growth rate), out pacing
@@
 photoperiod, achieving fastest growth under long photoperiods and peak
-PAR between 50 \~100 µmol photons m^-2^ s^-1^. Thus, the designation of
+PAR between 30 \~100 µmol photons m^-2^ s^-1^. Thus, the designation of
 SS120 as a LL strain is dependent upon the [O~2~]. SS120 did not,
@@
 fastest growth rates between blue peak PAR of 30 µmol photons m^-2^
-s^-1^ and 50 µmol photons m^-2^ s^-1^ and photoperiods longer than 8 h,
+s^-1^ and 50 µmol photons m^-2^ s^-1^ and photoperiods longer than 12 h,
 indicated by the contour line labeled 0.52 d^-1^ representing the 90^th^
@@
 exploiting higher peak PAR and longer photoperiods. Figure
-\@ref(fig:MIT9313GAM)E shows that MIT9313can exploit all blue PAR levels
+\@ref(fig:MIT9313GAM)E shows that MIT9313 can exploit all blue PAR levels
 and most photoperiods with 90^th^ percentile of fastest growth rate
@@
 \@ref(fig:MIT9313GAM)F shows that MIT9313 maintains growth even under
-2.5 µM O~2~, under photoperiods between 4 and 8 h and peak blue PAR
+2.5 µM O~2~, under photoperiods between 8 and 12 h and peak blue PAR
 between 50 to 100 µmol photons m^-2^ s^-1^ PAR. Thus the designation of

### 2024-03-15 Code/Manuscript_O2.Rmd
Minor edits

@@
 
-To Be Entered through PLoSONe system and deleted here Czech Academy of
-Science (OP) visiting fellowship supporting DAC work at AlgaTech Canada
-Research Chair in Phytoplankton Ecophysiology (DAC) Natural Sciences and
-Engineering Research Council of Canada, 'Latitude and Light' (DAC)
-Canada Foundation for Innovation (DAC) New Brunswick Foundation for
-Innovation (DAC and MS) Rice Graduate Fellowship 2021 and 2022 (MS)
-
-XXX PLOS requires grant numbers XXX
+To Be Entered through PLoSONe system and deleted here 
+Czech Academy of Science (OP) visiting fellowship supporting DAC work at AlgaTech 
+Canada Research Chair in Phytoplankton Ecophysiology (DAC), Grant number CRC-2017-00075 
+Natural Sciences and Engineering Research Council of Canada, 'Latitude and Light' (DAC)
+Canada Foundation for Innovation (DAC) 
+New Brunswick Foundation for Innovation (DAC and MS) 
+Rice Graduate Fellowship 2021 and 2022 (MS)
+
+The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.
 

### 2024-03-15 Code/Manuscript_O2.Rmd
Added to Data availabilty section

@@
 values files and are available at
-<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData>.
+<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData/MultiCultiData1.zip>.
+<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData/MultiCultiData2.zip>.
+<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData/MultiCultiData3.zip>.
+All data obtained from the Jaz spectrometer were saved as text files and are available at
+<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData/JazEmData.zip>.
+All data obtained from the Olis 14 UV/VIS Clarity Spectrophotometer were saved as ascii files and are available at
+<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData/OlisData.zip>.
+Meta Data for the Multicultivator runs were imported and saved as a .Rds and available at
+<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData/CultureCatalog.Rds>.
+
 Annotated code for data import, transformations and analyses are

### 2024-03-18 Code/Manuscript_O2.Rmd
Changed a few "Photosynthetic" to "Photosynthetically" when used for PUR or PAR.

@@
 
-To estimate the Photosynthetic Usable Radiation (PUR), a proxy of
+To estimate the Photosynthetically Usable Radiation (PUR), a proxy of
 incident photons that can be absorbed by the cells, for each *P. marinus* ecotype, 
-the imposed Photosynthetic Active Radiation (PAR) was
+the imposed Photosynthetically Active Radiation (PAR) was
 first determined using the reported delivery of sinusoidal diel PAR
@@
 # This is Fig9.tiff
- BluevsRedPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
+ BluevsRedPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetically Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
                     "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",
@@
 # This is S4_Fig.tiff 
-PhotoperiodPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetic Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
+PhotoperiodPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetically Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
                     "Rows separate data from levels of imposed dissolved O~2~ concentrations as 250 µM, 25 µM and 2.5 µM.",

### 2024-03-18 Code/Import_MCData.Rmd
Minor edits

@@
 rowwise. This requires careful 'arrange' of the rows. It imports a
-metadata Catalog and merges the metadata with the imported data based
+metadata catalog (Data/RawData/"CultureCatalog.Rds") and merges the metadata with the imported data based
 upon shared values for the variables 'MC', 'Tube', and 'Filename' which
@@
 
-# Multiculti data files are too large to upload in a single .zip so uploaded 3 .zipped folders. Uncomment the 'DataIn' line with the folder name containing the intended files for import.   
+# Multicultivator data files are too large to upload in a single .zip therefore 3 .zipped folders are uploaded.
+Uncomment the 'DataIn' line with the folder name containing the intended files for import.
  # DataIn <- file.path("..", "Data", "RawData", "MultiCultiData1.zip")

### 2024-03-18 Code/Process_MCData.Rmd
Edits to 'Intro' sections

@@
 Implement logistic and other growth curve fits to MultiCulti growth trajectories.
+Individually tidied Muticultivator runs are imported from "Data/ImportedData/ImportedMCData" folder, processed and saved as .Rds in the "Data/ProcessedData/ProcessedMCData" folder.
+This script calculates deltaOD and filters data after x hours of decline growth from maximum in OD720 or deltaOD prior to implementing growth curve fits.
 
@@
 Run only first time in session
-
 ```{r load libraries}

### 2024-03-18 Code/Import_OlisData.Rmd
New file path to Culture Catalog
minor edit

@@
 
-Import_OlisData.Rmd imports OLIS CLARiTY spectrophotometer files from Data/RawData/OlisData.zip folder and stored in Data/ImportedData/ImportedOlisData folder as: 
-Baltic_Photoperiod_Imported_OlisData.Rds
+Import_OlisData.Rmd imports OLIS 14 UV/VIS Clarity spectrophotometer files from Data/RawData/OlisData.zip folder and stored in Data/ImportedData/ImportedOlisData folder as: 
+PICO_Imported_OlisData.Rds
 
@@
 ```{r read locally stored metadata from rds}
-CultureCatalog <- readRDS(file = file.path("..", "Data","CultureCatalog.Rds"))
+CultureCatalog <- readRDS(file = file.path("..", "Data","RawData" ,"CultureCatalog.Rds"))
 

### 2024-03-20 Code/Manuscript_O2.Rmd
SOme Saito edits

@@
 
-We used the OceansMap Protein Portal (OPP;
-<https://proteinportal.whoi.edu/>) [@saitoDevelopmentOceanProtein2021]
+We used the Ocean Protein Portal (OPP;
+<https://www.oceanproteinportal.org/>) [@saitoDevelopmentOceanProtein2021]
 to analyze the distribution of proteins from clades of *P. marinus* in
@@
 
-## MetaProteomics {.unnumbered}
-
-The OceansMap Protein Portal is an open access online data repository
-(Woods Hole Oceanographic Institute, WHOI) of mass spectroscopy data on
-marine microbial peptides, sampled from various depths and locations
+## Metaproteomics {.unnumbered}
+
+The Ocean Protein Portal is an open access online data repository
+(Woods Hole Oceanographic Institution, WHOI) of mass spectroscopy data on
+marine microbial proteins, sampled from various depths and locations
 worldwide [@saitoDevelopmentOceanProtein2021]. We screened a subset of
@@
 analyses were collected from 7 locations in the tropical North Pacific
-ocean along 150 W from 18 N of the equator between October 1, 2011 and
-October 25, 2011 during the voyage of the R/V Kilo Moana MetZyme cruise
+Ocean along 150 W from 18 N of the equator between October 1, 2011 and
+October 25, 2011 during the voyage of the R/V Kilo Moana MetZyme expedition
 [@rollingdecktorepositoryCruiseKM1128RV2015]; original datasets in the
 Biological and Chemical Oceanography Data Management Office (BCO-DMO)
-repository [@saitoPeptidesTheirSpectral2018]. Oxygen concentration
+repository (https://www.bco-dmo.org/project/2236) [@saitoPeptidesTheirSpectral2018]. Oxygen concentration
 levels at the location of sampling were recorded. The methodology for
@@
 
-## MetaProteomics bioinformatic analyses {.unnumbered}
+## Metaproteomics bioinformatic analyses {.unnumbered}
 
 Metaproteomic datasets were obtained from the KM1128 entry in the
-BCO-DMO database [@saitoPeptidesTheirSpectral2018] accessed via the OPP
-in June 2019. Datasets contained: i) Peptide sequences and sample
+BCO-DMO repository [@saitoPeptidesTheirSpectral2018] accessed via the OPP
+in June 2019 at https://www.bco-dmo.org/dataset-deployment/730728.
+This dataset included biomass in the 0.2 to 3.0 micron size fractionated filter size as described in Saito et al., 2014 where *Prochlorococcus* is found.
+Datasets contained: i) Protein sequences and sample
 identification (ID) number; ii) Sample ID number, station, depth in
@@
 [O~2~].\
-The depth and [O~2~] were joined to peptide sequence and BLASTP
+The depth and [O~2~] (also from BCO-DMO at https://www.bco-dmo.org/dataset/646115/) were joined to protein sequence and BLASTP
 annotations by ID number, depth and station using *tidyverse* package
@@
 The resulting merged dataset was filtered for those *Prochlorococcus*
-peptides, detected from 0 to 300 m below the surface, annotated as a
+protein, detected from 0 to 300 m below the surface, annotated as a
 subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb);
@@
 When assessing the presence of a particular protein complex at a
-sampling location, all peptides belonging to all subunits of the complex
+sampling location, all proteins belonging to all subunits of the complex
 were included to give the greatest number of data points. As this data
-was acquired on a discovery mission rather than through targeted peptide
-approaches, it is difficult to discern accuracies of strain assignment
+was acquired by survey proteomics (data dependent acquisition) rather than through targeted peptide
+approaches (e.g. parallel reaction monitoring), it is difficult to discern accuracies of strain assignment
 annotations, particularly as the proteins of interest in this study are
-highly conserved across strains. We are, however, confident in clade
+highly conserved across strains [@saitoNeedlesBlueSea2015]. We are, however, confident in clade
 classifications for each protein examined. The data is also limited

### 2024-03-20 Code/Manuscript_O2.Rmd
Finished Saito edits

@@
   - name: Aurora Mattison
-    institute: [mta, ubc]
+    institute: [mtachem, ubc]
   - name: Laurel Genge
@@
   - dfo: 'Fisheries and Oceans Canada, Ecosystems Management Branch, Dartmouth, Nova Scotia, Canada'
+  - ug: 'Institute of Oceanography, University of Gdansk, Gdynia, Poland'
+  - algatech: 'Institute of Microbiology, Center Algatech, Laboratory of Photosynthesis, Trebon, Czech Republic'
   - sfx: 'Department of Chemistry, St. Frances Xavier University, Antigonish, Nova Scotia, Canada'
-  - algatech: 'Institute of Microbiology, Center Algatech, Laboratory of Photosynthesis, Trebon, Czech Republic'
-  - ug: 'Institute of Oceanography, University of Gdansk, Gdynia, Poland'
 date: "`r format(Sys.Date())`"
@@
 in June 2019 at https://www.bco-dmo.org/dataset-deployment/730728.
-This dataset included biomass in the 0.2 to 3.0 micron size fractionated filter size as described in Saito et al., 2014 where *Prochlorococcus* is found.
+This dataset included biomass in the 0.2 to 3.0 micron size fractionated filter size as described in Saito *et al*.
+[@saitoMultipleNutrientStresses2014] where *Prochlorococcus* is found.
 Datasets contained: i) Protein sequences and sample
@@
 When assessing the presence of a particular protein complex at a
-sampling location, all proteins belonging to all subunits of the complex
-were included to give the greatest number of data points. As this data
+sampling location, the spectral counts were summed between proteins within the protein subunit to give the greatest number of data points. As this data
 was acquired by survey proteomics (data dependent acquisition) rather than through targeted peptide
-approaches (e.g. parallel reaction monitoring), it is difficult to discern accuracies of strain assignment
-annotations, particularly as the proteins of interest in this study are
+approaches (e.g. parallel reaction monitoring), it is difficult to discern accuracies of strain assignment annotations, particularly as the proteins of interest in this study are
 highly conserved across strains [@saitoNeedlesBlueSea2015]. We are, however, confident in clade
@@
 known spectrum for that peptide in the SEQUEST database, hence some
-peptides of interest may not be identifiable. Furthermore, a peptide
-must be detected above a certain threshold abundance in order to be
-considered an accurate ‘hit’.
+peptides of interest may not be identifiable.
+This MetZyme dataset used a deep paired metagenomic database (https://www.ebi.ac.uk/pride/archive/projects/PXD030684) to enable this peptide-to-spectrum matching [@saitoMultipleNutrientStresses2014; @saundersMicrobialFunctionalDiversity2022].
+Furthermore, protein identifications were based on peptide to spectrum matching using SEQUESTHT within Proteome Discoverer software (Thermo) and spectral counts were enumerated using Scaffold software (Proteome Software) using a FDR of <0.1% on the peptide level as described in Saunders *et al*.
+[@saundersMETATRYPMetaproteomicLeast2020].
 

### 2024-03-20 Code/Manuscript_O2.Rmd
moved .bib to 'DOCS' folder

@@
 always_allow_html: true
-bibliography: [Manuscript_O2.bib, RPackages.bib, FaultyCitations.bib]
-csl: plos-one.csl
+bibliography: ["`r file.path('..', 'Docs', 'Manuscript_O2.bib')`", "`r file.path('..', 'Docs', 'RPackages.bib')`", "`r file.path('..', 'Docs', 'FaultyCitations.bib')`"]
+csl: "`r file.path('..', 'Docs', 'plos-one.csl')`"
 editor_options: 

### 2024-03-20 Code/Manuscript_O2.Rmd
edits for PLOS submission

@@
 balance electron transport, which may exclude it from growth under our
-lowest 2.5 µmol O~2~ L^-1^ condition. SS120 from Clade LLII/III is
+lowest, 2.5 µmol O~2~ L^-1^, condition. SS120 from Clade LLII/III is
 restricted to low light under full 250 µmol O~2~ L^-1^, shows expanded
@@
 Controlled growth experiments were performed using MCMIX-OD or MC1000-OD
-PSI Multicultivators (Figure \@ref(fig:LabeledMC); PSI, Drásov, Czech
+PSI Multicultivators (Fig. \@ref(fig:LabeledMC); PSI, Drásov, Czech
 Republic). Each multicultivator individually controls 8 tubes at a
@@
 
-Figure \@ref(fig:deltaODLogGrowthPlot) is an example of chlorophyll
+Fig. \@ref(fig:deltaODLogGrowthPlot) is an example of chlorophyll
 specific growth estimates fitted from the high resolution ΔOD
@@
 \@ref(eq:WeightedPUR) and PAR is the imposed peak light level (µmol
-photons m^-2^ s^-1^). Figure (\@ref(fig:PurParPlot)) shows the
+photons m^-2^ s^-1^). Fig. (\@ref(fig:PurParPlot)) shows the
 calculated peak PUR (µmol photons m^-2^ d^-1^) vs. imposed
@@
 
-Figure \@ref(fig:OverlayPlots) provide visual representations of PUR,
+Fig. \@ref(fig:OverlayPlots) provide visual representations of PUR,
 the black solid line and shaded area, in relation to the imposed PAR,
 the dotted line, under each imposed spectral wavebands for *P. marinus*
-MED4 (A-C), SS120 (D-F) and MIT9313 (G-I). Figure
+MED4 (A-C), SS120 (D-F) and MIT9313 (G-I). Fig.
 (\@ref(fig:PurParPlot)) shows the relationship between calculated PUR
@@
 analyzed. We focused our analysis here on core photosynthetic protein
-complexes, for clades HL, LLI, LLII/III and LLIV (Figure
-\@ref(fig:CladeProchloroPhotosynthDepthO2) as a function of depth (a
+complexes, for clades HL, LLI, LLII/III and LLIV (Fig.
+\@ref(fig:CladeProchloroPhotosynthDepthO2)) as a function of depth (a
 proxy for light intensity) and measured [O~2~]. Photosynthetic complexes
@@
 *Prochlorococcus marinus* MED4, clade HLI, growth under 250 µM O~2~
-increased with higher imposed PAR and longer photoperiods (Figure
+increased with higher imposed PAR and longer photoperiods (Fig.
 \@ref(fig:MED4PAR)), across all spectral wavebands. No growth was
@@
 O~2~ showed fastest growth when the photoperiod was 16 h for each
-spectral waveband, across PAR levels (Figure \@ref(fig:MED4PAR)). The
+spectral waveband, across PAR levels (Fig. \@ref(fig:MED4PAR)). The
 µ~max~ was
@@
 
-MED4 did not grow when sparged to the lowest [O~2~] of 2.5 µM (Figure
+MED4 did not grow when sparged to the lowest [O~2~] of 2.5 µM (Fig.
 \@ref(fig:MED4PAR)). 2.5 µM O~2~ growth experiments were not conducted
@@
 
-The GAM model in Figure \@ref(fig:MED4GAM) summarizes MED4 growth
+The GAM model in Fig. \@ref(fig:MED4GAM) summarizes MED4 growth
 responses to red (A and B) or blue (C and D) peak PAR and photoperiod across 2
@@
 line representing the 90^th^ percentile of maximum achieved growth rate
-(Figure \@ref(fig:MED4GAM)C). Growth decreased with decreasing
+(Fig. \@ref(fig:MED4GAM)C). Growth decreased with decreasing
 photoperiod and decreasing peak PAR. Under red light growth was
 generally slower but the pattern of growth responses to photoperiod and
-PAR was similar (Figure \@ref(fig:MED4GAM)A). Note the exclusion of MED4
-from growth under 4 h photoperiod under both red and blue light (Figure
+PAR was similar (Fig. \@ref(fig:MED4GAM)A). Note the exclusion of MED4
+from growth under 4 h photoperiod under both red and blue light (Fig.
 \@ref(fig:MED4GAM)). Under 25 µM O~2~ MED4 showed similar growth
@@
 increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^
-peak PAR and across all spectral wavebands (Figure \@ref(fig:SS120PAR)).
+peak PAR and across all spectral wavebands (Fig. \@ref(fig:SS120PAR)).
 No growth was observed under any blue light photoperiods when exposed to
@@
 photoperiod for red spectral waveband, however under blue light, SS120
-was able to grow (Figure \@ref(fig:SS120PAR)). In contrast to the growth
+was able to grow (Fig. \@ref(fig:SS120PAR)). In contrast to the growth
 trends of the 250 µM O~2~ and PAR of 90 µmol photons m^-2^ s^-1^
@@
 SS120 did not reproducibly grow when sparged to the lowest O~2~ of 2.5
-µM (Figure \@ref(fig:SS120PAR)). 2.5 µM O~2~ growth experiments were not
+µM (Fig. \@ref(fig:SS120PAR)). 2.5 µM O~2~ growth experiments were not
 conducted for 4 and 16 h photoperiods under PAR of 180 µmol photons
@@
 
-The GAM model in Figure \@ref(fig:SS120GAM) summarizes growth responses
+The GAM model in Fig. \@ref(fig:SS120GAM) summarizes growth responses
 of SS120 to red (A and B) or blue (C and D) peak PAR and photoperiod, across the
-2 imposed oxygen concentrations. Under 250 µM O~2~, Figure
+2 imposed oxygen concentrations. Under 250 µM O~2~, Fig.
 \@ref(fig:SS120GAM)C showed highest growth rates below blue light PAR of
@@
 (representing the 90^th^ percentile of achieved growth rate), out pacing
-the 90^th^ percentile fastest growth rates under 250 µM O~2~ (Figure
-\@ref(fig:SS120GAM)D). Under red light and 25 µM O~2~ (Figure
+the 90^th^ percentile fastest growth rates under 250 µM O~2~ (Fig.
+\@ref(fig:SS120GAM)D). Under red light and 25 µM O~2~ (Fig.
 \@ref(fig:SS120GAM)B) SS120 grew across most conditions of peak PAR and
@@
 increased with longer photoperiods, under low 30 µmol photons m^-2^
-s^-1^ peak PAR, (Figure \@ref(fig:MIT9313PAR)). Under intermediate 90
+s^-1^ peak PAR, (Fig. \@ref(fig:MIT9313PAR)). Under intermediate 90
 µmol photons m^-2^ s^-1^ peak PAR growth rates decreased with increasing
@@
 For MIT9313 under 25 µM O~2~, growth rate increased with increasing
-photoperiods for all spectral wavebands tested (Figure
+photoperiods for all spectral wavebands tested (Fig.
 \@ref(fig:MIT9313PAR)), with the fastest overall growth rate for MIT9313
@@
 generally slower than under the parallel experiments at 25 µM O~2~
-(Figure \@ref(fig:MIT9313PAR)). Growth estimates showed scatter among
+(Fig. \@ref(fig:MIT9313PAR)). Growth estimates showed scatter among
 replicates, suggesting 2.5 µM O~2~ is near the tolerance limit for
@@
 
-The GAM model in Figure \@ref(fig:MIT9313GAM) summarizes MIT9313 growth
+The GAM model in Fig. \@ref(fig:MIT9313GAM) summarizes MIT9313 growth
 responses to red (A-C) or blue (D-F) peak PAR and photoperiod. Under
-250 µM O~2~, Figure \@ref(fig:MIT9313GAM)D shows MIT9313 achieves
+250 µM O~2~, Fig. \@ref(fig:MIT9313GAM)D shows MIT9313 achieves
 fastest growth rates between blue peak PAR of 30 µmol photons m^-2^
@@
 indicated by the contour line labeled 0.52 d^-1^ representing the 90^th^
-percentile of achieved growth rates. Figure \@ref(fig:MIT9313GAM)D also
+percentile of achieved growth rates. Fig. \@ref(fig:MIT9313GAM)D also
 shows that growth rate increases with longer photoperiods, as long as
@@
 contrast, under red light and 250 µM O~2~ MIT9313 grows faster while
-exploiting higher peak PAR and longer photoperiods. Figure
+exploiting higher peak PAR and longer photoperiods. Fig.
 \@ref(fig:MIT9313GAM)E shows that MIT9313 can exploit all blue PAR levels
 and most photoperiods with 90^th^ percentile of fastest growth rate
-between 30 to 100 µmol photons m^-2^ s^-1^ PAR. Figure
+between 30 to 100 µmol photons m^-2^ s^-1^ PAR. Fig.
 \@ref(fig:MIT9313GAM)F shows that MIT9313 maintains growth even under
@@
 between 50 to 100 µmol photons m^-2^ s^-1^ PAR. Thus the designation of
-MIT9313 as a LL clade is dependent upon [O~2~] and light spectra (Figure \@ref(fig:MIT9313GAM)E).
+MIT9313 as a LL clade is dependent upon [O~2~] and light spectra (Fig. \@ref(fig:MIT9313GAM)E).
 
@@
 almost 3 times that of white LED light, and about 5 times that of the
-red light (Figure \@ref(fig:PurParPlot)), despite being derived from the
+red light (Fig. \@ref(fig:PurParPlot)), despite being derived from the
 same photoperiods and peak PAR regimes. As such, only blue light
@@
 delivered cumulative diel PUR equivalent to other photoperiod treatments
-(Figure \@ref(fig:PhotoperiodPurFitsPlots)A-C). In parallel MED4
+(Fig. \@ref(fig:PhotoperiodPurFitsPlots)A-C). In parallel MED4
 showed no growth under 2.5 µM O~2~, no matter the level of diel
@@
 cumulative diel PUR, with saturation of growth rate achieved around 1.0
-x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A and B),
+x 10^6^ µmol m^-2^d^-1^ (Fig. \@ref(fig:BluevsRedPurFitsPlots)A and B),
 and no evidence of inhibition of growth at any achieved cumulative diel
 PUR. Under the 'artificial' growth treatment of red light, MED4 achieved
-more growth per unit diel cumulative PUR (Figure
+more growth per unit diel cumulative PUR (Fig.
 \@ref(fig:BluevsRedPurFitsPlots)A and B), consistent with Murphy *et al*.
@@
 photoinactivation of PSII, than equivalent levels of blue light. For
-distinct fits for different photoperiods refer to Figure
+distinct fits for different photoperiods refer to Fig.
 \@ref(fig:PhotoperiodPurFitsPlots) A-C.
@@
 The representative of the LLII/III clade, *P. marinus* SS120 showed
-almost no growth under 2.5 µM O~2~ experiments (Figure
+almost no growth under 2.5 µM O~2~ experiments (Fig.
 \@ref(fig:PhotoperiodPurFitsPlots)F). Most 4 h photoperiod treatments of
@@
 delivered cumulative diel PUR equivalent to other photoperiod treatments
-(Figure \@ref(fig:PhotoperiodPurFitsPlots)D). Again using
+(Fig. \@ref(fig:PhotoperiodPurFitsPlots)D). Again using
 [@harrisonPhotosynthesisirradianceRelationshipsPolar1986], SS120 did not
@@
 cumulative diel PUR under any spectral waveband or photoperiod
-combination, under 250 µM O~2~ (Figure
+combination, under 250 µM O~2~ (Fig.
 \@ref(fig:PhotoperiodPurFitsPlots)D).
@@
 consistent with lower cost of growth through lower photoinactivation
-under red light (Figure \@ref(fig:BluevsRedPurFitsPlots)E)
+under red light (Fig. \@ref(fig:BluevsRedPurFitsPlots)E)
 [@murphyPhotoinactivationPhotosystemII2017]. For distinct fits for
-different photoperiods refer to Figure
+different photoperiods refer to Fig.
 \@ref(fig:PhotoperiodPurFitsPlots) D-F.
@@
 inhibition of growth, across photoperiods, and spectral wavebands
-(Figure \@ref(fig:PhotoperiodPurFitsPlots)G). Under 25 µM O~2~ MIT9313
+(Fig. \@ref(fig:PhotoperiodPurFitsPlots)G). Under 25 µM O~2~ MIT9313
 showed higher growth rates over a wider plateau, with a greatly extended
 exploitation of higher cumulative diel PUR, with full growth inhibition
-only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Figure
+only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Fig.
 \@ref(fig:PhotoperiodPurFitsPlots)H). MIT9313 growth under 2.5 µM O~2~
@@
 full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^
-d^-1^ cumulative diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).
+d^-1^ cumulative diel PUR (Fig. \@ref(fig:PhotoperiodPurFitsPlots)I).
 
@@
 of growth, due to decreased photoinactivation of PSII under red,
-compared to blue, wavebands (Figure
+compared to blue, wavebands (Fig.
 \@ref(fig:BluevsRedPurFitsPlots)G and H). Interestingly, this protective
@@
 possibly because photoinactivation is strongly suppressed under this low
-[O~2~] (Figure \@ref(fig:BluevsRedPurFitsPlots)I). For distinct fits for
-different photoperiod fits refer to Figure
+[O~2~] (Fig. \@ref(fig:BluevsRedPurFitsPlots)I). For distinct fits for
+different photoperiod fits refer to Fig.
 \@ref(fig:PhotoperiodPurFitsPlots) G-I.
@@
 SS120 and clade LLIV MIT9313 show generally similar patterns vs. [O~2~]
-and depth, a proxy for peak PAR (Figure
+and depth, a proxy for peak PAR (Fig.
 \@ref(fig:CladeProchloroProteinMetabDepthO2)). FtsH3, inferred to
 mediate PSI assembly, likewise shows a similar pattern between MED4 and
-MIT9313 (Figure \@ref(fig:CladeProchloroProteinMetabDepthO2)). But only
+MIT9313 (Fig. \@ref(fig:CladeProchloroProteinMetabDepthO2)). But only
 MED4 shows the presence of the FtsH1 & FtsH2 isoforms inferred to
 mediate PSII repair, and then only in near-surface samples subject to
-higher light levels. Furthermore, even though MIT9313 grows (Figure
+higher light levels. Furthermore, even though MIT9313 grows (Fig.
 \@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~]
-(Figure \@ref(fig:CladeProchloroPhotosynthDepthO2)), no FtsH from
-MIT9313 is detected at low [O~2~] (Figure
+(Fig. \@ref(fig:CladeProchloroPhotosynthDepthO2)), no FtsH from
+MIT9313 is detected at low [O~2~] (Fig.
 \@ref(fig:CladeProchloroProteinMetabDepthO2)), suggesting limited
@@
 
-Figure \@ref(fig:ProchlorococcusEnzymeKms) shows the measured or
+Fig. \@ref(fig:ProchlorococcusEnzymeKms) shows the measured or
 inferred K~M~ for [O~2~] for enzymes encoded by genes 
@@
 inter-system transport chain. The approximate K~M~ for [O~2~] of \~ 25
-µM for ubiquinol oxidase (non electrogenic) (Figure
+µM for ubiquinol oxidase (non electrogenic) (Fig.
 \@ref(fig:ProchlorococcusEnzymeKms)) is comparable to the lower limit
-for growth of MED4 in our experiments (Figure \@ref(fig:MED4GAM)). We
+for growth of MED4 in our experiments (Fig. \@ref(fig:MED4GAM)). We
 suggest that dependence upon this enzyme excludes MED4 from low oxygen
-zones. The genome scan shows SS120 and MIT9313 lack this gene (Figure
+zones. The genome scan shows SS120 and MIT9313 lack this gene (Fig.
 \@ref(fig:ProchlorococcusEnzymeKms)), and therefore, lack this
@@
 gene encoding (S)-2-hydroxy-acid oxidase is encoded in the MIT9313
-genome (Figure \@ref(fig:ProchlorococcusEnzymeKms)). (S)-2-hydroxy-acid
+genome (Fig. \@ref(fig:ProchlorococcusEnzymeKms)). (S)-2-hydroxy-acid
 oxidase catalyzes the reaction of 2-hydroxy acid with O~2~ to produce
@@
 photoinhibition and circumvent its limitations on PSII repair to exploit
-higher light. Figure \@ref(fig:ProchlorococcusEnzymeKms) also shows that
+higher light. Fig. \@ref(fig:ProchlorococcusEnzymeKms) also shows that
 *P. marinus* SS120 is the only tested ecotype to lack the pyridoxal
@@
 grow as well as *P. marinus* MIT9313, when exposed to high light stress
-under 25 µM O~2~ and not at all under 2.5 µM O~2~ (Figure
+under 25 µM O~2~ and not at all under 2.5 µM O~2~ (Fig.
 \@ref(fig:SS120PAR)).
@@
 
-Figure \@ref(fig:DNARepairFig) shows genes encoding DNA repair for *P.
+Fig. \@ref(fig:DNARepairFig) shows genes encoding DNA repair for *P.
 marinus* strains. As expected, *P. marinus* MED4 possesses the largest,
@@
 and NATL2A were the only strains to possess a gene encoding
-deoxyribodipyrimidine photolyase (Figure \@ref(fig:DNARepairFig) and
+deoxyribodipyrimidine photolyase (Fig. \@ref(fig:DNARepairFig) and
 \@ref(fig:ProchlorococcusLightEnzymes)), which, in the presence of blue
@@
 MIT9313, actually tolerate approximately 1.0 x 10^6^ µmol photons m^-2^
-d^-1^ of PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)E,H), comparable
+d^-1^ of PUR (Fig. \@ref(fig:PhotoperiodPurFitsPlots)E and H), comparable
 to the representative HL clade, MED4 which also exhibited growth
 saturation at the same cumulative diel PUR of 1.0 x 10^6^ µmol photons
-m^-2^ d^-1^ (Figure \@ref(fig:PhotoperiodPurFitsPlots)A and B). Growth under
+m^-2^ d^-1^ (Fig. \@ref(fig:PhotoperiodPurFitsPlots)A and B). Growth under
 lower O~2~ allowed MIT9313 to substantially increase its exploitation of
-higher diel PUR (Figure \@ref(fig:PhotoperiodPurFitsPlots)I).
+higher diel PUR (Fig. \@ref(fig:PhotoperiodPurFitsPlots)I).
 
@@
 habitats of 2.5 µM O~2~, but can, grow under OMZ regions with 25 µM
-O~2~. Genomic (Figure \@ref(fig:ProchlorococcusEnzymeKms)) and
+O~2~. Genomic (Fig. \@ref(fig:ProchlorococcusEnzymeKms)) and
 transcriptional analyses [@bergResponsesPsbAHli2011] suggest MED4 is
@@
 layer, nor did they report[O~2~] at depth. Our growth findings are
-consistent with Figure \@ref(fig:CladeProchloroPhotosynthDepthO2)
+consistent with Fig. \@ref(fig:CladeProchloroPhotosynthDepthO2)
 showing PSII proteins annotated as MED4, clade HLI, at depths up to 200
@@
 with a higher tolerance for higher cumulative diel PUR under 25 µM O~2~,
-compared to 250 µM O~2~ (Figure \@ref(fig:PhotoperiodPurFitsPlots)).
+compared to 250 µM O~2~ (Fig. \@ref(fig:PhotoperiodPurFitsPlots)).
 Thus, SS120 can exploit higher PAR environments, within OMZ. SS120 is
 likely excluded from the combination of higher [O~2~] and higher PAR by
-genomic limitations on capacity for DNA repair (Figure
+genomic limitations on capacity for DNA repair (Fig.
 \@ref(fig:DNARepairFig)), and possibly by limited capacity for synthesis
-of reactive oxygen quenchers (Figure
+of reactive oxygen quenchers (Fig.
 \@ref(fig:ProchlorococcusEnzymeKms)). Our growth results are supported
@@
 fragment length polymorphism analyses, at depths above 40 m, where light
-levels are higher, within OMZ, and by Figure
+levels are higher, within OMZ, and by Fig.
 \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSII protein subunits
@@
 higher light levels and cumulative diel PUR, but only under low oxygen
-conditions of 25 µM and 2.5 µM (Figure \@ref(fig:MIT9313PAR)), enabling
+conditions of 25 µM and 2.5 µM (Fig. \@ref(fig:MIT9313PAR)), enabling
 MIT9313 to grow in OMZ, even at depths closer to the surface. MIT9313
@@
 [@cunaneCrystalStructureAnalysis2005], with a K~M~ for [O~2~] of \~ 250
-µM (Figure \@ref(fig:ProchlorococcusEnzymeKms)), which produces
+µM (Fig. \@ref(fig:ProchlorococcusEnzymeKms)), which produces
 H~2~O~2~. Growth at lower [O~2~] may protect MIT9313 from
@@
 expand into broader ecological niches. These results are supported by
-Figure \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSI protein
+Fig. \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSI protein
 subunits annotated as derived from MIT9313 detected at depths \> 120 m,
@@
 
+# References {.unnumbered}
+
+<div id="refs"></div>
+
+\newpage
+
 # Supporting information {.unnumbered}
@@
                       "The temperature of culture tubes are collectively controlled via heating or cooling of the aquarium water.",
-                      "Gas with specific oxygen concentrations is bubbled through a humidifier and passed through a 0.2 um filter.",
+                      "Gas with specific oxygen concentrations is bubbled through a humidifier and passed through a 0.2 µm filter.",
 
@@
 
+Makoto Saito for edits and feedback pertaining to the Ocean Protein Portal dataset.   
 Miranda Corkum maintained cultures and trained personnel in culture
@@
 
-To Be Entered through PLoSONe system and deleted here 
 Czech Academy of Science (OP) visiting fellowship supporting DAC work at AlgaTech
+
 Canada Research Chair in Phytoplankton Ecophysiology (DAC), Grant number CRC-2017-00075
+
 Natural Sciences and Engineering Research Council of Canada, 'Latitude and Light' (DAC)
+
 Canada Foundation for Innovation (DAC)
-New Brunswick Foundation for Innovation (DAC and MS) 
-Rice Graduate Fellowship 2021 and 2022 (MS)
+
+New Brunswick Innovation Foundation (DAC)
+
+New Brunswick Innovation Foundation STEM Scholarship 2021 and 2022 (MS)
+
+Mount Allison University Rice Graduate Fellowship 2021 and 2022 (MS)
 
@@
 \newpage
-
-# References {.unnumbered}

### 2024-03-25 Code/Plots_GAM.Rmd
Corrected file path in "Intro"

@@
 The gam function from the R package mgcv (Wood, 2022) was used to model the growth rate with smoothing terms to indicate the 90, 50 and 10% quantiles.
-"PICO_Merged_GrowthFitsPURPAR.Rds" is called in from \Data\CleanData\CleanedMCData folder and generated GAM plots are saved in \Output\Figures folder as .png.
+"PICO_Merged_GrowthFitsPURPAR.Rds" is called in from \Data\CleanData folder and generated GAM plots are saved in \Output\Figures folder as .png.
 

### 2024-03-25 Code/Plots_GAM.Rmd
Changed title to match Rmd name

@@
 ---
-title: "ManuscriptGAM"
+title: "Plots_GAM"
 author:

### 2024-03-25 Code/Plots_GAM.Rmd
minor edit to intro

@@
 This .Rmd produces a Generalized Additive Model (GAM) to examine the relationship between the chlorophyll proxy (ΔOD) growth rate across the blue and red spectral wavebands, photoperiod and PAR levels for each P.marinus ecotype in this study.
-The gam function from the R package mgcv (Wood, 2022) was used to model the growth rate with smoothing terms to indicate the 90, 50 and 10% quantiles.
+The GAM function from the R package mgcv (Wood, 2022) was used to model the growth rate with smoothing terms to indicate the 90, 50 and 10% quantiles.
 "PICO_Merged_GrowthFitsPURPAR.Rds" is called in from \Data\CleanData folder and generated GAM plots are saved in \Output\Figures folder as .png.

### 2024-03-25 Code/Plots_Genome.Rmd
Changed title names to match rmd name
minor edit to units in caption

--- 2024-03-04 Code/ManuscriptGenome.Rmd
@@
 ---
-title: "R Notebook"
+title: "Plots_Genome"
 ---
@@
 ```{r, ProchlorococcusEnzymeKms, fig.cap = ProchlorococcusEnzymeKms_cap, fig.width = 20, fig.height = 10}
-ProchlorococcusEnzymeKms_cap <- glue("**Comparison of log~10~(K~m~ for O~2~ in mM) vs.genes encoding O~2~ utilizing enzymes in *Prochlorococcus***, faceted by their respective strains.",
+ProchlorococcusEnzymeKms_cap <- glue("**Comparison of log~10~(K~m~ for O~2~ in µM) vs.genes encoding O~2~ utilizing enzymes in *Prochlorococcus***, faceted by their respective strains.",
                                      "Symbol color corresponds to number of genes encoding O~2~ utilizing enzymes.",

### 2024-03-25 Code/Plots_Growth.Rmd
Changed title names to match rmd name
Added an "Introduction"

@@
 ---
-title: "ManuscriptFigures"
+title: "Plots_Growth"
 author: 
@@
 ---
+
+# Introduction
+
+This .Rmd reads in "PICO_Merged_GrowthFitsPURPAR.Rds" from the "Data/CleanData" folder and generates figures that are later called into "Manuscript_O2.Rmd".
+The generated plots are saved in the "Output/Figures" folder.
 

### 2024-03-25 Code/Plots_PURFits.Rmd
Changed title names to match rmd name
Added an "Introduction"

@@
 ---
-title: "ManuscriptPURFits"
+title: "Plots_PURFits"
 author: 
@@
 
-To Do
+# Introduction
+
+This .Rmd generates a one-way ANOVA to examine statistical differences between Harrison and Platt four parameter model fit to 660 nm (red light) and 450 nm (blue light) growth data for each combination of strain and [O~2~].
+Additionally, a one-way ANOVA was used to examine statistical differences between Harrison and Platt [53] four parameter model fit to each photoperiod (4 h, 8 h, 12 h, 16 h) and pooled photoperiod growth data for each combination of strain and [O~2~].
+Photoperiod growth data that showed complete growth inhibition for each combination of strain, [O~2~] and imposed spectral waveband were omitted from the pooled photoperiod model.
+Statistical differences were determined at P value < 0.05.
+It can be safely assumed that *P.marinus* dies at PAR of 0 µE therefore, dummy values of no growth (µ = 0) for dark conditions were assigned for each combination of [O~2~], photoperiod and spectral waveband for each strain to anchor the starting point of the model.
+
+The four parameters are:
+I: incident light, umol photons m^-2^ s^-1^
+a: alpha, initial slope of light response curve under limiting light; the 'affinity' of the culture for light.
+Pmax: maximum rate of photosynthesis; umol O~2~ chl^-1^ s^-1^; the 'capacity' of the culture for photosynthesis.
+b: beta 'photoinhibition' term for decline in oxygen evolution under increasing incident light.  This decrease can result from multiple mechanisms.
+
+"PICO_Merged_GrowthFitsPURPAR.Rds" is called in from \Data\CleanData folder and generated PUR fit plots are saved as .png in \Output\Figures folder.
 

### 2024-03-27 Code/Plots_Genome.Rmd
Plots_Genome.Rmd integration with GitHub

--- 2024-03-01 Code/ManuscriptGenome.Rmd
@@
 ---
-title: "R Notebook"
-output: html_notebook
+title: "Plots_Genome"
 ---
@@
 combinedHits can be found on https://doi.org/10.5061/dryad.kh1893284. Filtered to only include Prochlorococcus genomes.
+
 ```{r}
@@
 
-```{r}
-MergedData <- readRDS(file.path(DataIn, "ProchlorococcusGenomeData.Rds"))
+```{r read ProchlorococcusGenomeO2Data}
+MergedData <- readRDS(file.path(DataIn, "ProchlorococcusGenomeO2Data.Rds"))
 ```
@@
 ```{r, , fig.width = 7, fig.height = 5}
-MergedData %>%
-  filter(!is.na(Gene_count),
-         Taxa == "Prokaryote") %>%
-  group_by(EC) %>%
-  mutate(Km_mM_min = min(Km_mM), 
-         Km_mM_max = max(Km_mM)) %>% 
-  ggplot() +
-  geom_errorbar(aes(x = reorder(EnzymeName, Km_mM), ymin = log10(Km_mM_min), ymax = log10(Km_mM_max))) +
-  geom_point(aes(x = reorder(EnzymeName, Km_mM), y = log10(Km_mM), color = log10(Km_mM))) +
-  geom_hline(yintercept = log10(1e-3), linetype = "dotted") +
-  geom_hline(yintercept = log10(5e-3), linetype = "dotted") +
-  geom_hline(yintercept = log10(230e-3), linetype = "dotted", color = "red") +
-  geom_hline(yintercept = log10(290e-3), linetype = "dotted", color = "red") +
-  scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
-  theme_bw() +
-  ggpubr::rotate_x_text(angle = 70) 
+# MergedData %>%
+#   filter(!is.na(Gene_count),
+#          Taxa == "Prokaryote") %>%
+#   group_by(EC) %>%
+#   mutate(Km_mM_min = min(Km_mM), 
+#          Km_mM_max = max(Km_mM)) %>% 
+#   ggplot() +
+#   geom_errorbar(aes(x = reorder(EnzymeName, Km_mM), ymin = log10(Km_mM_min), ymax = log10(Km_mM_max))) +
+#   geom_point(aes(x = reorder(EnzymeName, Km_mM), y = log10(Km_mM), color = log10(Km_mM))) +
+#   geom_hline(yintercept = log10(1e-3), linetype = "dotted") +
+#   geom_hline(yintercept = log10(5e-3), linetype = "dotted") +
+#   geom_hline(yintercept = log10(230e-3), linetype = "dotted", color = "red") +
+#   geom_hline(yintercept = log10(290e-3), linetype = "dotted", color = "red") +
+#   scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
+#   theme_bw() +
+#   ggpubr::rotate_x_text(angle = 70) 
 ```
@@
                            TRUE ~ Km_mM_max)) %>% 
+  # mutate(Km_mM = case_when(EnzymeName == "Flavodiiron (Flv1a/3a)" ~ 10/1000,
+  #                          TRUE ~ Km_mM)) %>% 
   ungroup() %>% 
@@
   geom_errorbar(aes(x = reorder(EnzymeName, Km_mM * 1000), ymin = log10(Km_mM_min* 1000), ymax = log10(Km_mM_max* 1000))) +
+  # geom_ribbon(aes(ymin = log10(5e-4), ymax =  log10(5e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "blue") +
+  # geom_ribbon(aes(ymax = log10(5e-2), ymin =  log10(5e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "green") +
+  # geom_ribbon(aes(ymax = log10(280e-3), ymin =  log10(230e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "#FF0000") +
   annotate(geom = "rect", ymin = log10(5e-4 * 1000), ymax =  log10(5e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "blue") +
@@
   geom_text(aes(x = 18.5, y = 2.5, label = "[O2] ≈ 250 µM"), color = "#FF0000", size = 6) +
+  # geom_hline(yintercept = log10(5e-4), linetype = "dotted") +
+  # geom_hline(yintercept = log10(5e-3), linetype = "dotted") +
+  # geom_hline(yintercept = log10(5e-3), linetype = "dotted", color = "brown") +
+  # geom_hline(yintercept = log10(5e-2), linetype = "dotted", color = "brown") +
+  # geom_hline(yintercept = log10(230e-3), linetype = "dotted", color = "red") +
+  # geom_hline(yintercept = log10(290e-3), linetype = "dotted", color = "red") +
+  # scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
   ggh4x::facet_nested(rows = vars(StrainLabel)) +
@@
   labs(# title = ~K[m] ~O[2] ~  "for *Prochlorococcus* Enzymes using Oxygen", # "Estimates of Affinities of *Prochlorococcus* Enzymes for Oxygen" # "Affinities for Phytoplankton Enzymes for Oxygen", 
-       x = "Enzyme Name",
+       x = "Enzyme name",
        y = ~log[10] ~ "("~K[m] ~O[2] ~"(µM))",
-       size = "Gene Count",
+       size = "Gene count",
        shape = ""~K[m]) +
@@
 
-```{r, ProchlorococcusEnzyme,  fig.width = 7, fig.height = 5}
-# ProchlorococcusEnzyme <- MergedData %>%
-#   filter(!is.na(Gene_count)) %>%
-#   # filter(PriSec == "Primary") %>%
-#   filter(FileName == "Prochlorococcus_marinus_MIT9313-aa-gen"| FileName == "Prochlorococcus_marinus_pastoris_CCMP1986-aa-gen" | FileName == "Prochlorococcus_marinus_marinus_CCMP1375-aa-gen") %>%
-#   # group_by(EC) %>%
-#   # mutate(ECNumberTotal = sum(Gene_count)) %>%
-#   # ungroup() %>% View()
-#   # filter(ECNumberTotal != 0) %>%
-#   ggplot() +
-#   geom_point(aes(x = reorder(EnzymeName, Km_mM), y = interaction(Genus, species, Strain, sep = " "), size = Gene_count, color = log10(AvgKm_mM))) +
-#   facet_grid(rows = vars(Genus), scales = "free", space = "free") +
-#   scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
-#   scale_x_discrete(position = "top") +
-#   scale_radius(breaks = c(1,2,3,4,5), range = c(2.5,5)) +
-#   theme_bw() +
-#   ggpubr::rotate_x_text(hjust = 0, angle = 70) +
-#   labs(x = "Enzyme Name",
-#        y = "Organism",
-#        size = "Gene Count", 
-#        color = "log10(Km (mM))")
-# 
-# ProchlorococcusEnzyme
-```
-
-```{r, ProchlorococcusEnzyme ggsave, include = FALSE}
-# ggsave(filename = file.path(Figures, "ProchlorococcusEnzyme.png"), plot = ProchlorococcusEnzyme, height = 10, width = 10)
+```{r read ProchlorococcusGenomeDNARepairData}
+DNARepair <- readRDS(file.path(DataIn, "ProchlorococcusGenomeDNARepairData.Rds"))
 ```
@@
 ```{r, DNARepair}
-DNARepair <- MetaData %>% 
-  left_join(., DataIn, by = c("FileName" = "genome")) %>% 
-  filter(Genus == "Prochlorococcus") %>% 
-  separate_rows(GOs, sep = ",") %>% 
-  filter(Strain %in% c("CCMP1986", "CCMP1375", "MIT9313", "NATL2A")) %>% 
-  filter(GOs %in% c("GO:0006281", "GO:0000716", "GO:0000725", "GO:0006284", "GO:0006289", "GO:0006298", "GO:0006302", "GO:0009432", "GO:0006974", "GO:0003904", "GO:0003914") | EC %in% c("4.1.99.3", "4.1.99.13", "1.13.11.33", "3.2.2.17", "5.6.2.3", "6.5.1.1", "6.5.1.2"))
+# DNARepair <- MetaData %>% 
+#   left_join(., DataIn, by = c("FileName" = "genome")) %>% 
+#   filter(Genus == "Prochlorococcus") %>% 
+#   separate_rows(GOs, sep = ",") %>% 
+#   filter(Strain %in% c("CCMP1986", "CCMP1375", "MIT9313", "NATL2A")) %>% 
+#   filter(GOs %in% c("GO:0006281", "GO:0000716", "GO:0000725", "GO:0006284", "GO:0006289", "GO:0006298", "GO:0006302", "GO:0009432", "GO:0006974", "GO:0003904", "GO:0003914") | 
+#            EC %in% c("3.1.3.18", 
+#     "3.6.1.56", 
+#     "3.1.22.4",
+#     "3.1.21.10", 
+#     "6.5.1.2", 
+#     "6.5.1.1",
+#     "6.5.1.8", 
+#     "2.1.1.63", 
+#     "3.2.2.27", 
+#     "3.1.3.99", 
+#     "4.2.1.130",
+#     "3.1.11.1",
+#     "5.6.2.3",
+#     "4.2.99.18",
+#     "2.7.7.7",
+#     "3.2.2.21",
+#     "3.5.1.124",
+#     "3.2.2.23",
+#     "3.2.2.20",
+#     "3.6.1.58",
+#     "3.1.11.6",
+#     "3.1.21.2",
+#     "3.1.11.2",
+#     "3.2.2.31",
+#     "5.6.2.4",
+#     "3.1.11.5",
+#     "2.7.7.86",
+#     "3.6.1.69",
+#     "2.1.1.319",
+#     "2.1.1.357",
+#     "2.1.1.359",
+#     "2.1.1.360",
+#     "2.7.7.85", 
+#     "3.6.1.55",
+#     "4.1.99.3"))
 
-DNARepairFig <- DNARepair %>% 
+DNARepairTab <- DNARepair %>% 
   mutate(EnzymeName = case_when(EC == "3.2.2.21" ~ "DNA-3-methyladenine glycosylase II",
                                 EC == "3.1.22.4" ~ "crossover junction endodeoxyribonuclease",
+                                EC == "3.1.11.6" ~ "exodeoxyribonuclease VII",
+                                EC == "3.2.2.21" ~ "DNA-3-methyladenine glycosylase II",
+                                EC == "3.1.3.18" ~ "phosphoglycolate phosphatase",
+                                EC == "3.2.2.23" ~ "DNA-formamidopyrimidine glycosylase",
+                                EC == "3.1.11.2" ~ "exodeoxyribonuclease III",
+                                EC == "4.2.99.18" ~ "DNA-(apurinic or apyrimidinic site) lyase",
+                                EC == "3.2.2.27" ~ "uracil-DNA glycosylase",
+                                EC == "3.1.11.5" ~ "exodeoxyribonuclease V",
                                 EC == "6.5.1.2" ~ "DNA ligase (NAD+)",
+                                EC == "4.1.99.3" ~ "deoxyribodipyrimidine photolyase",
                                 EC == "6.5.1.1" ~ "DNA ligase (ATP)",
-                                EC == "4.1.99.3" ~ "deoxyribodipyrimidine photo-lyase")) %>% 
+                                EC == "2.7.7.7" ~ "DNA-directed DNA polymerase")) %>% 
   mutate(StrainLabel = case_when(Strain == "CCMP1375" ~ "SS120",
@@
                                  Strain == "NATL2A" ~ "NATL2A")) %>%
-  mutate(StrainLabel = factor(StrainLabel, levels = c("MED4", "NATL2A", "SS120", "MIT9313"))) %>%
+  mutate(StrainLabel = factor(StrainLabel, levels = c("MED4", "NATL2A", "SS120", "MIT9313")))
+
+DNARepairFig <- DNARepairTab %>% 
   ggplot() +
-  geom_point(aes(x = EnzymeName, y = StrainLabel, size = (Gene_count))) + #y = interaction(Genus, species, StrainLabel, sep = " ")
+  geom_point(aes(x = fct_reorder(EnzymeName, desc(Gene_count)), y = StrainLabel, size = (Gene_count))) + #y = interaction(Genus, species, StrainLabel, sep = " ")
   # facet_grid(rows = vars(Genus), scales = "free", space = "free") +
@@
   theme_bw() +
-  ggpubr::rotate_x_text(hjust = 1, angle = 70)  +
-  labs(x = "Enzyme Name",
+  ggpubr::rotate_x_text(hjust = 1, angle = 80)  +
+  labs(x = "Enzyme name",
        #y = "Organism",
-       color = "Gene Count",
-       size = "Gene Count") +
+       color = "Gene count",
+       size = "Gene count") +
   facet_grid(rows = vars(StrainLabel), scale = "free") +
@@
          axis.title.y = element_blank(),
-         axis.title.x = element_text(vjust=10),
+         axis.title.x = element_text(vjust=5),
         axis.ticks.y = element_blank(),
+  # axis.title = element_text(size = 40, color = "black"),
+  #        title = element_text(size = 30),
+  #     # axis.text.x = element_text(size = 30, color = "black"),
+  #       axis.text.y = element_text(size = 30, color = "black"),
         strip.text = element_text(size = 6),
         legend.box.background = element_rect(colour = "black")
+  #       # legend.key.size = unit(10, 'cm'), #change legend key size
+  #       # legend.key.height = unit(2, 'cm'), #change legend key height
+  #       # legend.key.width = unit(1, 'cm'), #change legend key width
+  #       legend.title =  element_text(size = 30),  #change legend title font size
+  #       legend.text = element_text(size = 30))   #change legend text font size
   )
@@
 DNARepairFig
+   # ggpubr::rotate_x_text(hjust = 0) 
 ```
@@
 ggsave(filename = file.path(Figures, "DNARepairFig.png"), plot = DNARepairFig, height =5 , width = 5)
-```
-
-```{r import LightEnzymes, include = FALSE}
-LightEnzymes <- read_csv(file.path(Data, "LightEnzymes.csv")) %>% 
-  select(-c(`...4`, `...5`)) %>% 
-  filter(is.na(Remove))
+ggsave(filename = file.path(Figures, "Fig12.tiff"), plot = DNARepairFig, height =5 , width = 5, compression = "lzw")
 ```
@@
 ```{r LightEnzymes, include=FALSE}
-LightEnzymesList <- LightEnzymes$EC
-LightEnzymesMerged <- MetaData %>% 
-  filter(Genus == "Prochlorococcus" | Taxa == "Diatom") %>% 
-  left_join(., DataIn, by = c("FileName" = "genome")) %>% 
-  filter(EC %in% LightEnzymesList) %>% 
-  left_join(., LightEnzymes, by = c("EC"), relationship = "many-to-many") %>% 
-  filter(Description != "KM Value") %>% 
-  separate_rows(GOs, sep = ",") %>% 
-  mutate(EnzymeName = case_when(EC == "1.3.1.33" ~ "(light-dependent) protochlorophyllide reductase",
-                                EC == "2.4.1.14" ~ "sucrose-phosphate synthase",
-                                EC == "2.5.1.32" ~ "15-cis-phytoene synthase",
-                                EC == "4.6.1.1" ~ "adenylate cyclase",
-                                EC == "4.4.1.5" ~ "lactoylglutathione lyase",
-                                EC == "4.2.3.5" ~ "chorismate synthase",
-                                EC == "2.7.1.148" ~ "4-(cytidine 5'-diphospho)-2-C-methyl-D-erythritol kinase",
-                                EC == "4.2.99.18" ~ "DNA-(apurinic or apyrimidinic site) lyase",
-                                EC == "3.4.11.1" ~ "leucyl aminopeptidase",
-                                EC == "2.4.1.255" ~ "protein O-GlcNAc transferase",
-                                EC == "3.1.4.4" ~ "phospholipase D",
-                                EC == "1.1.3.20" ~ "long-chain-alcohol oxidase",
-                                EC == "1.7.1.1" ~ "nitrate reductase (NADH)",
-                                EC == "2.3.1.87" ~ "aralkylamine N-acetyltransferase",
-                                EC == "1.3.8.1" ~ "short-chain acyl-CoA dehydrogenase",
-                                EC == "3.4.21.19" ~ "glutamyl endopeptidase",
-                                EC == "4.6.1.2" ~ "guanylate cyclase",
-                                EC == "1.7.7.2" ~ "ferredoxin-nitrate reductase",
-                                EC == "4.2.1.84" ~ "nitrile hydratase",
-                                EC == "1.10.3.3" ~ "L-ascorbate oxidase",
-                                EC == "3.2.1.80" ~ "fructan beta-fructosidase",
-                                EC == "2.3.1.37" ~ "5-aminolevulinate synthase",
-                                EC == "3.1.4.35" ~ "3',5'-cyclic-GMP phosphodiesterase",
-                                EC == "4.1.99.3" ~ "deoxyribodipyrimidine photo-lyase"))
+# LightEnzymesList <- LightEnzymes$EC
+# LightEnzymesMerged <- MetaData %>% 
+#   filter(Genus == "Prochlorococcus" | Taxa == "Diatom") %>% 
+#   left_join(., DataIn, by = c("FileName" = "genome")) %>% 
+#   filter(EC %in% LightEnzymesList) %>% 
+#   left_join(., LightEnzymes, by = c("EC"), relationship = "many-to-many") %>% 
+#   filter(Description != "KM Value") %>% 
+#   separate_rows(GOs, sep = ",") %>% 
+#   mutate(EnzymeName = case_when(EC == "1.3.1.33" ~ "(light-dependent) protochlorophyllide reductase",
+#                                 EC == "2.4.1.14" ~ "sucrose-phosphate synthase",
+#                                 EC == "2.5.1.32" ~ "15-cis-phytoene synthase",
+#                                 EC == "4.6.1.1" ~ "adenylate cyclase",
+#                                 EC == "4.4.1.5" ~ "lactoylglutathione lyase",
+#                                 EC == "4.2.3.5" ~ "chorismate synthase",
+#                                 EC == "2.7.1.148" ~ "4-(cytidine 5'-diphospho)-2-C-methyl-D-erythritol kinase",
+#                                 EC == "4.2.99.18" ~ "DNA-(apurinic or apyrimidinic site) lyase",
+#                                 EC == "3.4.11.1" ~ "leucyl aminopeptidase",
+#                                 EC == "2.4.1.255" ~ "protein O-GlcNAc transferase",
+#                                 EC == "3.1.4.4" ~ "phospholipase D",
+#                                 EC == "1.1.3.20" ~ "long-chain-alcohol oxidase",
+#                                 EC == "1.7.1.1" ~ "nitrate reductase (NADH)",
+#                                 EC == "2.3.1.87" ~ "aralkylamine N-acetyltransferase",
+#                                 EC == "1.3.8.1" ~ "short-chain acyl-CoA dehydrogenase",
+#                                 EC == "3.4.21.19" ~ "glutamyl endopeptidase",
+#                                 EC == "4.6.1.2" ~ "guanylate cyclase",
+#                                 EC == "1.7.7.2" ~ "ferredoxin-nitrate reductase",
+#                                 EC == "4.2.1.84" ~ "nitrile hydratase",
+#                                 EC == "1.10.3.3" ~ "L-ascorbate oxidase",
+#                                 EC == "3.2.1.80" ~ "fructan beta-fructosidase",
+#                                 EC == "2.3.1.37" ~ "5-aminolevulinate synthase",
+#                                 EC == "3.1.4.35" ~ "3',5'-cyclic-GMP phosphodiesterase",
+#                                 EC == "4.1.99.3" ~ "deoxyribodipyrimidine photolyase")) 
+# saveRDS(object = LightEnzymesMerged, file = file.path("..", "Data", "ProchlorococcusGenomeLightData.Rds"))
+#   
+```
 
+```{r read ProchlorococcusGenomeLightData}
+LightEnzymesMerged <- readRDS(file.path(DataIn, "ProchlorococcusGenomeLightData.Rds"))
 ```
@@
                                            )
-
 ProchlorococcusLightEnzymesFig <- LightEnzymesMerged %>% 
@@
   mutate(Compound = case_when(Compound == "blue-light regulator 2" ~ "light",
-                              TRUE ~ Compound)) %>% 
+                              Compound == "UVB-light" ~ "UV light",
+                              TRUE ~ Compound),
+         Description = case_when(Description == "Activating Compound" ~ "Activator",
+                                 TRUE ~ Description),) %>% 
   ggplot() +
@@
 
-  labs(x = "Enzyme Name",
+  labs(x = "Enzyme name",
        # y = "Organism",
-       size = "Gene Count",
-       color = "Gene Count") +
+       size = "Gene count",
+       color = "Gene count") +
   # scale_size_manual(values = c(1,2,3,4), breaks)
   theme_bw() +
-  ggpubr::rotate_x_text(hjust = 1, angle = 70) +
+  ggpubr::rotate_x_text(hjust = 1, angle = 80) +
   theme(axis.text = element_text(size = 7, color = "black"),
@@
         strip.text = element_text(size = 6),
-  legend.position = "bottom",
+  legend.position = "right",
   legend.key.size = unit(1, 'cm'),
@@
 ```{r, save ProchlorococcusLightEnzymesFig, ggsave, include = FALSE} 
-ggsave(filename = file.path(Figures, "ProchlorococcusLightEnzymesFig.png"), plot = ProchlorococcusLightEnzymesFig, height = 6, width = 8)
+ggsave(filename = file.path(Figures, "ProchlorococcusLightEnzymes.png"), plot = ProchlorococcusLightEnzymesFig, height = 5, width = 6)
+ggsave(filename = file.path(Figures, "S5_Fig.tiff"), plot = ProchlorococcusLightEnzymesFig, height = 5, width = 6, compression = "lzw")
 ```
-
-```{r}
-LightGOs <- MergedData %>% 
-  separate_rows(GOs, sep = ",") %>% 
-  filter(GOs %in% c("GO:0010018", "GO:0009785", "GO:0009882", "GO:0031516", "GO:0031517", "GO:0009883"))
-
-LightKOs <- MergedData %>% 
-  separate_rows(KEGG_ko, sep = ",") %>% 
-  filter(KEGG_ko %in% c("ko:K02295", "ko:K12120", "ko:K12122", "ko:K12121", "ko:K12123"))
-```
-
-```{r, fig.width = 7, fig.height = 7}
-MergedData %>%
-  filter(!is.na(Gene_count)) %>%
-  filter(PriSec == "Primary") %>%
-  filter(Genus == "Prochlorococcus") %>%
-  # filter(FileName == "Prochlorococcus_marinus_MIT9313-aa-gen"| FileName == "Prochlorococcus_marinus_pastoris_CCMP1986-aa-gen" | FileName == "Prochlorococcus_marinus_marinus_CCMP1375-aa-gen") %>%
-  # group_by(EC) %>%
-  # mutate(ECNumberTotal = sum(Gene_count)) %>%
-  # ungroup() %>% View()
-  # filter(ECNumberTotal != 0) %>%
-  ggplot() +
-  geom_point(aes(x = reorder(EnzymeName, Km_mM), y = FileName, size = Gene_count, color = log10(AvgKm_mM))) +
-  facet_grid(rows = vars(Genus), scales = "free", space = "free") +
-  scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
-  scale_x_discrete(position = "top") +
-  scale_radius(breaks = c(1,2,3,4,5), range = c(1,4)) +
-  theme_bw() +
-  ggpubr::rotate_x_text(hjust = 0) 
-```
-
-```{r, fig.width = 7, fig.height = 7}
-MergedData %>%
-  filter(!is.na(Gene_count)) %>%
-  filter(PriSec == "Primary") %>%
-  # filter(FileName == "Prochlorococcus_marinus_MIT9313-aa-gen"| FileName == "Prochlorococcus_marinus_pastoris_CCMP1986-aa-gen" | FileName == "Prochlorococcus_marinus_marinus_CCMP1375-aa-gen") %>%
-  # group_by(EC) %>%
-  # mutate(ECNumberTotal = sum(Gene_count)) %>%
-  # ungroup() %>% View()
-  # filter(ECNumberTotal != 0) %>%
-  ggplot() +
-  geom_point(aes(x = reorder(EnzymeName, Km_mM), y = FileName, size = Gene_count, color = log10(AvgKm_mM))) +
-  facet_grid(rows = vars(Genus), scales = "free", space = "free") +
-  scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
-  scale_x_discrete(position = "top") +
-  scale_radius(breaks = c(1,2,3,4,5), range = c(1,4)) +
-  theme_bw() +
-  ggpubr::rotate_x_text(hjust = 0) 
-```

### 2024-03-27 Code/Plots_Genome.Rmd
Update Plots_Genome.Rmd

@@
 Figures <- file.path("..", "Output", "Figures")
+PLOSFiguresRoundX <- file.path("..", "Output", "PLOSFiguresRound1")
 # BLAST <- file.path("..", "BLAST")
@@
 ```{r, ProchlorococcusEnzymeKms ggsave, include = FALSE} 
-ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms.png"), plot = ProchlorococcusEnzymeKms, height = 23, width = 20)
+ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms.png"), plot = ProchlorococcusEnzymeKms, height = 20, width = 17)
+ggsave(filename = file.path(PLOSFiguresRoundX, "Fig11.tiff"), plot = ProchlorococcusEnzymeKms, height = 20, width = 17, compression = "lzw")
 ```
@@
 ggsave(filename = file.path(Figures, "DNARepairFig.png"), plot = DNARepairFig, height =5 , width = 5)
-ggsave(filename = file.path(Figures, "Fig12.tiff"), plot = DNARepairFig, height =5 , width = 5, compression = "lzw")
+ggsave(filename = file.path(PLOSFiguresRoundX, "Fig12.tiff"), plot = DNARepairFig, height =5 , width = 5, compression = "lzw")
 ```
@@
 ggsave(filename = file.path(Figures, "ProchlorococcusLightEnzymes.png"), plot = ProchlorococcusLightEnzymesFig, height = 5, width = 6)
-ggsave(filename = file.path(Figures, "S5_Fig.tiff"), plot = ProchlorococcusLightEnzymesFig, height = 5, width = 6, compression = "lzw")
+ggsave(filename = file.path(PLOSFiguresRoundX, "S5_Fig.tiff"), plot = ProchlorococcusLightEnzymesFig, height = 5, width = 6, compression = "lzw")
 ```

### 2024-03-27 Code/Import_JazEmData.Rmd
tidied variable names

@@
   mutate(Filename = str_remove(Filename, pattern = " "))  %>% 
-  separate(col = Filename, into = c("ObsDate", "MultiCulti", "Par_ue", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE) %>% 
+  separate(col = Filename, into = c("ObsDate", "MultiCulti", "SetPar_uE", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE) %>% 
   mutate(FilenameJaz=Filename) %>% 
@@
 mutate(ObsDate = ymd(ObsDate),
-       Par_ue = as.numeric(Par_ue),
+       SetPar_uE = as.numeric(SetPar_uE),
        WL = as.factor(WL))
@@
 JazSpecTrim <- JazSpecTrim %>% 
-   group_by(MultiCulti, Par_ue, WL, Wavelength) %>%
+   group_by(MultiCulti, SetPar_uE, WL, Wavelength) %>%
   mutate(MCEm_nm = round(Wavelength)) %>%
   ungroup() %>%
-  group_by(FilenameJaz, MultiCulti, Par_ue, WL, MCEm_nm, EmMax_nm, ObsDate) %>%
+  group_by(FilenameJaz, MultiCulti, SetPar_uE, WL, MCEm_nm, EmMax_nm, ObsDate) %>%
   summarise(MeanEmission = mean(Counts)) %>%
@@
          MC = MultiCulti,
-         SetPar_uE = Par_ue,
          MC_SpectralID = paste(MC,WL, sep = "_")) %>% 

### 2024-03-27 Code/Import_JazEmData.Rmd
deleted variable name that no longer existed

@@
          MCMeasuredPar_uE = 'MeasuredPar_uE') %>% 
-  select(-c(Par_ue, MultiCulti, Date))
+  select(-c(MultiCulti, Date))
 

### 2024-03-27 Code/Manuscript_O2.Rmd
Changed path for knitted Word and html to "Output" folder

@@
     wrap: 72
+knit: (function(input, encoding) {
+  rmarkdown::render(input,
+                    output_dir = file.path('..', 'Output'),
+                    output_format = c("bookdown::word_document2", "bookdown::html_document2"),
+                    clean = TRUE)})
 ---

### 2024-03-27 Code/Manuscript_O2.Rmd
Changed table header alignment to remove tabs in header when knitted but it did not work

@@
                           "EC",
-                          "Kegg Orthology")
+                          "Kegg Orthology"),
+            align = "lll"
              )
@@
                           "Spectral waveband (nm)"),
-              align = "lccccc"
+              align = "llllll"
              )

### 2024-03-28 Code/Process_MCData.Rmd
Added code annotations

@@
 
-InitialTime <- 24 #hours to filter off start of data set to eliminate initial fluctuations common in SS120
+InitialTime <- 24 # hours to filter off start of data set to eliminate initial fluctuations common in SS120
 
-ReplaceOD <- 0.0001 #replace OD720 and/or deltaOD when log of original OD results in NAN or infinite #
+ReplaceOD <- 0.0001 # replace  OD720 and/or deltaOD when log of original deltaOD results in NAN or infinite #
 
-TruncFactor = 0.5 # fraction of max OD for truncating full growth trajectory to compare mu.
+TruncFactor = 0.5 # fraction of max OD for truncating full growth trajectory; used to compare mu.
 
-GrowthFlagError <- 0.20 # percentage of growth parameter is flagged as growth when std error is less than xx of mu.
+RollWindow = 20 # used to generate rolling averages: measurements every 5 min; 20 points is 1.67 h
 
-RollWindow = 20 #measurements every 5 min; 20 points is 1 h to generate rolling averages
+OD720GrowthFlagValue = 0.010 # OD720 absolute change for setting 'GrowthFlag' = 1 and 'DeclineFlag' = 1; did culture show  growth;
 
-OD720GrowthFlagValue = 0.010 # OD720 absolute change for setting GrowthFlag = 1 and DeclineFlag = 1; did culture show  growth;
-
-deltaODGrowthFlagValue = 0.007 #deltaOD absolute change for setting GrowthFlag = 1 and DeclineFlag = 1; did culture show  growth;
+deltaODGrowthFlagValue = 0.007 # deltaOD absolute change for setting 'GrowthFlag' = 1 and 'DeclineFlag' = 1; did culture show  growth;
 
@@
 
-DeclineWindow <- 12 #duration in hours overwhich we test for decline from max in OD720 or deltaOD
+DeclineWindow <- 12 # duration in hours overwhich we test for decline from max in OD720 or deltaOD
 
@@
 ```{r set colours}
-MyWavelengths = c(405, 450, 470, 530, 620, 660, 730, "WW")
-MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(450), w_length2rgb(470), w_length2rgb(530),            w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black"))
+
+MyWavelengths = c(405, 450, 470, 530, 620, 660, 730, "WW") # Multicultivator available wavelengths 
+MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(450), w_length2rgb(470), w_length2rgb(530),            w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black")) # set colors specific to wavelength using the'photobiologyWavebands' package
 
@@
 Run only first time in session
-
 ```{r previously processed files}
 list.files(path = DataOut, pattern = Project, full.names = TRUE)
-
 ```
@@
 
-Exported from runs of MultiDataImport.Rmd Run only first time in session
-
+Exported from runs of Import_MCData.Rmd. Run only first time in session
 ```{r list tidied data files}
@@
   filter(!is.nan(log(OD680))) %>%
-  mutate(#log of zero results in -infinite #'s. Replace with 0.0001. Replacing with 0 creates very low (10e-20) rollmeans which results in very high log normalized values further on in this chunk.
+  mutate(#log of zero results in -infinite #'s.
+Replace with 0.0001.
+Replacing with 0 creates very low (10e-20) rollmeans which results in very high log normalized values further on in this chunk.
+The following mutuate only replaces deltaOD if needed and not OD720 because deltaOD values may be very small at start of Multicultivator runs and may initially drift < 0 while OD720 remains > 0.
+Without replacing these negative deltaOD values, both OD720 and deltOD data points will be filtered out.
        deltaOD = if_else(!is.infinite(log(deltaOD)), deltaOD, ReplaceOD),
@@
          rollmeandeltaOD = zoo::rollmean(deltaOD, k = RollWindow, align = "left", fill = NA),
-         lognormOD720 = if_else(OD720 == (min(rollmeanOD720, na.rm = TRUE)), ReplaceOD, log(OD720/min(rollmeanOD720, na.rm = TRUE))),
-         lognormdeltaOD = if_else(deltaOD == (min(rollmeandeltaOD, na.rm = TRUE)), ReplaceOD, log(deltaOD/min(rollmeandeltaOD, na.rm = TRUE)))) %>%
+         lognormOD720 = if_else(OD720 == (min(rollmeanOD720, na.rm = TRUE)), ReplaceOD, 
+                                log(OD720/min(rollmeanOD720, na.rm = TRUE))),
+         lognormdeltaOD = if_else(deltaOD == (min(rollmeandeltaOD, na.rm = TRUE)), ReplaceOD, 
+                                  log(deltaOD/min(rollmeandeltaOD, na.rm = TRUE)))) %>%
   mutate(LagSeedOD720 = time[which.min(rollmeanOD720)],

### 2024-04-02 Code/Process_MCData.Rmd
Lined up code so that they were easier to read

@@
                             data = .x,
-                            start = list(Lmax = max(.$rollmeanOD720, na.rm = TRUE),  Lmu = (log(max(.$rollmeanOD720, na.rm = TRUE)) - log(min(.$rollmeanOD720, na.rm = TRUE)))/max(.$time), Lintercept = min(.$rollmeanOD720, na.rm = TRUE)),
+                            start = list(Lmax = max(.$rollmeanOD720, na.rm = TRUE),  
+                                         Lmu = (log(max(.$rollmeanOD720, na.rm = TRUE)) - log(min(.$rollmeanOD720, na.rm = TRUE)))/max(.$time),
+                                         Lintercept = min(.$rollmeanOD720, na.rm = TRUE)),
                             control = list(maxiter = 500)), otherwise = NULL)),
@@
                             filter(OD720 <= (max(OD720) * TruncFactor)),
-                            start = list(Lmax = max(.$rollmeanOD720, na.rm = TRUE),  Lmu = (log(max(.$rollmeanOD720, na.rm = TRUE)) - log(min(.$rollmeanOD720, na.rm = TRUE)))/max(.$time), Lintercept = min(.$rollmeanOD720, na.rm = TRUE)),
+                            start = list(Lmax = max(.$rollmeanOD720, na.rm = TRUE),
+                                         Lmu = (log(max(.$rollmeanOD720, na.rm = TRUE)) - log(min(.$rollmeanOD720, na.rm = TRUE)))/max(.$time),
+                                         Lintercept = min(.$rollmeanOD720, na.rm = TRUE)),
                             control = list(maxiter = 500)), otherwise = NULL)),
@@
                             data = .x,
-                            start = list(Lmax = max(.$rollmeandeltaOD, na.rm = TRUE),  Lmu = (log(max(.$rollmeandeltaOD, na.rm = TRUE)) - log(min(.$rollmeandeltaOD, na.rm =  TRUE)))/max(.$time), Lintercept = min(.$rollmeandeltaOD, na.rm = TRUE)),
+                            start = list(Lmax = max(.$rollmeandeltaOD, na.rm = TRUE),
+                                         Lmu = (log(max(.$rollmeandeltaOD, na.rm = TRUE)) - log(min(.$rollmeandeltaOD, na.rm =  TRUE)))/max(.$time),
+                                         Lintercept = min(.$rollmeandeltaOD, na.rm = TRUE)),
                             control = list(maxiter = 500)), otherwise = NULL)),
@@
                             filter(deltaOD <= (max(deltaOD) * TruncFactor)),
-                            start = list(Lmax = max(.$rollmeandeltaOD, na.rm = TRUE),  Lmu = (log(max(.$rollmeandeltaOD, na.rm = TRUE)) - log(min(.$rollmeandeltaOD, na.rm = TRUE)))/max(.$time), Lintercept = min(.$rollmeandeltaOD, na.rm = TRUE)),
+                            start = list(Lmax = max(.$rollmeandeltaOD, na.rm = TRUE),
+                                         Lmu = (log(max(.$rollmeandeltaOD, na.rm = TRUE)) - log(min(.$rollmeandeltaOD, na.rm = TRUE)))/max(.$time),
+                                         Lintercept = min(.$rollmeandeltaOD, na.rm = TRUE)),
                             control = list(maxiter = 500)), otherwise = NULL)),
@@
          ) %>%
-   mutate(GrowthAmpdeltaOD = if_else(deltaOD_TimetoMax <= MaxAmpHour | is.na(deltaOD_TimetoMax), map(tubedata, ~growth_amp_decline(y = .$rollmeandeltaOD)), map(tubedata, ~growth_amp(y = .$rollmeandeltaOD))),
-          GrowthAmpOD720 = if_else(OD720_TimetoMax <= MaxAmpHour | is.na(OD720_TimetoMax), map(tubedata, ~growth_amp_decline(y = .$rollmeanOD720)), map(tubedata, ~growth_amp(y = .$rollmeanOD720)))
+   mutate(GrowthAmpdeltaOD = if_else(deltaOD_TimetoMax <= MaxAmpHour | is.na(deltaOD_TimetoMax),
+                                     map(tubedata, ~growth_amp_decline(y = .$rollmeandeltaOD)),
+                                     map(tubedata, ~growth_amp(y = .$rollmeandeltaOD))),
+          GrowthAmpOD720 = if_else(OD720_TimetoMax <= MaxAmpHour | is.na(OD720_TimetoMax),
+                                   map(tubedata, ~growth_amp_decline(y = .$rollmeanOD720)),
+                                   map(tubedata, ~growth_amp(y = .$rollmeanOD720)))
          )
@@
                   ActinicMid_dayOD720,rollmeanOD720,rollmeandeltaOD,lognormOD720, lognormdeltaOD, LagSeedOD720, LagSeeddeltaOD)) %>%
-   mutate(GrowthAmpdeltaOD_14days = if_else(deltaOD_TimetoMax <= MaxAmpHour | is.na(deltaOD_TimetoMax), map(tubedata, ~growth_amp_decline(y = .$rollmeandeltaOD)), map(tubedata, ~growth_amp(y = .$rollmeandeltaOD))),
-          GrowthAmpOD720_14days = if_else(OD720_TimetoMax <= MaxAmpHour| is.na(OD720_TimetoMax) , map(tubedata, ~growth_amp_decline(y = .$rollmeanOD720)), map(tubedata, ~growth_amp(y = .$rollmeanOD720))),
+   mutate(GrowthAmpdeltaOD_14days = if_else(deltaOD_TimetoMax <= MaxAmpHour | is.na(deltaOD_TimetoMax),
+                                            map(tubedata, ~growth_amp_decline(y = .$rollmeandeltaOD)),
+                                            map(tubedata, ~growth_amp(y = .$rollmeandeltaOD))),
+          GrowthAmpOD720_14days = if_else(OD720_TimetoMax <= MaxAmpHour| is.na(OD720_TimetoMax),
+                                          map(tubedata, ~growth_amp_decline(y = .$rollmeanOD720)),
+                                          map(tubedata, ~growth_amp(y = .$rollmeanOD720))),
           minRollMeanOD720_14days = map(tubedata, ~min(.$rollmeanOD720, na.rm = TRUE)),

### 2024-04-03 Code/Merge_MCGrowthData.Rmd
Added missing data and reprocessed run #78. Regnerated GAM and plots
Fixed annotation for a variable

@@
 
-GrowthFlagError <- 0.2     # percentage of mu that std error must be less than
+GrowthFlagError <- 0.2     # What fraction of mu to determine if the growth fit is accepted relative to the std error.
 
@@
 
-# Save Long DF for GAM and Nested for further analysis 
+# Save Nested for further analysis 
 ```{r save files}

### 2024-04-03 Code/Plots_Growth.Rmd
Removed redundant chunks

@@
 
-# Make O2_uM and WL as factor levels from highest to lowest
-```{r O2 levels}
+# Make O2_uM and WL as factor levels from highest to lowest and calculate deltaOD growth per day
+```{r factor O2 levels and calc mu per day }
 
@@
          deltaOD_Lmu_se_day = deltaOD_Lmu_se * 24)
-#  Par_ue = factor(Par_ue, levels =  c(180, 120, 100,90,60, 30, 15))
+
 ```
 
-```{r set colours}
+```{r set WL colours }
 
@@
 MCMIXColours
-
-ColoursStrain = c(MIT9313 = "#E69F00", SS120 = "#F0E442", MED4 = "#CC79A7" )
-
-MyOxygen = c(2.5, 25, 250 )
-# O2Colours = c("#99CCFF", "dodgerblue", "blue1")
-O2Colours = c("#FFCC00", "#FF9900", "#663300")
-names(O2Colours) <- MyOxygen
-O2Colours
-
-MyOxygen = c(2.5, 25, 250 )
-O2LineType = c("dotted", "longdash", "solid")
-names(O2LineType) <- MyOxygen
-O2LineType
-
-MyPhotoperiods = as.factor(c(4, 8, 12, 16))
-ColoursPhotoperiod = c("gray88", "lightcyan3", "gray47", "gray8")
-names(ColoursPhotoperiod) <- MyPhotoperiods
-ColoursPhotoperiod
 
@@
 ```
-
-# Overlay whole cell absorbance with emission spectra
-```{r MED4 All Spectral Emission,  fig.height = 10, fig.width = 10}
-
-MED4OverlayPlots <- PURPARFits %>%
-  filter(Strain == "MED4",
-          Par_ue == 90,
-          O2_Category == "High" & WL == 450 & Photoperiod == 12 |
-          O2_Category == "High" & WL == 530 & Photoperiod == 16 |
-          O2_Category == "Intermediate" & WL == "WW" & Photoperiod == 16 |
-          O2_Category == "Intermediate" & WL == 660 & Photoperiod == 12) %>%
-  mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste("Growth", "waveband", "=", WL, "nm", sep = " "),
-        WL %in% c("WW") ~ paste("Growth", "waveband", "=", "White LED", sep = " "))) %>% 
-   unnest(cols = c(PurData), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_longer(cols = c(PurData_PURAbsWholeCell_Norm440, PurData_AbsNorm440,  PurData_MC_NormEm), values_to = "Abs_Em_Value", names_to = "Abs_Em_Names") %>%
-ggplot()+
-  geom_area(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, fill = as.factor(WL)), color = "black", 
-            size = 0.5, alpha = 0.7, show.legend = FALSE, 
-            data = . %>% filter(Abs_Em_Names == "PurData_PURAbsWholeCell_Norm440")) +
-  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = Abs_Em_Names,  linetype = Abs_Em_Names), size = 0.85) +
-  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = as.factor(WL),  linetype = Abs_Em_Names), size = 1.0, data = . %>% filter(Abs_Em_Names == "PurData_MC_NormEm")) +
-  scale_color_manual(values = c(MCMIXColours, "PurData_PURAbsWholeCell_Norm440" = "black", "PurData_AbsNorm440" = "darkorchid3", "PurData_MC_NormEm" = "white")) +
-  scale_linetype_manual(values = c("PurData_PURAbsWholeCell_Norm440" = "solid", "PurData_AbsNorm440" = "twodash",  "PurData_MC_NormEm" = "dotted"),
-                        labels = c("Whole cell abs.",  "LED emission", "PUR")) +
-  scale_fill_manual(values = MCMIXColours) +
- # guides(colour = FALSE) +
-  labs(y = "Normalized absorbance and emission", x = "Wavelength (nm)") +
-  labs(linetype = "Spectra type")+
-  scale_y_continuous(breaks=seq(0, 1.5, by = 0.25)) +
- # coord_cartesian(ylim = c (0, 0.2)) +
-   facet_wrap(vars(WL),
-              labeller = labeller(strain = label_value, WL = label_value, Photoperiod = label_both, Par_ue = label_both, O2_Category = label_both, Pur_ue = label_both)) +
-  geom_text(aes(x = 430, y = 1.1, label = WL_label, color = as.factor(WL)), show.legend = FALSE,
-    # parse = TRUE,
-    hjust = 0,
-    vjust = 1,
-    size = 5.0
-  )  +
-   geom_text(aes(x = 560, y = 0.95, label = paste("PAR", "=", Par_ue, sep = " "), show.legend = FALSE, ),
-    # parse = TRUE,
-    hjust = 0,
-    vjust = 1,
-    size = 5.0
-  )  +
-  geom_text(aes(x = 560, y = 0.85, label = paste("PUR", "=", Pur_ue,sep = " "), show.legend = FALSE, ),
-    # parse = TRUE,
-    hjust = 0,
-    vjust = 1,
-    size = 5.0
-  )  +
-  guides(color = "none") +
-  theme_bw() +
- theme(strip.text = element_blank(),
-       legend.background = element_rect(color = "transparent", fill = "transparent"),
-        legend.text = element_text(size = 18),
-        legend.title = element_text(size = 20),
-        # legend.position = c(0.94,0.96),
-        legend.position = "top",
-        axis.title = element_text(vjust = 1.0, size = 20),
-        # strip.text.x = element_text(size = 20),
-        axis.text = element_text(size = 15, color = "black"))
-
-MED4OverlayPlots <- tag_facet(MED4OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
-
-MED4OverlayPlots
-
-```
-
-```{r save MED4 PUR overlay plots}
-
-# ggsave(file = file.path(PlotsOut, paste("MED4OverlayPlots",".png",sep = "")), plot = MED4OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-```
-
-```{r MIT9313 All Spectral Emission,  fig.height = 10, fig.width = 10}
-
-MIT9313OverlayPlots <- PURPARFits %>%
-   filter(Strain == "MIT9313",
-          O2_Category == "High",
-          Par_ue == 30,
-          Photoperiod == 12 & WL == 450 |
-          Photoperiod == 12 & WL == 530 |
-          Photoperiod == 12 & WL == 660 |
-          Photoperiod == 16 & WL == "WW") %>% 
-  mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste("Growth", "wavelength", "=", WL, "nm", sep = " "),
-        WL %in% c("WW") ~ paste("Growth", "wavelength", "=", "White LED", sep = " "))) %>% 
-   unnest(cols = c(PurData), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_longer(cols = c(PurData_PURAbsWholeCell_Norm440, PurData_AbsNorm440,  PurData_MC_NormEm), values_to = "Abs_Em_Value", names_to = "Abs_Em_Names") %>%
-ggplot()+
-  geom_area(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, fill = as.factor(WL)), color = "black", 
-            size = 0.5, alpha = 0.7, show.legend = FALSE, 
-            data = . %>% filter(Abs_Em_Names == "PurData_PURAbsWholeCell_Norm440")) +
-  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = Abs_Em_Names,  linetype = Abs_Em_Names), size = 0.85) +
-  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = as.factor(WL),  linetype = Abs_Em_Names), size = 1.0, data = . %>% filter(Abs_Em_Names == "PurData_MC_NormEm")) +
-  scale_color_manual(values = c(MCMIXColours, "PurData_PURAbsWholeCell_Norm440" = "black", "PurData_AbsNorm440" = "darkorchid3", "PurData_MC_NormEm" = "white")) +
-  scale_linetype_manual(values = c("PurData_PURAbsWholeCell_Norm440" = "solid", "PurData_AbsNorm440" = "twodash",  "PurData_MC_NormEm" = "dotted"),
-                        labels = c("Whole cell abs.",  "LED emission", "PUR")) +
-  scale_fill_manual(values = MCMIXColours) +
- # guides(colour = FALSE) +
-  labs(y = "Normalized absorbance and emission", x = "Wavelength (nm)") +
-  labs(linetype = "Spectra type")+
-  scale_y_continuous(breaks=seq(0, 1.5, by = 0.25)) +
- # coord_cartesian(ylim = c (0, 0.2)) +
-   facet_wrap(vars(WL),
-              labeller = labeller(strain = label_value, WL = label_value, Photoperiod = label_both, Par_ue = label_both, O2_Category = label_both, Pur_ue = label_both)) +
-  geom_text(aes(x = 430, y = 1.1, label = WL_label, color = as.factor(WL)), show.legend = FALSE,
-    # parse = TRUE,
-    hjust = 0,
-    vjust = 1,
-    size = 5.0
-  )  +
-   geom_text(aes(x = 560, y = 0.95, label = paste("PAR", "=", Par_ue, sep = " "), show.legend = FALSE, ),
-    # parse = TRUE,
-    hjust = 0,
-    vjust = 1,
-    size = 5.0
-  )  +
-  geom_text(aes(x = 560, y = 0.85, label = paste("PUR", "=", Pur_ue,sep = " "), show.legend = FALSE, ),
-    # parse = TRUE,
-    hjust = 0,
-    vjust = 1,
-    size = 5.0
-  )  +
-  guides(color = "none") +
-  theme_bw() +
- theme(strip.text = element_blank(),
-       legend.background = element_rect(color = "transparent", fill = "transparent"),
-        legend.text = element_text(size = 18),
-        legend.title = element_text(size = 20),
-        # legend.position = c(0.94,0.96),
-        legend.position = "top",
-        axis.title = element_text(vjust = 1.0, size = 20),
-        # strip.text.x = element_text(size = 20),
-        axis.text = element_text(size = 15, color = "black"))
-
- MIT9313OverlayPlots <- tag_facet(MIT9313OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
-
- MIT9313OverlayPlots
-```
-
-```{r save MIT9313 PUR overlay plots}
-
-# ggsave(file = file.path(PlotsOut, paste("MIT9313OverlayPlots",".png",sep = "")), plot = MIT9313OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-```
-
-```{r SS120 PUR overlay with legend,  fig.height = 10, fig.width = 10}
-
- SS120OverlayPlots <- PURPARFits %>%
-   filter(Strain == "SS120",
-          O2_Category == "High",
-          Par_ue == 30,
-          Photoperiod == 8 |
-          Photoperiod == 12 & WL == 530,
-          Run != 113 & Run != 112) %>%
-  mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste("Growth", "wavelength", "=", WL, "nm", sep = " "),
-        WL %in% c("WW") ~ paste("Growth", "wavelength", "=", "White LED", sep = " "))) %>% 
-   unnest(cols = c(PurData), names_sep = "_", keep_empty = TRUE) %>%
-  pivot_longer(cols = c(PurData_PURAbsWholeCell_Norm440, PurData_AbsNorm440,  PurData_MC_NormEm), values_to = "Abs_Em_Value", names_to = "Abs_Em_Names") %>%
-ggplot()+
-  geom_area(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, fill = as.factor(WL)), color = "black", 
-            size = 0.5, alpha = 0.7, show.legend = FALSE, 
-            data = . %>% filter(Abs_Em_Names == "PurData_PURAbsWholeCell_Norm440")) +
-  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = Abs_Em_Names,  linetype = Abs_Em_Names), size = 0.85) +
-  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = as.factor(WL),  linetype = Abs_Em_Names), size = 1.0, data = . %>% filter(Abs_Em_Names == "PurData_MC_NormEm")) +
-  scale_color_manual(values = c(MCMIXColours, "PurData_PURAbsWholeCell_Norm440" = "black", "PurData_AbsNorm440" = "darkorchid3", "PurData_MC_NormEm" = "white")) +
- scale_linetype_manual(values = c("PurData_PURAbsWholeCell_Norm440" = "solid", "PurData_AbsNorm440" = "twodash",  "PurData_MC_NormEm" = "dotted"),
-                        labels = c("Whole cell abs.",  "LED emission", "PUR")) +
-  scale_fill_manual(values = MCMIXColours) +
- # guides(colour = FALSE) +
-  labs(y = "Normalized absorbance and emission", x = "Wavelength (nm)") +
-  labs(linetype = "Spectra type")+
-  scale_y_continuous(breaks=seq(0, 1.5, by = 0.25)) +
- # coord_cartesian(ylim = c (0, 0.2)) +
-   facet_wrap(vars(WL),
-              labeller = labeller(strain = label_value, WL = label_value, Photoperiod = label_both, Par_ue = label_both, O2_Category = label_both, Pur_ue = label_both))+
-  geom_text(aes(x = 430, y = 1.1, label = WL_label, color = as.factor(WL)), show.legend = FALSE,
-    # parse = TRUE,
-    hjust = 0,
-    vjust = 1,
-    size = 5.0
-  )  +
-   geom_text(aes(x = 560, y = 0.95, label = paste("PAR", "=", Par_ue, sep = " "), show.legend = FALSE, ),
-    # parse = TRUE,
-    hjust = 0,
-    vjust = 1,
-    size = 5.0
-  )  +
-  geom_text(aes(x = 560, y = 0.85, label = paste("PUR", "=", Pur_ue,sep = " "), show.legend = FALSE, ),
-    # parse = TRUE,
-    hjust = 0,
-    vjust = 1,
-    size = 5.0
-  )  +
-  guides(color = "none") +
-  theme_bw() +
- theme(strip.text = element_blank(),
-       legend.background = element_rect(color = "transparent", fill = "transparent"),
-        legend.text = element_text(size = 18),
-        legend.title = element_text(size = 20),
-        # legend.position = c(0.94,0.96),
-        legend.position = "top",
-        axis.title = element_text(vjust = 1.0, size = 20),
-        # strip.text.x = element_text(size = 20),
-        axis.text = element_text(size = 15, color = "black"))
-
- SS120OverlayPlots <- tag_facet(SS120OverlayPlots, open = "", close = "", tag_pool = LETTERS, size = 8)
-
- SS120OverlayPlots
-
-```
-
-```{r save SS120 PUR overlay plots}
-
-# ggsave(file = file.path(PlotsOut, paste("SS120OverlayPlots",".png",sep = "")), plot = SS120OverlayPlots, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-```

### 2024-04-04 Code/Plots_Genome.Rmd
Corrected missing y axis

@@
          Genus == "Prochlorococcus",
+         # Strain %in% c("CCMP1986", "MIT9313"),
          Strain %in% c("CCMP1375", "CCMP1986", "MIT9313", "NATL2A"),
@@
          axis.title.x = element_text(vjust=8),
-         axis.title.y = element_blank(),
+         # axis.title.y = element_blank(),
          title = element_text(size = 30),
@@
 ```{r, ProchlorococcusEnzymeKms ggsave, include = FALSE} 
-ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms.png"), plot = ProchlorococcusEnzymeKms, height = 20, width = 17)
+ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms.png"), plot = ProchlorococcusEnzymeKms, height = 23, width = 17)
 ggsave(filename = file.path(PLOSFiguresRoundX, "Fig11.tiff"), plot = ProchlorococcusEnzymeKms, height = 20, width = 17, compression = "lzw")
+# ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms_julie.png"), plot = ProchlorococcusEnzymeKms, height = 23, width = 17)
 ```

### 2024-04-10 Code/Plots_PURFits.Rmd
Fixed some annotations
annotated chunks and removed redundant variables

@@
 Make O2_uM and WL as factor levels from highest to lowest and remove all green light (WL= 530) growth data
-```{r O2 levels}
+```{r factor O2 WL and photoperiod}
 
@@
 # model with dummy dark, 0 PAR,  growth rates.
-Also removed data if no growth occurred for an O2 and photoperiod combination so that the model including all photoperiods would not be skewed towards zero.
+Nested by strain and [O2].
+Filtered out data if no growth occurred for an O2 and photoperiod combination for each strain so that the model including all photoperiods would not be skewed towards zero.
 PURPARStrainO2NestModels_filtered <- PURPARFits_dummy |>
@@
 
-# PURPARStrainO2NestModels <- PURPARFits_dummy |>
-#   nest(data = -c("Strain","O2_uM")) |>
-#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
-#                               data = .x,
-#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1), 
-#                               lower = c(0, 0, 0),
-#                               upper = c(1,1,100),
-#                               control = list(maxiter = 500)
-#                          ), NULL)
-#                          )
-#          ) |>
-#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
-#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
-#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
-#          ) |>
-#   mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
-#                               data = .x,
-#                               start = LinEqnStart
-#                          ), NULL)
-#                          )
-#          ) |>
-#   mutate(GRClm_Param = map(GRClm_Model, tidy),
-#          GRClm_Predict = map(GRClm_Model, possibly(augment)),
-#          GRClm_Glance = map(GRClm_Model, possibly(glance))
-#          )
-
-# # model with dummy dark, 0 PAR, 0 growth rates
-# PURPARStrainO2PhotoNestModels <- PURPARFits_dummy  |>
-#  nest(data = -c("Strain","O2_uM", "Photoperiod")) |>
-#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
-#                               data = .x,
-#                               start = list(a = 1e-8, b = 1e-9, Pmax = 1),
-#                               lower = c(-0, 0, 0),
-#                               upper = c(1,1,100),
-#                               control = list(maxiter = 500)
-#                          ), NULL)
-#                          )
-#          ) |>
-#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
-#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
-#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
-#          ) |>
-#   mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
-#                               data = .x,
-#                               start = LinEqnStart
-#                          ), NULL)
-#                          )
-#          ) |>
-#   mutate(GRClm_Param = map(GRClm_Model, tidy),
-#          GRClm_Predict = map(GRClm_Model, possibly(augment)),
-#          GRClm_Glance = map(GRClm_Model, possibly(glance))
-#          )
-
+# model with dummy dark, 0 PAR,  growth rates. Nested by strain, [O2] and photoperiod.
 PURPARStrainO2PhotoNestModels <- PURPARFits_dummy |>
@@
 
-# model with dummy dark, 0 PAR,  growth rates
+# model with dummy dark, 0 PAR,  growth rates. Nested by strain, [O2] and wavelength.
 PURPARStrainO2WLNestModels <- PURPARFits_dummy |>
@@
 
-# 
-# # model with dummy dark, 0 PAR,  growth rates
+# # model with dummy dark, 0 PAR,  growth rates. Nested by strain, [O2], photoperiod and wavelength. NOTE: not enough data to model fits for this combination.
 # PURPARStrainO2PeriodWLNest <- PURPARFits_dummy |>
@@
 
-# Want platt model for all fits that did not fail and lm for platt models that returned a NULL
+# Want platt model for all fits that did not fail and lm for platt models that returned a NULL. NULLs were returned due to no growth across strain, O2 and photoperiod conditions.
 ```{r}
@@
 # Join  
-StrainO2Photoperiod_AllModels <- full_join(KeepPlattModel, KeepLmModel)
+ StrainO2Photoperiod_PlattLmModel <- full_join(KeepPlattModel, KeepLmModel)
 
@@
 # O2 and Photoperiod nested data frame containing the fits for each photoperiod for each strain
- StrainO2Photoperiod_PlattLmModel <- StrainO2Photoperiod_AllModels |>
+ StrainO2Photoperiod_PlattLmModel <-  StrainO2Photoperiod_PlattLmModel |>
    pivot_longer(cols = -c(Strain, O2_uM, Photoperiod, data)) |>
@@
 # Join  
-StrainO2_AllModels <- full_join(KeepPlattModel, KeepLmModel)
+StrainO2filtered_PlattLmModel <- full_join(KeepPlattModel, KeepLmModel)
 
 # O2 nested data frame containing the single fit of pooled photoperiods 
- StrainO2filtered_PlattLmModel <- StrainO2_AllModels|>
+ StrainO2filtered_PlattLmModel <- StrainO2filtered_PlattLmModel|>
   # select(-c(data)) |>
@@
  remove(KeepLmModel)
- # remove(StrainO2Photoperiod_AllModels)
- # remove(StrainO2_AllModels)
 
@@
   facet_grid(rows = vars(O2_uM), cols = vars(Strain)) +
-    labs(title = "Single fit for each strain in each [O2]- all photoperiods included that had growth") +
+    labs(title = "Single fit and model indicated.
+Data omitted that showed complete growth \n inhibition for each combination of strain, [O2] and photoperiod except when \n complete inhibition occurred for a combination of strain and [O2].") +
   theme_bw()
@@
   facet_grid(rows = vars(O2_uM, Photoperiod), cols = vars(Strain)) +
-    labs(title = "Fits to be used for ANOVA comparison to single fit across each strain and [O2]") +
+    labs(title = "Photoperiod fits to be used for ANOVA comparison to single fit across each \n strain and [O2].") +
   theme_bw()
@@
 
-# Wider_Photoperiods <- StrainO2Photoperiod_PlattLmModel %>% 
-#   mutate(PhotoperiodLabel = Photoperiod) %>% 
-#   select(Strain, Photoperiod, O2_uM, Model, Predict, data, PhotoperiodLabel) %>% 
-#   pivot_wider(names_from = PhotoperiodLabel, values_from = c(Model, Predict)) %>% 
-#     unnest(data) %>% 
-#   group_by(Strain, O2_uM) %>% 
-#     nest(Data_Photoperiod = -c(Strain, O2_uM, Model_16,Model_12, Model_8, Model_4, Predict_16, Predict_12, Predict_8, Predict_4)) %>% 
-#   filter(!is.null(Model_16) & !is.null(Predict_16) |
-#            !is.null(Model_12) & !is.null(Predict_12)|
-#            !is.null(Model_8) & !is.null(Predict_8) |
-#            !is.null(Model_4) & !is.null(Predict_4))
-
-# Wider_Photoperiods <- StrainO2Photoperiod_PlattLmModel %>% 
-#   select(Strain, Photoperiod, O2_uM, Model, Predict) %>% 
-#   pivot_wider(names_from = Photoperiod, values_from = c(Model, Predict)) %>% 
-#   unnest(Predict_16, keep_empty = TRUE) %>% 
-#     mutate(Photoperiod = 16)%>% 
-#     nest(Predict_16 = -c(Strain, O2_uM, Model_16, Model_12, Model_8, Model_4, Predict_12, Predict_8, Predict_4)) %>% 
-#   unnest(Predict_12, keep_empty = TRUE) %>% 
-#     mutate(Photoperiod = 12)%>% 
-#     nest(Predict_12 = -c(Strain, O2_uM, Model_16, Model_12, Model_8, Model_4, Predict_16, Predict_8, Predict_4))%>% 
-#   unnest(Predict_8, keep_empty = TRUE) %>% 
-#     mutate(Photoperiod = 8)%>% 
-#     nest(Predict_8 = -c(Strain, O2_uM, Model_16, Model_12, Model_8, Model_4, Predict_16, Predict_12, Predict_4))%>% 
-#   unnest(Predict_4, keep_empty = TRUE) %>% 
-#     mutate(Photoperiod = 4)%>% 
-#     nest(Predict_4 = -c(Strain, O2_uM, Model_16, Model_12, Model_8, Model_4, Predict_16, Predict_12, Predict_8))
-
-# this contains 1 fit through all photoperiods, the photoperiods with no growth were filtered out.
+# this contains 1 fit through all photoperiods for each strain and [O2] combination.
+Data omitted that showed complete growth inhibition for each combination of strain, [O2] and photoperiod except when complete inhibition occurred for a combination of strain and [O2].
 AllPhotoperiods <- StrainO2filtered_PlattLmModel %>% 
@@
 
-# Fits are added that are not sig different individually,  next add fits that were sig different dynamically
+# Individual fits are added that are sig different from the pooled photoperiod fit. 
+Better way to do this is dynamically using p values from the ANOVA. 
 ```{r Pur plot strain faceted in columns, fig.height=10, fig.width=10}
@@
 
-Need test, other than nesting, to determine if Photoperiod has a significant influence (and interaction) on growth rate?
-
-GrowthRate function of PUR, 
-  separate models for Strain & O2_uM,
-
-GrowthRate function of PUR in interaction term with Photoperiod and/or light colour
-  separate models for Strain & O2_uM,
-
 ```{r, save PURFitPlots}
@@
 
-# model with dummy dark, 0 PAR,  growth rates.
-Also removed data if no growth occurred for an O2 and photoperiod combination so that the model including all photoperiods would not be skewed towards zero.
-StrainO2NestModels <- PURPARFits_dummy |>
+# model with dummy dark, 0 PAR,  growth rates. Nested by strain and [O2]. 
+PURPARStrainO2NestModels <- PURPARFits_dummy |>
   nest(data = -c("Strain","O2_uM")) |>
@@
 
-StrainO2NestModels <- full_join(StrainO2NestModels, AllData)
-
-# model with dummy dark, 0 PAR,  growth rates
-PURPARStrainO2WLNestModels <- PURPARFits_dummy |>
-  nest(data = -c("Strain","O2_uM", "WL")) |>
-  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
-                              data = .x,
-                              start = list(a = 1e-7, b = 1e-8, Pmax = 1),
-                              lower = c(0, 0, 0),
-                              upper = c(1,1,100),
-                              control = list(maxiter = 500)
-                         ), NULL)
-                         )
-         ) |>
-  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
-         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
-         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
-         )|>
-  mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
-                              data = .x,
-                              start = LinEqnStart
-                         ), NULL)
-                         )
-         ) |>
-  mutate(GRClm_Param = map(GRClm_Model, tidy),
-         GRClm_Predict = map(GRClm_Model, possibly(augment)),
-         GRClm_Glance = map(GRClm_Model, possibly(glance))
-         )
+PURPARStrainO2NestModels <- full_join(PURPARStrainO2NestModels, AllData)
 
@@
 # Join  
-StrainO2WL_AllModels <- bind_rows(KeepPlattModel, KeepLmModel)
+ StrainO2WL_PlattLmModel <- bind_rows(KeepPlattModel, KeepLmModel)
 
@@
 # O2 and WL nested data frame containing the fits for each WL for each strain
- StrainO2WL_PlattLmModel <- StrainO2WL_AllModels |>
+ StrainO2WL_PlattLmModel <-  StrainO2WL_PlattLmModel |>
    pivot_longer(cols = -c(Strain, O2_uM, WL, data)) |>
@@
  #filter to keep platt models
-KeepPlattModel <- StrainO2NestModels|>
+KeepPlattModel <- PURPARStrainO2NestModels|>
   select(-c(GRClm_Glance, GRClm_Model, GRClm_Param, GRClm_Predict)) |>
@@
 #filter to keep only the models that failed to fit a platt model, fits by lm remains. 
-KeepLmModel <- StrainO2NestModels|>
+KeepLmModel <- PURPARStrainO2NestModels|>
   filter(map_lgl(GRCplatt_Model, is.null)) |>
@@
 # Join  
-StrainO2_AllModels <- full_join(KeepPlattModel, KeepLmModel)
+StrainO2_PlattLmModel <- full_join(KeepPlattModel, KeepLmModel)
 
 # O2 nested data frame containing the single fit of pooled WLs 
- StrainO2_PlattLmModel <- StrainO2_AllModels|>
+ StrainO2_PlattLmModel <- StrainO2_PlattLmModel|>
   # select(-c(data)) |>
@@
  remove(KeepLmModel)
- # remove(StrainO2WL_AllModels)
- # remove(StrainO2_AllModels)
 
@@
   facet_grid(rows = vars(O2_uM, WL), cols = vars(Strain)) +
-    labs(title = "Fits to be used for ANOVA comparison to single fit across each strain and [O2]") +
+    labs(title = "Fits across wavelengths used for one-way ANOVA comparison to eachother for each strain and [O2] combination") +
   theme_bw()
@@
 
-# ANOVA comparison of red light to blue light for each strain and [O2]. 
+# ANOVA comparison of red light to blue light for each strain and [O2] combination. 
 ```{r compare 1 red and blue light fits}

### 2024-04-11 Code/Plots_PURFits.Rmd
more edits
Removed redundant code and fixed linetype through WL and Photoperiod legend

@@
 
-# # model with dummy dark, 0 PAR,  growth rates. Nested by strain, [O2], photoperiod and wavelength. NOTE: not enough data to model fits for this combination.
-# PURPARStrainO2PeriodWLNest <- PURPARFits_dummy |>
-#   nest(data = -c("Strain","O2_uM", "Photoperiod", "WL")) |>
-#   mutate(GRCplatt_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ grcplatt(I = PURPhotonDose_day, a, b, Pmax),
-#                               data = .x,
-#                               start = list(a = 1e-7, b = 1e-8, Pmax = 1),
-#                               lower = c(0, 0, 0),
-#                               upper = c(1,1,100),
-#                               control = list(maxiter = 500)
-#                          ), NULL)
-#                          )
-#          ) |>
-#   mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
-#          GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
-#          GRCplatt_Glance = map(GRCplatt_Model, possibly(glance))
-#          )|>
-#   mutate(GRClm_Model = map(data, possibly(~nlsLM(deltaOD_Lmu_corr_day ~ LinEqn(x = PURPhotonDose_day,  M, Intercept),
-#                               data = .x,
-#                               start = LinEqnStart
-#                          ), NULL)
-#                          )
-#          ) |>
-#   mutate(GRClm_Param = map(GRClm_Model, tidy),
-#          GRClm_Predict = map(GRClm_Model, possibly(augment)),
-#          GRClm_Glance = map(GRClm_Model, possibly(glance))
-#          )
 remove(AllData)
@@
   geom_point(aes(x = PURPhotonDose_day, y = deltaOD_Lmu_corr_day, colour = WL)) +
-  # geom_line(aes(x = PURPhotonDose_day, y = `.fitted`)) +
      scale_colour_manual(values = MCMIXColours) +
@@
  StrainO2filtered_PlattLmModel <- StrainO2filtered_PlattLmModel|>
-  # select(-c(data)) |>
   pivot_longer(cols = -c(Strain, O2_uM, data, Data_all)) |>
@@
  remove(KeepLmModel)
+ remove(PURPARStrainO2NestModels_filtered)
+ remove(PURPARStrainO2PhotoNestModels)
 
@@
 
-AllFitsCombined <- left_join(Wider_Photoperiods, AllPhotoperiods)
-
-ANOVA_AllPhotoperiods <- AllFitsCombined %>% 
+AllFitsCombinedPhoto <- left_join(Wider_Photoperiods, AllPhotoperiods)
+
+ANOVA_AllPhotoperiods <- AllFitsCombinedPhoto %>% 
   mutate(twelve = `Model_12`,
@@
 
-# %>% 
-#   mutate(p.value = case_when(is.na(p.value) ~ 0,
-#                              TRUE ~ p.value)) # Changed all failed fits to p.value = 0
-  # mutate(pval = pluck(value, "p.value", 2))
-
 ANOVA_AllPhotoperiods %>% 
@@
          Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>%
-    # mutate(Photoperiod1 = factor(Photoperiod1, levels = c('four','eight', 'twelve', 'sixteen'))) %>% 
   ggplot() +
@@
 remove(AllPhotoperiods)
+remove(StrainO2filtered_PlattLmModel)
+remove(StrainO2Photoperiod_PlattLmModel)
 
@@
 
-PhotoperiodPurFitsPlots <- AllFitsCombined |>
+PhotoperiodPurFitsPlots <- AllFitsCombinedPhoto |>
   unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
@@
         fill = "none",) +
-        #color = guide_legend(nrow = 1)) +
- # guides(shape = guide_legend(nrow = 1)) +
   theme_bw() +
@@
         axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
-        # strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"), 
         legend.key.size = unit(1.8, 'cm'), #change legend key size
@@
 remove(AllData)
+remove(PURPARFits_dummy)
 
@@
  StrainO2_PlattLmModel <- StrainO2_PlattLmModel|>
-  # select(-c(data)) |>
   pivot_longer(cols = -c(Strain, O2_uM, data, Data_all)) |>
@@
  remove(KeepLmModel)
+ remove(PURPARStrainO2NestModels)
+ remove(PURPARStrainO2WLNestModels)
 
@@
   facet_grid(rows = vars(O2_uM, WL), cols = vars(Strain)) +
-    labs(title = "Fits across wavelengths used for one-way ANOVA comparison to eachother for each strain and [O2] combination") +
+    labs(title = "Fits across wavelengths used for one-way ANOVA comparison \n to eachother for each strain and [O2] combination") +
   theme_bw()
@@
 
-# %>% 
-#   mutate(p.value = case_when(is.na(p.value) ~ 0,
-#                              TRUE ~ p.value)) # Changed all failed fits to p.value = 0
-  # mutate(pval = pluck(value, "p.value", 2))
-
 ANOVA_AllWL %>% 
@@
 remove(AllWL)
-
+remove(StrainO2_PlattLmModel)
+remove(StrainO2WL_PlattLmModel)
 ```
@@
   geom_line(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(WL)), size = 1, show.legend = T) +
-# geom_line(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(Photoperiod)), size = 1, show.legend = F) +
-# geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(Data_all_WL)), size = 1, show.legend = F) +
   geom_rect(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, fill = "white") +
@@
   scale_y_continuous(breaks = c(0,0.25, 0.5, 0.75, 1.0), limits = c (0, 1.05)) +
+  scale_linetype_manual(values = c("solid", "dashed"), labels = c(italic("P") ~ "value <0.05", italic("P") ~ "value >0.05")) +
   scale_colour_manual(values = MCMIXColours, labels = c("660 nm", "450 nm")) +
-  scale_linetype_manual(values = c("solid", "dashed"), labels = c(italic("P") ~ "value <0.05", italic("P") ~ "value >0.05")) +
   scale_shape_manual(values = PhotoperiodShapes, labels = c("16 h", "12 h", "8 h", "4 h"))  +
@@
    linetype = guide_legend(order = 1),
-        fill = "none") +
- #        color = guide_legend(nrow = 1)) +
- # guides(shape = guide_legend(nrow = 1)) +
+         fill = "none",
+         shape = guide_legend(override.aes = list(linetype = 0)),
+         color = guide_legend(override.aes = list(linetype = 0))) +
   theme_bw()  +
@@
 knitr::kable(WLAnovaTable,
-             caption = "pvalues for each ANOVA comparison of fit of red and blue light in each O~2~ experiment for each strain.",
+             caption = "p values for each ANOVA comparison of fit of red and blue light in each O~2~ experiment for each strain.",
             col.names =  c("Strain",

### 2024-05-12 Code/Process_OlisJazEmData.Rmd
Fixed duplication of data

--- 2024-01-18 Code/Process_OlisJazEmData.Rmd
@@
 
-# Left join Olis whole cell absorbance data with Jaz MC emission data. Emission measurements were performed on the mixed color MCMIX004 and the white light MC257
+# Left join Olis whole cell absorbance data with Jaz MC emission data. Emission measurements were performed on the mixed color MCMIX004 and the white light MC257 Multicultivators
 ```{r join whole cell absorbance with MC emission data}
@@
 OlisJazMetaData <- OlisJazMetaData %>% 
+  filter(E_days != 1) %>%  # remove absorbance spectra data collected during lag phase
   group_by(SampleID, E_days) %>%

### 2024-05-15 Code/Manuscript_O2.Rmd
annotated chunks and removed redundant variables
Fixed formatting for PLOSONE Fig caption

@@
 Controlled growth experiments were performed using MCMIX-OD or MC1000-OD
-PSI Multicultivators (Fig. \@ref(fig:LabeledMC); PSI, Drásov, Czech
+PSI Multicultivators (Fig \@ref(fig:LabeledMC); PSI, Drásov, Czech
 Republic). Each multicultivator individually controls 8 tubes at a
@@
 
-Fig. \@ref(fig:deltaODLogGrowthPlot) is an example of chlorophyll
+Fig \@ref(fig:deltaODLogGrowthPlot) is an example of chlorophyll
 specific growth estimates fitted from the high resolution ΔOD
@@
 \@ref(eq:WeightedPUR) and PAR is the imposed peak light level (µmol
-photons m^-2^ s^-1^). Fig. (\@ref(fig:PurParPlot)) shows the
+photons m^-2^ s^-1^). Fig (\@ref(fig:PurParPlot)) shows the
 calculated peak PUR (µmol photons m^-2^ d^-1^) vs. imposed
@@
 
-Fig. \@ref(fig:OverlayPlots) provide visual representations of PUR,
+Fig \@ref(fig:OverlayPlots) provide visual representations of PUR,
 the black solid line and shaded area, in relation to the imposed PAR,
 the dotted line, under each imposed spectral wavebands for *P. marinus*
-MED4 (A-C), SS120 (D-F) and MIT9313 (G-I). Fig.
-(\@ref(fig:PurParPlot)) shows the relationship between calculated PUR
+MED4 (A-C), SS120 (D-F) and MIT9313 (G-I). Fig (\@ref(fig:PurParPlot)) shows the relationship between calculated PUR
 vs. imposed PAR for each *P. marinus* and each spectral waveband.
@@
 Photoperiod growth data that showed complete growth inhibition for each
-combination of strain, [O~2~] and imposed spectral waveband were omitted
-from the pooled photoperiod model. Statistical differences were
+combination of strain, [O~2~] and imposed spectral waveband were omitted from the pooled photoperiod model. Statistical differences were
 determined at *P* value \< 0.05.
@@
 
-```{r PurParPlot, fig.cap = PurParPlot_cap , fig.height = 20, fig.width = 10, echo = FALSE}
+```{r PurParPlot, fig.cap = PurParPlot_cap, fig.height = 20, fig.width = 10, echo = FALSE}
 
@@
 analyzed. We focused our analysis here on core photosynthetic protein
-complexes, for clades HL, LLI, LLII/III and LLIV (Fig.
-\@ref(fig:CladeProchloroPhotosynthDepthO2)) as a function of depth (a
+complexes, for clades HL, LLI, LLII/III and LLIV (Fig \@ref(fig:CladeProchloroPhotosynthDepthO2)) as a function of depth (a
 proxy for light intensity) and measured [O~2~]. Photosynthetic complexes
@@
 *Prochlorococcus marinus* MED4, clade HLI, growth under 250 µM O~2~
-increased with higher imposed PAR and longer photoperiods (Fig.
-\@ref(fig:MED4PAR)), across all spectral wavebands. No growth was
+increased with higher imposed PAR and longer photoperiods (Fig \@ref(fig:MED4PAR)), across all spectral wavebands. No growth was
 observed under any imposed conditions under a 4 h photoperiod. The
@@
 O~2~ showed fastest growth when the photoperiod was 16 h for each
-spectral waveband, across PAR levels (Fig. \@ref(fig:MED4PAR)). The
+spectral waveband, across PAR levels (Fig \@ref(fig:MED4PAR)). The
 µ~max~ was
@@
 
-MED4 did not grow when sparged to the lowest [O~2~] of 2.5 µM (Fig.
-\@ref(fig:MED4PAR)). 2.5 µM O~2~ growth experiments were not conducted
+MED4 did not grow when sparged to the lowest [O~2~] of 2.5 µM (Fig \@ref(fig:MED4PAR)). 2.5 µM O~2~ growth experiments were not conducted
 for 4 and 16 h photoperiods, as no reproducible growth occurred when
@@
 
-The GAM model in Fig. \@ref(fig:MED4GAM) summarizes MED4 growth
+The GAM model in Fig \@ref(fig:MED4GAM) summarizes MED4 growth
 responses to red (A and B) or blue (C and D) peak PAR and photoperiod across 2
@@
 line representing the 90^th^ percentile of maximum achieved growth rate
-(Fig. \@ref(fig:MED4GAM)C). Growth decreased with decreasing
+(Fig \@ref(fig:MED4GAM)C). Growth decreased with decreasing
 photoperiod and decreasing peak PAR. Under red light growth was
 generally slower but the pattern of growth responses to photoperiod and
-PAR was similar (Fig. \@ref(fig:MED4GAM)A). Note the exclusion of MED4
-from growth under 4 h photoperiod under both red and blue light (Fig.
-\@ref(fig:MED4GAM)). Under 25 µM O~2~ MED4 showed similar growth
+PAR was similar (Fig \@ref(fig:MED4GAM)A). Note the exclusion of MED4
+from growth under 4 h photoperiod under both red and blue light (Fig \@ref(fig:MED4GAM)). Under 25 µM O~2~ MED4 showed similar growth
 responses, but was excluded from both 4 and 8 h photoperiods. MED4 did
@@
 increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^
-peak PAR and across all spectral wavebands (Fig. \@ref(fig:SS120PAR)).
+peak PAR and across all spectral wavebands (Fig \@ref(fig:SS120PAR)).
 No growth was observed under any blue light photoperiods when exposed to
@@
 photoperiod for red spectral waveband, however under blue light, SS120
-was able to grow (Fig. \@ref(fig:SS120PAR)). In contrast to the growth
+was able to grow (Fig \@ref(fig:SS120PAR)). In contrast to the growth
 trends of the 250 µM O~2~ and PAR of 90 µmol photons m^-2^ s^-1^
@@
 SS120 did not reproducibly grow when sparged to the lowest O~2~ of 2.5
-µM (Fig. \@ref(fig:SS120PAR)). 2.5 µM O~2~ growth experiments were not
+µM (Fig \@ref(fig:SS120PAR)). 2.5 µM O~2~ growth experiments were not
 conducted for 4 and 16 h photoperiods under PAR of 180 µmol photons
@@
 
-The GAM model in Fig. \@ref(fig:SS120GAM) summarizes growth responses
+The GAM model in Fig \@ref(fig:SS120GAM) summarizes growth responses
 of SS120 to red (A and B) or blue (C and D) peak PAR and photoperiod, across the
-2 imposed oxygen concentrations. Under 250 µM O~2~, Fig.
-\@ref(fig:SS120GAM)C showed highest growth rates below blue light PAR of
+2 imposed oxygen concentrations. Under 250 µM O~2~, Fig \@ref(fig:SS120GAM)C showed highest growth rates below blue light PAR of
 50 µmol photons m^-2^ s^-1^ and photoperiods between 8 and 12 h,
@@
 (representing the 90^th^ percentile of achieved growth rate), out pacing
-the 90^th^ percentile fastest growth rates under 250 µM O~2~ (Fig.
-\@ref(fig:SS120GAM)D). Under red light and 25 µM O~2~ (Fig.
-\@ref(fig:SS120GAM)B) SS120 grew across most conditions of peak PAR and
+the 90^th^ percentile fastest growth rates under 250 µM O~2~ (Fig \@ref(fig:SS120GAM)D). Under red light and 25 µM O~2~ (Fig \@ref(fig:SS120GAM)B) SS120 grew across most conditions of peak PAR and
 photoperiod, achieving fastest growth under long photoperiods and peak
@@
 increased with longer photoperiods, under low 30 µmol photons m^-2^
-s^-1^ peak PAR, (Fig. \@ref(fig:MIT9313PAR)). Under intermediate 90
+s^-1^ peak PAR, (Fig \@ref(fig:MIT9313PAR)). Under intermediate 90
 µmol photons m^-2^ s^-1^ peak PAR growth rates decreased with increasing
@@
 For MIT9313 under 25 µM O~2~, growth rate increased with increasing
-photoperiods for all spectral wavebands tested (Fig.
-\@ref(fig:MIT9313PAR)), with the fastest overall growth rate for MIT9313
+photoperiods for all spectral wavebands tested (Fig \@ref(fig:MIT9313PAR)), with the fastest overall growth rate for MIT9313
 `r PURPARFits %>% filter(Strain == "MIT9313", WL == "WW", O2_uM == "25", Photoperiod == 16, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
@@
 generally slower than under the parallel experiments at 25 µM O~2~
-(Fig. \@ref(fig:MIT9313PAR)). Growth estimates showed scatter among
+(Fig \@ref(fig:MIT9313PAR)). Growth estimates showed scatter among
 replicates, suggesting 2.5 µM O~2~ is near the tolerance limit for
@@
 
-The GAM model in Fig. \@ref(fig:MIT9313GAM) summarizes MIT9313 growth
+The GAM model in Fig \@ref(fig:MIT9313GAM) summarizes MIT9313 growth
 responses to red (A-C) or blue (D-F) peak PAR and photoperiod. Under
-250 µM O~2~, Fig. \@ref(fig:MIT9313GAM)D shows MIT9313 achieves
+250 µM O~2~, Fig \@ref(fig:MIT9313GAM)D shows MIT9313 achieves
 fastest growth rates between blue peak PAR of 30 µmol photons m^-2^
@@
 indicated by the contour line labeled 0.52 d^-1^ representing the 90^th^
-percentile of achieved growth rates. Fig. \@ref(fig:MIT9313GAM)D also
+percentile of achieved growth rates. Fig \@ref(fig:MIT9313GAM)D also
 shows that growth rate increases with longer photoperiods, as long as
@@
 contrast, under red light and 250 µM O~2~ MIT9313 grows faster while
-exploiting higher peak PAR and longer photoperiods. Fig.
-\@ref(fig:MIT9313GAM)E shows that MIT9313 can exploit all blue PAR levels
+exploiting higher peak PAR and longer photoperiods. Fig \@ref(fig:MIT9313GAM)E shows that MIT9313 can exploit all blue PAR levels
 and most photoperiods with 90^th^ percentile of fastest growth rate
-between 30 to 100 µmol photons m^-2^ s^-1^ PAR. Fig.
-\@ref(fig:MIT9313GAM)F shows that MIT9313 maintains growth even under
+between 30 to 100 µmol photons m^-2^ s^-1^ PAR. Fig \@ref(fig:MIT9313GAM)F shows that MIT9313 maintains growth even under
 2.5 µM O~2~, under photoperiods between 8 and 12 h and peak blue PAR
 between 50 to 100 µmol photons m^-2^ s^-1^ PAR. Thus the designation of
-MIT9313 as a LL clade is dependent upon [O~2~] and light spectra (Fig. \@ref(fig:MIT9313GAM)E).
+MIT9313 as a LL clade is dependent upon [O~2~] and light spectra (Fig \@ref(fig:MIT9313GAM)E).
 
@@
 almost 3 times that of white LED light, and about 5 times that of the
-red light (Fig. \@ref(fig:PurParPlot)), despite being derived from the
+red light (Fig \@ref(fig:PurParPlot)), despite being derived from the
 same photoperiods and peak PAR regimes. As such, only blue light
@@
 delivered cumulative diel PUR equivalent to other photoperiod treatments
-(Fig. \@ref(fig:PhotoperiodPurFitsPlots)A-C). In parallel MED4
+(Fig \@ref(fig:PhotoperiodPurFitsPlots)A-C). In parallel MED4
 showed no growth under 2.5 µM O~2~, no matter the level of diel
@@
 cumulative diel PUR, with saturation of growth rate achieved around 1.0
-x 10^6^ µmol m^-2^d^-1^ (Fig. \@ref(fig:BluevsRedPurFitsPlots)A and B),
+x 10^6^ µmol m^-2^d^-1^ (Fig \@ref(fig:BluevsRedPurFitsPlots)A and B),
 and no evidence of inhibition of growth at any achieved cumulative diel
 PUR. Under the 'artificial' growth treatment of red light, MED4 achieved
-more growth per unit diel cumulative PUR (Fig.
-\@ref(fig:BluevsRedPurFitsPlots)A and B), consistent with Murphy *et al*.
+more growth per unit diel cumulative PUR (Fig \@ref(fig:BluevsRedPurFitsPlots)A and B), consistent with Murphy *et al*.
 [@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for
@@
 photoinactivation of PSII, than equivalent levels of blue light. For
-distinct fits for different photoperiods refer to Fig.
-\@ref(fig:PhotoperiodPurFitsPlots) A-C.
+distinct fits for different photoperiods refer to Fig \@ref(fig:PhotoperiodPurFitsPlots) A-C.
 
 The representative of the LLII/III clade, *P. marinus* SS120 showed
-almost no growth under 2.5 µM O~2~ experiments (Fig.
-\@ref(fig:PhotoperiodPurFitsPlots)F). Most 4 h photoperiod treatments of
+almost no growth under 2.5 µM O~2~ experiments (Fig \@ref(fig:PhotoperiodPurFitsPlots)F). Most 4 h photoperiod treatments of
 SS120 also did not grow under 250 µM O~2~ , even when a 4 h photoperiod
 delivered cumulative diel PUR equivalent to other photoperiod treatments
-(Fig. \@ref(fig:PhotoperiodPurFitsPlots)D). Again using
+(Fig \@ref(fig:PhotoperiodPurFitsPlots)D). Again using
 [@harrisonPhotosynthesisirradianceRelationshipsPolar1986], SS120 did not
@@
 cumulative diel PUR under any spectral waveband or photoperiod
-combination, under 250 µM O~2~ (Fig.
-\@ref(fig:PhotoperiodPurFitsPlots)D).
+combination, under 250 µM O~2~ (Fig \@ref(fig:PhotoperiodPurFitsPlots)D).
 
@@
 consistent with lower cost of growth through lower photoinactivation
-under red light (Fig. \@ref(fig:BluevsRedPurFitsPlots)E)
+under red light (Fig \@ref(fig:BluevsRedPurFitsPlots)E)
 [@murphyPhotoinactivationPhotosystemII2017]. For distinct fits for
-different photoperiods refer to Fig.
-\@ref(fig:PhotoperiodPurFitsPlots) D-F.
+different photoperiods refer to Fig \@ref(fig:PhotoperiodPurFitsPlots) D-F.
 
@@
 inhibition of growth, across photoperiods, and spectral wavebands
-(Fig. \@ref(fig:PhotoperiodPurFitsPlots)G). Under 25 µM O~2~ MIT9313
+(Fig \@ref(fig:PhotoperiodPurFitsPlots)G). Under 25 µM O~2~ MIT9313
 showed higher growth rates over a wider plateau, with a greatly extended
 exploitation of higher cumulative diel PUR, with full growth inhibition
-only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Fig.
-\@ref(fig:PhotoperiodPurFitsPlots)H). MIT9313 growth under 2.5 µM O~2~
+only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Fig \@ref(fig:PhotoperiodPurFitsPlots)H). MIT9313 growth under 2.5 µM O~2~
 showed a wider, lower, flatter response to cumulative diel PUR, with
 full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^
-d^-1^ cumulative diel PUR (Fig. \@ref(fig:PhotoperiodPurFitsPlots)I).
+d^-1^ cumulative diel PUR (Fig \@ref(fig:PhotoperiodPurFitsPlots)I).
 
@@
 of growth, due to decreased photoinactivation of PSII under red,
-compared to blue, wavebands (Fig.
-\@ref(fig:BluevsRedPurFitsPlots)G and H). Interestingly, this protective
+compared to blue, wavebands (Fig \@ref(fig:BluevsRedPurFitsPlots)G and H). Interestingly, this protective
 effect of red light disappears for MIT9313 growing under 2.5 µM O~2~,
 possibly because photoinactivation is strongly suppressed under this low
-[O~2~] (Fig. \@ref(fig:BluevsRedPurFitsPlots)I). For distinct fits for
-different photoperiod fits refer to Fig.
-\@ref(fig:PhotoperiodPurFitsPlots) G-I.
+[O~2~] (Fig \@ref(fig:BluevsRedPurFitsPlots)I). For distinct fits for
+different photoperiod fits refer to Fig \@ref(fig:PhotoperiodPurFitsPlots) G-I.
 
@@
 SS120 and clade LLIV MIT9313 show generally similar patterns vs. [O~2~]
-and depth, a proxy for peak PAR (Fig.
-\@ref(fig:CladeProchloroProteinMetabDepthO2)). FtsH3, inferred to
+and depth, a proxy for peak PAR (Fig \@ref(fig:CladeProchloroProteinMetabDepthO2)). FtsH3, inferred to
 mediate PSI assembly, likewise shows a similar pattern between MED4 and
-MIT9313 (Fig. \@ref(fig:CladeProchloroProteinMetabDepthO2)). But only
+MIT9313 (Fig \@ref(fig:CladeProchloroProteinMetabDepthO2)). But only
 MED4 shows the presence of the FtsH1 & FtsH2 isoforms inferred to
 mediate PSII repair, and then only in near-surface samples subject to
-higher light levels. Furthermore, even though MIT9313 grows (Fig.
-\@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~]
-(Fig. \@ref(fig:CladeProchloroPhotosynthDepthO2)), no FtsH from
-MIT9313 is detected at low [O~2~] (Fig.
-\@ref(fig:CladeProchloroProteinMetabDepthO2)), suggesting limited
+higher light levels. Furthermore, even though MIT9313 grows (Fig \@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~]
+(Fig \@ref(fig:CladeProchloroPhotosynthDepthO2)), no FtsH from
+MIT9313 is detected at low [O~2~] (Fig \@ref(fig:CladeProchloroProteinMetabDepthO2)), suggesting limited
 requirement for protein turnover under low [O~2~].
@@
 
-Fig. \@ref(fig:ProchlorococcusEnzymeKms) shows the measured or
+Fig \@ref(fig:ProchlorococcusEnzymeKms) shows the measured or
 inferred K~M~ for [O~2~] for enzymes encoded by genes 
@@
 inter-system transport chain. The approximate K~M~ for [O~2~] of \~ 25
-µM for ubiquinol oxidase (non electrogenic) (Fig.
-\@ref(fig:ProchlorococcusEnzymeKms)) is comparable to the lower limit
-for growth of MED4 in our experiments (Fig. \@ref(fig:MED4GAM)). We
+µM for ubiquinol oxidase (non electrogenic) (Fig \@ref(fig:ProchlorococcusEnzymeKms)) is comparable to the lower limit
+for growth of MED4 in our experiments (Fig \@ref(fig:MED4GAM)). We
 suggest that dependence upon this enzyme excludes MED4 from low oxygen
-zones. The genome scan shows SS120 and MIT9313 lack this gene (Fig.
-\@ref(fig:ProchlorococcusEnzymeKms)), and therefore, lack this
+zones. The genome scan shows SS120 and MIT9313 lack this gene (Fig \@ref(fig:ProchlorococcusEnzymeKms)), and therefore, lack this
 oxygen-dependent path to cope with changing excitation. Conversely, a
 gene encoding (S)-2-hydroxy-acid oxidase is encoded in the MIT9313
-genome (Fig. \@ref(fig:ProchlorococcusEnzymeKms)). (S)-2-hydroxy-acid
+genome (Fig \@ref(fig:ProchlorococcusEnzymeKms)). (S)-2-hydroxy-acid
 oxidase catalyzes the reaction of 2-hydroxy acid with O~2~ to produce
@@
 photoinhibition and circumvent its limitations on PSII repair to exploit
-higher light. Fig. \@ref(fig:ProchlorococcusEnzymeKms) also shows that
+higher light. Fig \@ref(fig:ProchlorococcusEnzymeKms) also shows that
 *P. marinus* SS120 is the only tested ecotype to lack the pyridoxal
@@
 grow as well as *P. marinus* MIT9313, when exposed to high light stress
-under 25 µM O~2~ and not at all under 2.5 µM O~2~ (Fig.
-\@ref(fig:SS120PAR)).
+under 25 µM O~2~ and not at all under 2.5 µM O~2~ (Fig \@ref(fig:SS120PAR)).
 
@@
 
-Fig. \@ref(fig:DNARepairFig) shows genes encoding DNA repair for *P.
+Fig \@ref(fig:DNARepairFig) shows genes encoding DNA repair for *P.
 marinus* strains. As expected, *P. marinus* MED4 possesses the largest,
@@
 and NATL2A were the only strains to possess a gene encoding
-deoxyribodipyrimidine photolyase (Fig. \@ref(fig:DNARepairFig) and
+deoxyribodipyrimidine photolyase (Fig \@ref(fig:DNARepairFig) and
 \@ref(fig:ProchlorococcusLightEnzymes)), which, in the presence of blue
@@
 MIT9313, actually tolerate approximately 1.0 x 10^6^ µmol photons m^-2^
-d^-1^ of PUR (Fig. \@ref(fig:PhotoperiodPurFitsPlots)E and H), comparable
+d^-1^ of PUR (Fig \@ref(fig:PhotoperiodPurFitsPlots)E and H), comparable
 to the representative HL clade, MED4 which also exhibited growth
 saturation at the same cumulative diel PUR of 1.0 x 10^6^ µmol photons
-m^-2^ d^-1^ (Fig. \@ref(fig:PhotoperiodPurFitsPlots)A and B). Growth under
+m^-2^ d^-1^ (Fig \@ref(fig:PhotoperiodPurFitsPlots)A and B). Growth under
 lower O~2~ allowed MIT9313 to substantially increase its exploitation of
-higher diel PUR (Fig. \@ref(fig:PhotoperiodPurFitsPlots)I).
+higher diel PUR (Fig \@ref(fig:PhotoperiodPurFitsPlots)I).
 
@@
 habitats of 2.5 µM O~2~, but can, grow under OMZ regions with 25 µM
-O~2~. Genomic (Fig. \@ref(fig:ProchlorococcusEnzymeKms)) and
+O~2~. Genomic (Fig \@ref(fig:ProchlorococcusEnzymeKms)) and
 transcriptional analyses [@bergResponsesPsbAHli2011] suggest MED4 is
@@
 layer, nor did they report[O~2~] at depth. Our growth findings are
-consistent with Fig. \@ref(fig:CladeProchloroPhotosynthDepthO2)
+consistent with Fig \@ref(fig:CladeProchloroPhotosynthDepthO2)
 showing PSII proteins annotated as MED4, clade HLI, at depths up to 200
@@
 with a higher tolerance for higher cumulative diel PUR under 25 µM O~2~,
-compared to 250 µM O~2~ (Fig. \@ref(fig:PhotoperiodPurFitsPlots)).
+compared to 250 µM O~2~ (Fig \@ref(fig:PhotoperiodPurFitsPlots)).
 Thus, SS120 can exploit higher PAR environments, within OMZ. SS120 is
 likely excluded from the combination of higher [O~2~] and higher PAR by
-genomic limitations on capacity for DNA repair (Fig.
-\@ref(fig:DNARepairFig)), and possibly by limited capacity for synthesis
-of reactive oxygen quenchers (Fig.
-\@ref(fig:ProchlorococcusEnzymeKms)). Our growth results are supported
+genomic limitations on capacity for DNA repair (Fig \@ref(fig:DNARepairFig)), and possibly by limited capacity for synthesis
+of reactive oxygen quenchers (Fig \@ref(fig:ProchlorococcusEnzymeKms)). Our growth results are supported
 by Lavin *et al*. [@lavinNovelLineagesProchlorococcus2010] who found
@@
 fragment length polymorphism analyses, at depths above 40 m, where light
-levels are higher, within OMZ, and by Fig.
-\@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSII protein subunits
+levels are higher, within OMZ, and by Fig \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSII protein subunits
 annotated as derived from SS120 at all depths ranging from 20 to 200 m
@@
 higher light levels and cumulative diel PUR, but only under low oxygen
-conditions of 25 µM and 2.5 µM (Fig. \@ref(fig:MIT9313PAR)), enabling
+conditions of 25 µM and 2.5 µM (Fig \@ref(fig:MIT9313PAR)), enabling
 MIT9313 to grow in OMZ, even at depths closer to the surface. MIT9313
@@
 [@cunaneCrystalStructureAnalysis2005], with a K~M~ for [O~2~] of \~ 250
-µM (Fig. \@ref(fig:ProchlorococcusEnzymeKms)), which produces
+µM (Fig \@ref(fig:ProchlorococcusEnzymeKms)), which produces
 H~2~O~2~. Growth at lower [O~2~] may protect MIT9313 from
@@
 expand into broader ecological niches. These results are supported by
-Fig. \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSI protein
+Fig \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSI protein
 subunits annotated as derived from MIT9313 detected at depths \> 120 m,

### 2024-05-21 Code/Manuscript_O2.Rmd
Plos reveiwer Edits

@@
 warming may open permissive temperatures in new, poleward photic
-regimes, along with expanded Oxygen Minimum Zones. We used ocean protein
+regimes, along with expanded Oxygen Minimum Zones. We used ocean protein portal
 data to help guide testing of
@@
 photosynthetic prokaryote, with cell diameters ranging from 0.5 to 0.7
-µm [@chisholmProchlorococcusMarinusNov1992]. Despite small cell size,
+µm [@chisholmProchlorococcusMarinusNov1992]. Despite its small cell size,
 *P. marinus* contribute 13 to 48% of net primary production in
@@
 HLI, HLII, LLI, LLII/III and LIV
-[@billerProchlorococcusStructureFunction2015]. Current niches of *P.
-marinus* strains span ocean water columns
+[@mooreComparativePhysiologySynechococcus1995; @mooreCulturingMarineCyanobacterium2007; @billerProchlorococcusStructureFunction2015]. Current niches of *P.marinus* strains span ocean water columns
 [@veldhuisVerticalDistributionPigment1990;
@@
 m depth. Clades LLII and LLIII, including cultured strain SS120, are
-grouped together as the second oldest phylogenetic lineage diversifying
-in the *P. marinus* radiation, with an affinity for low light. Clade
+grouped together as early branching phylogenetic lineage diversifying
+in the *P. marinus* radiation, with a preference for low light. Clade
 LLIV, including cultured strain MIT9313, falls near the base of the
@@
 waters, with increases in *P. marinus* of approximately 50% in the more
-poleward regions of their distributions.
+poleward regions of their distributions. @follettTrophicInteractionsHeterotrophic2022 however, model interactions of heterotrophic  bacteria  that may influence latitudinal expansion of *P. marinus*.
 
@@
 
-*Prochlorococcus* remain challenging to culture, as their reduced
-genomes – the smallest of any known oxyphototroph – render them
-partially dependent upon mutualistic heterotrophic bacteria to detoxify
-reactive oxygen species [@morrisFacilitationRobustGrowth2008;
-@morrisDependenceCyanobacteriumProchlorococcus2011]. MED4, SS120 and
-MIT9313 have been successfully cultured in laboratories
-[@mooreComparativePhysiologySynechococcus1995;
-@mooreCulturingMarineCyanobacterium2007], and used to show that ecotypic
-classifications correspond to biochemical differences among strains
-[@bonisteelStrainSpecificDifferences2018]. Three xenic cultures of *P.
-marinus* were obtained from Bigelow Labs, NCMA Maine, USA. MED4
+Three xenic cultures of *P.marinus* were obtained from Bigelow Labs, NCMA Maine, USA. MED4
 (CCMP1986) is from High-Light adapted (HLI) clade; SS120 (CCMP1375) is
@@
 curves is equivalent to the area of a triangular photoregime of
-equivalent photoperiod (Campbell, unpub), therefore the equation to
+equivalent photoperiod, therefore the equation to
 determine the cumulative diel PUR (µmol photons m^-2^ d^-1^) is one half
@@
 Proteins from 13 annotated strains of *P. marinus* were detected across
-depths and oxygen concentrations in the ocean proteins data set
+depths and oxygen concentrations in the OPP data set
 analyzed. We focused our analysis here on core photosynthetic protein
-complexes, for clades HL, LLI, LLII/III and LLIV (Fig \@ref(fig:CladeProchloroPhotosynthDepthO2)) as a function of depth (a
+complexes, for clades HLI, LLI, LLII/III and LLIV (Fig \@ref(fig:CladeProchloroPhotosynthDepthO2)) as a function of depth (a
 proxy for light intensity) and measured [O~2~]. Photosynthetic complexes
@@
 present across the depth/light axes, with more representation at lower
-[O\~2], and fewer near surface detections. Complexes from clade LLII/III
-(ex. SS120) were also detected across the depth/light and [O~2~] ranges,
-with more detections at deeper, darker depths. Clade LLIV (ex. MIT9313)
-photosynthetic complexes were also were detected throughout the
+[O~2~], and fewer near surface detections. Complexes from clade LLII/III
+(including strain SS120) were also detected across the depth/light and [O~2~] ranges,
+with more detections at deeper, darker depths. Clade LLIV (including strain MIT9313)
+photosynthetic complexes were also detected throughout the
 depth/light and [O~2~], ranges, with the most frequent detections at
@@
 
-*Prochlorococcus marinus* MED4, clade HLI, growth under 250 µM O~2~
-increased with higher imposed PAR and longer photoperiods (Fig \@ref(fig:MED4PAR)), across all spectral wavebands. No growth was
+*Prochlorococcus marinus* MED4, clade HLI, grew under 250 µM O~2~ and growth rates increased with higher imposed PAR and longer photoperiods (Fig \@ref(fig:MED4PAR)), across all spectral wavebands.
+No growth was
 observed under any imposed conditions under a 4 h photoperiod. The
@@
 photoperiods. Red light 16 h photoperiod experiments were not performed
-due to time constraints. \newpage
+due to time constraints.
+
+\newpage
 
@@
 `r PURPARFits %>% filter(Strain == "MIT9313", WL == "450", O2_uM == "2.5", Photoperiod == 12, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
-d^-1^ achieved under 12 h blue light photoperiod and PAR of 90 µmol
+d^-1^, achieved under 12 h blue light photoperiod and PAR of 90 µmol
 photons m^-2^ s^-1^. The 2.5 µM O~2~ white LED treatments under 4, 8 and
@@
 
-Under full atmospheric [O~2~] and blue light, LL clades of
+*Prochlorococcus*, with their reduce genomes are the smallest of any known oxyphototroph, render them
+partially dependent upon mutualistic heterotrophic bacteria to detoxify
+reactive oxygen species [@morrisFacilitationRobustGrowth2008;
+@morrisDependenceCyanobacteriumProchlorococcus2011]. Under full atmospheric [O~2~] and blue light, LL clades of
 *Prochlorococcus* are restricted to growth under low light, in part
@@
 several paths, including direct absorbance of UV or blue light, in
-parallel with generation of Reactive Oxygen Species (ROS) if the
+parallel with generation of ROS if the
 electron flow is slowed [@aroPhotoinhibitionPhotosystemII1993],
@@
 Fig \@ref(fig:ProchlorococcusEnzymeKms) shows the measured or
-inferred K~M~ for [O~2~] for enzymes encoded by genes 
+inferred K~m~ for [O~2~] for enzymes encoded by genes 
 [@omarAnnotationGenesEncoding2023] from *P. marinus* strains, from clades
@@
 light [@bergResponsesPsbAHli2011], by dissipating electrons from the
-inter-system transport chain. The approximate K~M~ for [O~2~] of \~ 25
+inter-system transport chain. The approximate K~m~ for [O~2~] of \~ 25
 µM for ubiquinol oxidase (non electrogenic) (Fig \@ref(fig:ProchlorococcusEnzymeKms)) is comparable to the lower limit
@@
 toxic H~2~O~2~ [@cunaneCrystalStructureAnalysis2005]. (S)-2-hydroxy-acid
-oxidase has an approximate K~M~ for [O~2~] of \~ 250 µM, and produces
+oxidase has an approximate K~m~ for [O~2~] of \~ 250 µM, and produces
 H~2~O~2~, so growth at lower [O~2~] may protect MIT9313 from
@@
 [@sancarStructureFunctionDNA2003]. *Prochlorococcus marinus* MED4 was
-also the only strain to possesses a gene encoding DNA ligase, which uses
+also the only strain to possess a gene encoding DNA repair ligase, which uses
 ATP as a cofactor for DNA repair. The absence of genes encoding
-deoxyribodipyrimidine photolyase and DNA ligase (ATP) in *P. marinus*
-MIT9313 and *P. marinus* SS120 explain why these two strains cannot
+deoxyribodipyrimidine photolyase and DNA repair ligase (ATP) in *P. marinus*
+MIT9313 and *P. marinus* SS120 contribute, in part, to the inability of these two strains to
 tolerate growth under full [O~2~] and high light, found at the ocean
@@
 encoding photolyase, a gene found in HL clades. The presence of
-deoxyribodipyrimidine photolyase and absence of DNA ligase (ATP)
+deoxyribodipyrimidine photolyase and absence of DNA repair ligase (ATP)
 supports why NATL2A tolerates limited exposure to high light and why
@@
 ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction
-balance in the intersystem electron transport chain, with a K~M~ for
+balance in the intersystem electron transport chain, with a K~m~ for
 [O~2~] of \~25 µM O~2~. On the other hand, MED4 shows inducible
@@
 likely excluded from the combination of higher [O~2~] and higher PAR by
-genomic limitations on capacity for DNA repair (Fig \@ref(fig:DNARepairFig)), and possibly by limited capacity for synthesis
-of reactive oxygen quenchers (Fig \@ref(fig:ProchlorococcusEnzymeKms)). Our growth results are supported
+genomic limitations on capacity for DNA repair (Fig \@ref(fig:DNARepairFig)), and possibly by limited capacity for synthesis of reactive oxygen quenchers (Fig \@ref(fig:ProchlorococcusEnzymeKms)).
+Our growth results are supported
 by Lavin *et al*. [@lavinNovelLineagesProchlorococcus2010] who found
@@
 carries a gene encoding (S)-2-hydroxy-acid oxidase
-[@cunaneCrystalStructureAnalysis2005], with a K~M~ for [O~2~] of \~ 250
+[@cunaneCrystalStructureAnalysis2005], with a K~m~ for [O~2~] of \~ 250
 µM (Fig \@ref(fig:ProchlorococcusEnzymeKms)), which produces

### 2024-05-21 Code/Plots_GAM.Rmd
Plos reveiwer Edits

@@
 ```{r project data}
-FP1 <- ".."
-Project <- "PICO"
-FileID <- "GAM"
-Expert <- "MiSa" #MiSa SySl
+
 GamFit <- "PICO_Merged_GrowthFitsPURPAR.Rds"
@@
 DataOut <- file.path("..","Data", "CleanData")
+PlotsIn <- file.path("..","Output", "Figures")
 PlotsOut <- file.path("..","Output", "Figures")
@@
 #https://stackoverflow.com/questions/22772279/converting-multiple-columns-from-character-to-numeric-format-in-r
-
-GamPara <- "Lmu" # Stabds for growth estimates determined by logistic model
 
@@
 library(vegan)
-library(cowplot)
 library(glue)
@@
 library(Rcpp) #'Rcpp' package provides R functions as well as C++ classes which offer a seamless integration of R and C++.
-
-```
-
-# Read data nad select relevant columns
+library(patchwork)
+
+```
+
+# Read data and select relevant columns
 ```{r read data and select relevant columns}
@@
 
-GrowthFits <- GrowthFits %>% 
+GAMGrowthFits <- GrowthFits %>% 
  dplyr::select(c(Filename, PrimaryOperator, Tube, SampleID, Run, Photoperiod, Strain, WL, O2_Category, O2_uM, LightShape, Pur_ue, Par_ue, PURPhotonDose_day, PARPhotonDose_day, OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se))
-
-ReplNo <- GrowthFits %>%
-  distinct(Photoperiod, Strain, O2_uM, WL, Par_ue)
 
@@
 ```{r set up df for GAM}
- Pivot_Longer_OD720_est <- GrowthFits %>% 
+ Pivot_Longer_OD720_est <- GAMGrowthFits %>% 
   dplyr::select(-c(OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se)) %>%
@@
 
-# OD720 pivot longer Gmax, Gmu, Glag , Lmu, Lmax and Lintercept standard error
-Pivot_Longer_OD720_se <- GrowthFits %>%
+# OD720 pivot longer  Lmu, Lmax and Lintercept standard error
+Pivot_Longer_OD720_se <- GAMGrowthFits %>%
   dplyr::select(-c(OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept, deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se)) %>%
@@
 
-# deltaOD pivot longer Gmax, Gmu, Glag, Lmu, Lmax and Lintercept estimates
-Pivot_Longer_deltaOD_est <- GrowthFits %>%
+# deltaOD pivot longer Lmu, Lmax and Lintercept estimates
+Pivot_Longer_deltaOD_est <- GAMGrowthFits %>%
   dplyr::select(-c(OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se,  deltaOD_Lmu_se, deltaOD_Lmax_se, deltaOD_Lintercept_se)) %>%
@@
 
-# deltaOD pivot longer Gmax, Gmu, Glag , Lmu, Lmax and Lintercept standard error
-Pivot_Longer_deltaOD_se <- GrowthFits %>%
+# deltaOD pivot longer Lmu, Lmax and Lintercept standard error
+Pivot_Longer_deltaOD_se <- GAMGrowthFits %>%
   dplyr::select(-c(OD720_Lmu_corr, OD720_Lmax, OD720_Lintercept, OD720_Lmu_se, OD720_Lmax_se, OD720_Lintercept_se, deltaOD_Lmu_corr, deltaOD_Lmax, deltaOD_Lintercept)) %>%
@@
 
-remove(Pivot_Longer_deltaOD_est, Pivot_Longer_deltaOD_se)
+remove(Pivot_Longer_deltaOD_est, Pivot_Longer_deltaOD_se, GAMGrowthFits)
 
 #Join OD720 and deltaOD fits data
-ComGrowthFits <- rbind(Longer_OD720_Joined, Longer_deltaOD_Joined) %>%
+PicoGrowthFits <- rbind(Longer_OD720_Joined, Longer_deltaOD_Joined) %>%
   mutate_if(is.numeric, round, digits = 3) %>% 
@@
 
-glimpse(ComGrowthFits)
+glimpse(PicoGrowthFits)
 
@@
 GamVar = "450"
-
-#DummyDF for MED4; MED4 is a high light strain, based on literature it can grow up to 800 uE; we never exposed it to such high light levels and will not impose an upper end, but only a lower, i.e.
-Par_ue = 0, Lmu = 0, there are no reliable points for low O2 in shorter photoperiods
-Strain <- c("MED4")
-Photoperiod <- c(4, 8, 12, 16)
-Par_ue<- c(0)
-O2_uM <- c(2.5, 25.0, 250.0)
-WL <- c(450, 530, 660, "WW")
-estimate <- c(0)
-term <- GamPara
-Wavelength <- c("deltaOD", "OD720")
-Tube <- c(9)
-
-DummyDF_MED4 <- expand_grid(
-  Strain, Photoperiod, Par_ue, O2_uM, WL, estimate, Wavelength, term, Tube
-  ) %>%
-  mutate(Lmu_seFlag = 1) 
-DummyDF_Expand_MED4 <- rbind(DummyDF_MED4, DummyDF_MED4, DummyDF_MED4)
-
-#DummyDF for MIT9313; MIT9313 is a low light strain, based on literature it can only grow up to 300 uE WW; MIT9313 consistently died at various light colors and oxygen levels latest at ~PAR 400; it can safely be assumed it dies at par_ue = 0
-Strain <- c("MIT9313")
-Photoperiod <- c(4, 8, 12, 16)
-Par_ue<- c(0)
-O2_uM <- c(2.5, 25.0, 250.0)
-WL <- c(450, 530, 660, "WW")
-estimate <- c(0)
-term <- GamPara
-Wavelength <- c("deltaOD", "OD720")
-Tube <- c(9)
-
-DummyDF_MIT9313 <- expand_grid(
-  Strain, Photoperiod, Par_ue, O2_uM, WL, estimate, Wavelength, term, Tube
-  ) %>%
-  mutate(Lmu_seFlag = 1) 
-DummyDF_Expand_MIT9313 <- rbind(DummyDF_MIT9313, DummyDF_MIT9313, DummyDF_MIT9313)
-
-#DummyDF for SS120; SS120 is a low light strain, based on literature it can only grow up to 300 uE WW; SS120 consistently died at various light colors and oxygen levels latest at ~PAR 400; it can safely be assumed it dies at par_ue = 0
-Strain <- c("SS120")
-Photoperiod <- c(4, 8, 12, 16)
-Par_ue<- c(0, 400)
-O2_uM <- c(2.5, 25.0, 250.0)
-WL <- c(450, 530, 660, "WW")
-estimate <- c(0)
-term <- GamPara
-Wavelength <- c("deltaOD", "OD720")
-Tube <- c(9)
-
-DummyDF_SS120 <- expand_grid(
-  Strain, Photoperiod, Par_ue, O2_uM, WL, estimate, Wavelength, term, Tube
-  ) %>%
-  mutate(Lmu_seFlag = 1) 
-DummyDF_Expand_SS120 <- rbind(DummyDF_SS120, DummyDF_SS120, DummyDF_SS120)
-
-DummyDF_Expand <- rbind(DummyDF_Expand_SS120, DummyDF_Expand_MIT9313, DummyDF_Expand_MED4)
-
-PicoGrowthFits <-    ComGrowthFits # full_join(ComGrowthFits, DummyDF_Expand)
+GAMParaMod = "Lmu" # Stands for growth estimates determined by logistic model
 
 PicoLmuAb <- PicoGrowthFits %>%
-  filter(term %in% GamPara) %>%
+  filter(term %in% GAMParaMod) %>%
   filter(Wavelength %in% GamWL) %>%
@@
 ```{r GAM separate niches hypervolume for red light}
-GamWL = c("deltaOD", "OD720") #deltaOD OD720
-Proxy= "[~Chl]" #~Chl ~Cells 
-GamParaMod = "Lmu"
-GamVar = c("660")
-ErrorTolGrowth = 30 # defined for the growth estimates
+GamWL = c("deltaOD") #deltaOD or OD720
+GamParaMod = "Lmu" # logistic model growth estimates
+GamVar = "660" # growth spectral wavelength
+ErrorTolGrowth = 30 # the amplitude tolerance of the standard error of the fitted growth estimates
+ErrorTol = 30 # the amplitude tolerance of the standard error of the fitted GAM
+
+#https://stackoverflow.com/questions/49570452/is-it-possible-to-specify-lower-bound-in-response-variable-during-smooth-with-ga 
+possibGAM = possibly(.f = mgcv::gam, otherwise = NULL)
+possibPRED = possibly(.f = mgcv::predict.gam, otherwise = NULL)
+
+PAR_Photoperiod_Model_predi <- expand_grid(
+  Par_ue = seq(from=min(10), 
+              to=max(200), 
+              length.out = 100),
+  Photoperiod = seq(from=min(2), 
+              to=max(18), 
+              length.out = 100)
+)
+
+PicoGAM <- PicoGrowthFits %>%
+  ungroup() %>%
+  dplyr::mutate(Lmu_seFlag = case_when(se/estimate*100 < ErrorTolGrowth ~ 1, # flag to include data where Standarderror smaller than +/- Errortolerance
+                         FALSE ~ 0)) %>%
+  dplyr::filter(
+                estimate == 0 |
+                estimate != 0 & Lmu_seFlag == 1, # include no growths and growths that meet se tolerance. 
+                term %in% GamParaMod, 
+                Wavelength %in% GamWL
+                ) %>%
+  mutate(estimate = estimate*24, # to convert growth from per hour to per day
+         se = se*24) %>% # to convert standard error from per hour to per day
+  group_by(Strain, Wavelength, WL, O2_uM) %>%
+  nest() %>%
+  dplyr::arrange(Strain, Wavelength, WL, O2_uM) %>%
+  mutate(GamModel = map(data, ~possibGAM(estimate ~ s(Par_ue, k = 3) + s(Photoperiod, k = 3) + ti(Photoperiod, Par_ue, k = 3),  data = .x,
+                                    family = "gaussian"(link = "log"), 
+                                    method = "REML")),
+         predicted = map(GamModel, ~possibPRED(.x, newdata = PAR_Photoperiod_Model_predi, type = 'response', se.fit=TRUE)),
+         augmented = map(GamModel, ~augment(.x))
+         )
+
+PicoGAM_Pred <- PicoGAM %>%
+  dplyr::select(Strain, Wavelength, WL, O2_uM, predicted) %>%
+  dplyr::filter(predicted != "NULL") %>%
+  rowwise() %>%
+  mutate(db = list(cbind(predicted, PAR_Photoperiod_Model_predi))) %>%
+  dplyr::select(-predicted) %>%
+  unnest(col = db) %>%
+  group_by(Strain, Wavelength, WL, O2_uM) %>%
+  dplyr::filter(fit < 1.2) %>% # with two exceptions, growth rates were never higher than 1.2; GAM model creates some unrealistic high growth rates due to low data availability
+  mutate(
+    IsFitGood = case_when(se.fit/fit*100 < ErrorTol ~ 1, # flags faulty data where Standarderror larger +/- Errortolerance
+                         se.fit/fit*100 > ErrorTol ~ 0
+                    )
+  ) %>% 
+  dplyr::filter(IsFitGood == 1)
+
+```
+
+# Generate GAM for blue light conditions for all strains using chlorophyll proxy logistic growth rate. 
+```{r GAM separate niches hypervolume for blue light}
+GamWL = c("deltaOD") #deltaOD or OD720
+GamParaMod = "Lmu" # logistic model growth estimates
+GamVar = "450" # growth spectral wavelength
+ErrorTolGrowth = 30 # the amplitude tolerance of the standard error of the fitted growth estimates
 ErrorTol = 30 # defined for the GAM fit
-# OxyLev = 25
 
@@
   mutate(
-    IsFitGood = case_when(se.fit/fit*100 < ErrorTol ~ 1, #flags faulty data where Standarderror larger +/- Errortolerance
+    IsFitGood = case_when(se.fit/fit*100 < ErrorTol ~ 1, # flags faulty data where Standarderror larger +/- Errortolerance
                          se.fit/fit*100 > ErrorTol ~ 0
                     )
-    #se_erro_per = se.fit/fit*100
-  # ,fit = case_when(fit >= quantile(fit, 0.75, na.rm = TRUE) ~ fit*1, #leaves only top-10%, that means fastest growth rates in the dataframe
-  #                 FALSE ~ fit)
-  ) %>% 
-  dplyr::filter(IsFitGood == 1)
-
-```
-
-# Generate GAM for blue light conditions for all strains using chlorophyll proxy logistic growth rate. 
-```{r GAM separate niches hypervolume for blue light}
-GamWL = c("deltaOD", "OD720") #deltaOD OD720
-Proxy= "[~Chl]" #~Chl ~Cells 
-GamParaMod = "Lmu"
-GamVar = c("450")
-ErrorTolGrowth = 30 # defined for the growth estimates
-ErrorTol = 30 # defined for the GAM fit
-# OxyLev = 25
-
-#https://stackoverflow.com/questions/49570452/is-it-possible-to-specify-lower-bound-in-response-variable-during-smooth-with-ga 
-possibGAM = possibly(.f = mgcv::gam, otherwise = NULL)
-possibPRED = possibly(.f = mgcv::predict.gam, otherwise = NULL)
-
-PAR_Photoperiod_Model_predi <- expand_grid(
-  Par_ue = seq(from=min(10), 
-              to=max(200), 
-              length.out = 100),
-  Photoperiod = seq(from=min(2), 
-              to=max(18), 
-              length.out = 100)
-)
-
-PicoGAM <- PicoGrowthFits %>%
-  ungroup() %>%
-  dplyr::mutate(Lmu_seFlag = case_when(se/estimate*100 < ErrorTolGrowth ~ 1, #filters faulty data where Standarderror larger +/- Errortolerance
-                         FALSE ~ 0)) %>%
-  dplyr::filter(
-                estimate == 0 |
-                estimate != 0 & Lmu_seFlag == 1,
-                term %in% GamParaMod, 
-                Wavelength %in% GamWL
-                ) %>%
-  mutate(estimate = estimate*24, #to convert growth from per hour to per day
-         se = se*24) %>%
-  group_by(Strain, Wavelength, WL, O2_uM) %>%
-  nest() %>%
-  dplyr::arrange(Strain, Wavelength, WL, O2_uM) %>%
-  mutate(GamModel = map(data, ~possibGAM(estimate ~ s(Par_ue, k = 3) + s(Photoperiod, k = 3) + ti(Photoperiod, Par_ue, k = 3),  data = .x,
-                                    family = "gaussian"(link = "log"), 
-                                    method = "REML")),
-         predicted = map(GamModel, ~possibPRED(.x, newdata = PAR_Photoperiod_Model_predi, type = 'response', se.fit=TRUE)),
-         augmented = map(GamModel, ~augment(.x))
-         )
-
-PicoGAM_Pred <- PicoGAM %>%
-  dplyr::select(Strain, Wavelength, WL, O2_uM, predicted) %>%
-  dplyr::filter(predicted != "NULL") %>%
-  rowwise() %>%
-  mutate(db = list(cbind(predicted, PAR_Photoperiod_Model_predi))) %>%
-  dplyr::select(-predicted) %>%
-  unnest(col = db) %>%
-  group_by(Strain, Wavelength, WL, O2_uM) %>%
-  dplyr::filter(fit < 1.2) %>% #with two exceptions, growth rates were never higher than 1.2; GAM model creates some unrealistic high growth rates due to low data availability
-  mutate(
-    IsFitGood = case_when(se.fit/fit*100 < ErrorTol ~ 1, #flags faulty data where Standarderror larger +/- Errortolerance
-                         se.fit/fit*100 > ErrorTol ~ 0
-                    )
-    #se_erro_per = se.fit/fit*100
-  # ,fit = case_when(fit >= quantile(fit, 0.75, na.rm = TRUE) ~ fit*1, #leaves only top-10%, that means fastest growth rates in the dataframe
-  #                 FALSE ~ fit)
   ) %>% 
@@
   mutate(
-         OxygenLabel = "Oxygen concentration (uM)",
-         O2_level = case_when(O2_uM == 2.5 ~ "low",
-                              O2_uM == 25 ~ "intermediate",
-                              O2_uM == 250 ~ "high"),
          Color_name = case_when(WL == "450" ~ 'Blue',
@@
                                 WL == "660" ~ 'Red',
-                                WL == "WW" ~ 'White')) %>%
-  unite(WL_O2, Color_name, O2_level, sep = "_", remove = FALSE)
+                                WL == "WW" ~ 'White'))
 
@@
     scale_y_continuous(limits = c(10, 200))  +
-    xlab(NULL)+
-      ylab(NULL)+ 
+    labs(title = bquote("D.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
+    xlab("Photoperiod (h)") +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
+    # xlab(NULL)+
+    #   ylab(NULL)+ 
   theme_classic() +
@@
     scale_y_continuous(limits = c(10, 200)) +
-    xlab(NULL)+
-      ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
+    xlab("Photoperiod (h)") +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
+    # xlab(NULL) +
+    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
 theme_classic() +
    theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
+         axis.title.x = element_blank(),
+         axis.text.x = element_blank(),
+          # axis.title.x = element_text(size=20),
            axis.title.y = element_text(size=35)))
@@
 
+test <-  plot_grid(MED4PAR, LabelledCombinedGam, labels = "AUTO", ncol = 1) 
+test
+```
+
+```{r, MED4PAR, fig.height=10, fig.width=10}
+MyWavelengths = c("WW", 660, 450)
+
+MCMIXColours = c("black", "brown", "steelblue")
+
+names(MCMIXColours) <- MyWavelengths
+MCMIXColours
+
+  data_text <- data.frame( ParLabel=c("PAR~(µmol~photons~m^{-2}~s^{-1})"), OxygenLabel = c("Oxygen~concentration~(µM)"),Par_ue = c("30"), O2_uM = c("250"), label = c('A'))
+
+MED4PAR <- GrowthFits %>%
+   filter(Strain == "MED4",
+           Par_ue %in% c(30,90,180),
+          WL %in% c("WW", 450, 660),
+          deltaOD_Lmu_corr == 0 |
+          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
+  mutate(PhotoperiodLabelTitle = "Photoperiod~(h)",
+         OxygenLabel = "Oxygen~concentration~(µM)",
+         WLlabelTitle = "Growth~wavelength~(nm)",
+         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
+         # Par_ue = factor(Par_ue, levels = c(30, 90, 180)),
+         # O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         WL = factor(WL, levels = c("WW", 660, 530, 450)),
+         deltaOD_Lmu_corr_day = deltaOD_Lmu_corr * 24,
+         deltaOD_Lmu_se_day = deltaOD_Lmu_se * 24) %>% 
+  ggplot()  +
+    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.75, show.legend = F) +
+   geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5, show.legend = F) +
+    geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 1) +
+    geom_text(data=data_text, aes(x=5.5, y=0.8, label=label), size=7) +
+ labs( y = "Chlorophyll specific growth rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
+   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3, show.legend = F) +
+  scale_y_continuous(breaks = c(0,0.25,  0.5, 0.75, 1.0), limits = c (0, 1.05)) +
+  # coord_cartesian(ylim = c (0, 0.07)) +
+  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
+   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
+  ggh4x::facet_nested(cols = vars(ParLabel, factor(Par_ue, levels = c("30", "90","180"))), rows = vars(OxygenLabel, factor(O2_uM, levels= c("250", "25","2.5"))), 
+                    labeller = label_parsed) + 
+ guides(linetype = "none") +
+   theme_bw() +
+   theme( panel.grid.major = element_blank(),
+          panel.grid.minor = element_blank(),
+     axis.title.x.bottom = element_text(size = 16, color = "black", vjust = 1.0),
+      axis.title.y = element_text(size = 16, color = "black", vjust = 1.0),
+       axis.title.x.top = element_text(size = 16, color = "black", vjust = 1.0),
+       axis.text.x = element_text(size = 12, color = "black", angle = 0, hjust = 0.5, vjust = 1),
+        axis.text.y = element_text(size = 12, color = "black", angle = 0, hjust = 1.0),
+       axis.text.x.top = element_blank(),
+       axis.ticks.x.top = element_blank(),
+       strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=12),
+        # strip.background=element_rect(color="grey87", fill = "grey82"),
+        # strip.background=element_rect(fill = "white"),
+        legend.key.size = unit(1, 'cm'), #change legend key size
+        legend.key.height = unit(1, 'cm'), #change legend key height
+        legend.key.width = unit(0.5, 'cm'), #change legend key width
+        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
+        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
+        legend.title = element_text(size = 16),  #change legend title font size
+        legend.text = element_text(size = 12),   #change legend text font size
+        legend.position = "top") +
+  labs(color = "Growth wavelength (nm)",
+       fill = "Growth wavelength (nm)")
+MED4PAR
+
+```
+
+``` {r MED4GAM Plot Blue WL 250, fig.height=5, fig.width=5}
+GamStrain = "MED4" 
+GamColor = "Blue"
+WL_nm = 450 
+PlotWL <- "deltaOD"
+data_text <- data.frame(label = c('450 nm, 250 µM'))
+# data_textB <- data.frame(label = c('B'))
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+  #        fit == min(fit, na.rm = TRUE)) %>%
+  # distinct(fit)
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White'))
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+HyperChlPlot <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "250"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "250") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourMED4BlueHigh <- ggplot(na.omit(HyperChlPlot)) + 
+    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
+    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+    geom_text(data=data_text, aes(x=6, y=180, label=label), size=4) +
+     # geom_text(data=data_textB, aes(x=5, y=190, label=label), size=7) +
+   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
+    xlab("Photoperiod (h)") +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
+    # xlab(NULL) +
+    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=12),
+        axis.title = element_text(size=16),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+         axis.title.y = element_blank(),
+         # axis.title.y = element_text(margin=margin(r=10)),
+         axis.title.x = element_blank(),
+        # axis.title.x = element_text(margin=margin(t=10)),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.15,0.30),
+        legend.text = element_text(size=11)))
+
+```
+
+```{r MED4GAM Plot Blue WL 250, fig.height=5, fig.width=5}
+GamStrain = "MED4" 
+GamColor = "Blue"
+WL_nm = 450 
+PlotWL <- "deltaOD"
+data_text <- data.frame(label = c('450 nm, 25 µM'))
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+  #        fit == min(fit, na.rm = TRUE)) %>%
+  # distinct(fit)
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White'))
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+HyperChlPlot <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "25"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "25") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourMED4BlueInt <- ggplot(na.omit(HyperChlPlot)) + 
+    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit)) +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
+    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+    geom_text(data=data_text, aes(x=6, y=180, label=label), size=4) +
+   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
+    xlab("Photoperiod (h)") +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
+    # xlab(NULL) +
+    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=12),
+        axis.title = element_text(size=16),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+         # axis.title.y = element_text(margin=margin(r=10)),
+         axis.title.y = element_blank(),
+        axis.title.x = element_text(margin=margin(t=10)),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.15,0.30),
+        legend.text = element_text(size=11)))
+
+```
+
+``` {r MED4GAM Plot Red WL 250, fig.height=5, fig.width=5}
+GamStrain = "MED4" 
+GamColor = "Red"
+WL_nm = 660 
+PlotWL <- "deltaOD"
+data_textB <- data.frame(label = c('B'))
+data_text <- data.frame(label = c('660 nm, 250 µM'))
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+  #        fit == min(fit, na.rm = TRUE)) %>%
+  # distinct(fit)
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White'))
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+HyperChlPlot <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "250"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "250") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourMED4RedHigh <- ggplot(na.omit(HyperChlPlot)) + 
+    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", w_length2rgb(660)), limits  = range(minMu, 1.0), na.value = "white") +
+    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+    geom_text(data=data_textB, aes(x=5, y=195, label=label), size=7) +
+     geom_text(data=data_text, aes(x=6, y=180, label=label), size=4) +
+  # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
+    xlab("Photoperiod (h)") +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
+    # xlab(NULL) +
+    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=12),
+        axis.title = element_text(size=16),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+         # axis.title.y = element_text(margin=margin(r=10)),
+         axis.title.x = element_blank(),
+        # axis.title.x = element_text(margin=margin(t=10)),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.15,0.30),
+        legend.text = element_text(size=11)))
+
+```
+
+``` {r MED4GAM Plot Red WL 25, fig.height=5, fig.width=5}
+GamStrain = "MED4" 
+GamColor = "Red"
+WL_nm = 660 
+PlotWL <- "deltaOD"
+data_text <- data.frame(label = c('660 nm, 25 µM'))
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+  #        fit == min(fit, na.rm = TRUE)) %>%
+  # distinct(fit)
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White'))
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+HyperChlPlot <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "25"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "25") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourMED4RedInt <- ggplot(na.omit(HyperChlPlot)) + 
+    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit)) +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", w_length2rgb(660)), limits  = range(minMu, 1.0), na.value = "white") +
+    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 200)) +
+    geom_text(data=data_text, aes(x=6, y=180, label=label), size=4) +
+   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
+    xlab("Photoperiod (h)") +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
+    # xlab(NULL) +
+    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=12),
+        axis.title = element_text(size=16),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+         # axis.title.y = element_text(margin=margin(r=10)),
+        # axis.title.y = element_blank(),
+        axis.title.x = element_text(margin=margin(t=10)),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.15,0.30),
+        legend.text = element_text(size=11)))
+
+```
+
+```{r, MED4PARGAM, fig.height = 20, fig.width=10, warning=FALSE}
+
+MED4PARGAM <-  MED4PAR / (ContourMED4RedHigh + ContourMED4BlueHigh)/ (ContourMED4RedInt + ContourMED4BlueInt)
+
+MED4PARGAM
+
 ```
@@
 # MED4GAM,png for manuscript
- ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "GAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = LabelledCombinedGam,  height = 10, width = 10)
+ ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "PARGAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = MED4PARGAM,  height = 15, width = 10)
 
 # MED4GAM is Fig4.tiff for PLOSONE submission
- ggsave(file = file.path(PlotsOutPLOS, "Fig4.tiff", fsep = .Platform$file.sep), plot = LabelledCombinedGam, device = NULL, scale = 1,  height = 10, width = 10, compression = "lzw")
+ ggsave(file = file.path(PlotsOutPLOS, "Fig4.tiff", fsep = .Platform$file.sep), plot = MED4PARGAM, device = NULL, scale = 1,  height = 10, width = 10, compression = "lzw")
 

### 2024-05-22 Output/PLOSFiguresRound1/ResponsetoReviewers.txt
Opening .rtf in Wordpad had formatting issues. Created document in Wordpad, now .txt

PONE-D-24-11318
Prochlorococcus marinus responses to light and oxygen
PLOS ONE

José A. Fernández Robledo, Ph.D. 
Academic Editor 
PLOS ONE

Dear Dr. Fernández Robledo,

We thank you and the reviewers for constructive feedback, which we have addressed through revisions, as outlined below.

•	separate file labeled 'Revised Manuscript with Track Changes'.
•	An unmarked version of your revised paper without tracked changes. You should upload this as a separate file labeled 'Manuscript'.

1. Please ensure that your manuscript meets PLOS ONE's style requirements, including those for file 
naming. The PLOS ONE style templates can be found at  
https://journals.plos.org/plosone/s/file?id=wjVg/PLOSOne_formatting_sample_main_body.pdf and  
https://journals.plos.org/plosone/s/file?id=ba62/PLOSOne_formatting_sample_title_authors_affiliation
s.pdf

2. Please note that PLOS ONE has specific guidelines on code sharing for submissions in which author-
generated code underpins the findings in the manuscript. In these cases, all author-generated code 
must be made available without restrictions upon publication of the work. Please review our guidelines 
at https://journals.plos.org/plosone/s/materials-and-software-sharing#loc-sharing-code and ensure that 
your code is shared in a way that follows best practice and facilitates reproducibility and reuse.
3. Thank you for uploading your study's underlying data set. Unfortunately, the repository you have 
noted in your Data Availability statement does not qualify as an acceptable data repository according to 
PLOS's standards.

At this time, please upload the minimal data set necessary to replicate your study's findings to a stable, 
public repository (such as figshare or Dryad) and provide us with the relevant URLs, DOIs, or accession 
numbers that may be used to access these data. For a list of recommended repositories and additional 
information on PLOS standards for data deposition, please see 
https://journals.plos.org/plosone/s/recommended-repositories.

4. We note that you have referenced (Campbell, unpub) on page 17, which has currently not yet been 
accepted for publication. Please remove this from your References and amend this to state in the body 
of your manuscript: (ie “Bewick et al. [Unpublished]”) as detailed online in our guide for authors 
http://journals.plos.org/plosone/s/submission-guidelines#loc-reference-style

We removed this citation.

5. We notice that your supplementary [Supplemental Figures 1-5 and S1 Table] are included in the 
manuscript file. Please remove them and upload them with the file type 'Supporting Information'. Please 
ensure that each Supporting Information file has a legend listed in the manuscript after the references 
list.

6. Please review your reference list to ensure that it is complete and correct. If you have cited papers 
that have been retracted, please include the rationale for doing so in the manuscript text, or remove 
these references and replace them with relevant current references. Any changes to the reference list 
should be mentioned in the rebuttal letter that accompanies your revised manuscript. If you need to cite 
a retracted article, indicate the article’s retracted status in the References list and also include a citation 
and full reference for the retraction notice.

Reviewers' comments:

Reviewer's Responses to Questions
Comments to the Author

Reviewer #1: This manuscript presents a helpful expansion of our knowledge of the ecological tolerance 
ranges of several Prochlorococcus ecotypes. It is especially interesting in its implications for range 
expansion of this genus under potential future conditions, although this angle could be expanded on in 
my opinion, as I explain below.

Specific Comments:

The abstract seems to omit any discussion of the conclusions/bigger picture of the study.

Line 55: LLII/III and LLIV are not the “oldest” clades, but the most basal or early branching.
We have edited the text:
Line XXX

Line 369: The authors invoke “limitations in the annotation process” to explain the lack of evidence for 
MED4 ATP synthase. What does this mean? The MED4 genome surely contains ATP synthase genes.

We agree that the MED4 genome includes genes encoding ATP Synthase, but in the Ocean Protein Portal database no ATP Synthase peptides are annotated as coming from MED4. This likely reflects an annotation assignment issue because the ATP Synthase proteins are highly conserved, so assignments to strains or clades of Prochlorococcus may be ambiguous.
We have edited the text:
Line XXX:

Paragraph starting L363: Why is there no discussion of the Rubisco data? Or especially the absence 
thereof at low O2 for ecotypes HL1 and LL1? Since Rubisco is one of the most abundant proteins in a 
photosynthesizing cell, does this indicate that these ecotypes are present but not actively fixing carbon 
under these conditions? Also, is it worth noting that LLIV is the only variety to be detected at all in the 
deepest low O2 site -- which would appear to be consistent with subsequent findings in this study?

Figures 3 through 8: These figures are obviously the crux of the results in this paper, but as they are 
currently presented it is relatively difficult to think clearly about them. I feel like they could be combined 
into 2 or 3 full page figures which might make it easier to make the relevant comparisons; either by 
combining the two types of figure (growth rates and model fits) for each ecotype, or else all the growth 
rate curves together in one figure and all the model plots together in another.

Thank you for this suggestion. We have combined the growth rate figure with the GAM model for each strain.

I'm also not sure I understand why the red light data is relevant -- perhaps by moving it to supplemental, 
it would be easier to compile these data into compound figures?

XXXX Want to keep as is. Will add more justification for red light. Reviewer 2 wants more about differences b/t blue and red (energy input from these 2 WL) XXXXX

I also wonder if the data from the model fits could be used to predict which of the three ecotypes would 
prevail (have the highest growth rate) across the parameter space depicted, resulting in another figure 
showing something like "zones of exclusion" for each ecotype, which would be interesting in terms of 
predictive power. One could easily imagine applying those "zones of exclusion" to a map of the actual 
ocean at various depths, or even comparing current with projected future conditions of spreading 
OMZs. This is merely a suggestion -- I don't expect the authors to necessarily do this, but I think if they 
chose to it would make the manuscript of broader interest.

L482, 536, 548: some experiments were not performed “due to time constraints”. I'm not sure I 
understand this, although I am interpreting it along the lines of "the person doing the experiments 
graduated"… In any case, it seems like these particularly treatments were unlikely to grow, so it's not 
important that they were omitted -- but maybe there is a better way to phrase this that doesn’t sound 
so fishy?

Figure S4 — It is very hard to see the fit lines other than the pooled fit. Consider using different colors 
and solid lines since this is online.

Table 1: The trees described in the legend should be included in the supplemental material.

Fig 11: Despite the fact that it is explained in the legend, the figure should probably indicate that O2 
values are log Km, or else put actual values on the log-scale Y axis. Also, the axis should indicate the 
units for Km. Finally, why is the red band so narrow compared to the green and blue?

We apologize for the omissions and have fixed the y-axis label and units. The red band is narrow because the log .........XXX

L757: The authors should specify that this is a DNA repair ligase, not the DNA ligase that seals Okazaki 
fragments during DNA replication (assuming this is the case).

Changed DNA ligase to DNA repair ligase. 
Lines XXX:

L 758: Photolyase should not have been relevant in the lab experiments because there is no UV light 
emitted (AFAIK) by the bulbs used in the Multicultivator. Also, it is unlikely that the absence of these two 
genes is sufficient to explain why these strains can’t grow at the ocean’s surface.

We have edited the text:
Line XXX:

Fig 12: Phosphoglycolate phosphatase is a major enzyme in the photorespiration pathway — what does 
it have to do with DNA repair? There is evidence that 2-phosphoglycolate causes oxidative stress, but I 
don’t think this enzyme is properly a DNA repair enzyme.

Summary and Conclusion: I feel like the authors really need to expand their discussion of how these 
findings apply to the future ocean. Where are OMZs likely to expand? Are there specific examples of 
regions where LLIV might expand to the surface? What would it mean for LLIV to become competitive 
against HLI and HLII? I think this is likely to be similar to scenarios where Synechococcus may 
outcompete Prochlorococcus, since LLIV is quite similar to Syn in terms of size and genome repertoire. 
I'm not sure where exactly such a discussion should end up, but I think it is important that the authors 
try to "seal the deal" a bit better in this concluding section and relate the findings back to the issues laid 
out in the introduction.

Reviewer #2: Savoie et al describe a beautiful and extensive set of detailed Prochlorococcus growth rate 
measurements for three strains, representing distinct ecotypes, under varied conditions of light and 
oxygen concentration. The work adds a lot of interesting and useful information concerning the impact 
of varied photoperiods, wavelengths/PUR, and oxygen concentrations to the literature. These data are 
also connected to hypotheses about the potential role of DNA repair and PSII maintenance to explain 
the results. The methods are appropriately detailed, and the experiments appear to have been done 
with great care. The data are available in a usable form.

My primary concern with the manuscript comes from the way the results are framed throughout. The 
authors describe results as informing about the growth of Prochlorococcus across a matrix of different 
conditions. However, my interpretation of the methods is that the authors took from a maintenance 
culture kept under standard growth conditions and then immediately transferred them into the 
Multicultivator to look at responses. This is of course completely valid, but extensive experience by 
many in the field (e.g. described in Moore et al 2007 Limn. Oceanog. Methods and elsewhere) is that 
these cells typically require multiple generations to acclimate to new growth conditions. I read these 
data as more reflecting the immediate response of Prochlorococcus to environmental changes. It is 
quite conceivable that some of these strains may exhibit a different growth rate than what you report if 
allowed to gradually acclimate to their new condition rather than directly move them. I would suggest 
that the framing and interpretation of the paper should reflect this. I also have no idea whether this 
might have influenced the surprising observations of MIT9313 growth at relatively high PAR. Global 
change scenarios would presumably give cells many generations to physiologically acclimate to 
differences (as well as to evolutionarily adapt).

This reviewer found the manuscript to be quite difficult to read as I kept wanting to understand how 
different strains were responding to similar types of variables, which made me have to constantly flip 
through and reread parts of the manuscript to find the information. Establishing a clearer overall 
summary narrative early on, as opposed to presenting a laundry list of data, might help. For instance, 
more clearly motivating the questions driving the analyses in each section would help; many paragraphs 
simply start with “Figure X shows…”. But, the organization of the paper is of course up to the authors.

Minor points:

General note: the manuscript text at some points refers broadly to “growth”, and other places is more 
specific about drawing conclusions about “growth rate”. I would suggest being clearer in some way that 
you are focused on growth rate and not growth yield.

We edited the text to use 'growth rate' throughout.

40: Despite _its_ small cell size (?)

We have edited the text:
Line XXX:

56: “Affinity” for low light? Consider rephrasing

We have edited the text:
Line XXX:

84: Follett et al 2022 PNAS showed that temp is not the only factor influencing poleward issues - 
ecological interactions may further impact poleward shift during warming

We have edited the text:
Line XXX:

199: Could you please state more about why you are confident in this assignment? What validation or 
metric leads you to this?

209: It seems overly general to blame the culturing difficulties solely on having reduced genomes – in 
this context, it is the lack of just one gene (catalase) that matters, and reduced genomes reflect an 
outcome of the ultimate suite of selective pressures acting on these systems.

We have edited the text:
Line XXX:

363: Could the authors comment somewhere on why you took this proteomic approach to examine the 
baseline distribution of Pro across O2 and depth, as opposed to (or at least in concert with) the 
extensive metagenomic, amplicon, qPCR, etc datasets of ecotype abundances available?

407: growth -> grew?

We have edited the text:
Line XXX:

428: How many replicates were carried out for most experiments? Perhaps I just missed it, but please be 
sure this information is clear in the methods

431, and generally throughout the paper: Would the authors care to comment on any connection 
between the differences in blue vs red light growth and the underlying amount of energy input from 
these different wavelengths?

XXX Energy- blue have shorter WL so high energy, red longer WL so lower energy??? XXXX

Fig 4 and related figures: It might be useful to plot the specific measured points within the countour plot

We have combined the growth rate figure with the GAM model for each strain.

685: The lack of detected FtsH could simply be a factor of low overall spectral counts and detection 
limits in the dataset; please provide more context to help the reader understand whether this could be 
just a small number problem with respect to MIT9313 in low O2 samples; Fig. 10 seems to just show a 
binary detected/not detected value.

### 2024-05-22 Code/Plots_GAM.Rmd
New plots

@@
 
-```
-
-# Plot red light GAM for MED4
-``` {r MED4GAM Plot Red WL}
-GamStrain = "MED4" 
-GamColor = "Red" 
-WL_nm = 660 
-PlotWL <- "deltaOD"
-
-maxMu <- PicoGAM_Pred %>%
-  ungroup() %>%
-  filter(Wavelength %in% PlotWL) %>%
-  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
-maxMu <- maxMu$fit
-
-minMu <- PicoGAM_Pred %>%
-  ungroup() %>%
-  filter(Wavelength %in% PlotWL) %>%
-  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
-  #        fit == min(fit, na.rm = TRUE)) %>%
-  # distinct(fit)
-minMu <- minMu$fit
-
-PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
-  filter(Wavelength %in% PlotWL,
-         Strain %in% GamStrain,
-         WL %in% WL_nm) %>%
-  mutate(
-         Color_name = case_when(WL == "450" ~ 'Blue',
-                                WL == "530" ~ 'Green',
-                                WL == "660" ~ 'Red',
-                                WL == "WW" ~ 'White'))
-
-WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
-
-ColourDF <- data.frame(
-  ColorName = c('Blue', 'Green', 'Red', 'White'),
-  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
-) %>%
-  filter(ColorName %in% GamColor) %>%
-  dplyr::select(WL_O2_Colors)
-
-ContourBreaks <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL
-  ) %>%
-  group_by(O2_uM) %>%
-  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
-         median50 = quantile(fit, 0.5, na.rm = TRUE),
-         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
-  ungroup() %>%
-  dplyr::select(O2_uM, upper10, median50, lower10) %>%
-  distinct() %>%
-  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
-  mutate(quantileValue = round(quantileValue, digits = 2))
-
-##############
-###plot
-#https://stackoverflow.com/questions/28775036/ggplot-line-graph-with-na-values
-#https://stackoverflow.com/questions/6906661/ggplot2-make-missing-value-in-geom-tile-not-blank
-#https://stackoverflow.com/questions/24822621/multiple-legends-in-a-plot-with-geom-tile
-#https://stackoverflow.com/questions/43395219/plotting-multiple-layers-with-geom-raster-or-geom-tile-or-geom-rect
-#https://stackoverflow.com/questions/59949635/ggplot-align-grid-lines-with-end-of-geom-tile
-#https://stackoverflow.com/questions/22945651/remove-space-between-plotted-data-and-the-axes
-#https://stackoverflow.com/questions/5293715/how-to-use-greek-symbols-in-ggplot2
-
-HyperChlPlotLow <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL,
-         O2_uM == "2.5"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "2.5") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-     xlab(NULL)+
-      ylab(NULL)+
-    theme_classic() +
-    theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35)))
-
-HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL,
-         O2_uM == "25"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "25") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    xlab(NULL)+
-      ylab(NULL)+
-   theme_classic() +
-  theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=23)))
-
-HyperChlPlotHigh <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL,
-         O2_uM == "250"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "250") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    xlab(NULL)+
-      ylab(NULL)+
-    #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
-    theme_classic() +
-   theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35)))
-
-g_legend<-function(a.gplot){
-  tmp <- ggplot_gtable(ggplot_build(a.gplot))
-  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
-  legend <- tmp$grobs[[leg]]
-  legend
-}
-
-(g_dummy1 <- ggplot(subset(HyperChlPlotLow, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
-+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
-  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend1 <- g_legend(g_dummy1)
-(g_dummy2 <- ggplot(subset(HyperChlPlotInt, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
-+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
-  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend2 <- g_legend(g_dummy2)
-(g_dummy3 <- ggplot(subset(HyperChlPlotHigh, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
-+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
-  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend3 <- g_legend(g_dummy3)
-
-# comment rows that are not included in grid arrange 
-LayoutNiche <- rbind(
-                      # c(3, 3, 3, 3, 6), # For 2.5 uM O2     # remove comment if want 2.5 uM O2 plotted
-                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2    # remove comment if want 2.5 uM O2 plotted
-                     c(2, 2, 2, 2, 5),   # For 25 uM O2
-                     c(2, 2, 2, 2, 5),   # For 25 uM O2
-                     c(1, 1, 1, 1, 4),   # For 250 uM O2
-                     c(1, 1, 1, 1, 4)    # For 250 uM O2
-                     )
-
-#LayoutNiche <- rbind(c(1, 1, 1, 2, 2, 2, 3, 3, 3, 4))
-
-p3_Red <- grid.arrange(
-                       # ContourLowO2 +   labs(title = bquote("C.
-" ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + theme(legend.position = 'none'),   # remove comment if want 2.5 uM O2 plotted
-                       ContourIntO2 + labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
-                         theme(legend.position = 'none'), 
-                       ContourHighO2 + labs(title = bquote("A.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
-                         theme(legend.position = 'none'),
-                       # legend1,   # remove comment if want 2.5 uM O2 plotted
-                        legend2, 
-                        legend3, 
-                       layout_matrix = LayoutNiche)
-
-```
-
-# Plot blue light GAM for MED4
-``` {r MED4GAM Plot Blue WL}
-GamStrain = "MED4" 
-GamColor = "Blue"
-WL_nm = 450 
-PlotWL <- "deltaOD"
-
-maxMu <- PicoGAM_Pred %>%
-  ungroup() %>%
-  filter(Wavelength %in% PlotWL) %>%
-  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
-maxMu <- maxMu$fit
-
-minMu <- PicoGAM_Pred %>%
-  ungroup() %>%
-  filter(Wavelength %in% PlotWL) %>%
-  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
-  #        fit == min(fit, na.rm = TRUE)) %>%
-  # distinct(fit)
-minMu <- minMu$fit
-
-PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
-  filter(Wavelength %in% PlotWL,
-         Strain %in% GamStrain,
-         WL %in% WL_nm) %>%
-  mutate(
-         Color_name = case_when(WL == "450" ~ 'Blue',
-                                WL == "530" ~ 'Green',
-                                WL == "660" ~ 'Red',
-                                WL == "WW" ~ 'White'))
-
-WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
-
-ColourDF <- data.frame(
-  ColorName = c('Blue', 'Green', 'Red', 'White'),
-  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
-) %>%
-  filter(ColorName %in% GamColor) %>%
-  dplyr::select(WL_O2_Colors)
-
-ContourBreaks <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL
-  ) %>%
-  group_by(O2_uM) %>%
-  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
-         median50 = quantile(fit, 0.5, na.rm = TRUE),
-         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
-  ungroup() %>%
-  dplyr::select(O2_uM, upper10, median50, lower10) %>%
-  distinct() %>%
-  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
-  mutate(quantileValue = round(quantileValue, digits = 2))
-
-##############
-###plot
-#https://stackoverflow.com/questions/28775036/ggplot-line-graph-with-na-values
-#https://stackoverflow.com/questions/6906661/ggplot2-make-missing-value-in-geom-tile-not-blank
-#https://stackoverflow.com/questions/24822621/multiple-legends-in-a-plot-with-geom-tile
-#https://stackoverflow.com/questions/43395219/plotting-multiple-layers-with-geom-raster-or-geom-tile-or-geom-rect
-#https://stackoverflow.com/questions/59949635/ggplot-align-grid-lines-with-end-of-geom-tile
-#https://stackoverflow.com/questions/22945651/remove-space-between-plotted-data-and-the-axes
-#https://stackoverflow.com/questions/5293715/how-to-use-greek-symbols-in-ggplot2
-
-HyperChlPlotLow <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL,
-         O2_uM == "2.5"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "2.5") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    xlab(NULL)+
-      ylab(NULL)+
-   theme_classic() +
-   theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35)))
-
-HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL,
-         O2_uM == "25"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "25") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200))  +
-    labs(title = bquote("D.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
-    xlab("Photoperiod (h)") +
-      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
-    # xlab(NULL)+
-    #   ylab(NULL)+ 
-  theme_classic() +
-   theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35)))
-
-HyperChlPlotHigh <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL,
-         O2_uM == "250"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "250") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
-    xlab("Photoperiod (h)") +
-      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
-    # xlab(NULL) +
-    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
-theme_classic() +
-   theme(axis.text=element_text(size=15),
-         axis.title.x = element_blank(),
-         axis.text.x = element_blank(),
-          # axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35)))
-
-g_legend<-function(a.gplot){
-  tmp <- ggplot_gtable(ggplot_build(a.gplot))
-  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
-  legend <- tmp$grobs[[leg]]
-  legend
-}
-
-(g_dummy1 <- ggplot(subset(HyperChlPlotLow, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
- + scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"),
- limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend1 <- g_legend(g_dummy1)
-(g_dummy2 <- ggplot(subset(HyperChlPlotInt, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
- + scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"),
-  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend2 <- g_legend(g_dummy2)
-(g_dummy3 <- ggplot(subset(HyperChlPlotHigh, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
-+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"),
-  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend3 <- g_legend(g_dummy3)
-
-# comment rows that are not included in grid arrange 
-LayoutNiche <- rbind(
-                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2   # remove comment if want 2.5 uM O2
-                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2   # remove comment if want 2.5 uM O2
-                     c(2, 2, 2, 2, 5),   # For 25 uM O2
-                     c(2, 2, 2, 2, 5),   # For 25 uM O2
-                     c(1, 1, 1, 1, 4),   # For 250 uM O2
-                     c(1, 1, 1, 1, 4)    # For 250 uM O2
-                     )
-
-#LayoutNiche <- rbind(c(1, 1, 1, 2, 2, 2, 3, 3, 3, 4))
-
-p3_Blue <- grid.arrange(
-                         # ContourLowO2 +   labs(title = bquote("F.
-" ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()),
-                        ContourIntO2 +  labs(title = bquote("D.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
-                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
-                        ContourHighO2 + labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
-                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()),
-                        # legend1,    # remove comment if want 2.5 uM O2
-                        legend2, 
-                        legend3, 
-                        layout_matrix = LayoutNiche)
-
-```
-
-```{r combine red and blue light MED4GAM plots}
-
-#combine red and blue GAM plots
-CombinedGAM <- plot_grid(p3_Red, p3_Blue, nrow = 1, align = "v")
-
-# common x-axis title
-x.grob <- textGrob("Photoperiod (h)", 
-                   gp = gpar(fontsize = 20))
-# common y-axis title
-y.grob <- textGrob("PAR (µmol photons"~ m^-2~ ~s^-1~ ")", 
-                   gp = gpar(fontface="bold", fontsize = 20), rot = 90)
-
-# add titles to plot
-LabelledCombinedGam <- grid.arrange(arrangeGrob(CombinedGAM, left = y.grob, bottom = x.grob))
-
-test <-  plot_grid(MED4PAR, LabelledCombinedGam, labels = "AUTO", ncol = 1) 
-test
 ```
@@
     scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    geom_text(data=data_text, aes(x=6, y=180, label=label), size=4) +
+    scale_y_continuous(limits = c(10, 205)) +
+    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
      # geom_text(data=data_textB, aes(x=5, y=190, label=label), size=7) +
@@
 
-```{r MED4GAM Plot Blue WL 250, fig.height=5, fig.width=5}
+```{r MED4GAM Plot Blue WL 25, fig.height=5, fig.width=5}
 GamStrain = "MED4" 
@@
     scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    geom_text(data=data_text, aes(x=6, y=180, label=label), size=4) +
+    scale_y_continuous(limits = c(10, 205)) +
+    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
    # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
@@
     scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    geom_text(data=data_textB, aes(x=5, y=195, label=label), size=7) +
-     geom_text(data=data_text, aes(x=6, y=180, label=label), size=4) +
+    scale_y_continuous(limits = c(10, 205)) +
+    geom_text(data=data_textB, aes(x=5, y=205, label=label), size=7) +
+     geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
@@
 
-```{r save MED4GAM plots}
+```{r save MED4PARGAM plots}
 # MED4GAM,png for manuscript
@@
 
-# Plot red light GAM for SS120
-``` {r SS120GAM Plot Red WL}
+```{r, SS120PAR, fig.height=10, fig.width=10}
+MyWavelengths = c("WW", 660, 450)
+
+MCMIXColours = c("black", "brown", "steelblue")
+
+names(MCMIXColours) <- MyWavelengths
+MCMIXColours
+
+  data_text <- data.frame( ParLabel=c("PAR~(µmol~photons~m^{-2}~s^{-1})"), OxygenLabel = c("Oxygen~concentration~(µM)"),Par_ue = c("30"), O2_uM = c("250"), label = c('A'))
+
+SS120PAR <- GrowthFits %>%
+   filter(Strain == "SS120",
+           Par_ue %in% c(30,90,180),
+          WL %in% c("WW", 450, 660),
+          deltaOD_Lmu_corr == 0 |
+          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
+  mutate(PhotoperiodLabelTitle = "Photoperiod~(h)",
+         OxygenLabel = "Oxygen~concentration~(µM)",
+         WLlabelTitle = "Growth~wavelength~(nm)",
+         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
+         # Par_ue = factor(Par_ue, levels = c(30, 90, 180)),
+         # O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         WL = factor(WL, levels = c("WW", 660, 530, 450)),
+         deltaOD_Lmu_corr_day = deltaOD_Lmu_corr * 24,
+         deltaOD_Lmu_se_day = deltaOD_Lmu_se * 24) %>% 
+  ggplot()  +
+    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.75, show.legend = F) +
+   geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5, show.legend = F) +
+    geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 1) +
+    geom_text(data=data_text, aes(x=5.5, y=0.8, label=label), size=7) +
+ labs( y = "Chlorophyll specific growth rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
+   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3, show.legend = F) +
+  scale_y_continuous(breaks = c(0,0.25,  0.5, 0.75, 1.0), limits = c (0, 1.05)) +
+  # coord_cartesian(ylim = c (0, 0.07)) +
+  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
+   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
+  ggh4x::facet_nested(cols = vars(ParLabel, factor(Par_ue, levels = c("30", "90","180"))), rows = vars(OxygenLabel, factor(O2_uM, levels= c("250", "25","2.5"))), 
+                    labeller = label_parsed) + 
+ guides(linetype = "none") +
+   theme_bw() +
+   theme( panel.grid.major = element_blank(),
+          panel.grid.minor = element_blank(),
+     axis.title.x.bottom = element_text(size = 16, color = "black", vjust = 1.0),
+      axis.title.y = element_text(size = 16, color = "black", vjust = 1.0),
+       axis.title.x.top = element_text(size = 16, color = "black", vjust = 1.0),
+       axis.text.x = element_text(size = 12, color = "black", angle = 0, hjust = 0.5, vjust = 1),
+        axis.text.y = element_text(size = 12, color = "black", angle = 0, hjust = 1.0),
+       axis.text.x.top = element_blank(),
+       axis.ticks.x.top = element_blank(),
+       strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=12),
+        # strip.background=element_rect(color="grey87", fill = "grey82"),
+        # strip.background=element_rect(fill = "white"),
+        legend.key.size = unit(1, 'cm'), #change legend key size
+        legend.key.height = unit(1, 'cm'), #change legend key height
+        legend.key.width = unit(0.5, 'cm'), #change legend key width
+        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
+        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
+        legend.title = element_text(size = 16),  #change legend title font size
+        legend.text = element_text(size = 12),   #change legend text font size
+        legend.position = "top") +
+  labs(color = "Growth wavelength (nm)",
+       fill = "Growth wavelength (nm)")
+SS120PAR
+
+```
+
+``` {r SS120GAM Plot Blue WL 250, fig.height=5, fig.width=5}
 GamStrain = "SS120" 
-GamColor = "Red" 
-WL_nm = 660 
+GamColor = "Blue"
+WL_nm = 450 
 PlotWL <- "deltaOD"
+data_text <- data.frame(label = c('450 nm, 250 µM'))
+# data_textB <- data.frame(label = c('B'))
 
@@
 
-##############
-###plot
-#https://stackoverflow.com/questions/28775036/ggplot-line-graph-with-na-values
-#https://stackoverflow.com/questions/6906661/ggplot2-make-missing-value-in-geom-tile-not-blank
-#https://stackoverflow.com/questions/24822621/multiple-legends-in-a-plot-with-geom-tile
-#https://stackoverflow.com/questions/43395219/plotting-multiple-layers-with-geom-raster-or-geom-tile-or-geom-rect
-#https://stackoverflow.com/questions/59949635/ggplot-align-grid-lines-with-end-of-geom-tile
-#https://stackoverflow.com/questions/22945651/remove-space-between-plotted-data-and-the-axes
-#https://stackoverflow.com/questions/5293715/how-to-use-greek-symbols-in-ggplot2
-
-HyperChlPlotLow <- PicoGAM_Plot_Prep %>%
+HyperChlPlot <- PicoGAM_Plot_Prep %>%
   filter(
@@
          Wavelength %in% PlotWL,
-         O2_uM == "2.5"
+         O2_uM == "250"
   )
 ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "2.5") 
+  filter(O2_uM == "250") 
 ContourLines <- ContourLines$quantileValue
 
-(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
+(ContourSS120BlueHigh <- ggplot(na.omit(HyperChlPlot)) + 
+    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
+    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
                         breaks = ContourLines,
@@
     scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-     xlab(NULL)+
-    theme_classic() +
-    theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35)))
-
-HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL,
-         O2_uM == "25"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "25") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    xlab(NULL)+
-      ylab(NULL)+
-   theme_classic() +
-  theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=23)))
-
-HyperChlPlotHigh <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL,
-         O2_uM == "250"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "250") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    xlab(NULL)+
-      ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
-    theme_classic() +
-   theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35)))
-
-g_legend<-function(a.gplot){
-  tmp <- ggplot_gtable(ggplot_build(a.gplot))
-  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
-  legend <- tmp$grobs[[leg]]
-  legend
-}
-
-(g_dummy1 <- ggplot(subset(HyperChlPlotLow, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
-+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
-  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend1 <- g_legend(g_dummy1)
-(g_dummy2 <- ggplot(subset(HyperChlPlotInt, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
-+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
-  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend2 <- g_legend(g_dummy2)
-(g_dummy3 <- ggplot(subset(HyperChlPlotHigh, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
-+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
-  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend3 <- g_legend(g_dummy3)
-
-# comment rows that are not included in grid arrange 
-LayoutNiche <- rbind(
-                      # c(3, 3, 3, 3, 6), # For 2.5 uM O2     # remove comment if want 2.5 uM O2
-                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2    # remove comment if want 2.5 uM O2
-                     c(2, 2, 2, 2, 5),   # For 25 uM O2
-                     c(2, 2, 2, 2, 5),   # For 25 uM O2
-                     c(1, 1, 1, 1, 4),   # For 250 uM O2
-                     c(1, 1, 1, 1, 4)    # For 250 uM O2
-                     )
-
-#LayoutNiche <- rbind(c(1, 1, 1, 2, 2, 2, 3, 3, 3, 4))
-
-p3_Red <- grid.arrange(
-                       # ContourLowO2 +   labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + theme(legend.position = 'none'),   # remove comment for MIT9313
-                       ContourIntO2 + labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
-                         theme(legend.position = 'none'), 
-                       ContourHighO2 + labs(title = bquote("A.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
-                         theme(legend.position = 'none'),
-                       # legend1,   # remove comment if want 2.5 uM O2
-                        legend2, 
-                        legend3, 
-                       layout_matrix = LayoutNiche)
-
-```
-
-# Plot blue light SS120GAM
-``` {r GAM Plot Blue WL}
+    scale_y_continuous(limits = c(10, 205)) +
+    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
+     # geom_text(data=data_textB, aes(x=5, y=190, label=label), size=7) +
+   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
+    xlab("Photoperiod (h)") +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
+    # xlab(NULL) +
+    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=12),
+        axis.title = element_text(size=16),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+         axis.title.y = element_blank(),
+         # axis.title.y = element_text(margin=margin(r=10)),
+         axis.title.x = element_blank(),
+        # axis.title.x = element_text(margin=margin(t=10)),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.15,0.30),
+        legend.text = element_text(size=11)))
+
+```
+
+```{r SS120GAM Plot Blue WL 25, fig.height=5, fig.width=5}
 GamStrain = "SS120" 
@@
 PlotWL <- "deltaOD"
+data_text <- data.frame(label = c('450 nm, 25 µM'))
 
@@
          Wavelength %in% PlotWL,
-         O2_uM == "2.5"
+         O2_uM == "25"
   )
 ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "2.5") 
+  filter(O2_uM == "25") 
 ContourLines <- ContourLines$quantileValue
 
-(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
+(ContourSS120BlueInt <- ggplot(na.omit(HyperChlPlot)) + 
+    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit)) +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
+    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
                         breaks = ContourLines,
@@
     scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    xlab(NULL)+
-      ylab(NULL)+
-   theme_classic() +
-   theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35)))
-
-HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL,
-         O2_uM == "25"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "25") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    xlab(NULL)+
-      ylab(NULL)+
-  theme_classic() +
-   theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35)))
-
-HyperChlPlotHigh <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         #DM == "Chl",
-         Wavelength %in% PlotWL,
-         O2_uM == "250"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "250") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    xlab(NULL)+
-      ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
-theme_classic() +
-   theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35)))
-
-g_legend<-function(a.gplot){
-  tmp <- ggplot_gtable(ggplot_build(a.gplot))
-  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
-  legend <- tmp$grobs[[leg]]
-  legend
-}
-
-(g_dummy1 <- ggplot(subset(HyperChlPlotLow, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
- + scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"),
- limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend1 <- g_legend(g_dummy1)
-(g_dummy2 <- ggplot(subset(HyperChlPlotInt, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
- + scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"),
-  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend2 <- g_legend(g_dummy2)
-(g_dummy3 <- ggplot(subset(HyperChlPlotHigh, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
-+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"),
-  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend3 <- g_legend(g_dummy3)
-
-# comment rows that are not included in grid arrange 
-LayoutNiche <- rbind(
-                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2   # remove comment if want 2.5 uM O2
-                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2   # remove comment if want 2.5 uM O2
-                     c(2, 2, 2, 2, 5),   # For 25 uM O2
-                     c(2, 2, 2, 2, 5),   # For 25 uM O2
-                     c(1, 1, 1, 1, 4),   # For 250 uM O2
-                     c(1, 1, 1, 1, 4)    # For 250 uM O2
-                     )
-
-#LayoutNiche <- rbind(c(1, 1, 1, 2, 2, 2, 3, 3, 3, 4))
-
-p3_Blue <- grid.arrange(
-                         # ContourLowO2 + labs(title = bquote("F.
-" ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()),  # remove comment if want 2.5 uM O2
-                        ContourIntO2 +  labs(title = bquote("D.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
-                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
-                        ContourHighO2 + labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
-                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()),
-                        # legend1,    # remove comment if want 2.5 uM O2
-                        legend2, 
-                        legend3, 
-                        layout_matrix = LayoutNiche)
-
-```
-
-```{r combine red and blue light SS120GAM plots}
-
-#combine red and blue GAM plots
-CombinedGAM <- plot_grid(p3_Red, p3_Blue, nrow = 1, align = "v")
-
-# common x-axis title
-x.grob <- textGrob("Photoperiod (h)", 
-                   gp = gpar(fontsize = 20))
-# common y-axis title
-y.grob <- textGrob("PAR (µmol photons"~ m^-2~ ~s^-1~ ")", 
-                   gp = gpar(fontface="bold", fontsize = 20), rot = 90)
-
-# add titles to plot
-LabelledCombinedGam <- grid.arrange(arrangeGrob(CombinedGAM, left = y.grob, bottom = x.grob))
-
-```
-
-```{r save SS120GAM plots}
-
-# SS120GAM.png for manuscript
- ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "GAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = LabelledCombinedGam,  height = 10, width = 10)
-
-# SS120GAM is Fig6.tiff for PLOSONE submission
- ggsave(file = file.path(PlotsOutPLOS, "Fig6.tiff", fsep = .Platform$file.sep), plot = LabelledCombinedGam, device = NULL, scale = 1,  height = 10, width = 10, compression = "lzw")
-
-```
-
-# Plot red light MIT9313 GAM
-``` {r MIT9313GAM Plot Red WL}
-GamStrain = "MIT9313"
+    scale_y_continuous(limits = c(10, 205)) +
+    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
+   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
+    xlab("Photoperiod (h)") +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
+    # xlab(NULL) +
+    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=12),
+        axis.title = element_text(size=16),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+         # axis.title.y = element_text(margin=margin(r=10)),
+         axis.title.y = element_blank(),
+        axis.title.x = element_text(margin=margin(t=10)),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.88,0.81),
+        legend.text = element_text(size=11)))
+
+```
+
+``` {r SS120GAM Plot Red WL 250, fig.height=5, fig.width=5}
+GamStrain = "SS120" 
 GamColor = "Red"
@@
 PlotWL <- "deltaOD"
+data_textB <- data.frame(label = c('B'))
+data_text <- data.frame(label = c('660 nm, 250 µM'))
 
@@
          Wavelength %in% PlotWL,
-         O2_uM == "2.5"
+         O2_uM == "250"
   )
 ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "2.5") 
+  filter(O2_uM == "250") 
 ContourLines <- ContourLines$quantileValue
 
-(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
+(ContourSS120RedHigh <- ggplot(na.omit(HyperChlPlot)) + 
+    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", w_length2rgb(660)), limits  = range(minMu, 1.0), na.value = "white") +
+    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
                         breaks = ContourLines,
@@
     scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-     xlab(NULL)+
-      ylab(NULL)+
-    theme_classic() +
-    theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35)))
-
-HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL,
-         O2_uM == "25"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "25") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    xlab(NULL)+
-      ylab(NULL)+
-   theme_classic() +
-  theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=23)))
-
-HyperChlPlotHigh <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL,
-         O2_uM == "250"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "250") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    xlab(NULL)+
-      ylab(NULL)+
-    #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
-    theme_classic() +
-   theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35)))
-
-g_legend<-function(a.gplot){
-  tmp <- ggplot_gtable(ggplot_build(a.gplot))
-  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
-  legend <- tmp$grobs[[leg]]
-  legend
-}
-
-(g_dummy1 <- ggplot(subset(HyperChlPlotLow, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
-+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
-  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend1 <- g_legend(g_dummy1)
-(g_dummy2 <- ggplot(subset(HyperChlPlotInt, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
-+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
-  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend2 <- g_legend(g_dummy2)
-(g_dummy3 <- ggplot(subset(HyperChlPlotHigh, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
-+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
-  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend3 <- g_legend(g_dummy3)
-
-# comment rows that are not included in grid arrange 
-LayoutNiche <- rbind(
-                     c(3, 3, 3, 3, 6), # For 2.5 uM O2    
-                     c(3, 3, 3, 3, 6), # For 2.5 uM O2  
-                     c(2, 2, 2, 2, 5),   # For 25 uM O2
-                     c(2, 2, 2, 2, 5),   # For 25 uM O2
-                     c(1, 1, 1, 1, 4),   # For 250 uM O2
-                     c(1, 1, 1, 1, 4)    # For 250 uM O2
-                     )
-
-#LayoutNiche <- rbind(c(1, 1, 1, 2, 2, 2, 3, 3, 3, 4))
-
-p3_Red <- grid.arrange(
-                       ContourLowO2 + labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
-                         theme(legend.position = 'none'),  
-                       ContourIntO2 + labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
-                         theme(legend.position = 'none'), 
-                       ContourHighO2 + labs(title = bquote("A.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
-                         theme(legend.position = 'none'), 
-                        legend1, 
-                        legend2, 
-                        legend3, 
-                       layout_matrix = LayoutNiche)
-
-```
-
-# Plot blue light MIT9313 GAM
-``` {r MIT9313GAM Plot Blue WL}
-GamStrain = "MIT9313"
-GamColor = "Blue"
-WL_nm = 450 
+    scale_y_continuous(limits = c(10, 205)) +
+    geom_text(data=data_textB, aes(x=5, y=205, label=label), size=7) +
+     geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
+  # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
+    xlab("Photoperiod (h)") +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
+    # xlab(NULL) +
+    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=12),
+        axis.title = element_text(size=16),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+         # axis.title.y = element_text(margin=margin(r=10)),
+         axis.title.x = element_blank(),
+        # axis.title.x = element_text(margin=margin(t=10)),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.15,0.30),
+        legend.text = element_text(size=11)))
+
+```
+
+``` {r SS120GAM Plot Red WL 25, fig.height=5, fig.width=5}
+GamStrain = "SS120" 
+GamColor = "Red"
+WL_nm = 660 
 PlotWL <- "deltaOD"
+data_text <- data.frame(label = c('660 nm, 25 µM'))
 
@@
 
-##############
-###plot
-#https://stackoverflow.com/questions/28775036/ggplot-line-graph-with-na-values
-#https://stackoverflow.com/questions/6906661/ggplot2-make-missing-value-in-geom-tile-not-blank
-#https://stackoverflow.com/questions/24822621/multiple-legends-in-a-plot-with-geom-tile
-#https://stackoverflow.com/questions/43395219/plotting-multiple-layers-with-geom-raster-or-geom-tile-or-geom-rect
-#https://stackoverflow.com/questions/59949635/ggplot-align-grid-lines-with-end-of-geom-tile
-#https://stackoverflow.com/questions/22945651/remove-space-between-plotted-data-and-the-axes
-#https://stackoverflow.com/questions/5293715/how-to-use-greek-symbols-in-ggplot2
-
-HyperChlPlotLow <- PicoGAM_Plot_Prep %>%
+HyperChlPlot <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "25"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "25") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourSS120RedInt <- ggplot(na.omit(HyperChlPlot)) + 
+    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit)) +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", w_length2rgb(660)), limits  = range(minMu, 1.0), na.value = "white") +
+    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 205)) +
+    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
+   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
+    xlab("Photoperiod (h)") +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
+    # xlab(NULL) +
+    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=12),
+        axis.title = element_text(size=16),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+         # axis.title.y = element_text(margin=margin(r=10)),
+        # axis.title.y = element_blank(),
+        axis.title.x = element_text(margin=margin(t=10)),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.88,0.81),
+        legend.text = element_text(size=11)))
+
+```
+
+```{r, SS120PARGAM, fig.height = 20, fig.width=10, warning=FALSE}
+
+SS120PARGAM <-  SS120PAR / (ContourSS120RedHigh + ContourSS120BlueHigh)/ (ContourSS120RedInt + ContourSS120BlueInt)
+
+SS120PARGAM
+
+```
+
+```{r save SS120GAM plots}
+
+# SS120GAM.png for manuscript
+ ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "PARGAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = SS120PARGAM,  height = 15, width = 10)
+
+# SS120GAM is Fig6.tiff for PLOSONE submission
+ ggsave(file = file.path(PlotsOutPLOS, "Fig6.tiff", fsep = .Platform$file.sep), plot = LabelledCombinedGam, device = NULL, scale = 1,  height = 10, width = 10, compression = "lzw")
+
+```
+
+```{r, MIT9313PAR, fig.height=10, fig.width=10}
+MyWavelengths = c("WW", 660, 450)
+
+MCMIXColours = c("black", "brown", "steelblue")
+
+names(MCMIXColours) <- MyWavelengths
+MCMIXColours
+
+  data_text <- data.frame( ParLabel=c("PAR~(µmol~photons~m^{-2}~s^{-1})"), OxygenLabel = c("Oxygen~concentration~(µM)"),Par_ue = c("30"), O2_uM = c("250"), label = c('A'))
+
+MIT9313PAR <- GrowthFits %>%
+   filter(Strain == "MIT9313",
+           Par_ue %in% c(30,90,180),
+          WL %in% c("WW", 450, 660),
+          deltaOD_Lmu_corr == 0 |
+          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
+  mutate(PhotoperiodLabelTitle = "Photoperiod~(h)",
+         OxygenLabel = "Oxygen~concentration~(µM)",
+         WLlabelTitle = "Growth~wavelength~(nm)",
+         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
+         # Par_ue = factor(Par_ue, levels = c(30, 90, 180)),
+         # O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         WL = factor(WL, levels = c("WW", 660, 530, 450)),
+         deltaOD_Lmu_corr_day = deltaOD_Lmu_corr * 24,
+         deltaOD_Lmu_se_day = deltaOD_Lmu_se * 24) %>% 
+  ggplot()  +
+    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.75, show.legend = F) +
+   geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5, show.legend = F) +
+    geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 1) +
+    geom_text(data=data_text, aes(x=5.5, y=0.8, label=label), size=7) +
+ labs( y = "Chlorophyll specific growth rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
+   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3, show.legend = F) +
+  scale_y_continuous(breaks = c(0,0.25,  0.5, 0.75, 1.0), limits = c (0, 1.05)) +
+  # coord_cartesian(ylim = c (0, 0.07)) +
+  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
+   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
+  ggh4x::facet_nested(cols = vars(ParLabel, factor(Par_ue, levels = c("30", "90","180"))), rows = vars(OxygenLabel, factor(O2_uM, levels= c("250", "25","2.5"))), 
+                    labeller = label_parsed) + 
+ guides(linetype = "none") +
+   theme_bw() +
+   theme( panel.grid.major = element_blank(),
+          panel.grid.minor = element_blank(),
+     axis.title.x.bottom = element_text(size = 16, color = "black", vjust = 1.0),
+      axis.title.y = element_text(size = 16, color = "black", vjust = 1.0),
+       axis.title.x.top = element_text(size = 16, color = "black", vjust = 1.0),
+       axis.text.x = element_text(size = 12, color = "black", angle = 0, hjust = 0.5, vjust = 1),
+        axis.text.y = element_text(size = 12, color = "black", angle = 0, hjust = 1.0),
+       axis.text.x.top = element_blank(),
+       axis.ticks.x.top = element_blank(),
+       strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=12),
+        # strip.background=element_rect(color="grey87", fill = "grey82"),
+        # strip.background=element_rect(fill = "white"),
+        legend.key.size = unit(1, 'cm'), #change legend key size
+        legend.key.height = unit(1, 'cm'), #change legend key height
+        legend.key.width = unit(0.5, 'cm'), #change legend key width
+        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
+        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
+        legend.title = element_text(size = 16),  #change legend title font size
+        legend.text = element_text(size = 12),   #change legend text font size
+        legend.position = "top") +
+  labs(color = "Growth wavelength (nm)",
+       fill = "Growth wavelength (nm)")
+MIT9313PAR
+
+```
+
+``` {r MIT9313GAM Plot Blue WL 250, fig.height=4.5, fig.width=4.5}
+GamStrain = "MIT9313" 
+GamColor = "Blue"
+WL_nm = 450 
+PlotWL <- "deltaOD"
+data_text <- data.frame(label = c('450 nm, 250 µM'))
+# data_textB <- data.frame(label = c('B'))
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White'))
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+HyperChlPlot <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "250"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "250") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourMIT9313BlueHigh <- ggplot(na.omit(HyperChlPlot)) + 
+    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
+    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 205)) +
+    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
+    xlab("Photoperiod (h)") +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
+#https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=12),
+        axis.title = element_text(size=16),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+         axis.title.y = element_blank(),
+         axis.title.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.15,0.30),
+        legend.text = element_text(size=11)))
+
+```
+
+```{r MIT9313GAM Plot Blue WL 25, fig.height=4.5, fig.width=4.5}
+GamStrain = "MIT9313" 
+GamColor = "Blue"
+WL_nm = 450 
+PlotWL <- "deltaOD"
+data_text <- data.frame(label = c('450 nm, 25 µM'))
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White'))
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+HyperChlPlot <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "25"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "25") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourMIT9313BlueInt <- ggplot(na.omit(HyperChlPlot)) + 
+    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
+    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 205)) +
+    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=12),
+        axis.title = element_text(size=16),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+         axis.title.y = element_blank(),
+         axis.title.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.88,0.81),
+        legend.text = element_text(size=11)))
+
+```
+
+```{r MIT9313GAM Plot Blue WL 2.5, fig.height=4.5, fig.width=4.5}
+GamStrain = "MIT9313" 
+GamColor = "Blue"
+WL_nm = 450 
+PlotWL <- "deltaOD"
+data_text <- data.frame(label = c('450 nm, 2.5 µM'))
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White'))
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+HyperChlPlot <- PicoGAM_Plot_Prep %>%
   filter(
@@
 
-(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
+(ContourMIT9313BlueLow <- ggplot(na.omit(HyperChlPlot)) + 
+    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = T) +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
+    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
                         breaks = ContourLines,
@@
     scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    xlab(NULL)+
-      ylab(NULL)+
-   theme_classic() +
-   theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35)))
-
-HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
+    scale_y_continuous(limits = c(10, 205)) +
+    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
+    xlab("Photoperiod (h)") +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=12),
+        axis.title = element_text(size=16),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+         axis.title.y = element_blank(),
+        axis.title.x = element_text(margin=margin(t=10)),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.88,0.76),
+        legend.text = element_text(size=11)))
+
+```
+
+``` {r MIT9313GAM Plot Red WL 250, fig.height=4.5, fig.width=4.5}
+GamStrain = "MIT9313" 
+GamColor = "Red"
+WL_nm = 660 
+PlotWL <- "deltaOD"
+data_textB <- data.frame(label = c('B'))
+data_text <- data.frame(label = c('660 nm, 250 µM'))
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+  #        fit == min(fit, na.rm = TRUE)) %>%
+  # distinct(fit)
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White'))
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+HyperChlPlot <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "250"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "250") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourMIT9313RedHigh <- ggplot(na.omit(HyperChlPlot)) + 
+    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", w_length2rgb(660)), limits  = range(minMu, 1.0), na.value = "white") +
+    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 205)) +
+    geom_text(data=data_textB, aes(x=5, y=205, label=label), size=7) +
+    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
+    xlab("Photoperiod (h)") +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=12),
+        axis.title = element_text(size=16),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+         axis.title.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.15,0.30),
+        legend.text = element_text(size=11)))
+
+```
+
+``` {r MIT9313GAM Plot Red WL 25, fig.height=4.5, fig.width=4.5}
+GamStrain = "MIT9313" 
+GamColor = "Red"
+WL_nm = 660 
+PlotWL <- "deltaOD"
+data_text <- data.frame(label = c('660 nm, 25 µM'))
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+  #        fit == min(fit, na.rm = TRUE)) %>%
+  # distinct(fit)
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White'))
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+HyperChlPlot <- PicoGAM_Plot_Prep %>%
   filter(
@@
 
-(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
+(ContourMIT9313RedInt <- ggplot(na.omit(HyperChlPlot)) + 
+    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", w_length2rgb(660)), limits  = range(minMu, 1.0), na.value = "white") +
+    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
                         breaks = ContourLines,
@@
     scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    xlab(NULL)+
-      ylab(NULL)+
-  theme_classic() +
-   theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35)))
-
-HyperChlPlotHigh <- PicoGAM_Plot_Prep %>%
+    scale_y_continuous(limits = c(10, 205)) +
+    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=12),
+        axis.title = element_text(size=16),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+        axis.title.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.88,0.81),
+        legend.text = element_text(size=11)))
+
+```
+
+``` {r MIT9313GAM Plot Red WL 2.5, fig.height=4.5, fig.width=4.5}
+GamStrain = "MIT9313" 
+GamColor = "Red"
+WL_nm = 660 
+PlotWL <- "deltaOD"
+data_text <- data.frame(label = c('660 nm, 2.5 µM'))
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+  #        fit == min(fit, na.rm = TRUE)) %>%
+  # distinct(fit)
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White'))
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+HyperChlPlot <- PicoGAM_Plot_Prep %>%
   filter(
@@
          Wavelength %in% PlotWL,
-         O2_uM == "250"
+         O2_uM == "2.5"
   )
 ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "250") 
+  filter(O2_uM == "2.5") 
 ContourLines <- ContourLines$quantileValue
 
-(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
-    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
-    metR::geom_contour2(aes(label = stat(level)),
+(ContourMIT9313RedLow <- ggplot(na.omit(HyperChlPlot)) + 
+    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit)) +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", w_length2rgb(660)), limits  = range(minMu, 1.0), na.value = "white") +
+    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
                         breaks = ContourLines,
@@
     scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 200)) +
-    xlab(NULL)+
-      ylab(NULL)+
-    #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
-theme_classic() +
-   theme(axis.text=element_text(size=15),
-          axis.title.x = element_text(size=20),
-           axis.title.y = element_text(size=35)))
-
-g_legend<-function(a.gplot){
-  tmp <- ggplot_gtable(ggplot_build(a.gplot))
-  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
-  legend <- tmp$grobs[[leg]]
-  legend
-}
-
-(g_dummy1 <- ggplot(subset(HyperChlPlotLow, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
- + scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"),
- limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend1 <- g_legend(g_dummy1)
-(g_dummy2 <- ggplot(subset(HyperChlPlotInt, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
- + scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"),
-  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend2 <- g_legend(g_dummy2)
-(g_dummy3 <- ggplot(subset(HyperChlPlotHigh, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
-+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"),
-  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
-legend3 <- g_legend(g_dummy3)
-
-# comment rows that are not included in grid arrange 
-LayoutNiche <- rbind(
-                     c(3, 3, 3, 3, 6), # For 2.5 uM O2   
-                     c(3, 3, 3, 3, 6), # For 2.5 uM O2  
-                     c(2, 2, 2, 2, 5),   # For 25 uM O2
-                     c(2, 2, 2, 2, 5),   # For 25 uM O2
-                     c(1, 1, 1, 1, 4),   # For 250 uM O2
-                     c(1, 1, 1, 1, 4)    # For 250 uM O2
-                     )
-
-#LayoutNiche <- rbind(c(1, 1, 1, 2, 2, 2, 3, 3, 3, 4))
-
-p3_Blue <- grid.arrange(
-                         ContourLowO2 + labs(title = bquote("F.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
-                           theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()),
-                        ContourIntO2 +  labs(title = bquote("E.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
-                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
-                        ContourHighO2 + labs(title = bquote("D.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
-                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()),                          
-                        legend1,    
-                        legend2, 
-                        legend3, 
-                        layout_matrix = LayoutNiche)  
-```
-
-```{r combine red and blue light MIT9313GAM plots}
-
-#combine red and blue GAM plots
-CombinedGAM <- plot_grid(p3_Red, p3_Blue, nrow = 1, align = "v")
-
-# common x-axis title
-x.grob <- textGrob("Photoperiod (h)", 
-                   gp = gpar(fontsize = 20))
-
-# common y-axis title
-y.grob <- textGrob("PAR (µmol photons"~ m^-2~ ~s^-1~ ")", 
-                   gp = gpar(fontface="bold", fontsize = 20), rot = 90)
-
-# add titles to plot
-LabelledCombinedGam <- grid.arrange(arrangeGrob(CombinedGAM, left = y.grob, bottom = x.grob))
+    scale_y_continuous(limits = c(10, 205)) +
+    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
+   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
+    xlab("Photoperiod (h)") +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
+    # xlab(NULL) +
+    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=12),
+        axis.title = element_text(size=16),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+         # axis.title.y = element_text(margin=margin(r=10)),
+        # axis.title.y = element_blank(),
+        axis.title.x = element_text(margin=margin(t=10)),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.88,0.76),
+        legend.text = element_text(size=11)))
+
+```
+
+```{r, MIT9313PARGAM, fig.height = 13, fig.width=7, warning=FALSE}
+
+MIT9313PARGAM <-  MIT9313PAR / (ContourMIT9313RedHigh + ContourMIT9313BlueHigh)/ (ContourMIT9313RedInt + ContourMIT9313BlueInt)/ (ContourMIT9313RedLow + ContourMIT9313BlueLow)
+
+MIT9313PARGAM
 
@@
 # MIT9313GAM.png for manuscript
- ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "GAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = LabelledCombinedGam,  height = 10, width = 10)
+ ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "PARGAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = MIT9313PARGAM,  height = 16.5, width = 10)
 

### 2024-05-23 Code/Plots_GAM.Rmd
Cleaned code

@@
 
+```{r, set colors for wavelength}
+
+MyWavelengths = c("WW", 660, 450)
+
+MCMIXColours = c("black", "brown", "steelblue")
+
+names(MCMIXColours) <- MyWavelengths
+MCMIXColours
+
+```
+
 # Read data and select relevant columns
@@
 ```{r, MED4PAR, fig.height=10, fig.width=10}
-MyWavelengths = c("WW", 660, 450)
-
-MCMIXColours = c("black", "brown", "steelblue")
-
-names(MCMIXColours) <- MyWavelengths
-MCMIXColours
 
@@
          ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
-         # Par_ue = factor(Par_ue, levels = c(30, 90, 180)),
-         # O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
+         WL = factor(WL, levels = c("WW", 660, 530, 450)),
+         deltaOD_Lmu_corr_day = deltaOD_Lmu_corr * 24,
+         deltaOD_Lmu_se_day = deltaOD_Lmu_se * 24) %>% 
+  ggplot()  +
+    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.75, show.legend = F) +
+   geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5, show.legend = F) +
+    geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 1) +
+    geom_text(data=data_text, aes(x=5.5, y=0.8, label=label), size=7) +
+ labs( y = "Chlorophyll specific growth rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
+   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3, show.legend = F) +
+  scale_y_continuous(breaks = c(0,0.25,  0.5, 0.75, 1.0), limits = c (0, 1.05)) +
+  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
+   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
+  ggh4x::facet_nested(cols = vars(ParLabel, factor(Par_ue, levels = c("30", "90","180"))), rows = vars(OxygenLabel, factor(O2_uM, levels= c("250", "25","2.5"))), 
+                    labeller = label_parsed) + 
+ guides(linetype = "none") +
+   theme_bw() +
+   theme( panel.grid.major = element_blank(),
+          panel.grid.minor = element_blank(),
+     axis.title.x.bottom = element_text(size = 16, color = "black", vjust = 1.0),
+      axis.title.y = element_text(size = 16, color = "black", vjust = 1.0),
+       axis.title.x.top = element_text(size = 16, color = "black", vjust = 1.0),
+       axis.text.x = element_text(size = 12, color = "black", angle = 0, hjust = 0.5, vjust = 1),
+        axis.text.y = element_text(size = 12, color = "black", angle = 0, hjust = 1.0),
+       axis.text.x.top = element_blank(),
+       axis.ticks.x.top = element_blank(),
+       strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=12),
+        legend.key.size = unit(1, 'cm'), #change legend key size
+        legend.key.height = unit(1, 'cm'), #change legend key height
+        legend.key.width = unit(0.5, 'cm'), #change legend key width
+        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
+        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
+        legend.title = element_text(size = 16),  #change legend title font size
+        legend.text = element_text(size = 12),   #change legend text font size
+        legend.position = "top") +
+  labs(color = "Growth wavelength (nm)",
+       fill = "Growth wavelength (nm)")
+MED4PAR
+
+```
+
+``` {r MED4GAM Plot Blue WL 250, fig.height=5, fig.width=5}
+GamStrain = "MED4" 
+GamColor = "Blue"
+WL_nm = 450 
+PlotWL <- "deltaOD"
+data_text <- data.frame(label = c('450 nm, 250 µM'))
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White'))
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+HyperChlPlot <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "250"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "250") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourMED4BlueHigh <- ggplot(na.omit(HyperChlPlot)) + 
+    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
+    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 205)) +
+    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
+    xlab("Photoperiod (h)") +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=12),
+        axis.title = element_text(size=16),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+         axis.title.y = element_blank(),
+         axis.title.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.15,0.30),
+        legend.text = element_text(size=11)))
+
+remove(ColourDF, ContourLines, HyperChlPlot, ContourBreaks, PicoGAM_Plot_Prep)
+```
+
+```{r MED4GAM Plot Blue WL 25, fig.height=5, fig.width=5}
+GamStrain = "MED4" 
+GamColor = "Blue"
+WL_nm = 450 
+PlotWL <- "deltaOD"
+data_text <- data.frame(label = c('450 nm, 25 µM'))
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White'))
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+HyperChlPlot <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "25"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "25") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourMED4BlueInt <- ggplot(na.omit(HyperChlPlot)) + 
+    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit)) +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
+    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 205)) +
+    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
+    xlab("Photoperiod (h)") +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=12),
+        axis.title = element_text(size=16),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+         axis.title.y = element_blank(),
+        axis.title.x = element_text(margin=margin(t=10)),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.15,0.30),
+        legend.text = element_text(size=11)))
+
+remove(ColourDF, ContourLines, HyperChlPlot, ContourBreaks, PicoGAM_Plot_Prep)
+
+```
+
+``` {r MED4GAM Plot Red WL 250, fig.height=5, fig.width=5}
+GamStrain = "MED4" 
+GamColor = "Red"
+WL_nm = 660 
+PlotWL <- "deltaOD"
+data_textB <- data.frame(label = c('B'))
+data_text <- data.frame(label = c('660 nm, 250 µM'))
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White'))
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+HyperChlPlot <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "250"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "250") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourMED4RedHigh <- ggplot(na.omit(HyperChlPlot)) + 
+    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", w_length2rgb(660)), limits  = range(minMu, 1.0), na.value = "white") +
+    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 205)) +
+    geom_text(data=data_textB, aes(x=5, y=205, label=label), size=7) +
+     geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
+    xlab("Photoperiod (h)") +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=12),
+        axis.title = element_text(size=16),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+         axis.title.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.15,0.30),
+        legend.text = element_text(size=11)))
+
+remove(ColourDF, ContourLines, HyperChlPlot, ContourBreaks, PicoGAM_Plot_Prep)
+
+```
+
+``` {r MED4GAM Plot Red WL 25, fig.height=5, fig.width=5}
+GamStrain = "MED4" 
+GamColor = "Red"
+WL_nm = 660 
+PlotWL <- "deltaOD"
+data_text <- data.frame(label = c('660 nm, 25 µM'))
+
+maxMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
+maxMu <- maxMu$fit
+
+minMu <- PicoGAM_Pred %>%
+  ungroup() %>%
+  filter(Wavelength %in% PlotWL) %>%
+  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
+minMu <- minMu$fit
+
+PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
+  filter(Wavelength %in% PlotWL,
+         Strain %in% GamStrain,
+         WL %in% WL_nm) %>%
+  mutate(
+         Color_name = case_when(WL == "450" ~ 'Blue',
+                                WL == "530" ~ 'Green',
+                                WL == "660" ~ 'Red',
+                                WL == "WW" ~ 'White'))
+
+WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
+
+ColourDF <- data.frame(
+  ColorName = c('Blue', 'Green', 'Red', 'White'),
+  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
+) %>%
+  filter(ColorName %in% GamColor) %>%
+  dplyr::select(WL_O2_Colors)
+
+ContourBreaks <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL
+  ) %>%
+  group_by(O2_uM) %>%
+  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
+         median50 = quantile(fit, 0.5, na.rm = TRUE),
+         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
+  ungroup() %>%
+  dplyr::select(O2_uM, upper10, median50, lower10) %>%
+  distinct() %>%
+  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
+  mutate(quantileValue = round(quantileValue, digits = 2))
+
+HyperChlPlot <- PicoGAM_Plot_Prep %>%
+  filter(
+         Strain %in% GamStrain,
+         Wavelength %in% PlotWL,
+         O2_uM == "25"
+  )
+ContourLines <- ContourBreaks %>%
+  filter(O2_uM == "25") 
+ContourLines <- ContourLines$quantileValue
+
+(ContourMED4RedInt <- ggplot(na.omit(HyperChlPlot)) + 
+    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit)) +
+    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", w_length2rgb(660)), limits  = range(minMu, 1.0), na.value = "white") +
+    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
+                        breaks = ContourLines,
+                        skip = 0) +
+    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
+    scale_y_continuous(limits = c(10, 205)) +
+    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
+    xlab("Photoperiod (h)") +
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=12),
+        axis.title = element_text(size=16),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+        axis.title.x = element_text(margin=margin(t=10)),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.15,0.30),
+        legend.text = element_text(size=11)))
+
+remove(ColourDF, ContourLines, HyperChlPlot, ContourBreaks, PicoGAM_Plot_Prep)
+
+```
+
+```{r, MED4PARGAM, fig.height = 20, fig.width=10, warning=FALSE}
+
+MED4PARGAM <-  MED4PAR / (ContourMED4RedHigh + ContourMED4BlueHigh)/ (ContourMED4RedInt + ContourMED4BlueInt)
+
+MED4PARGAM
+
+remove(MED4PAR, ContourMED4RedHigh, ContourMED4BlueHigh, ContourMED4RedInt, ContourMED4BlueInt)
+
+```
+
+```{r save MED4PARGAM plots}
+# MED4PARGAM.png for manuscript
+ ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "PARGAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = MED4PARGAM,  height = 15, width = 10)
+
+# MED4PARGAM is Fig4.tiff for PLOSONE submission
+ ggsave(file = file.path(PlotsOutPLOS, "Fig4.tiff", fsep = .Platform$file.sep), plot = MED4PARGAM, device = NULL, scale = 1,  height = 10, width = 10, compression = "lzw")
+
+```
+
+```{r, SS120PAR, fig.height=10, fig.width=10}
+
+data_text <- data.frame( ParLabel=c("PAR~(µmol~photons~m^{-2}~s^{-1})"), OxygenLabel = c("Oxygen~concentration~(µM)"),Par_ue = c("30"), O2_uM = c("250"), label = c('A'))
+
+SS120PAR <- GrowthFits %>%
+   filter(Strain == "SS120",
+           Par_ue %in% c(30,90,180),
+          WL %in% c("WW", 450, 660),
+          deltaOD_Lmu_corr == 0 |
+          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
+  mutate(PhotoperiodLabelTitle = "Photoperiod~(h)",
+         OxygenLabel = "Oxygen~concentration~(µM)",
+         WLlabelTitle = "Growth~wavelength~(nm)",
+         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
          WL = factor(WL, levels = c("WW", 660, 530, 450)),
@@
         strip.text = element_text(size=12),
-        # strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"),
         legend.key.size = unit(1, 'cm'), #change legend key size
@@
        fill = "Growth wavelength (nm)")
-MED4PAR
-
-```
-
-``` {r MED4GAM Plot Blue WL 250, fig.height=5, fig.width=5}
-GamStrain = "MED4" 
+SS120PAR
+
+```
+
+``` {r SS120GAM Plot Blue WL 250, fig.height=5, fig.width=5}
+GamStrain = "SS120" 
 GamColor = "Blue"
@@
 data_text <- data.frame(label = c('450 nm, 250 µM'))
-# data_textB <- data.frame(label = c('B'))
 
@@
   slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
-  #        fit == min(fit, na.rm = TRUE)) %>%
-  # distinct(fit)
 minMu <- minMu$fit
@@
 
-(ContourMED4BlueHigh <- ggplot(na.omit(HyperChlPlot)) + 
+(ContourSS120BlueHigh <- ggplot(na.omit(HyperChlPlot)) + 
     geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
@@
     geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
-     # geom_text(data=data_textB, aes(x=5, y=190, label=label), size=7) +
-   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
     xlab("Photoperiod (h)") +
-      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
-    # xlab(NULL) +
-    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
   theme_bw() +
@@
          axis.title.y = element_blank(),
-         # axis.title.y = element_text(margin=margin(r=10)),
          axis.title.x = element_blank(),
-        # axis.title.x = element_text(margin=margin(t=10)),
         legend.background = element_rect(fill="transparent"),
@@
 
-```
-
-```{r MED4GAM Plot Blue WL 25, fig.height=5, fig.width=5}
-GamStrain = "MED4" 
+remove(ColourDF, ContourLines, HyperChlPlot, ContourBreaks, PicoGAM_Plot_Prep)
+
+```
+
+```{r SS120GAM Plot Blue WL 25, fig.height=5, fig.width=5}
+GamStrain = "SS120" 
 GamColor = "Blue"
@@
 
-(ContourMED4BlueInt <- ggplot(na.omit(HyperChlPlot)) + 
+(ContourSS120BlueInt <- ggplot(na.omit(HyperChlPlot)) + 
     geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit)) +
@@
     geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
-   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
     xlab("Photoperiod (h)") +
-      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
-    # xlab(NULL) +
-    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
   theme_bw() +
@@
         strip.text = element_text(size=14),
-         # axis.title.y = element_text(margin=margin(r=10)),
          axis.title.y = element_blank(),
@@
         legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.15,0.30),
+        legend.position = c(0.88,0.81),
         legend.text = element_text(size=11)))
 
-```
-
-``` {r MED4GAM Plot Red WL 250, fig.height=5, fig.width=5}
-GamStrain = "MED4" 
+remove(ColourDF, ContourLines, HyperChlPlot, ContourBreaks, PicoGAM_Plot_Prep)
+
+```
+
+``` {r SS120GAM Plot Red WL 250, fig.height=5, fig.width=5}
+GamStrain = "SS120" 
 GamColor = "Red"
@@
 
-(ContourMED4RedHigh <- ggplot(na.omit(HyperChlPlot)) + 
+(ContourSS120RedHigh <- ggplot(na.omit(HyperChlPlot)) + 
     geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
@@
     scale_y_continuous(limits = c(10, 205)) +
-    geom_text(data=data_textB, aes(x=5, y=205, label=label), size=7) +
-     geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
-  # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
+    geom_text(data=data_textB, aes(x = 5, y = 205, label=label), size=7) +
+     geom_text(data=data_text, aes(x = 10, y = 205, label=label), size=4) +
     xlab("Photoperiod (h)") +
-      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
-    # xlab(NULL) +
-    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
+      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
   theme_bw() +
@@
         panel.grid.major = element_blank(),
-        axis.text = element_text(size=12),
-        axis.title = element_text(size=16),
+        axis.text = element_text(size = 12),
+        axis.title = element_text(size = 16),
         strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-         # axis.title.y = element_text(margin=margin(r=10)),
+        strip.text = element_text(size = 14),
          axis.title.x = element_blank(),
-        # axis.title.x = element_text(margin=margin(t=10)),
         legend.background = element_rect(fill="transparent"),
         legend.position = c(0.15,0.30),
-        legend.text = element_text(size=11)))
-
-```
-
-``` {r MED4GAM Plot Red WL 25, fig.height=5, fig.width=5}
-GamStrain = "MED4" 
+        legend.text = element_text(size = 11)))
+
+remove(ColourDF, ContourLines, HyperChlPlot, ContourBreaks, PicoGAM_Plot_Prep)
+
+```
+
+``` {r SS120GAM Plot Red WL 25, fig.height=5, fig.width=5}
+GamStrain = "SS120" 
 GamColor = "Red"
@@
 
-(ContourMED4RedInt <- ggplot(na.omit(HyperChlPlot)) + 
+(ContourSS120RedInt <- ggplot(na.omit(HyperChlPlot)) + 
     geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit)) +
@@
         strip.text = element_text(size=14),
-         # axis.title.y = element_text(margin=margin(r=10)),
-        # axis.title.y = element_blank(),
         axis.title.x = element_text(margin=margin(t=10)),
         legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.15,0.30),
+        legend.position = c(0.88,0.81),
         legend.text = element_text(size=11)))
 
-```
-
-```{r, MED4PARGAM, fig.height = 20, fig.width=10, warning=FALSE}
-
-MED4PARGAM <-  MED4PAR / (ContourMED4RedHigh + ContourMED4BlueHigh)/ (ContourMED4RedInt + ContourMED4BlueInt)
-
-MED4PARGAM
-
-```
-
-```{r save MED4PARGAM plots}
-# MED4GAM,png for manuscript
- ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "PARGAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = MED4PARGAM,  height = 15, width = 10)
-
-# MED4GAM is Fig4.tiff for PLOSONE submission
- ggsave(file = file.path(PlotsOutPLOS, "Fig4.tiff", fsep = .Platform$file.sep), plot = MED4PARGAM, device = NULL, scale = 1,  height = 10, width = 10, compression = "lzw")
-
-```
-
-```{r, SS120PAR, fig.height=10, fig.width=10}
-MyWavelengths = c("WW", 660, 450)
-
-MCMIXColours = c("black", "brown", "steelblue")
-
-names(MCMIXColours) <- MyWavelengths
-MCMIXColours
+remove(ColourDF, ContourLines, HyperChlPlot, ContourBreaks, PicoGAM_Plot_Prep)
+
+```
+
+```{r, SS120PARGAM, fig.height = 20, fig.width=10, warning=FALSE}
+
+SS120PARGAM <-  SS120PAR / (ContourSS120RedHigh + ContourSS120BlueHigh)/ (ContourSS120RedInt + ContourSS120BlueInt)
+
+SS120PARGAM
+
+remove(SS120PAR, ContourSS120RedHigh, ContourSS120BlueHigh, ContourSS120RedInt, ContourSS120BlueInt)
+
+```
+
+```{r save SS120GAM plots}
+
+# SS120PARGAM.png for manuscript
+ ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "PARGAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = SS120PARGAM,  height = 15, width = 10)
+
+# SS120PARGAM is Fig6.tiff for PLOSONE submission
+ ggsave(file = file.path(PlotsOutPLOS, "Fig6.tiff", fsep = .Platform$file.sep), plot = LabelledCombinedGam, device = NULL, scale = 1,  height = 10, width = 10, compression = "lzw")
+
+```
+
+```{r, MIT9313PAR, fig.height=10, fig.width=10}
 
@@
 
-SS120PAR <- GrowthFits %>%
-   filter(Strain == "SS120",
+MIT9313PAR <- GrowthFits %>%
+   filter(Strain == "MIT9313",
            Par_ue %in% c(30,90,180),
@@
          ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
-         # Par_ue = factor(Par_ue, levels = c(30, 90, 180)),
-         # O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
          WL = factor(WL, levels = c("WW", 660, 530, 450)),
@@
   scale_y_continuous(breaks = c(0,0.25,  0.5, 0.75, 1.0), limits = c (0, 1.05)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
   scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
@@
         strip.text = element_text(size=12),
-        # strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"),
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
-        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
-        legend.title = element_text(size = 16),  #change legend title font size
-        legend.text = element_text(size = 12),   #change legend text font size
-        legend.position = "top") +
-  labs(color = "Growth wavelength (nm)",
-       fill = "Growth wavelength (nm)")
-SS120PAR
-
-```
-
-``` {r SS120GAM Plot Blue WL 250, fig.height=5, fig.width=5}
-GamStrain = "SS120" 
-GamColor = "Blue"
-WL_nm = 450 
-PlotWL <- "deltaOD"
-data_text <- data.frame(label = c('450 nm, 250 µM'))
-# data_textB <- data.frame(label = c('B'))
-
-maxMu <- PicoGAM_Pred %>%
-  ungroup() %>%
-  filter(Wavelength %in% PlotWL) %>%
-  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
-maxMu <- maxMu$fit
-
-minMu <- PicoGAM_Pred %>%
-  ungroup() %>%
-  filter(Wavelength %in% PlotWL) %>%
-  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
-  #        fit == min(fit, na.rm = TRUE)) %>%
-  # distinct(fit)
-minMu <- minMu$fit
-
-PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
-  filter(Wavelength %in% PlotWL,
-         Strain %in% GamStrain,
-         WL %in% WL_nm) %>%
-  mutate(
-         Color_name = case_when(WL == "450" ~ 'Blue',
-                                WL == "530" ~ 'Green',
-                                WL == "660" ~ 'Red',
-                                WL == "WW" ~ 'White'))
-
-WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
-
-ColourDF <- data.frame(
-  ColorName = c('Blue', 'Green', 'Red', 'White'),
-  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
-) %>%
-  filter(ColorName %in% GamColor) %>%
-  dplyr::select(WL_O2_Colors)
-
-ContourBreaks <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL
-  ) %>%
-  group_by(O2_uM) %>%
-  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
-         median50 = quantile(fit, 0.5, na.rm = TRUE),
-         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
-  ungroup() %>%
-  dplyr::select(O2_uM, upper10, median50, lower10) %>%
-  distinct() %>%
-  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
-  mutate(quantileValue = round(quantileValue, digits = 2))
-
-HyperChlPlot <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL,
-         O2_uM == "250"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "250") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourSS120BlueHigh <- ggplot(na.omit(HyperChlPlot)) + 
-    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
-    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
-    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 205)) +
-    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
-     # geom_text(data=data_textB, aes(x=5, y=190, label=label), size=7) +
-   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
-    xlab("Photoperiod (h)") +
-      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
-    # xlab(NULL) +
-    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_text(size=12),
-        axis.title = element_text(size=16),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-         axis.title.y = element_blank(),
-         # axis.title.y = element_text(margin=margin(r=10)),
-         axis.title.x = element_blank(),
-        # axis.title.x = element_text(margin=margin(t=10)),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.15,0.30),
-        legend.text = element_text(size=11)))
-
-```
-
-```{r SS120GAM Plot Blue WL 25, fig.height=5, fig.width=5}
-GamStrain = "SS120" 
-GamColor = "Blue"
-WL_nm = 450 
-PlotWL <- "deltaOD"
-data_text <- data.frame(label = c('450 nm, 25 µM'))
-
-maxMu <- PicoGAM_Pred %>%
-  ungroup() %>%
-  filter(Wavelength %in% PlotWL) %>%
-  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
-maxMu <- maxMu$fit
-
-minMu <- PicoGAM_Pred %>%
-  ungroup() %>%
-  filter(Wavelength %in% PlotWL) %>%
-  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
-  #        fit == min(fit, na.rm = TRUE)) %>%
-  # distinct(fit)
-minMu <- minMu$fit
-
-PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
-  filter(Wavelength %in% PlotWL,
-         Strain %in% GamStrain,
-         WL %in% WL_nm) %>%
-  mutate(
-         Color_name = case_when(WL == "450" ~ 'Blue',
-                                WL == "530" ~ 'Green',
-                                WL == "660" ~ 'Red',
-                                WL == "WW" ~ 'White'))
-
-WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
-
-ColourDF <- data.frame(
-  ColorName = c('Blue', 'Green', 'Red', 'White'),
-  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
-) %>%
-  filter(ColorName %in% GamColor) %>%
-  dplyr::select(WL_O2_Colors)
-
-ContourBreaks <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL
-  ) %>%
-  group_by(O2_uM) %>%
-  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
-         median50 = quantile(fit, 0.5, na.rm = TRUE),
-         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
-  ungroup() %>%
-  dplyr::select(O2_uM, upper10, median50, lower10) %>%
-  distinct() %>%
-  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
-  mutate(quantileValue = round(quantileValue, digits = 2))
-
-HyperChlPlot <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL,
-         O2_uM == "25"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "25") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourSS120BlueInt <- ggplot(na.omit(HyperChlPlot)) + 
-    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit)) +
-    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, 1.0), na.value = "white") +
-    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 205)) +
-    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
-   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
-    xlab("Photoperiod (h)") +
-      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
-    # xlab(NULL) +
-    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_text(size=12),
-        axis.title = element_text(size=16),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-         # axis.title.y = element_text(margin=margin(r=10)),
-         axis.title.y = element_blank(),
-        axis.title.x = element_text(margin=margin(t=10)),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.88,0.81),
-        legend.text = element_text(size=11)))
-
-```
-
-``` {r SS120GAM Plot Red WL 250, fig.height=5, fig.width=5}
-GamStrain = "SS120" 
-GamColor = "Red"
-WL_nm = 660 
-PlotWL <- "deltaOD"
-data_textB <- data.frame(label = c('B'))
-data_text <- data.frame(label = c('660 nm, 250 µM'))
-
-maxMu <- PicoGAM_Pred %>%
-  ungroup() %>%
-  filter(Wavelength %in% PlotWL) %>%
-  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
-maxMu <- maxMu$fit
-
-minMu <- PicoGAM_Pred %>%
-  ungroup() %>%
-  filter(Wavelength %in% PlotWL) %>%
-  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
-  #        fit == min(fit, na.rm = TRUE)) %>%
-  # distinct(fit)
-minMu <- minMu$fit
-
-PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
-  filter(Wavelength %in% PlotWL,
-         Strain %in% GamStrain,
-         WL %in% WL_nm) %>%
-  mutate(
-         Color_name = case_when(WL == "450" ~ 'Blue',
-                                WL == "530" ~ 'Green',
-                                WL == "660" ~ 'Red',
-                                WL == "WW" ~ 'White'))
-
-WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
-
-ColourDF <- data.frame(
-  ColorName = c('Blue', 'Green', 'Red', 'White'),
-  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
-) %>%
-  filter(ColorName %in% GamColor) %>%
-  dplyr::select(WL_O2_Colors)
-
-ContourBreaks <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL
-  ) %>%
-  group_by(O2_uM) %>%
-  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
-         median50 = quantile(fit, 0.5, na.rm = TRUE),
-         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
-  ungroup() %>%
-  dplyr::select(O2_uM, upper10, median50, lower10) %>%
-  distinct() %>%
-  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
-  mutate(quantileValue = round(quantileValue, digits = 2))
-
-HyperChlPlot <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL,
-         O2_uM == "250"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "250") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourSS120RedHigh <- ggplot(na.omit(HyperChlPlot)) + 
-    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit), show.legend = F) +
-    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", w_length2rgb(660)), limits  = range(minMu, 1.0), na.value = "white") +
-    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 205)) +
-    geom_text(data=data_textB, aes(x=5, y=205, label=label), size=7) +
-     geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
-  # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
-    xlab("Photoperiod (h)") +
-      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
-    # xlab(NULL) +
-    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_text(size=12),
-        axis.title = element_text(size=16),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-         # axis.title.y = element_text(margin=margin(r=10)),
-         axis.title.x = element_blank(),
-        # axis.title.x = element_text(margin=margin(t=10)),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.15,0.30),
-        legend.text = element_text(size=11)))
-
-```
-
-``` {r SS120GAM Plot Red WL 25, fig.height=5, fig.width=5}
-GamStrain = "SS120" 
-GamColor = "Red"
-WL_nm = 660 
-PlotWL <- "deltaOD"
-data_text <- data.frame(label = c('660 nm, 25 µM'))
-
-maxMu <- PicoGAM_Pred %>%
-  ungroup() %>%
-  filter(Wavelength %in% PlotWL) %>%
-  slice(which.max(fit)) #base::max does not work with package photobiology loaded simultaneously 
-maxMu <- maxMu$fit
-
-minMu <- PicoGAM_Pred %>%
-  ungroup() %>%
-  filter(Wavelength %in% PlotWL) %>%
-  slice(which.min(fit)) #base::max does not work with package photobiology loaded simultaneously 
-  #        fit == min(fit, na.rm = TRUE)) %>%
-  # distinct(fit)
-minMu <- minMu$fit
-
-PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
-  filter(Wavelength %in% PlotWL,
-         Strain %in% GamStrain,
-         WL %in% WL_nm) %>%
-  mutate(
-         Color_name = case_when(WL == "450" ~ 'Blue',
-                                WL == "530" ~ 'Green',
-                                WL == "660" ~ 'Red',
-                                WL == "WW" ~ 'White'))
-
-WL_O2_Colors = c(Blue = w_length2rgb(450), green = w_length2rgb(530), red = w_length2rgb(660), white= "#FFCC00")
-
-ColourDF <- data.frame(
-  ColorName = c('Blue', 'Green', 'Red', 'White'),
-  WL_O2_Colors = c( w_length2rgb(450), w_length2rgb(530), w_length2rgb(660), "#FFCC00")
-) %>%
-  filter(ColorName %in% GamColor) %>%
-  dplyr::select(WL_O2_Colors)
-
-ContourBreaks <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL
-  ) %>%
-  group_by(O2_uM) %>%
-  mutate(upper10 = quantile(fit, 0.9, na.rm = TRUE),
-         median50 = quantile(fit, 0.5, na.rm = TRUE),
-         lower10 = quantile(fit, 0.1, na.rm = TRUE)) %>%
-  ungroup() %>%
-  dplyr::select(O2_uM, upper10, median50, lower10) %>%
-  distinct() %>%
-  pivot_longer(cols = c(upper10, median50, lower10), names_to = 'quantile', values_to = 'quantileValue') %>%
-  mutate(quantileValue = round(quantileValue, digits = 2))
-
-HyperChlPlot <- PicoGAM_Plot_Prep %>%
-  filter(
-         Strain %in% GamStrain,
-         Wavelength %in% PlotWL,
-         O2_uM == "25"
-  )
-ContourLines <- ContourBreaks %>%
-  filter(O2_uM == "25") 
-ContourLines <- ContourLines$quantileValue
-
-(ContourSS120RedInt <- ggplot(na.omit(HyperChlPlot)) + 
-    geom_tile(aes(Photoperiod, Par_ue, z = fit, fill = fit)) +
-    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", w_length2rgb(660)), limits  = range(minMu, 1.0), na.value = "white") +
-    metR::geom_contour2(aes(Photoperiod, Par_ue, z = fit, fill = fit, label = stat(level)),
-                        breaks = ContourLines,
-                        skip = 0) +
-    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
-    scale_y_continuous(limits = c(10, 205)) +
-    geom_text(data=data_text, aes(x=10, y=205, label=label), size=4) +
-   # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +
-    xlab("Photoperiod (h)") +
-      ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")")+
-    # xlab(NULL) +
-    #   ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_text(size=12),
-        axis.title = element_text(size=16),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-         # axis.title.y = element_text(margin=margin(r=10)),
-        # axis.title.y = element_blank(),
-        axis.title.x = element_text(margin=margin(t=10)),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.88,0.81),
-        legend.text = element_text(size=11)))
-
-```
-
-```{r, SS120PARGAM, fig.height = 20, fig.width=10, warning=FALSE}
-
-SS120PARGAM <-  SS120PAR / (ContourSS120RedHigh + ContourSS120BlueHigh)/ (ContourSS120RedInt + ContourSS120BlueInt)
-
-SS120PARGAM
-
-```
-
-```{r save SS120GAM plots}
-
-# SS120GAM.png for manuscript
- ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "PARGAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = SS120PARGAM,  height = 15, width = 10)
-
-# SS120GAM is Fig6.tiff for PLOSONE submission
- ggsave(file = file.path(PlotsOutPLOS, "Fig6.tiff", fsep = .Platform$file.sep), plot = LabelledCombinedGam, device = NULL, scale = 1,  height = 10, width = 10, compression = "lzw")
-
-```
-
-```{r, MIT9313PAR, fig.height=10, fig.width=10}
-MyWavelengths = c("WW", 660, 450)
-
-MCMIXColours = c("black", "brown", "steelblue")
-
-names(MCMIXColours) <- MyWavelengths
-MCMIXColours
-
-  data_text <- data.frame( ParLabel=c("PAR~(µmol~photons~m^{-2}~s^{-1})"), OxygenLabel = c("Oxygen~concentration~(µM)"),Par_ue = c("30"), O2_uM = c("250"), label = c('A'))
-
-MIT9313PAR <- GrowthFits %>%
-   filter(Strain == "MIT9313",
-           Par_ue %in% c(30,90,180),
-          WL %in% c("WW", 450, 660),
-          deltaOD_Lmu_corr == 0 |
-          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
-  mutate(PhotoperiodLabelTitle = "Photoperiod~(h)",
-         OxygenLabel = "Oxygen~concentration~(µM)",
-         WLlabelTitle = "Growth~wavelength~(nm)",
-         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
-         # Par_ue = factor(Par_ue, levels = c(30, 90, 180)),
-         # O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
-         WL = factor(WL, levels = c("WW", 660, 530, 450)),
-         deltaOD_Lmu_corr_day = deltaOD_Lmu_corr * 24,
-         deltaOD_Lmu_se_day = deltaOD_Lmu_se * 24) %>% 
-  ggplot()  +
-    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.75, show.legend = F) +
-   geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5, show.legend = F) +
-    geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 1) +
-    geom_text(data=data_text, aes(x=5.5, y=0.8, label=label), size=7) +
- labs( y = "Chlorophyll specific growth rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
-   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3, show.legend = F) +
-  scale_y_continuous(breaks = c(0,0.25,  0.5, 0.75, 1.0), limits = c (0, 1.05)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
-   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
-  ggh4x::facet_nested(cols = vars(ParLabel, factor(Par_ue, levels = c("30", "90","180"))), rows = vars(OxygenLabel, factor(O2_uM, levels= c("250", "25","2.5"))), 
-                    labeller = label_parsed) + 
- guides(linetype = "none") +
-   theme_bw() +
-   theme( panel.grid.major = element_blank(),
-          panel.grid.minor = element_blank(),
-     axis.title.x.bottom = element_text(size = 16, color = "black", vjust = 1.0),
-      axis.title.y = element_text(size = 16, color = "black", vjust = 1.0),
-       axis.title.x.top = element_text(size = 16, color = "black", vjust = 1.0),
-       axis.text.x = element_text(size = 12, color = "black", angle = 0, hjust = 0.5, vjust = 1),
-        axis.text.y = element_text(size = 12, color = "black", angle = 0, hjust = 1.0),
-       axis.text.x.top = element_blank(),
-       axis.ticks.x.top = element_blank(),
-       strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=12),
-        # strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"),
         legend.key.size = unit(1, 'cm'), #change legend key size
@@
 
+remove(ColourDF, ContourLines, HyperChlPlot, ContourBreaks, PicoGAM_Plot_Prep)
+
 ```
@@
         legend.text = element_text(size=11)))
+
+remove(ColourDF, ContourLines, HyperChlPlot, ContourBreaks, PicoGAM_Plot_Prep)
 
@@
         strip.text = element_text(size=14),
-         # axis.title.y = element_text(margin=margin(r=10)),
-        # axis.title.y = element_blank(),
         axis.title.x = element_text(margin=margin(t=10)),
@@
 
+remove(MIT9313PAR, ContourMIT9313RedHigh, ContourMIT9313BlueHigh, ContourMIT9313RedInt, ContourMIT9313BlueInt, ContourMIT9313RedLow, ContourMIT9313BlueLow)
+
 ```
@@
 
-# MIT9313GAM.png for manuscript
+# MIT9313PARGAM.png for manuscript
  ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "PARGAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = MIT9313PARGAM,  height = 16.5, width = 10)
 
-# MIT9313 GAM is Fig8.tiff for PLOSONE submission
+# MIT9313PARGAM is Fig8.tiff for PLOSONE submission
  ggsave(file = file.path(PlotsOutPLOS, "Fig8.tiff", fsep = .Platform$file.sep), plot = LabelledCombinedGam, device = NULL, scale = 1,  height = 10, width = 10,  compression = "lzw")

### 2024-05-23 Code/Manuscript_O2.Rmd
Added new PARGAM plots

@@
 
-*Prochlorococcus marinus* MED4, clade HLI, grew under 250 µM O~2~ and growth rates increased with higher imposed PAR and longer photoperiods (Fig \@ref(fig:MED4PAR)), across all spectral wavebands.
+*Prochlorococcus marinus* MED4, clade HLI, grew under 250 µM O~2~ and growth rates increased with higher imposed PAR and longer photoperiods (Fig \@ref(fig:MED4PARGAM)), across all spectral wavebands.
 No growth was
@@
 O~2~ showed fastest growth when the photoperiod was 16 h for each
-spectral waveband, across PAR levels (Fig \@ref(fig:MED4PAR)). The
+spectral waveband, across PAR levels (Fig \@ref(fig:MED4PARGAM)). The
 µ~max~ was
@@
 
-MED4 did not grow when sparged to the lowest [O~2~] of 2.5 µM (Fig \@ref(fig:MED4PAR)). 2.5 µM O~2~ growth experiments were not conducted
+MED4 did not grow when sparged to the lowest [O~2~] of 2.5 µM (Fig \@ref(fig:MED4PARGAM)). 2.5 µM O~2~ growth experiments were not conducted
 for 4 and 16 h photoperiods, as no reproducible growth occurred when
@@
 
-```{r MED4PAR, fig.cap = MED4PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+```{r MED4PARGAM, fig.cap = MED4PARGAM_cap, fig.height = 6, fig.width = 8, echo = FALSE}
 
 # This is Fig3.tiff
-MED4PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade) vs. photoperiod (h).**",
+MED4PARGAM_cap <- glue("**A. Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 (High-Light (HLI) near surface clade) vs. photoperiod (h).**",
                     "Rows separate data from levels of imposed dissolved O~2~ concentrations (250 µM, 25 µM and 2.5 µM).",
@@
                     "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
+                    "**B.
+Contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 grown under 660 nm (red) or 450 nm (blue) light.**",
+                    "X-axis is photoperiod (h).",
+                    "Y-axis is Photosynethetically Active Radiation (PAR, µmol photons m^-2^ s^-1^).",
+                    "Top left panel represents the model under 250 µM of O~2~ and red light.",
+                    "Bottom left panel represents the model under 25 µM of O~2~ and red light.",
+                    "Top right panel represents the model under 250 µM of O~2~ and blue light.",
+                    "Bottom right panel represents the model under 25 µM of O~2~ and blue light.",
+                    "Legends represent a colour gradient of growth rate from no growth (white) to 1.00 d^-1^ (dark red or dark blue).",
+                    "Labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",
 
@@
 
-knitr::include_graphics(file.path(FiguresIn, "MED4PAR.png"))
-```
-
-\newpage
-
-The GAM model in Fig \@ref(fig:MED4GAM) summarizes MED4 growth
-responses to red (A and B) or blue (C and D) peak PAR and photoperiod across 2
+knitr::include_graphics(file.path(FiguresIn, "MED4PARGAM.png"))
+```
+
+\newpage
+
+The GAM model in Fig \@ref(fig:MED4PARGAM)B summarizes MED4 growth
+responses to red or blue peak PAR and photoperiod across 2
 imposed oxygen concentrations. Under 250 µM O~2~ MED4 achieved fastest
 growth rates above peak blue light of \~180 µmol photons m^-2^ s^-1^,
-and the longest photoperiod of 16, indicated by the 0.64 d^-1^ contour
+and the longest photoperiod of 16 h, indicated by the 0.64 d^-1^ contour
 line representing the 90^th^ percentile of maximum achieved growth rate
-(Fig \@ref(fig:MED4GAM)C). Growth decreased with decreasing
+(Fig \@ref(fig:MED4PARGAM)B). Growth decreased with decreasing
 photoperiod and decreasing peak PAR. Under red light growth was
 generally slower but the pattern of growth responses to photoperiod and
-PAR was similar (Fig \@ref(fig:MED4GAM)A). Note the exclusion of MED4
-from growth under 4 h photoperiod under both red and blue light (Fig \@ref(fig:MED4GAM)). Under 25 µM O~2~ MED4 showed similar growth
+PAR was similar (Fig \@ref(fig:MED4PARGAM)B). Note the exclusion of MED4
+from growth under 4 h photoperiod under both red and blue light (Fig \@ref(fig:MED4PARGAM)B). Under 25 µM O~2~ MED4 showed similar growth
 responses, but was excluded from both 4 and 8 h photoperiods. MED4 did
@@
 
-```{r MED4GAM,  fig.cap = MED4GAM_cap, fig.height = 10, fig.width = 10, echo = FALSE}
-
-# This is Fig4.tiff
-MED4GAM_cap <- glue("**A contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MED4 grown under 660 nm (red) or 450 nm (blue) light.**",
-                    "X-axis is photoperiod (h).",
-                    "Y-axis is Photosynethetically Active Radiation (PAR, µmol photons m^-2^ s^-1^).",
-                    "**A.** represents the model under 250 µM of O~2~ and red light.",
-                    "**B.** represents the model under 25 µM of O~2~ and red light.",
-                    "**C.** represents the model under 250 µM of O~2~ and blue light.",
-                    "**D.** represents the model under 25 µM of O~2~ and blue light.",
-                    "Legends represent a colour gradient of growth rate from no growth (white) to 1.00 d^-1^ (dark red or dark blue).",
-                    "Labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",
-
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "MED4GAM.png"))
-
-```
-
-\newpage
-
 *Prochlorococcus marinus* SS120 clade LLII/III, growth under 250 µM O~2~
 increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^
-peak PAR and across all spectral wavebands (Fig \@ref(fig:SS120PAR)).
+peak PAR and across all spectral wavebands (Fig \@ref(fig:SS120PARGAM)).
 No growth was observed under any blue light photoperiods when exposed to
@@
 photoperiod for red spectral waveband, however under blue light, SS120
-was able to grow (Fig \@ref(fig:SS120PAR)). In contrast to the growth
+was able to grow (Fig \@ref(fig:SS120PARGAM)). In contrast to the growth
 trends of the 250 µM O~2~ and PAR of 90 µmol photons m^-2^ s^-1^
@@
 SS120 did not reproducibly grow when sparged to the lowest O~2~ of 2.5
-µM (Fig \@ref(fig:SS120PAR)). 2.5 µM O~2~ growth experiments were not
+µM (Fig \@ref(fig:SS120PARGAM)). 2.5 µM O~2~ growth experiments were not
 conducted for 4 and 16 h photoperiods under PAR of 180 µmol photons
@@
 
-```{r SS120PAR, fig.cap = SS120PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+```{r SS120PARGAM, fig.cap = SS120PARGAM_cap, fig.height = 6, fig.width = 8, echo = FALSE}
 
 # This is Fig5.tiff
-SS120PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low-Light (LLII/III) deep ocean clade) vs. photoperiod (h). **",
+SS120PARGAM_cap <- glue("**A. Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low-Light (LLII/III) deep ocean clade) vs. photoperiod (h). **",
                     "Rows separate data from levels of imposed dissolved O~2~ concentrations (250 µM, 25 µM and 2.5 µM).",
@@
                     "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
+                    "**B.
+Contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 grown under 660 nm (red) or 450 nm (blue) light.**",
+                    "X-axis is photoperiod (h).",
+                    "Y-axis is Photosynethetically Active Radiation (PAR, µmol photons m^-2^ s^-1^).",
+                   "Top left panel represents the model under 250 µM of O~2~ and red light.",
+                    "Bottom left panel represents the model under 25 µM of O~2~ and red light.",
+                    "Top right panel represents the model under 250 µM of O~2~ and blue light.",
+                    "Bottom right panel represents the model under 25 µM of O~2~ and blue light.",
+                    "Legends represent a colour gradient of growth rate from no growth (white) to 1.00 d^-1^ (dark red or dark blue).",
+                    "Labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",
 
@@
 
-knitr::include_graphics(file.path(FiguresIn, "SS120PAR.png"))
-
-```
-
-\newpage
-
-The GAM model in Fig \@ref(fig:SS120GAM) summarizes growth responses
-of SS120 to red (A and B) or blue (C and D) peak PAR and photoperiod, across the
-2 imposed oxygen concentrations. Under 250 µM O~2~, Fig \@ref(fig:SS120GAM)C showed highest growth rates below blue light PAR of
+knitr::include_graphics(file.path(FiguresIn, "SS120PARGAM.png"))
+
+```
+
+\newpage
+
+The GAM model in Fig \@ref(fig:SS120PARGAM)B summarizes growth responses
+of SS120 to red or blue peak PAR and photoperiod, across the
+2 imposed oxygen concentrations. Under 250 µM O~2~, Fig \@ref(fig:SS120PARGAM)B showed highest growth rates below blue light PAR of
 50 µmol photons m^-2^ s^-1^ and photoperiods between 8 and 12 h,
@@
 (representing the 90^th^ percentile of achieved growth rate), out pacing
-the 90^th^ percentile fastest growth rates under 250 µM O~2~ (Fig \@ref(fig:SS120GAM)D). Under red light and 25 µM O~2~ (Fig \@ref(fig:SS120GAM)B) SS120 grew across most conditions of peak PAR and
+the 90^th^ percentile fastest growth rates under 250 µM O~2~ (Fig \@ref(fig:SS120PARGAM)B).
+Under red light and 25 µM O~2~ (Fig \@ref(fig:SS120PARGAM)B) SS120 grew across most conditions of peak PAR and
 photoperiod, achieving fastest growth under long photoperiods and peak
@@
 however, grow reliably under tested conditions at 2.5 µM O~2~.
-
-\newpage
-
-```{r SS120GAM,  fig.cap = SS120GAM_cap, fig.height = 10, fig.width = 10, echo = FALSE}
-
-# This is Fig6.tiff
-SS120GAM_cap <- glue("**Contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 grown under 660 nm (red) or 450 nm (blue) light.**",
-                    "X-axis is photoperiod (h).",
-                    "Y-axis is Photosynethetically Active Radiation (PAR, µmol photons m^-2^ s^-1^).",
-                    "**A.** represents the model under 250 µM of O~2~ and red light.",
-                    "**B.** represents the model under 25 µM of O~2~ and red light.",
-                    "**C.** represents the model under 250 µM of O~2~ and blue light.",
-                    "**D.** represents the model under 25 µM of O~2~ and blue light.",
-                    "Legends represent a colour gradient of growth rate from no growth (white) to 1.00 d^-1^ (dark red or dark blue).",
-                    "Labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",
-
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "SS120GAM.png"))
-
-```
 
@@
 µM for ubiquinol oxidase (non electrogenic) (Fig \@ref(fig:ProchlorococcusEnzymeKms)) is comparable to the lower limit
-for growth of MED4 in our experiments (Fig \@ref(fig:MED4GAM)). We
+for growth of MED4 in our experiments (Fig \@ref(fig:MED4PARGAM)B). We
 suggest that dependence upon this enzyme excludes MED4 from low oxygen
@@
 grow as well as *P. marinus* MIT9313, when exposed to high light stress
-under 25 µM O~2~ and not at all under 2.5 µM O~2~ (Fig \@ref(fig:SS120PAR)).
+under 25 µM O~2~ and not at all under 2.5 µM O~2~ (Fig \@ref(fig:SS120PARGAM)).
 

### 2024-05-23 Code/Plots_Genome.Rmd
Address reviewer comments

--- 2024-03-27 Code/Plots_Genome.Rmd
@@
 
-ProchlorococcusEnzymeKms <- MergedData %>%
+(ProchlorococcusEnzymeKms <- MergedData %>%
   filter(!is.na(Gene_count),
          Genus == "Prochlorococcus",
+         # Strain %in% c("CCMP1986", "MIT9313"),
          Strain %in% c("CCMP1375", "CCMP1986", "MIT9313", "NATL2A"),
@@
   ggplot() +
-  geom_errorbar(aes(x = reorder(EnzymeName, Km_mM * 1000), ymin = log10(Km_mM_min* 1000), ymax = log10(Km_mM_max* 1000))) +
-  # geom_ribbon(aes(ymin = log10(5e-4), ymax =  log10(5e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "blue") +
-  # geom_ribbon(aes(ymax = log10(5e-2), ymin =  log10(5e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "green") +
-  # geom_ribbon(aes(ymax = log10(280e-3), ymin =  log10(230e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "#FF0000") +
-  annotate(geom = "rect", ymin = log10(5e-4 * 1000), ymax =  log10(5e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "blue") +
-  annotate(geom = "rect", ymax = log10(5e-2 * 1000), ymin =  log10(5e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "green") +
-  annotate(geom = "rect", ymax = log10(280e-3 * 1000), ymin =  log10(230e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "#FF0000") +
-  geom_point(aes(x = reorder(EnzymeName, Km_mM* 1000), y = log10(Km_mM* 1000), shape = as.logical(Estimated), size = Gene_count), stroke = 1) +
+  geom_errorbar(aes(x = reorder(EnzymeName, Km_mM * 1000), ymin = Km_mM_min* 1000, ymax = Km_mM_max* 1000)) +
+  # geom_ribbon(aes(ymin = (5e-4), ymax =  (5e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "blue") +
+  # geom_ribbon(aes(ymax = (5e-2), ymin =  (5e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "green") +
+  # geom_ribbon(aes(ymax = (280e-3), ymin =  (230e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "#FF0000") +
+  annotate(geom = "rect", ymin = (5e-4 * 1000), ymax =  (5e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "blue") +
+  annotate(geom = "rect", ymax = (5e-2 * 1000), ymin =  (5e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "green") +
+  annotate(geom = "rect", ymax = (280e-3 * 1000), ymin =  (230e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "#FF0000") +
+  geom_point(aes(x = reorder(EnzymeName, Km_mM* 1000), y = (Km_mM* 1000), shape = as.logical(Estimated), size = Gene_count), stroke = 1) +
   geom_vline(aes(xintercept = reorder(EnzymeName, Km_mM* 1000)), size = 2,  data = . %>% filter(is.na(Km_mM)), linetype = "solid") +
-  geom_text(aes(x = 18.5, y = 0.25, label = "[O2] ≈ 2.5 µM"), color = "blue", size = 6) +
-  geom_text(aes(x = 18.5, y = 1.2, label = "[O2] ≈ 25 µM"), color = "darkgreen", size = 6) +
-  geom_text(aes(x = 18.5, y = 2.5, label = "[O2] ≈ 250 µM"), color = "#FF0000", size = 6) +
-  # geom_hline(yintercept = log10(5e-4), linetype = "dotted") +
-  # geom_hline(yintercept = log10(5e-3), linetype = "dotted") +
-  # geom_hline(yintercept = log10(5e-3), linetype = "dotted", color = "brown") +
-  # geom_hline(yintercept = log10(5e-2), linetype = "dotted", color = "brown") +
-  # geom_hline(yintercept = log10(230e-3), linetype = "dotted", color = "red") +
-  # geom_hline(yintercept = log10(290e-3), linetype = "dotted", color = "red") +
+  geom_text(aes(x = 18.5, y = 2.5, label = "[O2] ≈ 2.5 µM"), color = "blue", size = 6) +
+  geom_text(aes(x = 18.5, y = 25, label = "[O2] ≈ 25 µM"), color = "darkgreen", size = 6) +
+  geom_text(aes(x = 18.5, y = 250, label = "[O2] ≈ 250 µM"), color = "#FF0000", size = 6) +
+  # geom_hline(yintercept = (5e-4), linetype = "dotted") +
+  # geom_hline(yintercept = (5e-3), linetype = "dotted") +
+  # geom_hline(yintercept = (5e-3), linetype = "dotted", color = "brown") +
+  # geom_hline(yintercept = (5e-2), linetype = "dotted", color = "brown") +
+  # geom_hline(yintercept = (230e-3), linetype = "dotted", color = "red") +
+  # geom_hline(yintercept = (290e-3), linetype = "dotted", color = "red") +
   # scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
@@
        x = "Enzyme name",
-       y = ~log[10] ~ "("~K[m] ~O[2] ~"(µM))",
+       y = ~K[m] ~O[2] ~"(µM)",
        size = "Gene count",
        shape = ""~K[m]) +
+  scale_y_continuous(trans=scales::pseudo_log_trans(base = 10),
+                     breaks=c(1, 10, 100, 1000, 10000, 100000)) + #,labels = expression(10^0, 10^1, 10^2, 10^3, 10^4, 10^5)
   guides(shape = guide_legend(override.aes = list(size=5))) +
@@
         legend.title =  element_text(size = 30),  #change legend title font size
-        legend.text = element_text(size = 30))   #change legend text font size
+        legend.text = element_text(size = 30)))   #change legend text font size
 
-ProchlorococcusEnzymeKms
 ```
@@
 ```{r, ProchlorococcusEnzymeKms ggsave, include = FALSE} 
-ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms.png"), plot = ProchlorococcusEnzymeKms, height = 20, width = 17)
-ggsave(filename = file.path(PLOSFiguresRoundX, "Fig11.tiff"), plot = ProchlorococcusEnzymeKms, height = 20, width = 17, compression = "lzw")
+ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms.png"), plot = ProchlorococcusEnzymeKms, height = 23, width = 17)
+# ggsave(filename = file.path(PLOSFiguresRoundX, "Fig11.tiff"), plot = ProchlorococcusEnzymeKms, height = 20, width = 17, compression = "lzw")
+# ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms_julie.png"), plot = ProchlorococcusEnzymeKms, height = 23, width = 17)
 ```

### 2024-05-23 Code/Manuscript_O2.Rmd
minor edits

@@
 from HLI (including strain MED4) were detected throughout the water
-column, predominantly at high [O~2~]. The absence of proteins annotated
-for the key ATP Synthase complex for Clade HLI, compared to annotated
+column, predominantly at high [O~2~]. Though present in the genome of MED4, the absence of proteins annotated as ATP Synthase complex for Clade HLI, compared to annotated
 detections of ATP Synthase across the other three clades suggests
@@
 µM (Fig \@ref(fig:SS120PARGAM)). 2.5 µM O~2~ growth experiments were not
-conducted for 4 and 16 h photoperiods under PAR of 180 µmol photons
+conducted for 4 and 16 h photoperiods under peak PAR of 180 µmol photons
+m^-2^ s^-1^ and for red light under peak PAR of 90 µmol photons
 m^-2^ s^-1^, as no growth occurred when SS120 was exposed to 8 and 12 h
-photoperiods. Red light 16 h photoperiod experiments were not performed
-due to time constraints.
+photoperiods.
 
@@
 16 h photoperiods and red light under 4 and 16 h photoperiods were not
-performed due to time constraints.
+performed as cultures were unlikely to grow.
 

### 2024-05-23 Output/PLOSRound2/ResponsetoReviewers.txt
MOved to new folder

--- 2024-05-22 Output/PLOSFiguresRound1/ResponsetoReviewers.txt
@@
 
+Thank you for this suggestion. We have edited the text:
+Line XXX:
+
 Figure S4 — It is very hard to see the fit lines other than the pooled fit. Consider using different colors 
@@
 
-We apologize for the omissions and have fixed the y-axis label and units. The red band is narrow because the log .........XXX
+We apologize for the omissions.
+We have revised the axis labels to make the log scaling more noticeable.
+The narrowness of the red bar (spanning 230 to 280 µM) should also be more apparent with the new scaling.
 
@@
 
-Changed DNA ligase to DNA repair ligase. 
+Thank you for your comment, the revised text now reads "DNA repair ligase".  
 Lines XXX:
@@
 
-We have edited the text:
+Thank you. We have edited the text:
 Line XXX:

### 2024-05-23 Code/Plots_GAM.Rmd
Fixed GAM plot for SS120

@@
 ErrorTolGrowth = 30 # the amplitude tolerance of the standard error of the fitted growth estimates
-ErrorTol = 30 # the amplitude tolerance of the standard error of the fitted GAM
+ErrorTol = 35 # the amplitude tolerance of the standard error of the fitted GAM
 
@@
 ErrorTolGrowth = 30 # the amplitude tolerance of the standard error of the fitted growth estimates
-ErrorTol = 30 # defined for the GAM fit
+ErrorTol = 35 # defined for the GAM fit
 

### 2024-05-23 Code/Manuscript_O2.Rmd
new .bib

@@
 FiguresIn <- file.path("..","Output", "Figures")
-FigureInO2Analy <- file.path(  "..", "..", "O2Analyses", "Output")
-
 ```
@@
 waters, with increases in *P. marinus* of approximately 50% in the more
-poleward regions of their distributions. @follettTrophicInteractionsHeterotrophic2022 however, model interactions of heterotrophic  bacteria  that may influence latitudinal expansion of *P. marinus*.
+poleward regions of their distributions. @follettTrophicInteractionsHeterotrophic2022, however, model interactions of heterotrophic  bacteria  that may influence latitudinal expansion of *P. marinus*.
 
@@
 PUR might simplify different photoperiods, spectral bands, and PAR
-levels into a common parameter, making growth response comparisons
+levels into a common parameter, making growth rate comparisons
 across strains and different oxygen levels more accessible. We aimed to
-detect whether growth responses are driven simply by cumulative diel
+detect whether growth rates are driven simply by cumulative diel
 PUR, or whether specific photoperiods, spectral bands or PAR levels have
@@
 approaches (e.g. parallel reaction monitoring), it is difficult to discern accuracies of strain assignment annotations, particularly as the proteins of interest in this study are
-highly conserved across strains [@saitoNeedlesBlueSea2015]. We are, however, confident in clade
-classifications for each protein examined. The data is also limited
+highly conserved across strains [@saitoNeedlesBlueSea2015]. The data is also limited
 because a peptide sequence was not determined unless there was already a
@@
 peptides of interest may not be identifiable.
-This MetZyme dataset used a deep paired metagenomic database (https://www.ebi.ac.uk/pride/archive/projects/PXD030684) to enable this peptide-to-spectrum matching [@saitoMultipleNutrientStresses2014; @saundersMicrobialFunctionalDiversity2022].
-Furthermore, protein identifications were based on peptide to spectrum matching using SEQUESTHT within Proteome Discoverer software (Thermo) and spectral counts were enumerated using Scaffold software (Proteome Software) using a FDR of <0.1% on the peptide level as described in Saunders *et al*.
+The MetZyme dataset used a deep paired metagenomic database (https://www.ebi.ac.uk/pride/archive/projects/PXD030684) to enable peptide-to-spectrum matching [@saitoMultipleNutrientStresses2014; @saundersMicrobialFunctionalDiversity2022].
+Furthermore, protein identifications were based on peptide-to-spectrum matching using SEQUESTHT within Proteome Discoverer software (Thermo) and spectral counts were enumerated using Scaffold software (Proteome Software) using a FDR of <0.1% on the peptide level as described in Saunders *et al*.
 [@saundersMETATRYPMetaproteomicLeast2020].
+While the accuracy of strain specific protein annotation is noted due to highly conserved common proteins, the two step approach of peptide-to-spectrum matching using deep paired metagenomics identify proteins at the clade classifications.
 
@@
 
-Three xenic cultures of *P.marinus* were obtained from Bigelow Labs, NCMA Maine, USA. MED4
+*Prochlorococcus* remain challenging to culture at high densities, partially due to their dependence upon mutualistic heterotrophic bacteria to detoxify
+reactive oxygen species [@morrisFacilitationRobustGrowth2008;
+@morrisDependenceCyanobacteriumProchlorococcus2011].
+MED4, SS120 and MIT9313 have been successfully cultured in laboratories [@mooreComparativePhysiologySynechococcus1995; @mooreCulturingMarineCyanobacterium2007], and used to show that ecotypic classifications correspond to biochemical differences among strains [@bonisteelStrainSpecificDifferences2018].
+Three xenic cultures of *P.marinus* were obtained from Bigelow Labs, NCMA Maine, USA.
+MED4
 (CCMP1986) is from High-Light adapted (HLI) clade; SS120 (CCMP1375) is
@@
 absence of growth of some strains under some levels of photoperiod, PAR,
-or [O~2~] meant we completed 268 growth factor treatment combinations.
+or [O~2~] meant we completed 268 growth factor treatment combinations with 1 to 3 replicates.
 
@@
 zone depths. Photoperiods were chosen to approximate diel cycles
-characteristic of current and hypothetical future niches of *P.
-marinus*; 16 h represents temperate (45°N) summer at the ocean surface;
+characteristic of current and hypothetical future niches of *P.marinus* and delivered approximating a sinusoidal sun rise and fall; 16 h represents temperate (45°N) summer at the ocean surface;
 12 h for equatorial (0°N) ocean surface or temperate (45°N) spring and
@@
 spring and fall at depth and equatorial (0°N) deep ocean depths; and 4 h
-for temperate (45°N) winter or deep ocean depths during temperate (45°N)
-spring and fall.
+for temperate (45°N) winter at deep ocean depths.
 
@@
 as corresponding to the Gene Ontology Term (<GO:0006281> - DNA repair),
-in *P. marinus* strains (MED4, MIT9313, SS120, and NATL2A). We grouped
+in *P. marinus* strains (MED4, NATL2A, SS120, and MIT9313). We grouped
 orthologs together by EC number and their KO number and determined the
@@
 depth and at low [O~2~], compared to other strains.
+Our analyses utilized a proteomics dataset; however, alternate approaches, such as metagenomics or metatranscriptomics, could have been employed to analyze ecotype abundances using the TARA Oceans [@pesantOpenScienceResources2015] dataset.
 
@@
 
-*Prochlorococcus marinus* MED4, clade HLI, grew under 250 µM O~2~ and growth rates increased with higher imposed PAR and longer photoperiods (Fig \@ref(fig:MED4PARGAM)), across all spectral wavebands.
+The growth rate for *Prochlorococcus marinus* MED4, clade HLI, under 250 µM O~2~, increased with higher imposed PAR and longer photoperiods (Fig \@ref(fig:MED4PARGAM)A), across all spectral wavebands.
 No growth was
@@
 
-# This is Fig5.tiff
+# This is Fig4.tiff
 SS120PARGAM_cap <- glue("**A. Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low-Light (LLII/III) deep ocean clade) vs. photoperiod (h). **",
@@
 increased with longer photoperiods, under low 30 µmol photons m^-2^
-s^-1^ peak PAR, (Fig \@ref(fig:MIT9313PAR)). Under intermediate 90
+s^-1^ peak PAR, (Fig \@ref(fig:MIT9313PARGAM)A). Under intermediate 90
 µmol photons m^-2^ s^-1^ peak PAR growth rates decreased with increasing
@@
 For MIT9313 under 25 µM O~2~, growth rate increased with increasing
-photoperiods for all spectral wavebands tested (Fig \@ref(fig:MIT9313PAR)), with the fastest overall growth rate for MIT9313
+photoperiods for all spectral wavebands tested (Fig \@ref(fig:MIT9313PARGAM)A), with the fastest overall growth rate for MIT9313
 `r PURPARFits %>% filter(Strain == "MIT9313", WL == "WW", O2_uM == "25", Photoperiod == 16, Par_ue == 90) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
@@
 generally slower than under the parallel experiments at 25 µM O~2~
-(Fig \@ref(fig:MIT9313PAR)). Growth estimates showed scatter among
+(Fig \@ref(fig:MIT9313PARGAM)A). Growth estimates showed scatter among
 replicates, suggesting 2.5 µM O~2~ is near the tolerance limit for
@@
 
-```{r MIT9313PAR, fig.cap = MIT9313PAR_cap, fig.height = 6, fig.width = 8, echo = FALSE}
-
-# This is Fig7.tiff
-MIT9313PAR_cap <- glue("**Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
+```{r MIT9313PARGAM, fig.cap = MIT9313PARGAM_cap, fig.height = 6, fig.width = 8, echo = FALSE}
+
+# This is Fig5.tiff
+MIT9313PARGAM_cap <- glue("**A. Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
                     "Rows separate data from levels of imposed dissolved O~2~ concentrations (250 µM, 25 µM and 2.5 µM).",
@@
                     "Large circles show mean or single determinations of growth rate from logistic curve fits; small circles show values for replicate determinations, if any: replicates often fall with larger circles.",
+                    "**B.
+Contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 grown under 660 nm (red) or 450 nm (blue) light.**",
+                    "X-axis is photoperiod (h).",
+                    "Y-axis is Photosynthetically Active Radiation (PAR; µmol photons m^-2^ s^-1^).",
+                   "Top left panel represents the model under 250 µM of O~2~ and red light.",
+                   "Center left panel represents the model under 25 µM of O~2~ and red light.",
+                   "Bottom left panel represents the model under 2.5 µM of O~2~ and red light.",
+                    "Top right panel represents the model under 250 µM of O~2~ and blue light.",
+                    "Center right panel represents the model under 25 µM of O~2~ and blue light.",
+                    "Bottom right panel represents the model under 2.5 µM of O~2~ and blue light.",
+                    "Legends represent a colour gradient of growth rate from no growth (white) to 1.00 d^-1^ (dark red or dark blue).",
+                    "Labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",
 
@@
 
-knitr::include_graphics(file.path(FiguresIn, "MIT9313PAR.png"))
-
-```
-
-\newpage
-
-The GAM model in Fig \@ref(fig:MIT9313GAM) summarizes MIT9313 growth
-responses to red (A-C) or blue (D-F) peak PAR and photoperiod. Under
-250 µM O~2~, Fig \@ref(fig:MIT9313GAM)D shows MIT9313 achieves
+knitr::include_graphics(file.path(FiguresIn, "MIT9313PARGAM.png"))
+
+```
+
+\newpage
+
+The GAM model in Fig \@ref(fig:MIT9313PARGAM)B summarizes MIT9313 growth
+responses to red or blue peak PAR and photoperiod. Under
+250 µM O~2~, Fig \@ref(fig:MIT9313PARGAM)B shows MIT9313 achieves
 fastest growth rates between blue peak PAR of 30 µmol photons m^-2^
@@
 indicated by the contour line labeled 0.52 d^-1^ representing the 90^th^
-percentile of achieved growth rates. Fig \@ref(fig:MIT9313GAM)D also
+percentile of achieved growth rates. Fig \@ref(fig:MIT9313PARGAM)B also
 shows that growth rate increases with longer photoperiods, as long as
@@
 contrast, under red light and 250 µM O~2~ MIT9313 grows faster while
-exploiting higher peak PAR and longer photoperiods. Fig \@ref(fig:MIT9313GAM)E shows that MIT9313 can exploit all blue PAR levels
+exploiting higher peak PAR and longer photoperiods. Fig \@ref(fig:MIT9313PARGAM)B shows that MIT9313 can exploit all blue PAR levels
 and most photoperiods with 90^th^ percentile of fastest growth rate
-between 30 to 100 µmol photons m^-2^ s^-1^ PAR. Fig \@ref(fig:MIT9313GAM)F shows that MIT9313 maintains growth even under
+between 30 to 100 µmol photons m^-2^ s^-1^ PAR. Fig \@ref(fig:MIT9313PARGAM)B shows that MIT9313 maintains growth even under
 2.5 µM O~2~, under photoperiods between 8 and 12 h and peak blue PAR
 between 50 to 100 µmol photons m^-2^ s^-1^ PAR. Thus the designation of
-MIT9313 as a LL clade is dependent upon [O~2~] and light spectra (Fig \@ref(fig:MIT9313GAM)E).
-
-\newpage
-
-```{r MIT9313GAM,  fig.cap = MIT9313GAM_cap, fig.height = 10, fig.width = 10, echo = FALSE}
-
-# This is Fig8.tiff
-MIT9313GAM_cap <- glue("**Contour plot of a Generalized Additive Model (GAM) representing the chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 grown under 660 nm (red) or 450 nm (blue) light.**",
-                    "X-axis is photoperiod (h).",
-                    "Y-axis is Photosynthetically Active Radiation (PAR; µmol photons m^-2^ s^-1^).",
-                    "**A.** represents the model under 250 µM of O~2~ and red light.",
-                    "**B.** represents the model under 25 µM of O~2~ and red light.",
-                    "**C.** represents the model under 2.5 µM of O~2~ and red light.",
-                    "**D.** represents the model under 250 µM of O~2~ and blue light.",
-                    "**E.** represents the model under 25 µM of O~2~ and blue light.",
-                    "**F.** represents the model under 2.5 µM of O~2~ and blue light.",
-                    "Legends represent a colour gradient of growth rate from no growth (white) to 1.00 d^-1^ (dark red or dark blue).",
-                    "Labeled contour lines indicate the 90%, 50%, and 10% quantiles for achieved growth rate.",
-
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "MIT9313GAM.png"))
-
-```
+MIT9313 as a LL clade is dependent upon [O~2~] and light spectra (Fig \@ref(fig:MIT9313PARGAM)B).
 
@@
 
-# This is Fig9.tiff
+# This is Fig6.tiff
  BluevsRedPurFitsPlots_cap <- glue("**Chlorophyll specific growth rate (d^-1^) vs. cumulative diel Photosynthetically Usable Radiation (PUR, µmol photons m^-2^ d^-1^).**",
@@
 
-*Prochlorococcus*, with their reduce genomes are the smallest of any known oxyphototroph, render them
-partially dependent upon mutualistic heterotrophic bacteria to detoxify
-reactive oxygen species [@morrisFacilitationRobustGrowth2008;
-@morrisDependenceCyanobacteriumProchlorococcus2011]. Under full atmospheric [O~2~] and blue light, LL clades of
+Under full atmospheric [O~2~] and blue light, LL clades of
 *Prochlorococcus* are restricted to growth under low light, in part
@@
 PCC6803.
-Protein homologies between *Prochlorococcus* and *Synechocystis* were determined by multiple sequence alignment with MUSCLE followed by construction of maximum likelihood phylogenetic tree using 1000 bootstrap replicates in MEGAX.",
+Protein homologies between *Prochlorococcus* and *Synechocystis* were extracted from @bonisteelStrainSpecificDifferences2018.",
               col.names =  c("Organism",
@@
 mediate PSII repair, and then only in near-surface samples subject to
-higher light levels. Furthermore, even though MIT9313 grows (Fig \@ref(fig:MIT9313GAM)), and is detected in the ocean at low [O~2~]
+higher light levels. Furthermore, even though MIT9313 grows (Fig \@ref(fig:MIT9313PARGAM)B), and is detected in the ocean at low [O~2~]
 (Fig \@ref(fig:CladeProchloroPhotosynthDepthO2)), no FtsH from
@@
 
-# This is Fig10.tiff
+# This is Fig7.tiff
 CladeProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein metabolism complexes.**", 
@@
 
-# This is Fig11.tiff
+# This is Fig8.tiff
 ProchlorococcusEnzymeKms_cap <- glue("**K~m~ values for oxygen metabolizing enzymes.**" ,
@@
 deoxyribodipyrimidine photolyase and DNA repair ligase (ATP) in *P. marinus*
-MIT9313 and *P. marinus* SS120 contribute, in part, to the inability of these two strains to
-tolerate growth under full [O~2~] and high light, found at the ocean
+MIT9313 and *P. marinus* SS120 may, in part, explain why these two strains cannot tolerate growth under full [O~2~] and high light, found at the ocean
 surface. Furthermore, the protective effect of lower [O~2~], allowing
@@
 
-#  This is Fig12.tiff
+#  This is Fig9.tiff
 DNARepairFig_cap <- glue("**Genes encoding DNA repair enzymes.**" ,
@@
 higher light levels and cumulative diel PUR, but only under low oxygen
-conditions of 25 µM and 2.5 µM (Fig \@ref(fig:MIT9313PAR)), enabling
+conditions of 25 µM and 2.5 µM (Fig \@ref(fig:MIT9313PARGAM)A), enabling
 MIT9313 to grow in OMZ, even at depths closer to the surface. MIT9313
@@
 
-All data obtained from the Multicultivator were saved as comma separated
-values files and are available at
-<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData/MultiCultiData1.zip>.
-<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData/MultiCultiData2.zip>.
-<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData/MultiCultiData3.zip>.
-All data obtained from the Jaz spectrometer were saved as text files and are available at
-<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData/JazEmData.zip>.
-All data obtained from the Olis 14 UV/VIS Clarity Spectrophotometer were saved as ascii files and are available at
-<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData/OlisData.zip>.
-Meta Data for the Multicultivator runs were imported and saved as a .Rds and available at
-<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData/CultureCatalog.Rds>.
+All data and metadata obtained from the Multicultivator were saved as comma separated
+values files and are available on the Borealis data repository (DOI pending).
 

### 2024-05-24 Output/PLOSRound2/ResponsetoReviewers.txt
edits

@@
 Line 55: LLII/III and LLIV are not the “oldest” clades, but the most basal or early branching.
-We have edited the text:
-Line XXX
+
+We have edited the text in the revised manuscript: "Clades LLII and LLIII, including cultured strain SS120, are grouped together as early branching phylogenetic lineage diversifying in the P.
+marinus radiation, with a preference for low light."
+Line: XXX
 
@@
 This likely reflects an annotation assignment issue because the ATP Synthase proteins are highly conserved, so assignments to strains or clades of Prochlorococcus may be ambiguous.
-We have edited the text:
-Line XXX:
+We have edited the text in the revised manuscript: "Though present in the genome of MED4, the absence of proteins annotated as ATP Synthase complex for Clade HLI, compared to annotated detections of ATP Synthase across the other three clades suggests limitations in the annotation process for highly conserved protein sequences."
+Line: XXX
 
@@
 
-Thank you for this suggestion. We have edited the text:
-Line XXX:
+Thank you for this suggestion. 
+We have edited the text:
+Line: XXX
 
@@
 Table 1: The trees described in the legend should be included in the supplemental material.
+
+Thank you for bringing this to our attention.
+We clarified the wording on line XXXX of the revised manuscripted.
+"Protein homologies between *Prochlorococcus* and *Synechocystis* were extracted from @bonisteelStrainSpecificDifferences2018."
 
@@
 Thank you for your comment, the revised text now reads "DNA repair ligase".  
-Lines XXX:
+Line: XXX
 
@@
 
-Thank you. We have edited the text:
-Line XXX:
+Thank you.
+The revised manuscript now reads: "The absence of genes encoding deoxyribodipyrimidine photolyase and DNA ligase (ATP) in P.
+marinus MIT9313 and P.
+marinus SS120 may, in part, explain why these two strains cannot tolerate growth under full [O2] and high light, found at the ocean surface."
+Line: XXX
 
@@
 
+Thank you for highlighting this oversight. 
+We added the following in the materials and methods section of the revised manuscript:
+"Each tube containing 70 mL of Pro99 media was inoculated with 10 mL of growing maintenance culture approximately 16 to 22 hours
+before the start of each growth experiment. The tubes containing the cultures were placed in the Multicultivator water bath set at 22°C, 
+sparged with the experimental [O2], and kept in the dark for approximately 12 hours until the photoregime of a sinusoidal photoperiod 
+commenced the following morning such that peak PAR occurred at noon each day."
+Line: XXX
+
+We added the following in the results and discussion section of the revised manuscript:
+"While we implemented measures to minimize the shock to cultures from exposure to experimental growth conditions by inoculating them the day
+ before the experiment began and employing a sinusoidal photoperiod with a gradual increase in PAR exposure, we acknowledge that cells typically
+ need multiple generations to acclimate to new growth conditions (Moore et al. 2007)."
+Line: XXX
+
 This reviewer found the manuscript to be quite difficult to read as I kept wanting to understand how 
@@
 We have edited the text:
-Line XXX:
+Line: XXX
 
@@
 
-We have edited the text:
-Line XXX:
+We have edited the text in the revised manuscript: "Clades LLII and LLIII, including cultured strain SS120, are grouped together as early branching phylogenetic lineage diversifying in the *P.
+marinus* radiation, with a preference for low light."
+Line: XXX
 
@@
 
-We have edited the text:
+Thank you for  bringing this to our attention.
+We have added the following text to the revised manuscript: "Follett et al 2022, however, model interactions of heterotrophic bacteria  that may influence latitudinal expansion of *P.
+marinus*."
 Line XXX:
@@
 
+Thank you for noting that this needs further clarification. 
+We have edited the paragraph for clarity in the revised manuscript adding: "While the accuracy of strain specific protein annotation is noted due to highly conserved common proteins, the two step approach of peptide-to-spectrum matching using deep paired metagenomics identify proteins at the clade classifications."
+Lines: XXX
+
 209: It seems overly general to blame the culturing difficulties solely on having reduced genomes – in 
@@
 
-We have edited the text:
+Thank you for your comment.
+We have edited the text in the revised manuscript: "Prochlorococcus remain challenging to culture at high densities, partially due to their dependence upon mutualistic heterotrophic bacteria to detoxify
+reactive oxygen species [48,49]." 
 Line XXX:
@@
 
+Thank you for your comment. We used proteomics as we have experience with cyanobacteria protein and have work flows in place.
+We have edited the text in the revised manuscript: "Our analyses utilized a proteomics dataset; however, alternate approaches, such as metagenomics or metatranscriptomics, could have been employed to analyze ecotype abundances using the TARA Oceans [@pesantOpenScienceResources2015] dataset."
+Line: XXX
+
 407: growth -> grew?
 
-We have edited the text:
+We have edited the text: "The growth rate for Prochlorococcus marinus MED4, clade HLI, under 250 µM O2, increased with higher imposed PAR and longer photoperiods (Fig 3A), across all spectral wavebands."
 Line XXX:
@@
 sure this information is clear in the methods
+
+Thank you for this comment. In this work we used 1 to 3 replicates depending on the experimental conditions. Specific number of replicates (shown as small dots in Figures (3 - 5)).
+We have edited the text in the revised manuscript:" Consistent absence of growth of some strains under some levels of photoperiod, PAR, or [O~2~] meant we completed 268 growth factor treatment combinations with 1 to 3 replicates."
+Line: XXX
 
@@
 
-We have combined the growth rate figure with the GAM model for each strain.
+Thank you for your suggestion. We have combined the growth rate figure with the GAM model for each strain. We believe this will aid the reader with interpreting both plots.
 

### 2024-05-24 Code/Manuscript_O2.Rmd
edits

@@
 common temperature of 22°C. Each tube containing 70 mL of Pro99 media
-was inoculated with 10 mL of growing maintenance culture. In a factorial
+was inoculated with 10 mL of growing maintenance culture approximately 16 to 22 hours before the start of each growth experiment.
+The tubes containing the cultures were placed in the Multicultivator water bath set at 22°C, sparged with the experimental [O~2~], and kept in the dark for approximately 12 hours until the photoregime of a sinusoidal photoperiod commenced the following morning such that peak PAR occurred at noon each day.
+In a factorial
 matrix design, each tube was then subject to an individual combination
@@
 bands, and [O~2~] to approximate current, and potential future,
-latitudinal, depth and seasonal niches for *Prochlorococcus* strains. As
+latitudinal, depth and seasonal niches for *Prochlorococcus* strains.
+While we implemented measures to minimize the shock to cultures from exposure to experimental growth conditions by inoculating them the day before the experiment began and employing a sinusoidal photoperiod with a gradual increase in PAR exposure, we acknowledge that cells typically need multiple generations to acclimate to new growth conditions [@mooreCulturingMarineCyanobacterium2007].
+As
 mentioned, growth under red light could prove mechanistically
@@
 2 imposed oxygen concentrations. Under 250 µM O~2~, Fig \@ref(fig:SS120PARGAM)B showed highest growth rates below blue light PAR of
-50 µmol photons m^-2^ s^-1^ and photoperiods between 8 and 12 h,
-indicated by the contour line labeled 0.18 d^-1^ (representing the
+50 µmol photons m^-2^ s^-1^ and photoperiods between 12 and 16 h,
+indicated by the contour line labeled 0.35 d^-1^ (representing the
 90^th^ percentile of achieved growth rate). Under 250 µM O~2~ SS120 is
@@
 PAR levels, achieving faster growth rates at a higher PAR of \~100 µmol
-photons m^-2^ s^-1^, indicated by the contour line labeled 0.41 d^-1^
+photons m^-2^ s^-1^, indicated by the contour line labeled 0.42 d^-1^
 (representing the 90^th^ percentile of achieved growth rate), out pacing
@@
 additionally, white LED and red light treatments induced growth across
-all tested photoperiods under 25 µM O~2~. The 25 µM O~2~, 4 h
-photoperiod experiments under white LED light and were not performed due
-to time constraints.
+all tested photoperiods under 25 µM O~2~.
 
@@
 generally slower than under the parallel experiments at 25 µM O~2~
-(Fig \@ref(fig:MIT9313PARGAM)A). Growth estimates showed scatter among
+(Fig \@ref(fig:MIT9313PARGAM)A). Growth rates showed scatter among
 replicates, suggesting 2.5 µM O~2~ is near the tolerance limit for
@@
 blue light treatments and peak PAR of 90 µmol photons m^-2^ s^-1^ but
-did not grow under 16 h photoperiod. Growth for MIT9313 under PAR of 180
+did not grow under 16 h photoperiod. Growth rates for MIT9313 under PAR of 180
 µmol photons m^-2^ s^-1^ and blue light treatment decreased with
@@
 contrast, under red light and 250 µM O~2~ MIT9313 grows faster while
-exploiting higher peak PAR and longer photoperiods. Fig \@ref(fig:MIT9313PARGAM)B shows that MIT9313 can exploit all blue PAR levels
-and most photoperiods with 90^th^ percentile of fastest growth rate
-between 30 to 100 µmol photons m^-2^ s^-1^ PAR. Fig \@ref(fig:MIT9313PARGAM)B shows that MIT9313 maintains growth even under
+exploiting higher peak PAR and longer photoperiods. MIT9313 can exploit all blue PAR levels
+and most photoperiods under 25 µM O~2~ with 90^th^ percentile of fastest growth rate
+between 30 to 100 µmol photons m^-2^ s^-1^ PAR. MIT9313 maintains growth even under
 2.5 µM O~2~, under photoperiods between 8 and 12 h and peak blue PAR

### 2024-05-24 Code/Manuscript_O2.Rmd
Added temperate niche table

@@
 
-Fig \@ref(fig:DNARepairFig) shows genes encoding DNA repair for *P.
-marinus* strains. As expected, *P. marinus* MED4 possesses the largest,
+Fig \@ref(fig:DNARepairFig) shows genes encoding DNA repair for *P.marinus* strains. As expected, *P. marinus* MED4 possesses the largest,
 most complete suite of genes encoding DNA repair enzymes, followed by
@@
 extend to the near surface.
+
+\newpage
+
+```{r read temperate niche sheet, include=FALSE}
+
+ProchloroNiches <- read_csv(file.path(DataIn, "Prochlorococcus_temperate_niches.csv"))
+
+ProchloroNiches <- ProchloroNiches %>% 
+  mutate(MED4 = case_when(MED4 == "Potential" ~ "+",
+                          MED4 == "Excluded" ~ "-"),
+         SS120 = case_when(SS120 == "Potential" ~ "+",
+                          SS120 == "Excluded" ~ "-"),
+         MIT9313 = case_when(MIT9313 == "Potential" ~ "+",
+                          MIT9313 == "Excluded" ~ "-"))
+
+```
+
+```{r NichesTable,  fig.height = 8, fig.width = 6, echo = FALSE}
+
+knitr::kable(ProchloroNiches,
+             caption = "Potential temperate niches for *Prochlorococcus marinus* ecotypes defined by season, depth, and oxygen; Full denotes 250 µM of dissolved oxygen and OMZ denotes 25 µM of dissolved oxygen.
+Plus symbols (+) indicate a potential niche, minus symbols (-) not a potential niche.",
+        align = "lllccc" )
+```
+
+\newpage
 

### 2024-05-24 Output/PLOSRound2/ResponsetoReviewers.txt
minor edits

@@
 Line: XXX
+XXXXX Mireille to address the wording pertaining to photolyase. We did not imply that photolyase was responsible for the results we found in lab but I will confirm this. XXXXXXXXXX
 

### 2024-05-27 Code/Manuscript_O2.Rmd
more edits

@@
 A Generalized Additive Model (GAM) [@woodGeneralizedAdditiveModels2017]
-was applied to the relation of chlorophyll-specific µ, d^-1^ to
+was applied to the relation of chlorophyll-specific µ d^-1^ to
 photoperiod and PAR level, for each growth [O~2~] level, and for the
@@
 [O~2~] (Fig \@ref(fig:BluevsRedPurFitsPlots)I). For distinct fits for
-different photoperiod fits refer to Fig \@ref(fig:PhotoperiodPurFitsPlots) G-I.
+different photoperiods refer to Fig \@ref(fig:PhotoperiodPurFitsPlots) G-I.
 
@@
 excluded from near-surface growth niches by high PAR, unless OMZ zones
-extend to the near surface.
+extend to the near surface (Table \@ref(tab:NichesTable).
 
@@
 
+XXXX Added this section , if keeping then Mirielle will add the citations to zotero XXXX
+
+The potential expansion of  *P.
+marinus*  polewards may contribute to the primary food base of an aquatic ecosystem that has already undergone changes in temperate northern waters; commercial fish populations are shifting with new species immigrating  [@zellerCheungZellerPauly2011], endangered whales actively searching for food sources are becoming more prevalent [@meyer-gutbrodMarineSpeciesRange2018] and the white shark seasonal presence is increasing  either due to rising ocean temperatures or following marine prey [@bastienInconspicuousRecoveringNorthward2020].
+While the exact impact of the presence of *P.
+marinus*  on the species distribution of marine wildlife in temperate northern waters is unknown, there is little doubt that *Prochlorococcus* will play a significant role in shaping this distribution.
+
 \newpage

### 2024-05-27 Code/Plots_PURFits.Rmd
Made fit lines thicker

@@
   geom_rect(xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, fill = "white") +
-  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 3.5, alpha = 1.0) +
-    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2.0, alpha = 0.6) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.80, linetype = "solid", show.legend = F, data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotted", show.legend = F, data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.80, linetype = "solid", show.legend = F, data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotdash", show.legend = F, data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dashed", show.legend = F, data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotted", show.legend = F, data = . %>% unnest(Predict_8) %>%  filter(Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.80, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotdash", show.legend = F, data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 25, Strain == "MIT9313")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "dotted", show.legend = F, data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.6, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +
+  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 3.5, alpha = 0.7) +
+    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2.0, alpha = 0.7) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.1, linetype = "solid", show.legend = F, data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "dotted", show.legend = F, data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.1, linetype = "solid", show.legend = F, data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "dotdash", show.legend = F, data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "dashed", show.legend = F, data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "dotted", show.legend = F, data = . %>% unnest(Predict_8) %>%  filter(Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.1, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "dotdash", show.legend = F, data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 25, Strain == "MIT9313")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "dotted", show.legend = F, data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +
  labs(y = "Chlorophyll specific growth rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +

### 2024-05-27 Output/PLOSRound2/ResponsetoReviewers.txt
more edits

@@
 We added the following in the results and discussion section of the revised manuscript:
-"While we implemented measures to minimize the shock to cultures from exposure to experimental growth conditions by inoculating them the day
+"While we implemented measures to minimize shock to cultures from exposure to experimental growth conditions by inoculating them the day
  before the experiment began and employing a sinusoidal photoperiod with a gradual increase in PAR exposure, we acknowledge that cells typically
@@
 XXX Energy- blue have shorter WL so high energy, red longer WL so lower energy??? XXXX
+XXX Can add something on line 827 to expand XXXXX
 

### 2024-05-27 Code/Manuscript_O2.Rmd
more edits

@@
 latitudinal, depth and seasonal niches for *Prochlorococcus* strains.
-While we implemented measures to minimize the shock to cultures from exposure to experimental growth conditions by inoculating them the day before the experiment began and employing a sinusoidal photoperiod with a gradual increase in PAR exposure, we acknowledge that cells typically need multiple generations to acclimate to new growth conditions [@mooreCulturingMarineCyanobacterium2007].
+While we implemented measures to minimize shock to cultures from exposure to experimental growth conditions by inoculating them the day before the experiment began and employing a sinusoidal photoperiod with a gradual increase in PAR exposure, we acknowledge that cells typically need multiple generations to acclimate to new growth conditions [@mooreCulturingMarineCyanobacterium2007].
 As

### 2024-05-27 Code/Plots_PURFits.Rmd
more edits

@@
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.1, linetype = "solid", show.legend = F, data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "dotted", show.legend = F, data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.1, linetype = "dotted", show.legend = F, data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.1, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.1, linetype = "solid", show.legend = F, data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "dotdash", show.legend = F, data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "dashed", show.legend = F, data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "dotted", show.legend = F, data = . %>% unnest(Predict_8) %>%  filter(Strain == "SS120")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.1, linetype = "dotdash", show.legend = F, data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.1, linetype = "dashed", show.legend = F, data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.1, linetype = "dotted", show.legend = F, data = . %>% unnest(Predict_8) %>%  filter(Strain == "SS120")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.1, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.1, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) +
-  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "dotdash", show.legend = F, data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 25, Strain == "MIT9313")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "dotted", show.legend = F, data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
-   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.9, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +
+  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.1, linetype = "dotdash", show.legend = F, data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.1, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 25, Strain == "MIT9313")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.1, linetype = "dotted", show.legend = F, data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
+   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 1.1, linetype = "aa", show.legend = F, data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +
  labs(y = "Chlorophyll specific growth rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +

### 2024-05-27 Output/PLOSRound2/ResponsetoReviewers.txt
edits

@@
 your code is shared in a way that follows best practice and facilitates reproducibility and reuse.
+
 3. Thank you for uploading your study's underlying data set. Unfortunately, the repository you have 
@@
 
+XXX Check XXX
+
 Reviewers' comments:
@@
 This likely reflects an annotation assignment issue because the ATP Synthase proteins are highly conserved, so assignments to strains or clades of Prochlorococcus may be ambiguous.
-We have edited the text in the revised manuscript: "Though present in the genome of MED4, the absence of proteins annotated as ATP Synthase complex for Clade HLI, compared to annotated detections of ATP Synthase across the other three clades suggests limitations in the annotation process for highly conserved protein sequences."
+We have edited the text in the revised manuscript: "Though present in the genome of MED4, the absence of proteins annotated as ATP Synthase complex for Clade HLI, compared to annotated detections of ATP Synthase across the other three clades suggests limitations in the OPP annotation process for highly conserved protein sequences."
 Line: XXX
@@
 
+ XXX Doug address RUBISCO XXX
+
 Figures 3 through 8: These figures are obviously the crux of the results in this paper, but as they are 
@@
 
-Thank you for this suggestion. We have combined the growth rate figure with the GAM model for each strain.
+Thank you for this suggestion. We have combined the growth rate figure with the GAM model for each strain to faciliate comparisons.
 
@@
 
-XXXX Want to keep as is. Will add more justification for red light. Reviewer 2 wants more about differences b/t blue and red (energy input from these 2 WL) XXXXX
+XXX MIreille rephrase   We have addressed the jusification of red light to the reveiwer 2. XXX
 
@@
 
+XXXX Predicting P. marinus is is beyond the scope of this study but we added a table....XXXXX
+
+XXX We added a table of potential growth in temperate zones in future temperate warmed oceans.XCXX
+
 L482, 536, 548: some experiments were not performed “due to time constraints”. I'm not sure I 
@@
 Thank you for this suggestion. 
-We have edited the text:
+We edited the text:
 Line: XXX
@@
 
+We edited the figure to clarify the fit lines:
+Line: XXX
+
 Table 1: The trees described in the legend should be included in the supplemental material.
@@
 We clarified the wording on line XXXX of the revised manuscripted.
-"Protein homologies between *Prochlorococcus* and *Synechocystis* were extracted from @bonisteelStrainSpecificDifferences2018."
+"Protein homologies for FtsH isoforms between *Prochlorococcus* and *Synechocystis* were extracted from @bonisteelStrainSpecificDifferences2018."
 
@@
 We have revised the axis labels to make the log scaling more noticeable.
-The narrowness of the red bar (spanning 230 to 280 µM) should also be more apparent with the new scaling.
+The narrowness of the red bar (spanning 230 to 280 µM) results from the log scaling of the y axis.
 
@@
 don’t think this enzyme is properly a DNA repair enzyme. 
+XXX Naaman to removeXXXXX
 
@@
 out in the introduction.
+
+We added the following to the Summary and Conclusion section:
+"In warming oceans *P.
+marinus* clades will differentially expand into new regions depending upon their different, interacting capacities to tolerate and exploit photoperiods, light levels, and [O~2~].
+Competition among clades will be driven not simply by light levels.
+Clade HLI (including MED4) is excluded from short photoperiod regimes, typical of temperate winter, or light attenuated depths.
+In contrast, clade LLIV (including MIT9313) might actually exploit higher light niches under OMZ conditions, where low O~2~ relieves the stresses of oxidation stress and PSII photoinhibition."
+Line:XXX
 
@@
 
-Thank you for highlighting this oversight. 
+Thank you for highlighting this issue. 
 We added the following in the materials and methods section of the revised manuscript:
-"Each tube containing 70 mL of Pro99 media was inoculated with 10 mL of growing maintenance culture approximately 16 to 22 hours
-before the start of each growth experiment. The tubes containing the cultures were placed in the Multicultivator water bath set at 22°C, 
-sparged with the experimental [O2], and kept in the dark for approximately 12 hours until the photoregime of a sinusoidal photoperiod 
-commenced the following morning such that peak PAR occurred at noon each day."
+"Each tube containing 70 mL of Pro99 media
+was inoculated around mid day of the 12 h maintenance photoperiod with 10 mL of growing maintenance preculture, to reach a starting OD680 of approximately 0.020.
+The tubes containing the cultures were then placed in the Multicultivator water bath set at 22°C, sparged with the experimental [O~2~], and kept at low light until late afternoon.
+Cultures were then in the dark for 12 to 16 hr until the photoregime of a sinusoidal photoperiod commenced the following morning, reaching peak PAR at noon each day.
+Cultures thus took approximately 24 h to move gradually from maintenance photoregime to the peak PAR of the experimental photoregime.
+Cultures were grown for  xx to yy days, until they reached stationary phase at OD680 of approximately 0.4 to 0.8 after approximately 5 generations of growth."
 Line: XXX
@@
 We added the following in the results and discussion section of the revised manuscript:
-"While we implemented measures to minimize shock to cultures from exposure to experimental growth conditions by inoculating them the day
- before the experiment began and employing a sinusoidal photoperiod with a gradual increase in PAR exposure, we acknowledge that cells typically
- need multiple generations to acclimate to new growth conditions (Moore et al. 2007)."
+"We implemented measures to minimize shock to cultures from exposure to experimental growth conditions by inoculating them the day before the experiment began, employing a sinusoidal photoperiod with a gradual increase in PAR exposure, and extracting exponential growth rates from logistic curves fit over approximately 5 generations of growth, to accommodate multiple generations to acclimate to the imposed growth conditions (Moore et al.
+2007)."
 Line: XXX
@@
 simply start with “Figure X shows…”. But, the organization of the paper is of course up to the authors.
+
+XXXX In response to reviewer 1 and reviewer 2 we have combined the growth rate figure with the GAM model for each strain to faciliate comparisons.
+We have edited the abstract, results and discussion to better convey the motivations and findings of the study.
+In particular lines  XXX to YYY and XXXXX
 
@@
 
-We have edited the text in the revised manuscript: "Clades LLII and LLIII, including cultured strain SS120, are grouped together as early branching phylogenetic lineage diversifying in the *P.
-marinus* radiation, with a preference for low light."
+We have edited the text in the revised manuscript: " Clades LLII and LLIII, including cultured strain SS120, are
+grouped together as early branching phylogenetic lineage in
+the *P. marinus* radiation, with a preference for low light."
 Line: XXX
@@
 Thank you for  bringing this to our attention.
-We have added the following text to the revised manuscript: "Follett et al 2022, however, model interactions of heterotrophic bacteria  that may influence latitudinal expansion of *P.
+We have added the following text to the revised manuscript: "Follett et al 2022, however, model interactions of heterotrophic bacteria  that may influence latitudinal expansions of *P.
 marinus*."
@@
 Thank you for noting that this needs further clarification. 
-We have edited the paragraph for clarity in the revised manuscript adding: "While the accuracy of strain specific protein annotation is noted due to highly conserved common proteins, the two step approach of peptide-to-spectrum matching using deep paired metagenomics identify proteins at the clade classifications."
+We have edited the paragraph for clarity in the revised manuscript adding: "While the accuracy of strain specific protein annotations are limited due to the high conservation of the target protein complexes, the two step approach of peptide-to-spectrum matching using deep paired metagenomics, does assign proteins at the level of clades."
 Lines: XXX
@@
 Thank you for your comment.
-We have edited the text in the revised manuscript: "Prochlorococcus remain challenging to culture at high densities, partially due to their dependence upon mutualistic heterotrophic bacteria to detoxify
+We have edited the text in the revised manuscript: "*Prochlorococcus* remain challenging to culture at high densities or under fluctuating environments, partially due to their dependence upon mutualistic heterotrophic bacteria to detoxify
 reactive oxygen species [48,49]." 
@@
 
-Thank you for your comment. We used proteomics as we have experience with cyanobacteria protein and have work flows in place.
+Thank you for your comment.
+Co-authors, Aurora MattisonXXX and Dr.
+Amanda Cockshutt, used the metaproteomics database as an extension of their earlier studies on the functional implications of differential protein allocations across different Prochlorococcus strains [Zorz, Bonisteel].
+Those studies indeed motivated the design of our growth matrix.
+Extending the study to include metagonomic analyses is valid but is beyond our scope.
 We have edited the text in the revised manuscript: "Our analyses utilized a proteomics dataset; however, alternate approaches, such as metagenomics or metatranscriptomics, could have been employed to analyze ecotype abundances using the TARA Oceans [@pesantOpenScienceResources2015] dataset."
@@
 
+XXX DOUGXXX 
 XXX Energy- blue have shorter WL so high energy, red longer WL so lower energy??? XXXX

### 2024-05-27 Code/Manuscript_O2.Rmd
edits

@@
 High-Light (HL) or Low-Light (LL). Only 5 out of 12 known
-*Prochlorococcus* genetic clades have cultured representatives to date;
+*P. marinus* genetic clades have cultured representatives to date;
 HLI, HLII, LLI, LLII/III and LIV
@@
 m depth. Clades LLII and LLIII, including cultured strain SS120, are
-grouped together as early branching phylogenetic lineage diversifying
-in the *P. marinus* radiation, with a preference for low light. Clade
+grouped together as early branching phylogenetic lineage in
+the *P. marinus* radiation, with a preference for low light. Clade
 LLIV, including cultured strain MIT9313, falls near the base of the
-*Prochlorococcus* radiation, and is characterized by preference for low
+*P. marinus* radiation, and has been characterized by preference for low
 light, typical of depths from 120 m to 200 m
 [@partenskyProchlorococcusMarinePhotosynthetic1999]. LLIV members are,
-as yet, the only cultured strains to have been found in Oxygen Minimum
+as yet, the only cultured *P. marinus* strains to have been found in Oxygen Minimum
 Zones (OMZ). Some, as yet, uncultured *P. marinus* strains in clades LLV
@@
 waters, with increases in *P. marinus* of approximately 50% in the more
-poleward regions of their distributions. @follettTrophicInteractionsHeterotrophic2022, however, model interactions of heterotrophic  bacteria  that may influence latitudinal expansion of *P. marinus*.
+poleward regions of their distributions.
+@follettTrophicInteractionsHeterotrophic2022, however, model interactions of heterotrophic  bacteria  that may influence latitudinal expansions of *P.
+marinus*.
 
@@
 When assessing the presence of a particular protein complex at a
-sampling location, the spectral counts were summed between proteins within the protein subunit to give the greatest number of data points. As this data
+sampling location, the spectral counts were summed from all protein subunits from the protein complex, to increase probability of detection. As this data
 was acquired by survey proteomics (data dependent acquisition) rather than through targeted peptide
@@
 [@saundersMETATRYPMetaproteomicLeast2020].
-While the accuracy of strain specific protein annotation is noted due to highly conserved common proteins, the two step approach of peptide-to-spectrum matching using deep paired metagenomics identify proteins at the clade classifications.
+While the accuracy of strain specific protein annotations are limited due to the high conservation of the target protein complexes, the two step approach of peptide-to-spectrum matching using deep paired metagenomics, does assign proteins at the level of clades.
 
@@
 
-*Prochlorococcus* remain challenging to culture at high densities, partially due to their dependence upon mutualistic heterotrophic bacteria to detoxify
+*Prochlorococcus* remain challenging to culture at high densities or under fluctuating environments, partially due to their dependence upon mutualistic heterotrophic bacteria to detoxify
 reactive oxygen species [@morrisFacilitationRobustGrowth2008;
@@
 
-Controlled growth experiments were performed using MCMIX-OD or MC1000-OD
+Controlled growth experiments were then performed using MCMIX-OD or MC1000-OD
 PSI Multicultivators (Fig \@ref(fig:LabeledMC); PSI, Drásov, Czech
@@
 common temperature of 22°C. Each tube containing 70 mL of Pro99 media
-was inoculated with 10 mL of growing maintenance culture approximately 16 to 22 hours before the start of each growth experiment.
-The tubes containing the cultures were placed in the Multicultivator water bath set at 22°C, sparged with the experimental [O~2~], and kept in the dark for approximately 12 hours until the photoregime of a sinusoidal photoperiod commenced the following morning such that peak PAR occurred at noon each day.
-In a factorial
-matrix design, each tube was then subject to an individual combination
+was inoculated around mid day of the 12 h maintenance photoperiod with 10 mL of growing maintenance preculture, to reach a starting OD680 of approximately 0.020.
+The tubes containing the cultures were then placed in the Multicultivator water bath set at 22°C, sparged with the experimental [O~2~], and kept at low light until late afternoon.
+Cultures were then in the dark for 12 to 16 hr until the photoregime of a sinusoidal photoperiod commenced the following morning, reaching peak PAR at noon each day.
+Cultures thus took approximately 24 h to move gradually from maintenance photoregime to the peak PAR of the experimental photoregime.
+Cultures were grown for  xx to yy days, until they reached stationary phase at OD680 of approximately 0.4 to 0.8 after approximately 5 generations of growth.
+
+In a factorial matrix design, each tube was subject to an individual combination
 of sinusoidal photoperiod (4, 8, 12, 16 h); reaching a peak PAR (30, 90,
@@
 Guided in part by the evidence of ocean distributions of proteins from
-*Prochlorococcus* we set up a matrix of photoperiods, PAR, spectral
-bands, and [O~2~] to approximate current, and potential future,
-latitudinal, depth and seasonal niches for *Prochlorococcus* strains.
-While we implemented measures to minimize shock to cultures from exposure to experimental growth conditions by inoculating them the day before the experiment began and employing a sinusoidal photoperiod with a gradual increase in PAR exposure, we acknowledge that cells typically need multiple generations to acclimate to new growth conditions [@mooreCulturingMarineCyanobacterium2007].
-As
-mentioned, growth under red light could prove mechanistically
-informative [@murphyPhotoinactivationPhotosystemII2017] to factors
-limiting *Prochlorococcus* growth, we therefore included the red
-spectral waveband even though it is not representative of
-*Prochlorococcus* niches. Although *Prochlorococcus* is currently
-limited to a narrow range of surface photoperiods, potential poleward
-latitudinal expansions, in combination with attenuation of light with
-depth, mean *Prochlorococcus* may potentially encounter a wide range of
+*Prochlorococcus* we set up a matrix of photoperiods, PAR, and [O~2~] to approximate current, and potential future,
+latitudinal, depth and seasonal niches for *Prochlorococcus* strains. As
+mentioned, growth under red light, although not representative of *Prochlorococcus* niches, is mechanistically
+informative [@murphyPhotoinactivationPhotosystemII2017] regarding photoinactivation of PSII.
+We implemented measures to minimize shock to cultures from exposure to experimental growth conditions by inoculating them the day before the experiment began, employing a sinusoidal photoperiod with a gradual increase in PAR exposure, and extracting growth rates from logistic curves fit over approximately 5 generations of growth, to accommodate multiple generations to acclimate to the imposed growth conditions [@mooreCulturingMarineCyanobacterium2007].
+Although the current subtropical distribution of *Prochlorococcus* spans a narrow range of photoperiods at the surface, light attenuation with depth shortens effective photoperiods as well as lowering peak PAR.
+Potential poleward
+latitudinal range expansions, in combination with attenuation of light with
+depth, mean *Prochlorococcus* clades may potentially encounter a wider range of
 photoperiods. Our growth rate determinations generally agree with those
@@
 to analyze the interactive growth responses of *Prochlorococcus* strains
-to varying [O~2~], spectral wavebands and photoperiods.
+to varying [O~2~], photoperiods and spectral wavebands.
 
@@
 PCC6803.
-Protein homologies between *Prochlorococcus* and *Synechocystis* were extracted from @bonisteelStrainSpecificDifferences2018.",
+Protein homologies for FtsH isoforms between *Prochlorococcus* and *Synechocystis* were extracted from @bonisteelStrainSpecificDifferences2018.",
               col.names =  c("Organism",
@@
 
-XXXX Added this section , if keeping then Mirielle will add the citations to zotero XXXX
-
-The potential expansion of  *P.
-marinus*  polewards may contribute to the primary food base of an aquatic ecosystem that has already undergone changes in temperate northern waters; commercial fish populations are shifting with new species immigrating  [@zellerCheungZellerPauly2011], endangered whales actively searching for food sources are becoming more prevalent [@meyer-gutbrodMarineSpeciesRange2018] and the white shark seasonal presence is increasing  either due to rising ocean temperatures or following marine prey [@bastienInconspicuousRecoveringNorthward2020].
-While the exact impact of the presence of *P.
-marinus*  on the species distribution of marine wildlife in temperate northern waters is unknown, there is little doubt that *Prochlorococcus* will play a significant role in shaping this distribution.
+In warming oceans *P.
+marinus* clades will differentially expand into new regions depending upon their different, interacting capacities to tolerate and exploit photoperiods, light levels, and [O~2~].
+Competition among clades will be driven not simply by light levels.
+Clade HLI (including MED4) is excluded from short photoperiod regimes, typical of temperate winter, or light attenuated depths.
+In contrast, clade LLIV (including MIT9313) might actually exploit higher light niches under OMZ conditions, where low O~2~ relieves the stresses of oxidation stress and PSII photoinhibition.
 

### 2024-05-27 Output/PLOSRound2/ResponsetoReviewers.txt
Doug edits done

@@
 
-José A. Fernández Robledo, Ph.D. 
+Jos? A. Fern?ndez Robledo, Ph.D. 
 Academic Editor 
@@
 
-Dear Dr. Fernández Robledo,
+Dear Dr. Fern?ndez Robledo,
 
@@
 
-•	separate file labeled 'Revised Manuscript with Track Changes'.
-•	An unmarked version of your revised paper without tracked changes. You should upload this as a separate file labeled 'Manuscript'.
+?	separate file labeled 'Revised Manuscript with Track Changes'.
+?	An unmarked version of your revised paper without tracked changes. You should upload this as a separate file labeled 'Manuscript'.
 
@@
 accepted for publication. Please remove this from your References and amend this to state in the body 
-of your manuscript: (ie “Bewick et al. [Unpublished]”) as detailed online in our guide for authors 
+of your manuscript: (ie ?Bewick et al. [Unpublished]?) as detailed online in our guide for authors 
 http://journals.plos.org/plosone/s/submission-guidelines#loc-reference-style
@@
 should be mentioned in the rebuttal letter that accompanies your revised manuscript. If you need to cite 
-a retracted article, indicate the article’s retracted status in the References list and also include a citation 
+a retracted article, indicate the article?s retracted status in the References list and also include a citation 
 and full reference for the retraction notice.
@@
 
-Line 55: LLII/III and LLIV are not the “oldest” clades, but the most basal or early branching.
+Line 55: LLII/III and LLIV are not the ?oldest? clades, but the most basal or early branching.
 
@@
 
-Line 369: The authors invoke “limitations in the annotation process” to explain the lack of evidence for 
+Line 369: The authors invoke ?limitations in the annotation process? to explain the lack of evidence for 
 MED4 ATP synthase. What does this mean? The MED4 genome surely contains ATP synthase genes.
@@
 
+We revised the text from lines 668 to XXX to incorporate these helpful observations.
+
 Figures 3 through 8: These figures are obviously the crux of the results in this paper, but as they are 
@@
 
-I'm also not sure I understand why the red light data is relevant -- perhaps by moving it to supplemental, 
-it would be easier to compile these data into compound figures?
+I'm also not sure I understand why the red light data is relevant -- perhaps by moving it to supplemental, it would be easier to compile these data into compound figures?
 
-XXX MIreille rephrase   We have addressed the jusification of red light to the reveiwer 2. XXX
+We briefly motivated the inclusion of the red light growth trials, as mechanistically informative, at line 706:
+" As mentioned, growth trials under red light, although not representative of *Prochlorococcus* niches, are mechanistically informative [@murphyPhotoinactivationPhotosystemII2017] regarding photoinactivation of PSII."
+
+Through the Discussion, notably under the discussion of the GAM models and responses to growth rate to increasing PUR, we return to the responses to red light to show that some 'high light' limitations on growth are interpretable as photoinhibition of PSII, which is more severe under blue, compared to red, light, notably at lines 1023-1032 (xXXX).
 
@@
 
-XXXX Predicting P. marinus is is beyond the scope of this study but we added a table....XXXXX
+Thank you for the comment.
+We added a table YY of potential strain growth in temperate seasonal and depth niches, in future temperate warmed oceans.
+The GAM model panels in figures XYZ show 'zones of exclusion' from light level, photoperiods, and oxygen regimes, as unshaded white areas where no growth is predicted.
+We indeed contemplating attempting global predicted distribution maps, but the interacting complexities of season, depth, changing extents of OMZ and extrapolation from culture growth, render it beyond the scope of this study.
 
-XXX We added a table of potential growth in temperate zones in future temperate warmed oceans.XCXX
+XXX
 
-L482, 536, 548: some experiments were not performed “due to time constraints”. I'm not sure I 
+L482, 536, 548: some experiments were not performed ?due to time constraints?. I'm not sure I 
 understand this, although I am interpreting it along the lines of "the person doing the experiments 
-graduated"… In any case, it seems like these particularly treatments were unlikely to grow, so it's not 
-important that they were omitted -- but maybe there is a better way to phrase this that doesn’t sound 
+graduated"? In any case, it seems like these particularly treatments were unlikely to grow, so it's not 
+important that they were omitted -- but maybe there is a better way to phrase this that doesn?t sound 
 so fishy?
@@
 
-Figure S4 — It is very hard to see the fit lines other than the pooled fit. Consider using different colors 
+Figure S4 ? It is very hard to see the fit lines other than the pooled fit. Consider using different colors 
 and solid lines since this is online.
@@
 We have revised the axis labels to make the log scaling more noticeable.
-The narrowness of the red bar (spanning 230 to 280 µM) results from the log scaling of the y axis.
+The narrowness of the red bar (spanning 230 to 280 ?M) results from the log scaling of the y axis.
 
@@
 emitted (AFAIK) by the bulbs used in the Multicultivator. Also, it is unlikely that the absence of these two 
-genes is sufficient to explain why these strains can’t grow at the ocean’s surface.
+genes is sufficient to explain why these strains can?t grow at the ocean?s surface.
 
@@
 
-Fig 12: Phosphoglycolate phosphatase is a major enzyme in the photorespiration pathway — what does 
+Fig 12: Phosphoglycolate phosphatase is a major enzyme in the photorespiration pathway ? what does 
 it have to do with DNA repair? There is evidence that 2-phosphoglycolate causes oxidative stress, but I 
-don’t think this enzyme is properly a DNA repair enzyme. 
+don?t think this enzyme is properly a DNA repair enzyme. 
 XXX Naaman to removeXXXXX
@@
 was inoculated around mid day of the 12 h maintenance photoperiod with 10 mL of growing maintenance preculture, to reach a starting OD680 of approximately 0.020.
-The tubes containing the cultures were then placed in the Multicultivator water bath set at 22°C, sparged with the experimental [O~2~], and kept at low light until late afternoon.
+The tubes containing the cultures were then placed in the Multicultivator water bath set at 22?C, sparged with the experimental [O~2~], and kept at low light until late afternoon.
 Cultures were then in the dark for 12 to 16 hr until the photoregime of a sinusoidal photoperiod commenced the following morning, reaching peak PAR at noon each day.
@@
 more clearly motivating the questions driving the analyses in each section would help; many paragraphs 
-simply start with “Figure X shows…”. But, the organization of the paper is of course up to the authors.
+simply start with ?Figure X shows??. But, the organization of the paper is of course up to the authors.
 
@@
 
-General note: the manuscript text at some points refers broadly to “growth”, and other places is more 
-specific about drawing conclusions about “growth rate”. I would suggest being clearer in some way that 
+General note: the manuscript text at some points refers broadly to ?growth?, and other places is more 
+specific about drawing conclusions about ?growth rate?. I would suggest being clearer in some way that 
 you are focused on growth rate and not growth yield.
@@
 
-56: “Affinity” for low light? Consider rephrasing
+56: ?Affinity? for low light? Consider rephrasing
 
@@
 
-209: It seems overly general to blame the culturing difficulties solely on having reduced genomes – in 
+209: It seems overly general to blame the culturing difficulties solely on having reduced genomes ? in 
 this context, it is the lack of just one gene (catalase) that matters, and reduced genomes reflect an 
@@
 
-We have edited the text: "The growth rate for Prochlorococcus marinus MED4, clade HLI, under 250 µM O2, increased with higher imposed PAR and longer photoperiods (Fig 3A), across all spectral wavebands."
+We have edited the text: "The growth rate for Prochlorococcus marinus MED4, clade HLI, under 250 ?M O2, increased with higher imposed PAR and longer photoperiods (Fig 3A), across all spectral wavebands."
 Line XXX:

### 2024-05-27 Code/Manuscript_O2.Rmd
Doug edits done

@@
 *Prochlorococcus marinus*, the smallest picocyanobacterium, comprises
-multiple clades with distinct niches across tropical and sub-tropical
+multiple clades with distinct niches, currently across tropical and sub-tropical
 oligotrophic ocean regions, including Oxygen Minimum Zones. Ocean
 warming may open permissive temperatures in new, poleward photic
-regimes, along with expanded Oxygen Minimum Zones. We used ocean protein portal
-data to help guide testing of
-*Prochlorococcus marinus* growth across a matrix of peak irradiances,
+regimes, along with expanded Oxygen Minimum Zones. We used ocean metaproteomic
+data to guide testing of *Prochlorococcus marinus* growth across a matrix of peak irradiances,
 photoperiods, spectral bands and dissolved oxygen. MED4 from Clade HLI
 requires greater than 4 h photoperiod, grows at 25 µmol O~2~ L^-1^ and
-above, and exploits high cumulative diel photon doses, yet shows
-accelerated growth when the cost of photoinactivation is lowered under
-red, vs. blue, actinic light. MED4 relies upon an alternative oxidase to
+above, and exploits high cumulative diel photon doses. MED4, however, relies upon an alternative oxidase to
 balance electron transport, which may exclude it from growth under our
@@
 under 2.5 µmol O~2~ L^-1^. Intermediate oxygen suppresses the cost of
-PSII photoinactivation, and enzymatic production of H~2~O~2~ in SS120,
-which has limited genomic capacity for PSII and DNA repair. MIT9313 from
+PSII photoinactivation, and possibly the enzymatic production of H~2~O~2~ in SS120,
+which has limitations on genomic capacity for PSII and DNA repair. MIT9313 from
 Clade LLIV is restricted to low blue irradiance under 250 µmol O~2~
@@
 PSII and production of reactive oxygen species.
+In warming oceans range expansions and competition among clades will be governed not simply by light levels.
+Short photoperiods governed by latitude, temperate winter, and depth attenuation of light, will exclude Clade HLI (including MED4).
+In contrast, clade LLII/III (including SS120), and especially clade LLIV (including MIT9313), may actually exploit higher light niches under expanding OMZ conditions, where low O~2~ relieves the stresses of oxidation stress and PSII photoinhibition.
 
@@
 complexes, for clades HLI, LLI, LLII/III and LLIV (Fig \@ref(fig:CladeProchloroPhotosynthDepthO2)) as a function of depth (a
-proxy for light intensity) and measured [O~2~]. Photosynthetic complexes
+proxy for light intensity) and measured [O~2~] at the sampling locations. Photosynthetic complexes
 from HLI (including strain MED4) were detected throughout the water
-column, predominantly at high [O~2~]. Though present in the genome of MED4, the absence of proteins annotated as ATP Synthase complex for Clade HLI, compared to annotated
-detections of ATP Synthase across the other three clades suggests
+column, but, with one exception, only under high [O~2~]. Though present in the genome of MED4, the absence of proteins annotated as ATP Synthase complex for Clade HLI, compared to annotated
+detections of ATP Synthase across the other three clades, suggests
 limitations in the annotation process for highly conserved protein
-sequences. Complexes from Clades LLI (including strain NATL2A) were also
-present across the depth/light axes, with more representation at lower
-[O~2~], and fewer near surface detections. Complexes from clade LLII/III
+sequences. Complexes from Clade LLI (including strain NATL2A) were also
+present across the depth/light axes, although with more protein detections at lower
+[O~2~], and fewer near surface detections of proteins from Clade LLI.
+Notwithstanding limitations on assignments of proteins to clades, detections of the abundant carbon fixation complex RUBISCO derived from HLI and LLI were notably absent from samples taken at lower [O~2~], suggesting limited capacity for carbon fixation by HLI and LLI under low [O~2~] habitats.
+Complexes from clade LLII/III
 (including strain SS120) were also detected across the depth/light and [O~2~] ranges,
 with more detections at deeper, darker depths. Clade LLIV (including strain MIT9313)
-photosynthetic complexes were also detected throughout the
-depth/light and [O~2~], ranges, with the most frequent detections at
-depth and at low [O~2~], compared to other strains.
-Our analyses utilized a proteomics dataset; however, alternate approaches, such as metagenomics or metatranscriptomics, could have been employed to analyze ecotype abundances using the TARA Oceans [@pesantOpenScienceResources2015] dataset.
+photosynthetic complexes were also detected throughout the depth/light and [O~2~], ranges, notably with the most frequent detections of proteins at both depth and at low [O~2~], compared to other strains.
+Our analyses utilized a proteomics dataset; however, alternate approaches, such as metagenomics or metatranscriptomics, could have been employed to analyze ecotype abundances using the TARA Oceans [@pesantOpenScienceResources2015] or other datasets.
 
@@
 Guided in part by the evidence of ocean distributions of proteins from
-*Prochlorococcus* we set up a matrix of photoperiods, PAR, and [O~2~] to approximate current, and potential future,
-latitudinal, depth and seasonal niches for *Prochlorococcus* strains. As
-mentioned, growth under red light, although not representative of *Prochlorococcus* niches, is mechanistically
-informative [@murphyPhotoinactivationPhotosystemII2017] regarding photoinactivation of PSII.
+*Prochlorococcus* we set up a matrix of photoperiods, PAR, and [O~2~] to approximate current, and potential future, latitudinal, depth and seasonal niches for *Prochlorococcus* strains. As
+mentioned, growth trials under red light, although not representative of *Prochlorococcus* niches, are mechanistically informative [@murphyPhotoinactivationPhotosystemII2017] regarding photoinactivation of PSII.
 We implemented measures to minimize shock to cultures from exposure to experimental growth conditions by inoculating them the day before the experiment began, employing a sinusoidal photoperiod with a gradual increase in PAR exposure, and extracting growth rates from logistic curves fit over approximately 5 generations of growth, to accommodate multiple generations to acclimate to the imposed growth conditions [@mooreCulturingMarineCyanobacterium2007].
@@
 Potential poleward
-latitudinal range expansions, in combination with attenuation of light with
-depth, mean *Prochlorococcus* clades may potentially encounter a wider range of
-photoperiods. Our growth rate determinations generally agree with those
-from Moore *et al*. [@mooreComparativePhysiologySynechococcus1995], for
-white LED and 250 µM O~2~, but our study is, to our knowledge, the first
-to analyze the interactive growth responses of *Prochlorococcus* strains
+latitudinal range expansions, in combination with attenuation of light with depth, mean *Prochlorococcus* clades may potentially encounter a wider range of photoperiods.
+Our growth rate determinations generally agree with those from Moore *et al*.
+[@mooreComparativePhysiologySynechococcus1995], for white LED and 250 µM O~2~, but our study is, to our knowledge, the first to analyze the interactive growth responses of *Prochlorococcus* strains
 to varying [O~2~], photoperiods and spectral wavebands.
@@
 The growth rate for *Prochlorococcus marinus* MED4, clade HLI, under 250 µM O~2~, increased with higher imposed PAR and longer photoperiods (Fig \@ref(fig:MED4PARGAM)A), across all spectral wavebands.
-No growth was
-observed under any imposed conditions under a 4 h photoperiod. The
-maximum growth rate (µ~max~) was
-`r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
-d^-1^ achieved under 180 µE blue light and 16 h photoperiod.
-
-Similar to growth trends under 250 µM O~2~, MED4 maintained at 25 µM
-O~2~ showed fastest growth when the photoperiod was 16 h for each
-spectral waveband, across PAR levels (Fig \@ref(fig:MED4PARGAM)). The
-µ~max~ was
-`r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "25", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
-d^-1^ (Table \@ref(tab:MaxGrowthTable)) achieved under 180 µmol photons
-m^-2^ s^-1^ blue light and 16 h photoperiod. The 4 h photoperiod
-experiments under white LED light were not performed as no growth was
-achieved when grown under an 8 h photoperiod of white LED light.
-
-MED4 did not grow when sparged to the lowest [O~2~] of 2.5 µM (Fig \@ref(fig:MED4PARGAM)). 2.5 µM O~2~ growth experiments were not conducted
-for 4 and 16 h photoperiods, as no reproducible growth occurred when
-MED4 was exposed to 8 and 12 h photoperiods.
+No growth was observed under any imposed conditions under a 4 h photoperiod.
+The maximum growth rate (µ~max~) was `r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ achieved under 180 µE blue light and 16 h photoperiod.
+
+Similar to growth trends under 250 µM O~2~, MED4 maintained at 25 µM O~2~ showed fastest growth when the photoperiod was 16 h for each spectral waveband, across PAR levels (Fig \@ref(fig:MED4PARGAM)).
+The
+µ~max~ was `r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "25", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ (Table \@ref(tab:MaxGrowthTable)) achieved under 180 µmol photons m^-2^ s^-1^ blue light and 16 h photoperiod.
+The 4 h photoperiod experiments under white LED light were not performed as no growth was achieved when grown under an 8 h photoperiod of white LED light.
+
+MED4 did not grow when sparged to the lowest [O~2~] of 2.5 µM (Fig \@ref(fig:MED4PARGAM)).
+2.5 µM O~2~ growth experiments were not conducted for 4 and 16 h photoperiods, as no reproducible growth occurred when MED4 was exposed to 8 and 12 h photoperiods under [O~2~] of 2.5 µM .
 
@@
 of SS120 to red or blue peak PAR and photoperiod, across the
-2 imposed oxygen concentrations. Under 250 µM O~2~, Fig \@ref(fig:SS120PARGAM)B showed highest growth rates below blue light PAR of
-50 µmol photons m^-2^ s^-1^ and photoperiods between 12 and 16 h,
+2 imposed oxygen concentrations. Under 250 µM O~2~, Fig \@ref(fig:SS120PARGAM)B showed highest growth rates below blue light PAR of 50 µmol photons m^-2^ s^-1^ and photoperiods between 12 and 16 h,
 indicated by the contour line labeled 0.35 d^-1^ (representing the
@@
 variable growth success of SS120 under 250 µM O~2~. Growth rate patterns
-under red light were similar, although somewhat faster. In contrast,
+under red light and 250 µM O~2~were similar, although somewhat faster. In contrast,
 under 25 µM O~2~ and a photoperiod of 8 h SS120 exploited all blue peak
@@
 the 90^th^ percentile fastest growth rates under 250 µM O~2~ (Fig \@ref(fig:SS120PARGAM)B).
-Under red light and 25 µM O~2~ (Fig \@ref(fig:SS120PARGAM)B) SS120 grew across most conditions of peak PAR and
+Under red light and 25 µM O~2~ (Fig \@ref(fig:SS120PARGAM)B) SS120 was able to grow across most conditions of peak PAR and
 photoperiod, achieving fastest growth under long photoperiods and peak
@@
 the blue peak PAR levels remain below 50 µmol photons m^-2^ s^-1^. In
-contrast, under red light and 250 µM O~2~ MIT9313 grows faster while
-exploiting higher peak PAR and longer photoperiods. MIT9313 can exploit all blue PAR levels
-and most photoperiods under 25 µM O~2~ with 90^th^ percentile of fastest growth rate
-between 30 to 100 µmol photons m^-2^ s^-1^ PAR. MIT9313 maintains growth even under
-2.5 µM O~2~, under photoperiods between 8 and 12 h and peak blue PAR
-between 50 to 100 µmol photons m^-2^ s^-1^ PAR. Thus the designation of
+contrast, under red light and 250 µM O~2~ MIT9313 is able to
+exploit higher peak PAR, across the range of photoperiods.
+MIT9313 can exploit all blue or red PAR levels and most photoperiods under 25 µM O~2~ with 90^th^ percentile of fastest growth rate between 30 to 100 µmol photons m^-2^ s^-1^ blue PAR.
+MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 8 and 12 h and peak blue PAR between 50 to 100 µmol photons m^-2^ s^-1^ PAR.
+Thus the designation of
 MIT9313 as a LL clade is dependent upon [O~2~] and light spectra (Fig \@ref(fig:MIT9313PARGAM)B).

### 2024-05-27 Output/PLOSRound2/ResponsetoReviewers.txt
replaced growth with growth rate where appropriate

@@
 
+Thank you for comment. We have added text to discuss the main conclusions of this study.
+
 Line 55: LLII/III and LLIV are not the ?oldest? clades, but the most basal or early branching.
 
-We have edited the text in the revised manuscript: "Clades LLII and LLIII, including cultured strain SS120, are grouped together as early branching phylogenetic lineage diversifying in the P.
-marinus radiation, with a preference for low light."
+We have edited the text in the revised manuscript: "Clades LLII and LLIII, including cultured strain SS120, are
+grouped together as early branching phylogenetic lineage in
+the P. marinus radiation, with a preference for low light."
 Line: XXX
@@
 
- XXX Doug address RUBISCO XXX
-
 We revised the text from lines 668 to XXX to incorporate these helpful observations.
+The following was added: " Notwithstanding limitations on assignments of proteins to clades, detections of the abundant carbon fixation complex RUBISCO derived from HLI and LLI were notably absent from samples taken at lower [O~2~], suggesting limited capacity for carbon fixation by HLI and LLI under low [O~2~] habitats."
 
@@
 The GAM model panels in figures XYZ show 'zones of exclusion' from light level, photoperiods, and oxygen regimes, as unshaded white areas where no growth is predicted.
-We indeed contemplating attempting global predicted distribution maps, but the interacting complexities of season, depth, changing extents of OMZ and extrapolation from culture growth, render it beyond the scope of this study.
+We indeed contemplated attempting global predicted distribution maps, but the interacting complexities of season, depth, changing extents of OMZ and extrapolation from culture growth, render it beyond the scope of this study.
 
@@
 Thank you for your comment.
-Co-authors, Aurora MattisonXXX and Dr.
+Co-authors, Aurora Mattison and Dr.
 Amanda Cockshutt, used the metaproteomics database as an extension of their earlier studies on the functional implications of differential protein allocations across different Prochlorococcus strains [Zorz, Bonisteel].

### 2024-05-27 Code/Manuscript_O2.Rmd
replaced growth with growth rate where appropriate

@@
 PSII and production of reactive oxygen species.
-In warming oceans range expansions and competition among clades will be governed not simply by light levels.
+In warming oceans, range expansions and competition among clades will be governed not simply by light levels.
 Short photoperiods governed by latitude, temperate winter, and depth attenuation of light, will exclude Clade HLI (including MED4).
@@
 
-*Prochlorococcus*, a genus of Cyanobacteria, is the smallest known
+*Prochlorococcus marinus*, a genus of Cyanobacteria, is the smallest known
 photosynthetic prokaryote, with cell diameters ranging from 0.5 to 0.7
@@
 
-## *Prochlorococcus* and changing niches {.unnumbered}
+## *Prochlorococcus marinus* and changing niches {.unnumbered}
 
@@
 @vaulotGrowthProchlorococcusPhotosynthetic1995 showed that
-*Prochlorococcus* replication of DNA occurs in the afternoon, while cell
+*P. marinus* replication of DNA occurs in the afternoon, while cell
 division occurs at night. To our knowledge, no study has as yet
-addressed *P. marinus* growth responses in relation to a range of
+addressed *P. marinus* growth rate responses in relation to a range of
 photoperiods.
@@
 correlates to depth attenuated peak light at the site of sampling. In parallel we
-analyzed the growth and physiological responses of representative
+analyzed the growth rate and physiological responses of representative
 strains from three clades of *P. marinus* under a matrix of [O~2~],
-light levels, spectral waveband ranges, and photoperiods, to approximate
+light levels, photoperiods and spectral waveband ranges, to approximate
 eco-physiological conditions representative of current and hypothetical
@@
 different ecotypes, expressing growth rates in terms of cumulative diel
-PUR might simplify different photoperiods, spectral bands, and PAR
-levels into a common parameter, making growth rate comparisons
+PUR might simplify different photoperiods, PAR levels, and spectral bands into a common parameter, making growth rate comparisons
 across strains and different oxygen levels more accessible. We aimed to
 detect whether growth rates are driven simply by cumulative diel
-PUR, or whether specific photoperiods, spectral bands or PAR levels have
+PUR, or whether specific photoperiods, PAR levels or spectral bands have
 independent, albeit interacting, effects on growth. We therefore
@@
 turnover, oxygen-dependent enzymes, and DNA repair enzymes, can explain
-the differential growth responses of strains under the matrix of light
+the differential growth rate responses of strains under the matrix of light
 and [O~2~] conditions of this study.
@@
 worldwide [@saitoDevelopmentOceanProtein2021]. We screened a subset of
-the OPP for proteins annotated as from *Prochlorococcus* strains, to
+the OPP for proteins annotated as from *P. marinus* strains, to
 identify differential strategies employed by strains living at varying
@@
 This dataset included biomass in the 0.2 to 3.0 micron size fractionated filter size as described in Saito *et al*.
-[@saitoMultipleNutrientStresses2014] where *Prochlorococcus* is found.
+[@saitoMultipleNutrientStresses2014] where *P.
+marinus* is found.
 Datasets contained: i) Protein sequences and sample
@@
 [@R-tidyverse] running under R v4.1.3 and RStudio v2023.06.0 [@RStudio].
-The resulting merged dataset was filtered for those *Prochlorococcus*
+The resulting merged dataset was filtered for those *P. marinus*
 protein, detected from 0 to 300 m below the surface, annotated as a
-subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb);
+subunit of *P. marinus* chlorophyll binding proteins (Pcb);
 Photosystem II (PSII); Cytochrome b~6~f (Cytb~6~f); Photosystem I (PSI);
@@
 (<https://www.megasoftware.net/>). Sequences for proteins for each of
-the thirteen *Prochlorococcus* strains identified in the dataset were
+the thirteen *P. marinus* strains identified in the dataset were
 aligned with MUSCLE using UPGMA cluster method and a lambda of 24 with a
@@
 trees were assembled using 1000 bootstrap replications with a 95% site
-coverage cut off. *Prochlorococcus* FtsH isoform identities, and
+coverage cut off. *Prochlorococcus marinus* FtsH isoform identities, and
 functions, were inferred by sequence comparisons to the characterized
@@
 
-## *Prochlorococcus* culturing and experimental design {.unnumbered}
-
-*Prochlorococcus* remain challenging to culture at high densities or under fluctuating environments, partially due to their dependence upon mutualistic heterotrophic bacteria to detoxify
+## *Prochlorococcus marinus* culturing and experimental design {.unnumbered}
+
+*Prochlorococcus marinus* remain challenging to culture at high densities or under fluctuating environments, partially due to their dependence upon mutualistic heterotrophic bacteria to detoxify
 reactive oxygen species [@morrisFacilitationRobustGrowth2008;
@@
 
-Controlled growth experiments were then performed using MCMIX-OD or MC1000-OD
+Controlled growth rate experiments were then performed using MCMIX-OD or MC1000-OD
 PSI Multicultivators (Fig \@ref(fig:LabeledMC); PSI, Drásov, Czech
@@
 absence of growth of some strains under some levels of photoperiod, PAR,
-or [O~2~] meant we completed 268 growth factor treatment combinations with 1 to 3 replicates.
+or [O~2~] meant we completed 268 growth rate factor treatment combinations with 1 to 3 replicates.
 
@@
 Fig \@ref(fig:deltaODLogGrowthPlot) is an example of chlorophyll
-specific growth estimates fitted from the high resolution ΔOD
+specific growth rate estimates fitted from the high resolution ΔOD
 measurements for each tube in a Multicultivator. The residuals of the
-logistic growth curve fit are shown. The imposed PAR (µmol photons m^-2^ s^-1^) are plotted for each tube and illustrates the applied photoperiod (h) regimes.
+logistic growth rate fit are shown. The imposed PAR (µmol photons m^-2^ s^-1^) are plotted for each tube and illustrates the applied photoperiod (h) regimes.
 
@@
 growth rate were included in the GAM. Our priority was the effects of
-ecologically relevant blue light on growth trends. We also included GAM
-analyses of growth responses to red light, which is not
+ecologically relevant blue light on growth rate trends. We also included GAM
+analyses of growth rate responses to red light, which is not
 ecophysiologically relevant, but which might prove mechanistically
@@
 [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter
-model fit to 660 nm (red light) and 450 nm (blue light) growth data for
+model fit to 660 nm (red light) and 450 nm (blue light) growth rate data for
 each combination of strain and [O~2~]. We also performed one-way ANOVA
@@
 model fit to each photoperiod (4 h, 8 h, 12 h, 16 h) and pooled
-photoperiod growth data for each combination of strain and [O~2~].
-Photoperiod growth data that showed complete growth inhibition for each
+photoperiod growth rate data for each combination of strain and [O~2~].
+Photoperiod growth rate data that showed complete growth inhibition for each
 combination of strain, [O~2~] and imposed spectral waveband were omitted from the pooled photoperiod model. Statistical differences were
@@
 
-## *Prochlorococcus* comparative genomics {.unnumbered}
+## *Prochlorococcus marinus* comparative genomics {.unnumbered}
 
@@
 the dataset with a list of enzyme Michaelis constant (K~m~) values from
-other organisms, as K~m~ values from *Prochlorococcus* were only
+other organisms, as K~m~ values from *P. marinus* were only
 available in the case of Ribulose bisphosphate carboxylase. Gene counts
@@
 
-## Detection of *Prochlorococcus* proteins across O~2~ and light niches in the ocean {.unnumbered}
+## Detection of *Prochlorococcus marinus* proteins across O~2~ and light niches in the ocean {.unnumbered}
 
@@
                        "Protein detections (circles) are plotted vs. O~2~ (µM) (X-axis) and depth (m) (Y-axis) at sample origin.",
-                       "Rows separate data annotated as from *Prochlorococcus* clades: HLI (including *P.
+                       "Rows separate data annotated as from *Prochlorococcus marinus* clades: HLI (including *P.
 marinus* MED4, solid black circles), LLI (including *P.
@@
                        "Columns show detections of proteins annotated as  Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
-                       "For comparison culture growth experimental conditions are indicated by horizontal grey lines for depths approximating peak Photosynthetically Active Radiation (PAR; µmol photons m^-2^ s^-1^); and vertical grey lines for imposed [O~2~] (µM).",
+                       "For comparison, culture growth rate experimental conditions are indicated by horizontal grey lines for depths approximating peak Photosynthetically Active Radiation (PAR; µmol photons m^-2^ s^-1^); and vertical grey lines for imposed [O~2~] (µM).",
                        "Data obtained from the Biological and Chemical Oceanography Data Management Office repository [@saitoPeptidesTheirSpectral2018].",
@@
 
-## *Prochlorococcus marinus* growth responses to photoperiod, PAR, spectral band, and [O~2~] {.unnumbered}
+## *Prochlorococcus marinus* growth rate responses to photoperiod, PAR, spectral band, and [O~2~] {.unnumbered}
 
 Guided in part by the evidence of ocean distributions of proteins from
-*Prochlorococcus* we set up a matrix of photoperiods, PAR, and [O~2~] to approximate current, and potential future, latitudinal, depth and seasonal niches for *Prochlorococcus* strains. As
-mentioned, growth trials under red light, although not representative of *Prochlorococcus* niches, are mechanistically informative [@murphyPhotoinactivationPhotosystemII2017] regarding photoinactivation of PSII.
+*P. marinus* we set up a matrix of photoperiods, PAR, and [O~2~] to approximate current, and potential future, latitudinal, depth and seasonal niches for *P. marinus* strains. As
+mentioned, growth rate trials under red light, although not representative of *P.
+marinus* niches, are mechanistically informative [@murphyPhotoinactivationPhotosystemII2017] regarding photoinactivation of PSII.
 We implemented measures to minimize shock to cultures from exposure to experimental growth conditions by inoculating them the day before the experiment began, employing a sinusoidal photoperiod with a gradual increase in PAR exposure, and extracting growth rates from logistic curves fit over approximately 5 generations of growth, to accommodate multiple generations to acclimate to the imposed growth conditions [@mooreCulturingMarineCyanobacterium2007].
-Although the current subtropical distribution of *Prochlorococcus* spans a narrow range of photoperiods at the surface, light attenuation with depth shortens effective photoperiods as well as lowering peak PAR.
+Although the current subtropical distribution of *P.
+marinus* spans a narrow range of photoperiods at the surface, light attenuation with depth shortens effective photoperiods as well as lowering peak PAR.
 Potential poleward
-latitudinal range expansions, in combination with attenuation of light with depth, mean *Prochlorococcus* clades may potentially encounter a wider range of photoperiods.
+latitudinal range expansions, in combination with attenuation of light with depth, mean *P.
+marinus* clades may potentially encounter a wider range of photoperiods.
 Our growth rate determinations generally agree with those from Moore *et al*.
-[@mooreComparativePhysiologySynechococcus1995], for white LED and 250 µM O~2~, but our study is, to our knowledge, the first to analyze the interactive growth responses of *Prochlorococcus* strains
+[@mooreComparativePhysiologySynechococcus1995], for white LED and 250 µM O~2~, but our study is, to our knowledge, the first to analyze the interactive growth rate responses of *P.
+marinus* strains
 to varying [O~2~], photoperiods and spectral wavebands.
 
-The growth rate for *Prochlorococcus marinus* MED4, clade HLI, under 250 µM O~2~, increased with higher imposed PAR and longer photoperiods (Fig \@ref(fig:MED4PARGAM)A), across all spectral wavebands.
+The growth rate for *P.
+marinus* MED4, clade HLI, under 250 µM O~2~, increased with higher imposed PAR and longer photoperiods (Fig \@ref(fig:MED4PARGAM)A), across all spectral wavebands.
 No growth was observed under any imposed conditions under a 4 h photoperiod.
@@
 
-Similar to growth trends under 250 µM O~2~, MED4 maintained at 25 µM O~2~ showed fastest growth when the photoperiod was 16 h for each spectral waveband, across PAR levels (Fig \@ref(fig:MED4PARGAM)).
+Similar to growth rate trends under 250 µM O~2~, MED4 maintained at 25 µM O~2~ showed fastest growth rate when the photoperiod was 16 h for each spectral waveband, across PAR levels (Fig \@ref(fig:MED4PARGAM)).
 The
@@
 MED4 did not grow when sparged to the lowest [O~2~] of 2.5 µM (Fig \@ref(fig:MED4PARGAM)).
-2.5 µM O~2~ growth experiments were not conducted for 4 and 16 h photoperiods, as no reproducible growth occurred when MED4 was exposed to 8 and 12 h photoperiods under [O~2~] of 2.5 µM .
+2.5 µM O~2~ growth rate experiments were not conducted for 4 and 16 h photoperiods, as no reproducible growth occurred when MED4 was exposed to 8 and 12 h photoperiods under [O~2~] of 2.5 µM .
 
@@
 
-The GAM model in Fig \@ref(fig:MED4PARGAM)B summarizes MED4 growth
+The GAM model in Fig \@ref(fig:MED4PARGAM)B summarizes MED4 growth rate
 responses to red or blue peak PAR and photoperiod across 2
@@
 line representing the 90^th^ percentile of maximum achieved growth rate
-(Fig \@ref(fig:MED4PARGAM)B). Growth decreased with decreasing
-photoperiod and decreasing peak PAR. Under red light growth was
-generally slower but the pattern of growth responses to photoperiod and
+(Fig \@ref(fig:MED4PARGAM)B). Growth rates decreased with decreasing
+photoperiod and decreasing peak PAR. Under red light, growth rates were
+generally slower but the pattern of growth rate responses to photoperiod and
 PAR was similar (Fig \@ref(fig:MED4PARGAM)B). Note the exclusion of MED4
-from growth under 4 h photoperiod under both red and blue light (Fig \@ref(fig:MED4PARGAM)B). Under 25 µM O~2~ MED4 showed similar growth
+from growth under 4 h photoperiod under both red and blue light (Fig \@ref(fig:MED4PARGAM)B). Under 25 µM O~2~ MED4 showed similar growth rate
 responses, but was excluded from both 4 and 8 h photoperiods. MED4 did
 not grow under 2.5 µM O~2~, so no GAM model was run. Considering the
-range of PAR levels, and spectral bands that MED4 can utilize, MED4 can
+range of PAR levels, and spectral wavebands that MED4 can utilize, MED4 can
 inhabit not just shallow depths, where light levels are high, but also
@@
 
-*Prochlorococcus marinus* SS120 clade LLII/III, growth under 250 µM O~2~
-increased with longer photoperiods, under 30 µmol photons m^-2^ s^-1^
-peak PAR and across all spectral wavebands (Fig \@ref(fig:SS120PARGAM)).
+The growth rates for *Prochlorococcus marinus* SS120 clade LLII/III, under 250 µM O~2~, 30 µmol photons m^-2^ s^-1^ peak PAR and across all spectral wavebands,
+increased with longer photoperiods (Fig \@ref(fig:SS120PARGAM)).
 No growth was observed under any blue light photoperiods when exposed to
@@
 
-Under 25 µM O~2~ and PAR of 30 µmol photons m^-2^ s^-1^ growth trends
+Under 25 µM O~2~ and PAR of 30 µmol photons m^-2^ s^-1^ growth rate trends
 were similar to 250 µM O~2~. SS120 showed no growth under a 4 h
 photoperiod for red spectral waveband, however under blue light, SS120
-was able to grow (Fig \@ref(fig:SS120PARGAM)). In contrast to the growth
+was able to grow (Fig \@ref(fig:SS120PARGAM)). In contrast to the growth rate
 trends of the 250 µM O~2~ and PAR of 90 µmol photons m^-2^ s^-1^
@@
 SS120 did not reproducibly grow when sparged to the lowest O~2~ of 2.5
-µM (Fig \@ref(fig:SS120PARGAM)). 2.5 µM O~2~ growth experiments were not
+µM (Fig \@ref(fig:SS120PARGAM)). 2.5 µM O~2~ growth rate experiments were not
 conducted for 4 and 16 h photoperiods under peak PAR of 180 µmol photons
@@
 
-The GAM model in Fig \@ref(fig:SS120PARGAM)B summarizes growth responses
+The GAM model in Fig \@ref(fig:SS120PARGAM)B summarizes growth rate responses
 of SS120 to red or blue peak PAR and photoperiod, across the
@@
 Under red light and 25 µM O~2~ (Fig \@ref(fig:SS120PARGAM)B) SS120 was able to grow across most conditions of peak PAR and
-photoperiod, achieving fastest growth under long photoperiods and peak
+photoperiod, achieving fastest growth rate under long photoperiods and peak
 PAR between 30 \~100 µmol photons m^-2^ s^-1^. Thus, the designation of
@@
 
-*Prochlorococcus marinus* MIT9313, clade LLIV, growth under 250 µM O~2~
+*Prochlorococcus marinus* MIT9313, clade LLIV, growth rates under 250 µM O~2~
 increased with longer photoperiods, under low 30 µmol photons m^-2^
@@
 white LED light photoperiod. In marked contrast to the 250 µM O~2~
-growth experiments, MIT9313 grew when exposed to peak PAR of 180 µmol
+growth rate experiments, MIT9313 grew when exposed to peak PAR of 180 µmol
 photons m^-2^ s^-1^ and blue light under all photoperiods except 16 h;
@@
 
-The GAM model in Fig \@ref(fig:MIT9313PARGAM)B summarizes MIT9313 growth
+The GAM model in Fig \@ref(fig:MIT9313PARGAM)B summarizes MIT9313 growth rate
 responses to red or blue peak PAR and photoperiod. Under
@@
 
-## PUR and growth responses {.unnumbered}
+## PUR and growth rate responses {.unnumbered}
 
@@
 photoperiod (h) (Equation \@ref(eq:SumPURDay)). We plotted growth rates vs. cumulative diel PUR to
-determine whether growth is a simple response to diel PUR, across
-imposed spectral wavebands, and photoperiods, or whether spectral
-wavebands or photoperiods have specific or interactive influences on
+determine whether growth rate is a simple response to diel PUR, across
+imposed photoperiods and spectral wavebands, or whether photoperiods or spectral
+wavebands have specific or interactive influences on
 growth, beyond cumulative diel PUR.
@@
 photons m^-2^ d^-1^. This spectral bias in the range of PUR leads us to
-caution in comparing model fits of growth in response to cumulative diel
+caution in comparing model fits of growth rate in response to cumulative diel
 PUR under red vs. blue wavebands. Furthermore, we found some distinct
@@
 photoperiods greater than 4 h, MED4 growth under blue light was
-described by a saturating response of growth
+described by a saturating response of growth rate
 [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] to increasing
@@
 
-Under both 25 and 250 µM O~2~ experiments, SS120 growth plateaued by
+Under both 25 and 250 µM O~2~ experiments, SS120 growth rate plateaued by
 about 5.0 x 10^5^ µmol photons m^-2^ d^-1^ diel PUR, with some scatter
@@
 The LLIV clade representative, *P. marinus* MIT9313, under 250 µM O~2~
-showed growth rising to a plateau by about 5 x 10^5^ µmol photons m^-2^
+showed growth rate rising to a plateau by about 5 x 10^5^ µmol photons m^-2^
 d^-1^ of cumulative diel PUR. Above about 1.0 x 10^6^ µmol photons m^-2^
@@
 exploitation of higher cumulative diel PUR, with full growth inhibition
-only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Fig \@ref(fig:PhotoperiodPurFitsPlots)H). MIT9313 growth under 2.5 µM O~2~
-showed a wider, lower, flatter response to cumulative diel PUR, with
+only above about 3.5 x 10^6^ µmol photons m^-2^ d^-1^ (Fig \@ref(fig:PhotoperiodPurFitsPlots)H).  Under 2.5 µM O~2~, MIT9313
+showed a wider, lower, flatter growth rate response to cumulative diel PUR, with
 full growth inhibition only above about 3.5 x 10^6^ µmol photons m^-2^
@@
 
-As with MED4 and SS120, our data again support enhanced growth under
+As with MED4 and SS120, our data again support enhanced growth rates under
 conditions of low cumulative diel PUR and 660 nm (red) spectral
-bandwidth, consistent with Murphy *et
-al*.[@murphyPhotoinactivationPhotosystemII2017] who found a lower cost
+bandwidth, consistent with Murphy *et al*.[@murphyPhotoinactivationPhotosystemII2017] who found a lower cost
 of growth, due to decreased photoinactivation of PSII under red,
@@
                       "Large symbols show mean of growth rate from logistic curve fits; small symbols show values from replicates, if any.",
-                    "Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to 660 nm (red lines) or 450 nm (blue lines) growth data for each combination of strain and dissolved oxygen shown with solid lines (red significantly different from blue, *P* value < 0.05) or dashed lines (red not significantly different from blue, *P* value > 0.05) tested using one-way ANOVA comparisons of fits.",
+                    "Harrison and Platt [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] 4 parameter model fit to 660 nm (red lines) or 450 nm (blue lines) growth rate data for each combination of strain and dissolved oxygen shown with solid lines (red significantly different from blue, *P* value < 0.05) or dashed lines (red not significantly different from blue, *P* value > 0.05) tested using one-way ANOVA comparisons of fits.",
                        .sep = " ")
@@
 
-## Photosystem II maintenance, oxygen metabolism, and DNA repair as limitations on *Prochlorococcus* growth {.unnumbered}
+## Photosystem II maintenance, oxygen metabolism, and DNA repair as limitations on *Prochlorococcus marinus* growth {.unnumbered}
 
 Under full atmospheric [O~2~] and blue light, LL clades of
-*Prochlorococcus* are restricted to growth under low light, in part
+*P. marinus* are restricted to growth under low light, in part
 because they suffer photoinhibition of Photosystem II (PSII) through
@@
 [@kanervoD1ProteinDegradation1993], mediated largely by a heterohexamer,
-termed in *Prochlorococcus* (FtsH1-FtsH2)~3~, a membrane-bound metalloprotease [@chibaMembraneProteinDegradation2002; @boehmSubunitOrganizationSynechocystis2012; @sacharzSubCellularLocation2015].
-
-*Prochlorococcus* genomes encode 4 FtsH proteins [@mannInvolvementFtsHHomologue2000; @adamFtsHProteasesChloroplasts2005], henceforth referred to
+termed in *P. marinus* (FtsH1-FtsH2)~3~, a membrane-bound metalloprotease [@chibaMembraneProteinDegradation2002; @boehmSubunitOrganizationSynechocystis2012; @sacharzSubCellularLocation2015].
+
+*Prochlorococcus marinus* genomes encode 4 FtsH proteins [@mannInvolvementFtsHHomologue2000; @adamFtsHProteasesChloroplasts2005], henceforth referred to
 as FtsH1-4, homologs to the characterized FtsH isoforms of the model
@@
 [@bonisteelStrainSpecificDifferences2018]. Through adaptation to steady
-low light, clade LLIV *Prochlorococcus* instead allocate resources to
+low light, clade LLIV *P. marinus* instead allocate resources to
 processes other than dynamic regulation of PSII repair.
@@
 PCC6803.
-Protein homologies for FtsH isoforms between *Prochlorococcus* and *Synechocystis* were extracted from @bonisteelStrainSpecificDifferences2018.",
+Protein homologies for FtsH isoforms between *Prochlorococcus marinus* and *Synechocystis* were extracted from @bonisteelStrainSpecificDifferences2018.",
               col.names =  c("Organism",
@@
                        "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome.",
-                       "For comparison, culture growth experimental conditions are indicated by horizontal grey lines for depths approximating peak Photosynthetically Active Radiation (PAR; µmol photons m^-2^ s^-1^); and vertical grey lines for [O~2~] (µM).",
+                       "For comparison, culture growth rate experimental conditions are indicated by horizontal grey lines for depths approximating peak Photosynthetically Active Radiation (PAR; µmol photons m^-2^ s^-1^); and vertical grey lines for [O~2~] (µM).",
                        "Data obtained from the Biological and Chemical Oceanography Data Management Office repository [@saitoPeptidesTheirSpectral2018].",
@@
 these strains to grow at higher light, may relate in part to suppression
-of DNA damage when generation of Reactive Oxygen Species is suppressed
+of DNA damage when generation of Reactive Oxygen Species (ROS) is suppressed
 at lower [O~2~]. NATL2A, a clade LLI, has been found near the ocean
@@
 supports why NATL2A tolerates limited exposure to high light and why
-NATL2A is unable to fully repair damaged DNA. *Prochlorococcus* are
+NATL2A is unable to fully repair damaged DNA. *Prochlorococcus marinus* are
 highly susceptible to hydrogen peroxide (H~2~O~2~) toxicity as they lack
@@
 [@morrisFacilitationRobustGrowth2008]. The small cell size of
-*Prochlorococcus* allow the reactive oxygen species (ROS), H~2~O~2~, to
+*P. marinus* allow the ROS, H~2~O~2~, to
 cross the cell membrane [@omarDiffusionalInteractionsMarine2022];
 however, accumulation of extracellular H~2~O~2~ remains toxic to
-*Prochlorococcus* [@morrisFacilitationRobustGrowth2008;
+*P. marinus* [@morrisFacilitationRobustGrowth2008;
 @morrisDependenceCyanobacteriumProchlorococcus2011].
@@
 d^-1^ of PUR (Fig \@ref(fig:PhotoperiodPurFitsPlots)E and H), comparable
-to the representative HL clade, MED4 which also exhibited growth
+to the representative HL clade, MED4 which also exhibited growth rate
 saturation at the same cumulative diel PUR of 1.0 x 10^6^ µmol photons
@@
 ability to thrive under very low [O~2~], potentially allowing it to
-expand into broader ecological niches. These results are supported by
+expand into broader ecological niches. Our results are supported by
 Fig \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSI protein
@@
 [@bagbyResponseProchlorococcusVarying2015] suggest that O~2~ has a
-protective role in *Prochlorococcus* under lower carbon dioxide
+protective role in *P. marinus* under lower carbon dioxide
 environments when carbon fixation is limited. The deep water
 environments typical for MIT9313 are relatively nutrient rich, and
-*Prochlorococcus* take up and metabolize various sugars
+*P. marinus* take up and metabolize various sugars
 [@gomez-baenaGlucoseUptakeIts2008;
@@
                                  "The green points are $\\Delta$OD measurements taken every 5 minutes.",
-                                 "The black lines are logistic growth curves fit using a nonlinear model regression (R package, minpack.lm).",
+                                 "The black lines are logistic growth rate curves fit using a nonlinear model regression (R package, minpack.lm).",
                                  "The gold points are the residuals of the fit.",
@@
 # This is S5_Fig.tiff 
-ProchlorococcusLightEnzymes_cap <- glue("***Prochlorococcus* genes encoding enzymes activated or inhibited by light.**",
+ProchlorococcusLightEnzymes_cap <- glue("***P. marinus* genes encoding enzymes activated or inhibited by light.**",
                          "The y-axis represents *Prochlorococcus marinus* strains.",

### 2024-05-28 Code/Import_MapMireillePro.Rmd
add map figure code

---
title: "Import_MetaData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

# Load Libraries and set Project Variables

```{r load libraries} 
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(ggpubr)
library(data.table)
library(googledrive)
library(googlesheets4)
library(ggspectra)
library(photobiologyWavebands)
library(photobiology)
library(tidyverse)
library("patchwork") # merging plots

```

```{r set project variables}
Project <- "BalticO2"
#DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedSolisensePigmentsData")

FigPath <- file.path("..", "Output", "Figures")
#FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")
```

----------------------------------------Create map ----------------------------------------------

# Create map
https://www.geeksforgeeks.org/how-to-make-world-map-with-ggplot2-in-r/

```{r}
world_coordinates <- map_data("world") 
world_coordinates$facetsSummerFull <- 'Season:~Summer~~~~~~~~~~~~~~Oxygen:~Full'
world_coordinates$facetsSpringFull <- 'Season:~Spring/Fall~~~~~~~~~~~~~~Oxygen:~Full'
world_coordinates$facetsWinterFull <- 'Season:~Winter~~~~~~~~~~~~~~Oxygen:~Full'
world_coordinates$facetsTropicFull <- 'Season:~All~year~~~~~~~~~~~~~~Oxygen:~Full'

world_coordinates$facetsSummerOMZ <- 'Season:~Summer~~~~~~~~~~~~~~Oxygen:~OMZ'
world_coordinates$facetsSpringOMZ <- 'Season:~Spring/Fall~~~~~~~~~~~~~~Oxygen:~OMZ'
world_coordinates$facetsWinterOMZ <- 'Season:~Winter~~~~~~~~~~~~~~Oxygen:~OMZ'
world_coordinates$facetsTropicOMZ <- 'Season:~All~year~~~~~~~~~~~~~~Oxygen:~OMZ'
```

```{r create GrowthCurve plot, fig.height = 4, fig.width = 6, warning = FALSE}
data_textA <- data.frame(label = c('A'))

d=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(35), y2=c(55))
d2=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-35), y2=c(-55))
d3=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-Inf), y2=c(Inf))
d4=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-15), y2=c(15))

SummerFull<-ggplot() + 
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
  labs(y = "Latitude", x = "Longitude") +
  ggh4x::facet_nested(cols = vars(facetsSummerFull), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        #axis.title.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
SummerFull

SpringFull<-ggplot() + 
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
  labs(y = "Latitude", x = "Longitude") +
  ggh4x::facet_nested(cols = vars(facetsSpringFull), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        #axis.title.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
SpringFull

WinterFull<-ggplot() + 
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
  labs(y = "Latitude", x = "Longitude") +
  ggh4x::facet_nested(cols = vars(facetsWinterFull), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        #axis.title.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
WinterFull

TropicFull<-ggplot() + 
  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
  labs(y = "Latitude", x = "Longitude") +
  ggh4x::facet_nested(cols = vars(facetsTropicFull), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        #axis.title.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
TropicFull
```

```{r, warning = FALSE, fig.height = 12, fig.width = 6}
Full<- (TropicFull/SpringFull/SummerFull/WinterFull)
Full                         
```

```{r create GrowthCurve plot, fig.height = 4, fig.width = 6, warning = FALSE}
data_textA <- data.frame(label = c('A'))

d=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(35), y2=c(55))
d2=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-35), y2=c(-55))
d3=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-Inf), y2=c(Inf))
d4=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-15), y2=c(15))

SummerOMZ<-ggplot() + 
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
  labs(y = "Latitude", x = "Longitude") +
  ggh4x::facet_nested(cols = vars(facetsSummerOMZ), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        #axis.title.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
SummerOMZ

SpringOMZ<-ggplot() + 
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
  labs(y = "Latitude", x = "Longitude") +
  ggh4x::facet_nested(cols = vars(facetsSpringOMZ), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        #axis.title.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
SpringOMZ

WinterOMZ<-ggplot() + 
  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
  labs(y = "Latitude", x = "Longitude") +
  ggh4x::facet_nested(cols = vars(facetsWinterOMZ), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        #axis.title.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
WinterOMZ

TropicOMZ<-ggplot() + 
  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
  labs(y = "Latitude", x = "Longitude") +
  ggh4x::facet_nested(cols = vars(facetsTropicOMZ), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        #axis.title.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
TropicOMZ
```

```{r, warning = FALSE, fig.height = 12, fig.width = 6}
OMZ<- (TropicOMZ/SpringOMZ/SummerFull/WinterOMZ)
OMZ                         
```
```{r}
# d=data.frame(x1=c(400, 700), x2=c(400, 700), y1=c(1), y2=c(2), t=c('a'), r=c(1))
# ggplot() + 
# scale_x_continuous(name="x") + 
# scale_y_continuous(name="y") +
# geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2, fill=t), color="black", alpha=0.5, show.legend = F) +
# geom_text(data=d, aes(x=x1+(x2-x1)/2, y=y1+(y2-y1)/2, label=r), size=4) +
#   
#   stat_wl_strip(aes(x = x1), ymin = -Inf, ymax = Inf, alpha = 0.5) +
#   scale_fill_identity() 
```

```{r}
# d=data.frame(x=c(550,700,700, 400, 550, 400), y=c(100,100,200, 100, 100, 200), t=c('a', 'a', 'a', 'b', 'b', 'b'), r=c(1,2,3, 4, 5, 6))
# ggplot() +
#   stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
#   scale_fill_identity() +
# geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
#   scale_y_continuous(breaks=seq(100, 200, by = 50)) +
#   coord_cartesian(ylim = c(100, 200)) 
```

```{r}
# world_coordinatesRainbow <- map_data("world") 
# world_coordinatesRainbow$nm <- c(400, 700)
# 
# ggplot() + 
#   stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = 100, alpha = 0.5, world_coordinatesRainbow) +
#   scale_fill_identity() +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank(),
#         axis.text = element_blank(),
#         axis.title = element_blank(),
#         axis.ticks = element_blank(),
#         strip.background = element_rect(fill="white"),
#         strip.text = element_text(size=14),
#         legend.background = element_rect(fill="transparent"),
#         legend.position = c(0.12,0.76),
#         legend.text = element_text(size=14))

```

```{r}

# 
# Rainbow<-ggplot() + 
#   geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
#   geom_map(data = world_coordinatesRainbow, map = world_coordinatesRainbow, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
#   #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
#   stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = 100, alpha = 0.5, world_coordinatesRainbow) +
#   scale_fill_identity() +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank(),
#         axis.text = element_text(size=14),
#         axis.title = element_text(size=18),
#         strip.background = element_rect(fill="white"),
#         strip.text = element_text(size=14),
#         axis.title.y = element_text(margin=margin(r=10)),
#         axis.title.x = element_text(margin=margin(t=10)),
#         #axis.title.x = element_blank(),
#         legend.background = element_rect(fill="transparent"),
#         legend.position = c(0.12,0.76),
#         legend.key.height= unit(0.005, 'cm'),
#         legend.spacing.x = unit(0.01, 'cm'),
#         legend.text = element_text(size=14))
# Rainbow
```

https://sape.inf.usi.ch/quick-reference/ggplot2/geom_polygon
```{r}
world_coordinatesRainbow <- map_data("world")
world_coordinatesRainbow$nm <- c(400, 700)

data_textTropicFullRainbowSurface <- data.frame(label = c('Near~surface:~MED4'))
data_textTropicFullRainbowDeep <- data.frame(label = c('Deep:~MED4~~SS120~~MIT9313'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
TropicFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textTropicFullRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textTropicFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
TropicFullRainbow

data_textSummerFullRainbowSurface <- data.frame(label = c('Near~surface:~MED4'))
data_textSummerFullRainbowDeep <- data.frame(label = c('Deep:~MED4~~SS120~~MIT9313'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SummerFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSummerFullRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textSummerFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SummerFullRainbow

data_textSpringFullRainbowSurface <- data.frame(label = c('Near~surface:~MED4'))
data_textSpringFullRainbowDeep <- data.frame(label = c('Deep:~MED4~~SS120~~MIT9313'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SpringFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSpringFullRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textSpringFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SpringFullRainbow

data_textWinterFullRainbowSurface <- data.frame(label = c('Near~surface'))
data_textWinterFullRainbowDeep <- data.frame(label = c('Deep:~MIT9313'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
WinterFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textWinterFullRainbowSurface, aes(x=500, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textWinterFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
WinterFullRainbow
```
```{r, warning = FALSE, fig.height = 12, fig.width = 6}
FullRainbow<- (TropicFullRainbow/SpringFullRainbow/SummerFullRainbow/WinterFullRainbow)
FullRainbow                         
```

```{r}
data_textTropicOMZRainbowSurface <- data.frame(label = c('Near~surface:~MED4~~SS120~~MIT9313'))
data_textTropicOMZRainbowDeep <- data.frame(label = c('Deep:~MED4~~SS120~~MIT9313'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
TropicOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textTropicOMZRainbowSurface, aes(x=530, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textTropicOMZRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
TropicOMZRainbow

data_textSummerOMZRainbowSurface <- data.frame(label = c('Near~surface:~MED4~~MIT9313'))
data_textSummerOMZRainbowDeep <- data.frame(label = c('Deep:~MED4~~SS120~~MIT9313'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SummerOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSummerOMZRainbowSurface, aes(x=500, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textSummerOMZRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SummerOMZRainbow

data_textSpringOMZRainbowSurface <- data.frame(label = c('Near~surface:~MED4~~SS120~~MIT9313'))
data_textSpringOMZRainbowDeep <- data.frame(label = c('Deep:~MED4~~SS120~~MIT9313'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SpringOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSpringOMZRainbowSurface, aes(x=530, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textSpringOMZRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SpringOMZRainbow

data_textWinterOMZRainbowSurface <- data.frame(label = c('Near~surface:~MIT9313'))
data_textWinterOMZRainbowDeep <- data.frame(label = c('Deep:~SS120~~MIT9313'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
WinterOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textWinterOMZRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textWinterOMZRainbowDeep, aes(x=480, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
WinterOMZRainbow
```
```{r, warning = FALSE, fig.height = 12, fig.width = 6}
OMZRainbow<- (TropicOMZRainbow/SpringOMZRainbow/SummerOMZRainbow/WinterOMZRainbow)
OMZRainbow                         
```

```{r, warning = FALSE, fig.height = 16, fig.width = 22}
MapCombo<-((TropicFull+TropicFullRainbow)+(TropicOMZ+TropicOMZRainbow))/((SpringFull+SpringFullRainbow)+(SpringOMZ+SpringOMZRainbow))/((SummerFull+SummerFullRainbow)+(SummerOMZ+SummerOMZRainbow))/((WinterFull+WinterFullRainbow)+(WinterOMZ+WinterOMZRainbow))
MapCombo                          
```

```{r, warning = FALSE, fig.height = 16, fig.width = 22}
MapCombo1<-((TropicFull+TropicFullRainbow))/((SpringFull+SpringFullRainbow))/((SummerFull+SummerFullRainbow))/((WinterFull+WinterFullRainbow))
MapCombo1                         
```

```{r, warning = FALSE, fig.height = 16, fig.width = 22}
MapCombo2<-((TropicOMZ+TropicOMZRainbow))/((SpringOMZ+SpringOMZRainbow))/((SummerOMZ+SummerOMZRainbow))/((WinterOMZ+WinterOMZRainbow))
MapCombo2                          
```

```{r, warning = FALSE, fig.height = 16, fig.width = 22}
library(ggpubr)
ggarrange(MapCombo1, MapCombo2, 
          ncol = 2, nrow = 1)
```

```{r save plot}
ggsave(file = file.path(FigPath, paste("Fig_MapComboMireillePro_2",".png",sep = "")), height=16, width= 22,  dpi = 300, limitsize = TRUE)
```

# Save rds for further analysis

```{r save rds}
# saveRDS(object = CultureCatalog, file = file.path("..", "Data", "ImportedData", "ImportedMetaData", "CultureCatalog.Rds"), compress = "xz")
```

# Variable names used in Data Dictionary

```{r}
#colnames(CultureCatalog)
```

```{r}
# # create data for world coordinates using map_data() function 
# world_coordinates <- map_data("world") 
#   
# # read volcano_eruption data from volcano.csv 
# volcano_eruption <- readr::read_csv("volcano.csv") 
#   
# # create world map using ggplot() function 
# ggplot() + 
# # geom_map() funct 
# ion takes world coordinates as input 
# # to plot world map color parameter determines the 
# # color of borders in map fill parameter determines the 
# # color of fill in map size determines the thickness of 
# # border in map 
#   geom_map( 
#     data = world, map = world, 
#     aes(long, lat, map_id = region), 
#     color = "green", fill= "lightyellow"
#   )+ 
# # geom_point function is used to plot scatter plot on top  
# # of world map 
# geom_point( 
#     data = volcano_eruption, 
#     aes(longitude, latitude, color = primary_volcano_type, 
#         size=population_within_10_km), 
#     alpha = 1 
#   ) + 
#   
# # legend.position as none removes the legend 
# theme(legend.position="none") 
```

### 2024-05-28 Code/Plots_Genome.Rmd
Update Plots_Genome.Rmd

@@
 Figures <- file.path("..", "Output", "Figures")
-PLOSFiguresRoundX <- file.path("..", "Output", "PLOSFiguresRound1")
+PLOSFiguresRoundX <- file.path("..", "Output", "PLOSRound2")
 # BLAST <- file.path("..", "BLAST")
@@
 ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms.png"), plot = ProchlorococcusEnzymeKms, height = 23, width = 17)
-# ggsave(filename = file.path(PLOSFiguresRoundX, "Fig11.tiff"), plot = ProchlorococcusEnzymeKms, height = 20, width = 17, compression = "lzw")
+ggsave(filename = file.path(PLOSFiguresRoundX, "Fig11.tiff"), plot = ProchlorococcusEnzymeKms, height = 20, width = 17, compression = "lzw")
 # ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms_julie.png"), plot = ProchlorococcusEnzymeKms, height = 23, width = 17)
@@
                                 EC == "3.2.2.21" ~ "DNA-3-methyladenine glycosylase II",
-                                EC == "3.1.3.18" ~ "phosphoglycolate phosphatase",
+                                # EC == "3.1.3.18" ~ "phosphoglycolate phosphatase",
                                 EC == "3.2.2.23" ~ "DNA-formamidopyrimidine glycosylase",
@@
 DNARepairFig <- DNARepairTab %>% 
+  filter(EC != "3.1.3.18") %>% #PGP is not truly a DNA repair enzyme. 
   ggplot() +

### 2024-05-28 Code/Import_MapMireillePro.Rmd
edits to map code

@@
 ---
-title: "Import_MetaData"
+title: "Import_Map"
 author:
@@
 ```{r load libraries} 
-library(lubridate)
-library(stringr)
+library(tidyverse)
+#library(lubridate)
+#library(stringr)
 library(broom)
-library(knitr)
+#library(knitr)
 library(OneR)
@@
 library(data.table)
-library(googledrive)
-library(googlesheets4)
+# library(googledrive)
+# library(googlesheets4)
 library(ggspectra)
@@
 library(photobiology)
-library(tidyverse)
+
 library("patchwork") # merging plots
@@
 ```{r set project variables}
-Project <- "BalticO2"
-#DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedSolisensePigmentsData")
+Project <- "prochlorococcus_O2"
 
@@
 #FigRdsPath <- file.path("..", "Output", "FiguresRds")
-TableRdsPath <- file.path("..", "Output", "TablesRDS")
+#TableRdsPath <- file.path("..", "Output", "TablesRDS")
 ```
@@
 
-```{r create GrowthCurve plot, fig.height = 4, fig.width = 6, warning = FALSE}
+```{r create map omz plot, fig.height = 4, fig.width = 6, warning = FALSE}
 data_textA <- data.frame(label = c('A'))
@@
 ```
-```{r}
-# d=data.frame(x1=c(400, 700), x2=c(400, 700), y1=c(1), y2=c(2), t=c('a'), r=c(1))
-# ggplot() + 
-# scale_x_continuous(name="x") + 
-# scale_y_continuous(name="y") +
-# geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2, fill=t), color="black", alpha=0.5, show.legend = F) +
-# geom_text(data=d, aes(x=x1+(x2-x1)/2, y=y1+(y2-y1)/2, label=r), size=4) +
-#   
-#   stat_wl_strip(aes(x = x1), ymin = -Inf, ymax = Inf, alpha = 0.5) +
-#   scale_fill_identity() 
-```
-
-```{r}
-# d=data.frame(x=c(550,700,700, 400, 550, 400), y=c(100,100,200, 100, 100, 200), t=c('a', 'a', 'a', 'b', 'b', 'b'), r=c(1,2,3, 4, 5, 6))
-# ggplot() +
-#   stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-#   scale_fill_identity() +
-# geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-#   scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-#   coord_cartesian(ylim = c(100, 200)) 
-```
-
-```{r}
-# world_coordinatesRainbow <- map_data("world") 
-# world_coordinatesRainbow$nm <- c(400, 700)
-# 
-# ggplot() + 
-#   stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = 100, alpha = 0.5, world_coordinatesRainbow) +
-#   scale_fill_identity() +
-#   theme_bw() +
-#   theme(panel.grid.minor = element_blank(),
-#         panel.grid.major = element_blank(),
-#         axis.text = element_blank(),
-#         axis.title = element_blank(),
-#         axis.ticks = element_blank(),
-#         strip.background = element_rect(fill="white"),
-#         strip.text = element_text(size=14),
-#         legend.background = element_rect(fill="transparent"),
-#         legend.position = c(0.12,0.76),
-#         legend.text = element_text(size=14))
-
-```
-
-```{r}
-
-# 
-# Rainbow<-ggplot() + 
-#   geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-#   geom_map(data = world_coordinatesRainbow, map = world_coordinatesRainbow, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-#   #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
-#   stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = 100, alpha = 0.5, world_coordinatesRainbow) +
-#   scale_fill_identity() +
-#   theme_bw() +
-#   theme(panel.grid.minor = element_blank(),
-#         panel.grid.major = element_blank(),
-#         axis.text = element_text(size=14),
-#         axis.title = element_text(size=18),
-#         strip.background = element_rect(fill="white"),
-#         strip.text = element_text(size=14),
-#         axis.title.y = element_text(margin=margin(r=10)),
-#         axis.title.x = element_text(margin=margin(t=10)),
-#         #axis.title.x = element_blank(),
-#         legend.background = element_rect(fill="transparent"),
-#         legend.position = c(0.12,0.76),
-#         legend.key.height= unit(0.005, 'cm'),
-#         legend.spacing.x = unit(0.01, 'cm'),
-#         legend.text = element_text(size=14))
-# Rainbow
-```
 
@@
 
-data_textTropicFullRainbowSurface <- data.frame(label = c('Near~surface:~MED4'))
-data_textTropicFullRainbowDeep <- data.frame(label = c('Deep:~MED4~~SS120~~MIT9313'))
+data_textTropicFullRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI'))
+data_textTropicFullRainbowDeep <- data.frame(label = c('Deep:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
 
-data_textSummerFullRainbowSurface <- data.frame(label = c('Near~surface:~MED4'))
-data_textSummerFullRainbowDeep <- data.frame(label = c('Deep:~MED4~~SS120~~MIT9313'))
+data_textSummerFullRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI'))
+data_textSummerFullRainbowDeep <- data.frame(label = c('Deep:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
 
-data_textSpringFullRainbowSurface <- data.frame(label = c('Near~surface:~MED4'))
-data_textSpringFullRainbowDeep <- data.frame(label = c('Deep:~MED4~~SS120~~MIT9313'))
+data_textSpringFullRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI'))
+data_textSpringFullRainbowDeep <- data.frame(label = c('Deep:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
 data_textWinterFullRainbowSurface <- data.frame(label = c('Near~surface'))
-data_textWinterFullRainbowDeep <- data.frame(label = c('Deep:~MIT9313'))
+data_textWinterFullRainbowDeep <- data.frame(label = c('Deep:~Clade~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
 ```{r}
-data_textTropicOMZRainbowSurface <- data.frame(label = c('Near~surface:~MED4~~SS120~~MIT9313'))
-data_textTropicOMZRainbowDeep <- data.frame(label = c('Deep:~MED4~~SS120~~MIT9313'))
+data_textTropicOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
+data_textTropicOMZRainbowDeep <- data.frame(label = c('Deep:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
 
-data_textSummerOMZRainbowSurface <- data.frame(label = c('Near~surface:~MED4~~MIT9313'))
-data_textSummerOMZRainbowDeep <- data.frame(label = c('Deep:~MED4~~SS120~~MIT9313'))
+data_textSummerOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI~~Clade~LLIV'))
+data_textSummerOMZRainbowDeep <- data.frame(label = c('Deep:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
 
-data_textSpringOMZRainbowSurface <- data.frame(label = c('Near~surface:~MED4~~SS120~~MIT9313'))
-data_textSpringOMZRainbowDeep <- data.frame(label = c('Deep:~MED4~~SS120~~MIT9313'))
+data_textSpringOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
+data_textSpringOMZRainbowDeep <- data.frame(label = c('Deep:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
 
-data_textWinterOMZRainbowSurface <- data.frame(label = c('Near~surface:~MIT9313'))
-data_textWinterOMZRainbowDeep <- data.frame(label = c('Deep:~SS120~~MIT9313'))
+data_textWinterOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clade~LLIV'))
+data_textWinterOMZRainbowDeep <- data.frame(label = c('Deep:~Clade~LLII/III~~Clade~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
 # Variable names used in Data Dictionary
-
-```{r}
-#colnames(CultureCatalog)
-```
-
-```{r}
-# # create data for world coordinates using map_data() function 
-# world_coordinates <- map_data("world") 
-#   
-# # read volcano_eruption data from volcano.csv 
-# volcano_eruption <- readr::read_csv("volcano.csv") 
-#   
-# # create world map using ggplot() function 
-# ggplot() + 
-# # geom_map() funct 
-# ion takes world coordinates as input 
-# # to plot world map color parameter determines the 
-# # color of borders in map fill parameter determines the 
-# # color of fill in map size determines the thickness of 
-# # border in map 
-#   geom_map( 
-#     data = world, map = world, 
-#     aes(long, lat, map_id = region), 
-#     color = "green", fill= "lightyellow"
-#   )+ 
-# # geom_point function is used to plot scatter plot on top  
-# # of world map 
-# geom_point( 
-#     data = volcano_eruption, 
-#     aes(longitude, latitude, color = primary_volcano_type, 
-#         size=population_within_10_km), 
-#     alpha = 1 
-#   ) + 
-#   
-# # legend.position as none removes the legend 
-# theme(legend.position="none") 
-```

### 2024-05-28 Code/Import_MapMireillePro.Rmd
changed filename for save.

@@
 ```{r save plot}
-ggsave(file = file.path(FigPath, paste("Fig_MapComboMireillePro_2",".png",sep = "")), height=16, width= 22,  dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(FigPath, paste("MapComboPro",".png",sep = "")), height=16, width= 22,  dpi = 300, limitsize = TRUE)
 ```

### 2024-05-28 Code/Manuscript_O2.Rmd
added niche map

@@
 
-```{r read temperate niche sheet, include=FALSE}
-
-ProchloroNiches <- read_csv(file.path(DataIn, "Prochlorococcus_temperate_niches.csv"))
-
-ProchloroNiches <- ProchloroNiches %>% 
-  mutate(MED4 = case_when(MED4 == "Potential" ~ "+",
-                          MED4 == "Excluded" ~ "-"),
-         SS120 = case_when(SS120 == "Potential" ~ "+",
-                          SS120 == "Excluded" ~ "-"),
-         MIT9313 = case_when(MIT9313 == "Potential" ~ "+",
-                          MIT9313 == "Excluded" ~ "-"))
-
-```
-
-```{r NichesTable,  fig.height = 8, fig.width = 6, echo = FALSE}
-
-knitr::kable(ProchloroNiches,
-             caption = "Potential temperate niches for *Prochlorococcus marinus* ecotypes defined by season, depth, and oxygen; Full denotes 250 µM of dissolved oxygen and OMZ denotes 25 µM of dissolved oxygen.
-Plus symbols (+) indicate a potential niche, minus symbols (-) not a potential niche.",
-        align = "lllccc" )
+```{r NichesMap, fig.cap = NichesMap_cap, fig.height = 15, fig.width = 15, echo = FALSE}
+
+NichesMap_cap <- glue(" Figure caption for Potential Temperate Future Niche map goes here.",
+
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "MapComboPro.png"))
+
 ```

### 2024-05-28 Code/Import_MapMireillePro.Rmd
Fixed some issues on map. Still need to be improved

@@
 world_coordinates <- map_data("world") 
+world_coordinates$facetsTropicFull <- 'Season:~All~year~~Hours~of~daylight:~12~~Oxygen:~Full'
+world_coordinates$facetsSpringFull <- 'Season:~Spring/Fall~~~~~~~~~~~~~~Oxygen:~Full'
 world_coordinates$facetsSummerFull <- 'Season:~Summer~~~~~~~~~~~~~~Oxygen:~Full'
-world_coordinates$facetsSpringFull <- 'Season:~Spring/Fall~~~~~~~~~~~~~~Oxygen:~Full'
 world_coordinates$facetsWinterFull <- 'Season:~Winter~~~~~~~~~~~~~~Oxygen:~Full'
-world_coordinates$facetsTropicFull <- 'Season:~All~year~~~~~~~~~~~~~~Oxygen:~Full'
 
+world_coordinates$facetsTropicOMZ <- 'Season:~All~year~~~~~~~~~~~~~~Oxygen:~OMZ'
+world_coordinates$facetsSpringOMZ <- 'Season:~Spring/Fall~~~~~~~~~~~~~~Oxygen:~OMZ'
 world_coordinates$facetsSummerOMZ <- 'Season:~Summer~~~~~~~~~~~~~~Oxygen:~OMZ'
-world_coordinates$facetsSpringOMZ <- 'Season:~Spring/Fall~~~~~~~~~~~~~~Oxygen:~OMZ'
 world_coordinates$facetsWinterOMZ <- 'Season:~Winter~~~~~~~~~~~~~~Oxygen:~OMZ'
-world_coordinates$facetsTropicOMZ <- 'Season:~All~year~~~~~~~~~~~~~~Oxygen:~OMZ'
+
 ```
@@
 d4=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-15), y2=c(15))
+d5=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-40), y2=c(40))
 
-SummerFull<-ggplot() + 
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
+data_textTropicFull <- data.frame(label = c('Season:~All~year~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~Full'))
+TropicFull<-ggplot() + 
+  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkblue", linetype = "dashed", alpha=0.7) +
+  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
   geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-  #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
+  geom_text(data=data_textTropicFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
+  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+  coord_cartesian(ylim = c(-90, 120)) +
   labs(y = "Latitude", x = "Longitude") +
-  ggh4x::facet_nested(cols = vars(facetsSummerFull), labeller = label_parsed) +
+  #ggh4x::facet_nested(cols = vars(facetsTropicFull), labeller = label_parsed) +
   theme_bw() +
@@
         axis.title.y = element_text(margin=margin(r=10)),
-        axis.title.x = element_text(margin=margin(t=10)),
-        #axis.title.x = element_blank(),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
         legend.background = element_rect(fill="transparent"),
@@
         legend.text = element_text(size=14))
-SummerFull
+TropicFull
 
+data_textSpringFull <- data.frame(label = c('Season:~Spring/Fall~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~Full'))
 SpringFull<-ggplot() + 
@@
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-  #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
+  geom_text(data=data_textSpringFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
+  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+  coord_cartesian(ylim = c(-90, 120)) +
   labs(y = "Latitude", x = "Longitude") +
-  ggh4x::facet_nested(cols = vars(facetsSpringFull), labeller = label_parsed) +
+  #ggh4x::facet_nested(cols = vars(facetsSpringFull), labeller = label_parsed) +
   theme_bw() +
@@
 
+data_textSummerFull <- data.frame(label = c('Season:~Summer~~~~~~~~Daylight:~16~h~~~~~~~~Oxygen:~Full'))
+SummerFull<-ggplot() + 
+  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
+  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
+  geom_text(data=data_textSummerFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
+  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+  coord_cartesian(ylim = c(-90, 120)) +
+  labs(y = "Latitude", x = "Longitude") +
+  #ggh4x::facet_nested(cols = vars(facetsSummerFull), labeller = label_parsed) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=14),
+        axis.title = element_text(size=18),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+        axis.title.y = element_text(margin=margin(r=10)),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14))
+SummerFull
+
+data_textWinterFull <- data.frame(label = c('Season:~Summer~~~~~~~~Daylight:~8~h~~~~~~~~Oxygen:~Full'))
 WinterFull<-ggplot() + 
@@
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-  #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
+  geom_text(data=data_textWinterFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
+  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+  coord_cartesian(ylim = c(-90, 120)) +
   labs(y = "Latitude", x = "Longitude") +
-  ggh4x::facet_nested(cols = vars(facetsWinterFull), labeller = label_parsed) +
+  #ggh4x::facet_nested(cols = vars(facetsWinterFull), labeller = label_parsed) +
   theme_bw() +
@@
 
-TropicFull<-ggplot() + 
-  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
-  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-  #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
-  labs(y = "Latitude", x = "Longitude") +
-  ggh4x::facet_nested(cols = vars(facetsTropicFull), labeller = label_parsed) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_text(size=14),
-        axis.title = element_text(size=18),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        axis.title.y = element_text(margin=margin(r=10)),
-        axis.title.x = element_text(margin=margin(t=10)),
-        #axis.title.x = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14))
-TropicFull
 ```
@@
 
-SummerOMZ<-ggplot() + 
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
+data_textTropicOMZ <- data.frame(label = c('Season:~All~year~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~OMZ'))
+TropicOMZ<-ggplot() + 
+  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkblue", linetype = "dashed", alpha=0.7) +
+  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
   geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-  #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
+  geom_text(data=data_textTropicOMZ, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
+  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+  coord_cartesian(ylim = c(-90, 120)) +
   labs(y = "Latitude", x = "Longitude") +
-  ggh4x::facet_nested(cols = vars(facetsSummerOMZ), labeller = label_parsed) +
+  #ggh4x::facet_nested(cols = vars(facetsTropicOMZ), labeller = label_parsed) +
   theme_bw() +
@@
         legend.text = element_text(size=14))
-SummerOMZ
+TropicOMZ
 
+data_textSpringOMZ <- data.frame(label = c('Season:~Spring/Fall~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~OMZ'))
 SpringOMZ<-ggplot() + 
@@
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-  #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
+  geom_text(data=data_textSpringOMZ, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
+  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+  coord_cartesian(ylim = c(-90, 120)) +
   labs(y = "Latitude", x = "Longitude") +
-  ggh4x::facet_nested(cols = vars(facetsSpringOMZ), labeller = label_parsed) +
+  #ggh4x::facet_nested(cols = vars(facetsSpringOMZ), labeller = label_parsed) +
   theme_bw() +
@@
 
+data_textSummerOMZ <- data.frame(label = c('Season:~Summer~~~~~~~~Daylight:~16~h~~~~~~~~Oxygen:~OMZ'))
+SummerOMZ<-ggplot() + 
+  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
+  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
+  geom_text(data=data_textSummerOMZ, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
+  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+  coord_cartesian(ylim = c(-90, 120)) +
+  labs(y = "Latitude", x = "Longitude") +
+  #ggh4x::facet_nested(cols = vars(facetsSummerOMZ), labeller = label_parsed) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=14),
+        axis.title = element_text(size=18),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+        axis.title.y = element_text(margin=margin(r=10)),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14))
+SummerOMZ
+
+data_textWinterOMZ <- data.frame(label = c('Season:~Summer~~~~~~~~Daylight:~8~h~~~~~~~~Oxygen:~OMZ'))
 WinterOMZ<-ggplot() + 
@@
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-  #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
+  geom_text(data=data_textWinterOMZ, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
+  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+  coord_cartesian(ylim = c(-90, 120)) +
   labs(y = "Latitude", x = "Longitude") +
-  ggh4x::facet_nested(cols = vars(facetsWinterOMZ), labeller = label_parsed) +
+  #ggh4x::facet_nested(cols = vars(facetsWinterOMZ), labeller = label_parsed) +
   theme_bw() +
@@
 
-TropicOMZ<-ggplot() + 
-  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
-  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-  #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
-  labs(y = "Latitude", x = "Longitude") +
-  ggh4x::facet_nested(cols = vars(facetsTropicOMZ), labeller = label_parsed) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_text(size=14),
-        axis.title = element_text(size=18),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        axis.title.y = element_text(margin=margin(r=10)),
-        axis.title.x = element_text(margin=margin(t=10)),
-        #axis.title.x = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14))
-TropicOMZ
 ```
@@
 ```{r, warning = FALSE, fig.height = 12, fig.width = 6}
-OMZ<- (TropicOMZ/SpringOMZ/SummerFull/WinterOMZ)
+OMZ<- (TropicOMZ/SpringOMZ/SummerOMZ/WinterOMZ)
 OMZ                         
@@
 data_textTropicFullRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI'))
-data_textTropicFullRainbowDeep <- data.frame(label = c('Deep:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
+data_textTropicFullRainbowDeep <- data.frame(label = c('Deep:~Clades~HLI~~LLII/III~~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
 data_textSummerFullRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI'))
-data_textSummerFullRainbowDeep <- data.frame(label = c('Deep:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
+data_textSummerFullRainbowDeep <- data.frame(label = c('Deep:~Clades~HLI~~LLII/III~~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
 data_textSpringFullRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI'))
-data_textSpringFullRainbowDeep <- data.frame(label = c('Deep:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
+data_textSpringFullRainbowDeep <- data.frame(label = c('Deep:~Clades~HLI~~LLII/III~~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
 ```{r}
-data_textTropicOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
-data_textTropicOMZRainbowDeep <- data.frame(label = c('Deep:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
+data_textTropicOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clades~HLI~~LLII/III~~LLIV'))
+data_textTropicOMZRainbowDeep <- data.frame(label = c('Deep:~Clades~HLI~~LLII/III~~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
 
-data_textSummerOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI~~Clade~LLIV'))
-data_textSummerOMZRainbowDeep <- data.frame(label = c('Deep:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
+data_textSummerOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clades~HLI~~LLIV'))
+data_textSummerOMZRainbowDeep <- data.frame(label = c('Deep:~Clades~HLI~~LLII/III~~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
 
-data_textSpringOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
-data_textSpringOMZRainbowDeep <- data.frame(label = c('Deep:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
+data_textSpringOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clades~HLI~~LLII/III~~LLIV'))
+data_textSpringOMZRainbowDeep <- data.frame(label = c('Deep:~Clades~HLI~~LLII/III~~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
 data_textWinterOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clade~LLIV'))
-data_textWinterOMZRainbowDeep <- data.frame(label = c('Deep:~Clade~LLII/III~~Clade~LLIV'))
+data_textWinterOMZRainbowDeep <- data.frame(label = c('Deep:~Clades~LLII/III~~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
 ```{r save plot}
-ggsave(file = file.path(FigPath, paste("MapComboPro",".png",sep = "")), height=16, width= 22,  dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(FigPath, paste("MapComboPro_2",".png",sep = "")), height=16, width= 22,  dpi = 300, limitsize = TRUE)
 ```

### 2024-05-28 Code/Plots_OceanProtein.Rmd
Changed title to match the rmd name

@@
 ---
-title: "OceanProteinPlots"
+title: "Plots_OceanProtein"
 ---
@@
   ggplot() +
-  geom_point(aes(x = O2, y= depth)) +
+  geom_jitter(aes(x = O2, y= depth), size = 0.5, width = 10, height = 10) +
   scale_x_continuous(limits = c(0, 260)) +
@@
   geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.1) +
-  facet_grid(factor(strain, levels = c("MED4", "SS120", "MIT9313")) ~ factor(complex, levels = c("psii", "cytb6f", "psi", "rubisco", "atp"), labels = PhotosynthLabels)) +
-  labs(y = "Depth (m)",
+  facet_grid(factor(strain, levels = c("MED4", "SS120", "MIT9313")) ~ factor(complex, levels = c("psii", "cytb6f", "psi","atp",  "rubisco"), labels = PhotosynthLabels)) +
+  labs(title = expression('Ocean detection of' ~italic(Prochlorococcus)~ 'photosynthesis complexes'),
+       y = "Depth (m)",
        x = expression("O"[2] ~ "(µM)")) +
@@
    labs(y = "Depth (m)",
-        x = expression("O"[2] ~ "(µM)")) +
+        x = expression("O"[2] ~ "(µM)"),
+        title = expression('Ocean detection of' ~italic(Prochlorococcus)~ 'protein metabolism complexes')) +
   theme_bw()
@@
   ggplot() +
-  geom_point(aes(x = O2, y= depth)) +
+   geom_jitter(aes(x = O2, y= depth), size = 0.5, width = 10, height = 10) +
   scale_x_continuous(limits = c(0, 260)) +
@@
   geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.1) +
-  facet_grid(factor(strain, levels = c("MED4", "NATL2A", "SS120", "MIT9313")) ~ factor(complex, levels = c("psii", "cytb6f", "psi", "rubisco", "atp"), labels = PhotosynthLabels)) +
+  facet_grid(factor(strain, levels = c("MED4", "NATL2A", "SS120", "MIT9313")) ~ factor(complex, levels = c("psii", "cytb6f", "psi",  "atp", "rubisco"), labels = PhotosynthLabels)) +
   labs(y = "Depth (m)",
@@
   geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.1) +
-  facet_grid(rows = vars(clade), cols = vars(factor(complex, levels = c("psii", "cytb6f", "psi", "rubisco", "atp"), labels = PhotosynthLabels))) +
+  facet_grid(rows = vars(clade), cols = vars(factor(complex, levels = c("psii", "cytb6f", "psi", "atp", "rubisco"), labels = PhotosynthLabels))) +
   labs(y = "Depth (m)",
@@
   ggplot() +
-  geom_point(aes(x = O2, y= depth), data = . %>% filter(strain %notin% AltStrainLabels)) +
+  geom_jitter(aes(x = O2, y= depth), data = . %>% filter(strain %notin% AltStrainLabels), size = 0.5, width = 10, height = 10) +
   annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, alpha = 0.75, fill = "white") +
-  geom_point(aes(x = O2, y= depth), data = . %>% filter(strain %in% AltStrainLabels)) +
+  geom_jitter(aes(x = O2, y= depth), data = . %>% filter(strain %in% AltStrainLabels), size = 0.5, width = 10, height = 10) +
   # geom_point(aes(x = O2, y= depth, alpha = StrainAlpha)) +
@@
   guides(alpha = 'none') +
-  facet_grid(rows = vars(CladeMergeFactor), cols = vars(factor(complex, levels = c("psii", "cytb6f", "psi", "rubisco", "atp"), labels = PhotosynthLabels))) +
+  facet_grid(rows = vars(CladeMergeFactor), cols = vars(factor(complex, levels = c("psii", "cytb6f", "psi", "atp", "rubisco"), labels = PhotosynthLabels))) +
   labs(y = "Depth (m)",

### 2024-05-28 Code/Import_MapMireillePro.Rmd
Fixed map plot :)

@@
 library(photobiology)
-
+library(ggforce) #ellipse
 library("patchwork") # merging plots
@@
 TropicFull<-ggplot() + 
-  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkblue", linetype = "dashed", alpha=0.7) +
+  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkblue", linetype = "dashed", alpha=0.9, size = 1) +
   geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
@@
 TropicOMZ<-ggplot() + 
-  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkblue", linetype = "dashed", alpha=0.7) +
+  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkblue", linetype = "dashed", alpha=0.9, size = 1) +
   geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
@@
 
-data_textTropicFullRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI'))
-data_textTropicFullRainbowDeep <- data.frame(label = c('Deep:~Clades~HLI~~LLII/III~~LLIV'))
+data_textTropicFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clade~HLI'))
+data_textTropicFullRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
   geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
   scale_y_continuous(breaks=seq(100, 200, by = 50)) +
   coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textTropicFullRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_textTropicFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_textTropicFullRainbowSurface, aes(x=500, y=215, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textTropicFullRainbowDeep, aes(x=515, y=90, label=label), size=4.5, parse=TRUE) +
   theme_bw() +
@@
 
-data_textSummerFullRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI'))
-data_textSummerFullRainbowDeep <- data.frame(label = c('Deep:~Clades~HLI~~LLII/III~~LLIV'))
+data_textSpringFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clade~HLI'))
+data_textSpringFullRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
+d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
+SpringFullRainbow<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+  scale_fill_identity() +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
+  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+  coord_cartesian(ylim = c(80, 220)) +
+  geom_text(data=data_textSpringFullRainbowSurface, aes(x=500, y=215, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textSpringFullRainbowDeep, aes(x=515, y=90, label=label), size=4.5, parse=TRUE) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_blank(),
+        axis.title = element_blank(),
+        axis.ticks = element_blank(),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.text = element_text(size=14))
+SpringFullRainbow
+
+data_textSummerFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clade~HLI'))
+data_textSummerFullRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
   geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
   scale_y_continuous(breaks=seq(100, 200, by = 50)) +
   coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textSummerFullRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_textSummerFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_textSummerFullRainbowSurface, aes(x=500, y=215, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textSummerFullRainbowDeep, aes(x=515, y=90, label=label), size=4.5, parse=TRUE) +
   theme_bw() +
@@
 
-data_textSpringFullRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI'))
-data_textSpringFullRainbowDeep <- data.frame(label = c('Deep:~Clades~HLI~~LLII/III~~LLIV'))
-d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-SpringFullRainbow<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textSpringFullRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_textSpringFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_blank(),
-        axis.title = element_blank(),
-        axis.ticks = element_blank(),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.text = element_text(size=14))
-SpringFullRainbow
-
-data_textWinterFullRainbowSurface <- data.frame(label = c('Near~surface'))
-data_textWinterFullRainbowDeep <- data.frame(label = c('Deep:~Clade~LLIV'))
+data_textWinterFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE)'))
+data_textWinterFullRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clade~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
   geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
   scale_y_continuous(breaks=seq(100, 200, by = 50)) +
   coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textWinterFullRainbowSurface, aes(x=500, y=210, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_textWinterFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_textWinterFullRainbowSurface, aes(x=470, y=215, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textWinterFullRainbowDeep, aes(x=475, y=90, label=label), size=4.5, parse=TRUE) +
   theme_bw() +
@@
 ```{r}
-data_textTropicOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clades~HLI~~LLII/III~~LLIV'))
-data_textTropicOMZRainbowDeep <- data.frame(label = c('Deep:~Clades~HLI~~LLII/III~~LLIV'))
+data_textTropicOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clades~HLI~~LLII/III~~LLIV'))
+data_textTropicOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
   geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
   scale_y_continuous(breaks=seq(100, 200, by = 50)) +
   coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textTropicOMZRainbowSurface, aes(x=530, y=210, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_textTropicOMZRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_textTropicOMZRainbowSurface, aes(x=535, y=215, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textTropicOMZRainbowDeep, aes(x=510, y=90, label=label), size=4.5, parse=TRUE) +
   theme_bw() +
@@
 
-data_textSummerOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clades~HLI~~LLIV'))
-data_textSummerOMZRainbowDeep <- data.frame(label = c('Deep:~Clades~HLI~~LLII/III~~LLIV'))
+data_textSpringOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clades~HLI~~LLII/III~~LLIV'))
+data_textSpringOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
+d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
+SpringOMZRainbow<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+  scale_fill_identity() +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
+  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+  coord_cartesian(ylim = c(80, 220)) +
+  geom_text(data=data_textSpringOMZRainbowSurface, aes(x=535, y=215, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textSpringOMZRainbowDeep, aes(x=510, y=90, label=label), size=4.5, parse=TRUE) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_blank(),
+        axis.title = element_blank(),
+        axis.ticks = element_blank(),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.text = element_text(size=14))
+SpringOMZRainbow
+
+data_textSummerOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clades~HLI~~LLIV'))
+data_textSummerOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
   geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
   scale_y_continuous(breaks=seq(100, 200, by = 50)) +
   coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textSummerOMZRainbowSurface, aes(x=500, y=210, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_textSummerOMZRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_textSummerOMZRainbowSurface, aes(x=515, y=215, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textSummerOMZRainbowDeep, aes(x=510, y=90, label=label), size=4.5, parse=TRUE) +
   theme_bw() +
@@
 
-data_textSpringOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clades~HLI~~LLII/III~~LLIV'))
-data_textSpringOMZRainbowDeep <- data.frame(label = c('Deep:~Clades~HLI~~LLII/III~~LLIV'))
-d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-SpringOMZRainbow<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textSpringOMZRainbowSurface, aes(x=530, y=210, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_textSpringOMZRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_blank(),
-        axis.title = element_blank(),
-        axis.ticks = element_blank(),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.text = element_text(size=14))
-SpringOMZRainbow
-
-data_textWinterOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clade~LLIV'))
-data_textWinterOMZRainbowDeep <- data.frame(label = c('Deep:~Clades~LLII/III~~LLIV'))
+data_textWinterOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clade~LLIV'))
+data_textWinterOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~LLII/III~~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
   geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
   scale_y_continuous(breaks=seq(100, 200, by = 50)) +
   coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textWinterOMZRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_textWinterOMZRainbowDeep, aes(x=480, y=90, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_textWinterOMZRainbowSurface, aes(x=500, y=215, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textWinterOMZRainbowDeep, aes(x=500, y=90, label=label), size=4.5, parse=TRUE) +
   theme_bw() +
@@
 ```{r, warning = FALSE, fig.height = 16, fig.width = 22}
-MapCombo<-((TropicFull+TropicFullRainbow)+(TropicOMZ+TropicOMZRainbow))/((SpringFull+SpringFullRainbow)+(SpringOMZ+SpringOMZRainbow))/((SummerFull+SummerFullRainbow)+(SummerOMZ+SummerOMZRainbow))/((WinterFull+WinterFullRainbow)+(WinterOMZ+WinterOMZRainbow))
-MapCombo                          
+# MapCombo<-((TropicFull+TropicFullRainbow)+(TropicOMZ+TropicOMZRainbow))/((SpringFull+SpringFullRainbow)+(SpringOMZ+SpringOMZRainbow))/((SummerFull+SummerFullRainbow)+(SummerOMZ+SummerOMZRainbow))/((WinterFull+WinterFullRainbow)+(WinterOMZ+WinterOMZRainbow))
+# MapCombo                          
 ```
@@
 ```{r save plot}
-ggsave(file = file.path(FigPath, paste("MapComboPro_2",".png",sep = "")), height=16, width= 22,  dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(FigPath, paste("MapComboPro",".png",sep = "")), height=16, width= 22,  dpi = 300, limitsize = TRUE)
 ```
@@
 
-# Variable names used in Data Dictionary
+https://ggforce.data-imaginist.com/reference/geom_ellipse.html
+elipse
+
+```{r}
+
+# ggplot() +
+#   geom_ellipse(aes(x0 = 550, y0 = 150, a = 150, b = 50, angle = pi / 4)) +
+#   coord_fixed()
+```
+
+```{r}
+# d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
+# ggplot() +
+#   stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+#   scale_fill_identity() +
+#   geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+#   scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+#   coord_cartesian(ylim = c(80, 220)) +
+#   theme_bw() +
+#   geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+#   coord_fixed()
+```

### 2024-05-28 Code/Import_MapMireillePro.Rmd
Replaced green strip to yellow on map b/c it was confusing

@@
 TropicFull<-ggplot() + 
-  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkblue", linetype = "dashed", alpha=0.9, size = 1) +
-  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkgreen", linetype = "dashed", alpha=1, size = 1) +
+  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.2) +
+  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
+
   geom_text(data=data_textTropicFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
@@
 SpringFull<-ggplot() + 
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.2) +
+  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
@@
 SummerFull<-ggplot() + 
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.2) +
+  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
@@
 WinterFull<-ggplot() + 
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.2) +
+  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
@@
 TropicOMZ<-ggplot() + 
-  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkblue", linetype = "dashed", alpha=0.9, size = 1) +
-  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkgreen", linetype = "dashed", alpha=0.9, size = 1) +
+  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
+
   geom_text(data=data_textTropicOMZ, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
@@
 SpringOMZ<-ggplot() + 
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
@@
 SummerOMZ<-ggplot() + 
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
@@
 WinterOMZ<-ggplot() + 
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +

### 2024-05-29 Code/Import_MapMireillePro.Rmd
New map

@@
   geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkgreen", linetype = "dashed", alpha=1, size = 1) +
-  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.2) +
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
   geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
@@
 SpringFull<-ggplot() + 
-  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.2) +
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
   geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
@@
 SummerFull<-ggplot() + 
-  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.2) +
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
   geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
@@
 WinterFull<-ggplot() + 
-  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.2) +
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
   geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
@@
   geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkgreen", linetype = "dashed", alpha=0.9, size = 1) +
-  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
   geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
@@
 SpringOMZ<-ggplot() + 
-  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
   geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
@@
 SummerOMZ<-ggplot() + 
-  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
   geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
@@
 WinterOMZ<-ggplot() + 
-  #geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
   geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
@@
 
-data_textTropicFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clade~HLI'))
-data_textTropicFullRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
+data_textTropicFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clade~HLI'))
+data_textTropicFullRainbowDeep <- data.frame(label = c('Deep~(30~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
   coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textTropicFullRainbowSurface, aes(x=500, y=215, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_textTropicFullRainbowDeep, aes(x=515, y=90, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textTropicFullRainbowSurface, aes(x=510, y=215, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textTropicFullRainbowDeep, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
   theme_bw() +
@@
 
-data_textSpringFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clade~HLI'))
-data_textSpringFullRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
+data_textSpringFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clade~HLI'))
+data_textSpringFullRainbowDeep <- data.frame(label = c('Deep~(30~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
   coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textSpringFullRainbowSurface, aes(x=500, y=215, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_textSpringFullRainbowDeep, aes(x=515, y=90, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textSpringFullRainbowSurface, aes(x=510, y=215, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textSpringFullRainbowDeep, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
   theme_bw() +
@@
 
-data_textSummerFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clade~HLI'))
-data_textSummerFullRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
+data_textSummerFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE~","~12~h):~Clade~HLI'))
+data_textSummerFullRainbowDeep <- data.frame(label = c('Deep~(30~µE~","~12~h):~Clades~HLI~","~LLII/III~","~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
   coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textSummerFullRainbowSurface, aes(x=500, y=215, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_textSummerFullRainbowDeep, aes(x=515, y=90, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textSummerFullRainbowSurface, aes(x=510, y=215, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textSummerFullRainbowDeep, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
   theme_bw() +
@@
 
-data_textWinterFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE)'))
-data_textWinterFullRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clade~LLIV'))
+data_textWinterFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE~","~4~h)'))
+data_textWinterFullRainbowDeep <- data.frame(label = c('Deep~(30~µE~","~4~h):~Clade~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
   coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textWinterFullRainbowSurface, aes(x=470, y=215, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_textWinterFullRainbowDeep, aes(x=475, y=90, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textWinterFullRainbowSurface, aes(x=480, y=215, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textWinterFullRainbowDeep, aes(x=485, y=90, label=label), size=4.5, parse=TRUE) +
   theme_bw() +
@@
 ```{r}
-data_textTropicOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clades~HLI~~LLII/III~~LLIV'))
-data_textTropicOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
+data_textTropicOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+data_textTropicOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
   coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textTropicOMZRainbowSurface, aes(x=535, y=215, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_textTropicOMZRainbowDeep, aes(x=510, y=90, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textTropicOMZRainbowSurface, aes(x=555, y=215, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textTropicOMZRainbowDeep, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
   theme_bw() +
@@
 
-data_textSpringOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clades~HLI~~LLII/III~~LLIV'))
-data_textSpringOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
+data_textSpringOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+data_textSpringOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
   coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textSpringOMZRainbowSurface, aes(x=535, y=215, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_textSpringOMZRainbowDeep, aes(x=510, y=90, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textSpringOMZRainbowSurface, aes(x=555, y=215, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textSpringOMZRainbowDeep, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
   theme_bw() +
@@
 
-data_textSummerOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clades~HLI~~LLIV'))
-data_textSummerOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
+data_textSummerOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE~","~12~h):~Clades~HLI~","~LLIV'))
+data_textSummerOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE~","~12~h):~Clades~HLI~","~LLII/III~","~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
   coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textSummerOMZRainbowSurface, aes(x=515, y=215, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_textSummerOMZRainbowDeep, aes(x=510, y=90, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textSummerOMZRainbowSurface, aes(x=535, y=215, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textSummerOMZRainbowDeep, aes(x=535, y=90, label=label), size=4.5, parse=TRUE) +
   theme_bw() +
@@
 
-data_textWinterOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clade~LLIV'))
-data_textWinterOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~LLII/III~~LLIV'))
+data_textWinterOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE~","~4~h):~Clade~LLIV'))
+data_textWinterOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE~","~4~h):~Clades~LLII/III~","~LLIV'))
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
@@
   coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textWinterOMZRainbowSurface, aes(x=500, y=215, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_textWinterOMZRainbowDeep, aes(x=500, y=90, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textWinterOMZRainbowSurface, aes(x=510, y=215, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textWinterOMZRainbowDeep, aes(x=510, y=90, label=label), size=4.5, parse=TRUE) +
   theme_bw() +
@@
 ```
+
+```{r}
+# library(ggthemes)
+# library(mapproj)
+# world_map = map_data("world") %>% 
+#   filter(! long > 180)
+# 
+# countries = world_map %>% 
+#   distinct(region) %>% 
+#   rowid_to_column()
+# 
+# countries %>% 
+#   ggplot(aes(map_id = region), fill = "midnightblue") +
+#   geom_map(map = world_map) +
+#   expand_limits(x = world_map$long, y = world_map$lat) +
+#   coord_map("moll") 
+#   #theme_map()
+# 
+# 
+# 
+# 
+# world_map = map_data("world") %>% 
+#   filter(! long > 180)
+#   
+# distinct(world_map, region) %>% 
+#   ggplot(aes(map_id = region), fill = "midnightblue") +
+#   geom_map(map = world_map) +
+#   expand_limits(x = world_map$long, y = world_map$lat) +
+#   coord_map("moll") 
+#   #coord_equal() 
+```

### 2024-05-29 Code/Plots_OceanProtein.Rmd
updates to ocean protein plots

@@
 
-ElectronTrans <- c("psii", "cytb6f", "psi", "rubisco", "atp")
+ElectronTrans <- c("psii", "cytb6f", "psi", "atp", "rubisco")
 
@@
   ggplot() +
-   geom_jitter(aes(x = O2, y= depth), size = 0.5, width = 10, height = 10) +
+   geom_jitter(aes(x = O2, y= depth), size = 0.5, width = 20, height = 20) +
   scale_x_continuous(limits = c(0, 260)) +
@@
   ggplot() +
-  geom_jitter(aes(x = O2, y= depth), size = 0.5, width = 10, height = 10) +
+  geom_jitter(aes(x = O2, y= depth), size = 0.5, width = 20, height = 20) +
   scale_x_continuous(limits = c(0, 260)) +
@@
 
-```{r clade_plots}
-CladeLabels <- c("HLI", "HLII", "LLI", "LLII",  "LLIII", "LLIV")
-
-PhotosynthLabels <- c("PSII", "Cytb6f", "PSI", "ATP Synthase", "RUBISCO")
-ProteinMetabLabels <- c("FtsH1", "FtsH2", "FtsH3", "FtsH4", "Ribosome")
-
-poi |>
-  filter(complex %in% ElectronTrans) |>
-  ggplot() +
-  geom_jitter(aes(x = O2, y= depth), size = 0.5, width = 10, height = 10) +
-  scale_x_continuous(limits = c(0, 260)) +
-  scale_y_reverse(limits = c(260, 0)) +
-  geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.1) +
-  geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.1) +
-  facet_grid(rows = vars(clade), cols = vars(factor(complex, levels = c("psii", "cytb6f", "psi", "atp", "rubisco"), labels = PhotosynthLabels))) +
-  labs(y = "Depth (m)",
-       x = expression("O"[2] ~ "(µM)")) +
-    # ) +
-  theme_bw()
-
- # ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.png")))
- # ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.tiff")))
-
-poi |>
-  filter(complex %in% ProteinMetab) |>
-  ggplot() +
-  geom_jitter(aes(x = O2, y= depth), size = 0.5, width = 10, height = 10) +
-  scale_x_continuous(limits = c(0, 260)) +
-  scale_y_reverse(limits = c(260, 0)) +
-  geom_vline(xintercept = O2_uM,   linewidth = 2, alpha = 0.1) +
-  geom_hline(yintercept = DepthPAR, linewidth = 2, alpha = 0.1) +
-  facet_grid(rows = vars(clade), cols = vars(factor(complex, levels = c("ftsh1", "ftsh2", "ftsh3", "ftsh4", "ribosome"), labels = ProteinMetabLabels))) +
-   labs(y = "Depth (m)",
-        x = expression("O"[2] ~ "(µM)")) +
-  theme_bw()
-
-  # ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.png")))
-  # ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.tiff")))
-
-```
-
 ```{r clademerge_plots}
@@
 
+#order of geom_ and annotate calls matters; 'annotate' overlays a semi transparent box over the first layer of geom_
 poi |>
@@
   ggplot() +
-  geom_jitter(aes(x = O2, y= depth), data = . %>% filter(strain %notin% AltStrainLabels), size = 0.5, width = 10, height = 10) +
+  geom_jitter(aes(x = O2, y= depth), data = . %>% filter(strain %notin% AltStrainLabels), size = 0.1, width = 20, height = 20) + #grey points not in AltStrainLabels
+ # geom_count(aes(x = O2, y= depth)) +
   annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, alpha = 0.75, fill = "white") +
-  geom_jitter(aes(x = O2, y= depth), data = . %>% filter(strain %in% AltStrainLabels), size = 0.5, width = 10, height = 10) +
+  geom_jitter(aes(x = O2, y= depth), data = . %>% filter(strain %in% AltStrainLabels), size = 0.1, width = 20, height = 20) + #black points in AltStrainLabels
   # geom_point(aes(x = O2, y= depth, alpha = StrainAlpha)) +
@@
     # ) +
-  theme_bw()
+  theme_bw() +
+  theme(strip.text = element_text(size = 8))
 
  ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.png")))
- ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSFiguresRound1", "Fig2.tiff")))
+ ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSRound2", "Fig2.tiff")))
 
@@
   ggplot() +
-  geom_jitter(aes(x = O2, y= depth), data = . %>% filter(strain %notin% AltStrainLabels), size = 0.5, width = 10, height = 10) +
+  geom_jitter(aes(x = O2, y= depth), data = . %>% filter(strain %notin% AltStrainLabels), size = 0.1, width = 20, height = 20) +
   annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, alpha = 0.75, fill = "white") +
-  geom_jitter(aes(x = O2, y= depth), data = . %>% filter(strain %in% AltStrainLabels), size = 0.5, width = 10, height = 10) +
+  geom_jitter(aes(x = O2, y= depth), data = . %>% filter(strain %in% AltStrainLabels), size = 0.1, width = 20, height = 20) +
   # geom_point(aes(x = O2, y= depth, alpha = StrainAlpha)) +
@@
         x = expression("O"[2] ~ "(µM)")) +
-  theme_bw()
+  theme_bw() +
+  theme(strip.text = element_text(size = 8))
 
    ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.png")))
-   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSFiguresRound1", "Fig10.tiff")))
+   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSRound2", "Fig10.tiff")))
 

### 2024-05-29 Code/Import_MapMireillePro.Rmd

@@
 
+world_coordinates$facetsPresent <- 'Present'
+world_coordinates$facetsFuture <- 'Future~temperate'
 ```
@@
   labs(y = "Latitude", x = "Longitude") +
-  #ggh4x::facet_nested(cols = vars(facetsTropicFull), labeller = label_parsed) +
+  ggh4x::facet_nested(rows = vars(facetsPresent), labeller = label_parsed, switch = "y") +
   theme_bw() +
@@
         panel.grid.major = element_blank(),
+        strip.placement = "outside",
+        strip.switch.pad.grid = unit(1, "cm"),
         axis.text = element_text(size=14),
-        axis.title = element_text(size=18),
+        axis.title = element_text(size=14),
         strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        axis.title.y = element_text(margin=margin(r=10)),
+        strip.text = element_text(size=18),
+        axis.title.y = element_text(vjust = -15),
         #axis.title.x = element_text(margin=margin(t=10)),
@@
   labs(y = "Latitude", x = "Longitude") +
-  #ggh4x::facet_nested(cols = vars(facetsSpringFull), labeller = label_parsed) +
+  ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
   theme_bw() +
@@
   labs(y = "Latitude", x = "Longitude") +
-  #ggh4x::facet_nested(cols = vars(facetsSummerFull), labeller = label_parsed) +
+  ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
   theme_bw() +
@@
   labs(y = "Latitude", x = "Longitude") +
-  #ggh4x::facet_nested(cols = vars(facetsWinterFull), labeller = label_parsed) +
+  ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
   theme_bw() +
@@
         panel.grid.major = element_blank(),
+        strip.placement = "outside",
+        strip.switch.pad.grid = unit(1, "cm"),
         axis.text = element_text(size=14),
-        axis.title = element_text(size=18),
+        axis.title = element_text(size=14),
         strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        axis.title.y = element_text(margin=margin(r=10)),
+        strip.text = element_text(size=18),
+        axis.title.y = element_text(vjust = -15),
         axis.title.x = element_text(margin=margin(t=10)),
@@
   labs(y = "Latitude", x = "Longitude") +
-  #ggh4x::facet_nested(cols = vars(facetsTropicOMZ), labeller = label_parsed) +
+  ggh4x::facet_nested(rows = vars(facetsPresent), labeller = label_parsed, switch = "y") +
   theme_bw() +
@@
   labs(y = "Latitude", x = "Longitude") +
-  #ggh4x::facet_nested(cols = vars(facetsSpringOMZ), labeller = label_parsed) +
+  ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
   theme_bw() +
@@
   labs(y = "Latitude", x = "Longitude") +
-  #ggh4x::facet_nested(cols = vars(facetsSummerOMZ), labeller = label_parsed) +
+  ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
   theme_bw() +
@@
   labs(y = "Latitude", x = "Longitude") +
-  #ggh4x::facet_nested(cols = vars(facetsWinterOMZ), labeller = label_parsed) +
+  ggh4x::facet_nested(rows =  vars(facetsFuture), labeller = label_parsed, switch = "y") +
   theme_bw() +
@@
 
-```{r, warning = FALSE, fig.height = 16, fig.width = 22}
+```{r, warning = FALSE, fig.height = 16, fig.width = 24}
 library(ggpubr)
@@
 ```{r save plot}
-ggsave(file = file.path(FigPath, paste("MapComboPro_2",".png",sep = "")), height=16, width= 22,  dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(FigPath, paste("MapComboPro",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
 ```

### 2024-05-29 Code/Import_MapMireillePro.Rmd
small edits
Fixed errors

@@
 
-data_textWinterFull <- data.frame(label = c('Season:~Summer~~~~~~~~Daylight:~8~h~~~~~~~~Oxygen:~Full'))
+data_textWinterFull <- data.frame(label = c('Season:~Winter~~~~~~~~Daylight:~8~h~~~~~~~~Oxygen:~Full'))
 WinterFull<-ggplot() + 
@@
 
-data_textWinterOMZ <- data.frame(label = c('Season:~Summer~~~~~~~~Daylight:~8~h~~~~~~~~Oxygen:~OMZ'))
+data_textWinterOMZ <- data.frame(label = c('Season:~Winter~~~~~~~~Daylight:~8~h~~~~~~~~Oxygen:~OMZ'))
 WinterOMZ<-ggplot() + 
@@
 
-# ggplot() +
-#   geom_ellipse(aes(x0 = 550, y0 = 150, a = 150, b = 50, angle = pi / 4)) +
-#   coord_fixed()
+ggplot() +
+  geom_ellipse(aes(x0 = 550, y0 = 150, a = 150, b = 50, angle = pi / 4)) +
+  coord_fixed()
 ```

### 2024-05-30 Code/Import_MapMireillePro.Rmd
Fighting with new map - not finish yet

--- 2024-05-29 Code/Import_MapMireillePro.Rmd
@@
 world_coordinates <- map_data("world") 
-world_coordinates$facetsTropicFull <- 'Season:~All~year~~Hours~of~daylight:~12~~Oxygen:~Full'
-world_coordinates$facetsSpringFull <- 'Season:~Spring/Fall~~~~~~~~~~~~~~Oxygen:~Full'
-world_coordinates$facetsSummerFull <- 'Season:~Summer~~~~~~~~~~~~~~Oxygen:~Full'
-world_coordinates$facetsWinterFull <- 'Season:~Winter~~~~~~~~~~~~~~Oxygen:~Full'
+world_coordinates$facetsTropicFull <- 'All~year~~~~~~~~~~~~~~Oxygen:~Full'
+world_coordinates$facetsSpringFull <- '21.03/21.09~~~~~~~~~~~~~~Oxygen:~Full'
+world_coordinates$facetsSummerFull <- '21.06~~~~~~~~~~~~~~Oxygen:~Full'
+world_coordinates$facetsWinterFull <- '21.12~~~~~~~~~~~~~~Oxygen:~Full'
 
-world_coordinates$facetsTropicOMZ <- 'Season:~All~year~~~~~~~~~~~~~~Oxygen:~OMZ'
-world_coordinates$facetsSpringOMZ <- 'Season:~Spring/Fall~~~~~~~~~~~~~~Oxygen:~OMZ'
-world_coordinates$facetsSummerOMZ <- 'Season:~Summer~~~~~~~~~~~~~~Oxygen:~OMZ'
-world_coordinates$facetsWinterOMZ <- 'Season:~Winter~~~~~~~~~~~~~~Oxygen:~OMZ'
+world_coordinates$facetsTropicOMZ <- 'All~year~~~~~~~~~~~~~~Oxygen:~OMZ'
+world_coordinates$facetsSpringOMZ <- '21.03/21.09~~~~~~~~~~~~~~Oxygen:~OMZ'
+world_coordinates$facetsSummerOMZ <- '21.06~~~~~~~~~~~~~~Oxygen:~OMZ'
+world_coordinates$facetsWinterOMZ <- '21.12~~~~~~~~~~~~~~Oxygen:~OMZ'
 
+world_coordinates$facetsPresent <- 'Present'
+world_coordinates$facetsFuture <- 'Future~scenario'
 ```
@@
 
-data_textTropicFull <- data.frame(label = c('Season:~All~year~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~Full'))
+data_textTropicFull <- data.frame(label = c('All~year'))
+data_textTropicFull2 <- data.frame(label = c('12~h'))
+data_textTropicFull3 <- data.frame(label = c('11/7~h'))
+
 TropicFull<-ggplot() + 
-  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkgreen", linetype = "dashed", alpha=1, size = 1) +
   geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
   geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
@@
   geom_text(data=data_textTropicFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
+  geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
@@
 
-data_textSpringFull <- data.frame(label = c('Season:~Spring/Fall~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~Full'))
+data_textWinterFull <- data.frame(label = c('21.12'))
+data_textWinterFull2 <- data.frame(label = c('8~h'))
+data_textWinterFull3 <- data.frame(label = c('16~h'))
+data_textWinterFull4 <- data.frame(label = c('8/4~h'))
+data_textWinterFull5 <- data.frame(label = c('15/10~h'))
+
+WinterFull<-ggplot() + 
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+    geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
+  geom_text(data=data_textWinterFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textWinterFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textWinterFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textWinterFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textWinterFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+  coord_cartesian(ylim = c(-90, 120)) +
+  labs(y = "Latitude", x = "Longitude") +
+  ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        strip.placement = "outside",
+        strip.switch.pad.grid = unit(1, "cm"),
+        axis.text = element_text(size=14),
+        axis.title = element_text(size=14),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=18),
+        axis.title.y = element_text(vjust = -15),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14))
+WinterFull
+
+data_textSpringFull <- data.frame(label = c('21.03/21.09'))
+data_textSpringFull2 <- data.frame(label = c('12~h'))
+data_textSpringFull3 <- data.frame(label = c('12~h'))
+
+data_textSpringFull4 <- data.frame(label = c('11/6~h'))
+data_textSpringFull5 <- data.frame(label = c('11/6~h'))
+
 SpringFull<-ggplot() + 
@@
   geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
   geom_text(data=data_textSpringFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textSpringFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textSpringFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textSpringFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textSpringFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+
   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
@@
 
-data_textSummerFull <- data.frame(label = c('Season:~Summer~~~~~~~~Daylight:~16~h~~~~~~~~Oxygen:~Full'))
+data_textSummerFull <- data.frame(label = c('21.06'))
+data_textSummerFull2 <- data.frame(label = c('16~h'))
+data_textSummerFull3 <- data.frame(label = c('8~h'))
+data_textSummerFull4 <- data.frame(label = c('15/10~h'))
+data_textSummerFull5 <- data.frame(label = c('8/4~h'))
 SummerFull<-ggplot() + 
@@
   geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+    geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
   geom_text(data=data_textSummerFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textSummerFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textSummerFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textSummerFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textSummerFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
+      geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
+      geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+
   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
@@
 
-data_textWinterFull <- data.frame(label = c('Season:~Summer~~~~~~~~Daylight:~8~h~~~~~~~~Oxygen:~Full'))
-WinterFull<-ggplot() + 
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-  geom_text(data=data_textWinterFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
-  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
-  coord_cartesian(ylim = c(-90, 120)) +
-  labs(y = "Latitude", x = "Longitude") +
-  #ggh4x::facet_nested(cols = vars(facetsWinterFull), labeller = label_parsed) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_text(size=14),
-        axis.title = element_text(size=18),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        axis.title.y = element_text(margin=margin(r=10)),
-        axis.title.x = element_text(margin=margin(t=10)),
-        #axis.title.x = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14))
-WinterFull
-
 ```
@@
 ```{r, warning = FALSE, fig.height = 12, fig.width = 6}
-Full<- (TropicFull/SpringFull/SummerFull/WinterFull)
+Full<- (TropicFull/WinterFull/SpringFull/SummerFull)
 Full                         
@@
 
-```{r create map omz plot, fig.height = 4, fig.width = 6, warning = FALSE}
-data_textA <- data.frame(label = c('A'))
+https://sape.inf.usi.ch/quick-reference/ggplot2/geom_polygon
 
-d=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(35), y2=c(55))
-d2=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-35), y2=c(-55))
-d3=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-Inf), y2=c(Inf))
-d4=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-15), y2=c(15))
-
-data_textTropicOMZ <- data.frame(label = c('Season:~All~year~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~OMZ'))
-TropicOMZ<-ggplot() + 
-  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkgreen", linetype = "dashed", alpha=0.9, size = 1) +
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
-  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-
-  geom_text(data=data_textTropicOMZ, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
-  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
-  coord_cartesian(ylim = c(-90, 120)) +
-  labs(y = "Latitude", x = "Longitude") +
-  #ggh4x::facet_nested(cols = vars(facetsTropicOMZ), labeller = label_parsed) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_text(size=14),
-        axis.title = element_text(size=18),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        axis.title.y = element_text(margin=margin(r=10)),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14))
-TropicOMZ
-
-data_textSpringOMZ <- data.frame(label = c('Season:~Spring/Fall~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~OMZ'))
-SpringOMZ<-ggplot() + 
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-  geom_text(data=data_textSpringOMZ, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
-  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
-  coord_cartesian(ylim = c(-90, 120)) +
-  labs(y = "Latitude", x = "Longitude") +
-  #ggh4x::facet_nested(cols = vars(facetsSpringOMZ), labeller = label_parsed) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_text(size=14),
-        axis.title = element_text(size=18),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        axis.title.y = element_text(margin=margin(r=10)),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14))
-SpringOMZ
-
-data_textSummerOMZ <- data.frame(label = c('Season:~Summer~~~~~~~~Daylight:~16~h~~~~~~~~Oxygen:~OMZ'))
-SummerOMZ<-ggplot() + 
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-  geom_text(data=data_textSummerOMZ, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
-  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
-  coord_cartesian(ylim = c(-90, 120)) +
-  labs(y = "Latitude", x = "Longitude") +
-  #ggh4x::facet_nested(cols = vars(facetsSummerOMZ), labeller = label_parsed) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_text(size=14),
-        axis.title = element_text(size=18),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        axis.title.y = element_text(margin=margin(r=10)),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14))
-SummerOMZ
-
-data_textWinterOMZ <- data.frame(label = c('Season:~Summer~~~~~~~~Daylight:~8~h~~~~~~~~Oxygen:~OMZ'))
-WinterOMZ<-ggplot() + 
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-  geom_text(data=data_textWinterOMZ, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
-  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
-  coord_cartesian(ylim = c(-90, 120)) +
-  labs(y = "Latitude", x = "Longitude") +
-  #ggh4x::facet_nested(cols = vars(facetsWinterOMZ), labeller = label_parsed) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_text(size=14),
-        axis.title = element_text(size=18),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        axis.title.y = element_text(margin=margin(r=10)),
-        axis.title.x = element_text(margin=margin(t=10)),
-        #axis.title.x = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14))
-WinterOMZ
-
+```{r, warning = FALSE, fig.height = 12, fig.width = 6}
+# OMZRainbow<- (TropicOMZRainbow/SpringOMZRainbow/SummerOMZRainbow/WinterOMZRainbow)
+# OMZRainbow                         
 ```
 
-```{r, warning = FALSE, fig.height = 12, fig.width = 6}
-OMZ<- (TropicOMZ/SpringOMZ/SummerOMZ/WinterOMZ)
-OMZ                         
+```{r, warning = FALSE, fig.height = 16, fig.width = 22}
+# MapCombo<-((TropicFull+TropicFullRainbow)+(TropicOMZ+TropicOMZRainbow))/((SpringFull+SpringFullRainbow)+(SpringOMZ+SpringOMZRainbow))/((SummerFull+SummerFullRainbow)+(SummerOMZ+SummerOMZRainbow))/((WinterFull+WinterFullRainbow)+(WinterOMZ+WinterOMZRainbow))
+# MapCombo                          
 ```
@@
 
-data_textTropicFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clade~HLI'))
-data_textTropicFullRainbowDeep <- data.frame(label = c('Deep~(30~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+data_text1 <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clade~HLI'))
+data_text2 <- data.frame(label = c('Near~surface~(180~µE~","~11~h):~Clade~HLI'))
+data_text3 <- data.frame(label = c('Near~surface~(180~µE~","~15~h):~Clade~HLI'))
+
+data_text4 <- data.frame(label = c('Deep~(30~µE~","~4~h):~Clade~LLIV'))
+data_text5 <- data.frame(label = c('Deep~(30~µE~","~6~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+data_text6 <- data.frame(label = c('Deep~(30~µE~","~7~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+data_text7 <- data.frame(label = c('Deep~(30~µE~","~10~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-TropicFullRainbow<-ggplot() +
+RainbowComboFull<-ggplot() +
   stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
@@
   coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textTropicFullRainbowSurface, aes(x=510, y=215, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_textTropicFullRainbowDeep, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_text1, aes(x=510, y=215, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_text2, aes(x=510, y=210, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_text3, aes(x=510, y=205, label=label), size=4.5, parse=TRUE) +
+
+  geom_text(data=data_text4, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_text5, aes(x=530, y=85, label=label), size=4.5, parse=TRUE) + 
+  geom_text(data=data_text6, aes(x=530, y=80, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_text7, aes(x=530, y=75, label=label), size=4.5, parse=TRUE) +
   theme_bw() +
@@
         legend.text = element_text(size=14))
-TropicFullRainbow
+RainbowComboFull
 
-data_textSpringFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clade~HLI'))
-data_textSpringFullRainbowDeep <- data.frame(label = c('Deep~(30~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+```
+```{r}
+world_coordinatesRainbow <- map_data("world")
+world_coordinatesRainbow$nm <- c(400, 700)
+
+data_text1d <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+data_text2d <- data.frame(label = c('Near~surface~(180~µE~","~11~h):~Clades~HLI~","~LLIV'))
+data_text3d <- data.frame(label = c('Near~surface~(180~µE~","~15~h):~Clades~HLI~","~LLIV'))
+
+data_text4d <- data.frame(label = c('Deep~(30~µE~","~4~h):~Clades~LLII/III~","~LLIV'))
+data_text5d <- data.frame(label = c('Deep~(30~µE~","~6~h):~Clades~LLII/III~","~LLIV'))
+data_text6d <- data.frame(label = c('Deep~(30~µE~","~7~h):~Clades~LLII/III~","~LLIV'))
+data_text7d <- data.frame(label = c('Deep~(30~µE~","~10~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-SpringFullRainbow<-ggplot() +
+RainbowComboOMZ<-ggplot() +
   stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
@@
   coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textSpringFullRainbowSurface, aes(x=510, y=215, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_textSpringFullRainbowDeep, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_text1d, aes(x=510, y=215, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_text2d, aes(x=510, y=210, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_text3d, aes(x=510, y=205, label=label), size=4.5, parse=TRUE) +
+
+  geom_text(data=data_text4d, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_text5d, aes(x=530, y=85, label=label), size=4.5, parse=TRUE) + 
+  geom_text(data=data_text6d, aes(x=530, y=80, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_text7d, aes(x=530, y=75, label=label), size=4.5, parse=TRUE) +
   theme_bw() +
@@
         legend.text = element_text(size=14))
-SpringFullRainbow
+RainbowComboOMZ
 
-data_textSummerFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE~","~12~h):~Clade~HLI'))
-data_textSummerFullRainbowDeep <- data.frame(label = c('Deep~(30~µE~","~12~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-SummerFullRainbow<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textSummerFullRainbowSurface, aes(x=510, y=215, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_textSummerFullRainbowDeep, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_blank(),
-        axis.title = element_blank(),
-        axis.ticks = element_blank(),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.text = element_text(size=14))
-SummerFullRainbow
-
-data_textWinterFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE~","~4~h)'))
-data_textWinterFullRainbowDeep <- data.frame(label = c('Deep~(30~µE~","~4~h):~Clade~LLIV'))
-d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-WinterFullRainbow<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textWinterFullRainbowSurface, aes(x=480, y=215, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_textWinterFullRainbowDeep, aes(x=485, y=90, label=label), size=4.5, parse=TRUE) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_blank(),
-        axis.title = element_blank(),
-        axis.ticks = element_blank(),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.text = element_text(size=14))
-WinterFullRainbow
-```
-```{r, warning = FALSE, fig.height = 12, fig.width = 6}
-FullRainbow<- (TropicFullRainbow/SpringFullRainbow/SummerFullRainbow/WinterFullRainbow)
-FullRainbow                         
 ```
 
-```{r}
-data_textTropicOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-data_textTropicOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-TropicOMZRainbow<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textTropicOMZRainbowSurface, aes(x=555, y=215, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_textTropicOMZRainbowDeep, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_blank(),
-        axis.title = element_blank(),
-        axis.ticks = element_blank(),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.text = element_text(size=14))
-TropicOMZRainbow
+```{r, warning = FALSE, fig.height = 16, fig.width = 24}
+library(ggpubr)
+ss<-ggarrange(RainbowComboFull, RainbowComboOMZ,
+          ncol = 1, nrow = 2)
+ss
 
-data_textSpringOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-data_textSpringOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-SpringOMZRainbow<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textSpringOMZRainbowSurface, aes(x=555, y=215, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_textSpringOMZRainbowDeep, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_blank(),
-        axis.title = element_blank(),
-        axis.ticks = element_blank(),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.text = element_text(size=14))
-SpringOMZRainbow
+zzz<- ggarrange(TropicFull, WinterFull, SpringFull, SummerFull, 
+          ncol = 1, nrow = 4)
+zzz
 
-data_textSummerOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE~","~12~h):~Clades~HLI~","~LLIV'))
-data_textSummerOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE~","~12~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-SummerOMZRainbow<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textSummerOMZRainbowSurface, aes(x=535, y=215, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_textSummerOMZRainbowDeep, aes(x=535, y=90, label=label), size=4.5, parse=TRUE) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_blank(),
-        axis.title = element_blank(),
-        axis.ticks = element_blank(),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.text = element_text(size=14))
-SummerOMZRainbow
+ggarrange(zzz, ss,
+          ncol = 2, nrow = 1)
 
-data_textWinterOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE~","~4~h):~Clade~LLIV'))
-data_textWinterOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE~","~4~h):~Clades~LLII/III~","~LLIV'))
-d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-WinterOMZRainbow<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_textWinterOMZRainbowSurface, aes(x=510, y=215, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_textWinterOMZRainbowDeep, aes(x=510, y=90, label=label), size=4.5, parse=TRUE) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_blank(),
-        axis.title = element_blank(),
-        axis.ticks = element_blank(),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.text = element_text(size=14))
-WinterOMZRainbow
-```
-```{r, warning = FALSE, fig.height = 12, fig.width = 6}
-OMZRainbow<- (TropicOMZRainbow/SpringOMZRainbow/SummerOMZRainbow/WinterOMZRainbow)
-OMZRainbow                         
-```
-
-```{r, warning = FALSE, fig.height = 16, fig.width = 22}
-# MapCombo<-((TropicFull+TropicFullRainbow)+(TropicOMZ+TropicOMZRainbow))/((SpringFull+SpringFullRainbow)+(SpringOMZ+SpringOMZRainbow))/((SummerFull+SummerFullRainbow)+(SummerOMZ+SummerOMZRainbow))/((WinterFull+WinterFullRainbow)+(WinterOMZ+WinterOMZRainbow))
-# MapCombo                          
-```
-
-```{r, warning = FALSE, fig.height = 16, fig.width = 22}
-MapCombo1<-((TropicFull+TropicFullRainbow))/((SpringFull+SpringFullRainbow))/((SummerFull+SummerFullRainbow))/((WinterFull+WinterFullRainbow))
-MapCombo1                         
-```
-
-```{r, warning = FALSE, fig.height = 16, fig.width = 22}
-MapCombo2<-((TropicOMZ+TropicOMZRainbow))/((SpringOMZ+SpringOMZRainbow))/((SummerOMZ+SummerOMZRainbow))/((WinterOMZ+WinterOMZRainbow))
-MapCombo2                          
-```
-
-```{r, warning = FALSE, fig.height = 16, fig.width = 22}
-library(ggpubr)
-ggarrange(MapCombo1, MapCombo2, 
-          ncol = 2, nrow = 1)
 ```
@@
 ```{r save plot}
-ggsave(file = file.path(FigPath, paste("MapComboPro_2",".png",sep = "")), height=16, width= 22,  dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(FigPath, paste("MapComboPro_30",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
 ```
+
+------------------------------------------------------------------------------------------------------------------------
 

### 2024-05-30 Output/PLOSRound2/ResponsetoReviewers.txt
more edits

@@
 We briefly motivated the inclusion of the red light growth trials, as mechanistically informative, at line 706:
-" As mentioned, growth trials under red light, although not representative of *Prochlorococcus* niches, are mechanistically informative [@murphyPhotoinactivationPhotosystemII2017] regarding photoinactivation of PSII."
+"As mentioned, growth trials under red light, although not representative of *Prochlorococcus* niches, are mechanistically informative [@murphyPhotoinactivationPhotosystemII2017] regarding photoinactivation of PSII."
 
@@
 Thank you for the comment.
-We added a table YY of potential strain growth in temperate seasonal and depth niches, in future temperate warmed oceans.
+
+XXXX  We added a new figure of potential strain growth in temperate seasonal and depth niches, in future temperate warmed oceans.
 The GAM model panels in figures XYZ show 'zones of exclusion' from light level, photoperiods, and oxygen regimes, as unshaded white areas where no growth is predicted.
-We indeed contemplated attempting global predicted distribution maps, but the interacting complexities of season, depth, changing extents of OMZ and extrapolation from culture growth, render it beyond the scope of this study.
+We indeed contemplated attempting global predicted distribution maps, but the interacting complexities of season, depth, changing extents of OMZ and extrapolation from culture growth, render it beyond the scope of this study.XXXX
 
@@
 
-Thank you.
-The revised manuscript now reads: "The absence of genes encoding deoxyribodipyrimidine photolyase and DNA ligase (ATP) in P.
+We agree.
+The added the following in the revised manuscript: "In this study we show that *P.
+marinus* SS120 and MIT9313 can tolerate light levels representative of the near ocean surface when the [O~2~] is 25 µM, however our growth rate experiments did not include wavebands in the UV range, we therefore do not know how the absence of deoxyribodipyrimidine photolyase under low [O~2] will impact the growth rates of *P.
+marinus* SS120 and MIT9313 when exposed to UV light."
+Lines: XXX
+To address the second part of your comment, the revised sentence now reads: "The absence of genes encoding deoxyribodipyrimidine photolyase and DNA ligase (ATP) in P.
 marinus MIT9313 and P.
@@
 Line: XXX
-XXXXX Mireille to address the wording pertaining to photolyase. We did not imply that photolyase was responsible for the results we found in lab but I will confirm this. XXXXXXXXXX
 
@@
 don?t think this enzyme is properly a DNA repair enzyme.
-XXX Naaman to removeXXXXX
+
+Thank you for brining this to our attention, we have removed phosphoglycolate phosphatase from the figure as it is indeed not directly involved in DNA repair but in clearing DNA damage repair products.
+Upon revisiting the interpretation of this figure, we have edited the text: "As expected, *P. marinus* NATL2A possesses the largest,
+most complete suite of genes encoding DNA repair enzymes, followed by *P. marinus* MIT9313."
+Lines: XXX
 
@@
 
-XXXX In response to reviewer 1 and reviewer 2 we have combined the growth rate figure with the GAM model for each strain to faciliate comparisons.
+In response to reviewer 1 and reviewer 2 we have combined the growth rate figure with the GAM model for each strain to faciliate comparisons. 
 We have edited the abstract, results and discussion to better convey the motivations and findings of the study. 

### 2024-05-30 Code/Import_MapMireillePro.Rmd

@@
 FigPath <- file.path("..", "Output", "Figures")
-#FigRdsPath <- file.path("..", "Output", "FiguresRds")
-#TableRdsPath <- file.path("..", "Output", "TablesRDS")
 ```
@@
 world_coordinates <- map_data("world")
-world_coordinates$facetsTropicFull <- 'All~year~~~~~~~~~~~~~~Oxygen:~Full'
-world_coordinates$facetsSpringFull <- '21.03/21.09~~~~~~~~~~~~~~Oxygen:~Full'
-world_coordinates$facetsSummerFull <- '21.06~~~~~~~~~~~~~~Oxygen:~Full'
-world_coordinates$facetsWinterFull <- '21.12~~~~~~~~~~~~~~Oxygen:~Full'
-
-world_coordinates$facetsTropicOMZ <- 'All~year~~~~~~~~~~~~~~Oxygen:~OMZ'
-world_coordinates$facetsSpringOMZ <- '21.03/21.09~~~~~~~~~~~~~~Oxygen:~OMZ'
-world_coordinates$facetsSummerOMZ <- '21.06~~~~~~~~~~~~~~Oxygen:~OMZ'
-world_coordinates$facetsWinterOMZ <- '21.12~~~~~~~~~~~~~~Oxygen:~OMZ'
 
@@
 world_coordinates$facetsFuture <- 'Future~scenario'
+
+data_textA <- data.frame(label = c('A'))
+data_textB <- data.frame(label = c('B'))
+data_textC <- data.frame(label = c('C'))
+data_textD <- data.frame(label = c('D'))
 ```
@@
 ```{r create GrowthCurve plot, fig.height = 4, fig.width = 6, warning = FALSE}
-data_textA <- data.frame(label = c('A'))
 
@@
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-
-  geom_text(data=data_textTropicFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
+  geom_text(data=data_textTropicFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
   geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
@@
 
-data_textWinterFull <- data.frame(label = c('21.12'))
-data_textWinterFull2 <- data.frame(label = c('8~h'))
+data_textWinterFull <- data.frame(label = c('Winter~or~summer~solstice'))
+data_textWinterFull2 <- data.frame(label = c('9~h'))
 data_textWinterFull3 <- data.frame(label = c('16~h'))
@@
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-  geom_text(data=data_textWinterFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textB, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
+    geom_text(data=data_textWinterFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
     geom_text(data=data_textWinterFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
@@
 
-data_textSpringFull <- data.frame(label = c('21.03/21.09'))
+data_textSpringFull <- data.frame(label = c('Vernal~equinox'))
 data_textSpringFull2 <- data.frame(label = c('12~h'))
@@
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-  geom_text(data=data_textSpringFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textC, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
+    geom_text(data=data_textSpringFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
     geom_text(data=data_textSpringFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
@@
 
-data_textSummerFull <- data.frame(label = c('21.06'))
+data_textSummerFull <- data.frame(label = c('Summer~or~winter~solstice'))
 data_textSummerFull2 <- data.frame(label = c('16~h'))
-data_textSummerFull3 <- data.frame(label = c('8~h'))
+data_textSummerFull3 <- data.frame(label = c('9~h'))
 data_textSummerFull4 <- data.frame(label = c('15/10~h'))
@@
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-  geom_text(data=data_textSummerFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textD, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
+    geom_text(data=data_textSummerFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
     geom_text(data=data_textSummerFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
@@
       geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
-
   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
@@
 https://sape.inf.usi.ch/quick-reference/ggplot2/geom_polygon
+
 ```{r}
+#FUll
 world_coordinatesRainbow <- map_data("world")
@@
 
+data_textFull <- data.frame(label = c('Oxygen:~Full'))
+data_textOMZ <- data.frame(label = c('Oxygen:~OMZ'))
+```
+
+```{r}
+#Full
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-RainbowComboFull<-ggplot() +
+RainbowTropicFull<-ggplot() +
   stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
@@
   scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_text1, aes(x=510, y=215, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_text2, aes(x=510, y=210, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_text3, aes(x=510, y=205, label=label), size=4.5, parse=TRUE) +
-
-  geom_text(data=data_text4, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_text5, aes(x=530, y=85, label=label), size=4.5, parse=TRUE) + 
-  geom_text(data=data_text6, aes(x=530, y=80, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_text7, aes(x=530, y=75, label=label), size=4.5, parse=TRUE) +
+  coord_cartesian(ylim = c(70, 230)) +
+  geom_text(data=data_textFull, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_text2, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text6, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
   theme_bw() +
@@
         legend.text = element_text(size=14))
-RainbowComboFull
+RainbowTropicFull
+
+RainbowWinterFull<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+  scale_fill_identity() +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
+  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+  coord_cartesian(ylim = c(70, 230)) +
+    geom_text(data=data_textFull, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_text1, aes(x=400, y=230, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text2, aes(x=400, y=220, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text3, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text4, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text6, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text7, aes(x=400, y=70, label=label, hjust=0), size=4.5, parse=TRUE) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_blank(),
+        axis.title = element_blank(),
+        axis.ticks = element_blank(),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.text = element_text(size=14))
+RainbowWinterFull
+
+RainbowSpringFull<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+  scale_fill_identity() +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
+  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+  coord_cartesian(ylim = c(70, 230)) +
+    geom_text(data=data_textFull, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_text2, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text5, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) + 
+  geom_text(data=data_text6, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_blank(),
+        axis.title = element_blank(),
+        axis.ticks = element_blank(),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.text = element_text(size=14))
+RainbowSpringFull
+
+RainbowSummerFull<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+  scale_fill_identity() +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
+  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+  coord_cartesian(ylim = c(70, 230)) +
+    geom_text(data=data_textFull, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_text1, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text2, aes(x=400, y=220, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text3, aes(x=400, y=230, label=label, hjust=0), size=4.5, parse=TRUE) +
+
+  geom_text(data=data_text4, aes(x=400, y=70, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text6, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text7, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_blank(),
+        axis.title = element_blank(),
+        axis.ticks = element_blank(),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.text = element_text(size=14))
+RainbowSummerFull
 
 ```
+
 ```{r}
+#Full combo
+# world_coordinatesRainbow <- map_data("world")
+# world_coordinatesRainbow$nm <- c(400, 700)
+# 
+# data_text1 <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clade~HLI'))
+# data_text2 <- data.frame(label = c('Near~surface~(180~µE~","~11~h):~Clade~HLI'))
+# data_text3 <- data.frame(label = c('Near~surface~(180~µE~","~15~h):~Clade~HLI'))
+# 
+# data_text4 <- data.frame(label = c('Deep~(30~µE~","~4~h):~Clade~LLIV'))
+# data_text5 <- data.frame(label = c('Deep~(30~µE~","~6~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+# data_text6 <- data.frame(label = c('Deep~(30~µE~","~7~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+# data_text7 <- data.frame(label = c('Deep~(30~µE~","~10~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+# 
+# 
+# d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
+# RainbowComboFull<-ggplot() +
+#   stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+#   scale_fill_identity() +
+#   geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+#   geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+#   coord_fixed() +
+#   scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+#   coord_cartesian(ylim = c(80, 220)) +
+#   geom_text(data=data_text1, aes(x=510, y=215, label=label), size=4.5, parse=TRUE) +
+#   geom_text(data=data_text2, aes(x=510, y=210, label=label), size=4.5, parse=TRUE) +
+#   geom_text(data=data_text3, aes(x=510, y=205, label=label), size=4.5, parse=TRUE) +
+#   
+#   geom_text(data=data_text4, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
+#   geom_text(data=data_text5, aes(x=530, y=85, label=label), size=4.5, parse=TRUE) + 
+#   geom_text(data=data_text6, aes(x=530, y=80, label=label), size=4.5, parse=TRUE) +
+#   geom_text(data=data_text7, aes(x=530, y=75, label=label), size=4.5, parse=TRUE) +
+#   theme_bw() +
+#   theme(panel.grid.minor = element_blank(),
+#         panel.grid.major = element_blank(),
+#         axis.text = element_blank(),
+#         axis.title = element_blank(),
+#         axis.ticks = element_blank(),
+#         strip.background = element_rect(fill="white"),
+#         strip.text = element_text(size=14),
+#         legend.background = element_rect(fill="transparent"),
+#         legend.position = c(0.12,0.76),
+#         legend.text = element_text(size=14))
+# RainbowComboFull
+
+```
+
+```{r}
+#OMZ
 world_coordinatesRainbow <- map_data("world")
@@
 data_text7d <- data.frame(label = c('Deep~(30~µE~","~10~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+```
 
+```{r}
+#OMZ
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-RainbowComboOMZ<-ggplot() +
+RainbowTropicOMZ<-ggplot() +
   stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
@@
   scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(80, 220)) +
-  geom_text(data=data_text1d, aes(x=510, y=215, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_text2d, aes(x=510, y=210, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_text3d, aes(x=510, y=205, label=label), size=4.5, parse=TRUE) +
-
-  geom_text(data=data_text4d, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_text5d, aes(x=530, y=85, label=label), size=4.5, parse=TRUE) + 
-  geom_text(data=data_text6d, aes(x=530, y=80, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_text7d, aes(x=530, y=75, label=label), size=4.5, parse=TRUE) +
+  coord_cartesian(ylim = c(70, 230)) +
+    geom_text(data=data_textOMZ, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_text2d, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text6d, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
   theme_bw() +
@@
         legend.text = element_text(size=14))
-RainbowComboOMZ
+RainbowTropicOMZ
+
+RainbowWinterOMZ<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+  scale_fill_identity() +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
+  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+  coord_cartesian(ylim = c(70, 230)) +
+      geom_text(data=data_textOMZ, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_text1d, aes(x=400, y=230, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text2d, aes(x=400, y=220, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text3d, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text4d, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text6d, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text7d, aes(x=400, y=70, label=label, hjust=0), size=4.5, parse=TRUE) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_blank(),
+        axis.title = element_blank(),
+        axis.ticks = element_blank(),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.text = element_text(size=14))
+RainbowWinterOMZ
+
+RainbowSpringOMZ<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+  scale_fill_identity() +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
+  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+  coord_cartesian(ylim = c(70, 230)) +
+      geom_text(data=data_textOMZ, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_text2d, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text5d, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) + 
+  geom_text(data=data_text6d, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_blank(),
+        axis.title = element_blank(),
+        axis.ticks = element_blank(),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.text = element_text(size=14))
+RainbowSpringOMZ
+
+RainbowSummerOMZ<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+  scale_fill_identity() +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
+  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+  coord_cartesian(ylim = c(70, 230)) +
+      geom_text(data=data_textOMZ, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_text1d, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text2d, aes(x=400, y=220, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text3d, aes(x=400, y=230, label=label, hjust=0), size=4.5, parse=TRUE) +
+
+  geom_text(data=data_text4d, aes(x=400, y=70, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text6d, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text7d, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_blank(),
+        axis.title = element_blank(),
+        axis.ticks = element_blank(),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=14),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.text = element_text(size=14))
+RainbowSummerOMZ
 
@@
 
-```{r, warning = FALSE, fig.height = 16, fig.width = 24}
-library(ggpubr)
-ss<-ggarrange(RainbowComboFull, RainbowComboOMZ,
-          ncol = 1, nrow = 2)
-ss
-
-zzz<- ggarrange(TropicFull, WinterFull, SpringFull, SummerFull, 
-          ncol = 1, nrow = 4)
-zzz
-
-ggarrange(zzz, ss,
-          ncol = 2, nrow = 1)
+```{r}
+#OMZ combo
+# world_coordinatesRainbow <- map_data("world")
+# world_coordinatesRainbow$nm <- c(400, 700)
+# 
+# data_text1d <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+# data_text2d <- data.frame(label = c('Near~surface~(180~µE~","~11~h):~Clades~HLI~","~LLIV'))
+# data_text3d <- data.frame(label = c('Near~surface~(180~µE~","~15~h):~Clades~HLI~","~LLIV'))
+# 
+# data_text4d <- data.frame(label = c('Deep~(30~µE~","~4~h):~Clades~LLII/III~","~LLIV'))
+# data_text5d <- data.frame(label = c('Deep~(30~µE~","~6~h):~Clades~LLII/III~","~LLIV'))
+# data_text6d <- data.frame(label = c('Deep~(30~µE~","~7~h):~Clades~LLII/III~","~LLIV'))
+# data_text7d <- data.frame(label = c('Deep~(30~µE~","~10~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+# 
+# 
+# d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
+# RainbowComboOMZ<-ggplot() +
+#   stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+#   scale_fill_identity() +
+#   geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+#   geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+#   coord_fixed() +
+#   scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+#   coord_cartesian(ylim = c(80, 220)) +
+#   geom_text(data=data_text1d, aes(x=510, y=215, label=label), size=4.5, parse=TRUE) +
+#   geom_text(data=data_text2d, aes(x=510, y=210, label=label), size=4.5, parse=TRUE) +
+#   geom_text(data=data_text3d, aes(x=510, y=205, label=label), size=4.5, parse=TRUE) +
+#   
+#   geom_text(data=data_text4d, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
+#   geom_text(data=data_text5d, aes(x=530, y=85, label=label), size=4.5, parse=TRUE) + 
+#   geom_text(data=data_text6d, aes(x=530, y=80, label=label), size=4.5, parse=TRUE) +
+#   geom_text(data=data_text7d, aes(x=530, y=75, label=label), size=4.5, parse=TRUE) +
+#   theme_bw() +
+#   theme(panel.grid.minor = element_blank(),
+#         panel.grid.major = element_blank(),
+#         axis.text = element_blank(),
+#         axis.title = element_blank(),
+#         axis.ticks = element_blank(),
+#         strip.background = element_rect(fill="white"),
+#         strip.text = element_text(size=14),
+#         legend.background = element_rect(fill="transparent"),
+#         legend.position = c(0.12,0.76),
+#         legend.text = element_text(size=14))
+# RainbowComboOMZ
 
@@
 
+```{r, fig.height = 16, fig.width = 24}
+OMZRainbow<- (TropicFull+RainbowTropicFull+RainbowTropicOMZ)/(WinterFull+RainbowWinterFull+RainbowWinterOMZ)/(SpringFull+RainbowSpringFull+RainbowSpringOMZ)/(SummerFull+RainbowSummerFull+RainbowSummerOMZ)
+OMZRainbow
+```
 ```{r save plot}
-ggsave(file = file.path(FigPath, paste("MapComboPro_30",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(FigPath, paste("MapComboPro_yeah",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
 ```
-
-------------------------------------------------------------------------------------------------------------------------
 
@@
 # saveRDS(object = CultureCatalog, file = file.path("..", "Data", "ImportedData", "ImportedMetaData", "CultureCatalog.Rds"), compress = "xz")
+```
+
+------------------------------------------------------------------------------------------------------------------------
+
+# Create map
+https://www.geeksforgeeks.org/how-to-make-world-map-with-ggplot2-in-r/
+
+```{r}
+world_coordinates2 <- map_data("world") %>% 
+  filter(! long > 180)
+
+world_coordinates2$facetsA <- '(A)~~~~All~year'
+world_coordinates2$facetsB <- '(B)~~~~Winter~or~summer~solstice'
+world_coordinates2$facetsC <- '(C)~~~~Vernal~equinox'
+world_coordinates2$facetsD <- '(D)~~~~Summer~or~winter~solstice'
+
+world_coordinates2$facetsPresent <- 'Present'
+world_coordinates2$facetsFuture <- 'Future~scenario'
+
+# data_textA <- data.frame(label = c('A'))
+# data_textB <- data.frame(label = c('B'))
+# data_textC <- data.frame(label = c('C'))
+# data_textD <- data.frame(label = c('D'))
+```
+
+```{r create GrowthCurve plot, fig.height = 4, fig.width = 6, warning = FALSE}
+
+d=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(35), y2=c(55))
+d2=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-35), y2=c(-55))
+d3=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-Inf), y2=c(Inf))
+d4=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-15), y2=c(15))
+d5=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-40), y2=c(40))
+
+data_textTropicFull <- data.frame(label = c('All~year'))
+data_textTropicFull2 <- data.frame(label = c('12~h'))
+data_textTropicFull3 <- data.frame(label = c('11/7~h'))
+
+TropicFull<-ggplot() + 
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  #geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
+  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
+  # geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
+  # geom_text(data=data_textTropicFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
+  geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+  coord_cartesian(ylim = c(-90, 120)) +
+  labs(y = "Latitude", x = "Longitude") +
+  ggh4x::facet_nested(rows = vars(facetsPresent), cols = vars(facetsA), labeller = label_parsed, switch = "y") +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        strip.placement = "outside",
+        strip.switch.pad.grid = unit(0.5, "cm"),
+        axis.text = element_text(size=14),
+        axis.title = element_text(size=14),
+        strip.background = element_rect(fill="white"),
+        strip.text.x = element_text(size=18, hjust = 0),
+        strip.text.y = element_text(size=18),
+        axis.title.y = element_text(vjust = -15),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14)) +
+  coord_map("moll")  
+TropicFull
+
+data_textWinterFull <- data.frame(label = c('Winter~or~summer~solstice'))
+data_textWinterFull2 <- data.frame(label = c('9~h'))
+data_textWinterFull3 <- data.frame(label = c('16~h'))
+data_textWinterFull4 <- data.frame(label = c('8/4~h'))
+data_textWinterFull5 <- data.frame(label = c('15/10~h'))
+
+WinterFull<-ggplot() + 
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+    geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  #geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
+  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
+    # geom_text(data=data_textB, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
+    # geom_text(data=data_textWinterFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
+    geom_text(data=data_textWinterFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textWinterFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textWinterFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textWinterFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+  coord_cartesian(ylim = c(-90, 120)) +
+  labs(y = "Latitude", x = "Longitude") +
+  ggh4x::facet_nested(rows = vars(facetsFuture), cols = vars(facetsB), labeller = label_parsed, switch = "y") +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        strip.placement = "outside",
+        strip.switch.pad.grid = unit(0.5, "cm"),
+        axis.text = element_text(size=14),
+        axis.title = element_text(size=14),
+        strip.background = element_rect(fill="white"),
+        strip.text.x = element_text(size=18, hjust = 0),
+        strip.text.y = element_text(size=18),
+        axis.title.y = element_text(vjust = -15),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14)) +
+  coord_map("moll") 
+WinterFull
+
+data_textSpringFull <- data.frame(label = c('Vernal~equinox'))
+data_textSpringFull2 <- data.frame(label = c('12~h'))
+data_textSpringFull3 <- data.frame(label = c('12~h'))
+data_textSpringFull4 <- data.frame(label = c('11/6~h'))
+data_textSpringFull5 <- data.frame(label = c('11/6~h'))
+
+SpringFull<-ggplot() + 
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  #geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
+  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
+    # geom_text(data=data_textC, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
+    # geom_text(data=data_textSpringFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
+    geom_text(data=data_textSpringFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textSpringFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textSpringFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textSpringFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+  coord_cartesian(ylim = c(-90, 120)) +
+  labs(y = "Latitude", x = "Longitude") +
+  ggh4x::facet_nested(rows = vars(facetsFuture), cols = vars(facetsC), labeller = label_parsed, switch = "y") +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        strip.placement = "outside",
+        strip.switch.pad.grid = unit(0.5, "cm"),
+        axis.text = element_text(size=14),
+        axis.title = element_text(size=14),
+        strip.background = element_rect(fill="white"),
+        strip.text.x = element_text(size=18, hjust = 0),
+        strip.text.y = element_text(size=18),
+        axis.title.y = element_text(vjust = -15),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14)) +
+  coord_map("moll") 
+SpringFull
+
+data_textSummerFull <- data.frame(label = c('Summer~or~winter~solstice'))
+data_textSummerFull2 <- data.frame(label = c('16~h'))
+data_textSummerFull3 <- data.frame(label = c('9~h'))
+data_textSummerFull4 <- data.frame(label = c('15/10~h'))
+data_textSummerFull5 <- data.frame(label = c('8/4~h'))
+SummerFull<-ggplot() + 
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+    geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  #geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
+  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
+    # geom_text(data=data_textD, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
+    # geom_text(data=data_textSummerFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
+    geom_text(data=data_textSummerFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textSummerFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textSummerFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textSummerFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
+      geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
+      geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+  coord_cartesian(ylim = c(-90, 120)) +
+  labs(y = "Latitude", x = "Longitude") +
+  ggh4x::facet_nested(rows = vars(facetsFuture), cols = vars(facetsD), labeller = label_parsed, switch = "y") +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        strip.placement = "outside",
+        strip.switch.pad.grid = unit(0.5, "cm"),
+        axis.text = element_text(size=14),
+        axis.title = element_text(size=14),
+        strip.background = element_rect(fill="white"),
+        strip.text.x = element_text(size=18, hjust = 0),
+        strip.text.y = element_text(size=18),
+        axis.title.y = element_text(vjust = -15),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14)) +
+  coord_map("moll") 
+SummerFull
+
+```
+
+```{r}
+#FUll
+world_coordinatesRainbow <- map_data("world")
+world_coordinatesRainbow$nm <- c(400, 700)
+
+world_coordinatesRainbow$facetsFull <- 'Oxygen:~Full'
+world_coordinatesRainbow$facetsOMZ <- 'Oxygen:~OMZ'
+
+data_text1 <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clade~HLI'))
+data_text2 <- data.frame(label = c('Near~surface~(180~µE~","~11~h):~Clade~HLI'))
+data_text3 <- data.frame(label = c('Near~surface~(180~µE~","~15~h):~Clade~HLI'))
+
+data_text4 <- data.frame(label = c('Deep~(30~µE~","~4~h):~Clade~LLIV'))
+data_text5 <- data.frame(label = c('Deep~(30~µE~","~6~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+data_text6 <- data.frame(label = c('Deep~(30~µE~","~7~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+data_text7 <- data.frame(label = c('Deep~(30~µE~","~10~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+
+data_textFull <- data.frame(label = c('Oxygen:~Full'))
+data_textOMZ <- data.frame(label = c('Oxygen:~OMZ'))
+```
+
+```{r}
+#Full
+d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
+RainbowTropicFull<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+  scale_fill_identity() +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
+  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+  coord_cartesian(ylim = c(70, 230)) +
+  #geom_text(data=data_textFull, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_text2, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text6, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
+  ggh4x::facet_nested(cols = vars(facetsFull), labeller = label_parsed) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        strip.placement = "outside",
+        strip.switch.pad.grid = unit(0.5, "cm"),
+        strip.background = element_rect(fill="white"),
+        strip.text.x = element_text(size=18, hjust = 0),
+        strip.text.y = element_text(size=18),
+        #axis.title.y = element_text(vjust = -15),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title = element_blank(),
+        axis.text = element_blank(),
+        axis.ticks = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14)) 
+RainbowTropicFull
+
+RainbowWinterFull<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+  scale_fill_identity() +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
+  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+  coord_cartesian(ylim = c(70, 230)) +
+    #geom_text(data=data_textFull, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_text1, aes(x=400, y=230, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text2, aes(x=400, y=220, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text3, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text4, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text6, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text7, aes(x=400, y=70, label=label, hjust=0), size=4.5, parse=TRUE) +
+    ggh4x::facet_nested(cols = vars(facetsFull), labeller = label_parsed) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        strip.placement = "outside",
+        strip.switch.pad.grid = unit(0.5, "cm"),
+        strip.background = element_rect(fill="white"),
+        strip.text.x = element_text(size=18, hjust = 0),
+        strip.text.y = element_text(size=18),
+        #axis.title.y = element_text(vjust = -15),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title = element_blank(),
+        axis.text = element_blank(),
+        axis.ticks = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14)) 
+RainbowWinterFull
+
+RainbowSpringFull<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+  scale_fill_identity() +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
+  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+  coord_cartesian(ylim = c(70, 230)) +
+    #geom_text(data=data_textFull, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_text2, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text5, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) + 
+  geom_text(data=data_text6, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
+    ggh4x::facet_nested(cols = vars(facetsFull), labeller = label_parsed) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        strip.placement = "outside",
+        strip.switch.pad.grid = unit(0.5, "cm"),
+        strip.background = element_rect(fill="white"),
+        strip.text.x = element_text(size=18, hjust = 0),
+        strip.text.y = element_text(size=18),
+        #axis.title.y = element_text(vjust = -15),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title = element_blank(),
+        axis.text = element_blank(),
+        axis.ticks = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14)) 
+RainbowSpringFull
+
+RainbowSummerFull<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+  scale_fill_identity() +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
+  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+  coord_cartesian(ylim = c(70, 230)) +
+    #geom_text(data=data_textFull, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_text1, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text2, aes(x=400, y=220, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text3, aes(x=400, y=230, label=label, hjust=0), size=4.5, parse=TRUE) +
+
+  geom_text(data=data_text4, aes(x=400, y=70, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text6, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text7, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
+    ggh4x::facet_nested(cols = vars(facetsFull), labeller = label_parsed) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        strip.placement = "outside",
+        strip.switch.pad.grid = unit(0.5, "cm"),
+        strip.background = element_rect(fill="white"),
+        strip.text.x = element_text(size=18, hjust = 0),
+        strip.text.y = element_text(size=18),
+        #axis.title.y = element_text(vjust = -15),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title = element_blank(),
+        axis.text = element_blank(),
+        axis.ticks = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14)) 
+RainbowSummerFull
+
+```
+
+```{r}
+#OMZ
+world_coordinatesRainbow <- map_data("world")
+world_coordinatesRainbow$nm <- c(400, 700)
+
+data_text1d <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+data_text2d <- data.frame(label = c('Near~surface~(180~µE~","~11~h):~Clades~HLI~","~LLIV'))
+data_text3d <- data.frame(label = c('Near~surface~(180~µE~","~15~h):~Clades~HLI~","~LLIV'))
+
+data_text4d <- data.frame(label = c('Deep~(30~µE~","~4~h):~Clades~LLII/III~","~LLIV'))
+data_text5d <- data.frame(label = c('Deep~(30~µE~","~6~h):~Clades~LLII/III~","~LLIV'))
+data_text6d <- data.frame(label = c('Deep~(30~µE~","~7~h):~Clades~LLII/III~","~LLIV'))
+data_text7d <- data.frame(label = c('Deep~(30~µE~","~10~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+```
+
+```{r}
+#OMZ
+d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
+RainbowTropicOMZ<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+  scale_fill_identity() +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
+  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+  coord_cartesian(ylim = c(70, 230)) +
+    #geom_text(data=data_textOMZ, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_text2d, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text6d, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
+    ggh4x::facet_nested(cols = vars(facetsOMZ), labeller = label_parsed) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        strip.placement = "outside",
+        strip.switch.pad.grid = unit(0.5, "cm"),
+        strip.background = element_rect(fill="white"),
+        strip.text.x = element_text(size=18, hjust = 0),
+        strip.text.y = element_text(size=18),
+        #axis.title.y = element_text(vjust = -15),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title = element_blank(),
+        axis.text = element_blank(),
+        axis.ticks = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14)) 
+RainbowTropicOMZ
+
+RainbowWinterOMZ<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+  scale_fill_identity() +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
+  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+  coord_cartesian(ylim = c(70, 230)) +
+      #geom_text(data=data_textOMZ, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_text1d, aes(x=400, y=230, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text2d, aes(x=400, y=220, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text3d, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text4d, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text6d, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text7d, aes(x=400, y=70, label=label, hjust=0), size=4.5, parse=TRUE) +
+      ggh4x::facet_nested(cols = vars(facetsOMZ), labeller = label_parsed) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        strip.placement = "outside",
+        strip.switch.pad.grid = unit(0.5, "cm"),
+        strip.background = element_rect(fill="white"),
+        strip.text.x = element_text(size=18, hjust = 0),
+        strip.text.y = element_text(size=18),
+        #axis.title.y = element_text(vjust = -15),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title = element_blank(),
+        axis.text = element_blank(),
+        axis.ticks = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14)) 
+RainbowWinterOMZ
+
+RainbowSpringOMZ<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+  scale_fill_identity() +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
+  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+  coord_cartesian(ylim = c(70, 230)) +
+      #geom_text(data=data_textOMZ, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_text2d, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text5d, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) + 
+  geom_text(data=data_text6d, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
+      ggh4x::facet_nested(cols = vars(facetsOMZ), labeller = label_parsed) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        strip.placement = "outside",
+        strip.switch.pad.grid = unit(0.5, "cm"),
+        strip.background = element_rect(fill="white"),
+        strip.text.x = element_text(size=18, hjust = 0),
+        strip.text.y = element_text(size=18),
+        #axis.title.y = element_text(vjust = -15),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title = element_blank(),
+        axis.text = element_blank(),
+        axis.ticks = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14)) 
+RainbowSpringOMZ
+
+RainbowSummerOMZ<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+  scale_fill_identity() +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  coord_fixed() +
+  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
+  coord_cartesian(ylim = c(70, 230)) +
+      #geom_text(data=data_textOMZ, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_text1d, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text2d, aes(x=400, y=220, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text3d, aes(x=400, y=230, label=label, hjust=0), size=4.5, parse=TRUE) +
+
+  geom_text(data=data_text4d, aes(x=400, y=70, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text6d, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_text7d, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
+      ggh4x::facet_nested(cols = vars(facetsOMZ), labeller = label_parsed) +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        strip.placement = "outside",
+        strip.switch.pad.grid = unit(0.5, "cm"),
+        strip.background = element_rect(fill="white"),
+        strip.text.x = element_text(size=18, hjust = 0),
+        strip.text.y = element_text(size=18),
+        #axis.title.y = element_text(vjust = -15),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title = element_blank(),
+        axis.text = element_blank(),
+        axis.ticks = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14)) 
+RainbowSummerOMZ
+
+```
+
+```{r, fig.height = 16, fig.width = 24}
+OMZRainbow2<- (TropicFull+RainbowTropicFull+RainbowTropicOMZ)/(WinterFull+RainbowWinterFull+RainbowWinterOMZ)/(SpringFull+RainbowSpringFull+RainbowSpringOMZ)/(SummerFull+RainbowSummerFull+RainbowSummerOMZ)
+OMZRainbow2
+```
+
+```{r save plot}
+ggsave(file = file.path(FigPath, paste("MapComboPro_yeah2",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
 ```
@@
 ```{r}
-# library(ggthemes)
-# library(mapproj)
-# world_map = map_data("world") %>% 
-#   filter(! long > 180)
-# 
-# countries = world_map %>% 
-#   distinct(region) %>% 
-#   rowid_to_column()
-# 
-# countries %>% 
-#   ggplot(aes(map_id = region), fill = "midnightblue") +
-#   geom_map(map = world_map) +
-#   expand_limits(x = world_map$long, y = world_map$lat) +
-#   coord_map("moll") 
-#   #theme_map()
-# 
-# 
-# 
-# 
-# world_map = map_data("world") %>% 
-#   filter(! long > 180)
-#   
-# distinct(world_map, region) %>% 
-#   ggplot(aes(map_id = region), fill = "midnightblue") +
-#   geom_map(map = world_map) +
-#   expand_limits(x = world_map$long, y = world_map$lat) +
-#   coord_map("moll") 
-#   #coord_equal() 
+world_coordinates2<-world_coordinates %>% 
+filter(! long > 180)
+
+d=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(35), y2=c(55))
+d2=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-35), y2=c(-55))
+d3=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-Inf), y2=c(Inf))
+d4=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-15), y2=c(15))
+d5=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-40), y2=c(40))
+
+data_textTropicFull <- data.frame(label = c('All~year'))
+data_textTropicFull2 <- data.frame(label = c('12~h'))
+data_textTropicFull3 <- data.frame(label = c('11/7~h'))
+
+TropicFull2<-ggplot() +
+
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.1) +
+  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
+  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
+  geom_text(data=data_textA, aes(x=100, y=120, label=label), size=7, parse=TRUE) +
+  geom_text(data=data_textTropicFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
+  geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
+  geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+  coord_cartesian(ylim = c(-90, 120)) +
+  labs(y = "Latitude", x = "Longitude") +
+  ggh4x::facet_nested(rows = vars(facetsPresent), labeller = label_parsed, switch = "y") +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        strip.placement = "outside",
+        strip.switch.pad.grid = unit(1, "cm"),
+        axis.text = element_text(size=14),
+        axis.title = element_text(size=14),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=18),
+        axis.title.y = element_text(vjust = -15),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14)) +
+  coord_map("moll") 
+TropicFull2
+
 ```
+
+```{r}
+library(ggthemes)
+library(mapproj)
+world_map = map_data("world") %>%
+  filter(! long > 180)
+
+countries = world_map %>%
+  distinct(region) %>%
+  rowid_to_column()
+
+countries %>%
+  ggplot(aes(map_id = region)) +
+    geom_map(map = world_map, fill = "midnightblue") +
+    geom_ellipse() +
+  coord_fixed(aes(x0 = 0, y0 = 0, a = 180, b = 80, angle = 0)) +
+  expand_limits(x = world_map$long, y = world_map$lat) +
+
+  coord_map("moll")
+
+  #theme_map()
+
+ggplot() +
+  geom_ellipse(aes(x0 = 0, y0 = 0, a = 180, b = 45, angle = 0)) +
+  coord_fixed()
+
+world_map = map_data("world") %>%
+  filter(! long > 180)
+
+distinct(world_map, region) %>%
+  ggplot(aes(map_id = region), fill = "midnightblue") +
+  geom_map(map = world_map) +
+  expand_limits(x = world_map$long, y = world_map$lat) +
+  coord_map("moll")
+  #coord_equal()
+```

### 2024-05-30 Code/Import_MapMireillePro.Rmd
New map - finished (I hope)

@@
 TropicFull<-ggplot() + 
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=1) +
   geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
-  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = 40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = -40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
   #geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
-  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
+  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "white", fill = "white", size = 0.2) +
   # geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
   # geom_text(data=data_textTropicFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
-  geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+  geom_text(data=data_textTropicFull2, aes(x=-170, y=0, label=label), size=4.5, parse=TRUE) +
+  geom_text(data=data_textTropicFull3, aes(x=170, y=0, label=label), size=4.5, parse=TRUE) +
   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
@@
 WinterFull<-ggplot() + 
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=1) +
   geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
@@
     geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
-  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = 40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = -40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
   #geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
-  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
+  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "white", fill = "white", size = 0.2) +
     # geom_text(data=data_textB, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
     # geom_text(data=data_textWinterFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
-    geom_text(data=data_textWinterFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textWinterFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textWinterFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textWinterFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textWinterFull2, aes(x=-160, y=45, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textWinterFull3, aes(x=-160, y=-45, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textWinterFull4, aes(x=160, y=45, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textWinterFull5, aes(x=160, y=-45, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textTropicFull2, aes(x=-170, y=0, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textTropicFull3, aes(x=170, y=0, label=label), size=4.5, parse=TRUE) +
   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
@@
 SpringFull<-ggplot() + 
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=1) +
   geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
@@
   geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
-  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = 40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = -40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
   #geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
-  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
+  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "white", fill = "white", size = 0.2) +
     # geom_text(data=data_textC, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
     # geom_text(data=data_textSpringFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
-    geom_text(data=data_textSpringFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textSpringFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textSpringFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textSpringFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textSpringFull2, aes(x=-160, y=45, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textSpringFull3, aes(x=-160, y=-45, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textSpringFull4, aes(x=160, y=45, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textSpringFull5, aes(x=160, y=-45, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textTropicFull2, aes(x=-170, y=0, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textTropicFull3, aes(x=170, y=0, label=label), size=4.5, parse=TRUE) +
   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
@@
 SummerFull<-ggplot() + 
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=1) +
   geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
@@
     geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
-  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = 40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = -40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
   #geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
-  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
+  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "white", fill = "white", size = 0.2) +
     # geom_text(data=data_textD, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
     # geom_text(data=data_textSummerFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
-    geom_text(data=data_textSummerFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textSummerFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textSummerFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textSummerFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
-      geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
-      geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+    geom_text(data=data_textSummerFull2, aes(x=-160, y=45, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textSummerFull3, aes(x=-160, y=-45, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textSummerFull4, aes(x=160, y=45, label=label), size=4.5, parse=TRUE) +
+    geom_text(data=data_textSummerFull5, aes(x=160, y=-45, label=label), size=4.5, parse=TRUE) +
+      geom_text(data=data_textTropicFull2, aes(x=-170, y=0, label=label), size=4.5, parse=TRUE) +
+      geom_text(data=data_textTropicFull3, aes(x=170, y=0, label=label), size=4.5, parse=TRUE) +
   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
@@
 
-world_coordinatesRainbow$facetsFull <- 'Oxygen:~Full'
-world_coordinatesRainbow$facetsOMZ <- 'Oxygen:~OMZ'
+world_coordinatesRainbow$facetsFull <- '~~~~Oxygen:~Full'
+world_coordinatesRainbow$facetsOMZ <- '~~~~Oxygen:~OMZ'
 
@@
 #OMZ
-world_coordinatesRainbow <- map_data("world")
-world_coordinatesRainbow$nm <- c(400, 700)
+# world_coordinatesRainbow <- map_data("world")
+# world_coordinatesRainbow$nm <- c(400, 700)
 
@@
 ```{r save plot}
-ggsave(file = file.path(FigPath, paste("MapComboPro_yeah2",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(FigPath, paste("MapComboPro_yeah3",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
 ```
@@
 ```
-
-```{r}
-world_coordinates2<-world_coordinates %>% 
-filter(! long > 180)
-
-d=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(35), y2=c(55))
-d2=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-35), y2=c(-55))
-d3=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-Inf), y2=c(Inf))
-d4=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-15), y2=c(15))
-d5=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-40), y2=c(40))
-
-data_textTropicFull <- data.frame(label = c('All~year'))
-data_textTropicFull2 <- data.frame(label = c('12~h'))
-data_textTropicFull3 <- data.frame(label = c('11/7~h'))
-
-TropicFull2<-ggplot() +
-
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.1) +
-  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
-  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
-  geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
-  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
-  geom_text(data=data_textA, aes(x=100, y=120, label=label), size=7, parse=TRUE) +
-  geom_text(data=data_textTropicFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
-  geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
-  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
-  coord_cartesian(ylim = c(-90, 120)) +
-  labs(y = "Latitude", x = "Longitude") +
-  ggh4x::facet_nested(rows = vars(facetsPresent), labeller = label_parsed, switch = "y") +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        strip.placement = "outside",
-        strip.switch.pad.grid = unit(1, "cm"),
-        axis.text = element_text(size=14),
-        axis.title = element_text(size=14),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=18),
-        axis.title.y = element_text(vjust = -15),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14)) +
-  coord_map("moll") 
-TropicFull2
-
-```
-
-```{r}
-library(ggthemes)
-library(mapproj)
-world_map = map_data("world") %>%
-  filter(! long > 180)
-
-countries = world_map %>%
-  distinct(region) %>%
-  rowid_to_column()
-
-countries %>%
-  ggplot(aes(map_id = region)) +
-    geom_map(map = world_map, fill = "midnightblue") +
-    geom_ellipse() +
-  coord_fixed(aes(x0 = 0, y0 = 0, a = 180, b = 80, angle = 0)) +
-  expand_limits(x = world_map$long, y = world_map$lat) +
-
-  coord_map("moll")
-
-  #theme_map()
-
-ggplot() +
-  geom_ellipse(aes(x0 = 0, y0 = 0, a = 180, b = 45, angle = 0)) +
-  coord_fixed()
-
-world_map = map_data("world") %>%
-  filter(! long > 180)
-
-distinct(world_map, region) %>%
-  ggplot(aes(map_id = region), fill = "midnightblue") +
-  geom_map(map = world_map) +
-  expand_limits(x = world_map$long, y = world_map$lat) +
-  coord_map("moll")
-  #coord_equal()
-```

### 2024-05-30 Code/Manuscript_O2.Rmd

@@
 
-Fig \@ref(fig:DNARepairFig) shows genes encoding DNA repair for *P.marinus* strains. As expected, *P. marinus* MED4 possesses the largest,
+XXXXX To gain insights into the growth rate responses across strains, particularly the responses to different oxygen levels [O~2~], we used a subset of the dataset of annotated phytoplankton genomes from Omar *et al*.
+[@omarAnnotationGenesEncoding2023].
+We extracted the genes encoding enzymes involved in DNA repair found in at least one *P.marinus* strain in this study *P.marinus* strain (Fig \@ref(fig:DNARepairFig).
+XXXX
+
+As expected, *P. marinus* NATL2A possesses the largest,
 most complete suite of genes encoding DNA repair enzymes, followed by
@@
 deoxyribodipyrimidine photolyase and DNA repair ligase (ATP) in *P. marinus*
-MIT9313 and *P. marinus* SS120 may, in part, explain why these two strains cannot tolerate growth under full [O~2~] and high light, found at the ocean
-surface. Furthermore, the protective effect of lower [O~2~], allowing
+SS120 and MIT9313 may, in part, explain why these two strains cannot tolerate growth under full [O~2~] and high light, found at the ocean
+surface.
+XXX In this study we show that *P.
+marinus* SS120 and MIT9313 can tolerate light levels representative of the near ocean surface when the [O~2~] is 25 µM, however our growth rate experiments did not include wavebands in the UV range, we therefore do not know how the absence of deoxyribodipyrimidine photolyase under low [O~2] will impact the growth rates of *P.
+marinus* SS120 and MIT9313 when exposed to UV light.
+XXXXX However, the protective effect of lower [O~2~], allowing
 these strains to grow at higher light, may relate in part to suppression

### 2024-05-30 Code/Import_MapMireillePro.Rmd
Cleaning df

@@
 ```
-
-https://ggforce.data-imaginist.com/reference/geom_ellipse.html
-elipse
-
-```{r}
-
-ggplot() +
-  geom_ellipse(aes(x0 = 550, y0 = 150, a = 150, b = 50, angle = pi / 4)) +
-  coord_fixed()
-```
-
-```{r}
-# d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-# ggplot() +
-#   stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-#   scale_fill_identity() +
-#   geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-#   scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-#   coord_cartesian(ylim = c(80, 220)) +
-#   theme_bw() +
-#   geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-#   coord_fixed()
-```

### 2024-05-31 Code/Import_MapMireillePro.Rmd
Map - small edits

@@
 ```{r save plot}
-ggsave(file = file.path(FigPath, paste("MapComboPro_yeah",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
+#ggsave(file = file.path(FigPath, paste("MapComboPro_yeah",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
 ```
@@
   #geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
-  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "white", fill = "white", size = 0.2) +
+  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
   # geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
@@
   #geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
-  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "white", fill = "white", size = 0.2) +
+  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
     # geom_text(data=data_textB, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
@@
   #geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
-  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "white", fill = "white", size = 0.2) +
+  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
     # geom_text(data=data_textC, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
@@
   #geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
-  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "white", fill = "white", size = 0.2) +
+  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
     # geom_text(data=data_textD, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
@@
 
-data_text1 <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clade~HLI'))
-data_text2 <- data.frame(label = c('Near~surface~(180~µE~","~11~h):~Clade~HLI'))
-data_text3 <- data.frame(label = c('Near~surface~(180~µE~","~15~h):~Clade~HLI'))
-
-data_text4 <- data.frame(label = c('Deep~(30~µE~","~4~h):~Clade~LLIV'))
-data_text5 <- data.frame(label = c('Deep~(30~µE~","~6~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-data_text6 <- data.frame(label = c('Deep~(30~µE~","~7~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-data_text7 <- data.frame(label = c('Deep~(30~µE~","~10~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+data_text1 <- data.frame(label = c('Near~surface~"~10m"~(180~µE~","~8~h):~Clade~HLI'))
+data_text2 <- data.frame(label = c('Near~surface~"~10m"~(180~µE~","~11~h):~Clade~HLI'))
+data_text3 <- data.frame(label = c('Near~surface~"~10m"~(180~µE~","~15~h):~Clade~HLI'))
+
+data_text4 <- data.frame(label = c('Deep~"~100m"~(30~µE~","~4~h):~Clade~LLIV'))
+data_text5 <- data.frame(label = c('Deep~"~100m"~(30~µE~","~6~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+data_text6 <- data.frame(label = c('Deep~"~100m"~(30~µE~","~7~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+data_text7 <- data.frame(label = c('Deep~"~100m"~(30~µE~","~10~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+
+data_text1d <- data.frame(label = c('Near~surface~"~10m"~(180~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
+data_text2d <- data.frame(label = c('Near~surface~"~10m"~(180~µE~","~11~h):~Clades~HLI~","~LLIV'))
+data_text3d <- data.frame(label = c('Near~surface~"~10m"~(180~µE~","~15~h):~Clades~HLI~","~LLIV'))
+
+data_text4d <- data.frame(label = c('Deep~"~100m"~(30~µE~","~4~h):~Clades~LLII/III~","~LLIV'))
+data_text5d <- data.frame(label = c('Deep~"~100m"~(30~µE~","~6~h):~Clades~LLII/III~","~LLIV'))
+data_text6d <- data.frame(label = c('Deep~"~100m"~(30~µE~","~7~h):~Clades~LLII/III~","~LLIV'))
+data_text7d <- data.frame(label = c('Deep~"~100m"~(30~µE~","~10~h):~Clades~HLI~","~LLII/III~","~LLIV'))
 
@@
 #OMZ
-# world_coordinatesRainbow <- map_data("world")
-# world_coordinatesRainbow$nm <- c(400, 700)
-
-data_text1d <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-data_text2d <- data.frame(label = c('Near~surface~(180~µE~","~11~h):~Clades~HLI~","~LLIV'))
-data_text3d <- data.frame(label = c('Near~surface~(180~µE~","~15~h):~Clades~HLI~","~LLIV'))
-
-data_text4d <- data.frame(label = c('Deep~(30~µE~","~4~h):~Clades~LLII/III~","~LLIV'))
-data_text5d <- data.frame(label = c('Deep~(30~µE~","~6~h):~Clades~LLII/III~","~LLIV'))
-data_text6d <- data.frame(label = c('Deep~(30~µE~","~7~h):~Clades~LLII/III~","~LLIV'))
-data_text7d <- data.frame(label = c('Deep~(30~µE~","~10~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-```
-
-```{r}
-#OMZ
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))

### 2024-05-31 Code/Plots_ProNicheMap.Rmd
Renamed .rmd and figure name

--- 2024-05-31 Code/Import_MapMireillePro.Rmd
@@
 library(tidyverse)
-#library(lubridate)
-#library(stringr)
 library(broom)
-#library(knitr)
 library(OneR)
@@
 library(data.table)
-# library(googledrive)
-# library(googlesheets4)
 library(ggspectra)
@@
 
-```{r create GrowthCurve plot, fig.height = 4, fig.width = 6, warning = FALSE}
+```{r create map plot, fig.height = 4, fig.width = 6, warning = FALSE}
 
@@
 ```{r save plot}
-ggsave(file = file.path(FigPath, paste("MapComboPro_yeah3",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
-```
+ggsave(file = file.path(FigPath, paste("NichesMap",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
+```

### 2024-05-31 Code/Plots_OceanProtein.Rmd
decreased the % jitter from 20 to 15

@@
   ggplot() +
-  geom_jitter(aes(x = O2, y= depth), data = . %>% filter(strain %notin% AltStrainLabels), size = 0.1, width = 20, height = 20) + #grey points not in AltStrainLabels
+  geom_jitter(aes(x = O2, y= depth), data = . %>% filter(strain %notin% AltStrainLabels), size = 0.1, width = 15, height = 15) + #grey points not in AltStrainLabels
  # geom_count(aes(x = O2, y= depth)) +
   annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, alpha = 0.75, fill = "white") +
-  geom_jitter(aes(x = O2, y= depth), data = . %>% filter(strain %in% AltStrainLabels), size = 0.1, width = 20, height = 20) + #black points in AltStrainLabels
+  geom_jitter(aes(x = O2, y= depth), data = . %>% filter(strain %in% AltStrainLabels), size = 0.1, width = 15, height = 15) + #black points in AltStrainLabels
   # geom_point(aes(x = O2, y= depth, alpha = StrainAlpha)) +
@@
 
- ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.png")))
- ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSRound2", "Fig2.tiff")))
+ ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.png")), device = NULL, scale = 1, height=15, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
+ ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSRound2", "Fig2.tiff")), device = NULL, scale = 1, height=15, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
 
@@
   ggplot() +
-  geom_jitter(aes(x = O2, y= depth), data = . %>% filter(strain %notin% AltStrainLabels), size = 0.1, width = 20, height = 20) +
+  geom_jitter(aes(x = O2, y= depth), data = . %>% filter(strain %notin% AltStrainLabels), size = 0.1, width = 15, height = 15) +
   annotate(geom = "rect", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf, alpha = 0.75, fill = "white") +
-  geom_jitter(aes(x = O2, y= depth), data = . %>% filter(strain %in% AltStrainLabels), size = 0.1, width = 20, height = 20) +
+  geom_jitter(aes(x = O2, y= depth), data = . %>% filter(strain %in% AltStrainLabels), size = 0.1, width = 15, height = 15) +
   # geom_point(aes(x = O2, y= depth, alpha = StrainAlpha)) +
@@
 
-   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.png")))
-   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSRound2", "Fig10.tiff")))
+   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.png")), device = NULL, scale = 1, height=15, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
+   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSRound2", "Fig10.tiff")), device = NULL, scale = 1, height=15, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
 

### 2024-05-31 Output/PLOSRound2/ResponsetoReviewers.txt
minor edits

@@
 
+We have removed these from the manuscript file.
+
 6. Please review your reference list to ensure that it is complete and correct. If you have cited papers 
@@
 
-Thank you for comment. We have added text to discuss the main conclusions of this study.
+-Thank you for comment. We have added text to discuss the main conclusions of this study.
 
@@
 
-We have edited the text in the revised manuscript: "Clades LLII and LLIII, including cultured strain SS120, are
+-We have edited the text in the revised manuscript: "Clades LLII and LLIII, including cultured strain SS120, are
 grouped together as early branching phylogenetic lineage in
@@
 
-We agree that the MED4 genome includes genes encoding ATP Synthase, but in the Ocean Protein Portal database no ATP Synthase peptides are annotated as coming from MED4.
-This likely reflects an annotation assignment issue because the ATP Synthase proteins are highly conserved, so assignments to strains or clades of Prochlorococcus may be ambiguous.
-We have edited the text in the revised manuscript: "Though present in the genome of MED4, the absence of proteins annotated as ATP Synthase complex for Clade HLI, compared to annotated detections of ATP Synthase across the other three clades suggests limitations in the OPP annotation process for highly conserved protein sequences."
+-We agree that the MED4 genome includes genes encoding ATP Synthase.
+Upon verifying our annotation assignments we discovered the problem with the absence of ATP Synthase from Clade HLI was not due to the limitations of the process but rather a mislabel of the column in figure 2.
+'ATP Synthase' should have been labelled 'RUBISCO'
+and 'RUBISCO' should have been labelled 'ATP Synthase'.
+However, in the Ocean Protein Portal database no RUBISCO peptides are annotated as coming from MED4.
+This likely reflects an annotation assignment issue because the RUBISCO proteins are highly conserved, so assignments to strains or clades of Prochlorococcus may be ambiguous.
+We have edited the text in the revised manuscript to reflect the limitation of the annotation process as it pertains to the highly conserved RUBISCO complex: "Though present in the genome of MED4, the absence of proteins annotated as RUBISCO complex for Clade HLI, compared to annotated detections of RUBISCO across the other three clades suggests limitations in the OPP annotation process for highly conserved protein sequences."
 Line: XXX
@@
 
-We revised the text from lines 668 to XXX to incorporate these helpful observations.
-The following was added: " Notwithstanding limitations on assignments of proteins to clades, detections of the abundant carbon fixation complex RUBISCO derived from HLI and LLI were notably absent from samples taken at lower [O~2~], suggesting limited capacity for carbon fixation by HLI and LLI under low [O~2~] habitats."
+- We revised the text from lines 668 to XXX to incorporate these helpful observations.
+The following was added: " Notwithstanding limitations on assignments of proteins to clades, detections of the abundant carbon fixation complex RUBISCO derived from HLI, LLI and LLII/III were notably absent from samples taken at lower [O~2~], suggesting limited capacity for carbon fixation by HLI,  LLI and LLII/III under low [O~2~] habitats."
 
@@
 
-Thank you for this suggestion. We have combined the growth rate figure with the GAM model for each strain to faciliate comparisons.
+- Thank you for this suggestion. We have combined the growth rate figure with the GAM model for each strain to faciliate comparisons.
 
@@
 
-Through the Discussion, notably under the discussion of the GAM models and responses to growth rate to increasing PUR, we return to the responses to red light to show that some 'high light' limitations on growth are interpretable as photoinhibition of PSII, which is more severe under blue, compared to red, light, notably at lines 1023-1032 (xXXX).
+-Through the Discussion, notably under the discussion of the GAM models and responses to growth rate to increasing PUR, we return to the responses to red light to show that some 'high light' limitations on growth are interpretable as photoinhibition of PSII, which is more severe under blue, compared to red, light, notably at lines 1023-1032 (xXXX).
 
@@
 
-Thank you for the comment.
+-Thank you for the comment.
 
@@
 
-Thank you for this suggestion. 
+-Thank you for this suggestion. 
 We edited the text:
@@
 
-We edited the figure to clarify the fit lines:
+-We edited the figure to clarify the fit lines:
 Line: XXX
@@
 
-Thank you for bringing this to our attention.
+-Thank you for bringing this to our attention.
 We clarified the wording on line XXXX of the revised manuscripted.
@@
 
-We apologize for the omissions.
+-We apologize for the omissions.
 We have revised the axis labels to make the log scaling more noticeable.

### 2024-05-31 Code/Manuscript_O2.Rmd
minor edits

@@
 
-Proteins from 13 annotated strains of *P. marinus* were detected across
+Proteins from 8 annotated strains of *P. marinus* were detected across
 depths and oxygen concentrations in the OPP data set
 analyzed. We focused our analysis here on core photosynthetic protein
-complexes, for clades HLI, LLI, LLII/III and LLIV (Fig \@ref(fig:CladeProchloroPhotosynthDepthO2)) as a function of depth (a
+complexes, for clades HLI (2 strains), LLI (2 strains), LLII/III (2 strains) and LLIV (2 strains) (Fig \@ref(fig:CladeProchloroPhotosynthDepthO2)) as a function of depth (a
 proxy for light intensity) and measured [O~2~] at the sampling locations. Photosynthetic complexes
-from HLI (including strain MED4) were detected throughout the water
-column, but, with one exception, only under high [O~2~]. Though present in the genome of MED4, the absence of proteins annotated as ATP Synthase complex for Clade HLI, compared to annotated
-detections of ATP Synthase across the other three clades, suggests
+from HLI (including strain MED4) and LLI (including strain NATL2A) were detected throughout the water
+column, predominately under high [O~2~]. Though present in the genome of MED4, the absence of proteins annotated as RUBISCO complex for clade HLI, compared to annotated
+detections of RUBISCO across the other three clades, suggests
 limitations in the annotation process for highly conserved protein
-sequences. Complexes from Clade LLI (including strain NATL2A) were also
-present across the depth/light axes, although with more protein detections at lower
-[O~2~], and fewer near surface detections of proteins from Clade LLI.
-Notwithstanding limitations on assignments of proteins to clades, detections of the abundant carbon fixation complex RUBISCO derived from HLI and LLI were notably absent from samples taken at lower [O~2~], suggesting limited capacity for carbon fixation by HLI and LLI under low [O~2~] habitats.
-Complexes from clade LLII/III
-(including strain SS120) were also detected across the depth/light and [O~2~] ranges,
-with more detections at deeper, darker depths. Clade LLIV (including strain MIT9313)
-photosynthetic complexes were also detected throughout the depth/light and [O~2~], ranges, notably with the most frequent detections of proteins at both depth and at low [O~2~], compared to other strains.
-Our analyses utilized a proteomics dataset; however, alternate approaches, such as metagenomics or metatranscriptomics, could have been employed to analyze ecotype abundances using the TARA Oceans [@pesantOpenScienceResources2015] or other datasets.
+sequences.
+Notwithstanding limitations on assignments of proteins to clades, detections of the abundant carbon fixation complex RUBISCO derived from HLI, LLI and LLII/III were notably absent from samples taken at lower [O~2~], suggesting limited capacity for carbon fixation by HLI,  LLI and LLII/III under low [O~2~] habitats.
+Clade LLII/III (including strain SS120)
+photosynthetic complexes were also detected throughout the depth/light and [O~2~] ranges, notably with the most frequent detections of proteins at both high and low [O~2~], compared to other strains.
+Complexes from LLIV (including strain MIT9313) were also detected across the depth/light and [O~2~] ranges, with more detections at deeper, darker depths and at low [O~2~].Our analyses utilized a proteomics dataset; however, alternate approaches, such as metagenomics or metatranscriptomics, could have been employed to analyze ecotype abundances using the TARA Oceans [@pesantOpenScienceResources2015] or other datasets.
 
@@
 CladeProchloroPhotosynthDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* photosynthesis complexes.**", 
-                       "Protein detections (circles) are plotted vs. O~2~ (µM) (X-axis) and depth (m) (Y-axis) at sample origin.",
+                       "Protein detections (circles) are plotted vs.
+O~2~ (µM) (x-axis) and depth (m) (y-axis) at sample origin with a 15% offset to seperate protein detections occupying the same origin.",
                        "Rows separate data annotated as from *Prochlorococcus marinus* clades: HLI (including *P.
@@
 
-```{r CladeProchloroProteinMetabDepthO2, fig.cap = CladeProchloroProteinMetabDepthO2_cap , fig.height = 20, fig.width = 10, echo = FALSE}
+```{r CladeProchloroProteinMetabDepthO2, fig.cap = CladeProchloroProteinMetabDepthO2_cap , fig.height = 20, fig.width = 20, echo = FALSE}
 
@@
 CladeProchloroProteinMetabDepthO2_cap <- glue("**Ocean detection of *Prochlorococcus marinus* protein metabolism complexes.**", 
-                       "Protein detections (circles) are plotted vs. O~2~ (µM) (X-axis) and depth (m) (Y-axis) at sample origin.",
+                       "Protein detections (circles) are plotted vs.
+O~2~ (µM) (x-axis) and depth (m) (y-axis) at sample origin with a 15% offset to seperate protein detections occupying the same origin.",
                        "Rows separate data annotated as from *Prochlorococcus marinus* clades: HLI (including *P.
@@
 
-```{r NichesMap, fig.cap = NichesMap_cap, fig.height = 15, fig.width = 15, echo = FALSE}
+```{r NichesMap, fig.cap = NichesMap_cap, fig.height = 20, fig.width = 20, echo = FALSE}
 
@@
 
-knitr::include_graphics(file.path(FiguresIn, "MapComboPro.png"))
+knitr::include_graphics(file.path(FiguresIn, "NichesMap.png"))
 

### 2024-05-31 Code/Plots_OceanProtein.Rmd
no change, was going to change the ggsave size but decided on default

@@
 
- ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.png")), device = NULL, scale = 1, height=15, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
- ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSRound2", "Fig2.tiff")), device = NULL, scale = 1, height=15, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
+ ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroPhotosynthDepthO2.png")))
+ ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSRound2", "Fig2.tiff")))
 
@@
 
-   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.png")), device = NULL, scale = 1, height=15, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
-   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSRound2", "Fig10.tiff")), device = NULL, scale = 1, height=15, width= 20, units = c("cm"),dpi = 300, limitsize = TRUE)
+   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.png")))
+   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSRound2", "Fig10.tiff")))
 

### 2024-06-03 Code/Manuscript_O2.Rmd
Doug text edits

@@
 balance electron transport, which may exclude it from growth under our
-lowest, 2.5 µmol O~2~ L^-1^, condition. SS120 from Clade LLII/III is
+lowest, 2.5 µmol O~2~ L^-1^, condition. SS120 from clade LLII/III is
 restricted to low light under full 250 µmol O~2~ L^-1^, shows expanded
@@
 In warming oceans, range expansions and competition among clades will be governed not simply by light levels.
-Short photoperiods governed by latitude, temperate winter, and depth attenuation of light, will exclude Clade HLI (including MED4).
+Short photoperiods governed by latitude, temperate winter, and depth attenuation of light, will exclude clade HLI (including MED4).
 In contrast, clade LLII/III (including SS120), and especially clade LLIV (including MIT9313), may actually exploit higher light niches under expanding OMZ conditions, where low O~2~ relieves the stresses of oxidation stress and PSII photoinhibition.
@@
 light, typical of depths from 120 m to 200 m
-[@partenskyProchlorococcusMarinePhotosynthetic1999]. LLIV members are,
+[@partenskyProchlorococcusMarinePhotosynthetic1999]. Clade LLIV members are,
 as yet, the only cultured *P. marinus* strains to have been found in Oxygen Minimum
@@
 
-## Detection of *Prochlorococcus marinus* proteins across O~2~ and light niches in the ocean {.unnumbered}
-
-Proteins from 8 annotated strains of *P. marinus* were detected across
-depths and oxygen concentrations in the OPP data set
-analyzed. We focused our analysis here on core photosynthetic protein
-complexes, for clades HLI (2 strains), LLI (2 strains), LLII/III (2 strains) and LLIV (2 strains) (Fig \@ref(fig:CladeProchloroPhotosynthDepthO2)) as a function of depth (a
-proxy for light intensity) and measured [O~2~] at the sampling locations. Photosynthetic complexes
-from HLI (including strain MED4) and LLI (including strain NATL2A) were detected throughout the water
-column, predominately under high [O~2~]. Though present in the genome of MED4, the absence of proteins annotated as RUBISCO complex for clade HLI, compared to annotated
+## Detection of proteins from *Prochlorococcus marinus* Clades across O~2~ and light niches in the ocean {.unnumbered}
+
+Proteins from *P.
+marinus* were detected across depths and oxygen concentrations in the OPP data set [@saitoPeptidesTheirSpectral2018].
+We focused our analyses on core photosynthetic protein complexes, annotated as coming from clades HLI (2 strains, including strain MED4 ); LLI (2 strains, including strain NATL2A); LLII/III (2 strains, including strain SS120) and LLIV (2 strains, including MIT9313) (Fig \@ref(fig:CladeProchloroPhotosynthDepthO2)), as a function of depth (a
+proxy for light level) and measured [O~2~] at the sampling locations. Photosynthetic complexes
+from clades HLI and LLI were detected throughout the water column, although predominately at stations with high [O~2~].
+Though present in the genome of MED4, the absence of proteins annotated as RUBISCO complex for clade HLI, compared to annotated
 detections of RUBISCO across the other three clades, suggests
-limitations in the annotation process for highly conserved protein
-sequences.
-Notwithstanding limitations on assignments of proteins to clades, detections of the abundant carbon fixation complex RUBISCO derived from HLI, LLI and LLII/III were notably absent from samples taken at lower [O~2~], suggesting limited capacity for carbon fixation by HLI,  LLI and LLII/III under low [O~2~] habitats.
-Clade LLII/III (including strain SS120)
-photosynthetic complexes were also detected throughout the depth/light and [O~2~] ranges, notably with the most frequent detections of proteins at both high and low [O~2~], compared to other strains.
-Complexes from LLIV (including strain MIT9313) were also detected across the depth/light and [O~2~] ranges, with more detections at deeper, darker depths and at low [O~2~].Our analyses utilized a proteomics dataset; however, alternate approaches, such as metagenomics or metatranscriptomics, could have been employed to analyze ecotype abundances using the TARA Oceans [@pesantOpenScienceResources2015] or other datasets.
+limitations in the annotation process assigning highly conserved protein
+sequences to clades.
+Notwithstanding limitations on assignments of proteins to clades, detections of the abundant carbon fixation complex RUBISCO derived from clades HLI, LLI and LLII/III were notably absent from stations at low [O~2~], suggesting limited capacity for carbon fixation by clades HLI,  LLI and LLII/LLIII under low [O~2~] habitats.
+Clade LLII/LLIII
+photosynthetic complexes were detected throughout the sampled ranges of depth/light and [O~2~], with  detections of proteins at both high and low [O~2~], compared to other strains.
+Complexes from LLIV (including strain MIT9313) were detected across the depth/light and [O~2~] ranges, with more detections at deeper, darker depths and at low [O~2~], compared to other clades.
+We note that detections of photosynthetic proteins from strain MIT9313 (dark symbols) show a particular bias towards low [O~2~] sampling stations, compared to the wider detections of clade LLIV.
+Our analyses utilized a proteomics dataset; however, alternate approaches, such as metagenomics or metatranscriptomics, could have been employed to analyze ecotype abundances using the TARA Oceans [@pesantOpenScienceResources2015] or other datasets.
 
@@
                        "Protein detections (circles) are plotted vs.
-O~2~ (µM) (x-axis) and depth (m) (y-axis) at sample origin with a 15% offset to seperate protein detections occupying the same origin.",
+O~2~ (µM) (x-axis) and depth (m) (y-axis) at sample origins, with 'jitter' offsets up to 15% of full axes scales, to visualize over-laid data points.",
                        "Rows separate data annotated as from *Prochlorococcus marinus* clades: HLI (including *P.
@@
                        "Columns show detections of proteins annotated as Photosystem II (PSII), Cytochromeb6f complex (Cytb6f), Photosystem I (PSI), ATP Synthase or Ribulose-1,5-bisphosphate oxygenase carboxylase (RUBISCO).",
-                       "For comparison, culture growth rate experimental conditions are indicated by horizontal grey lines for depths approximating peak Photosynthetically Active Radiation (PAR; µmol photons m^-2^ s^-1^); and vertical grey lines for imposed [O~2~] (µM).",
+                       "For comparison, experimental conditions for culture growth rate determinations are indicated by horizontal grey lines for depths, approximating peak Photosynthetically Active Radiation (PAR; µmol photons m^-2^ s^-1^); and vertical grey lines for imposed [O~2~] (µM).",
                        "Data obtained from the Biological and Chemical Oceanography Data Management Office repository [@saitoPeptidesTheirSpectral2018].",
@@
 # This is Fig4.tiff
-SS120PARGAM_cap <- glue("**A. Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low-Light (LLII/III) deep ocean clade) vs. photoperiod (h). **",
+SS120PARGAM_cap <- glue("**A. Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* SS120 (Low-Light, deep ocean clade LLII/III) vs. photoperiod (h). **",
                     "Rows separate data from levels of imposed dissolved O~2~ concentrations (250 µM, 25 µM and 2.5 µM).",
@@
 # This is Fig5.tiff
-MIT9313PARGAM_cap <- glue("**A. Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low-Light (LLIV) deep ocean clade) vs. photoperiod (h). **",
+MIT9313PARGAM_cap <- glue("**A. Chlorophyll specific growth rate (d^-1^) for *Prochlorococcus marinus* MIT9313 (Low-Light, deep ocean clade LLIV) vs. photoperiod (h). **",
                     "Rows separate data from levels of imposed dissolved O~2~ concentrations (250 µM, 25 µM and 2.5 µM).",
@@
 
-The representative of HLI clade, *P. marinus* MED4, showed no growth
+The representative of clade HLI, *P. marinus* MED4, showed no growth
 under any 4 h photoperiod treatments, even when a 4 h photoperiod
@@
 
-The representative of the LLII/III clade, *P. marinus* SS120 showed
+The representative of clade LLII/III, *P. marinus* SS120 showed
 almost no growth under 2.5 µM O~2~ experiments (Fig \@ref(fig:PhotoperiodPurFitsPlots)F). Most 4 h photoperiod treatments of
@@
 
-The LLIV clade representative, *P. marinus* MIT9313, under 250 µM O~2~
+The clade LLIV representative, *P. marinus* MIT9313, under 250 µM O~2~
 showed growth rate rising to a plateau by about 5 x 10^5^ µmol photons m^-2^
@@
 
-*Prochlorococcus marinus* genomes encode 4 FtsH proteins [@mannInvolvementFtsHHomologue2000; @adamFtsHProteasesChloroplasts2005], henceforth referred to
-as FtsH1-4, homologs to the characterized FtsH isoforms of the model
-freshwater cyanobacterium *Synechocystis sp.* PCC6803, and with presumably
-parallel functions (Table \@ref(tab:FtsHTable)). Upon a shift to higher
-light, HLI MED4 upregulates expression of FtsH1 and FtsH2
+*Prochlorococcus marinus* genomes encode 4 FtsH proteins [@mannInvolvementFtsHHomologue2000; @adamFtsHProteasesChloroplasts2005], henceforth referred to as FtsH1-4, homologs to the characterized FtsH isoforms of the model freshwater cyanobacterium *Synechocystis sp.* PCC6803, and with presumably parallel functions (Table \@ref(tab:FtsHTable)).
+Upon a shift to higher light, clade HLI MED4 upregulates expression of FtsH1 and FtsH2
 [@bonisteelStrainSpecificDifferences2018], homologs to the
 *Synechocystis* *slr*0228 and *slr*1604, implicated in PSII repair [@adamFtsHProteasesChloroplasts2005; @boehmSubunitOrganizationSynechocystis2012]. In
-contrast, representative LLIV strain MIT9313 shows no induction of
+contrast, representative clade LLIV strain MIT9313 shows no induction of
 expression of these FtsH protease isoforms when shifted to high light,
@@
 [@bonisteelStrainSpecificDifferences2018]. Through adaptation to steady
-low light, clade LLIV *P. marinus* instead allocate resources to
+low light, clade LLIV *P. marinus* instead allocates resources to
 processes other than dynamic regulation of PSII repair.
@@
 
-Ocean detections of proteins mediating protein metabolism support this
-interpretation of distinct FtsH function across clades of *P. marinus*.
-Ribosome proteins from clade HLI MED4, clade LLI NATL2A, clade LLII/III
-SS120 and clade LLIV MIT9313 show generally similar patterns vs. [O~2~]
-and depth, a proxy for peak PAR (Fig \@ref(fig:CladeProchloroProteinMetabDepthO2)). FtsH3, inferred to
-mediate PSI assembly, likewise shows a similar pattern between MED4 and
-MIT9313 (Fig \@ref(fig:CladeProchloroProteinMetabDepthO2)). But only
-MED4 shows the presence of the FtsH1 & FtsH2 isoforms inferred to
+Ocean detections of proteins [@saitoPeptidesTheirSpectral2018] mediating protein metabolism support this interpretation of distinct FtsH function across clades of *P.
+marinus*  (Fig \@ref(fig:CladeProchloroProteinMetabDepthO2)).
+Ribosome proteins annotated as from clade HLI (including MED4) were not detected at stations with low [O~2~], and near surface detections of ribosomes from clade HLI were far more frequent than detections at depth.
+Ribosome proteins from clade LLI (including NATL2A); clade LLII/III
+(including SS120) and clade LLIV (including MIT9313) show generally similar patterns vs. [O~2~] and depth, with at least some detections from stations with low [O~2~]. FtsH3, inferred to
+mediate PSI assembly, likewise shows a similar pattern between clade HLI and
+clade LLIV (Fig \@ref(fig:CladeProchloroProteinMetabDepthO2)). Only
+clade HLI shows the presence of FtsH1 isoforms, inferred to partner with FtsH2, to
 mediate PSII repair, and then only in near-surface samples subject to
-higher light levels. Furthermore, even though MIT9313 grows (Fig \@ref(fig:MIT9313PARGAM)B), and is detected in the ocean at low [O~2~]
+higher light levels. Furthermore, even though clade IV grows (Fig \@ref(fig:MIT9313PARGAM)B), and is detected in the ocean at low [O~2~]
 (Fig \@ref(fig:CladeProchloroPhotosynthDepthO2)), no FtsH from
-MIT9313 is detected at low [O~2~] (Fig \@ref(fig:CladeProchloroProteinMetabDepthO2)), suggesting limited
-requirement for protein turnover under low [O~2~].
+clade IV, nor indeed FtsH from any clade, is detected at low [O~2~] (Fig \@ref(fig:CladeProchloroProteinMetabDepthO2)), consistent with limited
+requirements for protein turnover under low [O~2~].
 
@@
                        "Columns show detections of proteins annotated as FtsH Protease Complexes (FtsH1, FtsH2, FtsH3) or the Ribosome.",
-                       "For comparison, culture growth rate experimental conditions are indicated by horizontal grey lines for depths approximating peak Photosynthetically Active Radiation (PAR; µmol photons m^-2^ s^-1^); and vertical grey lines for [O~2~] (µM).",
+                       "For comparison, experimental conditions for culture growth rate determinations are indicated by horizontal grey lines for depths approximating peak Photosynthetically Active Radiation (PAR; µmol photons m^-2^ s^-1^); and vertical grey lines for [O~2~] (µM).",
                        "Data obtained from the Biological and Chemical Oceanography Data Management Office repository [@saitoPeptidesTheirSpectral2018].",
@@
 inferred K~m~ for [O~2~] for enzymes encoded by genes 
-[@omarAnnotationGenesEncoding2023] from *P. marinus* strains, from clades
-HLI, LLI, LLII/III and LLIV. MED4 increases expression of alternative
+[@omarAnnotationGenesEncoding2023] from studied *P. marinus* strains, from clades HLI, LLI, LLII/III and LLIV. MED4 increases expression of alternative
 oxidase ('ubiquinol oxidase (non electrogenic)') to cope with changes in
@@
 for growth of MED4 in our experiments (Fig \@ref(fig:MED4PARGAM)B). We
-suggest that dependence upon this enzyme excludes MED4 from low oxygen
-zones. The genome scan shows SS120 and MIT9313 lack this gene (Fig \@ref(fig:ProchlorococcusEnzymeKms)), and therefore, lack this
+suggest that dependence upon ubiquinol oxidase excludes MED4 from low oxygen
+zones. The genome scan shows SS120 and MIT9313 lack the gene for ubiquinol oxidase (Fig \@ref(fig:ProchlorococcusEnzymeKms)), and therefore, lack this
 oxygen-dependent path to cope with changing excitation. Conversely, a
@@
 oxidase catalyzes the reaction of 2-hydroxy acid with O~2~ to produce
-toxic H~2~O~2~ [@cunaneCrystalStructureAnalysis2005]. (S)-2-hydroxy-acid
-oxidase has an approximate K~m~ for [O~2~] of \~ 250 µM, and produces
-H~2~O~2~, so growth at lower [O~2~] may protect MIT9313 from
-auto-intoxication from production of H~2~O~2~. We hypothesize that under
+toxic H~2~O~2~ [@cunaneCrystalStructureAnalysis2005], with an approximate K~m~ for [O~2~] of \~ 250 µM.
+Growth at lower [O~2~] may thus protect MIT9313 from auto-intoxication from production of H~2~O~2~ by (S)-2-hydroxy-acid oxidase.
+We hypothesize that under
 250 µM O~2~ and higher blue light, *P. marinus* MIT9313 suffered
@@
 photoinhibition is compounded by the limited inducible repair mechanism
-for PSII, due to the absence of FtsH 1 and 2 expression in *P. marinus*
-MIT9313 [@bonisteelStrainSpecificDifferences2018]. We hypothesize that
-under the conditions of our high light and 2.5 µM or 25 µM O~2~
+for PSII, due to the absence of inducible expression of FtsH 1 and 2  in *P.
+marinus* MIT9313 [@bonisteelStrainSpecificDifferences2018].
+We hypothesize that under the conditions of our high light and 2.5 µM or 25 µM O~2~
 experiments, the activity of the (S)-2-hydroxy-acid oxidase enzyme is
@@
 is inhibited, leading to less PSII damage, allowing MIT9313 to avoid
-photoinhibition and circumvent its limitations on PSII repair to exploit
+photoinhibition and circumvent its limitations on PSII repair, to exploit
 higher light. Fig \@ref(fig:ProchlorococcusEnzymeKms) also shows that
@@
 grow as well as *P. marinus* MIT9313, when exposed to high light stress
-under 25 µM O~2~ and not at all under 2.5 µM O~2~ (Fig \@ref(fig:SS120PARGAM)).
+even under 25 µM O~2~, and not at all under 2.5 µM O~2~ (Fig \@ref(fig:SS120PARGAM)).
 
@@
 
-XXXXX To gain insights into the growth rate responses across strains, particularly the responses to different oxygen levels [O~2~], we used a subset of the dataset of annotated phytoplankton genomes from Omar *et al*.
+To gain insights into the distinct growth rate responses across strains, particularly the responses to different oxygen levels [O~2~], we used a dataset of annotated phytoplankton genomes from Omar *et al*.
 [@omarAnnotationGenesEncoding2023].
-We extracted the genes encoding enzymes involved in DNA repair found in at least one *P.marinus* strain in this study *P.marinus* strain (Fig \@ref(fig:DNARepairFig).
-XXXX
-
-As expected, *P. marinus* NATL2A possesses the largest,
+We extracted those genes encoding enzymes involved in DNA repair present in at least one of the *P.marinus* study strains (Fig \@ref(fig:DNARepairFig).
+
+*P. marinus* NATL2A possesses the largest,
 most complete suite of genes encoding DNA repair enzymes, followed by
@@
 deoxyribodipyrimidine photolyase and DNA repair ligase (ATP) in *P. marinus*
-SS120 and MIT9313 may, in part, explain why these two strains cannot tolerate growth under full [O~2~] and high light, found at the ocean
+SS120 and MIT9313 may, in part, explain why these two strains cannot tolerate growth under full [O~2~] and high light, as found at the ocean
 surface.
-XXX In this study we show that *P.
-marinus* SS120 and MIT9313 can tolerate light levels representative of the near ocean surface when the [O~2~] is 25 µM, however our growth rate experiments did not include wavebands in the UV range, we therefore do not know how the absence of deoxyribodipyrimidine photolyase under low [O~2] will impact the growth rates of *P.
-marinus* SS120 and MIT9313 when exposed to UV light.
-XXXXX However, the protective effect of lower [O~2~], allowing
-these strains to grow at higher light, may relate in part to suppression
+We show that *P.
+marinus* SS120 and MIT9313 can, in contrast, tolerate light levels representative of the near surface ocean when  [O~2~] is 25 µM.
+Our growth rate experiments did not, however, include wavebands in the UV range, we therefore do not know whether the absence of deoxyribodipyrimidine photolyase under low [O~2] would impact the growth rates of *P.
+marinus* SS120 and MIT9313 when exposed to full spectrum, ocean surface light.
+The protective effects of lower [O~2~], allowing
+these strains to grow at higher light, likely relates in part to suppression
 of DNA damage when generation of Reactive Oxygen Species (ROS) is suppressed
@@
 surface during deep ocean mixing
-[@malmstromTemporalDynamicsProchlorococcus2010]. Malmstrom *et al*.
+[@malmstromTemporalDynamicsProchlorococcus2010] events. Malmstrom *et al*.
 [@malmstromTemporalDynamicsProchlorococcus2010] attributes NATL2A
 tolerance to short exposures of high light to the presence of the genes
-encoding photolyase, a gene found in HL clades. The presence of
+encoding photolyase, a gene also found in HL clades. The presence of
 deoxyribodipyrimidine photolyase and absence of DNA repair ligase (ATP)
@@
 genes which scavenge H~2~O~2~ molecules
-[@morrisFacilitationRobustGrowth2008]. The small cell size of
-*P. marinus* allow the ROS, H~2~O~2~, to
-cross the cell membrane [@omarDiffusionalInteractionsMarine2022];
-however, accumulation of extracellular H~2~O~2~ remains toxic to
-*P. marinus* [@morrisFacilitationRobustGrowth2008;
-@morrisDependenceCyanobacteriumProchlorococcus2011].
+[@morrisFacilitationRobustGrowth2008].
+The small cell size of *P.
+marinus* allow the ROS, H~2~O~2~, to cross the cell membrane [@omarDiffusionalInteractionsMarine2022]; however, accumulation of extracellular H~2~O~2~ remains toxic to *P.
+marinus* [@morrisFacilitationRobustGrowth2008; @morrisDependenceCyanobacteriumProchlorococcus2011].
 
@@
 
-*Prochlorococcus marinus* SS120, a LLII/III clade representative, showed
+*Prochlorococcus marinus* SS120, a clade LLII/III representative, showed
 an interactive inhibition of growth by oxygen and cumulative diel PUR,
@@
 by Lavin *et al*. [@lavinNovelLineagesProchlorococcus2010] who found
-evidence of LLII/III and LLIV ecotypes, using terminal restriction
+evidence of clades LLII/III and LLIV, using terminal restriction
 fragment length polymorphism analyses, at depths above 40 m, where light
@@
 
-*Prochlorococcus marinus* MIT9313, a LLIV clade representative, shows
+*Prochlorococcus marinus* MIT9313, a clade LLIV representative, shows
 potential to inhabit future warmer temperate zones year-round, as it

### 2024-06-03 Code/Plots_Genome.Rmd
Add highlight to enzymes referred to in text

@@
   ungroup() %>% 
+    mutate(EnzymeName_bold = case_when(EnzymeName %in% c("(S)-2-hydroxy-acid oxidase", "ubiquinol oxidase (non-electrogenic)", "pyridoxal 5'-phosphate synthase") ~ glue("<b>{EnzymeName}</b>"),
+                                     TRUE ~ EnzymeName)) %>% 
   ggplot() +
-  geom_errorbar(aes(x = reorder(EnzymeName, Km_mM * 1000), ymin = Km_mM_min* 1000, ymax = Km_mM_max* 1000)) +
+  geom_errorbar(aes(x = reorder(EnzymeName_bold, Km_mM * 1000), ymin = Km_mM_min* 1000, ymax = Km_mM_max* 1000)) +
   # geom_ribbon(aes(ymin = (5e-4), ymax =  (5e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "blue") +
@@
   annotate(geom = "rect", ymax = (280e-3 * 1000), ymin =  (230e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "#FF0000") +
-  geom_point(aes(x = reorder(EnzymeName, Km_mM* 1000), y = (Km_mM* 1000), shape = as.logical(Estimated), size = Gene_count), stroke = 1) +
-  geom_vline(aes(xintercept = reorder(EnzymeName, Km_mM* 1000)), size = 2,  data = . %>% filter(is.na(Km_mM)), linetype = "solid") +
+  geom_point(aes(x = reorder(EnzymeName_bold, Km_mM* 1000), y = (Km_mM* 1000), shape = as.logical(Estimated), size = Gene_count), stroke = 1) +
+  geom_vline(aes(xintercept = reorder(EnzymeName_bold, Km_mM* 1000)), size = 2,  data = . %>% filter(is.na(Km_mM)), linetype = "solid") +
   geom_text(aes(x = 18.5, y = 2.5, label = "[O2] ≈ 2.5 µM"), color = "blue", size = 6) +
@@
          title = element_text(size = 30),
-         axis.text.x = element_text(size = 30, color = "black"),
+         # axis.text.x = element_text(size = 30, color = "black"),
         axis.text.y = element_text(size = 20, color = "black"),
+        axis.text.x = ggtext::element_markdown(size = 30, color = "black"),
         strip.text = element_text(size = 30),
@@
          axis.title.y = element_blank(),
+         axis.text.x = ggtext::element_markdown(),
          axis.title.x = element_text(vjust=5),
@@
                                  TRUE ~ Description),) %>% 
+  mutate(EnzymeName_bold = case_when(EnzymeName %in% c("deoxyribodipyrimidine photolyase") ~ glue("<b>{EnzymeName}</b>"),
+                                     TRUE ~ EnzymeName)) %>% 
   ggplot() +
-  geom_point(aes(x = fct_reorder(EnzymeName, desc(Gene_count)), y = StrainLabel, size = as.character(Gene_count))) +
+  geom_point(aes(x = fct_reorder(EnzymeName_bold, desc(Gene_count)), y = StrainLabel, size = as.character(Gene_count))) +
   ggh4x::facet_nested(cols = vars(Description, Compound),rows = vars(StrainLabel),  scale = "free", space = "free") + #
@@
   theme(axis.text = element_text(size = 7, color = "black"),
+        axis.text.x = ggtext::element_markdown(),
         axis.text.y = element_blank(),

### 2024-06-03 Code/Manuscript_O2.Rmd
doug further edits

@@
 
-To gain insights into the distinct growth rate responses across strains, particularly the responses to different oxygen levels [O~2~], we used a dataset of annotated phytoplankton genomes from Omar *et al*.
+To gain insights into the distinct growth rate responses across strains, particularly the responses to different [O~2~], we used a dataset of annotated phytoplankton genomes from Omar *et al*.
 [@omarAnnotationGenesEncoding2023].
-We extracted those genes encoding enzymes involved in DNA repair present in at least one of the *P.marinus* study strains (Fig \@ref(fig:DNARepairFig).
-
-*P. marinus* NATL2A possesses the largest,
-most complete suite of genes encoding DNA repair enzymes, followed by
-*P. marinus* MIT9313. Conversely, *P. marinus* SS120 demonstrates the
-smallest genomic capacity for DNA repair. *Prochlorococcus marinus* MED4
-and NATL2A were the only strains to possess a gene encoding
-deoxyribodipyrimidine photolyase (Fig \@ref(fig:DNARepairFig) and
-\@ref(fig:ProchlorococcusLightEnzymes)), which, in the presence of blue
-light, is responsible for repairing DNA damaged by UV light
-[@sancarStructureFunctionDNA2003]. *Prochlorococcus marinus* MED4 was
-also the only strain to possess a gene encoding DNA repair ligase, which uses
-ATP as a cofactor for DNA repair. The absence of genes encoding
-deoxyribodipyrimidine photolyase and DNA repair ligase (ATP) in *P. marinus*
-SS120 and MIT9313 may, in part, explain why these two strains cannot tolerate growth under full [O~2~] and high light, as found at the ocean
-surface.
+We tabulated those genes encoding enzymes involved in DNA repair, present in at least one of the *P.marinus* study strains (Fig \@ref(fig:DNARepairFig).
+
+*P. marinus* NATL2A and MED4 possess the largest,
+most complete suites of genes encoding DNA repair enzymes.
+*Prochlorococcus marinus* MED4 and NATL2A both possess a gene encoding deoxyribodipyrimidine photolyase (Fig \@ref(fig:DNARepairFig) and \@ref(fig:ProchlorococcusLightEnzymes)), which, when activated by blue light, repairs DNA damaged by UV light
+[@sancarStructureFunctionDNA2003]. *Prochlorococcus marinus* MED4 was also the only strain to possess a gene encoding DNA repair ligase, which uses ATP as a cofactor for DNA repair.
+
+Conversely, *P.
+marinus* SS120 and MIT9313 lack genes encoding deoxyribodipyrimidine photolyase and DNA repair ligase (ATP), which may explain, in part, why these two strains cannot tolerate growth under full  250 µM [O~2~] and high light, as found at the ocean surface.
 We show that *P.
-marinus* SS120 and MIT9313 can, in contrast, tolerate light levels representative of the near surface ocean when  [O~2~] is 25 µM.
-Our growth rate experiments did not, however, include wavebands in the UV range, we therefore do not know whether the absence of deoxyribodipyrimidine photolyase under low [O~2] would impact the growth rates of *P.
-marinus* SS120 and MIT9313 when exposed to full spectrum, ocean surface light.
-The protective effects of lower [O~2~], allowing
-these strains to grow at higher light, likely relates in part to suppression
-of DNA damage when generation of Reactive Oxygen Species (ROS) is suppressed
-at lower [O~2~]. NATL2A, a clade LLI, has been found near the ocean
-surface during deep ocean mixing
-[@malmstromTemporalDynamicsProchlorococcus2010] events. Malmstrom *et al*.
-[@malmstromTemporalDynamicsProchlorococcus2010] attributes NATL2A
-tolerance to short exposures of high light to the presence of the genes
-encoding photolyase, a gene also found in HL clades. The presence of
-deoxyribodipyrimidine photolyase and absence of DNA repair ligase (ATP)
-supports why NATL2A tolerates limited exposure to high light and why
-NATL2A is unable to fully repair damaged DNA. *Prochlorococcus marinus* are
-highly susceptible to hydrogen peroxide (H~2~O~2~) toxicity as they lack
-genes which scavenge H~2~O~2~ molecules
+marinus* SS120 and MIT9313 do, in contrast, tolerate light levels representative of the near surface ocean at 25 µM [O~2~].
+Our growth rate experiments did not include wavebands in the UV range, so we do not know whether the absence of deoxyribodipyrimidine photolyase would inhibit the growth rates of *P.
+marinus* SS120 and MIT9313  under low [O~2] if exposed to full spectrum, ocean surface light.
+The protective effects of lower [O~2~], allowing these strains to grow at higher light, likely relates in part to suppression of DNA damage when generation of Reactive Oxygen Species (ROS) is suppressed at lower [O~2~].
+NATL2A, a clade LLI, has been found near the ocean surface during deep ocean mixing [@malmstromTemporalDynamicsProchlorococcus2010] events.
+Malmstrom *et al*.
+[@malmstromTemporalDynamicsProchlorococcus2010] indeed attribute NATL2A tolerance to short exposures of high light to the presence of the genes encoding photolyase, also found in HL clades.
+The presence of deoxyribodipyrimidine photolyase but absence of DNA repair ligase (ATP)
+supports why NATL2A tolerates limited exposure to high light and why NATL2A is unable to fully repair damaged DNA.
+*Prochlorococcus marinus* are highly susceptible to hydrogen peroxide (H~2~O~2~) toxicity as they lack genes which scavenge H~2~O~2~ molecules
 [@morrisFacilitationRobustGrowth2008].

### 2024-06-03 Code/Plots_Genome.Rmd
Highlight enzymes mentioned in text

@@
   filter(EC != "3.1.3.18") %>% #PGP is not truly a DNA repair enzyme. 
+  mutate(EnzymeName_bold = case_when(EnzymeName %in% c("DNA ligase (ATP)", "deoxyribodipyrimidine photolyase", "pyridoxal 5'-phosphate synthase") ~ glue("<b>{EnzymeName}</b>"),
+                                     TRUE ~ EnzymeName)) %>% 
   ggplot() +
-  geom_point(aes(x = fct_reorder(EnzymeName, desc(Gene_count)), y = StrainLabel, size = (Gene_count))) + #y = interaction(Genus, species, StrainLabel, sep = " ")
+  geom_point(aes(x = fct_reorder(EnzymeName_bold, desc(Gene_count)), y = StrainLabel, size = (Gene_count))) + #y = interaction(Genus, species, StrainLabel, sep = " ")
   # facet_grid(rows = vars(Genus), scales = "free", space = "free") +
@@
          axis.text.x = ggtext::element_markdown(),
-         axis.title.x = element_text(vjust=5),
+         axis.title.x = element_text(vjust=0),
         axis.ticks.y = element_blank(),

### 2024-06-04 Output/PLOSRound2/ResponsetoReviewers.txt
add text about OPP protein figure now having jitter points

@@
 This likely reflects an annotation assignment issue because the RUBISCO proteins are highly conserved, so assignments to strains or clades of Prochlorococcus may be ambiguous.
+We have edited the figure #XXX to add 'jitter' offsets up to 15% of full axes scales, to visualize over-laid data points. 
 We have edited the text in the revised manuscript to reflect the limitation of the annotation process as it pertains to the highly conserved RUBISCO complex: "Though present in the genome of MED4, the absence of proteins annotated as RUBISCO complex for Clade HLI, compared to annotated detections of RUBISCO across the other three clades suggests limitations in the OPP annotation process for highly conserved protein sequences."
@@
 We briefly motivated the inclusion of the red light growth trials, as mechanistically informative, at line 706:
-"As mentioned, growth trials under red light, although not representative of *Prochlorococcus* niches, are mechanistically informative [@murphyPhotoinactivationPhotosystemII2017] regarding photoinactivation of PSII."
+" As mentioned, growth rate trials under red light, although not representative of *P.
+marinus* niches, are mechanistically informative [@murphyPhotoinactivationPhotosystemII2017] regarding photoinactivation of PSII."
 
@@
 
-We have edited the text in the revised manuscript: " Clades LLII and LLIII, including cultured strain SS120, are
-grouped together as early branching phylogenetic lineage in
-the *P. marinus* radiation, with a preference for low light."
+We have edited the text in the revised manuscript: " Clades LLII and LLIII, including cultured strain SS120, are grouped together as early branching phylogenetic lineage in the *P.
+marinus* radiation, with a preference for low light."
 Line: XXX
@@
 Thank you for your comment.
-We have edited the text in the revised manuscript: "*Prochlorococcus* remain challenging to culture at high densities or under fluctuating environments, partially due to their dependence upon mutualistic heterotrophic bacteria to detoxify
+We have edited the text in the revised manuscript: "*Prochlorococcus marinus* remain challenging to culture at high densities or under fluctuating environments, partially due to their dependence upon mutualistic heterotrophic bacteria to detoxify
 reactive oxygen species [48,49]." 
@@
 binary detected/not detected value.
+
+Thank you for your suggestion. We have edited the figure #XXX to add 'jitter' offsets up to 15% of full axes scales, to visualize over-laid data points.

### 2024-06-04 Output/PLOSRound2/ResponsetoReviewers.txt
response to reviewer and text edits Doug

@@
 
-We thank you and the reviewers for constructive feedback, which we have addressed through revisions, as outlined below.
+We thank you and the reviewers for constructive feedback, which we have addressed through extensive revisions, outlined below.
 
@@
 
--Thank you for comment. We have added text to discuss the main conclusions of this study.
+-Thank you for comment. We added text to discuss the main conclusions of this study.
 
@@
 
--We have edited the text in the revised manuscript: "Clades LLII and LLIII, including cultured strain SS120, are
+-We edited the text in the revised manuscript: "Clades LLII and LLIII, including cultured strain SS120, are
 grouped together as early branching phylogenetic lineage in
@@
 This likely reflects an annotation assignment issue because the RUBISCO proteins are highly conserved, so assignments to strains or clades of Prochlorococcus may be ambiguous.
-We have edited the figure #XXX to add 'jitter' offsets up to 15% of full axes scales, to visualize over-laid data points. 
-We have edited the text in the revised manuscript to reflect the limitation of the annotation process as it pertains to the highly conserved RUBISCO complex: "Though present in the genome of MED4, the absence of proteins annotated as RUBISCO complex for Clade HLI, compared to annotated detections of RUBISCO across the other three clades suggests limitations in the OPP annotation process for highly conserved protein sequences."
+We edited the figure #XXX to add 'jitter' offsets up to 15% of full axes scales, to visualize over-laid data points. 
+We edited the text in the revised manuscript to reflect the limitation of the annotation process as it pertains to the highly conserved RUBISCO complex: "Though present in the genome of MED4, the absence of proteins annotated as RUBISCO complex for Clade HLI, compared to annotated detections of RUBISCO across the other three clades suggests limitations in the OPP annotation process for highly conserved protein sequences."
 Line: XXX
@@
 
-- Thank you for this suggestion. We have combined the growth rate figure with the GAM model for each strain to faciliate comparisons.
+- Thank you for this suggestion. We combined the growth rate figure with the GAM model for each strain to faciliate comparisons.
 
@@
 
--We apologize for the omissions.
-We have revised the axis labels to make the log scaling more noticeable.
-The narrowness of the red bar (spanning 230 to 280 ?M) results from the log scaling of the y axis.
+-We apologize for the omissions. We revised the axis labels to make the log scaling more noticeable. The narrowness of the red bar (spanning 230 to 280 ?M) results from the log scaling of the y axis.
 
@@
 
-Thank you for brining this to our attention, we have removed phosphoglycolate phosphatase from the figure as it is indeed not directly involved in DNA repair but in clearing DNA damage repair products.
-Upon revisiting the interpretation of this figure, we have edited the text: "As expected, *P. marinus* NATL2A possesses the largest,
+Thank you for brining this to our attention, we removed phosphoglycolate phosphatase from the figure as it is indeed not directly involved in DNA repair but in clearing DNA damage repair products.
+Upon revisiting the interpretation of this figure, we edited the text: "As expected, *P. marinus* NATL2A possesses the largest,
 most complete suite of genes encoding DNA repair enzymes, followed by *P. marinus* MIT9313."
@@
 In response to reviewer 1 and reviewer 2 we have combined the growth rate figure with the GAM model for each strain to faciliate comparisons. 
-We have edited the abstract, results and discussion to better convey the motivations and findings of the study. 
+We edited the abstract, results and discussion texts to better convey the motivations and findings of the study. 
 In particular lines  XXX to YYY and XXXXX
@@
 
-We have edited the text:
+We edited the text:
 Line: XXX
@@
 
-We have edited the text in the revised manuscript: " Clades LLII and LLIII, including cultured strain SS120, are grouped together as early branching phylogenetic lineage in the *P.
+We edited the text in the revised manuscript: " Clades LLII and LLIII, including cultured strain SS120, are grouped together as early branching phylogenetic lineage in the *P.
 marinus* radiation, with a preference for low light."
@@
 Thank you for  bringing this to our attention.
-We have added the following text to the revised manuscript: "Follett et al 2022, however, model interactions of heterotrophic bacteria  that may influence latitudinal expansions of *P.
+We added the following text to the revised manuscript: "Follett et al 2022, however, model interactions of heterotrophic bacteria  that may influence latitudinal expansions of *P.
 marinus*."
@@
 Thank you for noting that this needs further clarification. 
-We have edited the paragraph for clarity in the revised manuscript adding: "While the accuracy of strain specific protein annotations are limited due to the high conservation of the target protein complexes, the two step approach of peptide-to-spectrum matching using deep paired metagenomics, does assign proteins at the level of clades."
+We edited the paragraph for clarity in the revised manuscript adding: "While the accuracy of strain specific protein annotations are limited due to the high conservation of the target protein complexes, the two step approach of peptide-to-spectrum matching using deep paired metagenomics, does assign proteins at the level of clades."
 Lines: XXX
@@
 Thank you for your comment.
-We have edited the text in the revised manuscript: "*Prochlorococcus marinus* remain challenging to culture at high densities or under fluctuating environments, partially due to their dependence upon mutualistic heterotrophic bacteria to detoxify
+We edited the text in the revised manuscript: "*Prochlorococcus marinus* remain challenging to culture at high densities or under fluctuating environments, partially due to their dependence upon mutualistic heterotrophic bacteria to detoxify
 reactive oxygen species [48,49]." 
@@
 Extending the study to include metagonomic analyses is valid but is beyond our scope.
-We have edited the text in the revised manuscript: "Our analyses utilized a proteomics dataset; however, alternate approaches, such as metagenomics or metatranscriptomics, could have been employed to analyze ecotype abundances using the TARA Oceans [@pesantOpenScienceResources2015] dataset."
+We edited the text in the revised manuscript: "Our analyses utilized a proteomics dataset; however, alternate approaches, such as metagenomics or metatranscriptomics, could have been employed to analyze ecotype abundances using the TARA Oceans [@pesantOpenScienceResources2015] dataset."
 Line: XXX
@@
 
-We have edited the text: "The growth rate for Prochlorococcus marinus MED4, clade HLI, under 250 ?M O2, increased with higher imposed PAR and longer photoperiods (Fig 3A), across all spectral wavebands."
+We edited the text: "The growth rate for Prochlorococcus marinus MED4, clade HLI, under 250 ?M O2, increased with higher imposed PAR and longer photoperiods (Fig 3A), across all spectral wavebands."
 Line XXX:
@@
 Thank you for this comment. In this work we used 1 to 3 replicates depending on the experimental conditions. Specific number of replicates (shown as small dots in Figures (3 - 5)).
-We have edited the text in the revised manuscript:" Consistent absence of growth of some strains under some levels of photoperiod, PAR, or [O~2~] meant we completed 268 growth factor treatment combinations with 1 to 3 replicates."
+We edited the text in the revised manuscript:" Consistent absence of growth of some strains under some levels of photoperiod, PAR, or [O~2~] meant we completed 268 growth factor treatment combinations with 1 to 3 replicates."
 Line: XXX
@@
 
-XXX DOUGXXX 
-XXX Energy- blue have shorter WL so high energy, red longer WL so lower energy??? XXXX
-XXX Can add something on line 827 to expand XXXXX
+As outlined in responses to questions from Review 1, the implications of blue vs.
+red light wavebands indeed relate to the higher energy per photon in the blue light band.
+In particular blue light is absorbed well by chlorophyll, but is also directly absorbed by the manganese cluster of PSII, provoking one major path of photoinactivation, as discussed in Murphy et al.
+2017, and cited at lines XXX, YYY, ZZZ.
+In contrast, red light is absorbed well by chlorophyll, driving photosynthesis, but does not provoke direct photoinactivation of the PSII manganese cluster, lowering the metabolic cost of maintaining the photosynthetic system, compared to equivalent rates of photosynthesis driven by blue light.
+
+These issues are now discussed in relation to Figure PUR GROWTH, with a given amount of absorbed red light PUR provoking more growth than the equivalent absorbed blue light PUR.  In particular:
+
+"...MED4 achieved
+more growth per unit diel cumulative PUR (Fig \@ref(fig:BluevsRedPurFitsPlots)A and B), consistent with Murphy *et al*. [@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for
+growth under red light, for MED4, because red light provokes less
+photoinactivation of PSII, than equivalent levels of blue light. For
+distinct fits for different photoperiods refer to Fig \@ref(fig:PhotoperiodPurFitsPlots) A-C..."
 
@@
 
-Thank you for your suggestion. We have combined the growth rate figure with the GAM model for each strain. We believe this will aid the reader with interpreting both plots.
+Thank you for your suggestion. We combined the growth rate figure with the GAM model for each strain. We believe this will aid the reader with interpreting both plots.
 
@@
 
-Thank you for your suggestion. We have edited the figure #XXX to add 'jitter' offsets up to 15% of full axes scales, to visualize over-laid data points.
+Thank you for your suggestion.
+We agree that detection limits vary for different target proteins, particularly for detection of single proteins such as FtsH isoforms.
+Such issues are less problematic for summed detections of multiple proteins assigned to multi-protein complexes such as PSII.
+An analyses of mass spectrophotometric proteomic detection limits is beyond the scope of the paper.
+We however edited the figure #XXX to add 'jitter' offsets up to 15% of full axes scales, to visualize multiple previously over-laid data points.

### 2024-06-04 Code/Manuscript_O2.Rmd
minor edit
response to reviewer and text edits Doug

@@
 Our growth rate experiments did not include wavebands in the UV range, so we do not know whether the absence of deoxyribodipyrimidine photolyase would inhibit the growth rates of *P.
-marinus* SS120 and MIT9313  under low [O~2] if exposed to full spectrum, ocean surface light.
+marinus* SS120 and MIT9313  under low [O~2~] if exposed to full spectrum, ocean surface light.
 The protective effects of lower [O~2~], allowing these strains to grow at higher light, likely relates in part to suppression of DNA damage when generation of Reactive Oxygen Species (ROS) is suppressed at lower [O~2~].
@@
 
+XXXX
 The potential for niche expansion into temperate regions by *P. marinus*
 varies depending on the season, which influences achieved underwater
-photoperiods and light levels. Temperate summer delivers 11 hours of
+photoperiods and light levels. Temperate summer delivers ~11 hours of
 blue waveband light underwater, above the photic threshold of 20 µmol

### 2024-06-04 Output/PLOSRound2/ResponsetoReviewers.txt
minor edit

@@
 
-We have removed these from the manuscript file.
+We removed these from the manuscript file.
 
@@
 
-We briefly motivated the inclusion of the red light growth trials, as mechanistically informative, at line 706:
+We briefly motivated the inclusion of the red light growth trials, as mechanistically informative, at line XXX:
 " As mentioned, growth rate trials under red light, although not representative of *P.
@@
 
--Through the Discussion, notably under the discussion of the GAM models and responses to growth rate to increasing PUR, we return to the responses to red light to show that some 'high light' limitations on growth are interpretable as photoinhibition of PSII, which is more severe under blue, compared to red, light, notably at lines 1023-1032 (xXXX).
+-Through the Discussion, notably under the discussion of the GAM models and responses to growth rate to increasing PUR, we return to the responses to red light to show that some 'high light' limitations on growth are interpretable as photoinhibition of PSII, which is more severe under blue, compared to red, light, notably at lines XXXX-1032 (xXXX).
 
@@
 We clarified the wording on line XXXX of the revised manuscripted.
-"Protein homologies for FtsH isoforms between *Prochlorococcus* and *Synechocystis* were extracted from @bonisteelStrainSpecificDifferences2018."
+"Protein homologies for FtsH isoforms between *Prochlorococcus marinus* and *Synechocystis* were extracted from @bonisteelStrainSpecificDifferences2018."
 

### 2024-06-05 Code/Manuscript_O2.Rmd
Zorz added

@@
 from clades HLI and LLI were detected throughout the water column, although predominately at stations with high [O~2~].
-Though present in the genome of MED4, the absence of proteins annotated as RUBISCO complex for clade HLI, compared to annotated
-detections of RUBISCO across the other three clades, suggests
+Though present and expressed in the genome of MED4 [@zorzRUBISCOPhotosystemII2015], the absence of proteins annotated as RUBISCO complex for clade HLI, compared to annotated detections of RUBISCO across the other three clades, suggests
 limitations in the annotation process assigning highly conserved protein

### 2024-06-05 Output/PLOSRound2/ResponsetoReviewers.txt
added a word to response to reviewers

@@
 
-We thank you and the reviewers for constructive feedback, which we have addressed through extensive revisions, outlined below.
+We thank you and the reviewers for constructive feedback, which we have addressed through extensive revisions, outlined below, which we believe have improved the manuscript.
 
@@
 Co-authors, Aurora Mattison and Dr.
-Amanda Cockshutt, used the metaproteomics database as an extension of their earlier studies on the functional implications of differential protein allocations across different Prochlorococcus strains [Zorz, Bonisteel].
+Amanda Cockshutt, used the metaproteomics database as an extension of their earlier studies on the functional implications of differential protein allocations across different Prochlorococcus strains [Zorz et al.
+2015, Bonisteel et al.
+2018].
 Those studies indeed motivated the design of our growth matrix.

### 2024-06-05 Code/Plots_ProNicheMap.Rmd
Doug looked at map code
depth photoperiod .Rds summary read in
condition table for strain distributions

@@
 
-----------------------------------------Create map ----------------------------------------------
+```{r read photoperiod depth data}
+PhotoperiodDepth <- readRDS(file = file.path("..", "Data", "ProcessedData", "DepthPhotoperiodTableFilter.Rds"))
+
+PhotoperiodDepthOMZ <- PhotoperiodDepth |>
+  select(-c(ToD, DepthPARabs, DepthPARSine, DepthPARabsNA, Photicperiod:PhoticperiodSineSatPAR_h)) |>
+  filter(DepthNames %in% c("50 m", "100 m")) |>
+  relocate(DepthNames, .after = lat) |>
+  mutate(CladeHLI = 1,
+         CladeLLII_LLIII = 1,
+         CladeLLIV = 1)
+
+PhotoperiodDepthOMZ
+
+PhotoperiodDepthFullO2 <- PhotoperiodDepth |>
+  select(-c(ToD, DepthPARabs, DepthPARSine, DepthPARabsNA, Photicperiod:PhoticperiodSineSatPAR_h)) |>
+  filter(DepthNames %in% c("50 m", "100 m")) |>
+  relocate(DepthNames, .after = lat) |>
+   mutate(CladeHLI = 1,
+         CladeLLII_LLIII = 1,
+         CladeLLIV = 1)
+
+PhotoperiodDepthFullO2
+
+```
+
+```{r read spectral depth backdrop}
+DepthBackdrop <- readRDS(file = file.path("..", "Data", "ProcessedData", "DepthBackdrop.Rds"))
+
+DepthBackdrop 
+```
 
@@
 
-```{r}
+```{r world map}
 world_coordinates <- map_data("world")
 
-world_coordinates$facetsPresent <- 'Present'
 world_coordinates$facetsFuture <- 'Future~scenario'
@@
 data_textC <- data.frame(label = c('C'))
-data_textD <- data.frame(label = c('D'))
 ```

### 2024-06-05 Code/Plots_ProNicheMap.Rmd
Added potential niches for each strain

@@
   relocate(DepthNames, .after = lat) |>
-  mutate(CladeHLI = 1,
-         CladeLLII_LLIII = 1,
-         CladeLLIV = 1)
+  mutate(CladeHLI = case_when(DayofYear == "Winter Solstice" & lat == 45 ~ 0,
+                              DayofYear == "Equinox" & DepthNames == "100 m" & lat == 45 ~ 0,
+                              DayofYear == "Summer Solstice" & DepthNames == "100 m" & lat == 0  ~ 0,
+                              TRUE ~ 1)) |>
+  mutate(CladeLLII_LLIII = case_when(DayofYear == "Winter Solstice" & DepthNames == "100 m" & lat == 45 ~ 0,
+                                     DayofYear == "Winter Solstice" & lat == 0 ~ 0,
+                                     DayofYear == "Equinox" & DepthNames == "50 m" & lat == 45 ~ 0,
+                                     DayofYear == "Equinox" & lat == 0 ~ 0,
+                                     DayofYear == "Summer Solstice" & lat == 45  ~ 0,
+                                     DayofYear == "Summer Solstice" & DepthNames == "50 m" & lat == 0  ~ 0,
+                              TRUE ~ 1 ))  |>
+  mutate(CladeLLIV = case_when(DayofYear == "Winter Solstice" & DepthNames == "100 m" & lat == 45 ~ 0,
+                              TRUE ~ 1))
 
@@
   relocate(DepthNames, .after = lat) |>
-   mutate(CladeHLI = 1,
-         CladeLLII_LLIII = 1,
-         CladeLLIV = 1)
+  mutate(CladeHLI = case_when(DayofYear == "Winter Solstice" & DepthNames == "100 m" & lat == 45 ~ 0,
+                              TRUE ~ 1)) |>
+  mutate(CladeLLII_LLIII = case_when(DayofYear == "Winter Solstice" ~ 0,
+                                     DayofYear == "Equinox" & DepthNames == "50 m" & lat == 45 ~ 0,
+                                     DayofYear == "Equinox" & lat == 0 ~ 0,
+                                     DayofYear == "Summer Solstice" & lat == 45  ~ 0,
+                                     DayofYear == "Summer Solstice" & DepthNames == "50 m" & lat == 0  ~ 0,
+                              TRUE ~ 1 ))  |>
+  mutate(CladeLLIV = case_when(DayofYear == "Winter Solstice" & DepthNames == "100 m" & lat == 45 ~ 0,
+                               DayofYear == "Winter Solstice" & DepthNames == "50 m" & lat == 0 ~ 0,
+                               DayofYear == "Equinox" & DepthNames == "50 m" & lat == 45 ~ 0,
+                               DayofYear == "Equinox" & lat == 0 ~ 0,
+                               DayofYear == "Summer Solstice" & lat == 45  ~ 0,
+                               DayofYear == "Summer Solstice" & DepthNames == "50 m" & lat == 0  ~ 0,
+                              TRUE ~ 1))
 

### 2024-06-06 Code/Plots_ProNicheMap.Rmd
generated new niches map

@@
   mutate(CladeLLII_LLIII = case_when(DayofYear == "Winter Solstice" & DepthNames == "100 m" & lat == 45 ~ 0,
-                                     DayofYear == "Winter Solstice" & lat == 0 ~ 0,
-                                     DayofYear == "Equinox" & DepthNames == "50 m" & lat == 45 ~ 0,
-                                     DayofYear == "Equinox" & lat == 0 ~ 0,
+                                     DayofYear == "Winter Solstice" & DepthNames == "50 m" & lat == 0 ~ 0,
+                                     DayofYear == "Equinox" & DepthNames == "50 m" ~ 0,
                                      DayofYear == "Summer Solstice" & lat == 45  ~ 0,
@@
 ```{r read spectral depth backdrop}
-DepthBackdrop <- readRDS(file = file.path("..", "Data", "ProcessedData", "DepthBackdrop.Rds"))
-
-DepthBackdrop 
+DepthBackdrop <- readPNG("DepthBackdrop.png")
+# Get dimensions of the image
+width <- dim(DepthBackdrop)[2]
+height <- dim(DepthBackdrop)[1]
+
+# Plot the image
+plot(1:width, type = "n", xlim = c(0, width), ylim = c(0, height),
+     xlab = "", ylab = "", axes =FALSE)
+rasterImage(DepthBackdrop, 0, 0, width, height) 
+points(PhotoperiodDepthFullO2$PhoticperiodPeakSatPAR_h, PhotoperiodDepthFullO2$DepthNames, col = "red", pch = 16)
+
+```
+
+```{r, Niches figures, fig.height = 10, fig.width = 8, warning = FALSE}
+NichesFullO2North <- PhotoperiodDepthFullO2 %>%
+  filter(lat == 45) %>% 
+mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
+                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
+                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
+                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
+        TextLocation = 5) %>% 
+mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
+         lat = factor(lat, levels = c("45", "0"))) %>%
+ggplot()+
+  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
+            size = 0.5, alpha = 0, show.legend = TRUE)+
+  labs(title = "Full Oxygen") +
+  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+    facet_grid(rows = vars(lat),
+              cols = vars(DayofYear),
+              labeller = labeller(lat = label_both, DayofYear = label_both)) +
+   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
+   # parse = TRUE,
+    hjust = 0,
+    vjust = 1,
+    size = 3
+  )  +
+  guides(color = "none") +
+  theme_bw()+
+ theme(strip.text = element_text(size = 10),
+        axis.title = element_blank(),
+        # strip.text.x = element_text(size = 20),
+        axis.text.y = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x.bottom = element_blank(),
+        axis.ticks.y.left = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        plot.margin = unit(c(0,30,0,0), "pt"))
+
+NichesFullO2North
+
+NichesFullO2Equat <- PhotoperiodDepthFullO2 %>%
+  filter(lat == 0) %>% 
+mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
+                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
+                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
+                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
+        TextLocation = 5) %>% 
+mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
+         lat = factor(lat, levels = c("45", "0"))) %>%
+ggplot()+
+  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
+            size = 0.5, alpha = 0, show.legend = TRUE)+
+  # labs(title = "Full Oxygen") +
+  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+    facet_grid(rows = vars(lat),
+              cols = vars(DayofYear),
+              labeller = labeller(lat = label_both)) +
+   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
+   # parse = TRUE,
+    hjust = 0,
+    vjust = 1,
+    size = 3
+  )  +
+  guides(color = "none") +
+  theme_bw() +
+ theme(strip.text.x = element_blank(),
+       strip.text.y = element_text(size = 10),
+        axis.title = element_blank(),
+        # strip.text.x = element_text(size = 20),
+        axis.text.y = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x.bottom = element_blank(),
+        axis.ticks.y.left = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank())
+
+NichesFullO2Equat
+
+NichesOMZNorth <- PhotoperiodDepthOMZ %>%
+  filter(lat == 45) %>% 
+mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
+                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
+                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
+                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
+        TextLocation = 5) %>% 
+mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
+         lat = factor(lat, levels = c("45", "0"))) %>%
+ggplot()+
+  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
+            size = 0.5, alpha = 0, show.legend = TRUE)+
+   labs(title = "OMZ") +
+  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+    facet_grid(rows = vars(lat),
+              cols = vars(DayofYear),
+              labeller = labeller(lat = label_both)) +
+   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
+   # parse = TRUE,
+    hjust = 0,
+    vjust = 1,
+    size = 3
+  )  +
+  guides(color = "none") +
+  theme_bw() +
+ theme(strip.text.x = element_blank(),
+       strip.text.y = element_text(size = 10),
+        axis.title = element_blank(),
+        # strip.text.x = element_text(size = 20),
+        axis.text.y = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x.bottom = element_blank(),
+        axis.ticks.y.left = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank())
+
+NichesOMZNorth
+
+NichesOMZEquat <- PhotoperiodDepthOMZ %>%
+  filter(lat == 0) %>% 
+mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
+                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
+                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
+                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
+        TextLocation = 5) %>% 
+mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
+         lat = factor(lat, levels = c("45", "0"))) %>%
+ggplot()+
+  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
+            size = 0.5, alpha = 0, show.legend = TRUE)+
+  # labs(title = "Full Oxygen") +
+  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+    facet_grid(rows = vars(lat),
+              cols = vars(DayofYear),
+              labeller = labeller(lat = label_both)) +
+   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
+   # parse = TRUE,
+    hjust = 0,
+    vjust = 1,
+    size = 3
+  )  +
+  guides(color = "none") +
+  theme_bw() +
+ theme(strip.text.x = element_blank(),
+       strip.text.y = element_text(size = 10),
+        axis.title = element_blank(),
+        # strip.text.x = element_text(size = 20),
+        axis.text.y = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x.bottom = element_blank(),
+        axis.ticks.y.left = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank())
+
+NichesOMZEquat
+
 ```
@@
 
-world_coordinates$facetsFuture <- 'Future~scenario'
+# world_coordinates$facetsFuture <- 'Future~scenario'
 
@@
 data_textB <- data.frame(label = c('B'))
-data_textC <- data.frame(label = c('C'))
-```
-
-```{r create GrowthCurve plot, fig.height = 4, fig.width = 6, warning = FALSE}
+# data_textC <- data.frame(label = c('C'))
+```
+
+```{r create maps, fig.height = 10, fig.width = 6, warning = FALSE}
 
@@
 d5=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-40), y2=c(40))
-
-data_textTropicFull <- data.frame(label = c('All~year'))
-data_textTropicFull2 <- data.frame(label = c('12~h'))
-data_textTropicFull3 <- data.frame(label = c('11/7~h'))
-
-TropicFull<-ggplot() + 
+# 
+# data_textTropicFull <- data.frame(label = c('All~year'))
+# data_textTropicFull2 <- data.frame(label = c('12~h'))
+# data_textTropicFull3 <- data.frame(label = c('11/7~h'))
+# 
+# TropicFull<-ggplot() + 
+#   geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+#   geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+#   geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+#   geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+#   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
+#   geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
+#   geom_text(data=data_textTropicFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
+#   geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
+#   geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+#   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+#   coord_cartesian(ylim = c(-90, 120)) +
+#   labs(y = "Latitude", x = "Longitude") +
+#   ggh4x::facet_nested(rows = vars(facetsPresent), labeller = label_parsed, switch = "y") +
+#   theme_bw() +
+#   theme(panel.grid.minor = element_blank(),
+#         panel.grid.major = element_blank(),
+#         strip.placement = "outside",
+#         strip.switch.pad.grid = unit(1, "cm"),
+#         axis.text = element_text(size=14),
+#         axis.title = element_text(size=14),
+#         strip.background = element_rect(fill="white"),
+#         strip.text = element_text(size=18),
+#         axis.title.y = element_text(vjust = -15),
+#         #axis.title.x = element_text(margin=margin(t=10)),
+#         axis.title.x = element_blank(),
+#         axis.text.x = element_blank(),
+#         axis.ticks.x = element_blank(),
+#         legend.background = element_rect(fill="transparent"),
+#         legend.position = c(0.12,0.76),
+#         legend.key.height= unit(0.005, 'cm'),
+#         legend.spacing.x = unit(0.01, 'cm'),
+#         legend.text = element_text(size=14))
+# TropicFull
+
+# data_textWinterFull <- data.frame(label = c('Winter~or~summer~solstice'))
+# data_textWinterFull2 <- data.frame(label = c('9~h'))
+# data_textWinterFull3 <- data.frame(label = c('16~h'))
+# data_textWinterFull4 <- data.frame(label = c('8/4~h'))
+# data_textWinterFull5 <- data.frame(label = c('15/10~h'))
+
+FullO2map<-ggplot() + 
   geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
     geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
@@
     geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
-  geom_text(data=data_textTropicFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
-  geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textWinterFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
+    # geom_text(data=data_textWinterFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textWinterFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textWinterFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textWinterFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
@@
   labs(y = "Latitude", x = "Longitude") +
-  ggh4x::facet_nested(rows = vars(facetsPresent), labeller = label_parsed, switch = "y") +
+  # ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
   theme_bw() +
@@
         strip.text = element_text(size=18),
-        axis.title.y = element_text(vjust = -15),
+        axis.title.y = element_text(vjust = 1),
         #axis.title.x = element_text(margin=margin(t=10)),
@@
         legend.text = element_text(size=14))
-TropicFull
-
-data_textWinterFull <- data.frame(label = c('Winter~or~summer~solstice'))
-data_textWinterFull2 <- data.frame(label = c('9~h'))
-data_textWinterFull3 <- data.frame(label = c('16~h'))
-data_textWinterFull4 <- data.frame(label = c('8/4~h'))
-data_textWinterFull5 <- data.frame(label = c('15/10~h'))
-
-WinterFull<-ggplot() + 
+FullO2map
+
+# data_textSpringFull <- data.frame(label = c('Vernal~equinox'))
+# data_textSpringFull2 <- data.frame(label = c('12~h'))
+# data_textSpringFull3 <- data.frame(label = c('12~h'))
+# 
+# data_textSpringFull4 <- data.frame(label = c('11/6~h'))
+# data_textSpringFull5 <- data.frame(label = c('11/6~h'))
+
+OMZmap<-ggplot() + 
   geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
@@
      geom_text(data=data_textB, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
-    geom_text(data=data_textWinterFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
-    geom_text(data=data_textWinterFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textWinterFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textWinterFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textWinterFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textSpringFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
+    # geom_text(data=data_textSpringFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textSpringFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textSpringFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textSpringFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+    # 
   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
@@
   labs(y = "Latitude", x = "Longitude") +
-  ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
+  # ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
   theme_bw() +
@@
         legend.text = element_text(size=14))
-WinterFull
-
-data_textSpringFull <- data.frame(label = c('Vernal~equinox'))
-data_textSpringFull2 <- data.frame(label = c('12~h'))
-data_textSpringFull3 <- data.frame(label = c('12~h'))
-
-data_textSpringFull4 <- data.frame(label = c('11/6~h'))
-data_textSpringFull5 <- data.frame(label = c('11/6~h'))
-
-SpringFull<-ggplot() + 
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
-  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
-  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-    geom_text(data=data_textC, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
-    geom_text(data=data_textSpringFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
-    geom_text(data=data_textSpringFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textSpringFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textSpringFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textSpringFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
-
-  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
-  coord_cartesian(ylim = c(-90, 120)) +
-  labs(y = "Latitude", x = "Longitude") +
-  ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        strip.placement = "outside",
-        strip.switch.pad.grid = unit(1, "cm"),
-        axis.text = element_text(size=14),
-        axis.title = element_text(size=14),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=18),
-        axis.title.y = element_text(vjust = -15),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14))
-SpringFull
-
-data_textSummerFull <- data.frame(label = c('Summer~or~winter~solstice'))
-data_textSummerFull2 <- data.frame(label = c('16~h'))
-data_textSummerFull3 <- data.frame(label = c('9~h'))
-data_textSummerFull4 <- data.frame(label = c('15/10~h'))
-data_textSummerFull5 <- data.frame(label = c('8/4~h'))
-SummerFull<-ggplot() + 
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-    geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
-  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
-  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-    geom_text(data=data_textD, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
-    geom_text(data=data_textSummerFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
-    geom_text(data=data_textSummerFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textSummerFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textSummerFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
-    geom_text(data=data_textSummerFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
-      geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
-      geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
-  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
-  coord_cartesian(ylim = c(-90, 120)) +
-  labs(y = "Latitude", x = "Longitude") +
-  ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        strip.placement = "outside",
-        strip.switch.pad.grid = unit(1, "cm"),
-        axis.text = element_text(size=14),
-        axis.title = element_text(size=14),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=18),
-        axis.title.y = element_text(vjust = -15),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14))
-SummerFull
-
-```
-
-```{r, warning = FALSE, fig.height = 12, fig.width = 6}
-Full<- (TropicFull/WinterFull/SpringFull/SummerFull)
-Full                         
+OMZmap
+
+# data_textSummerFull <- data.frame(label = c('Summer~or~winter~solstice'))
+# data_textSummerFull2 <- data.frame(label = c('16~h'))
+# data_textSummerFull3 <- data.frame(label = c('9~h'))
+# data_textSummerFull4 <- data.frame(label = c('15/10~h'))
+# data_textSummerFull5 <- data.frame(label = c('8/4~h'))
+# SummerFull<-ggplot() + 
+#   geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+#   geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+#   geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+#     geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+#   geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+#   geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
+#   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
+#     geom_text(data=data_textD, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
+#     geom_text(data=data_textSummerFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
+#     geom_text(data=data_textSummerFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
+#     geom_text(data=data_textSummerFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
+#     geom_text(data=data_textSummerFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
+#     geom_text(data=data_textSummerFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
+#       geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
+#       geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+#   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+#   coord_cartesian(ylim = c(-90, 120)) +
+#   labs(y = "Latitude", x = "Longitude") +
+#   ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
+#   theme_bw() +
+#   theme(panel.grid.minor = element_blank(),
+#         panel.grid.major = element_blank(),
+#         strip.placement = "outside",
+#         strip.switch.pad.grid = unit(1, "cm"),
+#         axis.text = element_text(size=14),
+#         axis.title = element_text(size=14),
+#         strip.background = element_rect(fill="white"),
+#         strip.text = element_text(size=18),
+#         axis.title.y = element_text(vjust = -15),
+#         #axis.title.x = element_text(margin=margin(t=10)),
+#         axis.title.x = element_blank(),
+#         axis.text.x = element_blank(),
+#         axis.ticks.x = element_blank(),
+#         legend.background = element_rect(fill="transparent"),
+#         legend.position = c(0.12,0.76),
+#         legend.key.height= unit(0.005, 'cm'),
+#         legend.spacing.x = unit(0.01, 'cm'),
+#         legend.text = element_text(size=14))
+# SummerFull
+
+```
+
+```{r}
+
+```
+
+```{r, warning = FALSE, fig.height = 15, fig.width = 20}
+
+FullO2<- (FullO2map + (plot_spacer()/NichesFullO2North/NichesFullO2Equat/plot_spacer())) +
+  plot_layout(widths = c(3,2), heights = c(4,0.5))
+FullO2
+
+OMZ<- (OMZmap + (plot_spacer()/NichesOMZNorth/NichesOMZEquat/plot_spacer())) +
+  plot_layout(widths = c(3,2), heights = c(4,0.5))
+OMZ
+
+NichesMap <- (FullO2map + (plot_spacer()/NichesFullO2North/NichesFullO2Equat/plot_spacer())) / (OMZmap + (plot_spacer()/NichesOMZNorth/NichesOMZEquat/plot_spacer()))
+
+NichesMap
+
+```
+
+```{r save plot}
+ggsave(file = file.path(FigPath, paste("NichesMap",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
 ```
@@
 #FUll
-world_coordinatesRainbow <- map_data("world")
+# world_coordinatesRainbow <- map_data("world")
 world_coordinatesRainbow$nm <- c(400, 700)
 
-data_text1 <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clade~HLI'))
-data_text2 <- data.frame(label = c('Near~surface~(180~µE~","~11~h):~Clade~HLI'))
-data_text3 <- data.frame(label = c('Near~surface~(180~µE~","~15~h):~Clade~HLI'))
+data_text1 <- data.frame(label = c('~Clade~HLI'))
+data_text2 <- data.frame(label = c('~Clade~HLI'))
+data_text3 <- data.frame(label = c('~Clade~HLI'))
 
@@
 RainbowTropicFull<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  stat_wl_strip(aes(x = nm), ymin = 180, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+  scale_fill_identity() +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 170, b = 40, angle = pi / 20), fill = "white", colour = "white") +
   coord_fixed() +
@@
 ```
-
-```{r save plot}
-ggsave(file = file.path(FigPath, paste("NichesMap",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
-```

### 2024-06-06 Code/Plots_ProNicheMap.Rmd
put axis labels back on

@@
 ```{r read spectral depth backdrop}
+
+library("png")
 DepthBackdrop <- readPNG("DepthBackdrop.png")
@@
         # strip.text.x = element_text(size = 20),
-        axis.text.y = element_blank(),
+        axis.text.y = element_text(size = 10),
         axis.text.x = element_blank(),
@@
         # strip.text.x = element_text(size = 20),
-        axis.text.y = element_blank(),
+        axis.text.y = element_text(size = 10),
+        # axis.text.y = element_blank(),
+        # axis.text.y = element_text(size = 5),
          axis.text.x = element_blank(),
@@
   theme_bw() +
- theme(strip.text.x = element_blank(),
+ theme(strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
@@
         # strip.text.x = element_text(size = 20),
-        axis.text.y = element_blank(),
+        axis.text.y = element_text(size = 10),
+        # axis.text.y = element_blank(),
         axis.text.x = element_blank(),
@@
         # strip.text.x = element_text(size = 20),
-        axis.text.y = element_blank(),
+        axis.text.y = element_text(size = 10),
+        # axis.text.y = element_blank(),
          axis.text.x = element_blank(),
@@
 
-```{r}
-
-```
-
 ```{r, warning = FALSE, fig.height = 15, fig.width = 20}

### 2024-06-06 Code/Plots_ProNicheMap.Rmd
Map edits

@@
   filter(DepthNames %in% c("50 m", "100 m")) |>
+  mutate(DepthNames = factor(DepthNames, levels = c("100 m", "50 m")),
+         lat = factor(lat, levels = c("45", "0"))) |>
   relocate(DepthNames, .after = lat) |>
@@
 ```
-
-```{r, Niches figures, fig.height = 10, fig.width = 8, warning = FALSE}
+#fig.height = 10, fig.width = 8, warning = FALSE
+```{r, Niches figures}
 NichesFullO2North <- PhotoperiodDepthFullO2 %>%
@@
 
+-------------------------------------------------------------------------------------------------------------------
+---------------------------------------------- # SySl changes-----------------------------------------------------------
+----------------------------------------------------------------------------------------------------------------
+
+fig.height = 10, fig.width = 6, warning = FALSE
+```{r create maps}
+
+d=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(35), y2=c(55))
+d2=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-35), y2=c(-55))
+d3=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-Inf), y2=c(Inf))
+d4=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-15), y2=c(15))
+d5=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-40), y2=c(40))
+
+map<-ggplot() + 
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+    geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_hline(yintercept = 40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = -40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
+  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
+   # geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
+    # geom_text(data=data_textWinterFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
+    # geom_text(data=data_textWinterFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textWinterFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textWinterFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textWinterFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+  coord_cartesian(ylim = c(-90, 120)) +
+  labs(y = "Latitude", x = "Longitude") +
+  # ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        strip.placement = "outside",
+        strip.switch.pad.grid = unit(1, "cm"),
+        axis.text = element_text(size=14),
+        axis.title = element_text(size=14),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=18),
+        axis.title.y = element_text(vjust = 1),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14))
+map
+
+map2<-ggplot() + 
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=1) +
+  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+    geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_hline(yintercept = 40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = -40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
+  #geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
+  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
+    # geom_text(data=data_textD, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
+    # geom_text(data=data_textSummerFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
+    # geom_text(data=data_textSummerFull2, aes(x=-160, y=45, label=label), size=4.5, parse=TRUE) +
+    # geom_text(data=data_textSummerFull3, aes(x=-160, y=-45, label=label), size=4.5, parse=TRUE) +
+    # geom_text(data=data_textSummerFull4, aes(x=160, y=45, label=label), size=4.5, parse=TRUE) +
+    # geom_text(data=data_textSummerFull5, aes(x=160, y=-45, label=label), size=4.5, parse=TRUE) +
+    #   geom_text(data=data_textTropicFull2, aes(x=-170, y=0, label=label), size=4.5, parse=TRUE) +
+    #   geom_text(data=data_textTropicFull3, aes(x=170, y=0, label=label), size=4.5, parse=TRUE) +
+  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+  coord_cartesian(ylim = c(-90, 120)) +
+  labs(y = "Latitude", x = "Longitude") +
+  #ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=14),
+        axis.title = element_text(size=14),
+        strip.background = element_rect(fill="white"),
+        strip.text.x = element_text(size=18, hjust = 0),
+        strip.text.y = element_text(size=18),
+        axis.title.y = element_text(vjust = -15),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14)) +
+  coord_map("moll") 
+map2
+
+```
+
+#fig.height = 10, fig.width = 8, warning = FALSE
+   # parse = TRUE,
+    hjust = 0,
+    vjust = 1,
+```{r, Niches figures, fig.height = 4, fig.width = 8, warning = FALSE}
+
+# PhotoperiodDepthFullO2<-PhotoperiodDepthFullO2 %>% 
+# PhotoperiodDepthOMZ<-PhotoperiodDepthOMZ %>%
+
+NichesFullO2North <- PhotoperiodDepthFullO2 %>%
+  filter(lat == 45) %>% 
+mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
+                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
+                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
+                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
+        TextLocation = 5) %>% 
+ggplot()+
+  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
+            size = 0.5, alpha = 0, show.legend = TRUE)+
+  labs(title = "Full Oxygen") +
+  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+      coord_fixed(ratio = 1.7, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
+    facet_grid(cols = vars(DayofYear),
+              labeller = labeller(lat = label_both, DayofYear = label_value)) +
+   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
+    size = 6
+  )  +
+  guides(color = "none") +
+  theme_bw()+
+  theme(plot.title = element_text(vjust = 10),
+        panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=14),
+        #axis.title = element_text(size=14),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=18),
+        #axis.title.y = element_text(vjust = 1),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14))
+
+NichesFullO2North
+
+NichesFullO2Equat <- PhotoperiodDepthFullO2 %>%
+  filter(lat == 0) %>% 
+mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
+                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
+                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
+                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
+        TextLocation = 5) %>% 
+ggplot()+
+  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
+            size = 0.5, alpha = 0, show.legend = TRUE)+
+  # labs(title = "Full Oxygen") +
+  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+      coord_fixed(ratio = 1.7, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
+    facet_grid(cols = vars(DayofYear),
+              labeller = labeller(lat = label_both)) +
+   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
+    size = 6
+  )  +
+  guides(color = "none") +
+  theme_bw() +
+  theme(plot.title = element_text(vjust = 10),
+        panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=14),
+        #axis.title = element_text(size=14),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=18),
+        #axis.title.y = element_text(vjust = 1),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14))
+
+NichesFullO2Equat
+
+NichesOMZNorth <- PhotoperiodDepthOMZ %>%
+  filter(lat == 45) %>% 
+mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
+                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
+                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
+                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
+        TextLocation = 5) %>% 
+ggplot()+
+  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
+            size = 0.5, alpha = 0, show.legend = TRUE)+
+   labs(title = "Oxygen Minimum Zone") +
+  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+      coord_fixed(ratio = 1.7, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
+    facet_grid(cols = vars(DayofYear),
+              labeller = labeller(lat = label_both)) +
+   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
+    size = 6
+  )  +
+  guides(color = "none") +
+  theme_bw() +
+  theme(plot.title = element_text(vjust = 10),
+        panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=14),
+        #axis.title = element_text(size=14),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=18),
+        #axis.title.y = element_text(vjust = 1),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14))
+
+NichesOMZNorth
+
+NichesOMZEquat <- PhotoperiodDepthOMZ %>%
+  filter(lat == 0) %>% 
+mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
+                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
+                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
+                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
+        TextLocation = 5) %>%
+
+ggplot()+
+  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
+            size = 0.5, alpha = 0, show.legend = TRUE)+
+  # labs(title = "Full Oxygen") +
+  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+    coord_fixed(ratio = 1.7, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
+    facet_grid(cols = vars(DayofYear),
+              labeller = labeller(lat = label_both)) +
+   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
+    hjust = 0.5,
+    #vjust = 1,
+   size = 6)  +
+  guides(color = "none") +
+  theme_bw() +
+  theme(plot.title = element_text(vjust = 10),
+        panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=14),
+        #axis.title = element_text(size=14),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=18),
+        #axis.title.y = element_text(vjust = 1),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14))
+
+NichesOMZEquat
+
+```
+
+```{r}
+P1<-(NichesFullO2North/NichesFullO2Equat)
+P1
+
+P2<- (NichesOMZNorth/NichesOMZEquat)
+P2
+
+# P3<-P1+FullO2map+P2
+# P3
+
+ggarrange(P1, map, P2, ncol = 3, nrow = 1)
+
+# ggarrange(P1, map2, P2, ncol = 3, nrow = 1)
+
+```
+
+```{r save plot}
+ggsave(file = file.path(FigPath, paste("NichesMap_UglySS2",".png",sep = "")), height=12, width= 28,  dpi = 300, limitsize = TRUE)
+```
+
 https://sape.inf.usi.ch/quick-reference/ggplot2/geom_polygon

### 2024-06-06 Code/Manuscript_O2.Rmd
minor edits
caption for map figure

@@
 
-XXXX
+XXXXDoug
 The potential for niche expansion into temperate regions by *P. marinus*
@@
 
-NichesMap_cap <- glue(" Figure caption for Potential Temperate Future Niche map goes here.",
-
+NichesMap_cap <- glue(" Potential Future Niches for *Prochlorococcus* clades in a warming ocean. 
+The map shows current latitudinal distribution limits for *Prochlorococcus* (between green dashed lines), tropical and temperate  latitudinal regions (yellow bands). 
+Light levels, photoperiods and spectral bands, potentially permissive for growth of *Prochlorococcus* clades are determined by the interactions of latitude, season and depth attenuation of light.
+Potential clade occupancies under Full Oxygen (250 µM O~2~) are shown for 10-50 m and 100 m depths, in temperate vs.
+tropical regions, under depth-resolved photoperiods, approximating Winter Solstice, Equinox and Summer Solstice.
+Clade HLI is excluded from temperate depths by short photoperiods at Winter Solstice.
+Clades LLII/III are excluded from shallow depths by excessive light.
+Low Oxygen Zones (25 µM O~2~) drastically alter these potential occupancy patterns by excluding Clade HLI from the temperate winter solstice at all depths, and by expanding the exploitation of higher light by Clade LLIV.
+Potential clade occupancies for the southern temperate zone mirror the northern temperate zone occupancies.",
                        .sep = " ")

### 2024-06-06 Code/Plots_ProNicheMap.Rmd
New beautiful map :)

--- 2024-06-06 Code/Plots_ProNicheMap.Rmd
@@
 library(ggforce) #ellipse
+library("cowplot")
 library("patchwork") # merging plots
+library(grid) # for making one strip bigger - grid.draw
 
@@
 
+-------------------------------------------------------------------------------------------------------------------
+---------------------------------------------- # SySl changes-----------------------------------------------------------
+----------------------------------------------------------------------------------------------------------------
+
+fig.height = 10, fig.width = 6, warning = FALSE
+```{r create maps, fig.height = 8, fig.width = 10, warning = FALS}
+
+d=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(35), y2=c(55))
+d2=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-35), y2=c(-55))
+d3=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-Inf), y2=c(Inf))
+d4=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-15), y2=c(15))
+d5=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-40), y2=c(40))
+
+map<-ggplot() + 
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+    geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_hline(yintercept = 40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = -40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
+  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
+   # geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
+    # geom_text(data=data_textWinterFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
+    # geom_text(data=data_textWinterFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textWinterFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textWinterFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textWinterFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
+    # geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
+  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+  coord_cartesian(ylim = c(-90, 120)) +
+  coord_fixed(ratio = 2, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
+  labs(y = "Latitude", x = "Longitude") +
+  # ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=18),
+        axis.title = element_text(size=20),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=20),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14))
+map
+
+```
+
+#fig.height = 10, fig.width = 8, warning = FALSE
+   # parse = TRUE,
+    hjust = 0,
+    vjust = 1,
+```{r, Niches figures, fig.height = 4, fig.width = 8, warning = FALSE}
+
+# PhotoperiodDepthFullO2$facetsFull <- 'Full Oxygen'
+# PhotoperiodDepthOMZ$facetsOMZ <- 'Oxygen Minimum Zone'
+
+NichesFullO2North <- PhotoperiodDepthFullO2 %>%
+  filter(lat == 45) %>% 
+mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
+                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
+                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
+                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
+        TextLocation = 0) %>% 
+ggplot()+
+  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
+  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6)  +
+  labs(title = "Full Oxygen") +
+  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+  coord_fixed(ratio = 2, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
+  ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both, DayofYear = label_value)) +
+  guides(color = "none") +
+  theme_bw()+
+  theme(plot.title = element_text(size = 20),
+        panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=18),
+        #axis.title = element_text(size=14),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=18),
+        #axis.title.y = element_text(vjust = 1),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14)) 
+NichesFullO2North
+
+NichesFullO2Equat <- PhotoperiodDepthFullO2 %>%
+  filter(lat == 0) %>% 
+mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
+                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
+                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
+                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
+        TextLocation = 0) %>% 
+ggplot()+
+  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
+  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6)  +
+  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+  coord_fixed(ratio = 2, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
+  ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
+  guides(color = "none") +
+  theme_bw() +
+  theme(plot.title = element_text(vjust = 10),
+        panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=18),
+        #axis.title = element_text(size=14),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=18),
+        #axis.title.y = element_text(vjust = 1),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14))
+
+NichesFullO2Equat
+
+NichesOMZNorth <- PhotoperiodDepthOMZ %>%
+  filter(lat == 45) %>% 
+mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
+                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
+                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
+                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
+        TextLocation = 0) %>% 
+ggplot()+
+  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
+  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6)  +
+  labs(title = "Oxygen Minimum Zone") +
+  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+  coord_fixed(ratio = 2, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
+  ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
+  guides(color = "none") +
+  theme_bw() +
+  theme(plot.title = element_text(size = 20),
+        panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=18),
+        #axis.title = element_text(size=14),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=18),
+        #axis.title.y = element_text(vjust = 1),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14))
+
+NichesOMZNorth
+
+NichesOMZEquat <- PhotoperiodDepthOMZ %>%
+  filter(lat == 0) %>% 
+mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
+                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
+                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
+                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
+        TextLocation = 0) %>%
+
+ggplot()+
+  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
+  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6)  +
+  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+  coord_fixed(ratio = 2, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
+  ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
+  guides(color = "none") +
+  theme_bw() +
+  theme(plot.title = element_text(vjust = 10),
+        panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=18),
+        #axis.title = element_text(size=14),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=18),
+        #axis.title.y = element_text(vjust = 1),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14))
+
+NichesOMZEquat
+
+```
+
+```{r}
+# P1<-(NichesFullO2North/NichesFullO2Equat)
+# P1
+# 
+# P2<- (NichesOMZNorth/NichesOMZEquat)
+# P2 
+# 
+# ggarrange(P1, map, P2, ncol = 3, nrow = 1)
+
+```
+
+#Cool web about merging plots
+http://www.sthda.com/english/articles/24-ggpubr-publication-ready-plots/81-ggplot2-easy-way-to-mix-multiple-graphs-on-the-same-page/
+
+```{r, fig.height = 4, fig.width = 8, warning = FALSE}
+
+ggdraw() +
+  draw_plot(NichesFullO2North, x = 0, y = 0.65, width = .3, height = .3) +
+  draw_plot(NichesFullO2Equat, x = 0, y = 0.455, width = .3, height = .3) +
+  draw_plot(map, x = .1, y = .2, width = 0.8, height = 0.8) +
+  draw_plot(NichesOMZNorth, x = 0.7, y = 0.65, width = .3, height = 0.3) +
+  draw_plot(NichesOMZEquat, x = 0.7, y = 0.455, width = .3, height = 0.3)
+
+```
+
+```{r save plot}
+ggsave(file = file.path(FigPath, paste("NichesMap",".png",sep = "")), height=12, width= 28,  dpi = 300, limitsize = TRUE)
+```
+
 https://sape.inf.usi.ch/quick-reference/ggplot2/geom_polygon

### 2024-06-06 Code/Manuscript_O2.Rmd

@@
 *Prochlorococcus marinus*, the smallest picocyanobacterium, comprises
-multiple clades with distinct niches, currently across tropical and sub-tropical
+multiple clades occupying distinct niches, currently across tropical and sub-tropical
 oligotrophic ocean regions, including Oxygen Minimum Zones. Ocean
-warming may open permissive temperatures in new, poleward photic
+warming may open growth-permissive temperatures in new, poleward photic
 regimes, along with expanded Oxygen Minimum Zones. We used ocean metaproteomic
-data to guide testing of *Prochlorococcus marinus* growth across a matrix of peak irradiances,
+data on current *Prochlorococcus marinus* niches, to guide testing of *Prochlorococcus marinus* growth across a matrix of peak irradiances,
 photoperiods, spectral bands and dissolved oxygen. MED4 from Clade HLI
 requires greater than 4 h photoperiod, grows at 25 µmol O~2~ L^-1^ and
-above, and exploits high cumulative diel photon doses. MED4, however, relies upon an alternative oxidase to
-balance electron transport, which may exclude it from growth under our
+above, and exploits high cumulative diel photon doses. MED4, however, relies upon an alternative oxidase to balance electron transport, which may exclude it from growth under our
 lowest, 2.5 µmol O~2~ L^-1^, condition. SS120 from clade LLII/III is
@@
 PSII and production of reactive oxygen species.
-In warming oceans, range expansions and competition among clades will be governed not simply by light levels.
-Short photoperiods governed by latitude, temperate winter, and depth attenuation of light, will exclude clade HLI (including MED4).
-In contrast, clade LLII/III (including SS120), and especially clade LLIV (including MIT9313), may actually exploit higher light niches under expanding OMZ conditions, where low O~2~ relieves the stresses of oxidation stress and PSII photoinhibition.
+In warming oceans, range expansions and competition among clades will be governed not only by light levels.
+Short photoperiods governed by latitude, temperate winter, and depth attenuation of light, will exclude clade HLI (including MED4) from some habitats.
+In contrast, clade LLII/III (including SS120), and particularly clade LLIV (including MIT9313), may exploit higher light niches nearer the surface, under expanding OMZ conditions, where low O~2~ relieves the stresses of oxidation stress and PSII photoinhibition.
 
@@
 marinus* SS120 and MIT9313 lack genes encoding deoxyribodipyrimidine photolyase and DNA repair ligase (ATP), which may explain, in part, why these two strains cannot tolerate growth under full  250 µM [O~2~] and high light, as found at the ocean surface.
-We show that *P.
+*P.
 marinus* SS120 and MIT9313 do, in contrast, tolerate light levels representative of the near surface ocean at 25 µM [O~2~].
@@
 Malmstrom *et al*.
-[@malmstromTemporalDynamicsProchlorococcus2010] indeed attribute NATL2A tolerance to short exposures of high light to the presence of the genes encoding photolyase, also found in HL clades.
+[@malmstromTemporalDynamicsProchlorococcus2010] indeed attribute NATL2A tolerance of short exposures of high light to presence of genes encoding photolyase, also found in HL clades.
 The presence of deoxyribodipyrimidine photolyase but absence of DNA repair ligase (ATP)
-supports why NATL2A tolerates limited exposure to high light and why NATL2A is unable to fully repair damaged DNA.
-*Prochlorococcus marinus* are highly susceptible to hydrogen peroxide (H~2~O~2~) toxicity as they lack genes which scavenge H~2~O~2~ molecules
-[@morrisFacilitationRobustGrowth2008].
+supports why NATL2A tolerates limited exposure to high light, but is unable to fully repair damaged DNA.
+*Prochlorococcus marinus* are highly susceptible to hydrogen peroxide (H~2~O~2~) toxicity as they lack genes which scavenge H~2~O~2~ molecules [@morrisFacilitationRobustGrowth2008].
 The small cell size of *P.
@@
 
-XXXXDoug
-The potential for niche expansion into temperate regions by *P. marinus*
-varies depending on the season, which influences achieved underwater
-photoperiods and light levels. Temperate summer delivers ~11 hours of
-blue waveband light underwater, above the photic threshold of 20 µmol
-photons m^-2^ s^-1^, while temperate spring/fall delivers 8 hours of
-blue waveband light underwater, photoperiod ranges which are permissive
-for growth of all three *P. marinus*. In contrast temperate winter
-delivers only about 2 h of blue waveband light underwater above the
-photic threshold, which precludes growth of MED4 and SS120, even if
-winter waters reached permissive temperatures. MIT9313 and SS120 will be
-excluded from near-surface growth niches by high PAR, unless OMZ zones
-extend to the near surface (Table \@ref(tab:NichesTable).
-
-\newpage
-
-```{r NichesMap, fig.cap = NichesMap_cap, fig.height = 20, fig.width = 20, echo = FALSE}
-
-NichesMap_cap <- glue(" Potential Future Niches for *Prochlorococcus* clades in a warming ocean. 
-The map shows current latitudinal distribution limits for *Prochlorococcus* (between green dashed lines), tropical and temperate  latitudinal regions (yellow bands). 
-Light levels, photoperiods and spectral bands, potentially permissive for growth of *Prochlorococcus* clades are determined by the interactions of latitude, season and depth attenuation of light.
-Potential clade occupancies under Full Oxygen (250 µM O~2~) are shown for 10-50 m and 100 m depths, in temperate vs.
-tropical regions, under depth-resolved photoperiods, approximating Winter Solstice, Equinox and Summer Solstice.
-Clade HLI is excluded from temperate depths by short photoperiods at Winter Solstice.
-Clades LLII/III are excluded from shallow depths by excessive light.
-Low Oxygen Zones (25 µM O~2~) drastically alter these potential occupancy patterns by excluding Clade HLI from the temperate winter solstice at all depths, and by expanding the exploitation of higher light by Clade LLIV.
-Potential clade occupancies for the southern temperate zone mirror the northern temperate zone occupancies.",
-                       .sep = " ")
-
-knitr::include_graphics(file.path(FiguresIn, "NichesMap.png"))
-
-```
-
-\newpage
-
 Diverse *P. marinus* strains @billerProchlorococcusStructureFunction2015
 differentially exploit potential photoregimes, both at the surface and
-deep in the water column. Some *P. marinus* strains grow under low
-oxygen environments, similar to OMZ. The LL clades we tested can
+deeper in the water column. Some *P. marinus* strains grow under low
+oxygen environments, similar to OMZ. The LLII and LLIV clade representatives we tested can
 function as 'HL' in oxygen environments of 25 µM, and as low as 2.5 µM,
@@
 
+Potential niche expansions of clades of *P. marinus* into temperate regions
+vary depending on the season and the depth, which interact to govern both peak PAR levels and underwater photoperiods (Figure \@ref(fig:NichesMap).
+Temperate summer delivers ~12-14 hours of light, depending upon depth, above a photic threshold of 20 µmol photons m^-2^ s^-1^, while temperate spring/fall delivers ~9-11 hours; photoperiod ranges permissive for growth of all three *P.
+marinus*.
+In contrast temperate winter delivers shorter photoperiods which may exclude clade HLI.
+In parallel, excess peak PAR will exclude clades LLII/III and LLIV from most shallow niches, even under permissive temperatures.
+Expansion of OMZ drastically alters these patterns, by allowing clade LLIV to exploit a much wider range of lights, extending towards near-surface niches in both tropical and temperate zones, under permissive temperatures.
+
+\newpage
+
+```{r NichesMap, fig.cap = NichesMap_cap, fig.height = 20, fig.width = 20, echo = FALSE}
+
+NichesMap_cap <- glue(" Potential Future Niches for *Prochlorococcus* clades in a warming ocean. 
+The map shows current latitudinal distribution limits for *Prochlorococcus* (between green dashed lines), tropical and temperate  latitudinal regions (yellow bands). 
+Light levels, photoperiods and spectral bands, potentially permissive for growth of *Prochlorococcus* clades are determined by the interactions of latitude, season and depth attenuation of light.
+Potential clade occupancies under Full Oxygen (250 µM O~2~) are shown for 10-50 m and 100 m depths, in temperate vs.
+tropical regions, under depth-resolved photoperiods, approximating Winter Solstice, Equinox and Summer Solstice.
+Clade HLI is excluded from temperate depths by short photoperiods at Winter Solstice.
+Clades LLII/III are excluded from shallow depths by excessive light.
+Low Oxygen Zones (25 µM O~2~) drastically alter these potential occupancy patterns by excluding clade HLI from the temperate winter solstice at all depths, and by expanding the exploitation of higher light by Clade LLIV.
+Potential clade occupancies for the southern temperate zone mirror the northern temperate zone occupancies.",
+                       .sep = " ")
+
+knitr::include_graphics(file.path(FiguresIn, "NichesMap.png"))
+
+```
+
+\newpage
+
 # Summary and conclusions {.unnumbered}
 
-We analyzed growth rates for *P. marinus* clade HLI found near the ocean
-surface; clade LLII/III found deep in the water column; and clade LLIV
-also found in deep oceans, including OMZ, under a matrix of spectral
+We analyzed growth rates for *P. marinus* clade HLI usually found near the ocean
+surface; clade LLII/III found deeper in the water column; and clade LLIV
+also found in deep oceans, including current OMZ, under a matrix of spectral
 wavebands, irradiances, photoperiods and oxygen concentrations
@@
 representing high to low blue light levels, in the Pacific South East
-Ocean. Delmont and Eren [@delmontLinkingPangenomesMetagenomes2018] did
-not analyze data from depths beyond the subsurface chlorophyll maximum
-layer, nor did they report[O~2~] at depth. Our growth findings are
-consistent with Fig \@ref(fig:CladeProchloroPhotosynthDepthO2)
+Ocean. Our growth findings are consistent with Fig \@ref(fig:CladeProchloroPhotosynthDepthO2)
 showing PSII proteins annotated as MED4, clade HLI, at depths up to 200
@@
 genomic limitations on capacity for DNA repair (Fig \@ref(fig:DNARepairFig)), and possibly by limited capacity for synthesis of reactive oxygen quenchers (Fig \@ref(fig:ProchlorococcusEnzymeKms)).
-Our growth results are supported
-by Lavin *et al*. [@lavinNovelLineagesProchlorococcus2010] who found
+Our growth results are supported by Lavin *et al*.
+[@lavinNovelLineagesProchlorococcus2010] who found
 evidence of clades LLII/III and LLIV, using terminal restriction
 fragment length polymorphism analyses, at depths above 40 m, where light
-levels are higher, within OMZ, and by Fig \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSII protein subunits
-annotated as derived from SS120 at all depths ranging from 20 to 200 m
+levels are higher, within OMZ, and by Fig \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSII protein subunits annotated as derived from SS120 at all depths ranging from 20 to 200 m
 and all [O~2~] in an OMZ of the tropical North Pacific Ocean. SS120 grew
@@
 potential to inhabit future warmer temperate zones year-round, as it
-grows under a 4 h photoperiod, expected in winter, or at
+grows even under a 4 h photoperiod, expected in winter, or at
 light-attenuated depths. MIT9313 demonstrates an unexpected tolerance to
@@
 expand into broader ecological niches. Our results are supported by
-Fig \@ref(fig:CladeProchloroPhotosynthDepthO2) showing PSI protein
-subunits annotated as derived from MIT9313 detected at depths \> 120 m,
-along with PSII subunits at depths from 50 m to 200 m in regions where
+Fig \@ref(fig:CladeProchloroPhotosynthDepthO2) showing protein
+subunits derived from MIT9313 detected frequently at depths \> 120 m in regions where
 O~2~ was 15 µM. Bagby and Chisholm
@@
 @munoz-marinProchlorococcusCanUse2013] and amino acids
-[@zubkovDepthRelatedAmino2004]. In future work we aim to test whether
+[@zubkovDepthRelatedAmino2004]. In future work could test whether
 MIT9313 is using photosynthesis to drive CO~2~ fixation in low O~2~
@@
 Clade HLI (including MED4) is excluded from short photoperiod regimes, typical of temperate winter, or light attenuated depths.
-In contrast, clade LLIV (including MIT9313) might actually exploit higher light niches under OMZ conditions, where low O~2~ relieves the stresses of oxidation stress and PSII photoinhibition.
+In contrast, clade LLIV (including MIT9313) may exploit higher light niches under OMZ conditions, where low O~2~ relieves the stresses of oxidation stress and PSII photoinhibition.
 

### 2024-06-06 Code/Plots_ProNicheMap.Rmd
Map edits

@@
 ```{r save plot}
-ggsave(file = file.path(FigPath, paste("NichesMap",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
+#ggsave(file = file.path(FigPath, paste("NichesMap",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
 ```
@@
 
+# PhotoperiodDepthOMZ1<-PhotoperiodDepthOMZ %>% 
+# filter(DayofYear == "Summer Solstice")
+# PhotoperiodDepthOMZ1$nm <- c(400, 400, 700, 700)
+# PhotoperiodDepthOMZ1$de <- c(400, 400, 700, 700)
+# 
+# PhotoperiodDepthOMZ2<-PhotoperiodDepthOMZ %>% 
+# filter(DayofYear == "Winter Solstice")
+# PhotoperiodDepthOMZ2$nm <- c(400, 400, 700, 700)
+# 
+# PhotoperiodDepthOMZ3<-PhotoperiodDepthOMZ %>% 
+# filter(DayofYear == "Equinox")
+# PhotoperiodDepthOMZ3$nm <- c(400, 400, 700, 700)
+# 
+# PhotoperiodDepthOMZss<-rbind(PhotoperiodDepthOMZ1, PhotoperiodDepthOMZ2, PhotoperiodDepthOMZ3)
+
 NichesOMZEquat <- PhotoperiodDepthOMZ %>%
@@
 ggplot()+
+  # stat_wl_strip(aes(x = nm), ymin = "50 m", ymax = "100 m", alpha = 0.5, PhotoperiodDepthOMZss) +
+  # scale_fill_identity() +
   geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+

### 2024-06-06 Code/Plots_ProNicheMap.Rmd
Map edit

@@
         panel.grid.major = element_blank(),
-        axis.text = element_text(size=18),
-        axis.title = element_text(size=20),
+        axis.text = element_text(size=20),
+        axis.title = element_text(size=22),
         strip.background = element_rect(fill="white"),
@@
   geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
-  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6)  +
+  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6.5)  +
   labs(title = "Full Oxygen") +
@@
   theme_bw()+
-  theme(plot.title = element_text(size = 20),
+  theme(plot.title = element_text(size = 22),
         panel.grid.minor = element_blank(),
         panel.grid.major = element_blank(),
-        axis.text = element_text(size=18),
+        axis.text = element_text(size=20),
         #axis.title = element_text(size=14),
@@
   geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
-  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6)  +
+  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6.5)  +
   scale_x_continuous(breaks=seq(0, 25, by = 5)) +
@@
         panel.grid.major = element_blank(),
-        axis.text = element_text(size=18),
+        axis.text = element_text(size=20),
         #axis.title = element_text(size=14),
@@
   geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
-  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6)  +
+  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6.5)  +
   labs(title = "Oxygen Minimum Zone") +
@@
   theme_bw() +
-  theme(plot.title = element_text(size = 20),
+  theme(plot.title = element_text(size = 22),
         panel.grid.minor = element_blank(),
         panel.grid.major = element_blank(),
-        axis.text = element_text(size=18),
+        axis.text = element_text(size=20),
         #axis.title = element_text(size=14),

### 2024-06-06 Code/Manuscript_O2.Rmd
map discussion text edits

@@
 Potential niche expansions of clades of *P. marinus* into temperate regions
-vary depending on the season and the depth, which interact to govern both peak PAR levels and underwater photoperiods (Figure \@ref(fig:NichesMap).
+will vary depending on the season, and the depth, which interact to govern the growth limiting factors of peak PAR levels and underwater photoperiods (Figure \@ref(fig:NichesMap).
 Temperate summer delivers ~12-14 hours of light, depending upon depth, above a photic threshold of 20 µmol photons m^-2^ s^-1^, while temperate spring/fall delivers ~9-11 hours; photoperiod ranges permissive for growth of all three *P.
@@
 In parallel, excess peak PAR will exclude clades LLII/III and LLIV from most shallow niches, even under permissive temperatures.
-Expansion of OMZ drastically alters these patterns, by allowing clade LLIV to exploit a much wider range of lights, extending towards near-surface niches in both tropical and temperate zones, under permissive temperatures.
+
+Expansion of OMZ would drastically alter these patterns of potential niche extensions, by allowing clade LLIV to exploit a much wider range of lights, extending towards near-surface niches in both tropical and temperate zones, under permissive temperatures.
 

### 2024-06-06 Code/Manuscript_O2.Rmd
minor text edit to map discussion

@@
 
-Expansion of OMZ would drastically alter these patterns of potential niche extensions, by allowing clade LLIV to exploit a much wider range of lights, extending towards near-surface niches in both tropical and temperate zones, under permissive temperatures.
+Expansion of OMZ would drastically alter these patterns of potential niche extensions, by further restricting occurrences of clade HLI, but allowing clade LLIV to exploit a much wider range of lights, extending towards near-surface niches in both tropical and temperate zones, under permissive temperatures.
 

### 2024-06-06 Code/Plots_ProNicheMap.Rmd
Add rainbow

@@
 world_coordinates <- map_data("world") 
-
 # world_coordinates$facetsFuture <- 'Future~scenario'
@@
 
-# PhotoperiodDepthFullO2$facetsFull <- 'Full Oxygen'
-# PhotoperiodDepthOMZ$facetsOMZ <- 'Oxygen Minimum Zone'
+d=data.frame(x=c(-Inf,700,700), y=c(-Inf,-Inf,3), t=c('a', 'a', 'a'), r=c(1,2,3))
+
+PhotoperiodDepthFullO2<-PhotoperiodDepthFullO2
+PhotoperiodDepthFullO2$nm <- c(400, 400, 400, 400, 400, 400, 700, 700, 700, 700, 700, 700)
+
+PhotoperiodDepthOMZ<-PhotoperiodDepthOMZ
+PhotoperiodDepthOMZ$nm <- c(400, 400, 400, 400, 400, 400, 700, 700, 700, 700, 700, 700)
 
@@
                                 CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
-        TextLocation = 0) %>% 
+        TextLocation = 400) %>% 
 ggplot()+
-  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
+  geom_point(aes(x = nm, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
+  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = Inf, alpha = 0.3, PhotoperiodDepthFullO2) +
+  scale_fill_identity() +
+  # scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+  # coord_cartesian(xlim = c(0, 20)) +
+  coord_fixed(ratio = 55, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
+  #geom_ellipse(aes(x0 = 555, y0 = 1.43, a = 10, b = 2, angle = pi / 1), fill = "transparent", colour = "transparent") +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6.5)  +
+  ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
+  guides(color = "none") +
   labs(title = "Full Oxygen") +
-  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
-  coord_fixed(ratio = 2, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
-  ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both, DayofYear = label_value)) +
-  guides(color = "none") +
-  theme_bw()+
+  theme_bw() +
   theme(plot.title = element_text(size = 22),
@@
                                 CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
-        TextLocation = 0) %>% 
+        TextLocation = 400) %>% 
 ggplot()+
-  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
+  geom_point(aes(x = nm, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
+  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = Inf, alpha = 0.3, PhotoperiodDepthFullO2) +
+  scale_fill_identity() +
+  # scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+  # coord_cartesian(xlim = c(0, 20)) +
+  coord_fixed(ratio = 55, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
+  #geom_ellipse(aes(x0 = 555, y0 = 1.43, a = 10, b = 2, angle = pi / 1), fill = "transparent", colour = "transparent") +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6.5)  +
-  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
-  coord_fixed(ratio = 2, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
   ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
@@
                                 CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
-        TextLocation = 0) %>% 
+        TextLocation = 400) %>% 
 ggplot()+
-  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
+  geom_point(aes(x = nm, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
+  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = Inf, alpha = 0.3, PhotoperiodDepthOMZ) +
+  scale_fill_identity() +
+  # scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+  # coord_cartesian(xlim = c(0, 20)) +
+  coord_fixed(ratio = 55, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
+  #geom_ellipse(aes(x0 = 555, y0 = 1.43, a = 10, b = 2, angle = pi / 1), fill = "transparent", colour = "transparent") +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6.5)  +
-  labs(title = "Oxygen Minimum Zone") +
-  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
-  coord_fixed(ratio = 2, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
   ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
   guides(color = "none") +
+  labs(title = "Oxygen Minimum Zone") +
   theme_bw() +
@@
 NichesOMZNorth
-
-# PhotoperiodDepthOMZ1<-PhotoperiodDepthOMZ %>% 
-# filter(DayofYear == "Summer Solstice")
-# PhotoperiodDepthOMZ1$nm <- c(400, 400, 700, 700)
-# PhotoperiodDepthOMZ1$de <- c(400, 400, 700, 700)
-# 
-# PhotoperiodDepthOMZ2<-PhotoperiodDepthOMZ %>% 
-# filter(DayofYear == "Winter Solstice")
-# PhotoperiodDepthOMZ2$nm <- c(400, 400, 700, 700)
-# 
-# PhotoperiodDepthOMZ3<-PhotoperiodDepthOMZ %>% 
-# filter(DayofYear == "Equinox")
-# PhotoperiodDepthOMZ3$nm <- c(400, 400, 700, 700)
-# 
-# PhotoperiodDepthOMZss<-rbind(PhotoperiodDepthOMZ1, PhotoperiodDepthOMZ2, PhotoperiodDepthOMZ3)
 
@@
                                 CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
-        TextLocation = 0) %>%
+        TextLocation = 400) %>%
 
 ggplot()+
-  # stat_wl_strip(aes(x = nm), ymin = "50 m", ymax = "100 m", alpha = 0.5, PhotoperiodDepthOMZss) +
-  # scale_fill_identity() +
-  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
+  geom_point(aes(x = nm, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
+  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = Inf, alpha = 0.3, PhotoperiodDepthOMZ) +
+  scale_fill_identity() +
+  # scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+  # coord_cartesian(xlim = c(0, 20)) +
+  coord_fixed(ratio = 55, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
+  #geom_ellipse(aes(x0 = 555, y0 = 1.43, a = 10, b = 2, angle = pi / 1), fill = "transparent", colour = "transparent") +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6.5)  +
-  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
-  coord_fixed(ratio = 2, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
   ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
@@
 
+```{r, fig.height = 8, fig.width = 16, warning = FALSE}
+
+P1<-ggdraw() +
+  draw_plot(NichesFullO2North, x = 0.001, y = 0.695, width = .36, height = .22) +
+  draw_plot(NichesFullO2Equat, x = 0.001, y = 0.485, width = .36, height = .22) +
+  draw_plot(map, x = .179, y = .2, width = 0.8, height = 0.8) 
+P1
+
+P2<-ggdraw() +
+  draw_plot(NichesOMZNorth, x = 0.001, y = 0.695, width = .36, height = .22) +
+  draw_plot(NichesOMZEquat, x = 0.001, y = 0.485, width = .36, height = .22) +
+  draw_plot(map, x = .179, y = .2, width = 0.8, height = 0.8) 
+P2
+
+ggarrange(P1, P2, ncol = 1, nrow = 2)
+
+ggsave(file = file.path(FigPath, paste("NichesMap_2",".png",sep = "")), height=18, width= 20,  dpi = 300, limitsize = TRUE)
+```
+
+```{r save plot}
+ggsave(file = file.path(FigPath, paste("NichesMap_2",".png",sep = "")), height=8, width= 22,  dpi = 300, limitsize = TRUE)
+```
+
+---------------------------------------------------------------------------------------------------------------
+
+```{r read spectral depth backdrop}
+
+library("png")
+DepthBackdrop <- readPNG("DepthBackdrop.png")
+# Get dimensions of the image
+width <- dim(DepthBackdrop)[2]
+height <- dim(DepthBackdrop)[1]
+
+# Plot the image
+plot(1:width, type = "n", xlim = c(0, width), ylim = c(0, height),
+     xlab = "", ylab = "", axes =FALSE)
+rasterImage(DepthBackdrop, 0, 0, width, height)
+
+#points(PhotoperiodDepthFullO2$PhoticperiodPeakSatPAR_h, PhotoperiodDepthFullO2$DepthNames)
+
+```
+
 https://sape.inf.usi.ch/quick-reference/ggplot2/geom_polygon
@@
 ```{r}
-#FUll
-# world_coordinatesRainbow <- map_data("world")
-world_coordinatesRainbow$nm <- c(400, 700)
-
-data_text1 <- data.frame(label = c('~Clade~HLI'))
-data_text2 <- data.frame(label = c('~Clade~HLI'))
-data_text3 <- data.frame(label = c('~Clade~HLI'))
-
-data_text4 <- data.frame(label = c('Deep~(30~µE~","~4~h):~Clade~LLIV'))
-data_text5 <- data.frame(label = c('Deep~(30~µE~","~6~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-data_text6 <- data.frame(label = c('Deep~(30~µE~","~7~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-data_text7 <- data.frame(label = c('Deep~(30~µE~","~10~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-
-data_textFull <- data.frame(label = c('Oxygen:~Full'))
-data_textOMZ <- data.frame(label = c('Oxygen:~OMZ'))
+world_coordinatesRainbowSurface <- map_data("world") 
+world_coordinatesRainbowDepth <- map_data("world")
+
+world_coordinatesRainbowSurface$nm <- c(400, 700)
+world_coordinatesRainbowDepth$nm <- c(400, 550)
+
+data_textSurface <- data.frame(label = c('Near~Surface~(180~µE)'))
+data_textDepth <- data.frame(label = c('Deep~(30~µE)'))
 ```
@@
 d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-RainbowTropicFull<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 180, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 170, b = 40, angle = pi / 20), fill = "white", colour = "white") +
+ddepth=data.frame(x=c(400,700,700), y=c(160,160,260), t=c('a', 'a', 'a'), r=c(1,2,3))
+
+RainbowSurface<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 150, ymax = 200, alpha = 0.5, world_coordinatesRainbowSurface) +
+  scale_fill_identity() +
+  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "red", show.legend = F) +
+  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 40, angle = pi / 10), fill = "red", colour = "red") +
+  #geom_ellipse(aes(x0 = 555, y0 = 143, a = 170, b = 40, angle = pi / 20), fill = "white", colour = "white") +
   coord_fixed() +
@@
   coord_cartesian(ylim = c(70, 230)) +
-  geom_text(data=data_textFull, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_text2, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text6, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_textSurface, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
   theme_bw() +
@@
         legend.text = element_text(size=14))
-RainbowTropicFull
-
-RainbowWinterFull<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
+RainbowSurface
+
+RainbowSurface1<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbowSurface) +
   scale_fill_identity() +
   geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  #geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
   coord_fixed() +
@@
   coord_cartesian(ylim = c(70, 230)) +
-    geom_text(data=data_textFull, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_text1, aes(x=400, y=230, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text2, aes(x=400, y=220, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text3, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text4, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text6, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text7, aes(x=400, y=70, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_textDepth, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
   theme_bw() +
@@
         legend.text = element_text(size=14))
-RainbowWinterFull
-
-RainbowSpringFull<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+RainbowSurface1
+
+RainbowDepth1<-ggplot() +
+  stat_wl_strip(aes(x = nm), ymin = 180, ymax = 200, alpha = 0.5, world_coordinatesRainbowDepth) +
+  scale_fill_identity() +
+  geom_polygon(data=ddepth, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  #geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
+  #geom_ellipse(aes(x0 = 555, y0 = 143, a = 170, b = 40, angle = pi / 20), fill = "white", colour = "white") +
   coord_fixed() +
@@
   coord_cartesian(ylim = c(70, 230)) +
-    geom_text(data=data_textFull, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_text2, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text5, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) + 
-  geom_text(data=data_text6, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
+  geom_text(data=data_textSurface, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
   theme_bw() +
@@
         legend.text = element_text(size=14))
-RainbowSpringFull
-
-RainbowSummerFull<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(70, 230)) +
-    geom_text(data=data_textFull, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_text1, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text2, aes(x=400, y=220, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text3, aes(x=400, y=230, label=label, hjust=0), size=4.5, parse=TRUE) +
-
-  geom_text(data=data_text4, aes(x=400, y=70, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text6, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text7, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_blank(),
-        axis.title = element_blank(),
-        axis.ticks = element_blank(),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.text = element_text(size=14))
-RainbowSummerFull
+RainbowDepth1
 

### 2024-06-06 Code/Manuscript_O2.Rmd

@@
 NichesMap_cap <- glue(" Potential Future Niches for *Prochlorococcus* clades in a warming ocean. 
-The map shows current latitudinal distribution limits for *Prochlorococcus* (between green dashed lines), tropical and temperate  latitudinal regions (yellow bands). 
+The map shows current latitudinal distribution limits for *Prochlorococcus* (between green dashed lines), along with tropical and temperate  latitudinal regions (yellow bands). 
 Light levels, photoperiods and spectral bands, potentially permissive for growth of *Prochlorococcus* clades are determined by the interactions of latitude, season and depth attenuation of light.
@@
 Clade HLI is excluded from temperate depths by short photoperiods at Winter Solstice.
-Clades LLII/III are excluded from shallow depths by excessive light.
-Low Oxygen Zones (25 µM O~2~) drastically alter these potential occupancy patterns by excluding clade HLI from the temperate winter solstice at all depths, and by expanding the exploitation of higher light by Clade LLIV.
+Clades LLII/III and LLIV are excluded from shallow depths by excessive light.
+Low Oxygen Zones (25 µM O~2~) drastically alter these potential occupancy patterns by excluding clade HLI from the temperate winter solstice at all depths, and by expanding the exploitation of higher light zones by Clade LLIV.
 Potential clade occupancies for the southern temperate zone mirror the northern temperate zone occupancies.",

### 2024-06-07 Code/Manuscript_O2.Rmd
Fixed Equinox Lat 0, 100 m -added LLII and LLIV

--- 2024-06-06 Code/Manuscript_O2.Rmd
@@
 [@omarAnnotationGenesEncoding2023].
-We tabulated those genes encoding enzymes involved in DNA repair, present in at least one of the *P.marinus* study strains (Fig \@ref(fig:DNARepairFig).
+We tabulated those genes encoding enzymes involved in DNA repair, present in at least one of the *P.marinus* study strains (Fig \@ref(fig:DNARepairFig)).
 
@@
 Potential niche expansions of clades of *P. marinus* into temperate regions
-will vary depending on the season, and the depth, which interact to govern the growth limiting factors of peak PAR levels and underwater photoperiods (Figure \@ref(fig:NichesMap).
+will vary depending on the season, and the depth, which interact to govern the growth limiting factors of peak PAR levels and underwater photoperiods (Fig \@ref(fig:NichesMap)).
 Temperate summer delivers ~12-14 hours of light, depending upon depth, above a photic threshold of 20 µmol photons m^-2^ s^-1^, while temperate spring/fall delivers ~9-11 hours; photoperiod ranges permissive for growth of all three *P.
@@
 
-NichesMap_cap <- glue(" Potential Future Niches for *Prochlorococcus* clades in a warming ocean. 
-The map shows current latitudinal distribution limits for *Prochlorococcus* (between green dashed lines), tropical and temperate  latitudinal regions (yellow bands). 
-Light levels, photoperiods and spectral bands, potentially permissive for growth of *Prochlorococcus* clades are determined by the interactions of latitude, season and depth attenuation of light.
-Potential clade occupancies under Full Oxygen (250 µM O~2~) are shown for 10-50 m and 100 m depths, in temperate vs.
+NichesMap_cap <- glue("**Potential Future Niches for *Prochlorococcus* clades in a warming ocean.**",
+                      "The map shows current latitudinal distribution limits for *Prochlorococcus* (between green dashed lines), along with tropical and temperate  latitudinal regions (yellow bands).
+",
+"Light levels, photoperiods and spectral bands, potentially permissive for growth of *Prochlorococcus* clades are determined by the interactions of latitude, season and depth attenuation of light.",
+"Potential clade occupancies under Full Oxygen (250 µM O~2~) are shown for 10-50 m and 100 m depths, in temperate vs.
 tropical regions, under depth-resolved photoperiods, approximating Winter Solstice, Equinox and Summer Solstice.
 Clade HLI is excluded from temperate depths by short photoperiods at Winter Solstice.
-Clades LLII/III are excluded from shallow depths by excessive light.
-Low Oxygen Zones (25 µM O~2~) drastically alter these potential occupancy patterns by excluding clade HLI from the temperate winter solstice at all depths, and by expanding the exploitation of higher light by Clade LLIV.
-Potential clade occupancies for the southern temperate zone mirror the northern temperate zone occupancies.",
+Clades LLII/III and LLIV are excluded from shallow depths by excessive light.",
+"Low Oxygen Zones (25 µM O~2~) drastically alter these potential occupancy patterns by excluding clade HLI from the temperate winter solstice at all depths, and by expanding the exploitation of higher light zones by Clade LLIV.",
+"Potential clade occupancies for the southern temperate zone mirror the northern temperate zone occupancies.",
+
  .sep = " ")

### 2024-06-07 Code/Plots_ProNicheMap.Rmd
Fixed Equinox Lat 0, 100 m -added LLII and LLIV

@@
   mutate(CladeLLII_LLIII = case_when(DayofYear == "Winter Solstice" ~ 0,
-                                     DayofYear == "Equinox" & DepthNames == "50 m" & lat == 45 ~ 0,
-                                     DayofYear == "Equinox" & lat == 0 ~ 0,
+                                     DayofYear == "Equinox" & DepthNames == "50 m" ~ 0,
                                      DayofYear == "Summer Solstice" & lat == 45  ~ 0,
@@
                                DayofYear == "Winter Solstice" & DepthNames == "50 m" & lat == 0 ~ 0,
-                               DayofYear == "Equinox" & DepthNames == "50 m" & lat == 45 ~ 0,
-                               DayofYear == "Equinox" & lat == 0 ~ 0,
+                               DayofYear == "Equinox" & DepthNames == "50 m"  ~ 0,
                                DayofYear == "Summer Solstice" & lat == 45  ~ 0,
@@
 ```{r save plot}
-ggsave(file = file.path(FigPath, paste("NichesMap_2",".png",sep = "")), height=8, width= 22,  dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(FigPath, paste("NichesMap_2",".png",sep = "")), height=8, width= 22,  dpi = 300, limitsize = TRUE)
 ```

### 2024-06-07 Code/Plots_ProNicheMap.Rmd
Map - circle idea

--- 2024-06-06 Code/Plots_ProNicheMap.Rmd
@@
 fig.height = 10, fig.width = 6, warning = FALSE
-```{r create maps, fig.height = 8, fig.width = 10, warning = FALS}
+```{r create maps, fig.height = 8, fig.width = 10, warning = FALSE}
 
@@
    # geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
-    # geom_text(data=data_textWinterFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
-    # geom_text(data=data_textWinterFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
-    # geom_text(data=data_textWinterFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
-    # geom_text(data=data_textWinterFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
-    # geom_text(data=data_textWinterFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
-    # geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
-    # geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
@@
 map
+
+```
+
+```{r create maps, fig.height = 8, fig.width = 14, warning = FALSE}
+world_coordinates2 <- map_data("world") %>% 
+  filter(! long > 180)
+
+mapCircle<-ggplot() + 
+  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
+  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+    geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
+  geom_hline(yintercept = 40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
+  geom_hline(yintercept = -40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
+  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
+   # geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
+  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
+  coord_cartesian(ylim = c(-90, 90)) +
+  #coord_fixed(ratio = 2, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
+  labs(y = "Latitude", x = "Longitude") +
+  # ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
+  theme_bw() +
+  theme(panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_text(size=20),
+        axis.title = element_text(size=22),
+        strip.background = element_rect(fill="white"),
+        strip.text = element_text(size=20),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title.x = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_text(size=14)) +
+    coord_map("moll") 
+mapCircle
 
@@
 
+ggsave(file = file.path(FigPath, paste("NichesMap",".png",sep = "")), height=12, width= 28,  dpi = 300, limitsize = TRUE)
+
+ggdraw() +
+  draw_plot(NichesFullO2North, x = 0, y = 0.68, width = .26, height = .26) +
+  draw_plot(NichesFullO2Equat, x = 0, y = 0.51, width = .26, height = .26) +
+  draw_plot(mapCircle, x = .26, y = .29, width = 0.46, height = 0.7) +
+  draw_plot(NichesOMZNorth, x = 0.72, y = 0.68, width = .26, height = 0.26) +
+  draw_plot(NichesOMZEquat, x = 0.72, y = 0.51, width = .26, height = 0.26)
+
+ggsave(file = file.path(FigPath, paste("NichesMap_2",".png",sep = "")), height=12, width= 30,  dpi = 300, limitsize = TRUE)
 ```
@@
 ```{r save plot}
-ggsave(file = file.path(FigPath, paste("NichesMap",".png",sep = "")), height=12, width= 28,  dpi = 300, limitsize = TRUE)
+#ggsave(file = file.path(FigPath, paste("NichesMap",".png",sep = "")), height=12, width= 28,  dpi = 300, limitsize = TRUE)
+
+#ggsave(file = file.path(FigPath, paste("NichesMap_3",".png",sep = "")), height=12, width= 30,  dpi = 300, limitsize = TRUE)
 ```
@@
 
-ggsave(file = file.path(FigPath, paste("NichesMap_2",".png",sep = "")), height=18, width= 20,  dpi = 300, limitsize = TRUE)
-```
-
-```{r save plot}
-ggsave(file = file.path(FigPath, paste("NichesMap_2",".png",sep = "")), height=8, width= 22,  dpi = 300, limitsize = TRUE)
-```
-
+ggsave(file = file.path(FigPath, paste("NichesMap_3",".png",sep = "")), height=18, width= 20,  dpi = 300, limitsize = TRUE)
+```
+
+```{r, fig.height = 8, fig.width = 16, warning = FALSE}
+
+P1<-ggdraw() +
+  draw_plot(NichesFullO2North, x = 0.001, y = 0.750, width = .350, height = .22) +
+  draw_plot(NichesFullO2Equat, x = 0.001, y = 0.510, width = .350, height = .22) +
+  draw_plot(mapCircle, x = .350, y = .28, width = 0.7, height = 0.7) 
+P1
+
+P2<-ggdraw() +
+  draw_plot(NichesOMZNorth, x = 0.001, y = 0.750, width = .350, height = .22) +
+  draw_plot(NichesOMZEquat, x = 0.001, y = 0.510, width = .350, height = .22) +
+  draw_plot(mapCircle, x = .350, y = .28, width = 0.7, height = 0.7) 
+P2
+
+ggarrange(P1, P2, ncol = 1, nrow = 2)
+
+ggsave(file = file.path(FigPath, paste("NichesMap_4",".png",sep = "")), height=18, width= 21,  dpi = 300, limitsize = TRUE)
+```
+
+-----------------------------------------------------------------------------------------------------------------
+------------------------------------------- SySl End ----------------------------------------------------------
 ---------------------------------------------------------------------------------------------------------------
-
-```{r read spectral depth backdrop}
-
-library("png")
-DepthBackdrop <- readPNG("DepthBackdrop.png")
-# Get dimensions of the image
-width <- dim(DepthBackdrop)[2]
-height <- dim(DepthBackdrop)[1]
-
-# Plot the image
-plot(1:width, type = "n", xlim = c(0, width), ylim = c(0, height),
-     xlab = "", ylab = "", axes =FALSE)
-rasterImage(DepthBackdrop, 0, 0, width, height)
-
-#points(PhotoperiodDepthFullO2$PhoticperiodPeakSatPAR_h, PhotoperiodDepthFullO2$DepthNames)
-
-```
 

### 2024-06-07 Code/Plots_ProNicheMap.Rmd
Cleaning mess from yesterday (fixing version of circle globe map)

@@
 -------------------------------------------------------------------------------------------------------------------
----------------------------------------------- # SySl changes-----------------------------------------------------------
+---------------------------------------------- # SySl changes -----------------------------------------------------------
 ----------------------------------------------------------------------------------------------------------------
@@
 ggsave(file = file.path(FigPath, paste("NichesMap_4",".png",sep = "")), height=18, width= 21,  dpi = 300, limitsize = TRUE)
+
 ```

### 2024-06-07 Code/Plots_ProNicheMap.Rmd
Map - no rainbow

@@
   geom_point(aes(x = nm, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
-  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = Inf, alpha = 0.3, PhotoperiodDepthFullO2) +
-  scale_fill_identity() +
+  # stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = Inf, alpha = 0.3, PhotoperiodDepthFullO2) +
+  # scale_fill_identity() +
   # scale_x_continuous(breaks=seq(0, 25, by = 5)) +
@@
   #geom_ellipse(aes(x0 = 555, y0 = 1.43, a = 10, b = 2, angle = pi / 1), fill = "transparent", colour = "transparent") +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  #geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6.5)  +
@@
   geom_point(aes(x = nm, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
-  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = Inf, alpha = 0.3, PhotoperiodDepthOMZ) +
-  scale_fill_identity() +
+  # stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = Inf, alpha = 0.3, PhotoperiodDepthOMZ) +
+  # scale_fill_identity() +
   # scale_x_continuous(breaks=seq(0, 25, by = 5)) +

### 2024-06-07 Code/Manuscript_O2.Rmd
Added fig# for nichesmap.tiff

@@
 
+#  This is Fig10.tiff
 NichesMap_cap <- glue("**Potential Future Niches for *Prochlorococcus* clades in a warming ocean.**",

### 2024-06-09 Code/Plots_Genome.Rmd

@@
 ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms.png"), plot = ProchlorococcusEnzymeKms, height = 23, width = 17)
-ggsave(filename = file.path(PLOSFiguresRoundX, "Fig11.tiff"), plot = ProchlorococcusEnzymeKms, height = 20, width = 17, compression = "lzw")
+ggsave(filename = file.path(PLOSFiguresRoundX, "Fig8.tiff"), plot = ProchlorococcusEnzymeKms, height = 20, width = 17, compression = "lzw")
 # ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms_julie.png"), plot = ProchlorococcusEnzymeKms, height = 23, width = 17)
@@
 ggsave(filename = file.path(Figures, "DNARepairFig.png"), plot = DNARepairFig, height =5 , width = 5)
-ggsave(filename = file.path(PLOSFiguresRoundX, "Fig12.tiff"), plot = DNARepairFig, height =5 , width = 5, compression = "lzw")
+ggsave(filename = file.path(PLOSFiguresRoundX, "Fig9.tiff"), plot = DNARepairFig, height =5 , width = 5, compression = "lzw")
 ```

### 2024-06-09 Code/Plots_GAM.Rmd
Removed reference to Gompertz fits

@@
 plot(PicoLogGamAb, residuals = TRUE, pch = 1, all.terms = TRUE)
-
-#AIC of Gompertz-fitted model comparably low as to only-par and only-light model. 
-#Next step, fitting Strain-specific models. 
-#MED4 model to Par_ue-response falsely fits, due to badly fitted µ-rates -> cultures died, but model tried to fit anyway. Maybe filter everything below a certain R^2 in the fit?
 

### 2024-06-09 Code/Plots_ProNicheMap.Rmd
Regenerated a larger Niches figure and saved to .tiff

--- 2024-06-07 Code/Plots_ProNicheMap.Rmd
@@
 
-FigPath <- file.path("..", "Output", "Figures")
+PlotsOut <- file.path("..","Output", "Figures")
+PlotsOutPLOS <- file.path("..", "OutPut", "PLOSRound2")
 ```
@@
 ```{r read photoperiod depth data}
+
 PhotoperiodDepth <- readRDS(file = file.path("..", "Data", "ProcessedData", "DepthPhotoperiodTableFilter.Rds"))
 
+```
+
+```{r create df for full oxygen and OMZ potential niches}
+
+# add column for each clade with 1 for potential and 0 for no potential niche based on PAR at corresponding depths (50 and 100 m)   for temporal and equatorial zones.
 PhotoperiodDepthOMZ <- PhotoperiodDepth |>
@@
 
-library("png")
-DepthBackdrop <- readPNG("DepthBackdrop.png")
-# Get dimensions of the image
-width <- dim(DepthBackdrop)[2]
-height <- dim(DepthBackdrop)[1]
-
-# Plot the image
-plot(1:width, type = "n", xlim = c(0, width), ylim = c(0, height),
-     xlab = "", ylab = "", axes =FALSE)
-rasterImage(DepthBackdrop, 0, 0, width, height) 
-points(PhotoperiodDepthFullO2$PhoticperiodPeakSatPAR_h, PhotoperiodDepthFullO2$DepthNames, col = "red", pch = 16)
-
-```
+# library("png")
+# DepthBackdrop <- readPNG("DepthBackdrop.png")
+# # Get dimensions of the image
+# width <- dim(DepthBackdrop)[2]
+# height <- dim(DepthBackdrop)[1]
+# 
+# # Plot the image
+# plot(1:width, type = "n", xlim = c(0, width), ylim = c(0, height),
+#      xlab = "", ylab = "", axes =FALSE)
+# rasterImage(DepthBackdrop, 0, 0, width, height) 
+# points(PhotoperiodDepthFullO2$PhoticperiodPeakSatPAR_h, PhotoperiodDepthFullO2$DepthNames, col = "red", pch = 16)
+
+```
+
 #fig.height = 10, fig.width = 8, warning = FALSE
 ```{r, Niches figures}
-NichesFullO2North <- PhotoperiodDepthFullO2 %>%
-  filter(lat == 45) %>% 
-mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
-                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
-                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
-                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
-                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
-                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
-                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
-                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
-        TextLocation = 5) %>% 
-mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
-         lat = factor(lat, levels = c("45", "0"))) %>%
-ggplot()+
-  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
-            size = 0.5, alpha = 0, show.legend = TRUE)+
-  labs(title = "Full Oxygen") +
-  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
-    facet_grid(rows = vars(lat),
-              cols = vars(DayofYear),
-              labeller = labeller(lat = label_both, DayofYear = label_both)) +
-   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
-   # parse = TRUE,
-    hjust = 0,
-    vjust = 1,
-    size = 3
-  )  +
-  guides(color = "none") +
-  theme_bw()+
- theme(strip.text = element_text(size = 10),
-        axis.title = element_blank(),
-        # strip.text.x = element_text(size = 20),
-        axis.text.y = element_text(size = 10),
-        axis.text.x = element_blank(),
-        axis.ticks.x.bottom = element_blank(),
-        axis.ticks.y.left = element_blank(),
-        panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        plot.margin = unit(c(0,30,0,0), "pt"))
-
-NichesFullO2North
-
-NichesFullO2Equat <- PhotoperiodDepthFullO2 %>%
-  filter(lat == 0) %>% 
-mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
-                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
-                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
-                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
-                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
-                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
-                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
-                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
-        TextLocation = 5) %>% 
-mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
-         lat = factor(lat, levels = c("45", "0"))) %>%
-ggplot()+
-  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
-            size = 0.5, alpha = 0, show.legend = TRUE)+
+# 
+# 
+# NichesFullO2North <- PhotoperiodDepthFullO2 %>%
+#   filter(lat == 45) %>% 
+# mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
+#                                 CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
+#                                 CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
+#                                 CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
+#                                 CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
+#                                 CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
+#                                 CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
+#                                 CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
+#         TextLocation = 5) %>% 
+# mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
+#          lat = factor(lat, levels = c("45", "0"))) %>%
+# ggplot()+
+#   geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
+#             size = 0.5, alpha = 0, show.legend = TRUE)+
 #   labs(title = "Full Oxygen") +
-  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
-    facet_grid(rows = vars(lat),
-              cols = vars(DayofYear),
-              labeller = labeller(lat = label_both)) +
-   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
-   # parse = TRUE,
-    hjust = 0,
-    vjust = 1,
-    size = 3
-  )  +
-  guides(color = "none") +
-  theme_bw() +
- theme(strip.text.x = element_blank(),
-       strip.text.y = element_text(size = 10),
-        axis.title = element_blank(),
-        # strip.text.x = element_text(size = 20),
-        axis.text.y = element_text(size = 10),
-        # axis.text.y = element_blank(),
-        # axis.text.y = element_text(size = 5),
-         axis.text.x = element_blank(),
-        axis.ticks.x.bottom = element_blank(),
-        axis.ticks.y.left = element_blank(),
-        panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank())
-
-NichesFullO2Equat
-
-NichesOMZNorth <- PhotoperiodDepthOMZ %>%
-  filter(lat == 45) %>% 
-mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
-                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
-                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
-                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
-                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
-                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
-                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
-                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
-        TextLocation = 5) %>% 
-mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
-         lat = factor(lat, levels = c("45", "0"))) %>%
-ggplot()+
-  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
-            size = 0.5, alpha = 0, show.legend = TRUE)+
-   labs(title = "OMZ") +
-  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
-    facet_grid(rows = vars(lat),
-              cols = vars(DayofYear),
-              labeller = labeller(lat = label_both)) +
-   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
-   # parse = TRUE,
-    hjust = 0,
-    vjust = 1,
-    size = 3
-  )  +
-  guides(color = "none") +
-  theme_bw() +
- theme(strip.text.x = element_text(size = 10),
-       strip.text.y = element_text(size = 10),
-        axis.title = element_blank(),
-        # strip.text.x = element_text(size = 20),
-        axis.text.y = element_text(size = 10),
-        # axis.text.y = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x.bottom = element_blank(),
-        axis.ticks.y.left = element_blank(),
-        panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank())
-
-NichesOMZNorth
-
-NichesOMZEquat <- PhotoperiodDepthOMZ %>%
-  filter(lat == 0) %>% 
-mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
-                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
-                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
-                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
-                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
-                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
-                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
-                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
-        TextLocation = 5) %>% 
-mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
-         lat = factor(lat, levels = c("45", "0"))) %>%
-ggplot()+
-  geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
-            size = 0.5, alpha = 0, show.legend = TRUE)+
-  # labs(title = "Full Oxygen") +
-  scale_x_continuous(breaks=seq(0, 25, by = 5)) +
-    facet_grid(rows = vars(lat),
-              cols = vars(DayofYear),
-              labeller = labeller(lat = label_both)) +
-   geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
-   # parse = TRUE,
-    hjust = 0,
-    vjust = 1,
-    size = 3
-  )  +
-  guides(color = "none") +
-  theme_bw() +
- theme(strip.text.x = element_blank(),
-       strip.text.y = element_text(size = 10),
-        axis.title = element_blank(),
-        # strip.text.x = element_text(size = 20),
-        axis.text.y = element_text(size = 10),
-        # axis.text.y = element_blank(),
-         axis.text.x = element_blank(),
-        axis.ticks.x.bottom = element_blank(),
-        axis.ticks.y.left = element_blank(),
-        panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank())
-
-NichesOMZEquat
+#   scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+#     facet_grid(rows = vars(lat),
+#               cols = vars(DayofYear),
+#               labeller = labeller(lat = label_both, DayofYear = label_both)) +
+#    geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
+#    # parse = TRUE,
+#     hjust = 0,
+#     vjust = 1,
+#     size = 3
+#   )  +
+#   guides(color = "none") +
+#   theme_bw()+
+#  theme(strip.text = element_text(size = 10),
+#         axis.title = element_blank(),
+#         # strip.text.x = element_text(size = 20),
+#         axis.text.y = element_text(size = 10),
+#         axis.text.x = element_blank(),
+#         axis.ticks.x.bottom = element_blank(),
+#         axis.ticks.y.left = element_blank(),
+#         panel.grid.minor = element_blank(),
+#         panel.grid.major = element_blank(),
+#         plot.margin = unit(c(0,30,0,0), "pt"))
+# 
+# NichesFullO2North
+# 
+# NichesFullO2Equat <- PhotoperiodDepthFullO2 %>%
+#   filter(lat == 0) %>% 
+# mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
+#                                 CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
+#                                 CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
+#                                 CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
+#                                 CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
+#                                 CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
+#                                 CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
+#                                 CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
+#         TextLocation = 5) %>% 
+# mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
+#          lat = factor(lat, levels = c("45", "0"))) %>%
+# ggplot()+
+#   geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
+#             size = 0.5, alpha = 0, show.legend = TRUE)+
+#   # labs(title = "Full Oxygen") +
+#   scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+#     facet_grid(rows = vars(lat),
+#               cols = vars(DayofYear),
+#               labeller = labeller(lat = label_both)) +
+#    geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
+#    # parse = TRUE,
+#     hjust = 0,
+#     vjust = 1,
+#     size = 3
+#   )  +
+#   guides(color = "none") +
+#   theme_bw() +
+#  theme(strip.text.x = element_blank(),
+#        strip.text.y = element_text(size = 10),
+#         axis.title = element_blank(),
+#         # strip.text.x = element_text(size = 20),
+#         axis.text.y = element_text(size = 10),
+#         # axis.text.y = element_blank(),
+#         # axis.text.y = element_text(size = 5),
+#          axis.text.x = element_blank(),
+#         axis.ticks.x.bottom = element_blank(),
+#         axis.ticks.y.left = element_blank(),
+#         panel.grid.minor = element_blank(),
+#         panel.grid.major = element_blank())
+# 
+# NichesFullO2Equat
+# 
+# 
+# NichesOMZNorth <- PhotoperiodDepthOMZ %>%
+#   filter(lat == 45) %>% 
+# mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
+#                                 CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
+#                                 CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
+#                                 CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
+#                                 CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
+#                                 CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
+#                                 CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
+#                                 CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
+#         TextLocation = 5) %>% 
+# mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
+#          lat = factor(lat, levels = c("45", "0"))) %>%
+# ggplot()+
+#   geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
+#             size = 0.5, alpha = 0, show.legend = TRUE)+
+#    labs(title = "OMZ") +
+#   scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+#     facet_grid(rows = vars(lat),
+#               cols = vars(DayofYear),
+#               labeller = labeller(lat = label_both)) +
+#    geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
+#    # parse = TRUE,
+#     hjust = 0,
+#     vjust = 1,
+#     size = 3
+#   )  +
+#   guides(color = "none") +
+#   theme_bw() +
+#  theme(strip.text.x = element_text(size = 10),
+#        strip.text.y = element_text(size = 10),
+#         axis.title = element_blank(),
+#         # strip.text.x = element_text(size = 20),
+#         axis.text.y = element_text(size = 10),
+#         # axis.text.y = element_blank(),
+#         axis.text.x = element_blank(),
+#         axis.ticks.x.bottom = element_blank(),
+#         axis.ticks.y.left = element_blank(),
+#         panel.grid.minor = element_blank(),
+#         panel.grid.major = element_blank())
+# 
+# NichesOMZNorth
+# 
+# 
+# 
+# 
+# NichesOMZEquat <- PhotoperiodDepthOMZ %>%
+#   filter(lat == 0) %>% 
+# mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "Clade HLI",
+#                                 CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "Clades HLI, LLII/III",
+#                                 CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "Clades HLI, LLII/III, LLIV",
+#                                 CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "Clade LLII/III",
+#                                 CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "Clades LLII/III, LLIV",
+#                                 CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "Clade LLIV",
+#                                 CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "Clades HLI, LLIV",
+#                                 CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
+#         TextLocation = 5) %>% 
+# mutate(DepthNames = factor(DepthNames, levels = c("50 m", "100 m")),
+#          lat = factor(lat, levels = c("45", "0"))) %>%
+# ggplot()+
+#   geom_point(aes(x = PhoticperiodPeakSatPAR_h, y = DepthNames),
+#             size = 0.5, alpha = 0, show.legend = TRUE)+
+#   # labs(title = "Full Oxygen") +
+#   scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+#     facet_grid(rows = vars(lat),
+#               cols = vars(DayofYear),
+#               labeller = labeller(lat = label_both)) +
+#    geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE ),
+#    # parse = TRUE,
+#     hjust = 0,
+#     vjust = 1,
+#     size = 3
+#   )  +
+#   guides(color = "none") +
+#   theme_bw() +
+#  theme(strip.text.x = element_blank(),
+#        strip.text.y = element_text(size = 10),
+#         axis.title = element_blank(),
+#         # strip.text.x = element_text(size = 20),
+#         axis.text.y = element_text(size = 10),
+#         # axis.text.y = element_blank(),
+#          axis.text.x = element_blank(),
+#         axis.ticks.x.bottom = element_blank(),
+#         axis.ticks.y.left = element_blank(),
+#         panel.grid.minor = element_blank(),
+#         panel.grid.major = element_blank())
+# 
+# NichesOMZEquat
 
@@
 d5=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-40), y2=c(40))
-# 
-# data_textTropicFull <- data.frame(label = c('All~year'))
-# data_textTropicFull2 <- data.frame(label = c('12~h'))
-# data_textTropicFull3 <- data.frame(label = c('11/7~h'))
-# 
-# TropicFull<-ggplot() + 
-#   geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
-#   geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-#   geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
-#   geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
-#   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-#   geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
-#   geom_text(data=data_textTropicFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
-#   geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
-#   geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
-#   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
-#   coord_cartesian(ylim = c(-90, 120)) +
-#   labs(y = "Latitude", x = "Longitude") +
-#   ggh4x::facet_nested(rows = vars(facetsPresent), labeller = label_parsed, switch = "y") +
-#   theme_bw() +
-#   theme(panel.grid.minor = element_blank(),
-#         panel.grid.major = element_blank(),
-#         strip.placement = "outside",
-#         strip.switch.pad.grid = unit(1, "cm"),
-#         axis.text = element_text(size=14),
-#         axis.title = element_text(size=14),
-#         strip.background = element_rect(fill="white"),
-#         strip.text = element_text(size=18),
-#         axis.title.y = element_text(vjust = -15),
-#         #axis.title.x = element_text(margin=margin(t=10)),
-#         axis.title.x = element_blank(),
-#         axis.text.x = element_blank(),
-#         axis.ticks.x = element_blank(),
-#         legend.background = element_rect(fill="transparent"),
-#         legend.position = c(0.12,0.76),
-#         legend.key.height= unit(0.005, 'cm'),
-#         legend.spacing.x = unit(0.01, 'cm'),
-#         legend.text = element_text(size=14))
-# TropicFull
-
-# data_textWinterFull <- data.frame(label = c('Winter~or~summer~solstice'))
-# data_textWinterFull2 <- data.frame(label = c('9~h'))
-# data_textWinterFull3 <- data.frame(label = c('16~h'))
-# data_textWinterFull4 <- data.frame(label = c('8/4~h'))
-# data_textWinterFull5 <- data.frame(label = c('15/10~h'))
 
@@
     geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
-    # geom_text(data=data_textWinterFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
-    # geom_text(data=data_textWinterFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
-    # geom_text(data=data_textWinterFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
-    # geom_text(data=data_textWinterFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
-    # geom_text(data=data_textWinterFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
-    # geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
-    # geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
@@
 
-# data_textSpringFull <- data.frame(label = c('Vernal~equinox'))
-# data_textSpringFull2 <- data.frame(label = c('12~h'))
-# data_textSpringFull3 <- data.frame(label = c('12~h'))
-# 
-# data_textSpringFull4 <- data.frame(label = c('11/6~h'))
-# data_textSpringFull5 <- data.frame(label = c('11/6~h'))
-
 OMZmap<-ggplot() + 
@@
      geom_text(data=data_textB, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
-    # geom_text(data=data_textSpringFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
-    # geom_text(data=data_textSpringFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
-    # geom_text(data=data_textSpringFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
-    # geom_text(data=data_textSpringFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
-    # geom_text(data=data_textSpringFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
-    # geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
-    # geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
-    # 
   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
@@
 
-# data_textSummerFull <- data.frame(label = c('Summer~or~winter~solstice'))
-# data_textSummerFull2 <- data.frame(label = c('16~h'))
-# data_textSummerFull3 <- data.frame(label = c('9~h'))
-# data_textSummerFull4 <- data.frame(label = c('15/10~h'))
-# data_textSummerFull5 <- data.frame(label = c('8/4~h'))
-# SummerFull<-ggplot() + 
-#   geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
-#   geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-#   geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-#     geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-#   geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
-#   geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
-#   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-#     geom_text(data=data_textD, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
-#     geom_text(data=data_textSummerFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
-#     geom_text(data=data_textSummerFull2, aes(x=-180, y=50, label=label), size=3.5, parse=TRUE) +
-#     geom_text(data=data_textSummerFull3, aes(x=-180, y=-50, label=label), size=3.5, parse=TRUE) +
-#     geom_text(data=data_textSummerFull4, aes(x=180, y=50, label=label), size=3.5, parse=TRUE) +
-#     geom_text(data=data_textSummerFull5, aes(x=180, y=-50, label=label), size=3.5, parse=TRUE) +
-#       geom_text(data=data_textTropicFull2, aes(x=-180, y=0, label=label), size=3.5, parse=TRUE) +
-#       geom_text(data=data_textTropicFull3, aes(x=180, y=0, label=label), size=3.5, parse=TRUE) +
-#   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
-#   coord_cartesian(ylim = c(-90, 120)) +
-#   labs(y = "Latitude", x = "Longitude") +
-#   ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
-#   theme_bw() +
-#   theme(panel.grid.minor = element_blank(),
-#         panel.grid.major = element_blank(),
-#         strip.placement = "outside",
-#         strip.switch.pad.grid = unit(1, "cm"),
-#         axis.text = element_text(size=14),
-#         axis.title = element_text(size=14),
-#         strip.background = element_rect(fill="white"),
-#         strip.text = element_text(size=18),
-#         axis.title.y = element_text(vjust = -15),
-#         #axis.title.x = element_text(margin=margin(t=10)),
-#         axis.title.x = element_blank(),
-#         axis.text.x = element_blank(),
-#         axis.ticks.x = element_blank(),
-#         legend.background = element_rect(fill="transparent"),
-#         legend.position = c(0.12,0.76),
-#         legend.key.height= unit(0.005, 'cm'),
-#         legend.spacing.x = unit(0.01, 'cm'),
-#         legend.text = element_text(size=14))
-# SummerFull
-
-```
-
-```{r, warning = FALSE, fig.height = 15, fig.width = 20}
-
-FullO2<- (FullO2map + (plot_spacer()/NichesFullO2North/NichesFullO2Equat/plot_spacer())) +
-  plot_layout(widths = c(3,2), heights = c(4,0.5))
-FullO2
-
-OMZ<- (OMZmap + (plot_spacer()/NichesOMZNorth/NichesOMZEquat/plot_spacer())) +
-  plot_layout(widths = c(3,2), heights = c(4,0.5))
-OMZ
-
-NichesMap <- (FullO2map + (plot_spacer()/NichesFullO2North/NichesFullO2Equat/plot_spacer())) / (OMZmap + (plot_spacer()/NichesOMZNorth/NichesOMZEquat/plot_spacer()))
-
-NichesMap
-
-```
-
-```{r save plot}
-#ggsave(file = file.path(FigPath, paste("NichesMap",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
 ```
@@
 fig.height = 10, fig.width = 6, warning = FALSE
-```{r create maps, fig.height = 8, fig.width = 10, warning = FALSE}
+```{r create map, fig.height = 16, fig.width = 10, warning = FALSE}
 
@@
         axis.text = element_text(size=20),
-        axis.title = element_text(size=22),
+        axis.title = element_text(size=25),
         strip.background = element_rect(fill="white"),
@@
 
-```{r create maps, fig.height = 8, fig.width = 14, warning = FALSE}
+```{r create globe shape map, fig.height = 8, fig.width = 14, warning = FALSE}
 world_coordinates2 <- map_data("world") %>% 
@@
 
-#fig.height = 10, fig.width = 8, warning = FALSE
-   # parse = TRUE,
-    hjust = 0,
-    vjust = 1,
 ```{r, Niches figures, fig.height = 4, fig.width = 8, warning = FALSE}
@@
   #geom_ellipse(aes(x0 = 555, y0 = 1.43, a = 10, b = 2, angle = pi / 1), fill = "transparent", colour = "transparent") +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 6.5)  +
+  #geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 8)  +
   ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
@@
   theme_bw() +
-  theme(plot.title = element_text(size = 22),
+  theme(plot.title = element_text(size = 30),
         panel.grid.minor = element_blank(),
         panel.grid.major = element_blank(),
-        axis.text = element_text(size=20),
+        axis.text = element_text(size=25),
         #axis.title = element_text(size=14),
         strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=18),
+        strip.text = element_text(size=25),
         #axis.title.y = element_text(vjust = 1),
@@
         panel.grid.major = element_blank(),
-        axis.text = element_text(size=20),
+        axis.text = element_text(size=25),
         #axis.title = element_text(size=14),
         strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=18),
+        strip.text = element_text(size=25),
         #axis.title.y = element_text(vjust = 1),
@@
 
-```
-
-```{r}
-# P1<-(NichesFullO2North/NichesFullO2Equat)
-# P1
-# 
-# P2<- (NichesOMZNorth/NichesOMZEquat)
-# P2 
-# 
-# ggarrange(P1, map, P2, ncol = 3, nrow = 1)
+BlankPanel <- PhotoperiodDepthOMZ %>%
+  filter(lat == 0) %>% 
+mutate(TextLabel = (case_when(CladeHLI == 1 & CladeLLII_LLIII == 0 & CladeLLIV == 0 ~ "HLI",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 0 ~ "HLI, LLII/III",
+                                CladeHLI == 1 & CladeLLII_LLIII == 1 & CladeLLIV == 1 ~ "HLI, LLII/III, LLIV",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 0 ~ "LLII/III",
+                                CladeLLII_LLIII == 1 & CladeHLI == 0 & CladeLLIV == 1 ~ "LLII/III, LLIV",
+                                CladeLLIV == 1 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "LLIV",
+                                CladeLLIV == 1 & CladeHLI == 1 & CladeLLII_LLIII == 0 ~ "HLI, LLIV",
+                                CladeLLIV == 0 & CladeHLI == 0 & CladeLLII_LLIII == 0 ~ "")),
+        TextLocation = 400) %>%
+
+ggplot()+
+  geom_point(aes(x = nm, y = DepthNames), size = 0.5, alpha = 0, show.legend = TRUE)+
+  # stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = Inf, alpha = 0.3, PhotoperiodDepthOMZ) +
+  # scale_fill_identity() +
+  # scale_x_continuous(breaks=seq(0, 25, by = 5)) +
+  # coord_cartesian(xlim = c(0, 20)) +
+  coord_fixed(ratio = 55, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
+  #geom_ellipse(aes(x0 = 555, y0 = 1.43, a = 10, b = 2, angle = pi / 1), fill = "transparent", colour = "transparent") +
+  #geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
+  # geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 8)  +
+  ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
+  guides(color = "none") +
+  theme_bw() +
+  theme(plot.title = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.grid.major = element_blank(),
+        axis.text = element_blank(),
+        #axis.title = element_text(size=14),
+        strip.background = element_blank(),
+        strip.text = element_blank(),
+        #axis.title.y = element_text(vjust = 1),
+        #axis.title.x = element_text(margin=margin(t=10)),
+        axis.title = element_blank(),
+        axis.text.x = element_blank(),
+        axis.ticks = element_blank(),
+        panel.border =  element_blank(),
+        legend.background = element_rect(fill="transparent"),
+        legend.position = c(0.12,0.76),
+        legend.key.height= unit(0.005, 'cm'),
+        legend.spacing.x = unit(0.01, 'cm'),
+        legend.text = element_blank())
+
+BlankPanel
 
@@
 
-```{r, fig.height = 4, fig.width = 8, warning = FALSE}
-
-ggdraw() +
+```{r join figures, fig.height = 4, fig.width = 8, warning = FALSE}
+
+NichesMap_1 <- ggdraw() +
   draw_plot(NichesFullO2North, x = 0, y = 0.65, width = .3, height = .3) +
@@
 
-ggsave(file = file.path(FigPath, paste("NichesMap",".png",sep = "")), height=12, width= 28,  dpi = 300, limitsize = TRUE)
-
+```
+
+```{r save plot}
+
+# ggsave(file = file.path(PlotsOut, paste("NichesMap",".png",sep = "")), height=12, width= 28,  dpi = 300, limitsize = TRUE)
+# 
+# ggsave(file = file.path(PlotsOutPLOS, "Fig10.tiff"), plot = NichesMap, device = NULL, scale = 1, height=20, width= 30, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)
+
+```
+
+```{r}
 ggdraw() +
@@
 
-ggsave(file = file.path(FigPath, paste("NichesMap_2",".png",sep = "")), height=12, width= 30,  dpi = 300, limitsize = TRUE)
-```
-
-```{r save plot}
-#ggsave(file = file.path(FigPath, paste("NichesMap",".png",sep = "")), height=12, width= 28,  dpi = 300, limitsize = TRUE)
-
-#ggsave(file = file.path(FigPath, paste("NichesMap_3",".png",sep = "")), height=12, width= 30,  dpi = 300, limitsize = TRUE)
+# ggsave(file = file.path(PlotsOut, paste("NichesMap_2",".png",sep = "")), height=12, width= 28,  dpi = 300, limitsize = TRUE)
 ```
@@
 
-P1<-ggdraw() +
-  draw_plot(NichesFullO2North, x = 0.001, y = 0.695, width = .36, height = .22) +
-  draw_plot(NichesFullO2Equat, x = 0.001, y = 0.485, width = .36, height = .22) +
-  draw_plot(map, x = .179, y = .2, width = 0.8, height = 0.8) 
-P1
-
-P2<-ggdraw() +
-  draw_plot(NichesOMZNorth, x = 0.001, y = 0.695, width = .36, height = .22) +
-  draw_plot(NichesOMZEquat, x = 0.001, y = 0.485, width = .36, height = .22) +
-  draw_plot(map, x = .179, y = .2, width = 0.8, height = 0.8) 
-P2
-
-ggarrange(P1, P2, ncol = 1, nrow = 2)
-
-ggsave(file = file.path(FigPath, paste("NichesMap_3",".png",sep = "")), height=18, width= 20,  dpi = 300, limitsize = TRUE)
+# P1<-ggdraw() +
+#   draw_plot(NichesFullO2North, x = 0.001, y = 0.695, width = .36, height = .22) +
+#   draw_plot(NichesFullO2Equat, x = 0.001, y = 0.485, width = .36, height = .22) +
+#   draw_plot(map, x = .179, y = .2, width = 0.8, height = 0.8) 
+# P1
+# 
+# P2<-ggdraw() +
+#   draw_plot(NichesOMZNorth, x = 0.001, y = 0.695, width = .36, height = .22) +
+#   draw_plot(NichesOMZEquat, x = 0.001, y = 0.485, width = .36, height = .22) +
+#   draw_plot(map, x = .179, y = .2, width = 0.8, height = 0.8) 
+# P2
+# 
+# 
+# 
+# ggarrange(P1, P2, ncol = 1, nrow = 2,
+#           labels = c("A", "B"),  
+#           font.label = list(size = 25, color = "black"),
+#           align = "hv")
+
+# ggsave(file = file.path(PlotsOut, paste("NichesMap_3",".png",sep = "")), height=18, width= 20,  dpi = 300, limitsize = TRUE, bg='white')
+# 
+# ggsave(file = file.path(PlotsOutPLOS, "Fig10.tiff"), device = NULL, scale = 1, height=55, width= 55, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE, bg='white')
+```
+
+```{r NichesMap, fig.height = 8, fig.width = 16, warning = FALSE}
+
+LeftSide <-ggarrange(BlankPanel,NichesFullO2North, NichesFullO2Equat, BlankPanel,  ncol = 1, nrow = 4, heights = c(1, 2,2,3))
+FullO2 <- ggarrange(LeftSide, map, ncol = 2, nrow = 1)
+FullO2
+
+LeftSide <-ggarrange(BlankPanel, NichesOMZNorth, NichesOMZEquat, BlankPanel,  ncol = 1, nrow = 4 , heights = c(1, 2,2,3))
+FullOMZ <- ggarrange(LeftSide, map, ncol = 2, nrow = 1)
+FullOMZ
+
+NichesMap<- ggarrange(FullO2, FullOMZ, ncol = 1, nrow = 2,
+          labels = c("A", "B"),  
+          font.label = list(size = 30, color = "black"),
+          align = "hv")
+NichesMap
+
+ggsave(file = file.path(PlotsOut, paste("NichesMap",".png",sep = "")), plot = NichesMap, height=18, width= 20,  dpi = 300, limitsize = TRUE,  bg='white')
+
+ggsave(file = file.path(PlotsOutPLOS, "Fig10.tiff"), plot = NichesMap, device = NULL, scale = 1, height=55, width= 55, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE, bg='white')
 ```
@@
 
-ggsave(file = file.path(FigPath, paste("NichesMap_4",".png",sep = "")), height=18, width= 21,  dpi = 300, limitsize = TRUE)
+ggsave(file = file.path(PlotsOut, paste("NichesMap_4",".png",sep = "")), height=18, width= 21,  dpi = 300, limitsize = TRUE)
 
@@
 ---------------------------------------------------------------------------------------------------------------
-
-https://sape.inf.usi.ch/quick-reference/ggplot2/geom_polygon
-
-```{r, warning = FALSE, fig.height = 12, fig.width = 6}
-# OMZRainbow<- (TropicOMZRainbow/SpringOMZRainbow/SummerOMZRainbow/WinterOMZRainbow)
-# OMZRainbow                         
-```
-
-```{r, warning = FALSE, fig.height = 16, fig.width = 22}
-# MapCombo<-((TropicFull+TropicFullRainbow)+(TropicOMZ+TropicOMZRainbow))/((SpringFull+SpringFullRainbow)+(SpringOMZ+SpringOMZRainbow))/((SummerFull+SummerFullRainbow)+(SummerOMZ+SummerOMZRainbow))/((WinterFull+WinterFullRainbow)+(WinterOMZ+WinterOMZRainbow))
-# MapCombo                          
-```
-
-https://sape.inf.usi.ch/quick-reference/ggplot2/geom_polygon
-
-```{r}
-world_coordinatesRainbowSurface <- map_data("world") 
-world_coordinatesRainbowDepth <- map_data("world")
-
-world_coordinatesRainbowSurface$nm <- c(400, 700)
-world_coordinatesRainbowDepth$nm <- c(400, 550)
-
-data_textSurface <- data.frame(label = c('Near~Surface~(180~µE)'))
-data_textDepth <- data.frame(label = c('Deep~(30~µE)'))
-```
-
-```{r}
-#Full
-d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-ddepth=data.frame(x=c(400,700,700), y=c(160,160,260), t=c('a', 'a', 'a'), r=c(1,2,3))
-
-RainbowSurface<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 150, ymax = 200, alpha = 0.5, world_coordinatesRainbowSurface) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "red", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 40, angle = pi / 10), fill = "red", colour = "red") +
-  #geom_ellipse(aes(x0 = 555, y0 = 143, a = 170, b = 40, angle = pi / 20), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(70, 230)) +
-  geom_text(data=data_textSurface, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_blank(),
-        axis.title = element_blank(),
-        axis.ticks = element_blank(),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.text = element_text(size=14))
-RainbowSurface
-
-RainbowSurface1<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbowSurface) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  #geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(70, 230)) +
-  geom_text(data=data_textDepth, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_blank(),
-        axis.title = element_blank(),
-        axis.ticks = element_blank(),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.text = element_text(size=14))
-RainbowSurface1
-
-RainbowDepth1<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 180, ymax = 200, alpha = 0.5, world_coordinatesRainbowDepth) +
-  scale_fill_identity() +
-  geom_polygon(data=ddepth, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  #geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  #geom_ellipse(aes(x0 = 555, y0 = 143, a = 170, b = 40, angle = pi / 20), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(70, 230)) +
-  geom_text(data=data_textSurface, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_blank(),
-        axis.title = element_blank(),
-        axis.ticks = element_blank(),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.text = element_text(size=14))
-RainbowDepth1
-
-```
-
-```{r}
-#Full combo
-# world_coordinatesRainbow <- map_data("world")
-# world_coordinatesRainbow$nm <- c(400, 700)
-# 
-# data_text1 <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clade~HLI'))
-# data_text2 <- data.frame(label = c('Near~surface~(180~µE~","~11~h):~Clade~HLI'))
-# data_text3 <- data.frame(label = c('Near~surface~(180~µE~","~15~h):~Clade~HLI'))
-# 
-# data_text4 <- data.frame(label = c('Deep~(30~µE~","~4~h):~Clade~LLIV'))
-# data_text5 <- data.frame(label = c('Deep~(30~µE~","~6~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-# data_text6 <- data.frame(label = c('Deep~(30~µE~","~7~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-# data_text7 <- data.frame(label = c('Deep~(30~µE~","~10~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-# 
-# 
-# d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-# RainbowComboFull<-ggplot() +
-#   stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-#   scale_fill_identity() +
-#   geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-#   geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-#   coord_fixed() +
-#   scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-#   coord_cartesian(ylim = c(80, 220)) +
-#   geom_text(data=data_text1, aes(x=510, y=215, label=label), size=4.5, parse=TRUE) +
-#   geom_text(data=data_text2, aes(x=510, y=210, label=label), size=4.5, parse=TRUE) +
-#   geom_text(data=data_text3, aes(x=510, y=205, label=label), size=4.5, parse=TRUE) +
-#   
-#   geom_text(data=data_text4, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
-#   geom_text(data=data_text5, aes(x=530, y=85, label=label), size=4.5, parse=TRUE) + 
-#   geom_text(data=data_text6, aes(x=530, y=80, label=label), size=4.5, parse=TRUE) +
-#   geom_text(data=data_text7, aes(x=530, y=75, label=label), size=4.5, parse=TRUE) +
-#   theme_bw() +
-#   theme(panel.grid.minor = element_blank(),
-#         panel.grid.major = element_blank(),
-#         axis.text = element_blank(),
-#         axis.title = element_blank(),
-#         axis.ticks = element_blank(),
-#         strip.background = element_rect(fill="white"),
-#         strip.text = element_text(size=14),
-#         legend.background = element_rect(fill="transparent"),
-#         legend.position = c(0.12,0.76),
-#         legend.text = element_text(size=14))
-# RainbowComboFull
-
-```
-
-```{r}
-#OMZ
-world_coordinatesRainbow <- map_data("world")
-world_coordinatesRainbow$nm <- c(400, 700)
-
-data_text1d <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-data_text2d <- data.frame(label = c('Near~surface~(180~µE~","~11~h):~Clades~HLI~","~LLIV'))
-data_text3d <- data.frame(label = c('Near~surface~(180~µE~","~15~h):~Clades~HLI~","~LLIV'))
-
-data_text4d <- data.frame(label = c('Deep~(30~µE~","~4~h):~Clades~LLII/III~","~LLIV'))
-data_text5d <- data.frame(label = c('Deep~(30~µE~","~6~h):~Clades~LLII/III~","~LLIV'))
-data_text6d <- data.frame(label = c('Deep~(30~µE~","~7~h):~Clades~LLII/III~","~LLIV'))
-data_text7d <- data.frame(label = c('Deep~(30~µE~","~10~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-```
-
-```{r}
-#OMZ
-d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-RainbowTropicOMZ<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(70, 230)) +
-    geom_text(data=data_textOMZ, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_text2d, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text6d, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_blank(),
-        axis.title = element_blank(),
-        axis.ticks = element_blank(),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.text = element_text(size=14))
-RainbowTropicOMZ
-
-RainbowWinterOMZ<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(70, 230)) +
-      geom_text(data=data_textOMZ, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_text1d, aes(x=400, y=230, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text2d, aes(x=400, y=220, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text3d, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text4d, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text6d, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text7d, aes(x=400, y=70, label=label, hjust=0), size=4.5, parse=TRUE) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_blank(),
-        axis.title = element_blank(),
-        axis.ticks = element_blank(),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.text = element_text(size=14))
-RainbowWinterOMZ
-
-RainbowSpringOMZ<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(70, 230)) +
-      geom_text(data=data_textOMZ, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_text2d, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text5d, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) + 
-  geom_text(data=data_text6d, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_blank(),
-        axis.title = element_blank(),
-        axis.ticks = element_blank(),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.text = element_text(size=14))
-RainbowSpringOMZ
-
-RainbowSummerOMZ<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(70, 230)) +
-      geom_text(data=data_textOMZ, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_text1d, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text2d, aes(x=400, y=220, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text3d, aes(x=400, y=230, label=label, hjust=0), size=4.5, parse=TRUE) +
-
-  geom_text(data=data_text4d, aes(x=400, y=70, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text6d, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text7d, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        axis.text = element_blank(),
-        axis.title = element_blank(),
-        axis.ticks = element_blank(),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=14),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.text = element_text(size=14))
-RainbowSummerOMZ
-
-```
-
-```{r}
-#OMZ combo
-# world_coordinatesRainbow <- map_data("world")
-# world_coordinatesRainbow$nm <- c(400, 700)
-# 
-# data_text1d <- data.frame(label = c('Near~surface~(180~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-# data_text2d <- data.frame(label = c('Near~surface~(180~µE~","~11~h):~Clades~HLI~","~LLIV'))
-# data_text3d <- data.frame(label = c('Near~surface~(180~µE~","~15~h):~Clades~HLI~","~LLIV'))
-# 
-# data_text4d <- data.frame(label = c('Deep~(30~µE~","~4~h):~Clades~LLII/III~","~LLIV'))
-# data_text5d <- data.frame(label = c('Deep~(30~µE~","~6~h):~Clades~LLII/III~","~LLIV'))
-# data_text6d <- data.frame(label = c('Deep~(30~µE~","~7~h):~Clades~LLII/III~","~LLIV'))
-# data_text7d <- data.frame(label = c('Deep~(30~µE~","~10~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-# 
-# 
-# d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-# RainbowComboOMZ<-ggplot() +
-#   stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-#   scale_fill_identity() +
-#   geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-#   geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-#   coord_fixed() +
-#   scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-#   coord_cartesian(ylim = c(80, 220)) +
-#   geom_text(data=data_text1d, aes(x=510, y=215, label=label), size=4.5, parse=TRUE) +
-#   geom_text(data=data_text2d, aes(x=510, y=210, label=label), size=4.5, parse=TRUE) +
-#   geom_text(data=data_text3d, aes(x=510, y=205, label=label), size=4.5, parse=TRUE) +
-#   
-#   geom_text(data=data_text4d, aes(x=530, y=90, label=label), size=4.5, parse=TRUE) +
-#   geom_text(data=data_text5d, aes(x=530, y=85, label=label), size=4.5, parse=TRUE) + 
-#   geom_text(data=data_text6d, aes(x=530, y=80, label=label), size=4.5, parse=TRUE) +
-#   geom_text(data=data_text7d, aes(x=530, y=75, label=label), size=4.5, parse=TRUE) +
-#   theme_bw() +
-#   theme(panel.grid.minor = element_blank(),
-#         panel.grid.major = element_blank(),
-#         axis.text = element_blank(),
-#         axis.title = element_blank(),
-#         axis.ticks = element_blank(),
-#         strip.background = element_rect(fill="white"),
-#         strip.text = element_text(size=14),
-#         legend.background = element_rect(fill="transparent"),
-#         legend.position = c(0.12,0.76),
-#         legend.text = element_text(size=14))
-# RainbowComboOMZ
-
-```
-
-```{r, fig.height = 16, fig.width = 24}
-OMZRainbow<- (TropicFull+RainbowTropicFull+RainbowTropicOMZ)/(WinterFull+RainbowWinterFull+RainbowWinterOMZ)/(SpringFull+RainbowSpringFull+RainbowSpringOMZ)/(SummerFull+RainbowSummerFull+RainbowSummerOMZ)
-OMZRainbow
-```
-```{r save plot}
-#ggsave(file = file.path(FigPath, paste("MapComboPro_yeah",".png",sep = "")), height=16, width= 24,  dpi = 300, limitsize = TRUE)
-```
-
-# Save rds for further analysis
-
-```{r save rds}
-# saveRDS(object = CultureCatalog, file = file.path("..", "Data", "ImportedData", "ImportedMetaData", "CultureCatalog.Rds"), compress = "xz")
-```
-
-------------------------------------------------------------------------------------------------------------------------
-
-# Create map
-https://www.geeksforgeeks.org/how-to-make-world-map-with-ggplot2-in-r/
-
-```{r}
-world_coordinates2 <- map_data("world") %>% 
-  filter(! long > 180)
-
-world_coordinates2$facetsA <- '(A)~~~~All~year'
-world_coordinates2$facetsB <- '(B)~~~~Winter~or~summer~solstice'
-world_coordinates2$facetsC <- '(C)~~~~Vernal~equinox'
-world_coordinates2$facetsD <- '(D)~~~~Summer~or~winter~solstice'
-
-world_coordinates2$facetsPresent <- 'Present'
-world_coordinates2$facetsFuture <- 'Future~scenario'
-
-# data_textA <- data.frame(label = c('A'))
-# data_textB <- data.frame(label = c('B'))
-# data_textC <- data.frame(label = c('C'))
-# data_textD <- data.frame(label = c('D'))
-```
-
-```{r create map plot, fig.height = 4, fig.width = 6, warning = FALSE}
-
-d=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(35), y2=c(55))
-d2=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-35), y2=c(-55))
-d3=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-Inf), y2=c(Inf))
-d4=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-15), y2=c(15))
-d5=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-40), y2=c(40))
-
-data_textTropicFull <- data.frame(label = c('All~year'))
-data_textTropicFull2 <- data.frame(label = c('12~h'))
-data_textTropicFull3 <- data.frame(label = c('11/7~h'))
-
-TropicFull<-ggplot() + 
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=1) +
-  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_hline(yintercept = 40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
-  geom_hline(yintercept = -40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
-  #geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
-  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
-  # geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
-  # geom_text(data=data_textTropicFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_textTropicFull2, aes(x=-170, y=0, label=label), size=4.5, parse=TRUE) +
-  geom_text(data=data_textTropicFull3, aes(x=170, y=0, label=label), size=4.5, parse=TRUE) +
-  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
-  coord_cartesian(ylim = c(-90, 120)) +
-  labs(y = "Latitude", x = "Longitude") +
-  ggh4x::facet_nested(rows = vars(facetsPresent), cols = vars(facetsA), labeller = label_parsed, switch = "y") +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        strip.placement = "outside",
-        strip.switch.pad.grid = unit(0.5, "cm"),
-        axis.text = element_text(size=14),
-        axis.title = element_text(size=14),
-        strip.background = element_rect(fill="white"),
-        strip.text.x = element_text(size=18, hjust = 0),
-        strip.text.y = element_text(size=18),
-        axis.title.y = element_text(vjust = -15),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14)) +
-  coord_map("moll")  
-TropicFull
-
-data_textWinterFull <- data.frame(label = c('Winter~or~summer~solstice'))
-data_textWinterFull2 <- data.frame(label = c('9~h'))
-data_textWinterFull3 <- data.frame(label = c('16~h'))
-data_textWinterFull4 <- data.frame(label = c('8/4~h'))
-data_textWinterFull5 <- data.frame(label = c('15/10~h'))
-
-WinterFull<-ggplot() + 
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=1) +
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-    geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_hline(yintercept = 40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
-  geom_hline(yintercept = -40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
-  #geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
-  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
-    # geom_text(data=data_textB, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
-    # geom_text(data=data_textWinterFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
-    geom_text(data=data_textWinterFull2, aes(x=-160, y=45, label=label), size=4.5, parse=TRUE) +
-    geom_text(data=data_textWinterFull3, aes(x=-160, y=-45, label=label), size=4.5, parse=TRUE) +
-    geom_text(data=data_textWinterFull4, aes(x=160, y=45, label=label), size=4.5, parse=TRUE) +
-    geom_text(data=data_textWinterFull5, aes(x=160, y=-45, label=label), size=4.5, parse=TRUE) +
-    geom_text(data=data_textTropicFull2, aes(x=-170, y=0, label=label), size=4.5, parse=TRUE) +
-    geom_text(data=data_textTropicFull3, aes(x=170, y=0, label=label), size=4.5, parse=TRUE) +
-  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
-  coord_cartesian(ylim = c(-90, 120)) +
-  labs(y = "Latitude", x = "Longitude") +
-  ggh4x::facet_nested(rows = vars(facetsFuture), cols = vars(facetsB), labeller = label_parsed, switch = "y") +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        strip.placement = "outside",
-        strip.switch.pad.grid = unit(0.5, "cm"),
-        axis.text = element_text(size=14),
-        axis.title = element_text(size=14),
-        strip.background = element_rect(fill="white"),
-        strip.text.x = element_text(size=18, hjust = 0),
-        strip.text.y = element_text(size=18),
-        axis.title.y = element_text(vjust = -15),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14)) +
-  coord_map("moll") 
-WinterFull
-
-data_textSpringFull <- data.frame(label = c('Vernal~equinox'))
-data_textSpringFull2 <- data.frame(label = c('12~h'))
-data_textSpringFull3 <- data.frame(label = c('12~h'))
-data_textSpringFull4 <- data.frame(label = c('11/6~h'))
-data_textSpringFull5 <- data.frame(label = c('11/6~h'))
-
-SpringFull<-ggplot() + 
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=1) +
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_hline(yintercept = 40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
-  geom_hline(yintercept = -40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
-  #geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
-  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
-    # geom_text(data=data_textC, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
-    # geom_text(data=data_textSpringFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
-    geom_text(data=data_textSpringFull2, aes(x=-160, y=45, label=label), size=4.5, parse=TRUE) +
-    geom_text(data=data_textSpringFull3, aes(x=-160, y=-45, label=label), size=4.5, parse=TRUE) +
-    geom_text(data=data_textSpringFull4, aes(x=160, y=45, label=label), size=4.5, parse=TRUE) +
-    geom_text(data=data_textSpringFull5, aes(x=160, y=-45, label=label), size=4.5, parse=TRUE) +
-    geom_text(data=data_textTropicFull2, aes(x=-170, y=0, label=label), size=4.5, parse=TRUE) +
-    geom_text(data=data_textTropicFull3, aes(x=170, y=0, label=label), size=4.5, parse=TRUE) +
-  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
-  coord_cartesian(ylim = c(-90, 120)) +
-  labs(y = "Latitude", x = "Longitude") +
-  ggh4x::facet_nested(rows = vars(facetsFuture), cols = vars(facetsC), labeller = label_parsed, switch = "y") +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        strip.placement = "outside",
-        strip.switch.pad.grid = unit(0.5, "cm"),
-        axis.text = element_text(size=14),
-        axis.title = element_text(size=14),
-        strip.background = element_rect(fill="white"),
-        strip.text.x = element_text(size=18, hjust = 0),
-        strip.text.y = element_text(size=18),
-        axis.title.y = element_text(vjust = -15),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14)) +
-  coord_map("moll") 
-SpringFull
-
-data_textSummerFull <- data.frame(label = c('Summer~or~winter~solstice'))
-data_textSummerFull2 <- data.frame(label = c('16~h'))
-data_textSummerFull3 <- data.frame(label = c('9~h'))
-data_textSummerFull4 <- data.frame(label = c('15/10~h'))
-data_textSummerFull5 <- data.frame(label = c('8/4~h'))
-SummerFull<-ggplot() + 
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=1) +
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-    geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_hline(yintercept = 40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
-  geom_hline(yintercept = -40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
-  #geom_hline(yintercept = 60, fill = "white", color="white", linetype = "solid", alpha=1, size = 1) +
-  geom_map(data = world_coordinates2, map = world_coordinates2, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
-    # geom_text(data=data_textD, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
-    # geom_text(data=data_textSummerFull, aes(x=0, y=110, label=label), size=5, parse=TRUE) +
-    geom_text(data=data_textSummerFull2, aes(x=-160, y=45, label=label), size=4.5, parse=TRUE) +
-    geom_text(data=data_textSummerFull3, aes(x=-160, y=-45, label=label), size=4.5, parse=TRUE) +
-    geom_text(data=data_textSummerFull4, aes(x=160, y=45, label=label), size=4.5, parse=TRUE) +
-    geom_text(data=data_textSummerFull5, aes(x=160, y=-45, label=label), size=4.5, parse=TRUE) +
-      geom_text(data=data_textTropicFull2, aes(x=-170, y=0, label=label), size=4.5, parse=TRUE) +
-      geom_text(data=data_textTropicFull3, aes(x=170, y=0, label=label), size=4.5, parse=TRUE) +
-  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
-  coord_cartesian(ylim = c(-90, 120)) +
-  labs(y = "Latitude", x = "Longitude") +
-  ggh4x::facet_nested(rows = vars(facetsFuture), cols = vars(facetsD), labeller = label_parsed, switch = "y") +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        strip.placement = "outside",
-        strip.switch.pad.grid = unit(0.5, "cm"),
-        axis.text = element_text(size=14),
-        axis.title = element_text(size=14),
-        strip.background = element_rect(fill="white"),
-        strip.text.x = element_text(size=18, hjust = 0),
-        strip.text.y = element_text(size=18),
-        axis.title.y = element_text(vjust = -15),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14)) +
-  coord_map("moll") 
-SummerFull
-
-```
-
-```{r}
-#FUll
-world_coordinatesRainbow <- map_data("world")
-world_coordinatesRainbow$nm <- c(400, 700)
-
-world_coordinatesRainbow$facetsFull <- '~~~~Oxygen:~Full'
-world_coordinatesRainbow$facetsOMZ <- '~~~~Oxygen:~OMZ'
-
-data_text1 <- data.frame(label = c('Near~surface~"~10m"~(180~µE~","~8~h):~Clade~HLI'))
-data_text2 <- data.frame(label = c('Near~surface~"~10m"~(180~µE~","~11~h):~Clade~HLI'))
-data_text3 <- data.frame(label = c('Near~surface~"~10m"~(180~µE~","~15~h):~Clade~HLI'))
-
-data_text4 <- data.frame(label = c('Deep~"~100m"~(30~µE~","~4~h):~Clade~LLIV'))
-data_text5 <- data.frame(label = c('Deep~"~100m"~(30~µE~","~6~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-data_text6 <- data.frame(label = c('Deep~"~100m"~(30~µE~","~7~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-data_text7 <- data.frame(label = c('Deep~"~100m"~(30~µE~","~10~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-
-data_text1d <- data.frame(label = c('Near~surface~"~10m"~(180~µE~","~8~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-data_text2d <- data.frame(label = c('Near~surface~"~10m"~(180~µE~","~11~h):~Clades~HLI~","~LLIV'))
-data_text3d <- data.frame(label = c('Near~surface~"~10m"~(180~µE~","~15~h):~Clades~HLI~","~LLIV'))
-
-data_text4d <- data.frame(label = c('Deep~"~100m"~(30~µE~","~4~h):~Clades~LLII/III~","~LLIV'))
-data_text5d <- data.frame(label = c('Deep~"~100m"~(30~µE~","~6~h):~Clades~LLII/III~","~LLIV'))
-data_text6d <- data.frame(label = c('Deep~"~100m"~(30~µE~","~7~h):~Clades~LLII/III~","~LLIV'))
-data_text7d <- data.frame(label = c('Deep~"~100m"~(30~µE~","~10~h):~Clades~HLI~","~LLII/III~","~LLIV'))
-
-data_textFull <- data.frame(label = c('Oxygen:~Full'))
-data_textOMZ <- data.frame(label = c('Oxygen:~OMZ'))
-```
-
-```{r}
-#Full
-d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-RainbowTropicFull<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(70, 230)) +
-  #geom_text(data=data_textFull, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_text2, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text6, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
-  ggh4x::facet_nested(cols = vars(facetsFull), labeller = label_parsed) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        strip.placement = "outside",
-        strip.switch.pad.grid = unit(0.5, "cm"),
-        strip.background = element_rect(fill="white"),
-        strip.text.x = element_text(size=18, hjust = 0),
-        strip.text.y = element_text(size=18),
-        #axis.title.y = element_text(vjust = -15),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title = element_blank(),
-        axis.text = element_blank(),
-        axis.ticks = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14)) 
-RainbowTropicFull
-
-RainbowWinterFull<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(70, 230)) +
-    #geom_text(data=data_textFull, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_text1, aes(x=400, y=230, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text2, aes(x=400, y=220, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text3, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text4, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text6, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text7, aes(x=400, y=70, label=label, hjust=0), size=4.5, parse=TRUE) +
-    ggh4x::facet_nested(cols = vars(facetsFull), labeller = label_parsed) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        strip.placement = "outside",
-        strip.switch.pad.grid = unit(0.5, "cm"),
-        strip.background = element_rect(fill="white"),
-        strip.text.x = element_text(size=18, hjust = 0),
-        strip.text.y = element_text(size=18),
-        #axis.title.y = element_text(vjust = -15),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title = element_blank(),
-        axis.text = element_blank(),
-        axis.ticks = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14)) 
-RainbowWinterFull
-
-RainbowSpringFull<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(70, 230)) +
-    #geom_text(data=data_textFull, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_text2, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text5, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) + 
-  geom_text(data=data_text6, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
-    ggh4x::facet_nested(cols = vars(facetsFull), labeller = label_parsed) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        strip.placement = "outside",
-        strip.switch.pad.grid = unit(0.5, "cm"),
-        strip.background = element_rect(fill="white"),
-        strip.text.x = element_text(size=18, hjust = 0),
-        strip.text.y = element_text(size=18),
-        #axis.title.y = element_text(vjust = -15),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title = element_blank(),
-        axis.text = element_blank(),
-        axis.ticks = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14)) 
-RainbowSpringFull
-
-RainbowSummerFull<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(70, 230)) +
-    #geom_text(data=data_textFull, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_text1, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text2, aes(x=400, y=220, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text3, aes(x=400, y=230, label=label, hjust=0), size=4.5, parse=TRUE) +
-
-  geom_text(data=data_text4, aes(x=400, y=70, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text6, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text7, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
-    ggh4x::facet_nested(cols = vars(facetsFull), labeller = label_parsed) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        strip.placement = "outside",
-        strip.switch.pad.grid = unit(0.5, "cm"),
-        strip.background = element_rect(fill="white"),
-        strip.text.x = element_text(size=18, hjust = 0),
-        strip.text.y = element_text(size=18),
-        #axis.title.y = element_text(vjust = -15),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title = element_blank(),
-        axis.text = element_blank(),
-        axis.ticks = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14)) 
-RainbowSummerFull
-
-```
-
-```{r}
-#OMZ
-d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
-RainbowTropicOMZ<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(70, 230)) +
-    #geom_text(data=data_textOMZ, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_text2d, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text6d, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
-    ggh4x::facet_nested(cols = vars(facetsOMZ), labeller = label_parsed) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        strip.placement = "outside",
-        strip.switch.pad.grid = unit(0.5, "cm"),
-        strip.background = element_rect(fill="white"),
-        strip.text.x = element_text(size=18, hjust = 0),
-        strip.text.y = element_text(size=18),
-        #axis.title.y = element_text(vjust = -15),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title = element_blank(),
-        axis.text = element_blank(),
-        axis.ticks = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14)) 
-RainbowTropicOMZ
-
-RainbowWinterOMZ<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(70, 230)) +
-      #geom_text(data=data_textOMZ, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_text1d, aes(x=400, y=230, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text2d, aes(x=400, y=220, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text3d, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text4d, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text6d, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text7d, aes(x=400, y=70, label=label, hjust=0), size=4.5, parse=TRUE) +
-      ggh4x::facet_nested(cols = vars(facetsOMZ), labeller = label_parsed) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        strip.placement = "outside",
-        strip.switch.pad.grid = unit(0.5, "cm"),
-        strip.background = element_rect(fill="white"),
-        strip.text.x = element_text(size=18, hjust = 0),
-        strip.text.y = element_text(size=18),
-        #axis.title.y = element_text(vjust = -15),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title = element_blank(),
-        axis.text = element_blank(),
-        axis.ticks = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14)) 
-RainbowWinterOMZ
-
-RainbowSpringOMZ<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(70, 230)) +
-      #geom_text(data=data_textOMZ, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_text2d, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text5d, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) + 
-  geom_text(data=data_text6d, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
-      ggh4x::facet_nested(cols = vars(facetsOMZ), labeller = label_parsed) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        strip.placement = "outside",
-        strip.switch.pad.grid = unit(0.5, "cm"),
-        strip.background = element_rect(fill="white"),
-        strip.text.x = element_text(size=18, hjust = 0),
-        strip.text.y = element_text(size=18),
-        #axis.title.y = element_text(vjust = -15),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title = element_blank(),
-        axis.text = element_blank(),
-        axis.ticks = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14)) 
-RainbowSpringOMZ
-
-RainbowSummerOMZ<-ggplot() +
-  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
-  scale_fill_identity() +
-  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
-  coord_fixed() +
-  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
-  coord_cartesian(ylim = c(70, 230)) +
-      #geom_text(data=data_textOMZ, aes(x=650, y=230, label=label), size=5, parse=TRUE) +
-  geom_text(data=data_text1d, aes(x=400, y=210, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text2d, aes(x=400, y=220, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text3d, aes(x=400, y=230, label=label, hjust=0), size=4.5, parse=TRUE) +
-
-  geom_text(data=data_text4d, aes(x=400, y=70, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text6d, aes(x=400, y=80, label=label, hjust=0), size=4.5, parse=TRUE) +
-  geom_text(data=data_text7d, aes(x=400, y=90, label=label, hjust=0), size=4.5, parse=TRUE) +
-      ggh4x::facet_nested(cols = vars(facetsOMZ), labeller = label_parsed) +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        strip.placement = "outside",
-        strip.switch.pad.grid = unit(0.5, "cm"),
-        strip.background = element_rect(fill="white"),
-        strip.text.x = element_text(size=18, hjust = 0),
-        strip.text.y = element_text(size=18),
-        #axis.title.y = element_text(vjust = -15),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title = element_blank(),
-        axis.text = element_blank(),
-        axis.ticks = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14)) 
-RainbowSummerOMZ
-
-```
-
-```{r, fig.height = 16, fig.width = 24}
-OMZRainbow2<- (TropicFull+RainbowTropicFull+RainbowTropicOMZ)/(WinterFull+RainbowWinterFull+RainbowWinterOMZ)/(SpringFull+RainbowSpringFull+RainbowSpringOMZ)/(SummerFull+RainbowSummerFull+RainbowSummerOMZ)
-OMZRainbow2
-```

### 2024-06-09 Code/Manuscript_O2.Rmd
Knit

--- 2024-06-07 Code/Manuscript_O2.Rmd
@@
 
+#  This is Fig10.tiff
 NichesMap_cap <- glue("**Potential Future Niches for *Prochlorococcus* clades in a warming ocean.**",
-                      "The map shows current latitudinal distribution limits for *Prochlorococcus* (between green dashed lines), along with tropical and temperate  latitudinal regions (yellow bands).
-",
+                      "The maps shows current latitudinal distribution limits for *Prochlorococcus* (between green dashed lines), along with tropical and temperate  latitudinal regions (yellow bands).",
 "Light levels, photoperiods and spectral bands, potentially permissive for growth of *Prochlorococcus* clades are determined by the interactions of latitude, season and depth attenuation of light.",
-"Potential clade occupancies under Full Oxygen (250 µM O~2~) are shown for 10-50 m and 100 m depths, in temperate vs.
+"**A.** Potential clade occupancies under Full Oxygen (250 µM O~2~) are shown for 10-50 m and 100 m depths, in temperate vs.
 tropical regions, under depth-resolved photoperiods, approximating Winter Solstice, Equinox and Summer Solstice.
@@
 Clades LLII/III and LLIV are excluded from shallow depths by excessive light.",
-"Low Oxygen Zones (25 µM O~2~) drastically alter these potential occupancy patterns by excluding clade HLI from the temperate winter solstice at all depths, and by expanding the exploitation of higher light zones by Clade LLIV.",
+"**B.** Low Oxygen Zones (25 µM O~2~) drastically alter these potential occupancy patterns by excluding clade HLI from the temperate winter solstice at all depths, and by expanding the exploitation of higher light zones by Clade LLIV.",
 "Potential clade occupancies for the southern temperate zone mirror the northern temperate zone occupancies.",

### 2024-06-09 Code/Plots_GAM.Rmd
Regenerated .tiff

@@
 PlotsOut <- file.path("..","Output", "Figures")
-PlotsOutPLOS <- file.path("..", "OutPut", "PLOSFiguresRound1")
+PlotsOutPLOS <- file.path("..", "OutPut", "PLOSRound2")
 
@@
 
-# MED4PARGAM is Fig4.tiff for PLOSONE submission
- ggsave(file = file.path(PlotsOutPLOS, "Fig4.tiff", fsep = .Platform$file.sep), plot = MED4PARGAM, device = NULL, scale = 1,  height = 10, width = 10, compression = "lzw")
+# MED4PARGAM is Fig3.tiff for PLOSONE submission
+ ggsave(file = file.path(PlotsOutPLOS, "Fig3.tiff", fsep = .Platform$file.sep), plot = MED4PARGAM, device = NULL, scale = 1,  height = 16, width = 12, compression = "lzw")
 
@@
 
-# SS120PARGAM is Fig6.tiff for PLOSONE submission
- ggsave(file = file.path(PlotsOutPLOS, "Fig6.tiff", fsep = .Platform$file.sep), plot = LabelledCombinedGam, device = NULL, scale = 1,  height = 10, width = 10, compression = "lzw")
+# SS120PARGAM is Fig4.tiff for PLOSONE submission
+ ggsave(file = file.path(PlotsOutPLOS, "Fig4.tiff", fsep = .Platform$file.sep), plot = SS120PARGAM, device = NULL, scale = 1,  height = 16, width = 12, compression = "lzw")
 
@@
 
-# MIT9313PARGAM is Fig8.tiff for PLOSONE submission
- ggsave(file = file.path(PlotsOutPLOS, "Fig8.tiff", fsep = .Platform$file.sep), plot = LabelledCombinedGam, device = NULL, scale = 1,  height = 10, width = 10,  compression = "lzw")
-
-```
+# MIT9313PARGAM is Fig5.tiff for PLOSONE submission
+ ggsave(file = file.path(PlotsOutPLOS, "Fig5.tiff", fsep = .Platform$file.sep), plot = MIT9313PARGAM, device = NULL, scale = 1,  height = 18, width = 12,  compression = "lzw")
+
+```

### 2024-06-09 Code/Plots_Growth.Rmd
Removed PAR plot

@@
 
-# PAR plots
-```{r ParPlots, fig.height= 10, fig.width= 10}
-
-MED4PAR <- PURPARFits %>%
-   filter(Strain == "MED4",
-           Par_ue %in% c(30,90,180),
-          deltaOD_Lmu_corr == 0 |
-          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
-  mutate(PhotoperiodLabelTitle = "Photoperiod~(h)",
-         OxygenLabel = "Oxygen~concentration~(µM)",
-         WLlabelTitle = "Growth~wavelength~(nm)",
-         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
-         Par_ue = factor(Par_ue, levels = c(30, 90, 180))) %>%
-  ggplot()  +
-    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.75, show.legend = F) +
-   geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5, show.legend = F) +
-    geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 1) +
- labs( y = "Chlorophyll specific growth rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
-   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3, show.legend = F) +
-  scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
-   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
-  ggh4x::facet_nested(cols = vars(ParLabel, Par_ue), rows = vars(OxygenLabel, O2_uM), 
-                    labeller = label_parsed) + 
- guides(linetype = "none") +
-   theme_bw() +
-   theme( strip.text = element_text(size = 20),
-       axis.title.x.bottom = element_text(size = 28, color = "black", vjust = 1.0),
-      axis.title.y = element_text(size = 28, color = "black", vjust = 1.0),
-       axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
-       axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
-        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
-       axis.text.x.top = element_blank(),
-       axis.ticks.x.top = element_blank(),
-        # strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"),
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
-        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
-        legend.title = element_text(size = 25),  #change legend title font size
-        legend.text = element_text(size = 25),   #change legend text font size
-        legend.position = "top") +
-  labs(color = "Growth wavelength (nm)",
-       fill = "Growth wavelength (nm)")
-MED4PAR
-
-SS120PAR <- PURPARFits %>%
-   filter(Strain == "SS120",
-          Par_ue %in% c(30,90,180),
-          deltaOD_Lmu_corr == 0 |
-          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
-  mutate(PhotoperiodLabelTitle = "Photoperiod~(h)",
-         OxygenLabel = "Oxygen~concentration~(µM)",
-         WLlabelTitle = "Growth~wavelength~(nm)",
-         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
-         Par_ue = factor(Par_ue, levels = c(30, 90, 180))) %>%
-  ggplot() +
-    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.75, show.legend = F) +
-   geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5, show.legend = F) +
-    geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 1) +
- labs( y = "Chlorophyll specific growth rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
-   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3, show.legend = F) +
-  scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
-   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
-  ggh4x::facet_nested(cols = vars(ParLabel, Par_ue), rows = vars(OxygenLabel, O2_uM), 
-                    labeller = label_parsed) + 
- guides(linetype = "none") +
-   theme_bw() +
-   theme( strip.text = element_text(size = 20),
-       axis.title.x.bottom = element_text(size = 28, color = "black", vjust = 1.0),
-      axis.title.y = element_text(size = 28, color = "black", vjust = 1.0),
-       # axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
-       axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
-        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
-       axis.text.x.top = element_blank(),
-       axis.ticks.x.top = element_blank(),
-        # strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"),
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
-        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
-        legend.title = element_text(size = 25),  #change legend title font size
-        legend.text = element_text(size = 25),   #change legend text font size
-        legend.position = "top") +
-  labs(color = "Growth wavelength (nm)",
-       fill = "Growth wavelength (nm)")
-
-SS120PAR
-
-MIT9313PAR <- PURPARFits %>%
-   filter(Strain == "MIT9313",
-            Par_ue %in% c(30,90,180),
-          deltaOD_Lmu_corr == 0 |
-          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
-   mutate(PhotoperiodLabelTitle = "Photoperiod~(h)",
-         OxygenLabel = "Oxygen~concentration~(µM)",
-         WLlabelTitle = "Growth~wavelength~(nm)",
-         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
-         Par_ue = factor(Par_ue, levels = c(30, 90, 180))) %>%
-  ggplot() +
-    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.75, show.legend = F) +
-   geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5, show.legend = F) +
-    geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 1) +
- labs( y = "Chlorophyll specific growth rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
-   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3, show.legend = F) +
-  scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
-  # coord_cartesian(ylim = c (0, 0.07)) +
-  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450" )) +
-   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
-  ggh4x::facet_nested(cols = vars(ParLabel, Par_ue), rows = vars(OxygenLabel, O2_uM), 
-                    labeller = label_parsed) + 
- guides(linetype = "none") +
-   theme_bw() +
-   theme( strip.text = element_text(size = 20),
-       axis.title.x.bottom = element_text(size = 28, color = "black", vjust = 1.0),
-       axis.title.y = element_text(size = 28, color = "black", vjust = 1.0),
-       axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
-       axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
-        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
-       axis.text.x.top = element_blank(),
-       axis.ticks.x.top = element_blank(),
-        # strip.background=element_rect(color="grey87", fill = "grey82"),
-        # strip.background=element_rect(fill = "white"),
-        legend.key.size = unit(1, 'cm'), #change legend key size
-        legend.key.height = unit(1, 'cm'), #change legend key height
-        legend.key.width = unit(0.5, 'cm'), #change legend key width
-        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
-        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
-        legend.title = element_text(size = 25),  #change legend title font size
-        legend.text = element_text(size = 25),   #change legend text font size
-        legend.position = "top") +
-  labs(color = "Growth wavelength (nm)",
-       fill = "Growth wavelength (nm)" )
-
-MIT9313PAR
-```
-
-```{r, save PARPlots}
-
-ggsave(file = file.path(PlotsOut, paste("MED4PAR",".png",sep = "")), plot = MED4PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-ggsave(file = file.path(PlotsOutPLOS, "Fig3.tiff"), plot = MED4PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)
-
-ggsave(file = file.path(PlotsOut, paste("SS120PAR",".png",sep = "")), plot = SS120PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-ggsave(file = file.path(PlotsOutPLOS, "Fig5.tiff"), plot = SS120PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)
-
-ggsave(file = file.path(PlotsOut, paste("MIT9313PAR",".png",sep = "")), plot = MIT9313PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)
-
-ggsave(file = file.path(PlotsOutPLOS, "Fig7.tiff"), plot = MIT9313PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)
-
-```
-
 # Overlay whole cell absorbance with emission spectra all strain together

### 2024-06-09 Code/Plots_PURFits.Rmd
Generated PUR .tiff

@@
 
- ggsave(file = file.path(PlotsOutPLOS, paste("Fig9.tiff",sep = "")), plot = BluevsRedPurFitsPlots, device = NULL, scale = 1, height=40, width= 54, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)
+ ggsave(file = file.path(PlotsOutPLOS, paste("Fig6.tiff",sep = "")), plot = BluevsRedPurFitsPlots, device = NULL, scale = 1, height=40, width= 54, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)
 

### 2024-06-09 Code/Plots_OceanProtein.Rmd
Generated .tiff

@@
    ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "Figures", "CladeProchloroProteinMetabDepthO2.png")))
-   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSRound2", "Fig10.tiff")))
+   ggsave(plot = last_plot(), filename = (file.path("..", "OutPut", "PLOSRound2", "Fig7.tiff")))
 

### 2024-06-10 Code/Manuscript_O2.Rmd
added DOI
minor edit

@@
 Guided in part by the evidence of ocean distributions of proteins from
-*P. marinus* we set up a matrix of photoperiods, PAR, and [O~2~] to approximate current, and potential future, latitudinal, depth and seasonal niches for *P. marinus* strains. As
+*P. marinus*, we set up a matrix of photoperiods, PAR, and [O~2~] to approximate current, and potential future, latitudinal, depth and seasonal niches for *P. marinus* strains. As
 mentioned, growth rate trials under red light, although not representative of *P.
@@
 
-All data and metadata obtained from the Multicultivator were saved as comma separated
-values files and are available on the Borealis data repository (DOI pending).
+All data are available on the figshare data repository (10.6084/m9.figshare.25959061).
 

### 2024-06-10 Code/Plots_ProNicheMap.Rmd
Moved map to left side

@@
   guides(color = "none") +
-  labs(title = "Full Oxygen") +
+  labs(title = "Full Oxygen Zones") +
   theme_bw() +
@@
   guides(color = "none") +
-  labs(title = "Oxygen Minimum Zone") +
+  labs(title = "Low Oxygen Zones") +
   theme_bw() +
@@
 
-LeftSide <-ggarrange(BlankPanel,NichesFullO2North, NichesFullO2Equat, BlankPanel,  ncol = 1, nrow = 4, heights = c(1, 2,2,3))
-FullO2 <- ggarrange(LeftSide, map, ncol = 2, nrow = 1)
+RightSide <-ggarrange(BlankPanel,NichesFullO2North, NichesFullO2Equat, BlankPanel,  ncol = 1, nrow = 4, heights = c(1, 2,2,3))
+FullO2 <- ggarrange(map, RightSide, ncol = 2, nrow = 1)
 FullO2
 
-LeftSide <-ggarrange(BlankPanel, NichesOMZNorth, NichesOMZEquat, BlankPanel,  ncol = 1, nrow = 4 , heights = c(1, 2,2,3))
-FullOMZ <- ggarrange(LeftSide, map, ncol = 2, nrow = 1)
+RightSide <-ggarrange(BlankPanel, NichesOMZNorth, NichesOMZEquat, BlankPanel,  ncol = 1, nrow = 4 , heights = c(1, 2,2,3))
+FullOMZ <- ggarrange(map, RightSide,  ncol = 2, nrow = 1)
 FullOMZ

### 2024-06-10 Code/Manuscript_O2.Rmd
Knit with new map

@@
 The
-µ~max~ was `r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "25", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ (Table \@ref(tab:MaxGrowthTable)) achieved under 180 µmol photons m^-2^ s^-1^ blue light and 16 h photoperiod.
+µ~max~ was `r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "25", Photoperiod == 12) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)` d^-1^ (Table \@ref(tab:MaxGrowthTable)) achieved under 90 µmol photons m^-2^ s^-1^ blue light and 12 h photoperiod.
 The 4 h photoperiod experiments under white LED light were not performed as no growth was achieved when grown under an 8 h photoperiod of white LED light.
@@
 The growth rates for *Prochlorococcus marinus* SS120 clade LLII/III, under 250 µM O~2~, 30 µmol photons m^-2^ s^-1^ peak PAR and across all spectral wavebands,
-increased with longer photoperiods (Fig \@ref(fig:SS120PARGAM)).
+increased with longer photoperiods (Fig \@ref(fig:SS120PARGAM)A).
 No growth was observed under any blue light photoperiods when exposed to
@@
 photoperiod for red spectral waveband, however under blue light, SS120
-was able to grow (Fig \@ref(fig:SS120PARGAM)). In contrast to the growth rate
+was able to grow (Fig \@ref(fig:SS120PARGAM)A). In contrast to the growth rate
 trends of the 250 µM O~2~ and PAR of 90 µmol photons m^-2^ s^-1^
@@
 SS120 did not reproducibly grow when sparged to the lowest O~2~ of 2.5
-µM (Fig \@ref(fig:SS120PARGAM)). 2.5 µM O~2~ growth rate experiments were not
+µM (Fig \@ref(fig:SS120PARGAM)A). 2.5 µM O~2~ growth rate experiments were not
 conducted for 4 and 16 h photoperiods under peak PAR of 180 µmol photons
@@
 "Light levels, photoperiods and spectral bands, potentially permissive for growth of *Prochlorococcus* clades are determined by the interactions of latitude, season and depth attenuation of light.",
-"**A.** Potential clade occupancies under Full Oxygen (250 µM O~2~) are shown for 10-50 m and 100 m depths, in temperate vs.
+"**A.** Potential clade occupancies under Full Oxygen Zones (250 µM O~2~) are shown for 10-50 m and 100 m depths, in temperate vs.
 tropical regions, under depth-resolved photoperiods, approximating Winter Solstice, Equinox and Summer Solstice.

### 2024-06-10 Code/Manuscript_O2.Rmd
Fixed data availability section

@@
 
-All data are available on the figshare data repository (10.6084/m9.figshare.25959061).
-
-Annotated code for data import, transformations and analyses are
-available at
-<https://github.com/FundyPhytoPhys/prochlorococcus_o2/Code>.
+All data and annotated code for data import, transformations and analyses are
+available at are available on the figshare data repository (DOI: 10.6084/m9.figshare.25959061).
 

### 2024-06-10 Output/PLOSRound2/ResponsetoReviewers.txt
minor text edits to summary

@@
 "In warming oceans *P.
-marinus* clades will differentially expand into new regions depending upon their different, interacting capacities to tolerate and exploit photoperiods, light levels, and [O~2~].
-Competition among clades will be driven not simply by light levels.
+marinus* clades will differentially expand into new regions.
+Competition among clades will be driven not simply by light levels, but by their differing capacities to tolerate and exploit combinations of photoperiods, light levels, and [O~2~].
 Clade HLI (including MED4) is excluded from short photoperiod regimes, typical of temperate winter, or light attenuated depths.
-In contrast, clade LLIV (including MIT9313) might actually exploit higher light niches under OMZ conditions, where low O~2~ relieves the stresses of oxidation stress and PSII photoinhibition."
+In contrast, clade LLIV (including MIT9313) may exploit higher light niches under expanding OMZ conditions, where low O~2~ relieves the stresses of oxidation stress and PSII photoinhibition."
+
 Line:XXX

### 2024-06-10 Code/Manuscript_O2.Rmd
minor text edits to summary

@@
 In warming oceans *P.
-marinus* clades will differentially expand into new regions depending upon their different, interacting capacities to tolerate and exploit photoperiods, light levels, and [O~2~].
-Competition among clades will be driven not simply by light levels.
+marinus* clades will differentially expand into new regions.
+Competition among clades will be driven not simply by light levels, but by their differing capacities to tolerate and exploit combinations of photoperiods, light levels, and [O~2~].
 Clade HLI (including MED4) is excluded from short photoperiod regimes, typical of temperate winter, or light attenuated depths.
-In contrast, clade LLIV (including MIT9313) may exploit higher light niches under OMZ conditions, where low O~2~ relieves the stresses of oxidation stress and PSII photoinhibition.
+In contrast, clade LLIV (including MIT9313) may exploit higher light niches under expanding OMZ conditions, where low O~2~ relieves the stresses of oxidation stress and PSII photoinhibition.
 

### 2024-06-10 Code/Manuscript_O2.Rmd
minor edits

@@
 Clades LLII/III and LLIV are excluded from shallow depths by excessive light.",
-"**B.** Low Oxygen Zones (25 µM O~2~) drastically alter these potential occupancy patterns by excluding clade HLI from the temperate winter solstice at all depths, and by expanding the exploitation of higher light zones by Clade LLIV.",
+"**B.** Oxygen Minimum Zones (25 µM O~2~) drastically alter these potential occupancy patterns by excluding clade HLI from the temperate winter solstice at all depths, and by expanding the exploitation of higher light zones by Clade LLIV.",
 "Potential clade occupancies for the southern temperate zone mirror the northern temperate zone occupancies.",

### 2024-06-10 Output/PLOSRound2/ResponsetoReviewers.txt
edits to response to reviews

@@
 
-We thank you and the reviewers for constructive feedback, which we have addressed through extensive revisions, outlined below, which we believe have improved the manuscript.
+We thank you and the reviewers for constructive feedback, which we have addressed through extensive revisions, outlined in the response to reviewers, which we believe have improved the manuscript.
 

### 2024-06-10 Code/Plots_ProNicheMap.Rmd
Larger fonts for figures

@@
         panel.grid.major = element_blank(),
-        axis.text = element_text(size=20),
-        axis.title = element_text(size=25),
+        axis.text = element_text(size=25),
+        axis.title = element_text(size=28),
         strip.background = element_rect(fill="white"),
@@
         axis.text = element_text(size=20),
-        axis.title = element_text(size=25),
+        axis.title = element_text(size=28),
         strip.background = element_rect(fill="white"),
@@
         panel.grid.major = element_blank(),
-        axis.text = element_text(size=25),
+        axis.text = element_text(size=28),
         #axis.title = element_text(size=14),
         strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=25),
+        strip.text = element_text(size=28),
         #axis.title.y = element_text(vjust = 1),
@@
   guides(color = "none") +
-  labs(title = "Low Oxygen Zones") +
+  labs(title = "Oxygen Minimum Zones") +
   theme_bw() +

### 2024-06-10 Code/Plots_ProNicheMap.Rmd
fixed font size

@@
 
-```{r create maps, fig.height = 10, fig.width = 6, warning = FALSE}
-
-d=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(35), y2=c(55))
-d2=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-35), y2=c(-55))
-d3=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-Inf), y2=c(Inf))
-d4=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-15), y2=c(15))
-d5=data.frame(x1=c(-Inf), x2=c(Inf), y1=c(-40), y2=c(40))
-
-FullO2map<-ggplot() + 
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-    geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
-  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
-  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-    geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
-  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
-  coord_cartesian(ylim = c(-90, 120)) +
-  labs(y = "Latitude", x = "Longitude") +
-  # ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        strip.placement = "outside",
-        strip.switch.pad.grid = unit(1, "cm"),
-        axis.text = element_text(size=14),
-        axis.title = element_text(size=14),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=18),
-        axis.title.y = element_text(vjust = 1),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14))
-FullO2map
-
-OMZmap<-ggplot() + 
-  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
-  geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_rect(data=d2, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_hline(yintercept = 40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
-  geom_hline(yintercept = -40, fill = "transparent", color="olivedrab3", linetype = "dashed", alpha=1, size = 1) +
-  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
-     geom_text(data=data_textB, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
-  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
-  coord_cartesian(ylim = c(-90, 120)) +
-  labs(y = "Latitude", x = "Longitude") +
-  # ggh4x::facet_nested(rows = vars(facetsFuture), labeller = label_parsed, switch = "y") +
-  theme_bw() +
-  theme(panel.grid.minor = element_blank(),
-        panel.grid.major = element_blank(),
-        strip.placement = "outside",
-        strip.switch.pad.grid = unit(1, "cm"),
-        axis.text = element_text(size=14),
-        axis.title = element_text(size=14),
-        strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=18),
-        axis.title.y = element_text(vjust = 1),
-        #axis.title.x = element_text(margin=margin(t=10)),
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        legend.background = element_rect(fill="transparent"),
-        legend.position = c(0.12,0.76),
-        legend.key.height= unit(0.005, 'cm'),
-        legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14))
-OMZmap
-
-```
-
--------------------------------------------------------------------------------------------------------------------
----------------------------------------------- # SySl changes -----------------------------------------------------------
-----------------------------------------------------------------------------------------------------------------
-
-fig.height = 10, fig.width = 6, warning = FALSE
 ```{r create map, fig.height = 16, fig.width = 10, warning = FALSE}
@@
     geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "khaki1", color="khaki2", alpha=0.8) +
-  geom_hline(yintercept = 40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
-  geom_hline(yintercept = -40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1) +
-  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 0.2) +
+  geom_hline(yintercept = 40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1.5) +
+  geom_hline(yintercept = -40, fill = "transparent", color="chartreuse4", linetype = "dashed", alpha=1, size = 1.5) +
+  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 1.2) +
    # geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
@@
         panel.grid.major = element_blank(),
-        axis.text = element_text(size=25),
-        axis.title = element_text(size=28),
+        axis.text = element_text(size=28),
+        axis.title = element_text(size=30),
         strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=20),
+        strip.text = element_text(size=30),
         #axis.title.x = element_text(margin=margin(t=10)),
@@
         legend.spacing.x = unit(0.01, 'cm'),
-        legend.text = element_text(size=14)) 
+        legend.text = element_text(size=20)) 
 map
@@
   #geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
-  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 8)  +
+  geom_text(aes(x = TextLocation, y = DepthNames, label = paste(TextLabel), show.legend = FALSE), hjust = 0, size = 8.5)  +
   ggh4x::facet_nested(cols = vars(DayofYear), labeller = labeller(lat = label_both)) +
@@
         strip.background = element_rect(fill="white"),
-        strip.text = element_text(size=28),
+        strip.text = element_text(size=27),
         #axis.title.y = element_text(vjust = 1),
@@
 
-#Cool web about merging plots
-http://www.sthda.com/english/articles/24-ggpubr-publication-ready-plots/81-ggplot2-easy-way-to-mix-multiple-graphs-on-the-same-page/
-
-```{r join figures, fig.height = 4, fig.width = 8, warning = FALSE}
-
-NichesMap_1 <- ggdraw() +
-  draw_plot(NichesFullO2North, x = 0, y = 0.65, width = .3, height = .3) +
-  draw_plot(NichesFullO2Equat, x = 0, y = 0.455, width = .3, height = .3) +
-  draw_plot(map, x = .1, y = .2, width = 0.8, height = 0.8) +
-  draw_plot(NichesOMZNorth, x = 0.7, y = 0.65, width = .3, height = 0.3) +
-  draw_plot(NichesOMZEquat, x = 0.7, y = 0.455, width = .3, height = 0.3)
-
-```
-
-```{r save plot}
-
-# ggsave(file = file.path(PlotsOut, paste("NichesMap",".png",sep = "")), height=12, width= 28,  dpi = 300, limitsize = TRUE)
-# 
-# ggsave(file = file.path(PlotsOutPLOS, "Fig10.tiff"), plot = NichesMap, device = NULL, scale = 1, height=20, width= 30, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)
-
-```
-
-```{r}
-ggdraw() +
-  draw_plot(NichesFullO2North, x = 0, y = 0.68, width = .26, height = .26) +
-  draw_plot(NichesFullO2Equat, x = 0, y = 0.51, width = .26, height = .26) +
-  draw_plot(mapCircle, x = .26, y = .29, width = 0.46, height = 0.7) +
-  draw_plot(NichesOMZNorth, x = 0.72, y = 0.68, width = .26, height = 0.26) +
-  draw_plot(NichesOMZEquat, x = 0.72, y = 0.51, width = .26, height = 0.26)
-
-# ggsave(file = file.path(PlotsOut, paste("NichesMap_2",".png",sep = "")), height=12, width= 28,  dpi = 300, limitsize = TRUE)
-```
-
-```{r, fig.height = 8, fig.width = 16, warning = FALSE}
-
-# P1<-ggdraw() +
-#   draw_plot(NichesFullO2North, x = 0.001, y = 0.695, width = .36, height = .22) +
-#   draw_plot(NichesFullO2Equat, x = 0.001, y = 0.485, width = .36, height = .22) +
-#   draw_plot(map, x = .179, y = .2, width = 0.8, height = 0.8) 
-# P1
-# 
-# P2<-ggdraw() +
-#   draw_plot(NichesOMZNorth, x = 0.001, y = 0.695, width = .36, height = .22) +
-#   draw_plot(NichesOMZEquat, x = 0.001, y = 0.485, width = .36, height = .22) +
-#   draw_plot(map, x = .179, y = .2, width = 0.8, height = 0.8) 
-# P2
-# 
-# 
-# 
-# ggarrange(P1, P2, ncol = 1, nrow = 2,
-#           labels = c("A", "B"),  
-#           font.label = list(size = 25, color = "black"),
-#           align = "hv")
-
-# ggsave(file = file.path(PlotsOut, paste("NichesMap_3",".png",sep = "")), height=18, width= 20,  dpi = 300, limitsize = TRUE, bg='white')
-# 
-# ggsave(file = file.path(PlotsOutPLOS, "Fig10.tiff"), device = NULL, scale = 1, height=55, width= 55, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE, bg='white')
-```
-
 ```{r NichesMap, fig.height = 8, fig.width = 16, warning = FALSE}
@@
 ```
-
-```{r, fig.height = 8, fig.width = 16, warning = FALSE}
-
-P1<-ggdraw() +
-  draw_plot(NichesFullO2North, x = 0.001, y = 0.750, width = .350, height = .22) +
-  draw_plot(NichesFullO2Equat, x = 0.001, y = 0.510, width = .350, height = .22) +
-  draw_plot(mapCircle, x = .350, y = .28, width = 0.7, height = 0.7) 
-P1
-
-P2<-ggdraw() +
-  draw_plot(NichesOMZNorth, x = 0.001, y = 0.750, width = .350, height = .22) +
-  draw_plot(NichesOMZEquat, x = 0.001, y = 0.510, width = .350, height = .22) +
-  draw_plot(mapCircle, x = .350, y = .28, width = 0.7, height = 0.7) 
-P2
-
-ggarrange(P1, P2, ncol = 1, nrow = 2)
-
-ggsave(file = file.path(PlotsOut, paste("NichesMap_4",".png",sep = "")), height=18, width= 21,  dpi = 300, limitsize = TRUE)
-
-```
-
------------------------------------------------------------------------------------------------------------------
-------------------------------------------- SySl End ----------------------------------------------------------
----------------------------------------------------------------------------------------------------------------

### 2024-06-10 Code/Manuscript_O2.Rmd
minor edits

@@
 In warming oceans, range expansions and competition among clades will be governed not only by light levels.
-Short photoperiods governed by latitude, temperate winter, and depth attenuation of light, will exclude clade HLI (including MED4) from some habitats.
+Short photoperiods governed by latitude, temperate winters, and depth attenuation of light, will exclude clade HLI (including MED4) from some habitats.
 In contrast, clade LLII/III (including SS120), and particularly clade LLIV (including MIT9313), may exploit higher light niches nearer the surface, under expanding OMZ conditions, where low O~2~ relieves the stresses of oxidation stress and PSII photoinhibition.
@@
 The depth and [O~2~] (also from BCO-DMO at https://www.bco-dmo.org/dataset/646115/) were joined to protein sequence and BLASTP
-annotations by ID number, depth and station using *tidyverse* package
+annotations by ID number, depth and station using *tidyverse* packages
 [@R-tidyverse] running under R v4.1.3 and RStudio v2023.06.0 [@RStudio].
@@
 
-Similar to growth rate trends under 250 µM O~2~, MED4 maintained at 25 µM O~2~ showed fastest growth rate when the photoperiod was 16 h for each spectral waveband, across PAR levels (Fig \@ref(fig:MED4PARGAM)).
+Similar to growth rate trends under 250 µM O~2~, MED4 maintained at 25 µM O~2~ showed no growth under any imposed conditions under a 4 h photoperiod and the growth rate increased with higher imposed PAR and longer photoperiods (Fig \@ref(fig:MED4PARGAM)A).
 The
@@
 
-MED4 did not grow when sparged to the lowest [O~2~] of 2.5 µM (Fig \@ref(fig:MED4PARGAM)).
+MED4 did not grow when sparged to the lowest [O~2~] of 2.5 µM (Fig \@ref(fig:MED4PARGAM)A).
 2.5 µM O~2~ growth rate experiments were not conducted for 4 and 16 h photoperiods, as no reproducible growth occurred when MED4 was exposed to 8 and 12 h photoperiods under [O~2~] of 2.5 µM .
@@
 attenuation of light. The photoregimes of winter temperate zones, due to
-shorter photoperiods, exclude MED4 from growth at any depth, however
+shorter photoperiods, exclude MED4 from growth at deeper regions, however
 temperate photoperiods and light levels for the remainder of the year
@@
 photoperiods and showed growth inhibition at 12 and 16 h photoperiods
-under PAR of 180 µmol photons m^-2^ s^-1^ white LED, red or blue light.
+under PAR of 180 µmol photons m^-2^ s^-1^ white LED and growth inhibition across all photoperiods under red or blue light.
 The µ~max~ was
@@
 [@mooreComparativePhysiologySynechococcus1995] and are expected for a
-low light clade. The disjunct regions of the GAM plot results from
-variable growth success of SS120 under 250 µM O~2~. Growth rate patterns
-under red light and 250 µM O~2~were similar, although somewhat faster. In contrast,
+low light clade. Growth rate patterns
+under red light and 250 µM O~2~were similar, although somewhat faster. The disjunct regions of the GAM plot results from variable growth success of SS120 under 250 µM O~2~. In contrast,
 under 25 µM O~2~ and a photoperiod of 8 h SS120 exploited all blue peak
@@
 MIT9313 can exploit all blue or red PAR levels and most photoperiods under 25 µM O~2~ with 90^th^ percentile of fastest growth rate between 30 to 100 µmol photons m^-2^ s^-1^ blue PAR.
-MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 8 and 12 h and peak blue PAR between 50 to 100 µmol photons m^-2^ s^-1^ PAR.
+MIT9313 maintains growth even under 2.5 µM O~2~, under photoperiods between 8 and 12 h and peak blue PAR of \~100 µmol photons m^-2^ s^-1^.
 Thus the designation of
@@
 same photoperiods and peak PAR regimes. As such, only blue light
-experiments extend beyond a cumulative diel PUR of \~ 2 x 10^6^ µmol
+experiments extend beyond a cumulative diel PUR of \~2 x 10^6^ µmol
 photons m^-2^ d^-1^. This spectral bias in the range of PUR leads us to
@@
 [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] to increasing
-cumulative diel PUR, with saturation of growth rate achieved around 1.0
+cumulative diel PUR, with saturation of growth rate achieved around 3.0
 x 10^6^ µmol m^-2^d^-1^ (Fig \@ref(fig:BluevsRedPurFitsPlots)A and B),
@@
 light [@bergResponsesPsbAHli2011], by dissipating electrons from the
-inter-system transport chain. The approximate K~m~ for [O~2~] of \~ 25
+inter-system transport chain. The approximate K~m~ for [O~2~] of \~25
 µM for ubiquinol oxidase (non electrogenic) (Fig \@ref(fig:ProchlorococcusEnzymeKms)) is comparable to the lower limit
@@
 oxidase catalyzes the reaction of 2-hydroxy acid with O~2~ to produce
-toxic H~2~O~2~ [@cunaneCrystalStructureAnalysis2005], with an approximate K~m~ for [O~2~] of \~ 250 µM.
+toxic H~2~O~2~ [@cunaneCrystalStructureAnalysis2005], with an approximate K~m~ for [O~2~] of \~250 µM.
 Growth at lower [O~2~] may thus protect MIT9313 from auto-intoxication from production of H~2~O~2~ by (S)-2-hydroxy-acid oxidase.
@@
                                      "The solid circles represent K~m~ values from literature and the asterisks represent predicted values.",
-                                     "colours represent the gene counts.",
+                                     "Colours represent the gene counts.",
                                      "The red shaded area denotes a K~m~ oxygen concentration range from 230 to 280 µM.",
@@
 marinus*.
-In contrast temperate winter delivers shorter photoperiods which may exclude clade HLI.
+In contrast temperate winter delivers shorter photoperiods which may exclude clade HLI in deeper regions.
 In parallel, excess peak PAR will exclude clades LLII/III and LLIV from most shallow niches, even under permissive temperatures.
@@
 *Prochlorococcus marinus* MED4 requires more than 4 h of light per day;
-thus this strain will not exploit habitats typical of temperate winter
-or light attenuated depths, even if water temperatures warm into the
+thus this strain will not exploit habitats typical of temperate winters
+at light attenuated depths, even if water temperatures warm into the
 clade HLI tolerance range. MED4 is also excluded from the lowest oxygen
@@
 transcriptional analyses [@bergResponsesPsbAHli2011] suggest MED4 is
-excluded from growth below \~ 25 µM O~2~ because it relies upon a
+excluded from growth below \~25 µM O~2~ because it relies upon a
 ubiquinol oxidase, non-electrogenic, to maintain oxidation/reduction
@@
 carries a gene encoding (S)-2-hydroxy-acid oxidase
-[@cunaneCrystalStructureAnalysis2005], with a K~m~ for [O~2~] of \~ 250
+[@cunaneCrystalStructureAnalysis2005], with a K~m~ for [O~2~] of \~250
 µM (Fig \@ref(fig:ProchlorococcusEnzymeKms)), which produces
@@
 
-In warming oceans *P.
+In warming oceans, *P.
 marinus* clades will differentially expand into new regions.
 Competition among clades will be driven not simply by light levels, but by their differing capacities to tolerate and exploit combinations of photoperiods, light levels, and [O~2~].
-Clade HLI (including MED4) is excluded from short photoperiod regimes, typical of temperate winter, or light attenuated depths.
-In contrast, clade LLIV (including MIT9313) may exploit higher light niches under expanding OMZ conditions, where low O~2~ relieves the stresses of oxidation stress and PSII photoinhibition.
+Clade HLI (including MED4) is excluded from short photoperiod regimes, typical of temperate winters at light attenuated depths.
+In contrast, clade LLIV (including MIT9313) may exploit higher light niches under expanding OMZ conditions, where low O~2~ relieves the stresses of oxidative stress and PSII photoinhibition.
 
@@
 
+All data and annotated code are also available at https://github.com/FundyPhytoPhys/prochlorococcus_o2
+
 # Acknowledgements {.unnumbered}

### 2024-06-10 Code/Manuscript_O2.Rmd
minor edits

@@
 poleward regions of their distributions.
+Follett *et al*.
 @follettTrophicInteractionsHeterotrophic2022, however, model interactions of heterotrophic  bacteria  that may influence latitudinal expansions of *P.
@@
 Cultures thus took approximately 24 h to move gradually from maintenance photoregime to the peak PAR of the experimental photoregime.
-Cultures were grown for  xx to yy days, until they reached stationary phase at OD680 of approximately 0.4 to 0.8 after approximately 5 generations of growth.
+Cultures were grown for 7 to 14 days, until they reached stationary phase at OD680 of approximately 0.4 to 0.8 after approximately 5 generations of growth.
 
@@
 [@omarAnnotationGenesEncoding2023].
-We tabulated those genes encoding enzymes involved in DNA repair, present in at least one of the *P.marinus* study strains (Fig \@ref(fig:DNARepairFig)).
-
-*P. marinus* NATL2A and MED4 possess the largest,
+We tabulated those genes encoding enzymes involved in DNA repair, present in at least one of the *P.
+marinus* study strains (Fig \@ref(fig:DNARepairFig)).
+
+*Prochlorococcus marinus* NATL2A and MED4 possess the largest,
 most complete suites of genes encoding DNA repair enzymes.
@@
 marinus* SS120 and MIT9313 lack genes encoding deoxyribodipyrimidine photolyase and DNA repair ligase (ATP), which may explain, in part, why these two strains cannot tolerate growth under full  250 µM [O~2~] and high light, as found at the ocean surface.
-*P.
-marinus* SS120 and MIT9313 do, in contrast, tolerate light levels representative of the near surface ocean at 25 µM [O~2~].
+*Prochlorococcus marinus* SS120 and MIT9313 do, in contrast, tolerate light levels representative of the near surface ocean at 25 µM [O~2~].
 Our growth rate experiments did not include wavebands in the UV range, so we do not know whether the absence of deoxyribodipyrimidine photolyase would inhibit the growth rates of *P.
@@
   knitr::kable(.,
-             caption = "Enzymes shown in Figures \\@ref(fig:ProchlorococcusEnzymeKms),  \\@ref(fig:DNARepairFig) and \\@ref(fig:ProchlorococcusLightEnzymes) with their Enzyme Commission numbers (EC) and Kegg Orthology (KO).",
+             caption = "Enzymes shown in Fig \\@ref(fig:ProchlorococcusEnzymeKms),  \\@ref(fig:DNARepairFig) and \\@ref(fig:ProchlorococcusLightEnzymes) with their Enzyme Commission numbers (EC) and Kegg Orthology (KO).",
             col.names =  c(
@@
 MaxGrowthTable
+
 ```
@@
 McMackin (Mount Allison Students) assisted with culturing and setting up
-Multicultivator runs.
+multicultivator runs.
 

### 2024-06-10 Output/PLOSRound2/ResponsetoReviewers.txt
Added line #

@@
 
-XXX Check XXX
+Our reference list is complete.
 
@@
 the P. marinus radiation, with a preference for low light."
-Line: XXX
+Line: 64
 
@@
 This likely reflects an annotation assignment issue because the RUBISCO proteins are highly conserved, so assignments to strains or clades of Prochlorococcus may be ambiguous.
-We edited the figure #XXX to add 'jitter' offsets up to 15% of full axes scales, to visualize over-laid data points. 
-We edited the text in the revised manuscript to reflect the limitation of the annotation process as it pertains to the highly conserved RUBISCO complex: "Though present in the genome of MED4, the absence of proteins annotated as RUBISCO complex for Clade HLI, compared to annotated detections of RUBISCO across the other three clades suggests limitations in the OPP annotation process for highly conserved protein sequences."
-Line: XXX
+We edited the figure #2 to add 'jitter' offsets up to 15% of full axes scales, to visualize over-laid data points. 
+We edited the text in the revised manuscript to reflect the limitation of the annotation process as it pertains to the highly conserved RUBISCO complex: "Though present and expressed in the genome of MED4 [65], the absence of proteins annotated as RUBISCO complex for clade HLI, compared to annotated detections of RUBISCO across the other three clades, suggests limitations in the annotation process assigning highly conserved protein sequences to clades."
+Line: 394 to 398
 
@@
 
-- We revised the text from lines 668 to XXX to incorporate these helpful observations.
-The following was added: " Notwithstanding limitations on assignments of proteins to clades, detections of the abundant carbon fixation complex RUBISCO derived from HLI, LLI and LLII/III were notably absent from samples taken at lower [O~2~], suggesting limited capacity for carbon fixation by HLI,  LLI and LLII/III under low [O~2~] habitats."
+- We revised the text from lines 398 to 401 to incorporate these helpful observations.
+The following was added: "Notwithstanding limitations on assignments of proteins to clades, detections of the abundant carbon fixation complex RUBISCO derived from clades HLI, LLI and LLII/III were notably absent from stations at low [O2], suggesting limited capacity for carbon fixation by clades HLI, LLI and LLII/LLIII under low [O2] habitats."
 
@@
 
-We briefly motivated the inclusion of the red light growth trials, as mechanistically informative, at line XXX:
-" As mentioned, growth rate trials under red light, although not representative of *P.
+We briefly motivated the inclusion of the red light growth trials, as mechanistically informative, at line 432:
+"As mentioned, growth rate trials under red light, although not representative of *P.
 marinus* niches, are mechanistically informative [@murphyPhotoinactivationPhotosystemII2017] regarding photoinactivation of PSII."
 
--Through the Discussion, notably under the discussion of the GAM models and responses to growth rate to increasing PUR, we return to the responses to red light to show that some 'high light' limitations on growth are interpretable as photoinhibition of PSII, which is more severe under blue, compared to red, light, notably at lines XXXX-1032 (xXXX).
+-Through the Discussion, notably under the discussion of the GAM models and responses to growth rate to increasing PUR, we return to the responses to red light to show that some 'high light' limitations on growth are interpretable as photoinhibition of PSII, which is more severe under blue, compared to red, light, notably at lines 646-650.
 
@@
 -Thank you for the comment.
-
-XXXX  We added a new figure of potential strain growth in temperate seasonal and depth niches, in future temperate warmed oceans.
-The GAM model panels in figures XYZ show 'zones of exclusion' from light level, photoperiods, and oxygen regimes, as unshaded white areas where no growth is predicted.
-We indeed contemplated attempting global predicted distribution maps, but the interacting complexities of season, depth, changing extents of OMZ and extrapolation from culture growth, render it beyond the scope of this study.XXXX
-
-XXX
+We added a new figure (Fig 10) of potential clade occupancy in temperate and equatoral seasonal and depth niches, in future warmed oceans under full oxygen or oxygen minimum zones.
 
@@
 We edited the text:
-Line: XXX
+Lines: 454, 518, 586
 
@@
 -We edited the figure to clarify the fit lines:
-Line: XXX
 
@@
 -Thank you for bringing this to our attention.
-We clarified the wording on line XXXX of the revised manuscripted.
+We clarified the wording on line 720 of the revised manuscripted.
 "Protein homologies for FtsH isoforms between *Prochlorococcus marinus* and *Synechocystis* were extracted from @bonisteelStrainSpecificDifferences2018."
@@
 
--We apologize for the omissions. We revised the axis labels to make the log scaling more noticeable. The narrowness of the red bar (spanning 230 to 280 ?M) results from the log scaling of the y axis.
+-We apologize for the omissions.
+We revised the axis labels to make the log scaling more noticeable.
+The narrowness of the red bar (spanning 230 to 280 uM) results from the log scaling of the y axis.
+This is now Figure 8.
 
@@
 Thank you for your comment, the revised text now reads "DNA repair ligase".  
-Line: XXX
+Lines: 800, 803, 815
 
@@
 We agree.
-The added the following in the revised manuscript: "In this study we show that *P.
-marinus* SS120 and MIT9313 can tolerate light levels representative of the near ocean surface when the [O~2~] is 25 µM, however our growth rate experiments did not include wavebands in the UV range, we therefore do not know how the absence of deoxyribodipyrimidine photolyase under low [O~2] will impact the growth rates of *P.
-marinus* SS120 and MIT9313 when exposed to UV light."
-Lines: XXX
-To address the second part of your comment, the revised sentence now reads: "The absence of genes encoding deoxyribodipyrimidine photolyase and DNA ligase (ATP) in P.
-marinus MIT9313 and P.
-marinus SS120 may, in part, explain why these two strains cannot tolerate growth under full [O2] and high light, found at the ocean surface."
-Line: XXX
+The following was added in the revised manuscript: "Our growth rate experiments did not include wavebands in the UV range, so we do not know whether the absence of deoxyribodipyrimidine photolyase would inhibit the growth rates of P.
+marinus SS120 and MIT9313 under low [O2] if exposed to full spectrum, ocean surface light.
+"
+Lines: 806-809
+To address the second part of your comment, the revised sentence now reads: "Conversely, P.
+marinus SS120 and MIT9313 lack genes encoding deoxyribodipyrimidine photolyase and DNA repair ligase (ATP), which may explain, in part, why these two strains cannot tolerate growth under full 250 µM [O2] and high light, as found at the ocean surface."
+Lines: 802-805
 
@@
 
-Thank you for brining this to our attention, we removed phosphoglycolate phosphatase from the figure as it is indeed not directly involved in DNA repair but in clearing DNA damage repair products.
-Upon revisiting the interpretation of this figure, we edited the text: "As expected, *P. marinus* NATL2A possesses the largest,
-most complete suite of genes encoding DNA repair enzymes, followed by *P. marinus* MIT9313."
-Lines: XXX
+Thank you for bringing this to our attention, we removed phosphoglycolate phosphatase from the figure as it is indeed not directly involved in DNA repair but in clearing DNA damage repair products.
+This is now Figure 9.
+Upon revisiting the interpretation of this figure, we edited the text: "Prochlorococcus marinus NATL2A and MED4 possess the largest, most complete suites of genes encoding DNA repair enzymes."
+Lines: 796
 
@@
 We added the following to the Summary and Conclusion section:
-"In warming oceans *P.
-marinus* clades will differentially expand into new regions.
-Competition among clades will be driven not simply by light levels, but by their differing capacities to tolerate and exploit combinations of photoperiods, light levels, and [O~2~].
-Clade HLI (including MED4) is excluded from short photoperiod regimes, typical of temperate winter, or light attenuated depths.
-In contrast, clade LLIV (including MIT9313) may exploit higher light niches under expanding OMZ conditions, where low O~2~ relieves the stresses of oxidation stress and PSII photoinhibition."
-
-Line:XXX
+"In warming oceans, P.
+marinus clades will differentially expand into new regions.
+Competition among clades will be driven not simply by light levels, but by their differing capacities to tolerate and exploit combinations of photoperiods, light levels, and [O2].
+Clade HLI (including MED4) is excluded from short photoperiod regimes, typical of temperate winters at light attenuated depths.
+In contrast, clade LLIV (including MIT9313) may exploit higher light niches under expanding OMZ conditions, where low O2 relieves the stresses of oxidative stress and PSII photoinhibition."
+Lines:942-948
 
@@
 We added the following in the materials and methods section of the revised manuscript:
-"Each tube containing 70 mL of Pro99 media
-was inoculated around mid day of the 12 h maintenance photoperiod with 10 mL of growing maintenance preculture, to reach a starting OD680 of approximately 0.020.
-The tubes containing the cultures were then placed in the Multicultivator water bath set at 22?C, sparged with the experimental [O~2~], and kept at low light until late afternoon.
+"Each tube containing 70 mL of Pro99 media was inoculated around mid day of the 12 h maintenance photoperiod with 10 mL of growing maintenance preculture, to reach a starting OD680 of approximately 0.020.
+The tubes containing the cultures were then placed in the Multicultivator water bath set at 22°C, sparged with the experimental [O2], and kept at low light until late afternoon.
 Cultures were then in the dark for 12 to 16 hr until the photoregime of a sinusoidal photoperiod commenced the following morning, reaching peak PAR at noon each day.
 Cultures thus took approximately 24 h to move gradually from maintenance photoregime to the peak PAR of the experimental photoregime.
-Cultures were grown for  xx to yy days, until they reached stationary phase at OD680 of approximately 0.4 to 0.8 after approximately 5 generations of growth."
-Line: XXX
+Cultures were grown for 7 to 14 days, until they reached stationary phase at OD680 of approximately 0.4 to 0.8 after approximately 5 generations of growth."
+Lines: 237-247
 
@@
 2007)."
-Line: XXX
+Line: 434-439
 
@@
 
-In response to reviewer 1 and reviewer 2 we have combined the growth rate figure with the GAM model for each strain to faciliate comparisons. 
+In response to reviewer 1 and reviewer 2 we have combined the growth rate figure with the GAM model for each strain to faciliate comparisons. These are now figures 3-5. 
 We edited the abstract, results and discussion texts to better convey the motivations and findings of the study.
-In particular lines  XXX to YYY and XXXXX
 
@@
 
-We edited the text to use 'growth rate' throughout.
+Thank you for your suggestion. We edited the text to use 'growth rate' throughout.
 
@@
 
-We edited the text:
-Line: XXX
+We edited the text: "Despite its small cell size, "
+Line: 48
 
@@
 
-We edited the text in the revised manuscript: " Clades LLII and LLIII, including cultured strain SS120, are grouped together as early branching phylogenetic lineage in the *P.
+We edited the text in the revised manuscript: "Clades LLII and LLIII, including cultured strain SS120, are grouped together as early branching phylogenetic lineage in the *P.
 marinus* radiation, with a preference for low light."
-Line: XXX
+Line: 63
 
@@
 Thank you for  bringing this to our attention.
-We added the following text to the revised manuscript: "Follett et al 2022, however, model interactions of heterotrophic bacteria  that may influence latitudinal expansions of *P.
-marinus*."
-Line XXX:
+We added the following text to the revised manuscript: "Follett *et al*.
+, however, model interactions of heterotrophic  bacteria  that may influence latitudinal expansions of *P.
+marinus*"
+Line: 93
 
@@
 We edited the paragraph for clarity in the revised manuscript adding: "While the accuracy of strain specific protein annotations are limited due to the high conservation of the target protein complexes, the two step approach of peptide-to-spectrum matching using deep paired metagenomics, does assign proteins at the level of clades."
-Lines: XXX
+Lines: 215-218
 
@@
 Thank you for your comment.
-We edited the text in the revised manuscript: "*Prochlorococcus marinus* remain challenging to culture at high densities or under fluctuating environments, partially due to their dependence upon mutualistic heterotrophic bacteria to detoxify
-reactive oxygen species [48,49]." 
-Line XXX:
+We edited the text in the revised manuscript: "*Prochlorococcus marinus* remain challenging to culture at high densities or under fluctuating environments, partially due to their dependence upon mutualistic heterotrophic bacteria to detoxify reactive oxygen species [48,49]."
+Lines: 220-222
 
@@
 We edited the text in the revised manuscript: "Our analyses utilized a proteomics dataset; however, alternate approaches, such as metagenomics or metatranscriptomics, could have been employed to analyze ecotype abundances using the TARA Oceans [@pesantOpenScienceResources2015] dataset."
-Line: XXX
+Lines: 408-411
 
@@
 
-We edited the text: "The growth rate for Prochlorococcus marinus MED4, clade HLI, under 250 ?M O2, increased with higher imposed PAR and longer photoperiods (Fig 3A), across all spectral wavebands."
-Line XXX:
+We edited the text: "The growth rate for P. marinus MED4, clade HLI, under 250 µM O2, increased with higher imposed PAR and longer photoperiods (Fig 3A), across all spectral wavebands."
+Line: 447
 
@@
 Thank you for this comment. In this work we used 1 to 3 replicates depending on the experimental conditions. Specific number of replicates (shown as small dots in Figures (3 - 5)).
-We edited the text in the revised manuscript:" Consistent absence of growth of some strains under some levels of photoperiod, PAR, or [O~2~] meant we completed 268 growth factor treatment combinations with 1 to 3 replicates."
-Line: XXX
+We edited the text in the revised manuscript:"Consistent absence of growth of some strains under some levels of photoperiod, PAR, or [O2] meant we completed 268 growth rate factor treatment combinations with 1 to 3 replicates."
+Lines: 266-268
 
@@
 In particular blue light is absorbed well by chlorophyll, but is also directly absorbed by the manganese cluster of PSII, provoking one major path of photoinactivation, as discussed in Murphy et al.
-2017, and cited at lines XXX, YYY, ZZZ.
+2017, and cited at lines 307, 434, 648, 663, 676, and 894 .
 In contrast, red light is absorbed well by chlorophyll, driving photosynthesis, but does not provoke direct photoinactivation of the PSII manganese cluster, lowering the metabolic cost of maintaining the photosynthetic system, compared to equivalent rates of photosynthesis driven by blue light.
@@
 
-"...MED4 achieved
-more growth per unit diel cumulative PUR (Fig \@ref(fig:BluevsRedPurFitsPlots)A and B), consistent with Murphy *et al*. [@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for
-growth under red light, for MED4, because red light provokes less
-photoinactivation of PSII, than equivalent levels of blue light. For
-distinct fits for different photoperiods refer to Fig \@ref(fig:PhotoperiodPurFitsPlots) A-C..."
+"...MED4 achieved more growth per unit diel cumulative PUR (Fig 6A and B), consistent with Murphy *et al*.
+[@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for growth under red light, for MED4, because red light provokes less photoinactivation of PSII, than equivalent levels of blue light.
+For
+distinct fits for different photoperiods refer to S4A-C Fig..." 
+Lines: 647-650
 
@@
 
-Thank you for your suggestion. We combined the growth rate figure with the GAM model for each strain. We believe this will aid the reader with interpreting both plots.
+Thank you for your suggestion. We combined the growth rate figure with the GAM model for each strain. We believe this will aid the reader with interpreting both plots. These are now figures 3 to 5.
 
@@
 An analyses of mass spectrophotometric proteomic detection limits is beyond the scope of the paper.
-We however edited the figure #XXX to add 'jitter' offsets up to 15% of full axes scales, to visualize multiple previously over-laid data points.
+We however edited figures 2 and 7 to add 'jitter' offsets up to 15% of full axes scales, to visualize multiple previously over-laid data points.

### 2024-06-10 Code/Manuscript_O2.Rmd
minor edit

@@
 # This is S5_Fig.tiff 
-ProchlorococcusLightEnzymes_cap <- glue("***P. marinus* genes encoding enzymes activated or inhibited by light.**",
+ProchlorococcusLightEnzymes_cap <- glue("***Prochlorococcus marinus* genes encoding enzymes activated or inhibited by light.**",
                          "The y-axis represents *Prochlorococcus marinus* strains.",

### 2024-06-10 Code/Manuscript_O2.Rmd
minor edits

@@
 
-All data and annotated code for data import, transformations and analyses are
-available at are available on the figshare data repository (DOI: 10.6084/m9.figshare.25959061).
+All data and annotated code for data import, transformations and analyses are available on the figshare data repository (DOI: 10.6084/m9.figshare.25959061).
 

### 2024-06-10 Output/PLOSRound2/ResponsetoReviewers.txt
.docx response to reviewers

@@
 https://journals.plos.org/plosone/s/recommended-repositories.
+
+All data and annotated code for data import, transformations and analyses are
+available at are available on the figshare data repository (DOI: 10.6084/m9.figshare.25959061).
 
@@
 
--Thank you for comment. We added text to discuss the main conclusions of this study.
+-Thank you for your comment. We added text to discuss the main conclusions of this study.
 
@@
 This likely reflects an annotation assignment issue because the RUBISCO proteins are highly conserved, so assignments to strains or clades of Prochlorococcus may be ambiguous.
-We edited the figure #2 to add 'jitter' offsets up to 15% of full axes scales, to visualize over-laid data points. 
+We edited figure #2 to add 'jitter' offsets up to 15% of full axes scales, to visualize over-laid data points. 
 We edited the text in the revised manuscript to reflect the limitation of the annotation process as it pertains to the highly conserved RUBISCO complex: "Though present and expressed in the genome of MED4 [65], the absence of proteins annotated as RUBISCO complex for clade HLI, compared to annotated detections of RUBISCO across the other three clades, suggests limitations in the annotation process assigning highly conserved protein sequences to clades."
-Line: 394 to 398
+Lines: 394 to 398
 
@@
 
-- Thank you for this suggestion. We combined the growth rate figure with the GAM model for each strain to faciliate comparisons.
+- Thank you for this suggestion. We combined the growth rate figure with the GAM model for each strain to facilitate comparisons.
 
@@
 -Thank you for the comment.
-We added a new figure (Fig 10) of potential clade occupancy in temperate and equatoral seasonal and depth niches, in future warmed oceans under full oxygen or oxygen minimum zones.
+We added a new figure (Fig 10) of potential clade occupancy in temperate and equatorial seasonal and depth niches, in future warmed oceans under full oxygen or oxygen minimum zones.
 
@@
 -Thank you for this suggestion. 
-We edited the text:
-Lines: 454, 518, 586
+We edited the text at lines: 454, 518, 586
 
@@
 
--We edited the figure to clarify the fit lines:
+-We edited the figure to clarify the fit.
 
@@
 Thank you for noting that this needs further clarification. 
-We edited the paragraph for clarity in the revised manuscript adding: "While the accuracy of strain specific protein annotations are limited due to the high conservation of the target protein complexes, the two step approach of peptide-to-spectrum matching using deep paired metagenomics, does assign proteins at the level of clades."
+We edited the paragraph for clarity in the revised manuscript adding: "While the accuracy of strain specific protein annotations is limited due to the high conservation of the target protein complexes, the two step approach of peptide-to-spectrum matching using deep paired metagenomics, does assign proteins at the level of clades."
 Lines: 215-218
@@
 
-These issues are now discussed in relation to Figure PUR GROWTH, with a given amount of absorbed red light PUR provoking more growth than the equivalent absorbed blue light PUR.  In particular:
+These issues are now discussed in relation to figures 6 and S4, with a given amount of absorbed red light PUR provoking more growth than the equivalent absorbed blue light PUR.  In particular:
 
@@
 An analyses of mass spectrophotometric proteomic detection limits is beyond the scope of the paper.
-We however edited figures 2 and 7 to add 'jitter' offsets up to 15% of full axes scales, to visualize multiple previously over-laid data points.
+We, however, edited figures 2 and 7 to add 'jitter' offsets up to 15% of full axes scales, to visualize multiple previously over-laid data points.

### 2024-07-02 Code/Manuscript_O2.Rmd
FIxed gif. cap for fig10

@@
 "Light levels, photoperiods and spectral bands, potentially permissive for growth of *Prochlorococcus* clades are determined by the interactions of latitude, season and depth attenuation of light.",
-"**A.** Potential clade occupancies under Full Oxygen Zones (250 µM O~2~) are shown for 10-50 m and 100 m depths, in temperate vs.
+"**A.** Potential clade occupancies under hypothetical Full Oxygen Zones (250 µM O~2~) are indicated for 10-50 m and 100 m depths, in temperate vs.
 tropical regions, under depth-resolved photoperiods, approximating Winter Solstice, Equinox and Summer Solstice.
@@
 Clades LLII/III and LLIV are excluded from shallow depths by excessive light.",
-"**B.** Oxygen Minimum Zones (25 µM O~2~) drastically alter these potential occupancy patterns by excluding clade HLI from the temperate winter solstice at all depths, and by expanding the exploitation of higher light zones by Clade LLIV.",
+"**B.** Oxygen Minimum Zones (25 µM O~2~, not shown on map) would drastically alter these potential occupancy patterns by excluding clade HLI from the temperate winter solstice at all depths, and by expanding the exploitation of higher light zones by Clade LLIV.",
 "Potential clade occupancies for the southern temperate zone mirror the northern temperate zone occupancies.",

### 2024-07-02 Code/Plots_ProNicheMap.Rmd
FIxed maps and niches figure

@@
   guides(color = "none") +
-  labs(title = "Full Oxygen Zones") +
+  labs(title = "Temperate, Full Oxygen Zones") +
   theme_bw() +
@@
   guides(color = "none") +
+  labs(title = "Tropical, Full Oxygen Zones") +
   theme_bw() +
-  theme(plot.title = element_text(vjust = 10),
+  theme(plot.title = element_text(size = 30),
         panel.grid.minor = element_blank(),
@@
   guides(color = "none") +
-  labs(title = "Oxygen Minimum Zones") +
+  labs(title = "Temperate, Oxygen Minimum Zones") +
   theme_bw() +
@@
   guides(color = "none") +
+  labs(title = "Tropical, Oxygen Minimum Zones") +
   theme_bw() +
-  theme(plot.title = element_text(vjust = 10),
+  theme(plot.title = element_text(size = 30),
         panel.grid.minor = element_blank(),
@@
 
-RightSide <-ggarrange(BlankPanel,NichesFullO2North, NichesFullO2Equat, BlankPanel,  ncol = 1, nrow = 4, heights = c(1, 2,2,3))
+RightSide <-ggarrange(BlankPanel,NichesFullO2North, NichesFullO2Equat, BlankPanel,  ncol = 1, nrow = 4, heights = c(0.5, 2,2,3))
 FullO2 <- ggarrange(map, RightSide, ncol = 2, nrow = 1)
@@
 
-RightSide <-ggarrange(BlankPanel, NichesOMZNorth, NichesOMZEquat, BlankPanel,  ncol = 1, nrow = 4 , heights = c(1, 2,2,3))
+RightSide <-ggarrange(BlankPanel, NichesOMZNorth, NichesOMZEquat, BlankPanel,  ncol = 1, nrow = 4 , heights = c(0.5, 2,2,3))
 FullOMZ <- ggarrange(map, RightSide,  ncol = 2, nrow = 1)

### 2024-07-03 Code/Plots_ProNicheMap.Rmd
Fixed scale ratio of map in fig#10

@@
 PlotsOut <- file.path("..","Output", "Figures")
-PlotsOutPLOS <- file.path("..", "OutPut", "PLOSRound2")
+PlotsOutPLOS <- file.path("..", "OutPut", "PLOSRound3")
 ```
@@
   geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "gray50", fill = "gray50", size = 1.2) +
-   # geom_text(data=data_textA, aes(x=180, y=120, label=label), size=7, parse=TRUE) +
+   # geom_text(data="Latitude", aes(x=0, y=45, label=label), size=7, parse=TRUE) +
   scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
   coord_cartesian(ylim = c(-90, 120)) +
-  coord_fixed(ratio = 2, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
+  coord_fixed(ratio = 1, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
   labs(y = "Latitude", x = "Longitude") +
@@
 
-RightSide <-ggarrange(BlankPanel,NichesFullO2North, NichesFullO2Equat, BlankPanel,  ncol = 1, nrow = 4, heights = c(0.5, 2,2,3))
-FullO2 <- ggarrange(map, RightSide, ncol = 2, nrow = 1)
+RightSide <-ggarrange(BlankPanel,NichesFullO2North, NichesFullO2Equat, BlankPanel,  ncol = 1, nrow = 4, heights = c(1, 2,2,2))
+FullO2 <- ggarrange(map, RightSide, ncol = 2, nrow = 1, widths = c(1, 1))
 FullO2
 
-RightSide <-ggarrange(BlankPanel, NichesOMZNorth, NichesOMZEquat, BlankPanel,  ncol = 1, nrow = 4 , heights = c(0.5, 2,2,3))
-FullOMZ <- ggarrange(map, RightSide,  ncol = 2, nrow = 1)
+RightSide <-ggarrange(BlankPanel, NichesOMZNorth, NichesOMZEquat, BlankPanel,  ncol = 1, nrow = 4 , heights = c(1, 2,2,2))
+FullOMZ <- ggarrange(map, RightSide,  ncol = 2, nrow = 1, widths = c(1, 1))
 FullOMZ
@@
 
-ggsave(file = file.path(PlotsOut, paste("NichesMap",".png",sep = "")), plot = NichesMap, height=18, width= 20,  dpi = 300, limitsize = TRUE,  bg='white')
+ggsave(file = file.path(PlotsOut, paste("NichesMap",".png",sep = "")), plot = NichesMap, height=16, width= 25,  dpi = 300, limitsize = TRUE,  bg='white')
 
-ggsave(file = file.path(PlotsOutPLOS, "Fig10.tiff"), plot = NichesMap, device = NULL, scale = 1, height=55, width= 55, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE, bg='white')
+ggsave(file = file.path(PlotsOutPLOS, "Fig10.tiff"), plot = NichesMap, device = NULL, scale = 1, height=40, width= 70, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE, bg='white')
 ```

### 2024-07-04 Code/Manuscript_O2.Rmd
Created Round 3 folder for PLOSONE submission

@@
 "Light levels, photoperiods and spectral bands, potentially permissive for growth of *Prochlorococcus* clades are determined by the interactions of latitude, season and depth attenuation of light.",
-"**A.** Potential clade occupancies under hypothetical Full Oxygen Zones (250 µM O~2~) are indicated for 10-50 m and 100 m depths, in temperate vs.
+"**A.** Potential clade occupancies under hypothetical Full Oxygen Zones (250 µM O~2~, not shown on map) are shown for 10-50 m and 100 m depths, in temperate vs.
 tropical regions, under depth-resolved photoperiods, approximating Winter Solstice, Equinox and Summer Solstice.

### 2024-07-04 Code/Manuscript_O2.Rmd
Files for PlosOne submission

@@
 
-All data and annotated code for data import, transformations and analyses are available on the figshare data repository (DOI: 10.6084/m9.figshare.25959061).
+All data and annotated code for data import, transformations and analyses are available on the figshare data repository (https://doi.org/10.6084/m9.figshare.25959061.v1).
 

### 2024-07-11 Code/Manuscript_O2.Rmd
1 citation did not knit properly, used , instead of ;

@@
 homologous to *Synechocystis* *sll*1463, possibly involved in PSI
-biogenesis [@mannInvolvementFtsHHomologue2000; @krynickaFtsH4ProteaseControls2022,
+biogenesis [@mannInvolvementFtsHHomologue2000; @krynickaFtsH4ProteaseControls2022;
 @konikCyanobacterialFtsH4Protease2024]. FtsH3 expression did not

### 2024-07-11 Code/Manuscript_O2.Rmd
minor edits

@@
 low light clade. Growth rate patterns
-under red light and 250 µM O~2~were similar, although somewhat faster. The disjunct regions of the GAM plot results from variable growth success of SS120 under 250 µM O~2~. In contrast,
+under red light and 250 µM O~2~ were similar, although somewhat faster. The disjunct regions of the GAM plot results from variable growth success of SS120 under 250 µM O~2~. In contrast,
 under 25 µM O~2~ and a photoperiod of 8 h SS120 exploited all blue peak
@@
                        "Protein detections (circles) are plotted vs.
-O~2~ (µM) (x-axis) and depth (m) (y-axis) at sample origin with a 15% offset to seperate protein detections occupying the same origin.",
+O~2~ (µM) (x-axis) and depth (m) (y-axis) at sample origin with a 15% offset to separate protein detections occupying the same origin.",
                        "Rows separate data annotated as from *Prochlorococcus marinus* clades: HLI (including *P.

### 2025-07-14 Code/Plots_Genome.Rmd
line 177 `Km_mM_min = min(Km_mM, na.rm = TRUE)`

@@
 
+```{r, ProchlorococcusEnzymeKmsTrim, fig.cap = ProchlorococcusEnzymeKmsTrim_cap, fig.width = 20, fig.height = 10}
+
+ProchlorococcusEnzymeKmsTrim_cap <- glue("**Comparison of log~10~(K~m~ for O~2~ in mM) vs.genes encoding O~2~ utilizing enzymes in *Prochlorococcus***, faceted by their respective strains.",
+                                     "Symbol color corresponds to number of genes encoding O~2~ utilizing enzymes.",
+                                     "Symbol shape corresponds to whether the K~m~ was measured in the respective enzyme, or inferred from the K~m~ of a similar enzyme.",
+                                     "Black vertical line corresponds to the range of K~m~ for O~2~.",
+                                     "Vertical translucent bars correspond to concentrations of O~2~ in which *Prochlorococcus* strains were grown.",
+                                     "K~m~ values were obtained from other organisms, excluding Ribulose bisphosphate carboxylase.",
+                                     "Symbol absence means no sequences were detected in the genome."
+                                     )
+
+(ProchlorococcusEnzymeKmsTrim <- MergedData %>%
+  filter(!is.na(Gene_count),
+         Genus == "Prochlorococcus",
+         # Strain %in% c("CCMP1986", "MIT9313"),
+         Strain %in% c("CCMP1375", "CCMP1986", "MIT9313", "NATL2A"),
+         !is.na(Estimated),
+         Taxa == "Prokaryote",
+         EnzymeName %in% c("decaprenylphospho-beta-D-ribofuranose 2-dehydrogenase", "ubiquinol oxidase (non-electrogenic)","acireductone dioxygenase (Ni2+-requiring)", "pyridoxal 5'-phosphate synthase", "(S)-2-hydroxy-acid oxidase", "bacterial non-heme ferritin")) %>%
+  mutate(StrainLabel = case_when(Strain == "CCMP1375" ~ "SS120",
+                                 Strain == "CCMP1986" ~ "MED4",
+                                 Strain == "MIT9313" ~ "MIT9313",
+                                 Strain == "NATL2A" ~ "NATL2A")) %>%
+  mutate(StrainLabel = factor(StrainLabel, levels = c("MED4", "NATL2A", "SS120", "MIT9313"))) %>%
+  group_by(EC) %>%
+  mutate(#Km_mM_min = min(Km_mM, na.rm = TRUE), 
+         Km_mM_max = max(Km_mM, na.rm = TRUE),
+         Gene_count = as.character(Gene_count)) %>%
+  # mutate(Km_mM = case_when(Genus == "Prochlorococcus" & EC == "4.1.1.39" ~ 1.4,
+  #                          TRUE ~ Km_mM),
+  #        Km_mM_min = case_when(Genus == "Prochlorococcus" & EC == "4.1.1.39" ~ 1.4,
+  #                          TRUE ~ Km_mM_min),
+  #        Km_mM_max = case_when(Genus == "Prochlorococcus" & EC == "4.1.1.39" ~ 1.4,
+  #                          TRUE ~ Km_mM_max)) %>% 
+  # mutate(Km_mM = case_when(EnzymeName == "Flavodiiron (Flv1a/3a)" ~ 10/1000,
+  #                          TRUE ~ Km_mM)) %>% 
+  ungroup() %>% 
+    mutate(EnzymeName_bold = case_when(EnzymeName %in% c("(S)-2-hydroxy-acid oxidase", "ubiquinol oxidase (non-electrogenic)", "pyridoxal 5'-phosphate synthase") ~ glue("<b>{EnzymeName}</b>"),
+                                     TRUE ~ EnzymeName)) %>% 
+  ggplot() +
+  geom_errorbar(aes(x = reorder(EnzymeName_bold, Km_mM * 1000), ymin = Km_mM_min* 1000, ymax = Km_mM_max* 1000)) +
+  # geom_ribbon(aes(ymin = (5e-4), ymax =  (5e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "blue") +
+  # geom_ribbon(aes(ymax = (5e-2), ymin =  (5e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "green") +
+  # geom_ribbon(aes(ymax = (280e-3), ymin =  (230e-3), x = as.numeric(reorder(EnzymeName, Km_mM))), alpha = 0.3, fill = "#FF0000") +
+  annotate(geom = "rect", ymin = (5e-4 * 1000), ymax =  (5e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "blue") +
+  annotate(geom = "rect", ymax = (5e-2 * 1000), ymin =  (5e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "green") +
+  annotate(geom = "rect", ymax = (280e-3 * 1000), ymin =  (230e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "#FF0000") +
+  geom_point(aes(x = reorder(EnzymeName_bold, Km_mM* 1000), y = (Km_mM* 1000), shape = as.logical(Estimated), size = Gene_count), stroke = 1) +
+  geom_vline(aes(xintercept = reorder(EnzymeName_bold, Km_mM* 1000)), size = 2,  data = . %>% filter(is.na(Km_mM)), linetype = "solid") +
+  geom_text(aes(x = 18.5, y = 2.5, label = "[O2] ≈ 2.5 µM"), color = "blue", size = 6) +
+  geom_text(aes(x = 18.5, y = 25, label = "[O2] ≈ 25 µM"), color = "darkgreen", size = 6) +
+  geom_text(aes(x = 18.5, y = 250, label = "[O2] ≈ 250 µM"), color = "#FF0000", size = 6) +
+  # geom_hline(yintercept = (5e-4), linetype = "dotted") +
+  # geom_hline(yintercept = (5e-3), linetype = "dotted") +
+  # geom_hline(yintercept = (5e-3), linetype = "dotted", color = "brown") +
+  # geom_hline(yintercept = (5e-2), linetype = "dotted", color = "brown") +
+  # geom_hline(yintercept = (230e-3), linetype = "dotted", color = "red") +
+  # geom_hline(yintercept = (290e-3), linetype = "dotted", color = "red") +
+  # scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
+  ggh4x::facet_nested(rows = vars(StrainLabel)) +
+  theme_bw() +
+  ggpubr::rotate_x_text(angle = 80) +
+  scale_shape_manual(values = c(19,8), labels = c("FALSE" = "Measured", "TRUE" = "Inferred")) +
+  scale_color_brewer(palette="Dark2") +
+  labs(# title = ~K[m] ~O[2] ~  "for *Prochlorococcus* Enzymes using Oxygen", # "Estimates of Affinities of *Prochlorococcus* Enzymes for Oxygen" # "Affinities for Phytoplankton Enzymes for Oxygen", 
+       x = "Enzyme name",
+       y = ~K[m] ~O[2] ~"(µM)",
+       size = "Gene count",
+       shape = ""~K[m]) +
+  scale_y_continuous(trans=scales::pseudo_log_trans(base = 10),
+                     breaks=c(1, 10, 100, 1000, 10000, 100000)) + #,labels = expression(10^0, 10^1, 10^2, 10^3, 10^4, 10^5)
+  guides(shape = guide_legend(override.aes = list(size=5))) +
+   theme(axis.title = element_text(size = 45, color = "black"),
+         axis.title.x = element_text(vjust=8),
+         # axis.title.y = element_blank(),
+         title = element_text(size = 30),
+         # axis.text.x = element_text(size = 30, color = "black"),
+        axis.text.y = element_text(size = 20, color = "black"),
+        axis.text.x = ggtext::element_markdown(size = 30, color = "black"),
+        strip.text = element_text(size = 30),
+        legend.key.size = unit(2, 'cm'), #change legend key size
+        # legend.key.height = unit(2, 'cm'), #change legend key height
+        # legend.key.width = unit(1, 'cm'), #change legend key width
+        legend.title =  element_text(size = 30),  #change legend title font size
+        legend.text = element_text(size = 30))
+  )   #change legend text font size
+
+```
+
 ```{r read ProchlorococcusGenomeDNARepairData}

### 2025-07-14 Code/Plots_Genome.Rmd
working on trimmed O2 genome figure

@@
 
-(ProchlorococcusEnzymeKmsTrim <- MergedData %>%
+ProchlorococcusEnzymeKmsTrim <- MergedData %>%
   filter(!is.na(Gene_count),
@@
   group_by(EC) %>%
-  mutate(#Km_mM_min = min(Km_mM, na.rm = TRUE), 
+  mutate(Km_mM_min = min(Km_mM, na.rm = TRUE), 
          Km_mM_max = max(Km_mM, na.rm = TRUE),
@@
     mutate(EnzymeName_bold = case_when(EnzymeName %in% c("(S)-2-hydroxy-acid oxidase", "ubiquinol oxidase (non-electrogenic)", "pyridoxal 5'-phosphate synthase") ~ glue("<b>{EnzymeName}</b>"),
-                                     TRUE ~ EnzymeName)) %>% 
+                                     TRUE ~ EnzymeName))
+
+ ProchlorococcusEnzymeKmsTrim %>% 
   ggplot() +
@@
   geom_vline(aes(xintercept = reorder(EnzymeName_bold, Km_mM* 1000)), size = 2,  data = . %>% filter(is.na(Km_mM)), linetype = "solid") +
-  geom_text(aes(x = 18.5, y = 2.5, label = "[O2] ≈ 2.5 µM"), color = "blue", size = 6) +
-  geom_text(aes(x = 18.5, y = 25, label = "[O2] ≈ 25 µM"), color = "darkgreen", size = 6) +
-  geom_text(aes(x = 18.5, y = 250, label = "[O2] ≈ 250 µM"), color = "#FF0000", size = 6) +
-  # geom_hline(yintercept = (5e-4), linetype = "dotted") +
-  # geom_hline(yintercept = (5e-3), linetype = "dotted") +
-  # geom_hline(yintercept = (5e-3), linetype = "dotted", color = "brown") +
-  # geom_hline(yintercept = (5e-2), linetype = "dotted", color = "brown") +
-  # geom_hline(yintercept = (230e-3), linetype = "dotted", color = "red") +
-  # geom_hline(yintercept = (290e-3), linetype = "dotted", color = "red") +
-  # scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
+  geom_text(aes(x = 7, y = 2.5, label = "[O2] ≈ 2.5 µM"), color = "blue", size = 6) +
+  geom_text(aes(x = 7, y = 25, label = "[O2] ≈ 25 µM"), color = "darkgreen", size = 6) +
+  geom_text(aes(x = 7, y = 250, label = "[O2] ≈ 250 µM"), color = "#FF0000", size = 6) +
   ggh4x::facet_nested(rows = vars(StrainLabel)) +
@@
   scale_y_continuous(trans=scales::pseudo_log_trans(base = 10),
-                     breaks=c(1, 10, 100, 1000, 10000, 100000)) + #,labels = expression(10^0, 10^1, 10^2, 10^3, 10^4, 10^5)
+                     breaks=c(1, 10, 100, 1000, 10000, 100000)) +
    guides(shape = guide_legend(override.aes = list(size=5))) +
@@
          axis.title.x = element_text(vjust=8),
-         # axis.title.y = element_blank(),
          title = element_text(size = 30),
-         # axis.text.x = element_text(size = 30, color = "black"),
         axis.text.y = element_text(size = 20, color = "black"),
@@
         legend.key.size = unit(2, 'cm'), #change legend key size
-        # legend.key.height = unit(2, 'cm'), #change legend key height
-        # legend.key.width = unit(1, 'cm'), #change legend key width
         legend.title =  element_text(size = 30),  #change legend title font size
         legend.text = element_text(size = 30))
-  )   #change legend text font size
+     #change legend text font size
 

### 2025-07-14 Code/Plots_Genome.Rmd
trimmed version of Prochlorococcus O2 genome plot

--- 2024-06-09 Code/Plots_Genome.Rmd
@@
 
+```{r ProchlorococcusEnzymeKmsTrim, fig.cap=ProchlorococcusEnzymeKmsTrim_cap, fig.height=10, fig.width=20, message=FALSE, warning=FALSE}
+
+ProchlorococcusEnzymeKmsTrim_cap <- glue("**Comparison of log~10~(K~m~ for O~2~ in mM) vs.genes encoding O~2~ utilizing enzymes in *Prochlorococcus***, faceted by their respective strains.",
+                                     "Symbol color corresponds to number of genes encoding O~2~ utilizing enzymes.",
+                                     "Symbol shape corresponds to whether the K~m~ was measured in the respective enzyme, or inferred from the K~m~ of a similar enzyme.",
+                                     "Black vertical line corresponds to the range of K~m~ for O~2~.",
+                                     "Vertical translucent bars correspond to concentrations of O~2~ in which *Prochlorococcus* strains were grown.",
+                                     "K~m~ values were obtained from other organisms, excluding Ribulose bisphosphate carboxylase.",
+                                     "Symbol absence means no sequences were detected in the genome."
+                                     )
+
+ProchlorococcusEnzymeKmsTrim <- MergedData %>%
+  filter(!is.na(Gene_count),
+         Genus == "Prochlorococcus",
+         # Strain %in% c("CCMP1986", "MIT9313"),
+         Strain %in% c("CCMP1986", "MIT9313"),
+         !is.na(Estimated),
+         Taxa == "Prokaryote",
+         EnzymeName %in% c("decaprenylphospho-beta-D-ribofuranose 2-dehydrogenase", "ubiquinol oxidase (non-electrogenic)","acireductone dioxygenase (Ni2+-requiring)", "(S)-2-hydroxy-acid oxidase", "bacterial non-heme ferritin")) %>%
+  mutate(StrainLabel = case_when(Strain == "CCMP1375" ~ "SS120",
+                                 Strain == "CCMP1986" ~ "MED4",
+                                 Strain == "MIT9313" ~ "MIT9313",
+                                 Strain == "NATL2A" ~ "NATL2A")) %>%
+  mutate(StrainLabel = factor(StrainLabel, levels = c("MED4", "NATL2A", "SS120", "MIT9313"))) %>%
+  group_by(EC) %>%
+  mutate(Km_mM_min = min(Km_mM, na.rm = TRUE), 
+         Km_mM_max = max(Km_mM, na.rm = TRUE),
+         Gene_count = as.character(Gene_count)) %>%
+  # mutate(Km_mM = case_when(Genus == "Prochlorococcus" & EC == "4.1.1.39" ~ 1.4,
+  #                          TRUE ~ Km_mM),
+  #        Km_mM_min = case_when(Genus == "Prochlorococcus" & EC == "4.1.1.39" ~ 1.4,
+  #                          TRUE ~ Km_mM_min),
+  #        Km_mM_max = case_when(Genus == "Prochlorococcus" & EC == "4.1.1.39" ~ 1.4,
+  #                          TRUE ~ Km_mM_max)) %>% 
+  # mutate(Km_mM = case_when(EnzymeName == "Flavodiiron (Flv1a/3a)" ~ 10/1000,
+  #                          TRUE ~ Km_mM)) %>% 
+  ungroup() %>% 
+    mutate(EnzymeName_bold = case_when(EnzymeName %in% c("(S)-2-hydroxy-acid oxidase", "ubiquinol oxidase (non-electrogenic)") ~ glue("<b>{EnzymeName}</b>"),
+                                     TRUE ~ EnzymeName))
+
+ (ProchlorococcusEnzymeKmsTrimPlot <- ProchlorococcusEnzymeKmsTrim %>%
+  ggplot() +
+  geom_errorbar(aes(x = reorder(EnzymeName_bold, Km_mM * 1000), ymin = Km_mM_min* 1000, ymax = Km_mM_max* 1000)) +
+  annotate(geom = "rect", ymin = (5e-4 * 1000), ymax =  (5e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "blue") +
+  annotate(geom = "rect", ymax = (5e-2 * 1000), ymin =  (5e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "green") +
+  annotate(geom = "rect", ymax = (280e-3 * 1000), ymin =  (230e-3 * 1000), xmin = -Inf, xmax = Inf, alpha = 0.3, fill = "#FF0000") +
+  geom_point(aes(x = reorder(EnzymeName_bold, Km_mM* 1000), y = (Km_mM* 1000), shape = as.logical(Estimated)), stroke = 1) +
+  geom_vline(aes(xintercept = reorder(EnzymeName_bold, Km_mM* 1000)), size = 2,  data = . %>% filter(is.na(Km_mM)), linetype = "solid") +
+  geom_text(aes(x = 5.3, y = 2.5, label = "≈2.5 µM [O2]"), color = "blue", size = 6) +
+  geom_text(aes(x = 5.3, y = 25, label = "≈25 µM [O2]"), color = "darkgreen", size = 6) +
+  geom_text(aes(x = 5.3, y = 250, label = "≈250 µM [O2]"), color = "#FF0000", size = 6) +
+  ggh4x::facet_nested(rows = vars(StrainLabel)) +
+  theme_bw() +
+   ggpubr::rotate_x_text(angle = 80) + 
+   scale_shape_manual(values = c(19,8), labels = c("FALSE" = "Measured", "TRUE" = "Inferred")) +
+  scale_color_brewer(palette="Dark2") +
+   labs(# title = ~K[m] ~O[2] ~  "for *Prochlorococcus* Enzymes using Oxygen", # "Estimates of Affinities of *Prochlorococcus* Enzymes for Oxygen" # "Affinities for Phytoplankton Enzymes for Oxygen", 
+       x = "Enzyme name",
+       y = ~K[m] ~O[2] ~"(µM)",
+       size = "Gene count",
+       shape = ""~K[m]) +
+  scale_y_continuous(trans=scales::pseudo_log_trans(base = 10),
+                     breaks=c(1, 10, 100, 1000, 10000, 100000)) +
+   guides(shape = guide_legend(override.aes = list(size=5))) +
+   theme(axis.title = element_text(size = 30, color = "black"),
+          axis.title.x = element_text(vjust=8),
+          title = element_text(size = 30),
+         axis.text.y = element_text(size = 20, color = "black"),
+         axis.text.x = ggtext::element_markdown(size = 18, color = "black"),
+         strip.text = element_text(size = 30),
+         legend.key.size = unit(2, 'cm'), #change legend key size
+        legend.title =  element_text(size = 30),  #change legend title font size
+        legend.text = element_text(size = 30))
+ )
+     #change legend text font size
+
+```
+
+```{r, ProchlorococcusEnzymeKmsTrimPlot ggsave, include = FALSE} 
+ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKmsTrim.png"), plot = ProchlorococcusEnzymeKmsTrimPlot, height = 12, width = 17)
+```
+
 ```{r read ProchlorococcusGenomeDNARepairData}
